### 2018-01-24 Analyses.Rmd
First commit

---
title: "MP MetaAnalysis"
author: "Christina Bergmann"
output: 
  pdf_document:
    toc: true
---
```{r Setup, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)

### Load libraries
library(tidyverse)
library(metafor)
library(meta)
library(pwr)
library(knitr)
library(wesanderson)

```

#Preparation

Read in data and tidy up dataset

```{r ReadIn,  echo = FALSE}
#Get the data
source("scripts/calculateES.R")

```

```{r Preprocess, echo = FALSE}

db_ET <- db_ET %>%
  mutate(age.C = (mean_age_1-mean(mean_age_1, na.rm=TRUE))/30.44) %>%
  filter(mean_age_months < 31)

db_ET$collapse <- paste(db_ET$study_ID, db_ET$expt_num, db_ET$same_infant, sep = "_")

#Split into correct and MP database

db_ET_correct <- db_ET[db_ET$is_correct=="1",]
db_ET_MP <- db_ET[db_ET$is_mp=="1",]

#collapse over nonindependent MP rows for a *general* MP effect

collapse_rows <- function(db){
  db$collapse <- paste(db$study_ID, db$expt_num, db$same_infant, sep = "_")

  for(independent in unique(db$collapse)){
    if(length(db[db$collapse==independent])>1){
      sub = db[db$collapse==independent, ]
      sub$d_calc <- median(sub$d_calc)
      sub$d_var_calc <- median(sub$d_var_calc)
      sub$g_calc <- median(sub$g_calc)
      sub$g_var_calc <- median(sub$g_var_calc)
      sub$corr_imputed <- median(sub$corr_imputed)
      db <- db[!(db$collapse==independent),]
      db <- rbind(db, sub[1,])
    }
  }
  return(db)
}

#Because we do hierarchical models, we do not collapse. This is better when looking at an interaction effect.

#db_ET_correct = collapse_rows(db_ET_correct)

#db_ET_MP = collapse_rows(db_ET_MP)

#remove outliers, for now we have none, though
db_ET_MP$nooutlier = ifelse(db_ET_MP$g_calc > mean(db_ET_MP$g_calc, na.rm = TRUE) + 3*sd(db_ET_MP$g_calc, na.rm = TRUE) 
                         | db_ET_MP$g_calc < mean(db_ET_MP$g_calc, na.rm = TRUE) - 3*sd(db_ET_MP$g_calc, na.rm = TRUE),FALSE, TRUE)
db_ET_MP = db_ET_MP[db_ET_MP$nooutlier,]

db_ET_correct$nooutlier = ifelse(db_ET_correct$g_calc > mean(db_ET_correct$g_calc, na.rm = TRUE) + 3*sd(db_ET_correct$g_calc, na.rm = TRUE) 
                         | db_ET_correct$g_calc < mean(db_ET_correct$g_calc, na.rm = TRUE) - 3*sd(db_ET_correct$g_calc, na.rm = TRUE),FALSE, TRUE)
db_ET_correct = db_ET_correct[db_ET_correct$nooutlier,]

# make sure that both correct and mispronounced conditions are considered in descriptives

db_ET_correct$condition <- 1
db_ET_MP$condition <- 0

dat <- bind_rows(db_ET_correct, db_ET_MP)

# need data set of unique short cite by expt_num
# in order to calculate total number of infants

# need data set of unique short cite by condition

sum_dat <- dat[!duplicated(dat[c("short_cite", "same_infant")]),]
```

# Descriptive data

The database contains data from `r length(unique(dat$short_cite))` papers consisting of data from `r sum(sum_dat$n_1)` infants. In the tables below, we provide more descriptive information.

The next table shows what type of publications were included in our meta-analysis
```{r DescriptivesPubtype, echo = FALSE}

pub_info <- dat %>%
  group_by(publication_status) %>%
  summarize(n_unique = n_distinct(short_cite), count = n())

kable(pub_info)

```
The next table shows what type of publications were included in our meta-analysis
```{r DescriptivesPubtype, echo = FALSE}

pub_info <- dat %>%
  group_by(publication_status) %>%
  summarize(n_unique = n_distinct(short_cite), count = n())

kable(pub_info)

```

The table below shows based on which data we calculated effect sizes.

```{r DescriptivesES, echo = FALSE}
#how did we calculate effect sizes?

es_info <- dat %>%
  group_by(es_method) %>%
  summarize(n_unique = n_distinct(short_cite), count = n())

kable(es_info)
#table(dat$es_method, dat$short_cite)
# only missing from:
# Bailey & Plunkett (2002) <- crazy old data
# Renner (2017) <- just finished phd
# Tamasi (2016) <- standard deviations are wrong
#table(db_ET_MP$es_method)

```

We also have different ways of comparison of the time-course data, as the next table shows.
```{r DescriptivesComparison, echo = FALSE}
db_ET_correct$within_measure_descriptive <- ifelse(db_ET_correct$within_measure == "post",
 "post-naming phase compared with chance (=50%)",
ifelse(db_ET_correct$within_measure == "pre_post", "post-naming compared to pre-naming phase", "post-pre difference score compared with chance (=0)"))

comparison_info <- db_ET_correct %>%
  group_by(within_measure_descriptive) %>%
  summarize(n_unique = n_distinct(short_cite), count = n())

kable(comparison_info)
#table(db_ET_MP$es_method)
```

## Analysis time window

Where possible, we noted the time window for analysis. First, let's look at the offset (in milliseconds) after the start of the word, i.e. the begin of a give analysis window for a naming effect

```{r TimeWindowOffset}
offset_info <- db_ET_correct %>%
  group_by(offset) %>%
  summarize(count = n())

kable(offset_info)

```

Next we look at duration (in seconds) of the post naming window, here,too, we see a lot of heterogeneity.

```{r TimeWindowduration}
duration_info <- db_ET_correct %>%
  group_by(post_nam_dur) %>%
  summarize(count = n())

kable(duration_info)

```

In summary, we see little consistency in analysis methods of comparable studies looking at naming and mispronunciation effects.

## Early Ages
Even the youngest ages in the database (less than 1 year) show mispronunciation sensitivity

```{r YoungAge, echo = FALSE}
youngest <- subset(dat, min_age_1 < 365)

unique(youngest$short_cite)
youngest$cond_lab <- ifelse(youngest$condition == 1, "correct", "misp")
ggplot(youngest, aes(x=cond_lab, y = g_calc, color = cond_lab)) + geom_boxplot()

```

# Meta-Analysis

## Correct object identification effect

```{r MAcorrect}

rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ collapse | short_cite)

summary(rma_correct)

rma_correct_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = ~ collapse | short_cite)

summary(rma_correct_age)

```

## Mispronunciation object identification effect

```{r MAMP}

rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ collapse | short_cite)

summary(rma_MP)

rma_MP_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = ~ collapse | short_cite)

summary(rma_MP_age)
```

## Mispronunciation effect
```{r MPEffect}
db_ET_correct$condition <- 1
db_ET_MP$condition <- 0

dat <- bind_rows(db_ET_correct, db_ET_MP)

rma_MPeffect <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = ~ collapse | short_cite)

summary(rma_MPeffect)

rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ collapse | short_cite)

summary(rma_MPeffect_1)

rma_MPeffect_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = ~ collapse | short_cite)

summary(rma_MPeffect_age)

```

### Language effect

Followup: Per condition (correct or MP) the interaction with age

```{r LanguageEffectAnalyses}
dat$condition_label = ifelse(dat$condition==1, "correct", "MP")

dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
                           dat$native_lang=="German", "Germanic",
                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*lang_family, data = dat, random = ~ collapse | short_cite)
summary(rma_lang_interaction)
```

### Type of distractor

```{r DistractorType}

rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)

summary(rma_DistractorAge)

```

#### Subset to same age range

```{r DistractorTypeAge}

min_age <- min(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
max_age <- max(dat[dat$object_pair=="familiar_novel",]$mean_age_1)

dat_age= dat%>%
  filter(mean_age_1>min_age&mean_age_1<max_age)

rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)

summary(rma_DistractorAgeS)

```

### Distractor Overlap

```{r DistractorOverlap}

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)

summary(rma_DistractorOverlap)

```

## Number of features

```{r NFeatures}

db_ET_MPf = db_ET_MP %>%
  filter(n_feature != "1-3" & n_feature != "1-2" & n_feature != "2-3")

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature), data = db_ET_MPf, random = ~collapse | short_cite)

summary(rma_NFeatures)

rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C, data = db_ET_MPf, random = ~collapse | short_cite)

summary(rma_NFeaturesAge)
```

### Interaction with condition

```{r NFeaturesCondition}

dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*condition, data = dat_f, random = ~collapse | short_cite)

summary(rma_NFeatures)

rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C*condition, data = dat_f, random = ~collapse | short_cite)

summary(rma_NFeaturesAge)
```

## MP location

```{r Location}
#table(db_ET_MP$mispron_location)

db_ET_MPl = db_ET_MP %>%
  filter(mispron_location == "onset"  | mispron_location == "medial")

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_Location <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_MPl, random = ~collapse | short_cite)

summary(rma_Location)

rma_LocationAge <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*age.C, data = db_ET_MPl, random = ~collapse | short_cite)

summary(rma_LocationAge)
```

## MP type: Vowel, consonant, or tone?

```{r MPtype}
db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )

rma_TypeFeaturesMP <- rma.mv(g_calc, g_var_calc, mods = ~type_feature, data = db_MP_type, random = ~collapse | short_cite)

summary(rma_TypeFeaturesMP)

rma_TypeFeaturesMPAge <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)

summary(rma_TypeFeaturesMPAge)
```

### Interaction with condition
```{r MPtypeCondition}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
                type_feature == "tone")
dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))

rma_TypeFeatures <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*condition, data = dat_type, random = ~collapse | short_cite)

summary(rma_TypeFeatures)

rma_TypeFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*age.C*condition, data = dat_type, random = ~collapse | short_cite)

summary(rma_TypeFeaturesAge)
```

### Interaction with language
```{r MPtypeLanguage}
#dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
#                type_feature == "tone")

dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")

dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))

dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French", 
                                "Romanic", "Sino-Tibetian"))

dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")

rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family, data = dat_type_sub, random = ~collapse | short_cite)

summary(rma_TypeFeatures_Lang)
```

### Interaction with condition and language
```{r MPtypeLanguageCondition}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")# |
                #type_feature == "tone")
dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))

dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French", 
                                "Romanic", "Sino-Tibetian"))

dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
dat_type_sub$lang_family <- as.factor(dat_type_sub$lang_family)

rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family*condition, data = dat_type_sub, random = ~collapse | short_cite)

summary(rma_TypeFeatures_Lang)

```
## Correlation MP effect and vocabulary

First, let's take a look at which vocabulary data we have available.

```{r VocabularyData}
vocab_info <- db_ET_correct %>%
  mutate(has_vocab = ifelse(!is.na(r_comprehension), "comprehension", 
                            ifelse(!is.na(r_production), "production", "none"))) %>%
  group_by(has_vocab) %>%
  summarize(count = n())

kable(vocab_info)

```
We have 17 correlations, roughly evenly divided between comprehension and production data. There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we should both analyze this data separately and see whether it makes sense in a joint analysis.

```{r ComprehensionMeta}
#we're relying on the library meta function metacor
compr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_comprehension) & r_comprehension > -1)

metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
```

```{r ProductionMeta}
#we're relying on the library meta function metacor
prodr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_production) & r_production < 1)

metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
```

# Plotting
## Mispronunciation Effect by Age (color)
```{r PlotMPEffect}

# Color Blind palette:
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g),show.legend=FALSE) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_colour_manual(values=cbPalette)+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

min(dat$mean_age_1/30.44)
max(dat$mean_age_1/30.44)

#ggsave("figures/AgeEffect_log.jpg", p,height= 7,width= 6)

  jpeg(filename = "figures/AgeEffect_log.jpg", 
       width = 600, height = 400, units = "px")

  p

  dev.off()

```
## Mispronunciation Effect by Age (bw)
```{r PlotMPEffect_BW}

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape=condition_label, color=condition_label),
             show.legend=FALSE) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_color_grey()+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_BW.jpg", p,height= 3,width= 6)

```

## MP type: Consonant, Vowel, or Tone?
```{r PlotCVEffect}

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = type_feature),show.legend=FALSE) + 
  facet_grid(.~type_feature)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_CV.jpg", p)
```

## Language Family by MP type: Consonant, Vowel, or Tone?
```{r PlotCVEffect_Lang}

p <- ggplot(dat, aes(type_feature, g_calc, color = type_feature)) + 
  geom_boxplot() + 
  facet_grid(lang_family~condition_label)+
  #geom_line(y= 0, linetype="dotted") + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Language Family") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/LangFamily_CV.jpg", p)
```

## Number of Features
```{r PlotFeatEffect}

#dat_f <- subset(dat, n_feature == "0" | n_feature == "1" | n_feature == "2" | n_feature == "3")

p <- ggplot(dat_f, aes(mean_age_1/30.44, g_calc, color = n_feature)) + 
  geom_point(aes(size = weights_g, shape = n_feature),show.legend=FALSE) + 
  #facet_grid(.~type_feature)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_feat.jpg", p)

```

## Position of Mispronunciation
```{r PlotPositionEffect}

dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial" |
                mispron_location == "offset")

p <- ggplot(dat.p, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = mispron_location),show.legend=FALSE) + 
  facet_grid(.~mispron_location)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_position.jpg", p)

```

## Distractor Familiarity
```{r PlotDistFamEffect}

dat$condition_label = ifelse(dat$condition==1, "correct", "MP")
dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = dist_code),show.legend=FALSE) + 
  facet_grid(.~dist_code)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_color_manual(values=wes_palette(name="Darjeeling"))+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_distractor_fam.jpg", p)

```

## Distractor Familiarity (w/o age)
```{r PlotDistFamEffect_NoAge}

dat$condition_label = ifelse(dat$condition==1, "correct", "MP")
dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")

p <- ggplot(dat, aes(dist_code, g_calc, color = condition_label)) + 
  geom_boxplot() + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_color_manual(values=wes_palette(name="Darjeeling"))+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Distractor Familiarity") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/Distractor_fam_log.jpg", p)

```

## Distractor Familiarity (w/o age, subset to age range)
```{r PlotDistFamEffect_NoAge_AgeMatch}

min_age<-min(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
max_age <- max(dat[dat$object_pair=="familiar_novel",]$mean_age_1)

dat_age= dat%>%
  filter(mean_age_1>min_age&mean_age_1<max_age)

dat_age$condition_label = ifelse(dat_age$condition==1, "correct", "MP")
dat_age$dist_code <- ifelse(dat_age$object_pair == "familiar_familiar", "familiar", "unfamiliar")

p <- ggplot(dat_age, aes(dist_code, g_calc, color = condition_label)) + 
  geom_boxplot() + 
  #geom_line(y= 0, linetype="dotted") + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_color_manual(values=wes_palette(name="Darjeeling"))+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Distractor Familiarity") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeMatch_Distractor_fam_log.jpg", p)

```

## Overlap between distractor and target

```{r PlotDistOverlapEffect}

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = distractor_overlap),show.legend=FALSE) + 
  facet_grid(.~distractor_overlap)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_distractor_overlap.jpg", p)

```

## Language Family
```{r PlotLanguageEffect}

dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
                           dat$native_lang=="German", "Germanic",
                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = lang_family),show.legend=FALSE) + 
  facet_grid(.~lang_family)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_language.jpg", p)

```

### 2018-01-24 scripts/Meta_Analysis.R

@@ -1,0 +1,147 @@
+#### Read in data and clean up ####
+
+# This script was adapted from Christina Bergmann's script, which was
+# written to create meta-analytic models to examine behavior mispronunciation sensitivity
+# (segmenting artificial mini-languages based on statistics). 
+# Original Author: Christina Bergmann
+# chbergma'at'gmail.com
+# Current Author: Katie Von Holzen
+# last modified: January 17, 2018
+
+library(tidyverse)
+library(metafor)
+library(meta)
+library(pwr)
+library(knitr)
+library(wesanderson)
+
+#### Data read in ####
+
+#For now focusing on the eye tracking data
+source("scripts/calculateES.R")
+
+#### Preprocessing ####
+db_ET <- db_ET %>%
+  mutate(age.C = (mean_age_1-mean(mean_age_1, na.rm=TRUE))/30.44) %>%
+  filter(mean_age_months < 31)
+
+
+db_ET$collapse <- paste(db_ET$study_ID, db_ET$expt_num, db_ET$same_infant, sep = "_")
+
+#Split into correct and MP database
+
+db_ET_correct <- db_ET[db_ET$is_correct=="1",]
+db_ET_MP <- db_ET[db_ET$is_mp=="1",]
+
+#collapse over nonindependent MP rows for a *general* MP effect
+
+
+collapse_rows <- function(db){
+  db$collapse <- paste(db$study_ID, db$expt_num, db$same_infant, sep = "_")
+  
+  for(independent in unique(db$collapse)){
+    if(length(db[db$collapse==independent])>1){
+      sub = db[db$collapse==independent, ]
+      sub$d_calc <- median(sub$d_calc)
+      sub$d_var_calc <- median(sub$d_var_calc)
+      sub$g_calc <- median(sub$g_calc)
+      sub$g_var_calc <- median(sub$g_var_calc)
+      sub$corr_imputed <- median(sub$corr_imputed)
+      db <- db[!(db$collapse==independent),]
+      db <- rbind(db, sub[1,])
+    }
+  }
+  return(db)
+}
+
+
+#db_ET_correct = collapse_rows(db_ET_correct)
+
+#db_ET_MP = collapse_rows(db_ET_MP)
+
[…]

### 2018-01-24 scripts/Publication_Bias.R

@@ -1,0 +1,424 @@
+#### Bias and Replicability Analyses ####
+
+# This script was adapted from Christina Bergmann's script, which was
+# written to analyze bias and replicability in statistical learning studies 
+# (segmenting artificial mini-languages based on statistics). 
+# Original Author: Christina Bergmann
+# chbergma'at'gmail.com
+# last modified: January 22, 2018
+#   by Katie Von Holzen
+#### Load libraries ####
+
+library(metafor)
+library(pwr)
+
+#### get data ####
+
+source("scripts/Meta_Analysis.R")
+
+db_mpe <- dat
+rm(dat)
+
+#### get p curve code ####
+
+#source("scripts/p_curve_app_code.R")
+
+
+#### Publication Bias ####
+
+# Publication bias can become visible in funnel plot asymmetry. 
+# Metafor comes with several options to check this, I chose ranktest and regtest
+
+# this is the model of the mispronunciation effect, without age
+ranktest(rma_MPeffect)
+
+# correct object identification
+ranktest(rma_correct)
+
+# mispronounced object identification
+ranktest(rma_MP)
+
+
+# from models where we removed g > 2
+# correct object
+ranktest(rma_co2)
+
+# mispronounced object
+ranktest(rma_mp2)
+
+#No longer possible with switch from rma to rma.mv
+#regtest(rma_all)
+#regtest(rma_DR)
+
+# All datasets seem to have significant asymmetry 
+# See below for funnel plots
+
+#### Export Data for p-curve ####
+#The very pedestrian way because reasons. 
+
+db <- db_ET_correct
+#db <- db_ET_MP
+#db <- db_mpe
+
+
+# save text strings to paste into p-curve app
+# http://www.p-curve.com/app4/
+
+#sink("p_curve_app/p_curve_co.txt")
+#sink("p_curve_app/p_curve_mp.txt")
+
+for(line in 1:length(db$n_1)){
+  if(!is.na(db[line,]$t)){
+    newline = paste("t(", db[line,]$n_1-1, ")=",db[line,]$t, sep = "")
+    #write(newline, file = textfile, append = TRUE)
+    cat(newline)
+    cat("\n")
+    #write(newline, file = textfile, append = TRUE)    
+  }
+}
+
+#sink()
+
+#pcurve_app("p_curve_mp.txt","p_curve_app")
+#pcurve_app("p_curve_co.txt","p_curve_app")
+
+#### Power ####
+
+db_test <- db_ET_correct
[…]

### 2018-01-24 scripts/ReadIn.R

@@ -1,0 +1,15 @@
+#### Read in data and clean up ####
+
+# This script was written to pre-process MetaLab compatible spreadsheets on behavioral mispronunciation studies 
+# Author: Christina Bergmann
+# chbergma'at'gmail.com
+# last modified: Feb 2, 2017
+
+#### Data read in ####
+
+#For now focusing on the eye tracking data
+db_ET = read.csv("data/MA_ET.csv")
+
+#### Some cleanup ####
+
+#To be determined

### 2018-01-24 scripts/calculateES.R

@@ -1,0 +1,114 @@
+#### Calculate Effect Sizes ####
+
+# This script was written to calculate effect sizes in MetaLab compatible spreadsheets 
+# chbergma'at'gmail.com
+# last modified: Feb 1, 2017
+
+#### Load libraries ####
+
+#None needed right now
+
+#### Get data ####
+
+source("scripts/ReadIn.R")
+
+#### calculate paired ES based on available data ####
+
+# The formulae here are based on those in MetaLab
+# Link https://github.com/langcog/metalab/blob/master/scripts/compute_es.R
+
+# We only have 41 correlations. From those we take the variance, but set the mean to .5 (.16 seems awfully low) 
+median_corr = .5
+var_corr = .12 
+
+set.seed(111)
+db_ET$corr_imputed = rnorm(length(db_ET$n_1), mean = median_corr, sd = var_corr)
+
+# Initiate the additional columns for d and d_var
+
+db_ET$d_calc <- NA
+db_ET$d_var_calc <- NA
+db_ET$es_method <- "missing"
+
+db_ET$corr = ifelse(is.na(db_ET$corr), db_ET$corr_imputed, db_ET$corr)
+
+#Correlations are never perfect and cannot be higher than 1 or lower than 0, so fixing some possible imputation issues first. 
+db_ET$corr = ifelse(db_ET$corr>.8, .8, db_ET$corr)
+db_ET$corr = ifelse(db_ET$corr<0, .05, db_ET$corr)
+
+#Now compute effect sizes based on the data we have, row by row. MetaLab solves this a bit differently, here I opt for readability.
+
+
+#db_ET <- subset(db_ET, short_cite == "Tamasi (2016)")
+
+
+for(line in 1:length(db_ET$n_1)){
+  if(db_ET[line,]$participant_design == "within_two"){
+    if (complete.cases(db_ET[line,]$x_1, db_ET[line,]$x_2, db_ET[line,]$SD_1, db_ET[line,]$SD_2)) {
+      # Lipsey & Wilson, 3.14
+      pooled_SD <- sqrt((db_ET[line,]$SD_1 ^ 2 + db_ET[line,]$SD_2 ^ 2) / 2)
[…]

### 2018-01-24 Analyses.Rmd
commit dataset, figures, write-ups

@@
 
-#Because we do hierarchical models, we do not collapse. This is better when looking at an interaction effect.
-
 #db_ET_correct = collapse_rows(db_ET_correct)
@@
 
-The next table shows what type of publications were included in our meta-analysis
-```{r DescriptivesPubtype, echo = FALSE}
-
-pub_info <- dat %>%
-  group_by(publication_status) %>%
-  summarize(n_unique = n_distinct(short_cite), count = n())
-
-kable(pub_info)
-
-```
 The next table shows what type of publications were included in our meta-analysis
@@
 ```{r LanguageEffectAnalyses}
-dat$condition_label = ifelse(dat$condition==1, "correct", "MP")
+dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")
 
@@
 ```
+
 We have 17 correlations, roughly evenly divided between comprehension and production data.
@@
 # Plotting
+```{r PlotAPATheme}
+#Themes and plot
+apatheme=theme_bw()+
+  theme(#panel.grid.major=element_blank(),
+    #panel.grid.minor=element_blank(),
+    #panel.border=element_blank(),
+    axis.line=element_line(),
+    text=element_text(family='Times', size=25))
+
+```
 ## Mispronunciation Effect by Age (color)
 ```{r PlotMPEffect}
+
+dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
 
@@
   scale_colour_manual(values=cbPalette)+
-  theme_bw()+
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
+  apatheme +
+  theme(legend.title = element_blank(),
         legend.position = "bottom") + 
@@
   ylab("Effect size Hedges' g")
+
 p

### 2018-01-24 write-ups/PaperDraft.Rmd
commit dataset, figures, write-ups

---
title             : "The development of infants' responses to mispronunciations - a Meta-Analysis"
shorttitle        : "Mispronunciation Meta-Analysis"

author: 
  - name          : "Katie Von Holzen"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "45, rue des Saints-Peres, 75006 Paris, France"
    email         : "katie.m.vonholzen@gmail.com"
  - name          : "Christina Bergmann"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "Laboratoire Psychologie de la Perception, Université Paris Descartes"
  - id            : "2"
    institution   : "LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University"

author_note: >
  Complete departmental affiliations for each author (note the indentation, if you start a new paragraph).

  Enter author note here.

abstract: >
  Enter abstract here (note the indentation, if you start a new paragraph).

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

```{r include = FALSE}
library("papaja")
```

outline christina:

Main question: How do reactions to mispronunciations change over age, because we (1) know that infants notice MPs and (2) that their processing and representations mature.

Theory one: Infants develop more precise word- and sound-level representations. (Who would claim that for example?)  
Prediction: They become MORE sensitive to MPs.

Theory two: Infants can resolve MPs better as they get older, because they realize that the competitor is not the target. (kv: this comes from the way we test mispronunciation? familiar vs unfamiliar distractor? maybe that can be a thread throughout the paper) 
Prediction: They become LESS sensitive to MPs and this should be most pronounced with familiar objects as competitors.  (yes)

Theory three: Infants don't change how they process words over the time range covered, they just become more efficient information processors overall.  
Prediction: The effect sizes go up as infants mature but the MP effect (difference between correct and mp) remains constant.

Thus, a meta-analysis offers unique insights into theoretically crucial questions of how infants process words and phonemes.

```{r Notes as comments}

# moving notes from Christina here
#[Christina: Katie, I am adding the next sentences to set up a general analysis of age effects, but correct anything that is wrong]
#However, whether infants' sensitivity to mispronunciations increases or decreases over time is yet unknown [?????] and can serve to distinguish competing models of early language acquisition. If infants start out as overly cautous and specific language processors, their mispronunciation sensitivity should be larger at younger ages, as only later in life infants learn to contend with variability in their input [Add some references to Cathy Best and others here? Cite a concrete model? Not sure who says what any more].

#Alternatively, infants may start out with lexical representatins that are overly broad and might then reconsider and refine those representations as language experience accumulates [add references here too, I think that's sort of what Primir says, right?]. In this latter case, one would predict an increase in mispronunciation sensitivity as infants mature and become more competent language users.

#A third possibility is that infants' overall language processing becomes more efficient, but that their sensitivity to mispronunciations does not change -- accross infancy and toddlerhood, mispronunciations would thus be detected and lead to less looks at a target than correct pronunciations, but the effect would not change.

```

As infants develop into toddlers during their second and third years they learn new words in earnest while simultaneously refining their knowledge about the sounds that make up these words. Before children can correctly pronounce a word, they already show evidence of sensitivity to slight variations in the phonological form of that word. This *mispronunciation sensitivity* reflects the specificity with which infants represent the phonological information of familiar words and are sensitive to changes in this phonological information. As infants continue to develop into expert language users, their language processing matures and becomes more efficient. In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonetic details that differentiate words in their native language. In this paper, we aggregate and analyze the almost 20 years of literature investigating mispronunciation sensitivity in infants in an attempt to uncover the characteristics and trajectory of its development.

  At the turn of the millenia, infant langauge acquisition researchers had established that during their first year of life, infants are sensitive to changes in the phonetic detail of newly segmented words (Jusczyk & Aslin, 1995) and learned minimal pairs (Stager & Werker, 1997). Furthermore, when presented with image pairs, children fixate on one image upon hearing its label (Swingley & Fernald, 1998; Fernald, Pinto, Swingley, Weinberg, & McRoberts, 1998). Swingley and Aslin (2000) were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English were presented with pairs of images (e.g. baby, dog) and their eye movements to each image were coded offline. On "correct" trials, children heard the correct label for one of the images (e.g. baby). On "mispronounced" trials, children heard a mispronounced label of one of the images (e.g. vaby). Mean proportion of fixation to the target image (here: a baby) was calculated for both correct and mispronounced trials by dividing the target looking time by the sum of total looking time to both target and a distractor (proportion of target looking or PTL). Mean fixations in correct trials were significantly greater than that of mispronounced trials, although looks to the target were significantly greater than chance in both types of trials. We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance as *recognition*. Swingley and Aslin (2000) concluded that already before the second birthday, children represent words with sufficient detail to be sensitive to mispronunciations.

  The study of Swingley and Aslin (2000) as well as subsequent studies examining mispronunciation sensitivity address two complementary concepts in early phonological development: *phonological consistency* and *phonological distinctiveness*. Phonological consistency is the ability to accept phonological variation across different instances of a word, as long as the variation does not compromise the overall identity of the word. For example, different speakers - particularly across genders and accents - produce the same word with notable acoustic variation, although the word remains the same. In contrast, phonological distinctiveness describes the ability to differentiate between words that are phonologically similar, such as bad/bed or cat/rat. To successfully recognize words, infants must therefore simultaneously use both phonological consistency and distinctiveness to determine where phonological variation is appropriate and where it violates a word's identity.

  In the current study, we focus on infants' ability to correctly apply the principles of phonological distinctiveness and consistency by using a meta-analytic approach to investigate mispronunciation sensitivity. Considering that infants are sensitive to mispronunciations and that, in general, their processing matures with development, we examine the shape of mispronunciation sensitivity development. [Ch: Adding this] There are three distinct possibilities how mispronunciation sensitivity might change over developmen, which are respectively predicted by theoretical accounts and supported by single studies. By aggregating all available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants. Before we outline the meta-analytical approach in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.

  Young infants may begin cautiously in their approach to word recognition, rejecting any phonological variation in familiar words and only later learning to accept appropriate variability. According to the Perceptual Attunement account, this describes a shift away from specific native phonetic patterns to a more mature understanding of the abstract phonological structure of words (Best 1994, 1995). This shift is predicted to coincide with the vocabulary spurt around 18 months, and is therefore related to vocabulary growth. In this case, we would expect the size of mispronunciation sensitivity to be larger at younger ages and decrease as the child matures and learn more words, although children continue to detect mispronuncaitions.
Indeed, young infants are less likely than older infants to demonstrate recognition of familiar words (Best, Tyler, Gooding, Orlando, & Quann, 2009; Mulak, Best, & Tyler, 2013) or learn new words (Schmale, Hollich, & Seidl, 2011) from accented speakers.

  In contrast, young infants may instead begin with phonologically broad representations for familiar words and only refine their representations as language experience accumulates. PRIMIR (Processing Rich Information from Multidimensional Interactive Representations; Curtin & Werker, 2007; Werker & Curtin, 2005; Curtin, Byers-Heinlein, & Werker, 2011) describes the development of phonemic categories emerging as the number of word form-meaning linkages increase. Vocabulary growth, therefore, promotes more detailed phonological representations in familiar words. Following this account, we may predict an increase in mispronunciation sensitivity as infants mature and add more words to their growing lexicon.

  Finally, sensitivity to mispronunciation may not be modulated by development at all. Infants' overall language processing becomes more efficient, but their sensitivity to mispronunciations may not change. Accross infancy and toddlerhood, mispronunciations would thus be detected and lead to less looks at a target than correct pronunciations, but the size of this effect would not change, nor be related to vocabulary size.

  Research following the study by Swingley and Aslin (2000) has extended mispronunciation sensitivity to infants as young as 12 months (Mani & Plunkett, 2010), indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations. Regarding the change in mispronunciation sensitivity over development, however, only a handful of studies have compared more than one age group on the same mispronunciation task. For example [Ch: not sure what this is an example of], Swingley and Aslin (2000) tested infants from 18 to 23 months.  They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation effect) did not. This suggests that as children develop, they are more likely to look at the target in the presence of a mispronounced label and that age is not related to mispronunciation sensitivity. A similar response pattern has been found for British English learning infants aged between 18 and 24 months (Bailey and Plunkett, 2002) as well as younger French-learning infants at 12 and 17 months (Zesiger, Lozeron, Levy, & Frauenfelder, 2012). These studies award support to the prediction that mispronunciation sensitivity does not change with development.

  In contrast, other studies have found evidence for a change in mispronunciation sensitivity as children develop. More precisely, the difference in target looking for correct and mispronounced trials is smaller in younger infants and grows as infants develop. Mani and Plunkett (2007) tested 15-, 18-, and 24-month-olds learning British English; although all three groups were sensitive to mispronunciations, 15-month-olds showed a less robust sensitivity. An increase in sensitivity to mispronunciations has also been found from 20 to 24 months (van der Feest & Fikkert, 2015) and 18 to 15 months [Ch: ???? 15 to 18???] (Altvater Mackensen et al., 2013) in Dutch infants, as well as German infants from 22 to 25 months (Altvater-Mackensen, 2010). Furthermore, van der Feest and Fikkert (2015) found that sensitivity to specific kinds of mispronunciations develop at different ages depending on language infants are learning. In other words, the native language constrains which *kinds* of mispronunciations infants are sensitive to first, and that as infants develop, they become sensitive to other mispronunciations. These studies award support to the prediction that mispronunciation sensitivity improves with development.

  Finally, one study has found evidence for infants to become *less* sensitive to mispronunciations as children develop. Mani and Plunkett (2011) presented 18- and 24-month-olds with mispronunciations varying in the number of features changed (see below for a discussion of the role of features). 18-month-olds were sensitive to mispronunciations, regardless of the number of features changed. 24-month-olds, in contrast, fixated the target image equally for both correct and 1-feature mispronounced trials, although they were sensitive to larger mispronunciations. In other words, for 1-feature mispronunciations at least, sensitivity decreased from 18 to 24 months, providing support to the prediction that mispronunciation sensitivity may decrease with development.

  Why would mispronunciation sensitivity change as infants develop, and would it increase or decrease? One hypothesis is related to vocabulary growth. Both the Perceptual Attunement (Best, 1994; 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005; Curtin, Byers-Heinlein, & Werker, 2011) accounts situate a change in mispronunciation sensitivity occuring along with an increase in vocabulary size, particulary with the vocabulary spurt at about 18 months. Knowing more words helps infants shift their focus to the relevant [Ch: changed this from ingredients] phonetic dimensions needed for word recognition. On the one hand, a smaller lexicon does not require full specification to differentiate between words; as more phonologically similar words are learned, so does the need to have fully detailed representations for those words (Charles-Luce & Luce, 1995). On the other hand, a growing vocabulary is also related to more experience or familiarity with words, which may sharpen the detail of their representation (Barton, 1980).

  Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have found no relationship [Ch: Tricky, might also be a false negative or a small relationship, maybe reformulate: have concluded that there is no relationship] (Swingley & Aslin 2000; 2002; Bailey & Plunkett, 2002; Zesiger, Lozeron, Levy, & Frauenfelder, 2012; Swingley, 2009; Ballem & Plunkett, 2005; Mani & Plunkett, 2007; Mani, Coleman, & Plunkett, 2008). One notable exception comes from Mani and Plunkett (2010: keps and tups). Here, 12-month-old infants were divided into a low vocabulary and high vocabulary group based group median vocabulary size. High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations. Taken together, although recieving considerable support from theories of phono-lexical processing in language acquisition, there is very little evidence for a role of vocabulary size in mispronunciation sensitivity. In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to further disentangle the disconnect between theory and experimental results. [Ch: The disconnet is not quite clear to me right now.]

  Next to this core theoretically relevant investigation of the shape of mispronunciation sensitivity as infants develop, we can also address open questions regarding differences in experiment design and whether changes in procedure and stimuli tap into significantly different aspects of infants' ability to detect mispronunciations.

  In designing their mispronunciation stimuli, Swingley and Aslin (2000) chose consonant mispronunciations that were likely to confuse adults (Miller & Nicely, 1955). Subsequent research has settled on systematically modulating phonemic features to achieve mispronunciations of familiar words. The importance of controlling for the degree of phonological mismatch, as measured by number of features changed, is highlighted by studies that find graded sensitivity to both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes. In addition to number of features changed,  the type of feature changed may also play an important for mispronunciation sensitivity, as some acoustic characteristics provide more reliable cues than others (Mani, Coleman, & Plunkett, 2008; Mani & Plunkett, 2011).

  Although most research examining sensitivity to mispronunciations follows a similar design, there are some notable differences.  For example, Swingley and Aslin (2000) presented infants with pairs of familiar images, one serving as the labeled target and one as the unlabeled distractor. In contrast, White and Morgan (2008; see also Mani & Plunkett, 2011; Skorrupa et al., 2013; Swingley, 2016) presented infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects. By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied (Halberda, 2003; Markman, Wasow, & Hansen, 2003). Although mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared, the baseline preference for familiar compared to novel stimuli is thought to change as infants develop (Hunter & Ames, 1988).  In other words, in absentia of a label, infants may be more or less likely to fixate on an unfamiliar object. To account for inherent preferences to the target or distractor image, mispronunciation experiments typically compare the increase in fixations to the target image from a silent baseline to post-labeling or present the same yoked pairs of target and distractor images in in both a correct and mispronounced labelling context. [Ch: Do you want to bring up mutual exclusivity more explicitly here? I think it's fine the way you mention it, but we might say that this ability develops in the 2nd year as well - if I remember correctly.]

  Furthermore, when presenting infants with a familiar distractor image, some studies control from the phonological overlap between the labels for the target and distractor. For example, when examining sensitivity to a mispronunciation of the target word "dog", the vowel mispronunciation "dag" would be paired with a distractor image that shares onset overlap, such as "duck". This ensures that infants can not use the onset of the word to differentiate between the target and distractor images (Fernald, Swingely, & Pinto, 2001). Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change. The influence of distractor overlap also depends on the position of the mispronunciation in the word, which is typically at word onset, medial, or final positions. Models of spoken word processing place more or less importance on the position of a phoneme in a word.  The COHORT model (Marslen-Wilson & Zwisterlood, 1989) describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.  In contrast, the TRACE model (McClelland & Elman, 1986) describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset mispronunciations.

  TRACE has also been used to model infants' sensitivity to mispronunciation location (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth. In early language acquisition, infants typically know more consonant compared to vowel onset words. When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations. That position of mispronunciation, and by correlation whether it is a consonant or vowel mispronunciation, plays a role in mispronunciation sensitivity is related to the theory that consonants carry more weight in lexical processing (C-bias; see Nazzi, Poltrock, & Von Holzen, 2016 for a recent review). In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations. Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels. English-learning 12-, 15-, 18-, and 24-month-olds (Mani & Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds (Højen et al., unpublished) demonstrate similar sensitivity to consonant and vowel mispronunciations. One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronuciations (Swingley, 2016). The English-learning infants tested by Swingley were older than previous studies (mean age 28 months). In word learning, the C-bias has been found to develop later in English learning infants (Floccia, Nazzi, Delle Luche, Poltrock, & Goslin, 2014; Nazzi, Floccia, Moquet, & Butler, 2009). In the current meta-analysis, we attempt to synthesize studies examining sensitivity to consonant and vowel mispronunciations across different languages and ages to determine whether infants generally exhibit a C-bias in familiar word recognition.

  Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (perhaps refer to table of papers here? this will have language background information [Christina says yessssss - A table of all studies included like Alex does here might work: https://osf.io/z7xn3/]). Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare. In one series of studies, Ramon-Casas and colleagues (Ramon-Casas et al., 2009; Ramon-Casas & Bosch, 2010) tested both monolingual Spanish or Catalan and bilingual Spanish-Catalan on their detection of a vowel mispronunciation in familiar words. Both groups were sensitive to the vowel change when there was little overlap between the Spanish and Catalan labels of the familiar words (Ramon-Casas & Bosch, 2010), but only monolingual toddlers were sensitive to the vowel change in words that overlapped completely between Spanish and Catalan (Ramon-Casas et al., 2009). In this case, the comparison between Spanish and Catalan is relatively straightforward, as they share many phonologically overlapping words. This is not typically the case for most languages, where the phonology of the language differs, rendering equivalent mispronunciations in different languages almost impossible. By assessing evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach, it is possible to compare the development of mispronunciation effect across languages.

  [Ch: Should we explain here why the meta-analytic approach is useful and important? This might be necessary. Do you want todraft sth?]

## Methods

[Christina: Rewriting this section]

The present meta-analysis was conducted with maximal transparency and reproducibility in mind. To this end, we provide all data and analysis scripts and open our meta-analysis up for updates (Tsuji, Bergmann, & Cristia, 2015???). In addition, we follow the  Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials. (Moher, Liberati, Tetzlaff, Altman & PRISMAGroup, 2009).

# Study Selection

We first generated a list of potentially interesting items to be included in our meta-analysis by consulting our private collections for publications containing the search term "infant mispronunciation". This yielded 38 items. An additional 63 items were included based on recommendations from experts in the field. After removing duplicates, we screened the title and abstract to determine whether it met the following inclusion criteria: (1) original data was reported; (2) the item examined familiar word recognition; (3) infants studied were under 36-months-of-age; (4) the dependent variable was derived from proportion of looks to a target image in a eye tracked experiment. The final sample consisted of 20 journal articles, two proceedings papers, one thesis, and one unpublished report. We will refer to these 25 items collectively as papers. Table X provides an overview of all papers included in the present meta-analysis.

# Data Entry

The 25 published papers we identified as relevant were then coded with as much detail as possible and in compliance with guidelines set forward by MetaLab (Cite MEtalab). For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, experiment design and stimuli, and results. For the present analyses, we focus on the following characteristics:

1 Mean age reported per group of infants, in days;
2 Native language;
3 Size of mispronunciation, measured in features changed;
4 Type of mispronunciation: consonant, vowel, or tone;
5 Dependent variable: Either of the following, capturing infants' reaction to a given naming event (either mispronounced or correct): a) pre-post naming effect: calculated post - pre to give one value, typically compared to chance of 0 or to naming effect of another condition; b) pre-post: comparison of pre-naming and post-naming values; c) post = calculated for post-naming, typically compared to chance of 50%;
6 Condition: Were words mispronounced or not.

[Rewrite this section]
Each row in the database is a set of data that could give rise to an effect size. A given paper could appear in more than one row. This happened when there were multiple experiments, when there were multiple age groups within a single experiment, and when a unique group of infants was exposed to more than one condition (e.g. consonant versus vowel mispronunciations; Mani & Plunkett, 2007) – provided that results were broken down by experiment/infant group/condition in the source paper. In other words, we coded all outcomes that had been reported separately, and which had unique infant participants and/or method characteristics. For example, if the same infants were tested on two conditions and these were reported separately, then we entered two different rows (even though there was only one group of infants), with their methodological features and unique outcomes. To later unbias our data, we XXXX [Need to decide whether we want multilevel models or median data per participant] We will call each row a record. In all, there were 190 records.

## Data analysis

The effect size we report in the present paper is based on comparison of means, standardized by their variance. The most well-known effect size from this group is Cohen's *d* (Cite cohen). To correct for small sample sizes, we use as dependent variable Hedges' *g* instead of Cohen's *d*. In all cases we computed a first effect size for infants looks to target separated by condition (correct or mispronounced). A mispronunciation effect was then

For XXX papers, we 
[List here the different dependent variables]

[Add something about different analysis windows??]

metafor multilevel approach

# Results

## Descrivtives

Database statistics (N Papers, conditions, infants, age range covered)

## Preliminary Analyses

Funnel plot, pub bias

## Meta-analysis of correct and MP studies

separate models

interaction

plot

## Moderator analyses

- Competitor type (overlap vs. no overlap; familiar vs. unfamiliar)
- Position of mispronunciation
- Consonant vs. Vowel
- Language (English vs. ?)
- Number of features changed
- type of feature changed?  I doubt we have enough for it...
- Type of dv reported

# Discussion

\newpage

# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

### 2018-01-24 figures/example_plot.R

@@ -1,0 +1,73 @@
+setwd("~/Dropbox/MP_MA")
+
+library(ggplot2)
+library(wesanderson)
+library(reshape)
+library(doBy)
+
+std <- function(x) sd(x)/sqrt(length(x))
+
+correct <- rnorm(100, mean=0.730396429, sd=0.10471147)
+misp <- rnorm(100, mean=0.612614286, sd=0.093135265)
+
+cm <- data.frame(cbind(correct, misp))
+cm$sub <- seq(1, nrow(cm))
+
+dat.m2 <- melt(cm,
+               id=c(3),
+               measure=c(1:2),
+               variable="Measure", na.rm=T)
+names(dat.m2) <- c("sub", "condition", "PTL")
+
+
+box <- ggplot(data=dat.m2, aes(x=condition, y=PTL, fill=condition)) +
+  geom_boxplot()+
+  scale_fill_manual(values=wes_palette(name="Darjeeling"))+
+  theme_bw()+
+  annotate("segment", x = .67, xend = .67, y = .7, yend = .5, colour="black", size=1, arrow=arrow())+
+  annotate("segment", x = 1, xend = 2, y = .96, yend = .96, colour="black", size=1)+
+  annotate("text", x = .5, y = .63, parse = TRUE, label = "recognition",angle = 90, size = 10)+
+  annotate("text", x = 1.5, y = .99, parse = TRUE, label = "misp_sensitivity", size = 10)+
+  geom_hline(yintercept = .5)+
+  coord_cartesian(ylim = c(.35, 1))+
+  theme(text = element_text(size=30),
+        legend.position = "bottom",
+        legend.title = element_blank(),
+        axis.text.x = element_blank(),
+        axis.title.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank())+
+  ylab("Proportion of Target Looks")
+
+ggsave("Example_boxplot.jpg", box)
+
+d.p <- summaryBy(PTL~condition, data=dat.m2, FUN=c(mean, std))
+
+
+limits <- aes(ymax = PTL.mean+PTL.std, ymin=PTL.mean-PTL.std)
+dodge <- position_dodge(width=0.9)
+
+
+ex <- ggplot(data=d.p, aes(x=condition, y=PTL.mean, fill=condition)) +
+  geom_bar(stat = "identity", size=1.5, position=position_dodge(width = 0.9)) +
[…]

### 2018-01-25 Analyses.Rmd
update analyses and dataset for time window onset analysis

@@
 sum_dat <- dat[!duplicated(dat[c("short_cite", "same_infant")]),]
+time_wind_dat <- dat[!duplicated(dat[c("short_cite", "offset", "post_nam_dur")]),]
+
 ```
@@
 ```{r TimeWindowOffset}
-offset_info <- db_ET_correct %>%
+offset_info <- time_wind_dat %>%
   group_by(offset) %>%

### 2018-01-25 scripts/Publication_Bias.R

@@ -84,17 +84,17 @@ for(line in 1:length(db$n_1)){
 
 #### Power ####
 
-db_test <- db_ET_correct
+#db_test <- db_ET_correct
 #db_test <- db_ET_MP
-#db_test <- db_mpe
+db_test <- db_mpe
 
 # What is the average power to detect an effect (to be compared with p-curve estimate)
 d = rma.mv(g_calc, g_var_calc, data = db_test, random = ~ 1 | short_cite)$b[,1]
 # Let's try to extract the ES automagically later, for now I enter the value I had when running fir model by hand
 
-pwr.t.test(n = median(db_test$n_1, na.rm=TRUE), d = .95, sig.level = .05, type = "paired", alternative = "two.sided")
+pwr.t.test(n = median(db_test$n_1, na.rm=TRUE), d = .55, sig.level = .05, type = "paired", alternative = "two.sided")
 
-pwr.t.test(d = .228, sig.level = .05, type = "paired", power = .8, alternative = "two.sided")
+pwr.t.test(d = .55, sig.level = .05, type = "paired", power = .80, alternative = "two.sided")
 
 
 

### 2018-01-30 Analyses.Rmd
CogSci final prep; publication bias markdown file

@@
 time_wind_dat <- dat[!duplicated(dat[c("short_cite", "offset", "post_nam_dur")]),]
+distract_dat <- dat[!duplicated(dat[c("short_cite", "object_pair")]),]
 
@@
 #table(db_ET_MP$es_method)
+```
+
+This is a summary of the type of distractor used in an experiment
+
+```{r DescriptivesDISTRACT, echo = FALSE}
+#What kind of distractor was used?
+
+distr_info <- distract_dat %>%
+  group_by(object_pair) %>%
+  summarize(count = n())
+
+kable(distr_info)
+
 ```
@@
 
-```{r DistractorType}
+```{r DistractorTypeAge}
+
+rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
+
+summary(rma_Distractor)
+
+```
+
+## Type of Distractor with age
+```{r DistractorTypeAge}
 

### 2018-01-30 Publication_bias_analyses.Rmd
CogSci final prep; publication bias markdown file

---
title: "MP Publication Bias"
author: "originally Christina Bergmann, modified by Katie Von Holzen"
output: 
  pdf_document:
    toc: true
---
```{r Setup, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)

### Load libraries
library(metafor)
library(pwr)
library(ggplot2)
library(grid)
library(gridExtra)

```

#Preparation

Read in data and tidy up dataset

```{r ReadIn,  echo = FALSE}
#Get the data
source("scripts/Meta_Analysis.R")

# change name of mispronunciation sensitivity object
db_mpe <- dat
rm(dat)

```

# Funnel Plot Asymmetry
Use ranktest() to check for funnel plot asymmetry. All three tests show evidence of significant asymmetry.

```{r FunnelPlotAsymmetry, echo = FALSE}

# Publication bias can become visible in funnel plot asymmetry. 
# Metafor comes with several options to check this, I chose ranktest and regtest

# this is the model of the mispronunciation effect, without age
ranktest(rma_MPeffect)

# correct object identification
ranktest(rma_correct)

# mispronounced object identification
ranktest(rma_MP)

```

# Export data for p-curve

This step creates a text file that can be used in the p-curve app:
http://www.p-curve.com/app4/

These files can be found in "p_curve_app/"

for correct: p_curve_co.txt
for mispronounced: p_curve_mp.txt

Just copy and paste the .txt onto the website and voila!

NOTE: This will always append lines to the existing txt file, check for double writing!

```{r PcurveExport, echo = FALSE}

textfile_co = "p_curve_app/p_curve_co.txt"

for(line in 1:length(db_ET_correct$n_1)){
  if(!is.na(db_ET_correct[line,]$t)){
    newline = paste("t(", db_ET_correct[line,]$n_1-1, ")=",db_ET_correct[line,]$t, sep = "")
    write(newline, file = textfile_co, append = TRUE)
    #cat("\n")
    #write(newline, file = textfile, append = TRUE)    
  }
}

textfile_mp = "p_curve_app/p_curve_mp.txt"

for(line in 1:length(db_ET_MP$n_1)){
  if(!is.na(db_ET_MP[line,]$t)){
    newline = paste("t(", db_ET_MP[line,]$n_1-1, ")=",db_ET_MP[line,]$t, sep = "")
    write(newline, file = textfile_mp, append = TRUE)
    #cat("\n")
    #write(newline, file = textfile, append = TRUE)    
  }
}
```

# Calculate Power

# What is the power of the studies in the dataset?

```{r Power_exist, echo = FALSE}
d = rma.mv(g_calc, g_var_calc, data = db_mpe, random = ~ 1 | short_cite)$b[,1]

# estimate from mispronunciation sensitivity
mp_est <- coef(summary(rma_MPeffect))[2,]$estimate

pwr.t.test(n = median(db_mpe$n_1, na.rm=TRUE), d = mp_est, sig.level = .05, type = "paired", alternative = "two.sided")

```

# What is the average power to detect a mispronunciation sensitivity effect (to be compared with p-curve estimate)
```{r Power_plan, echo = FALSE}

# estimate from mispronunciation sensitivity
mp_est <- coef(summary(rma_MPeffect))[2,]$estimate

# one-sided t-test
pwr.t.test(d = mp_est, sig.level = .05, type = "paired", power = .80, alternative = "greater")

```

# Draw Funnel Plots

### Plots from Sakaluk, 2016
### https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/

## Funnel Plot for Correct Object Identification

```{r FunnelPrep, echo = FALSE}

#Themes and plot
apatheme=theme_bw()+
  theme(#panel.grid.major=element_blank(),
    #panel.grid.minor=element_blank(),
    #panel.border=element_blank(),
    axis.line=element_line(),
    text=element_text(family='Times', size=25),
    legend.position='none')

```

## Funnel Plot for Correct Object Identification

```{r FunnelCorrect, echo = FALSE}

#Rename a bunch of things for ease
dat_co = db_ET_correct
#dat_co=db_ET_correct
dat_co <-
  dat_co %>% 
  rename(cite = short_cite,
         yi = g_calc,
         vi = g_var_calc)

#Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order

dat_co <-
  dat_co %>% 
  select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>% 
  mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
  arrange(desc(yi))

#Get standard errors from variances
dat_co$se = sqrt(dat_co$vi)

#Calculate 95% CI values
dat_co$lowerci = (-1.96*dat_co$se)+dat_co$yi
dat_co$upperci = (1.96*dat_co$se)+dat_co$yi

#Store the meta-analytic estimate and its standard error from whatever model you run
#summary(rma_correct)
estimate_co = coef(summary(rma_correct))$estimate
se_co = coef(summary(rma_correct))$se

#Store a vector of values that spans the range from 0
#to the max value of impression (standard error) in your dataset.
#Make the increment (the final value) small enough (I choose 0.001)
#to ensure your whole range of data is captured
se.seq_co=seq(0, max(dat_co$se), 0.001)

#Now, compute vectors of the lower-limit and upper limit values for
#the 95% CI region, using the range of SE that you generated in the previous step, 
#and the stored value of your meta-analytic estimate.
ll95_co = estimate_co-(1.96*se.seq_co)
ul95_co = estimate_co+(1.96*se.seq_co)

#You can do this for a 99% CI region too
ll99_co = estimate_co-(3.29*se.seq_co)
ul99_co = estimate_co+(3.29*se.seq_co)

#And finally, do the same thing except now calculating the confidence interval
#for your meta-analytic estimate based on the stored value of its standard error
meanll95_co = estimate_co-(1.96*se_co)
meanul95_co = estimate_co+(1.96*se_co)

#Now, smash all of those calculated values into one data frame (called 'dfCI').
#You might get a warning about '...row names were found from a short variable...'
#You can ignore it.
dfCI_co = data.frame(ll95_co, ul95_co, ll99_co,
                  ul99_co, se.seq_co, estimate_co, meanll95_co, meanul95_co)

#Now we can actually make the funnel plot.
#Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
fp_co = ggplot(aes(x = se, y = yi), data = dat_co) +
  #Regression line for the FP asymmetry
  geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_co) +
  #Add your data-points to the scatterplot
  geom_point(size = 2.5, colour="black") +
  #
  #Give the x- and y- axes informative labels
  xlab('Standard Error') + ylab('Hedge\'s g')+
  # make sure both plots have same scale
  # still ylim because we haven't flipped yet
  #coord_cartesian(ylim = c(-1, 2.5))+
  #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
  #to the lower and upper limits of your 95% CI region
  #And dashed lines corresponding to your 99% CI region
  #Add lines corresponding to 0 and estimate
  geom_line(aes(x = se.seq_co, y = 0), linetype = 'solid', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = estimate_co), linetype = 'dashed', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = ll95_co), linetype = 'dotted', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = ul95_co), linetype = 'dotted', data = dfCI_co) +
  #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
  #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
  #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
  #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
  #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
  #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
  #at the top of the figure once we swap the x- and y-axes...
  scale_x_reverse()+
  #Specify the range and interval for the tick-marks of the y-axis (Zr);
  #Choose values that work for you based on your data
  #scale_y_continuous(breaks=seq(-.45,0.8,0.25))+
  #And now we flip the axes so that SE is on y- and Zr is on x-
  coord_flip()+
  #Finally, apply my APA-format theme (see code at end of post).
  #You could, alternatively, specify theme_bw() instead.
  apatheme

#Call the pretty funnel plot
fp_co +   ggtitle("Correct")
ggsave("figures/FunnelPlot_correct.pdf")
```

## Funnel Plot for Mispronunciation Object Identification

```{r FunnelMisp, echo = FALSE}

  #Rename a bunch of things for ease
dat_mp = db_ET_MP  
#dat_mp=db_ET_MP
  dat_mp <-
    dat_mp %>% 
    rename(cite = short_cite,
           yi = g_calc,
           vi = g_var_calc)

  #Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order

  dat_mp <-
    dat_mp %>% 
    select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>% 
    mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
    arrange(desc(yi))

  #Get standard errors from variances
  dat_mp$se = sqrt(dat_mp$vi)

  #Calculate 95% CI values
  dat_mp$lowerci = (-1.96*dat_mp$se)+dat_mp$yi
  dat_mp$upperci = (1.96*dat_mp$se)+dat_mp$yi

  #Store the meta-analytic estimate and its standard error from whatever model you run (substitute your own values)
  summary(rma_MP)
  estimate_mp = coef(summary(rma_MP))$estimate
  se_mp = coef(summary(rma_MP))$se

  #Store a vector of values that spans the range from 0
  #to the max value of impression (standard error) in your dataset.
  #Make the increment (the final value) small enough (I choose 0.001)
  #to ensure your whole range of data is captured
  se.seq_mp=seq(0, max(dat_mp$se), 0.001)

  #Now, compute vectors of the lower-limit and upper limit values for
  #the 95% CI region, using the range of SE that you generated in the previous step, 
  #and the stored value of your meta-analytic estimate.
  ll95_mp = estimate_mp-(1.96*se.seq_mp)
  ul95_mp = estimate_mp+(1.96*se.seq_mp)

  #You can do this for a 99% CI region too
  ll99_mp = estimate_mp-(3.29*se.seq_mp)
  ul99_mp = estimate_mp+(3.29*se.seq_mp)

  #And finally, do the same thing except now calculating the confidence interval
  #for your meta-analytic estimate based on the stored value of its standard error
  meanll95_mp = estimate_mp-(1.96*se_mp)
  meanul95_mp = estimate_mp+(1.96*se_mp)

  #Now, smash all of those calculated values into one data frame (called 'dfCI').
  #You might get a warning about '...row names were found from a short variable...'
  #You can ignore it.
  dfCI_mp = data.frame(ll95_mp, ul95_mp, ll99_mp,
                       ul99_mp, se.seq_mp, estimate_mp, meanll95_mp, meanul95_mp)

  #Now we can actually make the funnel plot.
  #Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
  fp_mp = ggplot(aes(x = se, y = yi), data = dat_mp) +
    #Regression line for the FP asymmetry
    geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_mp) +
    #Add your data-points to the scatterplot
    geom_point(size = 2.5, colour="black") +
    #
  #Give the x- and y- axes informative labels
  xlab('Standard Error') + ylab('Hedge\'s g')+
    # make sure both plots have same scale
    # still ylim because we haven't flipped yet
    #coord_cartesian(ylim = c(-1, 2.5))+
    #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
    #to the lower and upper limits of your 95% CI region
    #And dashed lines corresponding to your 99% CI region
    #Add lines corresponding to 0 and estimate
    geom_line(aes(x = se.seq_mp, y = 0), linetype = 'solid', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = estimate_mp), linetype = 'dashed', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = ll95_mp), linetype = 'dotted', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = ul95_mp), linetype = 'dotted', data = dfCI_mp) +
    #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
    #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
    #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
    #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
    #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
    #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
    #at the top of the figure once we swap the x- and y-axes...
    scale_x_reverse()+
    #Specify the range and interval for the tick-marks of the y-axis (Zr);
    #Choose values that work for you based on your data
    #scale_y_mpntinuous(breaks=seq(-.45,0.8,0.25))+
    #And now we flip the axes so that SE is on y- and Zr is on x-
    coord_flip()+
    #Finally, apply my APA-format theme (see code at end of post).
    #You could, alternatively, specify theme_bw() instead.
    apatheme

  #Call the pretty funnel plot
  fp_mp + ggtitle("Mispronunciation")
  ggsave("figures/FunnelPlot_misp.pdf")

```

## Combine both funnel plots for figure

```{r FunnelCombo, echo = FALSE}

  jpeg(filename = "figures/Funnel_Plots_Object_Identification.jpg", 
       width = 600, height = 400, units = "px")

  p <-   grid.arrange(fp_co, fp_mp, nrow = 1)
                      #top = textGrob("Object Identification", gp=gpar(fontsize=25)))
                      #top = "Object Identification")

  dev.off()

    grid.draw(p)

```

### 2018-02-05 Analyses.Rmd
Created CogSci markdown files for Analysis and Publication Bias
Markdown files have been uploaded to OSF CogSci Subproject.

@@
 distract_dat <- dat[!duplicated(dat[c("short_cite", "object_pair")]),]
+mix_co_mp <- dat[!duplicated(dat[c("short_cite", "word_correct_and_MP")]),]
 
@@
 kable(distr_info)
+
+```
+
+This is a summary of whether an experiment had both correct and mispronounced versions of the word in the experiment
+
+```{r DescriptivesCoMp, echo = FALSE}
+#What kind of distractor was used?
+
+mix_info <- mix_co_mp %>%
+  group_by(word_correct_and_MP) %>%
+  summarize(count = n())
+
+kable(mix_info)
 

### 2018-02-05 CogSci_Analyses.Rmd
Created CogSci markdown files for Analysis and Publication Bias
Markdown files have been uploaded to OSF CogSci Subproject.

--- 2018-01-30 Analyses.Rmd
@@
 ---
-title: "MP MetaAnalysis"
-author: "Christina Bergmann"
+title: "Mispronunciation MetaAnalysis for CogSci"
+author: "Christina Bergmann and Katie Von Holzen"
 output: 
@@
 ```{r Setup, echo = FALSE, warning=FALSE}
-knitr::opts_chunk$set(echo = TRUE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)
 
@@
 distract_dat <- dat[!duplicated(dat[c("short_cite", "object_pair")]),]
+mix_co_mp <- dat[!duplicated(dat[c("short_cite", "word_correct_and_MP")]),]
+vocab_dat <- dat[!duplicated(dat[c("short_cite")]),]
 
@@
 
-# Descriptive data
+# Systematic Study Collection
 
-The database contains data from `r length(unique(dat$short_cite))` papers consisting of data from `r sum(sum_dat$n_1)` infants. In the tables below, we provide more descriptive information.
+The database contains data from `r length(unique(dat$short_cite))` papers consisting of data from `r sum(sum_dat$n_1)` infants.
 
@@
   group_by(publication_status) %>%
-  summarize(n_unique = n_distinct(short_cite), count = n())
+  summarize(n_unique = n_distinct(short_cite))
 
@@
 
+# Effect Size Calculation
+
+## Type of Dependent Variable
+
+The table below summarized the type of dependent variable and subsequent comparison reported in each paper.
+
+```{r DescriptivesComparison, echo = FALSE}
+db_ET_correct$within_measure_descriptive <- ifelse(db_ET_correct$within_measure == "post",
+ "post-naming phase compared with chance (=50%)",
+ifelse(db_ET_correct$within_measure == "pre_post", "post-naming compared to pre-naming phase", "post-pre difference score compared with chance (=0)"))
+
+comparison_info <- db_ET_correct %>%
+  group_by(within_measure_descriptive) %>%
+  summarize(n_unique = n_distinct(short_cite))
+
+kable(comparison_info)
+#table(db_ET_MP$es_method)
+```
+
+## Data Used to Calculate Effect Sizes
+
 The table below shows based on which data we calculated effect sizes.
+If both raw means/standard deviations as well as t-values were available, we used raw means/standard deviations to calculate effect sizes.
 
@@
   group_by(es_method) %>%
-  summarize(n_unique = n_distinct(short_cite), count = n())
+  summarize(n_unique = n_distinct(short_cite))
 
@@
 
-We also have different ways of comparison of the time-course data, as the next table shows.
-```{r DescriptivesComparison, echo = FALSE}
-db_ET_correct$within_measure_descriptive <- ifelse(db_ET_correct$within_measure == "post",
- "post-naming phase compared with chance (=50%)",
-ifelse(db_ET_correct$within_measure == "pre_post", "post-naming compared to pre-naming phase", "post-pre difference score compared with chance (=0)"))
-
-comparison_info <- db_ET_correct %>%
-  group_by(within_measure_descriptive) %>%
-  summarize(n_unique = n_distinct(short_cite), count = n())
-
-kable(comparison_info)
-#table(db_ET_MP$es_method)
-```
-
-This is a summary of the type of distractor used in an experiment
-
-```{r DescriptivesDISTRACT, echo = FALSE}
-#What kind of distractor was used?
-
-distr_info <- distract_dat %>%
-  group_by(object_pair) %>%
-  summarize(count = n())
-
-kable(distr_info)
-
-```
-
-## Analysis time window
-
-Where possible, we noted the time window for analysis. First, let's look at the offset (in milliseconds) after the start of the word, i.e. the begin of a give analysis window for a naming effect
-
-```{r TimeWindowOffset}
-offset_info <- time_wind_dat %>%
-  group_by(offset) %>%
-  summarize(count = n())
-
-kable(offset_info)
-
-```
-
-Next we look at duration (in seconds) of the post naming window, here,too, we see a lot of heterogeneity.
-
-```{r TimeWindowduration}
-duration_info <- db_ET_correct %>%
-  group_by(post_nam_dur) %>%
-  summarize(count = n())
-
-kable(duration_info)
-
-```
-
-In summary, we see little consistency in analysis methods of comparable studies looking at naming and mispronunciation effects.
-
-## Early Ages
-Even the youngest ages in the database (less than 1 year) show mispronunciation sensitivity
-
-```{r YoungAge, echo = FALSE}
-youngest <- subset(dat, min_age_1 < 365)
-
-unique(youngest$short_cite)
-youngest$cond_lab <- ifelse(youngest$condition == 1, "correct", "misp")
-ggplot(youngest, aes(x=cond_lab, y = g_calc, color = cond_lab)) + geom_boxplot()
-
-```
-
 # Meta-Analysis
 
-## Correct object identification effect
+## Object Identification
+
+### Correct words
+
+Meta-analytic effect for correctly pronounced words in object identification.
 
@@
 
-rma_correct_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = ~ collapse | short_cite)
-
-summary(rma_correct_age)
-
 ```
 
-## Mispronunciation object identification effect
+### Mispronounced words
+
+Meta-analytic effect for mispronounced words in object identification.
 
@@
 
-rma_MP_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = ~ collapse | short_cite)
-
-summary(rma_MP_age)
 ```
 
-## Mispronunciation effect
+## Mispronunciation Sensitivity
+
+Meta-analytic effect for mispronunciation senstivity.
+
 ```{r MPEffect}
@@
 
-rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ collapse | short_cite)
+```
 
-summary(rma_MPeffect_1)
+## Age Moderator Effects
+
+### Object identification correct words
+
+Age moderator effects for object identification for correctly pronounced words.
+
+```{r MAcorrect_age}
+rma_correct_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = ~ collapse | short_cite)
+
+summary(rma_correct_age)
+
+```
+
+### Object identification mispronounced words
+
+Age moderator effects for object identification for mispronounced words.
+
+```{r MAMP_age}
+
+rma_MP_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = ~ collapse | short_cite)
+
+summary(rma_MP_age)
+```
+
+### Mispronunciation sensitivity
+
+Age moderator effects for mispronunciation sensitivity
+
+```{r MPEffect_age}
+db_ET_correct$condition <- 1
+db_ET_MP$condition <- 0
+
+dat <- bind_rows(db_ET_correct, db_ET_MP)
 
@@
 
-### Language effect
+# Plotting Mispronunciation Sensitivity by Age
 
-Followup: Per condition (correct or MP) the interaction with age
+This is the plot used in Figure 2. Effect sizes for correct pronunciations (yellow) and mispronunciations (blue) by participant age. Point size is inverse variance. The dashed line indicates zero.
 
-```{r LanguageEffectAnalyses}
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")
+```{r FunnelPrep, echo = FALSE}
 
-dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
-                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
-                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
-                           dat$native_lang=="German", "Germanic",
-                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
-                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
-                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))
-
-rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*lang_family, data = dat, random = ~ collapse | short_cite)
-summary(rma_lang_interaction)
-```
-
-### Type of distractor
-
-```{r DistractorTypeAge}
-
-rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
-
-summary(rma_Distractor)
-
-```
-
-## Type of Distractor with age
-```{r DistractorTypeAge}
-
-rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
-
-summary(rma_DistractorAge)
-
-```
-
-#### Subset to same age range
-
-```{r DistractorTypeAge}
-
-min_age <- min(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
-max_age <- max(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
-
-dat_age= dat%>%
-  filter(mean_age_1>min_age&mean_age_1<max_age)
-
-rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
-
-summary(rma_DistractorAgeS)
-
-```
-
-### Distractor Overlap
-
-```{r DistractorOverlap}
-
-rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
-
-summary(rma_DistractorOverlap)
-
-```
-
-## Number of features
-
-```{r NFeatures}
-
-db_ET_MPf = db_ET_MP %>%
-  filter(n_feature != "1-3" & n_feature != "1-2" & n_feature != "2-3")
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature), data = db_ET_MPf, random = ~collapse | short_cite)
-
-summary(rma_NFeatures)
-
-rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C, data = db_ET_MPf, random = ~collapse | short_cite)
-
-summary(rma_NFeaturesAge)
-```
-
-### Interaction with condition
-
-```{r NFeaturesCondition}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*condition, data = dat_f, random = ~collapse | short_cite)
-
-summary(rma_NFeatures)
-
-rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C*condition, data = dat_f, random = ~collapse | short_cite)
-
-summary(rma_NFeaturesAge)
-```
-
-## MP location
-
-```{r Location}
-#table(db_ET_MP$mispron_location)
-
-db_ET_MPl = db_ET_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_Location <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_MPl, random = ~collapse | short_cite)
-
-summary(rma_Location)
-
-rma_LocationAge <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
-
-summary(rma_LocationAge)
-```
-
-## MP type: Vowel, consonant, or tone?
-
-```{r MPtype}
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
-
-rma_TypeFeaturesMP <- rma.mv(g_calc, g_var_calc, mods = ~type_feature, data = db_MP_type, random = ~collapse | short_cite)
-
-summary(rma_TypeFeaturesMP)
-
-rma_TypeFeaturesMPAge <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)
-
-summary(rma_TypeFeaturesMPAge)
-```
-
-### Interaction with condition
-```{r MPtypeCondition}
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
-                type_feature == "tone")
-dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
-
-rma_TypeFeatures <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*condition, data = dat_type, random = ~collapse | short_cite)
-
-summary(rma_TypeFeatures)
-
-rma_TypeFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*age.C*condition, data = dat_type, random = ~collapse | short_cite)
-
-summary(rma_TypeFeaturesAge)
-```
-
-### Interaction with language
-```{r MPtypeLanguage}
-#dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
-#                type_feature == "tone")
-
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
-
-dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
-dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
-dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French",
-                                "Romanic", "Sino-Tibetian"))
-
-dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family, data = dat_type_sub, random = ~collapse | short_cite)
-
-summary(rma_TypeFeatures_Lang)
-```
-
-### Interaction with condition and language
-```{r MPtypeLanguageCondition}
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")# |
-                #type_feature == "tone")
-dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
-
-dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
-dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
-dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French",
-                                "Romanic", "Sino-Tibetian"))
-
-dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-dat_type_sub$lang_family <- as.factor(dat_type_sub$lang_family)
-
-rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family*condition, data = dat_type_sub, random = ~collapse | short_cite)
-
-summary(rma_TypeFeatures_Lang)
-
-```
-## Correlation MP effect and vocabulary
-
-First, let's take a look at which vocabulary data we have available.
-
-```{r VocabularyData}
-vocab_info <- db_ET_correct %>%
-  mutate(has_vocab = ifelse(!is.na(r_comprehension), "comprehension", 
-                            ifelse(!is.na(r_production), "production", "none"))) %>%
-  group_by(has_vocab) %>%
-  summarize(count = n())
-
-kable(vocab_info)
-
-```
-
-We have 17 correlations, roughly evenly divided between comprehension and production data.
-There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we should both analyze this data separately and see whether it makes sense in a joint analysis.
-
-```{r ComprehensionMeta}
-#we're relying on the library meta function metacor
-compr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_comprehension) & r_comprehension > -1)
-
-metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
-```
-
-```{r ProductionMeta}
-#we're relying on the library meta function metacor
-prodr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_production) & r_production < 1)
-
-metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
-```
-
-# Plotting
-```{r PlotAPATheme}
 #Themes and plot
@@
     axis.line=element_line(),
-    text=element_text(family='Times', size=25))
+    text=element_text(family='Times', size=25),
+    legend.position='none')
 
 ```
-## Mispronunciation Effect by Age (color)
-```{r PlotMPEffect}
+
+```{r PlotMPEffect, echo = FALSE}
 
@@
 
-p
+#p
 
-min(dat$mean_age_1/30.44)
-max(dat$mean_age_1/30.44)
+#min(dat$mean_age_1/30.44)
+#max(dat$mean_age_1/30.44)
 
@@
 
-  jpeg(filename = "figures/AgeEffect_log.jpg", 
-       width = 600, height = 400, units = "px")
+  #jpeg(filename = "figures/AgeEffect_log.jpg", 
+ #      width = 600, height = 400, units = "px")
 
@@
 
-  dev.off()
-
-```
-## Mispronunciation Effect by Age (bw)
-```{r PlotMPEffect_BW}
-
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape=condition_label, color=condition_label),
-             show.legend=FALSE) + 
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_color_grey()+
-  theme_bw()+
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_BW.jpg", p,height= 3,width= 6)
+  #dev.off()
 
@@
 
-## MP type: Consonant, Vowel, or Tone?
-```{r PlotCVEffect}
+# Supplementary Analyses for Discussion
 
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = type_feature),show.legend=FALSE) + 
-  facet_grid(.~type_feature)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
+This section includes supplementary analyses discussed in the Discussion section
 
-ggsave("figures/AgeEffect_log_CV.jpg", p)
-```
+## Vocabulary Data Available
 
-## Language Family by MP type: Consonant, Vowel, or Tone?
-```{r PlotCVEffect_Lang}
+This table summarizes which papers also measured vocabulary in the infants they tested.
 
-p <- ggplot(dat, aes(type_feature, g_calc, color = type_feature)) + 
-  geom_boxplot() + 
-  facet_grid(lang_family~condition_label)+
-  #geom_line(y= 0, linetype="dotted") + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Language Family") + 
-  ylab("Effect size Hedges' g")
-p
+```{r VocabularyData}
 
-ggsave("figures/LangFamily_CV.jpg", p)
-```
+vocab_info <- vocab_dat %>%
+  mutate(has_vocab = ifelse(!is.na(r_comprehension) & !is.na(r_production), "comprehension & production", 
+                            ifelse(!is.na(r_comprehension), "just comprehension",
+                            ifelse(!is.na(r_production), "just production", "none")))) %>%
+  group_by(has_vocab) %>%
+  summarize(count = n())
 
-## Number of Features
-```{r PlotFeatEffect}
-
-#dat_f <- subset(dat, n_feature == "0" | n_feature == "1" | n_feature == "2" | n_feature == "3")
-
-p <- ggplot(dat_f, aes(mean_age_1/30.44, g_calc, color = n_feature)) + 
-  geom_point(aes(size = weights_g, shape = n_feature),show.legend=FALSE) + 
-  #facet_grid(.~type_feature)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_feat.jpg", p)
+kable(vocab_info)
 
@@
 
-## Position of Mispronunciation
-```{r PlotPositionEffect}
+## Mispronunciation Sensitivity at Youngest Ages
 
-dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial" |
-                mispron_location == "offset")
+Mispronunciation sensitivity in the papers in our dataset with the youngest ages (< 12-months-of-age; Bergelson & Swingley, 2017; Mani & Plunkett, 2007; Zesiger et al., 2012).
 
-p <- ggplot(dat.p, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = mispron_location),show.legend=FALSE) + 
-  facet_grid(.~mispron_location)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
+```{r YoungAge, echo = FALSE}
+youngest <- subset(dat, min_age_1 < 365)
+
+#unique(youngest$short_cite)
+youngest$cond_lab <- ifelse(youngest$condition == 1, "correct", "misp")
+p <- ggplot(youngest, aes(x=cond_lab, y = g_calc, color = cond_lab)) + geom_boxplot()
+
 p
-
-ggsave("figures/AgeEffect_log_position.jpg", p)
 
@@
 
-## Distractor Familiarity
-```{r PlotDistFamEffect}
+## Known vs Novel Distractor Images
 
-dat$condition_label = ifelse(dat$condition==1, "correct", "MP")
-dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")
+This table summarizes which papers used a known or novel distractor image.
 
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = dist_code),show.legend=FALSE) + 
-  facet_grid(.~dist_code)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_color_manual(values=wes_palette(name="Darjeeling"))+
-  theme_bw()+
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
+```{r DescriptivesDISTRACT, echo = FALSE}
+#What kind of distractor was used?
 
-ggsave("figures/AgeEffect_log_distractor_fam.jpg", p)
+distr_info <- distract_dat %>%
+  group_by(object_pair) %>%
+  summarize(count = n())
+
+kable(distr_info)
 
@@
 
-## Distractor Familiarity (w/o age)
-```{r PlotDistFamEffect_NoAge}
+### Does distractor familiarity (known vs. novel) impact mispronunciation sensitivity?
 
-dat$condition_label = ifelse(dat$condition==1, "correct", "MP")
-dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")
+Preliminary moderator test examining the influence of distractor familiarity on mispronunciation sensitivity
+
+```{r DistractorTypeAge}
+
+rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
+
+summary(rma_Distractor)
+
+```
+
+## Plotting Influence of Distractor Familiarity
+
+```{r PlotDistFamEffect_NoAge, echo = FALSE}
+
+dat$condition_label = ifelse(dat$condition==1, "correct", "mispronunciation")
+dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "known", "novel")
 
@@
 
-ggsave("figures/Distractor_fam_log.jpg", p)
+#ggsave("figures/Distractor_fam_log.jpg", p)
 
 ```
-
-## Distractor Familiarity (w/o age, subset to age range)
-```{r PlotDistFamEffect_NoAge_AgeMatch}
-
-min_age<-min(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
-max_age <- max(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
-
-dat_age= dat%>%
-  filter(mean_age_1>min_age&mean_age_1<max_age)
-
-dat_age$condition_label = ifelse(dat_age$condition==1, "correct", "MP")
-dat_age$dist_code <- ifelse(dat_age$object_pair == "familiar_familiar", "familiar", "unfamiliar")
-
-p <- ggplot(dat_age, aes(dist_code, g_calc, color = condition_label)) + 
-  geom_boxplot() + 
-  #geom_line(y= 0, linetype="dotted") + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_color_manual(values=wes_palette(name="Darjeeling"))+
-  theme_bw()+
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Distractor Familiarity") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeMatch_Distractor_fam_log.jpg", p)
-
-```
-
-## Overlap between distractor and target
-
-```{r PlotDistOverlapEffect}
-
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = distractor_overlap),show.legend=FALSE) + 
-  facet_grid(.~distractor_overlap)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_distractor_overlap.jpg", p)
-
-```
-
-## Language Family
-```{r PlotLanguageEffect}
-
-dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
-                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
-                           dat$native_lang=="German", "Germanic",
-                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
-                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
-                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))
-
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = lang_family),show.legend=FALSE) + 
-  facet_grid(.~lang_family)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_language.jpg", p)
-
-```

### 2018-02-05 CogSci_Publication_bias.Rmd
Created CogSci markdown files for Analysis and Publication Bias
Markdown files have been uploaded to OSF CogSci Subproject.

--- 2018-01-30 Publication_bias_analyses.Rmd
@@
 ---
-title: "MP Publication Bias"
-author: "originally Christina Bergmann, modified by Katie Von Holzen"
+title: "Mispronunciation Sensitivity Publication Bias for CogSci"
+author: "Christina Bergmann and Katie Von Holzen"
 output: 
@@
 
-#Preparation
-
+# Preparation
 Read in data and tidy up dataset
@@
 # Funnel Plot Asymmetry
-Use ranktest() to check for funnel plot asymmetry. All three tests show evidence of significant asymmetry.
+Use ranktest() to check for funnel plot asymmetry. Both tests show evidence of significant asymmetry.
 
-```{r FunnelPlotAsymmetry, echo = FALSE}
+## Object Identification Correct Words
+
+```{r FunnelPlotAsymm_correct, echo = FALSE}
 
@@
 # Metafor comes with several options to check this, I chose ranktest and regtest
-
-# this is the model of the mispronunciation effect, without age
-ranktest(rma_MPeffect)
-
 # correct object identification
 ranktest(rma_correct)
+
+```
+
+## Object Identification Mispronounced Words
+
+```{r FunnelPlotAsymm_misp, echo = FALSE}
 
@@
 
-# Export data for p-curve
-
-This step creates a text file that can be used in the p-curve app:
-http://www.p-curve.com/app4/
-
-These files can be found in "p_curve_app/"
-
-for correct: p_curve_co.txt
-for mispronounced: p_curve_mp.txt
-
-Just copy and paste the .txt onto the website and voila!
-
-NOTE: This will always append lines to the existing txt file, check for double writing!
-
-```{r PcurveExport, echo = FALSE}
-
-textfile_co = "p_curve_app/p_curve_co.txt"
-
-for(line in 1:length(db_ET_correct$n_1)){
-  if(!is.na(db_ET_correct[line,]$t)){
-    newline = paste("t(", db_ET_correct[line,]$n_1-1, ")=",db_ET_correct[line,]$t, sep = "")
-    write(newline, file = textfile_co, append = TRUE)
-    #cat("\n")
-    #write(newline, file = textfile, append = TRUE)    
-  }
-}
-
-textfile_mp = "p_curve_app/p_curve_mp.txt"
-
-for(line in 1:length(db_ET_MP$n_1)){
-  if(!is.na(db_ET_MP[line,]$t)){
-    newline = paste("t(", db_ET_MP[line,]$n_1-1, ")=",db_ET_MP[line,]$t, sep = "")
-    write(newline, file = textfile_mp, append = TRUE)
-    #cat("\n")
-    #write(newline, file = textfile, append = TRUE)    
-  }
-}
-```
-
-# Calculate Power
-
-# What is the power of the studies in the dataset?
-
-```{r Power_exist, echo = FALSE}
-d = rma.mv(g_calc, g_var_calc, data = db_mpe, random = ~ 1 | short_cite)$b[,1]
-
-# estimate from mispronunciation sensitivity
-mp_est <- coef(summary(rma_MPeffect))[2,]$estimate
-
-pwr.t.test(n = median(db_mpe$n_1, na.rm=TRUE), d = mp_est, sig.level = .05, type = "paired", alternative = "two.sided")
-
-```
-
-# What is the average power to detect a mispronunciation sensitivity effect (to be compared with p-curve estimate)
-```{r Power_plan, echo = FALSE}
-
-# estimate from mispronunciation sensitivity
-mp_est <- coef(summary(rma_MPeffect))[2,]$estimate
-
-# one-sided t-test
-pwr.t.test(d = mp_est, sig.level = .05, type = "paired", power = .80, alternative = "greater")
-
-```
-
 # Draw Funnel Plots
 
-### Plots from Sakaluk, 2016
+### Plots adapted from Sakaluk, 2016, see also Black & Bergmann, 2017
 ### https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/
-
-## Funnel Plot for Correct Object Identification
 
@@
 fp_co +   ggtitle("Correct")
-ggsave("figures/FunnelPlot_correct.pdf")
+#ggsave("figures/FunnelPlot_correct.pdf")
+
 ```
@@
   #Store the meta-analytic estimate and its standard error from whatever model you run (substitute your own values)
-  summary(rma_MP)
+  #summary(rma_MP)
   estimate_mp = coef(summary(rma_MP))$estimate
@@
   fp_mp + ggtitle("Mispronunciation")
-  ggsave("figures/FunnelPlot_misp.pdf")
+#  ggsave("figures/FunnelPlot_misp.pdf")
 
@@
 
+Below is the plot used in Figure 1.
+Funnel plots for object identification for correct (left) and mispronounced (right) words, plotting the standard error of the effect size in relation to effect size.
+The black line marks zero, the dashed grey line marks the effect estimate, and the grey line marks funnel plot asymmetry.
+
 ```{r FunnelCombo, echo = FALSE}
 
-  jpeg(filename = "figures/Funnel_Plots_Object_Identification.jpg", 
-       width = 600, height = 400, units = "px")
+#  jpeg(filename = "figures/Funnel_Plots_Object_Identification.jpg", 
+#       width = 600, height = 400, units = "px")
 
@@
 
-  dev.off()
+#  dev.off()
 
@@
 ```
+
+# P-curve
+
+## Export Data for P-curve
+
+This step creates a text file that can be used in the p-curve app:
+http://www.p-curve.com/app4/
+
+for correct word object identification see "p_curve_co.txt" file
+
+for mispronounced word object identification see "p_curve_mp.txt" file
+
+Just copy and paste the .txt onto the website and voila!
+
+```{r PcurveExport, echo = FALSE}
+
+textfile_co = "p_curve_app/p_curve_co.txt"
+
+# make sure the file is made new with our loop
+if (file.exists(textfile_co)) {file.remove(textfile_co)}
+
+for(line in 1:length(db_ET_correct$n_1)){
+  if(!is.na(db_ET_correct[line,]$t)){
+    newline = paste("t(", db_ET_correct[line,]$n_1-1, ")=",db_ET_correct[line,]$t, sep = "")
+    write(newline, file = textfile_co, append = TRUE)
+    #cat("\n")
+    #write(newline, file = textfile, append = TRUE)    
+  }
+}
+
+textfile_mp = "p_curve_app/p_curve_mp.txt"
+
+# make sure the file is made new with our loop
+if (file.exists(textfile_mp)) {file.remove(textfile_mp)}
+
+for(line in 1:length(db_ET_MP$n_1)){
+  if(!is.na(db_ET_MP[line,]$t)){
+    newline = paste("t(", db_ET_MP[line,]$n_1-1, ")=",db_ET_MP[line,]$t, sep = "")
+    write(newline, file = textfile_mp, append = TRUE)
+    #cat("\n")
+    #write(newline, file = textfile, append = TRUE)    
+  }
+}
+
+```
+
+# Calculate Power
+
+```{r Power_exist_descript, echo = FALSE}
+d = rma.mv(g_calc, g_var_calc, data = db_mpe, random = ~ 1 | short_cite)$b[,1]
+
+# estimate from mispronunciation sensitivity
+mp_est <- round(coef(summary(rma_MPeffect))[2,]$estimate, 2)
+
+# one-sided t-test
+ptt <- pwr.t.test(d = mp_est, sig.level = .05, type = "paired", power = .80, alternative = "greater")
+
+```
+
+The median sample size across studies in our dataset was `r median(db_mpe$n_1, na.rm=TRUE)`.
+To study infants' mispronunciation senstivity, which we estimate to have an effect size of `r mp_est`, this test gives the number of participants (n = `r round(ptt$n, 2)`) required in a within-participant design using a one-sided t-test to conduct a study which has 80% power.
+
+```{r Power_plan, echo = FALSE}
+
+# one-sided t-test
+pwr.t.test(d = mp_est, sig.level = .05, type = "paired", power = .80, alternative = "greater")
+
+```

### 2018-05-09 CogSci_Publication_bias.Rmd
updated code for response to CogSci reviewers
- changed color to dark blue for age by effect size plot
- changed axis and overall titles for funnel plot

@@
   xlab('Standard Error') + ylab('Hedge\'s g')+
+  # give it a title
+    ggtitle("Correct") +
     # make sure both plots have same scale
     # still ylim because we haven't flipped yet
-  #coord_cartesian(ylim = c(-1, 2.5))+
+    #coord_cartesian(ylim = c(0.5, 0))+
   #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
@@
 #Call the pretty funnel plot
-fp_co +   ggtitle("Correct")
+fp_co
 #ggsave("figures/FunnelPlot_correct.pdf")
@@
   #Give the x- and y- axes informative labels
-  xlab('Standard Error') + ylab('Hedge\'s g')+
+  xlab('Standard Error') + 
+    # remove y label because it will be combined with the other funnel plot
+    ylab('Hedge\'s g')+
+    # give it a title
+    ggtitle("Mispronunciation") +
     # make sure both plots have same scale
-    # still ylim because we haven't flipped yet
-    #coord_cartesian(ylim = c(-1, 2.5))+
+    # still xlim because we haven't flipped yet
+    #coord_cartesian(xlim = c(0.5, 1))+
     #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
@@
     coord_flip()+
-    #Finally, apply my APA-format theme (see code at end of post).
+    #Finally, apply my APA-format theme (see previous).
     #You could, alternatively, specify theme_bw() instead.
-    apatheme
+    apatheme +
+    theme(axis.title.y = element_blank())
 
   #Call the pretty funnel plot
-  fp_mp + ggtitle("Mispronunciation")
+  fp_mp
 #  ggsave("figures/FunnelPlot_misp.pdf")
@@
 
-#  jpeg(filename = "figures/Funnel_Plots_Object_Identification.jpg", 
-#       width = 600, height = 400, units = "px")
+  jpeg(filename = "figures/Funnel_Plots_Object_Identification.jpg", 
+       width = 600, height = 400, units = "px")
 
@@
 
-#  dev.off()
+  dev.off()
 

### 2018-05-30 Paper_Analyses.Rmd
created "Paper_Analyses"
Paper_Analyses better reflects the order of analyses in the manuscript,
making writing easier.

--- 2018-02-05 Analyses.Rmd
@@
 
+# Plotting defaults
+
+```{r PlotAPATheme}
+#Themes and plot
+apatheme=theme_bw()+
+  theme(panel.grid.major=element_blank(),
+    panel.grid.minor=element_blank(),
+    panel.border=element_blank(),
+    axis.line=element_line(),
+    text=element_text(family='Times', size=25))
+
+```
+
 # Descriptive data
@@
 
+## Type of data on which we calculated effect sizes
 The table below shows based on which data we calculated effect sizes.
@@
 
+## Type of comparison of the time-course data calculated
 We also have different ways of comparison of the time-course data, as the next table shows.
+
 ```{r DescriptivesComparison, echo = FALSE}
@@
 
+## Type of distractor
 This is a summary of the type of distractor used in an experiment
@@
 
+## Whether word was pronounced both correctly as well as mispronounced
 This is a summary of whether an experiment had both correct and mispronounced versions of the word in the experiment
@@
 
-## Analysis time window
+## Size of analysis time window
 
@@
 
+## Duration of post naming window
 Next we look at duration (in seconds) of the post naming window, here,too, we see a lot of heterogeneity.
@@
 
-## Early Ages
+## Mispronunciation Sensitivity in the youngest ages
 Even the youngest ages in the database (less than 1 year) show mispronunciation sensitivity
@@
 
-## Correct object identification effect
+## Main Mispronunciation Sensitivity Effects
+
+### Correct object identification effect
 
@@
 
-rma_correct_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = ~ collapse | short_cite)
-
-summary(rma_correct_age)
+#kable(round(coef(summary(rma_correct)), 2))
 
@@
 
-## Mispronunciation object identification effect
+### Mispronunciation object identification effect
 
@@
 
-rma_MP_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = ~ collapse | short_cite)
-
-summary(rma_MP_age)
 ```
 
-## Mispronunciation effect
+### Mispronunciation Sensitivity effect
+
 ```{r MPEffect}
@@
 
+```
+
+## Main Mispronunciation Sensitivity Effects with Age Moderators
+
+### Correct object identification effect with age moderator
+
+```{r MAcorrect_age}
+
+rma_correct_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = ~ collapse | short_cite)
+
+summary(rma_correct_age)
+#kable(round(coef(summary(rma_correct_age)), 2))
+
+```
+
+### Mispronunciation object identification effect with age moderator
+
+```{r MAMP_age}
+
+rma_MP_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = ~ collapse | short_cite)
+
+summary(rma_MP_age)
+```
+
+### Mispronunciation Sensitivity effect with age moderator
+
+```{r MPEffect_age}
+db_ET_correct$condition <- 1
+db_ET_MP$condition <- 0
+
+dat <- bind_rows(db_ET_correct, db_ET_MP)
+
 rma_MPeffect_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = ~ collapse | short_cite)
@@
 
-### Language effect
+### Plot Mispronunciation Effect by Age (color)
 
-Followup: Per condition (correct or MP) the interaction with age
-
-```{r LanguageEffectAnalyses}
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")
-
-dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
-                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
-                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
-                           dat$native_lang=="German", "Germanic",
-                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
-                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
-                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))
-
-rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*lang_family, data = dat, random = ~ collapse | short_cite)
-summary(rma_lang_interaction)
-```
-
-### Type of distractor
-
-```{r DistractorTypeAge}
-
-rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
-
-summary(rma_Distractor)
-
-```
-
-## Type of Distractor with age
-```{r DistractorTypeAge}
-
-rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
-
-summary(rma_DistractorAge)
-
-```
-
-#### Subset to same age range
-
-```{r DistractorTypeAge}
-
-min_age <- min(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
-max_age <- max(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
-
-dat_age= dat%>%
-  filter(mean_age_1>min_age&mean_age_1<max_age)
-
-rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
-
-summary(rma_DistractorAgeS)
-
-```
-
-### Distractor Overlap
-
-```{r DistractorOverlap}
-
-rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
-
-summary(rma_DistractorOverlap)
-
-```
-
-## Number of features
-
-```{r NFeatures}
-
-db_ET_MPf = db_ET_MP %>%
-  filter(n_feature != "1-3" & n_feature != "1-2" & n_feature != "2-3")
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature), data = db_ET_MPf, random = ~collapse | short_cite)
-
-summary(rma_NFeatures)
-
-rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C, data = db_ET_MPf, random = ~collapse | short_cite)
-
-summary(rma_NFeaturesAge)
-```
-
-### Interaction with condition
-
-```{r NFeaturesCondition}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*condition, data = dat_f, random = ~collapse | short_cite)
-
-summary(rma_NFeatures)
-
-rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C*condition, data = dat_f, random = ~collapse | short_cite)
-
-summary(rma_NFeaturesAge)
-```
-
-## MP location
-
-```{r Location}
-#table(db_ET_MP$mispron_location)
-
-db_ET_MPl = db_ET_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_Location <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_MPl, random = ~collapse | short_cite)
-
-summary(rma_Location)
-
-rma_LocationAge <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
-
-summary(rma_LocationAge)
-```
-
-## MP type: Vowel, consonant, or tone?
-
-```{r MPtype}
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
-
-rma_TypeFeaturesMP <- rma.mv(g_calc, g_var_calc, mods = ~type_feature, data = db_MP_type, random = ~collapse | short_cite)
-
-summary(rma_TypeFeaturesMP)
-
-rma_TypeFeaturesMPAge <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)
-
-summary(rma_TypeFeaturesMPAge)
-```
-
-### Interaction with condition
-```{r MPtypeCondition}
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
-                type_feature == "tone")
-dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
-
-rma_TypeFeatures <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*condition, data = dat_type, random = ~collapse | short_cite)
-
-summary(rma_TypeFeatures)
-
-rma_TypeFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*age.C*condition, data = dat_type, random = ~collapse | short_cite)
-
-summary(rma_TypeFeaturesAge)
-```
-
-### Interaction with language
-```{r MPtypeLanguage}
-#dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
-#                type_feature == "tone")
-
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
-
-dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
-dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
-dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French",
-                                "Romanic", "Sino-Tibetian"))
-
-dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family, data = dat_type_sub, random = ~collapse | short_cite)
-
-summary(rma_TypeFeatures_Lang)
-```
-
-### Interaction with condition and language
-```{r MPtypeLanguageCondition}
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")# |
-                #type_feature == "tone")
-dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
-
-dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
-dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
-dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French",
-                                "Romanic", "Sino-Tibetian"))
-
-dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-dat_type_sub$lang_family <- as.factor(dat_type_sub$lang_family)
-
-rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family*condition, data = dat_type_sub, random = ~collapse | short_cite)
-
-summary(rma_TypeFeatures_Lang)
-
-```
-## Correlation MP effect and vocabulary
-
-First, let's take a look at which vocabulary data we have available.
-
-```{r VocabularyData}
-vocab_info <- db_ET_correct %>%
-  mutate(has_vocab = ifelse(!is.na(r_comprehension), "comprehension", 
-                            ifelse(!is.na(r_production), "production", "none"))) %>%
-  group_by(has_vocab) %>%
-  summarize(count = n())
-
-kable(vocab_info)
-
-```
-
-We have 17 correlations, roughly evenly divided between comprehension and production data.
-There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we should both analyze this data separately and see whether it makes sense in a joint analysis.
-
-```{r ComprehensionMeta}
-#we're relying on the library meta function metacor
-compr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_comprehension) & r_comprehension > -1)
-
-metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
-```
-
-```{r ProductionMeta}
-#we're relying on the library meta function metacor
-prodr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_production) & r_production < 1)
-
-metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
-```
-
-# Plotting
-```{r PlotAPATheme}
-#Themes and plot
-apatheme=theme_bw()+
-  theme(#panel.grid.major=element_blank(),
-    #panel.grid.minor=element_blank(),
-    #panel.border=element_blank(),
-    axis.line=element_line(),
-    text=element_text(family='Times', size=25))
-
-```
-## Mispronunciation Effect by Age (color)
 ```{r PlotMPEffect}
@@
 ```
-## Mispronunciation Effect by Age (bw)
+
+### Plot Mispronunciation Effect by Age (bw)
+
 ```{r PlotMPEffect_BW}
@@
 
-## MP type: Consonant, Vowel, or Tone?
+## Correlation MP effect and Vocabulary
+
+First, let's take a look at which vocabulary data we have available.
+
+```{r VocabularyData}
+vocab_info <- db_ET_correct %>%
+  mutate(has_vocab = ifelse(!is.na(r_comprehension), "comprehension", 
+                            ifelse(!is.na(r_production), "production", "none"))) %>%
+  group_by(has_vocab) %>%
+  summarize(count = n())
+
+kable(vocab_info)
+
+```
+
+We have 17 correlations, roughly evenly divided between comprehension and production data.
+There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we should both analyze this data separately and see whether it makes sense in a joint analysis.
+
+```{r ComprehensionMeta}
+#we're relying on the library meta function metacor
+compr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_comprehension) & r_comprehension > -1)
+
+metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
+```
+
+```{r ProductionMeta}
+#we're relying on the library meta function metacor
+prodr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_production) & r_production < 1)
+
+metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
+```
+
+## Number of features
+Size of mispronunciation, measured in features changed
+
+```{r NFeatures}
+
+db_ET_MPf = db_ET_MP %>%
+  filter(n_feature != "1-3" & n_feature != "1-2" & n_feature != "2-3")
+
+#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
+rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature), data = db_ET_MPf, random = ~collapse | short_cite)
+
+summary(rma_NFeatures)
+
+```
+
+### Number of features with condition moderator
+
+```{r NFeaturesCondition}
+
+dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
+                n_feature == "2" | n_feature == "3")
+
+#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
+rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*condition, data = dat_f, random = ~collapse | short_cite)
+
+summary(rma_NFeatures)
+
+```
+
+### Number of features with age moderator
+
+```{r NFeatures_age}
+
+db_ET_MPf = db_ET_MP %>%
+  filter(n_feature != "1-3" & n_feature != "1-2" & n_feature != "2-3")
+
+rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C, data = db_ET_MPf, random = ~collapse | short_cite)
+
+summary(rma_NFeaturesAge)
+```
+
+### Number of features with condition and age moderators
+
+```{r NFeaturesCondition_age}
+
+dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
+                n_feature == "2" | n_feature == "3")
+
+rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C*condition, data = dat_f, random = ~collapse | short_cite)
+
+summary(rma_NFeaturesAge)
+```
+
+### Plot number of Features
+
+```{r PlotFeatEffect}
+
+dat_f <- subset(dat, n_feature == "0" | n_feature == "1" | n_feature == "2" | n_feature == "3")
+
+dat_f$feat_cat <- ifelse(dat_f$n_feature == 1, "one",
+                         ifelse(dat_f$n_feature == 2, "two",
+                                ifelse(dat_f$n_feature == 3, "three",
+                                       ifelse(dat_f$n_feature == 0, "correct", "none"))))
+
+dat_f <- subset(dat_f, feat_cat != "none")
+
+p <- ggplot(dat_f, aes(mean_age_1/30.44, g_calc, color = feat_cat)) + 
+  geom_point(aes(size = weights_g, shape = feat_cat),show.legend=FALSE) + 
+  #facet_grid(.~type_feature)+
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  theme(text = element_text(size=16)) + 
+  xlab("Age in months") + 
+  ylab("Effect size Hedges' g")
+p
+
+ggsave("figures/AgeEffect_log_feat.jpg", p)
+
+```
+
+## Type of MP: Vowel, consonant, or tone
+
+```{r MPtype}
+db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
+
+rma_TypeFeaturesMP <- rma.mv(g_calc, g_var_calc, mods = ~type_feature, data = db_MP_type, random = ~collapse | short_cite)
+
+summary(rma_TypeFeaturesMP)
+
+```
+
+### Type of MP: Vowel, consonant, or tone with age moderator
+
+```{r MPtype_age}
+db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
+
+rma_TypeFeaturesMPAge <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)
+
+summary(rma_TypeFeaturesMPAge)
+```
+
+### Type of MP: Vowel, consonant, or tone with condition moderator
+
+```{r MPtypeCondition}
+dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
+                type_feature == "tone")
+dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
+
+rma_TypeFeatures <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*condition, data = dat_type, random = ~collapse | short_cite)
+
+summary(rma_TypeFeatures)
+
+```
+
+### Type of MP: Vowel, consonant, or tone with age and condition moderator
+
+```{r MPtypeCondition_age}
+dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
+                type_feature == "tone")
+dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
+
+rma_TypeFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*age.C*condition, data = dat_type, random = ~collapse | short_cite)
+
+summary(rma_TypeFeaturesAge)
+```
+
+### Type of MP with language family moderator
+
+```{r MPtypeLanguage}
+#dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
+#                type_feature == "tone")
+
+dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
+
+dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
+
+dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
+dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
+dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French",
+                                "Romanic", "Sino-Tibetian"))
+
+dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
+
+rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family, data = dat_type_sub, random = ~collapse | short_cite)
+
+summary(rma_TypeFeatures_Lang)
+```
+
+### Type of MP with language family and condition moderators
+
+```{r MPtypeLanguageCondition}
+dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")# |
+                #type_feature == "tone")
+dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
+
+dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
+dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
+dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French",
+                                "Romanic", "Sino-Tibetian"))
+
+dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
+dat_type_sub$lang_family <- as.factor(dat_type_sub$lang_family)
+
+rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family*condition, data = dat_type_sub, random = ~collapse | short_cite)
+
+summary(rma_TypeFeatures_Lang)
+
+```
+
+### Plot MP type: Consonant, Vowel, or Tone?
+
 ```{r PlotCVEffect}
@@
 
-## Language Family by MP type: Consonant, Vowel, or Tone?
+### Plot Language Family by MP type: Consonant, Vowel, or Tone?
 ```{r PlotCVEffect_Lang}
 
-p <- ggplot(dat, aes(type_feature, g_calc, color = type_feature)) + 
+p <- ggplot(dat_type_sub, aes(type_feature, g_calc, color = type_feature)) + 
   geom_boxplot() + 
@@
 
-## Number of Features
-```{r PlotFeatEffect}
+## Distractor Familiarity (familiary, unfamiliar)
 
-#dat_f <- subset(dat, n_feature == "0" | n_feature == "1" | n_feature == "2" | n_feature == "3")
+```{r DistractorType}
 
-p <- ggplot(dat_f, aes(mean_age_1/30.44, g_calc, color = n_feature)) + 
-  geom_point(aes(size = weights_g, shape = n_feature),show.legend=FALSE) + 
-  #facet_grid(.~type_feature)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
+rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
 
-ggsave("figures/AgeEffect_log_feat.jpg", p)
+summary(rma_Distractor)
 
@@
 
-## Position of Mispronunciation
-```{r PlotPositionEffect}
+### Distractor Familiarity with condition moderator
 
-dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial" |
-                mispron_location == "offset")
+```{r DistractorTypeCondition}
 
-p <- ggplot(dat.p, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = mispron_location),show.legend=FALSE) + 
-  facet_grid(.~mispron_location)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
+rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
 
-ggsave("figures/AgeEffect_log_position.jpg", p)
+summary(rma_Distractor)
 
@@
 
-## Distractor Familiarity
+### Distractor Familiarity with age moderator
+```{r DistractorTypeAge}
+
+rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
+
+summary(rma_DistractorAge)
+
+```
+
+### Distractor Familiarity with age and condition moderators
+```{r DistractorTypeConditionAge}
+
+rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
+
+summary(rma_DistractorAge)
+
+```
+
+### Distractor Familiarity with age moderator, subset to same age range
+
+```{r DistractorTypeAgeRangeSubset}
+
+min_age <- min(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
+max_age <- max(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
+
+dat_age= dat%>%
+  filter(mean_age_1>min_age&mean_age_1<max_age)
+
+rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
+
+summary(rma_DistractorAgeS)
+
+```
+
+### Plot Distractor Familiarity
+
 ```{r PlotDistFamEffect}
@@
 
-## Distractor Familiarity (w/o age)
+### Plot Distractor Familiarity (w/o age)
+
 ```{r PlotDistFamEffect_NoAge}
@@
 
-## Distractor Familiarity (w/o age, subset to age range)
+### Plot Distractor Familiarity (w/o age, subset to age range)
+
 ```{r PlotDistFamEffect_NoAge_AgeMatch}
@@
 
-## Overlap between distractor and target
+## Position of Mispronunciation (onset, medial)
+
+```{r Location}
+#table(db_ET_MP$mispron_location)
+
+db_ET_MPl = db_ET_MP %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
+
+#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
+rma_Location <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_MPl, random = ~collapse | short_cite)
+
+summary(rma_Location)
+
+```
+
+### Position of Mispronunciation with age moderator
+
+```{r Location_age}
+#table(db_ET_MP$mispron_location)
+
+db_ET_MPl = db_ET_MP %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
+
+rma_LocationAge <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
+
+summary(rma_LocationAge)
+```
+
+### Position of Mispronunciation with condition moderator
+
+```{r Location_condition}
+#table(db_ET_MP$mispron_location)
+
+db_ET_MPl = db_ET_MP %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
+
+rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition, data = db_ET_MPl, random = ~collapse | short_cite)
+
+summary(rma_LocationCondition)
+```
+
+### Position of Mispronunciation with age and condition moderators
+
+```{r Location_condition_age}
+#table(db_ET_MP$mispron_location)
+
+db_ET_MPl = db_ET_MP %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
+
+rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
+
+summary(rma_LocationCondition)
+```
+
+### Plot Position of Mispronunciation
+```{r PlotPositionEffect}
+
+#dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial" |
+#                mispron_location == "offset")
+
+dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial")
+
+p <- ggplot(dat.p, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
+  geom_point(aes(size = weights_g, shape = mispron_location),show.legend=FALSE) + 
+  facet_grid(.~mispron_location)+
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  theme(text = element_text(size=16)) + 
+  xlab("Age in months") + 
+  ylab("Effect size Hedges' g")
+p
+
+ggsave("figures/AgeEffect_log_position.jpg", p)
+
+```
+
+## Distractor Overlap
+
+```{r DistractorOverlap}
+
+rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
+
+summary(rma_DistractorOverlap)
+
+```
+
+### Distractor Overlap with age moderator
+
+```{r DistractorOverlap_age}
+
+rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
+
+summary(rma_DistractorOverlap)
+
+```
+
+### Distractor Overlap with condition moderator
+
+```{r DistractorOverlap_condition}
+
+rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
+
+summary(rma_DistractorOverlap)
+
+```
+
+### Distractor Overlap with age and condition moderators
+
+```{r DistractorOverlap_age_condition}
+
+rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
+
+summary(rma_DistractorOverlap)
+
+```
+
+### Plot Distractor Overlap
 
@@
 
-## Language Family
+## Language effect
+
+```{r LanguageEffectAnalyses}
+dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")
+
+dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
+                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
+                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
+                           dat$native_lang=="German", "Germanic",
+                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
+                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
+                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))
+
+rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~lang_family, data = dat, random = ~ collapse | short_cite)
+summary(rma_lang_interaction)
+
+```
+
+### Language effect with age moderator
+
+```{r LanguageEffectAnalyses_age}
+dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")
+
+dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
+                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
+                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
+                           dat$native_lang=="German", "Germanic",
+                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
+                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
+                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))
+
+rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*lang_family, data = dat, random = ~ collapse | short_cite)
+summary(rma_lang_interaction)
+
+```
+
+### Language effect with condition moderator
+
+```{r LanguageEffectAnalyses_condition}
+dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")
+
+dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
+                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
+                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
+                           dat$native_lang=="German", "Germanic",
+                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
+                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
+                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))
+
+rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~condition*lang_family, data = dat, random = ~ collapse | short_cite)
+summary(rma_lang_interaction)
+
+```
+
+### Language effect with age and condition moderators
+
+```{r LanguageEffectAnalyses_condition_age}
+dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")
+
+dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
+                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
+                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
+                           dat$native_lang=="German", "Germanic",
+                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
+                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
+                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))
+
+rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*lang_family, data = dat, random = ~ collapse | short_cite)
+summary(rma_lang_interaction)
+
+```
+
+### Plot Language Effect
 ```{r PlotLanguageEffect}

### 2018-06-21 Paper_Analyses.Rmd
ICIS_2018_poster_prep

@@
 
-The database contains data from `r length(unique(dat$short_cite))` papers consisting of data from `r sum(sum_dat$n_1)` infants. In the tables below, we provide more descriptive information.
+The database contains data from `r length(unique(dat$short_cite))` papers. In the tables below, we provide more descriptive information.
 
@@
 
+## Number of unique infants
+
+```{r DescriptivesInfnum, echo = FALSE}
+
+infnum_info <- dat[,c("unique_ID", "same_infant", "expt_num", "n_1")]
+infnum_info <- unique(infnum_info)
+
+number_of_infants <- sum(infnum_info$n_1)
+
+```
+
+The database contains data from `r number_of_infants` unique infants.
+
+## Number of unique experimental conditions
+
+```{r DescriptivesExpCond, echo = FALSE}
+
+condnum_info <- dat[,c("unique_ID", "same_infant", "expt_num", "expt_condition")]
+condnum_info <- unique(condnum_info)
+
+number_of_cond <- nrow(condnum_info)
+
+```
+
+The database contains data from `r number_of_cond` unique experimental conditions
+
 ## Type of comparison of the time-course data calculated
@@
 ```
+
+## Plotting Mispronunciation Effect
 
@@
 
-## Number of features
+## Number of Features Changed
+
+### Number of features
+
 Size of mispronunciation, measured in features changed
@@
 
-db_ET_MPf = db_ET_MP %>%
-  filter(n_feature != "1-3" & n_feature != "1-2" & n_feature != "2-3")
+db_ET_MPf  <- subset(db_ET_MP, n_feature == "0" | n_feature == "1" |
+                n_feature == "2" | n_feature == "3")
 
@@
 
-### Number of features with condition moderator
-
-```{r NFeaturesCondition}
+### Number of features subset to age range
+Size of mispronunciation, measured in features changed
+
+```{r NFeatures_subset}
 
@@
 
+mf <- subset(dat_f, n_feature == "3")
+min_age <- min(mf$mean_age_1)
+max_age <- max(mf$mean_age_1)
+
+dat_fage= dat_f%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
+rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature), data = dat_f, random = ~collapse | short_cite)
+
+summary(rma_NFeatures_agesub)
+
+```
+
+### Number of features with condition moderator
+
+```{r NFeaturesCondition}
+
+dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
+                n_feature == "2" | n_feature == "3")
+
 #rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
@@
 ```
+
+### Features changed with age moderator, subset to same age range
+
+```{r FeatureAgeRangeSubset}
+
+dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
+                n_feature == "2" | n_feature == "3")
+
+mf <- subset(dat_f, n_feature == "3")
+min_age <- min(mf$mean_age_1)
+max_age <- max(mf$mean_age_1)
+
+dat_fage= dat_f%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+rma_FeatureAgeS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(n_feature), data = dat_fage, random = ~ collapse | short_cite)
+
+summary(rma_FeatureAgeS)
+
+#rma_FeatureS <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(n_feature), data = dat_fage, random = ~ collapse | short_cite)
+
+#summary(rma_FeatureS)
+
+```
+
+## Plotting number of Features Changed
 
@@
 ```
+### Plot number of Features subsetted for age
+
+```{r PlotFeatEffect_agesubset}
+
+dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
+                n_feature == "2" | n_feature == "3")
+
+mf <- subset(dat_f, n_feature == "3")
+min_age <- min(mf$mean_age_1)
+max_age <- max(mf$mean_age_1)
+
+dat_fage= dat_f%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+dat_fage$feat_cat <- ifelse(dat_fage$n_feature == 1, "1-feature",
+                         ifelse(dat_fage$n_feature == 2, "2-feature",
+                                ifelse(dat_fage$n_feature == 3, "3-feature",
+                                       ifelse(dat_fage$n_feature == 0, "correct", "none"))))
+
+dat_fage <- subset(dat_fage, feat_cat != "none")
+
+dat_fage$Features_changed <- factor(dat_fage$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))
+
+# Color Blind palette:
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
+p <- ggplot(dat_fage, aes(mean_age_1/30.44, g_calc, color = Features_changed)) + 
+  geom_point(aes(size = weights_g, shape = Features_changed),show.legend=FALSE) + 
+  #facet_grid(.~type_feature)+
+    scale_colour_manual(values=cbPalette)+
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Effect size Hedges' g")
+p
+
+ggsave("figures/AgeEffect_log_feat_agesub.jpg", p)
+
+```
+
+### Plot number of Features subsetted for age Boxplot
+
+```{r PlotFeatEffect_agesubset_boxplot}
+
+dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
+                n_feature == "2" | n_feature == "3")
+
+mf <- subset(dat_f, n_feature == "3")
+min_age <- min(mf$mean_age_1)
+max_age <- max(mf$mean_age_1)
+
+dat_fage= dat_f%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+dat_fage$feat_cat <- ifelse(dat_fage$n_feature == 1, "1-feature",
+                         ifelse(dat_fage$n_feature == 2, "2-feature",
+                                ifelse(dat_fage$n_feature == 3, "3-feature",
+                                       ifelse(dat_fage$n_feature == 0, "correct", "none"))))
+
+dat_fage <- subset(dat_fage, feat_cat != "none")
+
+dat_fage$Features_changed <- factor(dat_fage$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))
+
+# Color Blind palette:
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
+p <- ggplot(dat_fage, aes(Features_changed, g_calc, fill = Features_changed)) + 
+  geom_boxplot() + 
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "none",
+        axis.title.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+ggsave("figures/AgeEffect_log_feat_agesub_noage.jpg", p)
+
+```
 
 ## Type of MP: Vowel, consonant, or tone
+
+### Type of MP: Vowel, consonant, or tone
 
@@
 ```
+
+## Plotting MP type: Consonant, Vowel, or Tone?
 
@@
 ### Plot Language Family by MP type: Consonant, Vowel, or Tone?
+
 ```{r PlotCVEffect_Lang}
@@
 
-### Distractor Familiarity with age moderator, subset to same age range
-
-```{r DistractorTypeAgeRangeSubset}
-
-min_age <- min(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
-max_age <- max(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
+### Distractor Familiarity with condition moderator, subset to same age range
+
+```{r DistractorTypeAgeRangeSubset_condition}
+
+mf <- subset(dat, object_pair=="familiar_novel")
+min_age <- min(mf$mean_age_1)
+
+mf <- subset(dat, object_pair=="familiar_familiar")
+max_age <- max(mf$mean_age_1)
 
 dat_age= dat%>%
-  filter(mean_age_1>min_age&mean_age_1<max_age)
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
+
+summary(rma_DistractorAgeS)
+
+```
+
+### Distractor Familiarity with age and condition moderator, subset to same age range
+
+```{r DistractorTypeAgeRangeSubset_agecondition}
+
+mf <- subset(dat, object_pair=="familiar_novel")
+min_age <- min(mf$mean_age_1)
+
+mf <- subset(dat, object_pair=="familiar_familiar")
+max_age <- max(mf$mean_age_1)
+
+dat_age= dat%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
 
@@
 ```
+
+### Plotting Distractor Familiarity
 
@@
 
-min_age<-min(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
-max_age <- max(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
+mf <- subset(dat, object_pair=="familiar_novel")
+min_age <- min(mf$mean_age_1)
+
+mf <- subset(dat, object_pair=="familiar_familiar")
+max_age <- max(mf$mean_age_1)
 
@@
 
-dat_age$condition_label = ifelse(dat_age$condition==1, "correct", "MP")
-dat_age$dist_code <- ifelse(dat_age$object_pair == "familiar_familiar", "familiar", "unfamiliar")
-
-p <- ggplot(dat_age, aes(dist_code, g_calc, color = condition_label)) + 
+dat_age$condition_label = ifelse(dat_age$condition==1, "correct", "mispronunciation")
+dat_age$dist_code <- ifelse(dat_age$object_pair == "familiar_familiar", "Familiar Distractor", "Unfamiliar Distractor")
+
+# Color Blind palette:
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
+p <- ggplot(dat_age, aes(condition_label, g_calc, fill = condition_label)) + 
   geom_boxplot() + 
-  #geom_line(y= 0, linetype="dotted") + 
+  facet_grid(.~dist_code) +
   #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_color_manual(values=wes_palette(name="Darjeeling"))+
-  theme_bw()+
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
   theme(text = element_text(size=25),
         legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+ggsave("figures/AgeMatch_Distractor_fam_log.jpg", p)
+
+```
+
+### Plot Distractor Familiarity by age subsetted for age
+
+```{r PlotDistFam}
+
+mf <- subset(dat, object_pair=="familiar_novel")
+min_age <- min(mf$mean_age_1)
+
+mf <- subset(dat, object_pair=="familiar_familiar")
+max_age <- max(mf$mean_age_1)
+
+dat_fage= dat%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+dat_fage$dist_fam <- ifelse(dat_fage$object_pair == "familiar_novel", "Novel Distractor", "Familiar Distractor")
+
+# Color Blind palette:
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
+p <- ggplot(dat_fage, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
+  geom_point(aes(size = weights_g, shape = dist_fam),show.legend=FALSE) + 
+  facet_grid(.~dist_fam)+
+    scale_colour_manual(values=cbPalette)+
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  apatheme +
+  theme(legend.title = element_blank(),
         legend.position = "bottom") + 
-  xlab("Distractor Familiarity") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeMatch_Distractor_fam_log.jpg", p)
+  xlab("Age in months") + 
+  ylab("Effect size Hedges' g")
+p
+
+ggsave("figures/AgeEffect_log_DistFam_agesub.jpg", p)
 
@@
 
-### Plot Position of Mispronunciation
+## Plotting Position of Mispronunciation
 ```{r PlotPositionEffect}
@@
 
-### Plot Distractor Overlap
+## Plotting Distractor Overlap
 
@@
 
-### Plot Language Effect
+## Plotting Language Effect
 ```{r PlotLanguageEffect}

### 2018-06-21 example_plot.R

@@ -1,0 +1,77 @@
+#setwd("~/Dropbox/MP_MA")
+
+library(ggplot2)
+library(wesanderson)
+library(reshape)
+library(doBy)
+
+std <- function(x) sd(x)/sqrt(length(x))
+
+correct <- rnorm(100, mean=0.730396429, sd=0.10471147)
+mispronunciation <- rnorm(100, mean=0.612614286, sd=0.093135265)
+
+cm <- data.frame(cbind(correct, mispronunciation))
+cm$sub <- seq(1, nrow(cm))
+
+dat.m2 <- melt(cm,
+               id=c(3),
+               measure=c(1:2),
+               variable="Measure", na.rm=T)
+names(dat.m2) <- c("sub", "condition", "PTL")
+
+# Color Blind palette:
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
+
+box <- ggplot(data=dat.m2, aes(x=condition, y=PTL, fill=condition)) +
+  geom_boxplot()+
+  #scale_fill_manual(values=wes_palette(name="Darjeeling"))+
+  scale_fill_manual(values=cbPalette)+
+  theme_bw()+
+  annotate("segment", x = .67, xend = .67, y = .7, yend = .5, colour="black", size=1, arrow=arrow())+
+  annotate("segment", x = 1.2, xend = 2.2, y = .96, yend = .96, colour="black", size=1)+
+  annotate("text", x = .5, y = .65, parse = TRUE, label = "recognition",angle = 90, size = 10)+
+  annotate("text", x = 1.75, y = .99, parse = TRUE, label = "misp_sensitivity", size = 10)+
+  geom_hline(yintercept = .5)+
+  coord_cartesian(ylim = c(.35, 1))+
+  theme(text = element_text(size=30),
+        legend.position = "bottom",
+        legend.title = element_blank(),
+        axis.text.x = element_blank(),
+        axis.title.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank())+
+  ylab("Proportion of Target Looks")
+
+ggsave("figures/Example_boxplot.jpg", box)
+
+d.p <- summaryBy(PTL~condition, data=dat.m2, FUN=c(mean, std))
+
+
[…]

### 2018-06-21 figures/example_plot.R

@@ -1,73 +1,0 @@
-setwd("~/Dropbox/MP_MA")
-
-library(ggplot2)
-library(wesanderson)
-library(reshape)
-library(doBy)
-
-std <- function(x) sd(x)/sqrt(length(x))
-
-correct <- rnorm(100, mean=0.730396429, sd=0.10471147)
-misp <- rnorm(100, mean=0.612614286, sd=0.093135265)
-
-cm <- data.frame(cbind(correct, misp))
-cm$sub <- seq(1, nrow(cm))
-
-dat.m2 <- melt(cm,
-               id=c(3),
-               measure=c(1:2),
-               variable="Measure", na.rm=T)
-names(dat.m2) <- c("sub", "condition", "PTL")
-
-
-box <- ggplot(data=dat.m2, aes(x=condition, y=PTL, fill=condition)) +
-  geom_boxplot()+
-  scale_fill_manual(values=wes_palette(name="Darjeeling"))+
-  theme_bw()+
-  annotate("segment", x = .67, xend = .67, y = .7, yend = .5, colour="black", size=1, arrow=arrow())+
-  annotate("segment", x = 1, xend = 2, y = .96, yend = .96, colour="black", size=1)+
-  annotate("text", x = .5, y = .63, parse = TRUE, label = "recognition",angle = 90, size = 10)+
-  annotate("text", x = 1.5, y = .99, parse = TRUE, label = "misp_sensitivity", size = 10)+
-  geom_hline(yintercept = .5)+
-  coord_cartesian(ylim = c(.35, 1))+
-  theme(text = element_text(size=30),
-        legend.position = "bottom",
-        legend.title = element_blank(),
-        axis.text.x = element_blank(),
-        axis.title.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        panel.grid.major = element_blank(), 
-        panel.grid.minor = element_blank())+
-  ylab("Proportion of Target Looks")
-
-ggsave("Example_boxplot.jpg", box)
-
-d.p <- summaryBy(PTL~condition, data=dat.m2, FUN=c(mean, std))
-
-
-limits <- aes(ymax = PTL.mean+PTL.std, ymin=PTL.mean-PTL.std)
-dodge <- position_dodge(width=0.9)
-
-
-ex <- ggplot(data=d.p, aes(x=condition, y=PTL.mean, fill=condition)) +
-  geom_bar(stat = "identity", size=1.5, position=position_dodge(width = 0.9)) +
[…]

### 2018-06-28 Paper_Analyses.Rmd
final ICIS 2018 poster

@@
 db_ET$collapse <- paste(db_ET$study_ID, db_ET$expt_num, db_ET$same_infant, sep = "_")
+
+# assign language families
+
+db_ET$lang_family = ifelse(db_ET$native_lang=="American English" | db_ET$native_lang=="British English" | db_ET$native_lang=="Dutch" |
+db_ET$native_lang=="Danish" | db_ET$native_lang=="Swedish" |
+db_ET$native_lang=="English" | db_ET$native_lang=="German", "Germanic", ifelse(db_ET$native_lang == "French" | db_ET$native_lang == "Catalan" | db_ET$native_lang == "Spanish" | db_ET$native_lang == "Catalan-Spanish" | db_ET$native_lang == "Swiss French",
+                                "Romanic", "Sino-Tibetian"))
 
@@
 
-# Plotting defaults
+Plotting defaults
 
@@
 
+# Color Blind palette:
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
 ```
@@
 
-## Main Mispronunciation Sensitivity Effects
+## Condition: Mispronunciation Sensitivity Effects
 
@@
 
-## Main Mispronunciation Sensitivity Effects with Age Moderators
+## Age: Mispronunciation Sensitivity Effects with Age Moderators
 
@@
 dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
-
-# Color Blind palette:
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
 
@@
   jpeg(filename = "figures/AgeEffect_log.jpg", 
-       width = 600, height = 400, units = "px")
+       width = 500, height = 300, units = "px")
 
@@
 
-## Correlation MP effect and Vocabulary
+## Vocabulary size: Correlation between mispronunciation sensitivity and vocabulary
 
@@
 
-## Number of Features Changed
+## Size of Mispronunciation: Measured in Features Changed
 
@@
 
-db_ET_MPf  <- subset(db_ET_MP, n_feature == "0" | n_feature == "1" |
+dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
                 n_feature == "2" | n_feature == "3")
@@
 #rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature), data = db_ET_MPf, random = ~collapse | short_cite)
+rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat.f, random = ~collapse | short_cite)
 
 summary(rma_NFeatures)
-
-```
+aov.feat <- anova(rma_NFeatures)
+
+n_feat <- round(coef(summary(rma_NFeatures))[2,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.feat)`
+
+Hedges' g was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
+(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)
+
+### Number of features with age moderator interaction
+
+Size of mispronunciation, measured in features changed
+
+```{r NFeatures_age}
+
+dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
+                n_feature == "2" | n_feature == "3")
+
+#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
+rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat.f, random = ~collapse | short_cite)
+
+summary(rma_NFeatures)
+aov.feat <- anova(rma_NFeatures)
+
+n_feat <- round(coef(summary(rma_NFeatures))[4,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.feat)`
+
+But there was no significant interaction between number of features changed and age:
+
+Hedges' g was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
+(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)
 
@@
 Size of mispronunciation, measured in features changed
+
+Number of features is still significant
 
@@
 
+#dat_fage$n_feature <- ordered(dat_fage$n_feature, levels = c("0", "1", "2", "3"))
+#dat_fage$n_feature <- as.numeric(dat_fage$n_feature)
+
 #rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature), data = dat_f, random = ~collapse | short_cite)
-
-summary(rma_NFeatures_agesub)
-
-```
-
-### Number of features with condition moderator
-
-```{r NFeaturesCondition}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*condition, data = dat_f, random = ~collapse | short_cite)
-
-summary(rma_NFeatures)
-
-```
-
-### Number of features with age moderator
-
-```{r NFeatures_age}
-
-db_ET_MPf  <- subset(db_ET_MP, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C, data = db_ET_MPf, random = ~collapse | short_cite)
-
-summary(rma_NFeaturesAge)
-```
-
-### Number of features with condition and age moderators
-
-```{r NFeaturesCondition_age}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C*condition, data = dat_f, random = ~collapse | short_cite)
-
-summary(rma_NFeaturesAge)
-```
-
-### Features changed with age moderator, subset to same age range
-
-```{r FeatureAgeRangeSubset}
+rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat_f, random = ~collapse | short_cite)
+
+#summary(rma_NFeatures_agesub)
+
+```
+
+### Number of features with age moderator subset to age range
+Size of mispronunciation, measured in features changed
+
+No interaction between features and age
+
+```{r NFeatures_subset_age}
 
@@
 
-rma_FeatureAgeS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(n_feature), data = dat_fage, random = ~ collapse | short_cite)
-
-summary(rma_FeatureAgeS)
-
-#rma_FeatureS <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(n_feature), data = dat_fage, random = ~ collapse | short_cite)
-
-#summary(rma_FeatureS)
+#dat_fage$n_feature <- ordered(dat_fage$n_feature, levels = c("0", "1", "2", "3"))
+#dat_fage$n_feature <- as.numeric(dat_fage$n_feature)
+
+#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
+rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat_f, random = ~collapse | short_cite)
+
+#summary(rma_NFeatures_agesub)
 
@@
 ```{r PlotFeatEffect}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" | n_feature == "2" | n_feature == "3")
-
-dat_f$feat_cat <- ifelse(dat_f$n_feature == 1, "one",
-                         ifelse(dat_f$n_feature == 2, "two",
-                                ifelse(dat_f$n_feature == 3, "three",
-                                       ifelse(dat_f$n_feature == 0, "correct", "none"))))
-
-dat_f <- subset(dat_f, feat_cat != "none")
-
-p <- ggplot(dat_f, aes(mean_age_1/30.44, g_calc, color = feat_cat)) + 
-  geom_point(aes(size = weights_g, shape = feat_cat),show.legend=FALSE) + 
-  #facet_grid(.~type_feature)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_feat.jpg", p)
-
-```
-### Plot number of Features subsetted for age
-
-```{r PlotFeatEffect_agesubset}
 
@@
 
-mf <- subset(dat_f, n_feature == "3")
-min_age <- min(mf$mean_age_1)
-max_age <- max(mf$mean_age_1)
-
-dat_fage= dat_f%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-dat_fage$feat_cat <- ifelse(dat_fage$n_feature == 1, "1-feature",
-                         ifelse(dat_fage$n_feature == 2, "2-feature",
-                                ifelse(dat_fage$n_feature == 3, "3-feature",
-                                       ifelse(dat_fage$n_feature == 0, "correct", "none"))))
-
-dat_fage <- subset(dat_fage, feat_cat != "none")
-
-dat_fage$Features_changed <- factor(dat_fage$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))
+# mf <- subset(dat_f, n_feature == "3")
+# min_age <- min(mf$mean_age_1)
+# max_age <- max(mf$mean_age_1)
+# 
+# dat_fage= dat_f%>%
+#   filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+dat_f$feat_cat <- ifelse(dat_f$n_feature == 1, "1-feature",
+                         ifelse(dat_f$n_feature == 2, "2-feature",
+                                ifelse(dat_f$n_feature == 3, "3-feature",
+                                       ifelse(dat_f$n_feature == 0, "correct", "none"))))
+
+dat_f <- subset(dat_f, feat_cat != "none")
+
+dat_f$Features_changed <- factor(dat_f$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))
 
@@
 
-p <- ggplot(dat_fage, aes(mean_age_1/30.44, g_calc, color = Features_changed)) + 
-  geom_point(aes(size = weights_g, shape = Features_changed),show.legend=FALSE) + 
-  #facet_grid(.~type_feature)+
-    scale_colour_manual(values=cbPalette)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_feat_agesub.jpg", p)
-
-```
-
-### Plot number of Features subsetted for age Boxplot
-
-```{r PlotFeatEffect_agesubset_boxplot}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-mf <- subset(dat_f, n_feature == "3")
-min_age <- min(mf$mean_age_1)
-max_age <- max(mf$mean_age_1)
-
-dat_fage= dat_f%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-dat_fage$feat_cat <- ifelse(dat_fage$n_feature == 1, "1-feature",
-                         ifelse(dat_fage$n_feature == 2, "2-feature",
-                                ifelse(dat_fage$n_feature == 3, "3-feature",
-                                       ifelse(dat_fage$n_feature == 0, "correct", "none"))))
-
-dat_fage <- subset(dat_fage, feat_cat != "none")
-
-dat_fage$Features_changed <- factor(dat_fage$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))
-
-# Color Blind palette:
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
-p <- ggplot(dat_fage, aes(Features_changed, g_calc, fill = Features_changed)) + 
+p <- ggplot(dat_f, aes(Features_changed, g_calc, fill = Features_changed)) + 
   geom_boxplot() + 
@@
 
-ggsave("figures/AgeEffect_log_feat_agesub_noage.jpg", p)
-
-```
-
-## Type of MP: Vowel, consonant, or tone
-
-### Type of MP: Vowel, consonant, or tone
-
-```{r MPtype}
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
-
-rma_TypeFeaturesMP <- rma.mv(g_calc, g_var_calc, mods = ~type_feature, data = db_MP_type, random = ~collapse | short_cite)
-
-summary(rma_TypeFeaturesMP)
-
-```
-
-### Type of MP: Vowel, consonant, or tone with age moderator
-
-```{r MPtype_age}
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
-
-rma_TypeFeaturesMPAge <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)
-
-summary(rma_TypeFeaturesMPAge)
-```
-
-### Type of MP: Vowel, consonant, or tone with condition moderator
-
-```{r MPtypeCondition}
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
-                type_feature == "tone")
-dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
-
-rma_TypeFeatures <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*condition, data = dat_type, random = ~collapse | short_cite)
-
-summary(rma_TypeFeatures)
-
-```
-
-### Type of MP: Vowel, consonant, or tone with age and condition moderator
-
-```{r MPtypeCondition_age}
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
-                type_feature == "tone")
-dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
-
-rma_TypeFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*age.C*condition, data = dat_type, random = ~collapse | short_cite)
-
-summary(rma_TypeFeaturesAge)
-```
-
-### Type of MP with language family moderator
-
-```{r MPtypeLanguage}
-#dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
-#                type_feature == "tone")
-
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
-
-dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
-dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
-dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French",
-                                "Romanic", "Sino-Tibetian"))
-
-dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family, data = dat_type_sub, random = ~collapse | short_cite)
-
-summary(rma_TypeFeatures_Lang)
-```
-
-### Type of MP with language family and condition moderators
-
-```{r MPtypeLanguageCondition}
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")# |
-                #type_feature == "tone")
-dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
-
-dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
-dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
-dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French",
-                                "Romanic", "Sino-Tibetian"))
-
-dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-dat_type_sub$lang_family <- as.factor(dat_type_sub$lang_family)
-
-rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family*condition, data = dat_type_sub, random = ~collapse | short_cite)
-
-summary(rma_TypeFeatures_Lang)
-
-```
-
-## Plotting MP type: Consonant, Vowel, or Tone?
-
-### Plot MP type: Consonant, Vowel, or Tone?
-
-```{r PlotCVEffect}
-
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = type_feature),show.legend=FALSE) + 
-  facet_grid(.~type_feature)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_CV.jpg", p)
-```
-
-### Plot Language Family by MP type: Consonant, Vowel, or Tone?
-
-```{r PlotCVEffect_Lang}
-
-p <- ggplot(dat_type_sub, aes(type_feature, g_calc, color = type_feature)) + 
-  geom_boxplot() + 
-  facet_grid(lang_family~condition_label)+
-  #geom_line(y= 0, linetype="dotted") + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Language Family") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/LangFamily_CV.jpg", p)
+  jpeg(filename = "figures/Number_of_Features.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
 ```
@@
 
-rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
+rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)
+
+#summary(rma_Distractor)
+
+aov.type <- anova(rma_Distractor)
+
+sum_eff <- round(coef(summary(rma_TypeFeatures_Lang))[2,], 2)
+
+```
+
+The moderator test was not significant:
+`print(aov.type)`
+
+No significant interaction between feature type and language family:
+
+Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
+
+### Distractor Familiarity with condition moderator
+
+```{r DistractorTypeCondition}
+
+rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
 
@@
 
-```
-
-### Distractor Familiarity with condition moderator
-
-```{r DistractorTypeCondition}
-
-rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
-
-summary(rma_Distractor)
-
-```
+aov.type <- anova(rma_Distractor)
+
+sum_eff <- round(coef(summary(rma_Distractor))[4,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+But there was no significant interaction between distractor familiarity and condition:
+
+Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
 
@@
 
-rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
-
-summary(rma_DistractorAge)
-
-```
+rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)
+
+#summary(rma_DistractorAge)
+
+aov.type <- anova(rma_DistractorAge)
+
+sum_eff <- round(coef(summary(rma_DistractorAge))[4,], 2)
+
+```
+The moderator test was not significant:
+`print(aov.type)`
+
+There was no significant interaction between distractor familiarity and age:
+
+Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
 
@@
 summary(rma_DistractorAge)  
-
-```
+aov.type <- anova(rma_DistractorAge)
+
+sum_eff <- round(coef(summary(rma_DistractorAge))[7,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+There was a significant interaction between distractor familiarity and condition, but not age:
+
+Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
+
+### Distractor Familiarity, subset to same age range
+
+```{r DistractorTypeAgeRangeSubset_condition}
+
+fn <- subset(dat, object_pair=="familiar_novel")
+min_fn <- min(mf$mean_age_1)
+max_fn <- max(mf$mean_age_1)
+
+ff <- subset(dat, object_pair=="familiar_familiar")
+min_ff <- min(ff$mean_age_1)
+max_ff <- max(ff$mean_age_1)
+
+min_age <- pmax(min_fn, min_ff)
+max_age <- pmin(max_fn, max_ff)
+
+dat_age= db_ET_MP%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
+
+#summary(rma_Distractor)
+
+aov.type <- anova(rma_Distractor)
+
+sum_eff <- round(coef(summary(rma_Distractor))[2,], 2)
+
+```
+
+The moderator test was not significant:
+`print(aov.type)`
+
+There was no significant effect of distractor familiarity:
+
+Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
 
@@
 ```{r DistractorTypeAgeRangeSubset_condition}
+
+fn <- subset(dat, object_pair=="familiar_novel")
+min_fn <- min(mf$mean_age_1)
+max_fn <- max(mf$mean_age_1)
+
+ff <- subset(dat, object_pair=="familiar_familiar")
+min_ff <- min(ff$mean_age_1)
+max_ff <- max(ff$mean_age_1)
+
+min_age <- pmax(min_fn, min_ff)
+max_age <- pmin(max_fn, max_ff)
+
+dat_age= dat%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
+
+summary(rma_DistractorAgeS)
+
+aov.type <- anova(rma_Distractor)
+
+sum_eff <- round(coef(summary(rma_Distractor))[4,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+There was a significant interaction between distractor familiarity and condition:
+
+Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
+
+### Distractor Familiarity with age and condition moderator, subset to same age range
+
+```{r DistractorTypeAgeRangeSubset_agecondition}
 
@@
 
-rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
-
-summary(rma_DistractorAgeS)
-
-```
-
-### Distractor Familiarity with age and condition moderator, subset to same age range
-
-```{r DistractorTypeAgeRangeSubset_agecondition}
+rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
+
+#summary(rma_DistractorAgeS)
+
+aov.type <- anova(rma_Distractor)
+
+sum_eff <- round(coef(summary(rma_Distractor))[8,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+There was no significant interaction between distractor familiarity, condition, and age:
+
+Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
+
+### Plotting Distractor Familiarity
+
+### Plot Distractor Familiarity
+
+```{r PlotDistFamEffect_NoAge_AgeMatch}
+
+dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
+dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "Familiar Distractor", "Unfamiliar Distractor")
+
+# Color Blind palette:
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
+p <- ggplot(dat, aes(condition_label, g_calc, fill = condition_label)) + 
+  geom_boxplot() + 
+  facet_grid(.~dist_code) +
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+  jpeg(filename = "figures/Distractor_fam.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
+### Plot Distractor Familiarity
+
+```{r PlotDistFamEffect_NoAge_AgeMatch}
+
+dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
+dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "Familiar Distractor", "Unfamiliar Distractor")
 
@@
   filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
-
-summary(rma_DistractorAgeS)
-
-```
-
-### Plotting Distractor Familiarity
-
-### Plot Distractor Familiarity
-
-```{r PlotDistFamEffect}
-
-dat$condition_label = ifelse(dat$condition==1, "correct", "MP")
-dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")
-
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = dist_code),show.legend=FALSE) + 
-  facet_grid(.~dist_code)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_color_manual(values=wes_palette(name="Darjeeling"))+
-  theme_bw()+
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_distractor_fam.jpg", p)
-
-```
-
-### Plot Distractor Familiarity (w/o age)
-
-```{r PlotDistFamEffect_NoAge}
-
-dat$condition_label = ifelse(dat$condition==1, "correct", "MP")
-dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")
-
-p <- ggplot(dat, aes(dist_code, g_calc, color = condition_label)) + 
-  geom_boxplot() + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_color_manual(values=wes_palette(name="Darjeeling"))+
-  theme_bw()+
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Distractor Familiarity") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/Distractor_fam_log.jpg", p)
-
-```
-
-### Plot Distractor Familiarity (w/o age, subset to age range)
-
-```{r PlotDistFamEffect_NoAge_AgeMatch}
-
-mf <- subset(dat, object_pair=="familiar_novel")
-min_age <- min(mf$mean_age_1)
-
-mf <- subset(dat, object_pair=="familiar_familiar")
-max_age <- max(mf$mean_age_1)
-
-dat_age= dat%>%
-  filter(mean_age_1>min_age&mean_age_1<max_age)
-
-dat_age$condition_label = ifelse(dat_age$condition==1, "correct", "mispronunciation")
-dat_age$dist_code <- ifelse(dat_age$object_pair == "familiar_familiar", "Familiar Distractor", "Unfamiliar Distractor")
-
-# Color Blind palette:
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
 
@@
 
-ggsave("figures/AgeMatch_Distractor_fam_log.jpg", p)
-
-```
-
-### Plot Distractor Familiarity by age subsetted for age
-
-```{r PlotDistFam}
+  jpeg(filename = "figures/Distractor_fam_age_AgeSubset.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
+### Plot Distractor Familiarity by age (subset to same age range)
+
+```{r PlotDistFamEffect_age}
+
+dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
+dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")
 
@@
 
-dat_fage= dat%>%
+dat_age= dat%>%
   filter(mean_age_1>=min_age&mean_age_1<=max_age)
 
-dat_fage$dist_fam <- ifelse(dat_fage$object_pair == "familiar_novel", "Novel Distractor", "Familiar Distractor")
-
-# Color Blind palette:
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
-p <- ggplot(dat_fage, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = dist_fam),show.legend=FALSE) + 
-  facet_grid(.~dist_fam)+
-    scale_colour_manual(values=cbPalette)+
+p <- ggplot(dat_age, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
+  geom_point(aes(size = weights_g, shape = dist_code),show.legend=FALSE) + 
+  facet_grid(.~dist_code)+
   geom_line(y= 0, linetype="dotted") + 
   geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  apatheme +
-  theme(legend.title = element_blank(),
+  scale_color_manual(values=cbPalette)+
+  theme_bw()+
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
         legend.position = "bottom") + 
@@
 
-ggsave("figures/AgeEffect_log_DistFam_agesub.jpg", p)
+  jpeg(filename = "figures/Distractor_fam_AgeSubset.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
 
@@
 ```
+
+## Type of MP: Vowel, consonant, or tone
+
+### Type of MP: Vowel, consonant, or tone role in object identification
+
+```{r MPtype}
+db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
+
+#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
+
+rma_TypeFeaturesMP <- rma.mv(g_calc, g_var_calc, mods = ~type_feature, data = db_MP_type, random = ~collapse | short_cite)
+
+#summary(rma_TypeFeaturesMP)
+
+aov.type <- anova(rma_TypeFeaturesMP)
+
+type_feat <- round(coef(summary(rma_TypeFeaturesMP))[2,], 2)
+
+```
+
+The moderator test was not significant:
+`print(aov.type)`
+
+No significant effect of feature type:
+
+Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
+(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
+
+### Type of MP: Vowel, consonant, or tone role in object identification with age moderator
+
+```{r MPtype_age}
+db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
+
+#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
+
+rma_TypeFeaturesMPage <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)
+
+#summary(rma_TypeFeaturesMPage)
+
+aov.type <- anova(rma_TypeFeaturesMPage)
+
+type_feat <- round(coef(summary(rma_TypeFeaturesMPage))[4,], 2)
+
+```
+
+The moderator test was not significant:
+`print(aov.type)`
+
+No significant effect of feature type:
+
+Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
+(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
+
+### Type of MP: Vowel, consonant, or tone role in object identification with language family moderator
+
+```{r MPtype_lang}
+db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
+
+#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
+
+dat_type_sub <- subset(db_MP_type, lang_family != "Sino-Tibetian")
+
+rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family, data = dat_type_sub, random = ~collapse | short_cite)
+
+#summary(rma_TypeFeatures_Lang)
+
+aov.type <- anova(rma_TypeFeatures_Lang)
+
+type_feat <- round(coef(summary(rma_TypeFeatures_Lang))[4,], 2)
+
+```
+The moderator test was not significant:
+`print(aov.type)`
+
+No significant interaction between feature type and language family:
+
+Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
+(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
+
+### Type of MP: Vowel, consonant, or tone with condition moderator
+
+```{r MPtype_cond}
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
+#db_type <- subset(dat, type_feature != "consonant_and_vowel")
+
+rma_TypeFeaturesMPcond <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition, data = db_type, random = ~collapse | short_cite)
+
+#summary(rma_TypeFeaturesMPcond)
+
+aov.type <- anova(rma_TypeFeaturesMPcond)
+
+type_feat <- round(coef(summary(rma_TypeFeaturesMPcond))[2,], 2)
+
+```
+
+The moderator test was not significant:
+`print(aov.type)`
+
+No significant interaction between feature type and condition:
+
+Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
+(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
+
+### Type of MP: Vowel, consonant, or tone with condition and age moderators
+
+```{r MPtype_cond_age}
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
+#db_type <- subset(dat, type_feature != "consonant_and_vowel")
+
+rma_TypeFeaturesMPcondage <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~collapse | short_cite)
+
+summary(rma_TypeFeaturesMPcondage)
+
+aov.type <- anova(rma_TypeFeaturesMPcondage)
+
+type_feat <- round(coef(summary(rma_TypeFeaturesMPcondage))[8,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+There was a significant interaction between feature type, condition, and age:
+
+Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
+(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
+
+### Type of MP: Vowel, consonant, or tone with language family and condition moderators
+
+```{r MPtype_cond_lang}
+db_MP_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
+
+#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
+
+dat_type_sub <- subset(db_MP_type, lang_family != "Sino-Tibetian")
+
+rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family*condition, data = dat_type_sub, random = ~collapse | short_cite)
+
+summary(rma_TypeFeatures_Lang)
+
+aov.type <- anova(rma_TypeFeatures_Lang)
+
+type_feat <- round(coef(summary(rma_TypeFeatures_Lang))[8,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+There was a significant interaction between feature type, language family, and condition:
+
+Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
+(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
+
+### Type of MP: Vowel, consonant, or tone with language family, condition, and age moderators
+
+```{r MPtype_cond_lang}
+dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
+
+#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
+
+dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
+
+rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family*condition*age.C, data = dat_type_sub, random = ~collapse | short_cite)
+
+summary(rma_TypeFeatures_Lang)
+
+aov.type <- anova(rma_TypeFeatures_Lang)
+
+type_feat <- round(coef(summary(rma_TypeFeatures_Lang))[8,], 2)
+
+```
+The moderator test was significant:
+`print(aov.type)`
+
+There was a significant interaction between feature type, age, and language family, and condition:
+
+Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
+(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
+
+## Plotting MP type: Consonant, Vowel, or Tone?
+
+### Plot MP type: feature type, condition, and age
+
+```{r PlotCVEffect_cond_age}
+
+dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
+dat_type$type_feature <- ifelse(dat_type$type_feature == "consonant", "Consonant", "Vowel")
+
+#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
+
+#dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
+
+dat_type$condition_label = ifelse(dat_type$condition==1, "Correct", "Mispronunciation")
+
+p <- ggplot(dat_type, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
+    facet_grid(.~type_feature)+
+  geom_point(aes(size = weights_g),show.legend=FALSE) + 
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+  jpeg(filename = "figures/FeatureType_Cond_Age.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
+### Plot Language Family by MP type: Consonant, Vowel, or Tone?
+
+```{r PlotCVEffect_Lang}
+
+dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
+dat_type$type_feature <- ifelse(dat_type$type_feature == "consonant", "Consonant", "Vowel")
+
+#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
+
+dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
+
+dat_type_sub$condition_label = ifelse(dat_type_sub$condition==1, "Correct", "Mispronunciation")
+
+p <- ggplot(dat_type_sub, aes(condition_label, g_calc, fill = condition_label)) + 
+  geom_boxplot() + 
+  facet_grid(.~type_feature*lang_family)+
+  #geom_line(y= 0, linetype="dotted") + 
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
+    scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  xlab("Language Family") + 
+  ylab("Effect size Hedges' g")
+p
+
+ jpeg(filename = "figures/FeatureType_Cond_LangFam.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
+### Plot MP type: feature type, condition, and age
+
+```{r PlotCVEffect_cond_age_fam}
+
+dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
+dat_type$type_feature <- ifelse(dat_type$type_feature == "consonant", "Consonant", "Vowel")
+
+#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
+
+dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
+
+dat_type_sub$condition_label = ifelse(dat_type_sub$condition==1, "Correct", "Mispronunciation")
+
+p <- ggplot(dat_type_sub, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
+    facet_grid(.~type_feature*lang_family)+
+  geom_point(aes(size = weights_g),show.legend=FALSE) + 
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+  jpeg(filename = "figures/FeatureType_Cond_Age_LangFam.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```

### 2018-07-05 Paper_Analyses.Rmd
fleshing out analyses for paper

@@
 
-```
+#aov.type <- anova(rma_correct)
+
+sum_eff <- round(coef(summary(rma_correct))[1,], 2)
+
+```
+
+Correct pronunciations were significantly greater than 0:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
 
@@
 
-```
+sum_eff <- round(coef(summary(rma_MP))[1,], 2)
+
+```
+
+Mispronunciations were significantly greater than 0:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
 
@@
 ```{r MPEffect}
-db_ET_correct$condition <- 1
-db_ET_MP$condition <- 0
-
-dat <- bind_rows(db_ET_correct, db_ET_MP)
 
@@
 
-rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ collapse | short_cite)
-
-summary(rma_MPeffect_1)
-
-```
+#rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ collapse | short_cite)
+
+#summary(rma_MPeffect_1)
+
+aov.type <- anova(rma_MPeffect)
+
+sum_eff <- round(coef(summary(rma_MPeffect))[2,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.feat)`
+
+There was a significant effect of condition:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
+(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)
 
@@
 
-```
+aov.type <- anova(rma_correct_age)
+
+sum_eff <- round(coef(summary(rma_correct_age))[2,], 2)
+
+```
+
+The moderator test was not significant:
+`print(aov.feat)`
+
+There was no significant effect of age:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
+(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)
 
@@
 summary(rma_MP_age)
-```
+
+aov.type <- anova(rma_MP_age)
+
+sum_eff <- round(coef(summary(rma_MP_age))[2,], 2)
+
+```
+
+The moderator test was not significant:
+`print(aov.feat)`
+
+There was no significant effect of age:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
+(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)
 
@@
 ```{r MPEffect_age}
-db_ET_correct$condition <- 1
-db_ET_MP$condition <- 0
-
-dat <- bind_rows(db_ET_correct, db_ET_MP)
 
@@
 
-```
-
-## Plotting Mispronunciation Effect
+aov.type <- anova(rma_MPeffect_age)
+
+sum_eff <- round(coef(summary(rma_MPeffect_age))[4,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.feat)`
+
+There was no significant interaction between condition and age:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
+(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)
 
@@
 
-### Plot Mispronunciation Effect by Age (bw)
-
-```{r PlotMPEffect_BW}
-
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape=condition_label, color=condition_label),
-             show.legend=FALSE) + 
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_color_grey()+
-  theme_bw()+
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_BW.jpg", p,height= 3,width= 6)
-
-```
-
 ## Vocabulary size: Correlation between mispronunciation sensitivity and vocabulary
@@
 
-Hedges' g was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
+There was a significant effect of number of features changed:
+
+Hedges' g for `rownames(n_feat)` was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
 (95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)
-
-### Number of features with age moderator interaction
-
-Size of mispronunciation, measured in features changed
-
-```{r NFeatures_age}
-
-dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat.f, random = ~collapse | short_cite)
-
-summary(rma_NFeatures)
-aov.feat <- anova(rma_NFeatures)
-
-n_feat <- round(coef(summary(rma_NFeatures))[4,], 2)
-
-```
-
-The moderator test was significant:
-`print(aov.feat)`
-
-But there was no significant interaction between number of features changed and age:
-
-Hedges' g was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
-(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)
-
-### Number of features subset to age range
-Size of mispronunciation, measured in features changed
-
-Number of features is still significant
-
-```{r NFeatures_subset}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-mf <- subset(dat_f, n_feature == "3")
-min_age <- min(mf$mean_age_1)
-max_age <- max(mf$mean_age_1)
-
-dat_fage= dat_f%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-#dat_fage$n_feature <- ordered(dat_fage$n_feature, levels = c("0", "1", "2", "3"))
-#dat_fage$n_feature <- as.numeric(dat_fage$n_feature)
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat_f, random = ~collapse | short_cite)
-
-#summary(rma_NFeatures_agesub)
-
-```
-
-### Number of features with age moderator subset to age range
-Size of mispronunciation, measured in features changed
-
-No interaction between features and age
-
-```{r NFeatures_subset_age}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-mf <- subset(dat_f, n_feature == "3")
-min_age <- min(mf$mean_age_1)
-max_age <- max(mf$mean_age_1)
-
-dat_fage= dat_f%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-#dat_fage$n_feature <- ordered(dat_fage$n_feature, levels = c("0", "1", "2", "3"))
-#dat_fage$n_feature <- as.numeric(dat_fage$n_feature)
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat_f, random = ~collapse | short_cite)
-
-#summary(rma_NFeatures_agesub)
-
-```
-
-## Plotting number of Features Changed
 
@@
 
+### Number of features with age moderator interaction
+
+Size of mispronunciation, measured in features changed
+
+```{r NFeatures_age}
+
+dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
+                n_feature == "2" | n_feature == "3")
+
+#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
+rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat.f, random = ~collapse | short_cite)
+
+#summary(rma_NFeatures)
+aov.feat <- anova(rma_NFeatures)
+
+n_feat <- round(coef(summary(rma_NFeatures))[4,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.feat)`
+
+But there was no significant interaction between number of features changed and age:
+
+Hedges' g for `rownames(n_feat)` was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
+(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)
+
+### Number of features subset to age range
+Size of mispronunciation, measured in features changed
+
+```{r NFeatures_subset}
+
+dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
+                n_feature == "2" | n_feature == "3")
+
+mf <- subset(dat_f, n_feature == "3")
+min_age <- min(mf$mean_age_1)
+max_age <- max(mf$mean_age_1)
+
+dat_fage= dat_f%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+#dat_fage$n_feature <- ordered(dat_fage$n_feature, levels = c("0", "1", "2", "3"))
+#dat_fage$n_feature <- as.numeric(dat_fage$n_feature)
+
+#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
+rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat_f, random = ~collapse | short_cite)
+
+#summary(rma_NFeatures_agesub)
+
+```
+
+### Number of features with age moderator subset to age range
+Size of mispronunciation, measured in features changed
+
+No interaction between features and age
+
+```{r NFeatures_subset_age}
+
+dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
+                n_feature == "2" | n_feature == "3")
+
+mf <- subset(dat_f, n_feature == "3")
+min_age <- min(mf$mean_age_1)
+max_age <- max(mf$mean_age_1)
+
+dat_fage= dat_f%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+#dat_fage$n_feature <- ordered(dat_fage$n_feature, levels = c("0", "1", "2", "3"))
+#dat_fage$n_feature <- as.numeric(dat_fage$n_feature)
+
+#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
+rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat_f, random = ~collapse | short_cite)
+
+#summary(rma_NFeatures_agesub)
+
+```
+
 ## Distractor Familiarity (familiary, unfamiliar)
@@
 
-Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+Hedges' g for `rownames(sum_eff)` was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
 (95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
@@
 
-summary(rma_Distractor)
+#summary(rma_Distractor)
 
@@
 
-Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+Hedges' g for `rownames(sum_eff)` was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
 (95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
 
-### Distractor Familiarity, subset to same age range
-
-```{r DistractorTypeAgeRangeSubset_condition}
-
-fn <- subset(dat, object_pair=="familiar_novel")
-min_fn <- min(mf$mean_age_1)
-max_fn <- max(mf$mean_age_1)
-
-ff <- subset(dat, object_pair=="familiar_familiar")
-min_ff <- min(ff$mean_age_1)
-max_ff <- max(ff$mean_age_1)
-
-min_age <- pmax(min_fn, min_ff)
-max_age <- pmin(max_fn, max_ff)
-
-dat_age= db_ET_MP%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
-
-#summary(rma_Distractor)
-
-aov.type <- anova(rma_Distractor)
-
-sum_eff <- round(coef(summary(rma_Distractor))[2,], 2)
-
-```
-
-The moderator test was not significant:
-`print(aov.type)`
-
-There was no significant effect of distractor familiarity:
-
-Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
-(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
-
-### Distractor Familiarity with condition moderator, subset to same age range
-
-```{r DistractorTypeAgeRangeSubset_condition}
-
-fn <- subset(dat, object_pair=="familiar_novel")
-min_fn <- min(mf$mean_age_1)
-max_fn <- max(mf$mean_age_1)
-
-ff <- subset(dat, object_pair=="familiar_familiar")
-min_ff <- min(ff$mean_age_1)
-max_ff <- max(ff$mean_age_1)
-
-min_age <- pmax(min_fn, min_ff)
-max_age <- pmin(max_fn, max_ff)
-
-dat_age= dat%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
-
-summary(rma_DistractorAgeS)
-
-aov.type <- anova(rma_Distractor)
-
-sum_eff <- round(coef(summary(rma_Distractor))[4,], 2)
-
-```
-
-The moderator test was significant:
-`print(aov.type)`
-
-There was a significant interaction between distractor familiarity and condition:
-
-Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
-(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
-
-### Distractor Familiarity with age and condition moderator, subset to same age range
-
-```{r DistractorTypeAgeRangeSubset_agecondition}
-
-mf <- subset(dat, object_pair=="familiar_novel")
-min_age <- min(mf$mean_age_1)
-
-mf <- subset(dat, object_pair=="familiar_familiar")
-max_age <- max(mf$mean_age_1)
-
-dat_age= dat%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
-
-#summary(rma_DistractorAgeS)
-
-aov.type <- anova(rma_Distractor)
-
-sum_eff <- round(coef(summary(rma_Distractor))[8,], 2)
-
-```
-
-The moderator test was significant:
-`print(aov.type)`
-
-There was no significant interaction between distractor familiarity, condition, and age:
-
-Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
-(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
-
-### Plotting Distractor Familiarity
-
-### Plot Distractor Familiarity
+### Plot Distractor familiarity and condition
 
@@
 
-### Plot Distractor Familiarity
+### Distractor Familiarity, subset to same age range
+
+```{r DistractorTypeAgeRangeSubset_condition}
+
+fn <- subset(dat, object_pair=="familiar_novel")
+min_fn <- min(mf$mean_age_1)
+max_fn <- max(mf$mean_age_1)
+
+ff <- subset(dat, object_pair=="familiar_familiar")
+min_ff <- min(ff$mean_age_1)
+max_ff <- max(ff$mean_age_1)
+
+min_age <- pmax(min_fn, min_ff)
+max_age <- pmin(max_fn, max_ff)
+
+dat_age= db_ET_MP%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
+
+#summary(rma_Distractor)
+
+aov.type <- anova(rma_Distractor)
+
+sum_eff <- round(coef(summary(rma_Distractor))[2,], 2)
+
+```
+
+The moderator test was not significant:
+`print(aov.type)`
+
+There was no significant effect of distractor familiarity:
+
+Hedges' g for `rownames(sum_eff)` was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
+
+### Distractor Familiarity with condition moderator, subset to same age range
+
+```{r DistractorTypeAgeRangeSubset_condition}
+
+fn <- subset(dat, object_pair=="familiar_novel")
+min_fn <- min(mf$mean_age_1)
+max_fn <- max(mf$mean_age_1)
+
+ff <- subset(dat, object_pair=="familiar_familiar")
+min_ff <- min(ff$mean_age_1)
+max_ff <- max(ff$mean_age_1)
+
+min_age <- pmax(min_fn, min_ff)
+max_age <- pmin(max_fn, max_ff)
+
+dat_age= dat%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
+
+summary(rma_DistractorAgeS)
+
+aov.type <- anova(rma_Distractor)
+
+sum_eff <- round(coef(summary(rma_Distractor))[4,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+There was a significant interaction between distractor familiarity and condition:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
+
+### Plot Distractor Familiarity with condition, subset to same age range
 
@@
 
-### Plot Distractor Familiarity by age (subset to same age range)
-
-```{r PlotDistFamEffect_age}
-
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
-dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")
+### Distractor Familiarity with age and condition moderator, subset to same age range
+
+```{r DistractorTypeAgeRangeSubset_agecondition}
 
@@
 
-p <- ggplot(dat_age, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = dist_code),show.legend=FALSE) + 
-  facet_grid(.~dist_code)+
+rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
+
+#summary(rma_DistractorAgeS)
+
+aov.type <- anova(rma_Distractor)
+
+sum_eff <- round(coef(summary(rma_Distractor))[8,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+There was no significant interaction between distractor familiarity, condition, and age:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
+
+## Position of Mispronunciation (onset, medial)
+
+```{r Location}
+#table(db_ET_MP$mispron_location)
+
+db_ET_MPl = db_ET_MP %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
+
+#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
+rma_Location <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_MPl, random = ~collapse | short_cite)
+
+#summary(rma_Location)
+
+aov.type <- anova(rma_Location)
+
+sum_eff <- round(coef(summary(rma_Location))[2,], 2)
+
+```
+
+The moderator test was not significant:
+`print(aov.type)`
+
+There was no significant effect of mispronunciation position:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
+
+### Position of Mispronunciation with age moderator
+
+```{r Location_age}
+#table(db_ET_MP$mispron_location)
+
+db_ET_MPl = db_ET_MP %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
+
+rma_LocationAge <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
+
+#summary(rma_LocationAge)
+
+aov.type <- anova(rma_LocationAge)
+
+sum_eff <- round(coef(summary(rma_LocationAge))[2,], 2)
+
+```
+
+The moderator test was not significant:
+`print(aov.type)`
+
+There was no significant interaction between mispronunciation position and condition:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
+
+### Position of Mispronunciation with condition moderator
+
+```{r Location_condition}
+#table(db_ET_MP$mispron_location)
+
+db_ET_MPl = dat %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
+
+rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition, data = db_ET_MPl, random = ~collapse | short_cite)
+
+#summary(rma_LocationCondition)
+
+aov.type <- anova(rma_LocationCondition)
+
+sum_eff <- round(coef(summary(rma_LocationCondition))[4,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+But there was no significant interaction between mispronunciation position and condition:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
+
+### Position of Mispronunciation with age and condition moderators
+
+```{r Location_condition_age}
+#table(db_ET_MP$mispron_location)
+
+db_ET_MPl = dat %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
+
+rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
+
+summary(rma_LocationCondition)
+
+aov.type <- anova(rma_LocationCondition)
+
+sum_eff <- round(coef(summary(rma_LocationCondition))[8,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+But there was no significant interaction between mispronunciation position, condition, and age:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
+
+## Plotting Position of Mispronunciation
+```{r PlotPositionEffect}
+
+#dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial" |
+#                mispron_location == "offset")
+
+dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial")
+
+p <- ggplot(dat.p, aes(condition_label, g_calc, fill = condition_label)) + 
+  facet_grid(.~mispron_location)+
+  geom_boxplot() + 
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+  jpeg(filename = "figures/Mispronunciation_position.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
+## Distractor Overlap
+
+```{r DistractorOverlap}
+
+db_ET_MPo = db_ET_MP %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
+
+#summary(rma_DistractorOverlap)
+
+aov.type <- anova(rma_DistractorOverlap)
+
+sum_eff1 <- round(coef(summary(rma_DistractorOverlap))[2,], 2)
+sum_eff2 <- round(coef(summary(rma_DistractorOverlap))[3,], 2)
+
+```
+
+The moderator test was not significant:
+`print(aov.type)`
+
+There was no significant effect of distractor overlap:
+
+Hedges' g for `row.names(sum_eff1)` was `toString(sum_eff1$estimate)` (SE = `toString(sum_eff1$se`)
+(95% CI [`toString(sum_eff1$ci.lb)`, `toString(sum_eff1$ci.ub)`], p = `toString(sum_eff1$pval)`)
+
+Hedges' g `row.names(sum_eff2)` was `toString(sum_eff2$estimate)` (SE = `toString(sum_eff2$se`)
+(95% CI [`toString(sum_eff2$ci.lb)`, `toString(sum_eff2$ci.ub)`], p = `toString(sum_eff2$pval)`)
+
+### Distractor Overlap with age moderator
+
+```{r DistractorOverlap_age}
+
+db_ET_MPo = db_ET_MP %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
+
+#summary(rma_DistractorOverlap)  
+aov.type <- anova(rma_DistractorOverlap)
+
+sum_eff1 <- round(coef(summary(rma_DistractorOverlap))[5,], 2)
+sum_eff2 <- round(coef(summary(rma_DistractorOverlap))[6,], 2)
+
+```
+
+The moderator test was not significant:
+`print(aov.type)`
+
+There was no significant interaction between distractor overlap and age:
+
+Hedges' g for `row.names(sum_eff1)` was `toString(sum_eff1$estimate)` (SE = `toString(sum_eff1$se`)
+(95% CI [`toString(sum_eff1$ci.lb)`, `toString(sum_eff1$ci.ub)`], p = `toString(sum_eff1$pval)`)
+
+Hedges' g `row.names(sum_eff2)` was `toString(sum_eff2$estimate)` (SE = `toString(sum_eff2$se`)
+(95% CI [`toString(sum_eff2$ci.lb)`, `toString(sum_eff2$ci.ub)`], p = `toString(sum_eff2$pval)`)
+
+### Distractor Overlap with condition moderator
+
+```{r DistractorOverlap_condition}
+
+db_ET_MPo = dat %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
+
+summary(rma_DistractorOverlap)
+
+aov.type <- anova(rma_DistractorOverlap)
+
+sum_eff1 <- round(coef(summary(rma_DistractorOverlap))[5,], 2)
+sum_eff2 <- round(coef(summary(rma_DistractorOverlap))[6,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+There was a significant interaction between distractor overlap and condition:
+
+Hedges' g for `row.names(sum_eff1)` was `toString(sum_eff1$estimate)` (SE = `toString(sum_eff1$se`)
+(95% CI [`toString(sum_eff1$ci.lb)`, `toString(sum_eff1$ci.ub)`], p = `toString(sum_eff1$pval)`)
+
+Hedges' g `row.names(sum_eff2)` was `toString(sum_eff2$estimate)` (SE = `toString(sum_eff2$se`)
+(95% CI [`toString(sum_eff2$ci.lb)`, `toString(sum_eff2$ci.ub)`], p = `toString(sum_eff2$pval)`)
+
+### Plotting Distractor Overlap with condition
+
+```{r PlotDistOverlapEffect}
+
+db_ET_MPo = dat %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+p <- ggplot(db_ET_MPo, aes(condition_label, g_calc, fill = condition_label)) + 
+  facet_grid(.~distractor_overlap)+
+  geom_boxplot() + 
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+  jpeg(filename = "figures/Distractor_overlap.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
+### Distractor Overlap with age and condition moderators
+
+```{r DistractorOverlap_age_condition}
+
+db_ET_MPo = dat %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
+
+summary(rma_DistractorOverlap)
+
+aov.type <- anova(rma_DistractorOverlap)
+
+sum_eff1 <- round(coef(summary(rma_DistractorOverlap))[11,], 2)
+sum_eff2 <- round(coef(summary(rma_DistractorOverlap))[12,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+There was a significant interaction between distractor overlap, condition, and age:
+
+Hedges' g for `row.names(sum_eff1)` was `toString(sum_eff1$estimate)` (SE = `toString(sum_eff1$se`)
+(95% CI [`toString(sum_eff1$ci.lb)`, `toString(sum_eff1$ci.ub)`], p = `toString(sum_eff1$pval)`)
+
+Hedges' g `row.names(sum_eff2)` was `toString(sum_eff2$estimate)` (SE = `toString(sum_eff2$se`)
+(95% CI [`toString(sum_eff2$ci.lb)`, `toString(sum_eff2$ci.ub)`], p = `toString(sum_eff2$pval)`)
+
+### Plot Distractor Overlap, condition, and age
+
+```{r PlotCVEffect_cond_age_fam}
+
+db_ET_MPo = dat %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+p <- ggplot(db_ET_MPo, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
+    facet_grid(.~distractor_overlap)+
+  geom_point(aes(size = weights_g),show.legend=FALSE) + 
   geom_line(y= 0, linetype="dotted") + 
   geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_color_manual(values=cbPalette)+
-  theme_bw()+
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
         legend.position = "bottom") + 
@@
   ylab("Effect size Hedges' g")
-p
-
-  jpeg(filename = "figures/Distractor_fam_AgeSubset.jpg", 
+
+p
+
+  jpeg(filename = "figures/Distractor_overlap_age.jpg", 
        width = 500, height = 300, units = "px")
@@
   dev.off()
-
-```
-
-## Position of Mispronunciation (onset, medial)
-
-```{r Location}
-#table(db_ET_MP$mispron_location)
-
-db_ET_MPl = db_ET_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_Location <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_MPl, random = ~collapse | short_cite)
-
-summary(rma_Location)
-
-```
-
-### Position of Mispronunciation with age moderator
-
-```{r Location_age}
-#table(db_ET_MP$mispron_location)
-
-db_ET_MPl = db_ET_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-rma_LocationAge <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
-
-summary(rma_LocationAge)
-```
-
-### Position of Mispronunciation with condition moderator
-
-```{r Location_condition}
-#table(db_ET_MP$mispron_location)
-
-db_ET_MPl = db_ET_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition, data = db_ET_MPl, random = ~collapse | short_cite)
-
-summary(rma_LocationCondition)
-```
-
-### Position of Mispronunciation with age and condition moderators
-
-```{r Location_condition_age}
-#table(db_ET_MP$mispron_location)
-
-db_ET_MPl = db_ET_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
-
-summary(rma_LocationCondition)
-```
-
-## Plotting Position of Mispronunciation
-```{r PlotPositionEffect}
-
-#dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial" |
-#                mispron_location == "offset")
-
-dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial")
-
-p <- ggplot(dat.p, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = mispron_location),show.legend=FALSE) + 
-  facet_grid(.~mispron_location)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_position.jpg", p)
-
-```
-
-## Distractor Overlap
-
-```{r DistractorOverlap}
-
-rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
-
-summary(rma_DistractorOverlap)
-
-```
-
-### Distractor Overlap with age moderator
-
-```{r DistractorOverlap_age}
-
-rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
-
-summary(rma_DistractorOverlap)
-
-```
-
-### Distractor Overlap with condition moderator
-
-```{r DistractorOverlap_condition}
-
-rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
-
-summary(rma_DistractorOverlap)
-
-```
-
-### Distractor Overlap with age and condition moderators
-
-```{r DistractorOverlap_age_condition}
-
-rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
-
-summary(rma_DistractorOverlap)
-
-```
-
-## Plotting Distractor Overlap
-
-```{r PlotDistOverlapEffect}
-
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = distractor_overlap),show.legend=FALSE) + 
-  facet_grid(.~distractor_overlap)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_distractor_overlap.jpg", p)
-
-```
-
-## Language effect
-
-```{r LanguageEffectAnalyses}
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")
-
-dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
-                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
-                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
-                           dat$native_lang=="German", "Germanic",
-                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
-                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
-                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))
-
-rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~lang_family, data = dat, random = ~ collapse | short_cite)
-summary(rma_lang_interaction)
-
-```
-
-### Language effect with age moderator
-
-```{r LanguageEffectAnalyses_age}
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")
-
-dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
-                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
-                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
-                           dat$native_lang=="German", "Germanic",
-                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
-                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
-                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))
-
-rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*lang_family, data = dat, random = ~ collapse | short_cite)
-summary(rma_lang_interaction)
-
-```
-
-### Language effect with condition moderator
-
-```{r LanguageEffectAnalyses_condition}
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")
-
-dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
-                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
-                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
-                           dat$native_lang=="German", "Germanic",
-                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
-                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
-                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))
-
-rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~condition*lang_family, data = dat, random = ~ collapse | short_cite)
-summary(rma_lang_interaction)
-
-```
-
-### Language effect with age and condition moderators
-
-```{r LanguageEffectAnalyses_condition_age}
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")
-
-dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
-                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
-                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
-                           dat$native_lang=="German", "Germanic",
-                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
-                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
-                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))
-
-rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*lang_family, data = dat, random = ~ collapse | short_cite)
-summary(rma_lang_interaction)
-
-```
-
-## Plotting Language Effect
-```{r PlotLanguageEffect}
-
-dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
-                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
-                           dat$native_lang=="German", "Germanic",
-                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
-                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
-                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))
-
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = lang_family),show.legend=FALSE) + 
-  facet_grid(.~lang_family)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_language.jpg", p)
 
@@
 
-Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
+Hedges' g for `rownames(sum_eff)`  was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
 (95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
@@
 
-Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
+Hedges' g for `rownames(sum_eff)`  was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
 (95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
-
-### Type of MP: Vowel, consonant, or tone with language family and condition moderators
-
-```{r MPtype_cond_lang}
-db_MP_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
-
-#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
-
-dat_type_sub <- subset(db_MP_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family*condition, data = dat_type_sub, random = ~collapse | short_cite)
-
-summary(rma_TypeFeatures_Lang)
-
-aov.type <- anova(rma_TypeFeatures_Lang)
-
-type_feat <- round(coef(summary(rma_TypeFeatures_Lang))[8,], 2)
-
-```
-
-The moderator test was significant:
-`print(aov.type)`
-
-There was a significant interaction between feature type, language family, and condition:
-
-Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
-(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
-
-### Type of MP: Vowel, consonant, or tone with language family, condition, and age moderators
-
-```{r MPtype_cond_lang}
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
-
-#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
-
-dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family*condition*age.C, data = dat_type_sub, random = ~collapse | short_cite)
-
-summary(rma_TypeFeatures_Lang)
-
-aov.type <- anova(rma_TypeFeatures_Lang)
-
-type_feat <- round(coef(summary(rma_TypeFeatures_Lang))[8,], 2)
-
-```
-The moderator test was significant:
-`print(aov.type)`
-
-There was a significant interaction between feature type, age, and language family, and condition:
-
-Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
-(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
-
-## Plotting MP type: Consonant, Vowel, or Tone?
 
@@
 ```
+
+### Type of MP: Vowel, consonant, or tone with language family and condition moderators
+
+```{r MPtype_cond_lang}
+db_MP_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
+
+#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
+
+dat_type_sub <- subset(db_MP_type, lang_family != "Sino-Tibetian")
+
+rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family*condition, data = dat_type_sub, random = ~collapse | short_cite)
+
+summary(rma_TypeFeatures_Lang)
+
+aov.type <- anova(rma_TypeFeatures_Lang)
+
+type_feat <- round(coef(summary(rma_TypeFeatures_Lang))[8,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+There was a significant interaction between feature type, language family, and condition:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
+(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
 
@@
 
+### Type of MP: Vowel, consonant, or tone with language family, condition, and age moderators
+
+```{r MPtype_cond_lang}
+dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
+
+#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
+
+dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
+
+rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family*condition*age.C, data = dat_type_sub, random = ~collapse | short_cite)
+
+summary(rma_TypeFeatures_Lang)
+
+aov.type <- anova(rma_TypeFeatures_Lang)
+
+type_feat <- round(coef(summary(rma_TypeFeatures_Lang))[8,], 2)
+
+```
+The moderator test was significant:
+`print(aov.type)`
+
+There was a significant interaction between feature type, age, and language family, and condition:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
+(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
+
 ### Plot MP type: feature type, condition, and age
@@
 ```
+
+## Language effect
+
+```{r LanguageEffectAnalyses}
+
+dat_lang <- subset(db_ET_MP, lang_family != "Sino-Tibetian")
+
+rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~lang_family, data = dat_lang, random = ~ collapse | short_cite)
+#summary(rma_lang_interaction)
+
+aov.type <- anova(rma_lang_interaction)
+
+type_feat <- round(coef(summary(rma_lang_interaction))[2,], 2)
+
+```
+
+The moderator test was not significant:
+`print(aov.type)`
+
+There was no significant effect of language family:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
+(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
+
+### Language effect with age moderator
+
+```{r LanguageEffectAnalyses_age}
+
+dat_lang <- subset(db_ET_MP, lang_family != "Sino-Tibetian")
+
+rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*lang_family, data = dat_lang, random = ~ collapse | short_cite)
+summary(rma_lang_interaction)
+
+aov.type <- anova(rma_lang_interaction)
+
+type_feat <- round(coef(summary(rma_lang_interaction))[4,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+There was a significant interaction between language family and age:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
+(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
+
+### Plot Language effect with age
+
+```{r PlotLanguageEffect}
+
+dat_lang <- subset(dat, lang_family != "Sino-Tibetian")
+
+p <- ggplot(dat_lang, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
+    facet_grid(.~lang_family)+
+  geom_point(aes(size = weights_g),show.legend=FALSE) + 
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+  jpeg(filename = "figures/Language_Age.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+```
+
+### Language effect with condition moderator
+
+```{r LanguageEffectAnalyses_condition}
+
+dat_lang <- subset(dat, lang_family != "Sino-Tibetian")
+
+rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~condition*lang_family, data = dat_lang, random = ~ collapse | short_cite)
+#summary(rma_lang_interaction)
+
+aov.type <- anova(rma_lang_interaction)
+
+type_feat <- round(coef(summary(rma_lang_interaction))[4,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+But, there was no significant interaction between language family and condition:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
+(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
+
+### Language effect with age and condition moderators
+
+```{r LanguageEffectAnalyses_condition_age}
+
+dat_lang <- subset(dat, lang_family != "Sino-Tibetian")
+
+rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*lang_family, data = dat_lang, random = ~ collapse | short_cite)
+#summary(rma_lang_interaction)
+
+aov.type <- anova(rma_lang_interaction)
+
+type_feat <- round(coef(summary(rma_lang_interaction))[8,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+But, there was no significant interaction between language family, age, and condition:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
+(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

### 2018-07-18 Paper_Analyses_monolinguals.Rmd
Cog_Sci_Talk_prep

--- 2018-07-05 Paper_Analyses.Rmd
@@
 ---
-title: "MP MetaAnalysis"
+title: "MP MetaAnalysis Monolinguals"
 author: "Christina Bergmann"
@@
   mutate(age.C = (mean_age_1-mean(mean_age_1, na.rm=TRUE))/30.44) %>%
-  filter(mean_age_months < 31)
+  filter(mean_age_months < 31, infant_type == "typical")
 
@@
 
-```{r PlotDistFamEffect_NoAge_AgeMatch}
+```{r PlotDistFamEffect_condition}
 
@@
 
-```{r DistractorTypeAgeRangeSubset_condition}
+```{r DistractorTypeAgeRangeSubset}
 
@@
 
-```{r PlotCVEffect_cond_age_fam}
+```{r PlotDistOverlap_cond_age}
 
@@
 
-```{r MPtype_cond_lang}
+```{r MPtype_cond_lang_age}
 dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )

### 2018-09-19 Paper_Analyses.Rmd
updated Methods/Results

--- 2018-06-21 Paper_Analyses.Rmd
@@
 library(knitr)
+library(ggplot2)
 library(wesanderson)
+library(grid)
+library(gridExtra)
+
+# set Table count at 0
+t_num <- 0
+
+# set Figure count at 0
+f_num <- 0
+
+r2 <- function(x){ round(x, 2)}
+
+psig <- function(x){
+  ifelse(x < .0001, "< .0001",
+         ifelse(x < .001, "< .001",
+                ifelse(x < .01, "< .01",
+                       ifelse(x > .01 & x < .05, paste("=", r2(x), sep = " "), paste("=", r2(x), sep = " ")))))
+}
 
@@
 ```{r ReadIn,  echo = FALSE}
-#Get the data
+
+#Get the effect size data
 source("scripts/calculateES.R")
@@
 
-# Plotting defaults
+Plotting defaults
 
-```{r PlotAPATheme}
+```{r PlotAPATheme, echo = FALSE}
 #Themes and plot
@@
 
+# Color Blind palette:
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
 ```
 
-# Descriptive data
+# Methods
 
-The database contains data from `r length(unique(dat$short_cite))` papers. In the tables below, we provide more descriptive information.
+The present meta-analysis was conducted with maximal transparency and reproducibility in mind.
+To this end, we provide all data and analysis scripts on the supplementary website (https://osf.io/rvbjs/) and open our meta-analysis up for updates (Tsuji, Bergmann, & Cristia, 2014).
+In addition, we follow the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials.
+(Moher, Liberati, Tetzlaff, Altman & PRISMAGroup, 2009).
 
-The next table shows what type of publications were included in our meta-analysis
+## Study Selection
+We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list.
+This process yielded 110 items.
+We then used the google scholar search engine to search for papers citing the original Swingley & Aslin (2000) publication.
+This search was conducted on 22 September, 2017 and yielded 288 results.
+We screened the 398 items, removing 99 duplicate items.
+We screened remaining 299 items for their title and abstract to determine whether it met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition; (3) infants studied were under 36-months-of-age; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; 5) the stimuli were auditory speech.
+The final sample (n = *`r length(unique(dat$short_cite))`*) consisted of `r with(dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(dat, n_distinct(short_cite[publication_status == "dissertation"]))` thesis, and `r with(dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports.
+We will refer to these items collectively as papers.
+Table 1 (Summary Table) provides an overview of all papers included in the present meta-analysis.
+
 ```{r DescriptivesPubtype, echo = FALSE}
+
+t_num <- t_num+1
 
@@
 
+pi <- dat[,c("short_cite", "publication_status")]
+pi <- unique(pi)
+
+c.plot <- ggplot(pi, aes(x= publication_status)) + 
+  geom_text(stat='count', aes(label=..count..), vjust=-1, size = 5)+
+  geom_bar(stat="count")+
+  coord_cartesian(ylim = c(0, 30))+
+  apatheme+
+  theme(axis.text.x = element_text(size = 20, angle = -45, hjust = .11),
+        axis.title.x = element_blank())
+
+c.plot
+
+  jpeg(filename = "figures/Pub_count.jpg", 
+       width = 500, height = 500, units = "px")
+
+  c.plot
+
+  dev.off()
+
 ```
 
-## Type of data on which we calculated effect sizes
-The table below shows based on which data we calculated effect sizes.
+## Data Entry
 
+The `r length(unique(dat$short_cite))` papers we identified as relevant were then coded with as much detail as possible (Tsuji, Bergmann, & Cristia, 2014; Bergmann et al., in press).
+For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results.
+For the present analyses, we focus on the following characteristics:
+1 Condition: Were words mispronounced or not;
+2 Mean age reported per group of infants, in days;
+3 Vocabulary size:  
+4 Size of mispronunciation, measured in features changed;
+5 Distractor familiarity: familiar, unfamiliar;
+6 Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;
+7 Position of mispronunciation: onset, medial, offset;
+8 Type of mispronunciation: consonant, vowel;
+
+We separated out conditions according to whether or not the target word was mispronounced to be able to investigate both infants' looking to the target picture separated by whether or not words were mispronounced and their mispronunciation sensitivity, which is the difference between looking in correct and mispronounced trials.
+When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  (e.g., consonant versus vowel mispronunciations; Mani & Plunkett, 2007).
+The fact that the same infants have contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section).
+We will call each row a record; in total there were `r nrow(dat)` records in our data.
+
+## Data analysis
+
+```{r DescriptivesComparison, echo = FALSE}
+db_ET_correct$within_measure_descriptive <- ifelse(db_ET_correct$within_measure == "post",
+ "post-naming phase compared with chance (=50%)",
+ifelse(db_ET_correct$within_measure == "pre_post", "post-naming compared to pre-naming phase", "post-pre difference score compared with chance (=0)"))
+
+comparison_info <- db_ET_correct %>%
+  group_by(within_measure_descriptive) %>%
+  summarize(n_unique = n_distinct(short_cite), count = n())
+
+kable(comparison_info)
+#table(db_ET_MP$es_method)
+```
 ```{r DescriptivesES, echo = FALSE}
@@
 
-## Number of unique infants
+All scripts and raw data are available on Open Science Framework (OSF).
+INSERT LINK AS FOOTNOTE HERE.
+Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to a baseline measurement.
+PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images.
+Across papers the baseline comparison varied; we used the baseline reported by the authors of each paper.
+Most papers (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post_naming_effect"]))`) subtracted the PTL score for the pre-naming phase from the PTL score for the post-naming phase.
+When interpreting this difference score, a positive value indicates that infants increased their looks to the target after hearing the naming label (correct or mispronounced).
+Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post"]))`) or compared post-naming PTL with chance (50%, (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "post"]))`)).
+For these comparisons, a positive difference score or a post-naming phase PTL score that is greater than the pre-naming phase PTL or chance indicate target looks that indicate object recognition after hearing the naming label.
 
-```{r DescriptivesInfnum, echo = FALSE}
+We report effect sizes for infants' looks to target pictures after hearing a correctly pronounced or mispronounced label (object identification) as well as the difference between effect sizes for correct and mispronounced trials (mispronunciation sensitivity).
+The effect size we report in the present paper are based on comparison of means, standardized by their variance.
+The most well-known effect size from this group is Cohen's *d* (Cite cohen).
+To correct for the small sample sizes common in infant research, however, we use as a dependent variable Hedges' *g* instead of Cohen's *d* (Hedges, 1981; Morris, 2000).
 
-infnum_info <- dat[,c("unique_ID", "same_infant", "expt_num", "n_1")]
-infnum_info <- unique(infnum_info)
+No authors made their raw data available.
+Instead, we calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(dat, n_distinct(short_cite[es_method == "group_means_one" | es_method == "group_means_two"]))`) or using reported t-values (*n* = `r with(dat, n_distinct(short_cite[es_method == "t_one" | es_method == "t_two"]))`).
+Raw means and standard deviations were extracted from figures for `r with(dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers.
+In a within-participation design, when two means are compared (i.e.
+looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values.
+One paper reported this correlation, while we were able to compute correlations using means, standard deviations, and t-values (following Csibra, et al.
+2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, submitted).
+Correlations were imputed for the remaining papers (see Black & Bergmann, 2017, for the same procedure).
+We computed a total of `r sum(dat$is_mp == 0)` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)` for mispronunciations.
 
-number_of_infants <- sum(infnum_info$n_1)
+To take into account the fact that the same infants contributed to multiple datapoints, we analyze our results in a multilevel approach using the R (R citation) package metafor (Viechtbauer, 20XX, Multulevel reference).
+This means we model as random effect that effect sizes from the same paper share are based on more similar studies than those across papers and that nested therein effects can stem from the same infants.
+
+## Publication Bias
+
+In the psychological sciences, there is a documented reluctance to publish null results.
+As a result, there is a potential for significant results to be valued over non-significant results (see Ferguson & Heene, 2012).
+To examine whether this is also the case in the mispronunciation sensitivity literature, which would bias the data analyzed in this meta-analysis, we conduct two tests.
+We first examine whether effect sizes are distributed as expected based on sampling error using the rank correlation test of funnel plot asymmetry with the R (R Core Team, 2016) package metafor (Viechtbauer, 2010).
+Effect szes with low-variance are closer to the estimated mean, while effect sizes with high-variance show an increased, evenly-distributed spread around the estimated mean.
+Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app (v4.0, p-curve.com; Simonsohn, Simmons, & Nelson, 2014).
+This tests for evidential value by examining whether the p-values have an expected distribution, regardless of whether the null hypothesis is true or not, as well as whether there is a larger proportion of p-values just below the typical alpha threshold of .05, which may indicate questionable research practices.
+Responses to correctly pronounced and mispronounced labels are predicted to show different patterns of looking behavior; as a result, we conduct these two analyses to assess publication bias separately for both conditions.
+
+## Meta-analysis
+
+The models reported are hierarchical random-effects models (infant groups nested within papers) of variance-weighted effect sizes with the R (R Core Team, 2016) package metafor
+(Viechtbauer, 2010).
+To investigate how development impacts mispronunciation sensitivity, our core theoretical investigation, we introduce age (centered; in days but transformed into months for ease of reading by dividing by 30.44) as a moderator to our main model.
+For the subsequent investigations of experimental characteristics, we introduce each characteristic as a moderator (more detail below).
+
+# Results
+
+## Publication Bias
+
+```{r FunnelPlotAsymm_correct, echo = FALSE}
+
+rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ collapse | short_cite)
+# Publication bias can become visible in funnel plot asymmetry. 
+# Metafor comes with several options to check this, I chose ranktest and regtest
+# correct object identification
+rmac <- ranktest(rma_correct)
+#rmac
 
@@
 
-The database contains data from `r number_of_infants` unique infants.
+```{r FunnelPlotAsymm_misp, echo=FALSE}
 
-## Number of unique experimental conditions
+rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ collapse | short_cite)
 
-```{r DescriptivesExpCond, echo = FALSE}
+# mispronounced object identification
+rmam <- ranktest(rma_MP)
+#rmam
+```
 
-condnum_info <- dat[,c("unique_ID", "same_infant", "expt_num", "expt_condition")]
-condnum_info <- unique(condnum_info)
+Figure 1 plots the funnel plots for object identification for both correct pronunciations and mispronunciations (code adapted from Sakaluk, 2016).
+Funnel plot assymmetry was significant for both correct pronunciations (Kendall's $\tau$ = `r r2(rmac$tau)`, *p* `r psig(rmac$pval)`) and mispronunciations (Kendall's $\tau$ = `r r2(rmam$tau)`, *p* `r psig(rmam$pval)`).
+These results, in conjunction with the assymmetric funnel plot (Figure 1) indicate bias in the literature.
+This is particularly evident for correct pronunciations, where larger effect sizes have greater variance (bottom right corner) and there are a smaller number of more precise effect sizes (i.e.
+smaller variance) than expected (top left, outside the triangle).
 
-number_of_cond <- nrow(condnum_info)
+```{r FunnelPrep, echo = FALSE}
+### Plots adapted from Sakaluk, 2016, see also Black & Bergmann, 2017
+### https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/
+
+#Themes and plot
+funnel_theme=theme_bw()+
+  theme(#panel.grid.major=element_blank(),
+    #panel.grid.minor=element_blank(),
+    #panel.border=element_blank(),
+    axis.line=element_line(),
+    text=element_text(family='Times', size=22),
+    legend.position='none')
 
@@
 
-The database contains data from `r number_of_cond` unique experimental conditions
+```{r FunnelCorrect, echo = FALSE}
 
-## Type of comparison of the time-course data calculated
-We also have different ways of comparison of the time-course data, as the next table shows.
+#Rename a bunch of things for ease
+dat_co = db_ET_correct
+#dat_co=db_ET_correct
+dat_co <-
+  dat_co %>% 
+  rename(cite = short_cite,
+         yi = g_calc,
+         vi = g_var_calc)
 
-```{r DescriptivesComparison, echo = FALSE}
-db_ET_correct$within_measure_descriptive <- ifelse(db_ET_correct$within_measure == "post",
- "post-naming phase compared with chance (=50%)",
-ifelse(db_ET_correct$within_measure == "pre_post", "post-naming compared to pre-naming phase", "post-pre difference score compared with chance (=0)"))
+#Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order
 
-comparison_info <- db_ET_correct %>%
-  group_by(within_measure_descriptive) %>%
-  summarize(n_unique = n_distinct(short_cite), count = n())
+dat_co <-
+  dat_co %>% 
+  select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>% 
+  mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
+  arrange(desc(yi))
 
-kable(comparison_info)
-#table(db_ET_MP$es_method)
-```
+#Get standard errors from variances
+dat_co$se = sqrt(dat_co$vi)
 
-## Type of distractor
-This is a summary of the type of distractor used in an experiment
+#Calculate 95% CI values
+dat_co$lowerci = (-1.96*dat_co$se)+dat_co$yi
+dat_co$upperci = (1.96*dat_co$se)+dat_co$yi
 
-```{r DescriptivesDISTRACT, echo = FALSE}
-#What kind of distractor was used?
+#Store the meta-analytic estimate and its standard error from whatever model you run
+#summary(rma_correct)
+estimate_co = coef(summary(rma_correct))$estimate
+se_co = coef(summary(rma_correct))$se
 
-distr_info <- distract_dat %>%
-  group_by(object_pair) %>%
-  summarize(count = n())
+#Store a vector of values that spans the range from 0
+#to the max value of impression (standard error) in your dataset.
+#Make the increment (the final value) small enough (I choose 0.001)
+#to ensure your whole range of data is captured
+se.seq_co=seq(0, max(dat_co$se), 0.001)
 
-kable(distr_info)
+#Now, compute vectors of the lower-limit and upper limit values for
+#the 95% CI region, using the range of SE that you generated in the previous step, 
+#and the stored value of your meta-analytic estimate.
+ll95_co = estimate_co-(1.96*se.seq_co)
+ul95_co = estimate_co+(1.96*se.seq_co)
+
+#You can do this for a 99% CI region too
+ll99_co = estimate_co-(3.29*se.seq_co)
+ul99_co = estimate_co+(3.29*se.seq_co)
+
+#And finally, do the same thing except now calculating the confidence interval
+#for your meta-analytic estimate based on the stored value of its standard error
+meanll95_co = estimate_co-(1.96*se_co)
+meanul95_co = estimate_co+(1.96*se_co)
+
+#Now, smash all of those calculated values into one data frame (called 'dfCI').
+#You might get a warning about '...row names were found from a short variable...'
+#You can ignore it.
+dfCI_co = data.frame(ll95_co, ul95_co, ll99_co,
+                  ul99_co, se.seq_co, estimate_co, meanll95_co, meanul95_co)
+
+#Now we can actually make the funnel plot.
+#Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
+fp_co = ggplot(aes(x = se, y = yi), data = dat_co) +
+  #Regression line for the FP asymmetry
+  geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_co) +
+  #Add your data-points to the scatterplot
+  geom_point(size = 2.5, colour="black") +
+  #
+  #Give the x- and y- axes informative labels
+  xlab('Standard Error') + ylab('Hedge\'s g')+
+  # give it a title
+    ggtitle("Correct") +
+    # make sure both plots have same scale
+    # still ylim because we haven't flipped yet
+    #coord_cartesian(ylim = c(0.5, 0))+
+  #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
+  #to the lower and upper limits of your 95% CI region
+  #And dashed lines corresponding to your 99% CI region
+  #Add lines corresponding to 0 and estimate
+  geom_line(aes(x = se.seq_co, y = 0), linetype = 'solid', data = dfCI_co) +
+  geom_line(aes(x = se.seq_co, y = estimate_co), linetype = 'dashed', data = dfCI_co) +
+  geom_line(aes(x = se.seq_co, y = ll95_co), linetype = 'dotted', data = dfCI_co) +
+  geom_line(aes(x = se.seq_co, y = ul95_co), linetype = 'dotted', data = dfCI_co) +
+  #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
+  #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
+  #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
+  #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
+  #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
+  #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
+  #at the top of the figure once we swap the x- and y-axes...
+  scale_x_reverse()+
+  #Specify the range and interval for the tick-marks of the y-axis (Zr);
+  #Choose values that work for you based on your data
+  #scale_y_continuous(breaks=seq(-.45,0.8,0.25))+
+  #And now we flip the axes so that SE is on y- and Zr is on x-
+  coord_flip()+
+  #Finally, apply my APA-format theme (see code at end of post).
+  #You could, alternatively, specify theme_bw() instead.
+  funnel_theme
+
+#Call the pretty funnel plot
+#fp_co
+#ggsave("figures/FunnelPlot_correct.pdf")
 
@@
 
-## Whether word was pronounced both correctly as well as mispronounced
-This is a summary of whether an experiment had both correct and mispronounced versions of the word in the experiment
+```{r FunnelMisp, echo = FALSE}
 
-```{r DescriptivesCoMp, echo = FALSE}
-#What kind of distractor was used?
+  #Rename a bunch of things for ease
+dat_mp = db_ET_MP  
+#dat_mp=db_ET_MP
+  dat_mp <-
+    dat_mp %>% 
+    rename(cite = short_cite,
+           yi = g_calc,
+           vi = g_var_calc)
 
-mix_info <- mix_co_mp %>%
-  group_by(word_correct_and_MP) %>%
-  summarize(count = n())
+  #Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order
 
-kable(mix_info)
+  dat_mp <-
+    dat_mp %>% 
+    select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>% 
+    mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
+    arrange(desc(yi))
+
+  #Get standard errors from variances
+  dat_mp$se = sqrt(dat_mp$vi)
+
+  #Calculate 95% CI values
+  dat_mp$lowerci = (-1.96*dat_mp$se)+dat_mp$yi
+  dat_mp$upperci = (1.96*dat_mp$se)+dat_mp$yi
+
+  #Store the meta-analytic estimate and its standard error from whatever model you run (substitute your own values)
+  #summary(rma_MP)
+  estimate_mp = coef(summary(rma_MP))$estimate
+  se_mp = coef(summary(rma_MP))$se
+
+  #Store a vector of values that spans the range from 0
+  #to the max value of impression (standard error) in your dataset.
+  #Make the increment (the final value) small enough (I choose 0.001)
+  #to ensure your whole range of data is captured
+  se.seq_mp=seq(0, max(dat_mp$se), 0.001)
+
+  #Now, compute vectors of the lower-limit and upper limit values for
+  #the 95% CI region, using the range of SE that you generated in the previous step, 
+  #and the stored value of your meta-analytic estimate.
+  ll95_mp = estimate_mp-(1.96*se.seq_mp)
+  ul95_mp = estimate_mp+(1.96*se.seq_mp)
+
+  #You can do this for a 99% CI region too
+  ll99_mp = estimate_mp-(3.29*se.seq_mp)
+  ul99_mp = estimate_mp+(3.29*se.seq_mp)
+
+  #And finally, do the same thing except now calculating the confidence interval
+  #for your meta-analytic estimate based on the stored value of its standard error
+  meanll95_mp = estimate_mp-(1.96*se_mp)
+  meanul95_mp = estimate_mp+(1.96*se_mp)
+
+  #Now, smash all of those calculated values into one data frame (called 'dfCI').
+  #You might get a warning about '...row names were found from a short variable...'
+  #You can ignore it.
+  dfCI_mp = data.frame(ll95_mp, ul95_mp, ll99_mp,
+                       ul99_mp, se.seq_mp, estimate_mp, meanll95_mp, meanul95_mp)
+
+  #Now we can actually make the funnel plot.
+  #Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
+  fp_mp = ggplot(aes(x = se, y = yi), data = dat_mp) +
+    #Regression line for the FP asymmetry
+    geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_mp) +
+    #Add your data-points to the scatterplot
+    geom_point(size = 2.5, colour="black") +
+    #
+  #Give the x- and y- axes informative labels
+  xlab('Standard Error') + 
+    # remove y label because it will be combined with the other funnel plot
+    ylab('Hedge\'s g')+
+    # give it a title
+    ggtitle("Mispronunciation") +
+    # make sure both plots have same scale
+    # still xlim because we haven't flipped yet
+    #coord_cartesian(xlim = c(0.5, 1))+
+    #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
+    #to the lower and upper limits of your 95% CI region
+    #And dashed lines corresponding to your 99% CI region
+    #Add lines corresponding to 0 and estimate
+    geom_line(aes(x = se.seq_mp, y = 0), linetype = 'solid', data = dfCI_mp) +
+    geom_line(aes(x = se.seq_mp, y = estimate_mp), linetype = 'dashed', data = dfCI_mp) +
+    geom_line(aes(x = se.seq_mp, y = ll95_mp), linetype = 'dotted', data = dfCI_mp) +
+    geom_line(aes(x = se.seq_mp, y = ul95_mp), linetype = 'dotted', data = dfCI_mp) +
+    #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
+    #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
+    #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
+    #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
+    #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
+    #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
+    #at the top of the figure once we swap the x- and y-axes...
+    scale_x_reverse()+
+    #Specify the range and interval for the tick-marks of the y-axis (Zr);
+    #Choose values that work for you based on your data
+    #scale_y_mpntinuous(breaks=seq(-.45,0.8,0.25))+
+    #And now we flip the axes so that SE is on y- and Zr is on x-
+    coord_flip()+
+    #Finally, apply my APA-format theme (see previous).
+    #You could, alternatively, specify theme_bw() instead.
+    funnel_theme +
+    theme(axis.title.y = element_blank())
+
+  #Call the pretty funnel plot
+  #fp_mp
+#  ggsave("figures/FunnelPlot_misp.pdf")
 
@@
 
-## Size of analysis time window
+## Figure 1
 
-Where possible, we noted the time window for analysis. First, let's look at the offset (in milliseconds) after the start of the word, i.e. the begin of a give analysis window for a naming effect
+```{r FunnelCombo, echo = FALSE}
 
-```{r TimeWindowOffset}
-offset_info <- time_wind_dat %>%
-  group_by(offset) %>%
-  summarize(count = n())
+  jpeg(filename = "figures/Figure_1_Funnel_Plots_Object_Identification.jpg", 
+       width = 600, height = 400, units = "px")
 
-kable(offset_info)
+  p <-   grid.arrange(fp_co, fp_mp, nrow = 1)
+                      #top = textGrob("Object Identification", gp=gpar(fontsize=25)))
+                      #top = "Figure 1. Funnel Plots")
+  dev.off()
+
+    grid.draw(p)
 
@@
 
-## Duration of post naming window
-Next we look at duration (in seconds) of the post naming window, here,too, we see a lot of heterogeneity.
+```{r PcurveExport, echo = FALSE}
 
-```{r TimeWindowduration}
-duration_info <- db_ET_correct %>%
-  group_by(post_nam_dur) %>%
-  summarize(count = n())
+textfile_co = "p_curve_app/p_curve_co.txt"
 
-kable(duration_info)
+# make sure the file is made new with our loop
+if (file.exists(textfile_co)) {file.remove(textfile_co)}
+
+for(line in 1:length(db_ET_correct$n_1)){
+  if(!is.na(db_ET_correct[line,]$t)){
+    newline = paste("t(", db_ET_correct[line,]$n_1-1, ")=",db_ET_correct[line,]$t, sep = "")
+    write(newline, file = textfile_co, append = TRUE)
+    #cat("\n")
+    #write(newline, file = textfile, append = TRUE)    
+  }
+}
+
+textfile_mp = "p_curve_app/p_curve_mp.txt"
+
+# make sure the file is made new with our loop
+if (file.exists(textfile_mp)) {file.remove(textfile_mp)}
+
+for(line in 1:length(db_ET_MP$n_1)){
+  if(!is.na(db_ET_MP[line,]$t)){
+    newline = paste("t(", db_ET_MP[line,]$n_1-1, ")=",db_ET_MP[line,]$t, sep = "")
+    write(newline, file = textfile_mp, append = TRUE)
+    #cat("\n")
+    #write(newline, file = textfile, append = TRUE)    
+  }
+}
 
@@
 
-In summary, we see little consistency in analysis methods of comparable studies looking at naming and mispronunciation effects.
+```{r ReadIn_pcurve_app,  echo = FALSE}
 
-## Mispronunciation Sensitivity in the youngest ages
-Even the youngest ages in the database (less than 1 year) show mispronunciation sensitivity
+curdir <- getwd()
 
-```{r YoungAge, echo = FALSE}
-youngest <- subset(dat, min_age_1 < 365)
+#Get the effect size data
+source("scripts/p_curve_app_code.R")
 
-unique(youngest$short_cite)
-youngest$cond_lab <- ifelse(youngest$condition == 1, "correct", "misp")
-ggplot(youngest, aes(x=cond_lab, y = g_calc, color = cond_lab)) + geom_boxplot()
+# this gives the number of significant results
+# the Z value
+# and the significance
+pcd_correct <- pcurve_app("p_curve_co.txt",paste0(curdir, "/p_curve_app"))
+
+pcd_misp <- pcurve_app("p_curve_mp.txt",paste0(curdir, "/p_curve_app"))
 
@@
 
-# Meta-Analysis
+We next examined the p-curves for significant values from the correctly pronounced and mispronounced conditions.
+The p-curve based on `r pcd_correct$ksig` statistically significant values for correct pronunciations indicates that the data contain evidential value (Z = `r r2(pcd_correct$Zppr)`, p `r psig(pcd_correct$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05.
+The p-curve based on `r pcd_misp$ksig` statistically significant values for mispronunciations indicates that the data contain evidential value (Z = `r r2(pcd_misp$Zppr)`, p `r psig(pcd_misp$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05.
 
-## Main Mispronunciation Sensitivity Effects
+Taken together, these results suggest a tendency in the literature towards publication bias.
+As a result, our meta-analysis may systematically overestimate effect sizes and we therefore interpret all estimates with caution.
+The funnel plot asymmetry may also reflect heterogeneity in the data, perhaps due to some studies investigating more subtle effects than other studies.
+Yet, the p-curve analysis suggests that overall, the literature contains evidential value, reflecting a "real" effect.
+We therefore continue our meta-analysis.
 
-### Correct object identification effect
+## Meta-analysis
+
+### Object Identification for Correct and Mispronounced Words
 
@@
 
-summary(rma_correct)
+#summary(rma_correct)
+#kable(round(coef(summary(rma_correct)), 2))
 
-#kable(round(coef(summary(rma_correct)), 2))
+sum_eff <- coef(summary(rma_correct))[1,]
 
@@
 
-### Mispronunciation object identification effect
+We first calculated the meta-analytic effect for object identification in response to correctly pronounced words.
+The variance-weighted meta-analytic effect size Hedges’ *g* was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
+This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research) and that it is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object.
+Our analysis of funnel plot asymmetry, however, found evidence for publication.
+Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` suggests that this result is robust even when correcting for publication bias.
 
@@
 
-summary(rma_MP)
+#summary(rma_MP)
+
+sum_eff <- coef(summary(rma_MP))[1,]
 
@@
 
-### Mispronunciation Sensitivity effect
+We then calculated the meta-analytic effect for object identification in response to mispronounced words.
+In this case, the variance-weighted meta-analytic effect size Hedges’ g was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was also significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
+This is considered a small effect size (Cohen, 1988), but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object.
+We again note the publication bias (which was smaller in this condition), and the possibility that the effect size Hedges' *g* may be overestimated.
+But, as the p-curve indicated evidential value, we are confident in this result as well.
+
+Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, p `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, p `r psig(rma_MP$QEp)`).
+This indicated that the sample contains unexplained variance leading to significant difference across our studies beyond what is to be expected based on random sampling error.
+
+### Mispronunciation Sensitivity Meta-analytic Effect
 
 ```{r MPEffect}
-db_ET_correct$condition <- 1
-db_ET_MP$condition <- 0
-
-dat <- bind_rows(db_ET_correct, db_ET_MP)
 
@@
 
-summary(rma_MPeffect)
+#summary(rma_MPeffect)
 
-rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ collapse | short_cite)
+#rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ collapse | short_cite)
 
-summary(rma_MPeffect_1)
+#summary(rma_MPeffect_1)
+
+sum_eff <- coef(summary(rma_MPeffect))[2,]
 
@@
 
-## Main Mispronunciation Sensitivity Effects with Age Moderators
+The above two analyses considered the data from mispronounced and correctly pronounced words separately.
+To evaluate mispronunciation sensitivity, we then compared the effect size Hedges’ *g* for correct pronunciations with mispronunciations, merging the two datasets.
+The moderator test was significant, QM(`r r2(rma_MPeffect$m)`) = `r r2(rma_MPeffect$QM)`, p `r psig(rma_MPeffect$QMp)`.
+Hedges’ *g* for mispronunciation sensitivity was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that the two type of responses were significantly different from one another (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
+This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations.
+In other words, we observe a significant difference between the two conditions and can now quantify the modulation of fixation behavior in terms of standardized effect sizes.
 
-### Correct object identification effect with age moderator
+### Object Recognition and Mispronunciation Sensitivity Modulated by Age
 
@@
 
-summary(rma_correct_age)
+#summary(rma_correct_age)
 #kable(round(coef(summary(rma_correct_age)), 2))
+#aov.type <- anova(rma_correct_age)
+
+Csum_eff <- coef(summary(rma_correct_age))[2,]
 
 ```
-
-### Mispronunciation object identification effect with age moderator
 
@@
 
-summary(rma_MP_age)
+#summary(rma_MP_age)
+#aov.type <- anova(rma_MP_age)
+
+Msum_eff <- coef(summary(rma_MP_age))[2,]
+
 ```
 
-### Mispronunciation Sensitivity effect with age moderator
+To evaluate the different predictions for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered, in days).
+In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not.
+Age did not significantly modulate object identification in response to correctly pronounced (QM(`r r2(rma_correct_age$m)`) = `r r2(rma_correct_age$QM)`, p `r psig(rma_correct_age$QMp)`) or mispronounced words (QM(`r r2(rma_MP_age$m)`) = `r r2(rma_MP_age$QM)`, p `r psig(rma_MP_age$QMp)`).
+The lack of a significant modulation indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label.
+This relationship is plotted in Figure 2.
 
 ```{r MPEffect_age}
-db_ET_correct$condition <- 1
-db_ET_MP$condition <- 0
-
-dat <- bind_rows(db_ET_correct, db_ET_MP)
 
@@
 
-summary(rma_MPeffect_age)
+# summary(rma_MPeffect_age)  
+# 
+# aov.type <- anova(rma_MPeffect_age)
+
+sum_eff <- coef(summary(rma_MPeffect_age))[4,]
 
@@
 
-## Plotting Mispronunciation Effect
+We then examined the interaction between age and mispronunciation sensitivity (correct vs.
+mispronounced words) in our whole dataset.
+The moderator test was significant (QMQM(`r r2(rma_MPeffect_age$m)`) = `r r2(rma_MPeffect_age$QM)`, p `r psig(rma_MPeffect_age$QMp)`).
+The interaction between age and mispronunciation sensitivity, however, was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`), suggesting that as infants age, their mispronunciation sensitivity remains the same.
 
-### Plot Mispronunciation Effect by Age (color)
+## Figure 2
 
-```{r PlotMPEffect}
+```{r PlotMPEffect, echo = FALSE}
 
@@
 
-# Color Blind palette:
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
 p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g),show.legend=FALSE) + 
+  geom_point(aes(size = weights_g),show.legend=FALSE, alpha = .5) + 
   geom_line(y= 0, linetype="dotted") + 
@@
   theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
+        legend.position = "bottom",
+        text = element_text(size = 40)) + 
   xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
+  ylab("Hedges' g")
 
@@
 
-min(dat$mean_age_1/30.44)
-max(dat$mean_age_1/30.44)
+# min(dat$mean_age_1/30.44)
+# max(dat$mean_age_1/30.44)
 
@@
 
-  jpeg(filename = "figures/AgeEffect_log.jpg", 
-       width = 600, height = 400, units = "px")
+  jpeg(filename = "figures/Figure_2_AgeEffect.jpg", 
+       width = 700, height = 400, units = "px")
 
@@
 
-### Plot Mispronunciation Effect by Age (bw)
+### Vocabulary Size: Correlation Between Mispronunciation Sensitivity and Vocabulary
 
-```{r PlotMPEffect_BW}
-
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape=condition_label, color=condition_label),
-             show.legend=FALSE) + 
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_color_grey()+
-  theme_bw()+
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_BW.jpg", p,height= 3,width= 6)
-
-```
-
-## Correlation MP effect and Vocabulary
-
-First, let's take a look at which vocabulary data we have available.
-
-```{r VocabularyData}
+```{r VocabularyData, echo = FALSE}
 vocab_info <- db_ET_correct %>%
@@
   group_by(has_vocab) %>%
-  summarize(count = n())
+  summarize(count = n(),
+            papers = n_distinct(short_cite))
 
-kable(vocab_info)
+#kable(vocab_info)
+
+vocab_info2 <- db_ET_correct %>%
+  mutate(has_vocab = ifelse(!is.na(r_comprehension) | !is.na(r_production), "vocab", 
+                            "none")) %>%
+  group_by(has_vocab) %>%
+  summarize(count = n(),
+            papers = n_distinct(short_cite))
+
+vi1 <- as.data.frame(vocab_info)
+vi2 <- as.data.frame(vocab_info2)
 
@@
 
-We have 17 correlations, roughly evenly divided between comprehension and production data.
-There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we should both analyze this data separately and see whether it makes sense in a joint analysis.
+Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers; production = `r with(vi1, papers[has_vocab == "production"])`) analyzed the relationship between vocabulary scores and mispronunciation sensitivity.
+There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we analyze this data separately.
 
-```{r ComprehensionMeta}
+```{r ComprehensionMeta_correct}
 #we're relying on the library meta function metacor
@@
 
-```{r ProductionMeta}
+```{r ProductionMeta_correct}
 #we're relying on the library meta function metacor
@@
 
-## Number of Features Changed
+```{r ComprehensionMeta_MP}
+#we're relying on the library meta function metacor
+compr  <- subset(db_ET_MP, !is.na(db_ET_MP$r_comprehension) & r_comprehension > -1)
 
-### Number of features
-
-Size of mispronunciation, measured in features changed
-
-```{r NFeatures}
-
-db_ET_MPf  <- subset(db_ET_MP, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature), data = db_ET_MPf, random = ~collapse | short_cite)
-
-summary(rma_NFeatures)
-
+metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
 ```
 
-### Number of features subset to age range
-Size of mispronunciation, measured in features changed
+```{r ProductionMeta_MP}
+#we're relying on the library meta function metacor
+prodr  <- subset(db_ET_MP, !is.na(db_ET_MP$r_production) & r_production < 1)
 
-```{r NFeatures_subset}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-mf <- subset(dat_f, n_feature == "3")
-min_age <- min(mf$mean_age_1)
-max_age <- max(mf$mean_age_1)
-
-dat_fage= dat_f%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature), data = dat_f, random = ~collapse | short_cite)
-
-summary(rma_NFeatures_agesub)
-
+metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
 ```
 
-### Number of features with condition moderator
+### Interim Discussion
 
-```{r NFeaturesCondition}
+The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age.
+The results are clear: Although infants consider a mispronunciation as a better match with the target image than a distractor image, there was a consistent effect of mispronunciation sensitivity.
+This did not change with development.
+Of the 3 predictions and assumptions about the development of infants' sensitivity to mispronunciations discussed in the Introduction, the present results lend some support for the argument that mispronunciation sensitivity stays consistent as infants develop.
+This runs counter to existing theories of phono-lexical development, which predict either an increase (PRIMR ref) or decrease (Assim Model ref) in mispronunciation sensitivity.
+In sum, it seems that current theories of infants' phono-lexical development cannot fully capture our results and should be reconsidered with all the evidence in mind.
 
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*condition, data = dat_f, random = ~collapse | short_cite)
-
-summary(rma_NFeatures)
-
-```
-
-### Number of features with age moderator
-
-```{r NFeatures_age}
-
-db_ET_MPf  <- subset(db_ET_MP, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C, data = db_ET_MPf, random = ~collapse | short_cite)
-
-summary(rma_NFeaturesAge)
-```
-
-### Number of features with condition and age moderators
-
-```{r NFeaturesCondition_age}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C*condition, data = dat_f, random = ~collapse | short_cite)
-
-summary(rma_NFeaturesAge)
-```
-
-### Features changed with age moderator, subset to same age range
-
-```{r FeatureAgeRangeSubset}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-mf <- subset(dat_f, n_feature == "3")
-min_age <- min(mf$mean_age_1)
-max_age <- max(mf$mean_age_1)
-
-dat_fage= dat_f%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-rma_FeatureAgeS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(n_feature), data = dat_fage, random = ~ collapse | short_cite)
-
-summary(rma_FeatureAgeS)
-
-#rma_FeatureS <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(n_feature), data = dat_fage, random = ~ collapse | short_cite)
-
-#summary(rma_FeatureS)
-
-```
-
-## Plotting number of Features Changed
-
-### Plot number of Features
-
-```{r PlotFeatEffect}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" | n_feature == "2" | n_feature == "3")
-
-dat_f$feat_cat <- ifelse(dat_f$n_feature == 1, "one",
-                         ifelse(dat_f$n_feature == 2, "two",
-                                ifelse(dat_f$n_feature == 3, "three",
-                                       ifelse(dat_f$n_feature == 0, "correct", "none"))))
-
-dat_f <- subset(dat_f, feat_cat != "none")
-
-p <- ggplot(dat_f, aes(mean_age_1/30.44, g_calc, color = feat_cat)) + 
-  geom_point(aes(size = weights_g, shape = feat_cat),show.legend=FALSE) + 
-  #facet_grid(.~type_feature)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_feat.jpg", p)
-
-```
-### Plot number of Features subsetted for age
-
-```{r PlotFeatEffect_agesubset}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-mf <- subset(dat_f, n_feature == "3")
-min_age <- min(mf$mean_age_1)
-max_age <- max(mf$mean_age_1)
-
-dat_fage= dat_f%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-dat_fage$feat_cat <- ifelse(dat_fage$n_feature == 1, "1-feature",
-                         ifelse(dat_fage$n_feature == 2, "2-feature",
-                                ifelse(dat_fage$n_feature == 3, "3-feature",
-                                       ifelse(dat_fage$n_feature == 0, "correct", "none"))))
-
-dat_fage <- subset(dat_fage, feat_cat != "none")
-
-dat_fage$Features_changed <- factor(dat_fage$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))
-
-# Color Blind palette:
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
-p <- ggplot(dat_fage, aes(mean_age_1/30.44, g_calc, color = Features_changed)) + 
-  geom_point(aes(size = weights_g, shape = Features_changed),show.legend=FALSE) + 
-  #facet_grid(.~type_feature)+
-    scale_colour_manual(values=cbPalette)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_feat_agesub.jpg", p)
-
-```
-
-### Plot number of Features subsetted for age Boxplot
-
-```{r PlotFeatEffect_agesubset_boxplot}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-mf <- subset(dat_f, n_feature == "3")
-min_age <- min(mf$mean_age_1)
-max_age <- max(mf$mean_age_1)
-
-dat_fage= dat_f%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-dat_fage$feat_cat <- ifelse(dat_fage$n_feature == 1, "1-feature",
-                         ifelse(dat_fage$n_feature == 2, "2-feature",
-                                ifelse(dat_fage$n_feature == 3, "3-feature",
-                                       ifelse(dat_fage$n_feature == 0, "correct", "none"))))
-
-dat_fage <- subset(dat_fage, feat_cat != "none")
-
-dat_fage$Features_changed <- factor(dat_fage$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))
-
-# Color Blind palette:
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
-p <- ggplot(dat_fage, aes(Features_changed, g_calc, fill = Features_changed)) + 
-  geom_boxplot() + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "none",
-        axis.title.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-ggsave("figures/AgeEffect_log_feat_agesub_noage.jpg", p)
-
-```
-
-## Type of MP: Vowel, consonant, or tone
-
-### Type of MP: Vowel, consonant, or tone
-
-```{r MPtype}
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
-
-rma_TypeFeaturesMP <- rma.mv(g_calc, g_var_calc, mods = ~type_feature, data = db_MP_type, random = ~collapse | short_cite)
-
-summary(rma_TypeFeaturesMP)
-
-```
-
-### Type of MP: Vowel, consonant, or tone with age moderator
-
-```{r MPtype_age}
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
-
-rma_TypeFeaturesMPAge <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)
-
-summary(rma_TypeFeaturesMPAge)
-```
-
-### Type of MP: Vowel, consonant, or tone with condition moderator
-
-```{r MPtypeCondition}
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
-                type_feature == "tone")
-dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
-
-rma_TypeFeatures <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*condition, data = dat_type, random = ~collapse | short_cite)
-
-summary(rma_TypeFeatures)
-
-```
-
-### Type of MP: Vowel, consonant, or tone with age and condition moderator
-
-```{r MPtypeCondition_age}
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
-                type_feature == "tone")
-dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
-
-rma_TypeFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*age.C*condition, data = dat_type, random = ~collapse | short_cite)
-
-summary(rma_TypeFeaturesAge)
-```
-
-### Type of MP with language family moderator
-
-```{r MPtypeLanguage}
-#dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
-#                type_feature == "tone")
-
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
-
-dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
-dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
-dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French",
-                                "Romanic", "Sino-Tibetian"))
-
-dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family, data = dat_type_sub, random = ~collapse | short_cite)
-
-summary(rma_TypeFeatures_Lang)
-```
-
-### Type of MP with language family and condition moderators
-
-```{r MPtypeLanguageCondition}
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")# |
-                #type_feature == "tone")
-dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))
-
-dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
-dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
-dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French",
-                                "Romanic", "Sino-Tibetian"))
-
-dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-dat_type_sub$lang_family <- as.factor(dat_type_sub$lang_family)
-
-rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family*condition, data = dat_type_sub, random = ~collapse | short_cite)
-
-summary(rma_TypeFeatures_Lang)
-
-```
-
-## Plotting MP type: Consonant, Vowel, or Tone?
-
-### Plot MP type: Consonant, Vowel, or Tone?
-
-```{r PlotCVEffect}
-
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = type_feature),show.legend=FALSE) + 
-  facet_grid(.~type_feature)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_CV.jpg", p)
-```
-
-### Plot Language Family by MP type: Consonant, Vowel, or Tone?
-
-```{r PlotCVEffect_Lang}
-
-p <- ggplot(dat_type_sub, aes(type_feature, g_calc, color = type_feature)) + 
-  geom_boxplot() + 
-  facet_grid(lang_family~condition_label)+
-  #geom_line(y= 0, linetype="dotted") + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Language Family") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/LangFamily_CV.jpg", p)
-```
-
-## Distractor Familiarity (familiary, unfamiliar)
-
-```{r DistractorType}
-
-rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
-
-summary(rma_Distractor)
-
-```
-
-### Distractor Familiarity with condition moderator
-
-```{r DistractorTypeCondition}
-
-rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
-
-summary(rma_Distractor)
-
-```
-
-### Distractor Familiarity with age moderator
-```{r DistractorTypeAge}
-
-rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
-
-summary(rma_DistractorAge)
-
-```
-
-### Distractor Familiarity with age and condition moderators
-```{r DistractorTypeConditionAge}
-
-rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
-
-summary(rma_DistractorAge)
-
-```
-
-### Distractor Familiarity with condition moderator, subset to same age range
-
-```{r DistractorTypeAgeRangeSubset_condition}
-
-mf <- subset(dat, object_pair=="familiar_novel")
-min_age <- min(mf$mean_age_1)
-
-mf <- subset(dat, object_pair=="familiar_familiar")
-max_age <- max(mf$mean_age_1)
-
-dat_age= dat%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
-
-summary(rma_DistractorAgeS)
-
-```
-
-### Distractor Familiarity with age and condition moderator, subset to same age range
-
-```{r DistractorTypeAgeRangeSubset_agecondition}
-
-mf <- subset(dat, object_pair=="familiar_novel")
-min_age <- min(mf$mean_age_1)
-
-mf <- subset(dat, object_pair=="familiar_familiar")
-max_age <- max(mf$mean_age_1)
-
-dat_age= dat%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
-
-summary(rma_DistractorAgeS)
-
-```
-
-### Plotting Distractor Familiarity
-
-### Plot Distractor Familiarity
-
-```{r PlotDistFamEffect}
-
-dat$condition_label = ifelse(dat$condition==1, "correct", "MP")
-dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")
-
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = dist_code),show.legend=FALSE) + 
-  facet_grid(.~dist_code)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_color_manual(values=wes_palette(name="Darjeeling"))+
-  theme_bw()+
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_distractor_fam.jpg", p)
-
-```
-
-### Plot Distractor Familiarity (w/o age)
-
-```{r PlotDistFamEffect_NoAge}
-
-dat$condition_label = ifelse(dat$condition==1, "correct", "MP")
-dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")
-
-p <- ggplot(dat, aes(dist_code, g_calc, color = condition_label)) + 
-  geom_boxplot() + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_color_manual(values=wes_palette(name="Darjeeling"))+
-  theme_bw()+
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Distractor Familiarity") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/Distractor_fam_log.jpg", p)
-
-```
-
-### Plot Distractor Familiarity (w/o age, subset to age range)
-
-```{r PlotDistFamEffect_NoAge_AgeMatch}
-
-mf <- subset(dat, object_pair=="familiar_novel")
-min_age <- min(mf$mean_age_1)
-
-mf <- subset(dat, object_pair=="familiar_familiar")
-max_age <- max(mf$mean_age_1)
-
-dat_age= dat%>%
-  filter(mean_age_1>min_age&mean_age_1<max_age)
-
-dat_age$condition_label = ifelse(dat_age$condition==1, "correct", "mispronunciation")
-dat_age$dist_code <- ifelse(dat_age$object_pair == "familiar_familiar", "Familiar Distractor", "Unfamiliar Distractor")
-
-# Color Blind palette:
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
-p <- ggplot(dat_age, aes(condition_label, g_calc, fill = condition_label)) + 
-  geom_boxplot() + 
-  facet_grid(.~dist_code) +
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-ggsave("figures/AgeMatch_Distractor_fam_log.jpg", p)
-
-```
-
-### Plot Distractor Familiarity by age subsetted for age
-
-```{r PlotDistFam}
-
-mf <- subset(dat, object_pair=="familiar_novel")
-min_age <- min(mf$mean_age_1)
-
-mf <- subset(dat, object_pair=="familiar_familiar")
-max_age <- max(mf$mean_age_1)
-
-dat_fage= dat%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-dat_fage$dist_fam <- ifelse(dat_fage$object_pair == "familiar_novel", "Novel Distractor", "Familiar Distractor")
-
-# Color Blind palette:
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
-p <- ggplot(dat_fage, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = dist_fam),show.legend=FALSE) + 
-  facet_grid(.~dist_fam)+
-    scale_colour_manual(values=cbPalette)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_DistFam_agesub.jpg", p)
-
-```
-
-## Position of Mispronunciation (onset, medial)
-
-```{r Location}
-#table(db_ET_MP$mispron_location)
-
-db_ET_MPl = db_ET_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_Location <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_MPl, random = ~collapse | short_cite)
-
-summary(rma_Location)
-
-```
-
-### Position of Mispronunciation with age moderator
-
-```{r Location_age}
-#table(db_ET_MP$mispron_location)
-
-db_ET_MPl = db_ET_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-rma_LocationAge <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
-
-summary(rma_LocationAge)
-```
-
-### Position of Mispronunciation with condition moderator
-
-```{r Location_condition}
-#table(db_ET_MP$mispron_location)
-
-db_ET_MPl = db_ET_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition, data = db_ET_MPl, random = ~collapse | short_cite)
-
-summary(rma_LocationCondition)
-```
-
-### Position of Mispronunciation with age and condition moderators
-
-```{r Location_condition_age}
-#table(db_ET_MP$mispron_location)
-
-db_ET_MPl = db_ET_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
-
-summary(rma_LocationCondition)
-```
-
-## Plotting Position of Mispronunciation
-```{r PlotPositionEffect}
-
-#dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial" |
-#                mispron_location == "offset")
-
-dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial")
-
-p <- ggplot(dat.p, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = mispron_location),show.legend=FALSE) + 
-  facet_grid(.~mispron_location)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_position.jpg", p)
-
-```
-
-## Distractor Overlap
-
-```{r DistractorOverlap}
-
-rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
-
-summary(rma_DistractorOverlap)
-
-```
-
-### Distractor Overlap with age moderator
-
-```{r DistractorOverlap_age}
-
-rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
-
-summary(rma_DistractorOverlap)
-
-```
-
-### Distractor Overlap with condition moderator
-
-```{r DistractorOverlap_condition}
-
-rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
-
-summary(rma_DistractorOverlap)
-
-```
-
-### Distractor Overlap with age and condition moderators
-
-```{r DistractorOverlap_age_condition}
-
-rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
-
-summary(rma_DistractorOverlap)
-
-```
-
-## Plotting Distractor Overlap
-
-```{r PlotDistOverlapEffect}
-
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = distractor_overlap),show.legend=FALSE) + 
-  facet_grid(.~distractor_overlap)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_distractor_overlap.jpg", p)
-
-```
-
-## Language effect
-
-```{r LanguageEffectAnalyses}
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")
-
-dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
-                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
-                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
-                           dat$native_lang=="German", "Germanic",
-                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
-                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
-                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))
-
-rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~lang_family, data = dat, random = ~ collapse | short_cite)
-summary(rma_lang_interaction)
-
-```
-
-### Language effect with age moderator
-
-```{r LanguageEffectAnalyses_age}
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")
-
-dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
-                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
-                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
-                           dat$native_lang=="German", "Germanic",
-                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
-                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
-                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))
-
-rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*lang_family, data = dat, random = ~ collapse | short_cite)
-summary(rma_lang_interaction)
-
-```
-
-### Language effect with condition moderator
-
-```{r LanguageEffectAnalyses_condition}
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")
-
-dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
-                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
-                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
-                           dat$native_lang=="German", "Germanic",
-                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
-                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
-                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))
-
-rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~condition*lang_family, data = dat, random = ~ collapse | short_cite)
-summary(rma_lang_interaction)
-
-```
-
-### Language effect with age and condition moderators
-
-```{r LanguageEffectAnalyses_condition_age}
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")
-
-dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
-                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
-                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
-                           dat$native_lang=="German", "Germanic",
-                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
-                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
-                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))
-
-rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*lang_family, data = dat, random = ~ collapse | short_cite)
-summary(rma_lang_interaction)
-
-```
-
-## Plotting Language Effect
-```{r PlotLanguageEffect}
-
-dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
-                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
-                           dat$native_lang=="German", "Germanic",
-                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
-                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
-                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))
-
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g, shape = lang_family),show.legend=FALSE) + 
-  facet_grid(.~lang_family)+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  theme(text = element_text(size=16)) + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-p
-
-ggsave("figures/AgeEffect_log_language.jpg", p)
-
-```
+Alternatively, the lack of developmental change in mispronunciation sensitivity could be due to differences in the types of tasks given to infants of different ages.
+To examine this possibility, we include an exploratory analysis of whether different moderators and experimental design features were included at different ages.
+We return to this possibility after the Moderator Analyses.

### 2018-09-19 Paper_Analyses_sandbox.Rmd
updated Methods/Results

--- 2018-07-05 Paper_Analyses.Rmd
@@
 
-# Descriptive data
-
-The database contains data from `r length(unique(dat$short_cite))` papers. In the tables below, we provide more descriptive information.
-
-The next table shows what type of publications were included in our meta-analysis
+# Forest Plot
+
+```{r ForestPlot}
+
+#https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-met#a-analysis/
+
+#Rename a bunch of things for ease
+
+f.dat <-
+  dat %>% 
+  rename(cite = short_cite,
+         yi = g_calc,
+         vi = g_var_calc)
+
+#Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order
+
+f.dat <-
+  f.dat %>% 
+  select(cite, expt_num, same_infant, mean_age_1, yi, vi, condition) %>% 
+  mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
+  arrange(desc(yi))
+
+f.dat$condition_label <- ifelse(f.dat$condition==1, "Correct", "Mispronunciation")
+
+#Get standard errors from variances
+f.dat$se = sqrt(f.dat$vi)
+
+#Calculate 95% CI values
+f.dat$lowerci = (-1.96*f.dat$se)+f.dat$yi
+f.dat$upperci = (1.96*f.dat$se)+f.dat$yi
+
+p <-  ggplot(f.dat, aes(y=reorder(study_ref, -yi), x=yi, xmin=lowerci, xmax=upperci, color = condition_label))+
+  #Add f.data points and color them black
+  geom_point()+
+  #Add 'special' points for the summary estimates, by making them diamond shaped
+#  geom_point(f.data=subset(f.dat, tester=='Summary'), color='black', shape=18, size=4)+
+  #add the CI error bars
+  geom_errorbarh(height=.1)+
+  # set the colors to color blind
+    scale_colour_manual(values=cbPalette)+
+  #Specify the limits of the x-axis and relabel it to something more meaningful
+  scale_x_continuous(limits=c(-1.5,1.5), name='Standardized Mean Difference (g)')+
+  #Give y-axis a meaningful label
+  ylab('Reference')+
+  #Add a vertical dashed line indicating an effect size of zero, for reference
+  geom_vline(xintercept=0, color='grey', linetype='dashed')+
+  #Add a vertical line to show mean effect
+  geom_vline(xintercept=0.91, color='black', linetype='dashed')+
+    geom_vline(xintercept=0.25, color='blue', linetype='dashed')+
+  #Create sub-plots (i.e., facets) based on levels of setting
+  #And allow them to have their own unique axes (so authors don't redundantly repeat)
+  #facet_grid(setting~., scales= 'free', space='free')+
+  #Apply my APA theme
+  apatheme+
+      theme(text=element_text(family='Times', size=10),
+            legend.position = "bottom",
+            legend.title = element_blank())
+
+p
+
+  jpeg(filename = "figures/Forest_Plot.jpg", 
+       width = 700, height = 600, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
+# Methods
+
+## Study Selection
+
+The final sample (n = `r length(unique(dat$short_cite))`) consisted of `r with(dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(dat, n_distinct(short_cite[publication_status == "dissertation"]))` thesis, and `r with(dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports.
+We will refer to these items collectively as papers.
+Table X provides an overview of all papers included in the present meta-analysis.
+
 ```{r DescriptivesPubtype, echo = FALSE}
@@
 kable(pub_info)
+
+pi <- dat[,c("short_cite", "publication_status")]
+pi <- unique(pi)
+
+c.plot <- ggplot(pi, aes(x= publication_status)) + 
+  geom_text(stat='count', aes(label=..count..), vjust=-1, size = 5)+
+  geom_bar(stat="count")+
+  coord_cartesian(ylim = c(0, 30))+
+  apatheme+
+  theme(axis.text.x = element_text(size = 20, angle = -45, hjust = .11),
+        axis.title.x = element_blank())
+
+c.plot
+
+  jpeg(filename = "figures/Pub_count.jpg", 
+       width = 500, height = 500, units = "px")
+
+  c.plot
+
+  dev.off()
 
@@
 unique(youngest$short_cite)
-youngest$cond_lab <- ifelse(youngest$condition == 1, "correct", "misp")
-ggplot(youngest, aes(x=cond_lab, y = g_calc, color = cond_lab)) + geom_boxplot()
+youngest$cond_lab <- ifelse(youngest$condition == 1, "Correct", "Mispronunciation")
+
+ggplot(youngest, aes(x=cond_lab, y = g_calc, fill = cond_lab)) + 
+    geom_boxplot() + 
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "none",
+        axis.title.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+  jpeg(filename = "figures/Youngest.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
 
@@
 
+### Plot Object Identification
+
+```{r PlotObj_id}
+
+dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
+
+p <- ggplot(dat, aes(condition_label, g_calc, fill = condition_label)) + 
+  geom_boxplot() + 
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "none",
+        axis.title.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+#ggsave("figures/AgeEffect_log.jpg", p,height= 7,width= 6)
+
+  jpeg(filename = "figures/Object_ID.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
 ### Mispronunciation Sensitivity effect
@@
 p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g),show.legend=FALSE) + 
+  geom_point(aes(size = weights_g),show.legend=FALSE, alpha = .5) + 
   geom_line(y= 0, linetype="dotted") + 
@@
   jpeg(filename = "figures/AgeEffect_log.jpg", 
-       width = 500, height = 300, units = "px")
+       width = 700, height = 400, units = "px")
 
@@
   group_by(has_vocab) %>%
-  summarize(count = n())
+  summarize(count = n(),
+            papers = n_distinct(short_cite))
 
@@
 
+```{r Vocab_describe1}
+#how did vocabulary collection change over time?
+
+dv <- read.csv("data/vocab_collection.csv", header = T)
+
+years.v <- as.data.frame(seq(from = 2000, to = 2018, by = 1))
+relat.v <- c("no_vocab", "no_relationship", "positive")
+
+fake.v <- merge(years.v, relat.v, all = T)
+names(fake.v) <- c("year", "relationship")
+dat.v <- merge(dv, fake.v, by = c("year", "relationship"), all.y = T)
+dat.v$vocab <- as.character(dat.v$vocab)
+dat.v$relationship <- as.character(dat.v$relationship)
+dat.v$short_cite <- as.character(dat.v$short_cite)
+
+dat.v$vocab[is.na(dat.v$vocab)] <- "none"
+dat.v$short_cite <- ifelse(dat.v$vocab == "none", "none", dat.v$short_cite)
+
+dat.v$short_cite[is.na(dat.v$short_cite)] <- "none"
+
+dat.v$tested <- ifelse(dat.v$short_cite == "none", "no", "yes")
+
+vocab_data1 <- dat.v %>%
+  group_by(year, relationship, tested) %>%
+  summarize(count = n())
+
+vocab_data1 <- as.data.frame(vocab_data1)
+vocab_data1$count <- ifelse(vocab_data1$tested == "no", 0, vocab_data1$count)
+vocab_data1$year <- as.numeric(vocab_data1$year)
+
+vocab_data1$relationship <- ifelse(vocab_data1$relationship == "no_vocab", "None",
+                                   ifelse(vocab_data1$relationship == "positive", "Predicts",
+                                          "No Relationship"))
+vocab_data1$relationship <- factor(vocab_data1$relationship, levels = c("Predicts", "No Relationship", "None"))
+
+p <- ggplot(vocab_data1, aes(year, count, color = relationship)) + 
+  geom_line() + 
+  geom_point()+
+  scale_y_continuous(breaks = c(0, 1, 2, 3, 4), limits = c(0,4))+
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom")
+p
+
+  jpeg(filename = "figures/Vocab_findings.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
 ## Size of Mispronunciation: Measured in Features Changed
+
+### Number of infants and unique experimental conditions included in Features analysis
+
+```{r NFeatures_demographics}
+
+dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
+                n_feature == "2" | n_feature == "3")
+
+## Number of unique infants
+infnum_info <- dat.f[,c("unique_ID", "same_infant", "expt_num", "n_1")]
+infnum_info <- unique(infnum_info)
+
+number_of_infants <- sum(infnum_info$n_1)
+
+## Number of unique experimental conditions
+condnum_info <- dat.f[,c("unique_ID", "same_infant", "expt_num", "expt_condition")]
+condnum_info <- unique(condnum_info)
+
+number_of_cond <- nrow(condnum_info)
+
+```
 
@@
 #rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
+
 rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat_f, random = ~collapse | short_cite)
@@
 
-```{r DistractorType}
-
-rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)
+#### Correct condition
+
+```{r DistractorType_correct}
+
+rma_Distractor_correct <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = db_ET_correct, random = ~ collapse | short_cite)
+
+#summary(rma_Distractor_correct)
+
+aov.type <- anova(rma_Distractor_correct)
+
+sum_eff <- round(coef(summary(rma_Distractor_correct))[2,], 2)
+
+```
+
+#### Mispronunciation condition
+
+```{r DistractorType_misp}
+
+rma_Distractor_MP <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)
 
@@
 
-aov.type <- anova(rma_Distractor)
-
-sum_eff <- round(coef(summary(rma_TypeFeatures_Lang))[2,], 2)
+aov.type <- anova(rma_Distractor_MP)
+
+sum_eff <- round(coef(summary(rma_Distractor_MP))[2,], 2)
 
@@
 
-```{r PlotDistFamEffect_NoAge_AgeMatch}
+```{r PlotDistFamEffect_NoAge}
 
@@
 
-```{r DistractorTypeAgeRangeSubset_condition}
+```{r DistractorTypeAgeRangeSubset}
+
+s.plot <- ggplot(dat, aes(x= mean_age_1)) + 
+  geom_bar(stat="count")+
+  facet_grid(.~object_pair)
+
+s.plot
 
 fn <- subset(dat, object_pair=="familiar_novel")
-min_fn <- min(mf$mean_age_1)
-max_fn <- max(mf$mean_age_1)
+min_fn <- min(fn$mean_age_1)
+max_fn <- max(fn$mean_age_1)
+mean_fn <- mean(fn$mean_age_1)
+sd_fn <- sd(fn$mean_age_1)
 
@@
 max_ff <- max(ff$mean_age_1)
+mean_ff <- mean(ff$mean_age_1)
+sd_ff <- sd(ff$mean_age_1)
+
+t.test(fn$mean_age_1, ff$mean_age_1)
 
@@
 
-dat_age= db_ET_MP%>%
+dat_age_MP= db_ET_MP%>%
   filter(mean_age_1>=min_age&mean_age_1<=max_age)
 
-rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
-
-#summary(rma_Distractor)
-
-aov.type <- anova(rma_Distractor)
-
-sum_eff <- round(coef(summary(rma_Distractor))[2,], 2)
+rma_Distractor_MP <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat_age_MP, random = ~ collapse | short_cite)
+
+#summary(rma_Distractor_MP)
+
+aov.type <- anova(rma_Distractor_MP)
+
+sum_eff <- round(coef(summary(rma_Distractor_MP))[2,], 2)
+
+# correct pronunciations
+dat_age_correct= db_ET_correct%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+rma_Distractor_correct <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat_age_correct, random = ~ collapse | short_cite)
+
+#summary(rma_Distractor_correct)
+
+aov.type <- anova(rma_Distractor_correct)
+
+sum_eff <- round(coef(summary(rma_Distractor_correct))[2,], 2)
 
@@
 fn <- subset(dat, object_pair=="familiar_novel")
-min_fn <- min(mf$mean_age_1)
-max_fn <- max(mf$mean_age_1)
+min_fn <- min(fn$mean_age_1)
+max_fn <- max(fn$mean_age_1)
 
@@
 
+## Distractor Overlap
+
+### Object Recognition for Correct Pronunciations
+
+```{r DistractorOverlap_correct}
+
+db_ET_correctPo = db_ET_correct %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+db_ET_correctPo$distractor_overlap <- factor(db_ET_correctPo$distractor_overlap, levels = c("onset", "no", "novel"))
+
+rma_DistractorOverlap_correct <- rma.mv(g_calc, g_var_calc, mods = ~distractor_overlap, data = db_ET_correctPo, random = ~ collapse | short_cite)
+
+#summary(rma_DistractorOverlap_correct)
+
+aov.type <- anova(rma_DistractorOverlap_correct)
+
+sum_eff1 <- round(coef(summary(rma_DistractorOverlap_correct))[2,], 2)
+sum_eff2 <- round(coef(summary(rma_DistractorOverlap_correct))[3,], 2)
+
+```
+
+### Object Recognition for Mispronunciations
+
+```{r DistractorOverlap_misp}
+
+db_ET_MPo = db_ET_MP %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
+
+rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
+
+#summary(rma_DistractorOverlap)
+
+aov.type <- anova(rma_DistractorOverlap)
+
+sum_eff1 <- round(coef(summary(rma_DistractorOverlap))[2,], 2)
+sum_eff2 <- round(coef(summary(rma_DistractorOverlap))[3,], 2)
+
+```
+
+The moderator test was not significant:
+`print(aov.type)`
+
+There was no significant effect of distractor overlap:
+
+Hedges' g for `row.names(sum_eff1)` was `toString(sum_eff1$estimate)` (SE = `toString(sum_eff1$se`)
+(95% CI [`toString(sum_eff1$ci.lb)`, `toString(sum_eff1$ci.ub)`], p = `toString(sum_eff1$pval)`)
+
+Hedges' g `row.names(sum_eff2)` was `toString(sum_eff2$estimate)` (SE = `toString(sum_eff2$se`)
+(95% CI [`toString(sum_eff2$ci.lb)`, `toString(sum_eff2$ci.ub)`], p = `toString(sum_eff2$pval)`)
+
+### Distractor Overlap with condition moderator
+
+```{r DistractorOverlap_condition}
+
+db_ET_MPo = dat %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
+
+rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
+
+summary(rma_DistractorOverlap)
+
+aov.type <- anova(rma_DistractorOverlap)
+
+sum_eff1 <- round(coef(summary(rma_DistractorOverlap))[5,], 2)
+sum_eff2 <- round(coef(summary(rma_DistractorOverlap))[6,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+There was a significant interaction between distractor overlap and condition:
+
+Hedges' g for `row.names(sum_eff1)` was `toString(sum_eff1$estimate)` (SE = `toString(sum_eff1$se`)
+(95% CI [`toString(sum_eff1$ci.lb)`, `toString(sum_eff1$ci.ub)`], p = `toString(sum_eff1$pval)`)
+
+Hedges' g `row.names(sum_eff2)` was `toString(sum_eff2$estimate)` (SE = `toString(sum_eff2$se`)
+(95% CI [`toString(sum_eff2$ci.lb)`, `toString(sum_eff2$ci.ub)`], p = `toString(sum_eff2$pval)`)
+
+### Distractor Overlap with age moderator
+
+```{r DistractorOverlap_age}
+
+db_ET_MPo = db_ET_MP %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
+
+#summary(rma_DistractorOverlap)  
+aov.type <- anova(rma_DistractorOverlap)
+
+sum_eff1 <- round(coef(summary(rma_DistractorOverlap))[5,], 2)
+sum_eff2 <- round(coef(summary(rma_DistractorOverlap))[6,], 2)
+
+```
+
+The moderator test was not significant:
+`print(aov.type)`
+
+There was no significant interaction between distractor overlap and age:
+
+Hedges' g for `row.names(sum_eff1)` was `toString(sum_eff1$estimate)` (SE = `toString(sum_eff1$se`)
+(95% CI [`toString(sum_eff1$ci.lb)`, `toString(sum_eff1$ci.ub)`], p = `toString(sum_eff1$pval)`)
+
+Hedges' g `row.names(sum_eff2)` was `toString(sum_eff2$estimate)` (SE = `toString(sum_eff2$se`)
+(95% CI [`toString(sum_eff2$ci.lb)`, `toString(sum_eff2$ci.ub)`], p = `toString(sum_eff2$pval)`)
+
+### Plotting Distractor Overlap with condition
+
+```{r PlotDistOverlapEffect}
+
+db_ET_MPo = dat %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
+
+db_ET_MPo$condition_label <- ifelse(db_ET_MPo$condition==1, "Correct", "Mispronunciation")
+
+p <- ggplot(db_ET_MPo, aes(condition_label, g_calc, fill = condition_label)) + 
+  facet_grid(.~distractor_overlap)+
+  geom_boxplot() + 
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+  jpeg(filename = "figures/Distractor_overlap.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
+### Distractor Overlap with age and condition moderators
+
+```{r DistractorOverlap_age_condition}
+
+db_ET_MPo = dat %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
+
+rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
+
+summary(rma_DistractorOverlap)
+
+aov.type <- anova(rma_DistractorOverlap)
+
+sum_eff1 <- round(coef(summary(rma_DistractorOverlap))[11,], 2)
+sum_eff2 <- round(coef(summary(rma_DistractorOverlap))[12,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+There was a significant interaction between distractor overlap, condition, and age:
+
+Hedges' g for `row.names(sum_eff1)` was `toString(sum_eff1$estimate)` (SE = `toString(sum_eff1$se`)
+(95% CI [`toString(sum_eff1$ci.lb)`, `toString(sum_eff1$ci.ub)`], p = `toString(sum_eff1$pval)`)
+
+Hedges' g `row.names(sum_eff2)` was `toString(sum_eff2$estimate)` (SE = `toString(sum_eff2$se`)
+(95% CI [`toString(sum_eff2$ci.lb)`, `toString(sum_eff2$ci.ub)`], p = `toString(sum_eff2$pval)`)
+
+### Plot Distractor Overlap, condition, and age
+
+```{r PlotDistOverlap_cond_age}
+
+db_ET_MPo = dat %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
+
+db_ET_MPo$condition_label <- ifelse(db_ET_MPo$condition==1, "Correct", "Mispronunciation")
+
+p <- ggplot(db_ET_MPo, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
+    facet_grid(.~distractor_overlap)+
+  geom_point(aes(size = weights_g),show.legend=FALSE) + 
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+  jpeg(filename = "figures/Distractor_overlap_age.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
 ## Position of Mispronunciation (onset, medial)
 
-```{r Location}
+### Correct Object Recognition
+
+```{r Location_correct}
+#table(db_ET_MP$mispron_location)
+
+db_ET_correctl = db_ET_correct %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
+
+#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
+rma_Location_correct <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_correctl, random = ~collapse | short_cite)
+
+#summary(rma_Location_correct)
+
+aov.type <- anova(rma_Location_correct)
+
+sum_eff <- round(coef(summary(rma_Location_correct))[2,], 2)
+
+```
+
+### Mispronunciation Object Recognition
+
+```{r Location_misp}
 #table(db_ET_MP$mispron_location)
@@
 #rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_Location <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_MPl, random = ~collapse | short_cite)
-
-#summary(rma_Location)
-
-aov.type <- anova(rma_Location)
-
-sum_eff <- round(coef(summary(rma_Location))[2,], 2)
+rma_Location_MP <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_MPl, random = ~collapse | short_cite)
+
+#summary(rma_Location_MP)
+
+aov.type <- anova(rma_Location_MP)
+
+sum_eff <- round(coef(summary(rma_Location_MP))[2,], 2)
 
@@
 
+### Position of Mispronunciation with condition moderator
+
+```{r Location_condition}
+#table(db_ET_MP$mispron_location)
+
+db_ET_MPl = dat %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
+
+rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition, data = db_ET_MPl, random = ~collapse | short_cite)
+
+# summary(rma_LocationCondition)
+
+aov.type <- anova(rma_LocationCondition)
+
+sum_eff <- round(coef(summary(rma_LocationCondition))[4,], 2)
+
+```
+
+The moderator test was significant:
+`print(aov.type)`
+
+But there was no significant interaction between mispronunciation position and condition:
+
+Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
+(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
+
 ### Position of Mispronunciation with age moderator
@@
 db_ET_MPl = db_ET_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
+  filter(mispron_location == "onset"  | mispron_location == "medial" | is.na(mispron_location))
+
+db_ET_MPl$mispron_location <- as.character(db_ET_MPl$mispron_location)
+
+db_ET_MPl$mispron_location <- ifelse(is.na(db_ET_MPl$mispron_location), "none", db_ET_MPl$mispron_location)
+
+db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("none", "onset", "medial"))
 
@@
 
-### Position of Mispronunciation with condition moderator
-
-```{r Location_condition}
+### Position of Mispronunciation with age and condition moderators
+
+```{r Location_condition_age}
 #table(db_ET_MP$mispron_location)
@@
 
-rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition, data = db_ET_MPl, random = ~collapse | short_cite)
-
-#summary(rma_LocationCondition)
+rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
+
+summary(rma_LocationCondition)
 
@@
 
-sum_eff <- round(coef(summary(rma_LocationCondition))[4,], 2)
+sum_eff <- round(coef(summary(rma_LocationCondition))[8,], 2)
 
@@
 
-But there was no significant interaction between mispronunciation position and condition:
+But there was no significant interaction between mispronunciation position, condition, and age:
 
@@
 
-### Position of Mispronunciation with age and condition moderators
-
-```{r Location_condition_age}
-#table(db_ET_MP$mispron_location)
-
-db_ET_MPl = dat %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
-
-summary(rma_LocationCondition)
-
-aov.type <- anova(rma_LocationCondition)
-
-sum_eff <- round(coef(summary(rma_LocationCondition))[8,], 2)
-
-```
-
-The moderator test was significant:
-`print(aov.type)`
-
-But there was no significant interaction between mispronunciation position, condition, and age:
-
-Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
-(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)
-
 ## Plotting Position of Mispronunciation
@@
 
-dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial")
+dat.p = dat %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
 
@@
 
-## Distractor Overlap
-
-```{r DistractorOverlap}
-
-db_ET_MPo = db_ET_MP %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
-
-#summary(rma_DistractorOverlap)
-
-aov.type <- anova(rma_DistractorOverlap)
-
-sum_eff1 <- round(coef(summary(rma_DistractorOverlap))[2,], 2)
-sum_eff2 <- round(coef(summary(rma_DistractorOverlap))[3,], 2)
-
-```
-
-The moderator test was not significant:
-`print(aov.type)`
-
-There was no significant effect of distractor overlap:
-
-Hedges' g for `row.names(sum_eff1)` was `toString(sum_eff1$estimate)` (SE = `toString(sum_eff1$se`)
-(95% CI [`toString(sum_eff1$ci.lb)`, `toString(sum_eff1$ci.ub)`], p = `toString(sum_eff1$pval)`)
-
-Hedges' g `row.names(sum_eff2)` was `toString(sum_eff2$estimate)` (SE = `toString(sum_eff2$se`)
-(95% CI [`toString(sum_eff2$ci.lb)`, `toString(sum_eff2$ci.ub)`], p = `toString(sum_eff2$pval)`)
-
-### Distractor Overlap with age moderator
-
-```{r DistractorOverlap_age}
-
-db_ET_MPo = db_ET_MP %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
-
-#summary(rma_DistractorOverlap)  
-aov.type <- anova(rma_DistractorOverlap)
-
-sum_eff1 <- round(coef(summary(rma_DistractorOverlap))[5,], 2)
-sum_eff2 <- round(coef(summary(rma_DistractorOverlap))[6,], 2)
-
-```
-
-The moderator test was not significant:
-`print(aov.type)`
-
-There was no significant interaction between distractor overlap and age:
-
-Hedges' g for `row.names(sum_eff1)` was `toString(sum_eff1$estimate)` (SE = `toString(sum_eff1$se`)
-(95% CI [`toString(sum_eff1$ci.lb)`, `toString(sum_eff1$ci.ub)`], p = `toString(sum_eff1$pval)`)
-
-Hedges' g `row.names(sum_eff2)` was `toString(sum_eff2$estimate)` (SE = `toString(sum_eff2$se`)
-(95% CI [`toString(sum_eff2$ci.lb)`, `toString(sum_eff2$ci.ub)`], p = `toString(sum_eff2$pval)`)
-
-### Distractor Overlap with condition moderator
-
-```{r DistractorOverlap_condition}
-
-db_ET_MPo = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
-
-summary(rma_DistractorOverlap)
-
-aov.type <- anova(rma_DistractorOverlap)
-
-sum_eff1 <- round(coef(summary(rma_DistractorOverlap))[5,], 2)
-sum_eff2 <- round(coef(summary(rma_DistractorOverlap))[6,], 2)
-
-```
-
-The moderator test was significant:
-`print(aov.type)`
-
-There was a significant interaction between distractor overlap and condition:
-
-Hedges' g for `row.names(sum_eff1)` was `toString(sum_eff1$estimate)` (SE = `toString(sum_eff1$se`)
-(95% CI [`toString(sum_eff1$ci.lb)`, `toString(sum_eff1$ci.ub)`], p = `toString(sum_eff1$pval)`)
-
-Hedges' g `row.names(sum_eff2)` was `toString(sum_eff2$estimate)` (SE = `toString(sum_eff2$se`)
-(95% CI [`toString(sum_eff2$ci.lb)`, `toString(sum_eff2$ci.ub)`], p = `toString(sum_eff2$pval)`)
-
-### Plotting Distractor Overlap with condition
-
-```{r PlotDistOverlapEffect}
-
-db_ET_MPo = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-p <- ggplot(db_ET_MPo, aes(condition_label, g_calc, fill = condition_label)) + 
-  facet_grid(.~distractor_overlap)+
-  geom_boxplot() + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Distractor_overlap.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-### Distractor Overlap with age and condition moderators
-
-```{r DistractorOverlap_age_condition}
-
-db_ET_MPo = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
-
-summary(rma_DistractorOverlap)
-
-aov.type <- anova(rma_DistractorOverlap)
-
-sum_eff1 <- round(coef(summary(rma_DistractorOverlap))[11,], 2)
-sum_eff2 <- round(coef(summary(rma_DistractorOverlap))[12,], 2)
-
-```
-
-The moderator test was significant:
-`print(aov.type)`
-
-There was a significant interaction between distractor overlap, condition, and age:
-
-Hedges' g for `row.names(sum_eff1)` was `toString(sum_eff1$estimate)` (SE = `toString(sum_eff1$se`)
-(95% CI [`toString(sum_eff1$ci.lb)`, `toString(sum_eff1$ci.ub)`], p = `toString(sum_eff1$pval)`)
-
-Hedges' g `row.names(sum_eff2)` was `toString(sum_eff2$estimate)` (SE = `toString(sum_eff2$se`)
-(95% CI [`toString(sum_eff2$ci.lb)`, `toString(sum_eff2$ci.ub)`], p = `toString(sum_eff2$pval)`)
-
-### Plot Distractor Overlap, condition, and age
-
-```{r PlotCVEffect_cond_age_fam}
-
-db_ET_MPo = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-p <- ggplot(db_ET_MPo, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-    facet_grid(.~distractor_overlap)+
-  geom_point(aes(size = weights_g),show.legend=FALSE) + 
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Distractor_overlap_age.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
 ## Type of MP: Vowel, consonant, or tone
@@
 
+```{r MPtype_descriptive}
+
+cv_position <- db_ET_MP %>%
+  group_by(type_feature, mispron_location) %>%
+  summarize(count = n())
+
+kable(cv_position)
+
+family <- db_ET_MP %>%
+  group_by(lang_family) %>%
+  summarize(count = n())
+
+kable(family)
+
+cv_family <- db_ET_MP %>%
+  group_by(type_feature, lang_family) %>%
+  summarize(count = n())
+
+kable(cv_family)
+
+cv <- db_ET_MP %>%
+  group_by(type_feature) %>%
+  summarize(count = n())
+
+kable(cv)
+
+```
+
 ```{r MPtype}
+
 db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )

### 2018-09-19 scripts/p_curve_app_code.R

@@ -226,6 +226,18 @@ pcurve_app=function(file1,dir1)
   main.results=as.numeric(c(ktot, ksig, khalf, Zppr, p.Zppr, Zpp33, p.Zpp33, Zppr.half, p.Zppr.half, Zpp33.half, p.Zpp33.half))
   write(main.results, paste("STOUFFER_",filek,".txt", sep=""),sep="\n")
   
+  # edit KATIE VON HOLZEN
+  # Sept 18, 2018
+  #pcd <- c(ksig, Zppr, p.Zppr)
+  #npcd <- c("num_sig", "Z", "sig")
+  pcd <- as.data.frame(cbind(ksig, Zppr, p.Zppr))
+  return(pcd)
+  #pcurve.data <- as.data.frame()
+  
+  #return(ksig)
+  #return(Zppr)
+  #return(p.Zppr)
+  
   #3.4 BINOMIAL
   #Observed share of p<.025
   prop25.obs=sum(p<.025)/sum(p<.05)

### 2018-10-10 Paper_Analyses.Rmd
updated methods/results

@@
 title: "MP MetaAnalysis"
-author: "Christina Bergmann"
+author: "Christina Bergmann and Katie Von Holzen"
+date: '`r format(Sys.Date(), "%d %B, %Y")`'
 output: 
@@
 library(gridExtra)
+library(xtable)
+library(schoRsch)
+library(multcomp)
 
@@
 
+# function for creating 1 line paired t.test results
+t.xtable <- function(x) as.data.frame(xtable(
+  t_out(toutput=x, n.equal = TRUE, welch.df.exact = TRUE, welch.n = NA,
+        d.corr = TRUE, print = TRUE)
+))
+
+cur_dir <- getwd()
+
 ```
@@
 db_ET$native_lang=="English" | db_ET$native_lang=="German", "Germanic", ifelse(db_ET$native_lang == "French" | db_ET$native_lang == "Catalan" | db_ET$native_lang == "Spanish" | db_ET$native_lang == "Catalan-Spanish" | db_ET$native_lang == "Swiss French",
-                                "Romanic", "Sino-Tibetian"))
+                                "Romance", "Sino-Tibetian"))
 
@@
 To this end, we provide all data and analysis scripts on the supplementary website (https://osf.io/rvbjs/) and open our meta-analysis up for updates (Tsuji, Bergmann, & Cristia, 2014).
-In addition, we follow the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials.
-(Moher, Liberati, Tetzlaff, Altman & PRISMAGroup, 2009).
+In addition, we follow the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials (Moher, Liberati, Tetzlaff, Altman & PRISMAGroup, 2009).
+Figure X plots our PRISMA flowchart.
+
+![Figure X. PRISMA Flowchart.] (figures/PRISMA_MA_Mispronunciation.png)
 
 ## Study Selection
+
+```{r SummaryTable, echo = FALSE}
+
+dat_st <- dat
+
+dat_st$object_pair <- ifelse(dat_st$object_pair == "familiar_familiar", "Familiar", "Unfamiliar")
+
+Sum_table <- dat_st %>%
+      group_by(short_cite) %>% 
+      summarise(Ages_Tested_months = paste(unique(trunc(mean_age_1/30.34)), collapse=', '),
+                Vocabulary = ifelse(all(is.na(r_comprehension)) & all(is.na(r_production)), "None",
+                                ifelse(!all(is.na(r_comprehension)) & !all(is.na(r_production)), "Comprehension/Production",
+                                       ifelse(!all(is.na(r_comprehension)) & all(is.na(r_production)), "Comprehension", "Production"))),
+                Number_of_Features = paste(unique(n_feature), collapse=', '),
+                Distractor_Familiarity = paste(unique(object_pair), collapse=', '),
+                Distractor_Overlap = paste(unique(distractor_overlap), collapse=', '),
+                Mispronunciation_Position = paste(unique(mispron_location), collapse=', '),
+                Mispronunciation_type = paste(unique(type_feature), collapse=', '))
+
+kable(Sum_table)
+
+```
+
+[KATIE] THIS TABLE IS DEFINITELY NOT FINISHED!
+
 We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list.
@@
 
+[KATIE] I DON'T KNOW HOW TO INTERPRET THESE RESULTS... THE FIXED EFFECTS MODEL ISN'T SIGNIFICANT FOR ANY OF THESE. IS THAT MEANINGFUL?
+
 ```{r ComprehensionMeta_correct}
@@
 This runs counter to existing theories of phono-lexical development, which predict either an increase (PRIMR ref) or decrease (Assim Model ref) in mispronunciation sensitivity.
+
+[KATIE] CAN A CONCLUSION BE DRAWN FROM THE VOCABULARY RESULTS? IF SO, THIS IS THE PARAGRAPH
+
 In sum, it seems that current theories of infants' phono-lexical development cannot fully capture our results and should be reconsidered with all the evidence in mind.
@@
 Alternatively, the lack of developmental change in mispronunciation sensitivity could be due to differences in the types of tasks given to infants of different ages.
-To examine this possibility, we include an exploratory analysis of whether different moderators and experimental design features were included at different ages.
-We return to this possibility after the Moderator Analyses.
+To examine this possibility, we include an exploratory analysis of whether different moderators and experimental design features were included at different ages, in addition to investigating the role that these moderators play in mispronunciation sensitivity.
+
+## Moderator Analyses
+
+### Size of mispronunciation
+
+```{r NFeatures_demographics}
+
+dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
+                n_feature == "2" | n_feature == "3")
+
+nfeature_info <- dat.f %>%
+  group_by(n_feature) %>%
+  summarize(n_exp_conditions =  n())
+
+```
+
+To assess whether the number of features changed modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced using 1-, 2-, and 3-feature changes.
+We did not include data for which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent.
+The analysis was therefore based on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` experimental conditions for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations.
+Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an equal impact on mispronunciation sensitivity, following the argument of graded sensitivity (White & Aslin, 2008; Mani & Plunkett 2011).
+
+```{r NFeatures}
+
+dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
+                n_feature == "2" | n_feature == "3")
+
+rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat.f, random = ~collapse | short_cite)
+
+ sum_eff <- coef(summary(rma_NFeatures))[2,]
+
+```
+
+To understand the relationship between size of mispronunciation and mispronunciation sensitivity, we  evaluated the effect size Hedges’ *g* with number of features changed as a moderator.
+The moderator test was significant, QM(`r r2(rma_NFeatures$m)`) = `r r2(rma_NFeatures$QM)`, p `r psig(rma_NFeatures$QMp)`.
+Hedges’ *g* for number of features changed was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that as the number of features changed increased, the effect size Hedges’ g significantly decreased (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
+We plot this relationship in Figure X.
+This confirms previous findings of a graded sensitivity to the number of features changed for both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) mispronunciations as well as the importance of controlling for the degree of phonological mismatch in experimental design.
+
+```{r PlotFeatEffect, echo = FALSE}
+
+dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
+                n_feature == "2" | n_feature == "3")
+
+dat_f$feat_cat <- ifelse(dat_f$n_feature == 1, "1-feature",
+                         ifelse(dat_f$n_feature == 2, "2-feature",
+                                ifelse(dat_f$n_feature == 3, "3-feature",
+                                       ifelse(dat_f$n_feature == 0, "correct", "none"))))
+
+dat_f <- subset(dat_f, feat_cat != "none")
+
+dat_f$Features_changed <- factor(dat_f$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))
+
+p <- ggplot(dat_f, aes(Features_changed, g_calc, fill = Features_changed)) + 
+  geom_boxplot() + 
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "none",
+        axis.title.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+  jpeg(filename = "figures/Figure_3_Number_of_Features.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
+```{r NFeatures_age}
+
+dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
+                n_feature == "2" | n_feature == "3")
+
+rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat.f, random = ~collapse | short_cite)
+
+ sum_eff <- coef(summary(rma_NFeatures))[4,]
+
+```
+
+Although we did not have any specific predictions about the relationship between infant age and the impact of number of features changed on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
+When age was also included as a moderator, the moderator test was significant, QM(`r r2(rma_NFeatures$m)`) = `r r2(rma_NFeatures$QM)`, p `r psig(rma_NFeatures$QMp)`, but the interaction between age and number of features changed was not significant, $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
+This suggests that there is no relationship between infant age the impact of number of features changed on mispronunciation sensitivity.
+
+```{r NFeatures_subset}
+
+dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
+                n_feature == "2" | n_feature == "3")
+
+nfeature_ages <- dat.f %>%
+  group_by(n_feature) %>%
+  summarize(min_age = r2(min(mean_age_1, na.rm=TRUE)),
+            max_age = r2(max(mean_age_1, na.rm=TRUE)),
+            mean_age = r2(mean(mean_age_1, na.rm=TRUE)))
+
+mf <- subset(dat_f, n_feature == "3")
+min_age <- min(mf$mean_age_1)
+max_age <- max(mf$mean_age_1)
+
+dat_fage= dat_f%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat_fage, random = ~collapse | short_cite)
+
+ sum_eff1 <- coef(summary(rma_NFeatures_agesub))[2,]
+
+rma_AGENFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat_fage, random = ~collapse | short_cite)
+
+ sum_eff2 <- coef(summary(rma_AGENFeatures_agesub))[4,]
+
+```
+
+Although all papers included in the dataset also included correct pronunciations, not all papers included all three types of feature changes (i.e.
+1-3).
+The age range for each type of number of features changed was `r with(nfeature_ages, min_age[n_feature == 1])` - `r with(nfeature_ages, max_age[n_feature == 1])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 1])`) for 1-feature mispronunciations, `r with(nfeature_ages, min_age[n_feature == 2])` - `r with(nfeature_ages, max_age[n_feature == 2])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 2])`) for 2-feature mispronunciations, and `r with(nfeature_ages, min_age[n_feature == 3])` - `r with(nfeature_ages, max_age[n_feature == 3])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 3])`) for 3-feature mispronunciations.
+Focusing on the ages where all three numbers of features changed were tested (i.e.
+`r with(nfeature_ages, min_age[n_feature == 3])` - `r with(nfeature_ages, max_age[n_feature == 3])` days), however, did not change the pattern of results.
+
+[KATIE] DOES THE ABOVE PARAGRAPH NEED MORE MOTIVATION? SHOULD IT EVEN BE INCLUDED?
+
+### Distractor familiarity
+
+```{r DistractorType_misp}
+
+rma_Distractor_MP <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)
+
+rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
+
+sum_eff <- coef(summary(rma_Distractor))[4,]
+
+```
+
+We next assessed whether distractor familiarity has an impact on the size of mispronunciation sensitivity.
+First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images that were paired with either a familiar or an unfamiliar distractor image.
+The moderator test was not significant QM(`r r2(rma_Distractor_MP$m)`) = `r r2(rma_Distractor_MP$QM)`, p `r psig(rma_Distractor_MP$QMp)`.
+This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object.
+We next assessed whether distractor familiarity was related to mispronunciation sensitivity.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
+The moderator test was significant, QM(`r r2(rma_Distractor$m)`) = `r r2(rma_Distractor$QM)`, p `r psig(rma_Distractor$QMp)`, but the interaction between distractor familiarity and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
+These results suggest that overall, infants' familiarity with the distractor object (familiar or unfamiliar) did not impact their mispronunciation sensitivity.
+
+```{r PlotDistFamEffect_NoAge}
+
+dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
+dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "Familiar Distractor", "Unfamiliar Distractor")
+
+# Color Blind palette:
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
+p <- ggplot(dat, aes(condition_label, g_calc, fill = condition_label)) + 
+  geom_boxplot() + 
+  facet_grid(.~dist_code) +
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+  jpeg(filename = "figures/Figure_4Distractor_fam.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
+```{r DistractorTypeAge}
+
+rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)
+
+sum_eff <- coef(summary(rma_DistractorAge))[4,]
+
+rma_DistractorAgeMS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
+
+#summary(rma_DistractorAgeMS)
+
+sum_eff1 <- coef(summary(rma_DistractorAgeMS))[8,]
+sum_eff2 <- coef(summary(rma_DistractorAgeMS))[7,]
+
+```
+
+We next examined whether age modulates object recognition or mispronunciation sensitivity when the distractor image is familiar or unfamiliar.
+For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_DistractorAge$m)`) = `r r2(rma_DistractorAge$QM)`, p `r psig(rma_DistractorAge$QMp)`.
+This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object, regardless of their age.
+We next assessed whether the relationship between distractor familiarity and mispronunciation sensitivity was modulated by age.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
+The moderator test was significant, QM(`r r2(rma_DistractorAgeMS$m)`) = `r r2(rma_DistractorAgeMS$QM)`, p `r psig(rma_DistractorAgeMS$QMp)`.
+Although the three-way-interaction between condition, distractor familiarity, and age was not significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`), here the interaction between condition and distractor familiarity was significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`).
+
+[KATIE] WHAT DOES IT MEAN THAT IN THIS LAST TEST THERE WAS AN INTERACTION BETWEEN CONDITION AND DISTRACTOR FAMILIARITY, WHEN AGE WAS INCLUDED AS A MODERATOR?
+DOES THAT MEAN THAT AGE IS CONTROLLED FOR?
+UNDERSTANDING THIS WILL HELP ME FORMULATE THE CONCLUSION SENTENCE AND MOTIVATE THE NEXT SET OF ANALYSES.
+
+```{r DistractorTypeAgeRangeSubset}
+
+object_pair_ages <- dat %>%
+  group_by(object_pair) %>%
+  summarize(min_age = r2(min(mean_age_1, na.rm=TRUE)),
+            max_age = r2(max(mean_age_1, na.rm=TRUE)),
+            mean_age = r2(mean(mean_age_1, na.rm=TRUE)))
+
+fn <- subset(dat, object_pair=="familiar_novel")
+
+ff <- subset(dat, object_pair=="familiar_familiar")
+
+age_diff_dist <- t.xtable(t.test(fn$mean_age_1, ff$mean_age_1, paired = F))
+
+#t.test(fn$mean_age_1, ff$mean_age_1)
+
+opa <- as.data.frame(object_pair_ages)
+min_age <- max(opa$min_age)
+max_age <- min(opa$max_age)
+
+dat_age_MP= db_ET_MP%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+rma_Distractor_MP <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat_age_MP, random = ~ collapse | short_cite)
+
+#summary(rma_Distractor_MP)
+
+sum_eff <- round(coef(summary(rma_Distractor_MP))[2,], 2)
+
+# misp sensitivity
+dat_age= dat%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+rma_Distractor_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition, data = dat_age, random = ~ collapse | short_cite)
+
+#summary(rma_Distractor_MS)
+
+sum_eff <- coef(summary(rma_Distractor_MS))[2,]
+
+```
+
+Although we anticipated that older children may be more impacted by the presence of a unfamiliar compared to familiar distractor image, we found that age and distractor familiarity did not impact mispronunciation sensitivity.
+Inspection of the ages tested using different kinds of distractors, however, revealed differences.
+Infants tested using a familiar distractor were younger (M = 588.76 days, SD = 136.47, range = 207.8 - 768 days) than those infants tested using an unfamiliar distractor (M = 678.85 days, SD = 115.47, range = 544.48 - 920.2 days), which a two-sample t-test revealed to be a significant difference, t(153.83) = 5.30, p < .0001.
+
+[KATIE] SO, IS IT OKAY TO DO THE AGE SUBSET ANALYSIS AFTER THIS?
+SOMETHING LIKE "TO ENSURE THAT THE LACK OF A DIFFERENCE WASN'T DUE TO THE DIFFERENCE IN AGES OF INFANTS TESTED WITH DIFFERENT TYPES OF DISTRACTORS, WE ANALYZED A SUBSET OF PAPERS THAT TESTED AGES WHERE BOTH FAMILIAR AND UNFAMILIAR DISTRACTORS WERE USED." IN THE SUBSET ANALYSIS, FOR MISP SENSITIVITY, THERE IS A SIGNIFICANT INTERACTION BETWEEN DISTRACTOR FAMILIARITY AND CONDITION.
+
+### Phonological overlap between target and distractor
+
+```{r DistractorOverlap_descrip}
+
+dist_overlap_info <- dat %>%
+  group_by(distractor_overlap) %>%
+  summarize(n_exp_conditions =  n())
+
+```
+
+To assess whether phonological overlap between the target and distractor image labels has an impact on the size of mispronunciation sensitivity, we examined the meta-analytic effect for object identification in response to mispronunciations and mispronunciation sensitivity when the target-distractor pairs either shared the same onset phoneme, had no overlap, or where the distractor was an unfamiliar object.
+We did not include data for which the overlap included both the onset and medial phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset/medial"])`) or coda phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "coda"])`).
+The analysis was therefore based on a subset of the overall dataset, with `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset"])` experimental conditions containing onset phoneme overlap between the target and distractor, `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "no"])` containing no overlap between target and distractor, and `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "novel"])` for targets paired with unfamiliar distractor images.
+There were therfore three possibilities for distractor overlap: onset phoneme overlap, no overlap, and an unfamiliar distractor.
+In our analysis, we were interested in the difference between overlap and lack of overlap; therefore, experimental conditions containing onset phoneme overlap were coded as the reference condition and compared with responses to experimental conditions with no overlap or an unfamiliar distractor separately.
+
+[KATIE] CAN YOU CHECK THE WAY THAT I WROTE THE LAST SENTENCE?
+
+```{r DistractorOverlap}
+db_ET_MPo = db_ET_MP %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
+
+rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
+
+#summary(rma_DistractorOverlap)
+
+db_ET_MPo_MS = dat %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+db_ET_MPo_MS$distractor_overlap <- factor(db_ET_MPo_MS$distractor_overlap, levels = c("onset", "no", "novel"))
+
+rma_DistractorOverlapMS <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MPo_MS, random = ~ collapse | short_cite)
+
+#summary(rma_DistractorOverlapMS)
+
+sum_eff1 <- coef(summary(rma_DistractorOverlapMS))[5,]
+sum_eff2 <- coef(summary(rma_DistractorOverlapMS))[6,]
+
+```
+
+Regarding object identification in response to mispronunciations, when distractor overlap was included as a moderator, the moderator test was not significant QM(`r r2(rma_DistractorOverlap$m)`) = `r r2(rma_DistractorOverlap$QM)`, p `r psig(rma_DistractorOverlap$QMp)`.
+This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with a distractor image that contained overlap on the onset phoneme or no overlap with the target word, or was an unfamiliar object.
+We next assessed whether target-distractor overlap was related to mispronunciation sensitivity.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
+The moderator test was significant, QM(`r r2(rma_DistractorOverlapMS$m)`) = `r r2(rma_DistractorOverlapMS$QM)`, p `r psig(rma_DistractorOverlapMS$QMp)`.
+The interaction between condition and target-distractor pairs with no overlap was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`), suggesting that mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap.
+The interaction between condition and target-distractor pairs with an unfamiliar distractor was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`), suggesting that mispronunciation sensitivity was smaller when the distractor image shared the same onset phoneme as the target image compared to when the distractor image was an unfamiliar object.
+This can be seen in Figure X.
+
+```{r PlotDistOverlapEffect}
+
+db_ET_MPo = dat %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
+
+db_ET_MPo$condition_label <- ifelse(db_ET_MPo$condition==1, "Correct", "Mispronunciation")
+
+p <- ggplot(db_ET_MPo, aes(condition_label, g_calc, fill = condition_label)) + 
+  facet_grid(.~distractor_overlap)+
+  geom_boxplot() + 
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+  jpeg(filename = "figures/Figure_5_Distractor_overlap.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
+```{r DistractorOverlap_age}
+
+# object recognition
+db_ET_MPo = db_ET_MP %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
+
+rma_DistractorOverlap_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
+
+# mispronunciation sensitivity
+dat_MPo = dat %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+dat_MPo$distractor_overlap <- factor(dat_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
+
+rma_DistractorOverlap_age_MS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap*condition, data = dat_MPo, random = ~ collapse | short_cite)
+
+#summary(rma_DistractorOverlap_age_MS)
+
+sum_eff1 <- coef(summary(rma_DistractorOverlap_age_MS))[11,]
+sum_eff2 <- coef(summary(rma_DistractorOverlap_age_MS))[12,]
+
+```
+
+Although we did not have any specific predictions about the relationship between infant age and the impact of distractor overlap on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
+First, for object recognition in response to mispronunciations, when age in addition to distractor overlap was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_DistractorOverlap_age$m)`) = `r r2(rma_DistractorOverlap_age$QM)`, p `r psig(rma_DistractorOverlap_age$QMp)`, suggesting that upon hearing a mispronunciation, infants looks to the target image were similar for the three types of overlap, regardless of infant age.
+We next assessed whether the relationship between distractor overlap and mispronunciation sensitivity was modulated by age.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
+The moderator test was significant, QM(`r r2(rma_DistractorOverlap_age_MS$m)`) = `r r2(rma_DistractorOverlap_age_MS$QM)`, p `r psig(rma_DistractorOverlap_age_MS$QMp)`.
+The interaction between age, condition, and target-distractor pairs with no overlap was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`).
+As can be seen in Figure X, the difference between correct pronunciations and mispronunciations (mispronunciation sensitivity) stays steady across infant ages for both target words paired with distractors containing onset overlap with the target word as well as distractors containing no overlap.
+As infants aged, however, overall recognition (regardless of condition) increased for target-distractor pairs containing onset overlap, whereas for overall recognition decreased for target-distractor pairs containing no overlap.
+The interaction between age, condition, and target-distractor pairs with an unfamiliar distractor was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`).
+As can also be seen in Figure X, mispronunciation sensitivity for target words paired with unfamiliar distractors decreased with age, while it remained steady across a similar range of ages for target words paired with distractors containing onset overlap with the target word.
+
+```{r PlotDistOverlap_cond_age}
+
+db_ET_MPo = dat %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
+
+db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
+
+db_ET_MPo$condition_label <- ifelse(db_ET_MPo$condition==1, "Correct", "Mispronunciation")
+
+p <- ggplot(db_ET_MPo, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
+    facet_grid(.~distractor_overlap)+
+  geom_point(aes(size = weights_g),show.legend=FALSE) + 
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+  jpeg(filename = "figures/Figure_6_Distractor_overlap_age.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
+### Position of mispronunciation
+
+```{r Location_descrip}
+
+misp_location_info <- dat %>%
+  group_by(mispron_location) %>%
+  summarize(n_exp_conditions =  n())
+
+```
+
+To assess whether the position of the mispronunciation has an impact on mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to mispronunciations on the onset and medial phonemes.
+We did not include data for which the mispronunciation was located on the coda (*n* = `r with(misp_location_info, n_exp_conditions[mispron_location == "coda"])`), varied in regard to position (*n* = `r with(misp_location_info, n_exp_conditions[mispron_location == "coda/medial" | mispron_location == "onset/medial" | mispron_location == "onset/medial/coda"])`), or was not reported (*n* = `r with(misp_location_info, n_exp_conditions[is.na(mispron_location)])`).
+The analysis was therefore based on a subset of the overall dataset, with `r with(misp_location_info, n_exp_conditions[mispron_location == "onset"])` experimental conditions comparing a mispronunciation on the onset phoneme and `r with(misp_location_info, n_exp_conditions[mispron_location == "medial"])` experimental conditions comparing a mispronunciation on the medial phoneme.
+
+```{r Location_misp}
+#table(db_ET_MP$mispron_location)
+
+db_ET_MPl = db_ET_MP %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
+
+db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("onset", "medial"))
+
+#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
+rma_Location_MP <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_MPl, random = ~collapse | short_cite)
+
+db_ET_MPl = dat %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
+
+db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("onset", "medial"))
+
+rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition, data = db_ET_MPl, random = ~collapse | short_cite)
+
+sum_eff <- coef(summary(rma_LocationCondition))[4,]
+
+```
+
+Regarding object identification in response to mispronunciations, when mispronunciation location was included as a moderator, the moderator test was not significant QM(`r r2(rma_Location_MP$m)`) = `r r2(rma_Location_MP$QM)`, p `r psig(rma_Location_MP$QMp)`.
+This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was located on the onset or  medial phonemes.
+We next assessed whether mispronunciation location was related to mispronunciation sensitivity.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
+The moderator test was significant, QM(`r r2(rma_LocationCondition$m)`) = `r r2(rma_LocationCondition$QM)`, p `r psig(rma_LocationCondition$QMp)`, but the interaction between mispronunciation location and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
+These results suggest that overall, the location of the mispronunciation (onset, medial) did not impact mispronunciation sensitivity.
+
+```{r PlotPositionEffect}
+
+#dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial" |
+#                mispron_location == "offset")
+
+dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
+
+dat.p = dat %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
+
+dat.p$mispron_location <- factor(dat.p$mispron_location, levels = c("onset", "medial"))
+
+p <- ggplot(dat.p, aes(condition_label, g_calc, fill = condition_label)) + 
+  facet_grid(.~mispron_location)+
+  geom_boxplot() + 
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+  jpeg(filename = "figures/Figure_7_Mispronunciation_position.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
+```{r Location_misp_age}
+#table(db_ET_MP$mispron_location)
+
+db_ET_MPl = db_ET_MP %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
+
+db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("onset", "medial"))
+
+#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
+rma_Location_MP_age <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
+
+db_ET_MPl = dat %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
+
+db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("onset", "medial"))
+
+rma_LocationCondition_age <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
+
+sum_eff <- coef(summary(rma_LocationCondition))[8,]
+
+```
+
+Although we did not have any specific predictions about the relationship between infant age and the impact of mispronuncition location on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
+First, for object recognition in response to mispronunciations, when age in addition to mispronunciation location was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_Location_MP_age$m)`) = `r r2(rma_Location_MP_age$QM)`, p `r psig(rma_Location_MP_age$QMp)`, suggesting that upon hearing a mispronunciation, infants looks to the target image were similar for both onset and medial mispronunciations, regardless of infant age.
+We next assessed whether the relationship between mispronunciation location and mispronunciation sensitivity was modulated by age.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
+The moderator test was significant, QM(`r r2(rma_LocationCondition_age$m)`) = `r r2(rma_LocationCondition_age$QM)`, p `r psig(rma_LocationCondition_age$QMp)`, but the interaction between mispronunciation location, age, and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
+These results provide further evidence that location of the mispronunciation (onset, medial) did not impact mispronunciation sensitivity.
+
+### Type of mispronunciation (consonant or vowel)
+
+```{r CV_descript}
+
+CV_info <- dat %>%
+  group_by(type_feature) %>%
+  summarize(n_exp_conditions =  n())
+
+CV_location_info <- dat %>%
+  group_by(type_feature, mispron_location) %>%
+  summarize(n_exp_conditions =  n())
+
+```
+
+To assess whether the type of mispronunciation impacts sensitivity to mispronunciations, we calculated the meta-analytic effect for object identification in response to the type of mispronunciation.
+Although most theoretical discussion of mispronunciation type has focused on consonants and vowels, our dataset also included tone mispronunciations.
+In our analysis, we were interested in the difference between consonants and vowels, but also include an exploratory analysis of responses to tones, consonants, and vowels.
+We therefore conducted two sets of analyses, one analyzing consonants and vowels alone and a second comparing responses to tones with that of consonants and vowels, separately.
+For the latter analysis, tones were coded as the reference condition.
+We did not include data for which mispronunciation type varied within experiment and was not reported separately (*n* = `r with(CV_info, n_exp_conditions[type_feature == "consonant_and_vowel" | type_feature == "consonant_vowel_tone"])`).
+The analysis was therefore based on a subset of the overall dataset, with `r with(CV_info, n_exp_conditions[type_feature == "consonant"])` experimental conditions comparing a consonant mispronunciation, `r with(CV_info, n_exp_conditions[type_feature == "vowel"])` experimental conditions comparing a vowel mispronunciation, and `r with(CV_info, n_exp_conditions[type_feature == "tone"])` experimental conditions comparing a tone mispronunciation.
+Below, we first report the set of analyses comparing consonants with vowels before moving on to the second set of exploratory analyses comparing tones with that of consonants and vowels.
+
+[KATIE] WHAT DO YOU THINK ABOUT THIS?
+WE HAVE THE TONES AND ITS A NOVEL, INTERESTING THING, I THINK, AND PERHAPS WORTH IT TO INCLUDE A COMPARISON OF TONES ALONGSIDE THE MORE THEORETICALLY IMPORTANT COMPARISON BETWEEN CONSONANTS AND VOWELS.
+
+```{r MPtype_cv}
+
+# C vs. V
+db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel")
+
+db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("consonant", "vowel"))
+
+rma_TypeFeaturesMP <- rma.mv(g_calc, g_var_calc, mods = ~type_feature, data = db_MP_type, random = ~collapse | short_cite)
+
+# C vs. V with condition
+
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
+
+rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition, data = db_type, random = ~collapse | short_cite)
+
+sum_eff1 <- coef(summary(rma_TypeFeaturesMP_Condition))[4,]
+
+```
+
+We first analyzed experimental conditions where mispronunciation type was either a consonant or vowel.
+Regarding object identification in response to mispronunciations, when mispronunciation type was included as a moderator, the moderator test was not significant QM(`r r2(rma_TypeFeaturesMP$m)`) = `r r2(rma_TypeFeaturesMP$QM)`, p `r psig(rma_TypeFeaturesMP$QMp)`.
+This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was a consonant or a vowel.
+We next assessed whether type of mispronunciation (consonant or vowel) was related to mispronunciation sensitivity.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
+The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, p `r psig(rma_TypeFeaturesMP_Condition$QMp)`, but the interaction between mispronunciation type and condition was not significant $\beta$ = `r r2(sum_eff1$estimate)`, (SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`).
+These results suggest that overall, the type of  mispronunciation (consonant vs.
+vowel) did not impact mispronunciation sensitivity.
+
+```{r MPtype_cv_age}
+db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
+
+db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("consonant", "vowel"))
+
+rma_TypeFeaturesMPage <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)
+
+# with condition
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
+
+rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~collapse | short_cite)
+
+sum_eff <- coef(summary(rma_TypeFeaturesMP_Condition))[8,]
+
+```
+
+We next examined whether age modulates object recognition or mispronunciation sensitivity when the mispronunciation is a consonant or vowel.
+For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_TypeFeaturesMPage$m)`) = `r r2(rma_TypeFeaturesMPage$QM)`, p `r psig(rma_TypeFeaturesMPage$QMp)`.
+This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was on a consonant or vowel phoneme, regardless of their age.
+We next assessed whether the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity was modulated by age.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
+The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, p `r psig(rma_TypeFeaturesMP_Condition$QMp)`.
+The interaction between mispronunciation type, condition, and age was significant ($\beta$ = `r r2(sum_eff$estimate)`, SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
+As can be seen in Figure X, as infants age, mispronunciation sensitivity grows larger for vowel mispronunciations but becomes smaller for consonant mispronunciations.
+Noticeably, mispronunciation sensitivity appears greater for consonant compared to vowel mispronunciations at younger ages, but this difference shifts as infants age.
+
+```{r PlotCVEffect_cond_age}
+
+dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
+dat_type$type_feature <- ifelse(dat_type$type_feature == "consonant", "Consonant", "Vowel")
+
+#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
+
+#dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
+
+dat_type$condition_label = ifelse(dat_type$condition==1, "Correct", "Mispronunciation")
+
+p <- ggplot(dat_type, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
+    facet_grid(.~type_feature)+
+  geom_point(aes(size = weights_g),show.legend=FALSE) + 
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+  jpeg(filename = "figures/Figure_8_FeatureType_Cond_Age.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
+```{r MPtype_cv_lang_descript}
+
+family <- dat %>%
+  group_by(lang_family) %>%
+  summarize(count = n())
+
+lang_family <- dat %>%
+  group_by(native_lang, lang_family) %>%
+  summarize(count = n())
+
+cv_family <- dat %>%
+  group_by(type_feature, lang_family) %>%
+  summarize(count = n())
+
+```
+
+```{r MPtype_cv_lang}
+
+db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
+
+db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("consonant", "vowel"))
+
+db_MP_type <- subset(db_MP_type, lang_family != "Sino-Tibetian")
+
+rma_TypeFeaturesMPfam <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family, data = db_MP_type, random = ~collapse | short_cite)
+
+# with condition
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
+
+db_type <- subset(db_type, lang_family != "Sino-Tibetian")
+
+rma_TypeFeaturesMPC <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family, data = db_type, random = ~collapse | short_cite)
+
+sum_eff1 <- coef(summary(rma_TypeFeaturesMPC))[7,]
+sum_eff2 <- coef(summary(rma_TypeFeaturesMPC))[8,]
+
+# summary(glht(rma_TypeFeaturesMPC, linfct=cbind(contrMat(rep(1,8), type="Tukey"))), test=adjusted("none"))
+# 
+# ranef(rma_TypeFeaturesMPC)
+
+```
+
+To examine whether infants' native language impacts sensitivity to consonant and vowel mispronunciations, we classified infants into language families.
+Infants learning American English (*n* = `r with(lang_family, count[native_lang == "American English"])`), British English (*n* = `r with(lang_family, count[native_lang == "British English"])`), Danish (*n* = `r with(lang_family, count[native_lang == "Danish"])`), Dutch (*n* = `r with(lang_family, count[native_lang == "Dutch"])`), and German (*n* = `r with(lang_family, count[native_lang == "German"])`) were classified into the Germanic language family (*n* = `r with(family, count[lang_family == "Germanic"])`).
+Infants learning Catalan (*n* = `r with(lang_family, count[native_lang == "Catalan"])`), Spanish (*n* = `r with(lang_family, count[native_lang == "Spanish"])`), French (*n* = `r with(lang_family, count[native_lang == "French"])`), Catalan and Spanish simultaneously (i.e.
+bilinguals; *n* = `r with(lang_family, count[native_lang == "Catalan-Spanish"])`), and Swiss French (*n* = `r with(lang_family, count[native_lang == "Swiss French"])`) were classified into the Romance language family (*n* = `r with(family, count[lang_family == "Romance"])`).
+For object recognition in response to a mispronunciation, including language family as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_TypeFeaturesMPfam$m)`) = `r r2(rma_TypeFeaturesMPfam$QM)`, p `r psig(rma_TypeFeaturesMPfam$QMp)`.
+This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was on a consonant or vowel phoneme, regardless of the language family of their native language.
+We next assessed whether the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity was modulated by language family.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family as additional moderators.
+The moderator test was significant, QM(`r r2(rma_TypeFeaturesMPC$m)`) = `r r2(rma_TypeFeaturesMPC$QM)`, p `r psig(rma_TypeFeaturesMPC$QMp)`.
+The interaction between condition and language family was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`), suggesting XXXXXXXXXXXXXX.
+The interaction between mispronunciation type, condition, and language family was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`).
+As can be seen in Figure X, mispronunciation sensitivity for consonants was similar for Germanic and Romance languages.
+Mispronunciation sensitivity for vowels, however, was greater for Germanic compared to Romance languages.
+
+[KATIE] I'M NOT REALLY SURE WHAT THE CONDITION BY LANGUAGE FAMILY INTERACTION MEANS. SHOULD WE EVEN INTERPRET IT?
+
+```{r PlotCVEffect_Lang}
+
+dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
+dat_type$type_feature <- ifelse(dat_type$type_feature == "consonant", "Consonant", "Vowel")
+
+#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
+
+dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
+
+dat_type_sub$condition_label = ifelse(dat_type_sub$condition==1, "Correct", "Mispronunciation")
+
+p <- ggplot(dat_type_sub, aes(condition_label, g_calc, fill = condition_label)) + 
+  geom_boxplot() + 
+  facet_grid(.~type_feature*lang_family)+
+  #geom_line(y= 0, linetype="dotted") + 
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
+    scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  xlab("Language Family") + 
+  ylab("Effect size Hedges' g")
+p
+
+ jpeg(filename = "figures/Figure_9_FeatureType_Cond_LangFam.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
+```{r MPtype_cv_lang_age}
+
+db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
+
+db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("consonant", "vowel"))
+
+db_MP_type <- subset(db_MP_type, lang_family != "Sino-Tibetian")
+
+rma_TypeFeaturesMPfam <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family*age.C, data = db_MP_type, random = ~collapse | short_cite)
+
+ sum_eff1 <- coef(summary(rma_TypeFeaturesMPC))[8,]
+
+# with condition
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
+
+db_type <- subset(db_type, lang_family != "Sino-Tibetian")
+
+rma_TypeFeaturesMPC <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family, data = db_type, random = ~collapse | short_cite)
+
+sum_eff1 <- coef(summary(rma_TypeFeaturesMPC))[7,]
+sum_eff2 <- coef(summary(rma_TypeFeaturesMPC))[8,]
+
+# summary(glht(rma_TypeFeaturesMPC, linfct=cbind(contrMat(rep(1,8), type="Tukey"))), test=adjusted("none"))
+# 
+# ranef(rma_TypeFeaturesMPC)
+
+```
+
+Finally, we examined the relationship between language family and infant age and mispronunciation sensitivity to consonants and vowels.
+For object recognition in response to a mispronunciation, including language family and infant age as a moderator resulted in a moderator test that was significant, QM(`r r2(rma_TypeFeaturesMPfam$m)`) = `r r2(rma_TypeFeaturesMPfam$QM)`, p `r psig(rma_TypeFeaturesMPfam$QMp)`.
+The interaction between language family, age, and type of mispronunciation (consonant or vowel) was significant, ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`).
+As can be seen in Figure X, for infants learning Germanic languages, increasing age was related to increasing mispronunciation sensitivity for vowel mispronunciations, but decreasing sensitivity for consonant mispronunciations.
+In contrast, infants learning Romance languages have an even greater increase with age in sensitivity to vowel mispronunciations.
+Surprisingly, sensitivity to consonant mispronunciations shows a reversal in infants learning Romance languages: the growth in target looks for consonant mipronunciations increases and surpases that of target looks for correct pronunciations.
+
+[KATIE] AGAIN, THERE ARE ADDITIONAL INTERACTIONS THAT ARE SIGNIFICANT... SHOULD THEY BE INTERPRETED? ALSO, WTF ROMANCE LANGUAGES?
+
+```{r PlotCVEffect_cond_age_fam}
+
+dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
+dat_type$type_feature <- ifelse(dat_type$type_feature == "consonant", "Consonant", "Vowel")
+
+#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
+
+dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
+
+dat_type_sub$condition_label = ifelse(dat_type_sub$condition==1, "Correct", "Mispronunciation")
+
+p <- ggplot(dat_type_sub, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
+    facet_grid(.~type_feature*lang_family)+
+  geom_point(aes(size = weights_g),show.legend=FALSE) + 
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Effect size Hedges' g")
+
+p
+
+  jpeg(filename = "figures/Figure_10_FeatureType_Cond_Age_LangFam.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p
+
+  dev.off()
+
+```
+
+```{r MPtype_cvt}
+
+# C vs. V vs. T
+db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" | type_feature == "tone")
+
+db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("tone", "consonant", "vowel"))
+
+rma_TypeFeaturesMPT <- rma.mv(g_calc, g_var_calc, mods = ~type_feature, data = db_MP_type, random = ~collapse | short_cite)
+
+# C vs. V vs. T with condition
+
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel"| type_feature == "tone")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("tone", "consonant", "vowel"))
+
+rma_TypeFeaturesMP_ConditionT <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition, data = db_type, random = ~collapse | short_cite)
+
+sum_eff2c <- coef(summary(rma_TypeFeaturesMP_ConditionT))[5,]
+sum_eff2v <- coef(summary(rma_TypeFeaturesMP_ConditionT))[6,]
+
+```
+
+Although we had no predictions regarding mispronunciation sensitivity to tone mispronunciations, we included an exploratory analysis to examine whether responses to tone mispronunciations were different from that of consonants or vowels.
+Regarding object identification in response to mispronunciations, when mispronunciation type was included as a moderator, the moderator test was not significant QM(`r r2(rma_TypeFeaturesMPT$m)`) = `r r2(rma_TypeFeaturesMPT$QM)`, p `r psig(rma_TypeFeaturesMPT$QMp)`.
+This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for tone mispronunciations in comparison with both consonants and vowels.
+We next assessed whether type of mispronunciation (tone, consonant, vowel) was related to mispronunciation sensitivity.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
+The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_ConditionT$m)`) = `r r2(rma_TypeFeaturesMP_ConditionT$QM)`, p `r psig(rma_TypeFeaturesMP_ConditionT$QMp)`.
+The interaction between condition and consonant mispronunciations was not significant $\beta$ = `r r2(sum_eff2c$estimate)`, (SE = `r r2(sum_eff2c$se)`, 95% CI [`r r2(sum_eff2c$ci.lb)`, `r r2(sum_eff2c$ci.ub)`], p `r psig(sum_eff2c$pval)`), suggesting that there was no difference in looks to the target in response to consonant and tone mispronunciations.
+The interaction between condition and vowel mispronunciations was also not significant $\beta$ = `r r2(sum_eff2v$estimate)`, (SE = `r r2(sum_eff2v$se)`, 95% CI [`r r2(sum_eff2v$ci.lb)`, `r r2(sum_eff2v$ci.ub)`], p `r psig(sum_eff2v$pval)`), suggesting that there was no difference in looks to the target in response to vowel and tone mispronunciations.
+
+```{r MPtype_cvt_age}
+db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" | type_feature == "tone")
+
+db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("tone", "consonant", "vowel"))
+
+rma_TypeFeaturesMPage <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)
+
+# with condition
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" | type_feature == "tone")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("tone", "consonant", "vowel"))
+
+rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~collapse | short_cite)
+
+sum_eff1 <- coef(summary(rma_TypeFeaturesMP_Condition))[11,]
+sum_eff2 <- coef(summary(rma_TypeFeaturesMP_Condition))[12,]
+
+```
+
+We further included an exploratory analysis of the relationship between infant age and the impact of tone mispronunciations in comparison to consonant and vowel mispronunciations.
+First, for object recognition in response to mispronunciations, when age in addition to mispronunciation location was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_TypeFeaturesMPage$m)`) = `r r2(rma_TypeFeaturesMPage$QM)`, p `r psig(rma_TypeFeaturesMPage$QMp)`.
+This suggests that upon hearing a mispronunciation, infants looks to the target image were not different between tone and vowel or tone and consonant mispronunciations, regardless of their age.
+We next assessed whether the relationship between mispronunciation type (tone, consonant, vowel) and mispronunciation sensitivity was modulated by age.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
+The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, p `r psig(rma_TypeFeaturesMP_Condition$QMp)`, but the interactions between condition, age, and both consonant mispronciations ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`) and vowel mispronunciations ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`) were not significant.
+Infants' sensitivity to tone mispronunciations compared to consonant or vowel mispronunciations did not differ with age.
+
+[KATIE] WORTH IT TO INCLUDE LANGUAGE FAMILY ANALYSES TOO?
+
+# Discussion
+
+To Summarize:
+
+** Overall Meta-analytic Effect **
+
+  + Accept mispronunciations as labels for targets
+  + Sensitive to mispronunciations
+  + lack of change over development
+
+** Vocabulary **
+
+  + no relationship?
+  + talk about how few studies report it
+
+** Size of Mispronunciation **
+
+  + graded sensitivity to number of features changed in a mispronunciation
+  + importance for controlling in experimental design
+  + Perhaps a call for more studies to include multiple number of features changed, so that this can be assessed? There was a narrow age where this was actually manipulated.
+
+** Distractor Familiarity **
+
+  + Not really sure, check the results. A key interaction is significant in one model but not the other.
+  + Again, ages not matched very well for the two groups here. Decide about whether to include a age subset analysis
+
+** Phonological overlap between target and distractor **
+
+  + mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap
+  + this is rather the opposite of what one would expect, right?
+  + mispronunciation sensitivity was smaller when the distractor image shared the same onset phoneme as the target image compared to when the distractor image was an unfamiliar object
+  + Maybe it would be useful to have time course analyses to address this issue further
+  + As infants aged, overall recognition (regardless of condition) increased for target-distractor pairs containing onset overlap, whereas overall recognition decreased for target-distractor pairs containing no overlap.
+  + mispronunciation sensitivity for target words paired with unfamiliar distractors decreased with age, while it remained steady across a similar range of ages for target words paired with distractors containing onset overlap with the target word.
+
+** Position of mispronunciation **
+
+  + really no impact at all
+
+** Type of mispronunciation **
+
+  + Overall, no difference between consonants and vowels 
+  + Consonant mispronunciation sensitivity decreases with age
+  + Vowel mispronunciation sensitivity increases with age
+  + mispronunciation sensitivity for consonants similar for Germanic and Romance languages
+  + Mispronunciation sensitivity for vowels greater for Germanic compared to Romance languages
+  + For Germanic infants, increasing age was related to increasing mispronunciation sensitivity for vowel mispronunciations, but decreasing sensitivity for consonant mispronunciations. 
+  + For Romance infants, an even greater increase with age in sensitivity to vowel mispronunciations. 
+  + For Romance infants, the growth in target looks for consonant mipronunciations increases and surpases that of target looks for correct pronunciations
+  + exploratory analyses with tone mispronunciations suggest no great difference in sensitivity when compared to consonant and vowel mispronunciations
+
+When it comes to designing studies, best practices and current standards might not always overlap.
+Indeed, across a set of previous meta-analyses it was shown that particularly infant research does not adjust sample sizes according to the effect in question (Bergmann et al., in press).
+A meta-analysis is a first step in improving experiment planning by measuring the underlying effect and its variance, which is directly related to the sample needed to achieve satisfactory power in the null hypothesis significance testing framework.
+Failing to take effect sizes into account can both yield to underpowered research and to testing too many participants, both consequences are undesirable for a number of reasons that have been discussed in depth elsewhere.
+We will just briefly mention two that we consider most salient for theory building: Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature (citationcitation).
+Overpowered studies mean that participants were tested unnecessarily, which has substantial ethical consequences particularly when working with infants and other difficult to recruit and test populations.
+
+From Christina: let's make a note to put sth in the discussion about our curve being surprisingly flat for correctly pronounced words bc people adapt their analysis windows?
+Bc if you look at Molly's reaction time paper, there is a steep increase.
+
+Discussing the Moderator Analyses
+Maybe put them together into the ones that worked out as we predicted and those that didn’t?
+So, here is evidence that supports existing arguments, that doesn’t need to be a huge chunk.
+But then more space devoted to moderator analyses that didn’t work out according to predictions.
+
+It should be noted that the majority of consonant mispronunciations were located on the onset phoneme (*n* = `r with(CV_location_info, n_exp_conditions[type_feature == "consonant" & mispron_location == "onset"])`; total consonant conditions, *n* = `r with(CV_info, n_exp_conditions[type_feature == "consonant"])`), while the majority of vowel mispronunciations were located on the medial phoneme (*n* = `r with(CV_location_info, n_exp_conditions[type_feature == "vowel" & mispron_location == "medial"])`; total vowel conditions, *n* = `r with(CV_info, n_exp_conditions[type_feature == "vowel"])`).
+In their analysis using TRACE, Mayor and Plunkett (2014) found that the difference between sensitivity to consonant and vowel mispronunciations was due to infants' lexical knowlege consisting of a majority consonant onset words.
+
+[KATIE] COME BACK TO THIS.

### 2018-10-15 Paper_Analyses.Rmd

@@
     toc: true
+
+bibliography: references.bib
 ---
-```{r Setup, echo = FALSE, warning=FALSE}
-knitr::opts_chunk$set(echo = TRUE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)
+```{r Setup, echo = FALSE, warning=FALSE, warning = FALSE, error = FALSE, message = FALSE}
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)
 
 ### Load libraries
-library(tidyverse)
+
 library(metafor)
@@
 library(multcomp)
+library(poibin)
+library(tidyverse)
 
@@
 
-r2 <- function(x){ round(x, 2)}
+r2 <- function(x){ round(x, 3)}
+
+#[CHRISTINA: I prefer exact p-values with more granularity]
 
 psig <- function(x){
-  ifelse(x < .0001, "< .0001",
   ifelse(x < .001, "< .001",
-                ifelse(x < .01, "< .01",
-                       ifelse(x > .01 & x < .05, paste("=", r2(x), sep = " "), paste("=", r2(x), sep = " ")))))
+         #ifelse(x < .001, "< .001",
+                #ifelse(x < .01, "< .01",
+                       ifelse(x > .001 & x < .05, paste("=", r2(x), sep = " "), paste("=", r2(x), sep = " ")))#))
 }
@@
 
-cur_dir <- getwd()
-
-```
-
-#Preparation
-
-Read in data and tidy up dataset
-
-```{r ReadIn,  echo = FALSE}
+# [CHRISTINA This should not be necessary]
+#cur_dir <- getwd()
+
+```
+
+```{r ReadIn}
 
@@
 
-```{r Preprocess, echo = FALSE}
+```{r Preprocess}
 
@@
 
-Plotting defaults
-
-```{r PlotAPATheme, echo = FALSE}
+```{r PlotAPATheme}
+# Plotting defaults
+
 #Themes and plot
@@
 To this end, we provide all data and analysis scripts on the supplementary website (https://osf.io/rvbjs/) and open our meta-analysis up for updates (Tsuji, Bergmann, & Cristia, 2014).
+The most recent version is available via the website and the interactive platform MetaLab (metalab.stanford.edu; Bergmann et al., 2018).
+Since the present paper was written with embedded analysis scripts in R [@R], it is always possible to re-analyze an updated dataset.
 In addition, we follow the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials (Moher, Liberati, Tetzlaff, Altman & PRISMAGroup, 2009).
@@
 
-```{r SummaryTable, echo = FALSE}
+```{r SummaryTable}
 
@@
 
-kable(Sum_table)
+kable(Sum_table, col.names = c("Paper", "Age", "Vocabulary", "# Features", "Distractor", "Distractor name overlap", "MP Position", "MP Type"))
 
@@
 [KATIE] THIS TABLE IS DEFINITELY NOT FINISHED!
+[CHRISTINA suggestions: N features should be a range and exclude 0; we could abbreviate Comperehension/Production to Comp./Prod., etcetc]
 
@@
 
-```{r DescriptivesPubtype, echo = FALSE}
+```{r DescriptivesPubtype}
 
@@
 
-kable(pub_info)
-
-pi <- dat[,c("short_cite", "publication_status")]
-pi <- unique(pi)
-
-c.plot <- ggplot(pi, aes(x= publication_status)) + 
-  geom_text(stat='count', aes(label=..count..), vjust=-1, size = 5)+
-  geom_bar(stat="count")+
-  coord_cartesian(ylim = c(0, 30))+
-  apatheme+
-  theme(axis.text.x = element_text(size = 20, angle = -45, hjust = .11),
-        axis.title.x = element_blank())
-
-c.plot
-
-  jpeg(filename = "figures/Pub_count.jpg", 
-       width = 500, height = 500, units = "px")
-
-  c.plot
-
-  dev.off()
+kable(pub_info, col.names = c("Publication Type", "# Items", "# Effect Sizes"))
+
+# Not sure about this plot
+#pi <- dat[,c("short_cite", "publication_status")]
+#pi <- unique(pi)
+
+#c.plot <- ggplot(pi, aes(x= publication_status)) + 
+#  geom_text(stat='count', aes(label=..count..), vjust=-1, size = 5)+
+#  geom_bar(stat="count")+
+#  coord_cartesian(ylim = c(0, 30))+
+#  apatheme+
+#  theme(axis.text.x = element_text(size = 20, angle = -45, hjust = .11),
+#        axis.title.x = element_blank())
+
+#c.plot
+
+#  jpeg(filename = "figures/Pub_count.jpg", 
+#       width = 500, height = 500, units = "px")
+
+#  c.plot
+
+#  dev.off()
 
@@
 
-The `r length(unique(dat$short_cite))` papers we identified as relevant were then coded with as much detail as possible (Tsuji, Bergmann, & Cristia, 2014; Bergmann et al., in press).
+The `r length(unique(dat$short_cite))` papers we identified as relevant were then coded with as much detail as possible (Tsuji, Bergmann, & Cristia, 2014; Bergmann et al., 2018).
 For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results.
@@
 2 Mean age reported per group of infants, in days;  
-3 Vocabulary size:  
+3 Vocabulary size, measured by a standardized questionnaire or list;    
 4 Size of mispronunciation, measured in features changed;  
-5 Distractor familiarity: familiar, unfamiliar;
+5 Distractor familiarity: familiar or unfamiliar;  
 6 Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;  
-7 Position of mispronunciation: onset, medial, offset;
-8 Type of mispronunciation: consonant, vowel;
-
-We separated out conditions according to whether or not the target word was mispronounced to be able to investigate both infants' looking to the target picture separated by whether or not words were mispronounced and their mispronunciation sensitivity, which is the difference between looking in correct and mispronounced trials.
+7 Position of mispronunciation: onset, medial, offset, or mixed;  
+8 Type of mispronunciation: consonant, vowel, or both.
+
+We separated out conditions according to whether or not the target word was mispronounced to be able to investigate infants' looking to the target picture separated by whether or not words were mispronounced as well as their mispronunciation sensitivity, which is the difference between looks to the target in correct and mispronounced trials.
 When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  (e.g., consonant versus vowel mispronunciations; Mani & Plunkett, 2007).
-The fact that the same infants have contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section).
+The fact that the same infants contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section).
 We will call each row a record; in total there were `r nrow(dat)` records in our data.
@@
 
-kable(comparison_info)
+kable(comparison_info, col.names = c("Type of comparison", "# Papers", "# Effect Size"))
 #table(db_ET_MP$es_method)
 ```
-```{r DescriptivesES, echo = FALSE}
+
+```{r DescriptivesES}
 #how did we calculate effect sizes?
@@
 
-```
-
-All scripts and raw data are available on Open Science Framework (OSF).
-INSERT LINK AS FOOTNOTE HERE.
+#[KATIE] Can you also rename the factors here (like t_one)?
+#[CHRISTINA] Mpt sire what you man, like in the table? You rename things later on, so why not. 
+```
+
 Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to a baseline measurement.
@@
 Across papers the baseline comparison varied; we used the baseline reported by the authors of each paper.
-Most papers (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post_naming_effect"]))`) subtracted the PTL score for the pre-naming phase from the PTL score for the post-naming phase.
+Most papers (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post_naming_effect"]))`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase.
 When interpreting this difference score, a positive value indicates that infants increased their looks to the target after hearing the naming label (correct or mispronounced).
-Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post"]))`) or compared post-naming PTL with chance (50%, (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "post"]))`)).
-For these comparisons, a positive difference score or a post-naming phase PTL score that is greater than the pre-naming phase PTL or chance indicate target looks that indicate object recognition after hearing the naming label.
-
-We report effect sizes for infants' looks to target pictures after hearing a correctly pronounced or mispronounced label (object identification) as well as the difference between effect sizes for correct and mispronounced trials (mispronunciation sensitivity).
+Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post"]))`) or compared post-naming PTL with a chance level of 50%, (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "post"]))`).
+For all these comparisons, a positive difference score or a post-naming phase PTL score that is greater than the pre-naming phase PTL or chance indicate target looks that indicate object recognition after hearing the naming label.
+Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more relative increase in looks to the target.
+
+We report effect sizes for infants' looks to target pictures after hearing a correctly pronounced or a mispronounced label (object identification) as well as the difference between effect sizes for correct and mispronounced trials (i.e.
+mispronunciation sensitivity).
 The effect size we report in the present paper are based on comparison of means, standardized by their variance.
-The most well-known effect size from this group is Cohen's *d* (Cite cohen).
+The most well-known effect size from this group is Cohen's *d* [@cohen].
 To correct for the small sample sizes common in infant research, however, we use as a dependent variable Hedges' *g* instead of Cohen's *d* (Hedges, 1981; Morris, 2000).
 
-No authors made their raw data available.
-Instead, we calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(dat, n_distinct(short_cite[es_method == "group_means_one" | es_method == "group_means_two"]))`) or using reported t-values (*n* = `r with(dat, n_distinct(short_cite[es_method == "t_one" | es_method == "t_two"]))`).
+We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(dat, n_distinct(short_cite[es_method == "group_means_one" | es_method == "group_means_two"]))`) or using reported t-values (*n* = `r with(dat, n_distinct(short_cite[es_method == "t_one" | es_method == "t_two"]))`).
 Raw means and standard deviations were extracted from figures for `r with(dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers.
@@
 looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values.
-One paper reported this correlation, while we were able to compute correlations using means, standard deviations, and t-values (following Csibra, et al.
-2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, submitted).
+One paper reported this correlation [CHRISTINA: Can we cite this??]; we were able to compute correlations using means, standard deviations, and t-values [CHRISTINA: can we add N?] (following Csibra, et al.
+2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, 2018).
 Correlations were imputed for the remaining papers (see Black & Bergmann, 2017, for the same procedure).
-We computed a total of `r sum(dat$is_mp == 0)` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)` for mispronunciations.
-
-To take into account the fact that the same infants contributed to multiple datapoints, we analyze our results in a multilevel approach using the R (R citation) package metafor (Viechtbauer, 20XX, Multulevel reference).
+We could compute a total of `r sum(dat$is_mp == 0)` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)` for mispronunciations.
+
+To take into account the fact that the same infants contributed to multiple datapoints, we analyze our results in a multilevel approach using the R [@R] package metafor [@metafor].
 This means we model as random effect that effect sizes from the same paper share are based on more similar studies than those across papers and that nested therein effects can stem from the same infants.
@@
 ## Publication Bias
+
+[CHRISTINA: Do you think we have to revise this section? I think it's the same as in the proceedings paper.]
 
@@
 To examine whether this is also the case in the mispronunciation sensitivity literature, which would bias the data analyzed in this meta-analysis, we conduct two tests.
-We first examine whether effect sizes are distributed as expected based on sampling error using the rank correlation test of funnel plot asymmetry with the R (R Core Team, 2016) package metafor (Viechtbauer, 2010).
-Effect szes with low-variance are closer to the estimated mean, while effect sizes with high-variance show an increased, evenly-distributed spread around the estimated mean.
-Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app (v4.0, p-curve.com; Simonsohn, Simmons, & Nelson, 2014).
+We first examine whether effect sizes are distributed as expected based on sampling error using the rank correlation test of funnel plot asymmetry with the R [@R] package metafor [@metafor].
+Effect sizes with low-variance are expected to fall closer to the estimated mean, while effect sizes with high-variance should show an increased, evenly-distributed spread around the estimated mean.
+Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app (v4.0, p-curve.com; @pcurve).
 This tests for evidential value by examining whether the p-values have an expected distribution, regardless of whether the null hypothesis is true or not, as well as whether there is a larger proportion of p-values just below the typical alpha threshold of .05, which may indicate questionable research practices.
@@
 
-The models reported are hierarchical random-effects models (infant groups nested within papers) of variance-weighted effect sizes with the R (R Core Team, 2016) package metafor
-(Viechtbauer, 2010).
-To investigate how development impacts mispronunciation sensitivity, our core theoretical investigation, we introduce age (centered; in days but transformed into months for ease of reading by dividing by 30.44) as a moderator to our main model.
+The models reported are hierarchical random-effects models (infant groups nested within papers) of variance-weighted effect sizes with the R [@R] package metafor [@metafor].
+To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we introduce age (centered; continuous and measured in days but transformed into months for ease of reading by dividing by 30.44) as a moderator to our main model.
 For the subsequent investigations of experimental characteristics, we introduce each characteristic as a moderator (more detail below).
 
+[CHRISTINA: Let's both reread the full paper once it is ready and check that this is properly motivated and whether we do need to list them all.
+For now I think the last sentence is fine, but I would tend to prefer a reminder for the forgetful reader.]
+
 # Results
@@
 
-```{r FunnelPlotAsymm_correct, echo = FALSE}
+```{r FunnelPlotAsymm_correct}
 
@@
 
-```{r FunnelPlotAsymm_misp, echo=FALSE}
+```{r FunnelPlotAsymm_misp}
 
@@
 
-Figure 1 plots the funnel plots for object identification for both correct pronunciations and mispronunciations (code adapted from Sakaluk, 2016).
+Figure 1 shows the funnel plots for both correct pronunciations and mispronunciations (code adapted from Sakaluk, 2016).
 Funnel plot assymmetry was significant for both correct pronunciations (Kendall's $\tau$ = `r r2(rmac$tau)`, *p* `r psig(rmac$pval)`) and mispronunciations (Kendall's $\tau$ = `r r2(rmam$tau)`, *p* `r psig(rmam$pval)`).
-These results, in conjunction with the assymmetric funnel plot (Figure 1) indicate bias in the literature.
+These results, quantifying the assymmetry in the funnel plots (Figure 1), indicate bias in the literature.
 This is particularly evident for correct pronunciations, where larger effect sizes have greater variance (bottom right corner) and there are a smaller number of more precise effect sizes (i.e.
@@
 
-```{r FunnelPrep, echo = FALSE}
+[CHRISTINA: If we want to interpret here, how about the next bit.]
+
+The stronger publication bias for correct pronunciation might reflect the status of this condiction as a control.
+If infants were not looking to the target picture after hearing the correct label, the overall experiment design is called into questions.
+However, due to the small effect and sample sizes (which we will discuss in the following sections in more detail) one would expect the regular occurrence of null results even though as population infants would reliably show the expected object identification effect.
+
+We should also point out that funnel plot asymmetry can be caused by multiple factors beside publication bias.
+The funnel plot asymmetry may also reflect heterogeneity in the data, perhaps due to some studies investigating more subtle effects than other studies.
+[CHRISTINA: I have to add some bits here.]
+
+```{r FunnelPrep}
 ### Plots adapted from Sakaluk, 2016, see also Black & Bergmann, 2017
@@
 
-```{r FunnelCorrect, echo = FALSE}
+```{r FunnelCorrect}
 
 #Rename a bunch of things for ease
-dat_co = db_ET_correct
-#dat_co=db_ET_correct
-dat_co <-
-  dat_co %>% 
+dat_co = db_ET_correct %>% 
   rename(cite = short_cite,
          yi = g_calc,
-         vi = g_var_calc)
+         vi = g_var_calc) %>%
+  mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
+  dplyr::select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>%
+  arrange(desc(yi))
 
 #Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order
-
-dat_co <-
-  dat_co %>% 
-  select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>% 
-  mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
-  arrange(desc(yi))
 
@@
 
-```{r FunnelMisp, echo = FALSE}
+```{r FunnelMisp}
 
   #Rename a bunch of things for ease
-dat_mp = db_ET_MP  
-#dat_mp=db_ET_MP
-  dat_mp <-
-    dat_mp %>% 
+dat_mp = db_ET_MP %>%
     rename(cite = short_cite,
            yi = g_calc,
-           vi = g_var_calc)
-
-  #Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order
-
-  dat_mp <-
-    dat_mp %>% 
-    select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>% 
+           vi = g_var_calc) %>%
+    dplyr::select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>% 
     mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
     arrange(desc(yi))
+
+  #Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order
 
@@
 
-```{r FunnelCombo, echo = FALSE}
+```{r FunnelCombo}
 
@@
 
-```{r PcurveExport, echo = FALSE}
+```{r PcurveExport}
 
@@
 
-```{r ReadIn_pcurve_app,  echo = FALSE}
-
-curdir <- getwd()
+```{r ReadIn_pcurve_app,  echo = FALSE, error = FALSE}
 
@@
 # and the significance
-pcd_correct <- pcurve_app("p_curve_co.txt",paste0(curdir, "/p_curve_app"))
-
-pcd_misp <- pcurve_app("p_curve_mp.txt",paste0(curdir, "/p_curve_app"))
+pcd_correct <- pcurve_app("p_curve_co.txt", "p_curve_app")
+```
+
+```{r ReadIn_pcurve_app_2,  echo = FALSE, error = FALSE}
+pcd_misp <- pcurve_app("p_curve_mp.txt", "p_curve_app")
 
@@
 We next examined the p-curves for significant values from the correctly pronounced and mispronounced conditions.
-The p-curve based on `r pcd_correct$ksig` statistically significant values for correct pronunciations indicates that the data contain evidential value (Z = `r r2(pcd_correct$Zppr)`, p `r psig(pcd_correct$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05.
-The p-curve based on `r pcd_misp$ksig` statistically significant values for mispronunciations indicates that the data contain evidential value (Z = `r r2(pcd_misp$Zppr)`, p `r psig(pcd_misp$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05.
+The p-curve based on `r pcd_correct$ksig` statistically significant values for correct pronunciations indicates that the data contain evidential value (Z = `r r2(pcd_correct$Zppr)`, *p* `r psig(pcd_correct$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05.
+The p-curve based on `r pcd_misp$ksig` statistically significant values for mispronunciations indicates that the data contain evidential value (Z = `r r2(pcd_misp$Zppr)`, *p* `r psig(pcd_misp$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05.
+
+[CHRISTINA: CAn you add the stats for the non-sig results?]
 
@@
 As a result, our meta-analysis may systematically overestimate effect sizes and we therefore interpret all estimates with caution.
-The funnel plot asymmetry may also reflect heterogeneity in the data, perhaps due to some studies investigating more subtle effects than other studies.
 Yet, the p-curve analysis suggests that overall, the literature contains evidential value, reflecting a "real" effect.
@@
 
-We first calculated the meta-analytic effect for object identification in response to correctly pronounced words.
-The variance-weighted meta-analytic effect size Hedges’ *g* was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
-This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research) and that it is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object.
-Our analysis of funnel plot asymmetry, however, found evidence for publication.
+We first calculated the meta-analytic effect for object identification, i.e.
+looks to the target image in response to correctly pronounced words.
+The variance-weighted meta-analytic effect size Hedges' *g* was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
+This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research).
+That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object.
+Our analysis of funnel plot asymmetry, however, found evidence for publication bias, which might lead to an overestimated effect sizes as smaller, non-significant results might not be published.
 Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` suggests that this result is robust even when correcting for publication bias.
 
+[CHRISTINA: Can you explain what the CI lower bound means here? I don't follow.]
+
 ```{r MAMP}
@@
 We then calculated the meta-analytic effect for object identification in response to mispronounced words.
-In this case, the variance-weighted meta-analytic effect size Hedges’ g was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was also significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
+In this case, the variance-weighted meta-analytic effect size Hedges' *g* was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was also significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
 This is considered a small effect size (Cohen, 1988), but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object.
-We again note the publication bias (which was smaller in this condition), and the possibility that the effect size Hedges' *g* may be overestimated.
-But, as the p-curve indicated evidential value, we are confident in this result as well.
-
-Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, p `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, p `r psig(rma_MP$QEp)`).
+In other words, infants are able to resolve mispronunciations, a key skill in language processing We again note the publication bias (which was smaller in this condition), and the possibility that the effect size Hedges' *g* may be overestimated.
+But, as the p-curve indicated evidential value, we are confident in the overall patterns, namely that infants fixate the target even after hearing a mispronounced label.
+
+Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, *p* `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, *p* `r psig(rma_MP$QEp)`).
 This indicated that the sample contains unexplained variance leading to significant difference across our studies beyond what is to be expected based on random sampling error.
+We therefore continue with our moderator analysis.
 
@@
 The above two analyses considered the data from mispronounced and correctly pronounced words separately.
-To evaluate mispronunciation sensitivity, we then compared the effect size Hedges’ *g* for correct pronunciations with mispronunciations, merging the two datasets.
-The moderator test was significant, QM(`r r2(rma_MPeffect$m)`) = `r r2(rma_MPeffect$QM)`, p `r psig(rma_MPeffect$QMp)`.
-Hedges’ *g* for mispronunciation sensitivity was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that the two type of responses were significantly different from one another (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
+To evaluate mispronunciation sensitivity, we  compared the effect size Hedges' *g* for correct pronunciations with mispronunciations directly, merging the two datasets.
+The moderator test was significant, QM(`r r2(rma_MPeffect$m)`) = `r r2(rma_MPeffect$QM)`, *p* `r psig(rma_MPeffect$QMp)`.
+Hedges' *g* for mispronunciation sensitivity was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that the responses across conditions were significantly different (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
 This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations.
@@
 
-To evaluate the different predictions for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered, in days).
+To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered, in days).
 In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not.
-Age did not significantly modulate object identification in response to correctly pronounced (QM(`r r2(rma_correct_age$m)`) = `r r2(rma_correct_age$QM)`, p `r psig(rma_correct_age$QMp)`) or mispronounced words (QM(`r r2(rma_MP_age$m)`) = `r r2(rma_MP_age$QM)`, p `r psig(rma_MP_age$QMp)`).
-The lack of a significant modulation indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label.
+Age did not significantly modulate object identification in response to correctly pronounced (QM(`r r2(rma_correct_age$m)`) = `r r2(rma_correct_age$QM)`, *p* `r psig(rma_correct_age$QMp)`) or mispronounced words (QM(`r r2(rma_MP_age$m)`) = `r r2(rma_MP_age$QM)`, *p* `r psig(rma_MP_age$QMp)`).
+The lack of a significant modulation together with the small estimates indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label.
 This relationship is plotted in Figure 2.
+
+[CHRISTINA] CAN YOU ADD ESTIMATES AND THEIR CIS?? Ideally everywhere where you report a p-value
 
@@
 mispronounced words) in our whole dataset.
-The moderator test was significant (QMQM(`r r2(rma_MPeffect_age$m)`) = `r r2(rma_MPeffect_age$QM)`, p `r psig(rma_MPeffect_age$QMp)`).
-The interaction between age and mispronunciation sensitivity, however, was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`), suggesting that as infants age, their mispronunciation sensitivity remains the same.
+The moderator test was significant (QM(`r r2(rma_MPeffect_age$m)`) = `r r2(rma_MPeffect_age$QM)`, *p* `r psig(rma_MPeffect_age$QMp)`).
+This result is in line with the general observation that as infants mature they become better at language processing.
+The interaction between age and mispronunciation sensitivity, however, was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`), suggesting that as infants age, their mispronunciation sensitivity remains the same.
 
@@
 [KATIE] I DON'T KNOW HOW TO INTERPRET THESE RESULTS... THE FIXED EFFECTS MODEL ISN'T SIGNIFICANT FOR ANY OF THESE. IS THAT MEANINGFUL?
+[CHRISTINA] SO WE DON'T WANT TO INTERPRET THE FIXED EFFECTS MODEL AT ALL, IT IS NOT SUITABLE BECAUSE THERE IS VARIANCE BETWEEN EVERY RECORD (LANGUAGE ETC).
+I WOULD INTERPRET THE OVERALL CORRELATION AND THE CI, NOT THE P-VALUE (IN GENERAL).
+I ALSO WONDER WHETHER WE SHOULD MOVE THE SUBSET ANALYSES TO THE SUPPLEMENTARY MATERIALS AND JUST SAY OVERALL WE SEE NO RELATIONSHIPS AND CORRELATION COEFFICIENTS CONSISTENYL BELOW .1
+WE THEREFORE MUST CONCLUDE THAT WITHIN NARROW AGE GROUPS VOCABULARY DOES NOT INFLUENCE ANYTHING WE LOOK AT. WE CANNOT DO THIS ANALYSIS FPOR MP SENSITIVITY BECAUSE WE DON'T HAVE THE NECESSARY RAW DATA.
+(BUT I WONDER WHETHER WE COULD ENCODE THE REPORTED INTERACTION TERMS AND THE CORRELATION AND THEN DO SOMETHING WITH THAT?)
 
@@
 
+[cHRISTINA] I WOULD FOLLOW THE OUTLINE IN THE PREVIOUS PARAGRAPH HERE OR FLIP THE PARAGRAPH AROUND:
+1. ARE DIFFERENT MODERATORS USED AT DIFFERENT AGES? 
+TEST: sIMPLE CHI-SQUARED OF AGE GROUP VERSUS MODERATOR ASSIGNMENT (AGE GROUP DETERMINED BY LOOKING AT THE YOUNGEST AGE FOR X?)
+2. WHICH MODERATORS INFLUENCE MP SENSITIVITY
+TEST SIMPLE MA WITH MODERATOR TESTS
+
+OR 
+"FOR EACH POSSIBLE MODERATOR WHICH COULD INFLIENCE MP SENSITIVITY, WE FIRST TEST THIS POSSIBILITY AND THEN EVALUATE WHETHER THERE IS A SYSTEMATIC DIFFERENCE OF MANIPULATING THESE MODERATORS AS INFANTS MATURE, I.E.
+WHETHER OLDER INFANTS ARE TESTED ON A MORE DIFFICULT TASK "
+ALSO, AS FINAL FOLLOW-UP IT WOULD BE PERFECT TO JUST SUBSET ALL STUDIES WITH FAMILIAR DISTRACTORS, SAME NUMBER OF FEATURES, AND CHECK THAT OUR CONCLUSIONS HOLD UP REGARING MP SENSITIVITY
+
 ### Size of mispronunciation
+
+[CHRISTINA] I PREFER NUMBER OF FEATURES TO SIZE SOMEHOW
 
@@
 To assess whether the number of features changed modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced using 1-, 2-, and 3-feature changes.
-We did not include data for which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent.
-The analysis was therefore based on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` experimental conditions for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations.
+We did not include data for which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent (e.g., one mispronunciation included a 2-feature change whereas another only a 1-feature change).
+This analysis was therefore based on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` experimental conditions for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations.
 Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an equal impact on mispronunciation sensitivity, following the argument of graded sensitivity (White & Aslin, 2008; Mani & Plunkett 2011).
@@
 
-To understand the relationship between size of mispronunciation and mispronunciation sensitivity, we  evaluated the effect size Hedges’ *g* with number of features changed as a moderator.
-The moderator test was significant, QM(`r r2(rma_NFeatures$m)`) = `r r2(rma_NFeatures$QM)`, p `r psig(rma_NFeatures$QMp)`.
-Hedges’ *g* for number of features changed was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that as the number of features changed increased, the effect size Hedges’ g significantly decreased (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
+To understand the relationship between size of mispronunciation and mispronunciation sensitivity, we  evaluated the effect size Hedges' *g* with number of features changed as a moderator.
+The moderator test was significant, QM(`r r2(rma_NFeatures$m)`) = `r r2(rma_NFeatures$QM)`, *p* `r psig(rma_NFeatures$QMp)`.
+Hedges' *g* for number of features changed was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that as the number of features changed increased, the effect size Hedges' *g* significantly decreased (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
 We plot this relationship in Figure X.
@@
 
+  #[CHRISTINA] WHAT DO YOU THINK ABOUT VIOLIN PLOTS?
+
 ```
@@
 Although we did not have any specific predictions about the relationship between infant age and the impact of number of features changed on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
-When age was also included as a moderator, the moderator test was significant, QM(`r r2(rma_NFeatures$m)`) = `r r2(rma_NFeatures$QM)`, p `r psig(rma_NFeatures$QMp)`, but the interaction between age and number of features changed was not significant, $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
+When age was also included as a moderator, the moderator test was significant, QM(`r r2(rma_NFeatures$m)`) = `r r2(rma_NFeatures$QM)`, *p* `r psig(rma_NFeatures$QMp)`, but the interaction between age and number of features changed was not significant, $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
 This suggests that there is no relationship between infant age the impact of number of features changed on mispronunciation sensitivity.
@@
 [KATIE] DOES THE ABOVE PARAGRAPH NEED MORE MOTIVATION? SHOULD IT EVEN BE INCLUDED?
+[CHRISTINA] I THINK IT\S GREAT!
 
@@
 First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images that were paired with either a familiar or an unfamiliar distractor image.
-The moderator test was not significant QM(`r r2(rma_Distractor_MP$m)`) = `r r2(rma_Distractor_MP$QM)`, p `r psig(rma_Distractor_MP$QMp)`.
+The moderator test was not significant QM(`r r2(rma_Distractor_MP$m)`) = `r r2(rma_Distractor_MP$QM)`, *p* `r psig(rma_Distractor_MP$QMp)`.
 This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object.
@@
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_Distractor$m)`) = `r r2(rma_Distractor$QM)`, p `r psig(rma_Distractor$QMp)`, but the interaction between distractor familiarity and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
+The moderator test was significant, QM(`r r2(rma_Distractor$m)`) = `r r2(rma_Distractor$QM)`, *p* `r psig(rma_Distractor$QMp)`, but the interaction between distractor familiarity and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
 These results suggest that overall, infants' familiarity with the distractor object (familiar or unfamiliar) did not impact their mispronunciation sensitivity.
@@
 
+  #[CHRISTINA] AGAIN, WHAT DO YOU THINK OF VIOLINS?
+
 ```
@@
 We next examined whether age modulates object recognition or mispronunciation sensitivity when the distractor image is familiar or unfamiliar.
-For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_DistractorAge$m)`) = `r r2(rma_DistractorAge$QM)`, p `r psig(rma_DistractorAge$QMp)`.
+For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_DistractorAge$m)`) = `r r2(rma_DistractorAge$QM)`, *p* `r psig(rma_DistractorAge$QMp)`.
+[CHRISTINA] I WORRY A LOT AT THESE POINTS THAT THIS IS THE WHOLE P>.05 = NULL IS TRUE FALLACY.
+WE CAN NEVER HAVE EVIDENCE FOR THE NULL HYPOTHESIS.
+SO BETTER ITNERPRET ESTIMATES AND CIS.
+
 This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object, regardless of their age.
@@
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_DistractorAgeMS$m)`) = `r r2(rma_DistractorAgeMS$QM)`, p `r psig(rma_DistractorAgeMS$QMp)`.
-Although the three-way-interaction between condition, distractor familiarity, and age was not significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`), here the interaction between condition and distractor familiarity was significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`).
+The moderator test was significant, QM(`r r2(rma_DistractorAgeMS$m)`) = `r r2(rma_DistractorAgeMS$QM)`, *p* `r psig(rma_DistractorAgeMS$QMp)`.
+Although the three-way-interaction between condition, distractor familiarity, and age was not significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`), here the interaction between condition and distractor familiarity was significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], *p* `r psig(sum_eff2$pval)`).
 
@@
 UNDERSTANDING THIS WILL HELP ME FORMULATE THE CONCLUSION SENTENCE AND MOTIVATE THE NEXT SET OF ANALYSES.
+
+[CHRISTINA] I WOULD NOT OVERINTERPRET IT, THE ESTIMATE DID NOT DRAMATICALLY CHANGE, AND IT IS BARELY SIGNIFICANT. DOES THAT HELP?
 
@@
 
+[CHRISTINA] CAN YOU TURN THE NUMBERS INTO R CODE HERE? aLSO, NOT SURE WE NEED A T-TEST TO CONFIRM THE OBVIOUS.
+
 [KATIE] SO, IS IT OKAY TO DO THE AGE SUBSET ANALYSIS AFTER THIS?
 SOMETHING LIKE "TO ENSURE THAT THE LACK OF A DIFFERENCE WASN'T DUE TO THE DIFFERENCE IN AGES OF INFANTS TESTED WITH DIFFERENT TYPES OF DISTRACTORS, WE ANALYZED A SUBSET OF PAPERS THAT TESTED AGES WHERE BOTH FAMILIAR AND UNFAMILIAR DISTRACTORS WERE USED." IN THE SUBSET ANALYSIS, FOR MISP SENSITIVITY, THERE IS A SIGNIFICANT INTERACTION BETWEEN DISTRACTOR FAMILIARITY AND CONDITION.
+
+[CHRISTINA] YES!!!!!!
 
@@
 
+[CHRISTINA] SEEMS OK BUT I AM CONFUSED WHY OVERLAP IS THE BASELINE AND WHY YOU BRING IN NOVEL. I THINK YOU NEED TO SPELL THIS OUT MORE.
+
 ```{r DistractorOverlap}
@@
 
-Regarding object identification in response to mispronunciations, when distractor overlap was included as a moderator, the moderator test was not significant QM(`r r2(rma_DistractorOverlap$m)`) = `r r2(rma_DistractorOverlap$QM)`, p `r psig(rma_DistractorOverlap$QMp)`.
+Regarding object identification in response to mispronunciations, when distractor overlap was included as a moderator, the moderator test was not significant QM(`r r2(rma_DistractorOverlap$m)`) = `r r2(rma_DistractorOverlap$QM)`, *p* `r psig(rma_DistractorOverlap$QMp)`.
+[CHRISTINA] AGAIN DO NOT RELY ON P-VALUES BUT ON ESTIMATES AND CIS
 This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with a distractor image that contained overlap on the onset phoneme or no overlap with the target word, or was an unfamiliar object.
@@
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_DistractorOverlapMS$m)`) = `r r2(rma_DistractorOverlapMS$QM)`, p `r psig(rma_DistractorOverlapMS$QMp)`.
-The interaction between condition and target-distractor pairs with no overlap was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`), suggesting that mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap.
-The interaction between condition and target-distractor pairs with an unfamiliar distractor was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`), suggesting that mispronunciation sensitivity was smaller when the distractor image shared the same onset phoneme as the target image compared to when the distractor image was an unfamiliar object.
+The moderator test was significant, QM(`r r2(rma_DistractorOverlapMS$m)`) = `r r2(rma_DistractorOverlapMS$QM)`, *p* `r psig(rma_DistractorOverlapMS$QMp)`.
+The interaction between condition and target-distractor pairs with no overlap was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`), suggesting that mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap.
+The interaction between condition and target-distractor pairs with an unfamiliar distractor was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], *p* `r psig(sum_eff2$pval)`), suggesting that mispronunciation sensitivity was smaller when the distractor image shared the same onset phoneme as the target image compared to when the distractor image was an unfamiliar object.
 This can be seen in Figure X.
+
+[christina] I THINK THESE SHOULD BE TWO SEPARATE ANALYSES... NOVEL IS CONCEPTUALLY DIFFERENT.
 
@@
 Although we did not have any specific predictions about the relationship between infant age and the impact of distractor overlap on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
-First, for object recognition in response to mispronunciations, when age in addition to distractor overlap was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_DistractorOverlap_age$m)`) = `r r2(rma_DistractorOverlap_age$QM)`, p `r psig(rma_DistractorOverlap_age$QMp)`, suggesting that upon hearing a mispronunciation, infants looks to the target image were similar for the three types of overlap, regardless of infant age.
+First, for object recognition in response to mispronunciations, when age in addition to distractor overlap was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_DistractorOverlap_age$m)`) = `r r2(rma_DistractorOverlap_age$QM)`, *p* `r psig(rma_DistractorOverlap_age$QMp)`, suggesting that upon hearing a mispronunciation, infants looks to the target image were similar for the three types of overlap, regardless of infant age.
 We next assessed whether the relationship between distractor overlap and mispronunciation sensitivity was modulated by age.
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_DistractorOverlap_age_MS$m)`) = `r r2(rma_DistractorOverlap_age_MS$QM)`, p `r psig(rma_DistractorOverlap_age_MS$QMp)`.
-The interaction between age, condition, and target-distractor pairs with no overlap was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`).
+The moderator test was significant, QM(`r r2(rma_DistractorOverlap_age_MS$m)`) = `r r2(rma_DistractorOverlap_age_MS$QM)`, *p* `r psig(rma_DistractorOverlap_age_MS$QMp)`.
+The interaction between age, condition, and target-distractor pairs with no overlap was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`).
 As can be seen in Figure X, the difference between correct pronunciations and mispronunciations (mispronunciation sensitivity) stays steady across infant ages for both target words paired with distractors containing onset overlap with the target word as well as distractors containing no overlap.
 As infants aged, however, overall recognition (regardless of condition) increased for target-distractor pairs containing onset overlap, whereas for overall recognition decreased for target-distractor pairs containing no overlap.
-The interaction between age, condition, and target-distractor pairs with an unfamiliar distractor was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`).
+The interaction between age, condition, and target-distractor pairs with an unfamiliar distractor was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], *p* `r psig(sum_eff2$pval)`).
 As can also be seen in Figure X, mispronunciation sensitivity for target words paired with unfamiliar distractors decreased with age, while it remained steady across a similar range of ages for target words paired with distractors containing onset overlap with the target word.
@@
 
-Regarding object identification in response to mispronunciations, when mispronunciation location was included as a moderator, the moderator test was not significant QM(`r r2(rma_Location_MP$m)`) = `r r2(rma_Location_MP$QM)`, p `r psig(rma_Location_MP$QMp)`.
+Regarding object identification in response to mispronunciations, when mispronunciation location was included as a moderator, the moderator test was not significant QM(`r r2(rma_Location_MP$m)`) = `r r2(rma_Location_MP$QM)`, *p* `r psig(rma_Location_MP$QMp)`.
 This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was located on the onset or  medial phonemes.
@@
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_LocationCondition$m)`) = `r r2(rma_LocationCondition$QM)`, p `r psig(rma_LocationCondition$QMp)`, but the interaction between mispronunciation location and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
+The moderator test was significant, QM(`r r2(rma_LocationCondition$m)`) = `r r2(rma_LocationCondition$QM)`, *p* `r psig(rma_LocationCondition$QMp)`, but the interaction between mispronunciation location and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
 These results suggest that overall, the location of the mispronunciation (onset, medial) did not impact mispronunciation sensitivity.
@@
 Although we did not have any specific predictions about the relationship between infant age and the impact of mispronuncition location on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
-First, for object recognition in response to mispronunciations, when age in addition to mispronunciation location was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_Location_MP_age$m)`) = `r r2(rma_Location_MP_age$QM)`, p `r psig(rma_Location_MP_age$QMp)`, suggesting that upon hearing a mispronunciation, infants looks to the target image were similar for both onset and medial mispronunciations, regardless of infant age.
+First, for object recognition in response to mispronunciations, when age in addition to mispronunciation location was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_Location_MP_age$m)`) = `r r2(rma_Location_MP_age$QM)`, *p* `r psig(rma_Location_MP_age$QMp)`, suggesting that upon hearing a mispronunciation, infants looks to the target image were similar for both onset and medial mispronunciations, regardless of infant age.
 We next assessed whether the relationship between mispronunciation location and mispronunciation sensitivity was modulated by age.
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_LocationCondition_age$m)`) = `r r2(rma_LocationCondition_age$QM)`, p `r psig(rma_LocationCondition_age$QMp)`, but the interaction between mispronunciation location, age, and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
+The moderator test was significant, QM(`r r2(rma_LocationCondition_age$m)`) = `r r2(rma_LocationCondition_age$QM)`, *p* `r psig(rma_LocationCondition_age$QMp)`, but the interaction between mispronunciation location, age, and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
 These results provide further evidence that location of the mispronunciation (onset, medial) did not impact mispronunciation sensitivity.
@@
 We first analyzed experimental conditions where mispronunciation type was either a consonant or vowel.
-Regarding object identification in response to mispronunciations, when mispronunciation type was included as a moderator, the moderator test was not significant QM(`r r2(rma_TypeFeaturesMP$m)`) = `r r2(rma_TypeFeaturesMP$QM)`, p `r psig(rma_TypeFeaturesMP$QMp)`.
+Regarding object identification in response to mispronunciations, when mispronunciation type was included as a moderator, the moderator test was not significant QM(`r r2(rma_TypeFeaturesMP$m)`) = `r r2(rma_TypeFeaturesMP$QM)`, *p* `r psig(rma_TypeFeaturesMP$QMp)`.
 This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was a consonant or a vowel.
@@
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, p `r psig(rma_TypeFeaturesMP_Condition$QMp)`, but the interaction between mispronunciation type and condition was not significant $\beta$ = `r r2(sum_eff1$estimate)`, (SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`).
+The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, *p* `r psig(rma_TypeFeaturesMP_Condition$QMp)`, but the interaction between mispronunciation type and condition was not significant $\beta$ = `r r2(sum_eff1$estimate)`, (SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`).
 These results suggest that overall, the type of  mispronunciation (consonant vs.
@@
 We next examined whether age modulates object recognition or mispronunciation sensitivity when the mispronunciation is a consonant or vowel.
-For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_TypeFeaturesMPage$m)`) = `r r2(rma_TypeFeaturesMPage$QM)`, p `r psig(rma_TypeFeaturesMPage$QMp)`.
+For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_TypeFeaturesMPage$m)`) = `r r2(rma_TypeFeaturesMPage$QM)`, *p* `r psig(rma_TypeFeaturesMPage$QMp)`.
 This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was on a consonant or vowel phoneme, regardless of their age.
@@
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, p `r psig(rma_TypeFeaturesMP_Condition$QMp)`.
-The interaction between mispronunciation type, condition, and age was significant ($\beta$ = `r r2(sum_eff$estimate)`, SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
+The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, *p* `r psig(rma_TypeFeaturesMP_Condition$QMp)`.
+The interaction between mispronunciation type, condition, and age was significant ($\beta$ = `r r2(sum_eff$estimate)`, SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
 As can be seen in Figure X, as infants age, mispronunciation sensitivity grows larger for vowel mispronunciations but becomes smaller for consonant mispronunciations.
@@
 bilinguals; *n* = `r with(lang_family, count[native_lang == "Catalan-Spanish"])`), and Swiss French (*n* = `r with(lang_family, count[native_lang == "Swiss French"])`) were classified into the Romance language family (*n* = `r with(family, count[lang_family == "Romance"])`).
-For object recognition in response to a mispronunciation, including language family as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_TypeFeaturesMPfam$m)`) = `r r2(rma_TypeFeaturesMPfam$QM)`, p `r psig(rma_TypeFeaturesMPfam$QMp)`.
+For object recognition in response to a mispronunciation, including language family as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_TypeFeaturesMPfam$m)`) = `r r2(rma_TypeFeaturesMPfam$QM)`, *p* `r psig(rma_TypeFeaturesMPfam$QMp)`.
 This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was on a consonant or vowel phoneme, regardless of the language family of their native language.
@@
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family as additional moderators.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMPC$m)`) = `r r2(rma_TypeFeaturesMPC$QM)`, p `r psig(rma_TypeFeaturesMPC$QMp)`.
-The interaction between condition and language family was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`), suggesting XXXXXXXXXXXXXX.
-The interaction between mispronunciation type, condition, and language family was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`).
+The moderator test was significant, QM(`r r2(rma_TypeFeaturesMPC$m)`) = `r r2(rma_TypeFeaturesMPC$QM)`, *p* `r psig(rma_TypeFeaturesMPC$QMp)`.
+The interaction between condition and language family was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`), suggesting XXXXXXXXXXXXXX.
+The interaction between mispronunciation type, condition, and language family was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], *p* `r psig(sum_eff2$pval)`).
 As can be seen in Figure X, mispronunciation sensitivity for consonants was similar for Germanic and Romance languages.
@@
 Finally, we examined the relationship between language family and infant age and mispronunciation sensitivity to consonants and vowels.
-For object recognition in response to a mispronunciation, including language family and infant age as a moderator resulted in a moderator test that was significant, QM(`r r2(rma_TypeFeaturesMPfam$m)`) = `r r2(rma_TypeFeaturesMPfam$QM)`, p `r psig(rma_TypeFeaturesMPfam$QMp)`.
-The interaction between language family, age, and type of mispronunciation (consonant or vowel) was significant, ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`).
+For object recognition in response to a mispronunciation, including language family and infant age as a moderator resulted in a moderator test that was significant, QM(`r r2(rma_TypeFeaturesMPfam$m)`) = `r r2(rma_TypeFeaturesMPfam$QM)`, *p* `r psig(rma_TypeFeaturesMPfam$QMp)`.
+The interaction between language family, age, and type of mispronunciation (consonant or vowel) was significant, ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`).
 As can be seen in Figure X, for infants learning Germanic languages, increasing age was related to increasing mispronunciation sensitivity for vowel mispronunciations, but decreasing sensitivity for consonant mispronunciations.
@@
 Although we had no predictions regarding mispronunciation sensitivity to tone mispronunciations, we included an exploratory analysis to examine whether responses to tone mispronunciations were different from that of consonants or vowels.
-Regarding object identification in response to mispronunciations, when mispronunciation type was included as a moderator, the moderator test was not significant QM(`r r2(rma_TypeFeaturesMPT$m)`) = `r r2(rma_TypeFeaturesMPT$QM)`, p `r psig(rma_TypeFeaturesMPT$QMp)`.
+Regarding object identification in response to mispronunciations, when mispronunciation type was included as a moderator, the moderator test was not significant QM(`r r2(rma_TypeFeaturesMPT$m)`) = `r r2(rma_TypeFeaturesMPT$QM)`, *p* `r psig(rma_TypeFeaturesMPT$QMp)`.
 This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for tone mispronunciations in comparison with both consonants and vowels.
@@
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_ConditionT$m)`) = `r r2(rma_TypeFeaturesMP_ConditionT$QM)`, p `r psig(rma_TypeFeaturesMP_ConditionT$QMp)`.
-The interaction between condition and consonant mispronunciations was not significant $\beta$ = `r r2(sum_eff2c$estimate)`, (SE = `r r2(sum_eff2c$se)`, 95% CI [`r r2(sum_eff2c$ci.lb)`, `r r2(sum_eff2c$ci.ub)`], p `r psig(sum_eff2c$pval)`), suggesting that there was no difference in looks to the target in response to consonant and tone mispronunciations.
-The interaction between condition and vowel mispronunciations was also not significant $\beta$ = `r r2(sum_eff2v$estimate)`, (SE = `r r2(sum_eff2v$se)`, 95% CI [`r r2(sum_eff2v$ci.lb)`, `r r2(sum_eff2v$ci.ub)`], p `r psig(sum_eff2v$pval)`), suggesting that there was no difference in looks to the target in response to vowel and tone mispronunciations.
+The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_ConditionT$m)`) = `r r2(rma_TypeFeaturesMP_ConditionT$QM)`, *p* `r psig(rma_TypeFeaturesMP_ConditionT$QMp)`.
+The interaction between condition and consonant mispronunciations was not significant $\beta$ = `r r2(sum_eff2c$estimate)`, (SE = `r r2(sum_eff2c$se)`, 95% CI [`r r2(sum_eff2c$ci.lb)`, `r r2(sum_eff2c$ci.ub)`], *p* `r psig(sum_eff2c$pval)`), suggesting that there was no difference in looks to the target in response to consonant and tone mispronunciations.
+The interaction between condition and vowel mispronunciations was also not significant $\beta$ = `r r2(sum_eff2v$estimate)`, (SE = `r r2(sum_eff2v$se)`, 95% CI [`r r2(sum_eff2v$ci.lb)`, `r r2(sum_eff2v$ci.ub)`], *p* `r psig(sum_eff2v$pval)`), suggesting that there was no difference in looks to the target in response to vowel and tone mispronunciations.
 
@@
 We further included an exploratory analysis of the relationship between infant age and the impact of tone mispronunciations in comparison to consonant and vowel mispronunciations.
-First, for object recognition in response to mispronunciations, when age in addition to mispronunciation location was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_TypeFeaturesMPage$m)`) = `r r2(rma_TypeFeaturesMPage$QM)`, p `r psig(rma_TypeFeaturesMPage$QMp)`.
+First, for object recognition in response to mispronunciations, when age in addition to mispronunciation location was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_TypeFeaturesMPage$m)`) = `r r2(rma_TypeFeaturesMPage$QM)`, *p* `r psig(rma_TypeFeaturesMPage$QMp)`.
 This suggests that upon hearing a mispronunciation, infants looks to the target image were not different between tone and vowel or tone and consonant mispronunciations, regardless of their age.
@@
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, p `r psig(rma_TypeFeaturesMP_Condition$QMp)`, but the interactions between condition, age, and both consonant mispronciations ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`) and vowel mispronunciations ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`) were not significant.
+The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, *p* `r psig(rma_TypeFeaturesMP_Condition$QMp)`, but the interactions between condition, age, and both consonant mispronciations ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`) and vowel mispronunciations ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], *p* `r psig(sum_eff2$pval)`) were not significant.
 Infants' sensitivity to tone mispronunciations compared to consonant or vowel mispronunciations did not differ with age.
@@
 Discussing the Moderator Analyses
-Maybe put them together into the ones that worked out as we predicted and those that didn’t?
-So, here is evidence that supports existing arguments, that doesn’t need to be a huge chunk.
-But then more space devoted to moderator analyses that didn’t work out according to predictions.
+Maybe put them together into the ones that worked out as we predicted and those that didn't?
+So, here is evidence that supports existing arguments, that doesn't need to be a huge chunk.
+But then more space devoted to moderator analyses that didn't work out according to predictions.
 
@@
 [KATIE] COME BACK TO THIS.
+
+# References

### 2018-10-23 Paper_Analyses.Rmd
convert to papaja, temporary references fix

@@
 ---
-title: "MP MetaAnalysis"
-author: "Christina Bergmann and Katie Von Holzen"
-date: '`r format(Sys.Date(), "%d %B, %Y")`'
-output: 
-  pdf_document:
-    toc: true
-
-bibliography: references.bib
+title             : "The development of infants' responses to mispronunciations - A Meta-Analysis"
+shorttitle        : "Mispronunciation Meta-Analysis"
+
+author: 
+  - name          : "Katie Von Holzen"
+    affiliation   : "1,2"
+    corresponding : yes    # Define only one corresponding author
+    address       : "0221A LeFrak Hall, University of Maryland, College Park, MD 20742"
+    email         : "katie.m.vonholzen@gmail.com"
+  - name          : "Christina Bergmann"
+    affiliation   : "3,4"
+
+affiliation:
+  - id            : "1"
+    institution   : "Language Development Laboratory, University of Maryland, USA"
+  - id            : "2"
+    institution   : "Laboratoire Psychologie de la Perception, Université Paris Descartes"
+  - id            : "3"
+    institution   : "Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands"
+  - id            : "4"
+    institution   : "LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University"
+
+abstract: |
+  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+
+  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
+
+  One sentence clearly stating the **general problem** being addressed by  this particular study.
+
+  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
+
+  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
+
+  One or two sentences to put the results into a more **general context**.
+
+  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
+
+keywords          : "keywords"
+wordcount         : "X"
+
+floatsintext      : no
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : yes
+mask              : no
+draft             : no
+citeproc          : no
+
+documentclass     : "apa6"
+classoption       : "man"
+output            : papaja::apa6_pdf
 ---
+
 ```{r Setup, echo = FALSE, warning=FALSE, warning = FALSE, error = FALSE, message = FALSE}
@@
 
+# bibliography      : ["MISP_MA_BIB.bib"]
+
+# [KATIE] BIBLIOGRAPHY CURRENTLY REMOVED, AS IT IS CAUSING ERRORS WITH PAPAJA
+# THIS IS PARTIALLY DUE TO THE WAY I CREATE IT USING MENDELEY. 
+# TOO LAZY FOR THE MOMENT TO COMPLETELY OVERHAUL THIS
+
+# BUT, OTHER PROBLEMS INCLUDE HAVING PAPAJA INSTALLED IN THE USER AND NOT SYSTEM LIBRARY
+# https://github.com/crsh/papaja/issues/162
+# devtools::with_libpaths(new = "/usr/lib/R/library/", install_github('crsh/papaja'))
+
+# AND THE NEED TO SET citeproc: no
+# https://github.com/crsh/papaja/issues/96
+
+# STILL NEED TO FIGURE OUT WHAT ACTUAL PROBLEM IS, THIS IS CURRENTLY JUST A WORKAROUND
+
 ### Load libraries
-
+library(papaja)
 library(metafor)
@@
 
-# set Table count at 0
-t_num <- 0
-
-# set Figure count at 0
-f_num <- 0
-
 r2 <- function(x){ round(x, 3)}
-
-#[CHRISTINA: I prefer exact p-values with more granularity]
 
@@
 ))
-
-# [CHRISTINA This should not be necessary]
-#cur_dir <- getwd()
 
@@
 
+# Introduction
+
+Acquiring a first language means that young learners are solving a host of tasks in a short amount of time.
+As infants develop into toddlers during their second and third years they learn new words in earnest while simultaneously refining their knowledge about the sounds that make up these words.
+Before children can correctly pronounce a word, they already show evidence of sensitivity to slight variations in the phonological form of that word.
+This mispronunciation sensitivity reflects the specificity with which infants represent the phonological information of familiar words and are sensitive to changes that might signal a change in word meaning.
+As infants continue to develop into expert language users, their language processing matures and becomes more efficient.
+In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonetic details that differentiate words in their native language (e.g.
+cat-hat).
+In this paper, we aggregate and analyze the almost 20 years of literature investigating mispronunciation sensitivity in infants in an attempt to uncover its characteristics and the trajectory of its development.
+
+  At the turn of the millenia, infant language acquisition researchers had established that during their first years of life, infants are sensitive to changes in the phonetic detail of newly segmented words (Jusczyk & Aslin, 1995) and learned minimal pairs (Stager & Werker, 1997).
+Furthermore, when presented with familiar image pairs, children fixate on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg, & McRoberts, 1998).
+Swingley and Aslin (2000) were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English were presented with pairs of images (e.g.
+baby, dog) and their eye movements to each image were coded offline.
+On "correct" trials, children heard the correct label for one of the images (e.g.
+baby).
+On "mispronounced" trials, children heard a mispronounced label of one of the images (e.g.
+vaby).
+Mean proportion of fixation to the target image (here: a baby) was calculated for both correct and mispronounced trials by dividing the target looking time by the sum of total looking time to both target and a distractor (proportion of target looking or PTL).
+Mean fixations in correct trials were significantly greater than in mispronounced trials, although looks to the target were significantly greater than chance in both types of trials.
+We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance as *recognition*.
+Swingley and Aslin (2000) concluded that already before the second birthday, children represent words with sufficient detail to be sensitive to mispronunciations.
+
+  The study of Swingley and Aslin (2000) as well as subsequent studies examining mispronunciation sensitivity address two complementary concepts in early phonological development: *phonological constancy* and *phonological distinctiveness*.
+Phonological constancy is the ability to accept phonological variation across different instances of a word, as long as the variation does not compromise the overall identity of the word.
+For example, different speakers - particularly across genders and accents - produce the same word with notable acoustic variation, although the word remains the same.
+In contrast, phonological distinctiveness describes the ability to differentiate between different words that happen to be phonologically similar, such as bad/bed or cat/hat.
+To successfully recognize words, infants must therefore simultaneously use both phonological constancy and distinctiveness to determine where phonological variation is appropriate and where it changes a word's meaning.
+
+  In the current study, we focus on infants' developing ability to correctly apply the principles of phonological distinctiveness and constancy by using a meta-analytic approach to investigate mispronunciation sensitivity.
+Considering that infants are sensitive to mispronunciations and that, in general, their processing matures with development, we examine the shape of mispronunciation sensitivity over the course of the second and third year.
+There are three distinct possibilities how mispronunciation sensitivity might change as infants become native speakers, which are all respectively predicted by theoretical accounts and supported by single studies.
+By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants.
+Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.
+
+  Young infants may begin cautiously in their approach to word recognition, rejecting any phonological variation in familiar words and only later learning to accept appropriate variability.
+According to the Perceptual Attunement account, this describes a shift away from specific native phonetic patterns to a more mature understanding of the abstract phonological structure of words (Best 1994, 1995).
+This shift is predicted to coincide with the vocabulary spurt around 18 months, and is therefore related to vocabulary growth.
+In this case, we would expect the size of mispronunciation sensitivity to be larger at younger ages and *decrease* as the child matures and learn more words, although children continue to detect mispronunciations.
+Indeed, young infants are less likely than older infants to demonstrate recognition of familiar words (Best, Tyler, Gooding, Orlando, & Quann, 2009; Mulak, Best, & Tyler, 2013) or learn new words (Schmale, Hollich, & Seidl, 2011) from accented speakers.
+
+  According to a different theoretical framework, young infants may instead begin with phonologically broad representations for familiar words and only refine their representations as language experience accumulates.
+PRIMIR (Processing Rich Information from Multidimensional Interactive Representations; Curtin & Werker, 2007; Werker & Curtin, 2005; Curtin, Byers-Heinlein, & Werker, 2011) describes the development of phonemic categories emerging as the number of word form-meaning linkages increases.
+Vocabulary growth, therefore, promotes more detailed phonological representations in familiar words.
+Following this account, we predict an *increase* in mispronunciation sensitivity as infants mature and add more words to their growing lexicon.
+
+  Finally, sensitivity to mispronunciation may not be modulated by development at all.
+Infants' overall language processing becomes more efficient, but their sensitivity to mispronunciations may not change.
+Across infancy and toddlerhood, mispronunciations would thus be detected and lead to less looks at a target than correct pronunciations, but the size of this effect would not change, nor be related to vocabulary size.
+This pattern is not predicted by any mainstream theory of language acquisition, but for completeness we mention it here.
+
+  Research following the seminal study by Swingley and Aslin (2000) has extended mispronunciation sensitivity to infants as young as 12 months (Mani & Plunkett, 2010), indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations.
+Regarding the change in mispronunciation sensitivity over development, however, only a handful of studies have compared more than one age group on the same mispronunciation task (see Table X), making the current meta-analysis very informative.
+One study has found evidence for infants to become *less* sensitive to mispronunciations as children develop.
+Mani and Plunkett (2011) presented 18- and 24-month-olds with mispronunciations varying in the number of features changed (see below for a discussion of the role of features).
+18-month-olds were sensitive to mispronunciations, regardless of the number of features changed.
+24-month-olds, in contrast, fixated the target image equally for both correct and 1-feature mispronounced trials, although they were sensitive to larger mispronunciations.
+In other words, for 1-feature mispronunciations at least, sensitivity decreased from 18 to 24 months, providing support to the prediction that mispronunciation sensitivity may decrease with development.
+
+  In contrast, other studies have found evidence for *greater* mispronunciation sensitivity as children develop.
+More precisely, the difference in target looking for correct and mispronounced trials is smaller in younger infants and grows as infants develop.
+Mani and Plunkett (2007) tested 15-, 18-, and 24-month-olds learning British English; although all three groups were sensitive to mispronunciations, 15-month-olds showed a less robust sensitivity.
+An increase in sensitivity to mispronunciations has also been found from 20 to 24 months (van der Feest & Fikkert, 2015) and 15 to 18 months (Altvater Mackensen et al., 2013) in Dutch infants, as well as German infants from 22 to 25 months (Altvater-Mackensen, 2010).
+Furthermore, van der Feest and Fikkert (2015) found that sensitivity to specific kinds of mispronunciations develop at different ages depending on language infants are learning.
+In other words, the native language constraints which *kinds* of mispronunciations infants are sensitive to first, and that as infants develop, they become sensitive to other mispronunciations.
+These studies award support to the prediction that mispronunciation sensitivity improves with development.
+
+Finally, some studies have found no difference in mispronunciation sensitivity at different ages.
+Swingley and Aslin (2000) tested infants over a wide age range of 5 months (18 to 23 months).
+They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation effect) did not.
+This suggests that as children develop, they are more likely to look at the target in the presence of a mispronounced label and that age is not related to mispronunciation sensitivity.
+A similar response pattern has been found for British English learning infants aged between 18 and 24 months (Bailey & Plunkett, 2002) as well as younger French-learning infants at 12 and 17 months (Zesiger, Lozeron, Levy, & Frauenfelder, 2012).
+These studies award support to the prediction that mispronunciation sensitivity does not change with development.
+
+  Why would mispronunciation sensitivity change as infants develop, and would it increase or decrease?
+The main hypothesis is related to vocabulary growth.
+Both the Perceptual Attunement (Best, 1994; 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005; Curtin, Byers-Heinlein, & Werker, 2011) accounts situate a change in mispronunciation sensitivity occurring along with an increase in vocabulary size, particularly with the vocabulary spurt at about 18 months.
+Knowing more words helps infants shift their focus to the relevant phonetic dimensions needed for word recognition.
+On the one hand, a smaller lexicon does not require full specification to differentiate between words; as more phonologically similar words are learned, so does the need to have fully detailed representations for those words (Charles-Luce & Luce, 1995).
+On the other hand, a growing vocabulary is also related to more experience or familiarity with words, which may sharpen the detail of their representation (Barton, 1980).
+
+  Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship (Swingley & Aslin 2000; 2002; Bailey & Plunkett, 2002; Zesiger, Lozeron, Levy, & Frauenfelder, 2012; Swingley, 2009; Ballem & Plunkett, 2005; Mani & Plunkett, 2007; Mani, Coleman, & Plunkett, 2008).
+One notable exception comes from Mani and Plunkett (2010: keps and tups).
+Here, 12-month-old infants were divided into a low vocabulary and high vocabulary group based group median vocabulary size.
+High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations.
+Taken together, although receiving considerable support from theories of phono-lexical processing in language acquisition, there is very little evidence for a role of vocabulary size in mispronunciation sensitivity.
+In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to further disentangle the disconnect between theory and experimental results.
+
+  Next to this core theoretically relevant investigation of the shape of development of infants' mispronunciation sensitivity, we take the opportunity of a systematic aggregation of data to address open questions regarding differences in experiment design and whether changes in procedure and stimuli tap into significantly different aspects of infants' ability to detect mispronunciations.
+
+  In designing their mispronunciation stimuli, Swingley and Aslin (2000) chose consonant mispronunciations that were likely to confuse adults (Miller & Nicely, 1955).
+Subsequent research has settled on systematically modulating phonemic features to achieve mispronunciations of familiar words.
+By utilizing mispronunciations consisting of phonemic changes, these experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level (i.e.
+1-feature, 2-features, 3-features, etc.).
+The importance of controlling for the degree of phonological mismatch, as measured by number of features changed, is further highlighted by studies that find graded sensitivity to both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes.
+
+  Although most research examining sensitivity to mispronunciations follows a similar design, there are some notable differences.
+For example, Swingley and Aslin (2000) presented infants with pairs of familiar images, one serving as the labeled target and one as the unlabeled distractor.
+In contrast, White and Morgan (2008; see also Mani & Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects.
+By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied (Halberda, 2003; Markman, Wasow, & Hansen, 2003).
+Infants ages 24 and 30 months associate a novel label with an unfamiliar object, although only 30-month-olds retained this label-object pairing (Bion, Borovsky, and Fernald, 2013).
+In contrast, 18-month-olds did not learn to associate a novel label with an unfamiliar object, providing evidence that this ability is developing from 18 to 30 months.
+We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by whether the distractor used is familiar or unfamiliar.
+Although mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared, the baseline preference for familiar compared to novel stimuli is also thought to change as infants develop (Hunter & Ames, 1988).
+Furthermore, young children have been found to look longer at objects for which they know the name, compared to objects of an unknown name (Schafer & Plukett, 1998).
+In other words, in absentia of a label, infants may be more or less likely to fixate on an unfamiliar object.
+To account for inherent preferences to the target or distractor image, mispronunciation experiments typically compare the increase in fixations to the target image from a silent baseline to post-labeling or present the same yoked pairs of target and distractor images in in both a correct and mispronounced labelling context.
+Considering this evidence, we may expect that in older, but not younger, children, the presence of an unfamiliar distractor may lead to greater mispronunciation sensitivity than in the presence of a familiar distractor.
+
+  Furthermore, when presenting infants with a familiar distractor image, some studies control the phonological overlap between the labels for the target and distractor.
+For example, when examining sensitivity to a mispronunciation of the target word "dog", the vowel mispronunciation "dag" would be paired with a distractor image that shares onset overlap, such as "duck".
+This ensures that infants can not use the onset of the word to differentiate between the target and distractor images (Fernald, Swingley, & Pinto, 2001).
+Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.
+The influence of distractor overlap also depends on the position of the mispronunciation in the word, which can be at word onset, medial, or final positions.
+Models of spoken word processing place more or less importance on the position of a phoneme in a word.
+The COHORT model (Marslen-Wilson & Zwitserlood, 1989) describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.
+In contrast, the TRACE model (McClelland & Elman, 1986) describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.
+
+  TRACE has also been used to model infants' sensitivity to mispronunciation location (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth.
+In early language acquisition, infants typically know more consonant compared to vowel onset words.
+When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations.
+The prevalence of consonant onset words may contribute to the finding that consonants carry more weight in lexical processing (C-bias; see Nazzi, Poltrock, & Von Holzen, 2016 for a recent review).
+In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations.
+Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels.
+English-learning 12-, 15-, 18-, and 24-month-olds (Mani & Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds (Hojen et al., unpublished) demonstrate similar sensitivity to consonant and vowel mispronunciations.
+One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations (Swingley, 2016).
+The English-learning infants tested by Swingley were older than previous studies (mean age 28 months).
+In word learning, the C-bias has been found to develop later in English learning infants (Floccia, Nazzi, Delle Luche, Poltrock, & Goslin, 2014; Nazzi, Floccia, Moquet, & Butler, 2009).
+In the current meta-analysis, we attempt to synthesize studies examining sensitivity to consonant and vowel mispronunciations across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence (Floccia et al., 2014; Keidel et al., 2007; Nazzi et al., 2016).
+We further examine the impact of language family on mispronunciation sensitivity to consonants and vowels, as C-bias emergence has been found to have a different developmental trajectory for Romance (French, Italian) compared to Germanic (British English, Danish) languages (Nazzi et al., 2016).
+
+[KATIE] Christina had noted something to herself for this paragraph: Subset by language?
+
+  Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (see Summary_Table).
+Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare.
+Yet, studies testing infants from different language backgrounds on similar sets of stimuli find similar sensitivity to mispronunciations (Ramon-Casas et al., 2009; Ramon-Casas & Bosch, 2010).
+Although we do not explicitly compare overall mispronunciation sensitivity by language (although see previous paragraph for rationale to test by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.
+
+Taken together, the studies we have reviewed begin to paint a picture of the development of mispronunciation sensitivity.
+Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding.
+In our analysis, we examine the factors modulating the development of mispronunciation sensitivity, which are both of theoretical and practical importance.
+Meta-analyses can not only help us summarize the current state of research, but can also help us evaluate theories to drive future research and make hands-on recommendations for experiment planning.
+
 # Methods
@@
 [CHRISTINA suggestions: N features should be a range and exclude 0; we could abbreviate Comperehension/Production to Comp./Prod., etcetc]
+[KATIE] I'll think about how to implement that! Might end up having to adjust the table by hand, there is a lot of variation between studies.
 
@@
 
-t_num <- t_num+1
-
 pub_info <- dat %>%
@@
 kable(pub_info, col.names = c("Publication Type", "# Items", "# Effect Sizes"))
-
-# Not sure about this plot
-#pi <- dat[,c("short_cite", "publication_status")]
-#pi <- unique(pi)
-
-#c.plot <- ggplot(pi, aes(x= publication_status)) + 
-#  geom_text(stat='count', aes(label=..count..), vjust=-1, size = 5)+
-#  geom_bar(stat="count")+
-#  coord_cartesian(ylim = c(0, 30))+
-#  apatheme+
-#  theme(axis.text.x = element_text(size = 20, angle = -45, hjust = .11),
-#        axis.title.x = element_blank())
-
-#c.plot
-
-#  jpeg(filename = "figures/Pub_count.jpg", 
-#       width = 500, height = 500, units = "px")
-
-#  c.plot
-
-#  dev.off()
 
@@
 
-kable(es_info)
+#kable(es_info)
 #table(dat$es_method, dat$short_cite)
@@
 # Renner (2017) <- just finished phd
-# Tamasi (2016) <- standard deviations are wrong
 #table(db_ET_MP$es_method)
@@
 #[CHRISTINA] Mpt sire what you man, like in the table? You rename things later on, so why not.
+#[KATIE] Actually, do we really need this table? When everything is summarized in the text, is that good enough?
+
+corr_info <- dat %>%
+  group_by(imputed_corr) %>%
+  summarize(n_unique = n_distinct(short_cite), count = n())
+
 ```
@@
 looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values.
-One paper reported this correlation [CHRISTINA: Can we cite this??]; we were able to compute correlations using means, standard deviations, and t-values [CHRISTINA: can we add N?] (following Csibra, et al.
+Upon request we were provided with correlation values for one paper (Altvater-Mackensen, 2010); we were able to compute correlations using means, standard deviations, and t-values for *n* = `r with(corr_info, n_unique[imputed_corr == "no"]) - 1` (following Csibra, et al.
 2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, 2018).
@@
 [CHRISTINA: Do you think we have to revise this section? I think it's the same as in the proceedings paper.]
+[KATIE: Are you concerned about the Publication Bias section in particular, or the Methods as a whole?
+In general, some of the Methods was written before the CogSci paper and in other places to flesh things out I rewrote what we had.
+Its definitely giving the same information and sometimes the wording is close, because there's not too many different ways to explain what a funnel plot is :)]
 
@@
 For now I think the last sentence is fine, but I would tend to prefer a reminder for the forgetful reader.]
+[KATIE: that's reasonable! We had just listed everything 7 paragraphs before, which doesn't seem like a lot of "space".]
 
@@
 [CHRISTINA: If we want to interpret here, how about the next bit.]
+[KATIE: YES! This is an excellent point!!!]
 
@@
 If infants were not looking to the target picture after hearing the correct label, the overall experiment design is called into questions.
-However, due to the small effect and sample sizes (which we will discuss in the following sections in more detail) one would expect the regular occurrence of null results even though as population infants would reliably show the expected object identification effect.
+However, due to the small effect and sample sizes (which we will discuss in the following sections in more detail) one would expect the regular occurrence of null results even though as a population infants would reliably show the expected object identification effect.
 
@@
 [CHRISTINA: CAn you add the stats for the non-sig results?]
-
-Taken together, these results suggest a tendency in the literature towards publication bias.
+[KATIE: Are there stats that can be computed on the non-sig results? Or do you just want an n for significant and non-significant studies?]
+
+Taken together, the results suggest a tendency in the literature towards publication bias.
 As a result, our meta-analysis may systematically overestimate effect sizes and we therefore interpret all estimates with caution.
@@
 Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` suggests that this result is robust even when correcting for publication bias.
+In other words, we are confident that the true population mean lies above zero for object recognition of correctly pronounced words.
 
 [CHRISTINA: Can you explain what the CI lower bound means here? I don't follow.]
+[KATIE: What do you think about this? The CI lower bound stuff here actually comes from something you wrote, so tell me whether its correct.]
 
@@
 [CHRISTINA] CAN YOU ADD ESTIMATES AND THEIR CIS?? Ideally everywhere where you report a p-value
+[KATIE: Do you know how to calculate Estimates and CIs for the Test of Moderators? Or do you mean reporting the estimates and CIs even when the moderator test is not significant?]
 
@@
 WE THEREFORE MUST CONCLUDE THAT WITHIN NARROW AGE GROUPS VOCABULARY DOES NOT INFLUENCE ANYTHING WE LOOK AT. WE CANNOT DO THIS ANALYSIS FPOR MP SENSITIVITY BECAUSE WE DON'T HAVE THE NECESSARY RAW DATA.
-(BUT I WONDER WHETHER WE COULD ENCODE THE REPORTED INTERACTION TERMS AND THE CORRELATION AND THEN DO SOMETHING WITH THAT?)
+[KATIE: Ah, so because for each paper the correlation and CI values straddle 0, this indicates that there really isn't much evidence for a relationship?
+I think it could make sense to add this to supplementary materials.
+Over the summer, I had also played around with looking at how collection of vocabulary data has dropped off over the years, even though more mispronunciation studies have been published.
+That might be something interesting to add.
+If we truly think that this is what is driving the development of mispronunciation sensitivity, then why are people not collecting this data?]
+(BUT I WONDER WHETHER WECOULD ENCODE THE REPORTED INTERACTION TERMS AND THE CORRELATION AND THEN DO SOMETHING WITH THAT?)
+[KATIE: I'm not really sure what you mean by this :(]
 
@@
 
-### Size of mispronunciation
-
-[CHRISTINA] I PREFER NUMBER OF FEATURES TO SIZE SOMEHOW
+[KATIE: I prefer this second option, first looking at the moderators in general and then looking at whether there is this systematic difference with age.
+The latter is exploratory, so I feel like this information should not preceed our planned analyses.]
+
+### Number of features changed
 
@@
 
-To understand the relationship between size of mispronunciation and mispronunciation sensitivity, we  evaluated the effect size Hedges' *g* with number of features changed as a moderator.
+To understand the relationship between number of features changed and mispronunciation sensitivity, we  evaluated the effect size Hedges' *g* with number of features changed as a moderator.
 The moderator test was significant, QM(`r r2(rma_NFeatures$m)`) = `r r2(rma_NFeatures$QM)`, *p* `r psig(rma_NFeatures$QMp)`.
@@
 `r with(nfeature_ages, min_age[n_feature == 3])` - `r with(nfeature_ages, max_age[n_feature == 3])` days), however, did not change the pattern of results.
-
-[KATIE] DOES THE ABOVE PARAGRAPH NEED MORE MOTIVATION? SHOULD IT EVEN BE INCLUDED?
-[CHRISTINA] I THINK IT\S GREAT!
 
@@
 [CHRISTINA] I WOULD NOT OVERINTERPRET IT, THE ESTIMATE DID NOT DRAMATICALLY CHANGE, AND IT IS BARELY SIGNIFICANT. DOES THAT HELP?
+
+[KATIE: I think so. I've just removed that part]
 
@@
 
+\newpage
+
 # References
+```{r create_r-references}
+#r_refs(file = "r-MISP_MA_BIB.bib")
+```
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id = "refs"></div>
+\endgroup

### 2018-10-23 Paper_Analyses.tex
convert to papaja, temporary references fix

--- 2018-10-23 Paper_Analyses.Rmd
@@
----
-title             : "The development of infants' responses to mispronunciations - A Meta-Analysis"
-shorttitle        : "Mispronunciation Meta-Analysis"
-
-author: 
-  - name          : "Katie Von Holzen"
-    affiliation   : "1,2"
-    corresponding : yes    # Define only one corresponding author
-    address       : "0221A LeFrak Hall, University of Maryland, College Park, MD 20742"
-    email         : "katie.m.vonholzen@gmail.com"
-  - name          : "Christina Bergmann"
-    affiliation   : "3,4"
-
-affiliation:
-  - id            : "1"
-    institution   : "Language Development Laboratory, University of Maryland, USA"
-  - id            : "2"
-    institution   : "Laboratoire Psychologie de la Perception, Université Paris Descartes"
-  - id            : "3"
-    institution   : "Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands"
-  - id            : "4"
-    institution   : "LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University"
-
-abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-keywords          : "keywords"
-wordcount         : "X"
-
-floatsintext      : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-citeproc          : no
-
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
----
-
-```{r Setup, echo = FALSE, warning=FALSE, warning = FALSE, error = FALSE, message = FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)
-
-# bibliography      : ["MISP_MA_BIB.bib"]
-
-# [KATIE] BIBLIOGRAPHY CURRENTLY REMOVED, AS IT IS CAUSING ERRORS WITH PAPAJA
-# THIS IS PARTIALLY DUE TO THE WAY I CREATE IT USING MENDELEY. 
-# TOO LAZY FOR THE MOMENT TO COMPLETELY OVERHAUL THIS
-
-# BUT, OTHER PROBLEMS INCLUDE HAVING PAPAJA INSTALLED IN THE USER AND NOT SYSTEM LIBRARY
-# https://github.com/crsh/papaja/issues/162
-# devtools::with_libpaths(new = "/usr/lib/R/library/", install_github('crsh/papaja'))
-
-# AND THE NEED TO SET citeproc: no
-# https://github.com/crsh/papaja/issues/96
-
-# STILL NEED TO FIGURE OUT WHAT ACTUAL PROBLEM IS, THIS IS CURRENTLY JUST A WORKAROUND
-
-### Load libraries
-library(papaja)
-library(metafor)
-library(meta)
-library(pwr)
-library(knitr)
-library(ggplot2)
-library(wesanderson)
-library(grid)
-library(gridExtra)
-library(xtable)
-library(schoRsch)
-library(multcomp)
-library(poibin)
-library(tidyverse)
-
-r2 <- function(x){ round(x, 3)}
-
-psig <- function(x){
-  ifelse(x < .001, "< .001",
-         #ifelse(x < .001, "< .001",
-                #ifelse(x < .01, "< .01",
-                       ifelse(x > .001 & x < .05, paste("=", r2(x), sep = " "), paste("=", r2(x), sep = " ")))#))
+\documentclass[man]{apa6}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={The development of infants' responses to mispronunciations - A Meta-Analysis},
+            pdfauthor={Katie Von Holzen~\& Christina Bergmann},
+            pdfkeywords={keywords},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
 }
-
-# function for creating 1 line paired t.test results
-t.xtable <- function(x) as.data.frame(xtable(
-  t_out(toutput=x, n.equal = TRUE, welch.df.exact = TRUE, welch.n = NA,
-        d.corr = TRUE, print = TRUE)
-))
-
-```
-
-```{r ReadIn}
-
-#Get the effect size data
-source("scripts/calculateES.R")
-
-```
-
-```{r Preprocess}
-
-db_ET <- db_ET %>%
-  mutate(age.C = (mean_age_1-mean(mean_age_1, na.rm=TRUE))/30.44) %>%
-  filter(mean_age_months < 31)
-
-db_ET$collapse <- paste(db_ET$study_ID, db_ET$expt_num, db_ET$same_infant, sep = "_")
-
-# assign language families
-
-db_ET$lang_family = ifelse(db_ET$native_lang=="American English" | db_ET$native_lang=="British English" | db_ET$native_lang=="Dutch" |
-db_ET$native_lang=="Danish" | db_ET$native_lang=="Swedish" |
-db_ET$native_lang=="English" | db_ET$native_lang=="German", "Germanic", ifelse(db_ET$native_lang == "French" | db_ET$native_lang == "Catalan" | db_ET$native_lang == "Spanish" | db_ET$native_lang == "Catalan-Spanish" | db_ET$native_lang == "Swiss French",
-                                "Romance", "Sino-Tibetian"))
-
-#Split into correct and MP database
-
-db_ET_correct <- db_ET[db_ET$is_correct=="1",]
-db_ET_MP <- db_ET[db_ET$is_mp=="1",]
-
-#collapse over nonindependent MP rows for a *general* MP effect
-
-collapse_rows <- function(db){
-  db$collapse <- paste(db$study_ID, db$expt_num, db$same_infant, sep = "_")
-
-  for(independent in unique(db$collapse)){
-    if(length(db[db$collapse==independent])>1){
-      sub = db[db$collapse==independent, ]
-      sub$d_calc <- median(sub$d_calc)
-      sub$d_var_calc <- median(sub$d_var_calc)
-      sub$g_calc <- median(sub$g_calc)
-      sub$g_var_calc <- median(sub$g_var_calc)
-      sub$corr_imputed <- median(sub$corr_imputed)
-      db <- db[!(db$collapse==independent),]
-      db <- rbind(db, sub[1,])
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
+
+%%% Change title format to be more compact
+\usepackage{titling}
+
+% Create subtitle command for use in maketitle
+\newcommand{\subtitle}[1]{
+  \posttitle{
+    \begin{center}\large#1\end{center}
     }
 }
-  return(db)
+
+\setlength{\droptitle}{-2em}
+  \title{The development of infants' responses to mispronunciations - A
+Meta-Analysis}
+  \pretitle{\vspace{\droptitle}\centering\huge}
+  \posttitle{\par}
+  \author{Katie Von Holzen\textsuperscript{1,2}~\& Christina
+Bergmann\textsuperscript{3,4}}
+  \preauthor{\centering\large\emph}
+  \postauthor{\par}
+  \date{}
+  \predate{}\postdate{}
+
+\shorttitle{Mispronunciation Meta-Analysis}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Language Development Laboratory, University of Maryland, USA\\\textsuperscript{2} Laboratoire Psychologie de la Perception, Université Paris Descartes\\\textsuperscript{3} Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands\\\textsuperscript{4} LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University}
+\keywords{keywords\newline\indent Word count: X}
+\usepackage{csquotes}
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
+
+\usepackage{longtable}
+\usepackage{lscape}
+\usepackage{multirow}
+\usepackage{tabularx}
+\usepackage[flushleft]{threeparttable}
+\usepackage{threeparttablex}
+
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+\DeclareDelayedFloatFlavor{ThreePartTable}{table}
+\DeclareDelayedFloatFlavor{lltable}{table}
+\DeclareDelayedFloatFlavor*{longtable}{table}
+\makeatletter
+\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
+\makeatother
+\usepackage{lineno}
+
+\linenumbers
+
+\authornote{
+
+Correspondence concerning this article should be addressed to Katie Von
+Holzen, 0221A LeFrak Hall, University of Maryland, College Park, MD
+20742. E-mail:
+\href{mailto:katie.m.vonholzen@gmail.com}{\nolinkurl{katie.m.vonholzen@gmail.com}}}
+
+\abstract{
+One or two sentences providing a \textbf{basic introduction} to the
+field, comprehensible to a scientist in any discipline.
+
+Two to three sentences of \textbf{more detailed background},
+comprehensible to scientists in related disciplines.
+
+One sentence clearly stating the \textbf{general problem} being
+addressed by this particular study.
+
+One sentence summarizing the main result (with the words ``\textbf{here
+we show}'' or their equivalent).
+
+Two or three sentences explaining what the \textbf{main result} reveals
+in direct comparison to what was thought to be the case previously, or
+how the main result adds to previous knowledge.
+
+One or two sentences to put the results into a more \textbf{general
+context}.
+
+Two or three sentences to provide a \textbf{broader perspective},
+readily comprehensible to a scientist in any discipline.
+
 }
 
-#db_ET_correct = collapse_rows(db_ET_correct)
-
-#db_ET_MP = collapse_rows(db_ET_MP)
-
-#remove outliers, for now we have none, though
-db_ET_MP$nooutlier = ifelse(db_ET_MP$g_calc > mean(db_ET_MP$g_calc, na.rm = TRUE) + 3*sd(db_ET_MP$g_calc, na.rm = TRUE) 
-                         | db_ET_MP$g_calc < mean(db_ET_MP$g_calc, na.rm = TRUE) - 3*sd(db_ET_MP$g_calc, na.rm = TRUE),FALSE, TRUE)
-db_ET_MP = db_ET_MP[db_ET_MP$nooutlier,]
-
-db_ET_correct$nooutlier = ifelse(db_ET_correct$g_calc > mean(db_ET_correct$g_calc, na.rm = TRUE) + 3*sd(db_ET_correct$g_calc, na.rm = TRUE) 
-                         | db_ET_correct$g_calc < mean(db_ET_correct$g_calc, na.rm = TRUE) - 3*sd(db_ET_correct$g_calc, na.rm = TRUE),FALSE, TRUE)
-db_ET_correct = db_ET_correct[db_ET_correct$nooutlier,]
-
-# make sure that both correct and mispronounced conditions are considered in descriptives
-
-db_ET_correct$condition <- 1
-db_ET_MP$condition <- 0
-
-dat <- bind_rows(db_ET_correct, db_ET_MP)
-
-# need data set of unique short cite by expt_num
-# in order to calculate total number of infants
-
-# need data set of unique short cite by condition
-
-sum_dat <- dat[!duplicated(dat[c("short_cite", "same_infant")]),]
-time_wind_dat <- dat[!duplicated(dat[c("short_cite", "offset", "post_nam_dur")]),]
-distract_dat <- dat[!duplicated(dat[c("short_cite", "object_pair")]),]
-mix_co_mp <- dat[!duplicated(dat[c("short_cite", "word_correct_and_MP")]),]
-
-```
-
-```{r PlotAPATheme}
-# Plotting defaults
-
-#Themes and plot
-apatheme=theme_bw()+
-  theme(panel.grid.major=element_blank(),
-    panel.grid.minor=element_blank(),
-    panel.border=element_blank(),
-    axis.line=element_line(),
-    text=element_text(family='Times', size=25))
-
-# Color Blind palette:
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
-```
-
-# Introduction
-
-Acquiring a first language means that young learners are solving a host of tasks in a short amount of time.
-As infants develop into toddlers during their second and third years they learn new words in earnest while simultaneously refining their knowledge about the sounds that make up these words.
-Before children can correctly pronounce a word, they already show evidence of sensitivity to slight variations in the phonological form of that word.
-This mispronunciation sensitivity reflects the specificity with which infants represent the phonological information of familiar words and are sensitive to changes that might signal a change in word meaning.
-As infants continue to develop into expert language users, their language processing matures and becomes more efficient.
-In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonetic details that differentiate words in their native language (e.g.
-cat-hat).
-In this paper, we aggregate and analyze the almost 20 years of literature investigating mispronunciation sensitivity in infants in an attempt to uncover its characteristics and the trajectory of its development.
-
-  At the turn of the millenia, infant language acquisition researchers had established that during their first years of life, infants are sensitive to changes in the phonetic detail of newly segmented words (Jusczyk & Aslin, 1995) and learned minimal pairs (Stager & Werker, 1997).
-Furthermore, when presented with familiar image pairs, children fixate on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg, & McRoberts, 1998).
-Swingley and Aslin (2000) were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English were presented with pairs of images (e.g.
-baby, dog) and their eye movements to each image were coded offline.
-On "correct" trials, children heard the correct label for one of the images (e.g.
-baby).
-On "mispronounced" trials, children heard a mispronounced label of one of the images (e.g.
-vaby).
-Mean proportion of fixation to the target image (here: a baby) was calculated for both correct and mispronounced trials by dividing the target looking time by the sum of total looking time to both target and a distractor (proportion of target looking or PTL).
-Mean fixations in correct trials were significantly greater than in mispronounced trials, although looks to the target were significantly greater than chance in both types of trials.
-We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance as *recognition*.
-Swingley and Aslin (2000) concluded that already before the second birthday, children represent words with sufficient detail to be sensitive to mispronunciations.
-
-  The study of Swingley and Aslin (2000) as well as subsequent studies examining mispronunciation sensitivity address two complementary concepts in early phonological development: *phonological constancy* and *phonological distinctiveness*.
-Phonological constancy is the ability to accept phonological variation across different instances of a word, as long as the variation does not compromise the overall identity of the word.
-For example, different speakers - particularly across genders and accents - produce the same word with notable acoustic variation, although the word remains the same.
-In contrast, phonological distinctiveness describes the ability to differentiate between different words that happen to be phonologically similar, such as bad/bed or cat/hat.
-To successfully recognize words, infants must therefore simultaneously use both phonological constancy and distinctiveness to determine where phonological variation is appropriate and where it changes a word's meaning.
-
-  In the current study, we focus on infants' developing ability to correctly apply the principles of phonological distinctiveness and constancy by using a meta-analytic approach to investigate mispronunciation sensitivity.
-Considering that infants are sensitive to mispronunciations and that, in general, their processing matures with development, we examine the shape of mispronunciation sensitivity over the course of the second and third year.
-There are three distinct possibilities how mispronunciation sensitivity might change as infants become native speakers, which are all respectively predicted by theoretical accounts and supported by single studies.
-By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants.
-Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.
-
-  Young infants may begin cautiously in their approach to word recognition, rejecting any phonological variation in familiar words and only later learning to accept appropriate variability.
-According to the Perceptual Attunement account, this describes a shift away from specific native phonetic patterns to a more mature understanding of the abstract phonological structure of words (Best 1994, 1995).
-This shift is predicted to coincide with the vocabulary spurt around 18 months, and is therefore related to vocabulary growth.
-In this case, we would expect the size of mispronunciation sensitivity to be larger at younger ages and *decrease* as the child matures and learn more words, although children continue to detect mispronunciations.
-Indeed, young infants are less likely than older infants to demonstrate recognition of familiar words (Best, Tyler, Gooding, Orlando, & Quann, 2009; Mulak, Best, & Tyler, 2013) or learn new words (Schmale, Hollich, & Seidl, 2011) from accented speakers.
-
-  According to a different theoretical framework, young infants may instead begin with phonologically broad representations for familiar words and only refine their representations as language experience accumulates.
-PRIMIR (Processing Rich Information from Multidimensional Interactive Representations; Curtin & Werker, 2007; Werker & Curtin, 2005; Curtin, Byers-Heinlein, & Werker, 2011) describes the development of phonemic categories emerging as the number of word form-meaning linkages increases.
-Vocabulary growth, therefore, promotes more detailed phonological representations in familiar words.
-Following this account, we predict an *increase* in mispronunciation sensitivity as infants mature and add more words to their growing lexicon.
-
-  Finally, sensitivity to mispronunciation may not be modulated by development at all.
-Infants' overall language processing becomes more efficient, but their sensitivity to mispronunciations may not change.
-Across infancy and toddlerhood, mispronunciations would thus be detected and lead to less looks at a target than correct pronunciations, but the size of this effect would not change, nor be related to vocabulary size.
-This pattern is not predicted by any mainstream theory of language acquisition, but for completeness we mention it here.
-
-  Research following the seminal study by Swingley and Aslin (2000) has extended mispronunciation sensitivity to infants as young as 12 months (Mani & Plunkett, 2010), indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations.
-Regarding the change in mispronunciation sensitivity over development, however, only a handful of studies have compared more than one age group on the same mispronunciation task (see Table X), making the current meta-analysis very informative.
-One study has found evidence for infants to become *less* sensitive to mispronunciations as children develop.
-Mani and Plunkett (2011) presented 18- and 24-month-olds with mispronunciations varying in the number of features changed (see below for a discussion of the role of features).
-18-month-olds were sensitive to mispronunciations, regardless of the number of features changed.
-24-month-olds, in contrast, fixated the target image equally for both correct and 1-feature mispronounced trials, although they were sensitive to larger mispronunciations.
-In other words, for 1-feature mispronunciations at least, sensitivity decreased from 18 to 24 months, providing support to the prediction that mispronunciation sensitivity may decrease with development.
-
-  In contrast, other studies have found evidence for *greater* mispronunciation sensitivity as children develop.
-More precisely, the difference in target looking for correct and mispronounced trials is smaller in younger infants and grows as infants develop.
-Mani and Plunkett (2007) tested 15-, 18-, and 24-month-olds learning British English; although all three groups were sensitive to mispronunciations, 15-month-olds showed a less robust sensitivity.
-An increase in sensitivity to mispronunciations has also been found from 20 to 24 months (van der Feest & Fikkert, 2015) and 15 to 18 months (Altvater Mackensen et al., 2013) in Dutch infants, as well as German infants from 22 to 25 months (Altvater-Mackensen, 2010).
-Furthermore, van der Feest and Fikkert (2015) found that sensitivity to specific kinds of mispronunciations develop at different ages depending on language infants are learning.
-In other words, the native language constraints which *kinds* of mispronunciations infants are sensitive to first, and that as infants develop, they become sensitive to other mispronunciations.
-These studies award support to the prediction that mispronunciation sensitivity improves with development.
-
-Finally, some studies have found no difference in mispronunciation sensitivity at different ages.
-Swingley and Aslin (2000) tested infants over a wide age range of 5 months (18 to 23 months).
-They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation effect) did not.
-This suggests that as children develop, they are more likely to look at the target in the presence of a mispronounced label and that age is not related to mispronunciation sensitivity.
-A similar response pattern has been found for British English learning infants aged between 18 and 24 months (Bailey & Plunkett, 2002) as well as younger French-learning infants at 12 and 17 months (Zesiger, Lozeron, Levy, & Frauenfelder, 2012).
-These studies award support to the prediction that mispronunciation sensitivity does not change with development.
-
-  Why would mispronunciation sensitivity change as infants develop, and would it increase or decrease?
-The main hypothesis is related to vocabulary growth.
-Both the Perceptual Attunement (Best, 1994; 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005; Curtin, Byers-Heinlein, & Werker, 2011) accounts situate a change in mispronunciation sensitivity occurring along with an increase in vocabulary size, particularly with the vocabulary spurt at about 18 months.
-Knowing more words helps infants shift their focus to the relevant phonetic dimensions needed for word recognition.
-On the one hand, a smaller lexicon does not require full specification to differentiate between words; as more phonologically similar words are learned, so does the need to have fully detailed representations for those words (Charles-Luce & Luce, 1995).
-On the other hand, a growing vocabulary is also related to more experience or familiarity with words, which may sharpen the detail of their representation (Barton, 1980).
-
-  Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship (Swingley & Aslin 2000; 2002; Bailey & Plunkett, 2002; Zesiger, Lozeron, Levy, & Frauenfelder, 2012; Swingley, 2009; Ballem & Plunkett, 2005; Mani & Plunkett, 2007; Mani, Coleman, & Plunkett, 2008).
-One notable exception comes from Mani and Plunkett (2010: keps and tups).
-Here, 12-month-old infants were divided into a low vocabulary and high vocabulary group based group median vocabulary size.
-High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations.
-Taken together, although receiving considerable support from theories of phono-lexical processing in language acquisition, there is very little evidence for a role of vocabulary size in mispronunciation sensitivity.
-In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to further disentangle the disconnect between theory and experimental results.
-
-  Next to this core theoretically relevant investigation of the shape of development of infants' mispronunciation sensitivity, we take the opportunity of a systematic aggregation of data to address open questions regarding differences in experiment design and whether changes in procedure and stimuli tap into significantly different aspects of infants' ability to detect mispronunciations.
-
-  In designing their mispronunciation stimuli, Swingley and Aslin (2000) chose consonant mispronunciations that were likely to confuse adults (Miller & Nicely, 1955).
-Subsequent research has settled on systematically modulating phonemic features to achieve mispronunciations of familiar words.
-By utilizing mispronunciations consisting of phonemic changes, these experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level (i.e.
-1-feature, 2-features, 3-features, etc.).
-The importance of controlling for the degree of phonological mismatch, as measured by number of features changed, is further highlighted by studies that find graded sensitivity to both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes.
-
-  Although most research examining sensitivity to mispronunciations follows a similar design, there are some notable differences.
-For example, Swingley and Aslin (2000) presented infants with pairs of familiar images, one serving as the labeled target and one as the unlabeled distractor.
-In contrast, White and Morgan (2008; see also Mani & Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects.
-By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied (Halberda, 2003; Markman, Wasow, & Hansen, 2003).
-Infants ages 24 and 30 months associate a novel label with an unfamiliar object, although only 30-month-olds retained this label-object pairing (Bion, Borovsky, and Fernald, 2013).
-In contrast, 18-month-olds did not learn to associate a novel label with an unfamiliar object, providing evidence that this ability is developing from 18 to 30 months.
-We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by whether the distractor used is familiar or unfamiliar.
-Although mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared, the baseline preference for familiar compared to novel stimuli is also thought to change as infants develop (Hunter & Ames, 1988).
-Furthermore, young children have been found to look longer at objects for which they know the name, compared to objects of an unknown name (Schafer & Plukett, 1998).
-In other words, in absentia of a label, infants may be more or less likely to fixate on an unfamiliar object.
-To account for inherent preferences to the target or distractor image, mispronunciation experiments typically compare the increase in fixations to the target image from a silent baseline to post-labeling or present the same yoked pairs of target and distractor images in in both a correct and mispronounced labelling context.
-Considering this evidence, we may expect that in older, but not younger, children, the presence of an unfamiliar distractor may lead to greater mispronunciation sensitivity than in the presence of a familiar distractor.
-
-  Furthermore, when presenting infants with a familiar distractor image, some studies control the phonological overlap between the labels for the target and distractor.
-For example, when examining sensitivity to a mispronunciation of the target word "dog", the vowel mispronunciation "dag" would be paired with a distractor image that shares onset overlap, such as "duck".
-This ensures that infants can not use the onset of the word to differentiate between the target and distractor images (Fernald, Swingley, & Pinto, 2001).
-Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.
-The influence of distractor overlap also depends on the position of the mispronunciation in the word, which can be at word onset, medial, or final positions.
-Models of spoken word processing place more or less importance on the position of a phoneme in a word.
-The COHORT model (Marslen-Wilson & Zwitserlood, 1989) describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.
-In contrast, the TRACE model (McClelland & Elman, 1986) describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.
-
-  TRACE has also been used to model infants' sensitivity to mispronunciation location (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth.
-In early language acquisition, infants typically know more consonant compared to vowel onset words.
-When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations.
-The prevalence of consonant onset words may contribute to the finding that consonants carry more weight in lexical processing (C-bias; see Nazzi, Poltrock, & Von Holzen, 2016 for a recent review).
-In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations.
-Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels.
-English-learning 12-, 15-, 18-, and 24-month-olds (Mani & Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds (Hojen et al., unpublished) demonstrate similar sensitivity to consonant and vowel mispronunciations.
-One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations (Swingley, 2016).
-The English-learning infants tested by Swingley were older than previous studies (mean age 28 months).
-In word learning, the C-bias has been found to develop later in English learning infants (Floccia, Nazzi, Delle Luche, Poltrock, & Goslin, 2014; Nazzi, Floccia, Moquet, & Butler, 2009).
-In the current meta-analysis, we attempt to synthesize studies examining sensitivity to consonant and vowel mispronunciations across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence (Floccia et al., 2014; Keidel et al., 2007; Nazzi et al., 2016).
-We further examine the impact of language family on mispronunciation sensitivity to consonants and vowels, as C-bias emergence has been found to have a different developmental trajectory for Romance (French, Italian) compared to Germanic (British English, Danish) languages (Nazzi et al., 2016).
-
-[KATIE] Christina had noted something to herself for this paragraph: Subset by language?
-
-  Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (see Summary_Table).
-Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare.
-Yet, studies testing infants from different language backgrounds on similar sets of stimuli find similar sensitivity to mispronunciations (Ramon-Casas et al., 2009; Ramon-Casas & Bosch, 2010).
-Although we do not explicitly compare overall mispronunciation sensitivity by language (although see previous paragraph for rationale to test by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.
-
-Taken together, the studies we have reviewed begin to paint a picture of the development of mispronunciation sensitivity.
-Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding.
-In our analysis, we examine the factors modulating the development of mispronunciation sensitivity, which are both of theoretical and practical importance.
-Meta-analyses can not only help us summarize the current state of research, but can also help us evaluate theories to drive future research and make hands-on recommendations for experiment planning.
-
-# Methods
-
-The present meta-analysis was conducted with maximal transparency and reproducibility in mind.
-To this end, we provide all data and analysis scripts on the supplementary website (https://osf.io/rvbjs/) and open our meta-analysis up for updates (Tsuji, Bergmann, & Cristia, 2014).
-The most recent version is available via the website and the interactive platform MetaLab (metalab.stanford.edu; Bergmann et al., 2018).
-Since the present paper was written with embedded analysis scripts in R [@R], it is always possible to re-analyze an updated dataset.
-In addition, we follow the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials (Moher, Liberati, Tetzlaff, Altman & PRISMAGroup, 2009).
-Figure X plots our PRISMA flowchart.
-
-![Figure X. PRISMA Flowchart.] (figures/PRISMA_MA_Mispronunciation.png)
-
-## Study Selection
-
-```{r SummaryTable}
-
-dat_st <- dat
-
-dat_st$object_pair <- ifelse(dat_st$object_pair == "familiar_familiar", "Familiar", "Unfamiliar")
-
-Sum_table <- dat_st %>%
-      group_by(short_cite) %>% 
-      summarise(Ages_Tested_months = paste(unique(trunc(mean_age_1/30.34)), collapse=', '),
-                Vocabulary = ifelse(all(is.na(r_comprehension)) & all(is.na(r_production)), "None",
-                                ifelse(!all(is.na(r_comprehension)) & !all(is.na(r_production)), "Comprehension/Production",
-                                       ifelse(!all(is.na(r_comprehension)) & all(is.na(r_production)), "Comprehension", "Production"))),
-                Number_of_Features = paste(unique(n_feature), collapse=', '),
-                Distractor_Familiarity = paste(unique(object_pair), collapse=', '),
-                Distractor_Overlap = paste(unique(distractor_overlap), collapse=', '),
-                Mispronunciation_Position = paste(unique(mispron_location), collapse=', '),
-                Mispronunciation_type = paste(unique(type_feature), collapse=', '))
-
-kable(Sum_table, col.names = c("Paper", "Age", "Vocabulary", "# Features", "Distractor", "Distractor name overlap", "MP Position", "MP Type"))
-
-```
-
-[KATIE] THIS TABLE IS DEFINITELY NOT FINISHED!
-[CHRISTINA suggestions: N features should be a range and exclude 0; we could abbreviate Comperehension/Production to Comp./Prod., etcetc]
-[KATIE] I'll think about how to implement that! Might end up having to adjust the table by hand, there is a lot of variation between studies.
-
-We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list.
-This process yielded 110 items.
-We then used the google scholar search engine to search for papers citing the original Swingley & Aslin (2000) publication.
-This search was conducted on 22 September, 2017 and yielded 288 results.
-We screened the 398 items, removing 99 duplicate items.
-We screened remaining 299 items for their title and abstract to determine whether it met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition; (3) infants studied were under 36-months-of-age; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; 5) the stimuli were auditory speech.
-The final sample (n = *`r length(unique(dat$short_cite))`*) consisted of `r with(dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(dat, n_distinct(short_cite[publication_status == "dissertation"]))` thesis, and `r with(dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports.
-We will refer to these items collectively as papers.
-Table 1 (Summary Table) provides an overview of all papers included in the present meta-analysis.
-
-```{r DescriptivesPubtype}
-
-pub_info <- dat %>%
-  group_by(publication_status) %>%
-  summarize(n_unique = n_distinct(short_cite), count = n())
-
-kable(pub_info, col.names = c("Publication Type", "# Items", "# Effect Sizes"))
-
-```
-
-## Data Entry
-
-The `r length(unique(dat$short_cite))` papers we identified as relevant were then coded with as much detail as possible (Tsuji, Bergmann, & Cristia, 2014; Bergmann et al., 2018).
-For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results.
-For the present analyses, we focus on the following characteristics:
-1 Condition: Were words mispronounced or not;  
-2 Mean age reported per group of infants, in days;  
-3 Vocabulary size, measured by a standardized questionnaire or list;    
-4 Size of mispronunciation, measured in features changed;  
-5 Distractor familiarity: familiar or unfamiliar;  
-6 Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;  
-7 Position of mispronunciation: onset, medial, offset, or mixed;  
+\usepackage{amsthm}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}{Lemma}[section]
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
+\newtheorem{corollary}{Corollary}[section]
+\newtheorem{proposition}{Proposition}[section]
+\theoremstyle{definition}
+\newtheorem{example}{Example}[section]
+\theoremstyle{definition}
+\newtheorem{exercise}{Exercise}[section]
+\theoremstyle{remark}
+\newtheorem*{remark}{Remark}
+\newtheorem*{solution}{Solution}
+\begin{document}
+\maketitle
+
+\section{Introduction}\label{introduction}
+
+Acquiring a first language means that young learners are solving a host
+of tasks in a short amount of time. As infants develop into toddlers
+during their second and third years they learn new words in earnest
+while simultaneously refining their knowledge about the sounds that make
+up these words. Before children can correctly pronounce a word, they
+already show evidence of sensitivity to slight variations in the
+phonological form of that word. This mispronunciation sensitivity
+reflects the specificity with which infants represent the phonological
+information of familiar words and are sensitive to changes that might
+signal a change in word meaning. As infants continue to develop into
+expert language users, their language processing matures and becomes
+more efficient. In a mature phono-lexical system, word recognition must
+balance flexibility to slight variation (e.g., speaker identity,
+accented speech) while distinguishing between phonetic details that
+differentiate words in their native language (e.g.~cat-hat). In this
+paper, we aggregate and analyze the almost 20 years of literature
+investigating mispronunciation sensitivity in infants in an attempt to
+uncover its characteristics and the trajectory of its development.
+
+At the turn of the millenia, infant language acquisition researchers had
+established that during their first years of life, infants are sensitive
+to changes in the phonetic detail of newly segmented words (Jusczyk \&
+Aslin, 1995) and learned minimal pairs (Stager \& Werker, 1997).
+Furthermore, when presented with familiar image pairs, children fixate
+on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg,
+\& McRoberts, 1998). Swingley and Aslin (2000) were the first to tie
+these lines of research together and investigate mispronunciation
+sensitivity in infant familiar word recognition: Children aged 18 to 23
+months learning American English were presented with pairs of images
+(e.g.~baby, dog) and their eye movements to each image were coded
+offline. On \enquote{correct} trials, children heard the correct label
+for one of the images (e.g.~baby). On \enquote{mispronounced} trials,
+children heard a mispronounced label of one of the images (e.g.~vaby).
+Mean proportion of fixation to the target image (here: a baby) was
+calculated for both correct and mispronounced trials by dividing the
+target looking time by the sum of total looking time to both target and
+a distractor (proportion of target looking or PTL). Mean fixations in
+correct trials were significantly greater than in mispronounced trials,
+although looks to the target were significantly greater than chance in
+both types of trials. We refer to this pattern of a difference between
+looks to correct and mispronounced words as \emph{mispronunciation
+sensitivity} and of looks to the target image above chance as
+\emph{recognition}. Swingley and Aslin (2000) concluded that already
+before the second birthday, children represent words with sufficient
+detail to be sensitive to mispronunciations.
+
+The study of Swingley and Aslin (2000) as well as subsequent studies
+examining mispronunciation sensitivity address two complementary
+concepts in early phonological development: \emph{phonological
+constancy} and \emph{phonological distinctiveness}. Phonological
+constancy is the ability to accept phonological variation across
+different instances of a word, as long as the variation does not
+compromise the overall identity of the word. For example, different
+speakers - particularly across genders and accents - produce the same
+word with notable acoustic variation, although the word remains the
+same. In contrast, phonological distinctiveness describes the ability to
+differentiate between different words that happen to be phonologically
+similar, such as bad/bed or cat/hat. To successfully recognize words,
+infants must therefore simultaneously use both phonological constancy
+and distinctiveness to determine where phonological variation is
+appropriate and where it changes a word's meaning.
+
+In the current study, we focus on infants' developing ability to
+correctly apply the principles of phonological distinctiveness and
+constancy by using a meta-analytic approach to investigate
+mispronunciation sensitivity. Considering that infants are sensitive to
+mispronunciations and that, in general, their processing matures with
+development, we examine the shape of mispronunciation sensitivity over
+the course of the second and third year. There are three distinct
+possibilities how mispronunciation sensitivity might change as infants
+become native speakers, which are all respectively predicted by
+theoretical accounts and supported by single studies. By aggregating all
+publicly available evidence using meta-analysis, we can examine
+developmental trends making use of data from a much larger and diverse
+sample of infants. Before we outline the meta-analytical approach and
+its advantages in detail, we first discuss the proposals this study
+seeks to disentangle and the data supporting each of the accounts.
+
+Young infants may begin cautiously in their approach to word
+recognition, rejecting any phonological variation in familiar words and
+only later learning to accept appropriate variability. According to the
+Perceptual Attunement account, this describes a shift away from specific
+native phonetic patterns to a more mature understanding of the abstract
+phonological structure of words (Best 1994, 1995). This shift is
+predicted to coincide with the vocabulary spurt around 18 months, and is
+therefore related to vocabulary growth. In this case, we would expect
+the size of mispronunciation sensitivity to be larger at younger ages
+and \emph{decrease} as the child matures and learn more words, although
+children continue to detect mispronunciations. Indeed, young infants are
+less likely than older infants to demonstrate recognition of familiar
+words (Best, Tyler, Gooding, Orlando, \& Quann, 2009; Mulak, Best, \&
+Tyler, 2013) or learn new words (Schmale, Hollich, \& Seidl, 2011) from
+accented speakers.
+
+According to a different theoretical framework, young infants may
+instead begin with phonologically broad representations for familiar
+words and only refine their representations as language experience
+accumulates. PRIMIR (Processing Rich Information from Multidimensional
+Interactive Representations; Curtin \& Werker, 2007; Werker \& Curtin,
+2005; Curtin, Byers-Heinlein, \& Werker, 2011) describes the development
+of phonemic categories emerging as the number of word form-meaning
+linkages increases. Vocabulary growth, therefore, promotes more detailed
+phonological representations in familiar words. Following this account,
+we predict an \emph{increase} in mispronunciation sensitivity as infants
+mature and add more words to their growing lexicon.
+
+Finally, sensitivity to mispronunciation may not be modulated by
+development at all. Infants' overall language processing becomes more
+efficient, but their sensitivity to mispronunciations may not change.
+Across infancy and toddlerhood, mispronunciations would thus be detected
+and lead to less looks at a target than correct pronunciations, but the
+size of this effect would not change, nor be related to vocabulary size.
+This pattern is not predicted by any mainstream theory of language
+acquisition, but for completeness we mention it here.
+
+Research following the seminal study by Swingley and Aslin (2000) has
+extended mispronunciation sensitivity to infants as young as 12 months
+(Mani \& Plunkett, 2010), indicating that from early stages of the
+developing lexicon onwards, infants can and do detect mispronunciations.
+Regarding the change in mispronunciation sensitivity over development,
+however, only a handful of studies have compared more than one age group
+on the same mispronunciation task (see Table X), making the current
+meta-analysis very informative. One study has found evidence for infants
+to become \emph{less} sensitive to mispronunciations as children
+develop. Mani and Plunkett (2011) presented 18- and 24-month-olds with
+mispronunciations varying in the number of features changed (see below
+for a discussion of the role of features). 18-month-olds were sensitive
+to mispronunciations, regardless of the number of features changed.
+24-month-olds, in contrast, fixated the target image equally for both
+correct and 1-feature mispronounced trials, although they were sensitive
+to larger mispronunciations. In other words, for 1-feature
+mispronunciations at least, sensitivity decreased from 18 to 24 months,
+providing support to the prediction that mispronunciation sensitivity
+may decrease with development.
+
+In contrast, other studies have found evidence for \emph{greater}
+mispronunciation sensitivity as children develop. More precisely, the
+difference in target looking for correct and mispronounced trials is
+smaller in younger infants and grows as infants develop. Mani and
+Plunkett (2007) tested 15-, 18-, and 24-month-olds learning British
+English; although all three groups were sensitive to mispronunciations,
+15-month-olds showed a less robust sensitivity. An increase in
+sensitivity to mispronunciations has also been found from 20 to 24
+months (van der Feest \& Fikkert, 2015) and 15 to 18 months (Altvater
+Mackensen et al., 2013) in Dutch infants, as well as German infants from
+22 to 25 months (Altvater-Mackensen, 2010). Furthermore, van der Feest
+and Fikkert (2015) found that sensitivity to specific kinds of
+mispronunciations develop at different ages depending on language
+infants are learning. In other words, the native language constraints
+which \emph{kinds} of mispronunciations infants are sensitive to first,
+and that as infants develop, they become sensitive to other
+mispronunciations. These studies award support to the prediction that
+mispronunciation sensitivity improves with development.
+
+Finally, some studies have found no difference in mispronunciation
+sensitivity at different ages. Swingley and Aslin (2000) tested infants
+over a wide age range of 5 months (18 to 23 months). They found that age
+correlated with target fixations for both correct and mispronounced
+labels, whereas the difference between the two (mispronunciation effect)
+did not. This suggests that as children develop, they are more likely to
+look at the target in the presence of a mispronounced label and that age
+is not related to mispronunciation sensitivity. A similar response
+pattern has been found for British English learning infants aged between
+18 and 24 months (Bailey \& Plunkett, 2002) as well as younger
+French-learning infants at 12 and 17 months (Zesiger, Lozeron, Levy, \&
+Frauenfelder, 2012). These studies award support to the prediction that
+mispronunciation sensitivity does not change with development.
+
+Why would mispronunciation sensitivity change as infants develop, and
+would it increase or decrease? The main hypothesis is related to
+vocabulary growth. Both the Perceptual Attunement (Best, 1994; 1995) and
+PRIMIR (Curtin \& Werker, 2007; Werker \& Curtin, 2005; Curtin,
+Byers-Heinlein, \& Werker, 2011) accounts situate a change in
+mispronunciation sensitivity occurring along with an increase in
+vocabulary size, particularly with the vocabulary spurt at about 18
+months. Knowing more words helps infants shift their focus to the
+relevant phonetic dimensions needed for word recognition. On the one
+hand, a smaller lexicon does not require full specification to
+differentiate between words; as more phonologically similar words are
+learned, so does the need to have fully detailed representations for
+those words (Charles-Luce \& Luce, 1995). On the other hand, a growing
+vocabulary is also related to more experience or familiarity with words,
+which may sharpen the detail of their representation (Barton, 1980).
+
+Yet, the majority of studies examining a potential association between
+mispronunciation sensitivity and vocabulary size have concluded that
+there is no relationship (Swingley \& Aslin 2000; 2002; Bailey \&
+Plunkett, 2002; Zesiger, Lozeron, Levy, \& Frauenfelder, 2012; Swingley,
+2009; Ballem \& Plunkett, 2005; Mani \& Plunkett, 2007; Mani, Coleman,
+\& Plunkett, 2008). One notable exception comes from Mani and Plunkett
+(2010: keps and tups). Here, 12-month-old infants were divided into a
+low vocabulary and high vocabulary group based group median vocabulary
+size. High vocabulary infants showed greater sensitivity to vowel
+mispronunciations than low vocabulary infants, although this was not the
+case for consonant mispronunciations. Taken together, although receiving
+considerable support from theories of phono-lexical processing in
+language acquisition, there is very little evidence for a role of
+vocabulary size in mispronunciation sensitivity. In our current
+meta-analysis, we include the relationship between mispronunciation
+sensitivity and vocabulary size to further disentangle the disconnect
+between theory and experimental results.
+
+Next to this core theoretically relevant investigation of the shape of
+development of infants' mispronunciation sensitivity, we take the
+opportunity of a systematic aggregation of data to address open
+questions regarding differences in experiment design and whether changes
+in procedure and stimuli tap into significantly different aspects of
+infants' ability to detect mispronunciations.
+
+In designing their mispronunciation stimuli, Swingley and Aslin (2000)
+chose consonant mispronunciations that were likely to confuse adults
+(Miller \& Nicely, 1955). Subsequent research has settled on
+systematically modulating phonemic features to achieve mispronunciations
+of familiar words. By utilizing mispronunciations consisting of phonemic
+changes, these experiments examine infants' sensitivity to factors that
+change the identity of a word on a measurable level (i.e.~1-feature,
+2-features, 3-features, etc.). The importance of controlling for the
+degree of phonological mismatch, as measured by number of features
+changed, is further highlighted by studies that find graded sensitivity
+to both consonant (White \& Morgan, 2008) and vowel (Mani \& Plunkett,
+2011) feature changes.
+
+Although most research examining sensitivity to mispronunciations
+follows a similar design, there are some notable differences. For
+example, Swingley and Aslin (2000) presented infants with pairs of
+familiar images, one serving as the labeled target and one as the
+unlabeled distractor. In contrast, White and Morgan (2008; see also Mani
+\& Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented
+infants with pairs of familiar (labeled target) and unfamiliar
+(unlabeled distractor) objects. By using an unfamiliar object as a
+distractor, the infant is presented with a viable option onto which the
+mispronounced label can be applied (Halberda, 2003; Markman, Wasow, \&
+Hansen, 2003). Infants ages 24 and 30 months associate a novel label
+with an unfamiliar object, although only 30-month-olds retained this
+label-object pairing (Bion, Borovsky, and Fernald, 2013). In contrast,
+18-month-olds did not learn to associate a novel label with an
+unfamiliar object, providing evidence that this ability is developing
+from 18 to 30 months. We may find that if mispronunciation sensitivity
+changes as children develop, that this change is modulated by whether
+the distractor used is familiar or unfamiliar. Although mispronunciation
+sensitivity in the presence of a familiar compared to unfamiliar
+distractor has not been directly compared, the baseline preference for
+familiar compared to novel stimuli is also thought to change as infants
+develop (Hunter \& Ames, 1988). Furthermore, young children have been
+found to look longer at objects for which they know the name, compared
+to objects of an unknown name (Schafer \& Plukett, 1998). In other
+words, in absentia of a label, infants may be more or less likely to
+fixate on an unfamiliar object. To account for inherent preferences to
+the target or distractor image, mispronunciation experiments typically
+compare the increase in fixations to the target image from a silent
+baseline to post-labeling or present the same yoked pairs of target and
+distractor images in in both a correct and mispronounced labelling
+context. Considering this evidence, we may expect that in older, but not
+younger, children, the presence of an unfamiliar distractor may lead to
+greater mispronunciation sensitivity than in the presence of a familiar
+distractor.
+
+Furthermore, when presenting infants with a familiar distractor image,
+some studies control the phonological overlap between the labels for the
+target and distractor. For example, when examining sensitivity to a
+mispronunciation of the target word \enquote{dog}, the vowel
+mispronunciation \enquote{dag} would be paired with a distractor image
+that shares onset overlap, such as \enquote{duck}. This ensures that
+infants can not use the onset of the word to differentiate between the
+target and distractor images (Fernald, Swingley, \& Pinto, 2001).
+Instead, infants must pay attention to the mispronounced phoneme in
+order to successfully detect the change. The influence of distractor
+overlap also depends on the position of the mispronunciation in the
+word, which can be at word onset, medial, or final positions. Models of
+spoken word processing place more or less importance on the position of
+a phoneme in a word. The COHORT model (Marslen-Wilson \& Zwitserlood,
+1989) describes lexical access in one direction, with the importance of
+each phoneme decreasing as its position comes later in the word. In
+contrast, the TRACE model (McClelland \& Elman, 1986) describes lexical
+access as constantly updating and reevaluating the incoming speech input
+in the search for the correct lexical entry, and therefore can recover
+from word onset and to a lesser extent medial mispronunciations.
+
+TRACE has also been used to model infants' sensitivity to
+mispronunciation location (Mayor \& Plunkett, 2014), finding that as
+lexicon size increases, so does sensitivity to onset mispronunciations,
+whereas medial mispronunciations do not experience similar growth. In
+early language acquisition, infants typically know more consonant
+compared to vowel onset words. When tested on their recognition of
+familiar words, therefore, younger infants would show greater
+sensitivity to onset mispronunciations, which are frequently consonant
+mispronunciations. The prevalence of consonant onset words may
+contribute to the finding that consonants carry more weight in lexical
+processing (C-bias; see Nazzi, Poltrock, \& Von Holzen, 2016 for a
+recent review). In mispronunciation sensitivity, this would translate to
+consonant mispronunciations impairing word recognition to a greater
+degree than vowel mispronunciations. Yet, the handful of studies
+directly comparing sensitivity to consonant and vowel mispronunciations
+mostly find symmetry as opposed to an asymmetry between consonants and
+vowels. English-learning 12-, 15-, 18-, and 24-month-olds (Mani \&
+Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds
+(Hojen et al., unpublished) demonstrate similar sensitivity to consonant
+and vowel mispronunciations. One study did find weak evidence for
+greater sensitivity to consonant compared to vowel mispronunciations
+(Swingley, 2016). The English-learning infants tested by Swingley were
+older than previous studies (mean age 28 months). In word learning, the
+C-bias has been found to develop later in English learning infants
+(Floccia, Nazzi, Delle Luche, Poltrock, \& Goslin, 2014; Nazzi, Floccia,
+Moquet, \& Butler, 2009). In the current meta-analysis, we attempt to
+synthesize studies examining sensitivity to consonant and vowel
+mispronunciations across different ages to determine whether infants
+generally exhibit more sensitivity to consonant compared to vowel
+mispronunciations in familiar word recognition as predicted by a learned
+account of C-bias emergence (Floccia et al., 2014; Keidel et al., 2007;
+Nazzi et al., 2016). We further examine the impact of language family on
+mispronunciation sensitivity to consonants and vowels, as C-bias
+emergence has been found to have a different developmental trajectory
+for Romance (French, Italian) compared to Germanic (British English,
+Danish) languages (Nazzi et al., 2016).
+
+{[}KATIE{]} Christina had noted something to herself for this paragraph:
+Subset by language?
+
+Finally, mispronunciation sensitivity in infants has been examined in
+many different languages, such as English, Spanish, French, Dutch,
+German, Catalan, Danish, and Mandarin Chinese (see Summary\_Table).
+Infants learning different languages have different ages of acquisition
+for words in their early lexicon, leaving direct comparisons between
+languages within the same study difficult and as a result rare. Yet,
+studies testing infants from different language backgrounds on similar
+sets of stimuli find similar sensitivity to mispronunciations
+(Ramon-Casas et al., 2009; Ramon-Casas \& Bosch, 2010). Although we do
+not explicitly compare overall mispronunciation sensitivity by language
+(although see previous paragraph for rationale to test by language
+family), we assess evidence of mispronunciation sensitivity from many
+different languages using a meta-analytic approach.
+
+Taken together, the studies we have reviewed begin to paint a picture of
+the development of mispronunciation sensitivity. Each study contributes
+one separate brushstroke and it is only by examining all of them
+together that we can achieve a better understanding. In our analysis, we
+examine the factors modulating the development of mispronunciation
+sensitivity, which are both of theoretical and practical importance.
+Meta-analyses can not only help us summarize the current state of
+research, but can also help us evaluate theories to drive future
+research and make hands-on recommendations for experiment planning.
+
+\section{Methods}\label{methods}
+
+The present meta-analysis was conducted with maximal transparency and
+reproducibility in mind. To this end, we provide all data and analysis
+scripts on the supplementary website (\url{https://osf.io/rvbjs/}) and
+open our meta-analysis up for updates (Tsuji, Bergmann, \& Cristia,
+2014). The most recent version is available via the website and the
+interactive platform MetaLab (metalab.stanford.edu; Bergmann et al.,
+2018). Since the present paper was written with embedded analysis
+scripts in R {[}@R{]}, it is always possible to re-analyze an updated
+dataset. In addition, we follow the Preferred Reporting Items for
+Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the
+corresponding information available as supplementary materials (Moher,
+Liberati, Tetzlaff, Altman \& PRISMAGroup, 2009). Figure X plots our
+PRISMA flowchart.
+
+{[}Figure X. PRISMA Flowchart.{]}
+(figures/PRISMA\_MA\_Mispronunciation.png)
+
+\subsection{Study Selection}\label{study-selection}
+
+\begin{tabular}{l|l|l|l|l|l|l|l}
+\hline
+Paper & Age & Vocabulary & \# Features & Distractor & Distractor name overlap & MP Position & MP Type\\
+\hline
+Altvater-Mackensen (2010) & 22, 25 & None & 1 & Familiar, Unfamiliar & onset, novel & onset, onset/medial & consonant\\
+\hline
+Altvater-Mackensen et al. (2014) & 18, 25 & None & 0, 1 & Familiar & onset & onset & consonant\\
+\hline
+Bailey \& Plunkett (2002) & 18, 24 & Comprehension & 0, 1, 2 & Familiar & no & onset & consonant\\
+\hline
+Bergelson \& Swingley (2017) & 7, 9, 12, 6 & None & 0, NA & Familiar & no & onset/medial & vowel\\
+\hline
+Bernier \& White 2017 & 21 & None & 0, 1, 2, 3 & Unfamiliar & novel & onset & consonant\\
+\hline
+Delle Luche et al. (2015) & 20, 19 & None & 0, 1 & Familiar & onset & onset & consonant\_and\_vowel\\
+\hline
+Durrant et al. (2014) & 19, 20 & None & 0, 1 & Familiar & onset & onset & consonant\_and\_vowel\\
+\hline
+Hoehle et al. 2006 & 18 & None & 1 & Familiar & no & onset & consonant\\
+\hline
+Hojen et al. & 20 & Comprehension/Production & 2\_3 & Familiar & coda, onset & onset/medial, coda/medial & consonant\_and\_vowel, vowel, consonant\\
+\hline
+Mani \& Plunkett 2007 & 15, 18, 24, 14, 21 & Comprehension/Production & 0, 1\_2, 1 & Familiar & onset & onset & vowel, consonant\_and\_vowel, consonant\\
+\hline
+Mani \& Plunkett 2010 & 12 & Comprehension & 0, 1 & Familiar & onset & medial, onset & vowel, consonant\\
+\hline
+Mani \& Plunkett 2011 & 23, 17 & None & 0, 1\_2\_3, 1, 2, 3 & Unfamiliar & novel & medial & vowel\\
+\hline
+Mani, Coleman, \& Plunkett (2008) & 18 & Comprehension/Production & 0, 1 & Familiar & onset & medial & vowel\\
+\hline
+Ramon-Casas \& Bosch 2010 & 24, 25 & None & NA & Familiar & no & medial & vowel\\
+\hline
+Ramon-Casas et al. 2009 & 21, 20 & Production & NA & Familiar & no & medial & vowel\\
+\hline
+Ren \& Morgan, in press & 19 & None & 0, 1 & Unfamiliar & no & onset, coda & consonant\\
+\hline
+Skoruppa et al. 2013 & 24 & None & 0, 1 & Unfamiliar & onset/medial & coda & consonant\\
+\hline
+Swingley (2009) & 17 & Comprehension/Production & 0, 1 & Familiar & no & onset, coda & consonant\\
+\hline
+Swingley (2016) & 27, 28 & Production & 0, 1 & Unfamiliar & novel & onset/medial & consonant\_and\_vowel, consonant, vowel\\
+\hline
+Swingley \& Aslin (2000) & 20 & Comprehension & 0, 1 & Familiar & no & onset & consonant\_and\_vowel\\
+\hline
+Swingley \& Aslin (2002) & 15 & Comprehension/Production & 0, 1, 2 & Familiar & no & onset/medial & consonant\_and\_vowel\\
+\hline
+Swingley 2003 & 19 & Comprehension/Production & 0, 1 & Familiar & onset & onset, medial & consonant\\
+\hline
+Tamasi (2016) & 30 & None & 0, 1, 2, 3 & Unfamiliar & novel & onset & consonant\\
+\hline
+Tao \& Qinmei 2013 & 12 & None & NA & Familiar & no & NA & tone\\
+\hline
+Tao et al. 2012 & 16 & Comprehension & NA & Familiar & no & NA & tone\\
+\hline
+van der Feest \& Fikkert, 2015 & 24, 20 & None & 0, 1 & Familiar & onset & onset & consonant\\
+\hline
+van der Feest \& Johnson, 2016 & 24 & None & 0, 1 & Familiar & onset & onset & consonant\\
+\hline
+Wewalaarachchi et al. 2017 & 24 & None & 0, 1 & Unfamiliar & novel & onset/medial/coda & consonant\_vowel\_tone, vowel, consonant, tone\\
+\hline
+White \& Aslin (2011) & 18 & None & 1 & Unfamiliar & novel & medial & vowel\\
+\hline
+White \& Morgan (2008) & 18, 19 & None & 0, 1, 2, 3 & Unfamiliar & novel & onset & consonant\\
+\hline
+Zesiger \& Johr 2011 & 14 & None & 0, 1 & Familiar & no & onset, medial & consonant, vowel\\
+\hline
+Zesiger et al. (2012) & 12, 19 & Comprehension/Production & 0, 1, 2 & Familiar & no & onset & consonant\\
+\hline
+\end{tabular}
+
+{[}KATIE{]} THIS TABLE IS DEFINITELY NOT FINISHED! {[}CHRISTINA
+suggestions: N features should be a range and exclude 0; we could
+abbreviate Comperehension/Production to Comp./Prod.,
+etcetc{]}{[}KATIE{]} I'll think about how to implement that! Might end
+up having to adjust the table by hand, there is a lot of variation
+between studies.
+
+We first generated a list of potentially relevant items to be included
+in our meta-analysis by creating an expert list. This process yielded
+110 items. We then used the google scholar search engine to search for
+papers citing the original Swingley \& Aslin (2000) publication. This
+search was conducted on 22 September, 2017 and yielded 288 results. We
+screened the 398 items, removing 99 duplicate items. We screened
+remaining 299 items for their title and abstract to determine whether it
+met the following inclusion criteria: (1) original data was reported;
+(2) the experiment examined familiar word recognition; (3) infants
+studied were under 36-months-of-age; (4) the dependent variable was
+derived from proportion of looks to a target image versus a distractor
+in a eye movement experiment; 5) the stimuli were auditory speech. The
+final sample (n = \emph{32}) consisted of 27 journal articles, 1
+proceedings paper, 2 thesis, and 2 unpublished reports. We will refer to
+these items collectively as papers. Table 1 (Summary Table) provides an
+overview of all papers included in the present meta-analysis.
+
+\begin{tabular}{l|r|r}
+\hline
+Publication Type & \# Items & \# Effect Sizes\\
+\hline
+dissertation & 2 & 17\\
+\hline
+gray paper & 2 & 14\\
+\hline
+paper & 27 & 216\\
+\hline
+proceedings & 1 & 4\\
+\hline
+\end{tabular}
+
+\subsection{Data Entry}\label{data-entry}
+
+The 32 papers we identified as relevant were then coded with as much
+detail as possible (Tsuji, Bergmann, \& Cristia, 2014; Bergmann et al.,
+2018). For each experiment (note that a paper typically has multiple
+experiments), we entered variables describing the publication,
+population, experiment design and stimuli, and results. For the present
+analyses, we focus on the following characteristics:\\
+1 Condition: Were words mispronounced or not;\\
+2 Mean age reported per group of infants, in days;\\
+3 Vocabulary size, measured by a standardized questionnaire or list;\\
+4 Size of mispronunciation, measured in features changed;\\
+5 Distractor familiarity: familiar or unfamiliar;\\
+6 Phonological overlap between target and distractor: onset,
+onset/medial, rhyme, none, novel word;\\
+7 Position of mispronunciation: onset, medial, offset, or mixed;\\
 8 Type of mispronunciation: consonant, vowel, or both.
 
-We separated out conditions according to whether or not the target word was mispronounced to be able to investigate infants' looking to the target picture separated by whether or not words were mispronounced as well as their mispronunciation sensitivity, which is the difference between looks to the target in correct and mispronounced trials.
-When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  (e.g., consonant versus vowel mispronunciations; Mani & Plunkett, 2007).
-The fact that the same infants contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section).
-We will call each row a record; in total there were `r nrow(dat)` records in our data.
-
-## Data analysis
-
-```{r DescriptivesComparison, echo = FALSE}
-db_ET_correct$within_measure_descriptive <- ifelse(db_ET_correct$within_measure == "post",
- "post-naming phase compared with chance (=50%)",
-ifelse(db_ET_correct$within_measure == "pre_post", "post-naming compared to pre-naming phase", "post-pre difference score compared with chance (=0)"))
-
-comparison_info <- db_ET_correct %>%
-  group_by(within_measure_descriptive) %>%
-  summarize(n_unique = n_distinct(short_cite), count = n())
-
-kable(comparison_info, col.names = c("Type of comparison", "# Papers", "# Effect Size"))
-#table(db_ET_MP$es_method)
-```
-
-```{r DescriptivesES}
-#how did we calculate effect sizes?
-
-es_info <- dat %>%
-  group_by(es_method) %>%
-  summarize(n_unique = n_distinct(short_cite), count = n())
-
-#kable(es_info)
-#table(dat$es_method, dat$short_cite)
-# only missing from:
-# Bailey & Plunkett (2002) <- crazy old data
-# Renner (2017) <- just finished phd
-#table(db_ET_MP$es_method)
-
-#[KATIE] Can you also rename the factors here (like t_one)?
-#[CHRISTINA] Mpt sire what you man, like in the table? You rename things later on, so why not.
-#[KATIE] Actually, do we really need this table? When everything is summarized in the text, is that good enough?
-
-corr_info <- dat %>%
-  group_by(imputed_corr) %>%
-  summarize(n_unique = n_distinct(short_cite), count = n())
-
-```
-
-Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to a baseline measurement.
-PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images.
-Across papers the baseline comparison varied; we used the baseline reported by the authors of each paper.
-Most papers (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post_naming_effect"]))`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase.
-When interpreting this difference score, a positive value indicates that infants increased their looks to the target after hearing the naming label (correct or mispronounced).
-Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post"]))`) or compared post-naming PTL with a chance level of 50%, (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "post"]))`).
-For all these comparisons, a positive difference score or a post-naming phase PTL score that is greater than the pre-naming phase PTL or chance indicate target looks that indicate object recognition after hearing the naming label.
-Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more relative increase in looks to the target.
-
-We report effect sizes for infants' looks to target pictures after hearing a correctly pronounced or a mispronounced label (object identification) as well as the difference between effect sizes for correct and mispronounced trials (i.e.
-mispronunciation sensitivity).
-The effect size we report in the present paper are based on comparison of means, standardized by their variance.
-The most well-known effect size from this group is Cohen's *d* [@cohen].
-To correct for the small sample sizes common in infant research, however, we use as a dependent variable Hedges' *g* instead of Cohen's *d* (Hedges, 1981; Morris, 2000).
-
-We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(dat, n_distinct(short_cite[es_method == "group_means_one" | es_method == "group_means_two"]))`) or using reported t-values (*n* = `r with(dat, n_distinct(short_cite[es_method == "t_one" | es_method == "t_two"]))`).
-Raw means and standard deviations were extracted from figures for `r with(dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers.
-In a within-participation design, when two means are compared (i.e.
-looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values.
-Upon request we were provided with correlation values for one paper (Altvater-Mackensen, 2010); we were able to compute correlations using means, standard deviations, and t-values for *n* = `r with(corr_info, n_unique[imputed_corr == "no"]) - 1` (following Csibra, et al.
-2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, 2018).
-Correlations were imputed for the remaining papers (see Black & Bergmann, 2017, for the same procedure).
-We could compute a total of `r sum(dat$is_mp == 0)` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)` for mispronunciations.
-
-To take into account the fact that the same infants contributed to multiple datapoints, we analyze our results in a multilevel approach using the R [@R] package metafor [@metafor].
-This means we model as random effect that effect sizes from the same paper share are based on more similar studies than those across papers and that nested therein effects can stem from the same infants.
-
-## Publication Bias
-
-[CHRISTINA: Do you think we have to revise this section? I think it's the same as in the proceedings paper.]
-[KATIE: Are you concerned about the Publication Bias section in particular, or the Methods as a whole?
-In general, some of the Methods was written before the CogSci paper and in other places to flesh things out I rewrote what we had.
-Its definitely giving the same information and sometimes the wording is close, because there's not too many different ways to explain what a funnel plot is :)]
-
-In the psychological sciences, there is a documented reluctance to publish null results.
-As a result, there is a potential for significant results to be valued over non-significant results (see Ferguson & Heene, 2012).
-To examine whether this is also the case in the mispronunciation sensitivity literature, which would bias the data analyzed in this meta-analysis, we conduct two tests.
-We first examine whether effect sizes are distributed as expected based on sampling error using the rank correlation test of funnel plot asymmetry with the R [@R] package metafor [@metafor].
-Effect sizes with low-variance are expected to fall closer to the estimated mean, while effect sizes with high-variance should show an increased, evenly-distributed spread around the estimated mean.
-Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app (v4.0, p-curve.com; @pcurve).
-This tests for evidential value by examining whether the p-values have an expected distribution, regardless of whether the null hypothesis is true or not, as well as whether there is a larger proportion of p-values just below the typical alpha threshold of .05, which may indicate questionable research practices.
-Responses to correctly pronounced and mispronounced labels are predicted to show different patterns of looking behavior; as a result, we conduct these two analyses to assess publication bias separately for both conditions.
-
-## Meta-analysis
-
-The models reported are hierarchical random-effects models (infant groups nested within papers) of variance-weighted effect sizes with the R [@R] package metafor [@metafor].
-To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we introduce age (centered; continuous and measured in days but transformed into months for ease of reading by dividing by 30.44) as a moderator to our main model.
-For the subsequent investigations of experimental characteristics, we introduce each characteristic as a moderator (more detail below).
-
-[CHRISTINA: Let's both reread the full paper once it is ready and check that this is properly motivated and whether we do need to list them all.
-For now I think the last sentence is fine, but I would tend to prefer a reminder for the forgetful reader.]
-[KATIE: that's reasonable! We had just listed everything 7 paragraphs before, which doesn't seem like a lot of "space".]
-
-# Results
-
-## Publication Bias
-
-```{r FunnelPlotAsymm_correct}
-
-rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ collapse | short_cite)
-# Publication bias can become visible in funnel plot asymmetry. 
-# Metafor comes with several options to check this, I chose ranktest and regtest
-# correct object identification
-rmac <- ranktest(rma_correct)
-#rmac
-
-```
-
-```{r FunnelPlotAsymm_misp}
-
-rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ collapse | short_cite)
-
-# mispronounced object identification
-rmam <- ranktest(rma_MP)
-#rmam
-```
-
-Figure 1 shows the funnel plots for both correct pronunciations and mispronunciations (code adapted from Sakaluk, 2016).
-Funnel plot assymmetry was significant for both correct pronunciations (Kendall's $\tau$ = `r r2(rmac$tau)`, *p* `r psig(rmac$pval)`) and mispronunciations (Kendall's $\tau$ = `r r2(rmam$tau)`, *p* `r psig(rmam$pval)`).
-These results, quantifying the assymmetry in the funnel plots (Figure 1), indicate bias in the literature.
-This is particularly evident for correct pronunciations, where larger effect sizes have greater variance (bottom right corner) and there are a smaller number of more precise effect sizes (i.e.
-smaller variance) than expected (top left, outside the triangle).
-
-[CHRISTINA: If we want to interpret here, how about the next bit.]
-[KATIE: YES! This is an excellent point!!!]
-
-The stronger publication bias for correct pronunciation might reflect the status of this condiction as a control.
-If infants were not looking to the target picture after hearing the correct label, the overall experiment design is called into questions.
-However, due to the small effect and sample sizes (which we will discuss in the following sections in more detail) one would expect the regular occurrence of null results even though as a population infants would reliably show the expected object identification effect.
-
-We should also point out that funnel plot asymmetry can be caused by multiple factors beside publication bias.
-The funnel plot asymmetry may also reflect heterogeneity in the data, perhaps due to some studies investigating more subtle effects than other studies.
-[CHRISTINA: I have to add some bits here.]
-
-```{r FunnelPrep}
-### Plots adapted from Sakaluk, 2016, see also Black & Bergmann, 2017
-### https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/
-
-#Themes and plot
-funnel_theme=theme_bw()+
-  theme(#panel.grid.major=element_blank(),
-    #panel.grid.minor=element_blank(),
-    #panel.border=element_blank(),
-    axis.line=element_line(),
-    text=element_text(family='Times', size=22),
-    legend.position='none')
-
-```
-
-```{r FunnelCorrect}
-
-#Rename a bunch of things for ease
-dat_co = db_ET_correct %>% 
-  rename(cite = short_cite,
-         yi = g_calc,
-         vi = g_var_calc) %>%
-  mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
-  dplyr::select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>%
-  arrange(desc(yi))
-
-#Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order
-
-#Get standard errors from variances
-dat_co$se = sqrt(dat_co$vi)
-
-#Calculate 95% CI values
-dat_co$lowerci = (-1.96*dat_co$se)+dat_co$yi
-dat_co$upperci = (1.96*dat_co$se)+dat_co$yi
-
-#Store the meta-analytic estimate and its standard error from whatever model you run
-#summary(rma_correct)
-estimate_co = coef(summary(rma_correct))$estimate
-se_co = coef(summary(rma_correct))$se
-
-#Store a vector of values that spans the range from 0
-#to the max value of impression (standard error) in your dataset.
-#Make the increment (the final value) small enough (I choose 0.001)
-#to ensure your whole range of data is captured
-se.seq_co=seq(0, max(dat_co$se), 0.001)
-
-#Now, compute vectors of the lower-limit and upper limit values for
-#the 95% CI region, using the range of SE that you generated in the previous step, 
-#and the stored value of your meta-analytic estimate.
-ll95_co = estimate_co-(1.96*se.seq_co)
-ul95_co = estimate_co+(1.96*se.seq_co)
-
-#You can do this for a 99% CI region too
-ll99_co = estimate_co-(3.29*se.seq_co)
-ul99_co = estimate_co+(3.29*se.seq_co)
-
-#And finally, do the same thing except now calculating the confidence interval
-#for your meta-analytic estimate based on the stored value of its standard error
-meanll95_co = estimate_co-(1.96*se_co)
-meanul95_co = estimate_co+(1.96*se_co)
-
-#Now, smash all of those calculated values into one data frame (called 'dfCI').
-#You might get a warning about '...row names were found from a short variable...'
-#You can ignore it.
-dfCI_co = data.frame(ll95_co, ul95_co, ll99_co,
-                  ul99_co, se.seq_co, estimate_co, meanll95_co, meanul95_co)
-
-#Now we can actually make the funnel plot.
-#Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
-fp_co = ggplot(aes(x = se, y = yi), data = dat_co) +
-  #Regression line for the FP asymmetry
-  geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_co) +
-  #Add your data-points to the scatterplot
-  geom_point(size = 2.5, colour="black") +
-  #
-  #Give the x- and y- axes informative labels
-  xlab('Standard Error') + ylab('Hedge\'s g')+
-  # give it a title
-    ggtitle("Correct") +
-    # make sure both plots have same scale
-    # still ylim because we haven't flipped yet
-    #coord_cartesian(ylim = c(0.5, 0))+
-  #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
-  #to the lower and upper limits of your 95% CI region
-  #And dashed lines corresponding to your 99% CI region
-  #Add lines corresponding to 0 and estimate
-  geom_line(aes(x = se.seq_co, y = 0), linetype = 'solid', data = dfCI_co) +
-  geom_line(aes(x = se.seq_co, y = estimate_co), linetype = 'dashed', data = dfCI_co) +
-  geom_line(aes(x = se.seq_co, y = ll95_co), linetype = 'dotted', data = dfCI_co) +
-  geom_line(aes(x = se.seq_co, y = ul95_co), linetype = 'dotted', data = dfCI_co) +
-  #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
-  #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
-  #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
-  #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
-  #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
-  #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
-  #at the top of the figure once we swap the x- and y-axes...
-  scale_x_reverse()+
-  #Specify the range and interval for the tick-marks of the y-axis (Zr);
-  #Choose values that work for you based on your data
-  #scale_y_continuous(breaks=seq(-.45,0.8,0.25))+
-  #And now we flip the axes so that SE is on y- and Zr is on x-
-  coord_flip()+
-  #Finally, apply my APA-format theme (see code at end of post).
-  #You could, alternatively, specify theme_bw() instead.
-  funnel_theme
-
-#Call the pretty funnel plot
-#fp_co
-#ggsave("figures/FunnelPlot_correct.pdf")
-
-```
-
-```{r FunnelMisp}
-
-  #Rename a bunch of things for ease
-dat_mp = db_ET_MP %>%
-    rename(cite = short_cite,
-           yi = g_calc,
-           vi = g_var_calc) %>%
-    dplyr::select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>% 
-    mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
-    arrange(desc(yi))
-
-  #Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order
-
-  #Get standard errors from variances
-  dat_mp$se = sqrt(dat_mp$vi)
-
-  #Calculate 95% CI values
-  dat_mp$lowerci = (-1.96*dat_mp$se)+dat_mp$yi
-  dat_mp$upperci = (1.96*dat_mp$se)+dat_mp$yi
-
-  #Store the meta-analytic estimate and its standard error from whatever model you run (substitute your own values)
-  #summary(rma_MP)
-  estimate_mp = coef(summary(rma_MP))$estimate
-  se_mp = coef(summary(rma_MP))$se
-
-  #Store a vector of values that spans the range from 0
-  #to the max value of impression (standard error) in your dataset.
-  #Make the increment (the final value) small enough (I choose 0.001)
-  #to ensure your whole range of data is captured
-  se.seq_mp=seq(0, max(dat_mp$se), 0.001)
-
-  #Now, compute vectors of the lower-limit and upper limit values for
-  #the 95% CI region, using the range of SE that you generated in the previous step, 
-  #and the stored value of your meta-analytic estimate.
-  ll95_mp = estimate_mp-(1.96*se.seq_mp)
-  ul95_mp = estimate_mp+(1.96*se.seq_mp)
-
-  #You can do this for a 99% CI region too
-  ll99_mp = estimate_mp-(3.29*se.seq_mp)
-  ul99_mp = estimate_mp+(3.29*se.seq_mp)
-
-  #And finally, do the same thing except now calculating the confidence interval
-  #for your meta-analytic estimate based on the stored value of its standard error
-  meanll95_mp = estimate_mp-(1.96*se_mp)
-  meanul95_mp = estimate_mp+(1.96*se_mp)
-
-  #Now, smash all of those calculated values into one data frame (called 'dfCI').
-  #You might get a warning about '...row names were found from a short variable...'
-  #You can ignore it.
-  dfCI_mp = data.frame(ll95_mp, ul95_mp, ll99_mp,
-                       ul99_mp, se.seq_mp, estimate_mp, meanll95_mp, meanul95_mp)
-
-  #Now we can actually make the funnel plot.
-  #Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
-  fp_mp = ggplot(aes(x = se, y = yi), data = dat_mp) +
-    #Regression line for the FP asymmetry
-    geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_mp) +
-    #Add your data-points to the scatterplot
-    geom_point(size = 2.5, colour="black") +
-    #
-  #Give the x- and y- axes informative labels
-  xlab('Standard Error') + 
-    # remove y label because it will be combined with the other funnel plot
-    ylab('Hedge\'s g')+
-    # give it a title
-    ggtitle("Mispronunciation") +
-    # make sure both plots have same scale
-    # still xlim because we haven't flipped yet
-    #coord_cartesian(xlim = c(0.5, 1))+
-    #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
-    #to the lower and upper limits of your 95% CI region
-    #And dashed lines corresponding to your 99% CI region
-    #Add lines corresponding to 0 and estimate
-    geom_line(aes(x = se.seq_mp, y = 0), linetype = 'solid', data = dfCI_mp) +
-    geom_line(aes(x = se.seq_mp, y = estimate_mp), linetype = 'dashed', data = dfCI_mp) +
-    geom_line(aes(x = se.seq_mp, y = ll95_mp), linetype = 'dotted', data = dfCI_mp) +
-    geom_line(aes(x = se.seq_mp, y = ul95_mp), linetype = 'dotted', data = dfCI_mp) +
-    #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
-    #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
-    #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
-    #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
-    #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
-    #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
-    #at the top of the figure once we swap the x- and y-axes...
-    scale_x_reverse()+
-    #Specify the range and interval for the tick-marks of the y-axis (Zr);
-    #Choose values that work for you based on your data
-    #scale_y_mpntinuous(breaks=seq(-.45,0.8,0.25))+
-    #And now we flip the axes so that SE is on y- and Zr is on x-
-    coord_flip()+
-    #Finally, apply my APA-format theme (see previous).
-    #You could, alternatively, specify theme_bw() instead.
-    funnel_theme +
-    theme(axis.title.y = element_blank())
-
-  #Call the pretty funnel plot
-  #fp_mp
-#  ggsave("figures/FunnelPlot_misp.pdf")
-
-```
-
-## Figure 1
-
-```{r FunnelCombo}
-
-  jpeg(filename = "figures/Figure_1_Funnel_Plots_Object_Identification.jpg", 
-       width = 600, height = 400, units = "px")
-
-  p <-   grid.arrange(fp_co, fp_mp, nrow = 1)
-                      #top = textGrob("Object Identification", gp=gpar(fontsize=25)))
-                      #top = "Figure 1. Funnel Plots")
-  dev.off()
-
-    grid.draw(p)
-
-```
-
-```{r PcurveExport}
-
-textfile_co = "p_curve_app/p_curve_co.txt"
-
-# make sure the file is made new with our loop
-if (file.exists(textfile_co)) {file.remove(textfile_co)}
-
-for(line in 1:length(db_ET_correct$n_1)){
-  if(!is.na(db_ET_correct[line,]$t)){
-    newline = paste("t(", db_ET_correct[line,]$n_1-1, ")=",db_ET_correct[line,]$t, sep = "")
-    write(newline, file = textfile_co, append = TRUE)
-    #cat("\n")
-    #write(newline, file = textfile, append = TRUE)    
-  }
-}
-
-textfile_mp = "p_curve_app/p_curve_mp.txt"
-
-# make sure the file is made new with our loop
-if (file.exists(textfile_mp)) {file.remove(textfile_mp)}
-
-for(line in 1:length(db_ET_MP$n_1)){
-  if(!is.na(db_ET_MP[line,]$t)){
-    newline = paste("t(", db_ET_MP[line,]$n_1-1, ")=",db_ET_MP[line,]$t, sep = "")
-    write(newline, file = textfile_mp, append = TRUE)
-    #cat("\n")
-    #write(newline, file = textfile, append = TRUE)    
-  }
-}
-
-```
-
-```{r ReadIn_pcurve_app,  echo = FALSE, error = FALSE}
-
-#Get the effect size data
-source("scripts/p_curve_app_code.R")
-
-# this gives the number of significant results
-# the Z value
-# and the significance
-pcd_correct <- pcurve_app("p_curve_co.txt", "p_curve_app")
-```
-
-```{r ReadIn_pcurve_app_2,  echo = FALSE, error = FALSE}
-pcd_misp <- pcurve_app("p_curve_mp.txt", "p_curve_app")
-
-```
-
-We next examined the p-curves for significant values from the correctly pronounced and mispronounced conditions.
-The p-curve based on `r pcd_correct$ksig` statistically significant values for correct pronunciations indicates that the data contain evidential value (Z = `r r2(pcd_correct$Zppr)`, *p* `r psig(pcd_correct$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05.
-The p-curve based on `r pcd_misp$ksig` statistically significant values for mispronunciations indicates that the data contain evidential value (Z = `r r2(pcd_misp$Zppr)`, *p* `r psig(pcd_misp$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05.
-
-[CHRISTINA: CAn you add the stats for the non-sig results?]
-[KATIE: Are there stats that can be computed on the non-sig results? Or do you just want an n for significant and non-significant studies?]
-
-Taken together, the results suggest a tendency in the literature towards publication bias.
-As a result, our meta-analysis may systematically overestimate effect sizes and we therefore interpret all estimates with caution.
-Yet, the p-curve analysis suggests that overall, the literature contains evidential value, reflecting a "real" effect.
-We therefore continue our meta-analysis.
-
-## Meta-analysis
-
-### Object Identification for Correct and Mispronounced Words
-
-```{r MAcorrect}
-
-rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ collapse | short_cite)
-
-#summary(rma_correct)
-#kable(round(coef(summary(rma_correct)), 2))
-
-sum_eff <- coef(summary(rma_correct))[1,]
-
-```
-
-We first calculated the meta-analytic effect for object identification, i.e.
-looks to the target image in response to correctly pronounced words.
-The variance-weighted meta-analytic effect size Hedges' *g* was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
-This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research).
-That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object.
-Our analysis of funnel plot asymmetry, however, found evidence for publication bias, which might lead to an overestimated effect sizes as smaller, non-significant results might not be published.
-Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` suggests that this result is robust even when correcting for publication bias.
-In other words, we are confident that the true population mean lies above zero for object recognition of correctly pronounced words.
-
-[CHRISTINA: Can you explain what the CI lower bound means here? I don't follow.]
-[KATIE: What do you think about this? The CI lower bound stuff here actually comes from something you wrote, so tell me whether its correct.]
-
-```{r MAMP}
-
-rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ collapse | short_cite)
-
-#summary(rma_MP)
-
-sum_eff <- coef(summary(rma_MP))[1,]
-
-```
-
-We then calculated the meta-analytic effect for object identification in response to mispronounced words.
-In this case, the variance-weighted meta-analytic effect size Hedges' *g* was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was also significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
-This is considered a small effect size (Cohen, 1988), but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object.
-In other words, infants are able to resolve mispronunciations, a key skill in language processing We again note the publication bias (which was smaller in this condition), and the possibility that the effect size Hedges' *g* may be overestimated.
-But, as the p-curve indicated evidential value, we are confident in the overall patterns, namely that infants fixate the target even after hearing a mispronounced label.
-
-Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, *p* `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, *p* `r psig(rma_MP$QEp)`).
-This indicated that the sample contains unexplained variance leading to significant difference across our studies beyond what is to be expected based on random sampling error.
-We therefore continue with our moderator analysis.
-
-### Mispronunciation Sensitivity Meta-analytic Effect
-
-```{r MPEffect}
-
-rma_MPeffect <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = ~ collapse | short_cite)
-
-#summary(rma_MPeffect)
-
-#rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ collapse | short_cite)
-
-#summary(rma_MPeffect_1)
-
-sum_eff <- coef(summary(rma_MPeffect))[2,]
-
-```
-
-The above two analyses considered the data from mispronounced and correctly pronounced words separately.
-To evaluate mispronunciation sensitivity, we  compared the effect size Hedges' *g* for correct pronunciations with mispronunciations directly, merging the two datasets.
-The moderator test was significant, QM(`r r2(rma_MPeffect$m)`) = `r r2(rma_MPeffect$QM)`, *p* `r psig(rma_MPeffect$QMp)`.
-Hedges' *g* for mispronunciation sensitivity was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that the responses across conditions were significantly different (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
-This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations.
-In other words, we observe a significant difference between the two conditions and can now quantify the modulation of fixation behavior in terms of standardized effect sizes.
-
-### Object Recognition and Mispronunciation Sensitivity Modulated by Age
-
-```{r MAcorrect_age}
-
-rma_correct_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = ~ collapse | short_cite)
-
-#summary(rma_correct_age)
-#kable(round(coef(summary(rma_correct_age)), 2))
-#aov.type <- anova(rma_correct_age)
-
-Csum_eff <- coef(summary(rma_correct_age))[2,]
-
-```
-
-```{r MAMP_age}
-
-rma_MP_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = ~ collapse | short_cite)
-
-#summary(rma_MP_age)
-#aov.type <- anova(rma_MP_age)
-
-Msum_eff <- coef(summary(rma_MP_age))[2,]
-
-```
-
-To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered, in days).
-In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not.
-Age did not significantly modulate object identification in response to correctly pronounced (QM(`r r2(rma_correct_age$m)`) = `r r2(rma_correct_age$QM)`, *p* `r psig(rma_correct_age$QMp)`) or mispronounced words (QM(`r r2(rma_MP_age$m)`) = `r r2(rma_MP_age$QM)`, *p* `r psig(rma_MP_age$QMp)`).
-The lack of a significant modulation together with the small estimates indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label.
-This relationship is plotted in Figure 2.
-
-[CHRISTINA] CAN YOU ADD ESTIMATES AND THEIR CIS?? Ideally everywhere where you report a p-value
-[KATIE: Do you know how to calculate Estimates and CIs for the Test of Moderators? Or do you mean reporting the estimates and CIs even when the moderator test is not significant?]
-
-```{r MPEffect_age}
-
-rma_MPeffect_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = ~ collapse | short_cite)
-
-# summary(rma_MPeffect_age)  
-# 
-# aov.type <- anova(rma_MPeffect_age)
-
-sum_eff <- coef(summary(rma_MPeffect_age))[4,]
-
-```
-
-We then examined the interaction between age and mispronunciation sensitivity (correct vs.
-mispronounced words) in our whole dataset.
-The moderator test was significant (QM(`r r2(rma_MPeffect_age$m)`) = `r r2(rma_MPeffect_age$QM)`, *p* `r psig(rma_MPeffect_age$QMp)`).
-This result is in line with the general observation that as infants mature they become better at language processing.
-The interaction between age and mispronunciation sensitivity, however, was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`), suggesting that as infants age, their mispronunciation sensitivity remains the same.
-
-## Figure 2
-
-```{r PlotMPEffect, echo = FALSE}
-
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
-
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g),show.legend=FALSE, alpha = .5) + 
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom",
-        text = element_text(size = 40)) + 
-  xlab("Age in months") + 
-  ylab("Hedges' g")
-
-p
-
-# min(dat$mean_age_1/30.44)
-# max(dat$mean_age_1/30.44)
-
-#ggsave("figures/AgeEffect_log.jpg", p,height= 7,width= 6)
-
-  jpeg(filename = "figures/Figure_2_AgeEffect.jpg", 
-       width = 700, height = 400, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-### Vocabulary Size: Correlation Between Mispronunciation Sensitivity and Vocabulary
-
-```{r VocabularyData, echo = FALSE}
-vocab_info <- db_ET_correct %>%
-  mutate(has_vocab = ifelse(!is.na(r_comprehension), "comprehension", 
-                            ifelse(!is.na(r_production), "production", "none"))) %>%
-  group_by(has_vocab) %>%
-  summarize(count = n(),
-            papers = n_distinct(short_cite))
-
-#kable(vocab_info)
-
-vocab_info2 <- db_ET_correct %>%
-  mutate(has_vocab = ifelse(!is.na(r_comprehension) | !is.na(r_production), "vocab", 
-                            "none")) %>%
-  group_by(has_vocab) %>%
-  summarize(count = n(),
-            papers = n_distinct(short_cite))
-
-vi1 <- as.data.frame(vocab_info)
-vi2 <- as.data.frame(vocab_info2)
-
-```
-
-Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers; production = `r with(vi1, papers[has_vocab == "production"])`) analyzed the relationship between vocabulary scores and mispronunciation sensitivity.
-There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we analyze this data separately.
-
-[KATIE] I DON'T KNOW HOW TO INTERPRET THESE RESULTS... THE FIXED EFFECTS MODEL ISN'T SIGNIFICANT FOR ANY OF THESE. IS THAT MEANINGFUL?
-[CHRISTINA] SO WE DON'T WANT TO INTERPRET THE FIXED EFFECTS MODEL AT ALL, IT IS NOT SUITABLE BECAUSE THERE IS VARIANCE BETWEEN EVERY RECORD (LANGUAGE ETC).
-I WOULD INTERPRET THE OVERALL CORRELATION AND THE CI, NOT THE P-VALUE (IN GENERAL).
-I ALSO WONDER WHETHER WE SHOULD MOVE THE SUBSET ANALYSES TO THE SUPPLEMENTARY MATERIALS AND JUST SAY OVERALL WE SEE NO RELATIONSHIPS AND CORRELATION COEFFICIENTS CONSISTENYL BELOW .1
-WE THEREFORE MUST CONCLUDE THAT WITHIN NARROW AGE GROUPS VOCABULARY DOES NOT INFLUENCE ANYTHING WE LOOK AT. WE CANNOT DO THIS ANALYSIS FPOR MP SENSITIVITY BECAUSE WE DON'T HAVE THE NECESSARY RAW DATA.
-[KATIE: Ah, so because for each paper the correlation and CI values straddle 0, this indicates that there really isn't much evidence for a relationship?
-I think it could make sense to add this to supplementary materials.
-Over the summer, I had also played around with looking at how collection of vocabulary data has dropped off over the years, even though more mispronunciation studies have been published.
-That might be something interesting to add.
-If we truly think that this is what is driving the development of mispronunciation sensitivity, then why are people not collecting this data?]
-(BUT I WONDER WHETHER WECOULD ENCODE THE REPORTED INTERACTION TERMS AND THE CORRELATION AND THEN DO SOMETHING WITH THAT?)
-[KATIE: I'm not really sure what you mean by this :(]
-
-```{r ComprehensionMeta_correct}
-#we're relying on the library meta function metacor
-compr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_comprehension) & r_comprehension > -1)
-
-metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
-```
-
-```{r ProductionMeta_correct}
-#we're relying on the library meta function metacor
-prodr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_production) & r_production < 1)
-
-metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
-```
-
-```{r ComprehensionMeta_MP}
-#we're relying on the library meta function metacor
-compr  <- subset(db_ET_MP, !is.na(db_ET_MP$r_comprehension) & r_comprehension > -1)
-
-metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
-```
-
-```{r ProductionMeta_MP}
-#we're relying on the library meta function metacor
-prodr  <- subset(db_ET_MP, !is.na(db_ET_MP$r_production) & r_production < 1)
-
-metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
-```
-
-### Interim Discussion
-
-The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age.
-The results are clear: Although infants consider a mispronunciation as a better match with the target image than a distractor image, there was a consistent effect of mispronunciation sensitivity.
-This did not change with development.
-Of the 3 predictions and assumptions about the development of infants' sensitivity to mispronunciations discussed in the Introduction, the present results lend some support for the argument that mispronunciation sensitivity stays consistent as infants develop.
-This runs counter to existing theories of phono-lexical development, which predict either an increase (PRIMR ref) or decrease (Assim Model ref) in mispronunciation sensitivity.
-
-[KATIE] CAN A CONCLUSION BE DRAWN FROM THE VOCABULARY RESULTS? IF SO, THIS IS THE PARAGRAPH
-
-In sum, it seems that current theories of infants' phono-lexical development cannot fully capture our results and should be reconsidered with all the evidence in mind.
-
-Alternatively, the lack of developmental change in mispronunciation sensitivity could be due to differences in the types of tasks given to infants of different ages.
-To examine this possibility, we include an exploratory analysis of whether different moderators and experimental design features were included at different ages, in addition to investigating the role that these moderators play in mispronunciation sensitivity.
-
-## Moderator Analyses
-
-[cHRISTINA] I WOULD FOLLOW THE OUTLINE IN THE PREVIOUS PARAGRAPH HERE OR FLIP THE PARAGRAPH AROUND:
-1. ARE DIFFERENT MODERATORS USED AT DIFFERENT AGES? 
-TEST: sIMPLE CHI-SQUARED OF AGE GROUP VERSUS MODERATOR ASSIGNMENT (AGE GROUP DETERMINED BY LOOKING AT THE YOUNGEST AGE FOR X?)
-2. WHICH MODERATORS INFLUENCE MP SENSITIVITY
-TEST SIMPLE MA WITH MODERATOR TESTS
-
-OR 
-"FOR EACH POSSIBLE MODERATOR WHICH COULD INFLIENCE MP SENSITIVITY, WE FIRST TEST THIS POSSIBILITY AND THEN EVALUATE WHETHER THERE IS A SYSTEMATIC DIFFERENCE OF MANIPULATING THESE MODERATORS AS INFANTS MATURE, I.E.
-WHETHER OLDER INFANTS ARE TESTED ON A MORE DIFFICULT TASK "
-ALSO, AS FINAL FOLLOW-UP IT WOULD BE PERFECT TO JUST SUBSET ALL STUDIES WITH FAMILIAR DISTRACTORS, SAME NUMBER OF FEATURES, AND CHECK THAT OUR CONCLUSIONS HOLD UP REGARING MP SENSITIVITY
-
-[KATIE: I prefer this second option, first looking at the moderators in general and then looking at whether there is this systematic difference with age.
-The latter is exploratory, so I feel like this information should not preceed our planned analyses.]
-
-### Number of features changed
-
-```{r NFeatures_demographics}
-
-dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-nfeature_info <- dat.f %>%
-  group_by(n_feature) %>%
-  summarize(n_exp_conditions =  n())
-
-```
-
-To assess whether the number of features changed modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced using 1-, 2-, and 3-feature changes.
-We did not include data for which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent (e.g., one mispronunciation included a 2-feature change whereas another only a 1-feature change).
-This analysis was therefore based on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` experimental conditions for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations.
-Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an equal impact on mispronunciation sensitivity, following the argument of graded sensitivity (White & Aslin, 2008; Mani & Plunkett 2011).
-
-```{r NFeatures}
-
-dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat.f, random = ~collapse | short_cite)
-
- sum_eff <- coef(summary(rma_NFeatures))[2,]
-
-```
-
-To understand the relationship between number of features changed and mispronunciation sensitivity, we  evaluated the effect size Hedges' *g* with number of features changed as a moderator.
-The moderator test was significant, QM(`r r2(rma_NFeatures$m)`) = `r r2(rma_NFeatures$QM)`, *p* `r psig(rma_NFeatures$QMp)`.
-Hedges' *g* for number of features changed was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that as the number of features changed increased, the effect size Hedges' *g* significantly decreased (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
-We plot this relationship in Figure X.
-This confirms previous findings of a graded sensitivity to the number of features changed for both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) mispronunciations as well as the importance of controlling for the degree of phonological mismatch in experimental design.
-
-```{r PlotFeatEffect, echo = FALSE}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-dat_f$feat_cat <- ifelse(dat_f$n_feature == 1, "1-feature",
-                         ifelse(dat_f$n_feature == 2, "2-feature",
-                                ifelse(dat_f$n_feature == 3, "3-feature",
-                                       ifelse(dat_f$n_feature == 0, "correct", "none"))))
-
-dat_f <- subset(dat_f, feat_cat != "none")
-
-dat_f$Features_changed <- factor(dat_f$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))
-
-p <- ggplot(dat_f, aes(Features_changed, g_calc, fill = Features_changed)) + 
-  geom_boxplot() + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "none",
-        axis.title.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_3_Number_of_Features.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-  #[CHRISTINA] WHAT DO YOU THINK ABOUT VIOLIN PLOTS?
-
-```
-
-```{r NFeatures_age}
-
-dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat.f, random = ~collapse | short_cite)
-
- sum_eff <- coef(summary(rma_NFeatures))[4,]
-
-```
-
-Although we did not have any specific predictions about the relationship between infant age and the impact of number of features changed on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
-When age was also included as a moderator, the moderator test was significant, QM(`r r2(rma_NFeatures$m)`) = `r r2(rma_NFeatures$QM)`, *p* `r psig(rma_NFeatures$QMp)`, but the interaction between age and number of features changed was not significant, $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
-This suggests that there is no relationship between infant age the impact of number of features changed on mispronunciation sensitivity.
-
-```{r NFeatures_subset}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-nfeature_ages <- dat.f %>%
-  group_by(n_feature) %>%
-  summarize(min_age = r2(min(mean_age_1, na.rm=TRUE)),
-            max_age = r2(max(mean_age_1, na.rm=TRUE)),
-            mean_age = r2(mean(mean_age_1, na.rm=TRUE)))
-
-mf <- subset(dat_f, n_feature == "3")
-min_age <- min(mf$mean_age_1)
-max_age <- max(mf$mean_age_1)
-
-dat_fage= dat_f%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat_fage, random = ~collapse | short_cite)
-
- sum_eff1 <- coef(summary(rma_NFeatures_agesub))[2,]
-
-rma_AGENFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat_fage, random = ~collapse | short_cite)
-
- sum_eff2 <- coef(summary(rma_AGENFeatures_agesub))[4,]
-
-```
-
-Although all papers included in the dataset also included correct pronunciations, not all papers included all three types of feature changes (i.e.
-1-3).
-The age range for each type of number of features changed was `r with(nfeature_ages, min_age[n_feature == 1])` - `r with(nfeature_ages, max_age[n_feature == 1])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 1])`) for 1-feature mispronunciations, `r with(nfeature_ages, min_age[n_feature == 2])` - `r with(nfeature_ages, max_age[n_feature == 2])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 2])`) for 2-feature mispronunciations, and `r with(nfeature_ages, min_age[n_feature == 3])` - `r with(nfeature_ages, max_age[n_feature == 3])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 3])`) for 3-feature mispronunciations.
-Focusing on the ages where all three numbers of features changed were tested (i.e.
-`r with(nfeature_ages, min_age[n_feature == 3])` - `r with(nfeature_ages, max_age[n_feature == 3])` days), however, did not change the pattern of results.
-
-### Distractor familiarity
-
-```{r DistractorType_misp}
-
-rma_Distractor_MP <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)
-
-rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
-
-sum_eff <- coef(summary(rma_Distractor))[4,]
-
-```
-
-We next assessed whether distractor familiarity has an impact on the size of mispronunciation sensitivity.
-First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images that were paired with either a familiar or an unfamiliar distractor image.
-The moderator test was not significant QM(`r r2(rma_Distractor_MP$m)`) = `r r2(rma_Distractor_MP$QM)`, *p* `r psig(rma_Distractor_MP$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object.
-We next assessed whether distractor familiarity was related to mispronunciation sensitivity.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_Distractor$m)`) = `r r2(rma_Distractor$QM)`, *p* `r psig(rma_Distractor$QMp)`, but the interaction between distractor familiarity and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
-These results suggest that overall, infants' familiarity with the distractor object (familiar or unfamiliar) did not impact their mispronunciation sensitivity.
-
-```{r PlotDistFamEffect_NoAge}
-
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
-dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "Familiar Distractor", "Unfamiliar Distractor")
-
-# Color Blind palette:
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
-p <- ggplot(dat, aes(condition_label, g_calc, fill = condition_label)) + 
-  geom_boxplot() + 
-  facet_grid(.~dist_code) +
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_4Distractor_fam.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-  #[CHRISTINA] AGAIN, WHAT DO YOU THINK OF VIOLINS?
-
-```
-
-```{r DistractorTypeAge}
-
-rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)
-
-sum_eff <- coef(summary(rma_DistractorAge))[4,]
-
-rma_DistractorAgeMS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
-
-#summary(rma_DistractorAgeMS)
-
-sum_eff1 <- coef(summary(rma_DistractorAgeMS))[8,]
-sum_eff2 <- coef(summary(rma_DistractorAgeMS))[7,]
-
-```
-
-We next examined whether age modulates object recognition or mispronunciation sensitivity when the distractor image is familiar or unfamiliar.
-For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_DistractorAge$m)`) = `r r2(rma_DistractorAge$QM)`, *p* `r psig(rma_DistractorAge$QMp)`.
-[CHRISTINA] I WORRY A LOT AT THESE POINTS THAT THIS IS THE WHOLE P>.05 = NULL IS TRUE FALLACY.
-WE CAN NEVER HAVE EVIDENCE FOR THE NULL HYPOTHESIS.
-SO BETTER ITNERPRET ESTIMATES AND CIS.
-
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object, regardless of their age.
-We next assessed whether the relationship between distractor familiarity and mispronunciation sensitivity was modulated by age.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_DistractorAgeMS$m)`) = `r r2(rma_DistractorAgeMS$QM)`, *p* `r psig(rma_DistractorAgeMS$QMp)`.
-Although the three-way-interaction between condition, distractor familiarity, and age was not significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`), here the interaction between condition and distractor familiarity was significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], *p* `r psig(sum_eff2$pval)`).
-
-[KATIE] WHAT DOES IT MEAN THAT IN THIS LAST TEST THERE WAS AN INTERACTION BETWEEN CONDITION AND DISTRACTOR FAMILIARITY, WHEN AGE WAS INCLUDED AS A MODERATOR?
-DOES THAT MEAN THAT AGE IS CONTROLLED FOR?
-UNDERSTANDING THIS WILL HELP ME FORMULATE THE CONCLUSION SENTENCE AND MOTIVATE THE NEXT SET OF ANALYSES.
-
-[CHRISTINA] I WOULD NOT OVERINTERPRET IT, THE ESTIMATE DID NOT DRAMATICALLY CHANGE, AND IT IS BARELY SIGNIFICANT. DOES THAT HELP?
-
-[KATIE: I think so. I've just removed that part]
-
-```{r DistractorTypeAgeRangeSubset}
-
-object_pair_ages <- dat %>%
-  group_by(object_pair) %>%
-  summarize(min_age = r2(min(mean_age_1, na.rm=TRUE)),
-            max_age = r2(max(mean_age_1, na.rm=TRUE)),
-            mean_age = r2(mean(mean_age_1, na.rm=TRUE)))
-
-fn <- subset(dat, object_pair=="familiar_novel")
-
-ff <- subset(dat, object_pair=="familiar_familiar")
-
-age_diff_dist <- t.xtable(t.test(fn$mean_age_1, ff$mean_age_1, paired = F))
-
-#t.test(fn$mean_age_1, ff$mean_age_1)
-
-opa <- as.data.frame(object_pair_ages)
-min_age <- max(opa$min_age)
-max_age <- min(opa$max_age)
-
-dat_age_MP= db_ET_MP%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-rma_Distractor_MP <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat_age_MP, random = ~ collapse | short_cite)
-
-#summary(rma_Distractor_MP)
-
-sum_eff <- round(coef(summary(rma_Distractor_MP))[2,], 2)
-
-# misp sensitivity
-dat_age= dat%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-rma_Distractor_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition, data = dat_age, random = ~ collapse | short_cite)
-
-#summary(rma_Distractor_MS)
-
-sum_eff <- coef(summary(rma_Distractor_MS))[2,]
-
-```
-
-Although we anticipated that older children may be more impacted by the presence of a unfamiliar compared to familiar distractor image, we found that age and distractor familiarity did not impact mispronunciation sensitivity.
-Inspection of the ages tested using different kinds of distractors, however, revealed differences.
-Infants tested using a familiar distractor were younger (M = 588.76 days, SD = 136.47, range = 207.8 - 768 days) than those infants tested using an unfamiliar distractor (M = 678.85 days, SD = 115.47, range = 544.48 - 920.2 days), which a two-sample t-test revealed to be a significant difference, t(153.83) = 5.30, p < .0001.
-
-[CHRISTINA] CAN YOU TURN THE NUMBERS INTO R CODE HERE? aLSO, NOT SURE WE NEED A T-TEST TO CONFIRM THE OBVIOUS.
-
-[KATIE] SO, IS IT OKAY TO DO THE AGE SUBSET ANALYSIS AFTER THIS?
-SOMETHING LIKE "TO ENSURE THAT THE LACK OF A DIFFERENCE WASN'T DUE TO THE DIFFERENCE IN AGES OF INFANTS TESTED WITH DIFFERENT TYPES OF DISTRACTORS, WE ANALYZED A SUBSET OF PAPERS THAT TESTED AGES WHERE BOTH FAMILIAR AND UNFAMILIAR DISTRACTORS WERE USED." IN THE SUBSET ANALYSIS, FOR MISP SENSITIVITY, THERE IS A SIGNIFICANT INTERACTION BETWEEN DISTRACTOR FAMILIARITY AND CONDITION.
-
-[CHRISTINA] YES!!!!!!
-
-### Phonological overlap between target and distractor
-
-```{r DistractorOverlap_descrip}
-
-dist_overlap_info <- dat %>%
-  group_by(distractor_overlap) %>%
-  summarize(n_exp_conditions =  n())
-
-```
-
-To assess whether phonological overlap between the target and distractor image labels has an impact on the size of mispronunciation sensitivity, we examined the meta-analytic effect for object identification in response to mispronunciations and mispronunciation sensitivity when the target-distractor pairs either shared the same onset phoneme, had no overlap, or where the distractor was an unfamiliar object.
-We did not include data for which the overlap included both the onset and medial phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset/medial"])`) or coda phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "coda"])`).
-The analysis was therefore based on a subset of the overall dataset, with `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset"])` experimental conditions containing onset phoneme overlap between the target and distractor, `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "no"])` containing no overlap between target and distractor, and `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "novel"])` for targets paired with unfamiliar distractor images.
-There were therfore three possibilities for distractor overlap: onset phoneme overlap, no overlap, and an unfamiliar distractor.
-In our analysis, we were interested in the difference between overlap and lack of overlap; therefore, experimental conditions containing onset phoneme overlap were coded as the reference condition and compared with responses to experimental conditions with no overlap or an unfamiliar distractor separately.
-
-[KATIE] CAN YOU CHECK THE WAY THAT I WROTE THE LAST SENTENCE?
-
-[CHRISTINA] SEEMS OK BUT I AM CONFUSED WHY OVERLAP IS THE BASELINE AND WHY YOU BRING IN NOVEL. I THINK YOU NEED TO SPELL THIS OUT MORE.
-
-```{r DistractorOverlap}
-db_ET_MPo = db_ET_MP %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
-
-rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
-
-#summary(rma_DistractorOverlap)
-
-db_ET_MPo_MS = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-db_ET_MPo_MS$distractor_overlap <- factor(db_ET_MPo_MS$distractor_overlap, levels = c("onset", "no", "novel"))
-
-rma_DistractorOverlapMS <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MPo_MS, random = ~ collapse | short_cite)
-
-#summary(rma_DistractorOverlapMS)
-
-sum_eff1 <- coef(summary(rma_DistractorOverlapMS))[5,]
-sum_eff2 <- coef(summary(rma_DistractorOverlapMS))[6,]
-
-```
-
-Regarding object identification in response to mispronunciations, when distractor overlap was included as a moderator, the moderator test was not significant QM(`r r2(rma_DistractorOverlap$m)`) = `r r2(rma_DistractorOverlap$QM)`, *p* `r psig(rma_DistractorOverlap$QMp)`.
-[CHRISTINA] AGAIN DO NOT RELY ON P-VALUES BUT ON ESTIMATES AND CIS
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with a distractor image that contained overlap on the onset phoneme or no overlap with the target word, or was an unfamiliar object.
-We next assessed whether target-distractor overlap was related to mispronunciation sensitivity.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_DistractorOverlapMS$m)`) = `r r2(rma_DistractorOverlapMS$QM)`, *p* `r psig(rma_DistractorOverlapMS$QMp)`.
-The interaction between condition and target-distractor pairs with no overlap was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`), suggesting that mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap.
-The interaction between condition and target-distractor pairs with an unfamiliar distractor was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], *p* `r psig(sum_eff2$pval)`), suggesting that mispronunciation sensitivity was smaller when the distractor image shared the same onset phoneme as the target image compared to when the distractor image was an unfamiliar object.
-This can be seen in Figure X.
-
-[christina] I THINK THESE SHOULD BE TWO SEPARATE ANALYSES... NOVEL IS CONCEPTUALLY DIFFERENT.
-
-```{r PlotDistOverlapEffect}
-
-db_ET_MPo = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
-
-db_ET_MPo$condition_label <- ifelse(db_ET_MPo$condition==1, "Correct", "Mispronunciation")
-
-p <- ggplot(db_ET_MPo, aes(condition_label, g_calc, fill = condition_label)) + 
-  facet_grid(.~distractor_overlap)+
-  geom_boxplot() + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_5_Distractor_overlap.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-```{r DistractorOverlap_age}
-
-# object recognition
-db_ET_MPo = db_ET_MP %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
-
-rma_DistractorOverlap_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
-
-# mispronunciation sensitivity
-dat_MPo = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-dat_MPo$distractor_overlap <- factor(dat_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
-
-rma_DistractorOverlap_age_MS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap*condition, data = dat_MPo, random = ~ collapse | short_cite)
-
-#summary(rma_DistractorOverlap_age_MS)
-
-sum_eff1 <- coef(summary(rma_DistractorOverlap_age_MS))[11,]
-sum_eff2 <- coef(summary(rma_DistractorOverlap_age_MS))[12,]
-
-```
-
-Although we did not have any specific predictions about the relationship between infant age and the impact of distractor overlap on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
-First, for object recognition in response to mispronunciations, when age in addition to distractor overlap was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_DistractorOverlap_age$m)`) = `r r2(rma_DistractorOverlap_age$QM)`, *p* `r psig(rma_DistractorOverlap_age$QMp)`, suggesting that upon hearing a mispronunciation, infants looks to the target image were similar for the three types of overlap, regardless of infant age.
-We next assessed whether the relationship between distractor overlap and mispronunciation sensitivity was modulated by age.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_DistractorOverlap_age_MS$m)`) = `r r2(rma_DistractorOverlap_age_MS$QM)`, *p* `r psig(rma_DistractorOverlap_age_MS$QMp)`.
-The interaction between age, condition, and target-distractor pairs with no overlap was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`).
-As can be seen in Figure X, the difference between correct pronunciations and mispronunciations (mispronunciation sensitivity) stays steady across infant ages for both target words paired with distractors containing onset overlap with the target word as well as distractors containing no overlap.
-As infants aged, however, overall recognition (regardless of condition) increased for target-distractor pairs containing onset overlap, whereas for overall recognition decreased for target-distractor pairs containing no overlap.
-The interaction between age, condition, and target-distractor pairs with an unfamiliar distractor was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], *p* `r psig(sum_eff2$pval)`).
-As can also be seen in Figure X, mispronunciation sensitivity for target words paired with unfamiliar distractors decreased with age, while it remained steady across a similar range of ages for target words paired with distractors containing onset overlap with the target word.
-
-```{r PlotDistOverlap_cond_age}
-
-db_ET_MPo = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
-
-db_ET_MPo$condition_label <- ifelse(db_ET_MPo$condition==1, "Correct", "Mispronunciation")
-
-p <- ggplot(db_ET_MPo, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-    facet_grid(.~distractor_overlap)+
-  geom_point(aes(size = weights_g),show.legend=FALSE) + 
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_6_Distractor_overlap_age.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-### Position of mispronunciation
-
-```{r Location_descrip}
-
-misp_location_info <- dat %>%
-  group_by(mispron_location) %>%
-  summarize(n_exp_conditions =  n())
-
-```
-
-To assess whether the position of the mispronunciation has an impact on mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to mispronunciations on the onset and medial phonemes.
-We did not include data for which the mispronunciation was located on the coda (*n* = `r with(misp_location_info, n_exp_conditions[mispron_location == "coda"])`), varied in regard to position (*n* = `r with(misp_location_info, n_exp_conditions[mispron_location == "coda/medial" | mispron_location == "onset/medial" | mispron_location == "onset/medial/coda"])`), or was not reported (*n* = `r with(misp_location_info, n_exp_conditions[is.na(mispron_location)])`).
-The analysis was therefore based on a subset of the overall dataset, with `r with(misp_location_info, n_exp_conditions[mispron_location == "onset"])` experimental conditions comparing a mispronunciation on the onset phoneme and `r with(misp_location_info, n_exp_conditions[mispron_location == "medial"])` experimental conditions comparing a mispronunciation on the medial phoneme.
-
-```{r Location_misp}
-#table(db_ET_MP$mispron_location)
-
-db_ET_MPl = db_ET_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("onset", "medial"))
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_Location_MP <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_MPl, random = ~collapse | short_cite)
-
-db_ET_MPl = dat %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("onset", "medial"))
-
-rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition, data = db_ET_MPl, random = ~collapse | short_cite)
-
-sum_eff <- coef(summary(rma_LocationCondition))[4,]
-
-```
-
-Regarding object identification in response to mispronunciations, when mispronunciation location was included as a moderator, the moderator test was not significant QM(`r r2(rma_Location_MP$m)`) = `r r2(rma_Location_MP$QM)`, *p* `r psig(rma_Location_MP$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was located on the onset or  medial phonemes.
-We next assessed whether mispronunciation location was related to mispronunciation sensitivity.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_LocationCondition$m)`) = `r r2(rma_LocationCondition$QM)`, *p* `r psig(rma_LocationCondition$QMp)`, but the interaction between mispronunciation location and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
-These results suggest that overall, the location of the mispronunciation (onset, medial) did not impact mispronunciation sensitivity.
-
-```{r PlotPositionEffect}
-
-#dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial" |
-#                mispron_location == "offset")
-
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
-
-dat.p = dat %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-dat.p$mispron_location <- factor(dat.p$mispron_location, levels = c("onset", "medial"))
-
-p <- ggplot(dat.p, aes(condition_label, g_calc, fill = condition_label)) + 
-  facet_grid(.~mispron_location)+
-  geom_boxplot() + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_7_Mispronunciation_position.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-```{r Location_misp_age}
-#table(db_ET_MP$mispron_location)
-
-db_ET_MPl = db_ET_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("onset", "medial"))
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_Location_MP_age <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
-
-db_ET_MPl = dat %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("onset", "medial"))
-
-rma_LocationCondition_age <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
-
-sum_eff <- coef(summary(rma_LocationCondition))[8,]
-
-```
-
-Although we did not have any specific predictions about the relationship between infant age and the impact of mispronuncition location on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
-First, for object recognition in response to mispronunciations, when age in addition to mispronunciation location was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_Location_MP_age$m)`) = `r r2(rma_Location_MP_age$QM)`, *p* `r psig(rma_Location_MP_age$QMp)`, suggesting that upon hearing a mispronunciation, infants looks to the target image were similar for both onset and medial mispronunciations, regardless of infant age.
-We next assessed whether the relationship between mispronunciation location and mispronunciation sensitivity was modulated by age.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_LocationCondition_age$m)`) = `r r2(rma_LocationCondition_age$QM)`, *p* `r psig(rma_LocationCondition_age$QMp)`, but the interaction between mispronunciation location, age, and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
-These results provide further evidence that location of the mispronunciation (onset, medial) did not impact mispronunciation sensitivity.
-
-### Type of mispronunciation (consonant or vowel)
-
-```{r CV_descript}
-
-CV_info <- dat %>%
-  group_by(type_feature) %>%
-  summarize(n_exp_conditions =  n())
-
-CV_location_info <- dat %>%
-  group_by(type_feature, mispron_location) %>%
-  summarize(n_exp_conditions =  n())
-
-```
-
-To assess whether the type of mispronunciation impacts sensitivity to mispronunciations, we calculated the meta-analytic effect for object identification in response to the type of mispronunciation.
-Although most theoretical discussion of mispronunciation type has focused on consonants and vowels, our dataset also included tone mispronunciations.
-In our analysis, we were interested in the difference between consonants and vowels, but also include an exploratory analysis of responses to tones, consonants, and vowels.
-We therefore conducted two sets of analyses, one analyzing consonants and vowels alone and a second comparing responses to tones with that of consonants and vowels, separately.
-For the latter analysis, tones were coded as the reference condition.
-We did not include data for which mispronunciation type varied within experiment and was not reported separately (*n* = `r with(CV_info, n_exp_conditions[type_feature == "consonant_and_vowel" | type_feature == "consonant_vowel_tone"])`).
-The analysis was therefore based on a subset of the overall dataset, with `r with(CV_info, n_exp_conditions[type_feature == "consonant"])` experimental conditions comparing a consonant mispronunciation, `r with(CV_info, n_exp_conditions[type_feature == "vowel"])` experimental conditions comparing a vowel mispronunciation, and `r with(CV_info, n_exp_conditions[type_feature == "tone"])` experimental conditions comparing a tone mispronunciation.
-Below, we first report the set of analyses comparing consonants with vowels before moving on to the second set of exploratory analyses comparing tones with that of consonants and vowels.
-
-[KATIE] WHAT DO YOU THINK ABOUT THIS?
-WE HAVE THE TONES AND ITS A NOVEL, INTERESTING THING, I THINK, AND PERHAPS WORTH IT TO INCLUDE A COMPARISON OF TONES ALONGSIDE THE MORE THEORETICALLY IMPORTANT COMPARISON BETWEEN CONSONANTS AND VOWELS.
-
-```{r MPtype_cv}
-
-# C vs. V
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel")
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("consonant", "vowel"))
-
-rma_TypeFeaturesMP <- rma.mv(g_calc, g_var_calc, mods = ~type_feature, data = db_MP_type, random = ~collapse | short_cite)
-
-# C vs. V with condition
-
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition, data = db_type, random = ~collapse | short_cite)
-
-sum_eff1 <- coef(summary(rma_TypeFeaturesMP_Condition))[4,]
-
-```
-
-We first analyzed experimental conditions where mispronunciation type was either a consonant or vowel.
-Regarding object identification in response to mispronunciations, when mispronunciation type was included as a moderator, the moderator test was not significant QM(`r r2(rma_TypeFeaturesMP$m)`) = `r r2(rma_TypeFeaturesMP$QM)`, *p* `r psig(rma_TypeFeaturesMP$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was a consonant or a vowel.
-We next assessed whether type of mispronunciation (consonant or vowel) was related to mispronunciation sensitivity.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, *p* `r psig(rma_TypeFeaturesMP_Condition$QMp)`, but the interaction between mispronunciation type and condition was not significant $\beta$ = `r r2(sum_eff1$estimate)`, (SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`).
-These results suggest that overall, the type of  mispronunciation (consonant vs.
-vowel) did not impact mispronunciation sensitivity.
-
-```{r MPtype_cv_age}
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("consonant", "vowel"))
-
-rma_TypeFeaturesMPage <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~collapse | short_cite)
-
-sum_eff <- coef(summary(rma_TypeFeaturesMP_Condition))[8,]
-
-```
-
-We next examined whether age modulates object recognition or mispronunciation sensitivity when the mispronunciation is a consonant or vowel.
-For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_TypeFeaturesMPage$m)`) = `r r2(rma_TypeFeaturesMPage$QM)`, *p* `r psig(rma_TypeFeaturesMPage$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was on a consonant or vowel phoneme, regardless of their age.
-We next assessed whether the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity was modulated by age.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, *p* `r psig(rma_TypeFeaturesMP_Condition$QMp)`.
-The interaction between mispronunciation type, condition, and age was significant ($\beta$ = `r r2(sum_eff$estimate)`, SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
-As can be seen in Figure X, as infants age, mispronunciation sensitivity grows larger for vowel mispronunciations but becomes smaller for consonant mispronunciations.
-Noticeably, mispronunciation sensitivity appears greater for consonant compared to vowel mispronunciations at younger ages, but this difference shifts as infants age.
-
-```{r PlotCVEffect_cond_age}
-
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
-dat_type$type_feature <- ifelse(dat_type$type_feature == "consonant", "Consonant", "Vowel")
-
-#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
-
-#dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-
-dat_type$condition_label = ifelse(dat_type$condition==1, "Correct", "Mispronunciation")
-
-p <- ggplot(dat_type, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-    facet_grid(.~type_feature)+
-  geom_point(aes(size = weights_g),show.legend=FALSE) + 
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_8_FeatureType_Cond_Age.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-```{r MPtype_cv_lang_descript}
-
-family <- dat %>%
-  group_by(lang_family) %>%
-  summarize(count = n())
-
-lang_family <- dat %>%
-  group_by(native_lang, lang_family) %>%
-  summarize(count = n())
-
-cv_family <- dat %>%
-  group_by(type_feature, lang_family) %>%
-  summarize(count = n())
-
-```
-
-```{r MPtype_cv_lang}
-
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("consonant", "vowel"))
-
-db_MP_type <- subset(db_MP_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeaturesMPfam <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family, data = db_MP_type, random = ~collapse | short_cite)
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-db_type <- subset(db_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeaturesMPC <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family, data = db_type, random = ~collapse | short_cite)
-
-sum_eff1 <- coef(summary(rma_TypeFeaturesMPC))[7,]
-sum_eff2 <- coef(summary(rma_TypeFeaturesMPC))[8,]
-
-# summary(glht(rma_TypeFeaturesMPC, linfct=cbind(contrMat(rep(1,8), type="Tukey"))), test=adjusted("none"))
-# 
-# ranef(rma_TypeFeaturesMPC)
-
-```
-
-To examine whether infants' native language impacts sensitivity to consonant and vowel mispronunciations, we classified infants into language families.
-Infants learning American English (*n* = `r with(lang_family, count[native_lang == "American English"])`), British English (*n* = `r with(lang_family, count[native_lang == "British English"])`), Danish (*n* = `r with(lang_family, count[native_lang == "Danish"])`), Dutch (*n* = `r with(lang_family, count[native_lang == "Dutch"])`), and German (*n* = `r with(lang_family, count[native_lang == "German"])`) were classified into the Germanic language family (*n* = `r with(family, count[lang_family == "Germanic"])`).
-Infants learning Catalan (*n* = `r with(lang_family, count[native_lang == "Catalan"])`), Spanish (*n* = `r with(lang_family, count[native_lang == "Spanish"])`), French (*n* = `r with(lang_family, count[native_lang == "French"])`), Catalan and Spanish simultaneously (i.e.
-bilinguals; *n* = `r with(lang_family, count[native_lang == "Catalan-Spanish"])`), and Swiss French (*n* = `r with(lang_family, count[native_lang == "Swiss French"])`) were classified into the Romance language family (*n* = `r with(family, count[lang_family == "Romance"])`).
-For object recognition in response to a mispronunciation, including language family as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_TypeFeaturesMPfam$m)`) = `r r2(rma_TypeFeaturesMPfam$QM)`, *p* `r psig(rma_TypeFeaturesMPfam$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was on a consonant or vowel phoneme, regardless of the language family of their native language.
-We next assessed whether the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity was modulated by language family.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family as additional moderators.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMPC$m)`) = `r r2(rma_TypeFeaturesMPC$QM)`, *p* `r psig(rma_TypeFeaturesMPC$QMp)`.
-The interaction between condition and language family was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`), suggesting XXXXXXXXXXXXXX.
-The interaction between mispronunciation type, condition, and language family was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], *p* `r psig(sum_eff2$pval)`).
-As can be seen in Figure X, mispronunciation sensitivity for consonants was similar for Germanic and Romance languages.
-Mispronunciation sensitivity for vowels, however, was greater for Germanic compared to Romance languages.
-
-[KATIE] I'M NOT REALLY SURE WHAT THE CONDITION BY LANGUAGE FAMILY INTERACTION MEANS. SHOULD WE EVEN INTERPRET IT?
-
-```{r PlotCVEffect_Lang}
-
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
-dat_type$type_feature <- ifelse(dat_type$type_feature == "consonant", "Consonant", "Vowel")
-
-#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
-
-dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-
-dat_type_sub$condition_label = ifelse(dat_type_sub$condition==1, "Correct", "Mispronunciation")
-
-p <- ggplot(dat_type_sub, aes(condition_label, g_calc, fill = condition_label)) + 
-  geom_boxplot() + 
-  facet_grid(.~type_feature*lang_family)+
-  #geom_line(y= 0, linetype="dotted") + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-    scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        axis.text.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  xlab("Language Family") + 
-  ylab("Effect size Hedges' g")
-p
-
- jpeg(filename = "figures/Figure_9_FeatureType_Cond_LangFam.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-```{r MPtype_cv_lang_age}
-
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("consonant", "vowel"))
-
-db_MP_type <- subset(db_MP_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeaturesMPfam <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family*age.C, data = db_MP_type, random = ~collapse | short_cite)
-
- sum_eff1 <- coef(summary(rma_TypeFeaturesMPC))[8,]
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-db_type <- subset(db_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeaturesMPC <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family, data = db_type, random = ~collapse | short_cite)
-
-sum_eff1 <- coef(summary(rma_TypeFeaturesMPC))[7,]
-sum_eff2 <- coef(summary(rma_TypeFeaturesMPC))[8,]
-
-# summary(glht(rma_TypeFeaturesMPC, linfct=cbind(contrMat(rep(1,8), type="Tukey"))), test=adjusted("none"))
-# 
-# ranef(rma_TypeFeaturesMPC)
-
-```
-
-Finally, we examined the relationship between language family and infant age and mispronunciation sensitivity to consonants and vowels.
-For object recognition in response to a mispronunciation, including language family and infant age as a moderator resulted in a moderator test that was significant, QM(`r r2(rma_TypeFeaturesMPfam$m)`) = `r r2(rma_TypeFeaturesMPfam$QM)`, *p* `r psig(rma_TypeFeaturesMPfam$QMp)`.
-The interaction between language family, age, and type of mispronunciation (consonant or vowel) was significant, ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`).
-As can be seen in Figure X, for infants learning Germanic languages, increasing age was related to increasing mispronunciation sensitivity for vowel mispronunciations, but decreasing sensitivity for consonant mispronunciations.
-In contrast, infants learning Romance languages have an even greater increase with age in sensitivity to vowel mispronunciations.
-Surprisingly, sensitivity to consonant mispronunciations shows a reversal in infants learning Romance languages: the growth in target looks for consonant mipronunciations increases and surpases that of target looks for correct pronunciations.
-
-[KATIE] AGAIN, THERE ARE ADDITIONAL INTERACTIONS THAT ARE SIGNIFICANT... SHOULD THEY BE INTERPRETED? ALSO, WTF ROMANCE LANGUAGES?
-
-```{r PlotCVEffect_cond_age_fam}
-
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
-dat_type$type_feature <- ifelse(dat_type$type_feature == "consonant", "Consonant", "Vowel")
-
-#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
-
-dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-
-dat_type_sub$condition_label = ifelse(dat_type_sub$condition==1, "Correct", "Mispronunciation")
-
-p <- ggplot(dat_type_sub, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-    facet_grid(.~type_feature*lang_family)+
-  geom_point(aes(size = weights_g),show.legend=FALSE) + 
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_10_FeatureType_Cond_Age_LangFam.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-```{r MPtype_cvt}
-
-# C vs. V vs. T
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" | type_feature == "tone")
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("tone", "consonant", "vowel"))
-
-rma_TypeFeaturesMPT <- rma.mv(g_calc, g_var_calc, mods = ~type_feature, data = db_MP_type, random = ~collapse | short_cite)
-
-# C vs. V vs. T with condition
-
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel"| type_feature == "tone")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("tone", "consonant", "vowel"))
-
-rma_TypeFeaturesMP_ConditionT <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition, data = db_type, random = ~collapse | short_cite)
-
-sum_eff2c <- coef(summary(rma_TypeFeaturesMP_ConditionT))[5,]
-sum_eff2v <- coef(summary(rma_TypeFeaturesMP_ConditionT))[6,]
-
-```
-
-Although we had no predictions regarding mispronunciation sensitivity to tone mispronunciations, we included an exploratory analysis to examine whether responses to tone mispronunciations were different from that of consonants or vowels.
-Regarding object identification in response to mispronunciations, when mispronunciation type was included as a moderator, the moderator test was not significant QM(`r r2(rma_TypeFeaturesMPT$m)`) = `r r2(rma_TypeFeaturesMPT$QM)`, *p* `r psig(rma_TypeFeaturesMPT$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for tone mispronunciations in comparison with both consonants and vowels.
-We next assessed whether type of mispronunciation (tone, consonant, vowel) was related to mispronunciation sensitivity.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_ConditionT$m)`) = `r r2(rma_TypeFeaturesMP_ConditionT$QM)`, *p* `r psig(rma_TypeFeaturesMP_ConditionT$QMp)`.
-The interaction between condition and consonant mispronunciations was not significant $\beta$ = `r r2(sum_eff2c$estimate)`, (SE = `r r2(sum_eff2c$se)`, 95% CI [`r r2(sum_eff2c$ci.lb)`, `r r2(sum_eff2c$ci.ub)`], *p* `r psig(sum_eff2c$pval)`), suggesting that there was no difference in looks to the target in response to consonant and tone mispronunciations.
-The interaction between condition and vowel mispronunciations was also not significant $\beta$ = `r r2(sum_eff2v$estimate)`, (SE = `r r2(sum_eff2v$se)`, 95% CI [`r r2(sum_eff2v$ci.lb)`, `r r2(sum_eff2v$ci.ub)`], *p* `r psig(sum_eff2v$pval)`), suggesting that there was no difference in looks to the target in response to vowel and tone mispronunciations.
-
-```{r MPtype_cvt_age}
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" | type_feature == "tone")
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("tone", "consonant", "vowel"))
-
-rma_TypeFeaturesMPage <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" | type_feature == "tone")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("tone", "consonant", "vowel"))
-
-rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~collapse | short_cite)
-
-sum_eff1 <- coef(summary(rma_TypeFeaturesMP_Condition))[11,]
-sum_eff2 <- coef(summary(rma_TypeFeaturesMP_Condition))[12,]
-
-```
-
-We further included an exploratory analysis of the relationship between infant age and the impact of tone mispronunciations in comparison to consonant and vowel mispronunciations.
-First, for object recognition in response to mispronunciations, when age in addition to mispronunciation location was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_TypeFeaturesMPage$m)`) = `r r2(rma_TypeFeaturesMPage$QM)`, *p* `r psig(rma_TypeFeaturesMPage$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were not different between tone and vowel or tone and consonant mispronunciations, regardless of their age.
-We next assessed whether the relationship between mispronunciation type (tone, consonant, vowel) and mispronunciation sensitivity was modulated by age.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, *p* `r psig(rma_TypeFeaturesMP_Condition$QMp)`, but the interactions between condition, age, and both consonant mispronciations ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`) and vowel mispronunciations ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], *p* `r psig(sum_eff2$pval)`) were not significant.
-Infants' sensitivity to tone mispronunciations compared to consonant or vowel mispronunciations did not differ with age.
-
-[KATIE] WORTH IT TO INCLUDE LANGUAGE FAMILY ANALYSES TOO?
-
-# Discussion
+We separated out conditions according to whether or not the target word
+was mispronounced to be able to investigate infants' looking to the
+target picture separated by whether or not words were mispronounced as
+well as their mispronunciation sensitivity, which is the difference
+between looks to the target in correct and mispronounced trials. When
+the same infants were further exposed to multiple mispronunciation
+conditions and the results were reported separately in the paper, we
+also entered each condition as a separate row (e.g., consonant versus
+vowel mispronunciations; Mani \& Plunkett, 2007). The fact that the same
+infants contributed data to multiple rows (minimally those containing
+information on correct and mispronounced trials) leads to shared
+variance across effect sizes, which we account for in our analyses (see
+next section). We will call each row a record; in total there were 251
+records in our data.
+
+\subsection{Data analysis}\label{data-analysis}
+
+\begin{tabular}{l|r|r}
+\hline
+Type of comparison & \# Papers & \# Effect Size\\
+\hline
+post-naming compared to pre-naming phase & 10 & 29\\
+\hline
+post-naming phase compared with chance (=50\%) & 9 & 23\\
+\hline
+post-pre difference score compared with chance (=0) & 13 & 52\\
+\hline
+\end{tabular}
+
+Mispronunciation sensitivity studies typically examine infants'
+proportion of target looks (PTL) in comparison to a baseline
+measurement. PTL is calculated by dividing the percentage of looks to
+the target by the total percentage of looks to both the target and
+distractor images. Across papers the baseline comparison varied; we used
+the baseline reported by the authors of each paper. Most papers
+(\emph{n} = 13) subtracted the PTL score for a pre-naming phase from the
+PTL score for a post-naming phase. When interpreting this difference
+score, a positive value indicates that infants increased their looks to
+the target after hearing the naming label (correct or mispronounced).
+Other papers either compared post- and pre-naming PTL with one another
+(\emph{n} = 10) or compared post-naming PTL with a chance level of 50\%,
+(\emph{n} = 9). For all these comparisons, a positive difference score
+or a post-naming phase PTL score that is greater than the pre-naming
+phase PTL or chance indicate target looks that indicate object
+recognition after hearing the naming label. Consequently, positive
+effect sizes reflect more looks to the target picture after naming, and
+larger positive effect sizes indicate comparatively more relative
+increase in looks to the target.
+
+We report effect sizes for infants' looks to target pictures after
+hearing a correctly pronounced or a mispronounced label (object
+identification) as well as the difference between effect sizes for
+correct and mispronounced trials (i.e.~mispronunciation sensitivity).
+The effect size we report in the present paper are based on comparison
+of means, standardized by their variance. The most well-known effect
+size from this group is Cohen's \emph{d} {[}@cohen{]}. To correct for
+the small sample sizes common in infant research, however, we use as a
+dependent variable Hedges' \emph{g} instead of Cohen's \emph{d} (Hedges,
+1981; Morris, 2000).
+
+We calculated Hedges' \emph{g} using the raw means and standard
+deviations reported in the paper (\emph{n} = 25) or using reported
+t-values (\emph{n} = 9). Raw means and standard deviations were
+extracted from figures for 3 papers. In a within-participation design,
+when two means are compared (i.e.~looking during pre- and post-naming)
+it is necessary to obtain correlations between the two measurements at
+the participant level to calculate effect sizes and effect size variance
+based on t-values. Upon request we were provided with correlation values
+for one paper (Altvater-Mackensen, 2010); we were able to compute
+correlations using means, standard deviations, and t-values for \emph{n}
+= 4 (following Csibra, et al. 2016, Appendix B; see also Rabagliati,
+Ferguson, \& Lew-Williams, 2018). Correlations were imputed for the
+remaining papers (see Black \& Bergmann, 2017, for the same procedure).
+We could compute a total of 104 effect sizes for correct pronunciations
+and 147 for mispronunciations.
+
+To take into account the fact that the same infants contributed to
+multiple datapoints, we analyze our results in a multilevel approach
+using the R {[}@R{]} package metafor {[}@metafor{]}. This means we model
+as random effect that effect sizes from the same paper share are based
+on more similar studies than those across papers and that nested therein
+effects can stem from the same infants.
+
+\subsection{Publication Bias}\label{publication-bias}
+
+{[}CHRISTINA: Do you think we have to revise this section? I think it's
+the same as in the proceedings paper.{]}{[}KATIE: Are you concerned
+about the Publication Bias section in particular, or the Methods as a
+whole? In general, some of the Methods was written before the CogSci
+paper and in other places to flesh things out I rewrote what we had. Its
+definitely giving the same information and sometimes the wording is
+close, because there's not too many different ways to explain what a
+funnel plot is :){]}
+
+In the psychological sciences, there is a documented reluctance to
+publish null results. As a result, there is a potential for significant
+results to be valued over non-significant results (see Ferguson \&
+Heene, 2012). To examine whether this is also the case in the
+mispronunciation sensitivity literature, which would bias the data
+analyzed in this meta-analysis, we conduct two tests. We first examine
+whether effect sizes are distributed as expected based on sampling error
+using the rank correlation test of funnel plot asymmetry with the R
+{[}@R{]} package metafor {[}@metafor{]}. Effect sizes with low-variance
+are expected to fall closer to the estimated mean, while effect sizes
+with high-variance should show an increased, evenly-distributed spread
+around the estimated mean. Second, we analyze all of the significant
+results in the dataset using a p-curve from the p-curve app (v4.0,
+p-curve.com; @pcurve). This tests for evidential value by examining
+whether the p-values have an expected distribution, regardless of
+whether the null hypothesis is true or not, as well as whether there is
+a larger proportion of p-values just below the typical alpha threshold
+of .05, which may indicate questionable research practices. Responses to
+correctly pronounced and mispronounced labels are predicted to show
+different patterns of looking behavior; as a result, we conduct these
+two analyses to assess publication bias separately for both conditions.
+
+\subsection{Meta-analysis}\label{meta-analysis}
+
+The models reported are hierarchical random-effects models (infant
+groups nested within papers) of variance-weighted effect sizes with the
+R {[}@R{]} package metafor {[}@metafor{]}. To investigate how
+development impacts mispronunciation sensitivity, our core theoretical
+question, we introduce age (centered; continuous and measured in days
+but transformed into months for ease of reading by dividing by 30.44) as
+a moderator to our main model. For the subsequent investigations of
+experimental characteristics, we introduce each characteristic as a
+moderator (more detail below).
+
+{[}CHRISTINA: Let's both reread the full paper once it is ready and
+check that this is properly motivated and whether we do need to list
+them all. For now I think the last sentence is fine, but I would tend to
+prefer a reminder for the forgetful reader.{]}{[}KATIE: that's
+reasonable! We had just listed everything 7 paragraphs before, which
+doesn't seem like a lot of \enquote{space}.{]}
+
+\section{Results}\label{results}
+
+\subsection{Publication Bias}\label{publication-bias-1}
+
+Figure 1 shows the funnel plots for both correct pronunciations and
+mispronunciations (code adapted from Sakaluk, 2016). Funnel plot
+assymmetry was significant for both correct pronunciations (Kendall's
+\(\tau\) = 0.53, \emph{p} \textless{} .001) and mispronunciations
+(Kendall's \(\tau\) = 0.16, \emph{p} = 0.004). These results,
+quantifying the assymmetry in the funnel plots (Figure 1), indicate bias
+in the literature. This is particularly evident for correct
+pronunciations, where larger effect sizes have greater variance (bottom
+right corner) and there are a smaller number of more precise effect
+sizes (i.e.~smaller variance) than expected (top left, outside the
+triangle).
+
+{[}CHRISTINA: If we want to interpret here, how about the next
+bit.{]}{[}KATIE: YES! This is an excellent point!!!{]}
+
+The stronger publication bias for correct pronunciation might reflect
+the status of this condiction as a control. If infants were not looking
+to the target picture after hearing the correct label, the overall
+experiment design is called into questions. However, due to the small
+effect and sample sizes (which we will discuss in the following sections
+in more detail) one would expect the regular occurrence of null results
+even though as a population infants would reliably show the expected
+object identification effect.
+
+We should also point out that funnel plot asymmetry can be caused by
+multiple factors beside publication bias. The funnel plot asymmetry may
+also reflect heterogeneity in the data, perhaps due to some studies
+investigating more subtle effects than other studies. {[}CHRISTINA: I
+have to add some bits here.{]}
+
+\subsection{Figure 1}\label{figure-1}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{Paper_Analyses_files/figure-latex/FunnelCombo-1.pdf}
+\caption{}
+\end{figure}
+
+\begin{verbatim}
+## [1] TRUE
+\end{verbatim}
+
+\begin{verbatim}
+## [1] TRUE
+\end{verbatim}
+
+We next examined the p-curves for significant values from the correctly
+pronounced and mispronounced conditions. The p-curve based on 72
+statistically significant values for correct pronunciations indicates
+that the data contain evidential value (Z = -17.93, \emph{p} \textless{}
+.001) and there is no evidence of a large proportion of p-values just
+below the typical alpha threshold of .05. The p-curve based on 36
+statistically significant values for mispronunciations indicates that
+the data contain evidential value (Z = -6.81, \emph{p} \textless{} .001)
+and there is no evidence of a large proportion of p-values just below
+the typical alpha threshold of .05.
+
+{[}CHRISTINA: CAn you add the stats for the non-sig results?{]}{[}KATIE:
+Are there stats that can be computed on the non-sig results? Or do you
+just want an n for significant and non-significant studies?{]}
+
+Taken together, the results suggest a tendency in the literature towards
+publication bias. As a result, our meta-analysis may systematically
+overestimate effect sizes and we therefore interpret all estimates with
+caution. Yet, the p-curve analysis suggests that overall, the literature
+contains evidential value, reflecting a \enquote{real} effect. We
+therefore continue our meta-analysis.
+
+\subsection{Meta-analysis}\label{meta-analysis-1}
+
+\subsubsection{Object Identification for Correct and Mispronounced
+Words}\label{object-identification-for-correct-and-mispronounced-words}
+
+We first calculated the meta-analytic effect for object identification,
+i.e.~looks to the target image in response to correctly pronounced
+words. The variance-weighted meta-analytic effect size Hedges' \emph{g}
+was 0.91 (SE = 0.12) which was significantly different from zero (95\%
+CI {[}0.67, 1.14{]}, \emph{p} \textless{} .001). This is a rather large
+effect size (according to the criteria set by Cohen, 1988; see also
+Bergmann, et al., 2018; for comparative meta-analytic effect sizes in
+language acquisition research). That the effect size is significantly
+above zero suggests that when presented with the correctly pronounced
+label, infants fixated the corresponding object. Our analysis of funnel
+plot asymmetry, however, found evidence for publication bias, which
+might lead to an overestimated effect sizes as smaller, non-significant
+results might not be published. Although the effect size Hedges'
+\emph{g} may be overestimated for object identification in response to
+correctly pronounced words, the p-curve results and a CI lower bound of
+0.67 suggests that this result is robust even when correcting for
+publication bias. In other words, we are confident that the true
+population mean lies above zero for object recognition of correctly
+pronounced words.
+
+{[}CHRISTINA: Can you explain what the CI lower bound means here? I
+don't follow.{]}{[}KATIE: What do you think about this? The CI lower
+bound stuff here actually comes from something you wrote, so tell me
+whether its correct.{]}
+
+We then calculated the meta-analytic effect for object identification in
+response to mispronounced words. In this case, the variance-weighted
+meta-analytic effect size Hedges' \emph{g} was 0.25 (SE = 0.06) which
+was also significantly different from zero (95\% CI {[}0.13, 0.37{]},
+\emph{p} \textless{} .001). This is considered a small effect size
+(Cohen, 1988), but significantly above zero, which suggests that even
+when presented with a mispronounced label, infants fixated the correct
+object. In other words, infants are able to resolve mispronunciations, a
+key skill in language processing We again note the publication bias
+(which was smaller in this condition), and the possibility that the
+effect size Hedges' \emph{g} may be overestimated. But, as the p-curve
+indicated evidential value, we are confident in the overall patterns,
+namely that infants fixate the target even after hearing a mispronounced
+label.
+
+Heterogeneity was significant for both correctly pronounced (Q(103) =
+625.63, \emph{p} \textless{} .001) and mispronounced words, (Q(146) =
+462.51, \emph{p} \textless{} .001). This indicated that the sample
+contains unexplained variance leading to significant difference across
+our studies beyond what is to be expected based on random sampling
+error. We therefore continue with our moderator analysis.
+
+\subsubsection{Mispronunciation Sensitivity Meta-analytic
+Effect}\label{mispronunciation-sensitivity-meta-analytic-effect}
+
+The above two analyses considered the data from mispronounced and
+correctly pronounced words separately. To evaluate mispronunciation
+sensitivity, we compared the effect size Hedges' \emph{g} for correct
+pronunciations with mispronunciations directly, merging the two
+datasets. The moderator test was significant, QM(1) = 215.76, \emph{p}
+\textless{} .001. Hedges' \emph{g} for mispronunciation sensitivity was
+0.50 (SE = 0.03), which indicated that the responses across conditions
+were significantly different (95\% CI {[}0.43, 0.56{]}, \emph{p}
+\textless{} .001). This confirms that although infants fixate the
+correct object for both correct pronunciations and mispronunciations,
+the observed fixations to target (as measured by the effect sizes) were
+significantly greater for correct pronunciations. In other words, we
+observe a significant difference between the two conditions and can now
+quantify the modulation of fixation behavior in terms of standardized
+effect sizes.
+
+\subsubsection{Object Recognition and Mispronunciation Sensitivity
+Modulated by
+Age}\label{object-recognition-and-mispronunciation-sensitivity-modulated-by-age}
+
+To evaluate the different predictions we laid out in the introduction
+for how mispronunciation sensitivity will change as infants develop, we
+next added the moderator age (centered, in days). In the first analyses,
+we investigate the impact of age separately on conditions where words
+were either pronounced correctly or not. Age did not significantly
+modulate object identification in response to correctly pronounced
+(QM(1) = 0.68, \emph{p} = 0.41) or mispronounced words (QM(1) = 1.72,
+\emph{p} = 0.19). The lack of a significant modulation together with the
+small estimates indicates that there was no relationship between age and
+target looks in response to a correctly pronounced or mispronounced
+label. This relationship is plotted in Figure 2.
+
+{[}CHRISTINA{]} CAN YOU ADD ESTIMATES AND THEIR CIS?? Ideally everywhere
+where you report a p-value {[}KATIE: Do you know how to calculate
+Estimates and CIs for the Test of Moderators? Or do you mean reporting
+the estimates and CIs even when the moderator test is not
+significant?{]}
+
+We then examined the interaction between age and mispronunciation
+sensitivity (correct vs.~mispronounced words) in our whole dataset. The
+moderator test was significant (QM(3) = 218.62, \emph{p} \textless{}
+.001). This result is in line with the general observation that as
+infants mature they become better at language processing. The
+interaction between age and mispronunciation sensitivity, however, was
+not significant \(\beta\) = 0.00, (SE = 0.01, 95\% CI {[}-0.01, 0.02{]},
+\emph{p} = 0.731), suggesting that as infants age, their
+mispronunciation sensitivity remains the same.
+
+\subsection{Figure 2}\label{figure-2}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{Paper_Analyses_files/figure-latex/PlotMPEffect-1.pdf}
+\caption{}
+\end{figure}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
+
+\subsubsection{Vocabulary Size: Correlation Between Mispronunciation
+Sensitivity and
+Vocabulary}\label{vocabulary-size-correlation-between-mispronunciation-sensitivity-and-vocabulary}
+
+Of the 32 papers included in the meta-analysis, 8 (comprehension = 7
+papers; production = 1) analyzed the relationship between vocabulary
+scores and mispronunciation sensitivity. There is reason to believe that
+production data are different from comprehension data (the former being
+easier to estimate for parents in the typical questionnaire-based
+assessment), so we analyze this data separately.
+
+{[}KATIE{]} I DON'T KNOW HOW TO INTERPRET THESE RESULTS\ldots{} THE
+FIXED EFFECTS MODEL ISN'T SIGNIFICANT FOR ANY OF THESE. IS THAT
+MEANINGFUL? {[}CHRISTINA{]} SO WE DON'T WANT TO INTERPRET THE FIXED
+EFFECTS MODEL AT ALL, IT IS NOT SUITABLE BECAUSE THERE IS VARIANCE
+BETWEEN EVERY RECORD (LANGUAGE ETC). I WOULD INTERPRET THE OVERALL
+CORRELATION AND THE CI, NOT THE P-VALUE (IN GENERAL). I ALSO WONDER
+WHETHER WE SHOULD MOVE THE SUBSET ANALYSES TO THE SUPPLEMENTARY
+MATERIALS AND JUST SAY OVERALL WE SEE NO RELATIONSHIPS AND CORRELATION
+COEFFICIENTS CONSISTENYL BELOW .1 WE THEREFORE MUST CONCLUDE THAT WITHIN
+NARROW AGE GROUPS VOCABULARY DOES NOT INFLUENCE ANYTHING WE LOOK AT. WE
+CANNOT DO THIS ANALYSIS FPOR MP SENSITIVITY BECAUSE WE DON'T HAVE THE
+NECESSARY RAW DATA. {[}KATIE: Ah, so because for each paper the
+correlation and CI values straddle 0, this indicates that there really
+isn't much evidence for a relationship? I think it could make sense to
+add this to supplementary materials. Over the summer, I had also played
+around with looking at how collection of vocabulary data has dropped off
+over the years, even though more mispronunciation studies have been
+published. That might be something interesting to add. If we truly think
+that this is what is driving the development of mispronunciation
+sensitivity, then why are people not collecting this data?{]} (BUT I
+WONDER WHETHER WECOULD ENCODE THE REPORTED INTERACTION TERMS AND THE
+CORRELATION AND THEN DO SOMETHING WITH THAT?) {[}KATIE: I'm not really
+sure what you mean by this :({]}
+
+\begin{verbatim}
+##                                      COR            95%-CI %W(fixed)
+## Zesiger et al. (2012)             0.0610 [-0.3553; 0.4773]       5.8
+## Zesiger et al. (2012)            -0.1590 [-0.5663; 0.2483]       6.1
+## Mani, Coleman, & Plunkett (2008)  0.0300 [-0.2271; 0.2871]      15.2
+## Swingley & Aslin (2000)           0.1050 [-0.1564; 0.3664]      14.7
+## Mani & Plunkett 2007             -0.1700 [-0.5234; 0.1834]       8.0
+## Mani & Plunkett 2007             -0.1700 [-0.5175; 0.1775]       8.3
+## Swingley & Aslin (2002)           0.1410 [-0.2432; 0.5252]       6.8
+## Swingley & Aslin (2002)           0.1410 [-0.2596; 0.5416]       6.3
+## Swingley 2003                     0.3400 [ 0.0470; 0.6330]      11.7
+## Swingley 2003                     0.0600 [-0.3472; 0.4672]       6.1
+## Hojen et al.                      0.2220 [-0.2591; 0.7031]       4.3
+## Hojen et al.                      0.4820 [ 0.0935; 0.8705]       6.7
+##                                  %W(random)
+## Zesiger et al. (2012)                   6.2
+## Zesiger et al. (2012)                   6.5
+## Mani, Coleman, & Plunkett (2008)       13.7
+## Swingley & Aslin (2000)                13.4
+## Mani & Plunkett 2007                    8.3
+## Mani & Plunkett 2007                    8.5
+## Swingley & Aslin (2002)                 7.2
+## Swingley & Aslin (2002)                 6.7
+## Swingley 2003                          11.2
+## Swingley 2003                           6.5
+## Hojen et al.                            4.8
+## Hojen et al.                            7.0
+## 
+## Number of studies combined: k = 12
+## 
+##                         COR            95%-CI    z p-value
+## Fixed effect model   0.0897 [-0.0105; 0.1900] 1.75  0.0795
+## Random effects model 0.0893 [-0.0212; 0.1999] 1.58  0.1132
+## 
+## Quantifying heterogeneity:
+## tau^2 = 0.0060; H = 1.09 [1.00; 1.50]; I^2 = 15.7% [0.0%; 55.4%]
+## 
+## Test of heterogeneity:
+##      Q d.f. p-value
+##  13.05   11  0.2899
+## 
+## Details on meta-analytical method:
+## - Inverse variance method
+## - DerSimonian-Laird estimator for tau^2
+## - Untransformed correlations
+\end{verbatim}
+
+\begin{verbatim}
+##                                      COR            95%-CI %W(fixed)
+## Zesiger et al. (2012)            -0.0090 [-0.4268; 0.4088]       5.0
+## Zesiger et al. (2012)            -0.1720 [-0.5775; 0.2335]       5.3
+## Mani, Coleman, & Plunkett (2008)  0.0700 [-0.1861; 0.3261]      13.2
+## Mani & Plunkett 2007             -0.1100 [-0.4696; 0.2496]       6.7
+## Mani & Plunkett 2007             -0.1100 [-0.4635; 0.2435]       6.9
+## Swingley & Aslin (2002)           0.1820 [-0.1970; 0.5610]       6.0
+## Swingley & Aslin (2002)           0.1820 [-0.2131; 0.5771]       5.6
+## Swingley 2003                     0.1800 [-0.1406; 0.5006]       8.4
+## Swingley 2003                     0.0700 [-0.3367; 0.4767]       5.2
+## Ramon-Casas et al. 2009           0.0980 [-0.3068; 0.5028]       5.3
+## Ramon-Casas et al. 2009          -0.1470 [-0.5468; 0.2528]       5.4
+## Ramon-Casas et al. 2009          -0.2300 [-0.6171; 0.1571]       5.8
+## Ramon-Casas et al. 2009           0.2400 [-0.1451; 0.6251]       5.9
+## Ramon-Casas et al. 2009           0.4350 [ 0.1037; 0.7663]       7.9
+## Hojen et al.                      0.2220 [-0.2591; 0.7031]       3.7
+## Hojen et al.                     -0.1480 [-0.6430; 0.3470]       3.5
+##                                  %W(random)
+## Zesiger et al. (2012)                   5.0
+## Zesiger et al. (2012)                   5.3
+## Mani, Coleman, & Plunkett (2008)       13.2
+## Mani & Plunkett 2007                    6.7
+## Mani & Plunkett 2007                    6.9
+## Swingley & Aslin (2002)                 6.0
+## Swingley & Aslin (2002)                 5.6
+## Swingley 2003                           8.4
+## Swingley 2003                           5.2
+## Ramon-Casas et al. 2009                 5.3
+## Ramon-Casas et al. 2009                 5.4
+## Ramon-Casas et al. 2009                 5.8
+## Ramon-Casas et al. 2009                 5.9
+## Ramon-Casas et al. 2009                 7.9
+## Hojen et al.                            3.7
+## Hojen et al.                            3.5
+## 
+## Number of studies combined: k = 16
+## 
+##                         COR            95%-CI    z p-value
+## Fixed effect model   0.0601 [-0.0331; 0.1533] 1.26  0.2061
+## Random effects model 0.0601 [-0.0331; 0.1533] 1.26  0.2061
+## 
+## Quantifying heterogeneity:
+## tau^2 = 0; H = 1.00 [1.00; 1.42]; I^2 = 0.0% [0.0%; 50.7%]
+## 
+## Test of heterogeneity:
+##      Q d.f. p-value
+##  14.51   15  0.4870
+## 
+## Details on meta-analytical method:
+## - Inverse variance method
+## - DerSimonian-Laird estimator for tau^2
+## - Untransformed correlations
+\end{verbatim}
+
+\begin{verbatim}
+##                              COR             95%-CI %W(fixed) %W(random)
+## Bailey & Plunkett (2002)  0.0630 [-0.3441;  0.4701]       2.5        2.7
+## Bailey & Plunkett (2002) -0.0660 [-0.4729;  0.3409]       2.5        2.7
+## Bailey & Plunkett (2002)  0.0630 [-0.3441;  0.4701]       2.5        2.7
+## Bailey & Plunkett (2002) -0.0660 [-0.4729;  0.3409]       2.5        2.7
+## Bailey & Plunkett (2002)  0.0630 [-0.3441;  0.4701]       2.5        2.7
+## Bailey & Plunkett (2002) -0.0660 [-0.4729;  0.3409]       2.5        2.7
+## Bailey & Plunkett (2002)  0.0630 [-0.3441;  0.4701]       2.5        2.7
+## Bailey & Plunkett (2002) -0.0660 [-0.4729;  0.3409]       2.5        2.7
+## Swingley (2009)          -0.1200 [-0.3715;  0.1315]       6.4        5.6
+## Swingley (2009)           0.1300 [-0.1957;  0.4557]       3.8        3.8
+## Swingley & Aslin (2000)   0.4210 [ 0.2036;  0.6384]       8.6        6.7
+## Mani & Plunkett 2007     -0.0590 [-0.4349;  0.3169]       2.9        3.0
+## Mani & Plunkett 2007     -0.0590 [-0.4349;  0.3169]       2.9        3.0
+## Mani & Plunkett 2007     -0.1700 [-0.5234;  0.1834]       3.3        3.3
+## Mani & Plunkett 2007     -0.1700 [-0.5175;  0.1775]       3.4        3.4
+## Mani & Plunkett 2007      0.1000 [-0.2667;  0.4667]       3.0        3.2
+## Mani & Plunkett 2007     -0.2800 [-0.6214;  0.0614]       3.5        3.5
+## Mani & Plunkett 2007     -0.0700 [-0.3354;  0.1954]       5.8        5.2
+## Mani & Plunkett 2007      0.1000 [-0.1641;  0.3641]       5.8        5.2
+## Swingley & Aslin (2002)   0.1750 [-0.2050;  0.5550]       2.8        3.0
+## Swingley & Aslin (2002)   0.1750 [-0.2212;  0.5712]       2.6        2.8
+## Mani & Plunkett 2010     -0.3500 [-0.6640; -0.0360]       4.1        4.0
+## Swingley 2003             0.1500 [-0.1738;  0.4738]       3.9        3.8
+## Swingley 2003             0.1500 [-0.1738;  0.4738]       3.9        3.8
+## Swingley 2003             0.0600 [-0.3472;  0.4672]       2.4        2.7
+## Swingley 2003             0.0600 [-0.3472;  0.4672]       2.4        2.7
+## Hojen et al.             -0.0510 [-0.5557;  0.4537]       1.6        1.8
+## Hojen et al.              0.0510 [-0.4537;  0.5557]       1.6        1.8
+## Hojen et al.              0.0600 [-0.4442;  0.5642]       1.6        1.8
+## Hojen et al.             -0.0600 [-0.5642;  0.4442]       1.6        1.8
+## Tao et al. 2012           0.5700 [ 0.1710;  0.9690]       2.6        2.7
+## 
+## Number of studies combined: k = 31
+## 
+##                         COR            95%-CI    z p-value
+## Fixed effect model   0.0377 [-0.0260; 0.1014] 1.16  0.2465
+## Random effects model 0.0322 [-0.0399; 0.1043] 0.87  0.3818
+## 
+## Quantifying heterogeneity:
+## tau^2 = 0.0079; H = 1.11 [1.00; 1.39]; I^2 = 19.3% [0.0%; 48.4%]
+## 
+## Test of heterogeneity:
+##      Q d.f. p-value
+##  37.18   30  0.1719
+## 
+## Details on meta-analytical method:
+## - Inverse variance method
+## - DerSimonian-Laird estimator for tau^2
+## - Untransformed correlations
+\end{verbatim}
+
+\begin{verbatim}
+##                             COR             95%-CI %W(fixed) %W(random)
+## Swingley (2009)          0.0700 [-0.1839;  0.3239]       6.4        5.4
+## Swingley (2009)          0.1600 [-0.1628;  0.4828]       3.9        3.8
+## Mani & Plunkett 2007    -0.2820 [-0.6292;  0.0652]       3.4        3.4
+## Mani & Plunkett 2007    -0.2820 [-0.6292;  0.0652]       3.4        3.4
+## Mani & Plunkett 2007    -0.1100 [-0.4696;  0.2496]       3.2        3.3
+## Mani & Plunkett 2007    -0.1100 [-0.4635;  0.2435]       3.3        3.3
+## Mani & Plunkett 2007     0.2300 [-0.1208;  0.5808]       3.3        3.4
+## Mani & Plunkett 2007     0.2200 [-0.1325;  0.5725]       3.3        3.4
+## Mani & Plunkett 2007    -0.2700 [-0.5173; -0.0227]       6.7        5.5
+## Mani & Plunkett 2007    -0.0590 [-0.3248;  0.2068]       5.8        5.0
+## Swingley & Aslin (2002)  0.0290 [-0.3627;  0.4207]       2.7        2.8
+## Swingley & Aslin (2002)  0.0290 [-0.3793;  0.4373]       2.5        2.7
+## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
+## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
+## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
+## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
+## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
+## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
+## Swingley 2003            0.1500 [-0.1738;  0.4738]       3.9        3.8
+## Swingley 2003            0.1500 [-0.1738;  0.4738]       3.9        3.8
+## Swingley 2003            0.0700 [-0.3367;  0.4767]       2.5        2.7
+## Swingley 2003            0.0700 [-0.3367;  0.4767]       2.5        2.7
+## Ramon-Casas et al. 2009  0.0980 [-0.3068;  0.5028]       2.5        2.7
+## Ramon-Casas et al. 2009 -0.1470 [-0.5468;  0.2528]       2.6        2.7
+## Ramon-Casas et al. 2009 -0.2300 [-0.6171;  0.1571]       2.7        2.9
+## Ramon-Casas et al. 2009  0.2400 [-0.1451;  0.6251]       2.8        2.9
+## Ramon-Casas et al. 2009  0.4350 [ 0.1037;  0.7663]       3.7        3.7
+## Hojen et al.            -0.0510 [-0.5557;  0.4537]       1.6        1.8
+## Hojen et al.             0.0510 [-0.4537;  0.5557]       1.6        1.8
+## Hojen et al.             0.0790 [-0.4239;  0.5819]       1.6        1.9
+## Hojen et al.            -0.0790 [-0.5819;  0.4239]       1.6        1.9
+## 
+## Number of studies combined: k = 31
+## 
+##                          COR            95%-CI     z p-value
+## Fixed effect model   -0.0402 [-0.1043; 0.0238] -1.23  0.2181
+## Random effects model -0.0393 [-0.1127; 0.0340] -1.05  0.2931
+## 
+## Quantifying heterogeneity:
+## tau^2 = 0.0094; H = 1.13 [1.00; 1.42]; I^2 = 22.0% [0.0%; 50.1%]
+## 
+## Test of heterogeneity:
+##      Q d.f. p-value
+##  38.45   30  0.1386
+## 
+## Details on meta-analytical method:
+## - Inverse variance method
+## - DerSimonian-Laird estimator for tau^2
+## - Untransformed correlations
+\end{verbatim}
+
+\subsubsection{Interim Discussion}\label{interim-discussion}
+
+The main goal of this paper was to assess mispronunciation sensitivity
+and its maturation with age. The results are clear: Although infants
+consider a mispronunciation as a better match with the target image than
+a distractor image, there was a consistent effect of mispronunciation
+sensitivity. This did not change with development. Of the 3 predictions
+and assumptions about the development of infants' sensitivity to
+mispronunciations discussed in the Introduction, the present results
+lend some support for the argument that mispronunciation sensitivity
+stays consistent as infants develop. This runs counter to existing
+theories of phono-lexical development, which predict either an increase
+(PRIMR ref) or decrease (Assim Model ref) in mispronunciation
+sensitivity.
+
+{[}KATIE{]} CAN A CONCLUSION BE DRAWN FROM THE VOCABULARY RESULTS? IF
+SO, THIS IS THE PARAGRAPH
+
+In sum, it seems that current theories of infants' phono-lexical
+development cannot fully capture our results and should be reconsidered
+with all the evidence in mind.
+
+Alternatively, the lack of developmental change in mispronunciation
+sensitivity could be due to differences in the types of tasks given to
+infants of different ages. To examine this possibility, we include an
+exploratory analysis of whether different moderators and experimental
+design features were included at different ages, in addition to
+investigating the role that these moderators play in mispronunciation
+sensitivity.
+
+\subsection{Moderator Analyses}\label{moderator-analyses}
+
+{[}cHRISTINA{]} I WOULD FOLLOW THE OUTLINE IN THE PREVIOUS PARAGRAPH
+HERE OR FLIP THE PARAGRAPH AROUND: 1. ARE DIFFERENT MODERATORS USED AT
+DIFFERENT AGES? TEST: sIMPLE CHI-SQUARED OF AGE GROUP VERSUS MODERATOR
+ASSIGNMENT (AGE GROUP DETERMINED BY LOOKING AT THE YOUNGEST AGE FOR X?)
+2. WHICH MODERATORS INFLUENCE MP SENSITIVITY TEST SIMPLE MA WITH
+MODERATOR TESTS
+
+OR \enquote{FOR EACH POSSIBLE MODERATOR WHICH COULD INFLIENCE MP
+SENSITIVITY, WE FIRST TEST THIS POSSIBILITY AND THEN EVALUATE WHETHER
+THERE IS A SYSTEMATIC DIFFERENCE OF MANIPULATING THESE MODERATORS AS
+INFANTS MATURE, I.E. WHETHER OLDER INFANTS ARE TESTED ON A MORE
+DIFFICULT TASK} ALSO, AS FINAL FOLLOW-UP IT WOULD BE PERFECT TO JUST
+SUBSET ALL STUDIES WITH FAMILIAR DISTRACTORS, SAME NUMBER OF FEATURES,
+AND CHECK THAT OUR CONCLUSIONS HOLD UP REGARING MP SENSITIVITY
+
+{[}KATIE: I prefer this second option, first looking at the moderators
+in general and then looking at whether there is this systematic
+difference with age. The latter is exploratory, so I feel like this
+information should not preceed our planned analyses.{]}
+
+\subsubsection{Number of features
+changed}\label{number-of-features-changed}
+
+To assess whether the number of features changed modulates
+mispronunciation sensitivity, we calculated the meta-analytic effect for
+object identification in response to words that were pronounced
+correctly and mispronounced using 1-, 2-, and 3-feature changes. We did
+not include data for which the number of features changed in a
+mispronunciation was not specified or the number of features changed was
+not consistent (e.g., one mispronunciation included a 2-feature change
+whereas another only a 1-feature change). This analysis was therefore
+based on a subset of the overall dataset, with 81 experimental
+conditions for correct pronunciations, 108 for 1-feature
+mispronunciations, 16 for 2-feature mispronunciations, and 6 for
+3-feature mispronunciations. Each feature change (from 0 to 3; 0
+representing correct pronunciations) was considered to have an equal
+impact on mispronunciation sensitivity, following the argument of graded
+sensitivity (White \& Aslin, 2008; Mani \& Plunkett 2011).
+
+To understand the relationship between number of features changed and
+mispronunciation sensitivity, we evaluated the effect size Hedges'
+\emph{g} with number of features changed as a moderator. The moderator
+test was significant, QM(1) = 76.10, \emph{p} \textless{} .001. Hedges'
+\emph{g} for number of features changed was -0.12 (SE = 0.01), which
+indicated that as the number of features changed increased, the effect
+size Hedges' \emph{g} significantly decreased (95\% CI {[}-0.15,
+-0.10{]}, \emph{p} \textless{} .001). We plot this relationship in
+Figure X. This confirms previous findings of a graded sensitivity to the
+number of features changed for both consonant (White \& Morgan, 2008)
+and vowel (Mani \& Plunkett, 2011) mispronunciations as well as the
+importance of controlling for the degree of phonological mismatch in
+experimental design.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{Paper_Analyses_files/figure-latex/PlotFeatEffect-1.pdf}
+\caption{}
+\end{figure}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
+
+Although we did not have any specific predictions about the relationship
+between infant age and the impact of number of features changed on
+mispronunciation sensitivity, we included an exploratory analysis to
+examine this relationship. When age was also included as a moderator,
+the moderator test was significant, QM(3) = 81.11, \emph{p} \textless{}
+.001, but the interaction between age and number of features changed was
+not significant, \(\beta\) = 0.01, (SE = 0.00, 95\% CI {[}0, 0.01{]},
+\emph{p} = 0.069). This suggests that there is no relationship between
+infant age the impact of number of features changed on mispronunciation
+sensitivity.
+
+Although all papers included in the dataset also included correct
+pronunciations, not all papers included all three types of feature
+changes (i.e.~1-3). The age range for each type of number of features
+changed was 372.89 - 920.20 days (\emph{M} = 637.40) for 1-feature
+mispronunciations, 377.28 - 920.20 days (\emph{M} = 612.17) for
+2-feature mispronunciations, and 544.48 - 920.20 days (\emph{M} =
+661.64) for 3-feature mispronunciations. Focusing on the ages where all
+three numbers of features changed were tested (i.e.~544.48 - 920.20
+days), however, did not change the pattern of results.
+
+\subsubsection{Distractor familiarity}\label{distractor-familiarity}
+
+We next assessed whether distractor familiarity has an impact on the
+size of mispronunciation sensitivity. First, we calculated the
+meta-analytic effect for object identification in response to
+mispronounced target words/images that were paired with either a
+familiar or an unfamiliar distractor image. The moderator test was not
+significant QM(1) = 0.43, \emph{p} = 0.513. This suggests that upon
+hearing a mispronunciation, infants looks to the target image were
+similar for when the target image was paired with an image of a familiar
+or unfamiliar object. We next assessed whether distractor familiarity
+was related to mispronunciation sensitivity. We merged the two datasets
+and included condition (correct pronunciation, mispronunciation) as an
+additional moderator. The moderator test was significant, QM(3) =
+219.46, \emph{p} \textless{} .001, but the interaction between
+distractor familiarity and condition was not significant \(\beta\) =
+0.14, (SE = 0.08, 95\% CI {[}-0.02, 0.30{]}, \emph{p} = 0.08). These
+results suggest that overall, infants' familiarity with the distractor
+object (familiar or unfamiliar) did not impact their mispronunciation
+sensitivity.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{Paper_Analyses_files/figure-latex/PlotDistFamEffect_NoAge-1.pdf}
+\caption{}
+\end{figure}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
+
+We next examined whether age modulates object recognition or
+mispronunciation sensitivity when the distractor image is familiar or
+unfamiliar. For object recognition in response to a mispronunciation,
+including age as a moderator resulted in a moderator test that was not
+significant, QM(3) = 3.25, \emph{p} = 0.355. {[}CHRISTINA{]} I WORRY A
+LOT AT THESE POINTS THAT THIS IS THE WHOLE P\textgreater{}.05 = NULL IS
+TRUE FALLACY. WE CAN NEVER HAVE EVIDENCE FOR THE NULL HYPOTHESIS. SO
+BETTER ITNERPRET ESTIMATES AND CIS.
+
+This suggests that upon hearing a mispronunciation, infants looks to the
+target image were similar for when the target image was paired with an
+image of a familiar or unfamiliar object, regardless of their age. We
+next assessed whether the relationship between distractor familiarity
+and mispronunciation sensitivity was modulated by age. We merged the two
+datasets and included condition (correct pronunciation,
+mispronunciation) as well as age as additional moderators. The moderator
+test was significant, QM(7) = 224.96, \emph{p} \textless{} .001.
+Although the three-way-interaction between condition, distractor
+familiarity, and age was not significant (\(\beta\) = -0.02, SE = 0.02,
+95\% CI {[}-0.06, 0.02{]}, \emph{p} = 0.305), here the interaction
+between condition and distractor familiarity was significant (\(\beta\)
+= 0.18, SE = 0.09, 95\% CI {[}0, 0.35{]}, \emph{p} = 0.05).
+
+{[}KATIE{]} WHAT DOES IT MEAN THAT IN THIS LAST TEST THERE WAS AN
+INTERACTION BETWEEN CONDITION AND DISTRACTOR FAMILIARITY, WHEN AGE WAS
+INCLUDED AS A MODERATOR? DOES THAT MEAN THAT AGE IS CONTROLLED FOR?
+UNDERSTANDING THIS WILL HELP ME FORMULATE THE CONCLUSION SENTENCE AND
+MOTIVATE THE NEXT SET OF ANALYSES.
+
+{[}CHRISTINA{]} I WOULD NOT OVERINTERPRET IT, THE ESTIMATE DID NOT
+DRAMATICALLY CHANGE, AND IT IS BARELY SIGNIFICANT. DOES THAT HELP?
+
+{[}KATIE: I think so. I've just removed that part{]}
+
+\begin{verbatim}
+##                       Test                            Results
+## 1 Welch Two Sample t-test: t(153.83) = 5.30, p < .001, d = NA
+\end{verbatim}
+
+Although we anticipated that older children may be more impacted by the
+presence of a unfamiliar compared to familiar distractor image, we found
+that age and distractor familiarity did not impact mispronunciation
+sensitivity. Inspection of the ages tested using different kinds of
+distractors, however, revealed differences. Infants tested using a
+familiar distractor were younger (M = 588.76 days, SD = 136.47, range =
+207.8 - 768 days) than those infants tested using an unfamiliar
+distractor (M = 678.85 days, SD = 115.47, range = 544.48 - 920.2 days),
+which a two-sample t-test revealed to be a significant difference,
+t(153.83) = 5.30, p \textless{} .0001.
+
+{[}CHRISTINA{]} CAN YOU TURN THE NUMBERS INTO R CODE HERE? aLSO, NOT
+SURE WE NEED A T-TEST TO CONFIRM THE OBVIOUS.
+
+{[}KATIE{]} SO, IS IT OKAY TO DO THE AGE SUBSET ANALYSIS AFTER THIS?
+SOMETHING LIKE \enquote{TO ENSURE THAT THE LACK OF A DIFFERENCE WASN'T
+DUE TO THE DIFFERENCE IN AGES OF INFANTS TESTED WITH DIFFERENT TYPES OF
+DISTRACTORS, WE ANALYZED A SUBSET OF PAPERS THAT TESTED AGES WHERE BOTH
+FAMILIAR AND UNFAMILIAR DISTRACTORS WERE USED.} IN THE SUBSET ANALYSIS,
+FOR MISP SENSITIVITY, THERE IS A SIGNIFICANT INTERACTION BETWEEN
+DISTRACTOR FAMILIARITY AND CONDITION.
+
+{[}CHRISTINA{]} YES!!!!!!
+
+\subsubsection{Phonological overlap between target and
+distractor}\label{phonological-overlap-between-target-and-distractor}
+
+To assess whether phonological overlap between the target and distractor
+image labels has an impact on the size of mispronunciation sensitivity,
+we examined the meta-analytic effect for object identification in
+response to mispronunciations and mispronunciation sensitivity when the
+target-distractor pairs either shared the same onset phoneme, had no
+overlap, or where the distractor was an unfamiliar object. We did not
+include data for which the overlap included both the onset and medial
+phonemes (\emph{n} = 4) or coda phonemes (\emph{n} = 3). The analysis
+was therefore based on a subset of the overall dataset, with 104
+experimental conditions containing onset phoneme overlap between the
+target and distractor, 80 containing no overlap between target and
+distractor, and 60 for targets paired with unfamiliar distractor images.
+There were therfore three possibilities for distractor overlap: onset
+phoneme overlap, no overlap, and an unfamiliar distractor. In our
+analysis, we were interested in the difference between overlap and lack
+of overlap; therefore, experimental conditions containing onset phoneme
+overlap were coded as the reference condition and compared with
+responses to experimental conditions with no overlap or an unfamiliar
+distractor separately.
+
+{[}KATIE{]} CAN YOU CHECK THE WAY THAT I WROTE THE LAST SENTENCE?
+
+{[}CHRISTINA{]} SEEMS OK BUT I AM CONFUSED WHY OVERLAP IS THE BASELINE
+AND WHY YOU BRING IN NOVEL. I THINK YOU NEED TO SPELL THIS OUT MORE.
+
+Regarding object identification in response to mispronunciations, when
+distractor overlap was included as a moderator, the moderator test was
+not significant QM(2) = 1.78, \emph{p} = 0.412. {[}CHRISTINA{]} AGAIN DO
+NOT RELY ON P-VALUES BUT ON ESTIMATES AND CIS This suggests that upon
+hearing a mispronunciation, infants looks to the target image were
+similar for when the target image was paired with a distractor image
+that contained overlap on the onset phoneme or no overlap with the
+target word, or was an unfamiliar object. We next assessed whether
+target-distractor overlap was related to mispronunciation sensitivity.
+We merged the two datasets and included condition (correct
+pronunciation, mispronunciation) as an additional moderator. The
+moderator test was significant, QM(5) = 230.34, \emph{p} \textless{}
+.001. The interaction between condition and target-distractor pairs with
+no overlap was significant (\(\beta\) = -0.25, SE = 0.08, 95\% CI
+{[}-0.40, -0.10{]}, \emph{p} = 0.001), suggesting that mispronunciation
+sensitivity was greater when target-distractor pairs shared the same
+onset phoneme compared to when they shared no phonological overlap. The
+interaction between condition and target-distractor pairs with an
+unfamiliar distractor was also significant (\(\beta\) = 0.19, SE = 0.09,
+95\% CI {[}0.01, 0.37{]}, \emph{p} = 0.042), suggesting that
+mispronunciation sensitivity was smaller when the distractor image
+shared the same onset phoneme as the target image compared to when the
+distractor image was an unfamiliar object. This can be seen in Figure X.
+
+{[}christina{]} I THINK THESE SHOULD BE TWO SEPARATE ANALYSES\ldots{}
+NOVEL IS CONCEPTUALLY DIFFERENT.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{Paper_Analyses_files/figure-latex/PlotDistOverlapEffect-1.pdf}
+\caption{}
+\end{figure}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
+
+Although we did not have any specific predictions about the relationship
+between infant age and the impact of distractor overlap on
+mispronunciation sensitivity, we included an exploratory analysis to
+examine this relationship. First, for object recognition in response to
+mispronunciations, when age in addition to distractor overlap was also
+included as a moderator, the moderator test was not significant, QM(5) =
+5.99, \emph{p} = 0.308, suggesting that upon hearing a mispronunciation,
+infants looks to the target image were similar for the three types of
+overlap, regardless of infant age. We next assessed whether the
+relationship between distractor overlap and mispronunciation sensitivity
+was modulated by age. We merged the two datasets and included condition
+(correct pronunciation, mispronunciation) as well as age as additional
+moderators. The moderator test was significant, QM(11) = 243.40,
+\emph{p} \textless{} .001. The interaction between age, condition, and
+target-distractor pairs with no overlap was significant (\(\beta\) =
+-0.04, SE = 0.02, 95\% CI {[}-0.08, 0.00{]}, \emph{p} = 0.032). As can
+be seen in Figure X, the difference between correct pronunciations and
+mispronunciations (mispronunciation sensitivity) stays steady across
+infant ages for both target words paired with distractors containing
+onset overlap with the target word as well as distractors containing no
+overlap. As infants aged, however, overall recognition (regardless of
+condition) increased for target-distractor pairs containing onset
+overlap, whereas for overall recognition decreased for target-distractor
+pairs containing no overlap. The interaction between age, condition, and
+target-distractor pairs with an unfamiliar distractor was also
+significant (\(\beta\) = -0.05, SE = 0.02, 95\% CI {[}-0.09, 0.00{]},
+\emph{p} = 0.038). As can also be seen in Figure X, mispronunciation
+sensitivity for target words paired with unfamiliar distractors
+decreased with age, while it remained steady across a similar range of
+ages for target words paired with distractors containing onset overlap
+with the target word.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{Paper_Analyses_files/figure-latex/PlotDistOverlap_cond_age-1.pdf}
+\caption{}
+\end{figure}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
+
+\subsubsection{Position of
+mispronunciation}\label{position-of-mispronunciation}
+
+To assess whether the position of the mispronunciation has an impact on
+mispronunciation sensitivity, we calculated the meta-analytic effect for
+object identification in response to mispronunciations on the onset and
+medial phonemes. We did not include data for which the mispronunciation
+was located on the coda (\emph{n} = 10 and NA), varied in regard to
+position (\emph{n} = 3, 29, 8, and NA), or was not reported (\emph{n} =
+10). The analysis was therefore based on a subset of the overall
+dataset, with 143 and NA experimental conditions comparing a
+mispronunciation on the onset phoneme and 48 and NA experimental
+conditions comparing a mispronunciation on the medial phoneme.
+
+Regarding object identification in response to mispronunciations, when
+mispronunciation location was included as a moderator, the moderator
+test was not significant QM(1) = 0.04, \emph{p} = 0.838. This suggests
+that upon hearing a mispronunciation, infants looks to the target image
+were similar for when the mispronunciation was located on the onset or
+medial phonemes. We next assessed whether mispronunciation location was
+related to mispronunciation sensitivity. We merged the two datasets and
+included condition (correct pronunciation, mispronunciation) as an
+additional moderator. The moderator test was significant, QM(3) =
+180.76, \emph{p} \textless{} .001, but the interaction between
+mispronunciation location and condition was not significant \(\beta\) =
+0.05, (SE = 0.09, 95\% CI {[}-0.12, 0.22{]}, \emph{p} = 0.559). These
+results suggest that overall, the location of the mispronunciation
+(onset, medial) did not impact mispronunciation sensitivity.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{Paper_Analyses_files/figure-latex/PlotPositionEffect-1.pdf}
+\caption{}
+\end{figure}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
+
+Although we did not have any specific predictions about the relationship
+between infant age and the impact of mispronuncition location on
+mispronunciation sensitivity, we included an exploratory analysis to
+examine this relationship. First, for object recognition in response to
+mispronunciations, when age in addition to mispronunciation location was
+also included as a moderator, the moderator test was not significant,
+QM(3) = 1.22, \emph{p} = 0.747, suggesting that upon hearing a
+mispronunciation, infants looks to the target image were similar for
+both onset and medial mispronunciations, regardless of infant age. We
+next assessed whether the relationship between mispronunciation location
+and mispronunciation sensitivity was modulated by age. We merged the two
+datasets and included condition (correct pronunciation,
+mispronunciation) as well as age as additional moderators. The moderator
+test was significant, QM(7) = 185.34, \emph{p} \textless{} .001, but the
+interaction between mispronunciation location, age, and condition was
+not significant \(\beta\) = NA, (SE = NA, 95\% CI {[}NA, NA{]}, \emph{p}
+). These results provide further evidence that location of the
+mispronunciation (onset, medial) did not impact mispronunciation
+sensitivity.
+
+\subsubsection{Type of mispronunciation (consonant or
+vowel)}\label{type-of-mispronunciation-consonant-or-vowel}
+
+To assess whether the type of mispronunciation impacts sensitivity to
+mispronunciations, we calculated the meta-analytic effect for object
+identification in response to the type of mispronunciation. Although
+most theoretical discussion of mispronunciation type has focused on
+consonants and vowels, our dataset also included tone mispronunciations.
+In our analysis, we were interested in the difference between consonants
+and vowels, but also include an exploratory analysis of responses to
+tones, consonants, and vowels. We therefore conducted two sets of
+analyses, one analyzing consonants and vowels alone and a second
+comparing responses to tones with that of consonants and vowels,
+separately. For the latter analysis, tones were coded as the reference
+condition. We did not include data for which mispronunciation type
+varied within experiment and was not reported separately (\emph{n} = 21
+and 2). The analysis was therefore based on a subset of the overall
+dataset, with 145 experimental conditions comparing a consonant
+mispronunciation, 71 experimental conditions comparing a vowel
+mispronunciation, and 12 experimental conditions comparing a tone
+mispronunciation. Below, we first report the set of analyses comparing
+consonants with vowels before moving on to the second set of exploratory
+analyses comparing tones with that of consonants and vowels.
+
+{[}KATIE{]} WHAT DO YOU THINK ABOUT THIS? WE HAVE THE TONES AND ITS A
+NOVEL, INTERESTING THING, I THINK, AND PERHAPS WORTH IT TO INCLUDE A
+COMPARISON OF TONES ALONGSIDE THE MORE THEORETICALLY IMPORTANT
+COMPARISON BETWEEN CONSONANTS AND VOWELS.
+
+We first analyzed experimental conditions where mispronunciation type
+was either a consonant or vowel. Regarding object identification in
+response to mispronunciations, when mispronunciation type was included
+as a moderator, the moderator test was not significant QM(1) = 0.15,
+\emph{p} = 0.702. This suggests that upon hearing a mispronunciation,
+infants looks to the target image were similar for when the
+mispronunciation was a consonant or a vowel. We next assessed whether
+type of mispronunciation (consonant or vowel) was related to
+mispronunciation sensitivity. We merged the two datasets and included
+condition (correct pronunciation, mispronunciation) as an additional
+moderator. The moderator test was significant, QM(3) = 145.14, \emph{p}
+\textless{} .001, but the interaction between mispronunciation type and
+condition was not significant \(\beta\) = 0.06, (SE = 0.08, 95\% CI
+{[}-0.10, 0.21{]}, \emph{p} = 0.479). These results suggest that
+overall, the type of mispronunciation (consonant vs.~vowel) did not
+impact mispronunciation sensitivity.
+
+We next examined whether age modulates object recognition or
+mispronunciation sensitivity when the mispronunciation is a consonant or
+vowel. For object recognition in response to a mispronunciation,
+including age as a moderator resulted in a moderator test that was not
+significant, QM(3) = 1.54, \emph{p} = 0.672. This suggests that upon
+hearing a mispronunciation, infants looks to the target image were
+similar for when the mispronunciation was on a consonant or vowel
+phoneme, regardless of their age. We next assessed whether the
+relationship between mispronunciation type (consonant or vowel) and
+mispronunciation sensitivity was modulated by age. We merged the two
+datasets and included condition (correct pronunciation,
+mispronunciation) as well as age as additional moderators. The moderator
+test was significant, QM(7) = 153.79, \emph{p} \textless{} .001. The
+interaction between mispronunciation type, condition, and age was
+significant (\(\beta\) = 0.04, SE = 0.02, 95\% CI {[}0.01, 0.08{]},
+\emph{p} = 0.016). As can be seen in Figure X, as infants age,
+mispronunciation sensitivity grows larger for vowel mispronunciations
+but becomes smaller for consonant mispronunciations. Noticeably,
+mispronunciation sensitivity appears greater for consonant compared to
+vowel mispronunciations at younger ages, but this difference shifts as
+infants age.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{Paper_Analyses_files/figure-latex/PlotCVEffect_cond_age-1.pdf}
+\caption{}
+\end{figure}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
+
+To examine whether infants' native language impacts sensitivity to
+consonant and vowel mispronunciations, we classified infants into
+language families. Infants learning American English (\emph{n} = 56),
+British English (\emph{n} = 66), Danish (\emph{n} = 6), Dutch (\emph{n}
+= 58), and German (\emph{n} = 21) were classified into the Germanic
+language family (\emph{n} = 207). Infants learning Catalan (\emph{n} =
+4), Spanish (\emph{n} = 4), French (\emph{n} = 8), Catalan and Spanish
+simultaneously (i.e.~bilinguals; \emph{n} = 6), and Swiss French
+(\emph{n} = 6) were classified into the Romance language family
+(\emph{n} = 28). For object recognition in response to a
+mispronunciation, including language family as a moderator resulted in a
+moderator test that was not significant, QM(3) = 5.36, \emph{p} = 0.147.
+This suggests that upon hearing a mispronunciation, infants looks to the
+target image were similar for when the mispronunciation was on a
+consonant or vowel phoneme, regardless of the language family of their
+native language. We next assessed whether the relationship between
+mispronunciation type (consonant or vowel) and mispronunciation
+sensitivity was modulated by language family. We merged the two datasets
+and included condition (correct pronunciation, mispronunciation) as well
+as language family as additional moderators. The moderator test was
+significant, QM(7) = 158.89, \emph{p} \textless{} .001. The interaction
+between condition and language family was significant (\(\beta\) = 0.73,
+SE = 0.23, 95\% CI {[}0.27, 1.18{]}, \emph{p} = 0.002), suggesting
+XXXXXXXXXXXXXX. The interaction between mispronunciation type,
+condition, and language family was also significant (\(\beta\) = -0.87,
+SE = 0.28, 95\% CI {[}-1.42, -0.32{]}, \emph{p} = 0.002). As can be seen
+in Figure X, mispronunciation sensitivity for consonants was similar for
+Germanic and Romance languages. Mispronunciation sensitivity for vowels,
+however, was greater for Germanic compared to Romance languages.
+
+{[}KATIE{]} I'M NOT REALLY SURE WHAT THE CONDITION BY LANGUAGE FAMILY
+INTERACTION MEANS. SHOULD WE EVEN INTERPRET IT?
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{Paper_Analyses_files/figure-latex/PlotCVEffect_Lang-1.pdf}
+\caption{}
+\end{figure}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
+
+Finally, we examined the relationship between language family and infant
+age and mispronunciation sensitivity to consonants and vowels. For
+object recognition in response to a mispronunciation, including language
+family and infant age as a moderator resulted in a moderator test that
+was significant, QM(7) = 19.53, \emph{p} = 0.007. The interaction
+between language family, age, and type of mispronunciation (consonant or
+vowel) was significant, (\(\beta\) = 0.73, SE = 0.23, 95\% CI {[}0.27,
+1.18{]}, \emph{p} = 0.002). As can be seen in Figure X, for infants
+learning Germanic languages, increasing age was related to increasing
+mispronunciation sensitivity for vowel mispronunciations, but decreasing
+sensitivity for consonant mispronunciations. In contrast, infants
+learning Romance languages have an even greater increase with age in
+sensitivity to vowel mispronunciations. Surprisingly, sensitivity to
+consonant mispronunciations shows a reversal in infants learning Romance
+languages: the growth in target looks for consonant mipronunciations
+increases and surpases that of target looks for correct pronunciations.
+
+{[}KATIE{]} AGAIN, THERE ARE ADDITIONAL INTERACTIONS THAT ARE
+SIGNIFICANT\ldots{} SHOULD THEY BE INTERPRETED? ALSO, WTF ROMANCE
+LANGUAGES?
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{Paper_Analyses_files/figure-latex/PlotCVEffect_cond_age_fam-1.pdf}
+\caption{}
+\end{figure}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
+
+Although we had no predictions regarding mispronunciation sensitivity to
+tone mispronunciations, we included an exploratory analysis to examine
+whether responses to tone mispronunciations were different from that of
+consonants or vowels. Regarding object identification in response to
+mispronunciations, when mispronunciation type was included as a
+moderator, the moderator test was not significant QM(2) = 1.16, \emph{p}
+= 0.56. This suggests that upon hearing a mispronunciation, infants
+looks to the target image were similar for tone mispronunciations in
+comparison with both consonants and vowels. We next assessed whether
+type of mispronunciation (tone, consonant, vowel) was related to
+mispronunciation sensitivity. We merged the two datasets and included
+condition (correct pronunciation, mispronunciation) as an additional
+moderator. The moderator test was significant, QM(5) = 154.88, \emph{p}
+\textless{} .001. The interaction between condition and consonant
+mispronunciations was not significant \(\beta\) = -0.19, (SE = 0.21,
+95\% CI {[}-0.59, 0.21{]}, \emph{p} = 0.359), suggesting that there was
+no difference in looks to the target in response to consonant and tone
+mispronunciations. The interaction between condition and vowel
+mispronunciations was also not significant \(\beta\) = -0.13, (SE =
+0.21, 95\% CI {[}-0.55, 0.28{]}, \emph{p} = 0.528), suggesting that
+there was no difference in looks to the target in response to vowel and
+tone mispronunciations.
+
+We further included an exploratory analysis of the relationship between
+infant age and the impact of tone mispronunciations in comparison to
+consonant and vowel mispronunciations. First, for object recognition in
+response to mispronunciations, when age in addition to mispronunciation
+location was also included as a moderator, the moderator test was not
+significant, QM(5) = 2.78, \emph{p} = 0.733. This suggests that upon
+hearing a mispronunciation, infants looks to the target image were not
+different between tone and vowel or tone and consonant
+mispronunciations, regardless of their age. We next assessed whether the
+relationship between mispronunciation type (tone, consonant, vowel) and
+mispronunciation sensitivity was modulated by age. We merged the two
+datasets and included condition (correct pronunciation,
+mispronunciation) as well as age as additional moderators. The moderator
+test was significant, QM(11) = 163.85, \emph{p} \textless{} .001, but
+the interactions between condition, age, and both consonant
+mispronciations (\(\beta\) = 0.02, SE = 0.10, 95\% CI {[}-0.19, 0.22{]},
+\emph{p} = 0.871) and vowel mispronunciations (\(\beta\) = 0.06, SE =
+0.10, 95\% CI {[}-0.14, 0.27{]}, \emph{p} = 0.56) were not significant.
+Infants' sensitivity to tone mispronunciations compared to consonant or
+vowel mispronunciations did not differ with age.
+
+{[}KATIE{]} WORTH IT TO INCLUDE LANGUAGE FAMILY ANALYSES TOO?
+
+\section{Discussion}\label{discussion}
 
@@
 
-  + Accept mispronunciations as labels for targets
-  + Sensitive to mispronunciations
-  + lack of change over development
+\begin{itemize}
+\tightlist
+\item
+  Accept mispronunciations as labels for targets
+\item
+  Sensitive to mispronunciations
+\item
+  lack of change over development
+\end{itemize}
 
@@
 
-  + no relationship?
-  + talk about how few studies report it
+\begin{itemize}
+\tightlist
+\item
+  no relationship?
+\item
+  talk about how few studies report it
+\end{itemize}
 
@@
 
-  + graded sensitivity to number of features changed in a mispronunciation
-  + importance for controlling in experimental design
-  + Perhaps a call for more studies to include multiple number of features changed, so that this can be assessed? There was a narrow age where this was actually manipulated.
+\begin{itemize}
+\tightlist
+\item
+  graded sensitivity to number of features changed in a mispronunciation
+\item
+  importance for controlling in experimental design
+\item
+  Perhaps a call for more studies to include multiple number of features
+  changed, so that this can be assessed? There was a narrow age where
+  this was actually manipulated.
+\end{itemize}
 
@@
 
-  + Not really sure, check the results. A key interaction is significant in one model but not the other.
-  + Again, ages not matched very well for the two groups here. Decide about whether to include a age subset analysis
+\begin{itemize}
+\tightlist
+\item
+  Not really sure, check the results. A key interaction is significant
+  in one model but not the other.
+\item
+  Again, ages not matched very well for the two groups here. Decide
+  about whether to include a age subset analysis
+\end{itemize}
 
@@
 
-  + mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap
-  + this is rather the opposite of what one would expect, right?
-  + mispronunciation sensitivity was smaller when the distractor image shared the same onset phoneme as the target image compared to when the distractor image was an unfamiliar object
-  + Maybe it would be useful to have time course analyses to address this issue further
-  + As infants aged, overall recognition (regardless of condition) increased for target-distractor pairs containing onset overlap, whereas overall recognition decreased for target-distractor pairs containing no overlap.
-  + mispronunciation sensitivity for target words paired with unfamiliar distractors decreased with age, while it remained steady across a similar range of ages for target words paired with distractors containing onset overlap with the target word.
+\begin{itemize}
+\tightlist
+\item
+  mispronunciation sensitivity was greater when target-distractor pairs
+  shared the same onset phoneme compared to when they shared no
+  phonological overlap
+\item
+  this is rather the opposite of what one would expect, right?
+\item
+  mispronunciation sensitivity was smaller when the distractor image
+  shared the same onset phoneme as the target image compared to when the
+  distractor image was an unfamiliar object
+\item
+  Maybe it would be useful to have time course analyses to address this
+  issue further
+\item
+  As infants aged, overall recognition (regardless of condition)
+  increased for target-distractor pairs containing onset overlap,
+  whereas overall recognition decreased for target-distractor pairs
+  containing no overlap.
+\item
+  mispronunciation sensitivity for target words paired with unfamiliar
+  distractors decreased with age, while it remained steady across a
+  similar range of ages for target words paired with distractors
+  containing onset overlap with the target word.
+\end{itemize}
 
@@
 
-  + really no impact at all
+\begin{itemize}
+\tightlist
+\item
+  really no impact at all
+\end{itemize}
 
@@
 
-  + Overall, no difference between consonants and vowels 
-  + Consonant mispronunciation sensitivity decreases with age
-  + Vowel mispronunciation sensitivity increases with age
-  + mispronunciation sensitivity for consonants similar for Germanic and Romance languages
-  + Mispronunciation sensitivity for vowels greater for Germanic compared to Romance languages
-  + For Germanic infants, increasing age was related to increasing mispronunciation sensitivity for vowel mispronunciations, but decreasing sensitivity for consonant mispronunciations. 
-  + For Romance infants, an even greater increase with age in sensitivity to vowel mispronunciations. 
-  + For Romance infants, the growth in target looks for consonant mipronunciations increases and surpases that of target looks for correct pronunciations
-  + exploratory analyses with tone mispronunciations suggest no great difference in sensitivity when compared to consonant and vowel mispronunciations
-
-When it comes to designing studies, best practices and current standards might not always overlap.
-Indeed, across a set of previous meta-analyses it was shown that particularly infant research does not adjust sample sizes according to the effect in question (Bergmann et al., in press).
-A meta-analysis is a first step in improving experiment planning by measuring the underlying effect and its variance, which is directly related to the sample needed to achieve satisfactory power in the null hypothesis significance testing framework.
-Failing to take effect sizes into account can both yield to underpowered research and to testing too many participants, both consequences are undesirable for a number of reasons that have been discussed in depth elsewhere.
-We will just briefly mention two that we consider most salient for theory building: Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature (citationcitation).
-Overpowered studies mean that participants were tested unnecessarily, which has substantial ethical consequences particularly when working with infants and other difficult to recruit and test populations.
-
-From Christina: let's make a note to put sth in the discussion about our curve being surprisingly flat for correctly pronounced words bc people adapt their analysis windows?
-Bc if you look at Molly's reaction time paper, there is a steep increase.
-
-Discussing the Moderator Analyses
-Maybe put them together into the ones that worked out as we predicted and those that didn't?
-So, here is evidence that supports existing arguments, that doesn't need to be a huge chunk.
-But then more space devoted to moderator analyses that didn't work out according to predictions.
-
-It should be noted that the majority of consonant mispronunciations were located on the onset phoneme (*n* = `r with(CV_location_info, n_exp_conditions[type_feature == "consonant" & mispron_location == "onset"])`; total consonant conditions, *n* = `r with(CV_info, n_exp_conditions[type_feature == "consonant"])`), while the majority of vowel mispronunciations were located on the medial phoneme (*n* = `r with(CV_location_info, n_exp_conditions[type_feature == "vowel" & mispron_location == "medial"])`; total vowel conditions, *n* = `r with(CV_info, n_exp_conditions[type_feature == "vowel"])`).
-In their analysis using TRACE, Mayor and Plunkett (2014) found that the difference between sensitivity to consonant and vowel mispronunciations was due to infants' lexical knowlege consisting of a majority consonant onset words.
-
-[KATIE] COME BACK TO THIS.
+\begin{itemize}
+\tightlist
+\item
+  Overall, no difference between consonants and vowels
+\item
+  Consonant mispronunciation sensitivity decreases with age
+\item
+  Vowel mispronunciation sensitivity increases with age
+\item
+  mispronunciation sensitivity for consonants similar for Germanic and
+  Romance languages
+\item
+  Mispronunciation sensitivity for vowels greater for Germanic compared
+  to Romance languages
+\item
+  For Germanic infants, increasing age was related to increasing
+  mispronunciation sensitivity for vowel mispronunciations, but
+  decreasing sensitivity for consonant mispronunciations.
+\item
+  For Romance infants, an even greater increase with age in sensitivity
+  to vowel mispronunciations.
+\item
+  For Romance infants, the growth in target looks for consonant
+  mipronunciations increases and surpases that of target looks for
+  correct pronunciations
+\item
+  exploratory analyses with tone mispronunciations suggest no great
+  difference in sensitivity when compared to consonant and vowel
+  mispronunciations
+\end{itemize}
+
+When it comes to designing studies, best practices and current standards
+might not always overlap. Indeed, across a set of previous meta-analyses
+it was shown that particularly infant research does not adjust sample
+sizes according to the effect in question (Bergmann et al., in press). A
+meta-analysis is a first step in improving experiment planning by
+measuring the underlying effect and its variance, which is directly
+related to the sample needed to achieve satisfactory power in the null
+hypothesis significance testing framework. Failing to take effect sizes
+into account can both yield to underpowered research and to testing too
+many participants, both consequences are undesirable for a number of
+reasons that have been discussed in depth elsewhere. We will just
+briefly mention two that we consider most salient for theory building:
+Underpowered studies will lead to false negatives more frequently than
+expected, which in turn results in an unpublished body of literature
+(citationcitation). Overpowered studies mean that participants were
+tested unnecessarily, which has substantial ethical consequences
+particularly when working with infants and other difficult to recruit
+and test populations.
+
+From Christina: let's make a note to put sth in the discussion about our
+curve being surprisingly flat for correctly pronounced words bc people
+adapt their analysis windows? Bc if you look at Molly's reaction time
+paper, there is a steep increase.
+
+Discussing the Moderator Analyses Maybe put them together into the ones
+that worked out as we predicted and those that didn't? So, here is
+evidence that supports existing arguments, that doesn't need to be a
+huge chunk. But then more space devoted to moderator analyses that
+didn't work out according to predictions.
+
+It should be noted that the majority of consonant mispronunciations were
+located on the onset phoneme (\emph{n} = 120; total consonant
+conditions, \emph{n} = 145), while the majority of vowel
+mispronunciations were located on the medial phoneme (\emph{n} = 44;
+total vowel conditions, \emph{n} = 71). In their analysis using TRACE,
+Mayor and Plunkett (2014) found that the difference between sensitivity
+to consonant and vowel mispronunciations was due to infants' lexical
+knowlege consisting of a majority consonant onset words.
+
+{[}KATIE{]} COME BACK TO THIS.
 
@@
 
-# References
-```{r create_r-references}
-#r_refs(file = "r-MISP_MA_BIB.bib")
-```
+\section{References}\label{references}
 
 \begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id = "refs"></div>
+\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
+
+\hypertarget{refs}{}
+
 \endgroup
+
+\end{document}

### 2018-10-23 Untitled.Rmd
convert to papaja, temporary references fix

--- 2018-10-10 Paper_Analyses.Rmd
@@
 ---
-title: "MP MetaAnalysis"
-author: "Christina Bergmann and Katie Von Holzen"
-date: '`r format(Sys.Date(), "%d %B, %Y")`'
-output: 
-  pdf_document:
-    toc: true
+title             : "The title"
+shorttitle        : "Title"
+
+author: 
+  - name          : "First Author"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Postal address"
+    email         : "my@email.com"
+  - name          : "Ernst-August Doelle"
+    affiliation   : "1,2"
+
+affiliation:
+  - id            : "1"
+    institution   : "Wilhelm-Wundt-University"
+  - id            : "2"
+    institution   : "Konstanz Business School"
+
+authornote: |
+  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+
+  Enter author note here.
+
+abstract: |
+  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+
+  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
+
+  One sentence clearly stating the **general problem** being addressed by  this particular study.
+
+  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
+
+  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
+
+  One or two sentences to put the results into a more **general context**.
+
+  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
+
+  <!-- https://tinyurl.com/ybremelq -->
+
+keywords          : "keywords"
+wordcount         : "X"
+
+floatsintext      : no
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : yes
+mask              : no
+draft             : no
+citeproc          : no
+
+documentclass     : "apa6"
+classoption       : "man"
+output            : papaja::apa6_pdf
 ---
-```{r Setup, echo = FALSE, warning=FALSE}
-knitr::opts_chunk$set(echo = TRUE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)
 
-### Load libraries
-library(tidyverse)
-library(metafor)
-library(meta)
-library(pwr)
-library(knitr)
-library(ggplot2)
-library(wesanderson)
-library(grid)
-library(gridExtra)
-library(xtable)
-library(schoRsch)
-library(multcomp)
-
-# set Table count at 0
-t_num <- 0
-
-# set Figure count at 0
-f_num <- 0
-
-r2 <- function(x){ round(x, 2)}
-
-psig <- function(x){
-  ifelse(x < .0001, "< .0001",
-         ifelse(x < .001, "< .001",
-                ifelse(x < .01, "< .01",
-                       ifelse(x > .01 & x < .05, paste("=", r2(x), sep = " "), paste("=", r2(x), sep = " ")))))
-}
-
-# function for creating 1 line paired t.test results
-t.xtable <- function(x) as.data.frame(xtable(
-  t_out(toutput=x, n.equal = TRUE, welch.df.exact = TRUE, welch.n = NA,
-        d.corr = TRUE, print = TRUE)
-))
-
-cur_dir <- getwd()
-
+```{r setup, include = FALSE}
+library("papaja")
 ```
 
-#Preparation
-
-Read in data and tidy up dataset
-
-```{r ReadIn,  echo = FALSE}
-
-#Get the effect size data
-source("scripts/calculateES.R")
-
-```
-
-```{r Preprocess, echo = FALSE}
-
-db_ET <- db_ET %>%
-  mutate(age.C = (mean_age_1-mean(mean_age_1, na.rm=TRUE))/30.44) %>%
-  filter(mean_age_months < 31)
-
-db_ET$collapse <- paste(db_ET$study_ID, db_ET$expt_num, db_ET$same_infant, sep = "_")
-
-# assign language families
-
-db_ET$lang_family = ifelse(db_ET$native_lang=="American English" | db_ET$native_lang=="British English" | db_ET$native_lang=="Dutch" |
-db_ET$native_lang=="Danish" | db_ET$native_lang=="Swedish" |
-db_ET$native_lang=="English" | db_ET$native_lang=="German", "Germanic", ifelse(db_ET$native_lang == "French" | db_ET$native_lang == "Catalan" | db_ET$native_lang == "Spanish" | db_ET$native_lang == "Catalan-Spanish" | db_ET$native_lang == "Swiss French",
-                                "Romance", "Sino-Tibetian"))
-
-#Split into correct and MP database
-
-db_ET_correct <- db_ET[db_ET$is_correct=="1",]
-db_ET_MP <- db_ET[db_ET$is_mp=="1",]
-
-#collapse over nonindependent MP rows for a *general* MP effect
-
-collapse_rows <- function(db){
-  db$collapse <- paste(db$study_ID, db$expt_num, db$same_infant, sep = "_")
-
-  for(independent in unique(db$collapse)){
-    if(length(db[db$collapse==independent])>1){
-      sub = db[db$collapse==independent, ]
-      sub$d_calc <- median(sub$d_calc)
-      sub$d_var_calc <- median(sub$d_var_calc)
-      sub$g_calc <- median(sub$g_calc)
-      sub$g_var_calc <- median(sub$g_var_calc)
-      sub$corr_imputed <- median(sub$corr_imputed)
-      db <- db[!(db$collapse==independent),]
-      db <- rbind(db, sub[1,])
-    }
-  }
-  return(db)
-}
-
-#db_ET_correct = collapse_rows(db_ET_correct)
-
-#db_ET_MP = collapse_rows(db_ET_MP)
-
-#remove outliers, for now we have none, though
-db_ET_MP$nooutlier = ifelse(db_ET_MP$g_calc > mean(db_ET_MP$g_calc, na.rm = TRUE) + 3*sd(db_ET_MP$g_calc, na.rm = TRUE) 
-                         | db_ET_MP$g_calc < mean(db_ET_MP$g_calc, na.rm = TRUE) - 3*sd(db_ET_MP$g_calc, na.rm = TRUE),FALSE, TRUE)
-db_ET_MP = db_ET_MP[db_ET_MP$nooutlier,]
-
-db_ET_correct$nooutlier = ifelse(db_ET_correct$g_calc > mean(db_ET_correct$g_calc, na.rm = TRUE) + 3*sd(db_ET_correct$g_calc, na.rm = TRUE) 
-                         | db_ET_correct$g_calc < mean(db_ET_correct$g_calc, na.rm = TRUE) - 3*sd(db_ET_correct$g_calc, na.rm = TRUE),FALSE, TRUE)
-db_ET_correct = db_ET_correct[db_ET_correct$nooutlier,]
-
-# make sure that both correct and mispronounced conditions are considered in descriptives
-
-db_ET_correct$condition <- 1
-db_ET_MP$condition <- 0
-
-dat <- bind_rows(db_ET_correct, db_ET_MP)
-
-# need data set of unique short cite by expt_num
-# in order to calculate total number of infants
-
-# need data set of unique short cite by condition
-
-sum_dat <- dat[!duplicated(dat[c("short_cite", "same_infant")]),]
-time_wind_dat <- dat[!duplicated(dat[c("short_cite", "offset", "post_nam_dur")]),]
-distract_dat <- dat[!duplicated(dat[c("short_cite", "object_pair")]),]
-mix_co_mp <- dat[!duplicated(dat[c("short_cite", "word_correct_and_MP")]),]
-
-```
-
-Plotting defaults
-
-```{r PlotAPATheme, echo = FALSE}
-#Themes and plot
-apatheme=theme_bw()+
-  theme(panel.grid.major=element_blank(),
-    panel.grid.minor=element_blank(),
-    panel.border=element_blank(),
-    axis.line=element_line(),
-    text=element_text(family='Times', size=25))
-
-# Color Blind palette:
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
+```{r analysis-preferences}
+# Seed for random number generation
+set.seed(42)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
 ```
@@
 # Methods
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
+<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
 
-The present meta-analysis was conducted with maximal transparency and reproducibility in mind.
-To this end, we provide all data and analysis scripts on the supplementary website (https://osf.io/rvbjs/) and open our meta-analysis up for updates (Tsuji, Bergmann, & Cristia, 2014).
-In addition, we follow the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials (Moher, Liberati, Tetzlaff, Altman & PRISMAGroup, 2009).
-Figure X plots our PRISMA flowchart.
+## Participants
 
-![Figure X. PRISMA Flowchart.] (figures/PRISMA_MA_Mispronunciation.png)
+## Material
 
-## Study Selection
-
-```{r SummaryTable, echo = FALSE}
-
-dat_st <- dat
-
-dat_st$object_pair <- ifelse(dat_st$object_pair == "familiar_familiar", "Familiar", "Unfamiliar")
-
-Sum_table <- dat_st %>%
-      group_by(short_cite) %>% 
-      summarise(Ages_Tested_months = paste(unique(trunc(mean_age_1/30.34)), collapse=', '),
-                Vocabulary = ifelse(all(is.na(r_comprehension)) & all(is.na(r_production)), "None",
-                                ifelse(!all(is.na(r_comprehension)) & !all(is.na(r_production)), "Comprehension/Production",
-                                       ifelse(!all(is.na(r_comprehension)) & all(is.na(r_production)), "Comprehension", "Production"))),
-                Number_of_Features = paste(unique(n_feature), collapse=', '),
-                Distractor_Familiarity = paste(unique(object_pair), collapse=', '),
-                Distractor_Overlap = paste(unique(distractor_overlap), collapse=', '),
-                Mispronunciation_Position = paste(unique(mispron_location), collapse=', '),
-                Mispronunciation_type = paste(unique(type_feature), collapse=', '))
-
-kable(Sum_table)
-
-```
-
-[KATIE] THIS TABLE IS DEFINITELY NOT FINISHED!
-
-We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list.
-This process yielded 110 items.
-We then used the google scholar search engine to search for papers citing the original Swingley & Aslin (2000) publication.
-This search was conducted on 22 September, 2017 and yielded 288 results.
-We screened the 398 items, removing 99 duplicate items.
-We screened remaining 299 items for their title and abstract to determine whether it met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition; (3) infants studied were under 36-months-of-age; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; 5) the stimuli were auditory speech.
-The final sample (n = *`r length(unique(dat$short_cite))`*) consisted of `r with(dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(dat, n_distinct(short_cite[publication_status == "dissertation"]))` thesis, and `r with(dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports.
-We will refer to these items collectively as papers.
-Table 1 (Summary Table) provides an overview of all papers included in the present meta-analysis.
-
-```{r DescriptivesPubtype, echo = FALSE}
-
-t_num <- t_num+1
-
-pub_info <- dat %>%
-  group_by(publication_status) %>%
-  summarize(n_unique = n_distinct(short_cite), count = n())
-
-kable(pub_info)
-
-pi <- dat[,c("short_cite", "publication_status")]
-pi <- unique(pi)
-
-c.plot <- ggplot(pi, aes(x= publication_status)) + 
-  geom_text(stat='count', aes(label=..count..), vjust=-1, size = 5)+
-  geom_bar(stat="count")+
-  coord_cartesian(ylim = c(0, 30))+
-  apatheme+
-  theme(axis.text.x = element_text(size = 20, angle = -45, hjust = .11),
-        axis.title.x = element_blank())
-
-c.plot
-
-  jpeg(filename = "figures/Pub_count.jpg", 
-       width = 500, height = 500, units = "px")
-
-  c.plot
-
-  dev.off()
-
-```
-
-## Data Entry
-
-The `r length(unique(dat$short_cite))` papers we identified as relevant were then coded with as much detail as possible (Tsuji, Bergmann, & Cristia, 2014; Bergmann et al., in press).
-For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results.
-For the present analyses, we focus on the following characteristics:
-1 Condition: Were words mispronounced or not;
-2 Mean age reported per group of infants, in days;
-3 Vocabulary size:  
-4 Size of mispronunciation, measured in features changed;
-5 Distractor familiarity: familiar, unfamiliar;
-6 Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;
-7 Position of mispronunciation: onset, medial, offset;
-8 Type of mispronunciation: consonant, vowel;
-
-We separated out conditions according to whether or not the target word was mispronounced to be able to investigate both infants' looking to the target picture separated by whether or not words were mispronounced and their mispronunciation sensitivity, which is the difference between looking in correct and mispronounced trials.
-When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  (e.g., consonant versus vowel mispronunciations; Mani & Plunkett, 2007).
-The fact that the same infants have contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section).
-We will call each row a record; in total there were `r nrow(dat)` records in our data.
+## Procedure
 
@@
 
-```{r DescriptivesComparison, echo = FALSE}
-db_ET_correct$within_measure_descriptive <- ifelse(db_ET_correct$within_measure == "post",
- "post-naming phase compared with chance (=50%)",
-ifelse(db_ET_correct$within_measure == "pre_post", "post-naming compared to pre-naming phase", "post-pre difference score compared with chance (=0)"))
-
-comparison_info <- db_ET_correct %>%
-  group_by(within_measure_descriptive) %>%
-  summarize(n_unique = n_distinct(short_cite), count = n())
-
-kable(comparison_info)
-#table(db_ET_MP$es_method)
-```
-```{r DescriptivesES, echo = FALSE}
-#how did we calculate effect sizes?
-
-es_info <- dat %>%
-  group_by(es_method) %>%
-  summarize(n_unique = n_distinct(short_cite), count = n())
-
-kable(es_info)
-#table(dat$es_method, dat$short_cite)
-# only missing from:
-# Bailey & Plunkett (2002) <- crazy old data
-# Renner (2017) <- just finished phd
-# Tamasi (2016) <- standard deviations are wrong
-#table(db_ET_MP$es_method)
-
-```
-
-All scripts and raw data are available on Open Science Framework (OSF).
-INSERT LINK AS FOOTNOTE HERE.
-Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to a baseline measurement.
-PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images.
-Across papers the baseline comparison varied; we used the baseline reported by the authors of each paper.
-Most papers (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post_naming_effect"]))`) subtracted the PTL score for the pre-naming phase from the PTL score for the post-naming phase.
-When interpreting this difference score, a positive value indicates that infants increased their looks to the target after hearing the naming label (correct or mispronounced).
-Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post"]))`) or compared post-naming PTL with chance (50%, (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "post"]))`)).
-For these comparisons, a positive difference score or a post-naming phase PTL score that is greater than the pre-naming phase PTL or chance indicate target looks that indicate object recognition after hearing the naming label.
-
-We report effect sizes for infants' looks to target pictures after hearing a correctly pronounced or mispronounced label (object identification) as well as the difference between effect sizes for correct and mispronounced trials (mispronunciation sensitivity).
-The effect size we report in the present paper are based on comparison of means, standardized by their variance.
-The most well-known effect size from this group is Cohen's *d* (Cite cohen).
-To correct for the small sample sizes common in infant research, however, we use as a dependent variable Hedges' *g* instead of Cohen's *d* (Hedges, 1981; Morris, 2000).
-
-No authors made their raw data available.
-Instead, we calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(dat, n_distinct(short_cite[es_method == "group_means_one" | es_method == "group_means_two"]))`) or using reported t-values (*n* = `r with(dat, n_distinct(short_cite[es_method == "t_one" | es_method == "t_two"]))`).
-Raw means and standard deviations were extracted from figures for `r with(dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers.
-In a within-participation design, when two means are compared (i.e.
-looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values.
-One paper reported this correlation, while we were able to compute correlations using means, standard deviations, and t-values (following Csibra, et al.
-2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, submitted).
-Correlations were imputed for the remaining papers (see Black & Bergmann, 2017, for the same procedure).
-We computed a total of `r sum(dat$is_mp == 0)` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)` for mispronunciations.
-
-To take into account the fact that the same infants contributed to multiple datapoints, we analyze our results in a multilevel approach using the R (R citation) package metafor (Viechtbauer, 20XX, Multulevel reference).
-This means we model as random effect that effect sizes from the same paper share are based on more similar studies than those across papers and that nested therein effects can stem from the same infants.
-
-## Publication Bias
-
-In the psychological sciences, there is a documented reluctance to publish null results.
-As a result, there is a potential for significant results to be valued over non-significant results (see Ferguson & Heene, 2012).
-To examine whether this is also the case in the mispronunciation sensitivity literature, which would bias the data analyzed in this meta-analysis, we conduct two tests.
-We first examine whether effect sizes are distributed as expected based on sampling error using the rank correlation test of funnel plot asymmetry with the R (R Core Team, 2016) package metafor (Viechtbauer, 2010).
-Effect szes with low-variance are closer to the estimated mean, while effect sizes with high-variance show an increased, evenly-distributed spread around the estimated mean.
-Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app (v4.0, p-curve.com; Simonsohn, Simmons, & Nelson, 2014).
-This tests for evidential value by examining whether the p-values have an expected distribution, regardless of whether the null hypothesis is true or not, as well as whether there is a larger proportion of p-values just below the typical alpha threshold of .05, which may indicate questionable research practices.
-Responses to correctly pronounced and mispronounced labels are predicted to show different patterns of looking behavior; as a result, we conduct these two analyses to assess publication bias separately for both conditions.
-
-## Meta-analysis
-
-The models reported are hierarchical random-effects models (infant groups nested within papers) of variance-weighted effect sizes with the R (R Core Team, 2016) package metafor
-(Viechtbauer, 2010).
-To investigate how development impacts mispronunciation sensitivity, our core theoretical investigation, we introduce age (centered; in days but transformed into months for ease of reading by dividing by 30.44) as a moderator to our main model.
-For the subsequent investigations of experimental characteristics, we introduce each characteristic as a moderator (more detail below).
-
 # Results
-
-## Publication Bias
-
-```{r FunnelPlotAsymm_correct, echo = FALSE}
-
-rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ collapse | short_cite)
-# Publication bias can become visible in funnel plot asymmetry. 
-# Metafor comes with several options to check this, I chose ranktest and regtest
-# correct object identification
-rmac <- ranktest(rma_correct)
-#rmac
-
-```
-
-```{r FunnelPlotAsymm_misp, echo=FALSE}
-
-rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ collapse | short_cite)
-
-# mispronounced object identification
-rmam <- ranktest(rma_MP)
-#rmam
-```
-
-Figure 1 plots the funnel plots for object identification for both correct pronunciations and mispronunciations (code adapted from Sakaluk, 2016).
-Funnel plot assymmetry was significant for both correct pronunciations (Kendall's $\tau$ = `r r2(rmac$tau)`, *p* `r psig(rmac$pval)`) and mispronunciations (Kendall's $\tau$ = `r r2(rmam$tau)`, *p* `r psig(rmam$pval)`).
-These results, in conjunction with the assymmetric funnel plot (Figure 1) indicate bias in the literature.
-This is particularly evident for correct pronunciations, where larger effect sizes have greater variance (bottom right corner) and there are a smaller number of more precise effect sizes (i.e.
-smaller variance) than expected (top left, outside the triangle).
-
-```{r FunnelPrep, echo = FALSE}
-### Plots adapted from Sakaluk, 2016, see also Black & Bergmann, 2017
-### https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/
-
-#Themes and plot
-funnel_theme=theme_bw()+
-  theme(#panel.grid.major=element_blank(),
-    #panel.grid.minor=element_blank(),
-    #panel.border=element_blank(),
-    axis.line=element_line(),
-    text=element_text(family='Times', size=22),
-    legend.position='none')
-
-```
-
-```{r FunnelCorrect, echo = FALSE}
-
-#Rename a bunch of things for ease
-dat_co = db_ET_correct
-#dat_co=db_ET_correct
-dat_co <-
-  dat_co %>% 
-  rename(cite = short_cite,
-         yi = g_calc,
-         vi = g_var_calc)
-
-#Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order
-
-dat_co <-
-  dat_co %>% 
-  select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>% 
-  mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
-  arrange(desc(yi))
-
-#Get standard errors from variances
-dat_co$se = sqrt(dat_co$vi)
-
-#Calculate 95% CI values
-dat_co$lowerci = (-1.96*dat_co$se)+dat_co$yi
-dat_co$upperci = (1.96*dat_co$se)+dat_co$yi
-
-#Store the meta-analytic estimate and its standard error from whatever model you run
-#summary(rma_correct)
-estimate_co = coef(summary(rma_correct))$estimate
-se_co = coef(summary(rma_correct))$se
-
-#Store a vector of values that spans the range from 0
-#to the max value of impression (standard error) in your dataset.
-#Make the increment (the final value) small enough (I choose 0.001)
-#to ensure your whole range of data is captured
-se.seq_co=seq(0, max(dat_co$se), 0.001)
-
-#Now, compute vectors of the lower-limit and upper limit values for
-#the 95% CI region, using the range of SE that you generated in the previous step, 
-#and the stored value of your meta-analytic estimate.
-ll95_co = estimate_co-(1.96*se.seq_co)
-ul95_co = estimate_co+(1.96*se.seq_co)
-
-#You can do this for a 99% CI region too
-ll99_co = estimate_co-(3.29*se.seq_co)
-ul99_co = estimate_co+(3.29*se.seq_co)
-
-#And finally, do the same thing except now calculating the confidence interval
-#for your meta-analytic estimate based on the stored value of its standard error
-meanll95_co = estimate_co-(1.96*se_co)
-meanul95_co = estimate_co+(1.96*se_co)
-
-#Now, smash all of those calculated values into one data frame (called 'dfCI').
-#You might get a warning about '...row names were found from a short variable...'
-#You can ignore it.
-dfCI_co = data.frame(ll95_co, ul95_co, ll99_co,
-                  ul99_co, se.seq_co, estimate_co, meanll95_co, meanul95_co)
-
-#Now we can actually make the funnel plot.
-#Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
-fp_co = ggplot(aes(x = se, y = yi), data = dat_co) +
-  #Regression line for the FP asymmetry
-  geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_co) +
-  #Add your data-points to the scatterplot
-  geom_point(size = 2.5, colour="black") +
-  #
-  #Give the x- and y- axes informative labels
-  xlab('Standard Error') + ylab('Hedge\'s g')+
-  # give it a title
-    ggtitle("Correct") +
-    # make sure both plots have same scale
-    # still ylim because we haven't flipped yet
-    #coord_cartesian(ylim = c(0.5, 0))+
-  #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
-  #to the lower and upper limits of your 95% CI region
-  #And dashed lines corresponding to your 99% CI region
-  #Add lines corresponding to 0 and estimate
-  geom_line(aes(x = se.seq_co, y = 0), linetype = 'solid', data = dfCI_co) +
-  geom_line(aes(x = se.seq_co, y = estimate_co), linetype = 'dashed', data = dfCI_co) +
-  geom_line(aes(x = se.seq_co, y = ll95_co), linetype = 'dotted', data = dfCI_co) +
-  geom_line(aes(x = se.seq_co, y = ul95_co), linetype = 'dotted', data = dfCI_co) +
-  #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
-  #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
-  #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
-  #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
-  #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
-  #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
-  #at the top of the figure once we swap the x- and y-axes...
-  scale_x_reverse()+
-  #Specify the range and interval for the tick-marks of the y-axis (Zr);
-  #Choose values that work for you based on your data
-  #scale_y_continuous(breaks=seq(-.45,0.8,0.25))+
-  #And now we flip the axes so that SE is on y- and Zr is on x-
-  coord_flip()+
-  #Finally, apply my APA-format theme (see code at end of post).
-  #You could, alternatively, specify theme_bw() instead.
-  funnel_theme
-
-#Call the pretty funnel plot
-#fp_co
-#ggsave("figures/FunnelPlot_correct.pdf")
-
-```
-
-```{r FunnelMisp, echo = FALSE}
-
-  #Rename a bunch of things for ease
-dat_mp = db_ET_MP  
-#dat_mp=db_ET_MP
-  dat_mp <-
-    dat_mp %>% 
-    rename(cite = short_cite,
-           yi = g_calc,
-           vi = g_var_calc)
-
-  #Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order
-
-  dat_mp <-
-    dat_mp %>% 
-    select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>% 
-    mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
-    arrange(desc(yi))
-
-  #Get standard errors from variances
-  dat_mp$se = sqrt(dat_mp$vi)
-
-  #Calculate 95% CI values
-  dat_mp$lowerci = (-1.96*dat_mp$se)+dat_mp$yi
-  dat_mp$upperci = (1.96*dat_mp$se)+dat_mp$yi
-
-  #Store the meta-analytic estimate and its standard error from whatever model you run (substitute your own values)
-  #summary(rma_MP)
-  estimate_mp = coef(summary(rma_MP))$estimate
-  se_mp = coef(summary(rma_MP))$se
-
-  #Store a vector of values that spans the range from 0
-  #to the max value of impression (standard error) in your dataset.
-  #Make the increment (the final value) small enough (I choose 0.001)
-  #to ensure your whole range of data is captured
-  se.seq_mp=seq(0, max(dat_mp$se), 0.001)
-
-  #Now, compute vectors of the lower-limit and upper limit values for
-  #the 95% CI region, using the range of SE that you generated in the previous step, 
-  #and the stored value of your meta-analytic estimate.
-  ll95_mp = estimate_mp-(1.96*se.seq_mp)
-  ul95_mp = estimate_mp+(1.96*se.seq_mp)
-
-  #You can do this for a 99% CI region too
-  ll99_mp = estimate_mp-(3.29*se.seq_mp)
-  ul99_mp = estimate_mp+(3.29*se.seq_mp)
-
-  #And finally, do the same thing except now calculating the confidence interval
-  #for your meta-analytic estimate based on the stored value of its standard error
-  meanll95_mp = estimate_mp-(1.96*se_mp)
-  meanul95_mp = estimate_mp+(1.96*se_mp)
-
-  #Now, smash all of those calculated values into one data frame (called 'dfCI').
-  #You might get a warning about '...row names were found from a short variable...'
-  #You can ignore it.
-  dfCI_mp = data.frame(ll95_mp, ul95_mp, ll99_mp,
-                       ul99_mp, se.seq_mp, estimate_mp, meanll95_mp, meanul95_mp)
-
-  #Now we can actually make the funnel plot.
-  #Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
-  fp_mp = ggplot(aes(x = se, y = yi), data = dat_mp) +
-    #Regression line for the FP asymmetry
-    geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_mp) +
-    #Add your data-points to the scatterplot
-    geom_point(size = 2.5, colour="black") +
-    #
-  #Give the x- and y- axes informative labels
-  xlab('Standard Error') + 
-    # remove y label because it will be combined with the other funnel plot
-    ylab('Hedge\'s g')+
-    # give it a title
-    ggtitle("Mispronunciation") +
-    # make sure both plots have same scale
-    # still xlim because we haven't flipped yet
-    #coord_cartesian(xlim = c(0.5, 1))+
-    #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
-    #to the lower and upper limits of your 95% CI region
-    #And dashed lines corresponding to your 99% CI region
-    #Add lines corresponding to 0 and estimate
-    geom_line(aes(x = se.seq_mp, y = 0), linetype = 'solid', data = dfCI_mp) +
-    geom_line(aes(x = se.seq_mp, y = estimate_mp), linetype = 'dashed', data = dfCI_mp) +
-    geom_line(aes(x = se.seq_mp, y = ll95_mp), linetype = 'dotted', data = dfCI_mp) +
-    geom_line(aes(x = se.seq_mp, y = ul95_mp), linetype = 'dotted', data = dfCI_mp) +
-    #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
-    #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
-    #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
-    #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
-    #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
-    #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
-    #at the top of the figure once we swap the x- and y-axes...
-    scale_x_reverse()+
-    #Specify the range and interval for the tick-marks of the y-axis (Zr);
-    #Choose values that work for you based on your data
-    #scale_y_mpntinuous(breaks=seq(-.45,0.8,0.25))+
-    #And now we flip the axes so that SE is on y- and Zr is on x-
-    coord_flip()+
-    #Finally, apply my APA-format theme (see previous).
-    #You could, alternatively, specify theme_bw() instead.
-    funnel_theme +
-    theme(axis.title.y = element_blank())
-
-  #Call the pretty funnel plot
-  #fp_mp
-#  ggsave("figures/FunnelPlot_misp.pdf")
-
-```
-
-## Figure 1
-
-```{r FunnelCombo, echo = FALSE}
-
-  jpeg(filename = "figures/Figure_1_Funnel_Plots_Object_Identification.jpg", 
-       width = 600, height = 400, units = "px")
-
-  p <-   grid.arrange(fp_co, fp_mp, nrow = 1)
-                      #top = textGrob("Object Identification", gp=gpar(fontsize=25)))
-                      #top = "Figure 1. Funnel Plots")
-  dev.off()
-
-    grid.draw(p)
-
-```
-
-```{r PcurveExport, echo = FALSE}
-
-textfile_co = "p_curve_app/p_curve_co.txt"
-
-# make sure the file is made new with our loop
-if (file.exists(textfile_co)) {file.remove(textfile_co)}
-
-for(line in 1:length(db_ET_correct$n_1)){
-  if(!is.na(db_ET_correct[line,]$t)){
-    newline = paste("t(", db_ET_correct[line,]$n_1-1, ")=",db_ET_correct[line,]$t, sep = "")
-    write(newline, file = textfile_co, append = TRUE)
-    #cat("\n")
-    #write(newline, file = textfile, append = TRUE)    
-  }
-}
-
-textfile_mp = "p_curve_app/p_curve_mp.txt"
-
-# make sure the file is made new with our loop
-if (file.exists(textfile_mp)) {file.remove(textfile_mp)}
-
-for(line in 1:length(db_ET_MP$n_1)){
-  if(!is.na(db_ET_MP[line,]$t)){
-    newline = paste("t(", db_ET_MP[line,]$n_1-1, ")=",db_ET_MP[line,]$t, sep = "")
-    write(newline, file = textfile_mp, append = TRUE)
-    #cat("\n")
-    #write(newline, file = textfile, append = TRUE)    
-  }
-}
-
-```
-
-```{r ReadIn_pcurve_app,  echo = FALSE}
-
-curdir <- getwd()
-
-#Get the effect size data
-source("scripts/p_curve_app_code.R")
-
-# this gives the number of significant results
-# the Z value
-# and the significance
-pcd_correct <- pcurve_app("p_curve_co.txt",paste0(curdir, "/p_curve_app"))
-
-pcd_misp <- pcurve_app("p_curve_mp.txt",paste0(curdir, "/p_curve_app"))
-
-```
-
-We next examined the p-curves for significant values from the correctly pronounced and mispronounced conditions.
-The p-curve based on `r pcd_correct$ksig` statistically significant values for correct pronunciations indicates that the data contain evidential value (Z = `r r2(pcd_correct$Zppr)`, p `r psig(pcd_correct$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05.
-The p-curve based on `r pcd_misp$ksig` statistically significant values for mispronunciations indicates that the data contain evidential value (Z = `r r2(pcd_misp$Zppr)`, p `r psig(pcd_misp$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05.
-
-Taken together, these results suggest a tendency in the literature towards publication bias.
-As a result, our meta-analysis may systematically overestimate effect sizes and we therefore interpret all estimates with caution.
-The funnel plot asymmetry may also reflect heterogeneity in the data, perhaps due to some studies investigating more subtle effects than other studies.
-Yet, the p-curve analysis suggests that overall, the literature contains evidential value, reflecting a "real" effect.
-We therefore continue our meta-analysis.
-
-## Meta-analysis
-
-### Object Identification for Correct and Mispronounced Words
-
-```{r MAcorrect}
-
-rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ collapse | short_cite)
-
-#summary(rma_correct)
-#kable(round(coef(summary(rma_correct)), 2))
-
-sum_eff <- coef(summary(rma_correct))[1,]
-
-```
-
-We first calculated the meta-analytic effect for object identification in response to correctly pronounced words.
-The variance-weighted meta-analytic effect size Hedges’ *g* was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
-This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research) and that it is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object.
-Our analysis of funnel plot asymmetry, however, found evidence for publication.
-Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` suggests that this result is robust even when correcting for publication bias.
-
-```{r MAMP}
-
-rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ collapse | short_cite)
-
-#summary(rma_MP)
-
-sum_eff <- coef(summary(rma_MP))[1,]
-
-```
-
-We then calculated the meta-analytic effect for object identification in response to mispronounced words.
-In this case, the variance-weighted meta-analytic effect size Hedges’ g was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was also significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
-This is considered a small effect size (Cohen, 1988), but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object.
-We again note the publication bias (which was smaller in this condition), and the possibility that the effect size Hedges' *g* may be overestimated.
-But, as the p-curve indicated evidential value, we are confident in this result as well.
-
-Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, p `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, p `r psig(rma_MP$QEp)`).
-This indicated that the sample contains unexplained variance leading to significant difference across our studies beyond what is to be expected based on random sampling error.
-
-### Mispronunciation Sensitivity Meta-analytic Effect
-
-```{r MPEffect}
-
-rma_MPeffect <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = ~ collapse | short_cite)
-
-#summary(rma_MPeffect)
-
-#rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ collapse | short_cite)
-
-#summary(rma_MPeffect_1)
-
-sum_eff <- coef(summary(rma_MPeffect))[2,]
-
-```
-
-The above two analyses considered the data from mispronounced and correctly pronounced words separately.
-To evaluate mispronunciation sensitivity, we then compared the effect size Hedges’ *g* for correct pronunciations with mispronunciations, merging the two datasets.
-The moderator test was significant, QM(`r r2(rma_MPeffect$m)`) = `r r2(rma_MPeffect$QM)`, p `r psig(rma_MPeffect$QMp)`.
-Hedges’ *g* for mispronunciation sensitivity was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that the two type of responses were significantly different from one another (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
-This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations.
-In other words, we observe a significant difference between the two conditions and can now quantify the modulation of fixation behavior in terms of standardized effect sizes.
-
-### Object Recognition and Mispronunciation Sensitivity Modulated by Age
-
-```{r MAcorrect_age}
-
-rma_correct_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = ~ collapse | short_cite)
-
-#summary(rma_correct_age)
-#kable(round(coef(summary(rma_correct_age)), 2))
-#aov.type <- anova(rma_correct_age)
-
-Csum_eff <- coef(summary(rma_correct_age))[2,]
-
-```
-
-```{r MAMP_age}
-
-rma_MP_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = ~ collapse | short_cite)
-
-#summary(rma_MP_age)
-#aov.type <- anova(rma_MP_age)
-
-Msum_eff <- coef(summary(rma_MP_age))[2,]
-
-```
-
-To evaluate the different predictions for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered, in days).
-In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not.
-Age did not significantly modulate object identification in response to correctly pronounced (QM(`r r2(rma_correct_age$m)`) = `r r2(rma_correct_age$QM)`, p `r psig(rma_correct_age$QMp)`) or mispronounced words (QM(`r r2(rma_MP_age$m)`) = `r r2(rma_MP_age$QM)`, p `r psig(rma_MP_age$QMp)`).
-The lack of a significant modulation indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label.
-This relationship is plotted in Figure 2.
-
-```{r MPEffect_age}
-
-rma_MPeffect_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = ~ collapse | short_cite)
-
-# summary(rma_MPeffect_age)  
-# 
-# aov.type <- anova(rma_MPeffect_age)
-
-sum_eff <- coef(summary(rma_MPeffect_age))[4,]
-
-```
-
-We then examined the interaction between age and mispronunciation sensitivity (correct vs.
-mispronounced words) in our whole dataset.
-The moderator test was significant (QMQM(`r r2(rma_MPeffect_age$m)`) = `r r2(rma_MPeffect_age$QM)`, p `r psig(rma_MPeffect_age$QMp)`).
-The interaction between age and mispronunciation sensitivity, however, was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`), suggesting that as infants age, their mispronunciation sensitivity remains the same.
-
-## Figure 2
-
-```{r PlotMPEffect, echo = FALSE}
-
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
-
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  geom_point(aes(size = weights_g),show.legend=FALSE, alpha = .5) + 
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom",
-        text = element_text(size = 40)) + 
-  xlab("Age in months") + 
-  ylab("Hedges' g")
-
-p
-
-# min(dat$mean_age_1/30.44)
-# max(dat$mean_age_1/30.44)
-
-#ggsave("figures/AgeEffect_log.jpg", p,height= 7,width= 6)
-
-  jpeg(filename = "figures/Figure_2_AgeEffect.jpg", 
-       width = 700, height = 400, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-### Vocabulary Size: Correlation Between Mispronunciation Sensitivity and Vocabulary
-
-```{r VocabularyData, echo = FALSE}
-vocab_info <- db_ET_correct %>%
-  mutate(has_vocab = ifelse(!is.na(r_comprehension), "comprehension", 
-                            ifelse(!is.na(r_production), "production", "none"))) %>%
-  group_by(has_vocab) %>%
-  summarize(count = n(),
-            papers = n_distinct(short_cite))
-
-#kable(vocab_info)
-
-vocab_info2 <- db_ET_correct %>%
-  mutate(has_vocab = ifelse(!is.na(r_comprehension) | !is.na(r_production), "vocab", 
-                            "none")) %>%
-  group_by(has_vocab) %>%
-  summarize(count = n(),
-            papers = n_distinct(short_cite))
-
-vi1 <- as.data.frame(vocab_info)
-vi2 <- as.data.frame(vocab_info2)
-
-```
-
-Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers; production = `r with(vi1, papers[has_vocab == "production"])`) analyzed the relationship between vocabulary scores and mispronunciation sensitivity.
-There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we analyze this data separately.
-
-[KATIE] I DON'T KNOW HOW TO INTERPRET THESE RESULTS... THE FIXED EFFECTS MODEL ISN'T SIGNIFICANT FOR ANY OF THESE. IS THAT MEANINGFUL?
-
-```{r ComprehensionMeta_correct}
-#we're relying on the library meta function metacor
-compr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_comprehension) & r_comprehension > -1)
-
-metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
-```
-
-```{r ProductionMeta_correct}
-#we're relying on the library meta function metacor
-prodr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_production) & r_production < 1)
-
-metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
-```
-
-```{r ComprehensionMeta_MP}
-#we're relying on the library meta function metacor
-compr  <- subset(db_ET_MP, !is.na(db_ET_MP$r_comprehension) & r_comprehension > -1)
-
-metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
-```
-
-```{r ProductionMeta_MP}
-#we're relying on the library meta function metacor
-prodr  <- subset(db_ET_MP, !is.na(db_ET_MP$r_production) & r_production < 1)
-
-metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
-```
-
-### Interim Discussion
-
-The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age.
-The results are clear: Although infants consider a mispronunciation as a better match with the target image than a distractor image, there was a consistent effect of mispronunciation sensitivity.
-This did not change with development.
-Of the 3 predictions and assumptions about the development of infants' sensitivity to mispronunciations discussed in the Introduction, the present results lend some support for the argument that mispronunciation sensitivity stays consistent as infants develop.
-This runs counter to existing theories of phono-lexical development, which predict either an increase (PRIMR ref) or decrease (Assim Model ref) in mispronunciation sensitivity.
-
-[KATIE] CAN A CONCLUSION BE DRAWN FROM THE VOCABULARY RESULTS? IF SO, THIS IS THE PARAGRAPH
-
-In sum, it seems that current theories of infants' phono-lexical development cannot fully capture our results and should be reconsidered with all the evidence in mind.
-
-Alternatively, the lack of developmental change in mispronunciation sensitivity could be due to differences in the types of tasks given to infants of different ages.
-To examine this possibility, we include an exploratory analysis of whether different moderators and experimental design features were included at different ages, in addition to investigating the role that these moderators play in mispronunciation sensitivity.
-
-## Moderator Analyses
-
-### Size of mispronunciation
-
-```{r NFeatures_demographics}
-
-dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-nfeature_info <- dat.f %>%
-  group_by(n_feature) %>%
-  summarize(n_exp_conditions =  n())
-
-```
-
-To assess whether the number of features changed modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced using 1-, 2-, and 3-feature changes.
-We did not include data for which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent.
-The analysis was therefore based on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` experimental conditions for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations.
-Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an equal impact on mispronunciation sensitivity, following the argument of graded sensitivity (White & Aslin, 2008; Mani & Plunkett 2011).
-
-```{r NFeatures}
-
-dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat.f, random = ~collapse | short_cite)
-
- sum_eff <- coef(summary(rma_NFeatures))[2,]
-
-```
-
-To understand the relationship between size of mispronunciation and mispronunciation sensitivity, we  evaluated the effect size Hedges’ *g* with number of features changed as a moderator.
-The moderator test was significant, QM(`r r2(rma_NFeatures$m)`) = `r r2(rma_NFeatures$QM)`, p `r psig(rma_NFeatures$QMp)`.
-Hedges’ *g* for number of features changed was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that as the number of features changed increased, the effect size Hedges’ g significantly decreased (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
-We plot this relationship in Figure X.
-This confirms previous findings of a graded sensitivity to the number of features changed for both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) mispronunciations as well as the importance of controlling for the degree of phonological mismatch in experimental design.
-
-```{r PlotFeatEffect, echo = FALSE}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-dat_f$feat_cat <- ifelse(dat_f$n_feature == 1, "1-feature",
-                         ifelse(dat_f$n_feature == 2, "2-feature",
-                                ifelse(dat_f$n_feature == 3, "3-feature",
-                                       ifelse(dat_f$n_feature == 0, "correct", "none"))))
-
-dat_f <- subset(dat_f, feat_cat != "none")
-
-dat_f$Features_changed <- factor(dat_f$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))
-
-p <- ggplot(dat_f, aes(Features_changed, g_calc, fill = Features_changed)) + 
-  geom_boxplot() + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "none",
-        axis.title.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_3_Number_of_Features.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-```{r NFeatures_age}
-
-dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat.f, random = ~collapse | short_cite)
-
- sum_eff <- coef(summary(rma_NFeatures))[4,]
-
-```
-
-Although we did not have any specific predictions about the relationship between infant age and the impact of number of features changed on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
-When age was also included as a moderator, the moderator test was significant, QM(`r r2(rma_NFeatures$m)`) = `r r2(rma_NFeatures$QM)`, p `r psig(rma_NFeatures$QMp)`, but the interaction between age and number of features changed was not significant, $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
-This suggests that there is no relationship between infant age the impact of number of features changed on mispronunciation sensitivity.
-
-```{r NFeatures_subset}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-nfeature_ages <- dat.f %>%
-  group_by(n_feature) %>%
-  summarize(min_age = r2(min(mean_age_1, na.rm=TRUE)),
-            max_age = r2(max(mean_age_1, na.rm=TRUE)),
-            mean_age = r2(mean(mean_age_1, na.rm=TRUE)))
-
-mf <- subset(dat_f, n_feature == "3")
-min_age <- min(mf$mean_age_1)
-max_age <- max(mf$mean_age_1)
-
-dat_fage= dat_f%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat_fage, random = ~collapse | short_cite)
-
- sum_eff1 <- coef(summary(rma_NFeatures_agesub))[2,]
-
-rma_AGENFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat_fage, random = ~collapse | short_cite)
-
- sum_eff2 <- coef(summary(rma_AGENFeatures_agesub))[4,]
-
-```
-
-Although all papers included in the dataset also included correct pronunciations, not all papers included all three types of feature changes (i.e.
-1-3).
-The age range for each type of number of features changed was `r with(nfeature_ages, min_age[n_feature == 1])` - `r with(nfeature_ages, max_age[n_feature == 1])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 1])`) for 1-feature mispronunciations, `r with(nfeature_ages, min_age[n_feature == 2])` - `r with(nfeature_ages, max_age[n_feature == 2])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 2])`) for 2-feature mispronunciations, and `r with(nfeature_ages, min_age[n_feature == 3])` - `r with(nfeature_ages, max_age[n_feature == 3])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 3])`) for 3-feature mispronunciations.
-Focusing on the ages where all three numbers of features changed were tested (i.e.
-`r with(nfeature_ages, min_age[n_feature == 3])` - `r with(nfeature_ages, max_age[n_feature == 3])` days), however, did not change the pattern of results.
-
-[KATIE] DOES THE ABOVE PARAGRAPH NEED MORE MOTIVATION? SHOULD IT EVEN BE INCLUDED?
-
-### Distractor familiarity
-
-```{r DistractorType_misp}
-
-rma_Distractor_MP <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)
-
-rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
-
-sum_eff <- coef(summary(rma_Distractor))[4,]
-
-```
-
-We next assessed whether distractor familiarity has an impact on the size of mispronunciation sensitivity.
-First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images that were paired with either a familiar or an unfamiliar distractor image.
-The moderator test was not significant QM(`r r2(rma_Distractor_MP$m)`) = `r r2(rma_Distractor_MP$QM)`, p `r psig(rma_Distractor_MP$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object.
-We next assessed whether distractor familiarity was related to mispronunciation sensitivity.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_Distractor$m)`) = `r r2(rma_Distractor$QM)`, p `r psig(rma_Distractor$QMp)`, but the interaction between distractor familiarity and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
-These results suggest that overall, infants' familiarity with the distractor object (familiar or unfamiliar) did not impact their mispronunciation sensitivity.
-
-```{r PlotDistFamEffect_NoAge}
-
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
-dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "Familiar Distractor", "Unfamiliar Distractor")
-
-# Color Blind palette:
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
-p <- ggplot(dat, aes(condition_label, g_calc, fill = condition_label)) + 
-  geom_boxplot() + 
-  facet_grid(.~dist_code) +
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_4Distractor_fam.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-```{r DistractorTypeAge}
-
-rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)
-
-sum_eff <- coef(summary(rma_DistractorAge))[4,]
-
-rma_DistractorAgeMS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
-
-#summary(rma_DistractorAgeMS)
-
-sum_eff1 <- coef(summary(rma_DistractorAgeMS))[8,]
-sum_eff2 <- coef(summary(rma_DistractorAgeMS))[7,]
-
-```
-
-We next examined whether age modulates object recognition or mispronunciation sensitivity when the distractor image is familiar or unfamiliar.
-For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_DistractorAge$m)`) = `r r2(rma_DistractorAge$QM)`, p `r psig(rma_DistractorAge$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object, regardless of their age.
-We next assessed whether the relationship between distractor familiarity and mispronunciation sensitivity was modulated by age.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_DistractorAgeMS$m)`) = `r r2(rma_DistractorAgeMS$QM)`, p `r psig(rma_DistractorAgeMS$QMp)`.
-Although the three-way-interaction between condition, distractor familiarity, and age was not significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`), here the interaction between condition and distractor familiarity was significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`).
-
-[KATIE] WHAT DOES IT MEAN THAT IN THIS LAST TEST THERE WAS AN INTERACTION BETWEEN CONDITION AND DISTRACTOR FAMILIARITY, WHEN AGE WAS INCLUDED AS A MODERATOR?
-DOES THAT MEAN THAT AGE IS CONTROLLED FOR?
-UNDERSTANDING THIS WILL HELP ME FORMULATE THE CONCLUSION SENTENCE AND MOTIVATE THE NEXT SET OF ANALYSES.
-
-```{r DistractorTypeAgeRangeSubset}
-
-object_pair_ages <- dat %>%
-  group_by(object_pair) %>%
-  summarize(min_age = r2(min(mean_age_1, na.rm=TRUE)),
-            max_age = r2(max(mean_age_1, na.rm=TRUE)),
-            mean_age = r2(mean(mean_age_1, na.rm=TRUE)))
-
-fn <- subset(dat, object_pair=="familiar_novel")
-
-ff <- subset(dat, object_pair=="familiar_familiar")
-
-age_diff_dist <- t.xtable(t.test(fn$mean_age_1, ff$mean_age_1, paired = F))
-
-#t.test(fn$mean_age_1, ff$mean_age_1)
-
-opa <- as.data.frame(object_pair_ages)
-min_age <- max(opa$min_age)
-max_age <- min(opa$max_age)
-
-dat_age_MP= db_ET_MP%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-rma_Distractor_MP <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat_age_MP, random = ~ collapse | short_cite)
-
-#summary(rma_Distractor_MP)
-
-sum_eff <- round(coef(summary(rma_Distractor_MP))[2,], 2)
-
-# misp sensitivity
-dat_age= dat%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-rma_Distractor_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition, data = dat_age, random = ~ collapse | short_cite)
-
-#summary(rma_Distractor_MS)
-
-sum_eff <- coef(summary(rma_Distractor_MS))[2,]
-
-```
-
-Although we anticipated that older children may be more impacted by the presence of a unfamiliar compared to familiar distractor image, we found that age and distractor familiarity did not impact mispronunciation sensitivity.
-Inspection of the ages tested using different kinds of distractors, however, revealed differences.
-Infants tested using a familiar distractor were younger (M = 588.76 days, SD = 136.47, range = 207.8 - 768 days) than those infants tested using an unfamiliar distractor (M = 678.85 days, SD = 115.47, range = 544.48 - 920.2 days), which a two-sample t-test revealed to be a significant difference, t(153.83) = 5.30, p < .0001.
-
-[KATIE] SO, IS IT OKAY TO DO THE AGE SUBSET ANALYSIS AFTER THIS?
-SOMETHING LIKE "TO ENSURE THAT THE LACK OF A DIFFERENCE WASN'T DUE TO THE DIFFERENCE IN AGES OF INFANTS TESTED WITH DIFFERENT TYPES OF DISTRACTORS, WE ANALYZED A SUBSET OF PAPERS THAT TESTED AGES WHERE BOTH FAMILIAR AND UNFAMILIAR DISTRACTORS WERE USED." IN THE SUBSET ANALYSIS, FOR MISP SENSITIVITY, THERE IS A SIGNIFICANT INTERACTION BETWEEN DISTRACTOR FAMILIARITY AND CONDITION.
-
-### Phonological overlap between target and distractor
-
-```{r DistractorOverlap_descrip}
-
-dist_overlap_info <- dat %>%
-  group_by(distractor_overlap) %>%
-  summarize(n_exp_conditions =  n())
-
-```
-
-To assess whether phonological overlap between the target and distractor image labels has an impact on the size of mispronunciation sensitivity, we examined the meta-analytic effect for object identification in response to mispronunciations and mispronunciation sensitivity when the target-distractor pairs either shared the same onset phoneme, had no overlap, or where the distractor was an unfamiliar object.
-We did not include data for which the overlap included both the onset and medial phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset/medial"])`) or coda phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "coda"])`).
-The analysis was therefore based on a subset of the overall dataset, with `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset"])` experimental conditions containing onset phoneme overlap between the target and distractor, `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "no"])` containing no overlap between target and distractor, and `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "novel"])` for targets paired with unfamiliar distractor images.
-There were therfore three possibilities for distractor overlap: onset phoneme overlap, no overlap, and an unfamiliar distractor.
-In our analysis, we were interested in the difference between overlap and lack of overlap; therefore, experimental conditions containing onset phoneme overlap were coded as the reference condition and compared with responses to experimental conditions with no overlap or an unfamiliar distractor separately.
-
-[KATIE] CAN YOU CHECK THE WAY THAT I WROTE THE LAST SENTENCE?
-
-```{r DistractorOverlap}
-db_ET_MPo = db_ET_MP %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
-
-rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
-
-#summary(rma_DistractorOverlap)
-
-db_ET_MPo_MS = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-db_ET_MPo_MS$distractor_overlap <- factor(db_ET_MPo_MS$distractor_overlap, levels = c("onset", "no", "novel"))
-
-rma_DistractorOverlapMS <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MPo_MS, random = ~ collapse | short_cite)
-
-#summary(rma_DistractorOverlapMS)
-
-sum_eff1 <- coef(summary(rma_DistractorOverlapMS))[5,]
-sum_eff2 <- coef(summary(rma_DistractorOverlapMS))[6,]
-
-```
-
-Regarding object identification in response to mispronunciations, when distractor overlap was included as a moderator, the moderator test was not significant QM(`r r2(rma_DistractorOverlap$m)`) = `r r2(rma_DistractorOverlap$QM)`, p `r psig(rma_DistractorOverlap$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with a distractor image that contained overlap on the onset phoneme or no overlap with the target word, or was an unfamiliar object.
-We next assessed whether target-distractor overlap was related to mispronunciation sensitivity.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_DistractorOverlapMS$m)`) = `r r2(rma_DistractorOverlapMS$QM)`, p `r psig(rma_DistractorOverlapMS$QMp)`.
-The interaction between condition and target-distractor pairs with no overlap was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`), suggesting that mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap.
-The interaction between condition and target-distractor pairs with an unfamiliar distractor was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`), suggesting that mispronunciation sensitivity was smaller when the distractor image shared the same onset phoneme as the target image compared to when the distractor image was an unfamiliar object.
-This can be seen in Figure X.
-
-```{r PlotDistOverlapEffect}
-
-db_ET_MPo = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
-
-db_ET_MPo$condition_label <- ifelse(db_ET_MPo$condition==1, "Correct", "Mispronunciation")
-
-p <- ggplot(db_ET_MPo, aes(condition_label, g_calc, fill = condition_label)) + 
-  facet_grid(.~distractor_overlap)+
-  geom_boxplot() + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_5_Distractor_overlap.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-```{r DistractorOverlap_age}
-
-# object recognition
-db_ET_MPo = db_ET_MP %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
-
-rma_DistractorOverlap_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
-
-# mispronunciation sensitivity
-dat_MPo = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-dat_MPo$distractor_overlap <- factor(dat_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
-
-rma_DistractorOverlap_age_MS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap*condition, data = dat_MPo, random = ~ collapse | short_cite)
-
-#summary(rma_DistractorOverlap_age_MS)
-
-sum_eff1 <- coef(summary(rma_DistractorOverlap_age_MS))[11,]
-sum_eff2 <- coef(summary(rma_DistractorOverlap_age_MS))[12,]
-
-```
-
-Although we did not have any specific predictions about the relationship between infant age and the impact of distractor overlap on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
-First, for object recognition in response to mispronunciations, when age in addition to distractor overlap was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_DistractorOverlap_age$m)`) = `r r2(rma_DistractorOverlap_age$QM)`, p `r psig(rma_DistractorOverlap_age$QMp)`, suggesting that upon hearing a mispronunciation, infants looks to the target image were similar for the three types of overlap, regardless of infant age.
-We next assessed whether the relationship between distractor overlap and mispronunciation sensitivity was modulated by age.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_DistractorOverlap_age_MS$m)`) = `r r2(rma_DistractorOverlap_age_MS$QM)`, p `r psig(rma_DistractorOverlap_age_MS$QMp)`.
-The interaction between age, condition, and target-distractor pairs with no overlap was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`).
-As can be seen in Figure X, the difference between correct pronunciations and mispronunciations (mispronunciation sensitivity) stays steady across infant ages for both target words paired with distractors containing onset overlap with the target word as well as distractors containing no overlap.
-As infants aged, however, overall recognition (regardless of condition) increased for target-distractor pairs containing onset overlap, whereas for overall recognition decreased for target-distractor pairs containing no overlap.
-The interaction between age, condition, and target-distractor pairs with an unfamiliar distractor was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`).
-As can also be seen in Figure X, mispronunciation sensitivity for target words paired with unfamiliar distractors decreased with age, while it remained steady across a similar range of ages for target words paired with distractors containing onset overlap with the target word.
-
-```{r PlotDistOverlap_cond_age}
-
-db_ET_MPo = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
-
-db_ET_MPo$condition_label <- ifelse(db_ET_MPo$condition==1, "Correct", "Mispronunciation")
-
-p <- ggplot(db_ET_MPo, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-    facet_grid(.~distractor_overlap)+
-  geom_point(aes(size = weights_g),show.legend=FALSE) + 
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_6_Distractor_overlap_age.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-### Position of mispronunciation
-
-```{r Location_descrip}
-
-misp_location_info <- dat %>%
-  group_by(mispron_location) %>%
-  summarize(n_exp_conditions =  n())
-
-```
-
-To assess whether the position of the mispronunciation has an impact on mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to mispronunciations on the onset and medial phonemes.
-We did not include data for which the mispronunciation was located on the coda (*n* = `r with(misp_location_info, n_exp_conditions[mispron_location == "coda"])`), varied in regard to position (*n* = `r with(misp_location_info, n_exp_conditions[mispron_location == "coda/medial" | mispron_location == "onset/medial" | mispron_location == "onset/medial/coda"])`), or was not reported (*n* = `r with(misp_location_info, n_exp_conditions[is.na(mispron_location)])`).
-The analysis was therefore based on a subset of the overall dataset, with `r with(misp_location_info, n_exp_conditions[mispron_location == "onset"])` experimental conditions comparing a mispronunciation on the onset phoneme and `r with(misp_location_info, n_exp_conditions[mispron_location == "medial"])` experimental conditions comparing a mispronunciation on the medial phoneme.
-
-```{r Location_misp}
-#table(db_ET_MP$mispron_location)
-
-db_ET_MPl = db_ET_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("onset", "medial"))
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_Location_MP <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_MPl, random = ~collapse | short_cite)
-
-db_ET_MPl = dat %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("onset", "medial"))
-
-rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition, data = db_ET_MPl, random = ~collapse | short_cite)
-
-sum_eff <- coef(summary(rma_LocationCondition))[4,]
-
-```
-
-Regarding object identification in response to mispronunciations, when mispronunciation location was included as a moderator, the moderator test was not significant QM(`r r2(rma_Location_MP$m)`) = `r r2(rma_Location_MP$QM)`, p `r psig(rma_Location_MP$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was located on the onset or  medial phonemes.
-We next assessed whether mispronunciation location was related to mispronunciation sensitivity.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_LocationCondition$m)`) = `r r2(rma_LocationCondition$QM)`, p `r psig(rma_LocationCondition$QMp)`, but the interaction between mispronunciation location and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
-These results suggest that overall, the location of the mispronunciation (onset, medial) did not impact mispronunciation sensitivity.
-
-```{r PlotPositionEffect}
-
-#dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial" |
-#                mispron_location == "offset")
-
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
-
-dat.p = dat %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-dat.p$mispron_location <- factor(dat.p$mispron_location, levels = c("onset", "medial"))
-
-p <- ggplot(dat.p, aes(condition_label, g_calc, fill = condition_label)) + 
-  facet_grid(.~mispron_location)+
-  geom_boxplot() + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_7_Mispronunciation_position.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-```{r Location_misp_age}
-#table(db_ET_MP$mispron_location)
-
-db_ET_MPl = db_ET_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("onset", "medial"))
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_Location_MP_age <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
-
-db_ET_MPl = dat %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("onset", "medial"))
-
-rma_LocationCondition_age <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
-
-sum_eff <- coef(summary(rma_LocationCondition))[8,]
-
-```
-
-Although we did not have any specific predictions about the relationship between infant age and the impact of mispronuncition location on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
-First, for object recognition in response to mispronunciations, when age in addition to mispronunciation location was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_Location_MP_age$m)`) = `r r2(rma_Location_MP_age$QM)`, p `r psig(rma_Location_MP_age$QMp)`, suggesting that upon hearing a mispronunciation, infants looks to the target image were similar for both onset and medial mispronunciations, regardless of infant age.
-We next assessed whether the relationship between mispronunciation location and mispronunciation sensitivity was modulated by age.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_LocationCondition_age$m)`) = `r r2(rma_LocationCondition_age$QM)`, p `r psig(rma_LocationCondition_age$QMp)`, but the interaction between mispronunciation location, age, and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
-These results provide further evidence that location of the mispronunciation (onset, medial) did not impact mispronunciation sensitivity.
-
-### Type of mispronunciation (consonant or vowel)
-
-```{r CV_descript}
-
-CV_info <- dat %>%
-  group_by(type_feature) %>%
-  summarize(n_exp_conditions =  n())
-
-CV_location_info <- dat %>%
-  group_by(type_feature, mispron_location) %>%
-  summarize(n_exp_conditions =  n())
-
-```
-
-To assess whether the type of mispronunciation impacts sensitivity to mispronunciations, we calculated the meta-analytic effect for object identification in response to the type of mispronunciation.
-Although most theoretical discussion of mispronunciation type has focused on consonants and vowels, our dataset also included tone mispronunciations.
-In our analysis, we were interested in the difference between consonants and vowels, but also include an exploratory analysis of responses to tones, consonants, and vowels.
-We therefore conducted two sets of analyses, one analyzing consonants and vowels alone and a second comparing responses to tones with that of consonants and vowels, separately.
-For the latter analysis, tones were coded as the reference condition.
-We did not include data for which mispronunciation type varied within experiment and was not reported separately (*n* = `r with(CV_info, n_exp_conditions[type_feature == "consonant_and_vowel" | type_feature == "consonant_vowel_tone"])`).
-The analysis was therefore based on a subset of the overall dataset, with `r with(CV_info, n_exp_conditions[type_feature == "consonant"])` experimental conditions comparing a consonant mispronunciation, `r with(CV_info, n_exp_conditions[type_feature == "vowel"])` experimental conditions comparing a vowel mispronunciation, and `r with(CV_info, n_exp_conditions[type_feature == "tone"])` experimental conditions comparing a tone mispronunciation.
-Below, we first report the set of analyses comparing consonants with vowels before moving on to the second set of exploratory analyses comparing tones with that of consonants and vowels.
-
-[KATIE] WHAT DO YOU THINK ABOUT THIS?
-WE HAVE THE TONES AND ITS A NOVEL, INTERESTING THING, I THINK, AND PERHAPS WORTH IT TO INCLUDE A COMPARISON OF TONES ALONGSIDE THE MORE THEORETICALLY IMPORTANT COMPARISON BETWEEN CONSONANTS AND VOWELS.
-
-```{r MPtype_cv}
-
-# C vs. V
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel")
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("consonant", "vowel"))
-
-rma_TypeFeaturesMP <- rma.mv(g_calc, g_var_calc, mods = ~type_feature, data = db_MP_type, random = ~collapse | short_cite)
-
-# C vs. V with condition
-
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition, data = db_type, random = ~collapse | short_cite)
-
-sum_eff1 <- coef(summary(rma_TypeFeaturesMP_Condition))[4,]
-
-```
-
-We first analyzed experimental conditions where mispronunciation type was either a consonant or vowel.
-Regarding object identification in response to mispronunciations, when mispronunciation type was included as a moderator, the moderator test was not significant QM(`r r2(rma_TypeFeaturesMP$m)`) = `r r2(rma_TypeFeaturesMP$QM)`, p `r psig(rma_TypeFeaturesMP$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was a consonant or a vowel.
-We next assessed whether type of mispronunciation (consonant or vowel) was related to mispronunciation sensitivity.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, p `r psig(rma_TypeFeaturesMP_Condition$QMp)`, but the interaction between mispronunciation type and condition was not significant $\beta$ = `r r2(sum_eff1$estimate)`, (SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`).
-These results suggest that overall, the type of  mispronunciation (consonant vs.
-vowel) did not impact mispronunciation sensitivity.
-
-```{r MPtype_cv_age}
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("consonant", "vowel"))
-
-rma_TypeFeaturesMPage <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~collapse | short_cite)
-
-sum_eff <- coef(summary(rma_TypeFeaturesMP_Condition))[8,]
-
-```
-
-We next examined whether age modulates object recognition or mispronunciation sensitivity when the mispronunciation is a consonant or vowel.
-For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_TypeFeaturesMPage$m)`) = `r r2(rma_TypeFeaturesMPage$QM)`, p `r psig(rma_TypeFeaturesMPage$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was on a consonant or vowel phoneme, regardless of their age.
-We next assessed whether the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity was modulated by age.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, p `r psig(rma_TypeFeaturesMP_Condition$QMp)`.
-The interaction between mispronunciation type, condition, and age was significant ($\beta$ = `r r2(sum_eff$estimate)`, SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], p `r psig(sum_eff$pval)`).
-As can be seen in Figure X, as infants age, mispronunciation sensitivity grows larger for vowel mispronunciations but becomes smaller for consonant mispronunciations.
-Noticeably, mispronunciation sensitivity appears greater for consonant compared to vowel mispronunciations at younger ages, but this difference shifts as infants age.
-
-```{r PlotCVEffect_cond_age}
-
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
-dat_type$type_feature <- ifelse(dat_type$type_feature == "consonant", "Consonant", "Vowel")
-
-#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
-
-#dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-
-dat_type$condition_label = ifelse(dat_type$condition==1, "Correct", "Mispronunciation")
-
-p <- ggplot(dat_type, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-    facet_grid(.~type_feature)+
-  geom_point(aes(size = weights_g),show.legend=FALSE) + 
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_8_FeatureType_Cond_Age.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-```{r MPtype_cv_lang_descript}
-
-family <- dat %>%
-  group_by(lang_family) %>%
-  summarize(count = n())
-
-lang_family <- dat %>%
-  group_by(native_lang, lang_family) %>%
-  summarize(count = n())
-
-cv_family <- dat %>%
-  group_by(type_feature, lang_family) %>%
-  summarize(count = n())
-
-```
-
-```{r MPtype_cv_lang}
-
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("consonant", "vowel"))
-
-db_MP_type <- subset(db_MP_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeaturesMPfam <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family, data = db_MP_type, random = ~collapse | short_cite)
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-db_type <- subset(db_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeaturesMPC <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family, data = db_type, random = ~collapse | short_cite)
-
-sum_eff1 <- coef(summary(rma_TypeFeaturesMPC))[7,]
-sum_eff2 <- coef(summary(rma_TypeFeaturesMPC))[8,]
-
-# summary(glht(rma_TypeFeaturesMPC, linfct=cbind(contrMat(rep(1,8), type="Tukey"))), test=adjusted("none"))
-# 
-# ranef(rma_TypeFeaturesMPC)
-
-```
-
-To examine whether infants' native language impacts sensitivity to consonant and vowel mispronunciations, we classified infants into language families.
-Infants learning American English (*n* = `r with(lang_family, count[native_lang == "American English"])`), British English (*n* = `r with(lang_family, count[native_lang == "British English"])`), Danish (*n* = `r with(lang_family, count[native_lang == "Danish"])`), Dutch (*n* = `r with(lang_family, count[native_lang == "Dutch"])`), and German (*n* = `r with(lang_family, count[native_lang == "German"])`) were classified into the Germanic language family (*n* = `r with(family, count[lang_family == "Germanic"])`).
-Infants learning Catalan (*n* = `r with(lang_family, count[native_lang == "Catalan"])`), Spanish (*n* = `r with(lang_family, count[native_lang == "Spanish"])`), French (*n* = `r with(lang_family, count[native_lang == "French"])`), Catalan and Spanish simultaneously (i.e.
-bilinguals; *n* = `r with(lang_family, count[native_lang == "Catalan-Spanish"])`), and Swiss French (*n* = `r with(lang_family, count[native_lang == "Swiss French"])`) were classified into the Romance language family (*n* = `r with(family, count[lang_family == "Romance"])`).
-For object recognition in response to a mispronunciation, including language family as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_TypeFeaturesMPfam$m)`) = `r r2(rma_TypeFeaturesMPfam$QM)`, p `r psig(rma_TypeFeaturesMPfam$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was on a consonant or vowel phoneme, regardless of the language family of their native language.
-We next assessed whether the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity was modulated by language family.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family as additional moderators.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMPC$m)`) = `r r2(rma_TypeFeaturesMPC$QM)`, p `r psig(rma_TypeFeaturesMPC$QMp)`.
-The interaction between condition and language family was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`), suggesting XXXXXXXXXXXXXX.
-The interaction between mispronunciation type, condition, and language family was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`).
-As can be seen in Figure X, mispronunciation sensitivity for consonants was similar for Germanic and Romance languages.
-Mispronunciation sensitivity for vowels, however, was greater for Germanic compared to Romance languages.
-
-[KATIE] I'M NOT REALLY SURE WHAT THE CONDITION BY LANGUAGE FAMILY INTERACTION MEANS. SHOULD WE EVEN INTERPRET IT?
-
-```{r PlotCVEffect_Lang}
-
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
-dat_type$type_feature <- ifelse(dat_type$type_feature == "consonant", "Consonant", "Vowel")
-
-#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
-
-dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-
-dat_type_sub$condition_label = ifelse(dat_type_sub$condition==1, "Correct", "Mispronunciation")
-
-p <- ggplot(dat_type_sub, aes(condition_label, g_calc, fill = condition_label)) + 
-  geom_boxplot() + 
-  facet_grid(.~type_feature*lang_family)+
-  #geom_line(y= 0, linetype="dotted") + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-    scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        axis.text.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  xlab("Language Family") + 
-  ylab("Effect size Hedges' g")
-p
-
- jpeg(filename = "figures/Figure_9_FeatureType_Cond_LangFam.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-```{r MPtype_cv_lang_age}
-
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("consonant", "vowel"))
-
-db_MP_type <- subset(db_MP_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeaturesMPfam <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family*age.C, data = db_MP_type, random = ~collapse | short_cite)
-
- sum_eff1 <- coef(summary(rma_TypeFeaturesMPC))[8,]
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-db_type <- subset(db_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeaturesMPC <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family, data = db_type, random = ~collapse | short_cite)
-
-sum_eff1 <- coef(summary(rma_TypeFeaturesMPC))[7,]
-sum_eff2 <- coef(summary(rma_TypeFeaturesMPC))[8,]
-
-# summary(glht(rma_TypeFeaturesMPC, linfct=cbind(contrMat(rep(1,8), type="Tukey"))), test=adjusted("none"))
-# 
-# ranef(rma_TypeFeaturesMPC)
-
-```
-
-Finally, we examined the relationship between language family and infant age and mispronunciation sensitivity to consonants and vowels.
-For object recognition in response to a mispronunciation, including language family and infant age as a moderator resulted in a moderator test that was significant, QM(`r r2(rma_TypeFeaturesMPfam$m)`) = `r r2(rma_TypeFeaturesMPfam$QM)`, p `r psig(rma_TypeFeaturesMPfam$QMp)`.
-The interaction between language family, age, and type of mispronunciation (consonant or vowel) was significant, ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`).
-As can be seen in Figure X, for infants learning Germanic languages, increasing age was related to increasing mispronunciation sensitivity for vowel mispronunciations, but decreasing sensitivity for consonant mispronunciations.
-In contrast, infants learning Romance languages have an even greater increase with age in sensitivity to vowel mispronunciations.
-Surprisingly, sensitivity to consonant mispronunciations shows a reversal in infants learning Romance languages: the growth in target looks for consonant mipronunciations increases and surpases that of target looks for correct pronunciations.
-
-[KATIE] AGAIN, THERE ARE ADDITIONAL INTERACTIONS THAT ARE SIGNIFICANT... SHOULD THEY BE INTERPRETED? ALSO, WTF ROMANCE LANGUAGES?
-
-```{r PlotCVEffect_cond_age_fam}
-
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
-dat_type$type_feature <- ifelse(dat_type$type_feature == "consonant", "Consonant", "Vowel")
-
-#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
-
-dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-
-dat_type_sub$condition_label = ifelse(dat_type_sub$condition==1, "Correct", "Mispronunciation")
-
-p <- ggplot(dat_type_sub, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-    facet_grid(.~type_feature*lang_family)+
-  geom_point(aes(size = weights_g),show.legend=FALSE) + 
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_10_FeatureType_Cond_Age_LangFam.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-```{r MPtype_cvt}
-
-# C vs. V vs. T
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" | type_feature == "tone")
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("tone", "consonant", "vowel"))
-
-rma_TypeFeaturesMPT <- rma.mv(g_calc, g_var_calc, mods = ~type_feature, data = db_MP_type, random = ~collapse | short_cite)
-
-# C vs. V vs. T with condition
-
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel"| type_feature == "tone")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("tone", "consonant", "vowel"))
-
-rma_TypeFeaturesMP_ConditionT <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition, data = db_type, random = ~collapse | short_cite)
-
-sum_eff2c <- coef(summary(rma_TypeFeaturesMP_ConditionT))[5,]
-sum_eff2v <- coef(summary(rma_TypeFeaturesMP_ConditionT))[6,]
-
-```
-
-Although we had no predictions regarding mispronunciation sensitivity to tone mispronunciations, we included an exploratory analysis to examine whether responses to tone mispronunciations were different from that of consonants or vowels.
-Regarding object identification in response to mispronunciations, when mispronunciation type was included as a moderator, the moderator test was not significant QM(`r r2(rma_TypeFeaturesMPT$m)`) = `r r2(rma_TypeFeaturesMPT$QM)`, p `r psig(rma_TypeFeaturesMPT$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for tone mispronunciations in comparison with both consonants and vowels.
-We next assessed whether type of mispronunciation (tone, consonant, vowel) was related to mispronunciation sensitivity.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_ConditionT$m)`) = `r r2(rma_TypeFeaturesMP_ConditionT$QM)`, p `r psig(rma_TypeFeaturesMP_ConditionT$QMp)`.
-The interaction between condition and consonant mispronunciations was not significant $\beta$ = `r r2(sum_eff2c$estimate)`, (SE = `r r2(sum_eff2c$se)`, 95% CI [`r r2(sum_eff2c$ci.lb)`, `r r2(sum_eff2c$ci.ub)`], p `r psig(sum_eff2c$pval)`), suggesting that there was no difference in looks to the target in response to consonant and tone mispronunciations.
-The interaction between condition and vowel mispronunciations was also not significant $\beta$ = `r r2(sum_eff2v$estimate)`, (SE = `r r2(sum_eff2v$se)`, 95% CI [`r r2(sum_eff2v$ci.lb)`, `r r2(sum_eff2v$ci.ub)`], p `r psig(sum_eff2v$pval)`), suggesting that there was no difference in looks to the target in response to vowel and tone mispronunciations.
-
-```{r MPtype_cvt_age}
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" | type_feature == "tone")
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("tone", "consonant", "vowel"))
-
-rma_TypeFeaturesMPage <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" | type_feature == "tone")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("tone", "consonant", "vowel"))
-
-rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~collapse | short_cite)
-
-sum_eff1 <- coef(summary(rma_TypeFeaturesMP_Condition))[11,]
-sum_eff2 <- coef(summary(rma_TypeFeaturesMP_Condition))[12,]
-
-```
-
-We further included an exploratory analysis of the relationship between infant age and the impact of tone mispronunciations in comparison to consonant and vowel mispronunciations.
-First, for object recognition in response to mispronunciations, when age in addition to mispronunciation location was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_TypeFeaturesMPage$m)`) = `r r2(rma_TypeFeaturesMPage$QM)`, p `r psig(rma_TypeFeaturesMPage$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were not different between tone and vowel or tone and consonant mispronunciations, regardless of their age.
-We next assessed whether the relationship between mispronunciation type (tone, consonant, vowel) and mispronunciation sensitivity was modulated by age.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, p `r psig(rma_TypeFeaturesMP_Condition$QMp)`, but the interactions between condition, age, and both consonant mispronciations ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], p `r psig(sum_eff1$pval)`) and vowel mispronunciations ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], p `r psig(sum_eff2$pval)`) were not significant.
-Infants' sensitivity to tone mispronunciations compared to consonant or vowel mispronunciations did not differ with age.
-
-[KATIE] WORTH IT TO INCLUDE LANGUAGE FAMILY ANALYSES TOO?
 
@@
 
-To Summarize:
+\newpage
 
-** Overall Meta-analytic Effect **
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
-  + Accept mispronunciations as labels for targets
-  + Sensitive to mispronunciations
-  + lack of change over development
-
-** Vocabulary **
-
-  + no relationship?
-  + talk about how few studies report it
-
-** Size of Mispronunciation **
-
-  + graded sensitivity to number of features changed in a mispronunciation
-  + importance for controlling in experimental design
-  + Perhaps a call for more studies to include multiple number of features changed, so that this can be assessed? There was a narrow age where this was actually manipulated.
-
-** Distractor Familiarity **
-
-  + Not really sure, check the results. A key interaction is significant in one model but not the other.
-  + Again, ages not matched very well for the two groups here. Decide about whether to include a age subset analysis
-
-** Phonological overlap between target and distractor **
-
-  + mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap
-  + this is rather the opposite of what one would expect, right?
-  + mispronunciation sensitivity was smaller when the distractor image shared the same onset phoneme as the target image compared to when the distractor image was an unfamiliar object
-  + Maybe it would be useful to have time course analyses to address this issue further
-  + As infants aged, overall recognition (regardless of condition) increased for target-distractor pairs containing onset overlap, whereas overall recognition decreased for target-distractor pairs containing no overlap.
-  + mispronunciation sensitivity for target words paired with unfamiliar distractors decreased with age, while it remained steady across a similar range of ages for target words paired with distractors containing onset overlap with the target word.
-
-** Position of mispronunciation **
-
-  + really no impact at all
-
-** Type of mispronunciation **
-
-  + Overall, no difference between consonants and vowels 
-  + Consonant mispronunciation sensitivity decreases with age
-  + Vowel mispronunciation sensitivity increases with age
-  + mispronunciation sensitivity for consonants similar for Germanic and Romance languages
-  + Mispronunciation sensitivity for vowels greater for Germanic compared to Romance languages
-  + For Germanic infants, increasing age was related to increasing mispronunciation sensitivity for vowel mispronunciations, but decreasing sensitivity for consonant mispronunciations. 
-  + For Romance infants, an even greater increase with age in sensitivity to vowel mispronunciations. 
-  + For Romance infants, the growth in target looks for consonant mipronunciations increases and surpases that of target looks for correct pronunciations
-  + exploratory analyses with tone mispronunciations suggest no great difference in sensitivity when compared to consonant and vowel mispronunciations
-
-When it comes to designing studies, best practices and current standards might not always overlap.
-Indeed, across a set of previous meta-analyses it was shown that particularly infant research does not adjust sample sizes according to the effect in question (Bergmann et al., in press).
-A meta-analysis is a first step in improving experiment planning by measuring the underlying effect and its variance, which is directly related to the sample needed to achieve satisfactory power in the null hypothesis significance testing framework.
-Failing to take effect sizes into account can both yield to underpowered research and to testing too many participants, both consequences are undesirable for a number of reasons that have been discussed in depth elsewhere.
-We will just briefly mention two that we consider most salient for theory building: Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature (citationcitation).
-Overpowered studies mean that participants were tested unnecessarily, which has substantial ethical consequences particularly when working with infants and other difficult to recruit and test populations.
-
-From Christina: let's make a note to put sth in the discussion about our curve being surprisingly flat for correctly pronounced words bc people adapt their analysis windows?
-Bc if you look at Molly's reaction time paper, there is a steep increase.
-
-Discussing the Moderator Analyses
-Maybe put them together into the ones that worked out as we predicted and those that didn’t?
-So, here is evidence that supports existing arguments, that doesn’t need to be a huge chunk.
-But then more space devoted to moderator analyses that didn’t work out according to predictions.
-
-It should be noted that the majority of consonant mispronunciations were located on the onset phoneme (*n* = `r with(CV_location_info, n_exp_conditions[type_feature == "consonant" & mispron_location == "onset"])`; total consonant conditions, *n* = `r with(CV_info, n_exp_conditions[type_feature == "consonant"])`), while the majority of vowel mispronunciations were located on the medial phoneme (*n* = `r with(CV_location_info, n_exp_conditions[type_feature == "vowel" & mispron_location == "medial"])`; total vowel conditions, *n* = `r with(CV_info, n_exp_conditions[type_feature == "vowel"])`).
-In their analysis using TRACE, Mayor and Plunkett (2014) found that the difference between sensitivity to consonant and vowel mispronunciations was due to infants' lexical knowlege consisting of a majority consonant onset words.
-
-[KATIE] COME BACK TO THIS.
+<div id = "refs"></div>
+\endgroup

### 2018-10-23 Untitled.tex
convert to papaja, temporary references fix

--- 2018-10-23 Paper_Analyses.tex
@@
 \hypersetup{unicode=true,
-            pdftitle={The development of infants' responses to mispronunciations - A Meta-Analysis},
-            pdfauthor={Katie Von Holzen~\& Christina Bergmann},
+            pdftitle={The title},
+            pdfauthor={First Author~\& Ernst-August Doelle},
             pdfkeywords={keywords},
@@
 \setlength{\droptitle}{-2em}
-  \title{The development of infants' responses to mispronunciations - A
-Meta-Analysis}
+  \title{The title}
   \pretitle{\vspace{\droptitle}\centering\huge}
   \posttitle{\par}
-  \author{Katie Von Holzen\textsuperscript{1,2}~\& Christina
-Bergmann\textsuperscript{3,4}}
+  \author{First Author\textsuperscript{1}~\& Ernst-August
+Doelle\textsuperscript{1,2}}
   \preauthor{\centering\large\emph}
@@
 
-\shorttitle{Mispronunciation Meta-Analysis}
+\shorttitle{Title}
 \affiliation{
 \vspace{0.5cm}
-\textsuperscript{1} Language Development Laboratory, University of Maryland, USA\\\textsuperscript{2} Laboratoire Psychologie de la Perception, Université Paris Descartes\\\textsuperscript{3} Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands\\\textsuperscript{4} LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University}
+\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}
 \keywords{keywords\newline\indent Word count: X}
@@
 
-\authornote{
+\authornote{Add complete departmental affiliations for each
+author here. Each new line herein must be indented, like this line.
 
-Correspondence concerning this article should be addressed to Katie Von
-Holzen, 0221A LeFrak Hall, University of Maryland, College Park, MD
-20742. E-mail:
-\href{mailto:katie.m.vonholzen@gmail.com}{\nolinkurl{katie.m.vonholzen@gmail.com}}}
+Enter author note here.
+
+Correspondence concerning this article should be addressed to First
+Author, Postal address. E-mail:
+\href{mailto:my@email.com}{\nolinkurl{my@email.com}}}
 
@@
 
-\usepackage{amsthm}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{corollary}{Corollary}[section]
-\newtheorem{proposition}{Proposition}[section]
-\theoremstyle{definition}
-\newtheorem{example}{Example}[section]
-\theoremstyle{definition}
-\newtheorem{exercise}{Exercise}[section]
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\newtheorem*{solution}{Solution}
 \begin{document}
@@
 
-\section{Introduction}\label{introduction}
-
-Acquiring a first language means that young learners are solving a host
-of tasks in a short amount of time. As infants develop into toddlers
-during their second and third years they learn new words in earnest
-while simultaneously refining their knowledge about the sounds that make
-up these words. Before children can correctly pronounce a word, they
-already show evidence of sensitivity to slight variations in the
-phonological form of that word. This mispronunciation sensitivity
-reflects the specificity with which infants represent the phonological
-information of familiar words and are sensitive to changes that might
-signal a change in word meaning. As infants continue to develop into
-expert language users, their language processing matures and becomes
-more efficient. In a mature phono-lexical system, word recognition must
-balance flexibility to slight variation (e.g., speaker identity,
-accented speech) while distinguishing between phonetic details that
-differentiate words in their native language (e.g.~cat-hat). In this
-paper, we aggregate and analyze the almost 20 years of literature
-investigating mispronunciation sensitivity in infants in an attempt to
-uncover its characteristics and the trajectory of its development.
-
-At the turn of the millenia, infant language acquisition researchers had
-established that during their first years of life, infants are sensitive
-to changes in the phonetic detail of newly segmented words (Jusczyk \&
-Aslin, 1995) and learned minimal pairs (Stager \& Werker, 1997).
-Furthermore, when presented with familiar image pairs, children fixate
-on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg,
-\& McRoberts, 1998). Swingley and Aslin (2000) were the first to tie
-these lines of research together and investigate mispronunciation
-sensitivity in infant familiar word recognition: Children aged 18 to 23
-months learning American English were presented with pairs of images
-(e.g.~baby, dog) and their eye movements to each image were coded
-offline. On \enquote{correct} trials, children heard the correct label
-for one of the images (e.g.~baby). On \enquote{mispronounced} trials,
-children heard a mispronounced label of one of the images (e.g.~vaby).
-Mean proportion of fixation to the target image (here: a baby) was
-calculated for both correct and mispronounced trials by dividing the
-target looking time by the sum of total looking time to both target and
-a distractor (proportion of target looking or PTL). Mean fixations in
-correct trials were significantly greater than in mispronounced trials,
-although looks to the target were significantly greater than chance in
-both types of trials. We refer to this pattern of a difference between
-looks to correct and mispronounced words as \emph{mispronunciation
-sensitivity} and of looks to the target image above chance as
-\emph{recognition}. Swingley and Aslin (2000) concluded that already
-before the second birthday, children represent words with sufficient
-detail to be sensitive to mispronunciations.
-
-The study of Swingley and Aslin (2000) as well as subsequent studies
-examining mispronunciation sensitivity address two complementary
-concepts in early phonological development: \emph{phonological
-constancy} and \emph{phonological distinctiveness}. Phonological
-constancy is the ability to accept phonological variation across
-different instances of a word, as long as the variation does not
-compromise the overall identity of the word. For example, different
-speakers - particularly across genders and accents - produce the same
-word with notable acoustic variation, although the word remains the
-same. In contrast, phonological distinctiveness describes the ability to
-differentiate between different words that happen to be phonologically
-similar, such as bad/bed or cat/hat. To successfully recognize words,
-infants must therefore simultaneously use both phonological constancy
-and distinctiveness to determine where phonological variation is
-appropriate and where it changes a word's meaning.
-
-In the current study, we focus on infants' developing ability to
-correctly apply the principles of phonological distinctiveness and
-constancy by using a meta-analytic approach to investigate
-mispronunciation sensitivity. Considering that infants are sensitive to
-mispronunciations and that, in general, their processing matures with
-development, we examine the shape of mispronunciation sensitivity over
-the course of the second and third year. There are three distinct
-possibilities how mispronunciation sensitivity might change as infants
-become native speakers, which are all respectively predicted by
-theoretical accounts and supported by single studies. By aggregating all
-publicly available evidence using meta-analysis, we can examine
-developmental trends making use of data from a much larger and diverse
-sample of infants. Before we outline the meta-analytical approach and
-its advantages in detail, we first discuss the proposals this study
-seeks to disentangle and the data supporting each of the accounts.
-
-Young infants may begin cautiously in their approach to word
-recognition, rejecting any phonological variation in familiar words and
-only later learning to accept appropriate variability. According to the
-Perceptual Attunement account, this describes a shift away from specific
-native phonetic patterns to a more mature understanding of the abstract
-phonological structure of words (Best 1994, 1995). This shift is
-predicted to coincide with the vocabulary spurt around 18 months, and is
-therefore related to vocabulary growth. In this case, we would expect
-the size of mispronunciation sensitivity to be larger at younger ages
-and \emph{decrease} as the child matures and learn more words, although
-children continue to detect mispronunciations. Indeed, young infants are
-less likely than older infants to demonstrate recognition of familiar
-words (Best, Tyler, Gooding, Orlando, \& Quann, 2009; Mulak, Best, \&
-Tyler, 2013) or learn new words (Schmale, Hollich, \& Seidl, 2011) from
-accented speakers.
-
-According to a different theoretical framework, young infants may
-instead begin with phonologically broad representations for familiar
-words and only refine their representations as language experience
-accumulates. PRIMIR (Processing Rich Information from Multidimensional
-Interactive Representations; Curtin \& Werker, 2007; Werker \& Curtin,
-2005; Curtin, Byers-Heinlein, \& Werker, 2011) describes the development
-of phonemic categories emerging as the number of word form-meaning
-linkages increases. Vocabulary growth, therefore, promotes more detailed
-phonological representations in familiar words. Following this account,
-we predict an \emph{increase} in mispronunciation sensitivity as infants
-mature and add more words to their growing lexicon.
-
-Finally, sensitivity to mispronunciation may not be modulated by
-development at all. Infants' overall language processing becomes more
-efficient, but their sensitivity to mispronunciations may not change.
-Across infancy and toddlerhood, mispronunciations would thus be detected
-and lead to less looks at a target than correct pronunciations, but the
-size of this effect would not change, nor be related to vocabulary size.
-This pattern is not predicted by any mainstream theory of language
-acquisition, but for completeness we mention it here.
-
-Research following the seminal study by Swingley and Aslin (2000) has
-extended mispronunciation sensitivity to infants as young as 12 months
-(Mani \& Plunkett, 2010), indicating that from early stages of the
-developing lexicon onwards, infants can and do detect mispronunciations.
-Regarding the change in mispronunciation sensitivity over development,
-however, only a handful of studies have compared more than one age group
-on the same mispronunciation task (see Table X), making the current
-meta-analysis very informative. One study has found evidence for infants
-to become \emph{less} sensitive to mispronunciations as children
-develop. Mani and Plunkett (2011) presented 18- and 24-month-olds with
-mispronunciations varying in the number of features changed (see below
-for a discussion of the role of features). 18-month-olds were sensitive
-to mispronunciations, regardless of the number of features changed.
-24-month-olds, in contrast, fixated the target image equally for both
-correct and 1-feature mispronounced trials, although they were sensitive
-to larger mispronunciations. In other words, for 1-feature
-mispronunciations at least, sensitivity decreased from 18 to 24 months,
-providing support to the prediction that mispronunciation sensitivity
-may decrease with development.
-
-In contrast, other studies have found evidence for \emph{greater}
-mispronunciation sensitivity as children develop. More precisely, the
-difference in target looking for correct and mispronounced trials is
-smaller in younger infants and grows as infants develop. Mani and
-Plunkett (2007) tested 15-, 18-, and 24-month-olds learning British
-English; although all three groups were sensitive to mispronunciations,
-15-month-olds showed a less robust sensitivity. An increase in
-sensitivity to mispronunciations has also been found from 20 to 24
-months (van der Feest \& Fikkert, 2015) and 15 to 18 months (Altvater
-Mackensen et al., 2013) in Dutch infants, as well as German infants from
-22 to 25 months (Altvater-Mackensen, 2010). Furthermore, van der Feest
-and Fikkert (2015) found that sensitivity to specific kinds of
-mispronunciations develop at different ages depending on language
-infants are learning. In other words, the native language constraints
-which \emph{kinds} of mispronunciations infants are sensitive to first,
-and that as infants develop, they become sensitive to other
-mispronunciations. These studies award support to the prediction that
-mispronunciation sensitivity improves with development.
-
-Finally, some studies have found no difference in mispronunciation
-sensitivity at different ages. Swingley and Aslin (2000) tested infants
-over a wide age range of 5 months (18 to 23 months). They found that age
-correlated with target fixations for both correct and mispronounced
-labels, whereas the difference between the two (mispronunciation effect)
-did not. This suggests that as children develop, they are more likely to
-look at the target in the presence of a mispronounced label and that age
-is not related to mispronunciation sensitivity. A similar response
-pattern has been found for British English learning infants aged between
-18 and 24 months (Bailey \& Plunkett, 2002) as well as younger
-French-learning infants at 12 and 17 months (Zesiger, Lozeron, Levy, \&
-Frauenfelder, 2012). These studies award support to the prediction that
-mispronunciation sensitivity does not change with development.
-
-Why would mispronunciation sensitivity change as infants develop, and
-would it increase or decrease? The main hypothesis is related to
-vocabulary growth. Both the Perceptual Attunement (Best, 1994; 1995) and
-PRIMIR (Curtin \& Werker, 2007; Werker \& Curtin, 2005; Curtin,
-Byers-Heinlein, \& Werker, 2011) accounts situate a change in
-mispronunciation sensitivity occurring along with an increase in
-vocabulary size, particularly with the vocabulary spurt at about 18
-months. Knowing more words helps infants shift their focus to the
-relevant phonetic dimensions needed for word recognition. On the one
-hand, a smaller lexicon does not require full specification to
-differentiate between words; as more phonologically similar words are
-learned, so does the need to have fully detailed representations for
-those words (Charles-Luce \& Luce, 1995). On the other hand, a growing
-vocabulary is also related to more experience or familiarity with words,
-which may sharpen the detail of their representation (Barton, 1980).
-
-Yet, the majority of studies examining a potential association between
-mispronunciation sensitivity and vocabulary size have concluded that
-there is no relationship (Swingley \& Aslin 2000; 2002; Bailey \&
-Plunkett, 2002; Zesiger, Lozeron, Levy, \& Frauenfelder, 2012; Swingley,
-2009; Ballem \& Plunkett, 2005; Mani \& Plunkett, 2007; Mani, Coleman,
-\& Plunkett, 2008). One notable exception comes from Mani and Plunkett
-(2010: keps and tups). Here, 12-month-old infants were divided into a
-low vocabulary and high vocabulary group based group median vocabulary
-size. High vocabulary infants showed greater sensitivity to vowel
-mispronunciations than low vocabulary infants, although this was not the
-case for consonant mispronunciations. Taken together, although receiving
-considerable support from theories of phono-lexical processing in
-language acquisition, there is very little evidence for a role of
-vocabulary size in mispronunciation sensitivity. In our current
-meta-analysis, we include the relationship between mispronunciation
-sensitivity and vocabulary size to further disentangle the disconnect
-between theory and experimental results.
-
-Next to this core theoretically relevant investigation of the shape of
-development of infants' mispronunciation sensitivity, we take the
-opportunity of a systematic aggregation of data to address open
-questions regarding differences in experiment design and whether changes
-in procedure and stimuli tap into significantly different aspects of
-infants' ability to detect mispronunciations.
-
-In designing their mispronunciation stimuli, Swingley and Aslin (2000)
-chose consonant mispronunciations that were likely to confuse adults
-(Miller \& Nicely, 1955). Subsequent research has settled on
-systematically modulating phonemic features to achieve mispronunciations
-of familiar words. By utilizing mispronunciations consisting of phonemic
-changes, these experiments examine infants' sensitivity to factors that
-change the identity of a word on a measurable level (i.e.~1-feature,
-2-features, 3-features, etc.). The importance of controlling for the
-degree of phonological mismatch, as measured by number of features
-changed, is further highlighted by studies that find graded sensitivity
-to both consonant (White \& Morgan, 2008) and vowel (Mani \& Plunkett,
-2011) feature changes.
-
-Although most research examining sensitivity to mispronunciations
-follows a similar design, there are some notable differences. For
-example, Swingley and Aslin (2000) presented infants with pairs of
-familiar images, one serving as the labeled target and one as the
-unlabeled distractor. In contrast, White and Morgan (2008; see also Mani
-\& Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented
-infants with pairs of familiar (labeled target) and unfamiliar
-(unlabeled distractor) objects. By using an unfamiliar object as a
-distractor, the infant is presented with a viable option onto which the
-mispronounced label can be applied (Halberda, 2003; Markman, Wasow, \&
-Hansen, 2003). Infants ages 24 and 30 months associate a novel label
-with an unfamiliar object, although only 30-month-olds retained this
-label-object pairing (Bion, Borovsky, and Fernald, 2013). In contrast,
-18-month-olds did not learn to associate a novel label with an
-unfamiliar object, providing evidence that this ability is developing
-from 18 to 30 months. We may find that if mispronunciation sensitivity
-changes as children develop, that this change is modulated by whether
-the distractor used is familiar or unfamiliar. Although mispronunciation
-sensitivity in the presence of a familiar compared to unfamiliar
-distractor has not been directly compared, the baseline preference for
-familiar compared to novel stimuli is also thought to change as infants
-develop (Hunter \& Ames, 1988). Furthermore, young children have been
-found to look longer at objects for which they know the name, compared
-to objects of an unknown name (Schafer \& Plukett, 1998). In other
-words, in absentia of a label, infants may be more or less likely to
-fixate on an unfamiliar object. To account for inherent preferences to
-the target or distractor image, mispronunciation experiments typically
-compare the increase in fixations to the target image from a silent
-baseline to post-labeling or present the same yoked pairs of target and
-distractor images in in both a correct and mispronounced labelling
-context. Considering this evidence, we may expect that in older, but not
-younger, children, the presence of an unfamiliar distractor may lead to
-greater mispronunciation sensitivity than in the presence of a familiar
-distractor.
-
-Furthermore, when presenting infants with a familiar distractor image,
-some studies control the phonological overlap between the labels for the
-target and distractor. For example, when examining sensitivity to a
-mispronunciation of the target word \enquote{dog}, the vowel
-mispronunciation \enquote{dag} would be paired with a distractor image
-that shares onset overlap, such as \enquote{duck}. This ensures that
-infants can not use the onset of the word to differentiate between the
-target and distractor images (Fernald, Swingley, \& Pinto, 2001).
-Instead, infants must pay attention to the mispronounced phoneme in
-order to successfully detect the change. The influence of distractor
-overlap also depends on the position of the mispronunciation in the
-word, which can be at word onset, medial, or final positions. Models of
-spoken word processing place more or less importance on the position of
-a phoneme in a word. The COHORT model (Marslen-Wilson \& Zwitserlood,
-1989) describes lexical access in one direction, with the importance of
-each phoneme decreasing as its position comes later in the word. In
-contrast, the TRACE model (McClelland \& Elman, 1986) describes lexical
-access as constantly updating and reevaluating the incoming speech input
-in the search for the correct lexical entry, and therefore can recover
-from word onset and to a lesser extent medial mispronunciations.
-
-TRACE has also been used to model infants' sensitivity to
-mispronunciation location (Mayor \& Plunkett, 2014), finding that as
-lexicon size increases, so does sensitivity to onset mispronunciations,
-whereas medial mispronunciations do not experience similar growth. In
-early language acquisition, infants typically know more consonant
-compared to vowel onset words. When tested on their recognition of
-familiar words, therefore, younger infants would show greater
-sensitivity to onset mispronunciations, which are frequently consonant
-mispronunciations. The prevalence of consonant onset words may
-contribute to the finding that consonants carry more weight in lexical
-processing (C-bias; see Nazzi, Poltrock, \& Von Holzen, 2016 for a
-recent review). In mispronunciation sensitivity, this would translate to
-consonant mispronunciations impairing word recognition to a greater
-degree than vowel mispronunciations. Yet, the handful of studies
-directly comparing sensitivity to consonant and vowel mispronunciations
-mostly find symmetry as opposed to an asymmetry between consonants and
-vowels. English-learning 12-, 15-, 18-, and 24-month-olds (Mani \&
-Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds
-(Hojen et al., unpublished) demonstrate similar sensitivity to consonant
-and vowel mispronunciations. One study did find weak evidence for
-greater sensitivity to consonant compared to vowel mispronunciations
-(Swingley, 2016). The English-learning infants tested by Swingley were
-older than previous studies (mean age 28 months). In word learning, the
-C-bias has been found to develop later in English learning infants
-(Floccia, Nazzi, Delle Luche, Poltrock, \& Goslin, 2014; Nazzi, Floccia,
-Moquet, \& Butler, 2009). In the current meta-analysis, we attempt to
-synthesize studies examining sensitivity to consonant and vowel
-mispronunciations across different ages to determine whether infants
-generally exhibit more sensitivity to consonant compared to vowel
-mispronunciations in familiar word recognition as predicted by a learned
-account of C-bias emergence (Floccia et al., 2014; Keidel et al., 2007;
-Nazzi et al., 2016). We further examine the impact of language family on
-mispronunciation sensitivity to consonants and vowels, as C-bias
-emergence has been found to have a different developmental trajectory
-for Romance (French, Italian) compared to Germanic (British English,
-Danish) languages (Nazzi et al., 2016).
-
-{[}KATIE{]} Christina had noted something to herself for this paragraph:
-Subset by language?
-
-Finally, mispronunciation sensitivity in infants has been examined in
-many different languages, such as English, Spanish, French, Dutch,
-German, Catalan, Danish, and Mandarin Chinese (see Summary\_Table).
-Infants learning different languages have different ages of acquisition
-for words in their early lexicon, leaving direct comparisons between
-languages within the same study difficult and as a result rare. Yet,
-studies testing infants from different language backgrounds on similar
-sets of stimuli find similar sensitivity to mispronunciations
-(Ramon-Casas et al., 2009; Ramon-Casas \& Bosch, 2010). Although we do
-not explicitly compare overall mispronunciation sensitivity by language
-(although see previous paragraph for rationale to test by language
-family), we assess evidence of mispronunciation sensitivity from many
-different languages using a meta-analytic approach.
-
-Taken together, the studies we have reviewed begin to paint a picture of
-the development of mispronunciation sensitivity. Each study contributes
-one separate brushstroke and it is only by examining all of them
-together that we can achieve a better understanding. In our analysis, we
-examine the factors modulating the development of mispronunciation
-sensitivity, which are both of theoretical and practical importance.
-Meta-analyses can not only help us summarize the current state of
-research, but can also help us evaluate theories to drive future
-research and make hands-on recommendations for experiment planning.
-
 \section{Methods}\label{methods}
 
-The present meta-analysis was conducted with maximal transparency and
-reproducibility in mind. To this end, we provide all data and analysis
-scripts on the supplementary website (\url{https://osf.io/rvbjs/}) and
-open our meta-analysis up for updates (Tsuji, Bergmann, \& Cristia,
-2014). The most recent version is available via the website and the
-interactive platform MetaLab (metalab.stanford.edu; Bergmann et al.,
-2018). Since the present paper was written with embedded analysis
-scripts in R {[}@R{]}, it is always possible to re-analyze an updated
-dataset. In addition, we follow the Preferred Reporting Items for
-Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the
-corresponding information available as supplementary materials (Moher,
-Liberati, Tetzlaff, Altman \& PRISMAGroup, 2009). Figure X plots our
-PRISMA flowchart.
+We report how we determined our sample size, all data exclusions (if
+any), all manipulations, and all measures in the study.
 
-{[}Figure X. PRISMA Flowchart.{]}
-(figures/PRISMA\_MA\_Mispronunciation.png)
+\subsection{Participants}\label{participants}
 
-\subsection{Study Selection}\label{study-selection}
+\subsection{Material}\label{material}
 
-\begin{tabular}{l|l|l|l|l|l|l|l}
-\hline
-Paper & Age & Vocabulary & \# Features & Distractor & Distractor name overlap & MP Position & MP Type\\
-\hline
-Altvater-Mackensen (2010) & 22, 25 & None & 1 & Familiar, Unfamiliar & onset, novel & onset, onset/medial & consonant\\
-\hline
-Altvater-Mackensen et al. (2014) & 18, 25 & None & 0, 1 & Familiar & onset & onset & consonant\\
-\hline
-Bailey \& Plunkett (2002) & 18, 24 & Comprehension & 0, 1, 2 & Familiar & no & onset & consonant\\
-\hline
-Bergelson \& Swingley (2017) & 7, 9, 12, 6 & None & 0, NA & Familiar & no & onset/medial & vowel\\
-\hline
-Bernier \& White 2017 & 21 & None & 0, 1, 2, 3 & Unfamiliar & novel & onset & consonant\\
-\hline
-Delle Luche et al. (2015) & 20, 19 & None & 0, 1 & Familiar & onset & onset & consonant\_and\_vowel\\
-\hline
-Durrant et al. (2014) & 19, 20 & None & 0, 1 & Familiar & onset & onset & consonant\_and\_vowel\\
-\hline
-Hoehle et al. 2006 & 18 & None & 1 & Familiar & no & onset & consonant\\
-\hline
-Hojen et al. & 20 & Comprehension/Production & 2\_3 & Familiar & coda, onset & onset/medial, coda/medial & consonant\_and\_vowel, vowel, consonant\\
-\hline
-Mani \& Plunkett 2007 & 15, 18, 24, 14, 21 & Comprehension/Production & 0, 1\_2, 1 & Familiar & onset & onset & vowel, consonant\_and\_vowel, consonant\\
-\hline
-Mani \& Plunkett 2010 & 12 & Comprehension & 0, 1 & Familiar & onset & medial, onset & vowel, consonant\\
-\hline
-Mani \& Plunkett 2011 & 23, 17 & None & 0, 1\_2\_3, 1, 2, 3 & Unfamiliar & novel & medial & vowel\\
-\hline
-Mani, Coleman, \& Plunkett (2008) & 18 & Comprehension/Production & 0, 1 & Familiar & onset & medial & vowel\\
-\hline
-Ramon-Casas \& Bosch 2010 & 24, 25 & None & NA & Familiar & no & medial & vowel\\
-\hline
-Ramon-Casas et al. 2009 & 21, 20 & Production & NA & Familiar & no & medial & vowel\\
-\hline
-Ren \& Morgan, in press & 19 & None & 0, 1 & Unfamiliar & no & onset, coda & consonant\\
-\hline
-Skoruppa et al. 2013 & 24 & None & 0, 1 & Unfamiliar & onset/medial & coda & consonant\\
-\hline
-Swingley (2009) & 17 & Comprehension/Production & 0, 1 & Familiar & no & onset, coda & consonant\\
-\hline
-Swingley (2016) & 27, 28 & Production & 0, 1 & Unfamiliar & novel & onset/medial & consonant\_and\_vowel, consonant, vowel\\
-\hline
-Swingley \& Aslin (2000) & 20 & Comprehension & 0, 1 & Familiar & no & onset & consonant\_and\_vowel\\
-\hline
-Swingley \& Aslin (2002) & 15 & Comprehension/Production & 0, 1, 2 & Familiar & no & onset/medial & consonant\_and\_vowel\\
-\hline
-Swingley 2003 & 19 & Comprehension/Production & 0, 1 & Familiar & onset & onset, medial & consonant\\
-\hline
-Tamasi (2016) & 30 & None & 0, 1, 2, 3 & Unfamiliar & novel & onset & consonant\\
-\hline
-Tao \& Qinmei 2013 & 12 & None & NA & Familiar & no & NA & tone\\
-\hline
-Tao et al. 2012 & 16 & Comprehension & NA & Familiar & no & NA & tone\\
-\hline
-van der Feest \& Fikkert, 2015 & 24, 20 & None & 0, 1 & Familiar & onset & onset & consonant\\
-\hline
-van der Feest \& Johnson, 2016 & 24 & None & 0, 1 & Familiar & onset & onset & consonant\\
-\hline
-Wewalaarachchi et al. 2017 & 24 & None & 0, 1 & Unfamiliar & novel & onset/medial/coda & consonant\_vowel\_tone, vowel, consonant, tone\\
-\hline
-White \& Aslin (2011) & 18 & None & 1 & Unfamiliar & novel & medial & vowel\\
-\hline
-White \& Morgan (2008) & 18, 19 & None & 0, 1, 2, 3 & Unfamiliar & novel & onset & consonant\\
-\hline
-Zesiger \& Johr 2011 & 14 & None & 0, 1 & Familiar & no & onset, medial & consonant, vowel\\
-\hline
-Zesiger et al. (2012) & 12, 19 & Comprehension/Production & 0, 1, 2 & Familiar & no & onset & consonant\\
-\hline
-\end{tabular}
-
-{[}KATIE{]} THIS TABLE IS DEFINITELY NOT FINISHED! {[}CHRISTINA
-suggestions: N features should be a range and exclude 0; we could
-abbreviate Comperehension/Production to Comp./Prod.,
-etcetc{]}{[}KATIE{]} I'll think about how to implement that! Might end
-up having to adjust the table by hand, there is a lot of variation
-between studies.
-
-We first generated a list of potentially relevant items to be included
-in our meta-analysis by creating an expert list. This process yielded
-110 items. We then used the google scholar search engine to search for
-papers citing the original Swingley \& Aslin (2000) publication. This
-search was conducted on 22 September, 2017 and yielded 288 results. We
-screened the 398 items, removing 99 duplicate items. We screened
-remaining 299 items for their title and abstract to determine whether it
-met the following inclusion criteria: (1) original data was reported;
-(2) the experiment examined familiar word recognition; (3) infants
-studied were under 36-months-of-age; (4) the dependent variable was
-derived from proportion of looks to a target image versus a distractor
-in a eye movement experiment; 5) the stimuli were auditory speech. The
-final sample (n = \emph{32}) consisted of 27 journal articles, 1
-proceedings paper, 2 thesis, and 2 unpublished reports. We will refer to
-these items collectively as papers. Table 1 (Summary Table) provides an
-overview of all papers included in the present meta-analysis.
-
-\begin{tabular}{l|r|r}
-\hline
-Publication Type & \# Items & \# Effect Sizes\\
-\hline
-dissertation & 2 & 17\\
-\hline
-gray paper & 2 & 14\\
-\hline
-paper & 27 & 216\\
-\hline
-proceedings & 1 & 4\\
-\hline
-\end{tabular}
-
-\subsection{Data Entry}\label{data-entry}
-
-The 32 papers we identified as relevant were then coded with as much
-detail as possible (Tsuji, Bergmann, \& Cristia, 2014; Bergmann et al.,
-2018). For each experiment (note that a paper typically has multiple
-experiments), we entered variables describing the publication,
-population, experiment design and stimuli, and results. For the present
-analyses, we focus on the following characteristics:\\
-1 Condition: Were words mispronounced or not;\\
-2 Mean age reported per group of infants, in days;\\
-3 Vocabulary size, measured by a standardized questionnaire or list;\\
-4 Size of mispronunciation, measured in features changed;\\
-5 Distractor familiarity: familiar or unfamiliar;\\
-6 Phonological overlap between target and distractor: onset,
-onset/medial, rhyme, none, novel word;\\
-7 Position of mispronunciation: onset, medial, offset, or mixed;\\
-8 Type of mispronunciation: consonant, vowel, or both.
-
-We separated out conditions according to whether or not the target word
-was mispronounced to be able to investigate infants' looking to the
-target picture separated by whether or not words were mispronounced as
-well as their mispronunciation sensitivity, which is the difference
-between looks to the target in correct and mispronounced trials. When
-the same infants were further exposed to multiple mispronunciation
-conditions and the results were reported separately in the paper, we
-also entered each condition as a separate row (e.g., consonant versus
-vowel mispronunciations; Mani \& Plunkett, 2007). The fact that the same
-infants contributed data to multiple rows (minimally those containing
-information on correct and mispronounced trials) leads to shared
-variance across effect sizes, which we account for in our analyses (see
-next section). We will call each row a record; in total there were 251
-records in our data.
+\subsection{Procedure}\label{procedure}
 
@@
 
-\begin{tabular}{l|r|r}
-\hline
-Type of comparison & \# Papers & \# Effect Size\\
-\hline
-post-naming compared to pre-naming phase & 10 & 29\\
-\hline
-post-naming phase compared with chance (=50\%) & 9 & 23\\
-\hline
-post-pre difference score compared with chance (=0) & 13 & 52\\
-\hline
-\end{tabular}
-
-Mispronunciation sensitivity studies typically examine infants'
-proportion of target looks (PTL) in comparison to a baseline
-measurement. PTL is calculated by dividing the percentage of looks to
-the target by the total percentage of looks to both the target and
-distractor images. Across papers the baseline comparison varied; we used
-the baseline reported by the authors of each paper. Most papers
-(\emph{n} = 13) subtracted the PTL score for a pre-naming phase from the
-PTL score for a post-naming phase. When interpreting this difference
-score, a positive value indicates that infants increased their looks to
-the target after hearing the naming label (correct or mispronounced).
-Other papers either compared post- and pre-naming PTL with one another
-(\emph{n} = 10) or compared post-naming PTL with a chance level of 50\%,
-(\emph{n} = 9). For all these comparisons, a positive difference score
-or a post-naming phase PTL score that is greater than the pre-naming
-phase PTL or chance indicate target looks that indicate object
-recognition after hearing the naming label. Consequently, positive
-effect sizes reflect more looks to the target picture after naming, and
-larger positive effect sizes indicate comparatively more relative
-increase in looks to the target.
-
-We report effect sizes for infants' looks to target pictures after
-hearing a correctly pronounced or a mispronounced label (object
-identification) as well as the difference between effect sizes for
-correct and mispronounced trials (i.e.~mispronunciation sensitivity).
-The effect size we report in the present paper are based on comparison
-of means, standardized by their variance. The most well-known effect
-size from this group is Cohen's \emph{d} {[}@cohen{]}. To correct for
-the small sample sizes common in infant research, however, we use as a
-dependent variable Hedges' \emph{g} instead of Cohen's \emph{d} (Hedges,
-1981; Morris, 2000).
-
-We calculated Hedges' \emph{g} using the raw means and standard
-deviations reported in the paper (\emph{n} = 25) or using reported
-t-values (\emph{n} = 9). Raw means and standard deviations were
-extracted from figures for 3 papers. In a within-participation design,
-when two means are compared (i.e.~looking during pre- and post-naming)
-it is necessary to obtain correlations between the two measurements at
-the participant level to calculate effect sizes and effect size variance
-based on t-values. Upon request we were provided with correlation values
-for one paper (Altvater-Mackensen, 2010); we were able to compute
-correlations using means, standard deviations, and t-values for \emph{n}
-= 4 (following Csibra, et al. 2016, Appendix B; see also Rabagliati,
-Ferguson, \& Lew-Williams, 2018). Correlations were imputed for the
-remaining papers (see Black \& Bergmann, 2017, for the same procedure).
-We could compute a total of 104 effect sizes for correct pronunciations
-and 147 for mispronunciations.
-
-To take into account the fact that the same infants contributed to
-multiple datapoints, we analyze our results in a multilevel approach
-using the R {[}@R{]} package metafor {[}@metafor{]}. This means we model
-as random effect that effect sizes from the same paper share are based
-on more similar studies than those across papers and that nested therein
-effects can stem from the same infants.
-
-\subsection{Publication Bias}\label{publication-bias}
-
-{[}CHRISTINA: Do you think we have to revise this section? I think it's
-the same as in the proceedings paper.{]}{[}KATIE: Are you concerned
-about the Publication Bias section in particular, or the Methods as a
-whole? In general, some of the Methods was written before the CogSci
-paper and in other places to flesh things out I rewrote what we had. Its
-definitely giving the same information and sometimes the wording is
-close, because there's not too many different ways to explain what a
-funnel plot is :){]}
-
-In the psychological sciences, there is a documented reluctance to
-publish null results. As a result, there is a potential for significant
-results to be valued over non-significant results (see Ferguson \&
-Heene, 2012). To examine whether this is also the case in the
-mispronunciation sensitivity literature, which would bias the data
-analyzed in this meta-analysis, we conduct two tests. We first examine
-whether effect sizes are distributed as expected based on sampling error
-using the rank correlation test of funnel plot asymmetry with the R
-{[}@R{]} package metafor {[}@metafor{]}. Effect sizes with low-variance
-are expected to fall closer to the estimated mean, while effect sizes
-with high-variance should show an increased, evenly-distributed spread
-around the estimated mean. Second, we analyze all of the significant
-results in the dataset using a p-curve from the p-curve app (v4.0,
-p-curve.com; @pcurve). This tests for evidential value by examining
-whether the p-values have an expected distribution, regardless of
-whether the null hypothesis is true or not, as well as whether there is
-a larger proportion of p-values just below the typical alpha threshold
-of .05, which may indicate questionable research practices. Responses to
-correctly pronounced and mispronounced labels are predicted to show
-different patterns of looking behavior; as a result, we conduct these
-two analyses to assess publication bias separately for both conditions.
-
-\subsection{Meta-analysis}\label{meta-analysis}
-
-The models reported are hierarchical random-effects models (infant
-groups nested within papers) of variance-weighted effect sizes with the
-R {[}@R{]} package metafor {[}@metafor{]}. To investigate how
-development impacts mispronunciation sensitivity, our core theoretical
-question, we introduce age (centered; continuous and measured in days
-but transformed into months for ease of reading by dividing by 30.44) as
-a moderator to our main model. For the subsequent investigations of
-experimental characteristics, we introduce each characteristic as a
-moderator (more detail below).
-
-{[}CHRISTINA: Let's both reread the full paper once it is ready and
-check that this is properly motivated and whether we do need to list
-them all. For now I think the last sentence is fine, but I would tend to
-prefer a reminder for the forgetful reader.{]}{[}KATIE: that's
-reasonable! We had just listed everything 7 paragraphs before, which
-doesn't seem like a lot of \enquote{space}.{]}
-
 \section{Results}\label{results}
-
-\subsection{Publication Bias}\label{publication-bias-1}
-
-Figure 1 shows the funnel plots for both correct pronunciations and
-mispronunciations (code adapted from Sakaluk, 2016). Funnel plot
-assymmetry was significant for both correct pronunciations (Kendall's
-\(\tau\) = 0.53, \emph{p} \textless{} .001) and mispronunciations
-(Kendall's \(\tau\) = 0.16, \emph{p} = 0.004). These results,
-quantifying the assymmetry in the funnel plots (Figure 1), indicate bias
-in the literature. This is particularly evident for correct
-pronunciations, where larger effect sizes have greater variance (bottom
-right corner) and there are a smaller number of more precise effect
-sizes (i.e.~smaller variance) than expected (top left, outside the
-triangle).
-
-{[}CHRISTINA: If we want to interpret here, how about the next
-bit.{]}{[}KATIE: YES! This is an excellent point!!!{]}
-
-The stronger publication bias for correct pronunciation might reflect
-the status of this condiction as a control. If infants were not looking
-to the target picture after hearing the correct label, the overall
-experiment design is called into questions. However, due to the small
-effect and sample sizes (which we will discuss in the following sections
-in more detail) one would expect the regular occurrence of null results
-even though as a population infants would reliably show the expected
-object identification effect.
-
-We should also point out that funnel plot asymmetry can be caused by
-multiple factors beside publication bias. The funnel plot asymmetry may
-also reflect heterogeneity in the data, perhaps due to some studies
-investigating more subtle effects than other studies. {[}CHRISTINA: I
-have to add some bits here.{]}
-
-\subsection{Figure 1}\label{figure-1}
-
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Paper_Analyses_files/figure-latex/FunnelCombo-1.pdf}
-\caption{}
-\end{figure}
-
-\begin{verbatim}
-## [1] TRUE
-\end{verbatim}
-
-\begin{verbatim}
-## [1] TRUE
-\end{verbatim}
-
-We next examined the p-curves for significant values from the correctly
-pronounced and mispronounced conditions. The p-curve based on 72
-statistically significant values for correct pronunciations indicates
-that the data contain evidential value (Z = -17.93, \emph{p} \textless{}
-.001) and there is no evidence of a large proportion of p-values just
-below the typical alpha threshold of .05. The p-curve based on 36
-statistically significant values for mispronunciations indicates that
-the data contain evidential value (Z = -6.81, \emph{p} \textless{} .001)
-and there is no evidence of a large proportion of p-values just below
-the typical alpha threshold of .05.
-
-{[}CHRISTINA: CAn you add the stats for the non-sig results?{]}{[}KATIE:
-Are there stats that can be computed on the non-sig results? Or do you
-just want an n for significant and non-significant studies?{]}
-
-Taken together, the results suggest a tendency in the literature towards
-publication bias. As a result, our meta-analysis may systematically
-overestimate effect sizes and we therefore interpret all estimates with
-caution. Yet, the p-curve analysis suggests that overall, the literature
-contains evidential value, reflecting a \enquote{real} effect. We
-therefore continue our meta-analysis.
-
-\subsection{Meta-analysis}\label{meta-analysis-1}
-
-\subsubsection{Object Identification for Correct and Mispronounced
-Words}\label{object-identification-for-correct-and-mispronounced-words}
-
-We first calculated the meta-analytic effect for object identification,
-i.e.~looks to the target image in response to correctly pronounced
-words. The variance-weighted meta-analytic effect size Hedges' \emph{g}
-was 0.91 (SE = 0.12) which was significantly different from zero (95\%
-CI {[}0.67, 1.14{]}, \emph{p} \textless{} .001). This is a rather large
-effect size (according to the criteria set by Cohen, 1988; see also
-Bergmann, et al., 2018; for comparative meta-analytic effect sizes in
-language acquisition research). That the effect size is significantly
-above zero suggests that when presented with the correctly pronounced
-label, infants fixated the corresponding object. Our analysis of funnel
-plot asymmetry, however, found evidence for publication bias, which
-might lead to an overestimated effect sizes as smaller, non-significant
-results might not be published. Although the effect size Hedges'
-\emph{g} may be overestimated for object identification in response to
-correctly pronounced words, the p-curve results and a CI lower bound of
-0.67 suggests that this result is robust even when correcting for
-publication bias. In other words, we are confident that the true
-population mean lies above zero for object recognition of correctly
-pronounced words.
-
-{[}CHRISTINA: Can you explain what the CI lower bound means here? I
-don't follow.{]}{[}KATIE: What do you think about this? The CI lower
-bound stuff here actually comes from something you wrote, so tell me
-whether its correct.{]}
-
-We then calculated the meta-analytic effect for object identification in
-response to mispronounced words. In this case, the variance-weighted
-meta-analytic effect size Hedges' \emph{g} was 0.25 (SE = 0.06) which
-was also significantly different from zero (95\% CI {[}0.13, 0.37{]},
-\emph{p} \textless{} .001). This is considered a small effect size
-(Cohen, 1988), but significantly above zero, which suggests that even
-when presented with a mispronounced label, infants fixated the correct
-object. In other words, infants are able to resolve mispronunciations, a
-key skill in language processing We again note the publication bias
-(which was smaller in this condition), and the possibility that the
-effect size Hedges' \emph{g} may be overestimated. But, as the p-curve
-indicated evidential value, we are confident in the overall patterns,
-namely that infants fixate the target even after hearing a mispronounced
-label.
-
-Heterogeneity was significant for both correctly pronounced (Q(103) =
-625.63, \emph{p} \textless{} .001) and mispronounced words, (Q(146) =
-462.51, \emph{p} \textless{} .001). This indicated that the sample
-contains unexplained variance leading to significant difference across
-our studies beyond what is to be expected based on random sampling
-error. We therefore continue with our moderator analysis.
-
-\subsubsection{Mispronunciation Sensitivity Meta-analytic
-Effect}\label{mispronunciation-sensitivity-meta-analytic-effect}
-
-The above two analyses considered the data from mispronounced and
-correctly pronounced words separately. To evaluate mispronunciation
-sensitivity, we compared the effect size Hedges' \emph{g} for correct
-pronunciations with mispronunciations directly, merging the two
-datasets. The moderator test was significant, QM(1) = 215.76, \emph{p}
-\textless{} .001. Hedges' \emph{g} for mispronunciation sensitivity was
-0.50 (SE = 0.03), which indicated that the responses across conditions
-were significantly different (95\% CI {[}0.43, 0.56{]}, \emph{p}
-\textless{} .001). This confirms that although infants fixate the
-correct object for both correct pronunciations and mispronunciations,
-the observed fixations to target (as measured by the effect sizes) were
-significantly greater for correct pronunciations. In other words, we
-observe a significant difference between the two conditions and can now
-quantify the modulation of fixation behavior in terms of standardized
-effect sizes.
-
-\subsubsection{Object Recognition and Mispronunciation Sensitivity
-Modulated by
-Age}\label{object-recognition-and-mispronunciation-sensitivity-modulated-by-age}
-
-To evaluate the different predictions we laid out in the introduction
-for how mispronunciation sensitivity will change as infants develop, we
-next added the moderator age (centered, in days). In the first analyses,
-we investigate the impact of age separately on conditions where words
-were either pronounced correctly or not. Age did not significantly
-modulate object identification in response to correctly pronounced
-(QM(1) = 0.68, \emph{p} = 0.41) or mispronounced words (QM(1) = 1.72,
-\emph{p} = 0.19). The lack of a significant modulation together with the
-small estimates indicates that there was no relationship between age and
-target looks in response to a correctly pronounced or mispronounced
-label. This relationship is plotted in Figure 2.
-
-{[}CHRISTINA{]} CAN YOU ADD ESTIMATES AND THEIR CIS?? Ideally everywhere
-where you report a p-value {[}KATIE: Do you know how to calculate
-Estimates and CIs for the Test of Moderators? Or do you mean reporting
-the estimates and CIs even when the moderator test is not
-significant?{]}
-
-We then examined the interaction between age and mispronunciation
-sensitivity (correct vs.~mispronounced words) in our whole dataset. The
-moderator test was significant (QM(3) = 218.62, \emph{p} \textless{}
-.001). This result is in line with the general observation that as
-infants mature they become better at language processing. The
-interaction between age and mispronunciation sensitivity, however, was
-not significant \(\beta\) = 0.00, (SE = 0.01, 95\% CI {[}-0.01, 0.02{]},
-\emph{p} = 0.731), suggesting that as infants age, their
-mispronunciation sensitivity remains the same.
-
-\subsection{Figure 2}\label{figure-2}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotMPEffect-1.pdf}
-\caption{}
-\end{figure}
-
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
-\subsubsection{Vocabulary Size: Correlation Between Mispronunciation
-Sensitivity and
-Vocabulary}\label{vocabulary-size-correlation-between-mispronunciation-sensitivity-and-vocabulary}
-
-Of the 32 papers included in the meta-analysis, 8 (comprehension = 7
-papers; production = 1) analyzed the relationship between vocabulary
-scores and mispronunciation sensitivity. There is reason to believe that
-production data are different from comprehension data (the former being
-easier to estimate for parents in the typical questionnaire-based
-assessment), so we analyze this data separately.
-
-{[}KATIE{]} I DON'T KNOW HOW TO INTERPRET THESE RESULTS\ldots{} THE
-FIXED EFFECTS MODEL ISN'T SIGNIFICANT FOR ANY OF THESE. IS THAT
-MEANINGFUL? {[}CHRISTINA{]} SO WE DON'T WANT TO INTERPRET THE FIXED
-EFFECTS MODEL AT ALL, IT IS NOT SUITABLE BECAUSE THERE IS VARIANCE
-BETWEEN EVERY RECORD (LANGUAGE ETC). I WOULD INTERPRET THE OVERALL
-CORRELATION AND THE CI, NOT THE P-VALUE (IN GENERAL). I ALSO WONDER
-WHETHER WE SHOULD MOVE THE SUBSET ANALYSES TO THE SUPPLEMENTARY
-MATERIALS AND JUST SAY OVERALL WE SEE NO RELATIONSHIPS AND CORRELATION
-COEFFICIENTS CONSISTENYL BELOW .1 WE THEREFORE MUST CONCLUDE THAT WITHIN
-NARROW AGE GROUPS VOCABULARY DOES NOT INFLUENCE ANYTHING WE LOOK AT. WE
-CANNOT DO THIS ANALYSIS FPOR MP SENSITIVITY BECAUSE WE DON'T HAVE THE
-NECESSARY RAW DATA. {[}KATIE: Ah, so because for each paper the
-correlation and CI values straddle 0, this indicates that there really
-isn't much evidence for a relationship? I think it could make sense to
-add this to supplementary materials. Over the summer, I had also played
-around with looking at how collection of vocabulary data has dropped off
-over the years, even though more mispronunciation studies have been
-published. That might be something interesting to add. If we truly think
-that this is what is driving the development of mispronunciation
-sensitivity, then why are people not collecting this data?{]} (BUT I
-WONDER WHETHER WECOULD ENCODE THE REPORTED INTERACTION TERMS AND THE
-CORRELATION AND THEN DO SOMETHING WITH THAT?) {[}KATIE: I'm not really
-sure what you mean by this :({]}
-
-\begin{verbatim}
-##                                      COR            95%-CI %W(fixed)
-## Zesiger et al. (2012)             0.0610 [-0.3553; 0.4773]       5.8
-## Zesiger et al. (2012)            -0.1590 [-0.5663; 0.2483]       6.1
-## Mani, Coleman, & Plunkett (2008)  0.0300 [-0.2271; 0.2871]      15.2
-## Swingley & Aslin (2000)           0.1050 [-0.1564; 0.3664]      14.7
-## Mani & Plunkett 2007             -0.1700 [-0.5234; 0.1834]       8.0
-## Mani & Plunkett 2007             -0.1700 [-0.5175; 0.1775]       8.3
-## Swingley & Aslin (2002)           0.1410 [-0.2432; 0.5252]       6.8
-## Swingley & Aslin (2002)           0.1410 [-0.2596; 0.5416]       6.3
-## Swingley 2003                     0.3400 [ 0.0470; 0.6330]      11.7
-## Swingley 2003                     0.0600 [-0.3472; 0.4672]       6.1
-## Hojen et al.                      0.2220 [-0.2591; 0.7031]       4.3
-## Hojen et al.                      0.4820 [ 0.0935; 0.8705]       6.7
-##                                  %W(random)
-## Zesiger et al. (2012)                   6.2
-## Zesiger et al. (2012)                   6.5
-## Mani, Coleman, & Plunkett (2008)       13.7
-## Swingley & Aslin (2000)                13.4
-## Mani & Plunkett 2007                    8.3
-## Mani & Plunkett 2007                    8.5
-## Swingley & Aslin (2002)                 7.2
-## Swingley & Aslin (2002)                 6.7
-## Swingley 2003                          11.2
-## Swingley 2003                           6.5
-## Hojen et al.                            4.8
-## Hojen et al.                            7.0
-## 
-## Number of studies combined: k = 12
-## 
-##                         COR            95%-CI    z p-value
-## Fixed effect model   0.0897 [-0.0105; 0.1900] 1.75  0.0795
-## Random effects model 0.0893 [-0.0212; 0.1999] 1.58  0.1132
-## 
-## Quantifying heterogeneity:
-## tau^2 = 0.0060; H = 1.09 [1.00; 1.50]; I^2 = 15.7% [0.0%; 55.4%]
-## 
-## Test of heterogeneity:
-##      Q d.f. p-value
-##  13.05   11  0.2899
-## 
-## Details on meta-analytical method:
-## - Inverse variance method
-## - DerSimonian-Laird estimator for tau^2
-## - Untransformed correlations
-\end{verbatim}
-
-\begin{verbatim}
-##                                      COR            95%-CI %W(fixed)
-## Zesiger et al. (2012)            -0.0090 [-0.4268; 0.4088]       5.0
-## Zesiger et al. (2012)            -0.1720 [-0.5775; 0.2335]       5.3
-## Mani, Coleman, & Plunkett (2008)  0.0700 [-0.1861; 0.3261]      13.2
-## Mani & Plunkett 2007             -0.1100 [-0.4696; 0.2496]       6.7
-## Mani & Plunkett 2007             -0.1100 [-0.4635; 0.2435]       6.9
-## Swingley & Aslin (2002)           0.1820 [-0.1970; 0.5610]       6.0
-## Swingley & Aslin (2002)           0.1820 [-0.2131; 0.5771]       5.6
-## Swingley 2003                     0.1800 [-0.1406; 0.5006]       8.4
-## Swingley 2003                     0.0700 [-0.3367; 0.4767]       5.2
-## Ramon-Casas et al. 2009           0.0980 [-0.3068; 0.5028]       5.3
-## Ramon-Casas et al. 2009          -0.1470 [-0.5468; 0.2528]       5.4
-## Ramon-Casas et al. 2009          -0.2300 [-0.6171; 0.1571]       5.8
-## Ramon-Casas et al. 2009           0.2400 [-0.1451; 0.6251]       5.9
-## Ramon-Casas et al. 2009           0.4350 [ 0.1037; 0.7663]       7.9
-## Hojen et al.                      0.2220 [-0.2591; 0.7031]       3.7
-## Hojen et al.                     -0.1480 [-0.6430; 0.3470]       3.5
-##                                  %W(random)
-## Zesiger et al. (2012)                   5.0
-## Zesiger et al. (2012)                   5.3
-## Mani, Coleman, & Plunkett (2008)       13.2
-## Mani & Plunkett 2007                    6.7
-## Mani & Plunkett 2007                    6.9
-## Swingley & Aslin (2002)                 6.0
-## Swingley & Aslin (2002)                 5.6
-## Swingley 2003                           8.4
-## Swingley 2003                           5.2
-## Ramon-Casas et al. 2009                 5.3
-## Ramon-Casas et al. 2009                 5.4
-## Ramon-Casas et al. 2009                 5.8
-## Ramon-Casas et al. 2009                 5.9
-## Ramon-Casas et al. 2009                 7.9
-## Hojen et al.                            3.7
-## Hojen et al.                            3.5
-## 
-## Number of studies combined: k = 16
-## 
-##                         COR            95%-CI    z p-value
-## Fixed effect model   0.0601 [-0.0331; 0.1533] 1.26  0.2061
-## Random effects model 0.0601 [-0.0331; 0.1533] 1.26  0.2061
-## 
-## Quantifying heterogeneity:
-## tau^2 = 0; H = 1.00 [1.00; 1.42]; I^2 = 0.0% [0.0%; 50.7%]
-## 
-## Test of heterogeneity:
-##      Q d.f. p-value
-##  14.51   15  0.4870
-## 
-## Details on meta-analytical method:
-## - Inverse variance method
-## - DerSimonian-Laird estimator for tau^2
-## - Untransformed correlations
-\end{verbatim}
-
-\begin{verbatim}
-##                              COR             95%-CI %W(fixed) %W(random)
-## Bailey & Plunkett (2002)  0.0630 [-0.3441;  0.4701]       2.5        2.7
-## Bailey & Plunkett (2002) -0.0660 [-0.4729;  0.3409]       2.5        2.7
-## Bailey & Plunkett (2002)  0.0630 [-0.3441;  0.4701]       2.5        2.7
-## Bailey & Plunkett (2002) -0.0660 [-0.4729;  0.3409]       2.5        2.7
-## Bailey & Plunkett (2002)  0.0630 [-0.3441;  0.4701]       2.5        2.7
-## Bailey & Plunkett (2002) -0.0660 [-0.4729;  0.3409]       2.5        2.7
-## Bailey & Plunkett (2002)  0.0630 [-0.3441;  0.4701]       2.5        2.7
-## Bailey & Plunkett (2002) -0.0660 [-0.4729;  0.3409]       2.5        2.7
-## Swingley (2009)          -0.1200 [-0.3715;  0.1315]       6.4        5.6
-## Swingley (2009)           0.1300 [-0.1957;  0.4557]       3.8        3.8
-## Swingley & Aslin (2000)   0.4210 [ 0.2036;  0.6384]       8.6        6.7
-## Mani & Plunkett 2007     -0.0590 [-0.4349;  0.3169]       2.9        3.0
-## Mani & Plunkett 2007     -0.0590 [-0.4349;  0.3169]       2.9        3.0
-## Mani & Plunkett 2007     -0.1700 [-0.5234;  0.1834]       3.3        3.3
-## Mani & Plunkett 2007     -0.1700 [-0.5175;  0.1775]       3.4        3.4
-## Mani & Plunkett 2007      0.1000 [-0.2667;  0.4667]       3.0        3.2
-## Mani & Plunkett 2007     -0.2800 [-0.6214;  0.0614]       3.5        3.5
-## Mani & Plunkett 2007     -0.0700 [-0.3354;  0.1954]       5.8        5.2
-## Mani & Plunkett 2007      0.1000 [-0.1641;  0.3641]       5.8        5.2
-## Swingley & Aslin (2002)   0.1750 [-0.2050;  0.5550]       2.8        3.0
-## Swingley & Aslin (2002)   0.1750 [-0.2212;  0.5712]       2.6        2.8
-## Mani & Plunkett 2010     -0.3500 [-0.6640; -0.0360]       4.1        4.0
-## Swingley 2003             0.1500 [-0.1738;  0.4738]       3.9        3.8
-## Swingley 2003             0.1500 [-0.1738;  0.4738]       3.9        3.8
-## Swingley 2003             0.0600 [-0.3472;  0.4672]       2.4        2.7
-## Swingley 2003             0.0600 [-0.3472;  0.4672]       2.4        2.7
-## Hojen et al.             -0.0510 [-0.5557;  0.4537]       1.6        1.8
-## Hojen et al.              0.0510 [-0.4537;  0.5557]       1.6        1.8
-## Hojen et al.              0.0600 [-0.4442;  0.5642]       1.6        1.8
-## Hojen et al.             -0.0600 [-0.5642;  0.4442]       1.6        1.8
-## Tao et al. 2012           0.5700 [ 0.1710;  0.9690]       2.6        2.7
-## 
-## Number of studies combined: k = 31
-## 
-##                         COR            95%-CI    z p-value
-## Fixed effect model   0.0377 [-0.0260; 0.1014] 1.16  0.2465
-## Random effects model 0.0322 [-0.0399; 0.1043] 0.87  0.3818
-## 
-## Quantifying heterogeneity:
-## tau^2 = 0.0079; H = 1.11 [1.00; 1.39]; I^2 = 19.3% [0.0%; 48.4%]
-## 
-## Test of heterogeneity:
-##      Q d.f. p-value
-##  37.18   30  0.1719
-## 
-## Details on meta-analytical method:
-## - Inverse variance method
-## - DerSimonian-Laird estimator for tau^2
-## - Untransformed correlations
-\end{verbatim}
-
-\begin{verbatim}
-##                             COR             95%-CI %W(fixed) %W(random)
-## Swingley (2009)          0.0700 [-0.1839;  0.3239]       6.4        5.4
-## Swingley (2009)          0.1600 [-0.1628;  0.4828]       3.9        3.8
-## Mani & Plunkett 2007    -0.2820 [-0.6292;  0.0652]       3.4        3.4
-## Mani & Plunkett 2007    -0.2820 [-0.6292;  0.0652]       3.4        3.4
-## Mani & Plunkett 2007    -0.1100 [-0.4696;  0.2496]       3.2        3.3
-## Mani & Plunkett 2007    -0.1100 [-0.4635;  0.2435]       3.3        3.3
-## Mani & Plunkett 2007     0.2300 [-0.1208;  0.5808]       3.3        3.4
-## Mani & Plunkett 2007     0.2200 [-0.1325;  0.5725]       3.3        3.4
-## Mani & Plunkett 2007    -0.2700 [-0.5173; -0.0227]       6.7        5.5
-## Mani & Plunkett 2007    -0.0590 [-0.3248;  0.2068]       5.8        5.0
-## Swingley & Aslin (2002)  0.0290 [-0.3627;  0.4207]       2.7        2.8
-## Swingley & Aslin (2002)  0.0290 [-0.3793;  0.4373]       2.5        2.7
-## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
-## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
-## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
-## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
-## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
-## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
-## Swingley 2003            0.1500 [-0.1738;  0.4738]       3.9        3.8
-## Swingley 2003            0.1500 [-0.1738;  0.4738]       3.9        3.8
-## Swingley 2003            0.0700 [-0.3367;  0.4767]       2.5        2.7
-## Swingley 2003            0.0700 [-0.3367;  0.4767]       2.5        2.7
-## Ramon-Casas et al. 2009  0.0980 [-0.3068;  0.5028]       2.5        2.7
-## Ramon-Casas et al. 2009 -0.1470 [-0.5468;  0.2528]       2.6        2.7
-## Ramon-Casas et al. 2009 -0.2300 [-0.6171;  0.1571]       2.7        2.9
-## Ramon-Casas et al. 2009  0.2400 [-0.1451;  0.6251]       2.8        2.9
-## Ramon-Casas et al. 2009  0.4350 [ 0.1037;  0.7663]       3.7        3.7
-## Hojen et al.            -0.0510 [-0.5557;  0.4537]       1.6        1.8
-## Hojen et al.             0.0510 [-0.4537;  0.5557]       1.6        1.8
-## Hojen et al.             0.0790 [-0.4239;  0.5819]       1.6        1.9
-## Hojen et al.            -0.0790 [-0.5819;  0.4239]       1.6        1.9
-## 
-## Number of studies combined: k = 31
-## 
-##                          COR            95%-CI     z p-value
-## Fixed effect model   -0.0402 [-0.1043; 0.0238] -1.23  0.2181
-## Random effects model -0.0393 [-0.1127; 0.0340] -1.05  0.2931
-## 
-## Quantifying heterogeneity:
-## tau^2 = 0.0094; H = 1.13 [1.00; 1.42]; I^2 = 22.0% [0.0%; 50.1%]
-## 
-## Test of heterogeneity:
-##      Q d.f. p-value
-##  38.45   30  0.1386
-## 
-## Details on meta-analytical method:
-## - Inverse variance method
-## - DerSimonian-Laird estimator for tau^2
-## - Untransformed correlations
-\end{verbatim}
-
-\subsubsection{Interim Discussion}\label{interim-discussion}
-
-The main goal of this paper was to assess mispronunciation sensitivity
-and its maturation with age. The results are clear: Although infants
-consider a mispronunciation as a better match with the target image than
-a distractor image, there was a consistent effect of mispronunciation
-sensitivity. This did not change with development. Of the 3 predictions
-and assumptions about the development of infants' sensitivity to
-mispronunciations discussed in the Introduction, the present results
-lend some support for the argument that mispronunciation sensitivity
-stays consistent as infants develop. This runs counter to existing
-theories of phono-lexical development, which predict either an increase
-(PRIMR ref) or decrease (Assim Model ref) in mispronunciation
-sensitivity.
-
-{[}KATIE{]} CAN A CONCLUSION BE DRAWN FROM THE VOCABULARY RESULTS? IF
-SO, THIS IS THE PARAGRAPH
-
-In sum, it seems that current theories of infants' phono-lexical
-development cannot fully capture our results and should be reconsidered
-with all the evidence in mind.
-
-Alternatively, the lack of developmental change in mispronunciation
-sensitivity could be due to differences in the types of tasks given to
-infants of different ages. To examine this possibility, we include an
-exploratory analysis of whether different moderators and experimental
-design features were included at different ages, in addition to
-investigating the role that these moderators play in mispronunciation
-sensitivity.
-
-\subsection{Moderator Analyses}\label{moderator-analyses}
-
-{[}cHRISTINA{]} I WOULD FOLLOW THE OUTLINE IN THE PREVIOUS PARAGRAPH
-HERE OR FLIP THE PARAGRAPH AROUND: 1. ARE DIFFERENT MODERATORS USED AT
-DIFFERENT AGES? TEST: sIMPLE CHI-SQUARED OF AGE GROUP VERSUS MODERATOR
-ASSIGNMENT (AGE GROUP DETERMINED BY LOOKING AT THE YOUNGEST AGE FOR X?)
-2. WHICH MODERATORS INFLUENCE MP SENSITIVITY TEST SIMPLE MA WITH
-MODERATOR TESTS
-
-OR \enquote{FOR EACH POSSIBLE MODERATOR WHICH COULD INFLIENCE MP
-SENSITIVITY, WE FIRST TEST THIS POSSIBILITY AND THEN EVALUATE WHETHER
-THERE IS A SYSTEMATIC DIFFERENCE OF MANIPULATING THESE MODERATORS AS
-INFANTS MATURE, I.E. WHETHER OLDER INFANTS ARE TESTED ON A MORE
-DIFFICULT TASK} ALSO, AS FINAL FOLLOW-UP IT WOULD BE PERFECT TO JUST
-SUBSET ALL STUDIES WITH FAMILIAR DISTRACTORS, SAME NUMBER OF FEATURES,
-AND CHECK THAT OUR CONCLUSIONS HOLD UP REGARING MP SENSITIVITY
-
-{[}KATIE: I prefer this second option, first looking at the moderators
-in general and then looking at whether there is this systematic
-difference with age. The latter is exploratory, so I feel like this
-information should not preceed our planned analyses.{]}
-
-\subsubsection{Number of features
-changed}\label{number-of-features-changed}
-
-To assess whether the number of features changed modulates
-mispronunciation sensitivity, we calculated the meta-analytic effect for
-object identification in response to words that were pronounced
-correctly and mispronounced using 1-, 2-, and 3-feature changes. We did
-not include data for which the number of features changed in a
-mispronunciation was not specified or the number of features changed was
-not consistent (e.g., one mispronunciation included a 2-feature change
-whereas another only a 1-feature change). This analysis was therefore
-based on a subset of the overall dataset, with 81 experimental
-conditions for correct pronunciations, 108 for 1-feature
-mispronunciations, 16 for 2-feature mispronunciations, and 6 for
-3-feature mispronunciations. Each feature change (from 0 to 3; 0
-representing correct pronunciations) was considered to have an equal
-impact on mispronunciation sensitivity, following the argument of graded
-sensitivity (White \& Aslin, 2008; Mani \& Plunkett 2011).
-
-To understand the relationship between number of features changed and
-mispronunciation sensitivity, we evaluated the effect size Hedges'
-\emph{g} with number of features changed as a moderator. The moderator
-test was significant, QM(1) = 76.10, \emph{p} \textless{} .001. Hedges'
-\emph{g} for number of features changed was -0.12 (SE = 0.01), which
-indicated that as the number of features changed increased, the effect
-size Hedges' \emph{g} significantly decreased (95\% CI {[}-0.15,
--0.10{]}, \emph{p} \textless{} .001). We plot this relationship in
-Figure X. This confirms previous findings of a graded sensitivity to the
-number of features changed for both consonant (White \& Morgan, 2008)
-and vowel (Mani \& Plunkett, 2011) mispronunciations as well as the
-importance of controlling for the degree of phonological mismatch in
-experimental design.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotFeatEffect-1.pdf}
-\caption{}
-\end{figure}
-
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
-Although we did not have any specific predictions about the relationship
-between infant age and the impact of number of features changed on
-mispronunciation sensitivity, we included an exploratory analysis to
-examine this relationship. When age was also included as a moderator,
-the moderator test was significant, QM(3) = 81.11, \emph{p} \textless{}
-.001, but the interaction between age and number of features changed was
-not significant, \(\beta\) = 0.01, (SE = 0.00, 95\% CI {[}0, 0.01{]},
-\emph{p} = 0.069). This suggests that there is no relationship between
-infant age the impact of number of features changed on mispronunciation
-sensitivity.
-
-Although all papers included in the dataset also included correct
-pronunciations, not all papers included all three types of feature
-changes (i.e.~1-3). The age range for each type of number of features
-changed was 372.89 - 920.20 days (\emph{M} = 637.40) for 1-feature
-mispronunciations, 377.28 - 920.20 days (\emph{M} = 612.17) for
-2-feature mispronunciations, and 544.48 - 920.20 days (\emph{M} =
-661.64) for 3-feature mispronunciations. Focusing on the ages where all
-three numbers of features changed were tested (i.e.~544.48 - 920.20
-days), however, did not change the pattern of results.
-
-\subsubsection{Distractor familiarity}\label{distractor-familiarity}
-
-We next assessed whether distractor familiarity has an impact on the
-size of mispronunciation sensitivity. First, we calculated the
-meta-analytic effect for object identification in response to
-mispronounced target words/images that were paired with either a
-familiar or an unfamiliar distractor image. The moderator test was not
-significant QM(1) = 0.43, \emph{p} = 0.513. This suggests that upon
-hearing a mispronunciation, infants looks to the target image were
-similar for when the target image was paired with an image of a familiar
-or unfamiliar object. We next assessed whether distractor familiarity
-was related to mispronunciation sensitivity. We merged the two datasets
-and included condition (correct pronunciation, mispronunciation) as an
-additional moderator. The moderator test was significant, QM(3) =
-219.46, \emph{p} \textless{} .001, but the interaction between
-distractor familiarity and condition was not significant \(\beta\) =
-0.14, (SE = 0.08, 95\% CI {[}-0.02, 0.30{]}, \emph{p} = 0.08). These
-results suggest that overall, infants' familiarity with the distractor
-object (familiar or unfamiliar) did not impact their mispronunciation
-sensitivity.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotDistFamEffect_NoAge-1.pdf}
-\caption{}
-\end{figure}
-
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
-We next examined whether age modulates object recognition or
-mispronunciation sensitivity when the distractor image is familiar or
-unfamiliar. For object recognition in response to a mispronunciation,
-including age as a moderator resulted in a moderator test that was not
-significant, QM(3) = 3.25, \emph{p} = 0.355. {[}CHRISTINA{]} I WORRY A
-LOT AT THESE POINTS THAT THIS IS THE WHOLE P\textgreater{}.05 = NULL IS
-TRUE FALLACY. WE CAN NEVER HAVE EVIDENCE FOR THE NULL HYPOTHESIS. SO
-BETTER ITNERPRET ESTIMATES AND CIS.
-
-This suggests that upon hearing a mispronunciation, infants looks to the
-target image were similar for when the target image was paired with an
-image of a familiar or unfamiliar object, regardless of their age. We
-next assessed whether the relationship between distractor familiarity
-and mispronunciation sensitivity was modulated by age. We merged the two
-datasets and included condition (correct pronunciation,
-mispronunciation) as well as age as additional moderators. The moderator
-test was significant, QM(7) = 224.96, \emph{p} \textless{} .001.
-Although the three-way-interaction between condition, distractor
-familiarity, and age was not significant (\(\beta\) = -0.02, SE = 0.02,
-95\% CI {[}-0.06, 0.02{]}, \emph{p} = 0.305), here the interaction
-between condition and distractor familiarity was significant (\(\beta\)
-= 0.18, SE = 0.09, 95\% CI {[}0, 0.35{]}, \emph{p} = 0.05).
-
-{[}KATIE{]} WHAT DOES IT MEAN THAT IN THIS LAST TEST THERE WAS AN
-INTERACTION BETWEEN CONDITION AND DISTRACTOR FAMILIARITY, WHEN AGE WAS
-INCLUDED AS A MODERATOR? DOES THAT MEAN THAT AGE IS CONTROLLED FOR?
-UNDERSTANDING THIS WILL HELP ME FORMULATE THE CONCLUSION SENTENCE AND
-MOTIVATE THE NEXT SET OF ANALYSES.
-
-{[}CHRISTINA{]} I WOULD NOT OVERINTERPRET IT, THE ESTIMATE DID NOT
-DRAMATICALLY CHANGE, AND IT IS BARELY SIGNIFICANT. DOES THAT HELP?
-
-{[}KATIE: I think so. I've just removed that part{]}
-
-\begin{verbatim}
-##                       Test                            Results
-## 1 Welch Two Sample t-test: t(153.83) = 5.30, p < .001, d = NA
-\end{verbatim}
-
-Although we anticipated that older children may be more impacted by the
-presence of a unfamiliar compared to familiar distractor image, we found
-that age and distractor familiarity did not impact mispronunciation
-sensitivity. Inspection of the ages tested using different kinds of
-distractors, however, revealed differences. Infants tested using a
-familiar distractor were younger (M = 588.76 days, SD = 136.47, range =
-207.8 - 768 days) than those infants tested using an unfamiliar
-distractor (M = 678.85 days, SD = 115.47, range = 544.48 - 920.2 days),
-which a two-sample t-test revealed to be a significant difference,
-t(153.83) = 5.30, p \textless{} .0001.
-
-{[}CHRISTINA{]} CAN YOU TURN THE NUMBERS INTO R CODE HERE? aLSO, NOT
-SURE WE NEED A T-TEST TO CONFIRM THE OBVIOUS.
-
-{[}KATIE{]} SO, IS IT OKAY TO DO THE AGE SUBSET ANALYSIS AFTER THIS?
-SOMETHING LIKE \enquote{TO ENSURE THAT THE LACK OF A DIFFERENCE WASN'T
-DUE TO THE DIFFERENCE IN AGES OF INFANTS TESTED WITH DIFFERENT TYPES OF
-DISTRACTORS, WE ANALYZED A SUBSET OF PAPERS THAT TESTED AGES WHERE BOTH
-FAMILIAR AND UNFAMILIAR DISTRACTORS WERE USED.} IN THE SUBSET ANALYSIS,
-FOR MISP SENSITIVITY, THERE IS A SIGNIFICANT INTERACTION BETWEEN
-DISTRACTOR FAMILIARITY AND CONDITION.
-
-{[}CHRISTINA{]} YES!!!!!!
-
-\subsubsection{Phonological overlap between target and
-distractor}\label{phonological-overlap-between-target-and-distractor}
-
-To assess whether phonological overlap between the target and distractor
-image labels has an impact on the size of mispronunciation sensitivity,
-we examined the meta-analytic effect for object identification in
-response to mispronunciations and mispronunciation sensitivity when the
-target-distractor pairs either shared the same onset phoneme, had no
-overlap, or where the distractor was an unfamiliar object. We did not
-include data for which the overlap included both the onset and medial
-phonemes (\emph{n} = 4) or coda phonemes (\emph{n} = 3). The analysis
-was therefore based on a subset of the overall dataset, with 104
-experimental conditions containing onset phoneme overlap between the
-target and distractor, 80 containing no overlap between target and
-distractor, and 60 for targets paired with unfamiliar distractor images.
-There were therfore three possibilities for distractor overlap: onset
-phoneme overlap, no overlap, and an unfamiliar distractor. In our
-analysis, we were interested in the difference between overlap and lack
-of overlap; therefore, experimental conditions containing onset phoneme
-overlap were coded as the reference condition and compared with
-responses to experimental conditions with no overlap or an unfamiliar
-distractor separately.
-
-{[}KATIE{]} CAN YOU CHECK THE WAY THAT I WROTE THE LAST SENTENCE?
-
-{[}CHRISTINA{]} SEEMS OK BUT I AM CONFUSED WHY OVERLAP IS THE BASELINE
-AND WHY YOU BRING IN NOVEL. I THINK YOU NEED TO SPELL THIS OUT MORE.
-
-Regarding object identification in response to mispronunciations, when
-distractor overlap was included as a moderator, the moderator test was
-not significant QM(2) = 1.78, \emph{p} = 0.412. {[}CHRISTINA{]} AGAIN DO
-NOT RELY ON P-VALUES BUT ON ESTIMATES AND CIS This suggests that upon
-hearing a mispronunciation, infants looks to the target image were
-similar for when the target image was paired with a distractor image
-that contained overlap on the onset phoneme or no overlap with the
-target word, or was an unfamiliar object. We next assessed whether
-target-distractor overlap was related to mispronunciation sensitivity.
-We merged the two datasets and included condition (correct
-pronunciation, mispronunciation) as an additional moderator. The
-moderator test was significant, QM(5) = 230.34, \emph{p} \textless{}
-.001. The interaction between condition and target-distractor pairs with
-no overlap was significant (\(\beta\) = -0.25, SE = 0.08, 95\% CI
-{[}-0.40, -0.10{]}, \emph{p} = 0.001), suggesting that mispronunciation
-sensitivity was greater when target-distractor pairs shared the same
-onset phoneme compared to when they shared no phonological overlap. The
-interaction between condition and target-distractor pairs with an
-unfamiliar distractor was also significant (\(\beta\) = 0.19, SE = 0.09,
-95\% CI {[}0.01, 0.37{]}, \emph{p} = 0.042), suggesting that
-mispronunciation sensitivity was smaller when the distractor image
-shared the same onset phoneme as the target image compared to when the
-distractor image was an unfamiliar object. This can be seen in Figure X.
-
-{[}christina{]} I THINK THESE SHOULD BE TWO SEPARATE ANALYSES\ldots{}
-NOVEL IS CONCEPTUALLY DIFFERENT.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotDistOverlapEffect-1.pdf}
-\caption{}
-\end{figure}
-
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
-Although we did not have any specific predictions about the relationship
-between infant age and the impact of distractor overlap on
-mispronunciation sensitivity, we included an exploratory analysis to
-examine this relationship. First, for object recognition in response to
-mispronunciations, when age in addition to distractor overlap was also
-included as a moderator, the moderator test was not significant, QM(5) =
-5.99, \emph{p} = 0.308, suggesting that upon hearing a mispronunciation,
-infants looks to the target image were similar for the three types of
-overlap, regardless of infant age. We next assessed whether the
-relationship between distractor overlap and mispronunciation sensitivity
-was modulated by age. We merged the two datasets and included condition
-(correct pronunciation, mispronunciation) as well as age as additional
-moderators. The moderator test was significant, QM(11) = 243.40,
-\emph{p} \textless{} .001. The interaction between age, condition, and
-target-distractor pairs with no overlap was significant (\(\beta\) =
--0.04, SE = 0.02, 95\% CI {[}-0.08, 0.00{]}, \emph{p} = 0.032). As can
-be seen in Figure X, the difference between correct pronunciations and
-mispronunciations (mispronunciation sensitivity) stays steady across
-infant ages for both target words paired with distractors containing
-onset overlap with the target word as well as distractors containing no
-overlap. As infants aged, however, overall recognition (regardless of
-condition) increased for target-distractor pairs containing onset
-overlap, whereas for overall recognition decreased for target-distractor
-pairs containing no overlap. The interaction between age, condition, and
-target-distractor pairs with an unfamiliar distractor was also
-significant (\(\beta\) = -0.05, SE = 0.02, 95\% CI {[}-0.09, 0.00{]},
-\emph{p} = 0.038). As can also be seen in Figure X, mispronunciation
-sensitivity for target words paired with unfamiliar distractors
-decreased with age, while it remained steady across a similar range of
-ages for target words paired with distractors containing onset overlap
-with the target word.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotDistOverlap_cond_age-1.pdf}
-\caption{}
-\end{figure}
-
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
-\subsubsection{Position of
-mispronunciation}\label{position-of-mispronunciation}
-
-To assess whether the position of the mispronunciation has an impact on
-mispronunciation sensitivity, we calculated the meta-analytic effect for
-object identification in response to mispronunciations on the onset and
-medial phonemes. We did not include data for which the mispronunciation
-was located on the coda (\emph{n} = 10 and NA), varied in regard to
-position (\emph{n} = 3, 29, 8, and NA), or was not reported (\emph{n} =
-10). The analysis was therefore based on a subset of the overall
-dataset, with 143 and NA experimental conditions comparing a
-mispronunciation on the onset phoneme and 48 and NA experimental
-conditions comparing a mispronunciation on the medial phoneme.
-
-Regarding object identification in response to mispronunciations, when
-mispronunciation location was included as a moderator, the moderator
-test was not significant QM(1) = 0.04, \emph{p} = 0.838. This suggests
-that upon hearing a mispronunciation, infants looks to the target image
-were similar for when the mispronunciation was located on the onset or
-medial phonemes. We next assessed whether mispronunciation location was
-related to mispronunciation sensitivity. We merged the two datasets and
-included condition (correct pronunciation, mispronunciation) as an
-additional moderator. The moderator test was significant, QM(3) =
-180.76, \emph{p} \textless{} .001, but the interaction between
-mispronunciation location and condition was not significant \(\beta\) =
-0.05, (SE = 0.09, 95\% CI {[}-0.12, 0.22{]}, \emph{p} = 0.559). These
-results suggest that overall, the location of the mispronunciation
-(onset, medial) did not impact mispronunciation sensitivity.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotPositionEffect-1.pdf}
-\caption{}
-\end{figure}
-
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
-Although we did not have any specific predictions about the relationship
-between infant age and the impact of mispronuncition location on
-mispronunciation sensitivity, we included an exploratory analysis to
-examine this relationship. First, for object recognition in response to
-mispronunciations, when age in addition to mispronunciation location was
-also included as a moderator, the moderator test was not significant,
-QM(3) = 1.22, \emph{p} = 0.747, suggesting that upon hearing a
-mispronunciation, infants looks to the target image were similar for
-both onset and medial mispronunciations, regardless of infant age. We
-next assessed whether the relationship between mispronunciation location
-and mispronunciation sensitivity was modulated by age. We merged the two
-datasets and included condition (correct pronunciation,
-mispronunciation) as well as age as additional moderators. The moderator
-test was significant, QM(7) = 185.34, \emph{p} \textless{} .001, but the
-interaction between mispronunciation location, age, and condition was
-not significant \(\beta\) = NA, (SE = NA, 95\% CI {[}NA, NA{]}, \emph{p}
-). These results provide further evidence that location of the
-mispronunciation (onset, medial) did not impact mispronunciation
-sensitivity.
-
-\subsubsection{Type of mispronunciation (consonant or
-vowel)}\label{type-of-mispronunciation-consonant-or-vowel}
-
-To assess whether the type of mispronunciation impacts sensitivity to
-mispronunciations, we calculated the meta-analytic effect for object
-identification in response to the type of mispronunciation. Although
-most theoretical discussion of mispronunciation type has focused on
-consonants and vowels, our dataset also included tone mispronunciations.
-In our analysis, we were interested in the difference between consonants
-and vowels, but also include an exploratory analysis of responses to
-tones, consonants, and vowels. We therefore conducted two sets of
-analyses, one analyzing consonants and vowels alone and a second
-comparing responses to tones with that of consonants and vowels,
-separately. For the latter analysis, tones were coded as the reference
-condition. We did not include data for which mispronunciation type
-varied within experiment and was not reported separately (\emph{n} = 21
-and 2). The analysis was therefore based on a subset of the overall
-dataset, with 145 experimental conditions comparing a consonant
-mispronunciation, 71 experimental conditions comparing a vowel
-mispronunciation, and 12 experimental conditions comparing a tone
-mispronunciation. Below, we first report the set of analyses comparing
-consonants with vowels before moving on to the second set of exploratory
-analyses comparing tones with that of consonants and vowels.
-
-{[}KATIE{]} WHAT DO YOU THINK ABOUT THIS? WE HAVE THE TONES AND ITS A
-NOVEL, INTERESTING THING, I THINK, AND PERHAPS WORTH IT TO INCLUDE A
-COMPARISON OF TONES ALONGSIDE THE MORE THEORETICALLY IMPORTANT
-COMPARISON BETWEEN CONSONANTS AND VOWELS.
-
-We first analyzed experimental conditions where mispronunciation type
-was either a consonant or vowel. Regarding object identification in
-response to mispronunciations, when mispronunciation type was included
-as a moderator, the moderator test was not significant QM(1) = 0.15,
-\emph{p} = 0.702. This suggests that upon hearing a mispronunciation,
-infants looks to the target image were similar for when the
-mispronunciation was a consonant or a vowel. We next assessed whether
-type of mispronunciation (consonant or vowel) was related to
-mispronunciation sensitivity. We merged the two datasets and included
-condition (correct pronunciation, mispronunciation) as an additional
-moderator. The moderator test was significant, QM(3) = 145.14, \emph{p}
-\textless{} .001, but the interaction between mispronunciation type and
-condition was not significant \(\beta\) = 0.06, (SE = 0.08, 95\% CI
-{[}-0.10, 0.21{]}, \emph{p} = 0.479). These results suggest that
-overall, the type of mispronunciation (consonant vs.~vowel) did not
-impact mispronunciation sensitivity.
-
-We next examined whether age modulates object recognition or
-mispronunciation sensitivity when the mispronunciation is a consonant or
-vowel. For object recognition in response to a mispronunciation,
-including age as a moderator resulted in a moderator test that was not
-significant, QM(3) = 1.54, \emph{p} = 0.672. This suggests that upon
-hearing a mispronunciation, infants looks to the target image were
-similar for when the mispronunciation was on a consonant or vowel
-phoneme, regardless of their age. We next assessed whether the
-relationship between mispronunciation type (consonant or vowel) and
-mispronunciation sensitivity was modulated by age. We merged the two
-datasets and included condition (correct pronunciation,
-mispronunciation) as well as age as additional moderators. The moderator
-test was significant, QM(7) = 153.79, \emph{p} \textless{} .001. The
-interaction between mispronunciation type, condition, and age was
-significant (\(\beta\) = 0.04, SE = 0.02, 95\% CI {[}0.01, 0.08{]},
-\emph{p} = 0.016). As can be seen in Figure X, as infants age,
-mispronunciation sensitivity grows larger for vowel mispronunciations
-but becomes smaller for consonant mispronunciations. Noticeably,
-mispronunciation sensitivity appears greater for consonant compared to
-vowel mispronunciations at younger ages, but this difference shifts as
-infants age.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotCVEffect_cond_age-1.pdf}
-\caption{}
-\end{figure}
-
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
-To examine whether infants' native language impacts sensitivity to
-consonant and vowel mispronunciations, we classified infants into
-language families. Infants learning American English (\emph{n} = 56),
-British English (\emph{n} = 66), Danish (\emph{n} = 6), Dutch (\emph{n}
-= 58), and German (\emph{n} = 21) were classified into the Germanic
-language family (\emph{n} = 207). Infants learning Catalan (\emph{n} =
-4), Spanish (\emph{n} = 4), French (\emph{n} = 8), Catalan and Spanish
-simultaneously (i.e.~bilinguals; \emph{n} = 6), and Swiss French
-(\emph{n} = 6) were classified into the Romance language family
-(\emph{n} = 28). For object recognition in response to a
-mispronunciation, including language family as a moderator resulted in a
-moderator test that was not significant, QM(3) = 5.36, \emph{p} = 0.147.
-This suggests that upon hearing a mispronunciation, infants looks to the
-target image were similar for when the mispronunciation was on a
-consonant or vowel phoneme, regardless of the language family of their
-native language. We next assessed whether the relationship between
-mispronunciation type (consonant or vowel) and mispronunciation
-sensitivity was modulated by language family. We merged the two datasets
-and included condition (correct pronunciation, mispronunciation) as well
-as language family as additional moderators. The moderator test was
-significant, QM(7) = 158.89, \emph{p} \textless{} .001. The interaction
-between condition and language family was significant (\(\beta\) = 0.73,
-SE = 0.23, 95\% CI {[}0.27, 1.18{]}, \emph{p} = 0.002), suggesting
-XXXXXXXXXXXXXX. The interaction between mispronunciation type,
-condition, and language family was also significant (\(\beta\) = -0.87,
-SE = 0.28, 95\% CI {[}-1.42, -0.32{]}, \emph{p} = 0.002). As can be seen
-in Figure X, mispronunciation sensitivity for consonants was similar for
-Germanic and Romance languages. Mispronunciation sensitivity for vowels,
-however, was greater for Germanic compared to Romance languages.
-
-{[}KATIE{]} I'M NOT REALLY SURE WHAT THE CONDITION BY LANGUAGE FAMILY
-INTERACTION MEANS. SHOULD WE EVEN INTERPRET IT?
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotCVEffect_Lang-1.pdf}
-\caption{}
-\end{figure}
-
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
-Finally, we examined the relationship between language family and infant
-age and mispronunciation sensitivity to consonants and vowels. For
-object recognition in response to a mispronunciation, including language
-family and infant age as a moderator resulted in a moderator test that
-was significant, QM(7) = 19.53, \emph{p} = 0.007. The interaction
-between language family, age, and type of mispronunciation (consonant or
-vowel) was significant, (\(\beta\) = 0.73, SE = 0.23, 95\% CI {[}0.27,
-1.18{]}, \emph{p} = 0.002). As can be seen in Figure X, for infants
-learning Germanic languages, increasing age was related to increasing
-mispronunciation sensitivity for vowel mispronunciations, but decreasing
-sensitivity for consonant mispronunciations. In contrast, infants
-learning Romance languages have an even greater increase with age in
-sensitivity to vowel mispronunciations. Surprisingly, sensitivity to
-consonant mispronunciations shows a reversal in infants learning Romance
-languages: the growth in target looks for consonant mipronunciations
-increases and surpases that of target looks for correct pronunciations.
-
-{[}KATIE{]} AGAIN, THERE ARE ADDITIONAL INTERACTIONS THAT ARE
-SIGNIFICANT\ldots{} SHOULD THEY BE INTERPRETED? ALSO, WTF ROMANCE
-LANGUAGES?
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotCVEffect_cond_age_fam-1.pdf}
-\caption{}
-\end{figure}
-
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
-Although we had no predictions regarding mispronunciation sensitivity to
-tone mispronunciations, we included an exploratory analysis to examine
-whether responses to tone mispronunciations were different from that of
-consonants or vowels. Regarding object identification in response to
-mispronunciations, when mispronunciation type was included as a
-moderator, the moderator test was not significant QM(2) = 1.16, \emph{p}
-= 0.56. This suggests that upon hearing a mispronunciation, infants
-looks to the target image were similar for tone mispronunciations in
-comparison with both consonants and vowels. We next assessed whether
-type of mispronunciation (tone, consonant, vowel) was related to
-mispronunciation sensitivity. We merged the two datasets and included
-condition (correct pronunciation, mispronunciation) as an additional
-moderator. The moderator test was significant, QM(5) = 154.88, \emph{p}
-\textless{} .001. The interaction between condition and consonant
-mispronunciations was not significant \(\beta\) = -0.19, (SE = 0.21,
-95\% CI {[}-0.59, 0.21{]}, \emph{p} = 0.359), suggesting that there was
-no difference in looks to the target in response to consonant and tone
-mispronunciations. The interaction between condition and vowel
-mispronunciations was also not significant \(\beta\) = -0.13, (SE =
-0.21, 95\% CI {[}-0.55, 0.28{]}, \emph{p} = 0.528), suggesting that
-there was no difference in looks to the target in response to vowel and
-tone mispronunciations.
-
-We further included an exploratory analysis of the relationship between
-infant age and the impact of tone mispronunciations in comparison to
-consonant and vowel mispronunciations. First, for object recognition in
-response to mispronunciations, when age in addition to mispronunciation
-location was also included as a moderator, the moderator test was not
-significant, QM(5) = 2.78, \emph{p} = 0.733. This suggests that upon
-hearing a mispronunciation, infants looks to the target image were not
-different between tone and vowel or tone and consonant
-mispronunciations, regardless of their age. We next assessed whether the
-relationship between mispronunciation type (tone, consonant, vowel) and
-mispronunciation sensitivity was modulated by age. We merged the two
-datasets and included condition (correct pronunciation,
-mispronunciation) as well as age as additional moderators. The moderator
-test was significant, QM(11) = 163.85, \emph{p} \textless{} .001, but
-the interactions between condition, age, and both consonant
-mispronciations (\(\beta\) = 0.02, SE = 0.10, 95\% CI {[}-0.19, 0.22{]},
-\emph{p} = 0.871) and vowel mispronunciations (\(\beta\) = 0.06, SE =
-0.10, 95\% CI {[}-0.14, 0.27{]}, \emph{p} = 0.56) were not significant.
-Infants' sensitivity to tone mispronunciations compared to consonant or
-vowel mispronunciations did not differ with age.
-
-{[}KATIE{]} WORTH IT TO INCLUDE LANGUAGE FAMILY ANALYSES TOO?
 
@@
 
-To Summarize:
-
-** Overall Meta-analytic Effect **
-
-\begin{itemize}
-\tightlist
-\item
-  Accept mispronunciations as labels for targets
-\item
-  Sensitive to mispronunciations
-\item
-  lack of change over development
-\end{itemize}
-
-** Vocabulary **
-
-\begin{itemize}
-\tightlist
-\item
-  no relationship?
-\item
-  talk about how few studies report it
-\end{itemize}
-
-** Size of Mispronunciation **
-
-\begin{itemize}
-\tightlist
-\item
-  graded sensitivity to number of features changed in a mispronunciation
-\item
-  importance for controlling in experimental design
-\item
-  Perhaps a call for more studies to include multiple number of features
-  changed, so that this can be assessed? There was a narrow age where
-  this was actually manipulated.
-\end{itemize}
-
-** Distractor Familiarity **
-
-\begin{itemize}
-\tightlist
-\item
-  Not really sure, check the results. A key interaction is significant
-  in one model but not the other.
-\item
-  Again, ages not matched very well for the two groups here. Decide
-  about whether to include a age subset analysis
-\end{itemize}
-
-** Phonological overlap between target and distractor **
-
-\begin{itemize}
-\tightlist
-\item
-  mispronunciation sensitivity was greater when target-distractor pairs
-  shared the same onset phoneme compared to when they shared no
-  phonological overlap
-\item
-  this is rather the opposite of what one would expect, right?
-\item
-  mispronunciation sensitivity was smaller when the distractor image
-  shared the same onset phoneme as the target image compared to when the
-  distractor image was an unfamiliar object
-\item
-  Maybe it would be useful to have time course analyses to address this
-  issue further
-\item
-  As infants aged, overall recognition (regardless of condition)
-  increased for target-distractor pairs containing onset overlap,
-  whereas overall recognition decreased for target-distractor pairs
-  containing no overlap.
-\item
-  mispronunciation sensitivity for target words paired with unfamiliar
-  distractors decreased with age, while it remained steady across a
-  similar range of ages for target words paired with distractors
-  containing onset overlap with the target word.
-\end{itemize}
-
-** Position of mispronunciation **
-
-\begin{itemize}
-\tightlist
-\item
-  really no impact at all
-\end{itemize}
-
-** Type of mispronunciation **
-
-\begin{itemize}
-\tightlist
-\item
-  Overall, no difference between consonants and vowels
-\item
-  Consonant mispronunciation sensitivity decreases with age
-\item
-  Vowel mispronunciation sensitivity increases with age
-\item
-  mispronunciation sensitivity for consonants similar for Germanic and
-  Romance languages
-\item
-  Mispronunciation sensitivity for vowels greater for Germanic compared
-  to Romance languages
-\item
-  For Germanic infants, increasing age was related to increasing
-  mispronunciation sensitivity for vowel mispronunciations, but
-  decreasing sensitivity for consonant mispronunciations.
-\item
-  For Romance infants, an even greater increase with age in sensitivity
-  to vowel mispronunciations.
-\item
-  For Romance infants, the growth in target looks for consonant
-  mipronunciations increases and surpases that of target looks for
-  correct pronunciations
-\item
-  exploratory analyses with tone mispronunciations suggest no great
-  difference in sensitivity when compared to consonant and vowel
-  mispronunciations
-\end{itemize}
-
-When it comes to designing studies, best practices and current standards
-might not always overlap. Indeed, across a set of previous meta-analyses
-it was shown that particularly infant research does not adjust sample
-sizes according to the effect in question (Bergmann et al., in press). A
-meta-analysis is a first step in improving experiment planning by
-measuring the underlying effect and its variance, which is directly
-related to the sample needed to achieve satisfactory power in the null
-hypothesis significance testing framework. Failing to take effect sizes
-into account can both yield to underpowered research and to testing too
-many participants, both consequences are undesirable for a number of
-reasons that have been discussed in depth elsewhere. We will just
-briefly mention two that we consider most salient for theory building:
-Underpowered studies will lead to false negatives more frequently than
-expected, which in turn results in an unpublished body of literature
-(citationcitation). Overpowered studies mean that participants were
-tested unnecessarily, which has substantial ethical consequences
-particularly when working with infants and other difficult to recruit
-and test populations.
-
-From Christina: let's make a note to put sth in the discussion about our
-curve being surprisingly flat for correctly pronounced words bc people
-adapt their analysis windows? Bc if you look at Molly's reaction time
-paper, there is a steep increase.
-
-Discussing the Moderator Analyses Maybe put them together into the ones
-that worked out as we predicted and those that didn't? So, here is
-evidence that supports existing arguments, that doesn't need to be a
-huge chunk. But then more space devoted to moderator analyses that
-didn't work out according to predictions.
-
-It should be noted that the majority of consonant mispronunciations were
-located on the onset phoneme (\emph{n} = 120; total consonant
-conditions, \emph{n} = 145), while the majority of vowel
-mispronunciations were located on the medial phoneme (\emph{n} = 44;
-total vowel conditions, \emph{n} = 71). In their analysis using TRACE,
-Mayor and Plunkett (2014) found that the difference between sensitivity
-to consonant and vowel mispronunciations was due to infants' lexical
-knowlege consisting of a majority consonant onset words.
-
-{[}KATIE{]} COME BACK TO THIS.
-
 \newpage
-
-\section{References}\label{references}
 

### 2018-10-23 scripts/calculateES.R

@@ -30,6 +30,9 @@ db_ET$d_calc <- NA
 db_ET$d_var_calc <- NA
 db_ET$es_method <- "missing"
 
+
+db_ET$imputed_corr <- ifelse(is.na(db_ET$corr), "yes", "no")
+
 db_ET$corr = ifelse(is.na(db_ET$corr), db_ET$corr_imputed, db_ET$corr)
 
 #Correlations are never perfect and cannot be higher than 1 or lower than 0, so fixing some possible imputation issues first. 

### 2018-10-25 Paper_Analyses.Rmd
update 24.10.2018
better model interpretation
vocabulary summary
choosing figures to include

@@
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)
+
+# wordcount()
+# doesn't work...
+# https://github.com/benmarwick/wordcountaddin
 
@@
 
+g_SE <- function(x) paste0(r2(x$estimate), " (SE = ", r2(x$se), ")")
+
+CI_p <- function(x) paste0("(95% CI[", r2(x$ci.lb), ", ", r2(x$ci.ub), "], *p* ", psig(x$pval), ")")
+
+full_estimate <- function(x) paste0(" = ", r2(x$estimate), ", SE = ", r2(x$se), ", 95% CI[",  r2(x$ci.lb), ", ", r2(x$ci.ub),"], *p*", psig(x$pval))
+
+# moderator test
+mod_test <- function(x) paste0("QM(", r2(rma_MPeffect$m), ") = ", r2(rma_MPeffect$QM), ", *p*", psig(rma_MPeffect$QMp))
+
 ```
@@
 
-kable(pub_info, col.names = c("Publication Type", "# Items", "# Effect Sizes"))
+#kable(pub_info, col.names = c("Publication Type", "# Items", "# Effect Sizes"))
 
@@
 
-kable(comparison_info, col.names = c("Type of comparison", "# Papers", "# Effect Size"))
+#kable(comparison_info, col.names = c("Type of comparison", "# Papers", "# Effect Size"))
 #table(db_ET_MP$es_method)
@@
   summarize(n_unique = n_distinct(short_cite), count = n())
-
-#kable(es_info)
-#table(dat$es_method, dat$short_cite)
-# only missing from:
-# Bailey & Plunkett (2002) <- crazy old data
-# Renner (2017) <- just finished phd
-#table(db_ET_MP$es_method)
-
-#[KATIE] Can you also rename the factors here (like t_one)?
-#[CHRISTINA] Mpt sire what you man, like in the table? You rename things later on, so why not.
-#[KATIE] Actually, do we really need this table? When everything is summarized in the text, is that good enough?
 
@@
 
-We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(dat, n_distinct(short_cite[es_method == "group_means_one" | es_method == "group_means_two"]))`) or using reported t-values (*n* = `r with(dat, n_distinct(short_cite[es_method == "t_one" | es_method == "t_two"]))`).
+We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, n_distinct(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))`) or using reported t-values (*n* = `r with(es_info, n_distinct(n_unique[es_method == "t_one" | es_method == "t_two"]))`).
 Raw means and standard deviations were extracted from figures for `r with(dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers.
@@
 [KATIE: Are you concerned about the Publication Bias section in particular, or the Methods as a whole?
-In general, some of the Methods was written before the CogSci paper and in other places to flesh things out I rewrote what we had.
+In general, some of the Methods was written before the CogSci paper and in other places to flesh things out I rewrote what we had in the CogSci paper.
 Its definitely giving the same information and sometimes the wording is close, because there's not too many different ways to explain what a funnel plot is :)]
@@
 For now I think the last sentence is fine, but I would tend to prefer a reminder for the forgetful reader.]
-[KATIE: that's reasonable! We had just listed everything 7 paragraphs before, which doesn't seem like a lot of "space".]
+[KATIE: that's reasonable!
+We had just listed everything 7 paragraphs before, which doesn't seem like a lot of "space".
+Alternatively, this information could be listed in a table, and then just referred to.]
 
@@
 smaller variance) than expected (top left, outside the triangle).
-
-[CHRISTINA: If we want to interpret here, how about the next bit.]
-[KATIE: YES! This is an excellent point!!!]
 
@@
 
-```{r FunnelCombo}
+```{r FunnelCombo, echo = FALSE}
 
@@
 
-```{r PcurveExport}
+```{r PcurveExport, echo = FALSE}
 
@@
 
-[CHRISTINA: CAn you add the stats for the non-sig results?]
-[KATIE: Are there stats that can be computed on the non-sig results? Or do you just want an n for significant and non-significant studies?]
-
 Taken together, the results suggest a tendency in the literature towards publication bias.
@@
 looks to the target image in response to correctly pronounced words.
-The variance-weighted meta-analytic effect size Hedges' *g* was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
+The variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was significantly different from zero `r CI_p(sum_eff)`.
 This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research).
@@
 [CHRISTINA: Can you explain what the CI lower bound means here? I don't follow.]
-[KATIE: What do you think about this? The CI lower bound stuff here actually comes from something you wrote, so tell me whether its correct.]
+[KATIE: What do you think about this (last sentence)? The CI lower bound stuff here actually comes from something you wrote, so tell me whether its correct.]
 
@@
 We then calculated the meta-analytic effect for object identification in response to mispronounced words.
-In this case, the variance-weighted meta-analytic effect size Hedges' *g* was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`) which was also significantly different from zero (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
+In this case, the variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was also significantly different from zero `r CI_p(sum_eff)`.
 This is considered a small effect size (Cohen, 1988), but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object.
@@
 To evaluate mispronunciation sensitivity, we  compared the effect size Hedges' *g* for correct pronunciations with mispronunciations directly, merging the two datasets.
-The moderator test was significant, QM(`r r2(rma_MPeffect$m)`) = `r r2(rma_MPeffect$QM)`, *p* `r psig(rma_MPeffect$QMp)`.
-Hedges' *g* for mispronunciation sensitivity was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that the responses across conditions were significantly different (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
+The moderator test was significant, `r mod_test(rma_MPeffect)`.
+Hedges' *g* for mispronunciation sensitivity was `r g_SE(sum_eff)`, which indicated that the responses across conditions were significantly different `r CI_p(sum_eff)`.
 This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations.
@@
 In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not.
-Age did not significantly modulate object identification in response to correctly pronounced (QM(`r r2(rma_correct_age$m)`) = `r r2(rma_correct_age$QM)`, *p* `r psig(rma_correct_age$QMp)`) or mispronounced words (QM(`r r2(rma_MP_age$m)`) = `r r2(rma_MP_age$QM)`, *p* `r psig(rma_MP_age$QMp)`).
+Age did not significantly modulate object identification in response to correctly pronounced `r mod_test(rma_correct_age)` or mispronounce words `r mod_test(rma_MP_age)`.
 The lack of a significant modulation together with the small estimates indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label.
 This relationship is plotted in Figure 2.
-
-[CHRISTINA] CAN YOU ADD ESTIMATES AND THEIR CIS?? Ideally everywhere where you report a p-value
-[KATIE: Do you know how to calculate Estimates and CIs for the Test of Moderators? Or do you mean reporting the estimates and CIs even when the moderator test is not significant?]
 
@@
 mispronounced words) in our whole dataset.
-The moderator test was significant (QM(`r r2(rma_MPeffect_age$m)`) = `r r2(rma_MPeffect_age$QM)`, *p* `r psig(rma_MPeffect_age$QMp)`).
+The moderator test was significant `r mod_test(rma_MPeffect_age)`.
 This result is in line with the general observation that as infants mature they become better at language processing.
-The interaction between age and mispronunciation sensitivity, however, was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`), suggesting that as infants age, their mispronunciation sensitivity remains the same.
+The interaction between age and mispronunciation sensitivity, however, was not significant $\beta$`r full_estimate(sum_eff)`.
+The small estimate size, as well as inspection of Figure 2 suggests that as infants age, their mispronunciation sensitivity remains the same.
 
@@
 
-Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers; production = `r with(vi1, papers[has_vocab == "production"])`) analyzed the relationship between vocabulary scores and mispronunciation sensitivity.
+Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers; production = `r with(vi1, papers[has_vocab == "production"])`) analyzed the relationship between vocabulary scores and mispronunciation sensitivity, specifically object recognition for correct pronunciations and mispronunciations.
 There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we analyze this data separately.
 
-[KATIE] I DON'T KNOW HOW TO INTERPRET THESE RESULTS... THE FIXED EFFECTS MODEL ISN'T SIGNIFICANT FOR ANY OF THESE. IS THAT MEANINGFUL?
 [CHRISTINA] SO WE DON'T WANT TO INTERPRET THE FIXED EFFECTS MODEL AT ALL, IT IS NOT SUITABLE BECAUSE THERE IS VARIANCE BETWEEN EVERY RECORD (LANGUAGE ETC).
@@
 [KATIE: Ah, so because for each paper the correlation and CI values straddle 0, this indicates that there really isn't much evidence for a relationship?
-I think it could make sense to add this to supplementary materials.
+I've tried to write this out below, let me know what you think.
 Over the summer, I had also played around with looking at how collection of vocabulary data has dropped off over the years, even though more mispronunciation studies have been published.
@@
 
-metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
+CC <- metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
+
+# https://rdrr.io/cran/meta/man/forest.html
+#forest(CC)
+
 ```
@@
 
-metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
-```
+CP <- metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
+
+```
+
+[Katie: below, I'm using coweeta.uga.edu/publications/10436.pdf, page 80 as a model for writing up these results. I haven't the funniest clue what I'm doing! :p]
+
+We first considered the relationship between vocabulary and object recognition for correct pronunciations.
+Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for 9 of 12 experimental conditions, with correlation values ranging from -0.17 to 0.48.
+The mean effect size XXX was 0.0897, but did not differ significantly from zero (95% CI[-0.0105; 0.1900] *p* = .0795).
+Higher production scores were also associated with greater object recognition in response to correct pronunciations for 9 of 16 experimental conditions, with correlation values ranging from -0.23 to 0.44.
+The mean effect size XXX was 0.0601, but did not differ significantly from zero (95% CI[-0.0331; 0.1533] *p* = .2061).
+For both comprehension and production scores, the small correlation effect sizes and large variances suggest a lack of relationship between vocabulary and object recognition for correct pronunciations.
 
@@
 
-metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
+MC <- metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
 ```
@@
 
-metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
-```
+MP <- metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
+```
+
+We next considered the relationship between vocabulary and object recognition for mispronunciations.
+Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for 17 of 31 experimental conditions, with correlation values ranging from -0.35 to 0.57.
+The mean effect size XXX was 0.0377, but did not differ significantly from zero (95% CI[-0.0260; 0.1014] *p* = .2465).
+For production, however, lower production scores were associated with greater object recognition in response to mispronunciations for 16 of 31 experimental conditions, with correlation values ranging from -0.28 to 0.44.
+The mean effect size XXX was -0.0402, but did not differ significantly from zero (95% CI[-0.1043; 0.0238] *p* = .2181).
+For both comprehension and production scores, the small correlation effect sizes and large variances suggest a lack of relationship between vocabulary and object recognition for mispronunciations.
 
@@
 This runs counter to existing theories of phono-lexical development, which predict either an increase (PRIMR ref) or decrease (Assim Model ref) in mispronunciation sensitivity.
-
-[KATIE] CAN A CONCLUSION BE DRAWN FROM THE VOCABULARY RESULTS? IF SO, THIS IS THE PARAGRAPH
-
+Furthermore, counter to the predictions for the PRIMR (PRIMR ref) and Assimilation(Assim ref) models, we found no relationship between vocabulary and target looking for correct pronunciations or mispronunciations.
 In sum, it seems that current theories of infants' phono-lexical development cannot fully capture our results and should be reconsidered with all the evidence in mind.
@@
 Alternatively, the lack of developmental change in mispronunciation sensitivity could be due to differences in the types of tasks given to infants of different ages.
-To examine this possibility, we include an exploratory analysis of whether different moderators and experimental design features were included at different ages, in addition to investigating the role that these moderators play in mispronunciation sensitivity.
+In the following section, we investigate the role that different moderators play in mispronunciation sensitivity.
+To investigate the possibility of systematic differences in the tasks across ages, we additionally include an exploratory analysis of whether different moderators and experimental design features were included at different ages.
 
@@
 To understand the relationship between number of features changed and mispronunciation sensitivity, we  evaluated the effect size Hedges' *g* with number of features changed as a moderator.
-The moderator test was significant, QM(`r r2(rma_NFeatures$m)`) = `r r2(rma_NFeatures$QM)`, *p* `r psig(rma_NFeatures$QMp)`.
-Hedges' *g* for number of features changed was `r r2(sum_eff$estimate)` (SE = `r r2(sum_eff$se)`), which indicated that as the number of features changed increased, the effect size Hedges' *g* significantly decreased (95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
-We plot this relationship in Figure X.
+The moderator test was significant, `r mod_test(rma_NFeatures)`.
+Hedges' *g* for number of features changed was `r g_SE(sum_eff)`, which indicated that as the number of features changed increased, the effect size Hedges' *g* significantly decreased `r CI_p(sum_eff)`.
+We plot this relationship in Figure 3.
 This confirms previous findings of a graded sensitivity to the number of features changed for both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) mispronunciations as well as the importance of controlling for the degree of phonological mismatch in experimental design.
+
+## Figure 3
 
@@
 p <- ggplot(dat_f, aes(Features_changed, g_calc, fill = Features_changed)) + 
-  geom_boxplot() + 
+  geom_violin() + 
+  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
   #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
@@
 Although we did not have any specific predictions about the relationship between infant age and the impact of number of features changed on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
-When age was also included as a moderator, the moderator test was significant, QM(`r r2(rma_NFeatures$m)`) = `r r2(rma_NFeatures$QM)`, *p* `r psig(rma_NFeatures$QMp)`, but the interaction between age and number of features changed was not significant, $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
-This suggests that there is no relationship between infant age the impact of number of features changed on mispronunciation sensitivity.
+When age was also included as a moderator, the moderator test was significant, `r mod_test(rma_NFeatures)`, but the interaction between age and number of features changed was not significant, $\beta$`r full_estimate(sum_eff)`.
+The small effect size for the interaction between age and number of features changed suggests that the impact of number of features changed on mispronunciation sensitivity does not change with infant age.
 
@@
 The age range for each type of number of features changed was `r with(nfeature_ages, min_age[n_feature == 1])` - `r with(nfeature_ages, max_age[n_feature == 1])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 1])`) for 1-feature mispronunciations, `r with(nfeature_ages, min_age[n_feature == 2])` - `r with(nfeature_ages, max_age[n_feature == 2])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 2])`) for 2-feature mispronunciations, and `r with(nfeature_ages, min_age[n_feature == 3])` - `r with(nfeature_ages, max_age[n_feature == 3])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 3])`) for 3-feature mispronunciations.
-Focusing on the ages where all three numbers of features changed were tested (i.e.
+The reader should note that experimental conditions in which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent (e.g., one mispronunciation included a 2-feature change whereas another only a 1-feature change) are not included in these totals.
+An analysis focusing on the ages where all three numbers of features changed were tested (i.e.
 `r with(nfeature_ages, min_age[n_feature == 3])` - `r with(nfeature_ages, max_age[n_feature == 3])` days), however, did not change the pattern of results.
@@
 
+misp_recog <- coef(summary(rma_Distractor_MP))[2,]
+
 rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
 
-sum_eff <- coef(summary(rma_Distractor))[4,]
+misp_MS <- coef(summary(rma_Distractor))[4,]
 
@@
 First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images that were paired with either a familiar or an unfamiliar distractor image.
-The moderator test was not significant QM(`r r2(rma_Distractor_MP$m)`) = `r r2(rma_Distractor_MP$QM)`, *p* `r psig(rma_Distractor_MP$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object.
+The moderator test was not significant `r mod_test(rma_Distractor_MP)` and the estimate for distractor familiarity was relatively small, $\beta$`r full_estimate(misp_recog)`.
+This suggests that upon hearing a mispronunciation, infants' looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object.
 We next assessed whether distractor familiarity was related to mispronunciation sensitivity.
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_Distractor$m)`) = `r r2(rma_Distractor$QM)`, *p* `r psig(rma_Distractor$QMp)`, but the interaction between distractor familiarity and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
-These results suggest that overall, infants' familiarity with the distractor object (familiar or unfamiliar) did not impact their mispronunciation sensitivity.
+The moderator test was significant, `r mod_test(rma_Distractor)`, but the estimate for the interaction between distractor familiarity and condition was small and not significant $\beta$`r full_estimate(misp_MS)`.
+This relationship is plotted in Figure 4.
+The results suggest that overall, infants' familiarity with the distractor object (familiar or unfamiliar) did not impact their mispronunciation sensitivity.
+
+## Figure 4
 
@@
 
-p <- ggplot(dat, aes(condition_label, g_calc, fill = condition_label)) + 
-  geom_boxplot() + 
+p.DIST_ALL <- ggplot(dat, aes(condition_label, g_calc, fill = condition_label)) + 
+  geom_violin() + 
+  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
   facet_grid(.~dist_code) +
+  #labs(caption="a.") + 
   #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
@@
 
-p
-
-  jpeg(filename = "figures/Figure_4Distractor_fam.jpg", 
+p.DIST_ALL
+
+# lay <- rbind(c(1,1,2),
+#       c(3,3,3))
+
+  jpeg(filename = "figures/Figure_4_Distractor_Familiarity.jpg", 
        width = 500, height = 300, units = "px")
 
-  p
+p.DIST_ALL
 
 dev.off()
-
-  #[CHRISTINA] AGAIN, WHAT DO YOU THINK OF VIOLINS?
 
@@
 We next examined whether age modulates object recognition or mispronunciation sensitivity when the distractor image is familiar or unfamiliar.
-For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_DistractorAge$m)`) = `r r2(rma_DistractorAge$QM)`, *p* `r psig(rma_DistractorAge$QMp)`.
-[CHRISTINA] I WORRY A LOT AT THESE POINTS THAT THIS IS THE WHOLE P>.05 = NULL IS TRUE FALLACY.
-WE CAN NEVER HAVE EVIDENCE FOR THE NULL HYPOTHESIS.
-SO BETTER ITNERPRET ESTIMATES AND CIS.
-
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object, regardless of their age.
+Based on previous results, we expected older infants to look less to the target in response to mispronunciations and to have greater mispronunciation sensitivity than younger infants when the distractor was unfamiliar compared to familiar.
+For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant `r mod_test(rma_DistractorAge)`, and a small estimate for the interaction between age and object recognition ($\beta$`r full_estimate(sum_eff1)`.
+This suggests that upon hearing a mispronunciation, infant looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object, regardless of their age.
 We next assessed whether the relationship between distractor familiarity and mispronunciation sensitivity was modulated by age.
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_DistractorAgeMS$m)`) = `r r2(rma_DistractorAgeMS$QM)`, *p* `r psig(rma_DistractorAgeMS$QMp)`.
-Although the three-way-interaction between condition, distractor familiarity, and age was not significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`), here the interaction between condition and distractor familiarity was significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], *p* `r psig(sum_eff2$pval)`).
-
-[KATIE] WHAT DOES IT MEAN THAT IN THIS LAST TEST THERE WAS AN INTERACTION BETWEEN CONDITION AND DISTRACTOR FAMILIARITY, WHEN AGE WAS INCLUDED AS A MODERATOR?
-DOES THAT MEAN THAT AGE IS CONTROLLED FOR?
-UNDERSTANDING THIS WILL HELP ME FORMULATE THE CONCLUSION SENTENCE AND MOTIVATE THE NEXT SET OF ANALYSES.
-
-[CHRISTINA] I WOULD NOT OVERINTERPRET IT, THE ESTIMATE DID NOT DRAMATICALLY CHANGE, AND IT IS BARELY SIGNIFICANT. DOES THAT HELP?
-
-[KATIE: I think so. I've just removed that part]
+The moderator test was significant `r mod_test(rma_DistractorAgeMS)`.
+The estimate for the  three-way-interaction between condition, distractor familiarity, and age was small and not significant ($\beta$ = `r full_estimate(sum_eff1)`.
+We note that in this model, the interaction between condition and distractor familiarity was significant ($\beta$`r full_estimate(sum_eff2)`, this estimate is similar to the original estimate specifically examining this interaction in a previous model.
+Taken together, these results suggest that regardless of age, mispronunciation sensitivity was similar whether the distractor image was familiar or unfamiliar.
 
@@
             max_age = r2(max(mean_age_1, na.rm=TRUE)),
-            mean_age = r2(mean(mean_age_1, na.rm=TRUE)))
+            mean_age = r2(mean(mean_age_1, na.rm=TRUE)),
+            sd_age = r2(sd(mean_age_1, na.rm=TRUE)))
 
@@
 
-age_diff_dist <- t.xtable(t.test(fn$mean_age_1, ff$mean_age_1, paired = F))
+age_diff_dist <- t.test(fn$mean_age_1, ff$mean_age_1, paired = F)
 
@@
 
-rma_Distractor_MP <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat_age_MP, random = ~ collapse | short_cite)
+rma_Distractor_MP_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat_age_MP, random = ~ collapse | short_cite)
+
+misp_recog_agesub <- round(coef(summary(rma_Distractor_MP_agesub))[2,], 2)
+
+rma_DistractorAge_agesub <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(object_pair), data = dat_age_MP, random = ~ collapse | short_cite)
 
@@
 
-sum_eff <- round(coef(summary(rma_Distractor_MP))[2,], 2)
+misp_MS_agesub <- round(coef(summary(rma_DistractorAge_agesub))[4,], 2)
 
@@
 
-rma_Distractor_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition, data = dat_age, random = ~ collapse | short_cite)
+rma_Distractor_MS_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition, data = dat_age, random = ~ collapse | short_cite)
+
+misp_recog_Age_agesub <- round(coef(summary(rma_Distractor_MS_agesub))[4,], 2)
+
+rma_DistractorAgeMS_agesub <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
+
+misp_MS_Age_agesub <- round(coef(summary(rma_DistractorAgeMS_agesub))[8,], 2)
 
 #summary(rma_Distractor_MS)  
-
-sum_eff <- coef(summary(rma_Distractor_MS))[2,]
-
 ```
@@
 Inspection of the ages tested using different kinds of distractors, however, revealed differences.
-Infants tested using a familiar distractor were younger (M = 588.76 days, SD = 136.47, range = 207.8 - 768 days) than those infants tested using an unfamiliar distractor (M = 678.85 days, SD = 115.47, range = 544.48 - 920.2 days), which a two-sample t-test revealed to be a significant difference, t(153.83) = 5.30, p < .0001.
+Infants tested using a familiar distractor were younger (*M* = `r with(object_pair_ages, mean_age[object_pair == "familiar_familiar"])` days, *SD* = `r with(object_pair_ages, sd_age[object_pair == "familiar_familiar"])`, range = `r with(object_pair_ages, min_age[object_pair == "familiar_familiar"])` - `r with(object_pair_ages, max_age[object_pair == "familiar_familiar"])`) than those infants tested using an unfamiliar distractor (*M* = `r with(object_pair_ages, mean_age[object_pair == "familiar_novel"])` days, *SD* = `r with(object_pair_ages, sd_age[object_pair == "familiar_novel"])`, range = `r with(object_pair_ages, min_age[object_pair == "familiar_novel"])` - `r with(object_pair_ages, max_age[object_pair == "familiar_novel"])`), which a two-sample t-test revealed to be a significant difference, *t*(`r r2(age_diff_dist$parameter)`) = `r r2(age_diff_dist$statistic)`, *p* `r psig(age_diff_dist$p.value)`).
 
 [CHRISTINA] CAN YOU TURN THE NUMBERS INTO R CODE HERE? aLSO, NOT SURE WE NEED A T-TEST TO CONFIRM THE OBVIOUS.
-
-[KATIE] SO, IS IT OKAY TO DO THE AGE SUBSET ANALYSIS AFTER THIS?
-SOMETHING LIKE "TO ENSURE THAT THE LACK OF A DIFFERENCE WASN'T DUE TO THE DIFFERENCE IN AGES OF INFANTS TESTED WITH DIFFERENT TYPES OF DISTRACTORS, WE ANALYZED A SUBSET OF PAPERS THAT TESTED AGES WHERE BOTH FAMILIAR AND UNFAMILIAR DISTRACTORS WERE USED." IN THE SUBSET ANALYSIS, FOR MISP SENSITIVITY, THERE IS A SIGNIFICANT INTERACTION BETWEEN DISTRACTOR FAMILIARITY AND CONDITION.
-
-[CHRISTINA] YES!!!!!!
+[Katie: Is the t-test okay?]
+
+To ensure that the lack of a difference wasn't due to the ages of infants tested with different types of distractors, we repeated the previous model analyses on a subset of papers that tested infants at ages where both familiar and unfamiliar distractors were used (`r min_age` - `r max_age` days).
+We first considered object recognition is response to a mispronunciation.
+Here, the pattern of results for the subset of infants was similar to that of the entire dataset; the moderator test was not significant `r mod_test(rma_Distractor_MP_agesub)` and the estimate for distractor familiarity was small, $\beta$`r full_estimate(misp_recog_agesub)`.
+However, it should be noted that although small, the effect size estimate for distractor familiarity doubled from $\beta$`r r2(misp_recog$estimate)` in the entire dataset to $\beta$`r r2(misp_recog_agesub$estimate)` in the subset.
+We next assessed the relationship between distractor familiarity and mispronunciation sensitivity.
+Similar to the analysis with the entire dataset, the moderator test was significant `r mod_test(rma_Distractor_MS_agesub)`.
+Unlike the analysis with the entire dataset, however, the estimate for the interaction between distractor familiarity and condition was significant $\beta$`r full_estimate(misp_recog_Age_agesub)`, but small and similar to the estimate for this interaction in the full dataset $\beta$ = `r r2(misp_MS$estimate)`.
+
+Although the age range is relatively small in the subset of infant ages tested with both familiar and unfamiliar distractors (`r r2(max_age/30.44 - min_age/30.44)` months), these ages span the beginning of the vocabulary spurt.
+Considering infants' object looking behavior may be influenced by whether the label for the object is known (Schafer & Plunkett, 1998), however, this age range may still be informative for understanding the role of distractor familiarity on mispronunciation sensitivity and whether this is modulated by age.
+Similar to the full dataset, however, including age as a moderator of object recognition in response to familiar and unfamiliar distractors resulted in a moderator test that was not significant `r mod_test(rma_DistractorAge_agesub)`, and a small estimate for the interaction between age and object recognition ($\beta$`r full_estimate(misp_MS_agesub)`.
+Finally, we assessed whether the relationship between distractor familiarity and mispronunciation sensitivity was modulated by age in the subset of data.
+Again, similar to the full dataset, the moderator test was not significant `r mod_test(rma_DistractorAgeMS_agesub)` and the estimate for the three-way-interaction between condition, distractor familiarity, and age was small and not significant ($\beta$ = `r full_estimate(misp_MS_Age_agesub)`.
+
+[Katie: ultimately, the subset analysis doesn't show anything :( What conclusions can we draw?]
 
@@
 
-To assess whether phonological overlap between the target and distractor image labels has an impact on the size of mispronunciation sensitivity, we examined the meta-analytic effect for object identification in response to mispronunciations and mispronunciation sensitivity when the target-distractor pairs either shared the same onset phoneme, had no overlap, or where the distractor was an unfamiliar object.
-We did not include data for which the overlap included both the onset and medial phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset/medial"])`) or coda phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "coda"])`).
-The analysis was therefore based on a subset of the overall dataset, with `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset"])` experimental conditions containing onset phoneme overlap between the target and distractor, `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "no"])` containing no overlap between target and distractor, and `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "novel"])` for targets paired with unfamiliar distractor images.
-There were therfore three possibilities for distractor overlap: onset phoneme overlap, no overlap, and an unfamiliar distractor.
-In our analysis, we were interested in the difference between overlap and lack of overlap; therefore, experimental conditions containing onset phoneme overlap were coded as the reference condition and compared with responses to experimental conditions with no overlap or an unfamiliar distractor separately.
-
-[KATIE] CAN YOU CHECK THE WAY THAT I WROTE THE LAST SENTENCE?
+To assess whether phonological overlap between the target and distractor image labels has an impact on the size of mispronunciation sensitivity, we examined the meta-analytic effect for object identification in response to mispronunciations and mispronunciation sensitivity when the target-distractor pairs either had no overlap or shared the same onset phoneme.
+We did not include data for which the overlap included both the onset and medial phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset/medial"])`), coda phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "coda"])`), or for targets paired with an unfamiliar distractor image `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "novel"])`.
+The analysis was therefore based on a subset of the overall dataset, with `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset"])` experimental conditions containing onset phoneme overlap between the target and distractor and `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "no"])` containing no overlap between target and distractor.
 
 [CHRISTINA] SEEMS OK BUT I AM CONFUSED WHY OVERLAP IS THE BASELINE AND WHY YOU BRING IN NOVEL. I THINK YOU NEED TO SPELL THIS OUT MORE.
+
+[KATIE: I think we had talked about it and decided to include novel. I don't think it needs to be here necessarily, so I'll take it out, especially if its confusing.]
 
@@
 db_ET_MPo = db_ET_MP %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
+  filter(distractor_overlap == "onset"  |  distractor_overlap == "no")
+
+db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no"))
 
@@
 #summary(rma_DistractorOverlap)  
+sum_eff1 <- coef(summary(rma_DistractorOverlap))[2,]
 
 db_ET_MPo_MS = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-db_ET_MPo_MS$distractor_overlap <- factor(db_ET_MPo_MS$distractor_overlap, levels = c("onset", "no", "novel"))
+  filter(distractor_overlap == "onset"  | distractor_overlap == "no")
+
+db_ET_MPo_MS$distractor_overlap <- factor(db_ET_MPo_MS$distractor_overlap, levels = c("onset", "no"))
 
@@
 
-sum_eff1 <- coef(summary(rma_DistractorOverlapMS))[5,]
-sum_eff2 <- coef(summary(rma_DistractorOverlapMS))[6,]
-
-```
-
-Regarding object identification in response to mispronunciations, when distractor overlap was included as a moderator, the moderator test was not significant QM(`r r2(rma_DistractorOverlap$m)`) = `r r2(rma_DistractorOverlap$QM)`, *p* `r psig(rma_DistractorOverlap$QMp)`.
-[CHRISTINA] AGAIN DO NOT RELY ON P-VALUES BUT ON ESTIMATES AND CIS
+sum_eff2 <- coef(summary(rma_DistractorOverlapMS))[4,]
+
+```
+
+Regarding object identification in response to mispronunciations, when distractor overlap was included as a moderator, the moderator test was not significant `r mod_test(rma_DistractorOverlap)` and the estimate for distractor overlap was relatively small, $\beta$`r full_estimate(sum_eff1)`.
 This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with a distractor image that contained overlap on the onset phoneme or no overlap with the target word, or was an unfamiliar object.
@@
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_DistractorOverlapMS$m)`) = `r r2(rma_DistractorOverlapMS$QM)`, *p* `r psig(rma_DistractorOverlapMS$QMp)`.
-The interaction between condition and target-distractor pairs with no overlap was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`), suggesting that mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap.
-The interaction between condition and target-distractor pairs with an unfamiliar distractor was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], *p* `r psig(sum_eff2$pval)`), suggesting that mispronunciation sensitivity was smaller when the distractor image shared the same onset phoneme as the target image compared to when the distractor image was an unfamiliar object.
-This can be seen in Figure X.
-
-[christina] I THINK THESE SHOULD BE TWO SEPARATE ANALYSES... NOVEL IS CONCEPTUALLY DIFFERENT.
-
-```{r PlotDistOverlapEffect}
+The moderator test was significant `r mod_test(rma_DistractorOverlapMS)`.
+The estimate for the interaction between condition and distractor overlap was small, but significant ($\beta$ `r full_estimate(sum_eff2)`, suggesting that mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap.
+This relationship be seen in Figure 5a.
+
+```{r DistractorOverlap_age}
+
+# object recognition
+db_ET_MPo = db_ET_MP %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "no")
+
+db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no"))
+
+rma_DistractorOverlap_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
+
+sum_eff1 <- coef(summary(rma_DistractorOverlap_age))[4,]
+
+# mispronunciation sensitivity
+dat_MPo = dat %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "no")
+
+dat_MPo$distractor_overlap <- factor(dat_MPo$distractor_overlap, levels = c("onset", "no"))
+
+rma_DistractorOverlap_age_MS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap*condition, data = dat_MPo, random = ~ collapse | short_cite)
+
+#summary(rma_DistractorOverlap_age_MS)
+
+sum_eff2 <- coef(summary(rma_DistractorOverlap_age_MS))[8,]
+
+```
+
+Although we did not have any specific predictions about the relationship between infant age and the impact of distractor overlap on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
+First, for object recognition in response to mispronunciations, when age in addition to distractor overlap was also included as a moderator, the moderator test was not significant, `r mod_test(rma_DistractorOverlap_age)`, and the estimate for the interaction between age and distractor overlap was small, $\beta$`r full_estimate(sum_eff1)`.
+This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for both onset and no overlap, regardless of infant age.
+We next assessed whether the relationship between distractor overlap and mispronunciation sensitivity was modulated by age.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
+The moderator test was significant, `r mod_test(rma_DistractorOverlap_age_MS)` and the estimate for the three-way interaction between age, condition, and distractor overlap was significant, but relatively small ($\beta$ = `r full_estimate(sum_eff2)`.
+As can be seen in Figure 5b, the difference between correct pronunciations and mispronunciations (mispronunciation sensitivity) stays steady across infant ages for both target words paired with distractors containing onset overlap with the target word as well as distractors containing no overlap.
+As infants aged, however, overall recognition (regardless of condition) increased for target-distractor pairs containing onset overlap, whereas for overall recognition decreased for target-distractor pairs containing no overlap.
+
+## Figure 5
+
+```{r PlotDistOverlap_cond_age}
 
 db_ET_MPo = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
+  filter(distractor_overlap == "onset"  | distractor_overlap == "no")
+
+db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no"))
 
@@
 
-p <- ggplot(db_ET_MPo, aes(condition_label, g_calc, fill = condition_label)) + 
-  facet_grid(.~distractor_overlap)+
-  geom_boxplot() + 
+db_ET_MPo$distractor_label <- ifelse(db_ET_MPo$distractor_overlap=="onset", "Onset Overlap", "No Overlap")
+
+p.DIOV_M <- ggplot(db_ET_MPo, aes(condition_label, g_calc, fill = condition_label)) + 
+  facet_grid(.~distractor_label)+
+    geom_violin() + 
+  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
+  labs(caption="a")+
   #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
@@
 
-p
-
-  jpeg(filename = "figures/Figure_5_Distractor_overlap.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-```{r DistractorOverlap_age}
-
-# object recognition
-db_ET_MPo = db_ET_MP %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
-
-rma_DistractorOverlap_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
-
-# mispronunciation sensitivity
-dat_MPo = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-dat_MPo$distractor_overlap <- factor(dat_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
-
-rma_DistractorOverlap_age_MS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap*condition, data = dat_MPo, random = ~ collapse | short_cite)
-
-#summary(rma_DistractorOverlap_age_MS)
-
-sum_eff1 <- coef(summary(rma_DistractorOverlap_age_MS))[11,]
-sum_eff2 <- coef(summary(rma_DistractorOverlap_age_MS))[12,]
-
-```
-
-Although we did not have any specific predictions about the relationship between infant age and the impact of distractor overlap on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
-First, for object recognition in response to mispronunciations, when age in addition to distractor overlap was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_DistractorOverlap_age$m)`) = `r r2(rma_DistractorOverlap_age$QM)`, *p* `r psig(rma_DistractorOverlap_age$QMp)`, suggesting that upon hearing a mispronunciation, infants looks to the target image were similar for the three types of overlap, regardless of infant age.
-We next assessed whether the relationship between distractor overlap and mispronunciation sensitivity was modulated by age.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_DistractorOverlap_age_MS$m)`) = `r r2(rma_DistractorOverlap_age_MS$QM)`, *p* `r psig(rma_DistractorOverlap_age_MS$QMp)`.
-The interaction between age, condition, and target-distractor pairs with no overlap was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`).
-As can be seen in Figure X, the difference between correct pronunciations and mispronunciations (mispronunciation sensitivity) stays steady across infant ages for both target words paired with distractors containing onset overlap with the target word as well as distractors containing no overlap.
-As infants aged, however, overall recognition (regardless of condition) increased for target-distractor pairs containing onset overlap, whereas for overall recognition decreased for target-distractor pairs containing no overlap.
-The interaction between age, condition, and target-distractor pairs with an unfamiliar distractor was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], *p* `r psig(sum_eff2$pval)`).
-As can also be seen in Figure X, mispronunciation sensitivity for target words paired with unfamiliar distractors decreased with age, while it remained steady across a similar range of ages for target words paired with distractors containing onset overlap with the target word.
-
-```{r PlotDistOverlap_cond_age}
-
-db_ET_MPo = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")
-
-db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))
-
-db_ET_MPo$condition_label <- ifelse(db_ET_MPo$condition==1, "Correct", "Mispronunciation")
-
-p <- ggplot(db_ET_MPo, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-    facet_grid(.~distractor_overlap)+
+p.DIOV_AGE <- ggplot(db_ET_MPo, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
+    facet_grid(.~distractor_label)+
   geom_point(aes(size = weights_g),show.legend=FALSE) +
+  labs(caption="b")+
   geom_line(y= 0, linetype="dotted") + 
@@
 
-p
-
-  jpeg(filename = "figures/Figure_6_Distractor_overlap_age.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
+lay <- rbind(c(1), c(2))
+
+  jpeg(filename = "figures/Figure_5_Distractor_overlap_age.jpg", 
+       width = 500, height = 600, units = "px")
+
+ger.plot.age <- grid.arrange(p.DIOV_M, p.DIOV_AGE,
+                             layout_matrix = lay)
 
@@
 
+sum_eff2 <- coef(summary(rma_Location_MP))[2,]
+
 db_ET_MPl = dat %>%
@@
 
-sum_eff <- coef(summary(rma_LocationCondition))[4,]
-
-```
-
-Regarding object identification in response to mispronunciations, when mispronunciation location was included as a moderator, the moderator test was not significant QM(`r r2(rma_Location_MP$m)`) = `r r2(rma_Location_MP$QM)`, *p* `r psig(rma_Location_MP$QMp)`.
+sum_eff2 <- coef(summary(rma_LocationCondition))[4,]
+
+```
+
+Regarding object identification in response to mispronunciations, when mispronunciation location was included as a moderator, the moderator test was not significant `r mod_test(rma_Location_MP)` and the estimate for distractor overlap was small, $\beta$`r full_estimate(sum_eff1)`.
 This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was located on the onset or  medial phonemes.
@@
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_LocationCondition$m)`) = `r r2(rma_LocationCondition$QM)`, *p* `r psig(rma_LocationCondition$QMp)`, but the interaction between mispronunciation location and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
+The moderator test was significant, `r mod_test(rma_LocationCondition)`, but the estimate for the interaction between mispronunciation location and condition was small and not significant, $\beta$`r full_estimate(sum_eff2)`.
 These results suggest that overall, the location of the mispronunciation (onset, medial) did not impact mispronunciation sensitivity.
@@
 
-#dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial" |
-#                mispron_location == "offset")
-
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
-
-dat.p = dat %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-dat.p$mispron_location <- factor(dat.p$mispron_location, levels = c("onset", "medial"))
-
-p <- ggplot(dat.p, aes(condition_label, g_calc, fill = condition_label)) + 
-  facet_grid(.~mispron_location)+
-  geom_boxplot() + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_7_Mispronunciation_position.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
+# #dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial" |
+# #                mispron_location == "offset")
+# 
+# dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
+# 
+# dat.p = dat %>%
+#   filter(mispron_location == "onset"  | mispron_location == "medial")
+# 
+# dat.p$mispron_location <- factor(dat.p$mispron_location, levels = c("onset", "medial"))
+# 
+# 
+# p <- ggplot(dat.p, aes(condition_label, g_calc, fill = condition_label)) + 
+#   facet_grid(.~mispron_location)+
+#   geom_boxplot() + 
+#   #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+#   scale_fill_manual(values=cbPalette)+
+#   apatheme +
+#   theme(text = element_text(size=25),
+#         legend.title = element_blank(),
+#         legend.position = "bottom",
+#         axis.title.x = element_blank(),
+#         axis.text.x = element_blank(),
+#         axis.ticks.x = element_blank()) + 
+#   #xlab("Number of Features Changed") + 
+#   geom_hline(yintercept = 0, linetype="dotted") + 
+#   ylab("Effect size Hedges' g")
+# 
+# p
+# 
+#   jpeg(filename = "figures/Figure_7_Mispronunciation_position.jpg", 
+#        width = 500, height = 300, units = "px")
+# 
+#   p
+#   
+#   dev.off()
 
@@
 
+sum_eff1 <- coef(summary(rma_Location_MP_age))[4,]
+
 db_ET_MPl = dat %>%
@@
 
-sum_eff <- coef(summary(rma_LocationCondition))[8,]
-
-```
-
-Although we did not have any specific predictions about the relationship between infant age and the impact of mispronuncition location on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
-First, for object recognition in response to mispronunciations, when age in addition to mispronunciation location was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_Location_MP_age$m)`) = `r r2(rma_Location_MP_age$QM)`, *p* `r psig(rma_Location_MP_age$QMp)`, suggesting that upon hearing a mispronunciation, infants looks to the target image were similar for both onset and medial mispronunciations, regardless of infant age.
+sum_eff2 <- coef(summary(rma_LocationCondition))[8,]
+
+```
+
+According to TRACE, infants should become more sensitive to onset mispronunciations as their lexicon size grows, but sensitivity to medial mispronunciations should stay the same (Mayor & Plunkett, 2014).
+To examine this relationship, we included age as a moderator.
+First, for object recognition in response to mispronunciations, when age in addition to mispronunciation location was also included as a moderator, the moderator test was not significant, `r mod_test(rma_Location_MP)` and the estimate for the interaction between distractor overlap and age was small, $\beta$`r full_estimate(sum_eff1)`.
+This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for both onset and medial mispronunciations, regardless of infant age.
 We next assessed whether the relationship between mispronunciation location and mispronunciation sensitivity was modulated by age.
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_LocationCondition_age$m)`) = `r r2(rma_LocationCondition_age$QM)`, *p* `r psig(rma_LocationCondition_age$QMp)`, but the interaction between mispronunciation location, age, and condition was not significant $\beta$ = `r r2(sum_eff$estimate)`, (SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
+The moderator test was significant, `r mod_test(rma_LocationCondition)`, but the estimate for the three-way interaction between mispronunciation loction, condition, and age was small and not significant, $\beta$`r full_estimate(sum_eff2)`.
 These results provide further evidence that location of the mispronunciation (onset, medial) did not impact mispronunciation sensitivity.
+
+```{r MispLocationAgeRangeSubset}
+
+misp_location_ages <- dat %>%
+  group_by(mispron_location) %>%
+  summarize(min_age = r2(min(mean_age_1, na.rm=TRUE)),
+            max_age = r2(max(mean_age_1, na.rm=TRUE)),
+            mean_age = r2(mean(mean_age_1, na.rm=TRUE)),
+            sd_age = r2(sd(mean_age_1, na.rm=TRUE)))
+
+fn <- subset(dat, mispron_location=="onset")
+
+ff <- subset(dat, mispron_location=="medial")
+
+age_misp_location <- t.test(fn$mean_age_1, ff$mean_age_1, paired = F)
+
+#t.test(fn$mean_age_1, ff$mean_age_1)
+
+mla <- as.data.frame(misp_location_ages)
+mla <- subset(mla, mispron_location == "onset"  | mispron_location == "medial")
+min_age <- max(mla$min_age)
+max_age <- min(mla$max_age)
+
+dat_age_MP= db_ET_MP%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+dat_age_MP = dat_age_MP %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
+
+dat_age_MP$mispron_location <- factor(dat_age_MP$mispron_location, levels = c("onset", "medial"))
+
+rma_Location_MP_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(mispron_location), data = dat_age_MP, random = ~ collapse | short_cite)
+
+misp_recog_agesub <- coef(summary(rma_Location_MP_agesub))[1,]
+
+rma_LocationAge_agesub <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(mispron_location), data = dat_age_MP, random = ~ collapse | short_cite)
+
+#summary(rma_Location_MP)
+
+misp_MS_agesub <- coef(summary(rma_LocationAge_agesub))[4,]
+
+# misp sensitivity
+dat_age= dat%>%
+  filter(mean_age_1>=min_age&mean_age_1<=max_age)
+
+dat_age = dat_age %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial")
+
+dat_age$mispron_location <- factor(dat_age$mispron_location, levels = c("onset", "medial"))
+
+rma_Location_MS_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(mispron_location)*condition, data = dat_age, random = ~ collapse | short_cite)
+
+misp_recog_Age_agesub <- coef(summary(rma_Location_MS_agesub))[4,]
+
+rma_LocationAgeMS_agesub <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(mispron_location), data = dat_age, random = ~ collapse | short_cite)
+
+misp_MS_Age_agesub <- coef(summary(rma_LocationAgeMS_agesub))[8,]
+
+#summary(rma_Distractor_MS)  
+```
+
+Although we anticipated that older children may be more impacted by the position of a mispronunciation, we found no relationship.
+Inspection of the ages tested using on onset and medial mispronunciations, however, revealed differences.
+Infants tested on onset mispronunciations were older (*M* = `r with(misp_location_ages, mean_age[mispron_location == "onset"])` days, *SD* = `r with(misp_location_ages, sd_age[mispron_location == "onset"])`, range = `r with(misp_location_ages, min_age[mispron_location == "onset"])` - `r with(misp_location_ages, max_age[mispron_location == "onset"])`) than those infants tested on medial mispronunciations (*M* = `r with(misp_location_ages, mean_age[mispron_location == "medial"])` days, *SD* = `r with(misp_location_ages, sd_age[mispron_location == "medial"])`, range = `r with(misp_location_ages, min_age[mispron_location == "medial"])` - `r with(misp_location_ages, max_age[mispron_location == "medial"])`), which a two-sample t-test revealed to be a significant difference, *t*(`r r2(age_misp_location$parameter)`) = `r r2(age_misp_location$statistic)`, *p* `r psig(age_misp_location$p.value)`).
+
+To ensure that the lack of a difference wasn't due to the ages of infants tested with onset and medial mispronunciations, we repeated the previous model analyses on a subset of papers that tested infants at ages where onset and medial mispronunciations were tested (`r min_age` - `r max_age` days).
+The analyses on this subset of data did not differ from that of the analyses conducted on the entire data set.
+
+[Katie: ultimately, the subset analysis doesn't show anything :( What conclusions can we draw?]
 
@@
 
+sum_eff1 <- coef(summary(rma_TypeFeaturesMP))[2,]
+
 # C vs. V with condition
@@
 
-sum_eff1 <- coef(summary(rma_TypeFeaturesMP_Condition))[4,]
+sum_eff2 <- coef(summary(rma_TypeFeaturesMP_Condition))[4,]
 
@@
 We first analyzed experimental conditions where mispronunciation type was either a consonant or vowel.
-Regarding object identification in response to mispronunciations, when mispronunciation type was included as a moderator, the moderator test was not significant QM(`r r2(rma_TypeFeaturesMP$m)`) = `r r2(rma_TypeFeaturesMP$QM)`, *p* `r psig(rma_TypeFeaturesMP$QMp)`.
+Regarding object identification in response to mispronunciations, when mispronunciation type was included as a moderator, the moderator test was not significant, `r mod_test(rma_Location_MP)` and the estimate for mispronunciation type was small, $\beta$`r full_estimate(sum_eff1)`.
 This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was a consonant or a vowel.
@@
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, *p* `r psig(rma_TypeFeaturesMP_Condition$QMp)`, but the interaction between mispronunciation type and condition was not significant $\beta$ = `r r2(sum_eff1$estimate)`, (SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`).
+The moderator test was significant, `r mod_test(rma_LocationCondition)`, but the estimate for the interaction between mispronunciation type and condition was small and not significant, $\beta$`r full_estimate(sum_eff2)`.
 These results suggest that overall, the type of  mispronunciation (consonant vs.
@@
 
+sum_eff1 <- coef(summary(rma_TypeFeaturesMPage))[4,]
+
 # with condition
@@
 
-sum_eff <- coef(summary(rma_TypeFeaturesMP_Condition))[8,]
+sum_eff2 <- coef(summary(rma_TypeFeaturesMP_Condition))[8,]
 
@@
 We next examined whether age modulates object recognition or mispronunciation sensitivity when the mispronunciation is a consonant or vowel.
-For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_TypeFeaturesMPage$m)`) = `r r2(rma_TypeFeaturesMPage$QM)`, *p* `r psig(rma_TypeFeaturesMPage$QMp)`.
+For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant, `r mod_test(rma_TypeFeaturesMPage)` and the estimate for the interaction between mispronunciation type and age was small, $\beta$`r full_estimate(sum_eff1)`.
 This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was on a consonant or vowel phoneme, regardless of their age.
@@
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, *p* `r psig(rma_TypeFeaturesMP_Condition$QMp)`.
-The interaction between mispronunciation type, condition, and age was significant ($\beta$ = `r r2(sum_eff$estimate)`, SE = `r r2(sum_eff$se)`, 95% CI [`r r2(sum_eff$ci.lb)`, `r r2(sum_eff$ci.ub)`], *p* `r psig(sum_eff$pval)`).
-As can be seen in Figure X, as infants age, mispronunciation sensitivity grows larger for vowel mispronunciations but becomes smaller for consonant mispronunciations.
+The moderator test was significant, `r mod_test(rma_LocationCondition)`, and the estimate for the three-way interaction between mispronunciation type, condition, and age was small, but significant, $\beta$`r full_estimate(sum_eff2)`.
+As can be seen in Figure 6, as infants age, mispronunciation sensitivity grows larger for vowel mispronunciations but becomes smaller for consonant mispronunciations.
 Noticeably, mispronunciation sensitivity appears greater for consonant compared to vowel mispronunciations at younger ages, but this difference shifts as infants age.
+
+## Figure 6
 
@@
 
-  jpeg(filename = "figures/Figure_8_FeatureType_Cond_Age.jpg", 
+  jpeg(filename = "figures/Figure_6_FeatureType_Cond_Age.jpg", 
        width = 500, height = 300, units = "px")
@@
 
+sum_eff1 <- coef(summary(rma_TypeFeaturesMPfam))[4,]
+
 # with condition
@@
 
-sum_eff1 <- coef(summary(rma_TypeFeaturesMPC))[7,]
-sum_eff2 <- coef(summary(rma_TypeFeaturesMPC))[8,]
+sum_eff2 <- coef(summary(rma_TypeFeaturesMPC))[7,]
+sum_eff3 <- coef(summary(rma_TypeFeaturesMPC))[8,]
 
@@
 bilinguals; *n* = `r with(lang_family, count[native_lang == "Catalan-Spanish"])`), and Swiss French (*n* = `r with(lang_family, count[native_lang == "Swiss French"])`) were classified into the Romance language family (*n* = `r with(family, count[lang_family == "Romance"])`).
-For object recognition in response to a mispronunciation, including language family as a moderator resulted in a moderator test that was not significant, QM(`r r2(rma_TypeFeaturesMPfam$m)`) = `r r2(rma_TypeFeaturesMPfam$QM)`, *p* `r psig(rma_TypeFeaturesMPfam$QMp)`.
+
+For object recognition in response to a mispronunciation, including language family as a moderator resulted in a moderator test that was not significant, `r mod_test(rma_TypeFeaturesMPage)`, and the estimate for the interaction between mispronunciation type and language family was small, $\beta$`r full_estimate(sum_eff1)`.
 This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was on a consonant or vowel phoneme, regardless of the language family of their native language.
@@
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family as additional moderators.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMPC$m)`) = `r r2(rma_TypeFeaturesMPC$QM)`, *p* `r psig(rma_TypeFeaturesMPC$QMp)`.
-The interaction between condition and language family was significant ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`), suggesting XXXXXXXXXXXXXX.
-The interaction between mispronunciation type, condition, and language family was also significant ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], *p* `r psig(sum_eff2$pval)`).
-As can be seen in Figure X, mispronunciation sensitivity for consonants was similar for Germanic and Romance languages.
+The moderator test was significant, `r mod_test(rma_TypeFeaturesMPage)`, and the estimate for the three-way interaction between mispronunciation type, condition, language family was large and significant , $\beta$`r full_estimate(sum_eff3)`.
+As can be seen in Figure 7, mispronunciation sensitivity for consonants was similar for Germanic and Romance languages.
 Mispronunciation sensitivity for vowels, however, was greater for Germanic compared to Romance languages.
 
-[KATIE] I'M NOT REALLY SURE WHAT THE CONDITION BY LANGUAGE FAMILY INTERACTION MEANS. SHOULD WE EVEN INTERPRET IT?
+[KATIE] I'M NOT REALLY SURE WHAT THE CONDITION BY LANGUAGE FAMILY INTERACTION MEANS. SHOULD WE EVEN INTERPRET IT? MAYBE THAT THE ROMANCE LANGUAGE FAMILY HAD LOWER MISPRONUNCIATION SENSITIVITY?
+
+## Figure 7
 
@@
 p <- ggplot(dat_type_sub, aes(condition_label, g_calc, fill = condition_label)) + 
-  geom_boxplot() + 
   facet_grid(.~type_feature*lang_family)+
+    geom_violin() + 
+  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
   #geom_line(y= 0, linetype="dotted") + 
@@
 
- jpeg(filename = "figures/Figure_9_FeatureType_Cond_LangFam.jpg", 
+ jpeg(filename = "figures/Figure_7_FeatureType_Cond_LangFam.jpg", 
        width = 500, height = 300, units = "px")
@@
 
- sum_eff1 <- coef(summary(rma_TypeFeaturesMPC))[8,]
+ sum_eff1 <- coef(summary(rma_TypeFeaturesMPfam))[8,]
 
@@
 
-rma_TypeFeaturesMPC <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family, data = db_type, random = ~collapse | short_cite)
-
-sum_eff1 <- coef(summary(rma_TypeFeaturesMPC))[7,]
-sum_eff2 <- coef(summary(rma_TypeFeaturesMPC))[8,]
+rma_TypeFeaturesMPC <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family*age.C, data = db_type, random = ~collapse | short_cite)
+
+sum_eff2 <- coef(summary(rma_TypeFeaturesMPC))[7,]
+sum_eff3 <- coef(summary(rma_TypeFeaturesMPC))[8,]
 
@@
 Finally, we examined the relationship between language family and infant age and mispronunciation sensitivity to consonants and vowels.
-For object recognition in response to a mispronunciation, including language family and infant age as a moderator resulted in a moderator test that was significant, QM(`r r2(rma_TypeFeaturesMPfam$m)`) = `r r2(rma_TypeFeaturesMPfam$QM)`, *p* `r psig(rma_TypeFeaturesMPfam$QMp)`.
-The interaction between language family, age, and type of mispronunciation (consonant or vowel) was significant, ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`).
-As can be seen in Figure X, for infants learning Germanic languages, increasing age was related to increasing mispronunciation sensitivity for vowel mispronunciations, but decreasing sensitivity for consonant mispronunciations.
+For object recognition in response to a mispronunciation, including language family and infant age as a moderator resulted in a moderator test that was significant, `r mod_test(rma_TypeFeaturesMPage)`, and the estimate for the three-way interaction between mispronunciation type, language family, and age was small, but significant , $\beta$`r full_estimate(sum_eff3)`.
+As can be seen in Figure 8, looks to the target in response to a mispronunciation increased with age for infants learning a Germanic language, regardless of whether those mispronunciations were consonants or vowels.
+In contrast, infants learning Romance languages have an even greater increase with age in target looks in response to consonant mispronunciations, but there was no change with age for vowel mispronunciations.
+We next assessed whether the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity was modulated by language family and age.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family and age as additional moderators.
+The moderator test was significant, `r mod_test(rma_TypeFeaturesMPC)`, and the estimate for the four-way interaction between mispronunciation type, condition, language family, and age was small, but significant , $\beta$`r full_estimate(sum_eff3)`.
+As can also be seen in Figure 8, for infants learning Germanic languages, increasing age was related to increasing mispronunciation sensitivity for vowel mispronunciations, but decreasing sensitivity for consonant mispronunciations.
 In contrast, infants learning Romance languages have an even greater increase with age in sensitivity to vowel mispronunciations.
@@
 
-[KATIE] AGAIN, THERE ARE ADDITIONAL INTERACTIONS THAT ARE SIGNIFICANT... SHOULD THEY BE INTERPRETED? ALSO, WTF ROMANCE LANGUAGES?
+[KATIE] AGAIN, THERE ARE ADDITIONAL INTERACTIONS THAT ARE SIGNIFICANT... SHOULD THEY BE INTERPRETED? ALSO, WTF ROMANCE LANGUAGES? IS IT JUST NOT ENOUGH DATA?
+
+## Figure 8
 
@@
 
-  jpeg(filename = "figures/Figure_10_FeatureType_Cond_Age_LangFam.jpg", 
+  jpeg(filename = "figures/Figure_8_FeatureType_Cond_Age_LangFam.jpg", 
        width = 500, height = 300, units = "px")
@@
 
-[KATIE] WORTH IT TO INCLUDE LANGUAGE FAMILY ANALYSES TOO?
+[KATIE] WORTH IT TO INCLUDE LANGUAGE FAMILY ANALYSES TOO? I'M THINKING NO
 
@@
   + Not really sure, check the results. A key interaction is significant in one model but not the other.
-  + Again, ages not matched very well for the two groups here. Decide about whether to include a age subset analysis
+  + Again, ages not matched very well for the two groups here. Similar pattern of results for age subset analysis.
 
@@
   + this is rather the opposite of what one would expect, right?
-  + mispronunciation sensitivity was smaller when the distractor image shared the same onset phoneme as the target image compared to when the distractor image was an unfamiliar object
+  + [Katie: Yeah! Its really strange, so the time course analysis suggestion of yours is a very good one!]
   + Maybe it would be useful to have time course analyses to address this issue further
   + As infants aged, overall recognition (regardless of condition) increased for target-distractor pairs containing onset overlap, whereas overall recognition decreased for target-distractor pairs containing no overlap.
-  + mispronunciation sensitivity for target words paired with unfamiliar distractors decreased with age, while it remained steady across a similar range of ages for target words paired with distractors containing onset overlap with the target word.
 

### 2018-10-25 Paper_Analyses.tex
update 24.10.2018
better model interpretation
vocabulary summary
choosing figures to include

@@
 
-\begin{tabular}{l|r|r}
-\hline
-Publication Type & \# Items & \# Effect Sizes\\
-\hline
-dissertation & 2 & 17\\
-\hline
-gray paper & 2 & 14\\
-\hline
-paper & 27 & 216\\
-\hline
-proceedings & 1 & 4\\
-\hline
-\end{tabular}
-
 \subsection{Data Entry}\label{data-entry}
@@
 \subsection{Data analysis}\label{data-analysis}
-
-\begin{tabular}{l|r|r}
-\hline
-Type of comparison & \# Papers & \# Effect Size\\
-\hline
-post-naming compared to pre-naming phase & 10 & 29\\
-\hline
-post-naming phase compared with chance (=50\%) & 9 & 23\\
-\hline
-post-pre difference score compared with chance (=0) & 13 & 52\\
-\hline
-\end{tabular}
 
@@
 We calculated Hedges' \emph{g} using the raw means and standard
-deviations reported in the paper (\emph{n} = 25) or using reported
-t-values (\emph{n} = 9). Raw means and standard deviations were
+deviations reported in the paper (\emph{n} = 2) or using reported
+t-values (\emph{n} = 2). Raw means and standard deviations were
 extracted from figures for 3 papers. In a within-participation design,
@@
 whole? In general, some of the Methods was written before the CogSci
-paper and in other places to flesh things out I rewrote what we had. Its
-definitely giving the same information and sometimes the wording is
-close, because there's not too many different ways to explain what a
-funnel plot is :){]}
+paper and in other places to flesh things out I rewrote what we had in
+the CogSci paper. Its definitely giving the same information and
+sometimes the wording is close, because there's not too many different
+ways to explain what a funnel plot is :){]}
 
@@
 reasonable! We had just listed everything 7 paragraphs before, which
-doesn't seem like a lot of \enquote{space}.{]}
+doesn't seem like a lot of \enquote{space}. Alternatively, this
+information could be listed in a table, and then just referred to.{]}
 
@@
 
-{[}CHRISTINA: If we want to interpret here, how about the next
-bit.{]}{[}KATIE: YES! This is an excellent point!!!{]}
-
 The stronger publication bias for correct pronunciation might reflect
@@
 
-{[}CHRISTINA: CAn you add the stats for the non-sig results?{]}{[}KATIE:
-Are there stats that can be computed on the non-sig results? Or do you
-just want an n for significant and non-significant studies?{]}
-
 Taken together, the results suggest a tendency in the literature towards
@@
 words. The variance-weighted meta-analytic effect size Hedges' \emph{g}
-was 0.91 (SE = 0.12) which was significantly different from zero (95\%
-CI {[}0.67, 1.14{]}, \emph{p} \textless{} .001). This is a rather large
+was 0.908 (SE = 0.12) which was significantly different from zero (95\%
+CI{[}0.673, 1.143{]}, \emph{p} \textless{} .001). This is a rather large
 effect size (according to the criteria set by Cohen, 1988; see also
@@
 {[}CHRISTINA: Can you explain what the CI lower bound means here? I
-don't follow.{]}{[}KATIE: What do you think about this? The CI lower
-bound stuff here actually comes from something you wrote, so tell me
-whether its correct.{]}
+don't follow.{]}{[}KATIE: What do you think about this (last sentence)?
+The CI lower bound stuff here actually comes from something you wrote,
+so tell me whether its correct.{]}
 
@@
 meta-analytic effect size Hedges' \emph{g} was 0.25 (SE = 0.06) which
-was also significantly different from zero (95\% CI {[}0.13, 0.37{]},
+was also significantly different from zero (95\% CI{[}0.133, 0.367{]},
 \emph{p} \textless{} .001). This is considered a small effect size
@@
 pronunciations with mispronunciations directly, merging the two
-datasets. The moderator test was significant, QM(1) = 215.76, \emph{p}
-\textless{} .001. Hedges' \emph{g} for mispronunciation sensitivity was
-0.50 (SE = 0.03), which indicated that the responses across conditions
-were significantly different (95\% CI {[}0.43, 0.56{]}, \emph{p}
-\textless{} .001). This confirms that although infants fixate the
-correct object for both correct pronunciations and mispronunciations,
-the observed fixations to target (as measured by the effect sizes) were
-significantly greater for correct pronunciations. In other words, we
-observe a significant difference between the two conditions and can now
-quantify the modulation of fixation behavior in terms of standardized
-effect sizes.
+datasets. The moderator test was significant, QM(1) = 215.761,
+\emph{p}\textless{} .001. Hedges' \emph{g} for mispronunciation
+sensitivity was 0.495 (SE = 0.034), which indicated that the responses
+across conditions were significantly different (95\% CI{[}0.429,
+0.561{]}, \emph{p} \textless{} .001). This confirms that although
+infants fixate the correct object for both correct pronunciations and
+mispronunciations, the observed fixations to target (as measured by the
+effect sizes) were significantly greater for correct pronunciations. In
+other words, we observe a significant difference between the two
+conditions and can now quantify the modulation of fixation behavior in
+terms of standardized effect sizes.
 
@@
 were either pronounced correctly or not. Age did not significantly
-modulate object identification in response to correctly pronounced
-(QM(1) = 0.68, \emph{p} = 0.41) or mispronounced words (QM(1) = 1.72,
-\emph{p} = 0.19). The lack of a significant modulation together with the
-small estimates indicates that there was no relationship between age and
-target looks in response to a correctly pronounced or mispronounced
-label. This relationship is plotted in Figure 2.
-
-{[}CHRISTINA{]} CAN YOU ADD ESTIMATES AND THEIR CIS?? Ideally everywhere
-where you report a p-value {[}KATIE: Do you know how to calculate
-Estimates and CIs for the Test of Moderators? Or do you mean reporting
-the estimates and CIs even when the moderator test is not
-significant?{]}
+modulate object identification in response to correctly pronounced QM(1)
+= 215.761, \emph{p}\textless{} .001 or mispronounce words QM(1) =
+215.761, \emph{p}\textless{} .001. The lack of a significant modulation
+together with the small estimates indicates that there was no
+relationship between age and target looks in response to a correctly
+pronounced or mispronounced label. This relationship is plotted in
+Figure 2.
 
@@
 sensitivity (correct vs.~mispronounced words) in our whole dataset. The
-moderator test was significant (QM(3) = 218.62, \emph{p} \textless{}
-.001). This result is in line with the general observation that as
+moderator test was significant QM(1) = 215.761, \emph{p}\textless{}
+.001. This result is in line with the general observation that as
 infants mature they become better at language processing. The
 interaction between age and mispronunciation sensitivity, however, was
-not significant \(\beta\) = 0.00, (SE = 0.01, 95\% CI {[}-0.01, 0.02{]},
-\emph{p} = 0.731), suggesting that as infants age, their
+not significant \(\beta\) = 0.003, SE = 0.008, 95\% CI{[}-0.012,
+0.018{]}, \emph{p}= 0.731. The small estimate size, as well as
+inspection of Figure 2 suggests that as infants age, their
 mispronunciation sensitivity remains the same.
@@
 papers; production = 1) analyzed the relationship between vocabulary
-scores and mispronunciation sensitivity. There is reason to believe that
-production data are different from comprehension data (the former being
-easier to estimate for parents in the typical questionnaire-based
-assessment), so we analyze this data separately.
-
-{[}KATIE{]} I DON'T KNOW HOW TO INTERPRET THESE RESULTS\ldots{} THE
-FIXED EFFECTS MODEL ISN'T SIGNIFICANT FOR ANY OF THESE. IS THAT
-MEANINGFUL? {[}CHRISTINA{]} SO WE DON'T WANT TO INTERPRET THE FIXED
-EFFECTS MODEL AT ALL, IT IS NOT SUITABLE BECAUSE THERE IS VARIANCE
-BETWEEN EVERY RECORD (LANGUAGE ETC). I WOULD INTERPRET THE OVERALL
-CORRELATION AND THE CI, NOT THE P-VALUE (IN GENERAL). I ALSO WONDER
-WHETHER WE SHOULD MOVE THE SUBSET ANALYSES TO THE SUPPLEMENTARY
-MATERIALS AND JUST SAY OVERALL WE SEE NO RELATIONSHIPS AND CORRELATION
-COEFFICIENTS CONSISTENYL BELOW .1 WE THEREFORE MUST CONCLUDE THAT WITHIN
-NARROW AGE GROUPS VOCABULARY DOES NOT INFLUENCE ANYTHING WE LOOK AT. WE
-CANNOT DO THIS ANALYSIS FPOR MP SENSITIVITY BECAUSE WE DON'T HAVE THE
-NECESSARY RAW DATA. {[}KATIE: Ah, so because for each paper the
-correlation and CI values straddle 0, this indicates that there really
-isn't much evidence for a relationship? I think it could make sense to
-add this to supplementary materials. Over the summer, I had also played
-around with looking at how collection of vocabulary data has dropped off
-over the years, even though more mispronunciation studies have been
-published. That might be something interesting to add. If we truly think
-that this is what is driving the development of mispronunciation
-sensitivity, then why are people not collecting this data?{]} (BUT I
-WONDER WHETHER WECOULD ENCODE THE REPORTED INTERACTION TERMS AND THE
-CORRELATION AND THEN DO SOMETHING WITH THAT?) {[}KATIE: I'm not really
-sure what you mean by this :({]}
-
-\begin{verbatim}
-##                                      COR            95%-CI %W(fixed)
-## Zesiger et al. (2012)             0.0610 [-0.3553; 0.4773]       5.8
-## Zesiger et al. (2012)            -0.1590 [-0.5663; 0.2483]       6.1
-## Mani, Coleman, & Plunkett (2008)  0.0300 [-0.2271; 0.2871]      15.2
-## Swingley & Aslin (2000)           0.1050 [-0.1564; 0.3664]      14.7
-## Mani & Plunkett 2007             -0.1700 [-0.5234; 0.1834]       8.0
-## Mani & Plunkett 2007             -0.1700 [-0.5175; 0.1775]       8.3
-## Swingley & Aslin (2002)           0.1410 [-0.2432; 0.5252]       6.8
-## Swingley & Aslin (2002)           0.1410 [-0.2596; 0.5416]       6.3
-## Swingley 2003                     0.3400 [ 0.0470; 0.6330]      11.7
-## Swingley 2003                     0.0600 [-0.3472; 0.4672]       6.1
-## Hojen et al.                      0.2220 [-0.2591; 0.7031]       4.3
-## Hojen et al.                      0.4820 [ 0.0935; 0.8705]       6.7
-##                                  %W(random)
-## Zesiger et al. (2012)                   6.2
-## Zesiger et al. (2012)                   6.5
-## Mani, Coleman, & Plunkett (2008)       13.7
-## Swingley & Aslin (2000)                13.4
-## Mani & Plunkett 2007                    8.3
-## Mani & Plunkett 2007                    8.5
-## Swingley & Aslin (2002)                 7.2
-## Swingley & Aslin (2002)                 6.7
-## Swingley 2003                          11.2
-## Swingley 2003                           6.5
-## Hojen et al.                            4.8
-## Hojen et al.                            7.0
-## 
-## Number of studies combined: k = 12
-## 
-##                         COR            95%-CI    z p-value
-## Fixed effect model   0.0897 [-0.0105; 0.1900] 1.75  0.0795
-## Random effects model 0.0893 [-0.0212; 0.1999] 1.58  0.1132
-## 
-## Quantifying heterogeneity:
-## tau^2 = 0.0060; H = 1.09 [1.00; 1.50]; I^2 = 15.7% [0.0%; 55.4%]
-## 
-## Test of heterogeneity:
-##      Q d.f. p-value
-##  13.05   11  0.2899
-## 
-## Details on meta-analytical method:
-## - Inverse variance method
-## - DerSimonian-Laird estimator for tau^2
-## - Untransformed correlations
-\end{verbatim}
-
-\begin{verbatim}
-##                                      COR            95%-CI %W(fixed)
-## Zesiger et al. (2012)            -0.0090 [-0.4268; 0.4088]       5.0
-## Zesiger et al. (2012)            -0.1720 [-0.5775; 0.2335]       5.3
-## Mani, Coleman, & Plunkett (2008)  0.0700 [-0.1861; 0.3261]      13.2
-## Mani & Plunkett 2007             -0.1100 [-0.4696; 0.2496]       6.7
-## Mani & Plunkett 2007             -0.1100 [-0.4635; 0.2435]       6.9
-## Swingley & Aslin (2002)           0.1820 [-0.1970; 0.5610]       6.0
-## Swingley & Aslin (2002)           0.1820 [-0.2131; 0.5771]       5.6
-## Swingley 2003                     0.1800 [-0.1406; 0.5006]       8.4
-## Swingley 2003                     0.0700 [-0.3367; 0.4767]       5.2
-## Ramon-Casas et al. 2009           0.0980 [-0.3068; 0.5028]       5.3
-## Ramon-Casas et al. 2009          -0.1470 [-0.5468; 0.2528]       5.4
-## Ramon-Casas et al. 2009          -0.2300 [-0.6171; 0.1571]       5.8
-## Ramon-Casas et al. 2009           0.2400 [-0.1451; 0.6251]       5.9
-## Ramon-Casas et al. 2009           0.4350 [ 0.1037; 0.7663]       7.9
-## Hojen et al.                      0.2220 [-0.2591; 0.7031]       3.7
-## Hojen et al.                     -0.1480 [-0.6430; 0.3470]       3.5
-##                                  %W(random)
-## Zesiger et al. (2012)                   5.0
-## Zesiger et al. (2012)                   5.3
-## Mani, Coleman, & Plunkett (2008)       13.2
-## Mani & Plunkett 2007                    6.7
-## Mani & Plunkett 2007                    6.9
-## Swingley & Aslin (2002)                 6.0
-## Swingley & Aslin (2002)                 5.6
-## Swingley 2003                           8.4
-## Swingley 2003                           5.2
-## Ramon-Casas et al. 2009                 5.3
-## Ramon-Casas et al. 2009                 5.4
-## Ramon-Casas et al. 2009                 5.8
-## Ramon-Casas et al. 2009                 5.9
-## Ramon-Casas et al. 2009                 7.9
-## Hojen et al.                            3.7
-## Hojen et al.                            3.5
-## 
-## Number of studies combined: k = 16
-## 
-##                         COR            95%-CI    z p-value
-## Fixed effect model   0.0601 [-0.0331; 0.1533] 1.26  0.2061
-## Random effects model 0.0601 [-0.0331; 0.1533] 1.26  0.2061
-## 
-## Quantifying heterogeneity:
-## tau^2 = 0; H = 1.00 [1.00; 1.42]; I^2 = 0.0% [0.0%; 50.7%]
-## 
-## Test of heterogeneity:
-##      Q d.f. p-value
-##  14.51   15  0.4870
-## 
-## Details on meta-analytical method:
-## - Inverse variance method
-## - DerSimonian-Laird estimator for tau^2
-## - Untransformed correlations
-\end{verbatim}
-
-\begin{verbatim}
-##                              COR             95%-CI %W(fixed) %W(random)
-## Bailey & Plunkett (2002)  0.0630 [-0.3441;  0.4701]       2.5        2.7
-## Bailey & Plunkett (2002) -0.0660 [-0.4729;  0.3409]       2.5        2.7
-## Bailey & Plunkett (2002)  0.0630 [-0.3441;  0.4701]       2.5        2.7
-## Bailey & Plunkett (2002) -0.0660 [-0.4729;  0.3409]       2.5        2.7
-## Bailey & Plunkett (2002)  0.0630 [-0.3441;  0.4701]       2.5        2.7
-## Bailey & Plunkett (2002) -0.0660 [-0.4729;  0.3409]       2.5        2.7
-## Bailey & Plunkett (2002)  0.0630 [-0.3441;  0.4701]       2.5        2.7
-## Bailey & Plunkett (2002) -0.0660 [-0.4729;  0.3409]       2.5        2.7
-## Swingley (2009)          -0.1200 [-0.3715;  0.1315]       6.4        5.6
-## Swingley (2009)           0.1300 [-0.1957;  0.4557]       3.8        3.8
-## Swingley & Aslin (2000)   0.4210 [ 0.2036;  0.6384]       8.6        6.7
-## Mani & Plunkett 2007     -0.0590 [-0.4349;  0.3169]       2.9        3.0
-## Mani & Plunkett 2007     -0.0590 [-0.4349;  0.3169]       2.9        3.0
-## Mani & Plunkett 2007     -0.1700 [-0.5234;  0.1834]       3.3        3.3
-## Mani & Plunkett 2007     -0.1700 [-0.5175;  0.1775]       3.4        3.4
-## Mani & Plunkett 2007      0.1000 [-0.2667;  0.4667]       3.0        3.2
-## Mani & Plunkett 2007     -0.2800 [-0.6214;  0.0614]       3.5        3.5
-## Mani & Plunkett 2007     -0.0700 [-0.3354;  0.1954]       5.8        5.2
-## Mani & Plunkett 2007      0.1000 [-0.1641;  0.3641]       5.8        5.2
-## Swingley & Aslin (2002)   0.1750 [-0.2050;  0.5550]       2.8        3.0
-## Swingley & Aslin (2002)   0.1750 [-0.2212;  0.5712]       2.6        2.8
-## Mani & Plunkett 2010     -0.3500 [-0.6640; -0.0360]       4.1        4.0
-## Swingley 2003             0.1500 [-0.1738;  0.4738]       3.9        3.8
-## Swingley 2003             0.1500 [-0.1738;  0.4738]       3.9        3.8
-## Swingley 2003             0.0600 [-0.3472;  0.4672]       2.4        2.7
-## Swingley 2003             0.0600 [-0.3472;  0.4672]       2.4        2.7
-## Hojen et al.             -0.0510 [-0.5557;  0.4537]       1.6        1.8
-## Hojen et al.              0.0510 [-0.4537;  0.5557]       1.6        1.8
-## Hojen et al.              0.0600 [-0.4442;  0.5642]       1.6        1.8
-## Hojen et al.             -0.0600 [-0.5642;  0.4442]       1.6        1.8
-## Tao et al. 2012           0.5700 [ 0.1710;  0.9690]       2.6        2.7
-## 
-## Number of studies combined: k = 31
-## 
-##                         COR            95%-CI    z p-value
-## Fixed effect model   0.0377 [-0.0260; 0.1014] 1.16  0.2465
-## Random effects model 0.0322 [-0.0399; 0.1043] 0.87  0.3818
-## 
-## Quantifying heterogeneity:
-## tau^2 = 0.0079; H = 1.11 [1.00; 1.39]; I^2 = 19.3% [0.0%; 48.4%]
-## 
-## Test of heterogeneity:
-##      Q d.f. p-value
-##  37.18   30  0.1719
-## 
-## Details on meta-analytical method:
-## - Inverse variance method
-## - DerSimonian-Laird estimator for tau^2
-## - Untransformed correlations
-\end{verbatim}
-
-\begin{verbatim}
-##                             COR             95%-CI %W(fixed) %W(random)
-## Swingley (2009)          0.0700 [-0.1839;  0.3239]       6.4        5.4
-## Swingley (2009)          0.1600 [-0.1628;  0.4828]       3.9        3.8
-## Mani & Plunkett 2007    -0.2820 [-0.6292;  0.0652]       3.4        3.4
-## Mani & Plunkett 2007    -0.2820 [-0.6292;  0.0652]       3.4        3.4
-## Mani & Plunkett 2007    -0.1100 [-0.4696;  0.2496]       3.2        3.3
-## Mani & Plunkett 2007    -0.1100 [-0.4635;  0.2435]       3.3        3.3
-## Mani & Plunkett 2007     0.2300 [-0.1208;  0.5808]       3.3        3.4
-## Mani & Plunkett 2007     0.2200 [-0.1325;  0.5725]       3.3        3.4
-## Mani & Plunkett 2007    -0.2700 [-0.5173; -0.0227]       6.7        5.5
-## Mani & Plunkett 2007    -0.0590 [-0.3248;  0.2068]       5.8        5.0
-## Swingley & Aslin (2002)  0.0290 [-0.3627;  0.4207]       2.7        2.8
-## Swingley & Aslin (2002)  0.0290 [-0.3793;  0.4373]       2.5        2.7
-## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
-## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
-## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
-## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
-## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
-## Swingley (2016)         -0.2690 [-0.6326;  0.0946]       3.1        3.2
-## Swingley 2003            0.1500 [-0.1738;  0.4738]       3.9        3.8
-## Swingley 2003            0.1500 [-0.1738;  0.4738]       3.9        3.8
-## Swingley 2003            0.0700 [-0.3367;  0.4767]       2.5        2.7
-## Swingley 2003            0.0700 [-0.3367;  0.4767]       2.5        2.7
-## Ramon-Casas et al. 2009  0.0980 [-0.3068;  0.5028]       2.5        2.7
-## Ramon-Casas et al. 2009 -0.1470 [-0.5468;  0.2528]       2.6        2.7
-## Ramon-Casas et al. 2009 -0.2300 [-0.6171;  0.1571]       2.7        2.9
-## Ramon-Casas et al. 2009  0.2400 [-0.1451;  0.6251]       2.8        2.9
-## Ramon-Casas et al. 2009  0.4350 [ 0.1037;  0.7663]       3.7        3.7
-## Hojen et al.            -0.0510 [-0.5557;  0.4537]       1.6        1.8
-## Hojen et al.             0.0510 [-0.4537;  0.5557]       1.6        1.8
-## Hojen et al.             0.0790 [-0.4239;  0.5819]       1.6        1.9
-## Hojen et al.            -0.0790 [-0.5819;  0.4239]       1.6        1.9
-## 
-## Number of studies combined: k = 31
-## 
-##                          COR            95%-CI     z p-value
-## Fixed effect model   -0.0402 [-0.1043; 0.0238] -1.23  0.2181
-## Random effects model -0.0393 [-0.1127; 0.0340] -1.05  0.2931
-## 
-## Quantifying heterogeneity:
-## tau^2 = 0.0094; H = 1.13 [1.00; 1.42]; I^2 = 22.0% [0.0%; 50.1%]
-## 
-## Test of heterogeneity:
-##      Q d.f. p-value
-##  38.45   30  0.1386
-## 
-## Details on meta-analytical method:
-## - Inverse variance method
-## - DerSimonian-Laird estimator for tau^2
-## - Untransformed correlations
-\end{verbatim}
+scores and mispronunciation sensitivity, specifically object recognition
+for correct pronunciations and mispronunciations. There is reason to
+believe that production data are different from comprehension data (the
+former being easier to estimate for parents in the typical
+questionnaire-based assessment), so we analyze this data separately.
+
+{[}CHRISTINA{]} SO WE DON'T WANT TO INTERPRET THE FIXED EFFECTS MODEL AT
+ALL, IT IS NOT SUITABLE BECAUSE THERE IS VARIANCE BETWEEN EVERY RECORD
+(LANGUAGE ETC). I WOULD INTERPRET THE OVERALL CORRELATION AND THE CI,
+NOT THE P-VALUE (IN GENERAL). I ALSO WONDER WHETHER WE SHOULD MOVE THE
+SUBSET ANALYSES TO THE SUPPLEMENTARY MATERIALS AND JUST SAY OVERALL WE
+SEE NO RELATIONSHIPS AND CORRELATION COEFFICIENTS CONSISTENYL BELOW .1
+WE THEREFORE MUST CONCLUDE THAT WITHIN NARROW AGE GROUPS VOCABULARY DOES
+NOT INFLUENCE ANYTHING WE LOOK AT. WE CANNOT DO THIS ANALYSIS FPOR MP
+SENSITIVITY BECAUSE WE DON'T HAVE THE NECESSARY RAW DATA. {[}KATIE: Ah,
+so because for each paper the correlation and CI values straddle 0, this
+indicates that there really isn't much evidence for a relationship? I've
+tried to write this out below, let me know what you think. Over the
+summer, I had also played around with looking at how collection of
+vocabulary data has dropped off over the years, even though more
+mispronunciation studies have been published. That might be something
+interesting to add. If we truly think that this is what is driving the
+development of mispronunciation sensitivity, then why are people not
+collecting this data?{]} (BUT I WONDER WHETHER WECOULD ENCODE THE
+REPORTED INTERACTION TERMS AND THE CORRELATION AND THEN DO SOMETHING
+WITH THAT?) {[}KATIE: I'm not really sure what you mean by this :({]}
+
+{[}Katie: below, I'm using coweeta.uga.edu/publications/10436.pdf, page
+80 as a model for writing up these results. I haven't the funniest clue
+what I'm doing! :p{]}
+
+We first considered the relationship between vocabulary and object
+recognition for correct pronunciations. Higher comprehension scores were
+associated with greater object recognition in response to correct
+pronunciations for 9 of 12 experimental conditions, with correlation
+values ranging from -0.17 to 0.48. The mean effect size XXX was 0.0897,
+but did not differ significantly from zero (95\% CI{[}-0.0105; 0.1900{]}
+\emph{p} = .0795). Higher production scores were also associated with
+greater object recognition in response to correct pronunciations for 9
+of 16 experimental conditions, with correlation values ranging from
+-0.23 to 0.44. The mean effect size XXX was 0.0601, but did not differ
+significantly from zero (95\% CI{[}-0.0331; 0.1533{]} \emph{p} = .2061).
+For both comprehension and production scores, the small correlation
+effect sizes and large variances suggest a lack of relationship between
+vocabulary and object recognition for correct pronunciations.
+
+We next considered the relationship between vocabulary and object
+recognition for mispronunciations. Higher comprehension scores were
+associated with greater object recognition in response to correct
+pronunciations for 17 of 31 experimental conditions, with correlation
+values ranging from -0.35 to 0.57. The mean effect size XXX was 0.0377,
+but did not differ significantly from zero (95\% CI{[}-0.0260; 0.1014{]}
+\emph{p} = .2465). For production, however, lower production scores were
+associated with greater object recognition in response to
+mispronunciations for 16 of 31 experimental conditions, with correlation
+values ranging from -0.28 to 0.44. The mean effect size XXX was -0.0402,
+but did not differ significantly from zero (95\% CI{[}-0.1043; 0.0238{]}
+\emph{p} = .2181). For both comprehension and production scores, the
+small correlation effect sizes and large variances suggest a lack of
+relationship between vocabulary and object recognition for
+mispronunciations.
 
@@
 (PRIMR ref) or decrease (Assim Model ref) in mispronunciation
-sensitivity.
-
-{[}KATIE{]} CAN A CONCLUSION BE DRAWN FROM THE VOCABULARY RESULTS? IF
-SO, THIS IS THE PARAGRAPH
-
-In sum, it seems that current theories of infants' phono-lexical
-development cannot fully capture our results and should be reconsidered
-with all the evidence in mind.
+sensitivity. Furthermore, counter to the predictions for the PRIMR
+(PRIMR ref) and Assimilation(Assim ref) models, we found no relationship
+between vocabulary and target looking for correct pronunciations or
+mispronunciations. In sum, it seems that current theories of infants'
+phono-lexical development cannot fully capture our results and should be
+reconsidered with all the evidence in mind.
 
@@
 sensitivity could be due to differences in the types of tasks given to
-infants of different ages. To examine this possibility, we include an
-exploratory analysis of whether different moderators and experimental
-design features were included at different ages, in addition to
-investigating the role that these moderators play in mispronunciation
-sensitivity.
+infants of different ages. In the following section, we investigate the
+role that different moderators play in mispronunciation sensitivity. To
+investigate the possibility of systematic differences in the tasks
+across ages, we additionally include an exploratory analysis of whether
+different moderators and experimental design features were included at
+different ages.
 
@@
 \emph{g} with number of features changed as a moderator. The moderator
-test was significant, QM(1) = 76.10, \emph{p} \textless{} .001. Hedges'
-\emph{g} for number of features changed was -0.12 (SE = 0.01), which
+test was significant, QM(1) = 215.761, \emph{p}\textless{} .001. Hedges'
+\emph{g} for number of features changed was -0.123 (SE = 0.014), which
 indicated that as the number of features changed increased, the effect
-size Hedges' \emph{g} significantly decreased (95\% CI {[}-0.15,
--0.10{]}, \emph{p} \textless{} .001). We plot this relationship in
-Figure X. This confirms previous findings of a graded sensitivity to the
+size Hedges' \emph{g} significantly decreased (95\% CI{[}-0.151,
+-0.096{]}, \emph{p} \textless{} .001). We plot this relationship in
+Figure 3. This confirms previous findings of a graded sensitivity to the
 number of features changed for both consonant (White \& Morgan, 2008)
@@
 experimental design.
+
+\subsection{Figure 3}\label{figure-3}
 
@@
 examine this relationship. When age was also included as a moderator,
-the moderator test was significant, QM(3) = 81.11, \emph{p} \textless{}
+the moderator test was significant, QM(1) = 215.761, \emph{p}\textless{}
 .001, but the interaction between age and number of features changed was
-not significant, \(\beta\) = 0.01, (SE = 0.00, 95\% CI {[}0, 0.01{]},
-\emph{p} = 0.069). This suggests that there is no relationship between
-infant age the impact of number of features changed on mispronunciation
-sensitivity.
+not significant, \(\beta\) = 0.006, SE = 0.003, 95\% CI{[}0, 0.011{]},
+\emph{p}= 0.069. The small effect size for the interaction between age
+and number of features changed suggests that the impact of number of
+features changed on mispronunciation sensitivity does not change with
+infant age.
 
@@
 2-feature mispronunciations, and 544.48 - 920.20 days (\emph{M} =
-661.64) for 3-feature mispronunciations. Focusing on the ages where all
-three numbers of features changed were tested (i.e.~544.48 - 920.20
-days), however, did not change the pattern of results.
+661.64) for 3-feature mispronunciations. The reader should note that
+experimental conditions in which the number of features changed in a
+mispronunciation was not specified or the number of features changed was
+not consistent (e.g., one mispronunciation included a 2-feature change
+whereas another only a 1-feature change) are not included in these
+totals. An analysis focusing on the ages where all three numbers of
+features changed were tested (i.e.~544.48 - 920.20 days), however, did
+not change the pattern of results.
 
@@
 familiar or an unfamiliar distractor image. The moderator test was not
-significant QM(1) = 0.43, \emph{p} = 0.513. This suggests that upon
-hearing a mispronunciation, infants looks to the target image were
+significant QM(1) = 215.761, \emph{p}\textless{} .001 and the estimate
+for distractor familiarity was relatively small, \(\beta\) = -0.082, SE
+= 0.126, 95\% CI{[}-0.329, 0.164{]}, \emph{p}= 0.513. This suggests that
+upon hearing a mispronunciation, infants' looks to the target image were
 similar for when the target image was paired with an image of a familiar
@@
 and included condition (correct pronunciation, mispronunciation) as an
-additional moderator. The moderator test was significant, QM(3) =
-219.46, \emph{p} \textless{} .001, but the interaction between
-distractor familiarity and condition was not significant \(\beta\) =
-0.14, (SE = 0.08, 95\% CI {[}-0.02, 0.30{]}, \emph{p} = 0.08). These
-results suggest that overall, infants' familiarity with the distractor
-object (familiar or unfamiliar) did not impact their mispronunciation
+additional moderator. The moderator test was significant, QM(1) =
+215.761, \emph{p}\textless{} .001, but the estimate for the interaction
+between distractor familiarity and condition was small and not
+significant \(\beta\) = 0.141, SE = 0.081, 95\% CI{[}-0.017, 0.299{]},
+\emph{p}= 0.08. This relationship is plotted in Figure 4. The results
+suggest that overall, infants' familiarity with the distractor object
+(familiar or unfamiliar) did not impact their mispronunciation
 sensitivity.
+
+\subsection{Figure 4}\label{figure-4}
 
@@
 mispronunciation sensitivity when the distractor image is familiar or
-unfamiliar. For object recognition in response to a mispronunciation,
-including age as a moderator resulted in a moderator test that was not
-significant, QM(3) = 3.25, \emph{p} = 0.355. {[}CHRISTINA{]} I WORRY A
-LOT AT THESE POINTS THAT THIS IS THE WHOLE P\textgreater{}.05 = NULL IS
-TRUE FALLACY. WE CAN NEVER HAVE EVIDENCE FOR THE NULL HYPOTHESIS. SO
-BETTER ITNERPRET ESTIMATES AND CIS.
-
-This suggests that upon hearing a mispronunciation, infants looks to the
-target image were similar for when the target image was paired with an
-image of a familiar or unfamiliar object, regardless of their age. We
-next assessed whether the relationship between distractor familiarity
-and mispronunciation sensitivity was modulated by age. We merged the two
-datasets and included condition (correct pronunciation,
-mispronunciation) as well as age as additional moderators. The moderator
-test was significant, QM(7) = 224.96, \emph{p} \textless{} .001.
-Although the three-way-interaction between condition, distractor
-familiarity, and age was not significant (\(\beta\) = -0.02, SE = 0.02,
-95\% CI {[}-0.06, 0.02{]}, \emph{p} = 0.305), here the interaction
-between condition and distractor familiarity was significant (\(\beta\)
-= 0.18, SE = 0.09, 95\% CI {[}0, 0.35{]}, \emph{p} = 0.05).
-
-{[}KATIE{]} WHAT DOES IT MEAN THAT IN THIS LAST TEST THERE WAS AN
-INTERACTION BETWEEN CONDITION AND DISTRACTOR FAMILIARITY, WHEN AGE WAS
-INCLUDED AS A MODERATOR? DOES THAT MEAN THAT AGE IS CONTROLLED FOR?
-UNDERSTANDING THIS WILL HELP ME FORMULATE THE CONCLUSION SENTENCE AND
-MOTIVATE THE NEXT SET OF ANALYSES.
-
-{[}CHRISTINA{]} I WOULD NOT OVERINTERPRET IT, THE ESTIMATE DID NOT
-DRAMATICALLY CHANGE, AND IT IS BARELY SIGNIFICANT. DOES THAT HELP?
-
-{[}KATIE: I think so. I've just removed that part{]}
-
-\begin{verbatim}
-##                       Test                            Results
-## 1 Welch Two Sample t-test: t(153.83) = 5.30, p < .001, d = NA
-\end{verbatim}
+unfamiliar. Based on previous results, we expected older infants to look
+less to the target in response to mispronunciations and to have greater
+mispronunciation sensitivity than younger infants when the distractor
+was unfamiliar compared to familiar. For object recognition in response
+to a mispronunciation, including age as a moderator resulted in a
+moderator test that was not significant QM(1) = 215.761,
+\emph{p}\textless{} .001, and a small estimate for the interaction
+between age and object recognition (\(\beta\) = -0.02, SE = 0.02, 95\%
+CI{[}-0.059, 0.018{]}, \emph{p}= 0.305. This suggests that upon hearing
+a mispronunciation, infant looks to the target image were similar for
+when the target image was paired with an image of a familiar or
+unfamiliar object, regardless of their age. We next assessed whether the
+relationship between distractor familiarity and mispronunciation
+sensitivity was modulated by age. We merged the two datasets and
+included condition (correct pronunciation, mispronunciation) as well as
+age as additional moderators. The moderator test was significant QM(1) =
+215.761, \emph{p}\textless{} .001. The estimate for the
+three-way-interaction between condition, distractor familiarity, and age
+was small and not significant (\(\beta\) = = -0.02, SE = 0.02, 95\%
+CI{[}-0.059, 0.018{]}, \emph{p}= 0.305. We note that in this model, the
+interaction between condition and distractor familiarity was significant
+(\(\beta\) = 0.175, SE = 0.089, 95\% CI{[}0, 0.351{]}, \emph{p}= 0.05,
+this estimate is similar to the original estimate specifically examining
+this interaction in a previous model. Taken together, these results
+suggest that regardless of age, mispronunciation sensitivity was similar
+whether the distractor image was familiar or unfamiliar.
 
@@
 distractors, however, revealed differences. Infants tested using a
-familiar distractor were younger (M = 588.76 days, SD = 136.47, range =
-207.8 - 768 days) than those infants tested using an unfamiliar
-distractor (M = 678.85 days, SD = 115.47, range = 544.48 - 920.2 days),
-which a two-sample t-test revealed to be a significant difference,
-t(153.83) = 5.30, p \textless{} .0001.
+familiar distractor were younger (\emph{M} = 588.76 days, \emph{SD} =
+136.47, range = 207.80 - 768) than those infants tested using an
+unfamiliar distractor (\emph{M} = 678.85 days, \emph{SD} = 115.47, range
+= 544.48 - 920.20), which a two-sample t-test revealed to be a
+significant difference, \emph{t}(153.83) = 5.30, \emph{p} \textless{}
+.001).
 
 {[}CHRISTINA{]} CAN YOU TURN THE NUMBERS INTO R CODE HERE? aLSO, NOT
-SURE WE NEED A T-TEST TO CONFIRM THE OBVIOUS.
-
-{[}KATIE{]} SO, IS IT OKAY TO DO THE AGE SUBSET ANALYSIS AFTER THIS?
-SOMETHING LIKE \enquote{TO ENSURE THAT THE LACK OF A DIFFERENCE WASN'T
-DUE TO THE DIFFERENCE IN AGES OF INFANTS TESTED WITH DIFFERENT TYPES OF
-DISTRACTORS, WE ANALYZED A SUBSET OF PAPERS THAT TESTED AGES WHERE BOTH
-FAMILIAR AND UNFAMILIAR DISTRACTORS WERE USED.} IN THE SUBSET ANALYSIS,
-FOR MISP SENSITIVITY, THERE IS A SIGNIFICANT INTERACTION BETWEEN
-DISTRACTOR FAMILIARITY AND CONDITION.
-
-{[}CHRISTINA{]} YES!!!!!!
+SURE WE NEED A T-TEST TO CONFIRM THE OBVIOUS. {[}Katie: Is the t-test
+okay?{]}
+
+To ensure that the lack of a difference wasn't due to the ages of
+infants tested with different types of distractors, we repeated the
+previous model analyses on a subset of papers that tested infants at
+ages where both familiar and unfamiliar distractors were used (544.48 -
+768 days). We first considered object recognition is response to a
+mispronunciation. Here, the pattern of results for the subset of infants
+was similar to that of the entire dataset; the moderator test was not
+significant QM(1) = 215.761, \emph{p}\textless{} .001 and the estimate
+for distractor familiarity was small, \(\beta\) = -0.19, SE = 0.15, 95\%
+CI{[}-0.48, 0.1{]}, \emph{p}= 0.21. However, it should be noted that
+although small, the effect size estimate for distractor familiarity
+doubled from \(\beta\)-0.08 in the entire dataset to \(\beta\)-0.19 in
+the subset. We next assessed the relationship between distractor
+familiarity and mispronunciation sensitivity. Similar to the analysis
+with the entire dataset, the moderator test was significant QM(1) =
+215.761, \emph{p}\textless{} .001. Unlike the analysis with the entire
+dataset, however, the estimate for the interaction between distractor
+familiarity and condition was significant \(\beta\) = 0.19, SE = 0.09,
+95\% CI{[}0.01, 0.36{]}, \emph{p}= 0.04, but small and similar to the
+estimate for this interaction in the full dataset \(\beta\) = 0.14.
+
+Although the age range is relatively small in the subset of infant ages
+tested with both familiar and unfamiliar distractors (7.34 months),
+these ages span the beginning of the vocabulary spurt. Considering
+infants' object looking behavior may be influenced by whether the label
+for the object is known (Schafer \& Plunkett, 1998), however, this age
+range may still be informative for understanding the role of distractor
+familiarity on mispronunciation sensitivity and whether this is
+modulated by age. Similar to the full dataset, however, including age as
+a moderator of object recognition in response to familiar and unfamiliar
+distractors resulted in a moderator test that was not significant QM(1)
+= 215.761, \emph{p}\textless{} .001, and a small estimate for the
+interaction between age and object recognition (\(\beta\) = 0.02, SE =
+0.05, 95\% CI{[}-0.07, 0.11{]}, \emph{p}= 0.6. Finally, we assessed
+whether the relationship between distractor familiarity and
+mispronunciation sensitivity was modulated by age in the subset of data.
+Again, similar to the full dataset, the moderator test was not
+significant QM(1) = 215.761, \emph{p}\textless{} .001 and the estimate
+for the three-way-interaction between condition, distractor familiarity,
+and age was small and not significant (\(\beta\) = = -0.07, SE = 0.04,
+95\% CI{[}-0.14, 0{]}, \emph{p}= 0.06.
+
+{[}Katie: ultimately, the subset analysis doesn't show anything :( What
+conclusions can we draw?{]}
 
@@
 response to mispronunciations and mispronunciation sensitivity when the
-target-distractor pairs either shared the same onset phoneme, had no
-overlap, or where the distractor was an unfamiliar object. We did not
-include data for which the overlap included both the onset and medial
-phonemes (\emph{n} = 4) or coda phonemes (\emph{n} = 3). The analysis
-was therefore based on a subset of the overall dataset, with 104
-experimental conditions containing onset phoneme overlap between the
-target and distractor, 80 containing no overlap between target and
-distractor, and 60 for targets paired with unfamiliar distractor images.
-There were therfore three possibilities for distractor overlap: onset
-phoneme overlap, no overlap, and an unfamiliar distractor. In our
-analysis, we were interested in the difference between overlap and lack
-of overlap; therefore, experimental conditions containing onset phoneme
-overlap were coded as the reference condition and compared with
-responses to experimental conditions with no overlap or an unfamiliar
-distractor separately.
-
-{[}KATIE{]} CAN YOU CHECK THE WAY THAT I WROTE THE LAST SENTENCE?
+target-distractor pairs either had no overlap or shared the same onset
+phoneme. We did not include data for which the overlap included both the
+onset and medial phonemes (\emph{n} = 4), coda phonemes (\emph{n} = 3),
+or for targets paired with an unfamiliar distractor image 60. The
+analysis was therefore based on a subset of the overall dataset, with
+104 experimental conditions containing onset phoneme overlap between the
+target and distractor and 80 containing no overlap between target and
+distractor.
 
@@
 
+{[}KATIE: I think we had talked about it and decided to include novel. I
+don't think it needs to be here necessarily, so I'll take it out,
+especially if its confusing.{]}
+
 Regarding object identification in response to mispronunciations, when
 distractor overlap was included as a moderator, the moderator test was
-not significant QM(2) = 1.78, \emph{p} = 0.412. {[}CHRISTINA{]} AGAIN DO
-NOT RELY ON P-VALUES BUT ON ESTIMATES AND CIS This suggests that upon
-hearing a mispronunciation, infants looks to the target image were
-similar for when the target image was paired with a distractor image
-that contained overlap on the onset phoneme or no overlap with the
+not significant QM(1) = 215.761, \emph{p}\textless{} .001 and the
+estimate for distractor overlap was relatively small, \(\beta\) = 0.138,
+SE = 0.15, 95\% CI{[}-0.157, 0.432{]}, \emph{p}= 0.359. This suggests
+that upon hearing a mispronunciation, infants looks to the target image
+were similar for when the target image was paired with a distractor
+image that contained overlap on the onset phoneme or no overlap with the
 target word, or was an unfamiliar object. We next assessed whether
@@
 pronunciation, mispronunciation) as an additional moderator. The
-moderator test was significant, QM(5) = 230.34, \emph{p} \textless{}
-.001. The interaction between condition and target-distractor pairs with
-no overlap was significant (\(\beta\) = -0.25, SE = 0.08, 95\% CI
-{[}-0.40, -0.10{]}, \emph{p} = 0.001), suggesting that mispronunciation
-sensitivity was greater when target-distractor pairs shared the same
-onset phoneme compared to when they shared no phonological overlap. The
-interaction between condition and target-distractor pairs with an
-unfamiliar distractor was also significant (\(\beta\) = 0.19, SE = 0.09,
-95\% CI {[}0.01, 0.37{]}, \emph{p} = 0.042), suggesting that
-mispronunciation sensitivity was smaller when the distractor image
-shared the same onset phoneme as the target image compared to when the
-distractor image was an unfamiliar object. This can be seen in Figure X.
-
-{[}christina{]} I THINK THESE SHOULD BE TWO SEPARATE ANALYSES\ldots{}
-NOVEL IS CONCEPTUALLY DIFFERENT.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotDistOverlapEffect-1.pdf}
-\caption{}
-\end{figure}
-
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
+moderator test was significant QM(1) = 215.761, \emph{p}\textless{}
+.001. The estimate for the interaction between condition and distractor
+overlap was small, but significant (\(\beta\) = -0.247, SE = 0.078, 95\%
+CI{[}-0.399, -0.096{]}, \emph{p}= 0.001, suggesting that
+mispronunciation sensitivity was greater when target-distractor pairs
+shared the same onset phoneme compared to when they shared no
+phonological overlap. This relationship be seen in Figure 5a.
 
@@
 mispronunciations, when age in addition to distractor overlap was also
-included as a moderator, the moderator test was not significant, QM(5) =
-5.99, \emph{p} = 0.308, suggesting that upon hearing a mispronunciation,
-infants looks to the target image were similar for the three types of
-overlap, regardless of infant age. We next assessed whether the
-relationship between distractor overlap and mispronunciation sensitivity
-was modulated by age. We merged the two datasets and included condition
-(correct pronunciation, mispronunciation) as well as age as additional
-moderators. The moderator test was significant, QM(11) = 243.40,
-\emph{p} \textless{} .001. The interaction between age, condition, and
-target-distractor pairs with no overlap was significant (\(\beta\) =
--0.04, SE = 0.02, 95\% CI {[}-0.08, 0.00{]}, \emph{p} = 0.032). As can
-be seen in Figure X, the difference between correct pronunciations and
+included as a moderator, the moderator test was not significant, QM(1) =
+215.761, \emph{p}\textless{} .001, and the estimate for the interaction
+between age and distractor overlap was small, \(\beta\) = 0.011, SE =
+0.033, 95\% CI{[}-0.054, 0.077{]}, \emph{p}= 0.733. This suggests that
+upon hearing a mispronunciation, infants looks to the target image were
+similar for both onset and no overlap, regardless of infant age. We next
+assessed whether the relationship between distractor overlap and
+mispronunciation sensitivity was modulated by age. We merged the two
+datasets and included condition (correct pronunciation,
+mispronunciation) as well as age as additional moderators. The moderator
+test was significant, QM(1) = 215.761, \emph{p}\textless{} .001 and the
+estimate for the three-way interaction between age, condition, and
+distractor overlap was significant, but relatively small (\(\beta\) = =
+-0.04, SE = 0.019, 95\% CI{[}-0.078, -0.003{]}, \emph{p}= 0.034. As can
+be seen in Figure 5b, the difference between correct pronunciations and
 mispronunciations (mispronunciation sensitivity) stays steady across
@@
 overlap, whereas for overall recognition decreased for target-distractor
-pairs containing no overlap. The interaction between age, condition, and
-target-distractor pairs with an unfamiliar distractor was also
-significant (\(\beta\) = -0.05, SE = 0.02, 95\% CI {[}-0.09, 0.00{]},
-\emph{p} = 0.038). As can also be seen in Figure X, mispronunciation
-sensitivity for target words paired with unfamiliar distractors
-decreased with age, while it remained steady across a similar range of
-ages for target words paired with distractors containing onset overlap
-with the target word.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotDistOverlap_cond_age-1.pdf}
-\caption{}
-\end{figure}
+pairs containing no overlap.
+
+\subsection{Figure 5}\label{figure-5}
 
@@
 mispronunciation location was included as a moderator, the moderator
-test was not significant QM(1) = 0.04, \emph{p} = 0.838. This suggests
-that upon hearing a mispronunciation, infants looks to the target image
-were similar for when the mispronunciation was located on the onset or
-medial phonemes. We next assessed whether mispronunciation location was
-related to mispronunciation sensitivity. We merged the two datasets and
-included condition (correct pronunciation, mispronunciation) as an
-additional moderator. The moderator test was significant, QM(3) =
-180.76, \emph{p} \textless{} .001, but the interaction between
-mispronunciation location and condition was not significant \(\beta\) =
-0.05, (SE = 0.09, 95\% CI {[}-0.12, 0.22{]}, \emph{p} = 0.559). These
-results suggest that overall, the location of the mispronunciation
-(onset, medial) did not impact mispronunciation sensitivity.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotPositionEffect-1.pdf}
-\caption{}
-\end{figure}
-
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
-Although we did not have any specific predictions about the relationship
-between infant age and the impact of mispronuncition location on
-mispronunciation sensitivity, we included an exploratory analysis to
-examine this relationship. First, for object recognition in response to
-mispronunciations, when age in addition to mispronunciation location was
-also included as a moderator, the moderator test was not significant,
-QM(3) = 1.22, \emph{p} = 0.747, suggesting that upon hearing a
-mispronunciation, infants looks to the target image were similar for
-both onset and medial mispronunciations, regardless of infant age. We
-next assessed whether the relationship between mispronunciation location
-and mispronunciation sensitivity was modulated by age. We merged the two
-datasets and included condition (correct pronunciation,
-mispronunciation) as well as age as additional moderators. The moderator
-test was significant, QM(7) = 185.34, \emph{p} \textless{} .001, but the
-interaction between mispronunciation location, age, and condition was
-not significant \(\beta\) = NA, (SE = NA, 95\% CI {[}NA, NA{]}, \emph{p}
-). These results provide further evidence that location of the
+test was not significant QM(1) = 215.761, \emph{p}\textless{} .001 and
+the estimate for distractor overlap was small, \(\beta\) = 0.011, SE =
+0.033, 95\% CI{[}-0.054, 0.077{]}, \emph{p}= 0.733. This suggests that
+upon hearing a mispronunciation, infants looks to the target image were
+similar for when the mispronunciation was located on the onset or medial
+phonemes. We next assessed whether mispronunciation location was related
+to mispronunciation sensitivity. We merged the two datasets and included
+condition (correct pronunciation, mispronunciation) as an additional
+moderator. The moderator test was significant, QM(1) = 215.761,
+\emph{p}\textless{} .001, but the estimate for the interaction between
+mispronunciation location and condition was small and not significant,
+\(\beta\) = 0.051, SE = 0.088, 95\% CI{[}-0.121, 0.224{]}, \emph{p}=
+0.559. These results suggest that overall, the location of the
 mispronunciation (onset, medial) did not impact mispronunciation
 sensitivity.
+
+According to TRACE, infants should become more sensitive to onset
+mispronunciations as their lexicon size grows, but sensitivity to medial
+mispronunciations should stay the same (Mayor \& Plunkett, 2014). To
+examine this relationship, we included age as a moderator. First, for
+object recognition in response to mispronunciations, when age in
+addition to mispronunciation location was also included as a moderator,
+the moderator test was not significant, QM(1) = 215.761,
+\emph{p}\textless{} .001 and the estimate for the interaction between
+distractor overlap and age was small, \(\beta\) = 0.018, SE = 0.034,
+95\% CI{[}-0.048, 0.084{]}, \emph{p}= 0.596. This suggests that upon
+hearing a mispronunciation, infants looks to the target image were
+similar for both onset and medial mispronunciations, regardless of
+infant age. We next assessed whether the relationship between
+mispronunciation location and mispronunciation sensitivity was modulated
+by age. We merged the two datasets and included condition (correct
+pronunciation, mispronunciation) as well as age as additional
+moderators. The moderator test was significant, QM(1) = 215.761,
+\emph{p}\textless{} .001, but the estimate for the three-way interaction
+between mispronunciation loction, condition, and age was small and not
+significant, \(\beta\) = NA, SE = NA, 95\% CI{[}NA, NA{]}, \emph{p}NA.
+These results provide further evidence that location of the
+mispronunciation (onset, medial) did not impact mispronunciation
+sensitivity.
+
+Although we anticipated that older children may be more impacted by the
+position of a mispronunciation, we found no relationship. Inspection of
+the ages tested using on onset and medial mispronunciations, however,
+revealed differences. Infants tested on onset mispronunciations were
+older (\emph{M} = 634.03 and NA days, \emph{SD} = 116.41 and NA, range =
+372.89 and NA - 920.20 and NA) than those infants tested on medial
+mispronunciations (\emph{M} = 584.16 and NA days, \emph{SD} = 107.49 and
+NA, range = 372.89 and NA - 766 and NA), which a two-sample t-test
+revealed to be a significant difference, \emph{t}(86.84) = 2.72,
+\emph{p} = 0.008).
+
+To ensure that the lack of a difference wasn't due to the ages of
+infants tested with onset and medial mispronunciations, we repeated the
+previous model analyses on a subset of papers that tested infants at
+ages where onset and medial mispronunciations were tested (372.89 - 766
+days). The analyses on this subset of data did not differ from that of
+the analyses conducted on the entire data set.
+
+{[}Katie: ultimately, the subset analysis doesn't show anything :( What
+conclusions can we draw?{]}
 
@@
 response to mispronunciations, when mispronunciation type was included
-as a moderator, the moderator test was not significant QM(1) = 0.15,
-\emph{p} = 0.702. This suggests that upon hearing a mispronunciation,
+as a moderator, the moderator test was not significant, QM(1) = 215.761,
+\emph{p}\textless{} .001 and the estimate for mispronunciation type was
+small, \(\beta\) = 0.034, SE = 0.088, 95\% CI{[}-0.139, 0.207{]},
+\emph{p}= 0.702. This suggests that upon hearing a mispronunciation,
 infants looks to the target image were similar for when the
@@
 condition (correct pronunciation, mispronunciation) as an additional
-moderator. The moderator test was significant, QM(3) = 145.14, \emph{p}
-\textless{} .001, but the interaction between mispronunciation type and
-condition was not significant \(\beta\) = 0.06, (SE = 0.08, 95\% CI
-{[}-0.10, 0.21{]}, \emph{p} = 0.479). These results suggest that
-overall, the type of mispronunciation (consonant vs.~vowel) did not
-impact mispronunciation sensitivity.
+moderator. The moderator test was significant, QM(1) = 215.761,
+\emph{p}\textless{} .001, but the estimate for the interaction between
+mispronunciation type and condition was small and not significant,
+\(\beta\) = 0.056, SE = 0.079, 95\% CI{[}-0.099, 0.211{]}, \emph{p}=
+0.479. These results suggest that overall, the type of mispronunciation
+(consonant vs.~vowel) did not impact mispronunciation sensitivity.
 
@@
 including age as a moderator resulted in a moderator test that was not
-significant, QM(3) = 1.54, \emph{p} = 0.672. This suggests that upon
-hearing a mispronunciation, infants looks to the target image were
-similar for when the mispronunciation was on a consonant or vowel
-phoneme, regardless of their age. We next assessed whether the
-relationship between mispronunciation type (consonant or vowel) and
-mispronunciation sensitivity was modulated by age. We merged the two
-datasets and included condition (correct pronunciation,
+significant, QM(1) = 215.761, \emph{p}\textless{} .001 and the estimate
+for the interaction between mispronunciation type and age was small,
+\(\beta\) = 0.001, SE = 0.017, 95\% CI{[}-0.033, 0.034{]}, \emph{p}=
+0.961. This suggests that upon hearing a mispronunciation, infants looks
+to the target image were similar for when the mispronunciation was on a
+consonant or vowel phoneme, regardless of their age. We next assessed
+whether the relationship between mispronunciation type (consonant or
+vowel) and mispronunciation sensitivity was modulated by age. We merged
+the two datasets and included condition (correct pronunciation,
 mispronunciation) as well as age as additional moderators. The moderator
-test was significant, QM(7) = 153.79, \emph{p} \textless{} .001. The
-interaction between mispronunciation type, condition, and age was
-significant (\(\beta\) = 0.04, SE = 0.02, 95\% CI {[}0.01, 0.08{]},
-\emph{p} = 0.016). As can be seen in Figure X, as infants age,
-mispronunciation sensitivity grows larger for vowel mispronunciations
-but becomes smaller for consonant mispronunciations. Noticeably,
-mispronunciation sensitivity appears greater for consonant compared to
-vowel mispronunciations at younger ages, but this difference shifts as
-infants age.
+test was significant, QM(1) = 215.761, \emph{p}\textless{} .001, and the
+estimate for the three-way interaction between mispronunciation type,
+condition, and age was small, but significant, \(\beta\) = 0.044, SE =
+0.018, 95\% CI{[}0.008, 0.08{]}, \emph{p}= 0.016. As can be seen in
+Figure 6, as infants age, mispronunciation sensitivity grows larger for
+vowel mispronunciations but becomes smaller for consonant
+mispronunciations. Noticeably, mispronunciation sensitivity appears
+greater for consonant compared to vowel mispronunciations at younger
+ages, but this difference shifts as infants age.
+
+\subsection{Figure 6}\label{figure-6}
 
@@
 (\emph{n} = 6) were classified into the Romance language family
-(\emph{n} = 28). For object recognition in response to a
-mispronunciation, including language family as a moderator resulted in a
-moderator test that was not significant, QM(3) = 5.36, \emph{p} = 0.147.
-This suggests that upon hearing a mispronunciation, infants looks to the
-target image were similar for when the mispronunciation was on a
-consonant or vowel phoneme, regardless of the language family of their
-native language. We next assessed whether the relationship between
-mispronunciation type (consonant or vowel) and mispronunciation
-sensitivity was modulated by language family. We merged the two datasets
-and included condition (correct pronunciation, mispronunciation) as well
-as language family as additional moderators. The moderator test was
-significant, QM(7) = 158.89, \emph{p} \textless{} .001. The interaction
-between condition and language family was significant (\(\beta\) = 0.73,
-SE = 0.23, 95\% CI {[}0.27, 1.18{]}, \emph{p} = 0.002), suggesting
-XXXXXXXXXXXXXX. The interaction between mispronunciation type,
-condition, and language family was also significant (\(\beta\) = -0.87,
-SE = 0.28, 95\% CI {[}-1.42, -0.32{]}, \emph{p} = 0.002). As can be seen
-in Figure X, mispronunciation sensitivity for consonants was similar for
-Germanic and Romance languages. Mispronunciation sensitivity for vowels,
-however, was greater for Germanic compared to Romance languages.
+(\emph{n} = 28).
+
+For object recognition in response to a mispronunciation, including
+language family as a moderator resulted in a moderator test that was not
+significant, QM(1) = 215.761, \emph{p}\textless{} .001, and the estimate
+for the interaction between mispronunciation type and language family
+was small, \(\beta\) = 0.277, SE = 0.314, 95\% CI{[}-0.338, 0.892{]},
+\emph{p}= 0.378. This suggests that upon hearing a mispronunciation,
+infants looks to the target image were similar for when the
+mispronunciation was on a consonant or vowel phoneme, regardless of the
+language family of their native language. We next assessed whether the
+relationship between mispronunciation type (consonant or vowel) and
+mispronunciation sensitivity was modulated by language family. We merged
+the two datasets and included condition (correct pronunciation,
+mispronunciation) as well as language family as additional moderators.
+The moderator test was significant, QM(1) = 215.761, \emph{p}\textless{}
+.001, and the estimate for the three-way interaction between
+mispronunciation type, condition, language family was large and
+significant , \(\beta\) = -0.872, SE = 0.28, 95\% CI{[}-1.421,
+-0.323{]}, \emph{p}= 0.002. As can be seen in Figure 7, mispronunciation
+sensitivity for consonants was similar for Germanic and Romance
+languages. Mispronunciation sensitivity for vowels, however, was greater
+for Germanic compared to Romance languages.
 
 {[}KATIE{]} I'M NOT REALLY SURE WHAT THE CONDITION BY LANGUAGE FAMILY
-INTERACTION MEANS. SHOULD WE EVEN INTERPRET IT?
+INTERACTION MEANS. SHOULD WE EVEN INTERPRET IT? MAYBE THAT THE ROMANCE
+LANGUAGE FAMILY HAD LOWER MISPRONUNCIATION SENSITIVITY?
+
+\subsection{Figure 7}\label{figure-7}
 
@@
 family and infant age as a moderator resulted in a moderator test that
-was significant, QM(7) = 19.53, \emph{p} = 0.007. The interaction
-between language family, age, and type of mispronunciation (consonant or
-vowel) was significant, (\(\beta\) = 0.73, SE = 0.23, 95\% CI {[}0.27,
-1.18{]}, \emph{p} = 0.002). As can be seen in Figure X, for infants
-learning Germanic languages, increasing age was related to increasing
-mispronunciation sensitivity for vowel mispronunciations, but decreasing
-sensitivity for consonant mispronunciations. In contrast, infants
-learning Romance languages have an even greater increase with age in
-sensitivity to vowel mispronunciations. Surprisingly, sensitivity to
-consonant mispronunciations shows a reversal in infants learning Romance
-languages: the growth in target looks for consonant mipronunciations
-increases and surpases that of target looks for correct pronunciations.
+was significant, QM(1) = 215.761, \emph{p}\textless{} .001, and the
+estimate for the three-way interaction between mispronunciation type,
+language family, and age was small, but significant , \(\beta\) =
+-0.547, SE = 0.406, 95\% CI{[}-1.342, 0.248{]}, \emph{p}= 0.178. As can
+be seen in Figure 8, looks to the target in response to a
+mispronunciation increased with age for infants learning a Germanic
+language, regardless of whether those mispronunciations were consonants
+or vowels. In contrast, infants learning Romance languages have an even
+greater increase with age in target looks in response to consonant
+mispronunciations, but there was no change with age for vowel
+mispronunciations. We next assessed whether the relationship between
+mispronunciation type (consonant or vowel) and mispronunciation
+sensitivity was modulated by language family and age. We merged the two
+datasets and included condition (correct pronunciation,
+mispronunciation) as well as language family and age as additional
+moderators. The moderator test was significant, QM(1) = 215.761,
+\emph{p}\textless{} .001, and the estimate for the four-way interaction
+between mispronunciation type, condition, language family, and age was
+small, but significant , \(\beta\) = -0.547, SE = 0.406, 95\%
+CI{[}-1.342, 0.248{]}, \emph{p}= 0.178. As can also be seen in Figure 8,
+for infants learning Germanic languages, increasing age was related to
+increasing mispronunciation sensitivity for vowel mispronunciations, but
+decreasing sensitivity for consonant mispronunciations. In contrast,
+infants learning Romance languages have an even greater increase with
+age in sensitivity to vowel mispronunciations. Surprisingly, sensitivity
+to consonant mispronunciations shows a reversal in infants learning
+Romance languages: the growth in target looks for consonant
+mipronunciations increases and surpases that of target looks for correct
+pronunciations.
 
@@
 SIGNIFICANT\ldots{} SHOULD THEY BE INTERPRETED? ALSO, WTF ROMANCE
-LANGUAGES?
+LANGUAGES? IS IT JUST NOT ENOUGH DATA?
+
+\subsection{Figure 8}\label{figure-8}
 
@@
 
-{[}KATIE{]} WORTH IT TO INCLUDE LANGUAGE FAMILY ANALYSES TOO?
+{[}KATIE{]} WORTH IT TO INCLUDE LANGUAGE FAMILY ANALYSES TOO? I'M
+THINKING NO
 
@@
 \item
-  Again, ages not matched very well for the two groups here. Decide
-  about whether to include a age subset analysis
+  Again, ages not matched very well for the two groups here. Similar
+  pattern of results for age subset analysis.
 \end{itemize}
@@
 \item
-  mispronunciation sensitivity was smaller when the distractor image
-  shared the same onset phoneme as the target image compared to when the
-  distractor image was an unfamiliar object
+  {[}Katie: Yeah! Its really strange, so the time course analysis
+  suggestion of yours is a very good one!{]}
 \item
@@
   containing no overlap.
-\item
-  mispronunciation sensitivity for target words paired with unfamiliar
-  distractors decreased with age, while it remained steady across a
-  similar range of ages for target words paired with distractors
-  containing onset overlap with the target word.
 \end{itemize}

### 2018-11-07 Paper_Analyses.Rmd
developmental focused manuscript, researcher choices analysis

@@
 
+# Create the function for mode.
+getmode <- function(v) {
+   uniqv <- unique(v)
+   uniqv[which.max(tabulate(match(v, uniqv)))]
+}
+
 ```
@@
 
-  Next to this core theoretically relevant investigation of the shape of development of infants' mispronunciation sensitivity, we take the opportunity of a systematic aggregation of data to address open questions regarding differences in experiment design and whether changes in procedure and stimuli tap into significantly different aspects of infants' ability to detect mispronunciations.
-
-  In designing their mispronunciation stimuli, Swingley and Aslin (2000) chose consonant mispronunciations that were likely to confuse adults (Miller & Nicely, 1955).
-Subsequent research has settled on systematically modulating phonemic features to achieve mispronunciations of familiar words.
-By utilizing mispronunciations consisting of phonemic changes, these experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level (i.e.
-1-feature, 2-features, 3-features, etc.).
-The importance of controlling for the degree of phonological mismatch, as measured by number of features changed, is further highlighted by studies that find graded sensitivity to both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes.
-
-  Although most research examining sensitivity to mispronunciations follows a similar design, there are some notable differences.
-For example, Swingley and Aslin (2000) presented infants with pairs of familiar images, one serving as the labeled target and one as the unlabeled distractor.
-In contrast, White and Morgan (2008; see also Mani & Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects.
-By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied (Halberda, 2003; Markman, Wasow, & Hansen, 2003).
-Infants ages 24 and 30 months associate a novel label with an unfamiliar object, although only 30-month-olds retained this label-object pairing (Bion, Borovsky, and Fernald, 2013).
-In contrast, 18-month-olds did not learn to associate a novel label with an unfamiliar object, providing evidence that this ability is developing from 18 to 30 months.
-We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by whether the distractor used is familiar or unfamiliar.
-Although mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared, the baseline preference for familiar compared to novel stimuli is also thought to change as infants develop (Hunter & Ames, 1988).
-Furthermore, young children have been found to look longer at objects for which they know the name, compared to objects of an unknown name (Schafer & Plukett, 1998).
-In other words, in absentia of a label, infants may be more or less likely to fixate on an unfamiliar object.
-To account for inherent preferences to the target or distractor image, mispronunciation experiments typically compare the increase in fixations to the target image from a silent baseline to post-labeling or present the same yoked pairs of target and distractor images in in both a correct and mispronounced labelling context.
-Considering this evidence, we may expect that in older, but not younger, children, the presence of an unfamiliar distractor may lead to greater mispronunciation sensitivity than in the presence of a familiar distractor.
-
-  Furthermore, when presenting infants with a familiar distractor image, some studies control the phonological overlap between the labels for the target and distractor.
-For example, when examining sensitivity to a mispronunciation of the target word "dog", the vowel mispronunciation "dag" would be paired with a distractor image that shares onset overlap, such as "duck".
-This ensures that infants can not use the onset of the word to differentiate between the target and distractor images (Fernald, Swingley, & Pinto, 2001).
-Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.
-The influence of distractor overlap also depends on the position of the mispronunciation in the word, which can be at word onset, medial, or final positions.
-Models of spoken word processing place more or less importance on the position of a phoneme in a word.
-The COHORT model (Marslen-Wilson & Zwitserlood, 1989) describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.
-In contrast, the TRACE model (McClelland & Elman, 1986) describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.
-
-  TRACE has also been used to model infants' sensitivity to mispronunciation location (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth.
-In early language acquisition, infants typically know more consonant compared to vowel onset words.
-When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations.
-The prevalence of consonant onset words may contribute to the finding that consonants carry more weight in lexical processing (C-bias; see Nazzi, Poltrock, & Von Holzen, 2016 for a recent review).
-In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations.
-Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels.
-English-learning 12-, 15-, 18-, and 24-month-olds (Mani & Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds (Hojen et al., unpublished) demonstrate similar sensitivity to consonant and vowel mispronunciations.
-One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations (Swingley, 2016).
-The English-learning infants tested by Swingley were older than previous studies (mean age 28 months).
-In word learning, the C-bias has been found to develop later in English learning infants (Floccia, Nazzi, Delle Luche, Poltrock, & Goslin, 2014; Nazzi, Floccia, Moquet, & Butler, 2009).
-In the current meta-analysis, we attempt to synthesize studies examining sensitivity to consonant and vowel mispronunciations across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence (Floccia et al., 2014; Keidel et al., 2007; Nazzi et al., 2016).
-We further examine the impact of language family on mispronunciation sensitivity to consonants and vowels, as C-bias emergence has been found to have a different developmental trajectory for Romance (French, Italian) compared to Germanic (British English, Danish) languages (Nazzi et al., 2016).
-
-[KATIE] Christina had noted something to herself for this paragraph: Subset by language?
-
-  Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (see Summary_Table).
-Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare.
-Yet, studies testing infants from different language backgrounds on similar sets of stimuli find similar sensitivity to mispronunciations (Ramon-Casas et al., 2009; Ramon-Casas & Bosch, 2010).
-Although we do not explicitly compare overall mispronunciation sensitivity by language (although see previous paragraph for rationale to test by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.
-
 Taken together, the studies we have reviewed begin to paint a picture of the development of mispronunciation sensitivity.
 Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding.
-In our analysis, we examine the factors modulating the development of mispronunciation sensitivity, which are both of theoretical and practical importance.
 Meta-analyses can not only help us summarize the current state of research, but can also help us evaluate theories to drive future research and make hands-on recommendations for experiment planning.
@@
 
-dat_st$object_pair <- ifelse(dat_st$object_pair == "familiar_familiar", "Familiar", "Unfamiliar")
-
 Sum_table <- dat_st %>%
       group_by(short_cite) %>% 
-      summarise(Ages_Tested_months = paste(unique(trunc(mean_age_1/30.34)), collapse=', '),
+      summarise(Publication = unique(publication_status),
+        Ages_Tested_months = paste(unique(trunc(mean_age_1/30.34)), collapse=', '),
                 Vocabulary = ifelse(all(is.na(r_comprehension)) & all(is.na(r_production)), "None",
                                 ifelse(!all(is.na(r_comprehension)) & !all(is.na(r_production)), "Comprehension/Production",
-                                       ifelse(!all(is.na(r_comprehension)) & all(is.na(r_production)), "Comprehension", "Production"))),
-                Number_of_Features = paste(unique(n_feature), collapse=', '),
-                Distractor_Familiarity = paste(unique(object_pair), collapse=', '),
-                Distractor_Overlap = paste(unique(distractor_overlap), collapse=', '),
-                Mispronunciation_Position = paste(unique(mispron_location), collapse=', '),
-                Mispronunciation_type = paste(unique(type_feature), collapse=', '))
-
-kable(Sum_table, col.names = c("Paper", "Age", "Vocabulary", "# Features", "Distractor", "Distractor name overlap", "MP Position", "MP Type"))
+                                       ifelse(!all(is.na(r_comprehension)) & all(is.na(r_production)), "Comprehension", "Production"))))
+
+kable(Sum_table, col.names = c("Paper", "Publication format", "Age", "Vocabulary"))
 
@@
 [CHRISTINA suggestions: N features should be a range and exclude 0; we could abbreviate Comperehension/Production to Comp./Prod., etcetc]
-[KATIE] I'll think about how to implement that! Might end up having to adjust the table by hand, there is a lot of variation between studies.
+[KATIE] I've reduced the table to be about age and vocabulary, in order to have it more focused for the aim of this paper.
 
@@
 For the present analyses, we focus on the following characteristics:
+
 1 Condition: Were words mispronounced or not;  
@@
 3 Vocabulary size, measured by a standardized questionnaire or list;
-4 Size of mispronunciation, measured in features changed;  
-5 Distractor familiarity: familiar or unfamiliar;  
-6 Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;  
-7 Position of mispronunciation: onset, medial, offset, or mixed;  
-8 Type of mispronunciation: consonant, vowel, or both.
 
@@
 
-## Figure 1
+## (Insert Figure 1 about here)
 
@@
 
-## Figure 2
-
-```{r PlotMPEffect, echo = FALSE}
+## (Insert Figure 2 about here)
+
+```{r PlotMPEffect, echo = FALSE, fig.width=10,fig.height=11}
 
@@
 p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
+  ggtitle("a. Object Recognition")+
   geom_point(aes(size = weights_g),show.legend=FALSE, alpha = .5) + 
@@
   theme(legend.title = element_blank(),
-        legend.position = "bottom",
-        text = element_text(size = 40)) + 
+        legend.position = "bottom") + 
   xlab("Age in months") + 
@@
 
-p
+#p
+
+dat.cm <- dat[,c("short_cite", "is_correct", "is_mp","condition", "g_calc", "weights_g", "mean_age_1", "n_1")]
+
+dat.c <- subset(dat.cm, is_correct == 1)
+dat.m <- subset(dat.cm, is_mp == 1)
+
+dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "mean_age_1", "n_1"))
+
+dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
+
+p.diff <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity)) + 
+  ggtitle("b. Mispronunciation Sensitivity")+
+  geom_point(aes(size = n_1),show.legend=FALSE, alpha = .5) + 
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Mispronunciation Sensitivity")
 
@@
 
+lay <- rbind(c(1), c(2))
+#lay <- rbind(c(1,2))
+
   jpeg(filename = "figures/Figure_2_AgeEffect.jpg", 
-       width = 700, height = 400, units = "px")
-
-  p
+       width = 500, height = 700, units = "px")
+
+ger.plot.age <- grid.arrange(p, p.diff,
+                             layout_matrix = lay)
 
 dev.off()
+
+grid.draw(ger.plot.age)
 
@@
 
-Alternatively, the lack of developmental change in mispronunciation sensitivity could be due to differences in the types of tasks given to infants of different ages.
-In the following section, we investigate the role that different moderators play in mispronunciation sensitivity.
-To investigate the possibility of systematic differences in the tasks across ages, we additionally include an exploratory analysis of whether different moderators and experimental design features were included at different ages.
-
-## Moderator Analyses
-
-[cHRISTINA] I WOULD FOLLOW THE OUTLINE IN THE PREVIOUS PARAGRAPH HERE OR FLIP THE PARAGRAPH AROUND:
-1. ARE DIFFERENT MODERATORS USED AT DIFFERENT AGES? 
-TEST: sIMPLE CHI-SQUARED OF AGE GROUP VERSUS MODERATOR ASSIGNMENT (AGE GROUP DETERMINED BY LOOKING AT THE YOUNGEST AGE FOR X?)
-2. WHICH MODERATORS INFLUENCE MP SENSITIVITY
-TEST SIMPLE MA WITH MODERATOR TESTS
-
-OR 
-"FOR EACH POSSIBLE MODERATOR WHICH COULD INFLIENCE MP SENSITIVITY, WE FIRST TEST THIS POSSIBILITY AND THEN EVALUATE WHETHER THERE IS A SYSTEMATIC DIFFERENCE OF MANIPULATING THESE MODERATORS AS INFANTS MATURE, I.E.
-WHETHER OLDER INFANTS ARE TESTED ON A MORE DIFFICULT TASK "
-ALSO, AS FINAL FOLLOW-UP IT WOULD BE PERFECT TO JUST SUBSET ALL STUDIES WITH FAMILIAR DISTRACTORS, SAME NUMBER OF FEATURES, AND CHECK THAT OUR CONCLUSIONS HOLD UP REGARING MP SENSITIVITY
-
-[KATIE: I prefer this second option, first looking at the moderators in general and then looking at whether there is this systematic difference with age.
-The latter is exploratory, so I feel like this information should not preceed our planned analyses.]
-
-### Number of features changed
-
-```{r NFeatures_demographics}
-
-dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-nfeature_info <- dat.f %>%
-  group_by(n_feature) %>%
+Alternatively, it is possible that variation in the analysis approach lead to systematic differences in the size of mispronunciation sensitivity.
+Choices about the approach to data analysis have a higher possibility to be influenced by the shape of the data itself after collection, and are therefore susceptible to a higher rate of false-positives (Simmons, Nelson, & Simonsohn, 2011).
+Although we did not have specific predictions about these variables, such as size of time window analyzed or dependent variable calculated, we included these variables in our coding scheme for the meta-analysis dataset.
+As reported in the Methods section (and discussed in detail below), some of these variables varied widely across studies.
+In the following section, we include an exploratory analysis to investigate the possibility of systematic differences in the approach to analysis in general and across infant age.
+
+[KATIE] I've changed the above paragraph to lead to exploratory analyses, not moderators.
+Since the fmailiar/unfamiliar analysis doesn't really work out except for if we kind of subset and torture the data, I think its more interesting to talk about how choices of analysis / researcher degrees of freedom may influence the data
+
+## Exploratory Analyses
+
+We identified several variables to assess the influence of data analysis choices.
+These variables fall into two types of categories: time-related and dependent variable related.
+In the following analyses, we discuss the theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these choices have on mispronunciation sensitivity development.
+
+### Time-related analyses
+
+```{r time_choices_info}
+
+# trial length
+
+trial_length_info <- dat %>%
+  group_by(trial_length) %>%
   summarize(n_exp_conditions =  n())
-
-```
-
-To assess whether the number of features changed modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced using 1-, 2-, and 3-feature changes.
-We did not include data for which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent (e.g., one mispronunciation included a 2-feature change whereas another only a 1-feature change).
-This analysis was therefore based on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` experimental conditions for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations.
-Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an equal impact on mispronunciation sensitivity, following the argument of graded sensitivity (White & Aslin, 2008; Mani & Plunkett 2011).
-
-```{r NFeatures}
-
-dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat.f, random = ~collapse | short_cite)
-
- sum_eff <- coef(summary(rma_NFeatures))[2,]
-
-```
-
-To understand the relationship between number of features changed and mispronunciation sensitivity, we  evaluated the effect size Hedges' *g* with number of features changed as a moderator.
-The moderator test was significant, `r mod_test(rma_NFeatures)`.
-Hedges' *g* for number of features changed was `r g_SE(sum_eff)`, which indicated that as the number of features changed increased, the effect size Hedges' *g* significantly decreased `r CI_p(sum_eff)`.
-We plot this relationship in Figure 3.
-This confirms previous findings of a graded sensitivity to the number of features changed for both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) mispronunciations as well as the importance of controlling for the degree of phonological mismatch in experimental design.
-
-## Figure 3
-
-```{r PlotFeatEffect, echo = FALSE}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-dat_f$feat_cat <- ifelse(dat_f$n_feature == 1, "1-feature",
-                         ifelse(dat_f$n_feature == 2, "2-feature",
-                                ifelse(dat_f$n_feature == 3, "3-feature",
-                                       ifelse(dat_f$n_feature == 0, "correct", "none"))))
-
-dat_f <- subset(dat_f, feat_cat != "none")
-
-dat_f$Features_changed <- factor(dat_f$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))
-
-p <- ggplot(dat_f, aes(Features_changed, g_calc, fill = Features_changed)) + 
+        #post_naming = paste(unique(post_nam_dur), collapse=', '))
+
+trial.l <- cor.test(dat$trial_length, dat$mean_age_1)
+trial.length.plot <- ggplot(dat, aes(trial_length, age.C)) + geom_point() +geom_smooth(method = "lm")
+
+# post-naming
+post_name_info <- dat %>%
+  group_by(post_nam_dur) %>%
+  summarize(n_exp_conditions =  n())
+        #post_naming = paste(unique(post_nam_dur), collapse=', '))
+
+post.l <- cor.test(dat$post_nam_dur, dat$mean_age_1)
+post_nam_dur.plot <- ggplot(dat, aes(post_nam_dur, age.C)) + geom_point() +geom_smooth(method = "lm")
+
+# difference post vs. trial length
+dat$post_trial_match <- ifelse(dat$post_nam_dur == (dat$trial_length-dat$pre_nam_dur), "same", "different")
+dat$post_trial_prop <- dat$post_nam_dur/(dat$trial_length-dat$pre_nam_dur)
+
+post_trial_match_info <- dat %>%
+  group_by(post_trial_match) %>%
+  summarize(n_exp_conditions =  n())
+        #post_naming = paste(unique(post_nam_dur), collapse=', '))
+
+post_trial_prop_info <- dat %>%
+  group_by(post_trial_prop) %>%
+  summarize(n_exp_conditions =  n())
+        #post_naming = paste(unique(post_nam_dur), collapse=', '))
+
+post_match.l <- cor.test(dat$post_trial_prop, dat$mean_age_1)
+post_match.plot <- ggplot(subset(dat, post_trial_prop != 1), aes(post_trial_prop, age.C)) + geom_point() +geom_smooth(method = "lm")
+
+# offset
+offset_info <- dat %>%
+  group_by(offset) %>%
+  summarize(n_exp_conditions =  n())
+        #post_naming = paste(unique(post_nam_dur), collapse=', '))
+
+dob <- subset(dat, !is.na(offset) & offset < 1000)
+dob$offset_bin <- ifelse(dob$offset <371 & dob$offset > 359, 367, dob$offset)
+
+# offset
+offset_bin_info <- dob %>%
+  group_by(offset_bin) %>%
+  summarize(n_exp_conditions =  n())
+        #post_naming = paste(unique(post_nam_dur), collapse=', '))
+
+offset.l <- cor.test(dat$offset, dat$mean_age_1)
+offset.plot <- ggplot(dat, aes(offset, age.C)) + geom_point() +geom_smooth(method = "lm")
+
+```
+
+When designing mispronunciation sensitivity studies, experimenters choose the length of time each trial is presented.
+This includes both the length of time before the target object is named (pre-naming phase) as well as after (post-naming phase) and is determined prior to data collection.
+Across papers, trial length varied from `r with(trial_length_info, min(trial_length))*1000` to `r with(trial_length_info, max(trial_length))*1000` ms, with a mode of `r with(dat, getmode(trial_length))*1000` ms.
+There was an inverse relationship between infant age and trial length, such that younger infants were given trials of a longer length, although this correlation was not significant (*r* = `r trial.l$estimate`, *p* `r psig(trial.l$p.value)`).
+Presumably, younger infants may be given longer trials because their word recognition abilities may be slower than older infants (Fernald et al., 1998).
+
+Unlike the length of trial, the length of the post-naming phase analyzed can be chosen after the experimental data is collected.
+Interestingly, half of the experimental conditions were analyzed using the same length of post-naming phase as the infant heard in the actual experiment `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`, while the other half were analyzed using a shorter length of post-naming phase, excluding later portions of the post-naming phase `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`.
+Across papers, the length of the post-naming phase analyzed varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a mode of `r with(dat, getmode(post_nam_dur))*1000` ms.
+Similar to trial length, there was an inverse relationship between infant age and length of post-naming phase analyzed, such that younger infants were analyzed using a longer length of post-naming phase, although here the relationship was significant (*r* = `r post.l$estimate`, *p* `r psig(post.l$p.value)`).
+Again, the choice to analyze a shorter post-naming time window is likely related to evidence that speed of processing is slower in younger infants (Fernald et al., 1998).
+Furthermore, the proportion of post-naming phase time window analyzed in comprison to the total post-naming phase presented to infants significantly decreased with increasing infant age (*r* = `r post_match.l$estimate`, *p* `r psig(post_match.l$p.value)`).
+Although trial length did not differ by infant age, the size of the post-naming phase time window analyzed did differ by infant age.
+
+When analyzing eye-movements, it is important to consider the amount of time it takes for an eye movement to be initiated in response to a stimulus.
+Previous studies examining simple stimulus response latencies first determined that infants require at least 233 ms to initiate an eye-movement in response to a stimulus (Canfield & Haith, 1991).
+In mispronunciation sensitivity studies, however, this has often been extended to 367 ms (e.g.
+Swingley & Aslin, 2000, 2002, 2007).
+Across papers, the majority used a similar offset value (between 360 and 370 ms) for analysis (*n* = `r with(offset_bin_info, n_exp_conditions[offset_bin == "367"])`), but offset values ranged from `r with(offset_bin_info, min(offset_bin))` to `r with(offset_bin_info, max(offset_bin))` ms, and were not reported for `r with(offset_info, n_exp_conditions[is.na(offset)])` experimental conditions.
+We note that Swingley (2009) also included offset values of 1133 ms to analyze responses to coda mispronunciations.
+There was an inverse relationship between infant age and size of offset, such that younger infants were given longer offsets, although this correlation was not significant (*r* = `r offset.l$estimate`, *p* `r psig(offset.l$p.value)`).
+This lack of a relationship is perhaps driven by the field's consensus that an offset of about 367 ms is appropriate for analyzing word recognition with PTL measures, including studies that evaluate mispronunciation sensitivity.
+
+Although there are a priori reasons to choose the post-naming time window (infant age) or offset time (previous studies), these choices may occur after data collection and are therefore susceptible to a higher rate of false-positives.
+Considering that differences in these choice were systematically different across infant ages, at least for the post-naming time window, we next explored whether the size of the analyzed post-naming phase time window or the offset time influenced sensitivity to mispronunciations.
+
+### Length of post time
+
+```{r time_post}
+
+rma_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur), data = db_ET_MP, random = ~collapse | short_cite)
+
+ rma_post_dur_eff <- coef(summary(rma_post_dur))[2,]
+
+ rma_post_dur_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur)*condition, data = dat, random = ~collapse | short_cite)
+
+  rma_post_dur_MS_eff <- coef(summary(rma_post_dur_MS))[4,]
+
+  # age
+
+ rma_post_dur_AGE <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur)*age.C, data = db_ET_MP, random = ~collapse | short_cite)
+
+   rma_post_dur_AGE_eff <- coef(summary(rma_post_dur_MS))[4,]
+
+  rma_post_dur_AGE_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur)*age.C*condition, data = dat, random = ~collapse | short_cite)
+
+    rma_post_dur_AGE_MS_eff <- coef(summary(rma_post_dur_MS))[8,]
+
+```
+
+We first assessed whether size of post-naming phase analyzed had an impact on the size of mispronunciation sensitivity.
+First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images, including post-naming phase size as a moderator.
+The moderator test was not significant `r mod_test(rma_post_dur)` and the estimate for post-naming phase size was relatively small, $\beta$`r full_estimate(rma_post_dur_eff)`.
+This suggests that upon hearing a mispronunciation, infants' looks to the target image were similar regardless of the size of the post-naming phase analyzed.
+We next assessed whether post-naming phase size was related to mispronunciation sensitivity.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
+The moderator test was significant, `r mod_test(rma_post_dur_MS)`.
+The estimate for the interaction between post-naming phase size and condition was small but significant $\beta$`r full_estimate(rma_post_dur_MS_eff)`.
+This relationship is plotted in Figure 3a.
+The results suggest that although the size of the post-naming phase analyzed did not impact infants' likelihood to fixate the target upon hearing the mispronunciation, it did significantly impact mispronunciation sensitivity.
+Specifically, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) was significantly greater when the post-naming phase that was shorter in length.
+
+Considering that we also found a relationship between the length of the post-naming phase analyzed and infant age, such that younger ages had a longer post-naming phase time window of analysis, we next examined whether the size of post-naming phase analyzed modulated the development of mispronunciation sensitivity.
+For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant `r mod_test(rma_post_dur_AGE)`, and a small estimate for the interaction between age and size of post-naming phase ($\beta$`r full_estimate(rma_post_dur_AGE_eff)`.
+This suggests that upon hearing a mispronunciation, infant measured looks to the target image were similar, regardless of infant age or size of the post-naming phase analyzed.
+We next assessed whether the relationship between size of the post-naming phase analyzed and mispronunciation sensitivity was modulated by age.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
+The moderator test was significant `r mod_test(rma_post_dur_AGE_MS)`.
+The estimate for the  three-way-interaction between condition, size of post-naming phase, and age was small, but significant ($\beta$ = `r full_estimate(rma_post_dur_AGE_MS_eff)`.
+This relationship is plotted in Figure 3b.
+Smaller post-naming phase size lead to greater increases in mispronunciation sensitivity with development.
+For example, experimental conditions analyzed with a post-naming phase of 2000 ms or less, mispronunciation sensitivity increases with infant age, whereas a post-naming phase of greater than 2000 ms leads to either no impact of age on mispronunciation sensitivity or a negative relationship between age and mispronunciation sensitivity.
+
+## (Insert Figure 3 about here)
+
+```{r Plot_post_name_cond_age, echo = FALSE, fig.width=10,fig.height=11}
+
+dat$condition_label <- ifelse(dat$condition==1, "Correct", "Mispronunciation")
+
+dat$post_size <- ifelse(dat$post_nam_dur <= 2, "2000 ms or less",
+                       ifelse(dat$post_nam_dur > 2 & dat$post_nam_dur <= 3, "2001-3000 ms", "3001 ms or greater"))
+
+dat$post_size <- factor(dat$post_size, levels = c("2000 ms or less", "2001-3000 ms", "3001 ms or greater"))
+
+dat.cm <- dat[,c("short_cite", "is_correct", "is_mp", "post_size", "condition", "g_calc", "weights_g", "mean_age_1", "n_1")]
+
+dat.c <- subset(dat.cm, is_correct == 1)
+dat.m <- subset(dat.cm, is_mp == 1)
+
+dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "post_size", "mean_age_1", "n_1"))
+
+dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
+
+p.MS <- ggplot(dat.cm, aes(post_size, Misp_sensitivity, fill = post_size)) + 
+  #facet_grid(.~post_size)+
     geom_violin() + 
   geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
+  labs(caption="a")+
   #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
@@
         legend.position = "none",
-        axis.title.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_3_Number_of_Features.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-  #[CHRISTINA] WHAT DO YOU THINK ABOUT VIOLIN PLOTS?
-
-```
-
-```{r NFeatures_age}
-
-dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat.f, random = ~collapse | short_cite)
-
- sum_eff <- coef(summary(rma_NFeatures))[4,]
-
-```
-
-Although we did not have any specific predictions about the relationship between infant age and the impact of number of features changed on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
-When age was also included as a moderator, the moderator test was significant, `r mod_test(rma_NFeatures)`, but the interaction between age and number of features changed was not significant, $\beta$`r full_estimate(sum_eff)`.
-The small effect size for the interaction between age and number of features changed suggests that the impact of number of features changed on mispronunciation sensitivity does not change with infant age.
-
-```{r NFeatures_subset}
-
-dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
-                n_feature == "2" | n_feature == "3")
-
-nfeature_ages <- dat.f %>%
-  group_by(n_feature) %>%
-  summarize(min_age = r2(min(mean_age_1, na.rm=TRUE)),
-            max_age = r2(max(mean_age_1, na.rm=TRUE)),
-            mean_age = r2(mean(mean_age_1, na.rm=TRUE)))
-
-mf <- subset(dat_f, n_feature == "3")
-min_age <- min(mf$mean_age_1)
-max_age <- max(mf$mean_age_1)
-
-dat_fage= dat_f%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat_fage, random = ~collapse | short_cite)
-
- sum_eff1 <- coef(summary(rma_NFeatures_agesub))[2,]
-
-rma_AGENFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat_fage, random = ~collapse | short_cite)
-
- sum_eff2 <- coef(summary(rma_AGENFeatures_agesub))[4,]
-
-```
-
-Although all papers included in the dataset also included correct pronunciations, not all papers included all three types of feature changes (i.e.
-1-3).
-The age range for each type of number of features changed was `r with(nfeature_ages, min_age[n_feature == 1])` - `r with(nfeature_ages, max_age[n_feature == 1])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 1])`) for 1-feature mispronunciations, `r with(nfeature_ages, min_age[n_feature == 2])` - `r with(nfeature_ages, max_age[n_feature == 2])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 2])`) for 2-feature mispronunciations, and `r with(nfeature_ages, min_age[n_feature == 3])` - `r with(nfeature_ages, max_age[n_feature == 3])` days (*M* = `r with(nfeature_ages, mean_age[n_feature == 3])`) for 3-feature mispronunciations.
-The reader should note that experimental conditions in which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent (e.g., one mispronunciation included a 2-feature change whereas another only a 1-feature change) are not included in these totals.
-An analysis focusing on the ages where all three numbers of features changed were tested (i.e.
-`r with(nfeature_ages, min_age[n_feature == 3])` - `r with(nfeature_ages, max_age[n_feature == 3])` days), however, did not change the pattern of results.
-
-### Distractor familiarity
-
-```{r DistractorType_misp}
-
-rma_Distractor_MP <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)
-
-misp_recog <- coef(summary(rma_Distractor_MP))[2,]
-
-rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
-
-misp_MS <- coef(summary(rma_Distractor))[4,]
-
-```
-
-We next assessed whether distractor familiarity has an impact on the size of mispronunciation sensitivity.
-First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images that were paired with either a familiar or an unfamiliar distractor image.
-The moderator test was not significant `r mod_test(rma_Distractor_MP)` and the estimate for distractor familiarity was relatively small, $\beta$`r full_estimate(misp_recog)`.
-This suggests that upon hearing a mispronunciation, infants' looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object.
-We next assessed whether distractor familiarity was related to mispronunciation sensitivity.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, `r mod_test(rma_Distractor)`, but the estimate for the interaction between distractor familiarity and condition was small and not significant $\beta$`r full_estimate(misp_MS)`.
-This relationship is plotted in Figure 4.
-The results suggest that overall, infants' familiarity with the distractor object (familiar or unfamiliar) did not impact their mispronunciation sensitivity.
-
-## Figure 4
-
-```{r PlotDistFamEffect_NoAge}
-
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
-dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "Familiar Distractor", "Unfamiliar Distractor")
-
-# Color Blind palette:
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
-p.DIST_ALL <- ggplot(dat, aes(condition_label, g_calc, fill = condition_label)) + 
-  geom_violin() + 
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
-  facet_grid(.~dist_code) +
-  #labs(caption="a.") + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
         axis.title.x = element_blank(),
@@
   geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Effect size Hedges' g")
-
-p.DIST_ALL
-
-# lay <- rbind(c(1,1,2),
-#       c(3,3,3))
-
-  jpeg(filename = "figures/Figure_4_Distractor_Familiarity.jpg", 
-       width = 500, height = 300, units = "px")
-
-p.DIST_ALL
+  ylab("Misp. Sensitivity")
+
+p.AGE <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = post_size)) + 
+    #facet_grid(.~post_size)+
+  geom_point(aes(size = n_1),show.legend=FALSE) +
+  labs(caption="b")+
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Misp. Sensitivity")
+
+lay <- rbind(c(1), c(2))
+#lay <- rbind(c(1,2))
+
+  jpeg(filename = "figures/Figure_3_Post_name_size.jpg", 
+       width = 600, height = 600, units = "px")
+
+ger.plot.age <- grid.arrange(p.MS, p.AGE,
+                             layout_matrix = lay)
 
@@
 
-```
-
-```{r DistractorTypeAge}
-
-rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)
-
-sum_eff <- coef(summary(rma_DistractorAge))[4,]
-
-rma_DistractorAgeMS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
-
-#summary(rma_DistractorAgeMS)
-
-sum_eff1 <- coef(summary(rma_DistractorAgeMS))[8,]
-sum_eff2 <- coef(summary(rma_DistractorAgeMS))[7,]
-
-```
-
-We next examined whether age modulates object recognition or mispronunciation sensitivity when the distractor image is familiar or unfamiliar.
-Based on previous results, we expected older infants to look less to the target in response to mispronunciations and to have greater mispronunciation sensitivity than younger infants when the distractor was unfamiliar compared to familiar.
-For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant `r mod_test(rma_DistractorAge)`, and a small estimate for the interaction between age and object recognition ($\beta$`r full_estimate(sum_eff1)`.
-This suggests that upon hearing a mispronunciation, infant looks to the target image were similar for when the target image was paired with an image of a familiar or unfamiliar object, regardless of their age.
-We next assessed whether the relationship between distractor familiarity and mispronunciation sensitivity was modulated by age.
+grid.draw(ger.plot.age)
+
+```
+
+### Length of offset time
+
+```{r time_offset}
+
+rma_offset <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset), data = db_ET_MP, random = ~collapse | short_cite)
+
+rma_offset_eff <- coef(summary(rma_offset))[2,]
+
+ rma_offset_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*condition, data = dat, random = ~collapse | short_cite)
+
+  rma_offset_MS_eff <- coef(summary(rma_offset_MS))[4,]
+
+  # age
+
+ rma_offset_AGE <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*age.C, data = db_ET_MP, random = ~collapse | short_cite)
+
+   rma_offset_AGE_eff <- coef(summary(rma_offset_AGE))[4,]
+
+  rma_offset_AGE_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*age.C*condition, data = dat, random = ~collapse | short_cite)
+
+    rma_offset_AGE_MS_eff <- coef(summary(rma_offset_AGE_MS))[8,]
+
+```
+
+We next assessed whether offset time had an impact on the size of mispronunciation sensitivity.
+First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images, including offset time as a moderator.
+The moderator test was not significant `r mod_test(rma_offset)` and the estimate for offset time was very small, $\beta$`r full_estimate(rma_offset_eff)`.
+This suggests that upon hearing a mispronunciation, infants' looks to the target image were similar regardless of the offset time used to analyze the data.
+We next assessed whether offset time was related to mispronunciation sensitivity.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
+The moderator test was significant, `r mod_test(rma_post_dur_MS)`, but the estimate for the interaction between offset time and condition was very small and not significant $\beta$`r full_estimate(rma_offset_MS_eff)`.
+
+We next examined whether offset time modulated the development of mispronunciation sensitivity.
+For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant `r mod_test(rma_offset_AGE)`, and a very small estimate for the interaction between age and size of post-naming phase ($\beta$`r full_estimate(rma_offset_AGE_eff)`.
+This suggests that upon hearing a mispronunciation, infant measured looks to the target image were similar, regardless of infant age or offset time.
+We next assessed whether the relationship between offset time and mispronunciation sensitivity was modulated by age.
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant `r mod_test(rma_DistractorAgeMS)`.
-The estimate for the  three-way-interaction between condition, distractor familiarity, and age was small and not significant ($\beta$ = `r full_estimate(sum_eff1)`.
-We note that in this model, the interaction between condition and distractor familiarity was significant ($\beta$`r full_estimate(sum_eff2)`, this estimate is similar to the original estimate specifically examining this interaction in a previous model.
-Taken together, these results suggest that regardless of age, mispronunciation sensitivity was similar whether the distractor image was familiar or unfamiliar.
-
-```{r DistractorTypeAgeRangeSubset}
-
-object_pair_ages <- dat %>%
-  group_by(object_pair) %>%
-  summarize(min_age = r2(min(mean_age_1, na.rm=TRUE)),
-            max_age = r2(max(mean_age_1, na.rm=TRUE)),
-            mean_age = r2(mean(mean_age_1, na.rm=TRUE)),
-            sd_age = r2(sd(mean_age_1, na.rm=TRUE)))
-
-fn <- subset(dat, object_pair=="familiar_novel")
-
-ff <- subset(dat, object_pair=="familiar_familiar")
-
-age_diff_dist <- t.test(fn$mean_age_1, ff$mean_age_1, paired = F)
-
-#t.test(fn$mean_age_1, ff$mean_age_1)
-
-opa <- as.data.frame(object_pair_ages)
-min_age <- max(opa$min_age)
-max_age <- min(opa$max_age)
-
-dat_age_MP= db_ET_MP%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-rma_Distractor_MP_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat_age_MP, random = ~ collapse | short_cite)
-
-misp_recog_agesub <- round(coef(summary(rma_Distractor_MP_agesub))[2,], 2)
-
-rma_DistractorAge_agesub <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(object_pair), data = dat_age_MP, random = ~ collapse | short_cite)
-
-#summary(rma_Distractor_MP)
-
-misp_MS_agesub <- round(coef(summary(rma_DistractorAge_agesub))[4,], 2)
-
-# misp sensitivity
-dat_age= dat%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-rma_Distractor_MS_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition, data = dat_age, random = ~ collapse | short_cite)
-
-misp_recog_Age_agesub <- round(coef(summary(rma_Distractor_MS_agesub))[4,], 2)
-
-rma_DistractorAgeMS_agesub <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
-
-misp_MS_Age_agesub <- round(coef(summary(rma_DistractorAgeMS_agesub))[8,], 2)
-
-#summary(rma_Distractor_MS)  
-```
-
-Although we anticipated that older children may be more impacted by the presence of a unfamiliar compared to familiar distractor image, we found that age and distractor familiarity did not impact mispronunciation sensitivity.
-Inspection of the ages tested using different kinds of distractors, however, revealed differences.
-Infants tested using a familiar distractor were younger (*M* = `r with(object_pair_ages, mean_age[object_pair == "familiar_familiar"])` days, *SD* = `r with(object_pair_ages, sd_age[object_pair == "familiar_familiar"])`, range = `r with(object_pair_ages, min_age[object_pair == "familiar_familiar"])` - `r with(object_pair_ages, max_age[object_pair == "familiar_familiar"])`) than those infants tested using an unfamiliar distractor (*M* = `r with(object_pair_ages, mean_age[object_pair == "familiar_novel"])` days, *SD* = `r with(object_pair_ages, sd_age[object_pair == "familiar_novel"])`, range = `r with(object_pair_ages, min_age[object_pair == "familiar_novel"])` - `r with(object_pair_ages, max_age[object_pair == "familiar_novel"])`), which a two-sample t-test revealed to be a significant difference, *t*(`r r2(age_diff_dist$parameter)`) = `r r2(age_diff_dist$statistic)`, *p* `r psig(age_diff_dist$p.value)`).
-
-[CHRISTINA] CAN YOU TURN THE NUMBERS INTO R CODE HERE? aLSO, NOT SURE WE NEED A T-TEST TO CONFIRM THE OBVIOUS.
-[Katie: Is the t-test okay?]
-
-To ensure that the lack of a difference wasn't due to the ages of infants tested with different types of distractors, we repeated the previous model analyses on a subset of papers that tested infants at ages where both familiar and unfamiliar distractors were used (`r min_age` - `r max_age` days).
-We first considered object recognition is response to a mispronunciation.
-Here, the pattern of results for the subset of infants was similar to that of the entire dataset; the moderator test was not significant `r mod_test(rma_Distractor_MP_agesub)` and the estimate for distractor familiarity was small, $\beta$`r full_estimate(misp_recog_agesub)`.
-However, it should be noted that although small, the effect size estimate for distractor familiarity doubled from $\beta$`r r2(misp_recog$estimate)` in the entire dataset to $\beta$`r r2(misp_recog_agesub$estimate)` in the subset.
-We next assessed the relationship between distractor familiarity and mispronunciation sensitivity.
-Similar to the analysis with the entire dataset, the moderator test was significant `r mod_test(rma_Distractor_MS_agesub)`.
-Unlike the analysis with the entire dataset, however, the estimate for the interaction between distractor familiarity and condition was significant $\beta$`r full_estimate(misp_recog_Age_agesub)`, but small and similar to the estimate for this interaction in the full dataset $\beta$ = `r r2(misp_MS$estimate)`.
-
-Although the age range is relatively small in the subset of infant ages tested with both familiar and unfamiliar distractors (`r r2(max_age/30.44 - min_age/30.44)` months), these ages span the beginning of the vocabulary spurt.
-Considering infants' object looking behavior may be influenced by whether the label for the object is known (Schafer & Plunkett, 1998), however, this age range may still be informative for understanding the role of distractor familiarity on mispronunciation sensitivity and whether this is modulated by age.
-Similar to the full dataset, however, including age as a moderator of object recognition in response to familiar and unfamiliar distractors resulted in a moderator test that was not significant `r mod_test(rma_DistractorAge_agesub)`, and a small estimate for the interaction between age and object recognition ($\beta$`r full_estimate(misp_MS_agesub)`.
-Finally, we assessed whether the relationship between distractor familiarity and mispronunciation sensitivity was modulated by age in the subset of data.
-Again, similar to the full dataset, the moderator test was not significant `r mod_test(rma_DistractorAgeMS_agesub)` and the estimate for the three-way-interaction between condition, distractor familiarity, and age was small and not significant ($\beta$ = `r full_estimate(misp_MS_Age_agesub)`.
-
-[Katie: ultimately, the subset analysis doesn't show anything :( What conclusions can we draw?]
-
-### Phonological overlap between target and distractor
-
-```{r DistractorOverlap_descrip}
-
-dist_overlap_info <- dat %>%
-  group_by(distractor_overlap) %>%
+The moderator test was significant `r mod_test(rma_offset_AGE_MS)`, but the three-way-interaction between condition, offset time, and age was very small and not significant ($\beta$ = `r full_estimate(rma_offset_AGE_MS_eff)`.
+
+Taken together, these results suggest that offset time does not modulate mispronunciation sensitivity.
+There is no relationship between offset time and age, and we find no influence of offset time on the development of mispronunciation sensitivity.
+
+### Dependent variable-related analyses
+
+```{r dv_info}
+
+dv_info <- dat %>%
+  group_by(within_measure) %>%
   summarize(n_exp_conditions =  n())
 
-```
-
-To assess whether phonological overlap between the target and distractor image labels has an impact on the size of mispronunciation sensitivity, we examined the meta-analytic effect for object identification in response to mispronunciations and mispronunciation sensitivity when the target-distractor pairs either had no overlap or shared the same onset phoneme.
-We did not include data for which the overlap included both the onset and medial phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset/medial"])`), coda phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "coda"])`), or for targets paired with an unfamiliar distractor image `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "novel"])`.
-The analysis was therefore based on a subset of the overall dataset, with `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset"])` experimental conditions containing onset phoneme overlap between the target and distractor and `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "no"])` containing no overlap between target and distractor.
-
-[CHRISTINA] SEEMS OK BUT I AM CONFUSED WHY OVERLAP IS THE BASELINE AND WHY YOU BRING IN NOVEL. I THINK YOU NEED TO SPELL THIS OUT MORE.
-
-[KATIE: I think we had talked about it and decided to include novel. I don't think it needs to be here necessarily, so I'll take it out, especially if its confusing.]
-
-```{r DistractorOverlap}
-db_ET_MPo = db_ET_MP %>%
-  filter(distractor_overlap == "onset"  |  distractor_overlap == "no")
-
-db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no"))
-
-rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
-
-#summary(rma_DistractorOverlap)  
-sum_eff1 <- coef(summary(rma_DistractorOverlap))[2,]
-
-db_ET_MPo_MS = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "no")
-
-db_ET_MPo_MS$distractor_overlap <- factor(db_ET_MPo_MS$distractor_overlap, levels = c("onset", "no"))
-
-rma_DistractorOverlapMS <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MPo_MS, random = ~ collapse | short_cite)
-
-#summary(rma_DistractorOverlapMS)
-
-sum_eff2 <- coef(summary(rma_DistractorOverlapMS))[4,]
-
-```
-
-Regarding object identification in response to mispronunciations, when distractor overlap was included as a moderator, the moderator test was not significant `r mod_test(rma_DistractorOverlap)` and the estimate for distractor overlap was relatively small, $\beta$`r full_estimate(sum_eff1)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the target image was paired with a distractor image that contained overlap on the onset phoneme or no overlap with the target word, or was an unfamiliar object.
-We next assessed whether target-distractor overlap was related to mispronunciation sensitivity.
+dv.l <- summary(lm(age.C ~ within_measure, data = dat))
+
+dv.age.plot <- ggplot(dat, aes(within_measure, age.C)) +     geom_violin() + 
+  geom_jitter(height = 0, width = 0.1, alpha = 0.5)
+
+```
+
+Mispronunciation studies evaluate infants' proportion of target looks (PTL) in response to correct and mispronounced words.
+Experiments typically include a phase where no naming event has occured, whether correctly pronounced or mispronounced, which we refer to as the baseline.
+The purpose of the baseline is to ensure that infants do not have systematic preferences for the target or distractor (greater interest in a cat compared to cup) which may drive PTL scores in the post-naming phase.
+As described in the Data Analysis sub-section of the Methods, there was considerable variation across papers in way that baseline was calculated, resulting in different measured outcomes or dependent variables.
+Over half of the experimental conditions (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post_naming_effect"])`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase.
+This results in one value, which is then compared with a chance value of 0.
+When positive, this indicates that infants increased their looks to the target after hearing the naming label (correct or mispronounced) relative to the pre-naming baseline PTL.
+We will refer to this dependent variable as the Difference Score.
+Another dependent variable, which was used in `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` experimental conditions, directly compared compared the post- and pre-naming PTL scores with one another.
+This requires two values, one for the pre-naming phase and one for the post-naming phase.
+A greater post compared to pre-naming phase PTL indicates that increased their target looks after hearing the naming label.
+We will refer to this dependent variable as Pre vs.
+Post.
+Finally, the remaining `r with(dv_info, n_exp_conditions[within_measure == "post"])` experimental conditions compared the post-naming PTL score with a chance value of 50%.
+Here, the infants' pre-naming phase preferences are not considered and instead target fixations are evaluated based on the likelihood to fixate one of two pictures.
+We will refer to this dependent variable as Post.
+
+The Difference Score and Pre vs.
+Post can be considered similar to one another, in that they are calculated on the same type of data and consider pre-naming preferences.
+The Post dependent variable, in contrast, does not consider pre-naming preferences.
+To our knowledge, there is no theory or evidence to drive choice of dependent variable, which may explain the wide variation in dependent variable reported in the papers included in this meta-analysis.
+We next explored whether the type of dependent variable calculated influenced sensitivity to mispronunciations.
+Considering that the dependent variable Post differs in its consideration of pre-naming preferences, we directly compared mispronunciation sensitivity between Post as a reference condition and both Difference Score and Pre vs.
+Post dependent variables.
+
+```{r dependent_variable}
+
+dat$dv_label <- ifelse(dat$within_measure=="post", "Post",
+                       ifelse(dat$within_measure == "pre_post", "Post vs. Pre",
+                              "Difference Score"))
+
+dat$dv_label <- factor(dat$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
+
+db_ET_MP$dv_label <- ifelse(db_ET_MP$within_measure=="post", "Post",
+                       ifelse(db_ET_MP$within_measure == "pre_post", "Post vs. Pre",
+                              "Difference Score"))
+
+db_ET_MP$dv_label <- factor(db_ET_MP$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
+
+##########
+
+rma_within <- rma.mv(g_calc, g_var_calc, mods = ~dv_label, data = db_ET_MP, random = ~collapse | short_cite)
+
+rma_within_effprepost <- coef(summary(rma_within))[2,]
+rma_within_effdiff <- coef(summary(rma_within))[3,]
+
+ rma_within_MS <- rma.mv(g_calc, g_var_calc, mods = ~dv_label*condition, data = dat, random = ~collapse | short_cite)
+
+  rma_within_MS_effprepost <- coef(summary(rma_within_MS))[5,]
+  rma_within_MS_effdiff <- coef(summary(rma_within_MS))[6,]
+
+  # age
+
+ rma_within_AGE <- rma.mv(g_calc, g_var_calc, mods = ~dv_label*age.C, data = db_ET_MP, random = ~collapse | short_cite)
+
+   rma_within_AGE_effprepost <- coef(summary(rma_within_AGE))[5,]
+   rma_within_AGE_effdiff <- coef(summary(rma_within_AGE))[6,]
+
+  rma_within_AGE_MS <- rma.mv(g_calc, g_var_calc, mods = ~dv_label*age.C*condition, data = dat, random = ~collapse | short_cite)
+
+    rma_within_AGE_MS_effprepost <- coef(summary(rma_within_AGE_MS))[11,]
+    rma_within_AGE_MS_effdiff <- coef(summary(rma_within_AGE_MS))[12,]
+
+```
+
+We first assessed whether the choice of dependent variable had an impact on the size of mispronunciation sensitivity.
+First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images, including dependent variable as a moderator.
+The moderator test was significant `r mod_test(rma_within)`.
+The estimates for both the Pre vs.
+Post ($\beta$`r full_estimate(rma_within_effprepost)`) and Difference Score ($\beta$`r full_estimate(rma_within_effdiff)`) dependent variables were significantly smaller than that of the Post dependent variable.
+This suggests that reported looks to the target upon hearing a mispronunciation were greatest when the dependent variable was Post.
+We next assessed whether he dependent variable was related to mispronunciation sensitivity.
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant `r mod_test(rma_DistractorOverlapMS)`.
-The estimate for the interaction between condition and distractor overlap was small, but significant ($\beta$ `r full_estimate(sum_eff2)`, suggesting that mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap.
-This relationship be seen in Figure 5a.
-
-```{r DistractorOverlap_age}
-
-# object recognition
-db_ET_MPo = db_ET_MP %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "no")
-
-db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no"))
-
-rma_DistractorOverlap_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)
-
-sum_eff1 <- coef(summary(rma_DistractorOverlap_age))[4,]
-
-# mispronunciation sensitivity
-dat_MPo = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "no")
-
-dat_MPo$distractor_overlap <- factor(dat_MPo$distractor_overlap, levels = c("onset", "no"))
-
-rma_DistractorOverlap_age_MS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap*condition, data = dat_MPo, random = ~ collapse | short_cite)
-
-#summary(rma_DistractorOverlap_age_MS)
-
-sum_eff2 <- coef(summary(rma_DistractorOverlap_age_MS))[8,]
-
-```
-
-Although we did not have any specific predictions about the relationship between infant age and the impact of distractor overlap on mispronunciation sensitivity, we included an exploratory analysis to examine this relationship.
-First, for object recognition in response to mispronunciations, when age in addition to distractor overlap was also included as a moderator, the moderator test was not significant, `r mod_test(rma_DistractorOverlap_age)`, and the estimate for the interaction between age and distractor overlap was small, $\beta$`r full_estimate(sum_eff1)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for both onset and no overlap, regardless of infant age.
-We next assessed whether the relationship between distractor overlap and mispronunciation sensitivity was modulated by age.
+The moderator test was significant, `r mod_test(rma_within_MS)`.
+The estimate for the interaction between Pre vs.
+Post and condition was significantly smaller than that of the Post dependent variable ($\beta$`r full_estimate(rma_within_MS_effprepost)`), but the difference between the Difference Score and Post in the interaction with condition was small and not significant ($\beta$`r full_estimate(rma_within_MS_effdiff)`).
+This relationship is plotted in Figure 4a.
+The results suggest that dependent variable calculated significantly impacted the size fo the mispronunciation sensitivity effect, such that Post.
+vs.
+Pre showed a smaller mispronunciation sensitivity effect than Post, but no difference between the Difference Score and Post.
+
+We next examined whether the type of dependent variable calculated modulated the development of mispronunciation sensitivity.
+For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was significant `r mod_test(rma_post_dur_AGE)`, but the estimates for the interaction between Pre vs.
+Post and age ($\beta$`r full_estimate(rma_within_AGE_effprepost)`) as well as Difference Score and age ($\beta$`r full_estimate(rma_within_AGE_effdiff)`) were not different from that of the Post dependent variable.
+This suggests that upon hearing a mispronunciation, infant measured looks to the target image were similar, regardless of infant age or type of dependent variable.
+We next assessed whether the relationship between dependent variable and mispronunciation sensitivity was modulated by age.
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, `r mod_test(rma_DistractorOverlap_age_MS)` and the estimate for the three-way interaction between age, condition, and distractor overlap was significant, but relatively small ($\beta$ = `r full_estimate(sum_eff2)`.
-As can be seen in Figure 5b, the difference between correct pronunciations and mispronunciations (mispronunciation sensitivity) stays steady across infant ages for both target words paired with distractors containing onset overlap with the target word as well as distractors containing no overlap.
-As infants aged, however, overall recognition (regardless of condition) increased for target-distractor pairs containing onset overlap, whereas for overall recognition decreased for target-distractor pairs containing no overlap.
-
-## Figure 5
-
-```{r PlotDistOverlap_cond_age}
-
-db_ET_MPo = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "no")
-
-db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no"))
-
-db_ET_MPo$condition_label <- ifelse(db_ET_MPo$condition==1, "Correct", "Mispronunciation")
-
-db_ET_MPo$distractor_label <- ifelse(db_ET_MPo$distractor_overlap=="onset", "Onset Overlap", "No Overlap")
-
-p.DIOV_M <- ggplot(db_ET_MPo, aes(condition_label, g_calc, fill = condition_label)) + 
-  facet_grid(.~distractor_label)+
+The moderator test was significant `r mod_test(rma_within_AGE_MS)`.
+The estimate for the interaction between Pre vs.
+Post, condition, and age was significantly smaller than that of the Post dependent variable ($\beta$`r full_estimate(rma_within_AGE_MS_effprepost)`), but the difference between the Difference Score and Post in the interaction with condition and age was small and not significant ($\beta$`r full_estimate(rma_within_AGE_MS_effdiff)`).
+This relationship is plotted in Figure 4b.
+When the dependent variable was Pre vs.
+Post, mispronunciation sensitivity decreased with infant development, while in comparison, when the dependent variable was Post, mispronunciation sensitivity increased with infant development.
+There was no difference in mispronunciation sensitivity change with infant development between the Post and Difference Score dependent variables.
+
+## (Insert Figure 4 about here)
+
+```{r Plot_Within_cond_age_diff_score, echo = FALSE, fig.width=10,fig.height=11}
+
+dat.cm <- dat[,c("short_cite", "is_correct", "is_mp", "within_measure", "condition", "g_calc", "weights_g", "mean_age_1", "n_1")]
+
+dat.c <- subset(dat.cm, is_correct == 1)
+dat.m <- subset(dat.cm, is_mp == 1)
+
+dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "within_measure", "mean_age_1", "n_1"))
+
+dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
+
+dat.cm$condition_label <- ifelse(dat.cm$is_correct.x==1, "Correct", "Mispronunciation")
+
+dat.cm$dv_label <- ifelse(dat.cm$within_measure=="post", "Post",
+                       ifelse(dat.cm$within_measure == "pre_post", "Post vs. Pre",
+                              "Difference Score"))
+
+dat.cm$dv_label <- factor(dat.cm$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
+
+ms.agg <- ggplot(dat.cm, aes(dv_label, Misp_sensitivity, fill = dv_label)) + 
+  #facet_grid(.~dv_label)+
     geom_violin() + 
@@
   geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Effect size Hedges' g")
-
-p.DIOV_AGE <- ggplot(db_ET_MPo, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-    facet_grid(.~distractor_label)+
-  geom_point(aes(size = weights_g),show.legend=FALSE) +
+  ylab("Misp. Sensitivity")
+
+ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = dv_label)) + 
+    #facet_grid(.~dv_label)+
+  geom_point(aes(size = n_1),show.legend=FALSE) +
   labs(caption="b")+
   geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
   scale_colour_manual(values=cbPalette)+
@@
   xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
+  ylab("Misp. Sensitivity")
 
 lay <- rbind(c(1), c(2))
-
-  jpeg(filename = "figures/Figure_5_Distractor_overlap_age.jpg", 
+#lay <- rbind(c(1,2))
+
+  jpeg(filename = "figures/Figure_4_Dependent_variable.jpg", 
        width = 500, height = 600, units = "px")
 
-ger.plot.age <- grid.arrange(p.DIOV_M, p.DIOV_AGE,
+ger.plot.age <- grid.arrange(ms.agg, ms.age,
                              layout_matrix = lay)
@@
 
-```
-
-### Position of mispronunciation
-
-```{r Location_descrip}
-
-misp_location_info <- dat %>%
-  group_by(mispron_location) %>%
-  summarize(n_exp_conditions =  n())
-
-```
-
-To assess whether the position of the mispronunciation has an impact on mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to mispronunciations on the onset and medial phonemes.
-We did not include data for which the mispronunciation was located on the coda (*n* = `r with(misp_location_info, n_exp_conditions[mispron_location == "coda"])`), varied in regard to position (*n* = `r with(misp_location_info, n_exp_conditions[mispron_location == "coda/medial" | mispron_location == "onset/medial" | mispron_location == "onset/medial/coda"])`), or was not reported (*n* = `r with(misp_location_info, n_exp_conditions[is.na(mispron_location)])`).
-The analysis was therefore based on a subset of the overall dataset, with `r with(misp_location_info, n_exp_conditions[mispron_location == "onset"])` experimental conditions comparing a mispronunciation on the onset phoneme and `r with(misp_location_info, n_exp_conditions[mispron_location == "medial"])` experimental conditions comparing a mispronunciation on the medial phoneme.
-
-```{r Location_misp}
-#table(db_ET_MP$mispron_location)
-
-db_ET_MPl = db_ET_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("onset", "medial"))
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_Location_MP <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_MPl, random = ~collapse | short_cite)
-
-sum_eff2 <- coef(summary(rma_Location_MP))[2,]
-
-db_ET_MPl = dat %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("onset", "medial"))
-
-rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition, data = db_ET_MPl, random = ~collapse | short_cite)
-
-sum_eff2 <- coef(summary(rma_LocationCondition))[4,]
-
-```
-
-Regarding object identification in response to mispronunciations, when mispronunciation location was included as a moderator, the moderator test was not significant `r mod_test(rma_Location_MP)` and the estimate for distractor overlap was small, $\beta$`r full_estimate(sum_eff1)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was located on the onset or  medial phonemes.
-We next assessed whether mispronunciation location was related to mispronunciation sensitivity.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, `r mod_test(rma_LocationCondition)`, but the estimate for the interaction between mispronunciation location and condition was small and not significant, $\beta$`r full_estimate(sum_eff2)`.
-These results suggest that overall, the location of the mispronunciation (onset, medial) did not impact mispronunciation sensitivity.
-
-```{r PlotPositionEffect}
-
-# #dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial" |
-# #                mispron_location == "offset")
-# 
-# dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
-# 
-# dat.p = dat %>%
-#   filter(mispron_location == "onset"  | mispron_location == "medial")
-# 
-# dat.p$mispron_location <- factor(dat.p$mispron_location, levels = c("onset", "medial"))
-# 
-# 
-# p <- ggplot(dat.p, aes(condition_label, g_calc, fill = condition_label)) + 
-#   facet_grid(.~mispron_location)+
-#   geom_boxplot() + 
-#   #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-#   scale_fill_manual(values=cbPalette)+
-#   apatheme +
-#   theme(text = element_text(size=25),
-#         legend.title = element_blank(),
-#         legend.position = "bottom",
-#         axis.title.x = element_blank(),
-#         axis.text.x = element_blank(),
-#         axis.ticks.x = element_blank()) + 
-#   #xlab("Number of Features Changed") + 
-#   geom_hline(yintercept = 0, linetype="dotted") + 
-#   ylab("Effect size Hedges' g")
-# 
-# p
-# 
-#   jpeg(filename = "figures/Figure_7_Mispronunciation_position.jpg", 
-#        width = 500, height = 300, units = "px")
-# 
-#   p
-#   
-#   dev.off()
-
-```
-
-```{r Location_misp_age}
-#table(db_ET_MP$mispron_location)
-
-db_ET_MPl = db_ET_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("onset", "medial"))
-
-#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
-rma_Location_MP_age <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
-
-sum_eff1 <- coef(summary(rma_Location_MP_age))[4,]
-
-db_ET_MPl = dat %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("onset", "medial"))
-
-rma_LocationCondition_age <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
-
-sum_eff2 <- coef(summary(rma_LocationCondition))[8,]
-
-```
-
-According to TRACE, infants should become more sensitive to onset mispronunciations as their lexicon size grows, but sensitivity to medial mispronunciations should stay the same (Mayor & Plunkett, 2014).
-To examine this relationship, we included age as a moderator.
-First, for object recognition in response to mispronunciations, when age in addition to mispronunciation location was also included as a moderator, the moderator test was not significant, `r mod_test(rma_Location_MP)` and the estimate for the interaction between distractor overlap and age was small, $\beta$`r full_estimate(sum_eff1)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for both onset and medial mispronunciations, regardless of infant age.
-We next assessed whether the relationship between mispronunciation location and mispronunciation sensitivity was modulated by age.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, `r mod_test(rma_LocationCondition)`, but the estimate for the three-way interaction between mispronunciation loction, condition, and age was small and not significant, $\beta$`r full_estimate(sum_eff2)`.
-These results provide further evidence that location of the mispronunciation (onset, medial) did not impact mispronunciation sensitivity.
-
-```{r MispLocationAgeRangeSubset}
-
-misp_location_ages <- dat %>%
-  group_by(mispron_location) %>%
-  summarize(min_age = r2(min(mean_age_1, na.rm=TRUE)),
-            max_age = r2(max(mean_age_1, na.rm=TRUE)),
-            mean_age = r2(mean(mean_age_1, na.rm=TRUE)),
-            sd_age = r2(sd(mean_age_1, na.rm=TRUE)))
-
-fn <- subset(dat, mispron_location=="onset")
-
-ff <- subset(dat, mispron_location=="medial")
-
-age_misp_location <- t.test(fn$mean_age_1, ff$mean_age_1, paired = F)
-
-#t.test(fn$mean_age_1, ff$mean_age_1)
-
-mla <- as.data.frame(misp_location_ages)
-mla <- subset(mla, mispron_location == "onset"  | mispron_location == "medial")
-min_age <- max(mla$min_age)
-max_age <- min(mla$max_age)
-
-dat_age_MP= db_ET_MP%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-dat_age_MP = dat_age_MP %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-dat_age_MP$mispron_location <- factor(dat_age_MP$mispron_location, levels = c("onset", "medial"))
-
-rma_Location_MP_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(mispron_location), data = dat_age_MP, random = ~ collapse | short_cite)
-
-misp_recog_agesub <- coef(summary(rma_Location_MP_agesub))[1,]
-
-rma_LocationAge_agesub <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(mispron_location), data = dat_age_MP, random = ~ collapse | short_cite)
-
-#summary(rma_Location_MP)
-
-misp_MS_agesub <- coef(summary(rma_LocationAge_agesub))[4,]
-
-# misp sensitivity
-dat_age= dat%>%
-  filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
-dat_age = dat_age %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial")
-
-dat_age$mispron_location <- factor(dat_age$mispron_location, levels = c("onset", "medial"))
-
-rma_Location_MS_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(mispron_location)*condition, data = dat_age, random = ~ collapse | short_cite)
-
-misp_recog_Age_agesub <- coef(summary(rma_Location_MS_agesub))[4,]
-
-rma_LocationAgeMS_agesub <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(mispron_location), data = dat_age, random = ~ collapse | short_cite)
-
-misp_MS_Age_agesub <- coef(summary(rma_LocationAgeMS_agesub))[8,]
-
-#summary(rma_Distractor_MS)  
-```
-
-Although we anticipated that older children may be more impacted by the position of a mispronunciation, we found no relationship.
-Inspection of the ages tested using on onset and medial mispronunciations, however, revealed differences.
-Infants tested on onset mispronunciations were older (*M* = `r with(misp_location_ages, mean_age[mispron_location == "onset"])` days, *SD* = `r with(misp_location_ages, sd_age[mispron_location == "onset"])`, range = `r with(misp_location_ages, min_age[mispron_location == "onset"])` - `r with(misp_location_ages, max_age[mispron_location == "onset"])`) than those infants tested on medial mispronunciations (*M* = `r with(misp_location_ages, mean_age[mispron_location == "medial"])` days, *SD* = `r with(misp_location_ages, sd_age[mispron_location == "medial"])`, range = `r with(misp_location_ages, min_age[mispron_location == "medial"])` - `r with(misp_location_ages, max_age[mispron_location == "medial"])`), which a two-sample t-test revealed to be a significant difference, *t*(`r r2(age_misp_location$parameter)`) = `r r2(age_misp_location$statistic)`, *p* `r psig(age_misp_location$p.value)`).
-
-To ensure that the lack of a difference wasn't due to the ages of infants tested with onset and medial mispronunciations, we repeated the previous model analyses on a subset of papers that tested infants at ages where onset and medial mispronunciations were tested (`r min_age` - `r max_age` days).
-The analyses on this subset of data did not differ from that of the analyses conducted on the entire data set.
-
-[Katie: ultimately, the subset analysis doesn't show anything :( What conclusions can we draw?]
-
-### Type of mispronunciation (consonant or vowel)
-
-```{r CV_descript}
-
-CV_info <- dat %>%
-  group_by(type_feature) %>%
-  summarize(n_exp_conditions =  n())
-
-CV_location_info <- dat %>%
-  group_by(type_feature, mispron_location) %>%
-  summarize(n_exp_conditions =  n())
-
-```
-
-To assess whether the type of mispronunciation impacts sensitivity to mispronunciations, we calculated the meta-analytic effect for object identification in response to the type of mispronunciation.
-Although most theoretical discussion of mispronunciation type has focused on consonants and vowels, our dataset also included tone mispronunciations.
-In our analysis, we were interested in the difference between consonants and vowels, but also include an exploratory analysis of responses to tones, consonants, and vowels.
-We therefore conducted two sets of analyses, one analyzing consonants and vowels alone and a second comparing responses to tones with that of consonants and vowels, separately.
-For the latter analysis, tones were coded as the reference condition.
-We did not include data for which mispronunciation type varied within experiment and was not reported separately (*n* = `r with(CV_info, n_exp_conditions[type_feature == "consonant_and_vowel" | type_feature == "consonant_vowel_tone"])`).
-The analysis was therefore based on a subset of the overall dataset, with `r with(CV_info, n_exp_conditions[type_feature == "consonant"])` experimental conditions comparing a consonant mispronunciation, `r with(CV_info, n_exp_conditions[type_feature == "vowel"])` experimental conditions comparing a vowel mispronunciation, and `r with(CV_info, n_exp_conditions[type_feature == "tone"])` experimental conditions comparing a tone mispronunciation.
-Below, we first report the set of analyses comparing consonants with vowels before moving on to the second set of exploratory analyses comparing tones with that of consonants and vowels.
-
-[KATIE] WHAT DO YOU THINK ABOUT THIS?
-WE HAVE THE TONES AND ITS A NOVEL, INTERESTING THING, I THINK, AND PERHAPS WORTH IT TO INCLUDE A COMPARISON OF TONES ALONGSIDE THE MORE THEORETICALLY IMPORTANT COMPARISON BETWEEN CONSONANTS AND VOWELS.
-
-```{r MPtype_cv}
-
-# C vs. V
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel")
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("consonant", "vowel"))
-
-rma_TypeFeaturesMP <- rma.mv(g_calc, g_var_calc, mods = ~type_feature, data = db_MP_type, random = ~collapse | short_cite)
-
-sum_eff1 <- coef(summary(rma_TypeFeaturesMP))[2,]
-
-# C vs. V with condition
-
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition, data = db_type, random = ~collapse | short_cite)
-
-sum_eff2 <- coef(summary(rma_TypeFeaturesMP_Condition))[4,]
-
-```
-
-We first analyzed experimental conditions where mispronunciation type was either a consonant or vowel.
-Regarding object identification in response to mispronunciations, when mispronunciation type was included as a moderator, the moderator test was not significant, `r mod_test(rma_Location_MP)` and the estimate for mispronunciation type was small, $\beta$`r full_estimate(sum_eff1)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was a consonant or a vowel.
-We next assessed whether type of mispronunciation (consonant or vowel) was related to mispronunciation sensitivity.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, `r mod_test(rma_LocationCondition)`, but the estimate for the interaction between mispronunciation type and condition was small and not significant, $\beta$`r full_estimate(sum_eff2)`.
-These results suggest that overall, the type of  mispronunciation (consonant vs.
-vowel) did not impact mispronunciation sensitivity.
-
-```{r MPtype_cv_age}
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("consonant", "vowel"))
-
-rma_TypeFeaturesMPage <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)
-
-sum_eff1 <- coef(summary(rma_TypeFeaturesMPage))[4,]
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~collapse | short_cite)
-
-sum_eff2 <- coef(summary(rma_TypeFeaturesMP_Condition))[8,]
-
-```
-
-We next examined whether age modulates object recognition or mispronunciation sensitivity when the mispronunciation is a consonant or vowel.
-For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant, `r mod_test(rma_TypeFeaturesMPage)` and the estimate for the interaction between mispronunciation type and age was small, $\beta$`r full_estimate(sum_eff1)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was on a consonant or vowel phoneme, regardless of their age.
-We next assessed whether the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity was modulated by age.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, `r mod_test(rma_LocationCondition)`, and the estimate for the three-way interaction between mispronunciation type, condition, and age was small, but significant, $\beta$`r full_estimate(sum_eff2)`.
-As can be seen in Figure 6, as infants age, mispronunciation sensitivity grows larger for vowel mispronunciations but becomes smaller for consonant mispronunciations.
-Noticeably, mispronunciation sensitivity appears greater for consonant compared to vowel mispronunciations at younger ages, but this difference shifts as infants age.
-
-## Figure 6
-
-```{r PlotCVEffect_cond_age}
-
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
-dat_type$type_feature <- ifelse(dat_type$type_feature == "consonant", "Consonant", "Vowel")
-
-#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
-
-#dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-
-dat_type$condition_label = ifelse(dat_type$condition==1, "Correct", "Mispronunciation")
-
-p <- ggplot(dat_type, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-    facet_grid(.~type_feature)+
-  geom_point(aes(size = weights_g),show.legend=FALSE) + 
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_6_FeatureType_Cond_Age.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-```{r MPtype_cv_lang_descript}
-
-family <- dat %>%
-  group_by(lang_family) %>%
-  summarize(count = n())
-
-lang_family <- dat %>%
-  group_by(native_lang, lang_family) %>%
-  summarize(count = n())
-
-cv_family <- dat %>%
-  group_by(type_feature, lang_family) %>%
-  summarize(count = n())
-
-```
-
-```{r MPtype_cv_lang}
-
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("consonant", "vowel"))
-
-db_MP_type <- subset(db_MP_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeaturesMPfam <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family, data = db_MP_type, random = ~collapse | short_cite)
-
-sum_eff1 <- coef(summary(rma_TypeFeaturesMPfam))[4,]
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-db_type <- subset(db_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeaturesMPC <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family, data = db_type, random = ~collapse | short_cite)
-
-sum_eff2 <- coef(summary(rma_TypeFeaturesMPC))[7,]
-sum_eff3 <- coef(summary(rma_TypeFeaturesMPC))[8,]
-
-# summary(glht(rma_TypeFeaturesMPC, linfct=cbind(contrMat(rep(1,8), type="Tukey"))), test=adjusted("none"))
-# 
-# ranef(rma_TypeFeaturesMPC)
-
-```
-
-To examine whether infants' native language impacts sensitivity to consonant and vowel mispronunciations, we classified infants into language families.
-Infants learning American English (*n* = `r with(lang_family, count[native_lang == "American English"])`), British English (*n* = `r with(lang_family, count[native_lang == "British English"])`), Danish (*n* = `r with(lang_family, count[native_lang == "Danish"])`), Dutch (*n* = `r with(lang_family, count[native_lang == "Dutch"])`), and German (*n* = `r with(lang_family, count[native_lang == "German"])`) were classified into the Germanic language family (*n* = `r with(family, count[lang_family == "Germanic"])`).
-Infants learning Catalan (*n* = `r with(lang_family, count[native_lang == "Catalan"])`), Spanish (*n* = `r with(lang_family, count[native_lang == "Spanish"])`), French (*n* = `r with(lang_family, count[native_lang == "French"])`), Catalan and Spanish simultaneously (i.e.
-bilinguals; *n* = `r with(lang_family, count[native_lang == "Catalan-Spanish"])`), and Swiss French (*n* = `r with(lang_family, count[native_lang == "Swiss French"])`) were classified into the Romance language family (*n* = `r with(family, count[lang_family == "Romance"])`).
-
-For object recognition in response to a mispronunciation, including language family as a moderator resulted in a moderator test that was not significant, `r mod_test(rma_TypeFeaturesMPage)`, and the estimate for the interaction between mispronunciation type and language family was small, $\beta$`r full_estimate(sum_eff1)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for when the mispronunciation was on a consonant or vowel phoneme, regardless of the language family of their native language.
-We next assessed whether the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity was modulated by language family.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family as additional moderators.
-The moderator test was significant, `r mod_test(rma_TypeFeaturesMPage)`, and the estimate for the three-way interaction between mispronunciation type, condition, language family was large and significant , $\beta$`r full_estimate(sum_eff3)`.
-As can be seen in Figure 7, mispronunciation sensitivity for consonants was similar for Germanic and Romance languages.
-Mispronunciation sensitivity for vowels, however, was greater for Germanic compared to Romance languages.
-
-[KATIE] I'M NOT REALLY SURE WHAT THE CONDITION BY LANGUAGE FAMILY INTERACTION MEANS. SHOULD WE EVEN INTERPRET IT? MAYBE THAT THE ROMANCE LANGUAGE FAMILY HAD LOWER MISPRONUNCIATION SENSITIVITY?
-
-## Figure 7
-
-```{r PlotCVEffect_Lang}
-
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
-dat_type$type_feature <- ifelse(dat_type$type_feature == "consonant", "Consonant", "Vowel")
-
-#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
-
-dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-
-dat_type_sub$condition_label = ifelse(dat_type_sub$condition==1, "Correct", "Mispronunciation")
-
-p <- ggplot(dat_type_sub, aes(condition_label, g_calc, fill = condition_label)) + 
-  facet_grid(.~type_feature*lang_family)+
-    geom_violin() + 
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
-  #geom_line(y= 0, linetype="dotted") + 
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-    scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        axis.text.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  xlab("Language Family") + 
-  ylab("Effect size Hedges' g")
-p
-
- jpeg(filename = "figures/Figure_7_FeatureType_Cond_LangFam.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-```{r MPtype_cv_lang_age}
-
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("consonant", "vowel"))
-
-db_MP_type <- subset(db_MP_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeaturesMPfam <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*lang_family*age.C, data = db_MP_type, random = ~collapse | short_cite)
-
- sum_eff1 <- coef(summary(rma_TypeFeaturesMPfam))[8,]
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-db_type <- subset(db_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeaturesMPC <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family*age.C, data = db_type, random = ~collapse | short_cite)
-
-sum_eff2 <- coef(summary(rma_TypeFeaturesMPC))[7,]
-sum_eff3 <- coef(summary(rma_TypeFeaturesMPC))[8,]
-
-# summary(glht(rma_TypeFeaturesMPC, linfct=cbind(contrMat(rep(1,8), type="Tukey"))), test=adjusted("none"))
-# 
-# ranef(rma_TypeFeaturesMPC)
-
-```
-
-Finally, we examined the relationship between language family and infant age and mispronunciation sensitivity to consonants and vowels.
-For object recognition in response to a mispronunciation, including language family and infant age as a moderator resulted in a moderator test that was significant, `r mod_test(rma_TypeFeaturesMPage)`, and the estimate for the three-way interaction between mispronunciation type, language family, and age was small, but significant , $\beta$`r full_estimate(sum_eff3)`.
-As can be seen in Figure 8, looks to the target in response to a mispronunciation increased with age for infants learning a Germanic language, regardless of whether those mispronunciations were consonants or vowels.
-In contrast, infants learning Romance languages have an even greater increase with age in target looks in response to consonant mispronunciations, but there was no change with age for vowel mispronunciations.
-We next assessed whether the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity was modulated by language family and age.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family and age as additional moderators.
-The moderator test was significant, `r mod_test(rma_TypeFeaturesMPC)`, and the estimate for the four-way interaction between mispronunciation type, condition, language family, and age was small, but significant , $\beta$`r full_estimate(sum_eff3)`.
-As can also be seen in Figure 8, for infants learning Germanic languages, increasing age was related to increasing mispronunciation sensitivity for vowel mispronunciations, but decreasing sensitivity for consonant mispronunciations.
-In contrast, infants learning Romance languages have an even greater increase with age in sensitivity to vowel mispronunciations.
-Surprisingly, sensitivity to consonant mispronunciations shows a reversal in infants learning Romance languages: the growth in target looks for consonant mipronunciations increases and surpases that of target looks for correct pronunciations.
-
-[KATIE] AGAIN, THERE ARE ADDITIONAL INTERACTIONS THAT ARE SIGNIFICANT... SHOULD THEY BE INTERPRETED? ALSO, WTF ROMANCE LANGUAGES? IS IT JUST NOT ENOUGH DATA?
-
-## Figure 8
-
-```{r PlotCVEffect_cond_age_fam}
-
-dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
-dat_type$type_feature <- ifelse(dat_type$type_feature == "consonant", "Consonant", "Vowel")
-
-#db_MP_type <- subset(db_ET_MP, type_feature != "consonant_and_vowel")
-
-dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
-
-dat_type_sub$condition_label = ifelse(dat_type_sub$condition==1, "Correct", "Mispronunciation")
-
-p <- ggplot(dat_type_sub, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-    facet_grid(.~type_feature*lang_family)+
-  geom_point(aes(size = weights_g),show.legend=FALSE) + 
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Effect size Hedges' g")
-
-p
-
-  jpeg(filename = "figures/Figure_8_FeatureType_Cond_Age_LangFam.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p
-
-  dev.off()
-
-```
-
-```{r MPtype_cvt}
-
-# C vs. V vs. T
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" | type_feature == "tone")
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("tone", "consonant", "vowel"))
-
-rma_TypeFeaturesMPT <- rma.mv(g_calc, g_var_calc, mods = ~type_feature, data = db_MP_type, random = ~collapse | short_cite)
-
-# C vs. V vs. T with condition
-
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel"| type_feature == "tone")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("tone", "consonant", "vowel"))
-
-rma_TypeFeaturesMP_ConditionT <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition, data = db_type, random = ~collapse | short_cite)
-
-sum_eff2c <- coef(summary(rma_TypeFeaturesMP_ConditionT))[5,]
-sum_eff2v <- coef(summary(rma_TypeFeaturesMP_ConditionT))[6,]
-
-```
-
-Although we had no predictions regarding mispronunciation sensitivity to tone mispronunciations, we included an exploratory analysis to examine whether responses to tone mispronunciations were different from that of consonants or vowels.
-Regarding object identification in response to mispronunciations, when mispronunciation type was included as a moderator, the moderator test was not significant QM(`r r2(rma_TypeFeaturesMPT$m)`) = `r r2(rma_TypeFeaturesMPT$QM)`, *p* `r psig(rma_TypeFeaturesMPT$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were similar for tone mispronunciations in comparison with both consonants and vowels.
-We next assessed whether type of mispronunciation (tone, consonant, vowel) was related to mispronunciation sensitivity.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_ConditionT$m)`) = `r r2(rma_TypeFeaturesMP_ConditionT$QM)`, *p* `r psig(rma_TypeFeaturesMP_ConditionT$QMp)`.
-The interaction between condition and consonant mispronunciations was not significant $\beta$ = `r r2(sum_eff2c$estimate)`, (SE = `r r2(sum_eff2c$se)`, 95% CI [`r r2(sum_eff2c$ci.lb)`, `r r2(sum_eff2c$ci.ub)`], *p* `r psig(sum_eff2c$pval)`), suggesting that there was no difference in looks to the target in response to consonant and tone mispronunciations.
-The interaction between condition and vowel mispronunciations was also not significant $\beta$ = `r r2(sum_eff2v$estimate)`, (SE = `r r2(sum_eff2v$se)`, 95% CI [`r r2(sum_eff2v$ci.lb)`, `r r2(sum_eff2v$ci.ub)`], *p* `r psig(sum_eff2v$pval)`), suggesting that there was no difference in looks to the target in response to vowel and tone mispronunciations.
-
-```{r MPtype_cvt_age}
-db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" | type_feature == "tone")
-
-db_MP_type$type_feature <- factor(db_MP_type$type_feature, levels = c("tone", "consonant", "vowel"))
-
-rma_TypeFeaturesMPage <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" | type_feature == "tone")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("tone", "consonant", "vowel"))
-
-rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~collapse | short_cite)
-
-sum_eff1 <- coef(summary(rma_TypeFeaturesMP_Condition))[11,]
-sum_eff2 <- coef(summary(rma_TypeFeaturesMP_Condition))[12,]
-
-```
-
-We further included an exploratory analysis of the relationship between infant age and the impact of tone mispronunciations in comparison to consonant and vowel mispronunciations.
-First, for object recognition in response to mispronunciations, when age in addition to mispronunciation location was also included as a moderator, the moderator test was not significant, QM(`r r2(rma_TypeFeaturesMPage$m)`) = `r r2(rma_TypeFeaturesMPage$QM)`, *p* `r psig(rma_TypeFeaturesMPage$QMp)`.
-This suggests that upon hearing a mispronunciation, infants looks to the target image were not different between tone and vowel or tone and consonant mispronunciations, regardless of their age.
-We next assessed whether the relationship between mispronunciation type (tone, consonant, vowel) and mispronunciation sensitivity was modulated by age.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, QM(`r r2(rma_TypeFeaturesMP_Condition$m)`) = `r r2(rma_TypeFeaturesMP_Condition$QM)`, *p* `r psig(rma_TypeFeaturesMP_Condition$QMp)`, but the interactions between condition, age, and both consonant mispronciations ($\beta$ = `r r2(sum_eff1$estimate)`, SE = `r r2(sum_eff1$se)`, 95% CI [`r r2(sum_eff1$ci.lb)`, `r r2(sum_eff1$ci.ub)`], *p* `r psig(sum_eff1$pval)`) and vowel mispronunciations ($\beta$ = `r r2(sum_eff2$estimate)`, SE = `r r2(sum_eff2$se)`, 95% CI [`r r2(sum_eff2$ci.lb)`, `r r2(sum_eff2$ci.ub)`], *p* `r psig(sum_eff2$pval)`) were not significant.
-Infants' sensitivity to tone mispronunciations compared to consonant or vowel mispronunciations did not differ with age.
-
-[KATIE] WORTH IT TO INCLUDE LANGUAGE FAMILY ANALYSES TOO? I'M THINKING NO
+grid.draw(ger.plot.age)
+
+```
+
+## Controlling for researcher choice
+
+```{r reanalysis_misp_sens_dv_label}
+
+dat$dv_label <- ifelse(dat$within_measure=="post", "Post",
+                       ifelse(dat$within_measure == "pre_post", "Post vs. Pre",
+                              "Difference Score"))
+
+dat$dv_label <- factor(dat$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
+
+db_ET_MP$dv_label <- ifelse(db_ET_MP$within_measure=="post", "Post",
+                       ifelse(db_ET_MP$within_measure == "pre_post", "Post vs. Pre",
+                              "Difference Score"))
+
+db_ET_MP$dv_label <- factor(db_ET_MP$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
+
+db_ET_correct$dv_label <- ifelse(db_ET_correct$within_measure=="post", "Post",
+                       ifelse(db_ET_correct$within_measure == "pre_post", "Post vs. Pre",
+                              "Difference Score"))
+
+db_ET_correct$dv_label <- factor(db_ET_correct$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
+
+rma_correct_DV = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ collapse | short_cite, ~ dv_label | short_cite))
+
+#anova(rma_correct_DV, rma_correct)
+
+rma_MP_DV = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ collapse | short_cite, ~ dv_label | short_cite))
+
+#anova(rma_MP_DV, rma_MP)
+
+rma_MPeffect_DV <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ collapse | short_cite, ~ dv_label | short_cite))
+
+#anova(rma_MPeffect_DV, rma_MPeffect)
+
+rma_correct_age_DV = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ collapse | short_cite, ~ dv_label | short_cite))
+
+#anova(rma_correct_age_DV, rma_correct_age)
+
+rma_MP_age_DV = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ collapse | short_cite, ~ dv_label | short_cite))
+
+#anova(rma_MP_age_DV, rma_MP_age)
+
+rma_MPeffect_age_DV <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ collapse | short_cite, ~ dv_label | short_cite))
+
+#anova(rma_MPeffect_age_DV, rma_MPeffect_age)
+
+```
+
+```{r reanalysis_misp_sens_post_dur}
+
+rma_correct_post_dur = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ collapse | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+
+#anova(rma_correct_post_dur, rma_correct)
+
+rma_MP_post_dur = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ collapse | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+
+#anova(rma_MP_post_dur, rma_MP)
+
+rma_MPeffect_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ collapse | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+
+#anova(rma_MPeffect_post_dur, rma_MPeffect)
+
+rma_correct_age_post_dur = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ collapse | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+
+#anova(rma_correct_age_post_dur, rma_correct_age)
+
+rma_MP_age_post_dur = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ collapse | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+
+#anova(rma_MP_age_post_dur, rma_MP_age)
+
+rma_MPeffect_age_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ collapse | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+
+#anova(rma_MPeffect_age_post_dur, rma_MPeffect_age)
+
+```
 
@@
 
-** Size of Mispronunciation **
-
-  + graded sensitivity to number of features changed in a mispronunciation
-  + importance for controlling in experimental design
-  + Perhaps a call for more studies to include multiple number of features changed, so that this can be assessed? There was a narrow age where this was actually manipulated.
-
-** Distractor Familiarity **
-
-  + Not really sure, check the results. A key interaction is significant in one model but not the other.
-  + Again, ages not matched very well for the two groups here. Similar pattern of results for age subset analysis.
-
-** Phonological overlap between target and distractor **
-
-  + mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap
-  + this is rather the opposite of what one would expect, right?
-  + [Katie: Yeah! Its really strange, so the time course analysis suggestion of yours is a very good one!]
-  + Maybe it would be useful to have time course analyses to address this issue further
-  + As infants aged, overall recognition (regardless of condition) increased for target-distractor pairs containing onset overlap, whereas overall recognition decreased for target-distractor pairs containing no overlap.
-
-** Position of mispronunciation **
-
-  + really no impact at all
-
-** Type of mispronunciation **
-
-  + Overall, no difference between consonants and vowels 
-  + Consonant mispronunciation sensitivity decreases with age
-  + Vowel mispronunciation sensitivity increases with age
-  + mispronunciation sensitivity for consonants similar for Germanic and Romance languages
-  + Mispronunciation sensitivity for vowels greater for Germanic compared to Romance languages
-  + For Germanic infants, increasing age was related to increasing mispronunciation sensitivity for vowel mispronunciations, but decreasing sensitivity for consonant mispronunciations. 
-  + For Romance infants, an even greater increase with age in sensitivity to vowel mispronunciations. 
-  + For Romance infants, the growth in target looks for consonant mipronunciations increases and surpases that of target looks for correct pronunciations
-  + exploratory analyses with tone mispronunciations suggest no great difference in sensitivity when compared to consonant and vowel mispronunciations
+** Data Analysis Choices **
+
+  + Post-naming phase size and dependent variable impact misp sensitivity development
+  + Offset time does not impact misp sensitivity development
+  + the first two do not have theoretical frameworks to guide researchers, whereas offset time does
 
@@
 
-Discussing the Moderator Analyses
-Maybe put them together into the ones that worked out as we predicted and those that didn't?
-So, here is evidence that supports existing arguments, that doesn't need to be a huge chunk.
-But then more space devoted to moderator analyses that didn't work out according to predictions.
-
-It should be noted that the majority of consonant mispronunciations were located on the onset phoneme (*n* = `r with(CV_location_info, n_exp_conditions[type_feature == "consonant" & mispron_location == "onset"])`; total consonant conditions, *n* = `r with(CV_info, n_exp_conditions[type_feature == "consonant"])`), while the majority of vowel mispronunciations were located on the medial phoneme (*n* = `r with(CV_location_info, n_exp_conditions[type_feature == "vowel" & mispron_location == "medial"])`; total vowel conditions, *n* = `r with(CV_info, n_exp_conditions[type_feature == "vowel"])`).
-In their analysis using TRACE, Mayor and Plunkett (2014) found that the difference between sensitivity to consonant and vowel mispronunciations was due to infants' lexical knowlege consisting of a majority consonant onset words.
-
-[KATIE] COME BACK TO THIS.
-
 \newpage

### 2018-11-07 Paper_Analyses.tex
developmental focused manuscript, researcher choices analysis

@@
 
-Next to this core theoretically relevant investigation of the shape of
-development of infants' mispronunciation sensitivity, we take the
-opportunity of a systematic aggregation of data to address open
-questions regarding differences in experiment design and whether changes
-in procedure and stimuli tap into significantly different aspects of
-infants' ability to detect mispronunciations.
-
-In designing their mispronunciation stimuli, Swingley and Aslin (2000)
-chose consonant mispronunciations that were likely to confuse adults
-(Miller \& Nicely, 1955). Subsequent research has settled on
-systematically modulating phonemic features to achieve mispronunciations
-of familiar words. By utilizing mispronunciations consisting of phonemic
-changes, these experiments examine infants' sensitivity to factors that
-change the identity of a word on a measurable level (i.e.~1-feature,
-2-features, 3-features, etc.). The importance of controlling for the
-degree of phonological mismatch, as measured by number of features
-changed, is further highlighted by studies that find graded sensitivity
-to both consonant (White \& Morgan, 2008) and vowel (Mani \& Plunkett,
-2011) feature changes.
-
-Although most research examining sensitivity to mispronunciations
-follows a similar design, there are some notable differences. For
-example, Swingley and Aslin (2000) presented infants with pairs of
-familiar images, one serving as the labeled target and one as the
-unlabeled distractor. In contrast, White and Morgan (2008; see also Mani
-\& Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented
-infants with pairs of familiar (labeled target) and unfamiliar
-(unlabeled distractor) objects. By using an unfamiliar object as a
-distractor, the infant is presented with a viable option onto which the
-mispronounced label can be applied (Halberda, 2003; Markman, Wasow, \&
-Hansen, 2003). Infants ages 24 and 30 months associate a novel label
-with an unfamiliar object, although only 30-month-olds retained this
-label-object pairing (Bion, Borovsky, and Fernald, 2013). In contrast,
-18-month-olds did not learn to associate a novel label with an
-unfamiliar object, providing evidence that this ability is developing
-from 18 to 30 months. We may find that if mispronunciation sensitivity
-changes as children develop, that this change is modulated by whether
-the distractor used is familiar or unfamiliar. Although mispronunciation
-sensitivity in the presence of a familiar compared to unfamiliar
-distractor has not been directly compared, the baseline preference for
-familiar compared to novel stimuli is also thought to change as infants
-develop (Hunter \& Ames, 1988). Furthermore, young children have been
-found to look longer at objects for which they know the name, compared
-to objects of an unknown name (Schafer \& Plukett, 1998). In other
-words, in absentia of a label, infants may be more or less likely to
-fixate on an unfamiliar object. To account for inherent preferences to
-the target or distractor image, mispronunciation experiments typically
-compare the increase in fixations to the target image from a silent
-baseline to post-labeling or present the same yoked pairs of target and
-distractor images in in both a correct and mispronounced labelling
-context. Considering this evidence, we may expect that in older, but not
-younger, children, the presence of an unfamiliar distractor may lead to
-greater mispronunciation sensitivity than in the presence of a familiar
-distractor.
-
-Furthermore, when presenting infants with a familiar distractor image,
-some studies control the phonological overlap between the labels for the
-target and distractor. For example, when examining sensitivity to a
-mispronunciation of the target word \enquote{dog}, the vowel
-mispronunciation \enquote{dag} would be paired with a distractor image
-that shares onset overlap, such as \enquote{duck}. This ensures that
-infants can not use the onset of the word to differentiate between the
-target and distractor images (Fernald, Swingley, \& Pinto, 2001).
-Instead, infants must pay attention to the mispronounced phoneme in
-order to successfully detect the change. The influence of distractor
-overlap also depends on the position of the mispronunciation in the
-word, which can be at word onset, medial, or final positions. Models of
-spoken word processing place more or less importance on the position of
-a phoneme in a word. The COHORT model (Marslen-Wilson \& Zwitserlood,
-1989) describes lexical access in one direction, with the importance of
-each phoneme decreasing as its position comes later in the word. In
-contrast, the TRACE model (McClelland \& Elman, 1986) describes lexical
-access as constantly updating and reevaluating the incoming speech input
-in the search for the correct lexical entry, and therefore can recover
-from word onset and to a lesser extent medial mispronunciations.
-
-TRACE has also been used to model infants' sensitivity to
-mispronunciation location (Mayor \& Plunkett, 2014), finding that as
-lexicon size increases, so does sensitivity to onset mispronunciations,
-whereas medial mispronunciations do not experience similar growth. In
-early language acquisition, infants typically know more consonant
-compared to vowel onset words. When tested on their recognition of
-familiar words, therefore, younger infants would show greater
-sensitivity to onset mispronunciations, which are frequently consonant
-mispronunciations. The prevalence of consonant onset words may
-contribute to the finding that consonants carry more weight in lexical
-processing (C-bias; see Nazzi, Poltrock, \& Von Holzen, 2016 for a
-recent review). In mispronunciation sensitivity, this would translate to
-consonant mispronunciations impairing word recognition to a greater
-degree than vowel mispronunciations. Yet, the handful of studies
-directly comparing sensitivity to consonant and vowel mispronunciations
-mostly find symmetry as opposed to an asymmetry between consonants and
-vowels. English-learning 12-, 15-, 18-, and 24-month-olds (Mani \&
-Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds
-(Hojen et al., unpublished) demonstrate similar sensitivity to consonant
-and vowel mispronunciations. One study did find weak evidence for
-greater sensitivity to consonant compared to vowel mispronunciations
-(Swingley, 2016). The English-learning infants tested by Swingley were
-older than previous studies (mean age 28 months). In word learning, the
-C-bias has been found to develop later in English learning infants
-(Floccia, Nazzi, Delle Luche, Poltrock, \& Goslin, 2014; Nazzi, Floccia,
-Moquet, \& Butler, 2009). In the current meta-analysis, we attempt to
-synthesize studies examining sensitivity to consonant and vowel
-mispronunciations across different ages to determine whether infants
-generally exhibit more sensitivity to consonant compared to vowel
-mispronunciations in familiar word recognition as predicted by a learned
-account of C-bias emergence (Floccia et al., 2014; Keidel et al., 2007;
-Nazzi et al., 2016). We further examine the impact of language family on
-mispronunciation sensitivity to consonants and vowels, as C-bias
-emergence has been found to have a different developmental trajectory
-for Romance (French, Italian) compared to Germanic (British English,
-Danish) languages (Nazzi et al., 2016).
-
-{[}KATIE{]} Christina had noted something to herself for this paragraph:
-Subset by language?
-
-Finally, mispronunciation sensitivity in infants has been examined in
-many different languages, such as English, Spanish, French, Dutch,
-German, Catalan, Danish, and Mandarin Chinese (see Summary\_Table).
-Infants learning different languages have different ages of acquisition
-for words in their early lexicon, leaving direct comparisons between
-languages within the same study difficult and as a result rare. Yet,
-studies testing infants from different language backgrounds on similar
-sets of stimuli find similar sensitivity to mispronunciations
-(Ramon-Casas et al., 2009; Ramon-Casas \& Bosch, 2010). Although we do
-not explicitly compare overall mispronunciation sensitivity by language
-(although see previous paragraph for rationale to test by language
-family), we assess evidence of mispronunciation sensitivity from many
-different languages using a meta-analytic approach.
-
 Taken together, the studies we have reviewed begin to paint a picture of
@@
 one separate brushstroke and it is only by examining all of them
-together that we can achieve a better understanding. In our analysis, we
-examine the factors modulating the development of mispronunciation
-sensitivity, which are both of theoretical and practical importance.
-Meta-analyses can not only help us summarize the current state of
-research, but can also help us evaluate theories to drive future
-research and make hands-on recommendations for experiment planning.
+together that we can achieve a better understanding. Meta-analyses can
+not only help us summarize the current state of research, but can also
+help us evaluate theories to drive future research and make hands-on
+recommendations for experiment planning.
 
@@
 
-\begin{tabular}{l|l|l|l|l|l|l|l}
-\hline
-Paper & Age & Vocabulary & \# Features & Distractor & Distractor name overlap & MP Position & MP Type\\
-\hline
-Altvater-Mackensen (2010) & 22, 25 & None & 1 & Familiar, Unfamiliar & onset, novel & onset, onset/medial & consonant\\
-\hline
-Altvater-Mackensen et al. (2014) & 18, 25 & None & 0, 1 & Familiar & onset & onset & consonant\\
-\hline
-Bailey \& Plunkett (2002) & 18, 24 & Comprehension & 0, 1, 2 & Familiar & no & onset & consonant\\
-\hline
-Bergelson \& Swingley (2017) & 7, 9, 12, 6 & None & 0, NA & Familiar & no & onset/medial & vowel\\
-\hline
-Bernier \& White 2017 & 21 & None & 0, 1, 2, 3 & Unfamiliar & novel & onset & consonant\\
-\hline
-Delle Luche et al. (2015) & 20, 19 & None & 0, 1 & Familiar & onset & onset & consonant\_and\_vowel\\
-\hline
-Durrant et al. (2014) & 19, 20 & None & 0, 1 & Familiar & onset & onset & consonant\_and\_vowel\\
-\hline
-Hoehle et al. 2006 & 18 & None & 1 & Familiar & no & onset & consonant\\
-\hline
-Hojen et al. & 20 & Comprehension/Production & 2\_3 & Familiar & coda, onset & onset/medial, coda/medial & consonant\_and\_vowel, vowel, consonant\\
-\hline
-Mani \& Plunkett 2007 & 15, 18, 24, 14, 21 & Comprehension/Production & 0, 1\_2, 1 & Familiar & onset & onset & vowel, consonant\_and\_vowel, consonant\\
-\hline
-Mani \& Plunkett 2010 & 12 & Comprehension & 0, 1 & Familiar & onset & medial, onset & vowel, consonant\\
-\hline
-Mani \& Plunkett 2011 & 23, 17 & None & 0, 1\_2\_3, 1, 2, 3 & Unfamiliar & novel & medial & vowel\\
-\hline
-Mani, Coleman, \& Plunkett (2008) & 18 & Comprehension/Production & 0, 1 & Familiar & onset & medial & vowel\\
-\hline
-Ramon-Casas \& Bosch 2010 & 24, 25 & None & NA & Familiar & no & medial & vowel\\
-\hline
-Ramon-Casas et al. 2009 & 21, 20 & Production & NA & Familiar & no & medial & vowel\\
-\hline
-Ren \& Morgan, in press & 19 & None & 0, 1 & Unfamiliar & no & onset, coda & consonant\\
-\hline
-Skoruppa et al. 2013 & 24 & None & 0, 1 & Unfamiliar & onset/medial & coda & consonant\\
-\hline
-Swingley (2009) & 17 & Comprehension/Production & 0, 1 & Familiar & no & onset, coda & consonant\\
-\hline
-Swingley (2016) & 27, 28 & Production & 0, 1 & Unfamiliar & novel & onset/medial & consonant\_and\_vowel, consonant, vowel\\
-\hline
-Swingley \& Aslin (2000) & 20 & Comprehension & 0, 1 & Familiar & no & onset & consonant\_and\_vowel\\
-\hline
-Swingley \& Aslin (2002) & 15 & Comprehension/Production & 0, 1, 2 & Familiar & no & onset/medial & consonant\_and\_vowel\\
-\hline
-Swingley 2003 & 19 & Comprehension/Production & 0, 1 & Familiar & onset & onset, medial & consonant\\
-\hline
-Tamasi (2016) & 30 & None & 0, 1, 2, 3 & Unfamiliar & novel & onset & consonant\\
-\hline
-Tao \& Qinmei 2013 & 12 & None & NA & Familiar & no & NA & tone\\
-\hline
-Tao et al. 2012 & 16 & Comprehension & NA & Familiar & no & NA & tone\\
-\hline
-van der Feest \& Fikkert, 2015 & 24, 20 & None & 0, 1 & Familiar & onset & onset & consonant\\
-\hline
-van der Feest \& Johnson, 2016 & 24 & None & 0, 1 & Familiar & onset & onset & consonant\\
-\hline
-Wewalaarachchi et al. 2017 & 24 & None & 0, 1 & Unfamiliar & novel & onset/medial/coda & consonant\_vowel\_tone, vowel, consonant, tone\\
-\hline
-White \& Aslin (2011) & 18 & None & 1 & Unfamiliar & novel & medial & vowel\\
-\hline
-White \& Morgan (2008) & 18, 19 & None & 0, 1, 2, 3 & Unfamiliar & novel & onset & consonant\\
-\hline
-Zesiger \& Johr 2011 & 14 & None & 0, 1 & Familiar & no & onset, medial & consonant, vowel\\
-\hline
-Zesiger et al. (2012) & 12, 19 & Comprehension/Production & 0, 1, 2 & Familiar & no & onset & consonant\\
+\begin{tabular}{l|l|l|l}
+\hline
+Paper & Publication format & Age & Vocabulary\\
+\hline
+Altvater-Mackensen (2010) & dissertation & 22, 25 & None\\
+\hline
+Altvater-Mackensen et al. (2014) & paper & 18, 25 & None\\
+\hline
+Bailey \& Plunkett (2002) & paper & 18, 24 & Comprehension\\
+\hline
+Bergelson \& Swingley (2017) & paper & 7, 9, 12, 6 & None\\
+\hline
+Bernier \& White 2017 & proceedings & 21 & None\\
+\hline
+Delle Luche et al. (2015) & paper & 20, 19 & None\\
+\hline
+Durrant et al. (2014) & paper & 19, 20 & None\\
+\hline
+Hoehle et al. 2006 & paper & 18 & None\\
+\hline
+Hojen et al. & gray paper & 20 & Comprehension/Production\\
+\hline
+Mani \& Plunkett 2007 & paper & 15, 18, 24, 14, 21 & Comprehension/Production\\
+\hline
+Mani \& Plunkett 2010 & paper & 12 & Comprehension\\
+\hline
+Mani \& Plunkett 2011 & paper & 23, 17 & None\\
+\hline
+Mani, Coleman, \& Plunkett (2008) & paper & 18 & Comprehension/Production\\
+\hline
+Ramon-Casas \& Bosch 2010 & paper & 24, 25 & None\\
+\hline
+Ramon-Casas et al. 2009 & paper & 21, 20 & Production\\
+\hline
+Ren \& Morgan, in press & gray paper & 19 & None\\
+\hline
+Skoruppa et al. 2013 & paper & 24 & None\\
+\hline
+Swingley (2009) & paper & 17 & Comprehension/Production\\
+\hline
+Swingley (2016) & paper & 27, 28 & Production\\
+\hline
+Swingley \& Aslin (2000) & paper & 20 & Comprehension\\
+\hline
+Swingley \& Aslin (2002) & paper & 15 & Comprehension/Production\\
+\hline
+Swingley 2003 & paper & 19 & Comprehension/Production\\
+\hline
+Tamasi (2016) & dissertation & 30 & None\\
+\hline
+Tao \& Qinmei 2013 & paper & 12 & None\\
+\hline
+Tao et al. 2012 & paper & 16 & Comprehension\\
+\hline
+van der Feest \& Fikkert, 2015 & paper & 24, 20 & None\\
+\hline
+van der Feest \& Johnson, 2016 & paper & 24 & None\\
+\hline
+Wewalaarachchi et al. 2017 & paper & 24 & None\\
+\hline
+White \& Aslin (2011) & paper & 18 & None\\
+\hline
+White \& Morgan (2008) & paper & 18, 19 & None\\
+\hline
+Zesiger \& Johr 2011 & paper & 14 & None\\
+\hline
+Zesiger et al. (2012) & paper & 12, 19 & Comprehension/Production\\
 \hline
@@
 abbreviate Comperehension/Production to Comp./Prod.,
-etcetc{]}{[}KATIE{]} I'll think about how to implement that! Might end
-up having to adjust the table by hand, there is a lot of variation
-between studies.
+etcetc{]}{[}KATIE{]} I've reduced the table to be about age and
+vocabulary, in order to have it more focused for the aim of this paper.
 
@@
 population, experiment design and stimuli, and results. For the present
-analyses, we focus on the following characteristics:\\
+analyses, we focus on the following characteristics:
+
 1 Condition: Were words mispronounced or not;\\
 2 Mean age reported per group of infants, in days;\\
-3 Vocabulary size, measured by a standardized questionnaire or list;\\
-4 Size of mispronunciation, measured in features changed;\\
-5 Distractor familiarity: familiar or unfamiliar;\\
-6 Phonological overlap between target and distractor: onset,
-onset/medial, rhyme, none, novel word;\\
-7 Position of mispronunciation: onset, medial, offset, or mixed;\\
-8 Type of mispronunciation: consonant, vowel, or both.
+3 Vocabulary size, measured by a standardized questionnaire or list;
 
@@
 
-\subsection{Figure 1}\label{figure-1}
+\subsection{(Insert Figure 1 about
+here)}\label{insert-figure-1-about-here}
 
@@
 
-\subsection{Figure 2}\label{figure-2}
+\subsection{(Insert Figure 2 about
+here)}\label{insert-figure-2-about-here}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
 
@@
 \end{figure}
-
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
 
@@
 
-Alternatively, the lack of developmental change in mispronunciation
-sensitivity could be due to differences in the types of tasks given to
-infants of different ages. In the following section, we investigate the
-role that different moderators play in mispronunciation sensitivity. To
-investigate the possibility of systematic differences in the tasks
-across ages, we additionally include an exploratory analysis of whether
-different moderators and experimental design features were included at
-different ages.
-
-\subsection{Moderator Analyses}\label{moderator-analyses}
-
-{[}cHRISTINA{]} I WOULD FOLLOW THE OUTLINE IN THE PREVIOUS PARAGRAPH
-HERE OR FLIP THE PARAGRAPH AROUND: 1. ARE DIFFERENT MODERATORS USED AT
-DIFFERENT AGES? TEST: sIMPLE CHI-SQUARED OF AGE GROUP VERSUS MODERATOR
-ASSIGNMENT (AGE GROUP DETERMINED BY LOOKING AT THE YOUNGEST AGE FOR X?)
-2. WHICH MODERATORS INFLUENCE MP SENSITIVITY TEST SIMPLE MA WITH
-MODERATOR TESTS
-
-OR \enquote{FOR EACH POSSIBLE MODERATOR WHICH COULD INFLIENCE MP
-SENSITIVITY, WE FIRST TEST THIS POSSIBILITY AND THEN EVALUATE WHETHER
-THERE IS A SYSTEMATIC DIFFERENCE OF MANIPULATING THESE MODERATORS AS
-INFANTS MATURE, I.E. WHETHER OLDER INFANTS ARE TESTED ON A MORE
-DIFFICULT TASK} ALSO, AS FINAL FOLLOW-UP IT WOULD BE PERFECT TO JUST
-SUBSET ALL STUDIES WITH FAMILIAR DISTRACTORS, SAME NUMBER OF FEATURES,
-AND CHECK THAT OUR CONCLUSIONS HOLD UP REGARING MP SENSITIVITY
-
-{[}KATIE: I prefer this second option, first looking at the moderators
-in general and then looking at whether there is this systematic
-difference with age. The latter is exploratory, so I feel like this
-information should not preceed our planned analyses.{]}
-
-\subsubsection{Number of features
-changed}\label{number-of-features-changed}
-
-To assess whether the number of features changed modulates
-mispronunciation sensitivity, we calculated the meta-analytic effect for
-object identification in response to words that were pronounced
-correctly and mispronounced using 1-, 2-, and 3-feature changes. We did
-not include data for which the number of features changed in a
-mispronunciation was not specified or the number of features changed was
-not consistent (e.g., one mispronunciation included a 2-feature change
-whereas another only a 1-feature change). This analysis was therefore
-based on a subset of the overall dataset, with 81 experimental
-conditions for correct pronunciations, 108 for 1-feature
-mispronunciations, 16 for 2-feature mispronunciations, and 6 for
-3-feature mispronunciations. Each feature change (from 0 to 3; 0
-representing correct pronunciations) was considered to have an equal
-impact on mispronunciation sensitivity, following the argument of graded
-sensitivity (White \& Aslin, 2008; Mani \& Plunkett 2011).
-
-To understand the relationship between number of features changed and
-mispronunciation sensitivity, we evaluated the effect size Hedges'
-\emph{g} with number of features changed as a moderator. The moderator
-test was significant, QM(1) = 215.761, \emph{p}\textless{} .001. Hedges'
-\emph{g} for number of features changed was -0.123 (SE = 0.014), which
-indicated that as the number of features changed increased, the effect
-size Hedges' \emph{g} significantly decreased (95\% CI{[}-0.151,
--0.096{]}, \emph{p} \textless{} .001). We plot this relationship in
-Figure 3. This confirms previous findings of a graded sensitivity to the
-number of features changed for both consonant (White \& Morgan, 2008)
-and vowel (Mani \& Plunkett, 2011) mispronunciations as well as the
-importance of controlling for the degree of phonological mismatch in
-experimental design.
-
-\subsection{Figure 3}\label{figure-3}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotFeatEffect-1.pdf}
-\caption{}
-\end{figure}
+Alternatively, it is possible that variation in the analysis approach
+lead to systematic differences in the size of mispronunciation
+sensitivity. Choices about the approach to data analysis have a higher
+possibility to be influenced by the shape of the data itself after
+collection, and are therefore susceptible to a higher rate of
+false-positives (Simmons, Nelson, \& Simonsohn, 2011). Although we did
+not have specific predictions about these variables, such as size of
+time window analyzed or dependent variable calculated, we included these
+variables in our coding scheme for the meta-analysis dataset. As
+reported in the Methods section (and discussed in detail below), some of
+these variables varied widely across studies. In the following section,
+we include an exploratory analysis to investigate the possibility of
+systematic differences in the approach to analysis in general and across
+infant age.
+
+{[}KATIE{]} I've changed the above paragraph to lead to exploratory
+analyses, not moderators. Since the fmailiar/unfamiliar analysis doesn't
+really work out except for if we kind of subset and torture the data, I
+think its more interesting to talk about how choices of analysis /
+researcher degrees of freedom may influence the data
+
+\subsection{Exploratory Analyses}\label{exploratory-analyses}
+
+We identified several variables to assess the influence of data analysis
+choices. These variables fall into two types of categories: time-related
+and dependent variable related. In the following analyses, we discuss
+the theoretical motivation for these data analysis choices, the
+variation present in the current meta-analysis dataset, and the
+influence these choices have on mispronunciation sensitivity
+development.
+
+\subsubsection{Time-related analyses}\label{time-related-analyses}
+
+When designing mispronunciation sensitivity studies, experimenters
+choose the length of time each trial is presented. This includes both
+the length of time before the target object is named (pre-naming phase)
+as well as after (post-naming phase) and is determined prior to data
+collection. Across papers, trial length varied from 2750 to 13000 ms,
+with a mode of 5000 ms. There was an inverse relationship between infant
+age and trial length, such that younger infants were given trials of a
+longer length, although this correlation was not significant (\emph{r} =
+-0.11, \emph{p} = 0.086). Presumably, younger infants may be given
+longer trials because their word recognition abilities may be slower
+than older infants (Fernald et al., 1998).
+
+Unlike the length of trial, the length of the post-naming phase analyzed
+can be chosen after the experimental data is collected. Interestingly,
+half of the experimental conditions were analyzed using the same length
+of post-naming phase as the infant heard in the actual experiment 126,
+while the other half were analyzed using a shorter length of post-naming
+phase, excluding later portions of the post-naming phase 125. Across
+papers, the length of the post-naming phase analyzed varied from 1510 to
+6000 ms, with a mode of 2000 ms. Similar to trial length, there was an
+inverse relationship between infant age and length of post-naming phase
+analyzed, such that younger infants were analyzed using a longer length
+of post-naming phase, although here the relationship was significant
+(\emph{r} = -0.21, \emph{p} \textless{} .001). Again, the choice to
+analyze a shorter post-naming time window is likely related to evidence
+that speed of processing is slower in younger infants (Fernald et al.,
+1998). Furthermore, the proportion of post-naming phase time window
+analyzed in comprison to the total post-naming phase presented to
+infants significantly decreased with increasing infant age (\emph{r} =
+-0.18, \emph{p} = 0.004). Although trial length did not differ by infant
+age, the size of the post-naming phase time window analyzed did differ
+by infant age.
+
+When analyzing eye-movements, it is important to consider the amount of
+time it takes for an eye movement to be initiated in response to a
+stimulus. Previous studies examining simple stimulus response latencies
+first determined that infants require at least 233 ms to initiate an
+eye-movement in response to a stimulus (Canfield \& Haith, 1991). In
+mispronunciation sensitivity studies, however, this has often been
+extended to 367 ms (e.g.~Swingley \& Aslin, 2000, 2002, 2007). Across
+papers, the majority used a similar offset value (between 360 and 370
+ms) for analysis (\emph{n} = 151), but offset values ranged from 0 to
+500 ms, and were not reported for 36 experimental conditions. We note
+that Swingley (2009) also included offset values of 1133 ms to analyze
+responses to coda mispronunciations. There was an inverse relationship
+between infant age and size of offset, such that younger infants were
+given longer offsets, although this correlation was not significant
+(\emph{r} = -0.10, \emph{p} = 0.13). This lack of a relationship is
+perhaps driven by the field's consensus that an offset of about 367 ms
+is appropriate for analyzing word recognition with PTL measures,
+including studies that evaluate mispronunciation sensitivity.
+
+Although there are a priori reasons to choose the post-naming time
+window (infant age) or offset time (previous studies), these choices may
+occur after data collection and are therefore susceptible to a higher
+rate of false-positives. Considering that differences in these choice
+were systematically different across infant ages, at least for the
+post-naming time window, we next explored whether the size of the
+analyzed post-naming phase time window or the offset time influenced
+sensitivity to mispronunciations.
+
+\subsubsection{Length of post time}\label{length-of-post-time}
+
+We first assessed whether size of post-naming phase analyzed had an
+impact on the size of mispronunciation sensitivity. First, we calculated
+the meta-analytic effect for object identification in response to
+mispronounced target words/images, including post-naming phase size as a
+moderator. The moderator test was not significant QM(1) = 215.761,
+\emph{p}\textless{} .001 and the estimate for post-naming phase size was
+relatively small, \(\beta\) = 0.121, SE = 0.073, 95\% CI{[}-0.022,
+0.264{]}, \emph{p}= 0.097. This suggests that upon hearing a
+mispronunciation, infants' looks to the target image were similar
+regardless of the size of the post-naming phase analyzed. We next
+assessed whether post-naming phase size was related to mispronunciation
+sensitivity. We merged the two datasets and included condition (correct
+pronunciation, mispronunciation) as an additional moderator. The
+moderator test was significant, QM(1) = 215.761, \emph{p}\textless{}
+.001. The estimate for the interaction between post-naming phase size
+and condition was small but significant \(\beta\) = -0.156, SE = 0.051,
+95\% CI{[}-0.256, -0.056{]}, \emph{p}= 0.002. This relationship is
+plotted in Figure 3a. The results suggest that although the size of the
+post-naming phase analyzed did not impact infants' likelihood to fixate
+the target upon hearing the mispronunciation, it did significantly
+impact mispronunciation sensitivity. Specifically, the difference
+between target fixations for correctly pronounced and mispronounced
+items (mispronunciation sensitivity) was significantly greater when the
+post-naming phase that was shorter in length.
+
+Considering that we also found a relationship between the length of the
+post-naming phase analyzed and infant age, such that younger ages had a
+longer post-naming phase time window of analysis, we next examined
+whether the size of post-naming phase analyzed modulated the development
+of mispronunciation sensitivity. For object recognition in response to a
+mispronunciation, including age as a moderator resulted in a moderator
+test that was not significant QM(1) = 215.761, \emph{p}\textless{} .001,
+and a small estimate for the interaction between age and size of
+post-naming phase (\(\beta\) = -0.156, SE = 0.051, 95\% CI{[}-0.256,
+-0.056{]}, \emph{p}= 0.002. This suggests that upon hearing a
+mispronunciation, infant measured looks to the target image were
+similar, regardless of infant age or size of the post-naming phase
+analyzed. We next assessed whether the relationship between size of the
+post-naming phase analyzed and mispronunciation sensitivity was
+modulated by age. We merged the two datasets and included condition
+(correct pronunciation, mispronunciation) as well as age as additional
+moderators. The moderator test was significant QM(1) = 215.761,
+\emph{p}\textless{} .001. The estimate for the three-way-interaction
+between condition, size of post-naming phase, and age was small, but
+significant (\(\beta\) = = NA, SE = NA, 95\% CI{[}NA, NA{]}, \emph{p}NA.
+This relationship is plotted in Figure 3b. Smaller post-naming phase
+size lead to greater increases in mispronunciation sensitivity with
+development. For example, experimental conditions analyzed with a
+post-naming phase of 2000 ms or less, mispronunciation sensitivity
+increases with infant age, whereas a post-naming phase of greater than
+2000 ms leads to either no impact of age on mispronunciation sensitivity
+or a negative relationship between age and mispronunciation sensitivity.
+
+\subsection{(Insert Figure 3 about
+here)}\label{insert-figure-3-about-here}
 
@@
 
-Although we did not have any specific predictions about the relationship
-between infant age and the impact of number of features changed on
-mispronunciation sensitivity, we included an exploratory analysis to
-examine this relationship. When age was also included as a moderator,
-the moderator test was significant, QM(1) = 215.761, \emph{p}\textless{}
-.001, but the interaction between age and number of features changed was
-not significant, \(\beta\) = 0.006, SE = 0.003, 95\% CI{[}0, 0.011{]},
-\emph{p}= 0.069. The small effect size for the interaction between age
-and number of features changed suggests that the impact of number of
-features changed on mispronunciation sensitivity does not change with
-infant age.
-
-Although all papers included in the dataset also included correct
-pronunciations, not all papers included all three types of feature
-changes (i.e.~1-3). The age range for each type of number of features
-changed was 372.89 - 920.20 days (\emph{M} = 637.40) for 1-feature
-mispronunciations, 377.28 - 920.20 days (\emph{M} = 612.17) for
-2-feature mispronunciations, and 544.48 - 920.20 days (\emph{M} =
-661.64) for 3-feature mispronunciations. The reader should note that
-experimental conditions in which the number of features changed in a
-mispronunciation was not specified or the number of features changed was
-not consistent (e.g., one mispronunciation included a 2-feature change
-whereas another only a 1-feature change) are not included in these
-totals. An analysis focusing on the ages where all three numbers of
-features changed were tested (i.e.~544.48 - 920.20 days), however, did
-not change the pattern of results.
-
-\subsubsection{Distractor familiarity}\label{distractor-familiarity}
-
-We next assessed whether distractor familiarity has an impact on the
-size of mispronunciation sensitivity. First, we calculated the
-meta-analytic effect for object identification in response to
-mispronounced target words/images that were paired with either a
-familiar or an unfamiliar distractor image. The moderator test was not
-significant QM(1) = 215.761, \emph{p}\textless{} .001 and the estimate
-for distractor familiarity was relatively small, \(\beta\) = -0.082, SE
-= 0.126, 95\% CI{[}-0.329, 0.164{]}, \emph{p}= 0.513. This suggests that
-upon hearing a mispronunciation, infants' looks to the target image were
-similar for when the target image was paired with an image of a familiar
-or unfamiliar object. We next assessed whether distractor familiarity
-was related to mispronunciation sensitivity. We merged the two datasets
-and included condition (correct pronunciation, mispronunciation) as an
-additional moderator. The moderator test was significant, QM(1) =
-215.761, \emph{p}\textless{} .001, but the estimate for the interaction
-between distractor familiarity and condition was small and not
-significant \(\beta\) = 0.141, SE = 0.081, 95\% CI{[}-0.017, 0.299{]},
-\emph{p}= 0.08. This relationship is plotted in Figure 4. The results
-suggest that overall, infants' familiarity with the distractor object
-(familiar or unfamiliar) did not impact their mispronunciation
-sensitivity.
-
-\subsection{Figure 4}\label{figure-4}
-
 \begin{figure}[htbp]
 \centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotDistFamEffect_NoAge-1.pdf}
+\includegraphics{Paper_Analyses_files/figure-latex/Plot_post_name_cond_age-1.pdf}
 \caption{}
 \end{figure}
+
+\subsubsection{Length of offset time}\label{length-of-offset-time}
+
+We next assessed whether offset time had an impact on the size of
+mispronunciation sensitivity. First, we calculated the meta-analytic
+effect for object identification in response to mispronounced target
+words/images, including offset time as a moderator. The moderator test
+was not significant QM(1) = 215.761, \emph{p}\textless{} .001 and the
+estimate for offset time was very small, \(\beta\) = 0.001, SE = 0, 95\%
+CI{[}0, 0.001{]}, \emph{p}= 0.132. This suggests that upon hearing a
+mispronunciation, infants' looks to the target image were similar
+regardless of the offset time used to analyze the data. We next assessed
+whether offset time was related to mispronunciation sensitivity. We
+merged the two datasets and included condition (correct pronunciation,
+mispronunciation) as an additional moderator. The moderator test was
+significant, QM(1) = 215.761, \emph{p}\textless{} .001, but the estimate
+for the interaction between offset time and condition was very small and
+not significant \(\beta\) = 0, SE = 0, 95\% CI{[}-0.001, 0{]}, \emph{p}=
+0.505.
+
+We next examined whether offset time modulated the development of
+mispronunciation sensitivity. For object recognition in response to a
+mispronunciation, including age as a moderator resulted in a moderator
+test that was not significant QM(1) = 215.761, \emph{p}\textless{} .001,
+and a very small estimate for the interaction between age and size of
+post-naming phase (\(\beta\) = 0, SE = 0, 95\% CI{[}0, 0{]}, \emph{p}=
+0.924. This suggests that upon hearing a mispronunciation, infant
+measured looks to the target image were similar, regardless of infant
+age or offset time. We next assessed whether the relationship between
+offset time and mispronunciation sensitivity was modulated by age. We
+merged the two datasets and included condition (correct pronunciation,
+mispronunciation) as well as age as additional moderators. The moderator
+test was significant QM(1) = 215.761, \emph{p}\textless{} .001, but the
+three-way-interaction between condition, offset time, and age was very
+small and not significant (\(\beta\) = = 0, SE = 0, 95\% CI{[}0, 0{]},
+\emph{p}= 0.605.
+
+Taken together, these results suggest that offset time does not modulate
+mispronunciation sensitivity. There is no relationship between offset
+time and age, and we find no influence of offset time on the development
+of mispronunciation sensitivity.
+
+\subsubsection{Dependent variable-related
+analyses}\label{dependent-variable-related-analyses}
+
+Mispronunciation studies evaluate infants' proportion of target looks
+(PTL) in response to correct and mispronounced words. Experiments
+typically include a phase where no naming event has occured, whether
+correctly pronounced or mispronounced, which we refer to as the
+baseline. The purpose of the baseline is to ensure that infants do not
+have systematic preferences for the target or distractor (greater
+interest in a cat compared to cup) which may drive PTL scores in the
+post-naming phase. As described in the Data Analysis sub-section of the
+Methods, there was considerable variation across papers in way that
+baseline was calculated, resulting in different measured outcomes or
+dependent variables. Over half of the experimental conditions (\emph{n}
+= 129) subtracted the PTL score for a pre-naming phase from the PTL
+score for a post-naming phase. This results in one value, which is then
+compared with a chance value of 0. When positive, this indicates that
+infants increased their looks to the target after hearing the naming
+label (correct or mispronounced) relative to the pre-naming baseline
+PTL. We will refer to this dependent variable as the Difference Score.
+Another dependent variable, which was used in 69 experimental
+conditions, directly compared compared the post- and pre-naming PTL
+scores with one another. This requires two values, one for the
+pre-naming phase and one for the post-naming phase. A greater post
+compared to pre-naming phase PTL indicates that increased their target
+looks after hearing the naming label. We will refer to this dependent
+variable as Pre vs.~Post. Finally, the remaining 53 experimental
+conditions compared the post-naming PTL score with a chance value of
+50\%. Here, the infants' pre-naming phase preferences are not considered
+and instead target fixations are evaluated based on the likelihood to
+fixate one of two pictures. We will refer to this dependent variable as
+Post.
+
+The Difference Score and Pre vs.~Post can be considered similar to one
+another, in that they are calculated on the same type of data and
+consider pre-naming preferences. The Post dependent variable, in
+contrast, does not consider pre-naming preferences. To our knowledge,
+there is no theory or evidence to drive choice of dependent variable,
+which may explain the wide variation in dependent variable reported in
+the papers included in this meta-analysis. We next explored whether the
+type of dependent variable calculated influenced sensitivity to
+mispronunciations. Considering that the dependent variable Post differs
+in its consideration of pre-naming preferences, we directly compared
+mispronunciation sensitivity between Post as a reference condition and
+both Difference Score and Pre vs.~Post dependent variables.
+
+We first assessed whether the choice of dependent variable had an impact
+on the size of mispronunciation sensitivity. First, we calculated the
+meta-analytic effect for object identification in response to
+mispronounced target words/images, including dependent variable as a
+moderator. The moderator test was significant QM(1) = 215.761,
+\emph{p}\textless{} .001. The estimates for both the Pre vs.~Post
+(\(\beta\) = -0.369, SE = 0.143, 95\% CI{[}-0.65, -0.088{]}, \emph{p}=
+0.01) and Difference Score (\(\beta\) = -0.392, SE = 0.135, 95\%
+CI{[}-0.656, -0.128{]}, \emph{p}= 0.004) dependent variables were
+significantly smaller than that of the Post dependent variable. This
+suggests that reported looks to the target upon hearing a
+mispronunciation were greatest when the dependent variable was Post. We
+next assessed whether he dependent variable was related to
+mispronunciation sensitivity. We merged the two datasets and included
+condition (correct pronunciation, mispronunciation) as an additional
+moderator. The moderator test was significant, QM(1) = 215.761,
+\emph{p}\textless{} .001. The estimate for the interaction between Pre
+vs.~Post and condition was significantly smaller than that of the Post
+dependent variable (\(\beta\) = -0.392, SE = 0.101, 95\% CI{[}-0.59,
+-0.194{]}, \emph{p}\textless{} .001), but the difference between the
+Difference Score and Post in the interaction with condition was small
+and not significant (\(\beta\) = -0.01, SE = 0.098, 95\% CI{[}-0.203,
+0.183{]}, \emph{p}= 0.916). This relationship is plotted in Figure 4a.
+The results suggest that dependent variable calculated significantly
+impacted the size fo the mispronunciation sensitivity effect, such that
+Post. vs.~Pre showed a smaller mispronunciation sensitivity effect than
+Post, but no difference between the Difference Score and Post.
+
+We next examined whether the type of dependent variable calculated
+modulated the development of mispronunciation sensitivity. For object
+recognition in response to a mispronunciation, including age as a
+moderator resulted in a moderator test that was significant QM(1) =
+215.761, \emph{p}\textless{} .001, but the estimates for the interaction
+between Pre vs.~Post and age (\(\beta\) = -0.011, SE = 0.037, 95\%
+CI{[}-0.083, 0.061{]}, \emph{p}= 0.766) as well as Difference Score and
+age (\(\beta\) = -0.021, SE = 0.033, 95\% CI{[}-0.085, 0.043{]},
+\emph{p}= 0.516) were not different from that of the Post dependent
+variable. This suggests that upon hearing a mispronunciation, infant
+measured looks to the target image were similar, regardless of infant
+age or type of dependent variable. We next assessed whether the
+relationship between dependent variable and mispronunciation sensitivity
+was modulated by age. We merged the two datasets and included condition
+(correct pronunciation, mispronunciation) as well as age as additional
+moderators. The moderator test was significant QM(1) = 215.761,
+\emph{p}\textless{} .001. The estimate for the interaction between Pre
+vs.~Post, condition, and age was significantly smaller than that of the
+Post dependent variable (\(\beta\) = -0.089, SE = 0.03, 95\%
+CI{[}-0.148, -0.03{]}, \emph{p}= 0.003), but the difference between the
+Difference Score and Post in the interaction with condition and age was
+small and not significant (\(\beta\) = -0.036, SE = 0.027, 95\%
+CI{[}-0.088, 0.016{]}, \emph{p}= 0.174). This relationship is plotted in
+Figure 4b. When the dependent variable was Pre vs.~Post,
+mispronunciation sensitivity decreased with infant development, while in
+comparison, when the dependent variable was Post, mispronunciation
+sensitivity increased with infant development. There was no difference
+in mispronunciation sensitivity change with infant development between
+the Post and Difference Score dependent variables.
+
+\subsection{(Insert Figure 4 about
+here)}\label{insert-figure-4-about-here}
 
@@
 
-We next examined whether age modulates object recognition or
-mispronunciation sensitivity when the distractor image is familiar or
-unfamiliar. Based on previous results, we expected older infants to look
-less to the target in response to mispronunciations and to have greater
-mispronunciation sensitivity than younger infants when the distractor
-was unfamiliar compared to familiar. For object recognition in response
-to a mispronunciation, including age as a moderator resulted in a
-moderator test that was not significant QM(1) = 215.761,
-\emph{p}\textless{} .001, and a small estimate for the interaction
-between age and object recognition (\(\beta\) = -0.02, SE = 0.02, 95\%
-CI{[}-0.059, 0.018{]}, \emph{p}= 0.305. This suggests that upon hearing
-a mispronunciation, infant looks to the target image were similar for
-when the target image was paired with an image of a familiar or
-unfamiliar object, regardless of their age. We next assessed whether the
-relationship between distractor familiarity and mispronunciation
-sensitivity was modulated by age. We merged the two datasets and
-included condition (correct pronunciation, mispronunciation) as well as
-age as additional moderators. The moderator test was significant QM(1) =
-215.761, \emph{p}\textless{} .001. The estimate for the
-three-way-interaction between condition, distractor familiarity, and age
-was small and not significant (\(\beta\) = = -0.02, SE = 0.02, 95\%
-CI{[}-0.059, 0.018{]}, \emph{p}= 0.305. We note that in this model, the
-interaction between condition and distractor familiarity was significant
-(\(\beta\) = 0.175, SE = 0.089, 95\% CI{[}0, 0.351{]}, \emph{p}= 0.05,
-this estimate is similar to the original estimate specifically examining
-this interaction in a previous model. Taken together, these results
-suggest that regardless of age, mispronunciation sensitivity was similar
-whether the distractor image was familiar or unfamiliar.
-
-Although we anticipated that older children may be more impacted by the
-presence of a unfamiliar compared to familiar distractor image, we found
-that age and distractor familiarity did not impact mispronunciation
-sensitivity. Inspection of the ages tested using different kinds of
-distractors, however, revealed differences. Infants tested using a
-familiar distractor were younger (\emph{M} = 588.76 days, \emph{SD} =
-136.47, range = 207.80 - 768) than those infants tested using an
-unfamiliar distractor (\emph{M} = 678.85 days, \emph{SD} = 115.47, range
-= 544.48 - 920.20), which a two-sample t-test revealed to be a
-significant difference, \emph{t}(153.83) = 5.30, \emph{p} \textless{}
-.001).
-
-{[}CHRISTINA{]} CAN YOU TURN THE NUMBERS INTO R CODE HERE? aLSO, NOT
-SURE WE NEED A T-TEST TO CONFIRM THE OBVIOUS. {[}Katie: Is the t-test
-okay?{]}
-
-To ensure that the lack of a difference wasn't due to the ages of
-infants tested with different types of distractors, we repeated the
-previous model analyses on a subset of papers that tested infants at
-ages where both familiar and unfamiliar distractors were used (544.48 -
-768 days). We first considered object recognition is response to a
-mispronunciation. Here, the pattern of results for the subset of infants
-was similar to that of the entire dataset; the moderator test was not
-significant QM(1) = 215.761, \emph{p}\textless{} .001 and the estimate
-for distractor familiarity was small, \(\beta\) = -0.19, SE = 0.15, 95\%
-CI{[}-0.48, 0.1{]}, \emph{p}= 0.21. However, it should be noted that
-although small, the effect size estimate for distractor familiarity
-doubled from \(\beta\)-0.08 in the entire dataset to \(\beta\)-0.19 in
-the subset. We next assessed the relationship between distractor
-familiarity and mispronunciation sensitivity. Similar to the analysis
-with the entire dataset, the moderator test was significant QM(1) =
-215.761, \emph{p}\textless{} .001. Unlike the analysis with the entire
-dataset, however, the estimate for the interaction between distractor
-familiarity and condition was significant \(\beta\) = 0.19, SE = 0.09,
-95\% CI{[}0.01, 0.36{]}, \emph{p}= 0.04, but small and similar to the
-estimate for this interaction in the full dataset \(\beta\) = 0.14.
-
-Although the age range is relatively small in the subset of infant ages
-tested with both familiar and unfamiliar distractors (7.34 months),
-these ages span the beginning of the vocabulary spurt. Considering
-infants' object looking behavior may be influenced by whether the label
-for the object is known (Schafer \& Plunkett, 1998), however, this age
-range may still be informative for understanding the role of distractor
-familiarity on mispronunciation sensitivity and whether this is
-modulated by age. Similar to the full dataset, however, including age as
-a moderator of object recognition in response to familiar and unfamiliar
-distractors resulted in a moderator test that was not significant QM(1)
-= 215.761, \emph{p}\textless{} .001, and a small estimate for the
-interaction between age and object recognition (\(\beta\) = 0.02, SE =
-0.05, 95\% CI{[}-0.07, 0.11{]}, \emph{p}= 0.6. Finally, we assessed
-whether the relationship between distractor familiarity and
-mispronunciation sensitivity was modulated by age in the subset of data.
-Again, similar to the full dataset, the moderator test was not
-significant QM(1) = 215.761, \emph{p}\textless{} .001 and the estimate
-for the three-way-interaction between condition, distractor familiarity,
-and age was small and not significant (\(\beta\) = = -0.07, SE = 0.04,
-95\% CI{[}-0.14, 0{]}, \emph{p}= 0.06.
-
-{[}Katie: ultimately, the subset analysis doesn't show anything :( What
-conclusions can we draw?{]}
-
-\subsubsection{Phonological overlap between target and
-distractor}\label{phonological-overlap-between-target-and-distractor}
-
-To assess whether phonological overlap between the target and distractor
-image labels has an impact on the size of mispronunciation sensitivity,
-we examined the meta-analytic effect for object identification in
-response to mispronunciations and mispronunciation sensitivity when the
-target-distractor pairs either had no overlap or shared the same onset
-phoneme. We did not include data for which the overlap included both the
-onset and medial phonemes (\emph{n} = 4), coda phonemes (\emph{n} = 3),
-or for targets paired with an unfamiliar distractor image 60. The
-analysis was therefore based on a subset of the overall dataset, with
-104 experimental conditions containing onset phoneme overlap between the
-target and distractor and 80 containing no overlap between target and
-distractor.
-
-{[}CHRISTINA{]} SEEMS OK BUT I AM CONFUSED WHY OVERLAP IS THE BASELINE
-AND WHY YOU BRING IN NOVEL. I THINK YOU NEED TO SPELL THIS OUT MORE.
-
-{[}KATIE: I think we had talked about it and decided to include novel. I
-don't think it needs to be here necessarily, so I'll take it out,
-especially if its confusing.{]}
-
-Regarding object identification in response to mispronunciations, when
-distractor overlap was included as a moderator, the moderator test was
-not significant QM(1) = 215.761, \emph{p}\textless{} .001 and the
-estimate for distractor overlap was relatively small, \(\beta\) = 0.138,
-SE = 0.15, 95\% CI{[}-0.157, 0.432{]}, \emph{p}= 0.359. This suggests
-that upon hearing a mispronunciation, infants looks to the target image
-were similar for when the target image was paired with a distractor
-image that contained overlap on the onset phoneme or no overlap with the
-target word, or was an unfamiliar object. We next assessed whether
-target-distractor overlap was related to mispronunciation sensitivity.
-We merged the two datasets and included condition (correct
-pronunciation, mispronunciation) as an additional moderator. The
-moderator test was significant QM(1) = 215.761, \emph{p}\textless{}
-.001. The estimate for the interaction between condition and distractor
-overlap was small, but significant (\(\beta\) = -0.247, SE = 0.078, 95\%
-CI{[}-0.399, -0.096{]}, \emph{p}= 0.001, suggesting that
-mispronunciation sensitivity was greater when target-distractor pairs
-shared the same onset phoneme compared to when they shared no
-phonological overlap. This relationship be seen in Figure 5a.
-
-Although we did not have any specific predictions about the relationship
-between infant age and the impact of distractor overlap on
-mispronunciation sensitivity, we included an exploratory analysis to
-examine this relationship. First, for object recognition in response to
-mispronunciations, when age in addition to distractor overlap was also
-included as a moderator, the moderator test was not significant, QM(1) =
-215.761, \emph{p}\textless{} .001, and the estimate for the interaction
-between age and distractor overlap was small, \(\beta\) = 0.011, SE =
-0.033, 95\% CI{[}-0.054, 0.077{]}, \emph{p}= 0.733. This suggests that
-upon hearing a mispronunciation, infants looks to the target image were
-similar for both onset and no overlap, regardless of infant age. We next
-assessed whether the relationship between distractor overlap and
-mispronunciation sensitivity was modulated by age. We merged the two
-datasets and included condition (correct pronunciation,
-mispronunciation) as well as age as additional moderators. The moderator
-test was significant, QM(1) = 215.761, \emph{p}\textless{} .001 and the
-estimate for the three-way interaction between age, condition, and
-distractor overlap was significant, but relatively small (\(\beta\) = =
--0.04, SE = 0.019, 95\% CI{[}-0.078, -0.003{]}, \emph{p}= 0.034. As can
-be seen in Figure 5b, the difference between correct pronunciations and
-mispronunciations (mispronunciation sensitivity) stays steady across
-infant ages for both target words paired with distractors containing
-onset overlap with the target word as well as distractors containing no
-overlap. As infants aged, however, overall recognition (regardless of
-condition) increased for target-distractor pairs containing onset
-overlap, whereas for overall recognition decreased for target-distractor
-pairs containing no overlap.
-
-\subsection{Figure 5}\label{figure-5}
-
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
-\subsubsection{Position of
-mispronunciation}\label{position-of-mispronunciation}
-
-To assess whether the position of the mispronunciation has an impact on
-mispronunciation sensitivity, we calculated the meta-analytic effect for
-object identification in response to mispronunciations on the onset and
-medial phonemes. We did not include data for which the mispronunciation
-was located on the coda (\emph{n} = 10 and NA), varied in regard to
-position (\emph{n} = 3, 29, 8, and NA), or was not reported (\emph{n} =
-10). The analysis was therefore based on a subset of the overall
-dataset, with 143 and NA experimental conditions comparing a
-mispronunciation on the onset phoneme and 48 and NA experimental
-conditions comparing a mispronunciation on the medial phoneme.
-
-Regarding object identification in response to mispronunciations, when
-mispronunciation location was included as a moderator, the moderator
-test was not significant QM(1) = 215.761, \emph{p}\textless{} .001 and
-the estimate for distractor overlap was small, \(\beta\) = 0.011, SE =
-0.033, 95\% CI{[}-0.054, 0.077{]}, \emph{p}= 0.733. This suggests that
-upon hearing a mispronunciation, infants looks to the target image were
-similar for when the mispronunciation was located on the onset or medial
-phonemes. We next assessed whether mispronunciation location was related
-to mispronunciation sensitivity. We merged the two datasets and included
-condition (correct pronunciation, mispronunciation) as an additional
-moderator. The moderator test was significant, QM(1) = 215.761,
-\emph{p}\textless{} .001, but the estimate for the interaction between
-mispronunciation location and condition was small and not significant,
-\(\beta\) = 0.051, SE = 0.088, 95\% CI{[}-0.121, 0.224{]}, \emph{p}=
-0.559. These results suggest that overall, the location of the
-mispronunciation (onset, medial) did not impact mispronunciation
-sensitivity.
-
-According to TRACE, infants should become more sensitive to onset
-mispronunciations as their lexicon size grows, but sensitivity to medial
-mispronunciations should stay the same (Mayor \& Plunkett, 2014). To
-examine this relationship, we included age as a moderator. First, for
-object recognition in response to mispronunciations, when age in
-addition to mispronunciation location was also included as a moderator,
-the moderator test was not significant, QM(1) = 215.761,
-\emph{p}\textless{} .001 and the estimate for the interaction between
-distractor overlap and age was small, \(\beta\) = 0.018, SE = 0.034,
-95\% CI{[}-0.048, 0.084{]}, \emph{p}= 0.596. This suggests that upon
-hearing a mispronunciation, infants looks to the target image were
-similar for both onset and medial mispronunciations, regardless of
-infant age. We next assessed whether the relationship between
-mispronunciation location and mispronunciation sensitivity was modulated
-by age. We merged the two datasets and included condition (correct
-pronunciation, mispronunciation) as well as age as additional
-moderators. The moderator test was significant, QM(1) = 215.761,
-\emph{p}\textless{} .001, but the estimate for the three-way interaction
-between mispronunciation loction, condition, and age was small and not
-significant, \(\beta\) = NA, SE = NA, 95\% CI{[}NA, NA{]}, \emph{p}NA.
-These results provide further evidence that location of the
-mispronunciation (onset, medial) did not impact mispronunciation
-sensitivity.
-
-Although we anticipated that older children may be more impacted by the
-position of a mispronunciation, we found no relationship. Inspection of
-the ages tested using on onset and medial mispronunciations, however,
-revealed differences. Infants tested on onset mispronunciations were
-older (\emph{M} = 634.03 and NA days, \emph{SD} = 116.41 and NA, range =
-372.89 and NA - 920.20 and NA) than those infants tested on medial
-mispronunciations (\emph{M} = 584.16 and NA days, \emph{SD} = 107.49 and
-NA, range = 372.89 and NA - 766 and NA), which a two-sample t-test
-revealed to be a significant difference, \emph{t}(86.84) = 2.72,
-\emph{p} = 0.008).
-
-To ensure that the lack of a difference wasn't due to the ages of
-infants tested with onset and medial mispronunciations, we repeated the
-previous model analyses on a subset of papers that tested infants at
-ages where onset and medial mispronunciations were tested (372.89 - 766
-days). The analyses on this subset of data did not differ from that of
-the analyses conducted on the entire data set.
-
-{[}Katie: ultimately, the subset analysis doesn't show anything :( What
-conclusions can we draw?{]}
-
-\subsubsection{Type of mispronunciation (consonant or
-vowel)}\label{type-of-mispronunciation-consonant-or-vowel}
-
-To assess whether the type of mispronunciation impacts sensitivity to
-mispronunciations, we calculated the meta-analytic effect for object
-identification in response to the type of mispronunciation. Although
-most theoretical discussion of mispronunciation type has focused on
-consonants and vowels, our dataset also included tone mispronunciations.
-In our analysis, we were interested in the difference between consonants
-and vowels, but also include an exploratory analysis of responses to
-tones, consonants, and vowels. We therefore conducted two sets of
-analyses, one analyzing consonants and vowels alone and a second
-comparing responses to tones with that of consonants and vowels,
-separately. For the latter analysis, tones were coded as the reference
-condition. We did not include data for which mispronunciation type
-varied within experiment and was not reported separately (\emph{n} = 21
-and 2). The analysis was therefore based on a subset of the overall
-dataset, with 145 experimental conditions comparing a consonant
-mispronunciation, 71 experimental conditions comparing a vowel
-mispronunciation, and 12 experimental conditions comparing a tone
-mispronunciation. Below, we first report the set of analyses comparing
-consonants with vowels before moving on to the second set of exploratory
-analyses comparing tones with that of consonants and vowels.
-
-{[}KATIE{]} WHAT DO YOU THINK ABOUT THIS? WE HAVE THE TONES AND ITS A
-NOVEL, INTERESTING THING, I THINK, AND PERHAPS WORTH IT TO INCLUDE A
-COMPARISON OF TONES ALONGSIDE THE MORE THEORETICALLY IMPORTANT
-COMPARISON BETWEEN CONSONANTS AND VOWELS.
-
-We first analyzed experimental conditions where mispronunciation type
-was either a consonant or vowel. Regarding object identification in
-response to mispronunciations, when mispronunciation type was included
-as a moderator, the moderator test was not significant, QM(1) = 215.761,
-\emph{p}\textless{} .001 and the estimate for mispronunciation type was
-small, \(\beta\) = 0.034, SE = 0.088, 95\% CI{[}-0.139, 0.207{]},
-\emph{p}= 0.702. This suggests that upon hearing a mispronunciation,
-infants looks to the target image were similar for when the
-mispronunciation was a consonant or a vowel. We next assessed whether
-type of mispronunciation (consonant or vowel) was related to
-mispronunciation sensitivity. We merged the two datasets and included
-condition (correct pronunciation, mispronunciation) as an additional
-moderator. The moderator test was significant, QM(1) = 215.761,
-\emph{p}\textless{} .001, but the estimate for the interaction between
-mispronunciation type and condition was small and not significant,
-\(\beta\) = 0.056, SE = 0.079, 95\% CI{[}-0.099, 0.211{]}, \emph{p}=
-0.479. These results suggest that overall, the type of mispronunciation
-(consonant vs.~vowel) did not impact mispronunciation sensitivity.
-
-We next examined whether age modulates object recognition or
-mispronunciation sensitivity when the mispronunciation is a consonant or
-vowel. For object recognition in response to a mispronunciation,
-including age as a moderator resulted in a moderator test that was not
-significant, QM(1) = 215.761, \emph{p}\textless{} .001 and the estimate
-for the interaction between mispronunciation type and age was small,
-\(\beta\) = 0.001, SE = 0.017, 95\% CI{[}-0.033, 0.034{]}, \emph{p}=
-0.961. This suggests that upon hearing a mispronunciation, infants looks
-to the target image were similar for when the mispronunciation was on a
-consonant or vowel phoneme, regardless of their age. We next assessed
-whether the relationship between mispronunciation type (consonant or
-vowel) and mispronunciation sensitivity was modulated by age. We merged
-the two datasets and included condition (correct pronunciation,
-mispronunciation) as well as age as additional moderators. The moderator
-test was significant, QM(1) = 215.761, \emph{p}\textless{} .001, and the
-estimate for the three-way interaction between mispronunciation type,
-condition, and age was small, but significant, \(\beta\) = 0.044, SE =
-0.018, 95\% CI{[}0.008, 0.08{]}, \emph{p}= 0.016. As can be seen in
-Figure 6, as infants age, mispronunciation sensitivity grows larger for
-vowel mispronunciations but becomes smaller for consonant
-mispronunciations. Noticeably, mispronunciation sensitivity appears
-greater for consonant compared to vowel mispronunciations at younger
-ages, but this difference shifts as infants age.
-
-\subsection{Figure 6}\label{figure-6}
-
 \begin{figure}[htbp]
 \centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotCVEffect_cond_age-1.pdf}
+\includegraphics{Paper_Analyses_files/figure-latex/Plot_Within_cond_age_diff_score-1.pdf}
 \caption{}
@@
 
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
-To examine whether infants' native language impacts sensitivity to
-consonant and vowel mispronunciations, we classified infants into
-language families. Infants learning American English (\emph{n} = 56),
-British English (\emph{n} = 66), Danish (\emph{n} = 6), Dutch (\emph{n}
-= 58), and German (\emph{n} = 21) were classified into the Germanic
-language family (\emph{n} = 207). Infants learning Catalan (\emph{n} =
-4), Spanish (\emph{n} = 4), French (\emph{n} = 8), Catalan and Spanish
-simultaneously (i.e.~bilinguals; \emph{n} = 6), and Swiss French
-(\emph{n} = 6) were classified into the Romance language family
-(\emph{n} = 28).
-
-For object recognition in response to a mispronunciation, including
-language family as a moderator resulted in a moderator test that was not
-significant, QM(1) = 215.761, \emph{p}\textless{} .001, and the estimate
-for the interaction between mispronunciation type and language family
-was small, \(\beta\) = 0.277, SE = 0.314, 95\% CI{[}-0.338, 0.892{]},
-\emph{p}= 0.378. This suggests that upon hearing a mispronunciation,
-infants looks to the target image were similar for when the
-mispronunciation was on a consonant or vowel phoneme, regardless of the
-language family of their native language. We next assessed whether the
-relationship between mispronunciation type (consonant or vowel) and
-mispronunciation sensitivity was modulated by language family. We merged
-the two datasets and included condition (correct pronunciation,
-mispronunciation) as well as language family as additional moderators.
-The moderator test was significant, QM(1) = 215.761, \emph{p}\textless{}
-.001, and the estimate for the three-way interaction between
-mispronunciation type, condition, language family was large and
-significant , \(\beta\) = -0.872, SE = 0.28, 95\% CI{[}-1.421,
--0.323{]}, \emph{p}= 0.002. As can be seen in Figure 7, mispronunciation
-sensitivity for consonants was similar for Germanic and Romance
-languages. Mispronunciation sensitivity for vowels, however, was greater
-for Germanic compared to Romance languages.
-
-{[}KATIE{]} I'M NOT REALLY SURE WHAT THE CONDITION BY LANGUAGE FAMILY
-INTERACTION MEANS. SHOULD WE EVEN INTERPRET IT? MAYBE THAT THE ROMANCE
-LANGUAGE FAMILY HAD LOWER MISPRONUNCIATION SENSITIVITY?
-
-\subsection{Figure 7}\label{figure-7}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotCVEffect_Lang-1.pdf}
-\caption{}
-\end{figure}
-
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
-Finally, we examined the relationship between language family and infant
-age and mispronunciation sensitivity to consonants and vowels. For
-object recognition in response to a mispronunciation, including language
-family and infant age as a moderator resulted in a moderator test that
-was significant, QM(1) = 215.761, \emph{p}\textless{} .001, and the
-estimate for the three-way interaction between mispronunciation type,
-language family, and age was small, but significant , \(\beta\) =
--0.547, SE = 0.406, 95\% CI{[}-1.342, 0.248{]}, \emph{p}= 0.178. As can
-be seen in Figure 8, looks to the target in response to a
-mispronunciation increased with age for infants learning a Germanic
-language, regardless of whether those mispronunciations were consonants
-or vowels. In contrast, infants learning Romance languages have an even
-greater increase with age in target looks in response to consonant
-mispronunciations, but there was no change with age for vowel
-mispronunciations. We next assessed whether the relationship between
-mispronunciation type (consonant or vowel) and mispronunciation
-sensitivity was modulated by language family and age. We merged the two
-datasets and included condition (correct pronunciation,
-mispronunciation) as well as language family and age as additional
-moderators. The moderator test was significant, QM(1) = 215.761,
-\emph{p}\textless{} .001, and the estimate for the four-way interaction
-between mispronunciation type, condition, language family, and age was
-small, but significant , \(\beta\) = -0.547, SE = 0.406, 95\%
-CI{[}-1.342, 0.248{]}, \emph{p}= 0.178. As can also be seen in Figure 8,
-for infants learning Germanic languages, increasing age was related to
-increasing mispronunciation sensitivity for vowel mispronunciations, but
-decreasing sensitivity for consonant mispronunciations. In contrast,
-infants learning Romance languages have an even greater increase with
-age in sensitivity to vowel mispronunciations. Surprisingly, sensitivity
-to consonant mispronunciations shows a reversal in infants learning
-Romance languages: the growth in target looks for consonant
-mipronunciations increases and surpases that of target looks for correct
-pronunciations.
-
-{[}KATIE{]} AGAIN, THERE ARE ADDITIONAL INTERACTIONS THAT ARE
-SIGNIFICANT\ldots{} SHOULD THEY BE INTERPRETED? ALSO, WTF ROMANCE
-LANGUAGES? IS IT JUST NOT ENOUGH DATA?
-
-\subsection{Figure 8}\label{figure-8}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotCVEffect_cond_age_fam-1.pdf}
-\caption{}
-\end{figure}
-
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
-Although we had no predictions regarding mispronunciation sensitivity to
-tone mispronunciations, we included an exploratory analysis to examine
-whether responses to tone mispronunciations were different from that of
-consonants or vowels. Regarding object identification in response to
-mispronunciations, when mispronunciation type was included as a
-moderator, the moderator test was not significant QM(2) = 1.16, \emph{p}
-= 0.56. This suggests that upon hearing a mispronunciation, infants
-looks to the target image were similar for tone mispronunciations in
-comparison with both consonants and vowels. We next assessed whether
-type of mispronunciation (tone, consonant, vowel) was related to
-mispronunciation sensitivity. We merged the two datasets and included
-condition (correct pronunciation, mispronunciation) as an additional
-moderator. The moderator test was significant, QM(5) = 154.88, \emph{p}
-\textless{} .001. The interaction between condition and consonant
-mispronunciations was not significant \(\beta\) = -0.19, (SE = 0.21,
-95\% CI {[}-0.59, 0.21{]}, \emph{p} = 0.359), suggesting that there was
-no difference in looks to the target in response to consonant and tone
-mispronunciations. The interaction between condition and vowel
-mispronunciations was also not significant \(\beta\) = -0.13, (SE =
-0.21, 95\% CI {[}-0.55, 0.28{]}, \emph{p} = 0.528), suggesting that
-there was no difference in looks to the target in response to vowel and
-tone mispronunciations.
-
-We further included an exploratory analysis of the relationship between
-infant age and the impact of tone mispronunciations in comparison to
-consonant and vowel mispronunciations. First, for object recognition in
-response to mispronunciations, when age in addition to mispronunciation
-location was also included as a moderator, the moderator test was not
-significant, QM(5) = 2.78, \emph{p} = 0.733. This suggests that upon
-hearing a mispronunciation, infants looks to the target image were not
-different between tone and vowel or tone and consonant
-mispronunciations, regardless of their age. We next assessed whether the
-relationship between mispronunciation type (tone, consonant, vowel) and
-mispronunciation sensitivity was modulated by age. We merged the two
-datasets and included condition (correct pronunciation,
-mispronunciation) as well as age as additional moderators. The moderator
-test was significant, QM(11) = 163.85, \emph{p} \textless{} .001, but
-the interactions between condition, age, and both consonant
-mispronciations (\(\beta\) = 0.02, SE = 0.10, 95\% CI {[}-0.19, 0.22{]},
-\emph{p} = 0.871) and vowel mispronunciations (\(\beta\) = 0.06, SE =
-0.10, 95\% CI {[}-0.14, 0.27{]}, \emph{p} = 0.56) were not significant.
-Infants' sensitivity to tone mispronunciations compared to consonant or
-vowel mispronunciations did not differ with age.
-
-{[}KATIE{]} WORTH IT TO INCLUDE LANGUAGE FAMILY ANALYSES TOO? I'M
-THINKING NO
+\subsection{Controlling for researcher
+choice}\label{controlling-for-researcher-choice}
 
@@
 
-** Size of Mispronunciation **
+** Data Analysis Choices **
 
@@
 \item
-  graded sensitivity to number of features changed in a mispronunciation
+  Post-naming phase size and dependent variable impact misp sensitivity
+  development
 \item
-  importance for controlling in experimental design
+  Offset time does not impact misp sensitivity development
 \item
-  Perhaps a call for more studies to include multiple number of features
-  changed, so that this can be assessed? There was a narrow age where
-  this was actually manipulated.
-\end{itemize}
-
-** Distractor Familiarity **
-
-\begin{itemize}
-\tightlist
-\item
-  Not really sure, check the results. A key interaction is significant
-  in one model but not the other.
-\item
-  Again, ages not matched very well for the two groups here. Similar
-  pattern of results for age subset analysis.
-\end{itemize}
-
-** Phonological overlap between target and distractor **
-
-\begin{itemize}
-\tightlist
-\item
-  mispronunciation sensitivity was greater when target-distractor pairs
-  shared the same onset phoneme compared to when they shared no
-  phonological overlap
-\item
-  this is rather the opposite of what one would expect, right?
-\item
-  {[}Katie: Yeah! Its really strange, so the time course analysis
-  suggestion of yours is a very good one!{]}
-\item
-  Maybe it would be useful to have time course analyses to address this
-  issue further
-\item
-  As infants aged, overall recognition (regardless of condition)
-  increased for target-distractor pairs containing onset overlap,
-  whereas overall recognition decreased for target-distractor pairs
-  containing no overlap.
-\end{itemize}
-
-** Position of mispronunciation **
-
-\begin{itemize}
-\tightlist
-\item
-  really no impact at all
-\end{itemize}
-
-** Type of mispronunciation **
-
-\begin{itemize}
-\tightlist
-\item
-  Overall, no difference between consonants and vowels
-\item
-  Consonant mispronunciation sensitivity decreases with age
-\item
-  Vowel mispronunciation sensitivity increases with age
-\item
-  mispronunciation sensitivity for consonants similar for Germanic and
-  Romance languages
-\item
-  Mispronunciation sensitivity for vowels greater for Germanic compared
-  to Romance languages
-\item
-  For Germanic infants, increasing age was related to increasing
-  mispronunciation sensitivity for vowel mispronunciations, but
-  decreasing sensitivity for consonant mispronunciations.
-\item
-  For Romance infants, an even greater increase with age in sensitivity
-  to vowel mispronunciations.
-\item
-  For Romance infants, the growth in target looks for consonant
-  mipronunciations increases and surpases that of target looks for
-  correct pronunciations
-\item
-  exploratory analyses with tone mispronunciations suggest no great
-  difference in sensitivity when compared to consonant and vowel
-  mispronunciations
+  the first two do not have theoretical frameworks to guide researchers,
+  whereas offset time does
 \end{itemize}
@@
 
-Discussing the Moderator Analyses Maybe put them together into the ones
-that worked out as we predicted and those that didn't? So, here is
-evidence that supports existing arguments, that doesn't need to be a
-huge chunk. But then more space devoted to moderator analyses that
-didn't work out according to predictions.
-
-It should be noted that the majority of consonant mispronunciations were
-located on the onset phoneme (\emph{n} = 120; total consonant
-conditions, \emph{n} = 145), while the majority of vowel
-mispronunciations were located on the medial phoneme (\emph{n} = 44;
-total vowel conditions, \emph{n} = 71). In their analysis using TRACE,
-Mayor and Plunkett (2014) found that the difference between sensitivity
-to consonant and vowel mispronunciations was due to infants' lexical
-knowlege consisting of a majority consonant onset words.
-
-{[}KATIE{]} COME BACK TO THIS.
-
 \newpage

### 2018-11-09 Paper_Analyses.Rmd
added histograms for time-related analysis choices

@@
 trial.l <- cor.test(dat$trial_length, dat$mean_age_1)
-trial.length.plot <- ggplot(dat, aes(trial_length, age.C)) + geom_point() +geom_smooth(method = "lm")
+
+library(reshape)
+tdl <- dat[,c("short_cite", "trial_length", "post_nam_dur")]
+tdl <- melt(tdl, id = "short_cite")
+
+trial_length_hist <- ggplot(dat,aes(x=value)) + 
+  apatheme+
+    geom_histogram(data=subset(tdl,variable == 'trial_length'),fill = "red", alpha = 0.5) +
+    geom_histogram(data=subset(tdl,variable == 'post_nam_dur'),fill = "blue", alpha = 0.5)
 

### 2018-11-11 Paper_Analyses.Rmd
streamline same_infant analyses
replace collapse by same_infant_calc (as in metalab)

@@
 
-db_ET$collapse <- paste(db_ET$study_ID, db_ET$expt_num, db_ET$same_infant, sep = "_")
+db_ET$same_infant_calc <- paste(db_ET$study_ID, db_ET$expt_num, db_ET$same_infant, sep = "_")
 
@@
 db_ET_MP <- db_ET[db_ET$is_mp=="1",]
-
-#collapse over nonindependent MP rows for a *general* MP effect
-
-collapse_rows <- function(db){
-  db$collapse <- paste(db$study_ID, db$expt_num, db$same_infant, sep = "_")
-
-  for(independent in unique(db$collapse)){
-    if(length(db[db$collapse==independent])>1){
-      sub = db[db$collapse==independent, ]
-      sub$d_calc <- median(sub$d_calc)
-      sub$d_var_calc <- median(sub$d_var_calc)
-      sub$g_calc <- median(sub$g_calc)
-      sub$g_var_calc <- median(sub$g_var_calc)
-      sub$corr_imputed <- median(sub$corr_imputed)
-      db <- db[!(db$collapse==independent),]
-      db <- rbind(db, sub[1,])
-    }
-  }
-  return(db)
-}
-
-#db_ET_correct = collapse_rows(db_ET_correct)
-
-#db_ET_MP = collapse_rows(db_ET_MP)
 
@@
 
-rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ collapse | short_cite)
+rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ same_infant_calc | short_cite)
 # Publication bias can become visible in funnel plot asymmetry. 
@@
 
-rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ collapse | short_cite)
+rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ same_infant_calc | short_cite)
 
@@
 
-rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ collapse | short_cite)
+rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ same_infant_calc | short_cite)
 
@@
 
-rma_MPeffect <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = ~ collapse | short_cite)
+rma_MPeffect <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = ~ same_infant_calc | short_cite)
 
@@
 
-#rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ collapse | short_cite)
+#rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ same_infant_calc | short_cite)
 
@@
 
-rma_correct_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = ~ collapse | short_cite)
+rma_correct_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = ~ same_infant_calc | short_cite)
 
@@
 
-rma_MP_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = ~ collapse | short_cite)
+rma_MP_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = ~ same_infant_calc | short_cite)
 
@@
 
-rma_MPeffect_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = ~ collapse | short_cite)
+rma_MPeffect_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = ~ same_infant_calc | short_cite)
 
@@
 
-rma_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur), data = db_ET_MP, random = ~collapse | short_cite)
+rma_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur), data = db_ET_MP, random = ~same_infant_calc | short_cite)
 
@@
 
- rma_post_dur_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur)*condition, data = dat, random = ~collapse | short_cite)
+ rma_post_dur_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur)*condition, data = dat, random = ~same_infant_calc | short_cite)
 
@@
 
- rma_post_dur_AGE <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur)*age.C, data = db_ET_MP, random = ~collapse | short_cite)
+ rma_post_dur_AGE <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur)*age.C, data = db_ET_MP, random = ~same_infant_calc | short_cite)
 
@@
 
-  rma_post_dur_AGE_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur)*age.C*condition, data = dat, random = ~collapse | short_cite)
+  rma_post_dur_AGE_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur)*age.C*condition, data = dat, random = ~same_infant_calc | short_cite)
 
@@
 
-rma_offset <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset), data = db_ET_MP, random = ~collapse | short_cite)
+rma_offset <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset), data = db_ET_MP, random = ~same_infant_calc | short_cite)
 
@@
 
- rma_offset_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*condition, data = dat, random = ~collapse | short_cite)
+ rma_offset_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*condition, data = dat, random = ~same_infant_calc | short_cite)
 
@@
 
- rma_offset_AGE <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*age.C, data = db_ET_MP, random = ~collapse | short_cite)
+ rma_offset_AGE <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*age.C, data = db_ET_MP, random = ~same_infant_calc | short_cite)
 
@@
 
-  rma_offset_AGE_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*age.C*condition, data = dat, random = ~collapse | short_cite)
+  rma_offset_AGE_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*age.C*condition, data = dat, random = ~same_infant_calc | short_cite)
 
@@
 
-rma_within <- rma.mv(g_calc, g_var_calc, mods = ~dv_label, data = db_ET_MP, random = ~collapse | short_cite)
+rma_within <- rma.mv(g_calc, g_var_calc, mods = ~dv_label, data = db_ET_MP, random = ~same_infant_calc | short_cite)
 
@@
 
- rma_within_MS <- rma.mv(g_calc, g_var_calc, mods = ~dv_label*condition, data = dat, random = ~collapse | short_cite)
+ rma_within_MS <- rma.mv(g_calc, g_var_calc, mods = ~dv_label*condition, data = dat, random = ~same_infant_calc | short_cite)
 
@@
 
- rma_within_AGE <- rma.mv(g_calc, g_var_calc, mods = ~dv_label*age.C, data = db_ET_MP, random = ~collapse | short_cite)
+ rma_within_AGE <- rma.mv(g_calc, g_var_calc, mods = ~dv_label*age.C, data = db_ET_MP, random = ~same_infant_calc | short_cite)
 
@@
 
-  rma_within_AGE_MS <- rma.mv(g_calc, g_var_calc, mods = ~dv_label*age.C*condition, data = dat, random = ~collapse | short_cite)
+  rma_within_AGE_MS <- rma.mv(g_calc, g_var_calc, mods = ~dv_label*age.C*condition, data = dat, random = ~same_infant_calc | short_cite)
 
@@
 
-rma_correct_DV = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ collapse | short_cite, ~ dv_label | short_cite))
+rma_correct_DV = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
 
@@
 
-rma_MP_DV = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ collapse | short_cite, ~ dv_label | short_cite))
+rma_MP_DV = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
 
@@
 
-rma_MPeffect_DV <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ collapse | short_cite, ~ dv_label | short_cite))
+rma_MPeffect_DV <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
 
@@
 
-rma_correct_age_DV = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ collapse | short_cite, ~ dv_label | short_cite))
+rma_correct_age_DV = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
 
@@
 
-rma_MP_age_DV = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ collapse | short_cite, ~ dv_label | short_cite))
+rma_MP_age_DV = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
 
@@
 
-rma_MPeffect_age_DV <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ collapse | short_cite, ~ dv_label | short_cite))
+rma_MPeffect_age_DV <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
 
@@
 
-rma_correct_post_dur = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ collapse | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+rma_correct_post_dur = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
 
@@
 
-rma_MP_post_dur = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ collapse | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+rma_MP_post_dur = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
 
@@
 
-rma_MPeffect_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ collapse | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+rma_MPeffect_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
 
@@
 
-rma_correct_age_post_dur = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ collapse | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+rma_correct_age_post_dur = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
 
@@
 
-rma_MP_age_post_dur = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ collapse | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+rma_MP_age_post_dur = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
 
@@
 
-rma_MPeffect_age_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ collapse | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+rma_MPeffect_age_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
 

### 2018-11-11 Paper_Analyses.Rmd
Comments introduction

@@
 Acquiring a first language means that young learners are solving a host of tasks in a short amount of time.
-As infants develop into toddlers during their second and third years they learn new words in earnest while simultaneously refining their knowledge about the sounds that make up these words.
-Before children can correctly pronounce a word, they already show evidence of sensitivity to slight variations in the phonological form of that word.
-This mispronunciation sensitivity reflects the specificity with which infants represent the phonological information of familiar words and are sensitive to changes that might signal a change in word meaning.
-As infants continue to develop into expert language users, their language processing matures and becomes more efficient.
+As infants develop into toddlers during their second and third years they learn new words in earnest while simultaneously refining their knowledge about the sounds that make up these words [Primir, Kuhl, Best].
 In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonetic details that differentiate words in their native language (e.g.
 cat-hat).
+To build robust language knowledge, it seems ueful to acquire this ability early during development.
+Indeed, before children can correctly pronounce a word, they already are aware that slight phonological deviations might signal a change in word meaning [].
+This mispronunciation sensitivity reflects the specificity with which infants represent the phonological information of familiar words.
+As infants continue to develop into expert language users, their language processing matures and becomes more efficient, including their knowledge of what consistutes a permissible versus word-changing phonological deviation.
 In this paper, we aggregate and analyze the almost 20 years of literature investigating mispronunciation sensitivity in infants in an attempt to uncover its characteristics and the trajectory of its development.
@@
   At the turn of the millenia, infant language acquisition researchers had established that during their first years of life, infants are sensitive to changes in the phonetic detail of newly segmented words (Jusczyk & Aslin, 1995) and learned minimal pairs (Stager & Werker, 1997).
-Furthermore, when presented with familiar image pairs, children fixate on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg, & McRoberts, 1998).
-Swingley and Aslin (2000) were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English were presented with pairs of images (e.g.
-baby, dog) and their eye movements to each image were coded offline.
+Furthermore, when presented with familiar image pairs, children fixate on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg, & McRoberts, 1998; Tincoff & Jusczyk, 1999).
+Swingley and Aslin (2000) were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English saw pairs of images (e.g.
+a baby and a dog) and their eye movements to each image were recorded and subsequently coded offline.
 On "correct" trials, children heard the correct label for one of the images (e.g.
-baby).
+"baby").
 On "mispronounced" trials, children heard a mispronounced label of one of the images (e.g.
-vaby).
-Mean proportion of fixation to the target image (here: a baby) was calculated for both correct and mispronounced trials by dividing the target looking time by the sum of total looking time to both target and a distractor (proportion of target looking or PTL).
-Mean fixations in correct trials were significantly greater than in mispronounced trials, although looks to the target were significantly greater than chance in both types of trials.
-We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance as *recognition*.
+"vaby").
+The mean proportion of fixations to the target image (here: a baby) was calculated separately for both correct and mispronounced trials by dividing the target looking time by the sum of total looking time to both target and a distractor (proportion of target looking or PTL).
+Mean fixations in correct trials were significantly greater than in mispronounced trials, and in both conditions looks to the target were significantly greater than chance.
+We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance in each condition as *recognition*.
 Swingley and Aslin (2000) concluded that already before the second birthday, children represent words with sufficient detail to be sensitive to mispronunciations.
 
-  The study of Swingley and Aslin (2000) as well as subsequent studies examining mispronunciation sensitivity address two complementary concepts in early phonological development: *phonological constancy* and *phonological distinctiveness*.
-Phonological constancy is the ability to accept phonological variation across different instances of a word, as long as the variation does not compromise the overall identity of the word.
+[Christina: changed concepts to mechanisms in the next paragraph, because I want to refer to what they represent, but I am not sure it\s the right term]
+
+  The study of Swingley and Aslin (2000) as well as subsequent studies examining mispronunciation sensitivity address two complementary mechanisms in early phonological development: *phonological constancy* and *phonological distinctiveness*, which are both present in the mature language processing system.
+Phonological constancy is the ability to resolve phonological variation across different instances of a word, as long as the variation does not compromise the overall identity of the word.
 For example, different speakers - particularly across genders and accents - produce the same word with notable acoustic variation, although the word remains the same.
 In contrast, phonological distinctiveness describes the ability to differentiate between different words that happen to be phonologically similar, such as bad/bed or cat/hat.
-To successfully recognize words, infants must therefore simultaneously use both phonological constancy and distinctiveness to determine where phonological variation is appropriate and where it changes a word's meaning.
+To successfully recognize words, speakers of a given language must therefore simultaneously use both phonological constancy and distinctiveness to determine where phonological variation is appropriate and where it changes a word's meaning.
+Both abilities have to be acquired, because language systems differ in which sounds signal a meaning change.
 
@@
 There are three distinct possibilities how mispronunciation sensitivity might change as infants become native speakers, which are all respectively predicted by theoretical accounts and supported by single studies.
-By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants.
+By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see Frank et al., 2018; for a notable exception).
 Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.
@@
 In this case, we would expect the size of mispronunciation sensitivity to be larger at younger ages and *decrease* as the child matures and learn more words, although children continue to detect mispronunciations.
-Indeed, young infants are less likely than older infants to demonstrate recognition of familiar words (Best, Tyler, Gooding, Orlando, & Quann, 2009; Mulak, Best, & Tyler, 2013) or learn new words (Schmale, Hollich, & Seidl, 2011) from accented speakers.
+Indeed, young infants are more perturbed by accented speakers than older infants in their recognition of familiar words (Best, Tyler, Gooding, Orlando, & Quann, 2009; Mulak, Best, & Tyler, 2013) or learning of new words (Schmale, Hollich, & Seidl, 2011).
 
@@
 Swingley and Aslin (2000) tested infants over a wide age range of 5 months (18 to 23 months).
-They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation effect) did not.
+They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation sensitivity) did not.
 This suggests that as children develop, they are more likely to look at the target in the presence of a mispronounced label and that age is not related to mispronunciation sensitivity.
@@
 One notable exception comes from Mani and Plunkett (2010: keps and tups).
-Here, 12-month-old infants were divided into a low vocabulary and high vocabulary group based group median vocabulary size.
+Here, 12-month-old infants were divided into a low and high vocabulary group based on median vocabulary size.
 High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations.
@@
 
-Taken together, the studies we have reviewed begin to paint a picture of the development of mispronunciation sensitivity.
-Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding.
-Meta-analyses can not only help us summarize the current state of research, but can also help us evaluate theories to drive future research and make hands-on recommendations for experiment planning.
+In sum, the studies we have reviewed begin to paint a picture of the development of mispronunciation sensitivity.
+Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding of early language development.
+Meta-analyses can provide thus further insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and their mispronunciations sensitivity.
+Because we aggregate data over various age groups, this meta-analysis can also investigate the role of maturation by assessing the impact of age and vocabulary size.
+As a consequence, our results will be important in evaluating theories and drive future research.
+We also make hands-on recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses (Bergmann et al., 2018).
 

### 2018-11-11 Paper_Analyses.Rmd
Comments on methods section

@@
 The most recent version is available via the website and the interactive platform MetaLab (metalab.stanford.edu; Bergmann et al., 2018).
-Since the present paper was written with embedded analysis scripts in R [@R], it is always possible to re-analyze an updated dataset.
+Since the present paper was written with embedded analysis scripts in R [@R, @RMarkdown, @papaja], it is always possible to re-analyze an updated dataset.
 In addition, we follow the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials (Moher, Liberati, Tetzlaff, Altman & PRISMAGroup, 2009).
-Figure X plots our PRISMA flowchart.
+Figure X plots our PRISMA flowchart illustrating the paper selection procedure.
 
@@
                 Vocabulary = ifelse(all(is.na(r_comprehension)) & all(is.na(r_production)), "None",
-                                ifelse(!all(is.na(r_comprehension)) & !all(is.na(r_production)), "Comprehension/Production",
-                                       ifelse(!all(is.na(r_comprehension)) & all(is.na(r_production)), "Comprehension", "Production"))))
-
-kable(Sum_table, col.names = c("Paper", "Publication format", "Age", "Vocabulary"))
-
-```
-
-[KATIE] THIS TABLE IS DEFINITELY NOT FINISHED!
-[CHRISTINA suggestions: N features should be a range and exclude 0; we could abbreviate Comperehension/Production to Comp./Prod., etcetc]
-[KATIE] I've reduced the table to be about age and vocabulary, in order to have it more focused for the aim of this paper.
+                                ifelse(!all(is.na(r_comprehension)) & !all(is.na(r_production)), "Comp/Prod",
+                                       ifelse(!all(is.na(r_comprehension)) & all(is.na(r_production)), "Comp", "Prod"))))
+
+#kable(Sum_table, col.names = c("Paper", "Publication format", "Age", "Vocabulary"))
+apa_table(Sum_table, col.names = c("Paper", "Publication format", "Age", "Vocabulary"), caption = "Summary of all studies.")
+
+```
+[Christina] I've shortened the labels and wanted to try out apa_table
 
@@
 This search was conducted on 22 September, 2017 and yielded 288 results.
-We screened the 398 items, removing 99 duplicate items.
-We screened remaining 299 items for their title and abstract to determine whether it met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition; (3) infants studied were under 36-months-of-age; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; 5) the stimuli were auditory speech.
+We screened the resulting 398 items, removing 99 duplicate items.
+We screened remaining 299 items for their title and abstract to determine whether it met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 36-months-of-age; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech.
 The final sample (n = *`r length(unique(dat$short_cite))`*) consisted of `r with(dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(dat, n_distinct(short_cite[publication_status == "dissertation"]))` thesis, and `r with(dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports.
@@
 
-The `r length(unique(dat$short_cite))` papers we identified as relevant were then coded with as much detail as possible (Tsuji, Bergmann, & Cristia, 2014; Bergmann et al., 2018).
+The `r length(unique(dat$short_cite))` papers we identified as relevant were then coded with as much consistently reported detail as possible (Tsuji, Bergmann, & Cristia, 2014; Bergmann et al., 2018).
 For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results.
-For the present analyses, we focus on the following characteristics:
+For the analyses presented in this section, we focus on the following characteristics:
 
@@
 
-We separated out conditions according to whether or not the target word was mispronounced to be able to investigate infants' looking to the target picture separated by whether or not words were mispronounced as well as their mispronunciation sensitivity, which is the difference between looks to the target in correct and mispronounced trials.
+We separated conditions according to whether or not the target word was mispronounced to be able to investigate infants' looking to the target picture as well as their mispronunciation sensitivity, which is the difference between looks to the target in correct and mispronounced trials.
 When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  (e.g., consonant versus vowel mispronunciations; Mani & Plunkett, 2007).
@@
 ```
-
-Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to a baseline measurement.
+[Christina] I think it would be useful to say how many records, not papers, report each measure. e.g. "(n = xxx records from yyy papers)". Would that be ok?
+
+Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement.
 PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images.
 Across papers the baseline comparison varied; we used the baseline reported by the authors of each paper.
-Most papers (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post_naming_effect"]))`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase.
-When interpreting this difference score, a positive value indicates that infants increased their looks to the target after hearing the naming label (correct or mispronounced).
-Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post"]))`) or compared post-naming PTL with a chance level of 50%, (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "post"]))`).
-For all these comparisons, a positive difference score or a post-naming phase PTL score that is greater than the pre-naming phase PTL or chance indicate target looks that indicate object recognition after hearing the naming label.
-Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more relative increase in looks to the target.
+Most papers (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post_naming_effect"]))`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase and report a difference score.
+
+[Christina] Katie, do you know whether the difference is computed based on items, participants, trials...? Is there consistency?
+
+Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post"]))`), thus reporting two variables, or compared post-naming PTL with a chance level of 50%, (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "post"]))`).
+For all these comparisons, positive values (either as reported or after subtraction of chance level or a pre-naming PTL) indicate target looks towards the target object after hearing the label, i.e.
+a recognition effect.
+Standardized effect sizes based on mean differences, as calculated here, preserve the sign.
+Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more looks to the target.
 
@@
 To correct for the small sample sizes common in infant research, however, we use as a dependent variable Hedges' *g* instead of Cohen's *d* (Hedges, 1981; Morris, 2000).
+
+[Christina] These numbers seem wrong! Again, how about (xx effect sizes from yy papers)?
 
@@
 
-[CHRISTINA: Do you think we have to revise this section? I think it's the same as in the proceedings paper.]
-[KATIE: Are you concerned about the Publication Bias section in particular, or the Methods as a whole?
-In general, some of the Methods was written before the CogSci paper and in other places to flesh things out I rewrote what we had in the CogSci paper.
-Its definitely giving the same information and sometimes the wording is close, because there's not too many different ways to explain what a funnel plot is :)]
-
 In the psychological sciences, there is a documented reluctance to publish null results.
-As a result, there is a potential for significant results to be valued over non-significant results (see Ferguson & Heene, 2012).
+As a result, significant results tend to be over-reported and thus might be over-represented in our meta-analyses (see Ferguson & Heene, 2012).
 To examine whether this is also the case in the mispronunciation sensitivity literature, which would bias the data analyzed in this meta-analysis, we conduct two tests.
 We first examine whether effect sizes are distributed as expected based on sampling error using the rank correlation test of funnel plot asymmetry with the R [@R] package metafor [@metafor].
-Effect sizes with low-variance are expected to fall closer to the estimated mean, while effect sizes with high-variance should show an increased, evenly-distributed spread around the estimated mean.
+Effect sizes with low variance are expected to fall closer to the estimated mean, while effect sizes with high variance should show an increased, evenly-distributed spread around the estimated mean.
+Publication bias would lead to an uneven spread.
+
 Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app (v4.0, p-curve.com; @pcurve).
-This tests for evidential value by examining whether the p-values have an expected distribution, regardless of whether the null hypothesis is true or not, as well as whether there is a larger proportion of p-values just below the typical alpha threshold of .05, which may indicate questionable research practices.
-Responses to correctly pronounced and mispronounced labels are predicted to show different patterns of looking behavior; as a result, we conduct these two analyses to assess publication bias separately for both conditions.
+This p-curve tests for evidential value by examining whether the p-values follow the expected distribution of a right skew in case the alternative hypothesis is true, versus a flat distribution that speaks for no effect being present in the population and all significant effect being spurious.
+Responses to correctly pronounced and mispronounced labels are predicted to show different patterns of looking behavior, with some studies reporting no significant looks to the target when hearing a mispronounced label
+
+[Christina] Katie, is that right, can you add a citation?
+
+(i.e. there might be no effect present in the population, see e.g., ); as a result, we conduct these two analyses to assess publication bias separately for both conditions.
 
@@
 
-The models reported are hierarchical random-effects models (infant groups nested within papers) of variance-weighted effect sizes with the R [@R] package metafor [@metafor].
-To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we introduce age (centered; continuous and measured in days but transformed into months for ease of reading by dividing by 30.44) as a moderator to our main model.
-For the subsequent investigations of experimental characteristics, we introduce each characteristic as a moderator (more detail below).
-
-[CHRISTINA: Let's both reread the full paper once it is ready and check that this is properly motivated and whether we do need to list them all.
-For now I think the last sentence is fine, but I would tend to prefer a reminder for the forgetful reader.]
-[KATIE: that's reasonable!
-We had just listed everything 7 paragraphs before, which doesn't seem like a lot of "space".
-Alternatively, this information could be listed in a table, and then just referred to.]
+The models reported here are hierarchical random-effects models (infant groups nested within papers) of variance-weighted effect sizes, which we computed with the R [@R] package metafor [@metafor].
+To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we introduce age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44) as a moderator to our main model.
+For a subsequent exploratory investigations of experimental characteristics, we introduce each characteristic as a moderator (more detail below).
 

### 2018-11-13 Paper_Analyses.Rmd
Comments on confirmatory results

@@
 
-CI_p <- function(x) paste0("(95% CI[", r2(x$ci.lb), ", ", r2(x$ci.ub), "], *p* ", psig(x$pval), ")")
+CI_p <- function(x) paste0("(CI [", r2(x$ci.lb), ", ", r2(x$ci.ub), "], *p* ", psig(x$pval), ")")
 
@@
 We should also point out that funnel plot asymmetry can be caused by multiple factors beside publication bias.
-The funnel plot asymmetry may also reflect heterogeneity in the data, perhaps due to some studies investigating more subtle effects than other studies.
-[CHRISTINA: I have to add some bits here.]
+The funnel plot asymmetry may also reflect heterogeneity in the data.
+There are various possible sources of heterogeneity, which our subsequent moderator analyses will begin to address.
+Nonetheless, we will remain cautious in our interpretation of our findings and hope that an open dataset that can be expanded by the community will attract previously unpublished null results so we can better understand infants' developing mispronunciation sensitivity.
 
@@
   #Give the x- and y- axes informative labels
-  xlab('Standard Error') + ylab('Hedge\'s g')+
+  xlab('Standard Error') + ylab('Hedges\' g')+
   # give it a title
@@
     # remove y label because it will be combined with the other funnel plot
-    ylab('Hedge\'s g')+
+    ylab('Hedges\' g')+
     # give it a title
@@
 We next examined the p-curves for significant values from the correctly pronounced and mispronounced conditions.
-The p-curve based on `r pcd_correct$ksig` statistically significant values for correct pronunciations indicates that the data contain evidential value (Z = `r r2(pcd_correct$Zppr)`, *p* `r psig(pcd_correct$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05.
-The p-curve based on `r pcd_misp$ksig` statistically significant values for mispronunciations indicates that the data contain evidential value (Z = `r r2(pcd_misp$Zppr)`, *p* `r psig(pcd_misp$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05.
+The p-curve based on `r pcd_correct$ksig` statistically significant values for correct pronunciations indicates that the data contain evidential value (Z = `r r2(pcd_correct$Zppr)`, *p* `r psig(pcd_correct$p.Zppr)`) and we find no evidence of a large proportion of p-values just below the typical alpha threshold of .05 that researchers consistently apply in this line of research.
+The p-curve based on `r pcd_misp$ksig` statistically significant values for mispronunciations indicates that the data contain evidential value (Z = `r r2(pcd_misp$Zppr)`, *p* `r psig(pcd_misp$p.Zppr)`) and there is again no evidence of a large proportion of p-values just below the typical alpha threshold of .05.
 
@@
 As a result, our meta-analysis may systematically overestimate effect sizes and we therefore interpret all estimates with caution.
-Yet, the p-curve analysis suggests that overall, the literature contains evidential value, reflecting a "real" effect.
+Yet, the p-curve analysis suggests that the literature contains evidential value, reflecting a "real" effect.
 We therefore continue our meta-analysis.
@@
 
-We first calculated the meta-analytic effect for object identification, i.e.
-looks to the target image in response to correctly pronounced words.
+We first calculated the meta-analytic effect for infants' ability to identify objects when hearing correctly pronounced labels.
 The variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was significantly different from zero `r CI_p(sum_eff)`.
@@
 That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object.
-Our analysis of funnel plot asymmetry, however, found evidence for publication bias, which might lead to an overestimated effect sizes as smaller, non-significant results might not be published.
-Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` suggests that this result is robust even when correcting for publication bias.
+Our analysis of funnel plot asymmetry, however, found evidence for publication bias, which might lead to an overestimated effect sizes as smaller, non-significant results might not be published despite the fact that they should occur regularly even in well-powered studies.
+Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` which is substantially above zero suggests that this result should be robust even when correcting for publication bias.
 In other words, we are confident that the true population mean lies above zero for object recognition of correctly pronounced words.
-
-[CHRISTINA: Can you explain what the CI lower bound means here? I don't follow.]
-[KATIE: What do you think about this (last sentence)? The CI lower bound stuff here actually comes from something you wrote, so tell me whether its correct.]
 
@@
 This indicated that the sample contains unexplained variance leading to significant difference across our studies beyond what is to be expected based on random sampling error.
-We therefore continue with our moderator analysis.
+We therefore continue with our moderator analysis to investigate possible sources of this variance.
+
+[Christina] I am not sure about the placement of this paragraph because the next section cannot explain this heterogeneity, so maybe we should move it down to the beginning of the age part?
 
@@
 The above two analyses considered the data from mispronounced and correctly pronounced words separately.
-To evaluate mispronunciation sensitivity, we  compared the effect size Hedges' *g* for correct pronunciations with mispronunciations directly, merging the two datasets.
+To evaluate mispronunciation sensitivity, we compared the effect size Hedges' *g* for correct pronunciations with mispronunciations directly.
+To this end, we combined the two datasets.
 The moderator test was significant, `r mod_test(rma_MPeffect)`.
-Hedges' *g* for mispronunciation sensitivity was `r g_SE(sum_eff)`, which indicated that the responses across conditions were significantly different `r CI_p(sum_eff)`.
+The estimate for mispronunciation sensitivity was `r g_SE(sum_eff)`, and infants' looking times across conditions were significantly different `r CI_p(sum_eff)`.
 This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations.
-In other words, we observe a significant difference between the two conditions and can now quantify the modulation of fixation behavior in terms of standardized effect sizes.
+In other words, we observe a significant difference between the two conditions and can now quantify the modulation of fixation behavior in terms of standardized effect sizes and their variance.
+This first result has both theoretical and practical implications, as we can now reason about the amount of perturbance caused by mispronunciations and can plan future studies to further investigate this effect with suitable power.
 
@@
 To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered, in days). 
+[Christina] What about the whole months thing?
+
 In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not.
-Age did not significantly modulate object identification in response to correctly pronounced `r mod_test(rma_correct_age)` or mispronounce words `r mod_test(rma_MP_age)`.
+Age did not significantly modulate object identification in response to correctly pronounced (`r mod_test(rma_correct_age)`) or mispronounce words (`r mod_test(rma_MP_age)`).
 The lack of a significant modulation together with the small estimates indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label.
 This relationship is plotted in Figure 2.
+
+[Christina] OK there is a mismatch between what you write and the numbers, can you verify?
 
@@
 mispronounced words) in our whole dataset.
-The moderator test was significant `r mod_test(rma_MPeffect_age)`.
-This result is in line with the general observation that as infants mature they become better at language processing.
-The interaction between age and mispronunciation sensitivity, however, was not significant $\beta$`r full_estimate(sum_eff)`.
-The small estimate size, as well as inspection of Figure 2 suggests that as infants age, their mispronunciation sensitivity remains the same.
+The moderator test was significant (`r mod_test(rma_MPeffect_age)`).
+The interaction between age and mispronunciation sensitivity, however, was not significant ($\beta$ `r full_estimate(sum_eff)`), pointing to the moderator test being driven by the difference between conditions.
+The small estimate, as well as inspection of Figure 2 suggests that as infants age, their mispronunciation sensitivity remains the same.
 
@@
   ggtitle("b. Mispronunciation Sensitivity")+
-  geom_point(aes(size = n_1),show.legend=FALSE, alpha = .5) + 
+  geom_point(aes(size = n_1/2),show.legend=FALSE, alpha = .3) + 
   geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1), color = "black") +
   scale_colour_manual(values=cbPalette)+
@@
 
-Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers; production = `r with(vi1, papers[has_vocab == "production"])`) analyzed the relationship between vocabulary scores and mispronunciation sensitivity, specifically object recognition for correct pronunciations and mispronunciations.
+Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` analyzed the relationship between vocabulary scores and object recognition for correct pronunciations and mispronunciations (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers; production = `r with(vi1, papers[has_vocab == "production"])`).
 There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we analyze this data separately.
 
-[CHRISTINA] SO WE DON'T WANT TO INTERPRET THE FIXED EFFECTS MODEL AT ALL, IT IS NOT SUITABLE BECAUSE THERE IS VARIANCE BETWEEN EVERY RECORD (LANGUAGE ETC).
-I WOULD INTERPRET THE OVERALL CORRELATION AND THE CI, NOT THE P-VALUE (IN GENERAL).
-I ALSO WONDER WHETHER WE SHOULD MOVE THE SUBSET ANALYSES TO THE SUPPLEMENTARY MATERIALS AND JUST SAY OVERALL WE SEE NO RELATIONSHIPS AND CORRELATION COEFFICIENTS CONSISTENYL BELOW .1
-WE THEREFORE MUST CONCLUDE THAT WITHIN NARROW AGE GROUPS VOCABULARY DOES NOT INFLUENCE ANYTHING WE LOOK AT. WE CANNOT DO THIS ANALYSIS FPOR MP SENSITIVITY BECAUSE WE DON'T HAVE THE NECESSARY RAW DATA.
-[KATIE: Ah, so because for each paper the correlation and CI values straddle 0, this indicates that there really isn't much evidence for a relationship?
-I've tried to write this out below, let me know what you think.
-Over the summer, I had also played around with looking at how collection of vocabulary data has dropped off over the years, even though more mispronunciation studies have been published.
-That might be something interesting to add.
-If we truly think that this is what is driving the development of mispronunciation sensitivity, then why are people not collecting this data?]
-(BUT I WONDER WHETHER WECOULD ENCODE THE REPORTED INTERACTION TERMS AND THE CORRELATION AND THEN DO SOMETHING WITH THAT?)
-[KATIE: I'm not really sure what you mean by this :(]
+[Christina] Removed the previous comment chaos.
+So can you not only list papers but also n conditions above? With just 1 paper for production, I wouldn't analyze it to be honest. it's just not enough data. 
+I also liked your comments about the time line of this whole thing, can you extract the years of papers which report this?
+Might be extremely useful in the discussion and strengthens our case that there is no effect, bc people don't find the predicted relation with vocab.
+Also, cann you add a citation for comp vs prod? I think Evan Kidd had a paper on it, if you don't have one handy, I can look it up.
 
@@
 [Katie: below, I'm using coweeta.uga.edu/publications/10436.pdf, page 80 as a model for writing up these results. I haven't the funniest clue what I'm doing! :p]
+[Christina] looks good to me.
 
@@
 Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for 9 of 12 experimental conditions, with correlation values ranging from -0.17 to 0.48.
-The mean effect size XXX was 0.0897, but did not differ significantly from zero (95% CI[-0.0105; 0.1900] *p* = .0795).
+The mean effect size XXX was small with 0.0897, which did not differ significantly from zero (CI [-0.0105; 0.1900] *p* = .0795).
+However, the lower bound of the CI is close to zero, and one might hypothesize that with more power the small relationship might become significant.
+At the same time, a larger sample might confirm our conclusion that there is no relationship.
+
 Higher production scores were also associated with greater object recognition in response to correct pronunciations for 9 of 16 experimental conditions, with correlation values ranging from -0.23 to 0.44.
-The mean effect size XXX was 0.0601, but did not differ significantly from zero (95% CI[-0.0331; 0.1533] *p* = .2061).
+The mean effect size XXX was again small and not significantly different from zero with 0.0601 (CI [-0.0331; 0.1533] *p* = .2061).
 For both comprehension and production scores, the small correlation effect sizes and large variances suggest a lack of relationship between vocabulary and object recognition for correct pronunciations.
+However, we note again that comparatively few studies report the correlation between vocabulary and infants' responses to correct pronunciations to begin with and thus we cannot draw any firm conclusions based on this small sample of studies.
+
+[Christina] I think bc the effect is small but apparently consistent, we can reason that we might have a power problem and thus cannot draw firm conclusions.
 
@@
 Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for 17 of 31 experimental conditions, with correlation values ranging from -0.35 to 0.57.
-The mean effect size XXX was 0.0377, but did not differ significantly from zero (95% CI[-0.0260; 0.1014] *p* = .2465).
+The mean effect size XXX was 0.0377, but did not differ significantly from zero (CI[-0.0260; 0.1014] *p* = .2465).
 For production, however, lower production scores were associated with greater object recognition in response to mispronunciations for 16 of 31 experimental conditions, with correlation values ranging from -0.28 to 0.44.
-The mean effect size XXX was -0.0402, but did not differ significantly from zero (95% CI[-0.1043; 0.0238] *p* = .2181).
-For both comprehension and production scores, the small correlation effect sizes and large variances suggest a lack of relationship between vocabulary and object recognition for mispronunciations.
+The mean effect size XXX was -0.0402, (CI [-0.1043; 0.0238] *p* = .2181).
+For both comprehension and production scores, the small correlations and large variances suggest a lack of relationship between vocabulary and object recognition for mispronunciations.
+We again emphasize that we cannot draw firm conclusions due to the small number of studies we were able to include here.
+
+[Christina] Is there a reason the above numbers aren't read out as before?
+Also, I think the effect size is pearson's r, because that's what we put in, right?
 
@@
 The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age.
-The results are clear: Although infants consider a mispronunciation as a better match with the target image than a distractor image, there was a consistent effect of mispronunciation sensitivity.
+The results seem clear: Although infants consider a mispronunciation as a better match with the target image than a distractor image, there was a consistent effect of mispronunciation sensitivity.
 This did not change with development.
@@
 
-Alternatively, it is possible that variation in the analysis approach lead to systematic differences in the size of mispronunciation sensitivity.
-Choices about the approach to data analysis have a higher possibility to be influenced by the shape of the data itself after collection, and are therefore susceptible to a higher rate of false-positives (Simmons, Nelson, & Simonsohn, 2011).
-Although we did not have specific predictions about these variables, such as size of time window analyzed or dependent variable calculated, we included these variables in our coding scheme for the meta-analysis dataset.
-As reported in the Methods section (and discussed in detail below), some of these variables varied widely across studies.
+Alternatively, an effect of maturation might have been masked by other factors we have not yet captured in our analyses.
+A strong candidate that emerged during the construction of the present dataset and careful reading of the original papers is the analysis approach.
+We observed, as mentioned in the Methods section, large variance in the dependent variable reported, and additionally noted variance in the time window chosen for analyses.
+Researchers might adapt their analysis strategy to age or they might be influenced by having observed the data.
+In the latter case, we expect an increase in significant results, which at the same time can (partially) explain the publication bias we observe (Simmons, Nelson, & Simonsohn, 2011).
+
+We included size of time window analyzed or dependent variable calculated in our coding of the dataset because they are consistently reported and might be useful for experiment design in the future by highlighting typical choices and helping establish field standards.
 In the following section, we include an exploratory analysis to investigate the possibility of systematic differences in the approach to analysis in general and across infant age.
-
-[KATIE] I've changed the above paragraph to lead to exploratory analyses, not moderators.
-Since the fmailiar/unfamiliar analysis doesn't really work out except for if we kind of subset and torture the data, I think its more interesting to talk about how choices of analysis / researcher degrees of freedom may influence the data
+Our analyses will show that a standard, a priori registered analysis of looking while listening paradigms is needed and can improve the health of a currently biased literature.
+
+[Christina] The last sentence is a bit clunky, please improve.
 

### 2018-11-14 Paper_Analyses.Rmd

@@
 
-We identified several variables to assess the influence of data analysis choices.
-These variables fall into two types of categories: time-related and dependent variable related.
-In the following analyses, we discuss the theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these choices have on mispronunciation sensitivity development.
+[Christina] This section talked about several variables in 2 categories, but in reality there are only 2 variables, right?
+I am not 100% sure about total trial length as being the first or being mentioned at all, might it be better to focus on time window analyzed and then say "Oh, btw, total trial length totally does nothing so we don't have to discuss it further" I am not sure, so feel free to re-rewrite this, but now it better lines up with everything before because trial length kinda comes out of nowhere.
+
+We identified two sets of variables which varied across papers to assess the influence of data analysis choices on resulting effect size: the time course of a trial and time window analyzed and which dependent variable(s) were reported.
+In the following, we discuss the possible theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these analysis choices have on mispronunciation sensitivity development.
 
@@
 
-When designing mispronunciation sensitivity studies, experimenters choose the length of time each trial is presented.
+[Christina] Ideally load all libraries in the beginning of the doc. (reshape)
+
+[Christina] Is there a reason you choose mode and not median?
+
+[Christina] Would it make sense to present dependent variable first?
+
+[Christina] So if you go with my suggestion from above, I would just add this sentence at the beginning of the next paragraph: "Before we focus on analysis choice relating to time windows, we must first discuss overall trial length, because it limits the overall time window available to analyze and might thus predict which time window was analyzed."
+
+When designing mispronunciation sensitivity studies, experimenters can choose the length of time each trial is presented.
 This includes both the length of time before the target object is named (pre-naming phase) as well as after (post-naming phase) and is determined prior to data collection.
 Across papers, trial length varied from `r with(trial_length_info, min(trial_length))*1000` to `r with(trial_length_info, max(trial_length))*1000` ms, with a mode of `r with(dat, getmode(trial_length))*1000` ms.
-There was an inverse relationship between infant age and trial length, such that younger infants were given trials of a longer length, although this correlation was not significant (*r* = `r trial.l$estimate`, *p* `r psig(trial.l$p.value)`).
-Presumably, younger infants may be given longer trials because their word recognition abilities may be slower than older infants (Fernald et al., 1998).
+There was an inverse relationship between infant age and trial length, such that younger infants were presented with longer trials, although this correlation was not significant (*r* = `r trial.l$estimate`, *p* `r psig(trial.l$p.value)`).
+Presumably, younger infants may be exposed to longer trials because their word recognition abilities may be slower than older infants (Fernald et al., 1998).
 
 Unlike the length of trial, the length of the post-naming phase analyzed can be chosen after the experimental data is collected.
-Interestingly, half of the experimental conditions were analyzed using the same length of post-naming phase as the infant heard in the actual experiment `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`, while the other half were analyzed using a shorter length of post-naming phase, excluding later portions of the post-naming phase `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`.
+Interestingly, half of the experimental conditions were analyzed using the same length of post-naming phase as the infant heard in the actual experiment (`r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`), while the other half were analyzed using a shorter length of post-naming phase, excluding later portions of the post-naming phase (`r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`).
 Across papers, the length of the post-naming phase analyzed varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a mode of `r with(dat, getmode(post_nam_dur))*1000` ms.
-Similar to trial length, there was an inverse relationship between infant age and length of post-naming phase analyzed, such that younger infants were analyzed using a longer length of post-naming phase, although here the relationship was significant (*r* = `r post.l$estimate`, *p* `r psig(post.l$p.value)`).
+Similar to trial length, there was an inverse relationship between infant age and length of post-naming phase analyzed, such that younger infants'looking times were analyzed using a longer post-naming phase, here the relationship was significant (*r* = `r post.l$estimate`, *p* `r psig(post.l$p.value)`).
 Again, the choice to analyze a shorter post-naming time window is likely related to evidence that speed of processing is slower in younger infants (Fernald et al., 1998).
-Furthermore, the proportion of post-naming phase time window analyzed in comprison to the total post-naming phase presented to infants significantly decreased with increasing infant age (*r* = `r post_match.l$estimate`, *p* `r psig(post_match.l$p.value)`).
-Although trial length did not differ by infant age, the size of the post-naming phase time window analyzed did differ by infant age.
+
+[Christina] I think the proportion needs more explanation, also because later we have proportions of looks to target.
+
+Furthermore, the proportion of post-naming phase time window analyzed in comparison to the total post-naming phase presented to infants significantly decreased with increasing infant age (*r* = `r post_match.l$estimate`, *p* `r psig(post_match.l$p.value)`).
+To summarize, we observe variation in time-related aspects related to infants' age.
+This variation is most pronounced, and even significant, for the time window that is being analyzed after the target label has been heard.
+
+[Christina] The canfield & haith paper is for visual stimuli, right?
+So add that before "stimulus".
+And then add to the next sentence that the longer latnecies are because ther eis addiitonal language processing required which EEg shows in adults to take X ms (400 for N400?).
+
+[Christina] Can you add info how many papers did not report the analyzed variables? Across this whole section, I mean.
 
@@
 There was an inverse relationship between infant age and size of offset, such that younger infants were given longer offsets, although this correlation was not significant (*r* = `r offset.l$estimate`, *p* `r psig(offset.l$p.value)`).
-This lack of a relationship is perhaps driven by the field's consensus that an offset of about 367 ms is appropriate for analyzing word recognition with PTL measures, including studies that evaluate mispronunciation sensitivity.
-
-Although there are a priori reasons to choose the post-naming time window (infant age) or offset time (previous studies), these choices may occur after data collection and are therefore susceptible to a higher rate of false-positives.
-Considering that differences in these choice were systematically different across infant ages, at least for the post-naming time window, we next explored whether the size of the analyzed post-naming phase time window or the offset time influenced sensitivity to mispronunciations.
-
-### Length of post time
+This lack of a relationship is possibly driven by the field's consensus that an offset of about 367 ms is appropriate for analyzing word recognition with PTL measures, including studies that evaluate mispronunciation sensitivity.
+
+Although there are a priori reasons to choose the post-naming time window (infant age) or offset time (previous studies), these choices may occur after data collection and might therefore lead to a higher rate of false-positives (Gelman, A., & Loken, E.
+(2013).
+The garden of forking paths: Why multiple comparisons can be a problem, even when there is no “fishing expedition” or “p-hacking” and the research hypothesis was posited ahead of time.
+Department of Statistics, Columbia University.).
+Considering that these choices were systematically different across infant ages, at least for the post-naming time window, we next explored whether the size of the analyzed post-naming time window or the offset time influenced sensitivity to mispronunciations.
+
+### Length of post naming time window
 
@@
 
-We first assessed whether size of post-naming phase analyzed had an impact on the size of mispronunciation sensitivity.
-First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images, including post-naming phase size as a moderator.
+[Christina] I think it's a bit inconsistent whether it's post naming phase or window, how about window?
+Phase sounds wrong to me.
+or analysis window?
+I also find phase size odd, and again prefer window (window size).
+Your call though.
+
+We first assessed whether size of post-naming phase analyzed had an impact on the size of the reported mispronunciation sensitivity.
+First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images, including post-naming window size as a moderator.
+
+[Christina] the next bit is weird, in the pdf it's significant, but you write it's not. Also, I think the beta is quite large anbd the CI reasonably distinct from 0.
+
 The moderator test was not significant `r mod_test(rma_post_dur)` and the estimate for post-naming phase size was relatively small, $\beta$`r full_estimate(rma_post_dur_eff)`.
+
+[Christina] Even if a test is not significant, this next sentence is always wrong because we did not test whether it's the same (i.e. we did not do an equivalence or Bayesian test!)
 This suggests that upon hearing a mispronunciation, infants' looks to the target image were similar regardless of the size of the post-naming phase analyzed.
 We next assessed whether post-naming phase size was related to mispronunciation sensitivity.
+
+[Christina] To be sure, you base this again on the combined data and only plot differences for easier visualizations in figure 3?
+Ideally make that clear.
+Also, some suggestions to vary this sentence (also earlier in the paper)
+"To investigate mispronunciation sensitivity, we considered data from both conditions in a joint analysis"
+"Analyzing all data with condition (c, mp) as additional moderator leads to the following results"
+etcetc
+
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
@@
 The moderator test was significant `r mod_test(rma_post_dur_AGE_MS)`.
+
+[Christina] lots of NAs here in the pdf
+
 The estimate for the  three-way-interaction between condition, size of post-naming phase, and age was small, but significant ($\beta$ = `r full_estimate(rma_post_dur_AGE_MS_eff)`.
@@
 Smaller post-naming phase size lead to greater increases in mispronunciation sensitivity with development.
-For example, experimental conditions analyzed with a post-naming phase of 2000 ms or less, mispronunciation sensitivity increases with infant age, whereas a post-naming phase of greater than 2000 ms leads to either no impact of age on mispronunciation sensitivity or a negative relationship between age and mispronunciation sensitivity.
+
+[Christina] The next sentence as weird, check whether my corrections make sense
+
+For example, when experimental conditions were analyzed with a post-naming phase of 2000 ms or less, mispronunciation sensitivity increases with infant age, whereas there is no or a negative relation of mispronunciation sensitivity and age if the analyzed post-naming phase is greater than 2000 ms leads.
+In other words, all three possible hypotheses might be supported depending on analysis choices made.
+
+[Christina] I think it's important to remind the reader here that this is our key question, namely how age and mp sensitivity are related.
 
@@
 
-### Length of offset time
+### Offset after target naming
 
@@
 
-We next assessed whether offset time had an impact on the size of mispronunciation sensitivity.
-First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images, including offset time as a moderator.
+We next assessed whether the time between the target was named and the start of the analysis, namely offset time, had an impact on the size of the reported mispronunciation sensitivity.
+First, we calculated the meta-analytic effect size for object identification in response to mispronounced target words/images, including offset time as a moderator.
+
+[Christina] again, the pdf tells me sth different
+
 The moderator test was not significant `r mod_test(rma_offset)` and the estimate for offset time was very small, $\beta$`r full_estimate(rma_offset_eff)`.
+
+[Christina] Again, we didn't test, so say sth like "did not differ significantly."
+
 This suggests that upon hearing a mispronunciation, infants' looks to the target image were similar regardless of the offset time used to analyze the data.
 We next assessed whether offset time was related to mispronunciation sensitivity.
+
+[Christina] Again, rewording suggestion: "When investigating mispronunciation sensitivity by including condition, the moderator test with was ...
+
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, `r mod_test(rma_post_dur_MS)`, but the estimate for the interaction between offset time and condition was very small and not significant $\beta$`r full_estimate(rma_offset_MS_eff)`.
+The moderator test was significant, `r mod_test(rma_post_dur_MS)`, but the estimate for the interaction between offset time and condition was almost zero $\beta$`r full_estimate(rma_offset_MS_eff)`.
+
+[Christina] Generally, it might be easier to kick out all object recognition analyses (what do they tell us?) and start out that we only analyze MP sensitivity, i.e.
+consider the whole dataset and always include condition as moderator.
 
@@
 Experiments typically include a phase where no naming event has occured, whether correctly pronounced or mispronounced, which we refer to as the baseline.
-The purpose of the baseline is to ensure that infants do not have systematic preferences for the target or distractor (greater interest in a cat compared to cup) which may drive PTL scores in the post-naming phase.
+The purpose of the baseline is to ensure that infants do not have systematic preferences for the target or distractor (greater interest in a cat compared to a cup) which may drive PTL scores in the post-naming phase.
 As described in the Data Analysis sub-section of the Methods, there was considerable variation across papers in way that baseline was calculated, resulting in different measured outcomes or dependent variables.
@@
 We will refer to this dependent variable as the Difference Score.
-Another dependent variable, which was used in `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` experimental conditions, directly compared compared the post- and pre-naming PTL scores with one another.
+Another dependent variable, which was used in `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` experimental conditions, directly compared the post- and pre-naming PTL scores with one another.
 This requires two values, one for the pre-naming phase and one for the post-naming phase.
@@
 
+[Christina] Did I ask the following already: Do we know whether subtrations were on the trial level?
+Pre vs post is a bit differnt because it loses the individual bias accommodation and the correlation between pre and post on the participant / item level.
+
 The Difference Score and Pre vs.
@@
 The Post dependent variable, in contrast, does not consider pre-naming preferences.
+
+[Christina] Actually, in other domains (eeg, longitudinal studies, RCTs) people tlak a lot about whether or not to consider a baseline, so this is not strictly true.
+
 To our knowledge, there is no theory or evidence to drive choice of dependent variable, which may explain the wide variation in dependent variable reported in the papers included in this meta-analysis.
@@
 When the dependent variable was Pre vs.
-Post, mispronunciation sensitivity decreased with infant development, while in comparison, when the dependent variable was Post, mispronunciation sensitivity increased with infant development.
+Post, mispronunciation sensitivity decreased with infant age, while in comparison, when the dependent variable was Post, mispronunciation sensitivity increased with infant age.
 There was no difference in mispronunciation sensitivity change with infant development between the Post and Difference Score dependent variables.
@@
 
-## Controlling for researcher choice
+## Controlling for analysis choices
 

### 2018-11-24 Paper_Analyses.Rmd
small updates to manuscript, towards a final exploratory analysis

@@
   - id            : "1"
-    institution   : "Language Development Laboratory, University of Maryland, USA"
+    institution   : "Department of Hearing and Speech Sciences, University of Maryland, USA"
   - id            : "2"
@@
 
+# can't call reshape here, because it will interfere with other libraries
+#library(reshape)
+
 r2 <- function(x){ round(x, 3)}
@@
 # moderator test
-mod_test <- function(x) paste0("QM(", r2(rma_MPeffect$m), ") = ", r2(rma_MPeffect$QM), ", *p*", psig(rma_MPeffect$QMp))
+mod_test <- function(x) paste0("QM(", r2(x$m), ") = ", r2(x$QM), ", *p*", psig(x$QMp))
 
@@
 To build robust language knowledge, it seems ueful to acquire this ability early during development.
-Indeed, before children can correctly pronounce a word, they already are aware that slight phonological deviations might signal a change in word meaning [].
+Indeed, before children can correctly pronounce a word, they already are aware that slight phonological deviations might signal a change in word meaning [Clark & Clark, 1977].
 This mispronunciation sensitivity reflects the specificity with which infants represent the phonological information of familiar words.
@@
 Mean fixations in correct trials were significantly greater than in mispronounced trials, and in both conditions looks to the target were significantly greater than chance.
-We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance in each condition as *recognition*.
+We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance in each condition as *object identification*.
 Swingley and Aslin (2000) concluded that already before the second birthday, children represent words with sufficient detail to be sensitive to mispronunciations.
 
-[Christina: changed concepts to mechanisms in the next paragraph, because I want to refer to what they represent, but I am not sure it\s the right term]
-
-  The study of Swingley and Aslin (2000) as well as subsequent studies examining mispronunciation sensitivity address two complementary mechanisms in early phonological development: *phonological constancy* and *phonological distinctiveness*, which are both present in the mature language processing system.
+[Christina: changed concepts to mechanisms in the next paragraph, because I want to refer to what they represent, but I am not sure it's the right term]
+[Katie: Karen (Mulak) talks about these terms as concepts.
+Mechanisms to me means some sort of internalization, that they would have had this ability all along and just need to apply it.
+It could be that we fundamentally disagree on this, but to me these are things that infants discover.
+Later on we use principles.
+What about "principles that infants must discover"...
+"in order to form adult-like word representations"?
+I took away "which are both present in the mature language processing system".]
+
+  The study of Swingley and Aslin (2000) as well as subsequent studies examining mispronunciation sensitivity address two complementary principles that infants must discover in early phonological development in order to form adult-like word representations: *phonological constancy* and *phonological distinctiveness*.
 Phonological constancy is the ability to resolve phonological variation across different instances of a word, as long as the variation does not compromise the overall identity of the word.
@@
 
+[Katie: since we actually don't have theoretical framework support for the no-change theory, I've changed around the sentence below to explicitly say that only 2 of the 3 are predicted by theoretical accounts.]
+
   In the current study, we focus on infants' developing ability to correctly apply the principles of phonological distinctiveness and constancy by using a meta-analytic approach to investigate mispronunciation sensitivity.
 Considering that infants are sensitive to mispronunciations and that, in general, their processing matures with development, we examine the shape of mispronunciation sensitivity over the course of the second and third year.
-There are three distinct possibilities how mispronunciation sensitivity might change as infants become native speakers, which are all respectively predicted by theoretical accounts and supported by single studies.
+There are three distinct possibilities how mispronunciation sensitivity might change as infants become native speakers, which are all respectively supported by single studies and two predicted by theoretical accounts.
 By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see Frank et al., 2018; for a notable exception).
@@
 
-  Research following the seminal study by Swingley and Aslin (2000) has extended mispronunciation sensitivity to infants as young as 12 months (Mani & Plunkett, 2010), indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations.
+  Research following the seminal study by Swingley and Aslin (2000) has extended mispronunciation sensitivity to infants as young as 9 months (Bergelson & Swingley, 2017), indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations.
 Regarding the change in mispronunciation sensitivity over development, however, only a handful of studies have compared more than one age group on the same mispronunciation task (see Table X), making the current meta-analysis very informative.
@@
 
-```{r SummaryTable}
+```{r SummaryTable, results = "asis"}
 
@@
 [Christina] I've shortened the labels and wanted to try out apa_table
+[Katie] I like the idea, but does it work for you? It doesn't work for me...
+[Katie] We have it currently set at less than 31 months, not 36, so I've changed below.
 
@@
 We screened the resulting 398 items, removing 99 duplicate items.
-We screened remaining 299 items for their title and abstract to determine whether it met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 36-months-of-age; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech.
+We screened remaining 299 items for their title and abstract to determine whether it met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech.
 The final sample (n = *`r length(unique(dat$short_cite))`*) consisted of `r with(dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(dat, n_distinct(short_cite[publication_status == "dissertation"]))` thesis, and `r with(dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports.
@@
 comparison_info <- db_ET_correct %>%
-  group_by(within_measure_descriptive) %>%
+  group_by(within_measure) %>%
   summarize(n_unique = n_distinct(short_cite), count = n())
@@
 [Christina] I think it would be useful to say how many records, not papers, report each measure. e.g. "(n = xxx records from yyy papers)". Would that be ok?
+[Katie] Totally! I think that gives a good bit of information. Good suggestion!
 
@@
 Across papers the baseline comparison varied; we used the baseline reported by the authors of each paper.
-Most papers (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post_naming_effect"]))`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase and report a difference score.
+Most papers (*n* = `r with(comparison_info, count[within_measure == "pre_post_naming_effect"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post_naming_effect"])` papers) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase and report a difference score.
 
 [Christina] Katie, do you know whether the difference is computed based on items, participants, trials...? Is there consistency?
-
-Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "pre_post"]))`), thus reporting two variables, or compared post-naming PTL with a chance level of 50%, (*n* = `r with(db_ET_correct, n_distinct(short_cite[within_measure == "post"]))`).
+[Katie] From working with Nivi, we did it participants x condition or participants x trial (but mostly the former).
+But, this is not something we reported in papers.
+I don't think I read it at all when putting together the dataset for this either.
+
+Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(comparison_info, count[within_measure == "pre_post"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post"])` papers), thus reporting two variables, or compared post-naming PTL with a chance level of 50%, (*n* = `r with(comparison_info, count[within_measure == "post"])` records from `r with(comparison_info, n_unique[within_measure == "post"])` papers).
 For all these comparisons, positive values (either as reported or after subtraction of chance level or a pre-naming PTL) indicate target looks towards the target object after hearing the label, i.e.
@@
 [Christina] These numbers seem wrong! Again, how about (xx effect sizes from yy papers)?
-
-We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, n_distinct(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))`) or using reported t-values (*n* = `r with(es_info, n_distinct(n_unique[es_method == "t_one" | es_method == "t_two"]))`).
+[Katie] Well, they are kind of wrong :) Two papers report both for different experimental conditions.
+I've given the explanation now, not sure if that is good enough, but I'm really not sure how to say it a different way.
+[Katie] Do you want number of records and papers for the imputed correlations as well?
+You've put a -1, assuming there was something wrong with one of the papers or something like that?
+How does that shake out for number of records?
+
+We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, sum(count[es_method == "group_means_one" | es_method == "group_means_two"]))` records from `r with(es_info, sum(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))` papers) or using reported t-values (*n* = `r with(es_info, sum(count[es_method == "t_one" | es_method == "t_two"]))` records from `r with(es_info, sum(n_unique[es_method == "t_one" | es_method == "t_two"]))` papers).
+Two papers reported raw means and standard deviations for some experimental conditions and just t-values for the remaining experimental conditions (Swingley, 2016; Altvater-Mackensen et al., 2014).
 Raw means and standard deviations were extracted from figures for `r with(dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers.
@@
 This p-curve tests for evidential value by examining whether the p-values follow the expected distribution of a right skew in case the alternative hypothesis is true, versus a flat distribution that speaks for no effect being present in the population and all significant effect being spurious.
-Responses to correctly pronounced and mispronounced labels are predicted to show different patterns of looking behavior, with some studies reporting no significant looks to the target when hearing a mispronounced label
+Responses to correctly pronounced and mispronounced labels are predicted to show different patterns of looking behavior.
+In other words, there is an expectation that infants should look to the target when hearing a correct pronunciation, but some studies may report either significant looks or no  significant looks to the target when hearing a mispronounced label
 
 [Christina] Katie, is that right, can you add a citation? 
+[Katie] I've rewritten it a bit to be explicit about the difference between expectations for correct and mispronounced labels.
+I'm not sure what to cite though.
+The papers that find significant looks or no significant looks?
+That's basically the meta-analysis.
+Or some citation that talks about what looking to the target upon hearing a mispronunciation means in comparison to what target looks being decreased for mispronunciations relative to correct pronunciations means?
+I'm not so sure whether anyone has actually talked about that difference before, not sure what to cite.
 
@@
 
-Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, *p* `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, *p* `r psig(rma_MP$QEp)`).
-This indicated that the sample contains unexplained variance leading to significant difference across our studies beyond what is to be expected based on random sampling error.
-We therefore continue with our moderator analysis to investigate possible sources of this variance.
-
 [Christina] I am not sure about the placement of this paragraph because the next section cannot explain this heterogeneity, so maybe we should move it down to the beginning of the age part?
+[Katie] I think that makes sense, moving it!
 
@@
 
+Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, *p* `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, *p* `r psig(rma_MP$QEp)`), as well as mispronunciation sensitivity, which included the moderator condition, (QE(249) = `r r2(rma_MPeffect$QE)`, *p* `r psig(rma_MPeffect$QEp)`).
+This indicated that the sample contains unexplained variance leading to significant difference across our studies beyond what is to be expected based on random sampling error.
+We therefore continue with our moderator analysis to investigate possible sources of this variance.
+
 ### Object Recognition and Mispronunciation Sensitivity Modulated by Age
@@
 
-To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered, in days). 
+To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44 for Figure 2).
 [Christina] What about the whole months thing?
+[Katie] We had an explanation in the methods section for this, I've now added it again here.
 
 In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not.
-Age did not significantly modulate object identification in response to correctly pronounced (`r mod_test(rma_correct_age)`) or mispronounce words (`r mod_test(rma_MP_age)`).
-The lack of a significant modulation together with the small estimates indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label.
-This relationship is plotted in Figure 2.
+Age did not significantly modulate object identification in response to correctly pronounced (`r mod_test(rma_correct_age)`) or mispronounced words (`r mod_test(rma_MP_age)`).
+The lack of a significant modulation together with the small estimates (correct: $\beta$ `r full_estimate(Csum_eff)`; mispronunciation: $\beta$ `r full_estimate(Msum_eff)`) indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label.
+We plot both object recognition and mispronunciation sensitivity as a function of age in Figure 2.
 
 [Christina] OK there is a mismatch between what you write and the numbers, can you verify?
+[Katie] Good catch.
+For some reason, it was just copying over the moderator test from mispronunciation sensitivity, even though I was calling for the age moderator analysis.
+There is no significant moderator test, but it was just pasting the same one again and again.
+I've fixed my code, so it should be correct now!
 
@@
 ```{r VocabularyData, echo = FALSE}
-vocab_info <- db_ET_correct %>%
+vocab_info <- dat %>%
   mutate(has_vocab = ifelse(!is.na(r_comprehension), "comprehension", 
@@
 
-vocab_info2 <- db_ET_correct %>%
+vocab_info2 <- dat %>%
   mutate(has_vocab = ifelse(!is.na(r_comprehension) | !is.na(r_production), "vocab", 
@@
 
-Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` analyzed the relationship between vocabulary scores and object recognition for correct pronunciations and mispronunciations (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers; production = `r with(vi1, papers[has_vocab == "production"])`).
-There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we analyze this data separately.
+Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` analyzed the relationship between vocabulary scores and object recognition for correct pronunciations and mispronunciations (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers and `r with(vi1, count[has_vocab == "comprehension"])` records; production = `r with(vi1, papers[has_vocab == "production"])` papers and `r with(vi1, count[has_vocab == "production"])` records).
+There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment; Kidd citation), and we therefore planned to analyze these two types of vocabulary measurement separately.
+However, only `r with(vi1, papers[has_vocab == "production"])` papers reported correlations with productive vocabulary scores, limiting the conclusions that can be drawn.
+In our vocabulary analysis, we therefore focus exclusively on the relationship between comprehension and mispronunciation sensitivity.
 
@@
 Also, cann you add a citation for comp vs prod? I think Evan Kidd had a paper on it, if you don't have one handy, I can look it up.
+[Katie] I couldn't find what you are referring to.
+Could you add the Evan Kidd paper?
+Also, I added a histogram figure below, but I'm not so very sure that it is good enough to add to the paper (its under the heading "Potential Vocabulary Figure").
+Let me know what you think.
 
 ```{r ComprehensionMeta_correct}
+
+# coweeta.uga.edu/publications/10436.pdf, page 80 as a model for writing up these results
+
 #we're relying on the library meta function metacor
@@
 
+# number of positive correlations
+#CC$TE
+rel <- ifelse(CC$TE > 0, "pos", "neg")
+pos_rel <- sum(rel == "pos")
+neg_rel <- sum(rel == "neg")
+tot_rel <- pos_rel + neg_rel
+
+min_cor <- min(CC$TE)
+max_cor <- max(CC$TE)
+
 ```
@@
 #we're relying on the library meta function metacor
-prodr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_production) & r_production < 1)
-
-CP <- metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
-
-```
-
-[Katie: below, I'm using coweeta.uga.edu/publications/10436.pdf, page 80 as a model for writing up these results. I haven't the funniest clue what I'm doing! :p]
-[Christina] looks good to me.
-
-We first considered the relationship between vocabulary and object recognition for correct pronunciations.
-Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for 9 of 12 experimental conditions, with correlation values ranging from -0.17 to 0.48.
-The mean effect size XXX was small with 0.0897, which did not differ significantly from zero (CI [-0.0105; 0.1900] *p* = .0795).
-However, the lower bound of the CI is close to zero, and one might hypothesize that with more power the small relationship might become significant.
-At the same time, a larger sample might confirm our conclusion that there is no relationship.
-
-Higher production scores were also associated with greater object recognition in response to correct pronunciations for 9 of 16 experimental conditions, with correlation values ranging from -0.23 to 0.44.
+#prodr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_production) & r_production < 1)
+
+#CP <- metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
+
+#Higher production scores were also associated with greater object recognition in response to correct pronunciations for 9 of 16 experimental conditions, with correlation values ranging from -0.23 to 0.44.
 The mean effect size XXX was again small and not significantly different from zero with 0.0601 (CI [-0.0331; 0.1533] *p* = .2061).
@@
 
-[Christina] I think bc the effect is small but apparently consistent, we can reason that we might have a power problem and thus cannot draw firm conclusions.
+```
+
+We first considered the relationship between vocabulary and object recognition for correct pronunciations.
+Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for `r pos_rel` of `r tot_rel` experimental conditions, with correlation values ranging from `r min_cor` to `r max_cor`.
+The mean effect size Pearson's *r* of `r r2(CC$TE.fixed)` was small and did not differ significantly from zero (CI [`r r2(CC$lower.fixed)`; `r r2(CC$upper.fixed)`] *p* `r psig(CC$pval.fixed)`).
+However, the lower bound of the CI is close to zero, and one might hypothesize that with more power the small relationship might become significant.
+At the same time, a larger sample might confirm our conclusion that there is no relationship.
+As a result, we can not draw firm conclusions about the relationship between comprehension scores and object recognition in response to correct pronunciations.
 
@@
 MC <- metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
+
+# number of positive correlations
+#CC$TE
+rel <- ifelse(MC$TE > 0, "pos", "neg")
+pos_rel <- sum(rel == "pos")
+neg_rel <- sum(rel == "neg")
+tot_rel <- pos_rel + neg_rel
+
+min_cor <- min(MC$TE)
+max_cor <- max(MC$TE)
+
 ```
@@
 #we're relying on the library meta function metacor
-prodr  <- subset(db_ET_MP, !is.na(db_ET_MP$r_production) & r_production < 1)
-
-MP <- metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
+# prodr  <- subset(db_ET_MP, !is.na(db_ET_MP$r_production) & r_production < 1)
+# 
+# MP <- metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
+
+#For production, however, lower production scores were associated with greater object recognition in response to mispronunciations for 16 of 31 experimental conditions, with correlation values ranging from -0.28 to 0.44.
+The mean effect size XXX was -0.0402, (CI [-0.1043; 0.0238] *p* = .2181).
+
 ```
@@
 We next considered the relationship between vocabulary and object recognition for mispronunciations.
-Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for 17 of 31 experimental conditions, with correlation values ranging from -0.35 to 0.57.
-The mean effect size XXX was 0.0377, but did not differ significantly from zero (CI[-0.0260; 0.1014] *p* = .2465).
-For production, however, lower production scores were associated with greater object recognition in response to mispronunciations for 16 of 31 experimental conditions, with correlation values ranging from -0.28 to 0.44.
-The mean effect size XXX was -0.0402, (CI [-0.1043; 0.0238] *p* = .2181).
-For both comprehension and production scores, the small correlations and large variances suggest a lack of relationship between vocabulary and object recognition for mispronunciations.
+Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for `r pos_rel` of `r tot_rel` experimental conditions, with correlation values ranging from `r min_cor` to `r max_cor`.
+The mean effect size Pearson's *r* of `r r2(MC$TE.fixed)` was small and did not differ significantly from zero (CI [`r r2(MC$lower.fixed)`; `r r2(MC$upper.fixed)`] *p* `r psig(MC$pval.fixed)`).
+Similar to the relationship between comprehension scores and correct pronunciation object identification, the small correlations and large variances suggest a lack of relationship between vocabulary and object recognition for mispronunciations.
 We again emphasize that we cannot draw firm conclusions due to the small number of studies we were able to include here.
 
-[Christina] Is there a reason the above numbers aren't read out as before?
-Also, I think the effect size is pearson's r, because that's what we put in, right?
+## Potential Vocabulary Figure
+
+```{r Vocab_describe1}
+#how did vocabulary collection change over time?
+
+dv <- read.csv("data/vocab_collection.csv", header = T)
+
+years.v <- as.data.frame(seq(from = 2000, to = 2018, by = 1))
+relat.v <- c("no_vocab", "no_relationship", "positive")
+
+fake.v <- merge(years.v, relat.v, all = T)
+names(fake.v) <- c("year", "relationship")
+dat.v <- merge(dv, fake.v, by = c("year", "relationship"), all.y = T)
+dat.v$vocab <- as.character(dat.v$vocab)
+dat.v$relationship <- as.character(dat.v$relationship)
+dat.v$short_cite <- as.character(dat.v$short_cite)
+
+dat.v$vocab[is.na(dat.v$vocab)] <- "none"
+dat.v$short_cite <- ifelse(dat.v$vocab == "none", "none", dat.v$short_cite)
+
+dat.v$short_cite[is.na(dat.v$short_cite)] <- "none"
+
+dat.v$tested <- ifelse(dat.v$short_cite == "none", "no", "yes")
+
+dat.v$relationship <- ifelse(dat.v$relationship == "no_vocab", "None",
+                                   ifelse(dat.v$relationship == "positive", "Predictive",
+                                          "No Relationship"))
+dat.v$relationship <- factor(dat.v$relationship, levels = c("Predictive", "No Relationship", "None"))
+
+d.v <- subset(dat.v, short_cite != "none")
+
+d.v$Year <- d.v$year
+
+vocab_year <- ggplot(d.v,aes(x=Year, fill = relationship)) + 
+  apatheme+
+  geom_histogram(alpha = 0.5, bins = 20) +
+    scale_fill_manual(values=cbPalette)+
+     theme(legend.position = "bottom",
+           legend.title = element_blank())
+
+vocab_year
+
+  jpeg(filename = "figures/Vocab_findings.jpg", 
+       width = 500, height = 300, units = "px")
+
+vocab_year
+
+  dev.off()
+
+#   
+# 
+# vocab_data1 <- dat.v %>%
+#   group_by(year, relationship, tested) %>%
+#   summarize(count = n())
+# 
+# vocab_data1 <- as.data.frame(vocab_data1)
+# vocab_data1$count <- ifelse(vocab_data1$tested == "no", 0, vocab_data1$count)
+# vocab_data1$year <- as.numeric(vocab_data1$year)
+# 
+# vocab_data1$relationship <- ifelse(vocab_data1$relationship == "no_vocab", "None",
+#                                    ifelse(vocab_data1$relationship == "positive", "Predicts",
+#                                           "No Relationship"))
+# vocab_data1$relationship <- factor(vocab_data1$relationship, levels = c("Predicts", "No Relationship", "None"))
+# 
+# 
+# p <- ggplot(vocab_data1, aes(year, count, color = relationship)) + 
+#   geom_line() + 
+#   geom_point()+
+#   scale_y_continuous(breaks = c(0, 1, 2, 3, 4), limits = c(0,4))+
+#   scale_colour_manual(values=cbPalette)+
+#   apatheme +
+#   theme(legend.title = element_blank(),
+#         legend.position = "bottom")
+# p
+# 
+#   jpeg(filename = "figures/Vocab_findings.jpg", 
+#        width = 500, height = 300, units = "px")
+# 
+#   p
+#   
+#   dev.off()
+#  
+```
 
@@
 This runs counter to existing theories of phono-lexical development, which predict either an increase (PRIMR ref) or decrease (Assim Model ref) in mispronunciation sensitivity.
-Furthermore, counter to the predictions for the PRIMR (PRIMR ref) and Assimilation(Assim ref) models, we found no relationship between vocabulary and target looking for correct pronunciations or mispronunciations.
+Furthermore, counter to the predictions for the PRIMR (PRIMR ref) and Assimilation(Assim ref) models, we found no relationship between vocabulary and target looking for correct pronunciations or mispronunciations, although our analyses may be underpowered.
 In sum, it seems that current theories of infants' phono-lexical development cannot fully capture our results and should be reconsidered with all the evidence in mind.
@@
 A strong candidate that emerged during the construction of the present dataset and careful reading of the original papers is the analysis approach.
-We observed, as mentioned in the Methods section, large variance in the dependent variable reported, and additionally noted variance in the time window chosen for analyses.
+We observed, as mentioned in the Methods section, large variance in the dependent variable reported, and additionally noted variance in the size of the time window chosen for analyses.
 Researchers might adapt their analysis strategy to age or they might be influenced by having observed the data.
@@
 
-We included size of time window analyzed or dependent variable calculated in our coding of the dataset because they are consistently reported and might be useful for experiment design in the future by highlighting typical choices and helping establish field standards.
+We included details related to timing and type of dependent variable calculated in our coding of the dataset because they are consistently reported and might be useful for experiment design in the future by highlighting typical choices and helping establish field standards.
 In the following section, we include an exploratory analysis to investigate the possibility of systematic differences in the approach to analysis in general and across infant age.
-Our analyses will show that a standard, a priori registered analysis of looking while listening paradigms is needed and can improve the health of a currently biased literature.
-
-[Christina] The last sentence is a bit clunky, please improve.
+The purpose of this analysis is to better understand the influence of choices made in analyzing mispronunciation sensitivity studies as well as the influence these choices may have on our understanding of mispronunciation sensitivity development.
 
@@
 I am not 100% sure about total trial length as being the first or being mentioned at all, might it be better to focus on time window analyzed and then say "Oh, btw, total trial length totally does nothing so we don't have to discuss it further" I am not sure, so feel free to re-rewrite this, but now it better lines up with everything before because trial length kinda comes out of nowhere.
-
-We identified two sets of variables which varied across papers to assess the influence of data analysis choices on resulting effect size: the time course of a trial and time window analyzed and which dependent variable(s) were reported.
+[Katie] That's fair!
+I think we don't need the full analysis for total time presented, but I'd like to still mention all of them because it really shows that its something about this post-naming time window choice that influences it, and not just fishing around for variability until we find something that works.
+In the end there are 2 interesting analyses, but offset could have been interesting (but wasn't).
+Therefore, I'd still like to refer to the timing variables as a type of category.
+Otherwise, we say we'll do size of time window analyzed, but then we have information about other timing stuff as well.
+
+We identified two sets of variables which had the potential to vary across papers to assess the influence of data analysis choices on resulting effect size: timing (size of time window analyzed; offset time) and which dependent variable(s) were reported.
 In the following, we discuss the possible theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these analysis choices have on mispronunciation sensitivity development.
-
-### Time-related analyses
+We focus specifically on the size of the mispronunciation sensitivity effect, considering the whole dataset and including condition (correct pronunciation, mispronunciation) as moderator.
+
+### Timing
 
@@
 
+# can't call reshape earlier, because it will interfere with other libraries
+library(reshape)
+
 # trial length
-
-trial_length_info <- dat %>%
-  group_by(trial_length) %>%
+dat$post_nam_actual <- dat$trial_length - dat$pre_nam_dur
+
+post_length_info <- dat %>%
+  group_by(post_nam_actual) %>%
   summarize(n_exp_conditions =  n())
@@
 
-trial.l <- cor.test(dat$trial_length, dat$mean_age_1)
-
-library(reshape)
-tdl <- dat[,c("short_cite", "trial_length", "post_nam_dur")]
+trial.l <- cor.test(dat$post_nam_actual, dat$mean_age_1)
+
+tdl <- dat[,c("short_cite", "post_nam_actual", "post_nam_dur")]
 tdl <- melt(tdl, id = "short_cite")
@@
   apatheme+
-    geom_histogram(data=subset(tdl,variable == 'trial_length'),fill = "red", alpha = 0.5) +
+    geom_histogram(data=subset(tdl,variable == 'post_nam_actual'),fill = "red", alpha = 0.5) +
     geom_histogram(data=subset(tdl,variable == 'post_nam_dur'),fill = "blue", alpha = 0.5)
@@
 # difference post vs. trial length
-dat$post_trial_match <- ifelse(dat$post_nam_dur == (dat$trial_length-dat$pre_nam_dur), "same", "different")
+dat$post_trial_match <- ifelse(dat$post_nam_dur == dat$post_nam_actual, "same", "different")
 dat$post_trial_prop <- dat$post_nam_dur/(dat$trial_length-dat$pre_nam_dur)
@@
 
-```
-
-[Christina] Ideally load all libraries in the beginning of the doc. (reshape)
+detach("package:reshape", unload=TRUE)
+
+```
 
 [Christina] Is there a reason you choose mode and not median? 
+[Katie] Hmm, I felt like mode would be interesting, because it gives the most popular choice (74 experimental conditions).
+But, the median is only 500 ms less, so we could use that too (9 experimental conditions).
 
 [Christina] Would it make sense to present dependent variable first? 
-
-[Christina] So if you go with my suggestion from above, I would just add this sentence at the beginning of the next paragraph: "Before we focus on analysis choice relating to time windows, we must first discuss overall trial length, because it limits the overall time window available to analyze and might thus predict which time window was analyzed."
-
+[Katie] I don't have a strong opinion on this. If you think it would be better, then I can change it.
+
+In a typical trial in a mispronunciation sensitivity study, the target-distractor image pairs are first presented in silence, followed by auditory presentation of a carrier phrase or isolated presentation of the target word (correctly pronounced or mispronounced).
 When designing mispronunciation sensitivity studies, experimenters can choose the length of time each trial is presented.
 This includes both the length of time before the target object is named (pre-naming phase) as well as after (post-naming phase) and is determined prior to data collection.
-Across papers, trial length varied from `r with(trial_length_info, min(trial_length))*1000` to `r with(trial_length_info, max(trial_length))*1000` ms, with a mode of `r with(dat, getmode(trial_length))*1000` ms.
-There was an inverse relationship between infant age and trial length, such that younger infants were presented with longer trials, although this correlation was not significant (*r* = `r trial.l$estimate`, *p* `r psig(trial.l$p.value)`).
-Presumably, younger infants may be exposed to longer trials because their word recognition abilities may be slower than older infants (Fernald et al., 1998).
-
-Unlike the length of trial, the length of the post-naming phase analyzed can be chosen after the experimental data is collected.
+To examine the size of the time window analyzed in the post-naming phase, we must first consider overall length of time post-naming, because it limits the overall time window available to analyze and might thus predict which time window was analyzed.
+Across papers, actual post-naming phase length varied from `r with(post_length_info, min(post_nam_actual))*1000` to `r with(post_length_info, max(post_nam_actual))*1000` ms, with a median value of `r with(dat, median(post_nam_actual))*1000` ms.
+There was an inverse relationship between infant age and actual post-naming phase length, such that younger infants were presented with longer a longer post-naming phase, although this correlation was not significant (*r* = `r trial.l$estimate`, *p* `r psig(trial.l$p.value)`).
+Presumably, younger infants may be exposed to longer trials because their word recognition abilities are expected to be slower than older infants (Fernald et al., 1998).
+
+Unlike the actual post-naming phase length, the size of the post-naming time window analyzed can be chosen after the experimental data is collected.
 Interestingly, half of the experimental conditions were analyzed using the same length of post-naming phase as the infant heard in the actual experiment (`r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`), while the other half were analyzed using a shorter length of post-naming phase, excluding later portions of the post-naming phase (`r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`).
-Across papers, the length of the post-naming phase analyzed varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a mode of `r with(dat, getmode(post_nam_dur))*1000` ms.
-Similar to trial length, there was an inverse relationship between infant age and length of post-naming phase analyzed, such that younger infants'looking times were analyzed using a longer post-naming phase, here the relationship was significant (*r* = `r post.l$estimate`, *p* `r psig(post.l$p.value)`).
+Across papers, the length of the post-naming phase analyzed varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a median value of `r with(dat, median(post_nam_dur))*1000` ms.
+Similar to actual post-naming phase length, there was an inverse relationship between infant age and the size of the post-naming time window analyzed, such that younger infants' looking times were analyzed using a longer post-naming time window, here the relationship was significant (*r* = `r post.l$estimate`, *p* `r psig(post.l$p.value)`).
 Again, the choice to analyze a shorter post-naming time window is likely related to evidence that speed of processing is slower in younger infants (Fernald et al., 1998).
-
-[Christina] I think the proportion needs more explanation, also because later we have proportions of looks to target.
-
-Furthermore, the proportion of post-naming phase time window analyzed in comparison to the total post-naming phase presented to infants significantly decreased with increasing infant age (*r* = `r post_match.l$estimate`, *p* `r psig(post_match.l$p.value)`).
 To summarize, we observe variation in time-related aspects related to infants' age.
@@
 And then add to the next sentence that the longer latnecies are because ther eis addiitonal language processing required which EEg shows in adults to take X ms (400 for N400?).
+[Katie] I agree with the reasoning, but I don't think referring to adult ERP literature is the way to go. I've rewritten these sentences to be more faithful to the misp sensitivity literature.
 
 [Christina] Can you add info how many papers did not report the analyzed variables? Across this whole section, I mean. 
-
-When analyzing eye-movements, it is important to consider the amount of time it takes for an eye movement to be initiated in response to a stimulus.
+[Katie] All papers reported the actual post-naming phase length and the size of the post-naming time window analyzed.
+
+Another potential source of variation in studies that analyze eye-movements is the amount of time it takes for an eye movement to be initiated in response to a visual stimulus, which we refer to as offset time.
 Previous studies examining simple stimulus response latencies first determined that infants require at least 233 ms to initiate an eye-movement in response to a stimulus (Canfield & Haith, 1991).
-In mispronunciation sensitivity studies, however, this has often been extended to 367 ms (e.g.
-Swingley & Aslin, 2000, 2002, 2007).
-Across papers, the majority used a similar offset value (between 360 and 370 ms) for analysis (*n* = `r with(offset_bin_info, n_exp_conditions[offset_bin == "367"])`), but offset values ranged from `r with(offset_bin_info, min(offset_bin))` to `r with(offset_bin_info, max(offset_bin))` ms, and were not reported for `r with(offset_info, n_exp_conditions[is.na(offset)])` experimental conditions.
+In the first infant mispronunciation sensitivity study, Swingley and Aslin (2000) used an offset time of 367 ms, which was "an 'educated guess' based on studies...
+showing that target and distractor fixations tend to diverge at around 400 ms." (Swingley & Aslin, 2000, p.
+155).
+Upon inspecting the offset time values used in the papers in our meta-analysis, the majority used a similar offset time value (between 360 and 370 ms) for analysis (*n* = `r with(offset_bin_info, n_exp_conditions[offset_bin == "367"])`), but offset values ranged from `r with(offset_bin_info, min(offset_bin))` to `r with(offset_bin_info, max(offset_bin))` ms, and were not reported for `r with(offset_info, n_exp_conditions[is.na(offset)])` experimental conditions.
 We note that Swingley (2009) also included offset values of 1133 ms to analyze responses to coda mispronunciations.
@@
 (2013).
-The garden of forking paths: Why multiple comparisons can be a problem, even when there is no “fishing expedition” or “p-hacking” and the research hypothesis was posited ahead of time.
-Department of Statistics, Columbia University.).
-Considering that these choices were systematically different across infant ages, at least for the post-naming time window, we next explored whether the size of the analyzed post-naming time window or the offset time influenced sensitivity to mispronunciations.
-
-### Length of post naming time window
+Considering that these choices were systematically different across infant ages, at least for the post-naming time window, we next explored whether the size of time window analyzed or the offset time influenced sensitivity to mispronunciations.
+
+#### Size of post-naming time window analyzed
 
@@
 
-    rma_post_dur_AGE_MS_eff <- coef(summary(rma_post_dur_MS))[8,]
+    rma_post_dur_AGE_MS_eff <- coef(summary(rma_post_dur_AGE_MS))[8,]
+
+# First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images, including post-naming time window size as a moderator.
+The moderator test was not significant `r mod_test(rma_post_dur)` and the estimate for post-naming phase size was relatively small, $\beta$`r full_estimate(rma_post_dur_eff)`.
+
+#[Christina] Even if a test is not significant, this next sentence is always wrong because we did not test whether it's the same (i.e. we did not do an equivalence or Bayesian test!)
+#This suggests that upon hearing a mispronunciation, infants' looks to the target image did not differ as a result of the size of the post-naming time window analyzed.
+We next assessed whether post-naming phase size was related to mispronunciation sensitivity.
+
+#[Christina] To be sure, you base this again on the combined data and only plot differences for easier visualizations in figure 3?
+Ideally make that clear.
+Also, some suggestions to vary this sentence (also earlier in the paper)
+#"To investigate mispronunciation sensitivity, we considered data from both conditions in a joint analysis"
+#"Analyzing all data with condition (c, mp) as additional moderator leads to the following results"
+#etcetc
+
+# For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant `r mod_test(rma_post_dur_AGE)`, and a small estimate for the interaction between age and size of post-naming phase ($\beta$`r full_estimate(rma_post_dur_AGE_eff)`.
+This suggests that upon hearing a mispronunciation, infant measured looks to the target image were similar, regardless of infant age or size of the post-naming phase analyzed.
+We next assessed whether the relationship between size of the post-naming phase analyzed and mispronunciation sensitivity was modulated by age.
 
@@
 Your call though.
-
-We first assessed whether size of post-naming phase analyzed had an impact on the size of the reported mispronunciation sensitivity.
-First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images, including post-naming window size as a moderator.
-
-[Christina] the next bit is weird, in the pdf it's significant, but you write it's not. Also, I think the beta is quite large anbd the CI reasonably distinct from 0.
-
-The moderator test was not significant `r mod_test(rma_post_dur)` and the estimate for post-naming phase size was relatively small, $\beta$`r full_estimate(rma_post_dur_eff)`.
-
-[Christina] Even if a test is not significant, this next sentence is always wrong because we did not test whether it's the same (i.e. we did not do an equivalence or Bayesian test!)
-This suggests that upon hearing a mispronunciation, infants' looks to the target image were similar regardless of the size of the post-naming phase analyzed.
-We next assessed whether post-naming phase size was related to mispronunciation sensitivity.
-
-[Christina] To be sure, you base this again on the combined data and only plot differences for easier visualizations in figure 3?
-Ideally make that clear.
-Also, some suggestions to vary this sentence (also earlier in the paper)
-"To investigate mispronunciation sensitivity, we considered data from both conditions in a joint analysis"
-"Analyzing all data with condition (c, mp) as additional moderator leads to the following results"
-etcetc
-
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
+[Katie] I agree and I've updated it to refer to window size when talking about the analyzed portion and to  phase when refering to it as the entire actual presentation time.
+
+We first assessed whether size of the post-naming time window analyzed had an impact on the overall size of the reported mispronunciation sensitivity.
+We considered data from both conditions in a joint analysis and included condition (correct pronunciation, mispronunciation) as an additional moderator.
 The moderator test was significant, `r mod_test(rma_post_dur_MS)`.
@@
 This relationship is plotted in Figure 3a.
-The results suggest that although the size of the post-naming phase analyzed did not impact infants' likelihood to fixate the target upon hearing the mispronunciation, it did significantly impact mispronunciation sensitivity.
+The results suggest that the size of the post-naming phase analyzed significantly impacted mispronunciation sensitivity.
 Specifically, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) was significantly greater when the post-naming phase that was shorter in length.
 
-Considering that we also found a relationship between the length of the post-naming phase analyzed and infant age, such that younger ages had a longer post-naming phase time window of analysis, we next examined whether the size of post-naming phase analyzed modulated the development of mispronunciation sensitivity.
-For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant `r mod_test(rma_post_dur_AGE)`, and a small estimate for the interaction between age and size of post-naming phase ($\beta$`r full_estimate(rma_post_dur_AGE_eff)`.
-This suggests that upon hearing a mispronunciation, infant measured looks to the target image were similar, regardless of infant age or size of the post-naming phase analyzed.
-We next assessed whether the relationship between size of the post-naming phase analyzed and mispronunciation sensitivity was modulated by age.
+Considering that we also found a relationship between the length of the post-naming time window analyzed and infant age, such that younger ages had a longer window of analysis, we next examined whether the size of post-naming time window analyzed modulated the development of mispronunciation sensitivity.
 We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
 The moderator test was significant `r mod_test(rma_post_dur_AGE_MS)`.
-
-[Christina] lots of NAs here in the pdf
-
 The estimate for the  three-way-interaction between condition, size of post-naming phase, and age was small, but significant ($\beta$ = `r full_estimate(rma_post_dur_AGE_MS_eff)`.
-This relationship is plotted in Figure 3b.
-Smaller post-naming phase size lead to greater increases in mispronunciation sensitivity with development.
-
-[Christina] The next sentence as weird, check whether my corrections make sense
-
-For example, when experimental conditions were analyzed with a post-naming phase of 2000 ms or less, mispronunciation sensitivity increases with infant age, whereas there is no or a negative relation of mispronunciation sensitivity and age if the analyzed post-naming phase is greater than 2000 ms leads.
-In other words, all three possible hypotheses might be supported depending on analysis choices made.
-
-[Christina] I think it's important to remind the reader here that this is our key question, namely how age and mp sensitivity are related.
+As can be seen in Figure 3b, smaller post-naming time window size leads to greater increases in mispronunciation sensitivity with development.
+For example, when experimental conditions were analyzed with a post-naming time window of 2000 ms or less, mispronunciation sensitivity is found to increase with infant age.
+If the post-naming time window analyzed is greater than 2000 ms, however, there is no or a negative relation of mispronunciation sensitivity and age.
+In other words, all three possible hypotheses might be supported depending on analysis choices made regarding the size of the post-naming time window to analyze.
+This is especially important, considering that our key question is how mispronunciation sensitivity changes with development.
+These results suggest that conclusions about the relationship between infant age and mispronunciation sensitivity may be mediated by the size of the post-naming time window analyzed.
 
@@
   geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
-  labs(caption="a")+
+  labs(title="a")+
   #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
@@
   geom_point(aes(size = n_1),show.legend=FALSE) +
-  labs(caption="b")+
+  labs(title="b")+
   geom_line(y= 0, linetype="dotted") + 
@@
 
-### Offset after target naming
+#### Offset time after target naming
 
@@
 ```
-
-We next assessed whether the time between the target was named and the start of the analysis, namely offset time, had an impact on the size of the reported mispronunciation sensitivity.
-First, we calculated the meta-analytic effect size for object identification in response to mispronounced target words/images, including offset time as a moderator.
-
-[Christina] again, the pdf tells me sth different
-
-The moderator test was not significant `r mod_test(rma_offset)` and the estimate for offset time was very small, $\beta$`r full_estimate(rma_offset_eff)`.
-
-[Christina] Again, we didn't test, so say sth like "did not differ significantly."
-
-This suggests that upon hearing a mispronunciation, infants' looks to the target image were similar regardless of the offset time used to analyze the data.
-We next assessed whether offset time was related to mispronunciation sensitivity.
-
-[Christina] Again, rewording suggestion: "When investigating mispronunciation sensitivity by including condition, the moderator test with was ...
-
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, `r mod_test(rma_post_dur_MS)`, but the estimate for the interaction between offset time and condition was almost zero $\beta$`r full_estimate(rma_offset_MS_eff)`.
 
@@
 consider the whole dataset and always include condition as moderator.
-
-We next examined whether offset time modulated the development of mispronunciation sensitivity.
-For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant `r mod_test(rma_offset_AGE)`, and a very small estimate for the interaction between age and size of post-naming phase ($\beta$`r full_estimate(rma_offset_AGE_eff)`.
-This suggests that upon hearing a mispronunciation, infant measured looks to the target image were similar, regardless of infant age or offset time.
-We next assessed whether the relationship between offset time and mispronunciation sensitivity was modulated by age.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant `r mod_test(rma_offset_AGE_MS)`, but the three-way-interaction between condition, offset time, and age was very small and not significant ($\beta$ = `r full_estimate(rma_offset_AGE_MS_eff)`.
-
+[Katie] Agreed! I've gotten rid of all of the object recognition analyses and added an explanation at the beginning of the Exploratory Analysis section.
+
+We next assessed whether the time between the target was named and the start of the analysis, namely offset time, had an impact on the size of the reported mispronunciation sensitivity.
+When we included both condition and offset time as moderators, the moderator test was significant, `r mod_test(rma_post_dur_MS)`, but the estimate for the interaction between offset time and condition was almost zero $\beta$`r full_estimate(rma_offset_MS_eff)`.
+Although we found no relationship between offset time and infant age, we also examined whether the size of offset time modulated the development of mispronunciation sensitivity.
+When both offset time and condition were included as moderators, the moderator test was significant `r mod_test(rma_offset_AGE_MS)`, but the three-way-interaction between condition, offset time, and age was very small and not significant ($\beta$ = `r full_estimate(rma_offset_AGE_MS_eff)`.
 Taken together, these results suggest that offset time does not modulate mispronunciation sensitivity.
@@
 Pre vs post is a bit differnt because it loses the individual bias accommodation and the correlation between pre and post on the participant / item level.
+[Katie] You did. I'll put here my answer from before:
+From working with Nivi, we did it participants x condition or participants x trial (but mostly the former).
+But, this is not something we reported in papers.
+I don't think I read it at all when putting together the dataset for this either.
 
@@
 The Post dependent variable, in contrast, does not consider pre-naming preferences.
-
-[Christina] Actually, in other domains (eeg, longitudinal studies, RCTs) people tlak a lot about whether or not to consider a baseline, so this is not strictly true.
-
-To our knowledge, there is no theory or evidence to drive choice of dependent variable, which may explain the wide variation in dependent variable reported in the papers included in this meta-analysis.
+To our knowledge, there is no theory or evidence that explicitly drives choice of dependent variable in analysis of mispronunciation sensitivity, which may explain the wide variation in dependent variable reported in the papers included in this meta-analysis.
 We next explored whether the type of dependent variable calculated influenced sensitivity to mispronunciations.
@@
 We first assessed whether the choice of dependent variable had an impact on the size of mispronunciation sensitivity.
-First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images, including dependent variable as a moderator.
-The moderator test was significant `r mod_test(rma_within)`.
-The estimates for both the Pre vs.
-Post ($\beta$`r full_estimate(rma_within_effprepost)`) and Difference Score ($\beta$`r full_estimate(rma_within_effdiff)`) dependent variables were significantly smaller than that of the Post dependent variable.
-This suggests that reported looks to the target upon hearing a mispronunciation were greatest when the dependent variable was Post.
-We next assessed whether he dependent variable was related to mispronunciation sensitivity.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, `r mod_test(rma_within_MS)`.
+When we included both condition and dependent variable as moderators, the moderator test was significant `r mod_test(rma_within_MS)`.
 The estimate for the interaction between Pre vs.
@@
 We next examined whether the type of dependent variable calculated modulated the development of mispronunciation sensitivity.
-For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was significant `r mod_test(rma_post_dur_AGE)`, but the estimates for the interaction between Pre vs.
-Post and age ($\beta$`r full_estimate(rma_within_AGE_effprepost)`) as well as Difference Score and age ($\beta$`r full_estimate(rma_within_AGE_effdiff)`) were not different from that of the Post dependent variable.
-This suggests that upon hearing a mispronunciation, infant measured looks to the target image were similar, regardless of infant age or type of dependent variable.
-We next assessed whether the relationship between dependent variable and mispronunciation sensitivity was modulated by age.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant `r mod_test(rma_within_AGE_MS)`.
+When age was included as an additional moderator, the moderator test was significant `r mod_test(rma_within_AGE_MS)`.
 The estimate for the interaction between Pre vs.
@@
 There was no difference in mispronunciation sensitivity change with infant development between the Post and Difference Score dependent variables.
+Similar to size of post-naming time window analyzed, all three possible developmental hypotheses might be supported depending on the dependent variable reported.
+In other words, choice of dependent variable may influence the conclusion drawn regarding how mispronunciation sensitivity may change with infant age.
 
@@
 
-  + Post-naming phase size and dependent variable impact misp sensitivity development
+  + Post-naming time window size and dependent variable impact misp sensitivity development
   + Offset time does not impact misp sensitivity development

### 2018-11-24 Paper_Analyses.tex
small updates to manuscript, towards a final exploratory analysis

@@
 
-%%% Change title format to be more compact
-\usepackage{titling}
-
-% Create subtitle command for use in maketitle
-\newcommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
-}
-
-\setlength{\droptitle}{-2em}
   \title{The development of infants' responses to mispronunciations - A
 Meta-Analysis}
-  \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
     \author{Katie Von Holzen\textsuperscript{1,2}~\& Christina
 Bergmann\textsuperscript{3,4}}
-  \preauthor{\centering\large\emph}
-  \postauthor{\par}
     \date{}
-  \predate{}\postdate{}
 
@@
 \vspace{0.5cm}
-\textsuperscript{1} Language Development Laboratory, University of Maryland, USA\\\textsuperscript{2} Laboratoire Psychologie de la Perception, Université Paris Descartes\\\textsuperscript{3} Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands\\\textsuperscript{4} LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University}
+\textsuperscript{1} Department of Hearing and Speech Sciences, University of Maryland, USA\\\textsuperscript{2} Laboratoire Psychologie de la Perception, Université Paris Descartes\\\textsuperscript{3} Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands\\\textsuperscript{4} LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University}
 \keywords{keywords\newline\indent Word count: X}
@@
 while simultaneously refining their knowledge about the sounds that make
-up these words. Before children can correctly pronounce a word, they
-already show evidence of sensitivity to slight variations in the
-phonological form of that word. This mispronunciation sensitivity
-reflects the specificity with which infants represent the phonological
-information of familiar words and are sensitive to changes that might
-signal a change in word meaning. As infants continue to develop into
-expert language users, their language processing matures and becomes
-more efficient. In a mature phono-lexical system, word recognition must
-balance flexibility to slight variation (e.g., speaker identity,
-accented speech) while distinguishing between phonetic details that
-differentiate words in their native language (e.g.~cat-hat). In this
-paper, we aggregate and analyze the almost 20 years of literature
-investigating mispronunciation sensitivity in infants in an attempt to
-uncover its characteristics and the trajectory of its development.
+up these words {[}Primir, Kuhl, Best{]}. In a mature phono-lexical
+system, word recognition must balance flexibility to slight variation
+(e.g., speaker identity, accented speech) while distinguishing between
+phonetic details that differentiate words in their native language
+(e.g.~cat-hat). To build robust language knowledge, it seems ueful to
+acquire this ability early during development. Indeed, before children
+can correctly pronounce a word, they already are aware that slight
+phonological deviations might signal a change in word meaning {[}Clark
+\& Clark, 1977{]}. This mispronunciation sensitivity reflects the
+specificity with which infants represent the phonological information of
+familiar words. As infants continue to develop into expert language
+users, their language processing matures and becomes more efficient,
+including their knowledge of what consistutes a permissible versus
+word-changing phonological deviation. In this paper, we aggregate and
+analyze the almost 20 years of literature investigating mispronunciation
+sensitivity in infants in an attempt to uncover its characteristics and
+the trajectory of its development.
 
@@
 on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg,
-\& McRoberts, 1998). Swingley and Aslin (2000) were the first to tie
-these lines of research together and investigate mispronunciation
-sensitivity in infant familiar word recognition: Children aged 18 to 23
-months learning American English were presented with pairs of images
-(e.g.~baby, dog) and their eye movements to each image were coded
-offline. On \enquote{correct} trials, children heard the correct label
-for one of the images (e.g.~baby). On \enquote{mispronounced} trials,
-children heard a mispronounced label of one of the images (e.g.~vaby).
-Mean proportion of fixation to the target image (here: a baby) was
-calculated for both correct and mispronounced trials by dividing the
-target looking time by the sum of total looking time to both target and
-a distractor (proportion of target looking or PTL). Mean fixations in
-correct trials were significantly greater than in mispronounced trials,
-although looks to the target were significantly greater than chance in
-both types of trials. We refer to this pattern of a difference between
-looks to correct and mispronounced words as \emph{mispronunciation
-sensitivity} and of looks to the target image above chance as
-\emph{recognition}. Swingley and Aslin (2000) concluded that already
-before the second birthday, children represent words with sufficient
-detail to be sensitive to mispronunciations.
+\& McRoberts, 1998; Tincoff \& Jusczyk, 1999). Swingley and Aslin (2000)
+were the first to tie these lines of research together and investigate
+mispronunciation sensitivity in infant familiar word recognition:
+Children aged 18 to 23 months learning American English saw pairs of
+images (e.g.~a baby and a dog) and their eye movements to each image
+were recorded and subsequently coded offline. On \enquote{correct}
+trials, children heard the correct label for one of the images (e.g.
+\enquote{baby}). On \enquote{mispronounced} trials, children heard a
+mispronounced label of one of the images (e.g. \enquote{vaby}). The mean
+proportion of fixations to the target image (here: a baby) was
+calculated separately for both correct and mispronounced trials by
+dividing the target looking time by the sum of total looking time to
+both target and a distractor (proportion of target looking or PTL). Mean
+fixations in correct trials were significantly greater than in
+mispronounced trials, and in both conditions looks to the target were
+significantly greater than chance. We refer to this pattern of a
+difference between looks to correct and mispronounced words as
+\emph{mispronunciation sensitivity} and of looks to the target image
+above chance in each condition as \emph{object identification}. Swingley
+and Aslin (2000) concluded that already before the second birthday,
+children represent words with sufficient detail to be sensitive to
+mispronunciations.
+
+{[}Christina: changed concepts to mechanisms in the next paragraph,
+because I want to refer to what they represent, but I am not sure it's
+the right term{]}{[}Katie: Karen (Mulak) talks about these terms as
+concepts. Mechanisms to me means some sort of internalization, that they
+would have had this ability all along and just need to apply it. It
+could be that we fundamentally disagree on this, but to me these are
+things that infants discover. Later on we use principles. What about
+\enquote{principles that infants must discover}\ldots{} \enquote{in
+order to form adult-like word representations}? I took away
+\enquote{which are both present in the mature language processing
+system}.{]}
 
@@
 examining mispronunciation sensitivity address two complementary
-concepts in early phonological development: \emph{phonological
+principles that infants must discover in early phonological development
+in order to form adult-like word representations: \emph{phonological
 constancy} and \emph{phonological distinctiveness}. Phonological
-constancy is the ability to accept phonological variation across
+constancy is the ability to resolve phonological variation across
 different instances of a word, as long as the variation does not
@@
 similar, such as bad/bed or cat/hat. To successfully recognize words,
-infants must therefore simultaneously use both phonological constancy
-and distinctiveness to determine where phonological variation is
-appropriate and where it changes a word's meaning.
+speakers of a given language must therefore simultaneously use both
+phonological constancy and distinctiveness to determine where
+phonological variation is appropriate and where it changes a word's
+meaning. Both abilities have to be acquired, because language systems
+differ in which sounds signal a meaning change.
+
+{[}Katie: since we actually don't have theoretical framework support for
+the no-change theory, I've changed around the sentence below to
+explicitly say that only 2 of the 3 are predicted by theoretical
+accounts.{]}
 
@@
 possibilities how mispronunciation sensitivity might change as infants
-become native speakers, which are all respectively predicted by
-theoretical accounts and supported by single studies. By aggregating all
+become native speakers, which are all respectively supported by single
+studies and two predicted by theoretical accounts. By aggregating all
 publicly available evidence using meta-analysis, we can examine
 developmental trends making use of data from a much larger and diverse
-sample of infants. Before we outline the meta-analytical approach and
-its advantages in detail, we first discuss the proposals this study
-seeks to disentangle and the data supporting each of the accounts.
+sample of infants than is possible in most single studies (see Frank et
+al., 2018; for a notable exception). Before we outline the
+meta-analytical approach and its advantages in detail, we first discuss
+the proposals this study seeks to disentangle and the data supporting
+each of the accounts.
 
@@
 children continue to detect mispronunciations. Indeed, young infants are
-less likely than older infants to demonstrate recognition of familiar
-words (Best, Tyler, Gooding, Orlando, \& Quann, 2009; Mulak, Best, \&
-Tyler, 2013) or learn new words (Schmale, Hollich, \& Seidl, 2011) from
-accented speakers.
+more perturbed by accented speakers than older infants in their
+recognition of familiar words (Best, Tyler, Gooding, Orlando, \& Quann,
+2009; Mulak, Best, \& Tyler, 2013) or learning of new words (Schmale,
+Hollich, \& Seidl, 2011).
 
@@
 Research following the seminal study by Swingley and Aslin (2000) has
-extended mispronunciation sensitivity to infants as young as 12 months
-(Mani \& Plunkett, 2010), indicating that from early stages of the
+extended mispronunciation sensitivity to infants as young as 9 months
+(Bergelson \& Swingley, 2017), indicating that from early stages of the
 developing lexicon onwards, infants can and do detect mispronunciations.
@@
 correlated with target fixations for both correct and mispronounced
-labels, whereas the difference between the two (mispronunciation effect)
-did not. This suggests that as children develop, they are more likely to
-look at the target in the presence of a mispronounced label and that age
-is not related to mispronunciation sensitivity. A similar response
-pattern has been found for British English learning infants aged between
-18 and 24 months (Bailey \& Plunkett, 2002) as well as younger
-French-learning infants at 12 and 17 months (Zesiger, Lozeron, Levy, \&
-Frauenfelder, 2012). These studies award support to the prediction that
-mispronunciation sensitivity does not change with development.
+labels, whereas the difference between the two (mispronunciation
+sensitivity) did not. This suggests that as children develop, they are
+more likely to look at the target in the presence of a mispronounced
+label and that age is not related to mispronunciation sensitivity. A
+similar response pattern has been found for British English learning
+infants aged between 18 and 24 months (Bailey \& Plunkett, 2002) as well
+as younger French-learning infants at 12 and 17 months (Zesiger,
+Lozeron, Levy, \& Frauenfelder, 2012). These studies award support to
+the prediction that mispronunciation sensitivity does not change with
+development.
 
@@
 (2010: keps and tups). Here, 12-month-old infants were divided into a
-low vocabulary and high vocabulary group based group median vocabulary
-size. High vocabulary infants showed greater sensitivity to vowel
-mispronunciations than low vocabulary infants, although this was not the
-case for consonant mispronunciations. Taken together, although receiving
+low and high vocabulary group based on median vocabulary size. High
+vocabulary infants showed greater sensitivity to vowel mispronunciations
+than low vocabulary infants, although this was not the case for
+consonant mispronunciations. Taken together, although receiving
 considerable support from theories of phono-lexical processing in
@@
 
-Taken together, the studies we have reviewed begin to paint a picture of
-the development of mispronunciation sensitivity. Each study contributes
-one separate brushstroke and it is only by examining all of them
-together that we can achieve a better understanding. Meta-analyses can
-not only help us summarize the current state of research, but can also
-help us evaluate theories to drive future research and make hands-on
-recommendations for experiment planning.
+In sum, the studies we have reviewed begin to paint a picture of the
+development of mispronunciation sensitivity. Each study contributes one
+separate brushstroke and it is only by examining all of them together
+that we can achieve a better understanding of early language
+development. Meta-analyses can provide thus further insights by
+estimating the population effect, both of infants' responses to correct
+and mispronounced labels, and their mispronunciations sensitivity.
+Because we aggregate data over various age groups, this meta-analysis
+can also investigate the role of maturation by assessing the impact of
+age and vocabulary size. As a consequence, our results will be important
+in evaluating theories and drive future research. We also make hands-on
+recommendations for experiment planning, for example by providing an
+effect size estimate for a priori power analyses (Bergmann et al.,
+2018).
 
@@
 2018). Since the present paper was written with embedded analysis
-scripts in R {[}@R{]}, it is always possible to re-analyze an updated
-dataset. In addition, we follow the Preferred Reporting Items for
-Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the
-corresponding information available as supplementary materials (Moher,
-Liberati, Tetzlaff, Altman \& PRISMAGroup, 2009). Figure X plots our
-PRISMA flowchart.
+scripts in R {[}@R, @RMarkdown, @papaja{]}, it is always possible to
+re-analyze an updated dataset. In addition, we follow the Preferred
+Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA)
+guidelines and make the corresponding information available as
+supplementary materials (Moher, Liberati, Tetzlaff, Altman \&
+PRISMAGroup, 2009). Figure X plots our PRISMA flowchart illustrating the
+paper selection procedure.
 
@@
 
-\begin{tabular}{l|l|l|l}
-\hline
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:SummaryTable}Summary of all studies.}
+\begin{tabular}{llll}
+\toprule
 Paper & Publication format & Age & Vocabulary\\
-\hline
+\midrule
 Altvater-Mackensen (2010) & dissertation & 22, 25 & None\\
-\hline
 Altvater-Mackensen et al. (2014) & paper & 18, 25 & None\\
-\hline
-Bailey \& Plunkett (2002) & paper & 18, 24 & Comprehension\\
-\hline
+Bailey \& Plunkett (2002) & paper & 18, 24 & Comp\\
 Bergelson \& Swingley (2017) & paper & 7, 9, 12, 6 & None\\
-\hline
 Bernier \& White 2017 & proceedings & 21 & None\\
-\hline
 Delle Luche et al. (2015) & paper & 20, 19 & None\\
-\hline
 Durrant et al. (2014) & paper & 19, 20 & None\\
-\hline
 Hoehle et al. 2006 & paper & 18 & None\\
-\hline
-Hojen et al. & gray paper & 20 & Comprehension/Production\\
-\hline
-Mani \& Plunkett 2007 & paper & 15, 18, 24, 14, 21 & Comprehension/Production\\
-\hline
-Mani \& Plunkett 2010 & paper & 12 & Comprehension\\
-\hline
+Hojen et al. & gray paper & 20 & Comp/Prod\\
+Mani \& Plunkett 2007 & paper & 15, 18, 24, 14, 21 & Comp/Prod\\
+Mani \& Plunkett 2010 & paper & 12 & Comp\\
 Mani \& Plunkett 2011 & paper & 23, 17 & None\\
-\hline
-Mani, Coleman, \& Plunkett (2008) & paper & 18 & Comprehension/Production\\
-\hline
+Mani, Coleman, \& Plunkett (2008) & paper & 18 & Comp/Prod\\
 Ramon-Casas \& Bosch 2010 & paper & 24, 25 & None\\
-\hline
-Ramon-Casas et al. 2009 & paper & 21, 20 & Production\\
-\hline
+Ramon-Casas et al. 2009 & paper & 21, 20 & Prod\\
 Ren \& Morgan, in press & gray paper & 19 & None\\
-\hline
 Skoruppa et al. 2013 & paper & 24 & None\\
-\hline
-Swingley (2009) & paper & 17 & Comprehension/Production\\
-\hline
-Swingley (2016) & paper & 27, 28 & Production\\
-\hline
-Swingley \& Aslin (2000) & paper & 20 & Comprehension\\
-\hline
-Swingley \& Aslin (2002) & paper & 15 & Comprehension/Production\\
-\hline
-Swingley 2003 & paper & 19 & Comprehension/Production\\
-\hline
+Swingley (2009) & paper & 17 & Comp/Prod\\
+Swingley (2016) & paper & 27, 28 & Prod\\
+Swingley \& Aslin (2000) & paper & 20 & Comp\\
+Swingley \& Aslin (2002) & paper & 15 & Comp/Prod\\
+Swingley 2003 & paper & 19 & Comp/Prod\\
 Tamasi (2016) & dissertation & 30 & None\\
-\hline
 Tao \& Qinmei 2013 & paper & 12 & None\\
-\hline
-Tao et al. 2012 & paper & 16 & Comprehension\\
-\hline
+Tao et al. 2012 & paper & 16 & Comp\\
 van der Feest \& Fikkert, 2015 & paper & 24, 20 & None\\
-\hline
 van der Feest \& Johnson, 2016 & paper & 24 & None\\
-\hline
 Wewalaarachchi et al. 2017 & paper & 24 & None\\
-\hline
 White \& Aslin (2011) & paper & 18 & None\\
-\hline
 White \& Morgan (2008) & paper & 18, 19 & None\\
-\hline
 Zesiger \& Johr 2011 & paper & 14 & None\\
-\hline
-Zesiger et al. (2012) & paper & 12, 19 & Comprehension/Production\\
-\hline
+Zesiger et al. (2012) & paper & 12, 19 & Comp/Prod\\
+\bottomrule
 \end{tabular}
-
-{[}KATIE{]} THIS TABLE IS DEFINITELY NOT FINISHED! {[}CHRISTINA
-suggestions: N features should be a range and exclude 0; we could
-abbreviate Comperehension/Production to Comp./Prod.,
-etcetc{]}{[}KATIE{]} I've reduced the table to be about age and
-vocabulary, in order to have it more focused for the aim of this paper.
+\end{threeparttable}
+\end{center}
+\end{table}
+
+{[}Christina{]} I've shortened the labels and wanted to try out
+apa\_table {[}Katie{]} I like the idea, but does it work for you? It
+doesn't work for me\ldots{} {[}Katie{]} We have it currently set at less
+than 31 months, not 36, so I've changed below.
 
@@
 search was conducted on 22 September, 2017 and yielded 288 results. We
-screened the 398 items, removing 99 duplicate items. We screened
-remaining 299 items for their title and abstract to determine whether it
-met the following inclusion criteria: (1) original data was reported;
-(2) the experiment examined familiar word recognition; (3) infants
-studied were under 36-months-of-age; (4) the dependent variable was
-derived from proportion of looks to a target image versus a distractor
-in a eye movement experiment; 5) the stimuli were auditory speech. The
-final sample (n = \emph{32}) consisted of 27 journal articles, 1
-proceedings paper, 2 thesis, and 2 unpublished reports. We will refer to
-these items collectively as papers. Table 1 (Summary Table) provides an
-overview of all papers included in the present meta-analysis.
+screened the resulting 398 items, removing 99 duplicate items. We
+screened remaining 299 items for their title and abstract to determine
+whether it met the following inclusion criteria: (1) original data was
+reported; (2) the experiment examined familiar word recognition and
+mispronunciations; (3) infants studied were under 31-months-of-age; (4)
+the dependent variable was derived from proportion of looks to a target
+image versus a distractor in a eye movement experiment; (5) the stimuli
+were auditory speech. The final sample (n = \emph{32}) consisted of 27
+journal articles, 1 proceedings paper, 2 thesis, and 2 unpublished
+reports. We will refer to these items collectively as papers. Table 1
+(Summary Table) provides an overview of all papers included in the
+present meta-analysis.
 
@@
 The 32 papers we identified as relevant were then coded with as much
-detail as possible (Tsuji, Bergmann, \& Cristia, 2014; Bergmann et al.,
-2018). For each experiment (note that a paper typically has multiple
-experiments), we entered variables describing the publication,
-population, experiment design and stimuli, and results. For the present
-analyses, we focus on the following characteristics:
+consistently reported detail as possible (Tsuji, Bergmann, \& Cristia,
+2014; Bergmann et al., 2018). For each experiment (note that a paper
+typically has multiple experiments), we entered variables describing the
+publication, population, experiment design and stimuli, and results. For
+the analyses presented in this section, we focus on the following
+characteristics:
 
@@
 
-We separated out conditions according to whether or not the target word
-was mispronounced to be able to investigate infants' looking to the
-target picture separated by whether or not words were mispronounced as
-well as their mispronunciation sensitivity, which is the difference
-between looks to the target in correct and mispronounced trials. When
-the same infants were further exposed to multiple mispronunciation
-conditions and the results were reported separately in the paper, we
-also entered each condition as a separate row (e.g., consonant versus
-vowel mispronunciations; Mani \& Plunkett, 2007). The fact that the same
-infants contributed data to multiple rows (minimally those containing
-information on correct and mispronounced trials) leads to shared
-variance across effect sizes, which we account for in our analyses (see
-next section). We will call each row a record; in total there were 251
-records in our data.
+We separated conditions according to whether or not the target word was
+mispronounced to be able to investigate infants' looking to the target
+picture as well as their mispronunciation sensitivity, which is the
+difference between looks to the target in correct and mispronounced
+trials. When the same infants were further exposed to multiple
+mispronunciation conditions and the results were reported separately in
+the paper, we also entered each condition as a separate row (e.g.,
+consonant versus vowel mispronunciations; Mani \& Plunkett, 2007). The
+fact that the same infants contributed data to multiple rows (minimally
+those containing information on correct and mispronounced trials) leads
+to shared variance across effect sizes, which we account for in our
+analyses (see next section). We will call each row a record; in total
+there were 251 records in our data.
 
@@
 
+{[}Christina{]} I think it would be useful to say how many records, not
+papers, report each measure. e.g. \enquote{(n = xxx records from yyy
+papers)}. Would that be ok? {[}Katie{]} Totally! I think that gives a
+good bit of information. Good suggestion!
+
 Mispronunciation sensitivity studies typically examine infants'
-proportion of target looks (PTL) in comparison to a baseline
+proportion of target looks (PTL) in comparison to some baseline
 measurement. PTL is calculated by dividing the percentage of looks to
@@
 the baseline reported by the authors of each paper. Most papers
-(\emph{n} = 13) subtracted the PTL score for a pre-naming phase from the
-PTL score for a post-naming phase. When interpreting this difference
-score, a positive value indicates that infants increased their looks to
-the target after hearing the naming label (correct or mispronounced).
+(\emph{n} = 52 records from 13 papers) subtracted the PTL score for a
+pre-naming phase from the PTL score for a post-naming phase and report a
+difference score.
+
+{[}Christina{]} Katie, do you know whether the difference is computed
+based on items, participants, trials\ldots{}? Is there consistency?
+{[}Katie{]} From working with Nivi, we did it participants x condition
+or participants x trial (but mostly the former). But, this is not
+something we reported in papers. I don't think I read it at all when
+putting together the dataset for this either.
+
 Other papers either compared post- and pre-naming PTL with one another
-(\emph{n} = 10) or compared post-naming PTL with a chance level of 50\%,
-(\emph{n} = 9). For all these comparisons, a positive difference score
-or a post-naming phase PTL score that is greater than the pre-naming
-phase PTL or chance indicate target looks that indicate object
-recognition after hearing the naming label. Consequently, positive
-effect sizes reflect more looks to the target picture after naming, and
-larger positive effect sizes indicate comparatively more relative
-increase in looks to the target.
+(\emph{n} = 29 records from 10 papers), thus reporting two variables, or
+compared post-naming PTL with a chance level of 50\%, (\emph{n} = 23
+records from 9 papers). For all these comparisons, positive values
+(either as reported or after subtraction of chance level or a pre-naming
+PTL) indicate target looks towards the target object after hearing the
+label, i.e.~a recognition effect. Standardized effect sizes based on
+mean differences, as calculated here, preserve the sign. Consequently,
+positive effect sizes reflect more looks to the target picture after
+naming, and larger positive effect sizes indicate comparatively more
+looks to the target.
 
@@
 
+{[}Christina{]} These numbers seem wrong! Again, how about (xx effect
+sizes from yy papers)? {[}Katie{]} Well, they are kind of wrong :) Two
+papers report both for different experimental conditions. I've given the
+explanation now, not sure if that is good enough, but I'm really not
+sure how to say it a different way. {[}Katie{]} Do you want number of
+records and papers for the imputed correlations as well? You've put a
+-1, assuming there was something wrong with one of the papers or
+something like that? How does that shake out for number of records?
+
 We calculated Hedges' \emph{g} using the raw means and standard
-deviations reported in the paper (\emph{n} = 2) or using reported
-t-values (\emph{n} = 2). Raw means and standard deviations were
-extracted from figures for 3 papers. In a within-participation design,
-when two means are compared (i.e.~looking during pre- and post-naming)
-it is necessary to obtain correlations between the two measurements at
-the participant level to calculate effect sizes and effect size variance
-based on t-values. Upon request we were provided with correlation values
-for one paper (Altvater-Mackensen, 2010); we were able to compute
-correlations using means, standard deviations, and t-values for \emph{n}
-= 4 (following Csibra, et al. 2016, Appendix B; see also Rabagliati,
-Ferguson, \& Lew-Williams, 2018). Correlations were imputed for the
-remaining papers (see Black \& Bergmann, 2017, for the same procedure).
-We could compute a total of 104 effect sizes for correct pronunciations
-and 147 for mispronunciations.
+deviations reported in the paper (\emph{n} = 177 records from 25 papers)
+or using reported t-values (\emph{n} = 74 records from 9 papers). Two
+papers reported raw means and standard deviations for some experimental
+conditions and just t-values for the remaining experimental conditions
+(Swingley, 2016; Altvater-Mackensen et al., 2014). Raw means and
+standard deviations were extracted from figures for 3 papers. In a
+within-participation design, when two means are compared (i.e.~looking
+during pre- and post-naming) it is necessary to obtain correlations
+between the two measurements at the participant level to calculate
+effect sizes and effect size variance based on t-values. Upon request we
+were provided with correlation values for one paper (Altvater-Mackensen,
+2010); we were able to compute correlations using means, standard
+deviations, and t-values for \emph{n} = 4 (following Csibra, et al.
+2016, Appendix B; see also Rabagliati, Ferguson, \& Lew-Williams, 2018).
+Correlations were imputed for the remaining papers (see Black \&
+Bergmann, 2017, for the same procedure). We could compute a total of 104
+effect sizes for correct pronunciations and 147 for mispronunciations.
 
@@
 
-{[}CHRISTINA: Do you think we have to revise this section? I think it's
-the same as in the proceedings paper.{]}{[}KATIE: Are you concerned
-about the Publication Bias section in particular, or the Methods as a
-whole? In general, some of the Methods was written before the CogSci
-paper and in other places to flesh things out I rewrote what we had in
-the CogSci paper. Its definitely giving the same information and
-sometimes the wording is close, because there's not too many different
-ways to explain what a funnel plot is :){]}
-
 In the psychological sciences, there is a documented reluctance to
-publish null results. As a result, there is a potential for significant
-results to be valued over non-significant results (see Ferguson \&
-Heene, 2012). To examine whether this is also the case in the
-mispronunciation sensitivity literature, which would bias the data
-analyzed in this meta-analysis, we conduct two tests. We first examine
-whether effect sizes are distributed as expected based on sampling error
-using the rank correlation test of funnel plot asymmetry with the R
-{[}@R{]} package metafor {[}@metafor{]}. Effect sizes with low-variance
-are expected to fall closer to the estimated mean, while effect sizes
-with high-variance should show an increased, evenly-distributed spread
-around the estimated mean. Second, we analyze all of the significant
-results in the dataset using a p-curve from the p-curve app (v4.0,
-p-curve.com; @pcurve). This tests for evidential value by examining
-whether the p-values have an expected distribution, regardless of
-whether the null hypothesis is true or not, as well as whether there is
-a larger proportion of p-values just below the typical alpha threshold
-of .05, which may indicate questionable research practices. Responses to
-correctly pronounced and mispronounced labels are predicted to show
-different patterns of looking behavior; as a result, we conduct these
-two analyses to assess publication bias separately for both conditions.
+publish null results. As a result, significant results tend to be
+over-reported and thus might be over-represented in our meta-analyses
+(see Ferguson \& Heene, 2012). To examine whether this is also the case
+in the mispronunciation sensitivity literature, which would bias the
+data analyzed in this meta-analysis, we conduct two tests. We first
+examine whether effect sizes are distributed as expected based on
+sampling error using the rank correlation test of funnel plot asymmetry
+with the R {[}@R{]} package metafor {[}@metafor{]}. Effect sizes with
+low variance are expected to fall closer to the estimated mean, while
+effect sizes with high variance should show an increased,
+evenly-distributed spread around the estimated mean. Publication bias
+would lead to an uneven spread.
+
+Second, we analyze all of the significant results in the dataset using a
+p-curve from the p-curve app (v4.0, p-curve.com; @pcurve). This p-curve
+tests for evidential value by examining whether the p-values follow the
+expected distribution of a right skew in case the alternative hypothesis
+is true, versus a flat distribution that speaks for no effect being
+present in the population and all significant effect being spurious.
+Responses to correctly pronounced and mispronounced labels are predicted
+to show different patterns of looking behavior. In other words, there is
+an expectation that infants should look to the target when hearing a
+correct pronunciation, but some studies may report either significant
+looks or no significant looks to the target when hearing a mispronounced
+label
+
+{[}Christina{]} Katie, is that right, can you add a citation?
+{[}Katie{]} I've rewritten it a bit to be explicit about the difference
+between expectations for correct and mispronounced labels. I'm not sure
+what to cite though. The papers that find significant looks or no
+significant looks? That's basically the meta-analysis. Or some citation
+that talks about what looking to the target upon hearing a
+mispronunciation means in comparison to what target looks being
+decreased for mispronunciations relative to correct pronunciations
+means? I'm not so sure whether anyone has actually talked about that
+difference before, not sure what to cite.
+
+(i.e.~there might be no effect present in the population, see e.g., );
+as a result, we conduct these two analyses to assess publication bias
+separately for both conditions.
 
@@
 
-The models reported are hierarchical random-effects models (infant
-groups nested within papers) of variance-weighted effect sizes with the
-R {[}@R{]} package metafor {[}@metafor{]}. To investigate how
-development impacts mispronunciation sensitivity, our core theoretical
-question, we introduce age (centered; continuous and measured in days
-but transformed into months for ease of reading by dividing by 30.44) as
-a moderator to our main model. For the subsequent investigations of
-experimental characteristics, we introduce each characteristic as a
-moderator (more detail below).
-
-{[}CHRISTINA: Let's both reread the full paper once it is ready and
-check that this is properly motivated and whether we do need to list
-them all. For now I think the last sentence is fine, but I would tend to
-prefer a reminder for the forgetful reader.{]}{[}KATIE: that's
-reasonable! We had just listed everything 7 paragraphs before, which
-doesn't seem like a lot of \enquote{space}. Alternatively, this
-information could be listed in a table, and then just referred to.{]}
+The models reported here are hierarchical random-effects models (infant
+groups nested within papers) of variance-weighted effect sizes, which we
+computed with the R {[}@R{]} package metafor {[}@metafor{]}. To
+investigate how development impacts mispronunciation sensitivity, our
+core theoretical question, we introduce age (centered; continuous and
+measured in days but transformed into months for ease of interpreting
+estimates by dividing by 30.44) as a moderator to our main model. For a
+subsequent exploratory investigations of experimental characteristics,
+we introduce each characteristic as a moderator (more detail below).
 
@@
 multiple factors beside publication bias. The funnel plot asymmetry may
-also reflect heterogeneity in the data, perhaps due to some studies
-investigating more subtle effects than other studies. {[}CHRISTINA: I
-have to add some bits here.{]}
+also reflect heterogeneity in the data. There are various possible
+sources of heterogeneity, which our subsequent moderator analyses will
+begin to address. Nonetheless, we will remain cautious in our
+interpretation of our findings and hope that an open dataset that can be
+expanded by the community will attract previously unpublished null
+results so we can better understand infants' developing mispronunciation
+sensitivity.
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}
 \centering
@@
 that the data contain evidential value (Z = -17.93, \emph{p} \textless{}
-.001) and there is no evidence of a large proportion of p-values just
-below the typical alpha threshold of .05. The p-curve based on 36
-statistically significant values for mispronunciations indicates that
-the data contain evidential value (Z = -6.81, \emph{p} \textless{} .001)
-and there is no evidence of a large proportion of p-values just below
-the typical alpha threshold of .05.
+.001) and we find no evidence of a large proportion of p-values just
+below the typical alpha threshold of .05 that researchers consistently
+apply in this line of research. The p-curve based on 36 statistically
+significant values for mispronunciations indicates that the data contain
+evidential value (Z = -6.81, \emph{p} \textless{} .001) and there is
+again no evidence of a large proportion of p-values just below the
+typical alpha threshold of .05.
 
@@
 overestimate effect sizes and we therefore interpret all estimates with
-caution. Yet, the p-curve analysis suggests that overall, the literature
-contains evidential value, reflecting a \enquote{real} effect. We
-therefore continue our meta-analysis.
+caution. Yet, the p-curve analysis suggests that the literature contains
+evidential value, reflecting a \enquote{real} effect. We therefore
+continue our meta-analysis.
 
@@
 
-We first calculated the meta-analytic effect for object identification,
-i.e.~looks to the target image in response to correctly pronounced
-words. The variance-weighted meta-analytic effect size Hedges' \emph{g}
-was 0.908 (SE = 0.12) which was significantly different from zero (95\%
-CI{[}0.673, 1.143{]}, \emph{p} \textless{} .001). This is a rather large
-effect size (according to the criteria set by Cohen, 1988; see also
-Bergmann, et al., 2018; for comparative meta-analytic effect sizes in
-language acquisition research). That the effect size is significantly
-above zero suggests that when presented with the correctly pronounced
-label, infants fixated the corresponding object. Our analysis of funnel
-plot asymmetry, however, found evidence for publication bias, which
-might lead to an overestimated effect sizes as smaller, non-significant
-results might not be published. Although the effect size Hedges'
+We first calculated the meta-analytic effect for infants' ability to
+identify objects when hearing correctly pronounced labels. The
+variance-weighted meta-analytic effect size Hedges' \emph{g} was 0.908
+(SE = 0.12) which was significantly different from zero (CI {[}0.673,
+1.143{]}, \emph{p} \textless{} .001). This is a rather large effect size
+(according to the criteria set by Cohen, 1988; see also Bergmann, et
+al., 2018; for comparative meta-analytic effect sizes in language
+acquisition research). That the effect size is significantly above zero
+suggests that when presented with the correctly pronounced label,
+infants fixated the corresponding object. Our analysis of funnel plot
+asymmetry, however, found evidence for publication bias, which might
+lead to an overestimated effect sizes as smaller, non-significant
+results might not be published despite the fact that they should occur
+regularly even in well-powered studies. Although the effect size Hedges'
 \emph{g} may be overestimated for object identification in response to
 correctly pronounced words, the p-curve results and a CI lower bound of
-0.67 suggests that this result is robust even when correcting for
-publication bias. In other words, we are confident that the true
-population mean lies above zero for object recognition of correctly
-pronounced words.
-
-{[}CHRISTINA: Can you explain what the CI lower bound means here? I
-don't follow.{]}{[}KATIE: What do you think about this (last sentence)?
-The CI lower bound stuff here actually comes from something you wrote,
-so tell me whether its correct.{]}
+0.67 which is substantially above zero suggests that this result should
+be robust even when correcting for publication bias. In other words, we
+are confident that the true population mean lies above zero for object
+recognition of correctly pronounced words.
 
@@
 meta-analytic effect size Hedges' \emph{g} was 0.25 (SE = 0.06) which
-was also significantly different from zero (95\% CI{[}0.133, 0.367{]},
+was also significantly different from zero (CI {[}0.133, 0.367{]},
 \emph{p} \textless{} .001). This is considered a small effect size
@@
 
-Heterogeneity was significant for both correctly pronounced (Q(103) =
-625.63, \emph{p} \textless{} .001) and mispronounced words, (Q(146) =
-462.51, \emph{p} \textless{} .001). This indicated that the sample
-contains unexplained variance leading to significant difference across
-our studies beyond what is to be expected based on random sampling
-error. We therefore continue with our moderator analysis.
+{[}Christina{]} I am not sure about the placement of this paragraph
+because the next section cannot explain this heterogeneity, so maybe we
+should move it down to the beginning of the age part? {[}Katie{]} I
+think that makes sense, moving it!
 
@@
 sensitivity, we compared the effect size Hedges' \emph{g} for correct
-pronunciations with mispronunciations directly, merging the two
-datasets. The moderator test was significant, QM(1) = 215.761,
-\emph{p}\textless{} .001. Hedges' \emph{g} for mispronunciation
-sensitivity was 0.495 (SE = 0.034), which indicated that the responses
-across conditions were significantly different (95\% CI{[}0.429,
-0.561{]}, \emph{p} \textless{} .001). This confirms that although
-infants fixate the correct object for both correct pronunciations and
-mispronunciations, the observed fixations to target (as measured by the
-effect sizes) were significantly greater for correct pronunciations. In
-other words, we observe a significant difference between the two
-conditions and can now quantify the modulation of fixation behavior in
-terms of standardized effect sizes.
+pronunciations with mispronunciations directly. To this end, we combined
+the two datasets. The moderator test was significant, QM(1) = 215.761,
+\emph{p}\textless{} .001. The estimate for mispronunciation sensitivity
+was 0.495 (SE = 0.034), and infants' looking times across conditions
+were significantly different (CI {[}0.429, 0.561{]}, \emph{p}
+\textless{} .001). This confirms that although infants fixate the
+correct object for both correct pronunciations and mispronunciations,
+the observed fixations to target (as measured by the effect sizes) were
+significantly greater for correct pronunciations. In other words, we
+observe a significant difference between the two conditions and can now
+quantify the modulation of fixation behavior in terms of standardized
+effect sizes and their variance. This first result has both theoretical
+and practical implications, as we can now reason about the amount of
+perturbance caused by mispronunciations and can plan future studies to
+further investigate this effect with suitable power.
+
+Heterogeneity was significant for both correctly pronounced (Q(103) =
+625.63, \emph{p} \textless{} .001) and mispronounced words, (Q(146) =
+462.51, \emph{p} \textless{} .001), as well as mispronunciation
+sensitivity, which included the moderator condition, (QE(249) =
+1,088.14, \emph{p} \textless{} .001). This indicated that the sample
+contains unexplained variance leading to significant difference across
+our studies beyond what is to be expected based on random sampling
+error. We therefore continue with our moderator analysis to investigate
+possible sources of this variance.
 
@@
 for how mispronunciation sensitivity will change as infants develop, we
-next added the moderator age (centered, in days). In the first analyses,
-we investigate the impact of age separately on conditions where words
-were either pronounced correctly or not. Age did not significantly
-modulate object identification in response to correctly pronounced QM(1)
-= 215.761, \emph{p}\textless{} .001 or mispronounce words QM(1) =
-215.761, \emph{p}\textless{} .001. The lack of a significant modulation
-together with the small estimates indicates that there was no
-relationship between age and target looks in response to a correctly
-pronounced or mispronounced label. This relationship is plotted in
-Figure 2.
+next added the moderator age (centered; continuous and measured in days
+but transformed into months for ease of interpreting estimates by
+dividing by 30.44 for Figure 2). {[}Christina{]} What about the whole
+months thing? {[}Katie{]} We had an explanation in the methods section
+for this, I've now added it again here.
+
+In the first analyses, we investigate the impact of age separately on
+conditions where words were either pronounced correctly or not. Age did
+not significantly modulate object identification in response to
+correctly pronounced (QM(1) = 0.678, \emph{p}= 0.41) or mispronounced
+words (QM(1) = 1.715, \emph{p}= 0.19). The lack of a significant
+modulation together with the small estimates (correct: \(\beta\) =
+0.015, SE = 0.018, 95\% CI{[}-0.02, 0.049{]}, \emph{p}= 0.41;
+mispronunciation: \(\beta\) = 0.015, SE = 0.011, 95\% CI{[}-0.007,
+0.037{]}, \emph{p}= 0.19) indicates that there was no relationship
+between age and target looks in response to a correctly pronounced or
+mispronounced label. We plot both object recognition and
+mispronunciation sensitivity as a function of age in Figure 2.
+
+{[}Christina{]} OK there is a mismatch between what you write and the
+numbers, can you verify? {[}Katie{]} Good catch. For some reason, it was
+just copying over the moderator test from mispronunciation sensitivity,
+even though I was calling for the age moderator analysis. There is no
+significant moderator test, but it was just pasting the same one again
+and again. I've fixed my code, so it should be correct now!
 
@@
 sensitivity (correct vs.~mispronounced words) in our whole dataset. The
-moderator test was significant QM(1) = 215.761, \emph{p}\textless{}
-.001. This result is in line with the general observation that as
-infants mature they become better at language processing. The
-interaction between age and mispronunciation sensitivity, however, was
-not significant \(\beta\) = 0.003, SE = 0.008, 95\% CI{[}-0.012,
-0.018{]}, \emph{p}= 0.731. The small estimate size, as well as
-inspection of Figure 2 suggests that as infants age, their
+moderator test was significant (QM(3) = 218.621, \emph{p}\textless{}
+.001). The interaction between age and mispronunciation sensitivity,
+however, was not significant (\(\beta\) = 0.003, SE = 0.008, 95\%
+CI{[}-0.012, 0.018{]}, \emph{p}= 0.731), pointing to the moderator test
+being driven by the difference between conditions. The small estimate,
+as well as inspection of Figure 2 suggests that as infants age, their
 mispronunciation sensitivity remains the same.
@@
 
-Of the 32 papers included in the meta-analysis, 8 (comprehension = 7
-papers; production = 1) analyzed the relationship between vocabulary
-scores and mispronunciation sensitivity, specifically object recognition
-for correct pronunciations and mispronunciations. There is reason to
-believe that production data are different from comprehension data (the
-former being easier to estimate for parents in the typical
-questionnaire-based assessment), so we analyze this data separately.
-
-{[}CHRISTINA{]} SO WE DON'T WANT TO INTERPRET THE FIXED EFFECTS MODEL AT
-ALL, IT IS NOT SUITABLE BECAUSE THERE IS VARIANCE BETWEEN EVERY RECORD
-(LANGUAGE ETC). I WOULD INTERPRET THE OVERALL CORRELATION AND THE CI,
-NOT THE P-VALUE (IN GENERAL). I ALSO WONDER WHETHER WE SHOULD MOVE THE
-SUBSET ANALYSES TO THE SUPPLEMENTARY MATERIALS AND JUST SAY OVERALL WE
-SEE NO RELATIONSHIPS AND CORRELATION COEFFICIENTS CONSISTENYL BELOW .1
-WE THEREFORE MUST CONCLUDE THAT WITHIN NARROW AGE GROUPS VOCABULARY DOES
-NOT INFLUENCE ANYTHING WE LOOK AT. WE CANNOT DO THIS ANALYSIS FPOR MP
-SENSITIVITY BECAUSE WE DON'T HAVE THE NECESSARY RAW DATA. {[}KATIE: Ah,
-so because for each paper the correlation and CI values straddle 0, this
-indicates that there really isn't much evidence for a relationship? I've
-tried to write this out below, let me know what you think. Over the
-summer, I had also played around with looking at how collection of
-vocabulary data has dropped off over the years, even though more
-mispronunciation studies have been published. That might be something
-interesting to add. If we truly think that this is what is driving the
-development of mispronunciation sensitivity, then why are people not
-collecting this data?{]} (BUT I WONDER WHETHER WECOULD ENCODE THE
-REPORTED INTERACTION TERMS AND THE CORRELATION AND THEN DO SOMETHING
-WITH THAT?) {[}KATIE: I'm not really sure what you mean by this :({]}
-
-{[}Katie: below, I'm using coweeta.uga.edu/publications/10436.pdf, page
-80 as a model for writing up these results. I haven't the funniest clue
-what I'm doing! :p{]}
+Of the 32 papers included in the meta-analysis, 13 analyzed the
+relationship between vocabulary scores and object recognition for
+correct pronunciations and mispronunciations (comprehension = 11 papers
+and 43 records; production = 2 papers and 16 records). There is reason
+to believe that production data are different from comprehension data
+(the former being easier to estimate for parents in the typical
+questionnaire-based assessment; Kidd citation), and we therefore planned
+to analyze these two types of vocabulary measurement separately.
+However, only 2 papers reported correlations with productive vocabulary
+scores, limiting the conclusions that can be drawn. In our vocabulary
+analysis, we therefore focus exclusively on the relationship between
+comprehension and mispronunciation sensitivity.
+
+{[}Christina{]} Removed the previous comment chaos. So can you not only
+list papers but also n conditions above? With just 1 paper for
+production, I wouldn't analyze it to be honest. it's just not enough
+data. I also liked your comments about the time line of this whole
+thing, can you extract the years of papers which report this? Might be
+extremely useful in the discussion and strengthens our case that there
+is no effect, bc people don't find the predicted relation with vocab.
+Also, cann you add a citation for comp vs prod? I think Evan Kidd had a
+paper on it, if you don't have one handy, I can look it up. {[}Katie{]}
+I couldn't find what you are referring to. Could you add the Evan Kidd
+paper? Also, I added a histogram figure below, but I'm not so very sure
+that it is good enough to add to the paper (its under the heading
+\enquote{Potential Vocabulary Figure}). Let me know what you think.
 
@@
 pronunciations for 9 of 12 experimental conditions, with correlation
-values ranging from -0.17 to 0.48. The mean effect size XXX was 0.0897,
-but did not differ significantly from zero (95\% CI{[}-0.0105; 0.1900{]}
-\emph{p} = .0795). Higher production scores were also associated with
-greater object recognition in response to correct pronunciations for 9
-of 16 experimental conditions, with correlation values ranging from
--0.23 to 0.44. The mean effect size XXX was 0.0601, but did not differ
-significantly from zero (95\% CI{[}-0.0331; 0.1533{]} \emph{p} = .2061).
-For both comprehension and production scores, the small correlation
-effect sizes and large variances suggest a lack of relationship between
-vocabulary and object recognition for correct pronunciations.
+values ranging from -0.17 to 0.48. The mean effect size Pearson's
+\emph{r} of 0.09 was small and did not differ significantly from zero
+(CI {[}-0.01; 0.19{]} \emph{p} = 0.079). However, the lower bound of the
+CI is close to zero, and one might hypothesize that with more power the
+small relationship might become significant. At the same time, a larger
+sample might confirm our conclusion that there is no relationship. As a
+result, we can not draw firm conclusions about the relationship between
+comprehension scores and object recognition in response to correct
+pronunciations.
 
@@
 pronunciations for 17 of 31 experimental conditions, with correlation
-values ranging from -0.35 to 0.57. The mean effect size XXX was 0.0377,
-but did not differ significantly from zero (95\% CI{[}-0.0260; 0.1014{]}
-\emph{p} = .2465). For production, however, lower production scores were
-associated with greater object recognition in response to
-mispronunciations for 16 of 31 experimental conditions, with correlation
-values ranging from -0.28 to 0.44. The mean effect size XXX was -0.0402,
-but did not differ significantly from zero (95\% CI{[}-0.1043; 0.0238{]}
-\emph{p} = .2181). For both comprehension and production scores, the
-small correlation effect sizes and large variances suggest a lack of
-relationship between vocabulary and object recognition for
-mispronunciations.
+values ranging from -0.35 to 0.57. The mean effect size Pearson's
+\emph{r} of 0.04 was small and did not differ significantly from zero
+(CI {[}-0.03; 0.10{]} \emph{p} = 0.246). Similar to the relationship
+between comprehension scores and correct pronunciation object
+identification, the small correlations and large variances suggest a
+lack of relationship between vocabulary and object recognition for
+mispronunciations. We again emphasize that we cannot draw firm
+conclusions due to the small number of studies we were able to include
+here.
+
+\subsection{Potential Vocabulary
+Figure}\label{potential-vocabulary-figure}
+
+\begin{figure}
+\centering
+\includegraphics{Paper_Analyses_files/figure-latex/Vocab_describe1-1.pdf}
+\caption{}
+\end{figure}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
 
@@
 The main goal of this paper was to assess mispronunciation sensitivity
-and its maturation with age. The results are clear: Although infants
+and its maturation with age. The results seem clear: Although infants
 consider a mispronunciation as a better match with the target image than
@@
 between vocabulary and target looking for correct pronunciations or
-mispronunciations. In sum, it seems that current theories of infants'
-phono-lexical development cannot fully capture our results and should be
-reconsidered with all the evidence in mind.
-
-Alternatively, it is possible that variation in the analysis approach
-lead to systematic differences in the size of mispronunciation
-sensitivity. Choices about the approach to data analysis have a higher
-possibility to be influenced by the shape of the data itself after
-collection, and are therefore susceptible to a higher rate of
-false-positives (Simmons, Nelson, \& Simonsohn, 2011). Although we did
-not have specific predictions about these variables, such as size of
-time window analyzed or dependent variable calculated, we included these
-variables in our coding scheme for the meta-analysis dataset. As
-reported in the Methods section (and discussed in detail below), some of
-these variables varied widely across studies. In the following section,
-we include an exploratory analysis to investigate the possibility of
-systematic differences in the approach to analysis in general and across
-infant age.
-
-{[}KATIE{]} I've changed the above paragraph to lead to exploratory
-analyses, not moderators. Since the fmailiar/unfamiliar analysis doesn't
-really work out except for if we kind of subset and torture the data, I
-think its more interesting to talk about how choices of analysis /
-researcher degrees of freedom may influence the data
+mispronunciations, although our analyses may be underpowered. In sum, it
+seems that current theories of infants' phono-lexical development cannot
+fully capture our results and should be reconsidered with all the
+evidence in mind.
+
+Alternatively, an effect of maturation might have been masked by other
+factors we have not yet captured in our analyses. A strong candidate
+that emerged during the construction of the present dataset and careful
+reading of the original papers is the analysis approach. We observed, as
+mentioned in the Methods section, large variance in the dependent
+variable reported, and additionally noted variance in the size of the
+time window chosen for analyses. Researchers might adapt their analysis
+strategy to age or they might be influenced by having observed the data.
+In the latter case, we expect an increase in significant results, which
+at the same time can (partially) explain the publication bias we observe
+(Simmons, Nelson, \& Simonsohn, 2011).
+
+We included details related to timing and type of dependent variable
+calculated in our coding of the dataset because they are consistently
+reported and might be useful for experiment design in the future by
+highlighting typical choices and helping establish field standards. In
+the following section, we include an exploratory analysis to investigate
+the possibility of systematic differences in the approach to analysis in
+general and across infant age. The purpose of this analysis is to better
+understand the influence of choices made in analyzing mispronunciation
+sensitivity studies as well as the influence these choices may have on
+our understanding of mispronunciation sensitivity development.
 
@@
 
-We identified several variables to assess the influence of data analysis
-choices. These variables fall into two types of categories: time-related
-and dependent variable related. In the following analyses, we discuss
-the theoretical motivation for these data analysis choices, the
-variation present in the current meta-analysis dataset, and the
-influence these choices have on mispronunciation sensitivity
-development.
-
-\subsubsection{Time-related analyses}\label{time-related-analyses}
-
-When designing mispronunciation sensitivity studies, experimenters
-choose the length of time each trial is presented. This includes both
-the length of time before the target object is named (pre-naming phase)
-as well as after (post-naming phase) and is determined prior to data
-collection. Across papers, trial length varied from 2750 to 13000 ms,
-with a mode of 5000 ms. There was an inverse relationship between infant
-age and trial length, such that younger infants were given trials of a
-longer length, although this correlation was not significant (\emph{r} =
--0.11, \emph{p} = 0.086). Presumably, younger infants may be given
-longer trials because their word recognition abilities may be slower
-than older infants (Fernald et al., 1998).
-
-Unlike the length of trial, the length of the post-naming phase analyzed
-can be chosen after the experimental data is collected. Interestingly,
-half of the experimental conditions were analyzed using the same length
-of post-naming phase as the infant heard in the actual experiment 126,
-while the other half were analyzed using a shorter length of post-naming
-phase, excluding later portions of the post-naming phase 125. Across
-papers, the length of the post-naming phase analyzed varied from 1510 to
-6000 ms, with a mode of 2000 ms. Similar to trial length, there was an
-inverse relationship between infant age and length of post-naming phase
-analyzed, such that younger infants were analyzed using a longer length
-of post-naming phase, although here the relationship was significant
-(\emph{r} = -0.21, \emph{p} \textless{} .001). Again, the choice to
-analyze a shorter post-naming time window is likely related to evidence
-that speed of processing is slower in younger infants (Fernald et al.,
-1998). Furthermore, the proportion of post-naming phase time window
-analyzed in comprison to the total post-naming phase presented to
-infants significantly decreased with increasing infant age (\emph{r} =
--0.18, \emph{p} = 0.004). Although trial length did not differ by infant
-age, the size of the post-naming phase time window analyzed did differ
-by infant age.
-
-When analyzing eye-movements, it is important to consider the amount of
-time it takes for an eye movement to be initiated in response to a
-stimulus. Previous studies examining simple stimulus response latencies
+{[}Christina{]} This section talked about several variables in 2
+categories, but in reality there are only 2 variables, right? I am not
+100\% sure about total trial length as being the first or being
+mentioned at all, might it be better to focus on time window analyzed
+and then say \enquote{Oh, btw, total trial length totally does nothing
+so we don't have to discuss it further} I am not sure, so feel free to
+re-rewrite this, but now it better lines up with everything before
+because trial length kinda comes out of nowhere. {[}Katie{]} That's
+fair! I think maybe we don't need the full analysis for total time
+presented or for the offset analysis, but I'd like to still mention them
+because it really shows that its something about this post-naming time
+window choice that influences it, and not just fishing around for
+variability until we find something that works. In the end there are 2
+interesting analyses, but offset could have been interesting (but
+wasn't). Therefore, I'd still like to refer to the timing variables as a
+type of category. Otherwise, we say we'll do size of time window
+analyzed, but then we have information about other timing stuff as well.
+
+We identified two sets of variables which had the potential to vary
+across papers to assess the influence of data analysis choices on
+resulting effect size: timing (size of time window analyzed; offset
+time) and which dependent variable(s) were reported. In the following,
+we discuss the possible theoretical motivation for these data analysis
+choices, the variation present in the current meta-analysis dataset, and
+the influence these analysis choices have on mispronunciation
+sensitivity development. We focus specifically on the size of the
+mispronunciation sensitivity effect, considering the whole dataset and
+including condition (correct pronunciation, mispronunciation) as
+moderator.
+
+\subsubsection{Timing}\label{timing}
+
+{[}Christina{]} Is there a reason you choose mode and not median?
+{[}Katie{]} Hmm, I felt like mode would be interesting, because it gives
+the most popular choice (74 experimental conditions). But, the median is
+only 500 ms less, so we could use that too (9 experimental conditions).
+
+{[}Christina{]} Would it make sense to present dependent variable first?
+{[}Katie{]} I don't have a strong opinion on this. If you think it would
+be better, then I can change it.
+
+In a typical trial in a mispronunciation sensitivity study, the
+target-distractor image pairs are first presented in silence, followed
+by auditory presentation of a carrier phrase or isolated presentation of
+the target word (correctly pronounced or mispronounced). When designing
+mispronunciation sensitivity studies, experimenters can choose the
+length of time each trial is presented. This includes both the length of
+time before the target object is named (pre-naming phase) as well as
+after (post-naming phase) and is determined prior to data collection. To
+examine the size of the time window analyzed in the post-naming phase,
+we must first consider overall length of time post-naming, because it
+limits the overall time window available to analyze and might thus
+predict which time window was analyzed. Across papers, actual
+post-naming phase length varied from 2000 to 9000 ms, with a median
+value of 3500 ms. There was an inverse relationship between infant age
+and actual post-naming phase length, such that younger infants were
+presented with longer a longer post-naming phase, although this
+correlation was not significant (\emph{r} = 0.01, \emph{p} = 0.882).
+Presumably, younger infants may be exposed to longer trials because
+their word recognition abilities are expected to be slower than older
+infants (Fernald et al., 1998).
+
+Unlike the actual post-naming phase length, the size of the post-naming
+time window analyzed can be chosen after the experimental data is
+collected. Interestingly, half of the experimental conditions were
+analyzed using the same length of post-naming phase as the infant heard
+in the actual experiment (124), while the other half were analyzed using
+a shorter length of post-naming phase, excluding later portions of the
+post-naming phase (127). Across papers, the length of the post-naming
+phase analyzed varied from 1510 to 4000 ms, with a median value of 2500
+ms. Similar to actual post-naming phase length, there was an inverse
+relationship between infant age and the size of the post-naming time
+window analyzed, such that younger infants' looking times were analyzed
+using a longer post-naming time window, here the relationship was
+significant (\emph{r} = -0.23, \emph{p} \textless{} .001). Again, the
+choice to analyze a shorter post-naming time window is likely related to
+evidence that speed of processing is slower in younger infants (Fernald
+et al., 1998). To summarize, we observe variation in time-related
+aspects related to infants' age. This variation is most pronounced, and
+even significant, for the time window that is being analyzed after the
+target label has been heard.
+
+{[}Christina{]} The canfield \& haith paper is for visual stimuli,
+right? So add that before \enquote{stimulus}. And then add to the next
+sentence that the longer latnecies are because ther eis addiitonal
+language processing required which EEg shows in adults to take X ms (400
+for N400?). {[}Katie{]} I agree with the reasoning, but I don't think
+referring to adult ERP literature is the way to go. I've rewritten these
+sentences to be more faithful to the misp sensitivity literature.
+
+{[}Christina{]} Can you add info how many papers did not report the
+analyzed variables? Across this whole section, I mean. {[}Katie{]} All
+papers reported the actual post-naming phase length and the size of the
+post-naming time window analyzed.
+
+Another potential source of variation in studies that analyze
+eye-movements is the amount of time it takes for an eye movement to be
+initiated in response to a visual stimulus, which we refer to as offset
+time. Previous studies examining simple stimulus response latencies
 first determined that infants require at least 233 ms to initiate an
-eye-movement in response to a stimulus (Canfield \& Haith, 1991). In
-mispronunciation sensitivity studies, however, this has often been
-extended to 367 ms (e.g.~Swingley \& Aslin, 2000, 2002, 2007). Across
-papers, the majority used a similar offset value (between 360 and 370
-ms) for analysis (\emph{n} = 151), but offset values ranged from 0 to
-500 ms, and were not reported for 36 experimental conditions. We note
-that Swingley (2009) also included offset values of 1133 ms to analyze
-responses to coda mispronunciations. There was an inverse relationship
-between infant age and size of offset, such that younger infants were
-given longer offsets, although this correlation was not significant
-(\emph{r} = -0.10, \emph{p} = 0.13). This lack of a relationship is
-perhaps driven by the field's consensus that an offset of about 367 ms
-is appropriate for analyzing word recognition with PTL measures,
-including studies that evaluate mispronunciation sensitivity.
+eye-movement in response to a stimulus (Canfield \& Haith, 1991). In the
+first infant mispronunciation sensitivity study, Swingley and Aslin
+(2000) used an offset time of 367 ms, which was \enquote{an
+\enquote{educated guess} based on studies\ldots{} showing that target
+and distractor fixations tend to diverge at around 400 ms.} (Swingley \&
+Aslin, 2000, p.~155). Upon inspecting the offset time values used in the
+papers in our meta-analysis, the majority used a similar offset time
+value (between 360 and 370 ms) for analysis (\emph{n} = 151), but offset
+values ranged from 0 to 500 ms, and were not reported for 36
+experimental conditions. We note that Swingley (2009) also included
+offset values of 1133 ms to analyze responses to coda mispronunciations.
+There was an inverse relationship between infant age and size of offset,
+such that younger infants were given longer offsets, although this
+correlation was not significant (\emph{r} = -0.10, \emph{p} = 0.13).
+This lack of a relationship is possibly driven by the field's consensus
+that an offset of about 367 ms is appropriate for analyzing word
+recognition with PTL measures, including studies that evaluate
+mispronunciation sensitivity.
 
@@
 window (infant age) or offset time (previous studies), these choices may
-occur after data collection and are therefore susceptible to a higher
-rate of false-positives. Considering that differences in these choice
-were systematically different across infant ages, at least for the
-post-naming time window, we next explored whether the size of the
-analyzed post-naming phase time window or the offset time influenced
-sensitivity to mispronunciations.
-
-\subsubsection{Length of post time}\label{length-of-post-time}
-
-We first assessed whether size of post-naming phase analyzed had an
-impact on the size of mispronunciation sensitivity. First, we calculated
-the meta-analytic effect for object identification in response to
-mispronounced target words/images, including post-naming phase size as a
-moderator. The moderator test was not significant QM(1) = 215.761,
-\emph{p}\textless{} .001 and the estimate for post-naming phase size was
-relatively small, \(\beta\) = 0.121, SE = 0.073, 95\% CI{[}-0.022,
-0.264{]}, \emph{p}= 0.097. This suggests that upon hearing a
-mispronunciation, infants' looks to the target image were similar
-regardless of the size of the post-naming phase analyzed. We next
-assessed whether post-naming phase size was related to mispronunciation
-sensitivity. We merged the two datasets and included condition (correct
-pronunciation, mispronunciation) as an additional moderator. The
-moderator test was significant, QM(1) = 215.761, \emph{p}\textless{}
-.001. The estimate for the interaction between post-naming phase size
-and condition was small but significant \(\beta\) = -0.156, SE = 0.051,
-95\% CI{[}-0.256, -0.056{]}, \emph{p}= 0.002. This relationship is
-plotted in Figure 3a. The results suggest that although the size of the
-post-naming phase analyzed did not impact infants' likelihood to fixate
-the target upon hearing the mispronunciation, it did significantly
-impact mispronunciation sensitivity. Specifically, the difference
-between target fixations for correctly pronounced and mispronounced
-items (mispronunciation sensitivity) was significantly greater when the
-post-naming phase that was shorter in length.
+occur after data collection and might therefore lead to a higher rate of
+false-positives (Gelman, A., \& Loken, E. (2013). Considering that these
+choices were systematically different across infant ages, at least for
+the post-naming time window, we next explored whether the size of time
+window analyzed or the offset time influenced sensitivity to
+mispronunciations.
+
+\paragraph{Size of post-naming time window
+analyzed}\label{size-of-post-naming-time-window-analyzed}
+
+{[}Christina{]} I think it's a bit inconsistent whether it's post naming
+phase or window, how about window? Phase sounds wrong to me. or analysis
+window? I also find phase size odd, and again prefer window (window
+size). Your call though. {[}Katie{]} I agree and I've updated it to
+refer to window size when talking about the analyzed portion and to
+phase when refering to it as the entire actual presentation time.
+
+We first assessed whether size of the post-naming time window analyzed
+had an impact on the overall size of the reported mispronunciation
+sensitivity. We considered data from both conditions in a joint analysis
+and included condition (correct pronunciation, mispronunciation) as an
+additional moderator. The moderator test was significant, QM(3) =
+236.958, \emph{p}\textless{} .001. The estimate for the interaction
+between post-naming phase size and condition was small but significant
+\(\beta\) = -0.262, SE = 0.059, 95\% CI{[}-0.377, -0.148{]},
+\emph{p}\textless{} .001. This relationship is plotted in Figure 3a. The
+results suggest that the size of the post-naming phase analyzed
+significantly impacted mispronunciation sensitivity. Specifically, the
+difference between target fixations for correctly pronounced and
+mispronounced items (mispronunciation sensitivity) was significantly
+greater when the post-naming phase that was shorter in length.
 
 Considering that we also found a relationship between the length of the
-post-naming phase analyzed and infant age, such that younger ages had a
-longer post-naming phase time window of analysis, we next examined
-whether the size of post-naming phase analyzed modulated the development
-of mispronunciation sensitivity. For object recognition in response to a
-mispronunciation, including age as a moderator resulted in a moderator
-test that was not significant QM(1) = 215.761, \emph{p}\textless{} .001,
-and a small estimate for the interaction between age and size of
-post-naming phase (\(\beta\) = -0.156, SE = 0.051, 95\% CI{[}-0.256,
--0.056{]}, \emph{p}= 0.002. This suggests that upon hearing a
-mispronunciation, infant measured looks to the target image were
-similar, regardless of infant age or size of the post-naming phase
-analyzed. We next assessed whether the relationship between size of the
-post-naming phase analyzed and mispronunciation sensitivity was
-modulated by age. We merged the two datasets and included condition
-(correct pronunciation, mispronunciation) as well as age as additional
-moderators. The moderator test was significant QM(1) = 215.761,
-\emph{p}\textless{} .001. The estimate for the three-way-interaction
-between condition, size of post-naming phase, and age was small, but
-significant (\(\beta\) = = NA, SE = NA, 95\% CI{[}NA, NA{]}, \emph{p}NA.
-This relationship is plotted in Figure 3b. Smaller post-naming phase
-size lead to greater increases in mispronunciation sensitivity with
-development. For example, experimental conditions analyzed with a
-post-naming phase of 2000 ms or less, mispronunciation sensitivity
-increases with infant age, whereas a post-naming phase of greater than
-2000 ms leads to either no impact of age on mispronunciation sensitivity
-or a negative relationship between age and mispronunciation sensitivity.
+post-naming time window analyzed and infant age, such that younger ages
+had a longer window of analysis, we next examined whether the size of
+post-naming time window analyzed modulated the development of
+mispronunciation sensitivity. We merged the two datasets and included
+condition (correct pronunciation, mispronunciation) as well as age as
+additional moderators. The moderator test was significant QM(7) =
+247.322, \emph{p}\textless{} .001. The estimate for the
+three-way-interaction between condition, size of post-naming phase, and
+age was small, but significant (\(\beta\) = = -0.04, SE = 0.014, 95\%
+CI{[}-0.068, -0.012{]}, \emph{p}= 0.006. As can be seen in Figure 3b,
+smaller post-naming time window size leads to greater increases in
+mispronunciation sensitivity with development. For example, when
+experimental conditions were analyzed with a post-naming time window of
+2000 ms or less, mispronunciation sensitivity is found to increase with
+infant age. If the post-naming time window analyzed is greater than 2000
+ms, however, there is no or a negative relation of mispronunciation
+sensitivity and age. In other words, all three possible hypotheses might
+be supported depending on analysis choices made regarding the size of
+the post-naming time window to analyze. This is especially important,
+considering that our key question is how mispronunciation sensitivity
+changes with development. These results suggest that conclusions about
+the relationship between infant age and mispronunciation sensitivity may
+be mediated by the size of the post-naming time window analyzed.
 
@@
 
-\subsubsection{Length of offset time}\label{length-of-offset-time}
-
-We next assessed whether offset time had an impact on the size of
-mispronunciation sensitivity. First, we calculated the meta-analytic
-effect for object identification in response to mispronounced target
-words/images, including offset time as a moderator. The moderator test
-was not significant QM(1) = 215.761, \emph{p}\textless{} .001 and the
-estimate for offset time was very small, \(\beta\) = 0.001, SE = 0, 95\%
-CI{[}0, 0.001{]}, \emph{p}= 0.132. This suggests that upon hearing a
-mispronunciation, infants' looks to the target image were similar
-regardless of the offset time used to analyze the data. We next assessed
-whether offset time was related to mispronunciation sensitivity. We
-merged the two datasets and included condition (correct pronunciation,
-mispronunciation) as an additional moderator. The moderator test was
-significant, QM(1) = 215.761, \emph{p}\textless{} .001, but the estimate
-for the interaction between offset time and condition was very small and
-not significant \(\beta\) = 0, SE = 0, 95\% CI{[}-0.001, 0{]}, \emph{p}=
-0.505.
-
-We next examined whether offset time modulated the development of
-mispronunciation sensitivity. For object recognition in response to a
-mispronunciation, including age as a moderator resulted in a moderator
-test that was not significant QM(1) = 215.761, \emph{p}\textless{} .001,
-and a very small estimate for the interaction between age and size of
-post-naming phase (\(\beta\) = 0, SE = 0, 95\% CI{[}0, 0{]}, \emph{p}=
-0.924. This suggests that upon hearing a mispronunciation, infant
-measured looks to the target image were similar, regardless of infant
-age or offset time. We next assessed whether the relationship between
-offset time and mispronunciation sensitivity was modulated by age. We
-merged the two datasets and included condition (correct pronunciation,
-mispronunciation) as well as age as additional moderators. The moderator
-test was significant QM(1) = 215.761, \emph{p}\textless{} .001, but the
-three-way-interaction between condition, offset time, and age was very
-small and not significant (\(\beta\) = = 0, SE = 0, 95\% CI{[}0, 0{]},
-\emph{p}= 0.605.
-
-Taken together, these results suggest that offset time does not modulate
+\paragraph{Offset time after target
+naming}\label{offset-time-after-target-naming}
+
+{[}Christina{]} Generally, it might be easier to kick out all object
+recognition analyses (what do they tell us?) and start out that we only
+analyze MP sensitivity, i.e.~consider the whole dataset and always
+include condition as moderator. {[}Katie{]} Agreed! I've gotten rid of
+all of the object recognition analyses and added an explanation at the
+beginning of the Exploratory Analysis section.
+
+We next assessed whether the time between the target was named and the
+start of the analysis, namely offset time, had an impact on the size of
+the reported mispronunciation sensitivity. When we included both
+condition and offset time as moderators, the moderator test was
+significant, QM(3) = 236.958, \emph{p}\textless{} .001, but the estimate
+for the interaction between offset time and condition was almost zero
+\(\beta\) = 0, SE = 0, 95\% CI{[}-0.001, 0{]}, \emph{p}= 0.505. Although
+we found no relationship between offset time and infant age, we also
+examined whether the size of offset time modulated the development of
+mispronunciation sensitivity. When both offset time and condition were
+included as moderators, the moderator test was significant QM(7) =
+200.867, \emph{p}\textless{} .001, but the three-way-interaction between
+condition, offset time, and age was very small and not significant
+(\(\beta\) = = 0, SE = 0, 95\% CI{[}0, 0{]}, \emph{p}= 0.605. Taken
+together, these results suggest that offset time does not modulate
 mispronunciation sensitivity. There is no relationship between offset
@@
 have systematic preferences for the target or distractor (greater
-interest in a cat compared to cup) which may drive PTL scores in the
+interest in a cat compared to a cup) which may drive PTL scores in the
 post-naming phase. As described in the Data Analysis sub-section of the
@@
 Another dependent variable, which was used in 69 experimental
-conditions, directly compared compared the post- and pre-naming PTL
-scores with one another. This requires two values, one for the
-pre-naming phase and one for the post-naming phase. A greater post
-compared to pre-naming phase PTL indicates that increased their target
-looks after hearing the naming label. We will refer to this dependent
-variable as Pre vs.~Post. Finally, the remaining 53 experimental
-conditions compared the post-naming PTL score with a chance value of
-50\%. Here, the infants' pre-naming phase preferences are not considered
-and instead target fixations are evaluated based on the likelihood to
-fixate one of two pictures. We will refer to this dependent variable as
-Post.
+conditions, directly compared the post- and pre-naming PTL scores with
+one another. This requires two values, one for the pre-naming phase and
+one for the post-naming phase. A greater post compared to pre-naming
+phase PTL indicates that increased their target looks after hearing the
+naming label. We will refer to this dependent variable as Pre vs.~Post.
+Finally, the remaining 53 experimental conditions compared the
+post-naming PTL score with a chance value of 50\%. Here, the infants'
+pre-naming phase preferences are not considered and instead target
+fixations are evaluated based on the likelihood to fixate one of two
+pictures. We will refer to this dependent variable as Post.
+
+{[}Christina{]} Did I ask the following already: Do we know whether
+subtrations were on the trial level? Pre vs post is a bit differnt
+because it loses the individual bias accommodation and the correlation
+between pre and post on the participant / item level. {[}Katie{]} You
+did. I'll put here my answer from before: From working with Nivi, we did
+it participants x condition or participants x trial (but mostly the
+former). But, this is not something we reported in papers. I don't think
+I read it at all when putting together the dataset for this either.
 
@@
 contrast, does not consider pre-naming preferences. To our knowledge,
-there is no theory or evidence to drive choice of dependent variable,
-which may explain the wide variation in dependent variable reported in
-the papers included in this meta-analysis. We next explored whether the
-type of dependent variable calculated influenced sensitivity to
+there is no theory or evidence that explicitly drives choice of
+dependent variable in analysis of mispronunciation sensitivity, which
+may explain the wide variation in dependent variable reported in the
+papers included in this meta-analysis. We next explored whether the type
+of dependent variable calculated influenced sensitivity to
 mispronunciations. Considering that the dependent variable Post differs
@@
 We first assessed whether the choice of dependent variable had an impact
-on the size of mispronunciation sensitivity. First, we calculated the
-meta-analytic effect for object identification in response to
-mispronounced target words/images, including dependent variable as a
-moderator. The moderator test was significant QM(1) = 215.761,
-\emph{p}\textless{} .001. The estimates for both the Pre vs.~Post
-(\(\beta\) = -0.369, SE = 0.143, 95\% CI{[}-0.65, -0.088{]}, \emph{p}=
-0.01) and Difference Score (\(\beta\) = -0.392, SE = 0.135, 95\%
-CI{[}-0.656, -0.128{]}, \emph{p}= 0.004) dependent variables were
-significantly smaller than that of the Post dependent variable. This
-suggests that reported looks to the target upon hearing a
-mispronunciation were greatest when the dependent variable was Post. We
-next assessed whether he dependent variable was related to
-mispronunciation sensitivity. We merged the two datasets and included
-condition (correct pronunciation, mispronunciation) as an additional
-moderator. The moderator test was significant, QM(1) = 215.761,
-\emph{p}\textless{} .001. The estimate for the interaction between Pre
-vs.~Post and condition was significantly smaller than that of the Post
-dependent variable (\(\beta\) = -0.392, SE = 0.101, 95\% CI{[}-0.59,
--0.194{]}, \emph{p}\textless{} .001), but the difference between the
-Difference Score and Post in the interaction with condition was small
-and not significant (\(\beta\) = -0.01, SE = 0.098, 95\% CI{[}-0.203,
-0.183{]}, \emph{p}= 0.916). This relationship is plotted in Figure 4a.
-The results suggest that dependent variable calculated significantly
-impacted the size fo the mispronunciation sensitivity effect, such that
-Post. vs.~Pre showed a smaller mispronunciation sensitivity effect than
-Post, but no difference between the Difference Score and Post.
+on the size of mispronunciation sensitivity. When we included both
+condition and dependent variable as moderators, the moderator test was
+significant QM(5) = 259.817, \emph{p}\textless{} .001. The estimate for
+the interaction between Pre vs.~Post and condition was significantly
+smaller than that of the Post dependent variable (\(\beta\) = -0.392, SE
+= 0.101, 95\% CI{[}-0.59, -0.194{]}, \emph{p}\textless{} .001), but the
+difference between the Difference Score and Post in the interaction with
+condition was small and not significant (\(\beta\) = -0.01, SE = 0.098,
+95\% CI{[}-0.203, 0.183{]}, \emph{p}= 0.916). This relationship is
+plotted in Figure 4a. The results suggest that dependent variable
+calculated significantly impacted the size fo the mispronunciation
+sensitivity effect, such that Post. vs.~Pre showed a smaller
+mispronunciation sensitivity effect than Post, but no difference between
+the Difference Score and Post.
 
 We next examined whether the type of dependent variable calculated
-modulated the development of mispronunciation sensitivity. For object
-recognition in response to a mispronunciation, including age as a
-moderator resulted in a moderator test that was significant QM(1) =
-215.761, \emph{p}\textless{} .001, but the estimates for the interaction
-between Pre vs.~Post and age (\(\beta\) = -0.011, SE = 0.037, 95\%
-CI{[}-0.083, 0.061{]}, \emph{p}= 0.766) as well as Difference Score and
-age (\(\beta\) = -0.021, SE = 0.033, 95\% CI{[}-0.085, 0.043{]},
-\emph{p}= 0.516) were not different from that of the Post dependent
-variable. This suggests that upon hearing a mispronunciation, infant
-measured looks to the target image were similar, regardless of infant
-age or type of dependent variable. We next assessed whether the
-relationship between dependent variable and mispronunciation sensitivity
-was modulated by age. We merged the two datasets and included condition
-(correct pronunciation, mispronunciation) as well as age as additional
-moderators. The moderator test was significant QM(1) = 215.761,
-\emph{p}\textless{} .001. The estimate for the interaction between Pre
-vs.~Post, condition, and age was significantly smaller than that of the
-Post dependent variable (\(\beta\) = -0.089, SE = 0.03, 95\%
-CI{[}-0.148, -0.03{]}, \emph{p}= 0.003), but the difference between the
-Difference Score and Post in the interaction with condition and age was
-small and not significant (\(\beta\) = -0.036, SE = 0.027, 95\%
-CI{[}-0.088, 0.016{]}, \emph{p}= 0.174). This relationship is plotted in
-Figure 4b. When the dependent variable was Pre vs.~Post,
-mispronunciation sensitivity decreased with infant development, while in
+modulated the development of mispronunciation sensitivity. When age was
+included as an additional moderator, the moderator test was significant
+QM(11) = 273.585, \emph{p}\textless{} .001. The estimate for the
+interaction between Pre vs.~Post, condition, and age was significantly
+smaller than that of the Post dependent variable (\(\beta\) = -0.089, SE
+= 0.03, 95\% CI{[}-0.148, -0.03{]}, \emph{p}= 0.003), but the difference
+between the Difference Score and Post in the interaction with condition
+and age was small and not significant (\(\beta\) = -0.036, SE = 0.027,
+95\% CI{[}-0.088, 0.016{]}, \emph{p}= 0.174). This relationship is
+plotted in Figure 4b. When the dependent variable was Pre vs.~Post,
+mispronunciation sensitivity decreased with infant age, while in
 comparison, when the dependent variable was Post, mispronunciation
-sensitivity increased with infant development. There was no difference
-in mispronunciation sensitivity change with infant development between
-the Post and Difference Score dependent variables.
+sensitivity increased with infant age. There was no difference in
+mispronunciation sensitivity change with infant development between the
+Post and Difference Score dependent variables.
 
@@
 
-\subsection{Controlling for researcher
-choice}\label{controlling-for-researcher-choice}
+\subsection{Controlling for analysis
+choices}\label{controlling-for-analysis-choices}
 
@@
 \item
-  Post-naming phase size and dependent variable impact misp sensitivity
-  development
+  Post-naming time window size and dependent variable impact misp
+  sensitivity development
 \item

### 2018-12-03 Paper_Analyses.Rmd
Comments, now in rmd

@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_word
 ---
 
-```{r Setup, echo = FALSE, warning=FALSE, warning = FALSE, error = FALSE, message = FALSE}
+```{r Setup, echo = FALSE, warning=FALSE, error = FALSE, message = FALSE, tidy = TRUE}
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)
@@
 
-full_estimate <- function(x) paste0(" = ", r2(x$estimate), ", SE = ", r2(x$se), ", 95% CI[",  r2(x$ci.lb), ", ", r2(x$ci.ub),"], *p*", psig(x$pval))
+full_estimate <- function(x) paste0(" = ", r2(x$estimate), ", SE = ", r2(x$se), ", 95% CI[",  r2(x$ci.lb), ", ", r2(x$ci.ub),"], *p* ", psig(x$pval))
 
 # moderator test
-mod_test <- function(x) paste0("QM(", r2(x$m), ") = ", r2(x$QM), ", *p*", psig(x$QMp))
+mod_test <- function(x) paste0("QM(", r2(x$m), ") = ", r2(x$QM), ", *p* ", psig(x$QMp))
 
@@
 
-db_ET <- db_ET %>%
-  mutate(age.C = (mean_age_1-mean(mean_age_1, na.rm=TRUE))/30.44) %>%
-  filter(mean_age_months < 31)
+noES <- db_ET %>%
+  filter(is.na(d_calc)) %>%
+  group_by(short_cite) %>%
+  summarise(n_records = n())
 
@@
 
+descriptive_dat <- db_ET
+
+db_ET <- db_ET %>%
+  filter(!is.na(d_calc))
+
+db_ET <- db_ET %>%
+  mutate(age.C = (mean_age_1-mean(mean_age_1, na.rm=TRUE))/30.44) %>%
+  filter(mean_age_months < 31)
+
 #Split into correct and MP database
@@
 
-#remove outliers, for now we have none, though
+#remove outliers
 db_ET_MP$nooutlier = ifelse(db_ET_MP$g_calc > mean(db_ET_MP$g_calc, na.rm = TRUE) + 3*sd(db_ET_MP$g_calc, na.rm = TRUE) 
                          | db_ET_MP$g_calc < mean(db_ET_MP$g_calc, na.rm = TRUE) - 3*sd(db_ET_MP$g_calc, na.rm = TRUE),FALSE, TRUE)
+
+n_outlier_MP = sum(db_ET_MP$nooutlier==FALSE)
+
 db_ET_MP = db_ET_MP[db_ET_MP$nooutlier,]
+
+# 3 outliers
 
@@
                          | db_ET_correct$g_calc < mean(db_ET_correct$g_calc, na.rm = TRUE) - 3*sd(db_ET_correct$g_calc, na.rm = TRUE),FALSE, TRUE)
+
+n_outlier_correct = sum(db_ET_correct$nooutlier==FALSE)
+
 db_ET_correct = db_ET_correct[db_ET_correct$nooutlier,]
+
+# 2 outliers
 
@@
     panel.border=element_blank(),
-    axis.line=element_line(),
-    text=element_text(family='Times', size=25))
+    axis.line=element_line()#,
+    #text=element_text(family='Times', size=25)
+    )
 
@@
 ```
+
+[Christina: Big change: I just realized that we also need to report where we could not compute effect sizes, added this info. ]
 
@@
 I took away "which are both present in the mature language processing system".]
+[Christina: I like principles. This is then good for me.]
 
@@
 [Katie: since we actually don't have theoretical framework support for the no-change theory, I've changed around the sentence below to explicitly say that only 2 of the 3 are predicted by theoretical accounts.]
+[Christina: Works for me. I am just thinking what the Vihman-style framework says. do you happen to know? I think the Renner thesis discusses it.]
 
@@
 
-dat_st <- dat
+dat_st <- descriptive_dat
 
@@
       summarise(Publication = unique(publication_status),
-        Ages_Tested_months = paste(unique(trunc(mean_age_1/30.34)), collapse=', '),
+        Ages_Tested_months = paste(unique(trunc(mean_age_1/30.44)), collapse=', '),
                 Vocabulary = ifelse(all(is.na(r_comprehension)) & all(is.na(r_production)), "None",
@@
 ```
+
 [Christina] I've shortened the labels and wanted to try out apa_table
@@
 [Katie] We have it currently set at less than 31 months, not 36, so I've changed below.
+
+[Christina: OK to age. Apa table works for me, weird. It should come with papaja. Might be related to the issues you have wrt to citations? ]
+[Christina: Suggestions re: table. Add N effect sizes? you cna do it with summarise(number_ES = n()) I think]
+[Christina: Btw, I think I've corrected short_cite in the online spreadsheet, so the table should be fine now.]
 
@@
 This search was conducted on 22 September, 2017 and yielded 288 results.
-We screened the resulting 398 items, removing 99 duplicate items.
-We screened remaining 299 items for their title and abstract to determine whether it met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech.
-The final sample (n = *`r length(unique(dat$short_cite))`*) consisted of `r with(dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(dat, n_distinct(short_cite[publication_status == "dissertation"]))` thesis, and `r with(dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports.
+We removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech.
+The final sample (n = *`r length(unique(descriptive_dat$short_cite))`*) consisted of `r with(descriptive_dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "dissertation"]))` thesis, and `r with(descriptive_dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports.
 We will refer to these items collectively as papers.
@@
 
-The `r length(unique(dat$short_cite))` papers we identified as relevant were then coded with as much consistently reported detail as possible (Tsuji, Bergmann, & Cristia, 2014; Bergmann et al., 2018).
+The `r length(unique(descriptive_dat$short_cite))` papers we identified as relevant were then coded with as much consistently reported detail as possible (Tsuji, Bergmann, & Cristia, 2014; Bergmann et al., 2018).
 For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results.
@@
 The fact that the same infants contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section).
-We will call each row a record; in total there were `r nrow(dat)` records in our data.
+We will call each row a record; in total there were `r nrow(descriptive_dat)` records in our data.
 
@@
 
-es_info <- dat %>%
+es_info <- descriptive_dat %>%
+  filter(!is.na(d_calc)) %>%
   group_by(es_method) %>%
@@
 
-corr_info <- dat %>%
+corr_info <- descriptive_dat %>%
+  filter(!is.na(d_calc)) %>%
   group_by(imputed_corr) %>%
@@
 ```
-[Christina] I think it would be useful to say how many records, not papers, report each measure. e.g. "(n = xxx records from yyy papers)". Would that be ok?
-[Katie] Totally! I think that gives a good bit of information. Good suggestion!
-
-Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement.
-PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images.
-Across papers the baseline comparison varied; we used the baseline reported by the authors of each paper.
-Most papers (*n* = `r with(comparison_info, count[within_measure == "pre_post_naming_effect"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post_naming_effect"])` papers) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase and report a difference score.
-
-[Christina] Katie, do you know whether the difference is computed based on items, participants, trials...? Is there consistency?
-[Katie] From working with Nivi, we did it participants x condition or participants x trial (but mostly the former).
-But, this is not something we reported in papers.
-I don't think I read it at all when putting together the dataset for this either.
-
-Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(comparison_info, count[within_measure == "pre_post"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post"])` papers), thus reporting two variables, or compared post-naming PTL with a chance level of 50%, (*n* = `r with(comparison_info, count[within_measure == "post"])` records from `r with(comparison_info, n_unique[within_measure == "post"])` papers).
-For all these comparisons, positive values (either as reported or after subtraction of chance level or a pre-naming PTL) indicate target looks towards the target object after hearing the label, i.e.
-a recognition effect.
-Standardized effect sizes based on mean differences, as calculated here, preserve the sign.
-Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more looks to the target.
+
+[Christina: I needed to move this around because we first need to say that we could not compute some effect sizes and removed outlierts.]
 
@@
 How does that shake out for number of records?
-
-We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, sum(count[es_method == "group_means_one" | es_method == "group_means_two"]))` records from `r with(es_info, sum(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))` papers) or using reported t-values (*n* = `r with(es_info, sum(count[es_method == "t_one" | es_method == "t_two"]))` records from `r with(es_info, sum(n_unique[es_method == "t_one" | es_method == "t_two"]))` papers).
+[Christina: No clue what the -1 was, sorry.]
+
+We calculate Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, sum(count[es_method == "group_means_one" | es_method == "group_means_two"]))` records from `r with(es_info, sum(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))` papers) or using reported t-values (*n* = `r with(es_info, sum(count[es_method == "t_one" | es_method == "t_two"]))` records from `r with(es_info, sum(n_unique[es_method == "t_one" | es_method == "t_two"]))` papers).
 Two papers reported raw means and standard deviations for some experimental conditions and just t-values for the remaining experimental conditions (Swingley, 2016; Altvater-Mackensen et al., 2014).
-Raw means and standard deviations were extracted from figures for `r with(dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers.
+Raw means and standard deviations were extracted from figures for `r with(descriptive_dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers.
 In a within-participation design, when two means are compared (i.e.
 looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values.
-Upon request we were provided with correlation values for one paper (Altvater-Mackensen, 2010); we were able to compute correlations using means, standard deviations, and t-values for *n* = `r with(corr_info, n_unique[imputed_corr == "no"]) - 1` (following Csibra, et al.
+Upon request we were provided with correlation values for one paper (Altvater-Mackensen, 2010); we were able to compute correlations using means, standard deviations, and t-values for *n* = `r with(corr_info, n_unique[imputed_corr == "no"])` (following Csibra, et al.
 2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, 2018).
 Correlations were imputed for the remaining papers (see Black & Bergmann, 2017, for the same procedure).
-We could compute a total of `r sum(dat$is_mp == 0)` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)` for mispronunciations.
+For two papers, we could not derive any effect size (Ballem & Plunkett, Renner), and for a third paper, we do not have sufficient information in one record to compute effect sizes (Skoruppa).
+We compute a total of `r sum(dat$is_mp == 0)+n_outlier_correct` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)+n_outlier_MP` for mispronunciations.
+Following standard meta-analytic practice, we remove outliers, i.e.
+effect sizes more than 3 standard deviations from the respective mean effect size.
+This leads to the exclusion of `r n_outlier_correct` records for correct pronunciations and `r n_outlier_MP` records for mispronunciations.
 
@@
 This means we model as random effect that effect sizes from the same paper share are based on more similar studies than those across papers and that nested therein effects can stem from the same infants.
+
+[Christina: In the above 2 paragraphs I got confused, should it be present or past. I think it switched in the las tparagraph so I started to adapt, but I think it would be best for you to decide. ]
+
+Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement.
+PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images.
+Across papers the baseline comparison varied; we used the baseline reported by the authors of each paper.
+Most papers (*n* = `r with(comparison_info, count[within_measure == "pre_post_naming_effect"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post_naming_effect"])` papers) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase and report a difference score.
+
+Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(comparison_info, count[within_measure == "pre_post"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post"])` papers), thus reporting two variables, or compared post-naming PTL with a chance level of 50%, (*n* = `r with(comparison_info, count[within_measure == "post"])` records from `r with(comparison_info, n_unique[within_measure == "post"])` papers).
+For all these comparisons, positive values (either as reported or after subtraction of chance level or a pre-naming PTL) indicate target looks towards the target object after hearing the label, i.e.
+a recognition effect.
+Standardized effect sizes based on mean differences, as calculated here, preserve the sign.
+Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more looks to the target.
 
@@
 Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app (v4.0, p-curve.com; @pcurve).
-This p-curve tests for evidential value by examining whether the p-values follow the expected distribution of a right skew in case the alternative hypothesis is true, versus a flat distribution that speaks for no effect being present in the population and all significant effect being spurious.
+This p-curve tests for evidential value by examining whether the p-values follow the expected distribution of a right skew in case the alternative hypothesis is true, versus a flat distribution that speaks for no effect being present in the population and all observed significant effects being spurious.
 Responses to correctly pronounced and mispronounced labels are predicted to show different patterns of looking behavior.
-In other words, there is an expectation that infants should look to the target when hearing a correct pronunciation, but some studies may report either significant looks or no  significant looks to the target when hearing a mispronounced label
-
-[Christina] Katie, is that right, can you add a citation? 
-[Katie] I've rewritten it a bit to be explicit about the difference between expectations for correct and mispronounced labels.
-I'm not sure what to cite though.
-The papers that find significant looks or no significant looks?
-That's basically the meta-analysis.
-Or some citation that talks about what looking to the target upon hearing a mispronunciation means in comparison to what target looks being decreased for mispronunciations relative to correct pronunciations means?
-I'm not so sure whether anyone has actually talked about that difference before, not sure what to cite.
-
-(i.e. there might be no effect present in the population, see e.g., ); as a result, we conduct these two analyses to assess publication bias separately for both conditions.
+In other words, there is an expectation that infants should look to the target when hearing a correct pronunciation, but studies vary in their report of significant looks to the target when hearing a mispronounced label (i.e.
+there might be no effect present in the population, see e.g., ); as a result, we conduct these two analyses to assess publication bias separately for both conditions.
 
@@
 
+[Chrisitna: If you add prisma, then this is figure 2]
+
 Figure 1 shows the funnel plots for both correct pronunciations and mispronunciations (code adapted from Sakaluk, 2016).
@@
 
-We should also point out that funnel plot asymmetry can be caused by multiple factors beside publication bias.
-The funnel plot asymmetry may also reflect heterogeneity in the data.
+We should also point out that funnel plot asymmetry can be caused by multiple factors beside publication bias, such as heterogeneity in the data.
 There are various possible sources of heterogeneity, which our subsequent moderator analyses will begin to address.
-Nonetheless, we will remain cautious in our interpretation of our findings and hope that an open dataset that can be expanded by the community will attract previously unpublished null results so we can better understand infants' developing mispronunciation sensitivity.
+Nonetheless, we will remain cautious in our interpretation of our findings and hope that an open dataset which can be expanded by the community will attract previously unpublished null results so we can better understand infants' developing mispronunciation sensitivity.
 
@@
 Our analysis of funnel plot asymmetry, however, found evidence for publication bias, which might lead to an overestimated effect sizes as smaller, non-significant results might not be published despite the fact that they should occur regularly even in well-powered studies.
-Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` which is substantially above zero suggests that this result should be robust even when correcting for publication bias.
+Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)`, which is substantially above zero, together suggest that this result is somewhat robust.
 In other words, we are confident that the true population mean lies above zero for object recognition of correctly pronounced words.
@@
 But, as the p-curve indicated evidential value, we are confident in the overall patterns, namely that infants fixate the target even after hearing a mispronounced label.
-
-[Christina] I am not sure about the placement of this paragraph because the next section cannot explain this heterogeneity, so maybe we should move it down to the beginning of the age part?
-[Katie] I think that makes sense, moving it!
 
@@
 To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44 for Figure 2).
-[Christina] What about the whole months thing?
-[Katie] We had an explanation in the methods section for this, I've now added it again here.
 
@@
 
-[Christina] OK there is a mismatch between what you write and the numbers, can you verify?
-[Katie] Good catch.
-For some reason, it was just copying over the moderator test from mispronunciation sensitivity, even though I was calling for the age moderator analysis.
-There is no significant moderator test, but it was just pasting the same one again and again.
-I've fixed my code, so it should be correct now!
-
 ```{r MPEffect_age}
@@
 The moderator test was significant (`r mod_test(rma_MPeffect_age)`).
-The interaction between age and mispronunciation sensitivity, however, was not significant ($\beta$ `r full_estimate(sum_eff)`), pointing to the moderator test being driven by the difference between conditions.
+The interaction between age and mispronunciation sensitivity, however, was not significant ($\beta$ `r full_estimate(sum_eff)`); the moderator test was mainly driven by the difference between conditions.
 The small estimate, as well as inspection of Figure 2 suggests that as infants age, their mispronunciation sensitivity remains the same.
@@
 ## (Insert Figure 2 about here)
+
+[Christina] Can you try and align the axes for both plots?
 
@@
 dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
+dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
 
@@
   ggtitle("b. Mispronunciation Sensitivity")+
-  geom_point(aes(size = n_1/2),show.legend=FALSE, alpha = .3) + 
+  geom_point(aes(size = weight),show.legend=FALSE, alpha = .3) + 
   geom_line(y= 0, linetype="dotted") + 
@@
   xlab("Age in months") + 
-  ylab("Mispronunciation Sensitivity")
+  ylab("Hedges' g")
 
@@
 There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment; Kidd citation), and we therefore planned to analyze these two types of vocabulary measurement separately.
-However, only `r with(vi1, papers[has_vocab == "production"])` papers reported correlations with productive vocabulary scores, limiting the conclusions that can be drawn.
+However, because only `r with(vi1, papers[has_vocab == "production"])` papers reported correlations with productive vocabulary scores, only limited conclusions that can be drawn.
 In our vocabulary analysis, we therefore focus exclusively on the relationship between comprehension and mispronunciation sensitivity.
 
-[Christina] Removed the previous comment chaos.
-So can you not only list papers but also n conditions above? With just 1 paper for production, I wouldn't analyze it to be honest. it's just not enough data. 
+[Christina] So can you not only list papers but also n conditions above? With just 1 paper for production, I wouldn't analyze it to be honest. it's just not enough data. 
 I also liked your comments about the time line of this whole thing, can you extract the years of papers which report this?
@@
 
+[Christina] Here is the Kidd paper: https://pure.mpg.de/rest/items/item_2602612_8/component/file_3001229/content Not sur eif it helps.
+
 ```{r ComprehensionMeta_correct}
@@
 As a result, we can not draw firm conclusions about the relationship between comprehension scores and object recognition in response to correct pronunciations.
+
+[Christina] It's significant now!
 
@@
 But, the median is only 500 ms less, so we could use that too (9 experimental conditions).
+[Christina] Oh I get it, maybe if you add that? Whatever you prefer. I was just curious.
 
@@
 [Katie] I don't have a strong opinion on this. If you think it would be better, then I can change it.
+[Christina] Nah, your call.
 
@@
 This variation is most pronounced, and even significant, for the time window that is being analyzed after the target label has been heard.
-
-[Christina] The canfield & haith paper is for visual stimuli, right?
-So add that before "stimulus".
-And then add to the next sentence that the longer latnecies are because ther eis addiitonal language processing required which EEg shows in adults to take X ms (400 for N400?).
-[Katie] I agree with the reasoning, but I don't think referring to adult ERP literature is the way to go. I've rewritten these sentences to be more faithful to the misp sensitivity literature.
-
-[Christina] Can you add info how many papers did not report the analyzed variables? Across this whole section, I mean. 
-[Katie] All papers reported the actual post-naming phase length and the size of the post-naming time window analyzed.
 
@@
 ```
-
-[Christina] I think it's a bit inconsistent whether it's post naming phase or window, how about window?
-Phase sounds wrong to me.
-or analysis window?
-I also find phase size odd, and again prefer window (window size).
-Your call though.
-[Katie] I agree and I've updated it to refer to window size when talking about the analyzed portion and to  phase when refering to it as the entire actual presentation time.
 
@@
     #facet_grid(.~post_size)+
-  geom_point(aes(size = n_1),show.legend=FALSE) +
+  geom_point(aes(size = weight),show.legend=FALSE) +
   labs(title="b")+
@@
 ```
-
-[Christina] Generally, it might be easier to kick out all object recognition analyses (what do they tell us?) and start out that we only analyze MP sensitivity, i.e.
-consider the whole dataset and always include condition as moderator.
-[Katie] Agreed! I've gotten rid of all of the object recognition analyses and added an explanation at the beginning of the Exploratory Analysis section.
 
@@
 I don't think I read it at all when putting together the dataset for this either.
+[Christina] Mention in the discussion that we don't know this and it might be important to establish standard analysis pipelines for MP studies and that we need open data and code? ;)
 

### 2018-12-03 scripts/calculateES.R
Updated ES calc
Outlier removal no longer needed here

@@ -88,7 +88,7 @@ for(line in 1:length(db_ET$n_1)){
 
 #### Remove missing values ####
 
-db_ET = db_ET[!is.na(db_ET$d_calc),]
+
 
 
 #### Compute Hedge's g based on Cohen's d ####
@@ -105,13 +105,4 @@ db_ET$weights_g <-  1/(db_ET$g_var_calc)^2
 db_ET$weights_d <-  1/(db_ET$d_var_calc)^2
 
 
-#### Outlier removal ####
 
-
-# Following InWordD/standard practice, we will remove effect sizes more than 3 SD away from the median effect (in both positive and negative directions)
-
-db_ET$nooutlier = ifelse(db_ET$g_calc > mean(db_ET$g_calc, na.rm = TRUE) + 3*sd(db_ET$g_calc, na.rm = TRUE) 
-                         | db_ET$g_calc < mean(db_ET$g_calc, na.rm = TRUE) - 3*sd(db_ET$g_calc, na.rm = TRUE),FALSE, TRUE)
-
-#db_ET = db_ET[db_ET$nooutlier,]
-#02.02. 3 outlier, not removed because it might be that it's correct vs MP

### 2018-12-03 Paper_Analyses.Rmd
addressed comments by Christina; started on General Discussion

@@
 classoption       : "man"
-output            : papaja::apa6_word
+output            : papaja::apa6_pdf
+
+header-includes:
+  - \usepackage{setspace}
+  - \AtBeginEnvironment{tabular}{\singlespacing}
+  - \AtBeginEnvironment{lltable}{\singlespacing}
+  - \AtBeginEnvironment{tablenotes}{\doublespacing}
+  - \captionsetup[table]{font={stretch=1.5}}
+  - \captionsetup[figure]{font={stretch=1.5}}
 ---
@@
 
-[Christina: changed concepts to mechanisms in the next paragraph, because I want to refer to what they represent, but I am not sure it's the right term]
-[Katie: Karen (Mulak) talks about these terms as concepts.
-Mechanisms to me means some sort of internalization, that they would have had this ability all along and just need to apply it.
-It could be that we fundamentally disagree on this, but to me these are things that infants discover.
-Later on we use principles.
-What about "principles that infants must discover"...
-"in order to form adult-like word representations"?
-I took away "which are both present in the mature language processing system".]
-[Christina: I like principles. This is then good for me.]
-
   The study of Swingley and Aslin (2000) as well as subsequent studies examining mispronunciation sensitivity address two complementary principles that infants must discover in early phonological development in order to form adult-like word representations: *phonological constancy* and *phonological distinctiveness*.
@@
 [Christina: Works for me. I am just thinking what the Vihman-style framework says. do you happen to know? I think the Renner thesis discusses it.]
+[Katie: I wasn't really familiar with the Vihman framework, but looking at Renner's thesis and some of the original papers suggests that it really is about production, not perception.]
 
@@
 Since the present paper was written with embedded analysis scripts in R [@R, @RMarkdown, @papaja], it is always possible to re-analyze an updated dataset.
-In addition, we follow the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials (Moher, Liberati, Tetzlaff, Altman & PRISMAGroup, 2009).
-Figure X plots our PRISMA flowchart illustrating the paper selection procedure.
-
-![Figure X. PRISMA Flowchart.] (figures/PRISMA_MA_Mispronunciation.png)
+In addition, we followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials (Moher, Liberati, Tetzlaff, Altman & PRISMAGroup, 2009).
+Figure 1 plots our PRISMA flowchart illustrating the paper selection procedure.
+
+## (Insert Figure 2 about here)
+
+```{r PRISMA_image, echo= FALSE}
+
+knitr::include_graphics("figures/PRISMA_MA_Mispronunciation.png")
+
+# ! [Figure X. PRISMA Flowchart.] (Users/KatesOld/Documents/R_Git/figures/PRISMA_MA_Mispronunciation.png)
+
+```
 
@@
                                 ifelse(!all(is.na(r_comprehension)) & !all(is.na(r_production)), "Comp/Prod",
-                                       ifelse(!all(is.na(r_comprehension)) & all(is.na(r_production)), "Comp", "Prod"))))
-
-#kable(Sum_table, col.names = c("Paper", "Publication format", "Age", "Vocabulary"))
-apa_table(Sum_table, col.names = c("Paper", "Publication format", "Age", "Vocabulary"), caption = "Summary of all studies.")
-
-```
-
-[Christina] I've shortened the labels and wanted to try out apa_table
-[Katie] I like the idea, but does it work for you? It doesn't work for me...
-[Katie] We have it currently set at less than 31 months, not 36, so I've changed below.
-
-[Christina: OK to age. Apa table works for me, weird. It should come with papaja. Might be related to the issues you have wrt to citations? ]
-[Christina: Suggestions re: table. Add N effect sizes? you cna do it with summarise(number_ES = n()) I think]
-[Christina: Btw, I think I've corrected short_cite in the online spreadsheet, so the table should be fine now.]
+                                       ifelse(!all(is.na(r_comprehension)) & all(is.na(r_production)), "Comp", "Prod"))),
+        Effect_sizes_n = n())
+
+#kable(Sum_table, col.names = c("Paper", "Publication format", "Age", "Vocabulary", "N Effect Sizes"))
+apa_table(Sum_table, col.names = c("Paper", "Publication format", "Age", "Vocabulary", "N Effect Sizes"), caption = "Summary of all studies.", landscape = TRUE)
+
+```
 
@@
 We will refer to these items collectively as papers.
-Table 1 (Summary Table) provides an overview of all papers included in the present meta-analysis.
+Table 1 provides an overview of all papers included in the present meta-analysis.
+
+## (Insert Table 1 about here)
 
@@
 For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results.
-For the analyses presented in this section, we focus on the following characteristics:
+For the planned analyses to evaluate the development of mispronunciation sensitivity, we focus on the following characteristics:
 
@@
 
-We report effect sizes for infants' looks to target pictures after hearing a correctly pronounced or a mispronounced label (object identification) as well as the difference between effect sizes for correct and mispronounced trials (i.e.
+Effect sizes are reported for infants' looks to target pictures after hearing a correctly pronounced or a mispronounced label (object identification) as well as the difference between effect sizes for correct and mispronounced trials (i.e.
 mispronunciation sensitivity).
-The effect size we report in the present paper are based on comparison of means, standardized by their variance.
+The effect size reported in the present paper is based on comparison of means, standardized by their variance.
 The most well-known effect size from this group is Cohen's *d* [@cohen].
-To correct for the small sample sizes common in infant research, however, we use as a dependent variable Hedges' *g* instead of Cohen's *d* (Hedges, 1981; Morris, 2000).
-
-[Christina] These numbers seem wrong! Again, how about (xx effect sizes from yy papers)?
-[Katie] Well, they are kind of wrong :) Two papers report both for different experimental conditions.
-I've given the explanation now, not sure if that is good enough, but I'm really not sure how to say it a different way.
+To correct for the small sample sizes common in infant research, however, we used as a dependent variable Hedges' *g* instead of Cohen's *d* (Hedges, 1981; Morris, 2000).
+
 [Katie] Do you want number of records and papers for the imputed correlations as well?
@@
 
-We calculate Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, sum(count[es_method == "group_means_one" | es_method == "group_means_two"]))` records from `r with(es_info, sum(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))` papers) or using reported t-values (*n* = `r with(es_info, sum(count[es_method == "t_one" | es_method == "t_two"]))` records from `r with(es_info, sum(n_unique[es_method == "t_one" | es_method == "t_two"]))` papers).
+We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, sum(count[es_method == "group_means_one" | es_method == "group_means_two"]))` records from `r with(es_info, sum(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))` papers) or using reported t-values (*n* = `r with(es_info, sum(count[es_method == "t_one" | es_method == "t_two"]))` records from `r with(es_info, sum(n_unique[es_method == "t_one" | es_method == "t_two"]))` papers).
 Two papers reported raw means and standard deviations for some experimental conditions and just t-values for the remaining experimental conditions (Swingley, 2016; Altvater-Mackensen et al., 2014).
@@
 [Christina: In the above 2 paragraphs I got confused, should it be present or past. I think it switched in the las tparagraph so I started to adapt, but I think it would be best for you to decide. ]
+[Katie: Good catch. I've gone through the Methods section and changed everything to past, per APA guidelines.]
 
@@
 As a result, significant results tend to be over-reported and thus might be over-represented in our meta-analyses (see Ferguson & Heene, 2012).
-To examine whether this is also the case in the mispronunciation sensitivity literature, which would bias the data analyzed in this meta-analysis, we conduct two tests.
-We first examine whether effect sizes are distributed as expected based on sampling error using the rank correlation test of funnel plot asymmetry with the R [@R] package metafor [@metafor].
-Effect sizes with low variance are expected to fall closer to the estimated mean, while effect sizes with high variance should show an increased, evenly-distributed spread around the estimated mean.
+To examine whether this is also the case in the mispronunciation sensitivity literature, which would bias the data analyzed in this meta-analysis, we conducted two tests.
+We first examined whether effect sizes are distributed as expected based on sampling error using the rank correlation test of funnel plot asymmetry with the R [@R] package metafor [@metafor].
+Effect sizes with low variance were expected to fall closer to the estimated mean, while effect sizes with high variance should show an increased, evenly-distributed spread around the estimated mean.
 Publication bias would lead to an uneven spread.
@@
 This p-curve tests for evidential value by examining whether the p-values follow the expected distribution of a right skew in case the alternative hypothesis is true, versus a flat distribution that speaks for no effect being present in the population and all observed significant effects being spurious.
-Responses to correctly pronounced and mispronounced labels are predicted to show different patterns of looking behavior.
+Responses to correctly pronounced and mispronounced labels were predicted to show different patterns of looking behavior.
 In other words, there is an expectation that infants should look to the target when hearing a correct pronunciation, but studies vary in their report of significant looks to the target when hearing a mispronounced label (i.e.
-there might be no effect present in the population, see e.g., ); as a result, we conduct these two analyses to assess publication bias separately for both conditions.
+there might be no effect present in the population, see e.g., ); as a result, we conducted these two analyses to assess publication bias separately for both conditions.
 
@@
 The models reported here are hierarchical random-effects models (infant groups nested within papers) of variance-weighted effect sizes, which we computed with the R [@R] package metafor [@metafor].
-To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we introduce age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44) as a moderator to our main model.
-For a subsequent exploratory investigations of experimental characteristics, we introduce each characteristic as a moderator (more detail below).
+To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we introduced age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44) as a moderator to our main model.
+For a subsequent exploratory investigations of experimental characteristics, we introduced each characteristic as a moderator (more detail below).
 
@@
 
-[Chrisitna: If you add prisma, then this is figure 2]
-
-Figure 1 shows the funnel plots for both correct pronunciations and mispronunciations (code adapted from Sakaluk, 2016).
+Figure 2 shows the funnel plots for both correct pronunciations and mispronunciations (code adapted from Sakaluk, 2016).
 Funnel plot assymmetry was significant for both correct pronunciations (Kendall's $\tau$ = `r r2(rmac$tau)`, *p* `r psig(rmac$pval)`) and mispronunciations (Kendall's $\tau$ = `r r2(rmam$tau)`, *p* `r psig(rmam$pval)`).
@@
 
-## (Insert Figure 1 about here)
+## (Insert Figure 2 about here)
 
@@
 
-  jpeg(filename = "figures/Figure_1_Funnel_Plots_Object_Identification.jpg", 
+  jpeg(filename = "figures/Figure_2_Funnel_Plots_Object_Identification.jpg", 
        width = 600, height = 400, units = "px")
@@
 
-To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44 for Figure 2).
+To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44 for Figure 3).
 
@@
 The lack of a significant modulation together with the small estimates (correct: $\beta$ `r full_estimate(Csum_eff)`; mispronunciation: $\beta$ `r full_estimate(Msum_eff)`) indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label.
-We plot both object recognition and mispronunciation sensitivity as a function of age in Figure 2.
+We plot both object recognition and mispronunciation sensitivity as a function of age in Figure 3.
 
@@
 
-## (Insert Figure 2 about here)
+## (Insert Figure 3 about here)
 
 [Christina] Can you try and align the axes for both plots?
+[Katie] I can, but then the dotted line doesn't extend the full way (which I think is quite ugly). Not sure how to fix that.
 
@@
   scale_colour_manual(values=cbPalette)+
+  xlim(6, 31) +
   apatheme +
@@
 
-  jpeg(filename = "figures/Figure_2_AgeEffect.jpg", 
+  jpeg(filename = "figures/Figure_3_AgeEffect.jpg", 
        width = 500, height = 700, units = "px")
@@
 Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` analyzed the relationship between vocabulary scores and object recognition for correct pronunciations and mispronunciations (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers and `r with(vi1, count[has_vocab == "comprehension"])` records; production = `r with(vi1, papers[has_vocab == "production"])` papers and `r with(vi1, count[has_vocab == "production"])` records).
-There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment; Kidd citation), and we therefore planned to analyze these two types of vocabulary measurement separately.
+There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment; Tomasello & Mervis, 1994), and we therefore planned to analyze these two types of vocabulary measurement separately.
 However, because only `r with(vi1, papers[has_vocab == "production"])` papers reported correlations with productive vocabulary scores, only limited conclusions that can be drawn.
@@
 
-[Christina] So can you not only list papers but also n conditions above? With just 1 paper for production, I wouldn't analyze it to be honest. it's just not enough data. 
-I also liked your comments about the time line of this whole thing, can you extract the years of papers which report this?
-Might be extremely useful in the discussion and strengthens our case that there is no effect, bc people don't find the predicted relation with vocab.
-Also, cann you add a citation for comp vs prod? I think Evan Kidd had a paper on it, if you don't have one handy, I can look it up.
-[Katie] I couldn't find what you are referring to.
-Could you add the Evan Kidd paper?
-Also, I added a histogram figure below, but I'm not so very sure that it is good enough to add to the paper (its under the heading "Potential Vocabulary Figure").
-Let me know what you think.
-
-[Christina] Here is the Kidd paper: https://pure.mpg.de/rest/items/item_2602612_8/component/file_3001229/content Not sur eif it helps.
+[Katie: Tomasello reference - https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1540-5834.1994.tb00186.x]
 
@@
 Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for `r pos_rel` of `r tot_rel` experimental conditions, with correlation values ranging from `r min_cor` to `r max_cor`.
-The mean effect size Pearson's *r* of `r r2(CC$TE.fixed)` was small and did not differ significantly from zero (CI [`r r2(CC$lower.fixed)`; `r r2(CC$upper.fixed)`] *p* `r psig(CC$pval.fixed)`).
-However, the lower bound of the CI is close to zero, and one might hypothesize that with more power the small relationship might become significant.
-At the same time, a larger sample might confirm our conclusion that there is no relationship.
-As a result, we can not draw firm conclusions about the relationship between comprehension scores and object recognition in response to correct pronunciations.
+The mean effect size Pearson's *r* of `r r2(CC$TE.fixed)` was small but did differ significantly from zero (CI [`r r2(CC$lower.fixed)`; `r r2(CC$upper.fixed)`] *p* `r psig(CC$pval.fixed)`).
+However, the lower bound of the CI is close to zero and considering the small sample size, one might hypothesize that with more power the small relationship might become even larger.
+As a result, we can draw a tentative conclusion that there is a positive relationship between comprehension scores and object recognition in response to correct pronunciations.
 
 [Christina] It's significant now!
+[Katie] Must be because you removed the outliers. I've changed around the wording :)
 
@@
 The mean effect size Pearson's *r* of `r r2(MC$TE.fixed)` was small and did not differ significantly from zero (CI [`r r2(MC$lower.fixed)`; `r r2(MC$upper.fixed)`] *p* `r psig(MC$pval.fixed)`).
-Similar to the relationship between comprehension scores and correct pronunciation object identification, the small correlations and large variances suggest a lack of relationship between vocabulary and object recognition for mispronunciations.
-We again emphasize that we cannot draw firm conclusions due to the small number of studies we were able to include here.
-
-## Potential Vocabulary Figure
+The small correlation and large variances suggest a lack of relationship between vocabulary and object recognition for mispronunciations.
+We again emphasize that we cannot draw a firm conclusion due to the small number of studies we were able to include here.
+
+Figure 4 plots the year of publication for all the mispronunciation sensitivity studies included in this meta-analysis.
+This figure illustrates two things: the growing number of mispronunciation sensitivity studies and the waning number of studies measuring vocabulary.
+The lack of evidence for a relationship between mispronunciation sensitivity and vocabulary size in early studies may have contributed to increasingly fewer researchers including vocabulary measurements in their mispronunciation sensitivity experimental design.
+This may explain our underpowered analysis of the relationship between mispronunciation sensitivity and vocabulary size.
+
+## (Insert Figure 4 about here)
 
@@
 
-dat.v$relationship <- ifelse(dat.v$relationship == "no_vocab", "None",
+dat.v$relationship <- ifelse(dat.v$relationship == "no_vocab", "No Vocabulary",
                                    ifelse(dat.v$relationship == "positive", "Predictive",
                                           "No Relationship"))
-dat.v$relationship <- factor(dat.v$relationship, levels = c("Predictive", "No Relationship", "None"))
+dat.v$relationship <- factor(dat.v$relationship, levels = c("No Vocabulary", "Predictive", "No Relationship"))
 
@@
 
-  jpeg(filename = "figures/Vocab_findings.jpg", 
+  jpeg(filename = "figures/Figure_4_Vocab_findings.jpg", 
        width = 500, height = 300, units = "px")
@@
 The results seem clear: Although infants consider a mispronunciation as a better match with the target image than a distractor image, there was a consistent effect of mispronunciation sensitivity.
-This did not change with development.
+This did not change with development nor with vocabulary size.
 Of the 3 predictions and assumptions about the development of infants' sensitivity to mispronunciations discussed in the Introduction, the present results lend some support for the argument that mispronunciation sensitivity stays consistent as infants develop.
 This runs counter to existing theories of phono-lexical development, which predict either an increase (PRIMR ref) or decrease (Assim Model ref) in mispronunciation sensitivity.
-Furthermore, counter to the predictions for the PRIMR (PRIMR ref) and Assimilation(Assim ref) models, we found no relationship between vocabulary and target looking for correct pronunciations or mispronunciations, although our analyses may be underpowered.
-In sum, it seems that current theories of infants' phono-lexical development cannot fully capture our results and should be reconsidered with all the evidence in mind.
+Furthermore, although we found a relationship between vocabulary comprehension and target looking for correct pronunciations, we found no relationship between vocabulary and target looking for mispronunciations.
+This also runs counter to the predictions for the PRIMR (PRIMR ref) and Assimilation (Assim ref) models, but may be due to our analyses being underpowered.
+In sum, it seems that current theories of infants' phono-lexical development cannot fully capture our results, but that more investigation is needed to draw a firm conclusion.
 
@@
 
-[Christina] This section talked about several variables in 2 categories, but in reality there are only 2 variables, right?
-I am not 100% sure about total trial length as being the first or being mentioned at all, might it be better to focus on time window analyzed and then say "Oh, btw, total trial length totally does nothing so we don't have to discuss it further" I am not sure, so feel free to re-rewrite this, but now it better lines up with everything before because trial length kinda comes out of nowhere.
-[Katie] That's fair!
-I think we don't need the full analysis for total time presented, but I'd like to still mention all of them because it really shows that its something about this post-naming time window choice that influences it, and not just fishing around for variability until we find something that works.
-In the end there are 2 interesting analyses, but offset could have been interesting (but wasn't).
-Therefore, I'd still like to refer to the timing variables as a type of category.
-Otherwise, we say we'll do size of time window analyzed, but then we have information about other timing stuff as well.
-
 We identified two sets of variables which had the potential to vary across papers to assess the influence of data analysis choices on resulting effect size: timing (size of time window analyzed; offset time) and which dependent variable(s) were reported.
@@
 
-[Christina] Is there a reason you choose mode and not median? 
-[Katie] Hmm, I felt like mode would be interesting, because it gives the most popular choice (74 experimental conditions).
-But, the median is only 500 ms less, so we could use that too (9 experimental conditions).
-[Christina] Oh I get it, maybe if you add that? Whatever you prefer. I was just curious.
-
-[Christina] Would it make sense to present dependent variable first? 
-[Katie] I don't have a strong opinion on this. If you think it would be better, then I can change it.
-[Christina] Nah, your call.
-
 In a typical trial in a mispronunciation sensitivity study, the target-distractor image pairs are first presented in silence, followed by auditory presentation of a carrier phrase or isolated presentation of the target word (correctly pronounced or mispronounced).
@@
 Across papers, actual post-naming phase length varied from `r with(post_length_info, min(post_nam_actual))*1000` to `r with(post_length_info, max(post_nam_actual))*1000` ms, with a median value of `r with(dat, median(post_nam_actual))*1000` ms.
+We note that the most popular actual post-naming phase length was `r with(dat, getmode(post_nam_actual))*1000` ms, used in *n* = `r with(post_length_info, n_exp_conditions[post_nam_actual == getmode(post_length_info$n_exp_conditions)])` experimental conditions.
 There was an inverse relationship between infant age and actual post-naming phase length, such that younger infants were presented with longer a longer post-naming phase, although this correlation was not significant (*r* = `r trial.l$estimate`, *p* `r psig(trial.l$p.value)`).
@@
 Across papers, the length of the post-naming phase analyzed varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a median value of `r with(dat, median(post_nam_dur))*1000` ms.
+We note that the most popular actual post-naming phase length was `r with(dat, getmode(post_nam_dur))*1000` ms, used in *n* = `r with(post_name_info, n_exp_conditions[post_nam_dur == with(dat, getmode(post_nam_dur))])` experimental conditions.
 Similar to actual post-naming phase length, there was an inverse relationship between infant age and the size of the post-naming time window analyzed, such that younger infants' looking times were analyzed using a longer post-naming time window, here the relationship was significant (*r* = `r post.l$estimate`, *p* `r psig(post.l$p.value)`).
@@
 
-## (Insert Figure 3 about here)
+## (Insert Figure 5 about here)
 
@@
 
-  jpeg(filename = "figures/Figure_3_Post_name_size.jpg", 
+  jpeg(filename = "figures/Figure_5_Post_name_size.jpg", 
        width = 600, height = 600, units = "px")
@@
 This requires two values, one for the pre-naming phase and one for the post-naming phase.
-A greater post compared to pre-naming phase PTL indicates that increased their target looks after hearing the naming label.
+A greater post compared to pre-naming phase PTL indicates that infants increased their target looks after hearing the naming label.
 We will refer to this dependent variable as Pre vs.
@@
 We will refer to this dependent variable as Post.
-
-[Christina] Did I ask the following already: Do we know whether subtrations were on the trial level?
-Pre vs post is a bit differnt because it loses the individual bias accommodation and the correlation between pre and post on the participant / item level.
-[Katie] You did. I'll put here my answer from before:
-From working with Nivi, we did it participants x condition or participants x trial (but mostly the former).
-But, this is not something we reported in papers.
-I don't think I read it at all when putting together the dataset for this either.
-[Christina] Mention in the discussion that we don't know this and it might be important to establish standard analysis pipelines for MP studies and that we need open data and code? ;)
 
@@
 
-## (Insert Figure 4 about here)
+## (Insert Figure 6 about here)
 
@@
 
-  jpeg(filename = "figures/Figure_4_Dependent_variable.jpg", 
+  jpeg(filename = "figures/Figure_6_Dependent_variable.jpg", 
        width = 500, height = 600, units = "px")
@@
 
-# Discussion
-
-To Summarize:
-
-** Overall Meta-analytic Effect **
-
-  + Accept mispronunciations as labels for targets
-  + Sensitive to mispronunciations
-  + lack of change over development
-
-** Vocabulary **
-
-  + no relationship?
-  + talk about how few studies report it
+# General Discussion
+
+Overall, infants showed reliable correct object recognition when given both correctly pronounced and mispronounced labels.
+In other words, not only did infants correctly recognize object labels when they were correctly pronounced, they also were likely to accept mispronunciations as acceptable labels for targets.
+Mispronounced labels were considered a better match for target images than a distractor image, despite the differences in the phonological form of correctly pronounced and mispronounced words.
+Nonetheless, there was a considerable difference in target fixations in response to correctly pronounced and mispronounced labels, suggesting overall mispronunciation sensitivity in the current experimental literature.
+
+We next evaluated the developmental trajectory of infants' mispronunciation sensitivity.
+Based on previous theoretical accounts and existing experimental evidence, we envisioned three possible developmental patterns: increasing sensitivity, decreasing sensitivity, and unchanging sensitivity.
+We observed no influence of age when it was considered as a moderator of mispronunciation sensitivity.
+Of the two mainstream theories identified in our literature review, neither the Perceptual Attunement account (Best 1994, 1995) nor PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005) account for a lack of developmental change.
+The results of our meta-analysis are supported by a handful of studies directly comparing infants over a range of ages (Swingley & Aslin, 2000; Bailey & Plunkett, 2002; Zesiger et al., 2012), which also found no developmental change in mispronunciation sensitivity.
+
+Both the Perceptual Attunement (Best 1994, 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005) accounts link a change of mispronunciation sensitivity specifically with vocabulary growth, in comparison to development in general.
+Vocabulary growth leads to an increase (PRIMIR; Curtin & Werker, 2007; Werker & Curtin, 2005) or decrease (Perceptual Attunement; Best 1994, 1995) in mispronunciation sensitivity and vocabulary is expected to grow considerably in the age range considered in the current meta-analysis (see wordbank.stanford.edu; Frank et al., 2017).
+The lack of developmental effects found in the meta-analysis may therefore be due to using age, instead of vocabulary growth, as a facilitator for change in mispronunciation sensitivity.
+Yet, an analysis of correlations between vocabulary size and object recognition effect sizes does not support this argument.
+Although an increasing vocabulary size lead to increased object recognition for correctly pronounced words, this was not the case for mispronunciations.
+Some previous experimental evidence also supports a lack of a relationship between vocabulary size and mispronunciation sensitivity (e.g.
+Mani & Plunkett, 2007; Swingley &
+Aslin, 2000; but see Mani & Plunkett, 2010).
+This would suggest that object recognition for mispronunciations is not modulated by vocabulary size, contrary to the predictions of the Perceptual Attunement (Best 1994, 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005) accounts and further supporting the overall lack of an influence of age on mispronunciation sensitivity.
+
+What may these results mean for our understanding of phono-lexical development in infancy?
+Evidence that infants accept a mispronunciation (object identification) while simultaneously holding correctly pronounced and mispronounced labels as separate (mispronunciation sensitivity) may indcate an abstract understanding of words' phonological structure.
+It appears infants may understand that the mispronunciation and correct pronunciation's phonological form do not match, but that the mispronunciation is a better label for the target compared to the distractor image.
+The lack of age or vocabulary effects in our meta-analysis suggest that this understanding is present from an age when the earliest words are learned and is maintained throughout early lexical development.
+Already with the first words, infants have a sense of the importance of sounds in  the words present in their lexicon.
+We recommend that future theoretical accounts should consider this lack of developmental change.
+
+Although the lack of an relationship between mispronunciation sensitivity and vocabulary size may reflect a true effect, we note that this may also be the result of an underpowered analysis.
+Despite the theoretical implications, less than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total).
+We suggest that this may be the result of publication bias, specifically a desire to not publish null results.
+Although the number of mispronunciation sensitivity studies has experience growth, this has not translated to an increasing number of mispronunciation sensitivity studies also measuring vocabulary scores.
+
+[Katie] The above section is a bit clunky and I don't like it. Any suggestions for improvement?
+
+Then talk about the experimental decisions
 
@@
   + the first two do not have theoretical frameworks to guide researchers, whereas offset time does
+
+  [Christina] Did I ask the following already: Do we know whether subtrations were on the trial level?
+Pre vs post is a bit differnt because it loses the individual bias accommodation and the correlation between pre and post on the participant / item level.
+[Katie] You did. I'll put here my answer from before:
+From working with Nivi, we did it participants x condition or participants x trial (but mostly the former).
+But, this is not something we reported in papers.
+I don't think I read it at all when putting together the dataset for this either.
+[Christina] Mention in the discussion that we don't know this and it might be important to establish standard analysis pipelines for MP studies and that we need open data and code? ;)
 

### 2018-12-03 Paper_Analyses.tex
addressed comments by Christina; started on General Discussion

@@
 \linenumbers
+\usepackage{setspace}
+\AtBeginEnvironment{tabular}{\singlespacing}
+\AtBeginEnvironment{lltable}{\singlespacing}
+\AtBeginEnvironment{tablenotes}{\doublespacing}
+\captionsetup[table]{font={stretch=1.5}}
+\captionsetup[figure]{font={stretch=1.5}}
 
@@
 \maketitle
+
+{[}Christina: Big change: I just realized that we also need to report
+where we could not compute effect sizes, added this info. {]}
 
@@
 
-{[}Christina: changed concepts to mechanisms in the next paragraph,
-because I want to refer to what they represent, but I am not sure it's
-the right term{]}{[}Katie: Karen (Mulak) talks about these terms as
-concepts. Mechanisms to me means some sort of internalization, that they
-would have had this ability all along and just need to apply it. It
-could be that we fundamentally disagree on this, but to me these are
-things that infants discover. Later on we use principles. What about
-\enquote{principles that infants must discover}\ldots{} \enquote{in
-order to form adult-like word representations}? I took away
-\enquote{which are both present in the mature language processing
-system}.{]}
-
 The study of Swingley and Aslin (2000) as well as subsequent studies
@@
 explicitly say that only 2 of the 3 are predicted by theoretical
-accounts.{]}
+accounts.{]}{[}Christina: Works for me. I am just thinking what the
+Vihman-style framework says. do you happen to know? I think the Renner
+thesis discusses it.{]} {[}Katie: I wasn't really familiar with the
+Vihman framework, but looking at Renner's thesis and some of the
+original papers suggests that it really is about production, not
+perception.{]}
 
@@
 scripts in R {[}@R, @RMarkdown, @papaja{]}, it is always possible to
-re-analyze an updated dataset. In addition, we follow the Preferred
+re-analyze an updated dataset. In addition, we followed the Preferred
 Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA)
@@
 supplementary materials (Moher, Liberati, Tetzlaff, Altman \&
-PRISMAGroup, 2009). Figure X plots our PRISMA flowchart illustrating the
+PRISMAGroup, 2009). Figure 1 plots our PRISMA flowchart illustrating the
 paper selection procedure.
 
-{[}Figure X. PRISMA Flowchart.{]}
-(figures/PRISMA\_MA\_Mispronunciation.png)
+\subsection{(Insert Figure 2 about
+here)}\label{insert-figure-2-about-here}
+
+\begin{figure}
+\centering
+\includegraphics{figures/PRISMA_MA_Mispronunciation.png}
+\caption{}
+\end{figure}
 
@@
 
-\begin{table}[tbp]
-\begin{center}
-\begin{threeparttable}
-\caption{\label{tab:SummaryTable}Summary of all studies.}
-\begin{tabular}{llll}
+\begin{lltable}
+
+\begin{longtable}{lllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:SummaryTable}Summary of all studies.}\\
 \toprule
-Paper & Publication format & Age & Vocabulary\\
+Paper & Publication format & Age & Vocabulary & N Effect Sizes\\
 \midrule
-Altvater-Mackensen (2010) & dissertation & 22, 25 & None\\
-Altvater-Mackensen et al. (2014) & paper & 18, 25 & None\\
-Bailey \& Plunkett (2002) & paper & 18, 24 & Comp\\
-Bergelson \& Swingley (2017) & paper & 7, 9, 12, 6 & None\\
-Bernier \& White 2017 & proceedings & 21 & None\\
-Delle Luche et al. (2015) & paper & 20, 19 & None\\
-Durrant et al. (2014) & paper & 19, 20 & None\\
-Hoehle et al. 2006 & paper & 18 & None\\
-Hojen et al. & gray paper & 20 & Comp/Prod\\
-Mani \& Plunkett 2007 & paper & 15, 18, 24, 14, 21 & Comp/Prod\\
-Mani \& Plunkett 2010 & paper & 12 & Comp\\
-Mani \& Plunkett 2011 & paper & 23, 17 & None\\
-Mani, Coleman, \& Plunkett (2008) & paper & 18 & Comp/Prod\\
-Ramon-Casas \& Bosch 2010 & paper & 24, 25 & None\\
-Ramon-Casas et al. 2009 & paper & 21, 20 & Prod\\
-Ren \& Morgan, in press & gray paper & 19 & None\\
-Skoruppa et al. 2013 & paper & 24 & None\\
-Swingley (2009) & paper & 17 & Comp/Prod\\
-Swingley (2016) & paper & 27, 28 & Prod\\
-Swingley \& Aslin (2000) & paper & 20 & Comp\\
-Swingley \& Aslin (2002) & paper & 15 & Comp/Prod\\
-Swingley 2003 & paper & 19 & Comp/Prod\\
-Tamasi (2016) & dissertation & 30 & None\\
-Tao \& Qinmei 2013 & paper & 12 & None\\
-Tao et al. 2012 & paper & 16 & Comp\\
-van der Feest \& Fikkert, 2015 & paper & 24, 20 & None\\
-van der Feest \& Johnson, 2016 & paper & 24 & None\\
-Wewalaarachchi et al. 2017 & paper & 24 & None\\
-White \& Aslin (2011) & paper & 18 & None\\
-White \& Morgan (2008) & paper & 18, 19 & None\\
-Zesiger \& Johr 2011 & paper & 14 & None\\
-Zesiger et al. (2012) & paper & 12, 19 & Comp/Prod\\
+Altvater-Mackensen (2010) & dissertation & 22, 25 & None & 13\\
+Altvater-Mackensen et al. (2014) & paper & 18, 25 & None & 16\\
+Bailey \& Plunkett (2002) & paper & 18, 24 & Comp & 12\\
+Bergelson \& Swingley (2017) & paper & 6, 7, 9, 12 & None & 9\\
+Bernier \& White (2017) & proceedings & 21 & None & 4\\
+Delle Luche et al. (2015) & paper & 20, 19 & None & 4\\
+Durrant et al. (2014) & paper & 19, 20 & None & 4\\
+Höhle et al. (2006) & paper & 18 & None & 4\\
+Højen et al. (n.d.) & gray paper & 19, 20 & Comp/Prod & 6\\
+Mani \& Plunkett (2007) & paper & 15, 18, 24, 14, 20 & Comp/Prod & 14\\
+Mani \& Plunkett (2010) & paper & 12 & Comp & 8\\
+Mani \& Plunkett (2011) & paper & 23, 17 & None & 15\\
+Mani, Coleman, \& Plunkett (2008) & paper & 18 & Comp/Prod & 4\\
+Ramon-Casas \& Bosch (2010) & paper & 24, 25 & None & 4\\
+Ramon-Casas et al. (2009) & paper & 21, 20, 43, 44 & Prod & 14\\
+Ren \& Morgan (in press) & gray paper & 19 & None & 8\\
+Skoruppa et al. (2013) & paper & 23 & None & 4\\
+Swingley (2003) & paper & 19 & Comp/Prod & 6\\
+Swingley (2009) & paper & 17 & Comp/Prod & 4\\
+Swingley (2016) & paper & 27, 28 & Prod & 9\\
+Swingley \& Aslin (2000) & paper & 20 & Comp & 2\\
+Swingley \& Aslin (2002) & paper & 15 & Comp/Prod & 4\\
+Tamasi (2016) & dissertation & 30 & None & 4\\
+Tao \& Qinmei (2013) & paper & 12 & None & 4\\
+Tao et al. (2012) & paper & 16 & Comp & 6\\
+van der Feest \& Fikkert, (2015) & paper & 24, 20 & None & 16\\
+van der Feest \& Johnson (2016) & paper & 24 & None & 24\\
+Wewalaarachchi et al. (2017) & paper & 24 & None & 8\\
+White \& Aslin (2011) & paper & 18 & None & 4\\
+White \& Morgan (2008) & paper & 18, 19 & None & 12\\
+Zesiger \& Jöhr (2011) & paper & 14 & None & 8\\
+Zesiger et al. (2012) & paper & 12, 19 & Comp/Prod & 6\\
 \bottomrule
-\end{tabular}
-\end{threeparttable}
-\end{center}
-\end{table}
-
-{[}Christina{]} I've shortened the labels and wanted to try out
-apa\_table {[}Katie{]} I like the idea, but does it work for you? It
-doesn't work for me\ldots{} {[}Katie{]} We have it currently set at less
-than 31 months, not 36, so I've changed below.
+\end{longtable}
+\end{lltable}
 
@@
 search was conducted on 22 September, 2017 and yielded 288 results. We
-screened the resulting 398 items, removing 99 duplicate items. We
-screened remaining 299 items for their title and abstract to determine
-whether it met the following inclusion criteria: (1) original data was
-reported; (2) the experiment examined familiar word recognition and
-mispronunciations; (3) infants studied were under 31-months-of-age; (4)
-the dependent variable was derived from proportion of looks to a target
+removed 99 duplicate items and screened the remaining 299 items for
+their title and abstract to determine whether each met the following
+inclusion criteria: (1) original data was reported; (2) the experiment
+examined familiar word recognition and mispronunciations; (3) infants
+studied were under 31-months-of-age and typically developing; (4) the
+dependent variable was derived from proportion of looks to a target
 image versus a distractor in a eye movement experiment; (5) the stimuli
@@
 reports. We will refer to these items collectively as papers. Table 1
-(Summary Table) provides an overview of all papers included in the
-present meta-analysis.
+provides an overview of all papers included in the present
+meta-analysis.
+
+\subsection{(Insert Table 1 about
+here)}\label{insert-table-1-about-here}
 
@@
 publication, population, experiment design and stimuli, and results. For
-the analyses presented in this section, we focus on the following
-characteristics:
+the planned analyses to evaluate the development of mispronunciation
+sensitivity, we focus on the following characteristics:
 
@@
 analyses (see next section). We will call each row a record; in total
-there were 251 records in our data.
+there were 260 records in our data.
 
@@
 
-{[}Christina{]} I think it would be useful to say how many records, not
-papers, report each measure. e.g. \enquote{(n = xxx records from yyy
-papers)}. Would that be ok? {[}Katie{]} Totally! I think that gives a
-good bit of information. Good suggestion!
+{[}Christina: I needed to move this around because we first need to say
+that we could not compute some effect sizes and removed outlierts.{]}
+
+Effect sizes are reported for infants' looks to target pictures after
+hearing a correctly pronounced or a mispronounced label (object
+identification) as well as the difference between effect sizes for
+correct and mispronounced trials (i.e.~mispronunciation sensitivity).
+The effect size reported in the present paper is based on comparison of
+means, standardized by their variance. The most well-known effect size
+from this group is Cohen's \emph{d} {[}@cohen{]}. To correct for the
+small sample sizes common in infant research, however, we used as a
+dependent variable Hedges' \emph{g} instead of Cohen's \emph{d} (Hedges,
+1981; Morris, 2000).
+
+{[}Katie{]} Do you want number of records and papers for the imputed
+correlations as well? You've put a -1, assuming there was something
+wrong with one of the papers or something like that? How does that shake
+out for number of records? {[}Christina: No clue what the -1 was,
+sorry.{]}
+
+We calculated Hedges' \emph{g} using the raw means and standard
+deviations reported in the paper (\emph{n} = 186 records from 26 papers)
+or using reported t-values (\emph{n} = 74 records from 9 papers). Two
+papers reported raw means and standard deviations for some experimental
+conditions and just t-values for the remaining experimental conditions
+(Swingley, 2016; Altvater-Mackensen et al., 2014). Raw means and
+standard deviations were extracted from figures for 3 papers. In a
+within-participation design, when two means are compared (i.e.~looking
+during pre- and post-naming) it is necessary to obtain correlations
+between the two measurements at the participant level to calculate
+effect sizes and effect size variance based on t-values. Upon request we
+were provided with correlation values for one paper (Altvater-Mackensen,
+2010); we were able to compute correlations using means, standard
+deviations, and t-values for \emph{n} = 5 (following Csibra, et al.
+2016, Appendix B; see also Rabagliati, Ferguson, \& Lew-Williams, 2018).
+Correlations were imputed for the remaining papers (see Black \&
+Bergmann, 2017, for the same procedure). For two papers, we could not
+derive any effect size (Ballem \& Plunkett, Renner), and for a third
+paper, we do not have sufficient information in one record to compute
+effect sizes (Skoruppa). We compute a total of 106 effect sizes for
+correct pronunciations and 150 for mispronunciations. Following standard
+meta-analytic practice, we remove outliers, i.e.~effect sizes more than
+3 standard deviations from the respective mean effect size. This leads
+to the exclusion of 2 records for correct pronunciations and 3 records
+for mispronunciations.
+
+To take into account the fact that the same infants contributed to
+multiple datapoints, we analyze our results in a multilevel approach
+using the R {[}@R{]} package metafor {[}@metafor{]}. This means we model
+as random effect that effect sizes from the same paper share are based
+on more similar studies than those across papers and that nested therein
+effects can stem from the same infants.
+
+{[}Christina: In the above 2 paragraphs I got confused, should it be
+present or past. I think it switched in the las tparagraph so I started
+to adapt, but I think it would be best for you to decide. {]}{[}Katie:
+Good catch. I've gone through the Methods section and changed everything
+to past, per APA guidelines.{]}
 
@@
 difference score.
-
-{[}Christina{]} Katie, do you know whether the difference is computed
-based on items, participants, trials\ldots{}? Is there consistency?
-{[}Katie{]} From working with Nivi, we did it participants x condition
-or participants x trial (but mostly the former). But, this is not
-something we reported in papers. I don't think I read it at all when
-putting together the dataset for this either.
 
@@
 
-We report effect sizes for infants' looks to target pictures after
-hearing a correctly pronounced or a mispronounced label (object
-identification) as well as the difference between effect sizes for
-correct and mispronounced trials (i.e.~mispronunciation sensitivity).
-The effect size we report in the present paper are based on comparison
-of means, standardized by their variance. The most well-known effect
-size from this group is Cohen's \emph{d} {[}@cohen{]}. To correct for
-the small sample sizes common in infant research, however, we use as a
-dependent variable Hedges' \emph{g} instead of Cohen's \emph{d} (Hedges,
-1981; Morris, 2000).
-
-{[}Christina{]} These numbers seem wrong! Again, how about (xx effect
-sizes from yy papers)? {[}Katie{]} Well, they are kind of wrong :) Two
-papers report both for different experimental conditions. I've given the
-explanation now, not sure if that is good enough, but I'm really not
-sure how to say it a different way. {[}Katie{]} Do you want number of
-records and papers for the imputed correlations as well? You've put a
--1, assuming there was something wrong with one of the papers or
-something like that? How does that shake out for number of records?
-
-We calculated Hedges' \emph{g} using the raw means and standard
-deviations reported in the paper (\emph{n} = 177 records from 25 papers)
-or using reported t-values (\emph{n} = 74 records from 9 papers). Two
-papers reported raw means and standard deviations for some experimental
-conditions and just t-values for the remaining experimental conditions
-(Swingley, 2016; Altvater-Mackensen et al., 2014). Raw means and
-standard deviations were extracted from figures for 3 papers. In a
-within-participation design, when two means are compared (i.e.~looking
-during pre- and post-naming) it is necessary to obtain correlations
-between the two measurements at the participant level to calculate
-effect sizes and effect size variance based on t-values. Upon request we
-were provided with correlation values for one paper (Altvater-Mackensen,
-2010); we were able to compute correlations using means, standard
-deviations, and t-values for \emph{n} = 4 (following Csibra, et al.
-2016, Appendix B; see also Rabagliati, Ferguson, \& Lew-Williams, 2018).
-Correlations were imputed for the remaining papers (see Black \&
-Bergmann, 2017, for the same procedure). We could compute a total of 104
-effect sizes for correct pronunciations and 147 for mispronunciations.
-
-To take into account the fact that the same infants contributed to
-multiple datapoints, we analyze our results in a multilevel approach
-using the R {[}@R{]} package metafor {[}@metafor{]}. This means we model
-as random effect that effect sizes from the same paper share are based
-on more similar studies than those across papers and that nested therein
-effects can stem from the same infants.
-
 \subsection{Publication Bias}\label{publication-bias}
@@
 in the mispronunciation sensitivity literature, which would bias the
-data analyzed in this meta-analysis, we conduct two tests. We first
-examine whether effect sizes are distributed as expected based on
+data analyzed in this meta-analysis, we conducted two tests. We first
+examined whether effect sizes are distributed as expected based on
 sampling error using the rank correlation test of funnel plot asymmetry
 with the R {[}@R{]} package metafor {[}@metafor{]}. Effect sizes with
-low variance are expected to fall closer to the estimated mean, while
+low variance were expected to fall closer to the estimated mean, while
 effect sizes with high variance should show an increased,
@@
 is true, versus a flat distribution that speaks for no effect being
-present in the population and all significant effect being spurious.
-Responses to correctly pronounced and mispronounced labels are predicted
-to show different patterns of looking behavior. In other words, there is
-an expectation that infants should look to the target when hearing a
-correct pronunciation, but some studies may report either significant
-looks or no significant looks to the target when hearing a mispronounced
-label
-
-{[}Christina{]} Katie, is that right, can you add a citation?
-{[}Katie{]} I've rewritten it a bit to be explicit about the difference
-between expectations for correct and mispronounced labels. I'm not sure
-what to cite though. The papers that find significant looks or no
-significant looks? That's basically the meta-analysis. Or some citation
-that talks about what looking to the target upon hearing a
-mispronunciation means in comparison to what target looks being
-decreased for mispronunciations relative to correct pronunciations
-means? I'm not so sure whether anyone has actually talked about that
-difference before, not sure what to cite.
-
+present in the population and all observed significant effects being
+spurious. Responses to correctly pronounced and mispronounced labels
+were predicted to show different patterns of looking behavior. In other
+words, there is an expectation that infants should look to the target
+when hearing a correct pronunciation, but studies vary in their report
+of significant looks to the target when hearing a mispronounced label
 (i.e.~there might be no effect present in the population, see e.g., );
-as a result, we conduct these two analyses to assess publication bias
+as a result, we conducted these two analyses to assess publication bias
 separately for both conditions.
@@
 investigate how development impacts mispronunciation sensitivity, our
-core theoretical question, we introduce age (centered; continuous and
+core theoretical question, we introduced age (centered; continuous and
 measured in days but transformed into months for ease of interpreting
@@
 subsequent exploratory investigations of experimental characteristics,
-we introduce each characteristic as a moderator (more detail below).
+we introduced each characteristic as a moderator (more detail below).
 
@@
 
-Figure 1 shows the funnel plots for both correct pronunciations and
+Figure 2 shows the funnel plots for both correct pronunciations and
 mispronunciations (code adapted from Sakaluk, 2016). Funnel plot
@@
 We should also point out that funnel plot asymmetry can be caused by
-multiple factors beside publication bias. The funnel plot asymmetry may
-also reflect heterogeneity in the data. There are various possible
-sources of heterogeneity, which our subsequent moderator analyses will
-begin to address. Nonetheless, we will remain cautious in our
-interpretation of our findings and hope that an open dataset that can be
-expanded by the community will attract previously unpublished null
-results so we can better understand infants' developing mispronunciation
-sensitivity.
-
-\subsection{(Insert Figure 1 about
-here)}\label{insert-figure-1-about-here}
+multiple factors beside publication bias, such as heterogeneity in the
+data. There are various possible sources of heterogeneity, which our
+subsequent moderator analyses will begin to address. Nonetheless, we
+will remain cautious in our interpretation of our findings and hope that
+an open dataset which can be expanded by the community will attract
+previously unpublished null results so we can better understand infants'
+developing mispronunciation sensitivity.
+
+\subsection{(Insert Figure 2 about
+here)}\label{insert-figure-2-about-here-1}
 
@@
 correctly pronounced words, the p-curve results and a CI lower bound of
-0.67 which is substantially above zero suggests that this result should
-be robust even when correcting for publication bias. In other words, we
-are confident that the true population mean lies above zero for object
-recognition of correctly pronounced words.
+0.67, which is substantially above zero, together suggest that this
+result is somewhat robust. In other words, we are confident that the
+true population mean lies above zero for object recognition of correctly
+pronounced words.
 
@@
 
-{[}Christina{]} I am not sure about the placement of this paragraph
-because the next section cannot explain this heterogeneity, so maybe we
-should move it down to the beginning of the age part? {[}Katie{]} I
-think that makes sense, moving it!
-
 \subsubsection{Mispronunciation Sensitivity Meta-analytic
@@
 the two datasets. The moderator test was significant, QM(1) = 215.761,
-\emph{p}\textless{} .001. The estimate for mispronunciation sensitivity
+\emph{p} \textless{} .001. The estimate for mispronunciation sensitivity
 was 0.495 (SE = 0.034), and infants' looking times across conditions
@@
 but transformed into months for ease of interpreting estimates by
-dividing by 30.44 for Figure 2). {[}Christina{]} What about the whole
-months thing? {[}Katie{]} We had an explanation in the methods section
-for this, I've now added it again here.
+dividing by 30.44 for Figure 3).
 
@@
 not significantly modulate object identification in response to
-correctly pronounced (QM(1) = 0.678, \emph{p}= 0.41) or mispronounced
-words (QM(1) = 1.715, \emph{p}= 0.19). The lack of a significant
+correctly pronounced (QM(1) = 0.678, \emph{p} = 0.41) or mispronounced
+words (QM(1) = 1.715, \emph{p} = 0.19). The lack of a significant
 modulation together with the small estimates (correct: \(\beta\) =
-0.015, SE = 0.018, 95\% CI{[}-0.02, 0.049{]}, \emph{p}= 0.41;
+0.015, SE = 0.018, 95\% CI{[}-0.02, 0.049{]}, \emph{p} = 0.41;
 mispronunciation: \(\beta\) = 0.015, SE = 0.011, 95\% CI{[}-0.007,
-0.037{]}, \emph{p}= 0.19) indicates that there was no relationship
+0.037{]}, \emph{p} = 0.19) indicates that there was no relationship
 between age and target looks in response to a correctly pronounced or
 mispronounced label. We plot both object recognition and
-mispronunciation sensitivity as a function of age in Figure 2.
-
-{[}Christina{]} OK there is a mismatch between what you write and the
-numbers, can you verify? {[}Katie{]} Good catch. For some reason, it was
-just copying over the moderator test from mispronunciation sensitivity,
-even though I was calling for the age moderator analysis. There is no
-significant moderator test, but it was just pasting the same one again
-and again. I've fixed my code, so it should be correct now!
+mispronunciation sensitivity as a function of age in Figure 3.
 
@@
 sensitivity (correct vs.~mispronounced words) in our whole dataset. The
-moderator test was significant (QM(3) = 218.621, \emph{p}\textless{}
+moderator test was significant (QM(3) = 218.621, \emph{p} \textless{}
 .001). The interaction between age and mispronunciation sensitivity,
 however, was not significant (\(\beta\) = 0.003, SE = 0.008, 95\%
-CI{[}-0.012, 0.018{]}, \emph{p}= 0.731), pointing to the moderator test
-being driven by the difference between conditions. The small estimate,
-as well as inspection of Figure 2 suggests that as infants age, their
+CI{[}-0.012, 0.018{]}, \emph{p} = 0.731); the moderator test was mainly
+driven by the difference between conditions. The small estimate, as well
+as inspection of Figure 2 suggests that as infants age, their
 mispronunciation sensitivity remains the same.
 
-\subsection{(Insert Figure 2 about
-here)}\label{insert-figure-2-about-here}
+\subsection{(Insert Figure 3 about
+here)}\label{insert-figure-3-about-here}
+
+{[}Christina{]} Can you try and align the axes for both plots?
+{[}Katie{]} I can, but then the dotted line doesn't extend the full way
+(which I think is quite ugly). Not sure how to fix that.
 
@@
 correct pronunciations and mispronunciations (comprehension = 11 papers
-and 43 records; production = 2 papers and 16 records). There is reason
+and 39 records; production = 3 papers and 20 records). There is reason
 to believe that production data are different from comprehension data
 (the former being easier to estimate for parents in the typical
-questionnaire-based assessment; Kidd citation), and we therefore planned
-to analyze these two types of vocabulary measurement separately.
-However, only 2 papers reported correlations with productive vocabulary
-scores, limiting the conclusions that can be drawn. In our vocabulary
-analysis, we therefore focus exclusively on the relationship between
-comprehension and mispronunciation sensitivity.
-
-{[}Christina{]} Removed the previous comment chaos. So can you not only
-list papers but also n conditions above? With just 1 paper for
-production, I wouldn't analyze it to be honest. it's just not enough
-data. I also liked your comments about the time line of this whole
-thing, can you extract the years of papers which report this? Might be
-extremely useful in the discussion and strengthens our case that there
-is no effect, bc people don't find the predicted relation with vocab.
-Also, cann you add a citation for comp vs prod? I think Evan Kidd had a
-paper on it, if you don't have one handy, I can look it up. {[}Katie{]}
-I couldn't find what you are referring to. Could you add the Evan Kidd
-paper? Also, I added a histogram figure below, but I'm not so very sure
-that it is good enough to add to the paper (its under the heading
-\enquote{Potential Vocabulary Figure}). Let me know what you think.
+questionnaire-based assessment; Tomasello \& Mervis, 1994), and we
+therefore planned to analyze these two types of vocabulary measurement
+separately. However, because only 3 papers reported correlations with
+productive vocabulary scores, only limited conclusions that can be
+drawn. In our vocabulary analysis, we therefore focus exclusively on the
+relationship between comprehension and mispronunciation sensitivity.
+
+{[}Katie: Tomasello reference -
+\url{https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1540-5834.1994.tb00186.x}{]}
 
@@
 associated with greater object recognition in response to correct
-pronunciations for 9 of 12 experimental conditions, with correlation
-values ranging from -0.17 to 0.48. The mean effect size Pearson's
-\emph{r} of 0.09 was small and did not differ significantly from zero
-(CI {[}-0.01; 0.19{]} \emph{p} = 0.079). However, the lower bound of the
-CI is close to zero, and one might hypothesize that with more power the
-small relationship might become significant. At the same time, a larger
-sample might confirm our conclusion that there is no relationship. As a
-result, we can not draw firm conclusions about the relationship between
-comprehension scores and object recognition in response to correct
-pronunciations.
+pronunciations for 9 of 10 experimental conditions, with correlation
+values ranging from -0.16 to 0.48. The mean effect size Pearson's
+\emph{r} of 0.14 was small but did differ significantly from zero (CI
+{[}0.03; 0.25{]} \emph{p} = 0.012). However, the lower bound of the CI
+is close to zero and considering the small sample size, one might
+hypothesize that with more power the small relationship might become
+even larger. As a result, we can draw a tentative conclusion that there
+is a positive relationship between comprehension scores and object
+recognition in response to correct pronunciations.
+
+{[}Christina{]} It's significant now! {[}Katie{]} Must be because you
+removed the outliers. I've changed around the wording :)
 
@@
 associated with greater object recognition in response to correct
-pronunciations for 17 of 31 experimental conditions, with correlation
+pronunciations for 17 of 29 experimental conditions, with correlation
 values ranging from -0.35 to 0.57. The mean effect size Pearson's
-\emph{r} of 0.04 was small and did not differ significantly from zero
-(CI {[}-0.03; 0.10{]} \emph{p} = 0.246). Similar to the relationship
-between comprehension scores and correct pronunciation object
-identification, the small correlations and large variances suggest a
-lack of relationship between vocabulary and object recognition for
-mispronunciations. We again emphasize that we cannot draw firm
-conclusions due to the small number of studies we were able to include
-here.
-
-\subsection{Potential Vocabulary
-Figure}\label{potential-vocabulary-figure}
+\emph{r} of 0.05 was small and did not differ significantly from zero
+(CI {[}-0.01; 0.12{]} \emph{p} = 0.119). The small correlation and large
+variances suggest a lack of relationship between vocabulary and object
+recognition for mispronunciations. We again emphasize that we cannot
+draw a firm conclusion due to the small number of studies we were able
+to include here.
+
+Figure 4 plots the year of publication for all the mispronunciation
+sensitivity studies included in this meta-analysis. This figure
+illustrates two things: the growing number of mispronunciation
+sensitivity studies and the waning number of studies measuring
+vocabulary. The lack of evidence for a relationship between
+mispronunciation sensitivity and vocabulary size in early studies may
+have contributed to increasingly fewer researchers including vocabulary
+measurements in their mispronunciation sensitivity experimental design.
+This may explain our underpowered analysis of the relationship between
+mispronunciation sensitivity and vocabulary size.
+
+\subsection{(Insert Figure 4 about
+here)}\label{insert-figure-4-about-here}
 
@@
 a distractor image, there was a consistent effect of mispronunciation
-sensitivity. This did not change with development. Of the 3 predictions
-and assumptions about the development of infants' sensitivity to
-mispronunciations discussed in the Introduction, the present results
-lend some support for the argument that mispronunciation sensitivity
-stays consistent as infants develop. This runs counter to existing
-theories of phono-lexical development, which predict either an increase
-(PRIMR ref) or decrease (Assim Model ref) in mispronunciation
-sensitivity. Furthermore, counter to the predictions for the PRIMR
-(PRIMR ref) and Assimilation(Assim ref) models, we found no relationship
-between vocabulary and target looking for correct pronunciations or
-mispronunciations, although our analyses may be underpowered. In sum, it
+sensitivity. This did not change with development nor with vocabulary
+size. Of the 3 predictions and assumptions about the development of
+infants' sensitivity to mispronunciations discussed in the Introduction,
+the present results lend some support for the argument that
+mispronunciation sensitivity stays consistent as infants develop. This
+runs counter to existing theories of phono-lexical development, which
+predict either an increase (PRIMR ref) or decrease (Assim Model ref) in
+mispronunciation sensitivity. Furthermore, although we found a
+relationship between vocabulary comprehension and target looking for
+correct pronunciations, we found no relationship between vocabulary and
+target looking for mispronunciations. This also runs counter to the
+predictions for the PRIMR (PRIMR ref) and Assimilation (Assim ref)
+models, but may be due to our analyses being underpowered. In sum, it
 seems that current theories of infants' phono-lexical development cannot
-fully capture our results and should be reconsidered with all the
-evidence in mind.
+fully capture our results, but that more investigation is needed to draw
+a firm conclusion.
 
@@
 
-{[}Christina{]} This section talked about several variables in 2
-categories, but in reality there are only 2 variables, right? I am not
-100\% sure about total trial length as being the first or being
-mentioned at all, might it be better to focus on time window analyzed
-and then say \enquote{Oh, btw, total trial length totally does nothing
-so we don't have to discuss it further} I am not sure, so feel free to
-re-rewrite this, but now it better lines up with everything before
-because trial length kinda comes out of nowhere. {[}Katie{]} That's
-fair! I think maybe we don't need the full analysis for total time
-presented or for the offset analysis, but I'd like to still mention them
-because it really shows that its something about this post-naming time
-window choice that influences it, and not just fishing around for
-variability until we find something that works. In the end there are 2
-interesting analyses, but offset could have been interesting (but
-wasn't). Therefore, I'd still like to refer to the timing variables as a
-type of category. Otherwise, we say we'll do size of time window
-analyzed, but then we have information about other timing stuff as well.
-
 We identified two sets of variables which had the potential to vary
@@
 \subsubsection{Timing}\label{timing}
-
-{[}Christina{]} Is there a reason you choose mode and not median?
-{[}Katie{]} Hmm, I felt like mode would be interesting, because it gives
-the most popular choice (74 experimental conditions). But, the median is
-only 500 ms less, so we could use that too (9 experimental conditions).
-
-{[}Christina{]} Would it make sense to present dependent variable first?
-{[}Katie{]} I don't have a strong opinion on this. If you think it would
-be better, then I can change it.
 
@@
 post-naming phase length varied from 2000 to 9000 ms, with a median
-value of 3500 ms. There was an inverse relationship between infant age
-and actual post-naming phase length, such that younger infants were
-presented with longer a longer post-naming phase, although this
-correlation was not significant (\emph{r} = 0.01, \emph{p} = 0.882).
-Presumably, younger infants may be exposed to longer trials because
-their word recognition abilities are expected to be slower than older
-infants (Fernald et al., 1998).
+value of 3500 ms. We note that the most popular actual post-naming phase
+length was 4000 ms, used in \emph{n} = 74 experimental conditions. There
+was an inverse relationship between infant age and actual post-naming
+phase length, such that younger infants were presented with longer a
+longer post-naming phase, although this correlation was not significant
+(\emph{r} = 0.01, \emph{p} = 0.882). Presumably, younger infants may be
+exposed to longer trials because their word recognition abilities are
+expected to be slower than older infants (Fernald et al., 1998).
 
@@
 phase analyzed varied from 1510 to 4000 ms, with a median value of 2500
-ms. Similar to actual post-naming phase length, there was an inverse
-relationship between infant age and the size of the post-naming time
-window analyzed, such that younger infants' looking times were analyzed
-using a longer post-naming time window, here the relationship was
-significant (\emph{r} = -0.23, \emph{p} \textless{} .001). Again, the
-choice to analyze a shorter post-naming time window is likely related to
-evidence that speed of processing is slower in younger infants (Fernald
-et al., 1998). To summarize, we observe variation in time-related
-aspects related to infants' age. This variation is most pronounced, and
-even significant, for the time window that is being analyzed after the
-target label has been heard.
-
-{[}Christina{]} The canfield \& haith paper is for visual stimuli,
-right? So add that before \enquote{stimulus}. And then add to the next
-sentence that the longer latnecies are because ther eis addiitonal
-language processing required which EEg shows in adults to take X ms (400
-for N400?). {[}Katie{]} I agree with the reasoning, but I don't think
-referring to adult ERP literature is the way to go. I've rewritten these
-sentences to be more faithful to the misp sensitivity literature.
-
-{[}Christina{]} Can you add info how many papers did not report the
-analyzed variables? Across this whole section, I mean. {[}Katie{]} All
-papers reported the actual post-naming phase length and the size of the
-post-naming time window analyzed.
+ms. We note that the most popular actual post-naming phase length was
+2000 ms, used in \emph{n} = 97 experimental conditions. Similar to
+actual post-naming phase length, there was an inverse relationship
+between infant age and the size of the post-naming time window analyzed,
+such that younger infants' looking times were analyzed using a longer
+post-naming time window, here the relationship was significant (\emph{r}
+= -0.23, \emph{p} \textless{} .001). Again, the choice to analyze a
+shorter post-naming time window is likely related to evidence that speed
+of processing is slower in younger infants (Fernald et al., 1998). To
+summarize, we observe variation in time-related aspects related to
+infants' age. This variation is most pronounced, and even significant,
+for the time window that is being analyzed after the target label has
+been heard.
 
@@
 
-{[}Christina{]} I think it's a bit inconsistent whether it's post naming
-phase or window, how about window? Phase sounds wrong to me. or analysis
-window? I also find phase size odd, and again prefer window (window
-size). Your call though. {[}Katie{]} I agree and I've updated it to
-refer to window size when talking about the analyzed portion and to
-phase when refering to it as the entire actual presentation time.
-
 We first assessed whether size of the post-naming time window analyzed
@@
 additional moderator. The moderator test was significant, QM(3) =
-236.958, \emph{p}\textless{} .001. The estimate for the interaction
+236.958, \emph{p} \textless{} .001. The estimate for the interaction
 between post-naming phase size and condition was small but significant
-\(\beta\) = -0.262, SE = 0.059, 95\% CI{[}-0.377, -0.148{]},
-\emph{p}\textless{} .001. This relationship is plotted in Figure 3a. The
-results suggest that the size of the post-naming phase analyzed
-significantly impacted mispronunciation sensitivity. Specifically, the
-difference between target fixations for correctly pronounced and
-mispronounced items (mispronunciation sensitivity) was significantly
-greater when the post-naming phase that was shorter in length.
+\(\beta\) = -0.262, SE = 0.059, 95\% CI{[}-0.377, -0.148{]}, \emph{p}
+\textless{} .001. This relationship is plotted in Figure 3a. The results
+suggest that the size of the post-naming phase analyzed significantly
+impacted mispronunciation sensitivity. Specifically, the difference
+between target fixations for correctly pronounced and mispronounced
+items (mispronunciation sensitivity) was significantly greater when the
+post-naming phase that was shorter in length.
 
@@
 additional moderators. The moderator test was significant QM(7) =
-247.322, \emph{p}\textless{} .001. The estimate for the
+247.322, \emph{p} \textless{} .001. The estimate for the
 three-way-interaction between condition, size of post-naming phase, and
 age was small, but significant (\(\beta\) = = -0.04, SE = 0.014, 95\%
-CI{[}-0.068, -0.012{]}, \emph{p}= 0.006. As can be seen in Figure 3b,
+CI{[}-0.068, -0.012{]}, \emph{p} = 0.006. As can be seen in Figure 3b,
 smaller post-naming time window size leads to greater increases in
@@
 
-\subsection{(Insert Figure 3 about
-here)}\label{insert-figure-3-about-here}
+\subsection{(Insert Figure 5 about
+here)}\label{insert-figure-5-about-here}
 
@@
 
-{[}Christina{]} Generally, it might be easier to kick out all object
-recognition analyses (what do they tell us?) and start out that we only
-analyze MP sensitivity, i.e.~consider the whole dataset and always
-include condition as moderator. {[}Katie{]} Agreed! I've gotten rid of
-all of the object recognition analyses and added an explanation at the
-beginning of the Exploratory Analysis section.
-
 We next assessed whether the time between the target was named and the
@@
 condition and offset time as moderators, the moderator test was
-significant, QM(3) = 236.958, \emph{p}\textless{} .001, but the estimate
-for the interaction between offset time and condition was almost zero
-\(\beta\) = 0, SE = 0, 95\% CI{[}-0.001, 0{]}, \emph{p}= 0.505. Although
-we found no relationship between offset time and infant age, we also
-examined whether the size of offset time modulated the development of
-mispronunciation sensitivity. When both offset time and condition were
-included as moderators, the moderator test was significant QM(7) =
-200.867, \emph{p}\textless{} .001, but the three-way-interaction between
-condition, offset time, and age was very small and not significant
-(\(\beta\) = = 0, SE = 0, 95\% CI{[}0, 0{]}, \emph{p}= 0.605. Taken
-together, these results suggest that offset time does not modulate
-mispronunciation sensitivity. There is no relationship between offset
-time and age, and we find no influence of offset time on the development
-of mispronunciation sensitivity.
+significant, QM(3) = 236.958, \emph{p} \textless{} .001, but the
+estimate for the interaction between offset time and condition was
+almost zero \(\beta\) = 0, SE = 0, 95\% CI{[}-0.001, 0{]}, \emph{p} =
+0.505. Although we found no relationship between offset time and infant
+age, we also examined whether the size of offset time modulated the
+development of mispronunciation sensitivity. When both offset time and
+condition were included as moderators, the moderator test was
+significant QM(7) = 200.867, \emph{p} \textless{} .001, but the
+three-way-interaction between condition, offset time, and age was very
+small and not significant (\(\beta\) = = 0, SE = 0, 95\% CI{[}0, 0{]},
+\emph{p} = 0.605. Taken together, these results suggest that offset time
+does not modulate mispronunciation sensitivity. There is no relationship
+between offset time and age, and we find no influence of offset time on
+the development of mispronunciation sensitivity.
 
@@
 one for the post-naming phase. A greater post compared to pre-naming
-phase PTL indicates that increased their target looks after hearing the
-naming label. We will refer to this dependent variable as Pre vs.~Post.
-Finally, the remaining 53 experimental conditions compared the
-post-naming PTL score with a chance value of 50\%. Here, the infants'
-pre-naming phase preferences are not considered and instead target
-fixations are evaluated based on the likelihood to fixate one of two
-pictures. We will refer to this dependent variable as Post.
-
-{[}Christina{]} Did I ask the following already: Do we know whether
-subtrations were on the trial level? Pre vs post is a bit differnt
-because it loses the individual bias accommodation and the correlation
-between pre and post on the participant / item level. {[}Katie{]} You
-did. I'll put here my answer from before: From working with Nivi, we did
-it participants x condition or participants x trial (but mostly the
-former). But, this is not something we reported in papers. I don't think
-I read it at all when putting together the dataset for this either.
+phase PTL indicates that infants increased their target looks after
+hearing the naming label. We will refer to this dependent variable as
+Pre vs.~Post. Finally, the remaining 53 experimental conditions compared
+the post-naming PTL score with a chance value of 50\%. Here, the
+infants' pre-naming phase preferences are not considered and instead
+target fixations are evaluated based on the likelihood to fixate one of
+two pictures. We will refer to this dependent variable as Post.
 
@@
 condition and dependent variable as moderators, the moderator test was
-significant QM(5) = 259.817, \emph{p}\textless{} .001. The estimate for
+significant QM(5) = 259.817, \emph{p} \textless{} .001. The estimate for
 the interaction between Pre vs.~Post and condition was significantly
 smaller than that of the Post dependent variable (\(\beta\) = -0.392, SE
-= 0.101, 95\% CI{[}-0.59, -0.194{]}, \emph{p}\textless{} .001), but the
+= 0.101, 95\% CI{[}-0.59, -0.194{]}, \emph{p} \textless{} .001), but the
 difference between the Difference Score and Post in the interaction with
 condition was small and not significant (\(\beta\) = -0.01, SE = 0.098,
-95\% CI{[}-0.203, 0.183{]}, \emph{p}= 0.916). This relationship is
+95\% CI{[}-0.203, 0.183{]}, \emph{p} = 0.916). This relationship is
 plotted in Figure 4a. The results suggest that dependent variable
@@
 included as an additional moderator, the moderator test was significant
-QM(11) = 273.585, \emph{p}\textless{} .001. The estimate for the
+QM(11) = 273.585, \emph{p} \textless{} .001. The estimate for the
 interaction between Pre vs.~Post, condition, and age was significantly
 smaller than that of the Post dependent variable (\(\beta\) = -0.089, SE
-= 0.03, 95\% CI{[}-0.148, -0.03{]}, \emph{p}= 0.003), but the difference
-between the Difference Score and Post in the interaction with condition
-and age was small and not significant (\(\beta\) = -0.036, SE = 0.027,
-95\% CI{[}-0.088, 0.016{]}, \emph{p}= 0.174). This relationship is
-plotted in Figure 4b. When the dependent variable was Pre vs.~Post,
-mispronunciation sensitivity decreased with infant age, while in
-comparison, when the dependent variable was Post, mispronunciation
-sensitivity increased with infant age. There was no difference in
-mispronunciation sensitivity change with infant development between the
-Post and Difference Score dependent variables.
-
-\subsection{(Insert Figure 4 about
-here)}\label{insert-figure-4-about-here}
+= 0.03, 95\% CI{[}-0.148, -0.03{]}, \emph{p} = 0.003), but the
+difference between the Difference Score and Post in the interaction with
+condition and age was small and not significant (\(\beta\) = -0.036, SE
+= 0.027, 95\% CI{[}-0.088, 0.016{]}, \emph{p} = 0.174). This
+relationship is plotted in Figure 4b. When the dependent variable was
+Pre vs.~Post, mispronunciation sensitivity decreased with infant age,
+while in comparison, when the dependent variable was Post,
+mispronunciation sensitivity increased with infant age. There was no
+difference in mispronunciation sensitivity change with infant
+development between the Post and Difference Score dependent variables.
+Similar to size of post-naming time window analyzed, all three possible
+developmental hypotheses might be supported depending on the dependent
+variable reported. In other words, choice of dependent variable may
+influence the conclusion drawn regarding how mispronunciation
+sensitivity may change with infant age.
+
+\subsection{(Insert Figure 6 about
+here)}\label{insert-figure-6-about-here}
 
@@
 
-\section{Discussion}\label{discussion}
-
-To Summarize:
-
-** Overall Meta-analytic Effect **
-
-\begin{itemize}
-\tightlist
-\item
-  Accept mispronunciations as labels for targets
-\item
-  Sensitive to mispronunciations
-\item
-  lack of change over development
-\end{itemize}
-
-** Vocabulary **
-
-\begin{itemize}
-\tightlist
-\item
-  no relationship?
-\item
-  talk about how few studies report it
-\end{itemize}
+\section{General Discussion}\label{general-discussion}
+
+Overall, infants showed reliable correct object recognition when given
+both correctly pronounced and mispronounced labels. In other words, not
+only did infants correctly recognize object labels when they were
+correctly pronounced, they also were likely to accept mispronunciations
+as acceptable labels for targets. Mispronounced labels were considered a
+better match for target images than a distractor image, despite the
+differences in the phonological form of correctly pronounced and
+mispronounced words. Nonetheless, there was a considerable difference in
+target fixations in response to correctly pronounced and mispronounced
+labels, suggesting overall mispronunciation sensitivity in the current
+experimental literature.
+
+We next evaluated the developmental trajectory of infants'
+mispronunciation sensitivity. Based on previous theoretical accounts and
+existing experimental evidence, we envisioned three possible
+developmental patterns: increasing sensitivity, decreasing sensitivity,
+and unchanging sensitivity. We observed no influence of age when it was
+considered as a moderator of mispronunciation sensitivity. Of the two
+mainstream theories identified in our literature review, neither the
+Perceptual Attunement account (Best 1994, 1995) nor PRIMIR (Curtin \&
+Werker, 2007; Werker \& Curtin, 2005) account for a lack of
+developmental change. The results of our meta-analysis are supported by
+a handful of studies directly comparing infants over a range of ages
+(Swingley \& Aslin, 2000; Bailey \& Plunkett, 2002; Zesiger et al.,
+2012), which also found no developmental change in mispronunciation
+sensitivity.
+
+Both the Perceptual Attunement (Best 1994, 1995) and PRIMIR (Curtin \&
+Werker, 2007; Werker \& Curtin, 2005) accounts link a change of
+mispronunciation sensitivity specifically with vocabulary growth, in
+comparison to development in general. Vocabulary growth leads to an
+increase (PRIMIR; Curtin \& Werker, 2007; Werker \& Curtin, 2005) or
+decrease (Perceptual Attunement; Best 1994, 1995) in mispronunciation
+sensitivity and vocabulary is expected to grow considerably in the age
+range considered in the current meta-analysis (see
+wordbank.stanford.edu; Frank et al., 2017). The lack of developmental
+effects found in the meta-analysis may therefore be due to using age,
+instead of vocabulary growth, as a facilitator for change in
+mispronunciation sensitivity. Yet, an analysis of correlations between
+vocabulary size and object recognition effect sizes does not support
+this argument. Although an increasing vocabulary size lead to increased
+object recognition for correctly pronounced words, this was not the case
+for mispronunciations. Some previous experimental evidence also supports
+a lack of a relationship between vocabulary size and mispronunciation
+sensitivity (e.g.~Mani \& Plunkett, 2007; Swingley \& Aslin, 2000; but
+see Mani \& Plunkett, 2010). This would suggest that object recognition
+for mispronunciations is not modulated by vocabulary size, contrary to
+the predictions of the Perceptual Attunement (Best 1994, 1995) and
+PRIMIR (Curtin \& Werker, 2007; Werker \& Curtin, 2005) accounts and
+further supporting the overall lack of an influence of age on
+mispronunciation sensitivity.
+
+What may these results mean for our understanding of phono-lexical
+development in infancy? Evidence that infants accept a mispronunciation
+(object identification) while simultaneously holding correctly
+pronounced and mispronounced labels as separate (mispronunciation
+sensitivity) may indcate an abstract understanding of words'
+phonological structure. It appears infants may understand that the
+mispronunciation and correct pronunciation's phonological form do not
+match, but that the mispronunciation is a better label for the target
+compared to the distractor image. The lack of age or vocabulary effects
+in our meta-analysis suggest that this understanding is present from an
+age when the earliest words are learned and is maintained throughout
+early lexical development. Already with the first words, infants have a
+sense of the importance of sounds in the words present in their lexicon.
+We recommend that future theoretical accounts should consider this lack
+of developmental change.
+
+Although the lack of an relationship between mispronunciation
+sensitivity and vocabulary size may reflect a true effect, we note that
+this may also be the result of an underpowered analysis. Despite the
+theoretical implications, less than half of the papers included in this
+meta-analysis measured vocabulary (\emph{n} = 13; out of 32 papers
+total). We suggest that this may be the result of publication bias,
+specifically a desire to not publish null results. Although the number
+of mispronunciation sensitivity studies has experience growth, this has
+not translated to an increasing number of mispronunciation sensitivity
+studies also measuring vocabulary scores.
+
+{[}Katie{]} The above section is a bit clunky and I don't like it. Any
+suggestions for improvement?
+
+Then talk about the experimental decisions
 
@@
 \end{itemize}
+
+{[}Christina{]} Did I ask the following already: Do we know whether
+subtrations were on the trial level? Pre vs post is a bit differnt
+because it loses the individual bias accommodation and the correlation
+between pre and post on the participant / item level. {[}Katie{]} You
+did. I'll put here my answer from before: From working with Nivi, we did
+it participants x condition or participants x trial (but mostly the
+former). But, this is not something we reported in papers. I don't think
+I read it at all when putting together the dataset for this either.
+{[}Christina{]} Mention in the discussion that we don't know this and it
+might be important to establish standard analysis pipelines for MP
+studies and that we need open data and code? ;)
 

### 2018-12-04 Paper_Analyses.Rmd
first draft General Discussion

@@
 ```
-
-[Christina: Big change: I just realized that we also need to report where we could not compute effect sizes, added this info. ]
 
@@
 
-## Controlling for analysis choices
-
-```{r reanalysis_misp_sens_dv_label}
-
-dat$dv_label <- ifelse(dat$within_measure=="post", "Post",
-                       ifelse(dat$within_measure == "pre_post", "Post vs. Pre",
-                              "Difference Score"))
-
-dat$dv_label <- factor(dat$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
-
-db_ET_MP$dv_label <- ifelse(db_ET_MP$within_measure=="post", "Post",
-                       ifelse(db_ET_MP$within_measure == "pre_post", "Post vs. Pre",
-                              "Difference Score"))
-
-db_ET_MP$dv_label <- factor(db_ET_MP$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
-
-db_ET_correct$dv_label <- ifelse(db_ET_correct$within_measure=="post", "Post",
-                       ifelse(db_ET_correct$within_measure == "pre_post", "Post vs. Pre",
-                              "Difference Score"))
-
-db_ET_correct$dv_label <- factor(db_ET_correct$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
-
-rma_correct_DV = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
-
-#anova(rma_correct_DV, rma_correct)
-
-rma_MP_DV = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
-
-#anova(rma_MP_DV, rma_MP)
-
-rma_MPeffect_DV <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
-
-#anova(rma_MPeffect_DV, rma_MPeffect)
-
-rma_correct_age_DV = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
-
-#anova(rma_correct_age_DV, rma_correct_age)
-
-rma_MP_age_DV = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
-
-#anova(rma_MP_age_DV, rma_MP_age)
-
-rma_MPeffect_age_DV <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
-
-#anova(rma_MPeffect_age_DV, rma_MPeffect_age)
-
-```
-
-```{r reanalysis_misp_sens_post_dur}
-
-rma_correct_post_dur = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
-
-#anova(rma_correct_post_dur, rma_correct)
-
-rma_MP_post_dur = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
-
-#anova(rma_MP_post_dur, rma_MP)
-
-rma_MPeffect_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
-
-#anova(rma_MPeffect_post_dur, rma_MPeffect)
-
-rma_correct_age_post_dur = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
-
-#anova(rma_correct_age_post_dur, rma_correct_age)
-
-rma_MP_age_post_dur = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
-
-#anova(rma_MP_age_post_dur, rma_MP_age)
-
-rma_MPeffect_age_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
-
-#anova(rma_MPeffect_age_post_dur, rma_MPeffect_age)
-
-```
-
 # General Discussion
@@
 
-What may these results mean for our understanding of phono-lexical development in infancy?
 Evidence that infants accept a mispronunciation (object identification) while simultaneously holding correctly pronounced and mispronounced labels as separate (mispronunciation sensitivity) may indcate an abstract understanding of words' phonological structure.
-It appears infants may understand that the mispronunciation and correct pronunciation's phonological form do not match, but that the mispronunciation is a better label for the target compared to the distractor image.
+It appears that young infants may understand that the mispronunciation and correct pronunciation's phonological form do not match (phonological distinctiveness), but that the mispronunciation is a better label for the target compared to the distractor image (phonological constancy).
 The lack of age or vocabulary effects in our meta-analysis suggest that this understanding is present from an age when the earliest words are learned and is maintained throughout early lexical development.
-Already with the first words, infants have a sense of the importance of sounds in  the words present in their lexicon.
-We recommend that future theoretical accounts should consider this lack of developmental change.
+This implies mastery of the principles of phonological constancy and phonological distinctiveness at an age earlier than previously thought, which we recommend should be taken into account by future theoretical accounts.
 
@@
 
-Then talk about the experimental decisions
-
-** Data Analysis Choices **
-
-  + Post-naming time window size and dependent variable impact misp sensitivity development
-  + Offset time does not impact misp sensitivity development
-  + the first two do not have theoretical frameworks to guide researchers, whereas offset time does
-
-  [Christina] Did I ask the following already: Do we know whether subtrations were on the trial level?
-Pre vs post is a bit differnt because it loses the individual bias accommodation and the correlation between pre and post on the participant / item level.
-[Katie] You did. I'll put here my answer from before:
-From working with Nivi, we did it participants x condition or participants x trial (but mostly the former).
-But, this is not something we reported in papers.
-I don't think I read it at all when putting together the dataset for this either.
-[Christina] Mention in the discussion that we don't know this and it might be important to establish standard analysis pipelines for MP studies and that we need open data and code? ;)
-
-When it comes to designing studies, best practices and current standards might not always overlap.
-Indeed, across a set of previous meta-analyses it was shown that particularly infant research does not adjust sample sizes according to the effect in question (Bergmann et al., in press).
-A meta-analysis is a first step in improving experiment planning by measuring the underlying effect and its variance, which is directly related to the sample needed to achieve satisfactory power in the null hypothesis significance testing framework.
-Failing to take effect sizes into account can both yield to underpowered research and to testing too many participants, both consequences are undesirable for a number of reasons that have been discussed in depth elsewhere.
-We will just briefly mention two that we consider most salient for theory building: Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature (citationcitation).
-Overpowered studies mean that participants were tested unnecessarily, which has substantial ethical consequences particularly when working with infants and other difficult to recruit and test populations.
-
-From Christina: let's make a note to put sth in the discussion about our curve being surprisingly flat for correctly pronounced words bc people adapt their analysis windows?
-Bc if you look at Molly's reaction time paper, there is a steep increase.
+While creating the dataset on which this meta-analysis was based, we included as many details as possible to describe each study.
+During the coding of these characteristics, we noted a potential for variation in a handful of variables that relate to data analysis, specifically relating to timing (size of time window analyzed; offset time) and which dependent variable(s) were reported.
+We focused on these variables in particular because their choice can potentially be made after researchers have examined the data, leading to an inflated increase of significant results which may also explain the publication bias observed in the funnel plot assymmetry (Simmons, Nelson, & Simonsohn, 2011).
+To explore whether this variation contributed to the lack of developmental change observed in the overall meta-analysis, we included these variables as moderators in a set of exploratory analyses.
+We noted an interesting pattern of results, specifically that different conclusions about mispronunciation sensitivity, but more notably mispronunciation sensitivity development, could be drawn depending on the length of the post-naming time window analyzed as well as the type of dependent variable calculated in the experiment.
+
+Considering the timing variable, infants are expected to recognize words more quickly with age (Fernald, Swingley & Pinto, 2001; Swingley, Pinto & Fernald, 1999; Swingley & Fernald, 2002).
+This evidence has often guided decisions for the post-naming time window to be analyzed in mispronunciation sensitivity studies, including where to begin the time window (offset time) and how long this window should be (post-naming time window analyzed).
+Specifically, increasing age should lead to quicker reaction times, and therefore lower offset times.
+Yet, we found no evidence for a relationship between offset time and infant age nor that offset time modulated mispronunciation sensitivity.
+Indeed, a large majority used an offset time between 360 and 370 ms, which follows the best guess of Swingley and Aslin (2000) for the amount of time needed for infants to initiate eye movements in response to a spoken target word.
+
+In contrast, the length of the post-naming window analyzed was related to infant age and also found to modulate mispronunciation sensitivity.
+Younger infants may take longer to reliably identify the target image, and as a result the length of the post-naming time window analyzed may be longer in younger infants.
+This was born out in the meta-analysis: studies that tested younger infants used a longer post-naming time window.
+Longer post-naming time windows, however, resulted in a smaller effect size for mispronunciation sensitivity.
+Critically, the developmental trajectory of mispronunciation sensitivity changed depending on the length of the post-naming time window analyzed.
+Longer time windows resulted in decreasing or no change in mispronunciation sensitivity, while shorter time windows resulting in increasing mispronunciation sensitivity.
+Given a set of mispronunciation sensitivity data, a conclusion regarding the development of mispronunciation sensitivity would be different depending on the length of the post-naming time window analyzed.
+
+Unlike the timing variables, the origin of a potential relationship between the type of dependent variable calculated and mispronunciation sensitivity is much less clear.
+The majority of studies created a Difference Score, subtracting pre-naming phase PTL from that of post-naming phase PTL, while the remaining studies compared pre-naming PTL with post-naming PTL (Pre vs.
+Post) or analyzed post-naming PTL alone (Post).
+Both the Difference Score and the Pre vs.
+Post dependent variables consider pre-naming phase preferences for the target compared to distractor image, but were found to differentially modulate mispronunciation sensitivity.
+There was no difference in mispronunciation sensitivity between the Post and Difference Score dependent variables, but in comparison to Post, studies that reported the Pre vs.
+Post dependent variable had lower effect sizes for mispronunciation sensitivity.
+Furthermore, studies reporting the Pre vs.
+Post dependent variable showed decreasing mispronunciation sensitivity with age, while studies reporting a Difference Score or Post dependent variable showed an increase.
+Similar to the length of the post-naming time window analyzed, given a set of mispronunciation sensitivity data, a conclusion regarding the development of mispronunciation sensitivity would be different depending on the choice of dependent variable.
+
+Without access to the full datasets of the studies included in this meta-analysis, it is difficult to pinpoint the exact role played by these data analysis choices, specificially the length of the post-naming time window analyzed and the type of dependent variable reported.
+Access to such data would allow for a systematic analysis of the influence of these choices on the size of the effect of mispronunciation sensitivity as well as its developmental trajectory.
+Furthermore, sharing analysis code would allow for a clearer understanding of the approach to data analysis.
+For example, the Difference Score dependent variable substracts the pre-naming phase PTL from the post-naming phase PTL.
+Some studies compute this variable on the level of condition (e.g.
+White & Morgan, 2008), but this reduces SOMETHING, WHICH IS A BAD SOMETHING [Katie].
+In addition to shared data and code, it may be useful to establish standard analysis pipelines for mispronunciation studies.
+This would allow for a more uniform analysis of this phenomenon, as well as aid experimenters in future research planning.
+Finally, we recommend that experimenters consider analyzing the time course as a whole, instead of aggregating the proportion of target looking behavior over the entire trial.
+Both Growth Curve Analysis (Mirman et al., 2008; Law & Edwards, 2015) and Permutation Clusters Analysis (Maris & Oostenveld, 2007; Von Holzen & Mani, 2012) offer potential solutions for time course analysis.
 

### 2018-12-04 Paper_Analyses.tex
first draft General Discussion

@@
 
-{[}Christina: Big change: I just realized that we also need to report
-where we could not compute effect sizes, added this info. {]}
-
 \section{Introduction}\label{introduction}
@@
 Bailey \& Plunkett (2002) & paper & 18, 24 & Comp & 12\\
+Ballem \& Plunkett (2005) & paper & 14 & None & 4\\
 Bergelson \& Swingley (2017) & paper & 6, 7, 9, 12 & None & 9\\
@@
 Ren \& Morgan (in press) & gray paper & 19 & None & 8\\
-Skoruppa et al. (2013) & paper & 23 & None & 4\\
+Renner (2017) & dissertation & 17, 24 & None & 6\\
+Skoruppa et al. (2013) & paper & 23 & None & 5\\
 Swingley (2003) & paper & 19 & Comp/Prod & 6\\
@@
 image versus a distractor in a eye movement experiment; (5) the stimuli
-were auditory speech. The final sample (n = \emph{32}) consisted of 27
-journal articles, 1 proceedings paper, 2 thesis, and 2 unpublished
+were auditory speech. The final sample (n = \emph{34}) consisted of 28
+journal articles, 1 proceedings paper, 3 thesis, and 2 unpublished
 reports. We will refer to these items collectively as papers. Table 1
@@
 
-The 32 papers we identified as relevant were then coded with as much
+The 34 papers we identified as relevant were then coded with as much
 consistently reported detail as possible (Tsuji, Bergmann, \& Cristia,
@@
 analyses (see next section). We will call each row a record; in total
-there were 260 records in our data.
+there were 271 records in our data.
 
@@
 (Swingley, 2016; Altvater-Mackensen et al., 2014). Raw means and
-standard deviations were extracted from figures for 3 papers. In a
+standard deviations were extracted from figures for 4 papers. In a
 within-participation design, when two means are compared (i.e.~looking
@@
 
-\subsection{Controlling for analysis
-choices}\label{controlling-for-analysis-choices}
-
 \section{General Discussion}\label{general-discussion}
@@
 
-What may these results mean for our understanding of phono-lexical
-development in infancy? Evidence that infants accept a mispronunciation
-(object identification) while simultaneously holding correctly
-pronounced and mispronounced labels as separate (mispronunciation
-sensitivity) may indcate an abstract understanding of words'
-phonological structure. It appears infants may understand that the
-mispronunciation and correct pronunciation's phonological form do not
-match, but that the mispronunciation is a better label for the target
-compared to the distractor image. The lack of age or vocabulary effects
-in our meta-analysis suggest that this understanding is present from an
-age when the earliest words are learned and is maintained throughout
-early lexical development. Already with the first words, infants have a
-sense of the importance of sounds in the words present in their lexicon.
-We recommend that future theoretical accounts should consider this lack
-of developmental change.
+Evidence that infants accept a mispronunciation (object identification)
+while simultaneously holding correctly pronounced and mispronounced
+labels as separate (mispronunciation sensitivity) may indcate an
+abstract understanding of words' phonological structure. It appears that
+young infants may understand that the mispronunciation and correct
+pronunciation's phonological form do not match (phonological
+distinctiveness), but that the mispronunciation is a better label for
+the target compared to the distractor image (phonological constancy).
+The lack of age or vocabulary effects in our meta-analysis suggest that
+this understanding is present from an age when the earliest words are
+learned and is maintained throughout early lexical development. This
+implies mastery of the principles of phonological constancy and
+phonological distinctiveness at an age earlier than previously thought,
+which we recommend should be taken into account by future theoretical
+accounts.
 
@@
 
-Then talk about the experimental decisions
-
-** Data Analysis Choices **
-
-\begin{itemize}
-\tightlist
-\item
-  Post-naming time window size and dependent variable impact misp
-  sensitivity development
-\item
-  Offset time does not impact misp sensitivity development
-\item
-  the first two do not have theoretical frameworks to guide researchers,
-  whereas offset time does
-\end{itemize}
-
-{[}Christina{]} Did I ask the following already: Do we know whether
-subtrations were on the trial level? Pre vs post is a bit differnt
-because it loses the individual bias accommodation and the correlation
-between pre and post on the participant / item level. {[}Katie{]} You
-did. I'll put here my answer from before: From working with Nivi, we did
-it participants x condition or participants x trial (but mostly the
-former). But, this is not something we reported in papers. I don't think
-I read it at all when putting together the dataset for this either.
-{[}Christina{]} Mention in the discussion that we don't know this and it
-might be important to establish standard analysis pipelines for MP
-studies and that we need open data and code? ;)
-
-When it comes to designing studies, best practices and current standards
-might not always overlap. Indeed, across a set of previous meta-analyses
-it was shown that particularly infant research does not adjust sample
-sizes according to the effect in question (Bergmann et al., in press). A
-meta-analysis is a first step in improving experiment planning by
-measuring the underlying effect and its variance, which is directly
-related to the sample needed to achieve satisfactory power in the null
-hypothesis significance testing framework. Failing to take effect sizes
-into account can both yield to underpowered research and to testing too
-many participants, both consequences are undesirable for a number of
-reasons that have been discussed in depth elsewhere. We will just
-briefly mention two that we consider most salient for theory building:
-Underpowered studies will lead to false negatives more frequently than
-expected, which in turn results in an unpublished body of literature
-(citationcitation). Overpowered studies mean that participants were
-tested unnecessarily, which has substantial ethical consequences
-particularly when working with infants and other difficult to recruit
-and test populations.
-
-From Christina: let's make a note to put sth in the discussion about our
-curve being surprisingly flat for correctly pronounced words bc people
-adapt their analysis windows? Bc if you look at Molly's reaction time
-paper, there is a steep increase.
+While creating the dataset on which this meta-analysis was based, we
+included as many details as possible to describe each study. During the
+coding of these characteristics, we noted a potential for variation in a
+handful of variables that relate to data analysis, specifically relating
+to timing (size of time window analyzed; offset time) and which
+dependent variable(s) were reported. We focused on these variables in
+particular because their choice can potentially be made after
+researchers have examined the data, leading to an inflated increase of
+significant results which may also explain the publication bias observed
+in the funnel plot assymmetry (Simmons, Nelson, \& Simonsohn, 2011). To
+explore whether this variation contributed to the lack of developmental
+change observed in the overall meta-analysis, we included these
+variables as moderators in a set of exploratory analyses. We noted an
+interesting pattern of results, specifically that different conclusions
+about mispronunciation sensitivity, but more notably mispronunciation
+sensitivity development, could be drawn depending on the length of the
+post-naming time window analyzed as well as the type of dependent
+variable calculated in the experiment.
+
+Considering the timing variable, infants are expected to recognize words
+more quickly with age (Fernald, Swingley \& Pinto, 2001; Swingley, Pinto
+\& Fernald, 1999; Swingley \& Fernald, 2002). This evidence has often
+guided decisions for the post-naming time window to be analyzed in
+mispronunciation sensitivity studies, including where to begin the time
+window (offset time) and how long this window should be (post-naming
+time window analyzed). Specifically, increasing age should lead to
+quicker reaction times, and therefore lower offset times. Yet, we found
+no evidence for a relationship between offset time and infant age nor
+that offset time modulated mispronunciation sensitivity. Indeed, a large
+majority used an offset time between 360 and 370 ms, which follows the
+best guess of Swingley and Aslin (2000) for the amount of time needed
+for infants to initiate eye movements in response to a spoken target
+word.
+
+In contrast, the length of the post-naming window analyzed was related
+to infant age and also found to modulate mispronunciation sensitivity.
+Younger infants may take longer to reliably identify the target image,
+and as a result the length of the post-naming time window analyzed may
+be longer in younger infants. This was born out in the meta-analysis:
+studies that tested younger infants used a longer post-naming time
+window. Longer post-naming time windows, however, resulted in a smaller
+effect size for mispronunciation sensitivity. Critically, the
+developmental trajectory of mispronunciation sensitivity changed
+depending on the length of the post-naming time window analyzed. Longer
+time windows resulted in decreasing or no change in mispronunciation
+sensitivity, while shorter time windows resulting in increasing
+mispronunciation sensitivity. Given a set of mispronunciation
+sensitivity data, a conclusion regarding the development of
+mispronunciation sensitivity would be different depending on the length
+of the post-naming time window analyzed.
+
+Unlike the timing variables, the origin of a potential relationship
+between the type of dependent variable calculated and mispronunciation
+sensitivity is much less clear. The majority of studies created a
+Difference Score, subtracting pre-naming phase PTL from that of
+post-naming phase PTL, while the remaining studies compared pre-naming
+PTL with post-naming PTL (Pre vs.~Post) or analyzed post-naming PTL
+alone (Post). Both the Difference Score and the Pre vs.~Post dependent
+variables consider pre-naming phase preferences for the target compared
+to distractor image, but were found to differentially modulate
+mispronunciation sensitivity. There was no difference in
+mispronunciation sensitivity between the Post and Difference Score
+dependent variables, but in comparison to Post, studies that reported
+the Pre vs.~Post dependent variable had lower effect sizes for
+mispronunciation sensitivity. Furthermore, studies reporting the Pre
+vs.~Post dependent variable showed decreasing mispronunciation
+sensitivity with age, while studies reporting a Difference Score or Post
+dependent variable showed an increase. Similar to the length of the
+post-naming time window analyzed, given a set of mispronunciation
+sensitivity data, a conclusion regarding the development of
+mispronunciation sensitivity would be different depending on the choice
+of dependent variable.
+
+Without access to the full datasets of the studies included in this
+meta-analysis, it is difficult to pinpoint the exact role played by
+these data analysis choices, specificially the length of the post-naming
+time window analyzed and the type of dependent variable reported. Access
+to such data would allow for a systematic analysis of the influence of
+these choices on the size of the effect of mispronunciation sensitivity
+as well as its developmental trajectory. Furthermore, sharing analysis
+code would allow for a clearer understanding of the approach to data
+analysis. For example, the Difference Score dependent variable
+substracts the pre-naming phase PTL from the post-naming phase PTL. Some
+studies compute this variable on the level of condition (e.g.~White \&
+Morgan, 2008), but this reduces SOMETHING, WHICH IS A BAD SOMETHING
+{[}Katie{]}. In addition to shared data and code, it may be useful to
+establish standard analysis pipelines for mispronunciation studies. This
+would allow for a more uniform analysis of this phenomenon, as well as
+aid experimenters in future research planning. Finally, we recommend
+that experimenters consider analyzing the time course as a whole,
+instead of aggregating the proportion of target looking behavior over
+the entire trial. Both Growth Curve Analysis (Mirman et al., 2008; Law
+\& Edwards, 2015) and Permutation Clusters Analysis (Maris \&
+Oostenveld, 2007; Von Holzen \& Mani, 2012) offer potential solutions
+for time course analysis.
 

### 2018-12-04 Paper_Analyses_sandbox.Rmd
updated methods/results
first draft General Discussion

@@
 
-# mf <- subset(dat_f, n_feature == "3")
-# min_age <- min(mf$mean_age_1)
-# max_age <- max(mf$mean_age_1)
-# 
-# dat_fage= dat_f%>%
-#   filter(mean_age_1>=min_age&mean_age_1<=max_age)
-
 dat_f$feat_cat <- ifelse(dat_f$n_feature == 1, "1-feature",
@@
 (95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
+
+## Controlling for analysis choices
+
+```{r reanalysis_misp_sens_dv_label}
+
+dat$dv_label <- ifelse(dat$within_measure=="post", "Post",
+                       ifelse(dat$within_measure == "pre_post", "Post vs. Pre",
+                              "Difference Score"))
+
+dat$dv_label <- factor(dat$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
+
+db_ET_MP$dv_label <- ifelse(db_ET_MP$within_measure=="post", "Post",
+                       ifelse(db_ET_MP$within_measure == "pre_post", "Post vs. Pre",
+                              "Difference Score"))
+
+db_ET_MP$dv_label <- factor(db_ET_MP$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
+
+db_ET_correct$dv_label <- ifelse(db_ET_correct$within_measure=="post", "Post",
+                       ifelse(db_ET_correct$within_measure == "pre_post", "Post vs. Pre",
+                              "Difference Score"))
+
+db_ET_correct$dv_label <- factor(db_ET_correct$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
+
+rma_correct_DV = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
+
+#anova(rma_correct_DV, rma_correct)
+
+rma_MP_DV = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
+
+#anova(rma_MP_DV, rma_MP)
+
+rma_MPeffect_DV <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
+
+#anova(rma_MPeffect_DV, rma_MPeffect)
+
+rma_correct_age_DV = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
+
+#anova(rma_correct_age_DV, rma_correct_age)
+
+rma_MP_age_DV = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
+
+#anova(rma_MP_age_DV, rma_MP_age)
+
+rma_MPeffect_age_DV <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
+
+#anova(rma_MPeffect_age_DV, rma_MPeffect_age)
+
+```
+
+```{r reanalysis_misp_sens_post_dur}
+
+rma_correct_post_dur = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+
+#anova(rma_correct_post_dur, rma_correct)
+
+rma_MP_post_dur = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+
+#anova(rma_MP_post_dur, rma_MP)
+
+rma_MPeffect_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+
+#anova(rma_MPeffect_post_dur, rma_MPeffect)
+
+rma_correct_age_post_dur = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+
+#anova(rma_correct_age_post_dur, rma_correct_age)
+
+rma_MP_age_post_dur = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+
+#anova(rma_MP_age_post_dur, rma_MP_age)
+
+rma_MPeffect_age_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
+
+#anova(rma_MPeffect_age_post_dur, rma_MPeffect_age)
+
+```

### 2018-12-04 Paper_Analyses.Rmd
Latest comments

--- 2018-12-03 Paper_Analyses.Rmd
@@
 
-[Christina: Big change: I just realized that we also need to report where we could not compute effect sizes, added this info. ]
-
 # Introduction
@@
 
-[Katie: since we actually don't have theoretical framework support for the no-change theory, I've changed around the sentence below to explicitly say that only 2 of the 3 are predicted by theoretical accounts.]
-[Christina: Works for me. I am just thinking what the Vihman-style framework says. do you happen to know? I think the Renner thesis discusses it.]
-[Katie: I wasn't really familiar with the Vihman framework, but looking at Renner's thesis and some of the original papers suggests that it really is about production, not perception.]
-
   In the current study, we focus on infants' developing ability to correctly apply the principles of phonological distinctiveness and constancy by using a meta-analytic approach to investigate mispronunciation sensitivity.
@@
 
-[Christina: I needed to move this around because we first need to say that we could not compute some effect sizes and removed outlierts.]
-
 Effect sizes are reported for infants' looks to target pictures after hearing a correctly pronounced or a mispronounced label (object identification) as well as the difference between effect sizes for correct and mispronounced trials (i.e.
@@
 To correct for the small sample sizes common in infant research, however, we used as a dependent variable Hedges' *g* instead of Cohen's *d* (Hedges, 1981; Morris, 2000).
-
-[Katie] Do you want number of records and papers for the imputed correlations as well?
-You've put a -1, assuming there was something wrong with one of the papers or something like that?
-How does that shake out for number of records?
-[Christina: No clue what the -1 was, sorry.]
 
@@
 This means we model as random effect that effect sizes from the same paper share are based on more similar studies than those across papers and that nested therein effects can stem from the same infants.
-
-[Christina: In the above 2 paragraphs I got confused, should it be present or past. I think it switched in the las tparagraph so I started to adapt, but I think it would be best for you to decide. ]
-[Katie: Good catch. I've gone through the Methods section and changed everything to past, per APA guidelines.]
 
@@
 The mean effect size Pearson's *r* of `r r2(CC$TE.fixed)` was small but did differ significantly from zero (CI [`r r2(CC$lower.fixed)`; `r r2(CC$upper.fixed)`] *p* `r psig(CC$pval.fixed)`).
-However, the lower bound of the CI is close to zero and considering the small sample size, one might hypothesize that with more power the small relationship might become even larger.
 As a result, we can draw a tentative conclusion that there is a positive relationship between comprehension scores and object recognition in response to correct pronunciations.
-
-[Christina] It's significant now!
-[Katie] Must be because you removed the outliers. I've changed around the wording :)
 
@@
 The mean effect size Pearson's *r* of `r r2(MC$TE.fixed)` was small and did not differ significantly from zero (CI [`r r2(MC$lower.fixed)`; `r r2(MC$upper.fixed)`] *p* `r psig(MC$pval.fixed)`).
-The small correlation and large variances suggest a lack of relationship between vocabulary and object recognition for mispronunciations.
+The small correlation suggests a lack of relationship between vocabulary and object recognition for mispronunciations.
 We again emphasize that we cannot draw a firm conclusion due to the small number of studies we were able to include here.
@@
 This figure illustrates two things: the growing number of mispronunciation sensitivity studies and the waning number of studies measuring vocabulary.
-The lack of evidence for a relationship between mispronunciation sensitivity and vocabulary size in early studies may have contributed to increasingly fewer researchers including vocabulary measurements in their mispronunciation sensitivity experimental design.
+The lack of evidence for a relationship between mispronunciation sensitivity and vocabulary size in some early studies may have contributed to increasingly fewer researchers including vocabulary measurements in their mispronunciation sensitivity experimental design.
 This may explain our underpowered analysis of the relationship between mispronunciation sensitivity and vocabulary size.
@@
 We note that the most popular actual post-naming phase length was `r with(dat, getmode(post_nam_actual))*1000` ms, used in *n* = `r with(post_length_info, n_exp_conditions[post_nam_actual == getmode(post_length_info$n_exp_conditions)])` experimental conditions.
-There was an inverse relationship between infant age and actual post-naming phase length, such that younger infants were presented with longer a longer post-naming phase, although this correlation was not significant (*r* = `r trial.l$estimate`, *p* `r psig(trial.l$p.value)`).
-Presumably, younger infants may be exposed to longer trials because their word recognition abilities are expected to be slower than older infants (Fernald et al., 1998).
+There was no apparent relation between infant age and overall post-naming phase duration (*r* = `r trial.l$estimate`, *p* `r psig(trial.l$p.value)`).
+
+[Christina: this r is near 0.
+I wouldn't interpret this as positive relationship, so I changed the wording here and in the next paragraph.
+Btw, can you add confidence intervals for r?
+The info is in there, with `$conf.int[1]`  and `$conf.int[2]`]
 
 Unlike the actual post-naming phase length, the size of the post-naming time window analyzed can be chosen after the experimental data is collected.
-Interestingly, half of the experimental conditions were analyzed using the same length of post-naming phase as the infant heard in the actual experiment (`r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`), while the other half were analyzed using a shorter length of post-naming phase, excluding later portions of the post-naming phase (`r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`).
+Interestingly, half of the experimental conditions were analyzed using the same length of post-naming phase as the infant heard in the actual experiment (`r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`), while the other half were analyzed using a shorter portion of the post-naming phase, usually excluding later portions (`r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`).
 Across papers, the length of the post-naming phase analyzed varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a median value of `r with(dat, median(post_nam_dur))*1000` ms.
 We note that the most popular actual post-naming phase length was `r with(dat, getmode(post_nam_dur))*1000` ms, used in *n* = `r with(post_name_info, n_exp_conditions[post_nam_dur == with(dat, getmode(post_nam_dur))])` experimental conditions.
-Similar to actual post-naming phase length, there was an inverse relationship between infant age and the size of the post-naming time window analyzed, such that younger infants' looking times were analyzed using a longer post-naming time window, here the relationship was significant (*r* = `r post.l$estimate`, *p* `r psig(post.l$p.value)`).
-Again, the choice to analyze a shorter post-naming time window is likely related to evidence that speed of processing is slower in younger infants (Fernald et al., 1998).
+There was an inverse relationship between infant age and the size of the post-naming time window analyzed, such that younger infants' looking times were analyzed using a longer post-naming time window, here the relationship was significant (*r* = `r post.l$estimate`, *p* `r psig(post.l$p.value)`).
+The choice to analyze a shorter post-naming time window is likely related to evidence that speed of processing is slower in younger infants (Fernald et al., 1998).
 To summarize, we observe variation in time-related aspects related to infants' age.
-This variation is most pronounced, and even significant, for the time window that is being analyzed after the target label has been heard.
+
+[Christina: Below there is a .... Just so we don't forget it.]
 
@@
 
-Although there are a priori reasons to choose the post-naming time window (infant age) or offset time (previous studies), these choices may occur after data collection and might therefore lead to a higher rate of false-positives (Gelman, A., & Loken, E.
-(2013).
+Although there are a priori reasons to choose the post-naming time window (infant age) or offset time (previous studies), these choices may occur after data collection and might therefore lead to a higher rate of false-positives (Gelman & Loken, 2013).
 Considering that these choices were systematically different across infant ages, at least for the post-naming time window, we next explored whether the size of time window analyzed or the offset time influenced sensitivity to mispronunciations.
@@
 
+[Christina: There are some () missing in the following paragraphs, I am a bit tired now, can you check?]
+
 We first assessed whether size of the post-naming time window analyzed had an impact on the overall size of the reported mispronunciation sensitivity.
@@
 The results suggest that the size of the post-naming phase analyzed significantly impacted mispronunciation sensitivity.
-Specifically, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) was significantly greater when the post-naming phase that was shorter in length.
-
-Considering that we also found a relationship between the length of the post-naming time window analyzed and infant age, such that younger ages had a longer window of analysis, we next examined whether the size of post-naming time window analyzed modulated the development of mispronunciation sensitivity.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
+Specifically, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) was significantly greater when the post-naming phase was shorter.
+
+Considering that we found a significant relationship between the length of the post-naming time window analyzed and infant age, such that younger ages had a longer window of analysis, we next examined whether the size of post-naming time window analyzed modulated the estimated size of mispronunciation sensitivity.
+We therefore included age as additional moderator of the previous analysis.
 The moderator test was significant `r mod_test(rma_post_dur_AGE_MS)`.
-The estimate for the  three-way-interaction between condition, size of post-naming phase, and age was small, but significant ($\beta$ = `r full_estimate(rma_post_dur_AGE_MS_eff)`.
+The estimate for the  three-way-interaction between condition, size of post-naming phase, and age was small, but significant ($\beta$ = `r full_estimate(rma_post_dur_AGE_MS_eff)`).
 As can be seen in Figure 3b, smaller post-naming time window size leads to greater increases in mispronunciation sensitivity with development.
@@
 Taken together, these results suggest that offset time does not modulate mispronunciation sensitivity.
-There is no relationship between offset time and age, and we find no influence of offset time on the development of mispronunciation sensitivity.
+There is no relationship between offset time and age, and we find no influence of offset time on the estimated size of mispronunciation sensitivity over age.
+
+[Christina: Replaced development in the sentence above and earlier, because the analysis choice cannot affect the development, just our measure of it]
 
@@
 Post can be considered similar to one another, in that they are calculated on the same type of data and consider pre-naming preferences.
+[Christina: adding sth here].
+It should be noted, however, that the Difference Score can better counter act participant- and item-level differences, whereas Pre vs.
+Post is a group-level measure.
 The Post dependent variable, in contrast, does not consider pre-naming preferences.
@@
 
+[Christina: Do you want to add this section?]
+
 ```{r reanalysis_misp_sens_dv_label}
@@
 
-Overall, infants showed reliable correct object recognition when given both correctly pronounced and mispronounced labels.
-In other words, not only did infants correctly recognize object labels when they were correctly pronounced, they also were likely to accept mispronunciations as acceptable labels for targets.
+Overall, infants showed reliable object recognition when given both correctly pronounced and mispronounced labels.
+In other words, not only did infants recognize object labels when they were correctly pronounced, they also were likely to accept mispronunciations as acceptable labels for targets.
 Mispronounced labels were considered a better match for target images than a distractor image, despite the differences in the phonological form of correctly pronounced and mispronounced words.
 Nonetheless, there was a considerable difference in target fixations in response to correctly pronounced and mispronounced labels, suggesting overall mispronunciation sensitivity in the current experimental literature.
+In short, infants show knowledge of what constitutes unacceptable variation in word forms, displaying knowledge of the role of phonemic changes throughout the ages assessed here.
+At the same time, infants, like adults, can recover from mispronunciations.
 
 We next evaluated the developmental trajectory of infants' mispronunciation sensitivity.
-Based on previous theoretical accounts and existing experimental evidence, we envisioned three possible developmental patterns: increasing sensitivity, decreasing sensitivity, and unchanging sensitivity.
+Based on previous theoretical accounts and existing experimental evidence, we envisioned three possible developmental patterns: increasing, decreasing, and unchanging sensitivity.
 We observed no influence of age when it was considered as a moderator of mispronunciation sensitivity.
@@
 Vocabulary growth leads to an increase (PRIMIR; Curtin & Werker, 2007; Werker & Curtin, 2005) or decrease (Perceptual Attunement; Best 1994, 1995) in mispronunciation sensitivity and vocabulary is expected to grow considerably in the age range considered in the current meta-analysis (see wordbank.stanford.edu; Frank et al., 2017).
-The lack of developmental effects found in the meta-analysis may therefore be due to using age, instead of vocabulary growth, as a facilitator for change in mispronunciation sensitivity.
+The lack of developmental effects found in our meta-analysis may therefore be due to using age, instead of vocabulary growth, as a facilitator for change in mispronunciation sensitivity.
 Yet, an analysis of correlations between vocabulary size and object recognition effect sizes does not support this argument.
@@
 Some previous experimental evidence also supports a lack of a relationship between vocabulary size and mispronunciation sensitivity (e.g.
-Mani & Plunkett, 2007; Swingley &
-Aslin, 2000; but see Mani & Plunkett, 2010).
+Mani & Plunkett, 2007; Swingley & Aslin, 2000; but see Mani & Plunkett, 2010).
 This would suggest that object recognition for mispronunciations is not modulated by vocabulary size, contrary to the predictions of the Perceptual Attunement (Best 1994, 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005) accounts and further supporting the overall lack of an influence of age on mispronunciation sensitivity.
@@
 We suggest that this may be the result of publication bias, specifically a desire to not publish null results.
-Although the number of mispronunciation sensitivity studies has experience growth, this has not translated to an increasing number of mispronunciation sensitivity studies also measuring vocabulary scores.
+Although the number of mispronunciation sensitivity studies per year has seen an increase, this has not translated to an increasing number of mispronunciation sensitivity studies also measuring vocabulary scores.
 
@@
 
-Then talk about the experimental decisions
-
-** Data Analysis Choices **
-
-  + Post-naming time window size and dependent variable impact misp sensitivity development
-  + Offset time does not impact misp sensitivity development
+[Christina] It's a good start, let's see where we go from here. I jotted down some possible conclusions
+
+## Data Analysis Choices
+
+During data entry, we noted variation in how the different studies were analyzed, with the time window, offset from naming, and depending variable differing substantially in our sample.
+For the time window used for statistical analysis we find xxx
+
+The lack of a field standard can have dire consequences, as our analyses show.
+Depending on which analysis time window (see figure xx) or dependent variable (see figure xx) we focus on, we find support for any of the three possible trajectories of mispronunciation sensitivity.
+On one hand, this limits the conclusions we can draw.
+On the other hand, this finding emphasizes that current practices of free, seemingly ad hoc choices regarding data analyses are not sustainable if the field wants to move towards quantitative evidence for theories of language development.
+
+We take this opportunity to suggest two remedies: Preregistration can serve as proof of a priori decisions regarding data analysis.
+The peer reviewed form of Registered Reports has already been adopted by a large number of developmental journals, and general journals that publish developmental works, showing the field's increasing acceptance of such practices.
+Open data can allow others to re-analyze existing datasets to both examine the impact of analysis decisions and cumulatively analyze different datasets in the same way.
+
+[Christina: Are we submitting to a place with registered reports? We should!]
+
+  + Post-naming time window size analyzed and dependent variable impact misp sensitivity measured
+  + Offset time does not impact measurement of misp sensitivity 
   + the first two do not have theoretical frameworks to guide researchers, whereas offset time does
 
-  [Christina] Did I ask the following already: Do we know whether subtrations were on the trial level?
-Pre vs post is a bit differnt because it loses the individual bias accommodation and the correlation between pre and post on the participant / item level.
-[Katie] You did. I'll put here my answer from before:
-From working with Nivi, we did it participants x condition or participants x trial (but mostly the former).
-But, this is not something we reported in papers.
-I don't think I read it at all when putting together the dataset for this either.
-[Christina] Mention in the discussion that we don't know this and it might be important to establish standard analysis pipelines for MP studies and that we need open data and code? ;)
-
 When it comes to designing studies, best practices and current standards might not always overlap.
-Indeed, across a set of previous meta-analyses it was shown that particularly infant research does not adjust sample sizes according to the effect in question (Bergmann et al., in press).
+Indeed, across a set of previous meta-analyses it was shown that particularly infant research does not adjust sample sizes according to the effect in question (Bergmann et al., 2018).
 A meta-analysis is a first step in improving experiment planning by measuring the underlying effect and its variance, which is directly related to the sample needed to achieve satisfactory power in the null hypothesis significance testing framework.
@@
 
+## Limitations
+
 From Christina: let's make a note to put sth in the discussion about our curve being surprisingly flat for correctly pronounced words bc people adapt their analysis windows?
 Bc if you look at Molly's reaction time paper, there is a steep increase.
+
+## Conclusion
+
+First aggregation of studies
+
+Advice for experiment design and design to be standardized, ideally preregistered.
+
+Open science with anonymized data and more complex models might be the future, but without us noting the issues in the field, this cannot happen, so let's call for change now.
 

### 2018-12-05 Paper_Analyses.Rmd

@@
 
-## (Insert Figure 2 about here)
+## (Insert Figure 1 about here)
 
@@
 
-knitr::include_graphics("figures/PRISMA_MA_Mispronunciation.png")
+knitr::include_graphics("figures/Figure_1_PRISMA_MA_Mispronunciation.png")
 
@@
 Across papers the baseline comparison varied; we used the baseline reported by the authors of each paper.
-Most papers (*n* = `r with(comparison_info, count[within_measure == "pre_post_naming_effect"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post_naming_effect"])` papers) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase and report a difference score.
+Most papers (*n* = `r with(comparison_info, count[within_measure == "pre_post_naming_effect"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post_naming_effect"])` papers) subtracted the PTL score for a pre-naming baseline phase from the PTL score for a post-naming phase and report a difference score.
 
 Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(comparison_info, count[within_measure == "pre_post"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post"])` papers), thus reporting two variables, or compared post-naming PTL with a chance level of 50%, (*n* = `r with(comparison_info, count[within_measure == "post"])` records from `r with(comparison_info, n_unique[within_measure == "post"])` papers).
-For all these comparisons, positive values (either as reported or after subtraction of chance level or a pre-naming PTL) indicate target looks towards the target object after hearing the label, i.e.
+For all these comparisons, positive values (either as reported or after subtraction of chance level or a pre-naming baseline PTL) indicate target looks towards the target object after hearing the label, i.e.
 a recognition effect.
@@
 
-[Christina] Can you try and align the axes for both plots?
-[Katie] I can, but then the dotted line doesn't extend the full way (which I think is quite ugly). Not sure how to fix that.
-
 ```{r PlotMPEffect, echo = FALSE, fig.width=10,fig.height=11}
@@
   geom_point(aes(size = weights_g),show.legend=FALSE, alpha = .5) + 
-  geom_line(y= 0, linetype="dotted") + 
+  geom_segment(aes(x = 6, y = 0, xend = 31, yend = 0), linetype="dotted", color = "black")+
+  #geom_line(y= 0, linetype="dotted") + 
   geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
@@
   geom_point(aes(size = weight),show.legend=FALSE, alpha = .3) + 
-  geom_line(y= 0, linetype="dotted") + 
+  geom_segment(aes(x = 6, y = 0, xend = 31, yend = 0), linetype="dotted", color = "black")+
+  #geom_line(y= 0, linetype="dotted") + 
   geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1), color = "black") +
@@
 
-ger.plot.age <- grid.arrange(p, p.diff,
+MS_plot <- grid.arrange(p, p.diff,
                              layout_matrix = lay)
@@
 
-grid.draw(ger.plot.age)
+grid.draw(MS_plot)
 
@@
 We identified two sets of variables which had the potential to vary across papers to assess the influence of data analysis choices on resulting effect size: timing (size of time window analyzed; offset time) and which dependent variable(s) were reported.
-In the following, we discuss the possible theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these analysis choices have on mispronunciation sensitivity development.
+In the following, we discuss the possible theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these analysis choices may have have on measurements of mispronunciation sensitivity development.
 We focus specifically on the size of the mispronunciation sensitivity effect, considering the whole dataset and including condition (correct pronunciation, mispronunciation) as moderator.
@@
 We note that the most popular actual post-naming phase length was `r with(dat, getmode(post_nam_actual))*1000` ms, used in *n* = `r with(post_length_info, n_exp_conditions[post_nam_actual == getmode(post_length_info$n_exp_conditions)])` experimental conditions.
-There was no apparent relation between infant age and overall post-naming phase duration (*r* = `r trial.l$estimate`, *p* `r psig(trial.l$p.value)`).
-
-[Christina: this r is near 0.
-I wouldn't interpret this as positive relationship, so I changed the wording here and in the next paragraph.
-Btw, can you add confidence intervals for r?
-The info is in there, with `$conf.int[1]`  and `$conf.int[2]`]
+There was no apparent relation between infant age and overall post-naming phase duration (*r* = `r trial.l$estimate`, 95% CI[`r trial.l$conf.int[1]`, `r trial.l$conf.int[2]`], *p* `r psig(trial.l$p.value)`).
 
@@
 We note that the most popular actual post-naming phase length was `r with(dat, getmode(post_nam_dur))*1000` ms, used in *n* = `r with(post_name_info, n_exp_conditions[post_nam_dur == with(dat, getmode(post_nam_dur))])` experimental conditions.
-There was an inverse relationship between infant age and the size of the post-naming time window analyzed, such that younger infants' looking times were analyzed using a longer post-naming time window, here the relationship was significant (*r* = `r post.l$estimate`, *p* `r psig(post.l$p.value)`).
+There was an inverse relationship between infant age and the size of the post-naming time window analyzed, such that younger infants' looking times were analyzed using a longer post-naming time window, here the relationship was significant (*r* = `r post.l$estimate`, 95% CI[`r post.l$conf.int[1]`, `r post.l$conf.int[2]`], *p* `r psig(post.l$p.value)`).
 The choice to analyze a shorter post-naming time window is likely related to evidence that speed of processing is slower in younger infants (Fernald et al., 1998).
@@
 [Christina: Below there is a .... Just so we don't forget it.]
+[Katie: I put it in there on purpose, I'm quoting directly from the paper, but the original sentence doesn't make full sense in this context, so I cut out the part that doesn't fit.
+This is the original sentence:
+"The lower bound of 367 ms is an `educated guess' based on studies such as those cited above, and our data (here and in other studies) showing that target and distractor fixations tend to diverge at around 400 ms."
+]
 
@@
 Previous studies examining simple stimulus response latencies first determined that infants require at least 233 ms to initiate an eye-movement in response to a stimulus (Canfield & Haith, 1991).
-In the first infant mispronunciation sensitivity study, Swingley and Aslin (2000) used an offset time of 367 ms, which was "an 'educated guess' based on studies...
+In the first infant mispronunciation sensitivity study, Swingley and Aslin (2000) used an offset time of 367 ms, which was "an 'educated guess' based on studies .
+.
+.
 showing that target and distractor fixations tend to diverge at around 400 ms." (Swingley & Aslin, 2000, p.
@@
 Although there are a priori reasons to choose the post-naming time window (infant age) or offset time (previous studies), these choices may occur after data collection and might therefore lead to a higher rate of false-positives (Gelman & Loken, 2013).
-Considering that these choices were systematically different across infant ages, at least for the post-naming time window, we next explored whether the size of time window analyzed or the offset time influenced sensitivity to mispronunciations.
+Considering that these choices were systematically different across infant ages, at least for the post-naming time window analyzed, we next explored whether the size of time window analyzed or the offset time influenced sensitivity to mispronunciations.
 
@@
 
-[Christina: There are some () missing in the following paragraphs, I am a bit tired now, can you check?]
-
 We first assessed whether size of the post-naming time window analyzed had an impact on the overall size of the reported mispronunciation sensitivity.
 We considered data from both conditions in a joint analysis and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant, `r mod_test(rma_post_dur_MS)`.
-The estimate for the interaction between post-naming phase size and condition was small but significant $\beta$`r full_estimate(rma_post_dur_MS_eff)`.
+The moderator test was significant (`r mod_test(rma_post_dur_MS)`).
+The estimate for the interaction between post-naming phase size and condition was small but significant ($\beta$`r full_estimate(rma_post_dur_MS_eff)`).
 This relationship is plotted in Figure 3a.
@@
 
-Considering that we found a significant relationship between the length of the post-naming time window analyzed and infant age, such that younger ages had a longer window of analysis, we next examined whether the size of post-naming time window analyzed modulated the estimated size of mispronunciation sensitivity.
+Considering that we found a significant relationship between the length of the post-naming time window analyzed and infant age, such that younger ages had a longer window of analysis, we next examined whether the size of post-naming time window analyzed modulated the estimated size of mispronunciation sensitivity as infant age changed.
 We therefore included age as additional moderator of the previous analysis.
-The moderator test was significant `r mod_test(rma_post_dur_AGE_MS)`.
+The moderator test was significant (`r mod_test(rma_post_dur_AGE_MS)`).
 The estimate for the  three-way-interaction between condition, size of post-naming phase, and age was small, but significant ($\beta$ = `r full_estimate(rma_post_dur_AGE_MS_eff)`).
-As can be seen in Figure 3b, smaller post-naming time window size leads to greater increases in mispronunciation sensitivity with development.
+As can be seen in Figure 3b, smaller post-naming time window size leads to greater increases in measured mispronunciation sensitivity with development.
 For example, when experimental conditions were analyzed with a post-naming time window of 2000 ms or less, mispronunciation sensitivity is found to increase with infant age.
 If the post-naming time window analyzed is greater than 2000 ms, however, there is no or a negative relation of mispronunciation sensitivity and age.
-In other words, all three possible hypotheses might be supported depending on analysis choices made regarding the size of the post-naming time window to analyze.
+In other words, all three possible developmental hypotheses might be supported depending on analysis choices made regarding the size of the post-naming time window to analyze.
 This is especially important, considering that our key question is how mispronunciation sensitivity changes with development.
@@
 We next assessed whether the time between the target was named and the start of the analysis, namely offset time, had an impact on the size of the reported mispronunciation sensitivity.
-When we included both condition and offset time as moderators, the moderator test was significant, `r mod_test(rma_post_dur_MS)`, but the estimate for the interaction between offset time and condition was almost zero $\beta$`r full_estimate(rma_offset_MS_eff)`.
-Although we found no relationship between offset time and infant age, we also examined whether the size of offset time modulated the development of mispronunciation sensitivity.
-When both offset time and condition were included as moderators, the moderator test was significant `r mod_test(rma_offset_AGE_MS)`, but the three-way-interaction between condition, offset time, and age was very small and not significant ($\beta$ = `r full_estimate(rma_offset_AGE_MS_eff)`.
-Taken together, these results suggest that offset time does not modulate mispronunciation sensitivity.
+When we included both condition and offset time as moderators, the moderator test was significant (`r mod_test(rma_post_dur_MS)`), but the estimate for the interaction between offset time and condition was almost zero ($\beta$`r full_estimate(rma_offset_MS_eff)`).
+Although we found no relationship between offset time and infant age, we also examined whether the size of offset time modulated the the measure of mispronunciation sensitivity over infant age.
+When both offset time and condition were included as moderators, the moderator test was significant (`r mod_test(rma_offset_AGE_MS)`), but the three-way-interaction between condition, offset time, and age was very small and not significant ($\beta$ = `r full_estimate(rma_offset_AGE_MS_eff)`.
+Taken together, these results suggest that offset time does not modulate measured mispronunciation sensitivity.
 There is no relationship between offset time and age, and we find no influence of offset time on the estimated size of mispronunciation sensitivity over age.
-
-[Christina: Replaced development in the sentence above and earlier, because the analysis choice cannot affect the development, just our measure of it]
 
@@
 Mispronunciation studies evaluate infants' proportion of target looks (PTL) in response to correct and mispronounced words.
-Experiments typically include a phase where no naming event has occured, whether correctly pronounced or mispronounced, which we refer to as the baseline.
-The purpose of the baseline is to ensure that infants do not have systematic preferences for the target or distractor (greater interest in a cat compared to a cup) which may drive PTL scores in the post-naming phase.
-As described in the Data Analysis sub-section of the Methods, there was considerable variation across papers in way that baseline was calculated, resulting in different measured outcomes or dependent variables.
+Experiments typically include a phase where no naming event has occured, whether correctly pronounced or mispronounced, which we refer to as the pre-naming phase The purpose of the pre-naming phase is to ensure that infants do not have systematic preferences for the target or distractor (greater interest in a cat compared to a cup) which may drive PTL scores in the post-naming phase.
+As described in the Data Analysis sub-section of the Methods, however, there was considerable variation across papers in whether this pre-naming phase was used as a baseline measurement, or whether a different baseline measurement was used.
+This resulted in different measured outcomes or dependent variables.
 Over half of the experimental conditions (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post_naming_effect"])`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase.
@@
 Finally, the remaining `r with(dv_info, n_exp_conditions[within_measure == "post"])` experimental conditions compared the post-naming PTL score with a chance value of 50%.
-Here, the infants' pre-naming phase preferences are not considered and instead target fixations are evaluated based on the likelihood to fixate one of two pictures.
+Here, the infants' pre-naming phase baseline preferences are not considered and instead target fixations are evaluated based on the likelihood to fixate one of two pictures.
 We will refer to this dependent variable as Post.
@@
 Post is a group-level measure.
-The Post dependent variable, in contrast, does not consider pre-naming preferences.
+The Post dependent variable, in contrast, does not consider pre-naming baseline preferences.
 To our knowledge, there is no theory or evidence that explicitly drives choice of dependent variable in analysis of mispronunciation sensitivity, which may explain the wide variation in dependent variable reported in the papers included in this meta-analysis.
-We next explored whether the type of dependent variable calculated influenced sensitivity to mispronunciations.
-Considering that the dependent variable Post differs in its consideration of pre-naming preferences, we directly compared mispronunciation sensitivity between Post as a reference condition and both Difference Score and Pre vs.
+We next explored whether the type of dependent variable calculated influenced the estimated size of sensitivity to mispronunciations.
+Considering that the dependent variable Post differs in its consideration of pre-naming baseline preferences, substituting these for a chance value, we directly compared mispronunciation sensitivity between Post as a reference condition and both Difference Score and Pre vs.
 Post dependent variables.
@@
 
-We first assessed whether the choice of dependent variable had an impact on the size of mispronunciation sensitivity.
-When we included both condition and dependent variable as moderators, the moderator test was significant `r mod_test(rma_within_MS)`.
+We first assessed whether the choice of dependent variable had an impact on the size of estimated mispronunciation sensitivity.
+When we included both condition and dependent variable as moderators, the moderator test was significant (`r mod_test(rma_within_MS)`).
 The estimate for the interaction between Pre vs.
@@
 This relationship is plotted in Figure 4a.
-The results suggest that dependent variable calculated significantly impacted the size fo the mispronunciation sensitivity effect, such that Post.
+The results suggest that the reported dependent variable significantly impacted the size of the estimated mispronunciation sensitivity effect, such that studies reporting the Post.
 vs.
-Pre showed a smaller mispronunciation sensitivity effect than Post, but no difference between the Difference Score and Post.
-
-We next examined whether the type of dependent variable calculated modulated the development of mispronunciation sensitivity.
-When age was included as an additional moderator, the moderator test was significant `r mod_test(rma_within_AGE_MS)`.
+Pre dependent variable showed a smaller mispronunciation sensitivity effect than those reporting Post, but that there was no difference between the Difference Score and Post dependent variables.
+
+We next examined whether the type of dependent variable calculated modulated the the estimated change in mispronunciation sensitivity over infant age.
+When age was included as an additional moderator, the moderator test was significant (`r mod_test(rma_within_AGE_MS)`).
 The estimate for the interaction between Pre vs.
@@
 This relationship is plotted in Figure 4b.
-When the dependent variable was Pre vs.
-Post, mispronunciation sensitivity decreased with infant age, while in comparison, when the dependent variable was Post, mispronunciation sensitivity increased with infant age.
-There was no difference in mispronunciation sensitivity change with infant development between the Post and Difference Score dependent variables.
+When the dependent variable reported was Pre vs.
+Post, mispronunciation sensitivity was found to decrease with infant age, while in comparison, when the dependent variable was Post, mispronunciation sensitivity was found to increase with infant age.
+There was no difference in the estimated mispronunciation sensitivity change with infant age between the Post and Difference Score dependent variables.
+
 Similar to size of post-naming time window analyzed, all three possible developmental hypotheses might be supported depending on the dependent variable reported.
@@
 [Christina: Do you want to add this section?]
+[Katie: From what I came up with, it makes no difference to the conclusions we make in the regular models.
+But, I am not sure I did it right.
+I don't really feel like they have to be included, but if you think it would be good, then we can work on it.]
 
@@
 
-Overall, infants showed reliable object recognition when given both correctly pronounced and mispronounced labels.
+Overall, the results of the meta-analysis showed that infants reliably fixate the target object  when given both correctly pronounced and mispronounced labels.
 In other words, not only did infants recognize object labels when they were correctly pronounced, they also were likely to accept mispronunciations as acceptable labels for targets.
@@
 Some previous experimental evidence also supports a lack of a relationship between vocabulary size and mispronunciation sensitivity (e.g.
-Mani & Plunkett, 2007; Swingley & Aslin, 2000; but see Mani & Plunkett, 2010).
+Mani & Plunkett, 2007; Swingley & Aslin, 2000; Tao et al., 2012; but see Mani & Plunkett, 2010).
 This would suggest that object recognition for mispronunciations is not modulated by vocabulary size, contrary to the predictions of the Perceptual Attunement (Best 1994, 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005) accounts and further supporting the overall lack of an influence of age on mispronunciation sensitivity.
 
-What may these results mean for our understanding of phono-lexical development in infancy?
 Evidence that infants accept a mispronunciation (object identification) while simultaneously holding correctly pronounced and mispronounced labels as separate (mispronunciation sensitivity) may indcate an abstract understanding of words' phonological structure.
-It appears infants may understand that the mispronunciation and correct pronunciation's phonological form do not match, but that the mispronunciation is a better label for the target compared to the distractor image.
+It appears that young infants may understand that the mispronunciation and correct pronunciation's phonological form do not match (phonological distinctiveness), but that the mispronunciation is a better label for the target compared to the distractor image (phonological constancy).
 The lack of age or vocabulary effects in our meta-analysis suggest that this understanding is present from an age when the earliest words are learned and is maintained throughout early lexical development.
-Already with the first words, infants have a sense of the importance of sounds in  the words present in their lexicon.
-We recommend that future theoretical accounts should consider this lack of developmental change.
+This implies mastery of the principles of phonological constancy and phonological distinctiveness at an age earlier than previously thought, which we recommend should be taken into account by future theoretical accounts.
 
@@
 
-[Katie] The above section is a bit clunky and I don't like it. Any suggestions for improvement?
+[Katie] The above paragraph is a bit clunky and I don't like it. Any suggestions for improvement?
+
+## Data Analysis Choices
+
+While creating the dataset on which this meta-analysis was based, we included as many details as possible to describe each study.
+During the coding of these characteristics, we noted a potential for variation in a handful of variables that relate to data analysis, specifically relating to timing (size of time window analyzed; offset time) and which dependent variable(s) were reported.
+We focused on these variables in particular because their choice can potentially be made after researchers have examined the data, leading to an inflated increase of significant results which may also explain the publication bias observed in the funnel plot assymmetry (Simmons, Nelson, & Simonsohn, 2011).
+To explore whether this variation contributed to the lack of developmental change observed in the overall meta-analysis, we included these variables as moderators in a set of exploratory analyses.
+We noted an interesting pattern of results, specifically that different conclusions about mispronunciation sensitivity, but more notably mispronunciation sensitivity development, could be drawn depending on the length of the post-naming time window analyzed as well as the type of dependent variable calculated in the experiment.
 
@@
 
-## Data Analysis Choices
-
-During data entry, we noted variation in how the different studies were analyzed, with the time window, offset from naming, and depending variable differing substantially in our sample.
-For the time window used for statistical analysis we find xxx
-
-The lack of a field standard can have dire consequences, as our analyses show.
-Depending on which analysis time window (see figure xx) or dependent variable (see figure xx) we focus on, we find support for any of the three possible trajectories of mispronunciation sensitivity.
-On one hand, this limits the conclusions we can draw.
-On the other hand, this finding emphasizes that current practices of free, seemingly ad hoc choices regarding data analyses are not sustainable if the field wants to move towards quantitative evidence for theories of language development.
-
-We take this opportunity to suggest two remedies: Preregistration can serve as proof of a priori decisions regarding data analysis.
+Infants are expected to recognize words more quickly with age (Fernald, Swingley & Pinto, 2001; Swingley, Pinto & Fernald, 1999; Swingley & Fernald, 2002).
+This evidence has often guided decisions for the post-naming time window to be analyzed in mispronunciation sensitivity studies, including where to begin the time window (offset time) and how long this window should be (post-naming time window analyzed).
+Specifically, increasing age should lead to quicker reaction times, and therefore lower offset times.
+Yet, we found no evidence for a relationship between offset time and infant age nor that offset time modulated mispronunciation sensitivity.
+Indeed, a large majority used an offset time between 360 and 370 ms, which follows the best guess of Swingley and Aslin (2000) for the amount of time needed for infants to initiate eye movements in response to a spoken target word.
+
+In contrast, the length of the post-naming window analyzed was related to infant age and also found to modulate mispronunciation sensitivity.
+Younger infants may take longer to reliably identify the target image, and as a result the length of the post-naming time window analyzed may be longer in younger infants.
+This was born out in the meta-analysis: studies that tested younger infants used a longer post-naming time window.
+Longer post-naming time windows, however, resulted in a smaller effect size for mispronunciation sensitivity.
+Critically, the developmental trajectory of mispronunciation sensitivity changed depending on the length of the post-naming time window analyzed.
+Longer time windows resulted in decreasing or no change in mispronunciation sensitivity, while shorter time windows resulting in increasing mispronunciation sensitivity.
+Given a set of mispronunciation sensitivity data, a conclusion regarding the development of mispronunciation sensitivity would be different depending on the length of the post-naming time window analyzed.
+
+Unlike the timing variables, the origin of a potential relationship between the type of dependent variable calculated and mispronunciation sensitivity is much less clear.
+The majority of studies created a Difference Score, subtracting pre-naming phase PTL from that of post-naming phase PTL, while the remaining studies compared pre-naming PTL with post-naming PTL (Pre vs.
+Post) or analyzed post-naming PTL alone (Post).
+Both the Difference Score and the Pre vs.
+Post dependent variables consider pre-naming phase baseline preferences for the target compared to distractor image, but were found to differentially modulate mispronunciation sensitivity.
+There was no difference in mispronunciation sensitivity between the Post and Difference Score dependent variables, but in comparison to Post, studies that reported the Pre vs.
+Post dependent variable had lower effect sizes for mispronunciation sensitivity.
+Furthermore, studies reporting the Pre vs.
+Post dependent variable showed decreasing mispronunciation sensitivity with age, while studies reporting a Difference Score or Post dependent variable showed an increase.
+Similar to the length of the post-naming time window analyzed, given a set of mispronunciation sensitivity data, a conclusion regarding the development of mispronunciation sensitivity would be different depending on the choice of dependent variable.
+
+A lack of a field standards can have dire consequences, as our analyses show.
+Depending on which analysis time window (see Figure 5) or dependent variable (see Figure 6) we focus on, we find support for any of the three possible trajectories of mispronunciation sensitivity.
+On the one hand, this limits the conclusions we can draw.
+Without access to the full datasets or analysis code of the studies included in this meta-analysis, it is difficult to pinpoint the exact role played by these data analysis choices.
+On the other hand, this finding emphasizes that current practices of free, potentially ad hoc choices regarding data analyses are not sustainable if the field wants to move towards quantitative evidence for theories of language development.
+
+We take this opportunity to suggest several remedies.
+Preregistration can serve as proof of a priori decisions regarding data analysis or describing how data analysis decisions will be made once data is collected.
 The peer reviewed form of Registered Reports has already been adopted by a large number of developmental journals, and general journals that publish developmental works, showing the field's increasing acceptance of such practices.
 Open data can allow others to re-analyze existing datasets to both examine the impact of analysis decisions and cumulatively analyze different datasets in the same way.
+Furthermore, experimenters can analyze the time course as a whole, instead of aggregating the proportion of target looking behavior over the entire trial.
+This allows for a more detailed assessment of infants' fixations over time and reduces the need to reduce the time window of the post-naming phase for analysis.
+Both Growth Curve Analysis (Mirman et al., 2008; Law & Edwards, 2015) and Permutation Clusters Analysis (Maris & Oostenveld, 2007; Von Holzen & Mani, 2012; Delle Luche et al., 2015) offer potential solutions to analyze the full time course.
+In general, however, it may be useful to establish standard analysis pipelines for mispronunciation studies.
+This would allow for a more uniform analysis of this phenomenon, as well as aid experimenters in future research planning.
 
 [Christina: Are we submitting to a place with registered reports? We should!]
-
-  + Post-naming time window size analyzed and dependent variable impact misp sensitivity measured
-  + Offset time does not impact measurement of misp sensitivity 
-  + the first two do not have theoretical frameworks to guide researchers, whereas offset time does
+[Katie: We had been aiming for Cognition, but it doesn't have registered reports. But, Dev Sci does, although we're about 3,000 words above their word limit (Cognition doesn't have a word limit).]
+
+[Katie: this is a good paragraph, but I'm not sure where it fits. Its rather not specific for our current meta-analysis, but a general comment about the field.]
 
@@
 
+[Katie: I am not sure where to talk about this, or actually how to talk about this.]
+For example, the Difference Score dependent variable substracts the pre-naming phase PTL from the post-naming phase PTL.
+Some studies compute this variable on the level of condition (e.g.
+White & Morgan, 2008), but this reduces SOMETHING, WHICH IS A BAD SOMETHING.
+
 ## Limitations
 
-From Christina: let's make a note to put sth in the discussion about our curve being surprisingly flat for correctly pronounced words bc people adapt their analysis windows?
-Bc if you look at Molly's reaction time paper, there is a steep increase.
+The current meta-analysis aggregated studies designed to investigate mispronunciation sensitivity, but we note that these studies varied in their approach to study mispronunciation sensitivity.
+For example, some studies investigated specific questions which required additional manipulations, such as the impact of the number of phonological features changed in the mispronunciations on mispronunciation sensitivity (e.g.
+White & Morgan, 2008; Mani & Plunkett, 2011) or sensitivity to consonant and vowel mispronunciations (Mani & Plunkett, 2007; 2010 keps and tups; Hojen et al., unpublished; Swingley, 2016).
+These studies varied in their experimental design, such as whether infants were familiar with the distractor image (e.g.
+White and Morgan (2008; see also Mani & Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) or whether the labels for the target and distractor images contained phonological overlap (Fernald, Swingley, & Pinto, 2001).
+Futhermore, the infants included in this meta-analysis had a variety of native languages (English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese) and language backgrounds (monolingual, bilingual, monodialectal, multidialectal).
+Taken together, these variables have the potential to modulate infant mispronunciation sensitivity, but an investigation of these variables is out of the scope of the current meta-analysis.
+However, our dataset coded for and included these variables.
+We hope that future research will be able to better understand the role that these variables play in infants' senstivity to mispronunciations.
+
+Furthermore, the investigation of mispronunciation sensitivity does not singularly capture infant phono-lexical development.
+For example, studies investigating word form recognition, typically using the Headturn Preference Procedure (Mandel et al., 1995), allow for an investigation of the specificity of infants' word form representations without requiring word-object associations, which is required in the Intermodal Preferential Looking Paradigm (Golinkoff et al., 1987; 2013).
+As a result, this approach can be used with infants of a much younger age than typically examined.
+These studies compare infants' preference to listen to word lists that a correct compared to word lists that contain a mispronunciation (e.g.
+Bouchon et al., 2014; Swingley, 2005; Halle & de Boysson-Bardies, 1996; Vihman et al., 2004; Vihman & Majorano 2016; 2017; Poltrock & Nazzi, 2015; Delle Luche et al., 2016).
+In contrast, studies investigating recognition of accented words use stimuli that are naturally occuring as opposed to artificially manipulated, to achieve an altered phonological form (e.g.
+van Heughten et al., 2018; 2015; Buckler et al., 2017; van Heughten & Johnson, 2014; 2016; Best et al., 2009; Mulak et al., 2013; Schmale et al., 2010; 2012; Schmale & Seidel, 2009; Floccia et al., 2012; Durrant et al., 2014).
+This allows for an evaluation of phono-lexical development in response to a type of language that infants may encounter in everyday life.
+These investigations offer complementary approaches to infant phono-lexical development.
 
@@
 
-First aggregation of studies
-
-Advice for experiment design and design to be standardized, ideally preregistered.
-
-Open science with anonymized data and more complex models might be the future, but without us noting the issues in the field, this cannot happen, so let's call for change now.
+This meta-analysis comprises an aggregation of almost two decades of research on mispronunciation sensitivity, finding that although infants accept both corect pronunciations and mispronunciations as labels for a target image, they are more likely to accept correct pronunciations, which indcates sensitivity to mispronunciations in familiar words.
+Despite the predictions of theories of infant phono-lexical development, this sensitivity was not modulated by infant age or vocabulary.
+This suggests that at a young age, infants' representations for their first words may be already phonologically well-specified.
+We recommend future theoretical frameworks take this evidence into account.
+
+Despite this overall finding, however, we note evidence that data analysis choices can modulate conclusions about mispronunciation sensitivity development.
+Future studies should be carefully planned with this evidence in mind.
+Ideally, future experimental design and data analysis would become standardized which may be aided by the growing trend of preregistration and open science practices.
+Our analysis highlights how meta-analyses can aid in identification of issues in a particular field and play a vital role in how the field addresses such issues.
 

### 2018-12-05 Paper_Analyses.tex

@@
 
-{[}Katie: since we actually don't have theoretical framework support for
-the no-change theory, I've changed around the sentence below to
-explicitly say that only 2 of the 3 are predicted by theoretical
-accounts.{]}{[}Christina: Works for me. I am just thinking what the
-Vihman-style framework says. do you happen to know? I think the Renner
-thesis discusses it.{]} {[}Katie: I wasn't really familiar with the
-Vihman framework, but looking at Renner's thesis and some of the
-original papers suggests that it really is about production, not
-perception.{]}
-
 In the current study, we focus on infants' developing ability to
@@
 
-\subsection{(Insert Figure 2 about
-here)}\label{insert-figure-2-about-here}
+\subsection{(Insert Figure 1 about
+here)}\label{insert-figure-1-about-here}
 
@@
 \centering
-\includegraphics{figures/PRISMA_MA_Mispronunciation.png}
+\includegraphics{figures/Figure_1_PRISMA_MA_Mispronunciation.png}
 \caption{}
@@
 
-{[}Christina: I needed to move this around because we first need to say
-that we could not compute some effect sizes and removed outlierts.{]}
-
 Effect sizes are reported for infants' looks to target pictures after
@@
 1981; Morris, 2000).
-
-{[}Katie{]} Do you want number of records and papers for the imputed
-correlations as well? You've put a -1, assuming there was something
-wrong with one of the papers or something like that? How does that shake
-out for number of records? {[}Christina: No clue what the -1 was,
-sorry.{]}
 
@@
 
-{[}Christina: In the above 2 paragraphs I got confused, should it be
-present or past. I think it switched in the las tparagraph so I started
-to adapt, but I think it would be best for you to decide. {]}{[}Katie:
-Good catch. I've gone through the Methods section and changed everything
-to past, per APA guidelines.{]}
-
 Mispronunciation sensitivity studies typically examine infants'
@@
 (\emph{n} = 52 records from 13 papers) subtracted the PTL score for a
-pre-naming phase from the PTL score for a post-naming phase and report a
-difference score.
+pre-naming baseline phase from the PTL score for a post-naming phase and
+report a difference score.
 
@@
 (either as reported or after subtraction of chance level or a pre-naming
-PTL) indicate target looks towards the target object after hearing the
-label, i.e.~a recognition effect. Standardized effect sizes based on
-mean differences, as calculated here, preserve the sign. Consequently,
-positive effect sizes reflect more looks to the target picture after
-naming, and larger positive effect sizes indicate comparatively more
-looks to the target.
+baseline PTL) indicate target looks towards the target object after
+hearing the label, i.e.~a recognition effect. Standardized effect sizes
+based on mean differences, as calculated here, preserve the sign.
+Consequently, positive effect sizes reflect more looks to the target
+picture after naming, and larger positive effect sizes indicate
+comparatively more looks to the target.
 
@@
 \subsection{(Insert Figure 2 about
-here)}\label{insert-figure-2-about-here-1}
+here)}\label{insert-figure-2-about-here}
 
@@
 
-{[}Christina{]} Can you try and align the axes for both plots?
-{[}Katie{]} I can, but then the dotted line doesn't extend the full way
-(which I think is quite ugly). Not sure how to fix that.
-
 \begin{verbatim}
@@
 \emph{r} of 0.14 was small but did differ significantly from zero (CI
-{[}0.03; 0.25{]} \emph{p} = 0.012). However, the lower bound of the CI
-is close to zero and considering the small sample size, one might
-hypothesize that with more power the small relationship might become
-even larger. As a result, we can draw a tentative conclusion that there
-is a positive relationship between comprehension scores and object
-recognition in response to correct pronunciations.
-
-{[}Christina{]} It's significant now! {[}Katie{]} Must be because you
-removed the outliers. I've changed around the wording :)
+{[}0.03; 0.25{]} \emph{p} = 0.012). As a result, we can draw a tentative
+conclusion that there is a positive relationship between comprehension
+scores and object recognition in response to correct pronunciations.
 
@@
 \emph{r} of 0.05 was small and did not differ significantly from zero
-(CI {[}-0.01; 0.12{]} \emph{p} = 0.119). The small correlation and large
-variances suggest a lack of relationship between vocabulary and object
-recognition for mispronunciations. We again emphasize that we cannot
-draw a firm conclusion due to the small number of studies we were able
-to include here.
+(CI {[}-0.01; 0.12{]} \emph{p} = 0.119). The small correlation suggests
+a lack of relationship between vocabulary and object recognition for
+mispronunciations. We again emphasize that we cannot draw a firm
+conclusion due to the small number of studies we were able to include
+here.
 
@@
 vocabulary. The lack of evidence for a relationship between
-mispronunciation sensitivity and vocabulary size in early studies may
-have contributed to increasingly fewer researchers including vocabulary
-measurements in their mispronunciation sensitivity experimental design.
-This may explain our underpowered analysis of the relationship between
-mispronunciation sensitivity and vocabulary size.
+mispronunciation sensitivity and vocabulary size in some early studies
+may have contributed to increasingly fewer researchers including
+vocabulary measurements in their mispronunciation sensitivity
+experimental design. This may explain our underpowered analysis of the
+relationship between mispronunciation sensitivity and vocabulary size.
 
@@
 choices, the variation present in the current meta-analysis dataset, and
-the influence these analysis choices have on mispronunciation
-sensitivity development. We focus specifically on the size of the
-mispronunciation sensitivity effect, considering the whole dataset and
-including condition (correct pronunciation, mispronunciation) as
-moderator.
+the influence these analysis choices may have have on measurements of
+mispronunciation sensitivity development. We focus specifically on the
+size of the mispronunciation sensitivity effect, considering the whole
+dataset and including condition (correct pronunciation,
+mispronunciation) as moderator.
 
@@
 length was 4000 ms, used in \emph{n} = 74 experimental conditions. There
-was an inverse relationship between infant age and actual post-naming
-phase length, such that younger infants were presented with longer a
-longer post-naming phase, although this correlation was not significant
-(\emph{r} = 0.01, \emph{p} = 0.882). Presumably, younger infants may be
-exposed to longer trials because their word recognition abilities are
-expected to be slower than older infants (Fernald et al., 1998).
+was no apparent relation between infant age and overall post-naming
+phase duration (\emph{r} = 0.01, 95\% CI{[}-0.11, 0.13{]}, \emph{p} =
+0.882).
 
@@
 in the actual experiment (124), while the other half were analyzed using
-a shorter length of post-naming phase, excluding later portions of the
-post-naming phase (127). Across papers, the length of the post-naming
-phase analyzed varied from 1510 to 4000 ms, with a median value of 2500
-ms. We note that the most popular actual post-naming phase length was
-2000 ms, used in \emph{n} = 97 experimental conditions. Similar to
-actual post-naming phase length, there was an inverse relationship
-between infant age and the size of the post-naming time window analyzed,
-such that younger infants' looking times were analyzed using a longer
-post-naming time window, here the relationship was significant (\emph{r}
-= -0.23, \emph{p} \textless{} .001). Again, the choice to analyze a
-shorter post-naming time window is likely related to evidence that speed
-of processing is slower in younger infants (Fernald et al., 1998). To
-summarize, we observe variation in time-related aspects related to
-infants' age. This variation is most pronounced, and even significant,
-for the time window that is being analyzed after the target label has
-been heard.
+a shorter portion of the post-naming phase, usually excluding later
+portions (127). Across papers, the length of the post-naming phase
+analyzed varied from 1510 to 4000 ms, with a median value of 2500 ms. We
+note that the most popular actual post-naming phase length was 2000 ms,
+used in \emph{n} = 97 experimental conditions. There was an inverse
+relationship between infant age and the size of the post-naming time
+window analyzed, such that younger infants' looking times were analyzed
+using a longer post-naming time window, here the relationship was
+significant (\emph{r} = -0.23, 95\% CI{[}-0.35, -0.11{]}, \emph{p}
+\textless{} .001). The choice to analyze a shorter post-naming time
+window is likely related to evidence that speed of processing is slower
+in younger infants (Fernald et al., 1998). To summarize, we observe
+variation in time-related aspects related to infants' age.
+
+{[}Christina: Below there is a \ldots{}. Just so we don't forget
+it.{]}{[}Katie: I put it in there on purpose, I'm quoting directly from
+the paper, but the original sentence doesn't make full sense in this
+context, so I cut out the part that doesn't fit. This is the original
+sentence: \enquote{The lower bound of 367 ms is an `educated guess'
+based on studies such as those cited above, and our data (here and in
+other studies) showing that target and distractor fixations tend to
+diverge at around 400 ms.}{]}
 
@@
 (2000) used an offset time of 367 ms, which was \enquote{an
-\enquote{educated guess} based on studies\ldots{} showing that target
-and distractor fixations tend to diverge at around 400 ms.} (Swingley \&
+\enquote{educated guess} based on studies . . . showing that target and
+distractor fixations tend to diverge at around 400 ms.} (Swingley \&
 Aslin, 2000, p.~155). Upon inspecting the offset time values used in the
@@
 occur after data collection and might therefore lead to a higher rate of
-false-positives (Gelman, A., \& Loken, E. (2013). Considering that these
-choices were systematically different across infant ages, at least for
-the post-naming time window, we next explored whether the size of time
-window analyzed or the offset time influenced sensitivity to
+false-positives (Gelman \& Loken, 2013). Considering that these choices
+were systematically different across infant ages, at least for the
+post-naming time window analyzed, we next explored whether the size of
+time window analyzed or the offset time influenced sensitivity to
 mispronunciations.
@@
 and included condition (correct pronunciation, mispronunciation) as an
-additional moderator. The moderator test was significant, QM(3) =
-236.958, \emph{p} \textless{} .001. The estimate for the interaction
+additional moderator. The moderator test was significant (QM(3) =
+236.958, \emph{p} \textless{} .001). The estimate for the interaction
 between post-naming phase size and condition was small but significant
-\(\beta\) = -0.262, SE = 0.059, 95\% CI{[}-0.377, -0.148{]}, \emph{p}
-\textless{} .001. This relationship is plotted in Figure 3a. The results
-suggest that the size of the post-naming phase analyzed significantly
-impacted mispronunciation sensitivity. Specifically, the difference
-between target fixations for correctly pronounced and mispronounced
-items (mispronunciation sensitivity) was significantly greater when the
-post-naming phase that was shorter in length.
-
-Considering that we also found a relationship between the length of the
-post-naming time window analyzed and infant age, such that younger ages
-had a longer window of analysis, we next examined whether the size of
-post-naming time window analyzed modulated the development of
-mispronunciation sensitivity. We merged the two datasets and included
-condition (correct pronunciation, mispronunciation) as well as age as
-additional moderators. The moderator test was significant QM(7) =
-247.322, \emph{p} \textless{} .001. The estimate for the
-three-way-interaction between condition, size of post-naming phase, and
-age was small, but significant (\(\beta\) = = -0.04, SE = 0.014, 95\%
-CI{[}-0.068, -0.012{]}, \emph{p} = 0.006. As can be seen in Figure 3b,
-smaller post-naming time window size leads to greater increases in
-mispronunciation sensitivity with development. For example, when
-experimental conditions were analyzed with a post-naming time window of
-2000 ms or less, mispronunciation sensitivity is found to increase with
-infant age. If the post-naming time window analyzed is greater than 2000
-ms, however, there is no or a negative relation of mispronunciation
-sensitivity and age. In other words, all three possible hypotheses might
-be supported depending on analysis choices made regarding the size of
-the post-naming time window to analyze. This is especially important,
-considering that our key question is how mispronunciation sensitivity
-changes with development. These results suggest that conclusions about
-the relationship between infant age and mispronunciation sensitivity may
-be mediated by the size of the post-naming time window analyzed.
+(\(\beta\) = -0.262, SE = 0.059, 95\% CI{[}-0.377, -0.148{]}, \emph{p}
+\textless{} .001). This relationship is plotted in Figure 3a. The
+results suggest that the size of the post-naming phase analyzed
+significantly impacted mispronunciation sensitivity. Specifically, the
+difference between target fixations for correctly pronounced and
+mispronounced items (mispronunciation sensitivity) was significantly
+greater when the post-naming phase was shorter.
+
+Considering that we found a significant relationship between the length
+of the post-naming time window analyzed and infant age, such that
+younger ages had a longer window of analysis, we next examined whether
+the size of post-naming time window analyzed modulated the estimated
+size of mispronunciation sensitivity as infant age changed. We therefore
+included age as additional moderator of the previous analysis. The
+moderator test was significant (QM(7) = 247.322, \emph{p} \textless{}
+.001). The estimate for the three-way-interaction between condition,
+size of post-naming phase, and age was small, but significant (\(\beta\)
+= = -0.04, SE = 0.014, 95\% CI{[}-0.068, -0.012{]}, \emph{p} = 0.006).
+As can be seen in Figure 3b, smaller post-naming time window size leads
+to greater increases in measured mispronunciation sensitivity with
+development. For example, when experimental conditions were analyzed
+with a post-naming time window of 2000 ms or less, mispronunciation
+sensitivity is found to increase with infant age. If the post-naming
+time window analyzed is greater than 2000 ms, however, there is no or a
+negative relation of mispronunciation sensitivity and age. In other
+words, all three possible developmental hypotheses might be supported
+depending on analysis choices made regarding the size of the post-naming
+time window to analyze. This is especially important, considering that
+our key question is how mispronunciation sensitivity changes with
+development. These results suggest that conclusions about the
+relationship between infant age and mispronunciation sensitivity may be
+mediated by the size of the post-naming time window analyzed.
 
@@
 condition and offset time as moderators, the moderator test was
-significant, QM(3) = 236.958, \emph{p} \textless{} .001, but the
+significant (QM(3) = 236.958, \emph{p} \textless{} .001), but the
 estimate for the interaction between offset time and condition was
-almost zero \(\beta\) = 0, SE = 0, 95\% CI{[}-0.001, 0{]}, \emph{p} =
-0.505. Although we found no relationship between offset time and infant
-age, we also examined whether the size of offset time modulated the
-development of mispronunciation sensitivity. When both offset time and
-condition were included as moderators, the moderator test was
-significant QM(7) = 200.867, \emph{p} \textless{} .001, but the
-three-way-interaction between condition, offset time, and age was very
-small and not significant (\(\beta\) = = 0, SE = 0, 95\% CI{[}0, 0{]},
-\emph{p} = 0.605. Taken together, these results suggest that offset time
-does not modulate mispronunciation sensitivity. There is no relationship
-between offset time and age, and we find no influence of offset time on
-the development of mispronunciation sensitivity.
+almost zero (\(\beta\) = 0, SE = 0, 95\% CI{[}-0.001, 0{]}, \emph{p} =
+0.505). Although we found no relationship between offset time and infant
+age, we also examined whether the size of offset time modulated the the
+measure of mispronunciation sensitivity over infant age. When both
+offset time and condition were included as moderators, the moderator
+test was significant (QM(7) = 200.867, \emph{p} \textless{} .001), but
+the three-way-interaction between condition, offset time, and age was
+very small and not significant (\(\beta\) = = 0, SE = 0, 95\% CI{[}0,
+0{]}, \emph{p} = 0.605. Taken together, these results suggest that
+offset time does not modulate measured mispronunciation sensitivity.
+There is no relationship between offset time and age, and we find no
+influence of offset time on the estimated size of mispronunciation
+sensitivity over age.
 
@@
 correctly pronounced or mispronounced, which we refer to as the
-baseline. The purpose of the baseline is to ensure that infants do not
-have systematic preferences for the target or distractor (greater
-interest in a cat compared to a cup) which may drive PTL scores in the
-post-naming phase. As described in the Data Analysis sub-section of the
-Methods, there was considerable variation across papers in way that
-baseline was calculated, resulting in different measured outcomes or
-dependent variables. Over half of the experimental conditions (\emph{n}
-= 129) subtracted the PTL score for a pre-naming phase from the PTL
-score for a post-naming phase. This results in one value, which is then
-compared with a chance value of 0. When positive, this indicates that
-infants increased their looks to the target after hearing the naming
-label (correct or mispronounced) relative to the pre-naming baseline
-PTL. We will refer to this dependent variable as the Difference Score.
-Another dependent variable, which was used in 69 experimental
-conditions, directly compared the post- and pre-naming PTL scores with
-one another. This requires two values, one for the pre-naming phase and
-one for the post-naming phase. A greater post compared to pre-naming
-phase PTL indicates that infants increased their target looks after
-hearing the naming label. We will refer to this dependent variable as
-Pre vs.~Post. Finally, the remaining 53 experimental conditions compared
-the post-naming PTL score with a chance value of 50\%. Here, the
-infants' pre-naming phase preferences are not considered and instead
-target fixations are evaluated based on the likelihood to fixate one of
-two pictures. We will refer to this dependent variable as Post.
+pre-naming phase The purpose of the pre-naming phase is to ensure that
+infants do not have systematic preferences for the target or distractor
+(greater interest in a cat compared to a cup) which may drive PTL scores
+in the post-naming phase. As described in the Data Analysis sub-section
+of the Methods, however, there was considerable variation across papers
+in whether this pre-naming phase was used as a baseline measurement, or
+whether a different baseline measurement was used. This resulted in
+different measured outcomes or dependent variables. Over half of the
+experimental conditions (\emph{n} = 129) subtracted the PTL score for a
+pre-naming phase from the PTL score for a post-naming phase. This
+results in one value, which is then compared with a chance value of 0.
+When positive, this indicates that infants increased their looks to the
+target after hearing the naming label (correct or mispronounced)
+relative to the pre-naming baseline PTL. We will refer to this dependent
+variable as the Difference Score. Another dependent variable, which was
+used in 69 experimental conditions, directly compared the post- and
+pre-naming PTL scores with one another. This requires two values, one
+for the pre-naming phase and one for the post-naming phase. A greater
+post compared to pre-naming phase PTL indicates that infants increased
+their target looks after hearing the naming label. We will refer to this
+dependent variable as Pre vs.~Post. Finally, the remaining 53
+experimental conditions compared the post-naming PTL score with a chance
+value of 50\%. Here, the infants' pre-naming phase baseline preferences
+are not considered and instead target fixations are evaluated based on
+the likelihood to fixate one of two pictures. We will refer to this
+dependent variable as Post.
 
@@
 another, in that they are calculated on the same type of data and
-consider pre-naming preferences. The Post dependent variable, in
-contrast, does not consider pre-naming preferences. To our knowledge,
-there is no theory or evidence that explicitly drives choice of
-dependent variable in analysis of mispronunciation sensitivity, which
-may explain the wide variation in dependent variable reported in the
-papers included in this meta-analysis. We next explored whether the type
-of dependent variable calculated influenced sensitivity to
+consider pre-naming preferences. {[}Christina: adding sth here{]}. It
+should be noted, however, that the Difference Score can better counter
+act participant- and item-level differences, whereas Pre vs.~Post is a
+group-level measure. The Post dependent variable, in contrast, does not
+consider pre-naming baseline preferences. To our knowledge, there is no
+theory or evidence that explicitly drives choice of dependent variable
+in analysis of mispronunciation sensitivity, which may explain the wide
+variation in dependent variable reported in the papers included in this
+meta-analysis. We next explored whether the type of dependent variable
+calculated influenced the estimated size of sensitivity to
 mispronunciations. Considering that the dependent variable Post differs
-in its consideration of pre-naming preferences, we directly compared
-mispronunciation sensitivity between Post as a reference condition and
-both Difference Score and Pre vs.~Post dependent variables.
+in its consideration of pre-naming baseline preferences, substituting
+these for a chance value, we directly compared mispronunciation
+sensitivity between Post as a reference condition and both Difference
+Score and Pre vs.~Post dependent variables.
 
 We first assessed whether the choice of dependent variable had an impact
-on the size of mispronunciation sensitivity. When we included both
-condition and dependent variable as moderators, the moderator test was
-significant QM(5) = 259.817, \emph{p} \textless{} .001. The estimate for
-the interaction between Pre vs.~Post and condition was significantly
-smaller than that of the Post dependent variable (\(\beta\) = -0.392, SE
-= 0.101, 95\% CI{[}-0.59, -0.194{]}, \emph{p} \textless{} .001), but the
-difference between the Difference Score and Post in the interaction with
-condition was small and not significant (\(\beta\) = -0.01, SE = 0.098,
-95\% CI{[}-0.203, 0.183{]}, \emph{p} = 0.916). This relationship is
-plotted in Figure 4a. The results suggest that dependent variable
-calculated significantly impacted the size fo the mispronunciation
-sensitivity effect, such that Post. vs.~Pre showed a smaller
-mispronunciation sensitivity effect than Post, but no difference between
-the Difference Score and Post.
+on the size of estimated mispronunciation sensitivity. When we included
+both condition and dependent variable as moderators, the moderator test
+was significant (QM(5) = 259.817, \emph{p} \textless{} .001). The
+estimate for the interaction between Pre vs.~Post and condition was
+significantly smaller than that of the Post dependent variable
+(\(\beta\) = -0.392, SE = 0.101, 95\% CI{[}-0.59, -0.194{]}, \emph{p}
+\textless{} .001), but the difference between the Difference Score and
+Post in the interaction with condition was small and not significant
+(\(\beta\) = -0.01, SE = 0.098, 95\% CI{[}-0.203, 0.183{]}, \emph{p} =
+0.916). This relationship is plotted in Figure 4a. The results suggest
+that the reported dependent variable significantly impacted the size of
+the estimated mispronunciation sensitivity effect, such that studies
+reporting the Post. vs.~Pre dependent variable showed a smaller
+mispronunciation sensitivity effect than those reporting Post, but that
+there was no difference between the Difference Score and Post dependent
+variables.
 
 We next examined whether the type of dependent variable calculated
-modulated the development of mispronunciation sensitivity. When age was
-included as an additional moderator, the moderator test was significant
-QM(11) = 273.585, \emph{p} \textless{} .001. The estimate for the
-interaction between Pre vs.~Post, condition, and age was significantly
-smaller than that of the Post dependent variable (\(\beta\) = -0.089, SE
-= 0.03, 95\% CI{[}-0.148, -0.03{]}, \emph{p} = 0.003), but the
-difference between the Difference Score and Post in the interaction with
-condition and age was small and not significant (\(\beta\) = -0.036, SE
-= 0.027, 95\% CI{[}-0.088, 0.016{]}, \emph{p} = 0.174). This
-relationship is plotted in Figure 4b. When the dependent variable was
-Pre vs.~Post, mispronunciation sensitivity decreased with infant age,
-while in comparison, when the dependent variable was Post,
-mispronunciation sensitivity increased with infant age. There was no
-difference in mispronunciation sensitivity change with infant
-development between the Post and Difference Score dependent variables.
+modulated the the estimated change in mispronunciation sensitivity over
+infant age. When age was included as an additional moderator, the
+moderator test was significant (QM(11) = 273.585, \emph{p} \textless{}
+.001). The estimate for the interaction between Pre vs.~Post, condition,
+and age was significantly smaller than that of the Post dependent
+variable (\(\beta\) = -0.089, SE = 0.03, 95\% CI{[}-0.148, -0.03{]},
+\emph{p} = 0.003), but the difference between the Difference Score and
+Post in the interaction with condition and age was small and not
+significant (\(\beta\) = -0.036, SE = 0.027, 95\% CI{[}-0.088, 0.016{]},
+\emph{p} = 0.174). This relationship is plotted in Figure 4b. When the
+dependent variable reported was Pre vs.~Post, mispronunciation
+sensitivity was found to decrease with infant age, while in comparison,
+when the dependent variable was Post, mispronunciation sensitivity was
+found to increase with infant age. There was no difference in the
+estimated mispronunciation sensitivity change with infant age between
+the Post and Difference Score dependent variables.
+
 Similar to size of post-naming time window analyzed, all three possible
@@
 
+\subsection{Controlling for analysis
+choices}\label{controlling-for-analysis-choices}
+
+{[}Christina: Do you want to add this section?{]}{[}Katie: From what I
+came up with, it makes no difference to the conclusions we make in the
+regular models. But, I am not sure I did it right. I don't really feel
+like they have to be included, but if you think it would be good, then
+we can work on it.{]}
+
 \section{General Discussion}\label{general-discussion}
 
-Overall, infants showed reliable correct object recognition when given
-both correctly pronounced and mispronounced labels. In other words, not
-only did infants correctly recognize object labels when they were
-correctly pronounced, they also were likely to accept mispronunciations
-as acceptable labels for targets. Mispronounced labels were considered a
-better match for target images than a distractor image, despite the
-differences in the phonological form of correctly pronounced and
-mispronounced words. Nonetheless, there was a considerable difference in
-target fixations in response to correctly pronounced and mispronounced
-labels, suggesting overall mispronunciation sensitivity in the current
-experimental literature.
+Overall, the results of the meta-analysis showed that infants reliably
+fixate the target object when given both correctly pronounced and
+mispronounced labels. In other words, not only did infants recognize
+object labels when they were correctly pronounced, they also were likely
+to accept mispronunciations as acceptable labels for targets.
+Mispronounced labels were considered a better match for target images
+than a distractor image, despite the differences in the phonological
+form of correctly pronounced and mispronounced words. Nonetheless, there
+was a considerable difference in target fixations in response to
+correctly pronounced and mispronounced labels, suggesting overall
+mispronunciation sensitivity in the current experimental literature. In
+short, infants show knowledge of what constitutes unacceptable variation
+in word forms, displaying knowledge of the role of phonemic changes
+throughout the ages assessed here. At the same time, infants, like
+adults, can recover from mispronunciations.
 
@@
 existing experimental evidence, we envisioned three possible
-developmental patterns: increasing sensitivity, decreasing sensitivity,
-and unchanging sensitivity. We observed no influence of age when it was
-considered as a moderator of mispronunciation sensitivity. Of the two
-mainstream theories identified in our literature review, neither the
-Perceptual Attunement account (Best 1994, 1995) nor PRIMIR (Curtin \&
-Werker, 2007; Werker \& Curtin, 2005) account for a lack of
-developmental change. The results of our meta-analysis are supported by
-a handful of studies directly comparing infants over a range of ages
-(Swingley \& Aslin, 2000; Bailey \& Plunkett, 2002; Zesiger et al.,
-2012), which also found no developmental change in mispronunciation
-sensitivity.
+developmental patterns: increasing, decreasing, and unchanging
+sensitivity. We observed no influence of age when it was considered as a
+moderator of mispronunciation sensitivity. Of the two mainstream
+theories identified in our literature review, neither the Perceptual
+Attunement account (Best 1994, 1995) nor PRIMIR (Curtin \& Werker, 2007;
+Werker \& Curtin, 2005) account for a lack of developmental change. The
+results of our meta-analysis are supported by a handful of studies
+directly comparing infants over a range of ages (Swingley \& Aslin,
+2000; Bailey \& Plunkett, 2002; Zesiger et al., 2012), which also found
+no developmental change in mispronunciation sensitivity.
 
@@
 wordbank.stanford.edu; Frank et al., 2017). The lack of developmental
-effects found in the meta-analysis may therefore be due to using age,
+effects found in our meta-analysis may therefore be due to using age,
 instead of vocabulary growth, as a facilitator for change in
@@
 a lack of a relationship between vocabulary size and mispronunciation
-sensitivity (e.g.~Mani \& Plunkett, 2007; Swingley \& Aslin, 2000; but
-see Mani \& Plunkett, 2010). This would suggest that object recognition
-for mispronunciations is not modulated by vocabulary size, contrary to
-the predictions of the Perceptual Attunement (Best 1994, 1995) and
-PRIMIR (Curtin \& Werker, 2007; Werker \& Curtin, 2005) accounts and
-further supporting the overall lack of an influence of age on
-mispronunciation sensitivity.
+sensitivity (e.g.~Mani \& Plunkett, 2007; Swingley \& Aslin, 2000; Tao
+et al., 2012; but see Mani \& Plunkett, 2010). This would suggest that
+object recognition for mispronunciations is not modulated by vocabulary
+size, contrary to the predictions of the Perceptual Attunement (Best
+1994, 1995) and PRIMIR (Curtin \& Werker, 2007; Werker \& Curtin, 2005)
+accounts and further supporting the overall lack of an influence of age
+on mispronunciation sensitivity.
 
@@
 specifically a desire to not publish null results. Although the number
-of mispronunciation sensitivity studies has experience growth, this has
-not translated to an increasing number of mispronunciation sensitivity
-studies also measuring vocabulary scores.
-
-{[}Katie{]} The above section is a bit clunky and I don't like it. Any
+of mispronunciation sensitivity studies per year has seen an increase,
+this has not translated to an increasing number of mispronunciation
+sensitivity studies also measuring vocabulary scores.
+
+{[}Katie{]} The above paragraph is a bit clunky and I don't like it. Any
 suggestions for improvement?
+
+\subsection{Data Analysis Choices}\label{data-analysis-choices}
 
@@
 
-Considering the timing variable, infants are expected to recognize words
-more quickly with age (Fernald, Swingley \& Pinto, 2001; Swingley, Pinto
-\& Fernald, 1999; Swingley \& Fernald, 2002). This evidence has often
-guided decisions for the post-naming time window to be analyzed in
-mispronunciation sensitivity studies, including where to begin the time
-window (offset time) and how long this window should be (post-naming
-time window analyzed). Specifically, increasing age should lead to
-quicker reaction times, and therefore lower offset times. Yet, we found
-no evidence for a relationship between offset time and infant age nor
-that offset time modulated mispronunciation sensitivity. Indeed, a large
-majority used an offset time between 360 and 370 ms, which follows the
-best guess of Swingley and Aslin (2000) for the amount of time needed
-for infants to initiate eye movements in response to a spoken target
-word.
+{[}Christina{]} It's a good start, let's see where we go from here. I
+jotted down some possible conclusions
+
+Infants are expected to recognize words more quickly with age (Fernald,
+Swingley \& Pinto, 2001; Swingley, Pinto \& Fernald, 1999; Swingley \&
+Fernald, 2002). This evidence has often guided decisions for the
+post-naming time window to be analyzed in mispronunciation sensitivity
+studies, including where to begin the time window (offset time) and how
+long this window should be (post-naming time window analyzed).
+Specifically, increasing age should lead to quicker reaction times, and
+therefore lower offset times. Yet, we found no evidence for a
+relationship between offset time and infant age nor that offset time
+modulated mispronunciation sensitivity. Indeed, a large majority used an
+offset time between 360 and 370 ms, which follows the best guess of
+Swingley and Aslin (2000) for the amount of time needed for infants to
+initiate eye movements in response to a spoken target word.
 
@@
 alone (Post). Both the Difference Score and the Pre vs.~Post dependent
-variables consider pre-naming phase preferences for the target compared
-to distractor image, but were found to differentially modulate
+variables consider pre-naming phase baseline preferences for the target
+compared to distractor image, but were found to differentially modulate
 mispronunciation sensitivity. There was no difference in
@@
 
-Without access to the full datasets of the studies included in this
+A lack of a field standards can have dire consequences, as our analyses
+show. Depending on which analysis time window (see Figure 5) or
+dependent variable (see Figure 6) we focus on, we find support for any
+of the three possible trajectories of mispronunciation sensitivity. On
+the one hand, this limits the conclusions we can draw. Without access to
+the full datasets or analysis code of the studies included in this
 meta-analysis, it is difficult to pinpoint the exact role played by
-these data analysis choices, specificially the length of the post-naming
-time window analyzed and the type of dependent variable reported. Access
-to such data would allow for a systematic analysis of the influence of
-these choices on the size of the effect of mispronunciation sensitivity
-as well as its developmental trajectory. Furthermore, sharing analysis
-code would allow for a clearer understanding of the approach to data
-analysis. For example, the Difference Score dependent variable
+these data analysis choices. On the other hand, this finding emphasizes
+that current practices of free, potentially ad hoc choices regarding
+data analyses are not sustainable if the field wants to move towards
+quantitative evidence for theories of language development.
+
+We take this opportunity to suggest several remedies. Preregistration
+can serve as proof of a priori decisions regarding data analysis or
+describing how data analysis decisions will be made once data is
+collected. The peer reviewed form of Registered Reports has already been
+adopted by a large number of developmental journals, and general
+journals that publish developmental works, showing the field's
+increasing acceptance of such practices. Open data can allow others to
+re-analyze existing datasets to both examine the impact of analysis
+decisions and cumulatively analyze different datasets in the same way.
+Furthermore, experimenters can analyze the time course as a whole,
+instead of aggregating the proportion of target looking behavior over
+the entire trial. This allows for a more detailed assessment of infants'
+fixations over time and reduces the need to reduce the time window of
+the post-naming phase for analysis. Both Growth Curve Analysis (Mirman
+et al., 2008; Law \& Edwards, 2015) and Permutation Clusters Analysis
+(Maris \& Oostenveld, 2007; Von Holzen \& Mani, 2012; Delle Luche et
+al., 2015) offer potential solutions to analyze the full time course. In
+general, however, it may be useful to establish standard analysis
+pipelines for mispronunciation studies. This would allow for a more
+uniform analysis of this phenomenon, as well as aid experimenters in
+future research planning.
+
+{[}Christina: Are we submitting to a place with registered reports? We
+should!{]}{[}Katie: We had been aiming for Cognition, but it doesn't
+have registered reports. But, Dev Sci does, although we're about 3,000
+words above their word limit (Cognition doesn't have a word limit).{]}
+
+{[}Katie: this is a good paragraph, but I'm not sure where it fits. Its
+rather not specific for our current meta-analysis, but a general comment
+about the field.{]}
+
+When it comes to designing studies, best practices and current standards
+might not always overlap. Indeed, across a set of previous meta-analyses
+it was shown that particularly infant research does not adjust sample
+sizes according to the effect in question (Bergmann et al., 2018). A
+meta-analysis is a first step in improving experiment planning by
+measuring the underlying effect and its variance, which is directly
+related to the sample needed to achieve satisfactory power in the null
+hypothesis significance testing framework. Failing to take effect sizes
+into account can both yield to underpowered research and to testing too
+many participants, both consequences are undesirable for a number of
+reasons that have been discussed in depth elsewhere. We will just
+briefly mention two that we consider most salient for theory building:
+Underpowered studies will lead to false negatives more frequently than
+expected, which in turn results in an unpublished body of literature
+(citationcitation). Overpowered studies mean that participants were
+tested unnecessarily, which has substantial ethical consequences
+particularly when working with infants and other difficult to recruit
+and test populations.
+
+{[}Katie: I am not sure where to talk about this, or actually how to
+talk about this.{]} For example, the Difference Score dependent variable
 substracts the pre-naming phase PTL from the post-naming phase PTL. Some
 studies compute this variable on the level of condition (e.g.~White \&
-Morgan, 2008), but this reduces SOMETHING, WHICH IS A BAD SOMETHING
-{[}Katie{]}. In addition to shared data and code, it may be useful to
-establish standard analysis pipelines for mispronunciation studies. This
-would allow for a more uniform analysis of this phenomenon, as well as
-aid experimenters in future research planning. Finally, we recommend
-that experimenters consider analyzing the time course as a whole,
-instead of aggregating the proportion of target looking behavior over
-the entire trial. Both Growth Curve Analysis (Mirman et al., 2008; Law
-\& Edwards, 2015) and Permutation Clusters Analysis (Maris \&
-Oostenveld, 2007; Von Holzen \& Mani, 2012) offer potential solutions
-for time course analysis.
+Morgan, 2008), but this reduces SOMETHING, WHICH IS A BAD SOMETHING.
+
+\subsection{Limitations}\label{limitations}
+
+The current meta-analysis aggregated studies designed to investigate
+mispronunciation sensitivity, but we note that these studies varied in
+their approach to study mispronunciation sensitivity. For example, some
+studies investigated specific questions which required additional
+manipulations, such as the impact of the number of phonological features
+changed in the mispronunciations on mispronunciation sensitivity
+(e.g.~White \& Morgan, 2008; Mani \& Plunkett, 2011) or sensitivity to
+consonant and vowel mispronunciations (Mani \& Plunkett, 2007; 2010 keps
+and tups; Hojen et al., unpublished; Swingley, 2016). These studies
+varied in their experimental design, such as whether infants were
+familiar with the distractor image (e.g.~White and Morgan (2008; see
+also Mani \& Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) or
+whether the labels for the target and distractor images contained
+phonological overlap (Fernald, Swingley, \& Pinto, 2001). Futhermore,
+the infants included in this meta-analysis had a variety of native
+languages (English, Spanish, French, Dutch, German, Catalan, Danish, and
+Mandarin Chinese) and language backgrounds (monolingual, bilingual,
+monodialectal, multidialectal). Taken together, these variables have the
+potential to modulate infant mispronunciation sensitivity, but an
+investigation of these variables is out of the scope of the current
+meta-analysis. However, our dataset coded for and included these
+variables. We hope that future research will be able to better
+understand the role that these variables play in infants' senstivity to
+mispronunciations.
+
+Furthermore, the investigation of mispronunciation sensitivity does not
+singularly capture infant phono-lexical development. For example,
+studies investigating word form recognition, typically using the
+Headturn Preference Procedure (Mandel et al., 1995), allow for an
+investigation of the specificity of infants' word form representations
+without requiring word-object associations, which is required in the
+Intermodal Preferential Looking Paradigm (Golinkoff et al., 1987; 2013).
+As a result, this approach can be used with infants of a much younger
+age than typically examined. These studies compare infants' preference
+to listen to word lists that a correct compared to word lists that
+contain a mispronunciation (e.g.~Bouchon et al., 2014; Swingley, 2005;
+Halle \& de Boysson-Bardies, 1996; Vihman et al., 2004; Vihman \&
+Majorano 2016; 2017; Poltrock \& Nazzi, 2015; Delle Luche et al., 2016).
+In contrast, studies investigating recognition of accented words use
+stimuli that are naturally occuring as opposed to artificially
+manipulated, to achieve an altered phonological form (e.g.~van Heughten
+et al., 2018; 2015; Buckler et al., 2017; van Heughten \& Johnson, 2014;
+2016; Best et al., 2009; Mulak et al., 2013; Schmale et al., 2010; 2012;
+Schmale \& Seidel, 2009; Floccia et al., 2012; Durrant et al., 2014).
+This allows for an evaluation of phono-lexical development in response
+to a type of language that infants may encounter in everyday life. These
+investigations offer complementary approaches to infant phono-lexical
+development.
+
+\subsection{Conclusion}\label{conclusion}
+
+This meta-analysis comprises an aggregation of almost two decades of
+research on mispronunciation sensitivity, finding that although infants
+accept both corect pronunciations and mispronunciations as labels for a
+target image, they are more likely to accept correct pronunciations,
+which indcates sensitivity to mispronunciations in familiar words.
+Despite the predictions of theories of infant phono-lexical development,
+this sensitivity was not modulated by infant age or vocabulary. This
+suggests that at a young age, infants' representations for their first
+words may be already phonologically well-specified. We recommend future
+theoretical frameworks take this evidence into account.
+
+Despite this overall finding, however, we note evidence that data
+analysis choices can modulate conclusions about mispronunciation
+sensitivity development. Future studies should be carefully planned with
+this evidence in mind. Ideally, future experimental design and data
+analysis would become standardized which may be aided by the growing
+trend of preregistration and open science practices. Our analysis
+highlights how meta-analyses can aid in identification of issues in a
+particular field and play a vital role in how the field addresses such
+issues.
 

### 2018-12-07 Paper_Analyses.Rmd
added an abstract, keywords, and figure captions

@@
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-keywords          : "keywords"
+  As they develop into mature speakers of their native language, infants must not only learn words but also the sounds that make up those words.
+To do so, they must strike a balance between accepting some variation (e.g.
+mood, voice, accent), but appropriately rejecting variation when it changes a word's meaning (e.g.
+cat vs.
+hat).
+We focus on studies investigating infants' ability to detect mispronunciations in familiar words, which we refer to as mispronunciation sensitivity.
+The goal of this meta-analysis was to evaluate the development of mispronunciation sensitivity in infancy, allowing for a test of competing mainstream theoretical frameworks.
+The results show that although infants are sensitive to mispronunciations, they still accept these altered forms as labels for target objects.
+Interestingly, this ability is not modulated by age or vocabulary size, challenging existing theories and suggesting that a mature understanding of native language phonology is present in infants from an early age.
+Despite this finding, we discuss potential data analysis choices that may influence different conclusions about mispronunciation sensitivity development as well as offer recommendations to improve best practices in the study of mispronunciation sensitivity.
+
+keywords          : "language acquisition; mispronunciation sensitivity; word recognition; meta-analysis; lexicon"
 wordcount         : "X"
@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_docx
 
@@
     panel.border=element_blank(),
-    axis.line=element_line()#,
-    #text=element_text(family='Times', size=25)
-    )
+    axis.line=element_line(),
+    text=element_text(family='Times', size=25))
 
@@
 
-```{r PRISMA_image, echo= FALSE}
+```{r PRISMA_image, echo= FALSE, fig.cap="A PRISMA flowchart illustrating the selection procedure used to include studies in the current meta-analysis."}
 
@@
 
-```{r FunnelCombo, echo = FALSE}
+```{r FunnelCombo, echo = FALSE, fig.cap="Funnel plots for object identification, plotting the standard error of the effect size in relation to the effect size.
+The black line marks zero, the dashed grey line marks the effect estimate, and the grey line marks funnel plot assymetry."}
 
@@
 
-```{r PlotMPEffect, echo = FALSE, fig.width=10,fig.height=11}
+```{r PlotMPEffect, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for correct pronunciations (orange) and mispronunciations (blue) by participant age.
+Panel b: Effect sizes for mispronunciation sensitivyt (correct - mispronunciations) by participant age.
+For both panels, point size depicts inverse variance and the dashed line indicates zero (chance)."}
 
@@
 
-```{r Vocab_describe1}
+```{r Vocab_describe1, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (orange), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (green)."}
 #how did vocabulary collection change over time?
@@
 
-```{r Plot_post_name_cond_age, echo = FALSE, fig.width=10,fig.height=11}
+```{r Plot_post_name_cond_age, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different lengths of post-naming phase time windows analyzed: 2000 ms or less (orange), 2001 to 3000 ms (blue), and 3001 ms or greater (green).
+Although length of post-naming phase time window analyzed was included as a continuous variable in the meta-analytic model, it is divided into categories for ease of viewing.
+Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity as a function of age.
+The lines plot the linear regression and the gray shaded area indicates the standard error."}
 
@@
 
-```{r Plot_Within_cond_age_diff_score, echo = FALSE, fig.width=10,fig.height=11}
+```{r Plot_Within_cond_age_diff_score, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (orange), Post vs.
+Pre (blue), and Difference Score (green).
+Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity as a function of age.
+The lines plot the linear regression and the gray shaded area indicates the standard error."}
 
@@
 
+```{r reanalysis_misp_sens_dv_label}
+
 ## Controlling for analysis choices
 
-[Christina: Do you want to add this section?]
-[Katie: From what I came up with, it makes no difference to the conclusions we make in the regular models.
+#[Christina: Do you want to add this section?]
+#[Katie: From what I came up with, it makes no difference to the conclusions we make in the regular models.
 But, I am not sure I did it right.
 I don't really feel like they have to be included, but if you think it would be good, then we can work on it.]
-
-```{r reanalysis_misp_sens_dv_label}
 
@@
 In contrast, studies investigating recognition of accented words use stimuli that are naturally occuring as opposed to artificially manipulated, to achieve an altered phonological form (e.g.
-van Heughten et al., 2018; 2015; Buckler et al., 2017; van Heughten & Johnson, 2014; 2016; Best et al., 2009; Mulak et al., 2013; Schmale et al., 2010; 2012; Schmale & Seidel, 2009; Floccia et al., 2012; Durrant et al., 2014).
+van Heughten et al., 2018; 2015; Buckler et al., 2017; van Heughten & Johnson, 2014; 2016; Best et al., 2009; Mulak et al., 2013; Schmale et al., 2010; 2012; Schmale & Seidel, 2009; Floccia et al., 2012; Durrant et al., 2014; White & Aslin, 2011).
 This allows for an evaluation of phono-lexical development in response to a type of language that infants may encounter in everyday life.

### 2018-12-07 Paper_Analyses.tex
added an abstract, keywords, and figure captions

@@
             pdfauthor={Katie Von Holzen~\& Christina Bergmann},
-            pdfkeywords={keywords},
+            pdfkeywords={language acquisition; mispronunciation sensitivity; word recognition;
+meta-analysis; lexicon},
             pdfborder={0 0 0},
@@
 \textsuperscript{1} Department of Hearing and Speech Sciences, University of Maryland, USA\\\textsuperscript{2} Laboratoire Psychologie de la Perception, Université Paris Descartes\\\textsuperscript{3} Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands\\\textsuperscript{4} LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University}
-\keywords{keywords\newline\indent Word count: X}
+\keywords{language acquisition; mispronunciation sensitivity; word recognition; meta-analysis; lexicon\newline\indent Word count: X}
 \usepackage{csquotes}
@@
 \abstract{
-One or two sentences providing a \textbf{basic introduction} to the
-field, comprehensible to a scientist in any discipline.
-
-Two to three sentences of \textbf{more detailed background},
-comprehensible to scientists in related disciplines.
-
-One sentence clearly stating the \textbf{general problem} being
-addressed by this particular study.
-
-One sentence summarizing the main result (with the words ``\textbf{here
-we show}'' or their equivalent).
-
-Two or three sentences explaining what the \textbf{main result} reveals
-in direct comparison to what was thought to be the case previously, or
-how the main result adds to previous knowledge.
-
-One or two sentences to put the results into a more \textbf{general
-context}.
-
-Two or three sentences to provide a \textbf{broader perspective},
-readily comprehensible to a scientist in any discipline.
+As they develop into mature speakers of their native language, infants
+must not only learn words but also the sounds that make up those words.
+To do so, they must strike a balance between accepting some variation
+(e.g.~mood, voice, accent), but appropriately rejecting variation when
+it changes a word's meaning (e.g.~cat vs.~hat). We focus on studies
+investigating infants' ability to detect mispronunciations in familiar
+words, which we refer to as mispronunciation sensitivity. The goal of
+this meta-analysis was to evaluate the development of mispronunciation
+sensitivity in infancy, allowing for a test of competing mainstream
+theoretical frameworks. The results show that although infants are
+sensitive to mispronunciations, they still accept these altered forms as
+labels for target objects. Interestingly, this ability is not modulated
+by age or vocabulary size, challenging existing theories and suggesting
+that a mature understanding of native language phonology is present in
+infants from an early age. Despite this finding, we discuss potential
+data analysis choices that may influence different conclusions about
+mispronunciation sensitivity development as well as offer
+recommendations to improve best practices in the study of
+mispronunciation sensitivity.
 
@@
 \includegraphics{figures/Figure_1_PRISMA_MA_Mispronunciation.png}
-\caption{}
+\caption{(\#fig:PRISMA\_image)A PRISMA flowchart illustrating the
+selection procedure used to include studies in the current
+meta-analysis.}
 \end{figure}
@@
 \includegraphics{Paper_Analyses_files/figure-latex/FunnelCombo-1.pdf}
-\caption{}
+\caption{\label{fig:FunnelCombo}Funnel plots for object identification,
+plotting the standard error of the effect size in relation to the effect
+size. The black line marks zero, the dashed grey line marks the effect
+estimate, and the grey line marks funnel plot assymetry.}
 \end{figure}
@@
 \includegraphics{Paper_Analyses_files/figure-latex/PlotMPEffect-1.pdf}
-\caption{}
+\caption{\label{fig:PlotMPEffect}Panel a: Effect sizes for correct
+pronunciations (orange) and mispronunciations (blue) by participant age.
+Panel b: Effect sizes for mispronunciation sensitivyt (correct -
+mispronunciations) by participant age. For both panels, point size
+depicts inverse variance and the dashed line indicates zero (chance).}
 \end{figure}
@@
 \includegraphics{Paper_Analyses_files/figure-latex/Vocab_describe1-1.pdf}
-\caption{}
+\caption{(\#fig:Vocab\_describe1)Counts of studies included in the
+meta-analysis as a function of publication year, representing whether
+the study did not measure vocabulary (orange), did measure vocabulary
+and was reported to predict mispronunciation sensitivity (blue), or did
+measure vocabulary and was reported to not predict mispronunciation
+sensitivity (green).}
 \end{figure}
@@
 \includegraphics{Paper_Analyses_files/figure-latex/Plot_post_name_cond_age-1.pdf}
-\caption{}
+\caption{(\#fig:Plot\_post\_name\_cond\_age)Effect sizes for the
+different lengths of post-naming phase time windows analyzed: 2000 ms or
+less (orange), 2001 to 3000 ms (blue), and 3001 ms or greater (green).
+Although length of post-naming phase time window analyzed was included
+as a continuous variable in the meta-analytic model, it is divided into
+categories for ease of viewing. Panel a plots mispronunciation
+sensitivity aggregated over age, while panel b plots mispronunciation
+sensitivity as a function of age. The lines plot the linear regression
+and the gray shaded area indicates the standard error.}
 \end{figure}
@@
 \includegraphics{Paper_Analyses_files/figure-latex/Plot_Within_cond_age_diff_score-1.pdf}
-\caption{}
+\caption{(\#fig:Plot\_Within\_cond\_age\_diff\_score)Effect sizes for
+the different types of dependent variables calculated: Post (orange),
+Post vs.~Pre (blue), and Difference Score (green). Panel a plots
+mispronunciation sensitivity aggregated over age, while panel b plots
+mispronunciation sensitivity as a function of age. The lines plot the
+linear regression and the gray shaded area indicates the standard
+error.}
 \end{figure}
-
-\subsection{Controlling for analysis
-choices}\label{controlling-for-analysis-choices}
-
-{[}Christina: Do you want to add this section?{]}{[}Katie: From what I
-came up with, it makes no difference to the conclusions we make in the
-regular models. But, I am not sure I did it right. I don't really feel
-like they have to be included, but if you think it would be good, then
-we can work on it.{]}
 
@@
 2016; Best et al., 2009; Mulak et al., 2013; Schmale et al., 2010; 2012;
-Schmale \& Seidel, 2009; Floccia et al., 2012; Durrant et al., 2014).
-This allows for an evaluation of phono-lexical development in response
-to a type of language that infants may encounter in everyday life. These
-investigations offer complementary approaches to infant phono-lexical
-development.
+Schmale \& Seidel, 2009; Floccia et al., 2012; Durrant et al., 2014;
+White \& Aslin, 2011). This allows for an evaluation of phono-lexical
+development in response to a type of language that infants may encounter
+in everyday life. These investigations offer complementary approaches to
+infant phono-lexical development.
 

### 2019-01-04 Paper_Analyses.Rmd
implemented Caro's suggestions

@@
 
-  At the turn of the millenia, infant language acquisition researchers had established that during their first years of life, infants are sensitive to changes in the phonetic detail of newly segmented words (Jusczyk & Aslin, 1995) and learned minimal pairs (Stager & Werker, 1997).
-Furthermore, when presented with familiar image pairs, children fixate on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg, & McRoberts, 1998; Tincoff & Jusczyk, 1999).
+  At the turn of the millenium, infant language acquisition researchers had established that during their first years of life, infants are sensitive to changes in the phonetic detail of newly segmented words (Jusczyk & Aslin, 1995) and learned minimal pairs (Stager & Werker, 1997).
+Furthermore, when presented with familiar image pairs, children fixate on the referent of a spoken label (Fernald, Pinto, Swingley, Weinberg, & McRoberts, 1998; Tincoff & Jusczyk, 1999).
 Swingley and Aslin (2000) were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English saw pairs of images (e.g.
@@
 Regarding the change in mispronunciation sensitivity over development, however, only a handful of studies have compared more than one age group on the same mispronunciation task (see Table X), making the current meta-analysis very informative.
-One study has found evidence for infants to become *less* sensitive to mispronunciations as children develop.
+One study has found evidence for infants to become *less* sensitive to mispronunciations as they develop.
 Mani and Plunkett (2011) presented 18- and 24-month-olds with mispronunciations varying in the number of features changed (see below for a discussion of the role of features).
@@
 They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation sensitivity) did not.
-This suggests that as children develop, they are more likely to look at the target in the presence of a mispronounced label and that age is not related to mispronunciation sensitivity.
+This suggests that as children develop, they are more likely to look at the target in the presence of a correct or mispronounced label, but that the difference between the two does not change.
 A similar response pattern has been found for British English learning infants aged between 18 and 24 months (Bailey & Plunkett, 2002) as well as younger French-learning infants at 12 and 17 months (Zesiger, Lozeron, Levy, & Frauenfelder, 2012).
@@
 
+[Katie: Above paragraph changed to improve clarity, per Caroline's suggestion.]
+
   Why would mispronunciation sensitivity change as infants develop, and would it increase or decrease?
-The main hypothesis is related to vocabulary growth.
+The main hypotheses attribute change to vocabulary growth.
 Both the Perceptual Attunement (Best, 1994; 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005; Curtin, Byers-Heinlein, & Werker, 2011) accounts situate a change in mispronunciation sensitivity occurring along with an increase in vocabulary size, particularly with the vocabulary spurt at about 18 months.
-Knowing more words helps infants shift their focus to the relevant phonetic dimensions needed for word recognition.
-On the one hand, a smaller lexicon does not require full specification to differentiate between words; as more phonologically similar words are learned, so does the need to have fully detailed representations for those words (Charles-Luce & Luce, 1995).
-On the other hand, a growing vocabulary is also related to more experience or familiarity with words, which may sharpen the detail of their representation (Barton, 1980).
+As infants learn more words, their focus shifts to the relevant phonetic dimensions needed for word recognition.
+For example, an infant who knows a handful of words with few phonological neighbors would not need to have fully specified phonological representations in order to differentiate between these words.
+As more phonologically similar words are learned, however, the need for fully detailed phonological representations increases (Charles-Luce & Luce, 1995).
+Furthermore, a growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the detail of their phonological representation (Barton, 1980).
+If vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship between vocabulary size and mispronunciation sensitivity.
+
+[Katie: Above paragraph changed to improve clarity, per Caroline's suggestion.]
 
@@
 To take into account the fact that the same infants contributed to multiple datapoints, we analyze our results in a multilevel approach using the R [@R] package metafor [@metafor].
-This means we model as random effect that effect sizes from the same paper share are based on more similar studies than those across papers and that nested therein effects can stem from the same infants.
+We use a random effects model which estimates the mean and variance of effect sizes sampled from an assumed distribution of effect sizes.
+This also takes in to account the interdependence of effect sizes drawn from the same paper.
+
+[Katie: Christina, can you tell me whether the above paragraph is still correct? I've tried to make it easier to read. This was the previous sentence:
+This means we model as random effect that effect sizes from the same paper share are based on more similar studies than those across papers and that nested therein effects can stem from the same infants.]
 
@@
 To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we introduced age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44) as a moderator to our main model.
-For a subsequent exploratory investigations of experimental characteristics, we introduced each characteristic as a moderator (more detail below).
+For a subsequent exploratory investigation of experimental characteristics, we introduced each characteristic as a moderator (more detail below).
 
@@
 Figure 2 shows the funnel plots for both correct pronunciations and mispronunciations (code adapted from Sakaluk, 2016).
-Funnel plot assymmetry was significant for both correct pronunciations (Kendall's $\tau$ = `r r2(rmac$tau)`, *p* `r psig(rmac$pval)`) and mispronunciations (Kendall's $\tau$ = `r r2(rmam$tau)`, *p* `r psig(rmam$pval)`).
-These results, quantifying the assymmetry in the funnel plots (Figure 1), indicate bias in the literature.
+Funnel plot asymmetry was significant for both correct pronunciations (Kendall's $\tau$ = `r r2(rmac$tau)`, *p* `r psig(rmac$pval)`) and mispronunciations (Kendall's $\tau$ = `r r2(rmam$tau)`, *p* `r psig(rmam$pval)`).
+These results, quantifying the asymmetry in the funnel plots (Figure 1), indicate bias in the literature.
 This is particularly evident for correct pronunciations, where larger effect sizes have greater variance (bottom right corner) and there are a smaller number of more precise effect sizes (i.e.
@@
 ```{r FunnelCombo, echo = FALSE, fig.cap="Funnel plots for object identification, plotting the standard error of the effect size in relation to the effect size.
-The black line marks zero, the dashed grey line marks the effect estimate, and the grey line marks funnel plot assymetry."}
+The black line marks zero, the dashed grey line marks the effect estimate, and the grey line marks funnel plot asymmetry."}
 
@@
 The variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was significantly different from zero `r CI_p(sum_eff)`.
-This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research).
-That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object.
-Our analysis of funnel plot asymmetry, however, found evidence for publication bias, which might lead to an overestimated effect sizes as smaller, non-significant results might not be published despite the fact that they should occur regularly even in well-powered studies.
-Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)`, which is substantially above zero, together suggest that this result is somewhat robust.
+This is a large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research).
+That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants tended to fixate on the corresponding object.
+Although the publication bias present in our analysis of funnel plot asymmetry suggests that the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)`, which is substantially above zero, together suggest that this result is somewhat robust.
 In other words, we are confident that the true population mean lies above zero for object recognition of correctly pronounced words.
@@
 
-Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, *p* `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, *p* `r psig(rma_MP$QEp)`), as well as mispronunciation sensitivity, which included the moderator condition, (QE(249) = `r r2(rma_MPeffect$QE)`, *p* `r psig(rma_MPeffect$QEp)`).
-This indicated that the sample contains unexplained variance leading to significant difference across our studies beyond what is to be expected based on random sampling error.
+Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, *p* `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, *p* `r psig(rma_MP$QEp)`), as well as mispronunciation sensitivity, which included the moderator condition (QE(249) = `r r2(rma_MPeffect$QE)`, *p* `r psig(rma_MPeffect$QEp)`).
+This indicated that the sample contains unexplained variance leading to significant difference between studies beyond what is to be expected based on random sampling error.
 We therefore continue with our moderator analysis to investigate possible sources of this variance.
@@
 The interaction between age and mispronunciation sensitivity, however, was not significant ($\beta$ `r full_estimate(sum_eff)`); the moderator test was mainly driven by the difference between conditions.
-The small estimate, as well as inspection of Figure 2 suggests that as infants age, their mispronunciation sensitivity remains the same.
+The small estimate, as well as inspection of Figure 2 suggests that as infants age, their mispronunciation sensitivity neither increases or decreases.
 
@@
 ```{r PlotMPEffect, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for correct pronunciations (orange) and mispronunciations (blue) by participant age.
-Panel b: Effect sizes for mispronunciation sensitivyt (correct - mispronunciations) by participant age.
+Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) by participant age.
 For both panels, point size depicts inverse variance and the dashed line indicates zero (chance)."}
@@
 Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` analyzed the relationship between vocabulary scores and object recognition for correct pronunciations and mispronunciations (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers and `r with(vi1, count[has_vocab == "comprehension"])` records; production = `r with(vi1, papers[has_vocab == "production"])` papers and `r with(vi1, count[has_vocab == "production"])` records).
-There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment; Tomasello & Mervis, 1994), and we therefore planned to analyze these two types of vocabulary measurement separately.
-However, because only `r with(vi1, papers[has_vocab == "production"])` papers reported correlations with productive vocabulary scores, only limited conclusions that can be drawn.
+There is reason to believe that production data are different from comprehension data.
+Children comprehend more words than they can produce, leading to different estimates for comprehension and production.
+Production data is easier to estimate for parents in the typical questionnaire-based assessment and may therefore be more reliable (Tomasello & Mervis, 1994).
+As a result, we planned to analyze these two types of vocabulary measurement separately.
+However, because only `r with(vi1, papers[has_vocab == "production"])` papers reported correlations with productive vocabulary scores, only limited conclusions can be drawn.
 In our vocabulary analysis, we therefore focus exclusively on the relationship between comprehension and mispronunciation sensitivity.
@@
 Figure 4 plots the year of publication for all the mispronunciation sensitivity studies included in this meta-analysis.
-This figure illustrates two things: the growing number of mispronunciation sensitivity studies and the waning number of studies measuring vocabulary.
+This figure illustrates two things: the increasing number of mispronunciation sensitivity studies and the decreasing number of mispronunciation studies measuring vocabulary.
 The lack of evidence for a relationship between mispronunciation sensitivity and vocabulary size in some early studies may have contributed to increasingly fewer researchers including vocabulary measurements in their mispronunciation sensitivity experimental design.
@@
 The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age.
-The results seem clear: Although infants consider a mispronunciation as a better match with the target image than a distractor image, there was a consistent effect of mispronunciation sensitivity.
+The results seem clear: Although infants consider a mispronunciation to be a better match to the target image than to a distractor image, there was a consistent effect of mispronunciation sensitivity.
 This did not change with development nor with vocabulary size.
-Of the 3 predictions and assumptions about the development of infants' sensitivity to mispronunciations discussed in the Introduction, the present results lend some support for the argument that mispronunciation sensitivity stays consistent as infants develop.
+Of the three predictions about the development of infants' sensitivity to mispronunciations discussed in the Introduction, the present results lend some support for the argument that mispronunciation sensitivity stays consistent as infants develop.
 This runs counter to existing theories of phono-lexical development, which predict either an increase (PRIMR ref) or decrease (Assim Model ref) in mispronunciation sensitivity.
@@
 Alternatively, an effect of maturation might have been masked by other factors we have not yet captured in our analyses.
-A strong candidate that emerged during the construction of the present dataset and careful reading of the original papers is the analysis approach.
-We observed, as mentioned in the Methods section, large variance in the dependent variable reported, and additionally noted variance in the size of the time window chosen for analyses.
-Researchers might adapt their analysis strategy to age or they might be influenced by having observed the data.
-In the latter case, we expect an increase in significant results, which at the same time can (partially) explain the publication bias we observe (Simmons, Nelson, & Simonsohn, 2011).
-
-We included details related to timing and type of dependent variable calculated in our coding of the dataset because they are consistently reported and might be useful for experiment design in the future by highlighting typical choices and helping establish field standards.
+A strong candidate that emerged during the construction of the present dataset and careful reading of the original papers was the analysis approach.
+We observed, as mentioned in the Methods section, large variance in the dependent variable reported, and additionally noted variance in the size of the chosen post-naming analysis window.
+Researchers might adapt their analysis strategy to infants' age or they might be influenced by having observed the data.
+For example, consider the possibility that there is a true change in mispronunciation sensitivity over development.
+In this scenario, younger infants should show no sensitivity to mispronunciations while older infants would show large sensitivity to mispronunciations.
+This lack of mispronunciation sensitivity in younger infants may be more difficult to publish (Ferguson & Heene, 2012).
+In order to have publishable results, adjustments to the analysis approach could be made until a significant, but spurious, effect of mispronunciation sensitivity is found.
+This would lead to an increase in significant results and alter to observed developmental trajectory of mispronunciation while also (partially) explaining the publication bias we observe (Simmons, Nelson, & Simonsohn, 2011).
+We examine whether variation in the approach to data analysis may be have an influence on findings of mispronunciation sensitivity.
+
+[Katie: I've changed the above paragraph, particularly regarding why we should find an increase in significant results, as per Caroline's suggestion.]
+
+We included details related to timing and type of dependent variable in our coding of the dataset because they are consistently reported and might be useful for experiment design in the future by highlighting typical choices and helping establish field standards.
 In the following section, we include an exploratory analysis to investigate the possibility of systematic differences in the approach to analysis in general and across infant age.
-The purpose of this analysis is to better understand the influence of choices made in analyzing mispronunciation sensitivity studies as well as the influence these choices may have on our understanding of mispronunciation sensitivity development.
+The purpose of this analysis was to better understand the influence of choices made in analyzing mispronunciation sensitivity studies as well as the influence these choices may have on our understanding of mispronunciation sensitivity development.
 
@@
 
-We identified two sets of variables which had the potential to vary across papers to assess the influence of data analysis choices on resulting effect size: timing (size of time window analyzed; offset time) and which dependent variable(s) were reported.
+We identified two sets of variables which had the potential to vary across papers to assess the influence of data analysis choices on resulting effect size: timing (post-naming analysis window; offset time) and which dependent variable(s) were reported.
 In the following, we discuss the possible theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these analysis choices may have have on measurements of mispronunciation sensitivity development.
@@
 This includes both the length of time before the target object is named (pre-naming phase) as well as after (post-naming phase) and is determined prior to data collection.
-To examine the size of the time window analyzed in the post-naming phase, we must first consider overall length of time post-naming, because it limits the overall time window available to analyze and might thus predict which time window was analyzed.
-Across papers, actual post-naming phase length varied from `r with(post_length_info, min(post_nam_actual))*1000` to `r with(post_length_info, max(post_nam_actual))*1000` ms, with a median value of `r with(dat, median(post_nam_actual))*1000` ms.
-We note that the most popular actual post-naming phase length was `r with(dat, getmode(post_nam_actual))*1000` ms, used in *n* = `r with(post_length_info, n_exp_conditions[post_nam_actual == getmode(post_length_info$n_exp_conditions)])` experimental conditions.
-There was no apparent relation between infant age and overall post-naming phase duration (*r* = `r trial.l$estimate`, 95% CI[`r trial.l$conf.int[1]`, `r trial.l$conf.int[2]`], *p* `r psig(trial.l$p.value)`).
-
-Unlike the actual post-naming phase length, the size of the post-naming time window analyzed can be chosen after the experimental data is collected.
-Interestingly, half of the experimental conditions were analyzed using the same length of post-naming phase as the infant heard in the actual experiment (`r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`), while the other half were analyzed using a shorter portion of the post-naming phase, usually excluding later portions (`r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`).
-Across papers, the length of the post-naming phase analyzed varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a median value of `r with(dat, median(post_nam_dur))*1000` ms.
-We note that the most popular actual post-naming phase length was `r with(dat, getmode(post_nam_dur))*1000` ms, used in *n* = `r with(post_name_info, n_exp_conditions[post_nam_dur == with(dat, getmode(post_nam_dur))])` experimental conditions.
-There was an inverse relationship between infant age and the size of the post-naming time window analyzed, such that younger infants' looking times were analyzed using a longer post-naming time window, here the relationship was significant (*r* = `r post.l$estimate`, 95% CI[`r post.l$conf.int[1]`, `r post.l$conf.int[2]`], *p* `r psig(post.l$p.value)`).
-The choice to analyze a shorter post-naming time window is likely related to evidence that speed of processing is slower in younger infants (Fernald et al., 1998).
-To summarize, we observe variation in time-related aspects related to infants' age.
+To examine the size of the time window analyzed in the post-naming phase (post-naming analysis window), we must first consider overall length of time in post-naming (post-naming time window), because it limits the overall time window available to analyze and might thus predict the post-naming analysis window.
+Across papers, the length of the post-naming time window varied from `r with(post_length_info, min(post_nam_actual))*1000` to `r with(post_length_info, max(post_nam_actual))*1000` ms, with a median value of `r with(dat, median(post_nam_actual))*1000` ms.
+We note that the most popular post-naming time window length was `r with(dat, getmode(post_nam_actual))*1000` ms, used in *n* = `r with(post_length_info, n_exp_conditions[post_nam_actual == getmode(post_length_info$n_exp_conditions)])` experimental conditions.
+There was no apparent relation between infant age and post-naming time window length (*r* = `r trial.l$estimate`, 95% CI[`r trial.l$conf.int[1]`, `r trial.l$conf.int[2]`], *p* `r psig(trial.l$p.value)`).
+
+Unlike the post-naming time window, the post-naming analysis window can be chosen after the experimental data is collected.
+Interestingly, half of the experimental conditions were analyzed using the whole post-naming time window of the trial presented to the infant (*n* = `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`), while the other half were analyzed using a shorter portion of the post-naming time window, usually excluding later portions (*n* = `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`).
+Across papers, the length of the post-naming analysis window varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a median value of `r with(dat, median(post_nam_dur))*1000` ms.
+We note that the most popular post-naming analysis window length was `r with(dat, getmode(post_nam_dur))*1000` ms, used in *n* = `r with(post_name_info, n_exp_conditions[post_nam_dur == with(dat, getmode(post_nam_dur))])` experimental conditions.
+There was an inverse relationship between infant age and post-naming analysis window length, such that younger infants' looking times were analyzed using a longer post-naming analysis window, here the relationship was significant (*r* = `r post.l$estimate`, 95% CI[`r post.l$conf.int[1]`, `r post.l$conf.int[2]`], *p* `r psig(post.l$p.value)`).
+The choice to use a shorter post-naming analysis window with age is likely related to evidence that speed of processing is slower in younger infants (Fernald et al., 1998).
+To summarize, we observe variation in time-related analysis decisions related to infants' age.
 
@@
 
-Although there are a priori reasons to choose the post-naming time window (infant age) or offset time (previous studies), these choices may occur after data collection and might therefore lead to a higher rate of false-positives (Gelman & Loken, 2013).
-Considering that these choices were systematically different across infant ages, at least for the post-naming time window analyzed, we next explored whether the size of time window analyzed or the offset time influenced sensitivity to mispronunciations.
-
-#### Size of post-naming time window analyzed
+Although there are a priori reasons to choose the post-naming analysis window (infant age) or offset time (previous studies), these choices may occur after data collection and might therefore lead to a higher rate of false-positives (Gelman & Loken, 2013).
+Considering that these choices were systematically different across infant ages, at least for the post-naming analysis window, we next explored whether the post-naming analysis window length or the offset time influenced sensitivity to mispronunciations.
+
+#### Post-naming analysis window length
 
@@
 
-We first assessed whether size of the post-naming time window analyzed had an impact on the overall size of the reported mispronunciation sensitivity.
+We first assessed whether size of the post-naming analysis window had an impact on the overall size of the reported mispronunciation sensitivity.
 We considered data from both conditions in a joint analysis and included condition (correct pronunciation, mispronunciation) as an additional moderator.
 The moderator test was significant (`r mod_test(rma_post_dur_MS)`).
-The estimate for the interaction between post-naming phase size and condition was small but significant ($\beta$`r full_estimate(rma_post_dur_MS_eff)`).
+The estimate for the interaction between post-naming analysis window and condition was small but significant ($\beta$`r full_estimate(rma_post_dur_MS_eff)`).
 This relationship is plotted in Figure 3a.
-The results suggest that the size of the post-naming phase analyzed significantly impacted mispronunciation sensitivity.
-Specifically, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) was significantly greater when the post-naming phase was shorter.
-
-Considering that we found a significant relationship between the length of the post-naming time window analyzed and infant age, such that younger ages had a longer window of analysis, we next examined whether the size of post-naming time window analyzed modulated the estimated size of mispronunciation sensitivity as infant age changed.
+The results suggest that the size of the post-naming analysis window significantly impacted mispronunciation sensitivity.
+Specifically, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) was significantly greater when the post-naming analysis window was shorter.
+
+Considering that we found a significant relationship between the length of the post-naming analysis window and infant age, such that younger ages had a longer window of analysis, we next examined whether the size of the post-naming analysis window modulated the estimated size of mispronunciation sensitivity as infant age changed.
 We therefore included age as additional moderator of the previous analysis.
 The moderator test was significant (`r mod_test(rma_post_dur_AGE_MS)`).
-The estimate for the  three-way-interaction between condition, size of post-naming phase, and age was small, but significant ($\beta$ = `r full_estimate(rma_post_dur_AGE_MS_eff)`).
-As can be seen in Figure 3b, smaller post-naming time window size leads to greater increases in measured mispronunciation sensitivity with development.
-For example, when experimental conditions were analyzed with a post-naming time window of 2000 ms or less, mispronunciation sensitivity is found to increase with infant age.
-If the post-naming time window analyzed is greater than 2000 ms, however, there is no or a negative relation of mispronunciation sensitivity and age.
-In other words, all three possible developmental hypotheses might be supported depending on analysis choices made regarding the size of the post-naming time window to analyze.
+The estimate for the  three-way-interaction between condition, size of the post-naming analysis window, and age was small, but significant ($\beta$ = `r full_estimate(rma_post_dur_AGE_MS_eff)`).
+As can be seen in Figure 3b, a smaller post-naming analysis window leads to a greater increase in measured mispronunciation sensitivity with development.
+For example, when experimental conditions were analyzed with a post-naming analysis window of 2000 ms or less, mispronunciation sensitivity was found to increase with infant age.
+If the post-naming analysis window is greater than 2000 ms, however, there is no or a negative relation of mispronunciation sensitivity and age.
+In other words, all three possible developmental hypotheses might be supported depending on analysis choices made regarding the size of the post-naming analysis window.
 This is especially important, considering that our key question is how mispronunciation sensitivity changes with development.
-These results suggest that conclusions about the relationship between infant age and mispronunciation sensitivity may be mediated by the size of the post-naming time window analyzed.
+These results suggest that conclusions about the relationship between infant age and mispronunciation sensitivity may be mediated by the size of the post-naming analysis window.
 
@@
 
-```{r Plot_post_name_cond_age, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different lengths of post-naming phase time windows analyzed: 2000 ms or less (orange), 2001 to 3000 ms (blue), and 3001 ms or greater (green).
-Although length of post-naming phase time window analyzed was included as a continuous variable in the meta-analytic model, it is divided into categories for ease of viewing.
+```{r Plot_post_name_cond_age, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different lengths of the post-naming analysis window: 2000 ms or less (orange), 2001 to 3000 ms (blue), and 3001 ms or greater (green).
+Although length of the post-naming analysis window was included as a continuous variable in the meta-analytic model, it is divided into categories for ease of viewing.
 Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity as a function of age.
@@
 
-We next assessed whether the time between the target was named and the start of the analysis, namely offset time, had an impact on the size of the reported mispronunciation sensitivity.
+We next assessed whether the time between target naming and the start of the analysis, namely offset time, had an impact on the size of the reported mispronunciation sensitivity.
 When we included both condition and offset time as moderators, the moderator test was significant (`r mod_test(rma_post_dur_MS)`), but the estimate for the interaction between offset time and condition was almost zero ($\beta$`r full_estimate(rma_offset_MS_eff)`).
-Although we found no relationship between offset time and infant age, we also examined whether the size of offset time modulated the the measure of mispronunciation sensitivity over infant age.
+Although we found no relationship between offset time and infant age, we also examined whether the size of offset time modulated the measure of mispronunciation sensitivity over infant age.
 When both offset time and condition were included as moderators, the moderator test was significant (`r mod_test(rma_offset_AGE_MS)`), but the three-way-interaction between condition, offset time, and age was very small and not significant ($\beta$ = `r full_estimate(rma_offset_AGE_MS_eff)`.
@@
 
-We next examined whether the type of dependent variable calculated modulated the the estimated change in mispronunciation sensitivity over infant age.
+We next examined whether the type of dependent variable calculated modulated the estimated change in mispronunciation sensitivity over infant age.
 When age was included as an additional moderator, the moderator test was significant (`r mod_test(rma_within_AGE_MS)`).
@@
 
-Similar to size of post-naming time window analyzed, all three possible developmental hypotheses might be supported depending on the dependent variable reported.
+Similar to the length of the post-naming analysis window, all three possible developmental hypotheses might be supported depending on the dependent variable reported.
 In other words, choice of dependent variable may influence the conclusion drawn regarding how mispronunciation sensitivity may change with infant age.
@@
 
-Evidence that infants accept a mispronunciation (object identification) while simultaneously holding correctly pronounced and mispronounced labels as separate (mispronunciation sensitivity) may indcate an abstract understanding of words' phonological structure.
-It appears that young infants may understand that the mispronunciation and correct pronunciation's phonological form do not match (phonological distinctiveness), but that the mispronunciation is a better label for the target compared to the distractor image (phonological constancy).
+Evidence that infants accept a mispronunciation (object identification) while simultaneously holding correctly pronounced and mispronounced labels as separate (mispronunciation sensitivity) may indicate an abstract understanding of words' phonological structure.
+It appears that young infants may understand that the phonological form of mispronunciations and correct pronunciations do not match (phonological distinctiveness), but that the mispronunciation is a better label for the target compared to the distractor image (phonological constancy).
 The lack of age or vocabulary effects in our meta-analysis suggest that this understanding is present from an age when the earliest words are learned and is maintained throughout early lexical development.
@@
 
-Although the lack of an relationship between mispronunciation sensitivity and vocabulary size may reflect a true effect, we note that this may also be the result of an underpowered analysis.
-Despite the theoretical implications, less than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total).
-We suggest that this may be the result of publication bias, specifically a desire to not publish null results.
-Although the number of mispronunciation sensitivity studies per year has seen an increase, this has not translated to an increasing number of mispronunciation sensitivity studies also measuring vocabulary scores.
-
-[Katie] The above paragraph is a bit clunky and I don't like it. Any suggestions for improvement?
+Although the lack of a relationship between mispronunciation sensitivity and vocabulary size may reflect a true effect, we note that this may also be the result of an underpowered analysis.
+Despite the theoretical implications, fewer than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total).
+We suggest that this may be the result of publication bias.
+There are more mispronunciation sensitivity studies published every year, but this has not translated to an increasing number of mispronunciation sensitivity studies also measuring vocabulary scores.
 
@@
 While creating the dataset on which this meta-analysis was based, we included as many details as possible to describe each study.
-During the coding of these characteristics, we noted a potential for variation in a handful of variables that relate to data analysis, specifically relating to timing (size of time window analyzed; offset time) and which dependent variable(s) were reported.
-We focused on these variables in particular because their choice can potentially be made after researchers have examined the data, leading to an inflated increase of significant results which may also explain the publication bias observed in the funnel plot assymmetry (Simmons, Nelson, & Simonsohn, 2011).
+During the coding of these characteristics, we noted a potential for variation in a handful of variables that relate to data analysis, specifically relating to timing (post-naming analysis window; offset time) and to the calculation of the dependent variable reported.
+We focused on these variables in particular because their choice can potentially be made after researchers have examined the data, leading to an inflated increase of significant results which may also explain the publication bias observed in the funnel plot asymmetry (Simmons, Nelson, & Simonsohn, 2011).
 To explore whether this variation contributed to the lack of developmental change observed in the overall meta-analysis, we included these variables as moderators in a set of exploratory analyses.
-We noted an interesting pattern of results, specifically that different conclusions about mispronunciation sensitivity, but more notably mispronunciation sensitivity development, could be drawn depending on the length of the post-naming time window analyzed as well as the type of dependent variable calculated in the experiment.
+We noted an interesting pattern of results, specifically that different conclusions about mispronunciation sensitivity, but more notably mispronunciation sensitivity development, could be drawn depending on the length of the post-naming analysis window as well as the type of dependent variable calculated in the experiment.
 
@@
 Infants are expected to recognize words more quickly with age (Fernald, Swingley & Pinto, 2001; Swingley, Pinto & Fernald, 1999; Swingley & Fernald, 2002).
-This evidence has often guided decisions for the post-naming time window to be analyzed in mispronunciation sensitivity studies, including where to begin the time window (offset time) and how long this window should be (post-naming time window analyzed).
+This evidence has often guided decisions for the post-naming time window in mispronunciation sensitivity studies, including where to begin the time window (offset time) and how long this analysis window should be (post-naming analysis window).
 Specifically, increasing age should lead to quicker reaction times, and therefore lower offset times.
 Yet, we found no evidence for a relationship between offset time and infant age nor that offset time modulated mispronunciation sensitivity.
-Indeed, a large majority used an offset time between 360 and 370 ms, which follows the best guess of Swingley and Aslin (2000) for the amount of time needed for infants to initiate eye movements in response to a spoken target word.
-
-In contrast, the length of the post-naming window analyzed was related to infant age and also found to modulate mispronunciation sensitivity.
+Indeed, a majority of studies used an offset time between 360 and 370 ms, which follows the best guess of Swingley and Aslin (2000) for the amount of time needed for infants to initiate eye movements in response to a spoken target word.
+
+In contrast, the length of the post-naming analysis window was related to infant age and was also found to modulate mispronunciation sensitivity.
 Younger infants may take longer to reliably identify the target image, and as a result the length of the post-naming time window analyzed may be longer in younger infants.
-This was born out in the meta-analysis: studies that tested younger infants used a longer post-naming time window.
-Longer post-naming time windows, however, resulted in a smaller effect size for mispronunciation sensitivity.
-Critically, the developmental trajectory of mispronunciation sensitivity changed depending on the length of the post-naming time window analyzed.
-Longer time windows resulted in decreasing or no change in mispronunciation sensitivity, while shorter time windows resulting in increasing mispronunciation sensitivity.
-Given a set of mispronunciation sensitivity data, a conclusion regarding the development of mispronunciation sensitivity would be different depending on the length of the post-naming time window analyzed.
+This was born out in the meta-analysis: studies that tested younger infants used a longer post-naming analysis window.
+Longer post-naming analysis windows, however, resulted in a smaller effect size for mispronunciation sensitivity.
+Critically, the developmental trajectory of mispronunciation sensitivity changed depending on the length of the post-naming analysis window.
+Longer analysis windows resulted in decreasing or no change in mispronunciation sensitivity, while shorter analysis windows resulting in increasing mispronunciation sensitivity.
+Given a set of mispronunciation sensitivity data, a conclusion regarding the development of mispronunciation sensitivity would be different depending on the length of the post-naming analysis window.
 
@@
 
-A lack of a field standards can have dire consequences, as our analyses show.
+A lack of a field standard can have serious consequences, as our analyses show.
 Depending on which analysis time window (see Figure 5) or dependent variable (see Figure 6) we focus on, we find support for any of the three possible trajectories of mispronunciation sensitivity.
@@
 
-We take this opportunity to suggest several remedies.
+We take this opportunity to suggest several solutions.
 Preregistration can serve as proof of a priori decisions regarding data analysis or describing how data analysis decisions will be made once data is collected.
 The peer reviewed form of Registered Reports has already been adopted by a large number of developmental journals, and general journals that publish developmental works, showing the field's increasing acceptance of such practices.
-Open data can allow others to re-analyze existing datasets to both examine the impact of analysis decisions and cumulatively analyze different datasets in the same way.
-Furthermore, experimenters can analyze the time course as a whole, instead of aggregating the proportion of target looking behavior over the entire trial.
-This allows for a more detailed assessment of infants' fixations over time and reduces the need to reduce the time window of the post-naming phase for analysis.
+Sharing data (Open Data) can allow others to re-analyze existing datasets to both examine the impact of analysis decisions and cumulatively analyze different datasets in the same way.
+Experimenters can also opt to analyze the time course as a whole, instead of aggregating the proportion of target looking behavior over the entire trial.
+This allows for a more detailed assessment of infants' fixations over time and reduces the need to reduce the post-naming analysis window.
 Both Growth Curve Analysis (Mirman et al., 2008; Law & Edwards, 2015) and Permutation Clusters Analysis (Maris & Oostenveld, 2007; Von Holzen & Mani, 2012; Delle Luche et al., 2015) offer potential solutions to analyze the full time course.
-In general, however, it may be useful to establish standard analysis pipelines for mispronunciation studies.
+Furthermore, it may be useful to establish standard analysis pipelines for mispronunciation studies.
 This would allow for a more uniform analysis of this phenomenon, as well as aid experimenters in future research planning.
-
-[Christina: Are we submitting to a place with registered reports? We should!]
-[Katie: We had been aiming for Cognition, but it doesn't have registered reports. But, Dev Sci does, although we're about 3,000 words above their word limit (Cognition doesn't have a word limit).]
-
-[Katie: this is a good paragraph, but I'm not sure where it fits. Its rather not specific for our current meta-analysis, but a general comment about the field.]
+In general, however, a better understanding of how different levels of linguistic knowledge may drive looking behavior is needed.
+We hope this understanding can be achieved by applying the above suggestions.
+
+[Katie: I've rewritten the above paragraph as per Caroline's suggestion. I'm not very happy with the last sentence, but I don't want to leave the thought hanging.]
+
+[Katie: Below is a good paragraph, but I'm not sure where it fits. Its rather not specific for our current meta-analysis, but a general comment about the field.]
 
@@
 A meta-analysis is a first step in improving experiment planning by measuring the underlying effect and its variance, which is directly related to the sample needed to achieve satisfactory power in the null hypothesis significance testing framework.
-Failing to take effect sizes into account can both yield to underpowered research and to testing too many participants, both consequences are undesirable for a number of reasons that have been discussed in depth elsewhere.
+Failing to take effect sizes into account can both lead to underpowered research and to testing too many participants, both consequences are undesirable for a number of reasons that have been discussed in depth elsewhere.
 We will just briefly mention two that we consider most salient for theory building: Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature (citationcitation).
-Overpowered studies mean that participants were tested unnecessarily, which has substantial ethical consequences particularly when working with infants and other difficult to recruit and test populations.
+Overpowered studies mean that participants were tested unnecessarily, which has ethical implications particularly when working with infants and other difficult to recruit and test populations.
 
@@
 
-Furthermore, the investigation of mispronunciation sensitivity does not singularly capture infant phono-lexical development.
-For example, studies investigating word form recognition, typically using the Headturn Preference Procedure (Mandel et al., 1995), allow for an investigation of the specificity of infants' word form representations without requiring word-object associations, which is required in the Intermodal Preferential Looking Paradigm (Golinkoff et al., 1987; 2013).
-As a result, this approach can be used with infants of a much younger age than typically examined.
-These studies compare infants' preference to listen to word lists that a correct compared to word lists that contain a mispronunciation (e.g.
-Bouchon et al., 2014; Swingley, 2005; Halle & de Boysson-Bardies, 1996; Vihman et al., 2004; Vihman & Majorano 2016; 2017; Poltrock & Nazzi, 2015; Delle Luche et al., 2016).
-In contrast, studies investigating recognition of accented words use stimuli that are naturally occuring as opposed to artificially manipulated, to achieve an altered phonological form (e.g.
-van Heughten et al., 2018; 2015; Buckler et al., 2017; van Heughten & Johnson, 2014; 2016; Best et al., 2009; Mulak et al., 2013; Schmale et al., 2010; 2012; Schmale & Seidel, 2009; Floccia et al., 2012; Durrant et al., 2014; White & Aslin, 2011).
-This allows for an evaluation of phono-lexical development in response to a type of language that infants may encounter in everyday life.
-These investigations offer complementary approaches to infant phono-lexical development.
-
 ## Conclusion

### 2019-01-10 Paper_Analyses.Rmd
added references, organized old files

@@
 
+bibliography      : ["MISP_MA_BIB.bib"]
+
 floatsintext      : no
@@
 draft             : no
-citeproc          : no
 
@@
 classoption       : "man"
-output            : papaja::apa6_docx
+output            : papaja::apa6_pdf
 
@@
 # https://github.com/benmarwick/wordcountaddin
-
-# bibliography      : ["MISP_MA_BIB.bib"]
-
-# [KATIE] BIBLIOGRAPHY CURRENTLY REMOVED, AS IT IS CAUSING ERRORS WITH PAPAJA
-# THIS IS PARTIALLY DUE TO THE WAY I CREATE IT USING MENDELEY. 
-# TOO LAZY FOR THE MOMENT TO COMPLETELY OVERHAUL THIS
-
-# BUT, OTHER PROBLEMS INCLUDE HAVING PAPAJA INSTALLED IN THE USER AND NOT SYSTEM LIBRARY
-# https://github.com/crsh/papaja/issues/162
-# devtools::with_libpaths(new = "/usr/lib/R/library/", install_github('crsh/papaja'))
-
-# AND THE NEED TO SET citeproc: no
-# https://github.com/crsh/papaja/issues/96
-
-# STILL NEED TO FIGURE OUT WHAT ACTUAL PROBLEM IS, THIS IS CURRENTLY JUST A WORKAROUND
 
@@
 Acquiring a first language means that young learners are solving a host of tasks in a short amount of time.
-As infants develop into toddlers during their second and third years they learn new words in earnest while simultaneously refining their knowledge about the sounds that make up these words [Primir, Kuhl, Best].
-In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonetic details that differentiate words in their native language (e.g.
+As infants develop into toddlers during their second and third years they learn new words in earnest while simultaneously refining their knowledge about the sounds that make up these words [@Kuhl2004; @Curtin2007; @Werker2005; @Best1994; @Best1995].
+In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonetic details that differentiate words in a given language (e.g.
 cat-hat).
 To build robust language knowledge, it seems ueful to acquire this ability early during development.
-Indeed, before children can correctly pronounce a word, they already are aware that slight phonological deviations might signal a change in word meaning [Clark & Clark, 1977].
+Indeed, before children can correctly pronounce a word, they already are aware that slight phonological deviations might signal a change in word meaning [@clark1977].
 This mispronunciation sensitivity reflects the specificity with which infants represent the phonological information of familiar words.
 As infants continue to develop into expert language users, their language processing matures and becomes more efficient, including their knowledge of what consistutes a permissible versus word-changing phonological deviation.
-In this paper, we aggregate and analyze the almost 20 years of literature investigating mispronunciation sensitivity in infants in an attempt to uncover its characteristics and the trajectory of its development.
-
-  At the turn of the millenium, infant language acquisition researchers had established that during their first years of life, infants are sensitive to changes in the phonetic detail of newly segmented words (Jusczyk & Aslin, 1995) and learned minimal pairs (Stager & Werker, 1997).
-Furthermore, when presented with familiar image pairs, children fixate on the referent of a spoken label (Fernald, Pinto, Swingley, Weinberg, & McRoberts, 1998; Tincoff & Jusczyk, 1999).
-Swingley and Aslin (2000) were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English saw pairs of images (e.g.
+In this paper, we aggregate and analyze the nearly 20 years of literature investigating mispronunciation sensitivity in infants in an attempt to uncover its characteristics and the trajectory of its development.
+
+  At the turn of the millenium, infant language acquisition researchers had established that during their first years of life, infants are sensitive to changes in the phonetic detail of newly segmented words [@Jusczyk1995] and learned minimal pairs [@Stager1997].
+Furthermore, when presented with familiar image pairs, children fixate on the referent of a spoken label [@Fernald1998; @Tincoff1999].
+@Swingley2000 were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English saw pairs of images (e.g.
 a baby and a dog) and their eye movements to each image were recorded and subsequently coded offline.
@@
 We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance in each condition as *object identification*.
-Swingley and Aslin (2000) concluded that already before the second birthday, children represent words with sufficient detail to be sensitive to mispronunciations.
-
-  The study of Swingley and Aslin (2000) as well as subsequent studies examining mispronunciation sensitivity address two complementary principles that infants must discover in early phonological development in order to form adult-like word representations: *phonological constancy* and *phonological distinctiveness*.
+@Swingley2000 concluded that already before the second birthday, children represent words with sufficient detail to be sensitive to mispronunciations.
+
+  The study of @Swingley2000 as well as subsequent studies examining mispronunciation sensitivity address two complementary principles that infants must discover in early phonological development in order to form adult-like word representations and processing capabilities: *phonological constancy* and *phonological distinctiveness*.
 Phonological constancy is the ability to resolve phonological variation across different instances of a word, as long as the variation does not compromise the overall identity of the word.
@@
 Considering that infants are sensitive to mispronunciations and that, in general, their processing matures with development, we examine the shape of mispronunciation sensitivity over the course of the second and third year.
-There are three distinct possibilities how mispronunciation sensitivity might change as infants become native speakers, which are all respectively supported by single studies and two predicted by theoretical accounts.
+There are three distinct possibilities how mispronunciation sensitivity might change as infants become native speakers, which are all respectively supported by single studies and additionally two possibilities are predicted by key theoretical accounts.
 By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see Frank et al., 2018; for a notable exception).
@@
 
+[Katie: Christina, do you know which citation the Frank et al., 2018 citation is referring to above? He's published a gazilion papers in 2018]
+
   Young infants may begin cautiously in their approach to word recognition, rejecting any phonological variation in familiar words and only later learning to accept appropriate variability.
-According to the Perceptual Attunement account, this describes a shift away from specific native phonetic patterns to a more mature understanding of the abstract phonological structure of words (Best 1994, 1995).
-This shift is predicted to coincide with the vocabulary spurt around 18 months, and is therefore related to vocabulary growth.
+According to the Perceptual Attunement account, this describes a shift away from specific native phonetic patterns to a more mature understanding of the abstract phonological structure of words [@Best1994; @Best1995].
+This shift is predicted to coincide with the vocabulary spurt around 18 months, because it is causally related to vocabulary growth.
 In this case, we would expect the size of mispronunciation sensitivity to be larger at younger ages and *decrease* as the child matures and learn more words, although children continue to detect mispronunciations.
-Indeed, young infants are more perturbed by accented speakers than older infants in their recognition of familiar words (Best, Tyler, Gooding, Orlando, & Quann, 2009; Mulak, Best, & Tyler, 2013) or learning of new words (Schmale, Hollich, & Seidl, 2011).
+Indeed, young infants are more perturbed by accented speakers than older infants in their recognition of familiar words [@Best2009; @Mulak2014] or learning of new words [@Schmale2011].
 
   According to a different theoretical framework, young infants may instead begin with phonologically broad representations for familiar words and only refine their representations as language experience accumulates.
-PRIMIR (Processing Rich Information from Multidimensional Interactive Representations; Curtin & Werker, 2007; Werker & Curtin, 2005; Curtin, Byers-Heinlein, & Werker, 2011) describes the development of phonemic categories emerging as the number of word form-meaning linkages increases.
+PRIMIR ([Processing Rich Information from Multidimensional Interactive Representations; @Curtin2007; @Curtin2011; @Werker2005]) describes the development of phonemic categories emerging as the number of word form-meaning linkages increases.
 Vocabulary growth, therefore, promotes more detailed phonological representations in familiar words.
@@
 
-  Research following the seminal study by Swingley and Aslin (2000) has extended mispronunciation sensitivity to infants as young as 9 months (Bergelson & Swingley, 2017), indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations.
-Regarding the change in mispronunciation sensitivity over development, however, only a handful of studies have compared more than one age group on the same mispronunciation task (see Table X), making the current meta-analysis very informative.
+  Research following the seminal study by @Swingley2000 has extended mispronunciation sensitivity to infants as young as 9 months [@Bergelson2017], indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations.
+Regarding the change in mispronunciation sensitivity over development, however, only about half of studies have compared more than one age group on the same mispronunciation task (see Table 1), making the current meta-analysis very informative.
 One study has found evidence for infants to become *less* sensitive to mispronunciations as they develop.
-Mani and Plunkett (2011) presented 18- and 24-month-olds with mispronunciations varying in the number of features changed (see below for a discussion of the role of features).
+@Mani2011 presented 18- and 24-month-olds with mispronunciations varying in the number of phonological features changed (e.g., changing an p into a b, a 1-feature change, versus changing a p into a g, a 2-feature change).
 18-month-olds were sensitive to mispronunciations, regardless of the number of features changed.
@@
   In contrast, other studies have found evidence for *greater* mispronunciation sensitivity as children develop.
-More precisely, the difference in target looking for correct and mispronounced trials is smaller in younger infants and grows as infants develop.
-Mani and Plunkett (2007) tested 15-, 18-, and 24-month-olds learning British English; although all three groups were sensitive to mispronunciations, 15-month-olds showed a less robust sensitivity.
-An increase in sensitivity to mispronunciations has also been found from 20 to 24 months (van der Feest & Fikkert, 2015) and 15 to 18 months (Altvater Mackensen et al., 2013) in Dutch infants, as well as German infants from 22 to 25 months (Altvater-Mackensen, 2010).
-Furthermore, van der Feest and Fikkert (2015) found that sensitivity to specific kinds of mispronunciations develop at different ages depending on language infants are learning.
+More precisely, the difference in target looking for correct and mispronounced trials is reported to be smaller in younger infants and grows as infants develop.
+@Mani2007 tested 15-, 18-, and 24-month-olds learning British English; although all three groups were sensitive to mispronunciations, 15-month-olds showed a less robust sensitivity.
+An increase in sensitivity to mispronunciations has also been found from 20 to 24 months [@vanderFeest2015] and 15 to 18 months [@Altvater2014] in Dutch infants, as well as German infants from 22 to 25 months [@Altvater2010].
+Furthermore, @vanderFeest2015 found that sensitivity to specific kinds of mispronunciations develop at different ages depending on language infants are learning.
 In other words, the native language constraints which *kinds* of mispronunciations infants are sensitive to first, and that as infants develop, they become sensitive to other mispronunciations.
@@
 Finally, some studies have found no difference in mispronunciation sensitivity at different ages.
-Swingley and Aslin (2000) tested infants over a wide age range of 5 months (18 to 23 months).
+@Swingley2000 tested infants over a wide age range of 5 months (18 to 23 months).
 They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation sensitivity) did not.
 This suggests that as children develop, they are more likely to look at the target in the presence of a correct or mispronounced label, but that the difference between the two does not change.
-A similar response pattern has been found for British English learning infants aged between 18 and 24 months (Bailey & Plunkett, 2002) as well as younger French-learning infants at 12 and 17 months (Zesiger, Lozeron, Levy, & Frauenfelder, 2012).
+A similar response pattern has been found for British English learning infants aged between 18 and 24 months [@Bailey2002] as well as younger French-learning infants at 12 and 17 months [@Zesiger2012].
 These studies award support to the prediction that mispronunciation sensitivity does not change with development.
-
-[Katie: Above paragraph changed to improve clarity, per Caroline's suggestion.]
 
@@
 The main hypotheses attribute change to vocabulary growth.
-Both the Perceptual Attunement (Best, 1994; 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005; Curtin, Byers-Heinlein, & Werker, 2011) accounts situate a change in mispronunciation sensitivity occurring along with an increase in vocabulary size, particularly with the vocabulary spurt at about 18 months.
+Both the Perceptual Attunement [@Best1994; @Best1995] and PRIMIR [@Curtin2007; @Werker2005; @Curtin2011] accounts situate a change in mispronunciation sensitivity occurring along with an increase in vocabulary size, particularly with the vocabulary spurt at about 18 months.
 As infants learn more words, their focus shifts to the relevant phonetic dimensions needed for word recognition.
 For example, an infant who knows a handful of words with few phonological neighbors would not need to have fully specified phonological representations in order to differentiate between these words.
-As more phonologically similar words are learned, however, the need for fully detailed phonological representations increases (Charles-Luce & Luce, 1995).
-Furthermore, a growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the detail of their phonological representation (Barton, 1980).
+As more phonologically similar words are learned, however, the need for fully detailed phonological representations increases [@CharlesLuce1995].
+Furthermore, a growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the detail of their phonological representation [@Barton1980].
 If vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship between vocabulary size and mispronunciation sensitivity.
 
-[Katie: Above paragraph changed to improve clarity, per Caroline's suggestion.]
-
-  Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship (Swingley & Aslin 2000; 2002; Bailey & Plunkett, 2002; Zesiger, Lozeron, Levy, & Frauenfelder, 2012; Swingley, 2009; Ballem & Plunkett, 2005; Mani & Plunkett, 2007; Mani, Coleman, & Plunkett, 2008).
-One notable exception comes from Mani and Plunkett (2010: keps and tups).
+  Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship [@Swingley2000; @Swingley2002; @Swingley2009; @Zesiger2012; @Mani2008; @Bailey2002; @Mani2007; @Ballem2005].
+One notable exception comes from @Mani2010kepstups.
 Here, 12-month-old infants were divided into a low and high vocabulary group based on median vocabulary size.
@@
 In sum, the studies we have reviewed begin to paint a picture of the development of mispronunciation sensitivity.
-Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding of early language development.
-Meta-analyses can provide thus further insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and their mispronunciations sensitivity.
+Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding of the big picture of early language development.
+Meta-analyses can provide unique insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and their mispronunciations sensitivity.
 Because we aggregate data over various age groups, this meta-analysis can also investigate the role of maturation by assessing the impact of age and vocabulary size.
 As a consequence, our results will be important in evaluating theories and drive future research.
-We also make hands-on recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses (Bergmann et al., 2018).
+We also make hands-on recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses [@Bergmann2018].
 
@@
 The present meta-analysis was conducted with maximal transparency and reproducibility in mind.
-To this end, we provide all data and analysis scripts on the supplementary website (https://osf.io/rvbjs/) and open our meta-analysis up for updates (Tsuji, Bergmann, & Cristia, 2014).
-The most recent version is available via the website and the interactive platform MetaLab (metalab.stanford.edu; Bergmann et al., 2018).
+To this end, we provide all data and analysis scripts on the supplementary website (https://osf.io/rvbjs/) and open our meta-analysis up for updates [@Tsuji2014].
+The most recent version is available via the website and the interactive platform MetaLab ([https://metalab.stanford.edu; @Bergmann2018]).
 Since the present paper was written with embedded analysis scripts in R [@R, @RMarkdown, @papaja], it is always possible to re-analyze an updated dataset.
-In addition, we followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials (Moher, Liberati, Tetzlaff, Altman & PRISMAGroup, 2009).
+In addition, we followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials [@Moher2009].
 Figure 1 plots our PRISMA flowchart illustrating the paper selection procedure.
@@
 This process yielded 110 items.
-We then used the google scholar search engine to search for papers citing the original Swingley & Aslin (2000) publication.
+We then used the google scholar search engine to search for papers citing the original @Swingley2000 publication.
 This search was conducted on 22 September, 2017 and yielded 288 results.
 We removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech.
-The final sample (n = *`r length(unique(descriptive_dat$short_cite))`*) consisted of `r with(descriptive_dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "dissertation"]))` thesis, and `r with(descriptive_dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports.
+The final sample (n = *`r length(unique(descriptive_dat$short_cite))`*) consisted of `r with(descriptive_dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "dissertation"]))` theses, and `r with(descriptive_dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports.
 We will refer to these items collectively as papers.
@@
 
-The `r length(unique(descriptive_dat$short_cite))` papers we identified as relevant were then coded with as much consistently reported detail as possible (Tsuji, Bergmann, & Cristia, 2014; Bergmann et al., 2018).
+The `r length(unique(descriptive_dat$short_cite))` papers we identified as relevant were then coded with as much consistently reported detail as possible [@Tsuji2014; @Bergmann2018].
 For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results.
@@
 We separated conditions according to whether or not the target word was mispronounced to be able to investigate infants' looking to the target picture as well as their mispronunciation sensitivity, which is the difference between looks to the target in correct and mispronounced trials.
-When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  (e.g., consonant versus vowel mispronunciations; Mani & Plunkett, 2007).
+When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  ([e.g., consonant versus vowel mispronunciations; @Mani2007]).
 The fact that the same infants contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section).
@@
 The most well-known effect size from this group is Cohen's *d* [@cohen].
-To correct for the small sample sizes common in infant research, however, we used as a dependent variable Hedges' *g* instead of Cohen's *d* (Hedges, 1981; Morris, 2000).
-
-We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, sum(count[es_method == "group_means_one" | es_method == "group_means_two"]))` records from `r with(es_info, sum(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))` papers) or using reported t-values (*n* = `r with(es_info, sum(count[es_method == "t_one" | es_method == "t_two"]))` records from `r with(es_info, sum(n_unique[es_method == "t_one" | es_method == "t_two"]))` papers).
-Two papers reported raw means and standard deviations for some experimental conditions and just t-values for the remaining experimental conditions (Swingley, 2016; Altvater-Mackensen et al., 2014).
+To correct for the small sample sizes common in infant research, however, we used Hedges' *g* instead of Cohen's *d* [@Hedges1981; @morris2002combining].
+
+We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, sum(count[es_method == "group_means_one" | es_method == "group_means_two"]))` records from `r with(es_info, sum(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))` papers) or reported t-values (*n* = `r with(es_info, sum(count[es_method == "t_one" | es_method == "t_two"]))` records from `r with(es_info, sum(n_unique[es_method == "t_one" | es_method == "t_two"]))` papers).
+Two papers reported raw means and standard deviations for some experimental conditions and just t-values for the remaining experimental conditions [@Swingley2016; @Altvater2014].
 Raw means and standard deviations were extracted from figures for `r with(descriptive_dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers.
-In a within-participation design, when two means are compared (i.e.
-looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values.
-Upon request we were provided with correlation values for one paper (Altvater-Mackensen, 2010); we were able to compute correlations using means, standard deviations, and t-values for *n* = `r with(corr_info, n_unique[imputed_corr == "no"])` (following Csibra, et al.
-2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, 2018).
-Correlations were imputed for the remaining papers (see Black & Bergmann, 2017, for the same procedure).
-For two papers, we could not derive any effect size (Ballem & Plunkett, Renner), and for a third paper, we do not have sufficient information in one record to compute effect sizes (Skoruppa).
+In a within-participant design, when two means are compared (i.e.
+looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance.
+Upon request we were provided with correlation values for one paper [@Altvater2010]; we were able to compute correlations using means, standard deviations, and t-values for `r with(corr_info, n_unique[imputed_corr == "no"])` papers ([following @Csibra2016; see also @Rabagliati2018]).
+Correlations were imputed for the remaining papers ([see @Black2017 for the same procedure]).
+For two papers, we could not derive any effect size [@Ballem2005; @Renner2017], and for a third paper, we do not have sufficient information in one record to compute effect sizes [@Skoruppa2013].
 We compute a total of `r sum(dat$is_mp == 0)+n_outlier_correct` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)+n_outlier_MP` for mispronunciations.
@@
 
+[Katie: Mention of Renner here]
+
 To take into account the fact that the same infants contributed to multiple datapoints, we analyze our results in a multilevel approach using the R [@R] package metafor [@metafor].
-We use a random effects model which estimates the mean and variance of effect sizes sampled from an assumed distribution of effect sizes.
-This also takes in to account the interdependence of effect sizes drawn from the same paper.
-
-[Katie: Christina, can you tell me whether the above paragraph is still correct? I've tried to make it easier to read. This was the previous sentence:
-This means we model as random effect that effect sizes from the same paper share are based on more similar studies than those across papers and that nested therein effects can stem from the same infants.]
+We use a multilevel random effects model which estimates the mean and variance of effect sizes sampled from an assumed distribution of effect sizes.
+In the random effect structure we take into account the shared variance of effect sizes drawn from the same paper, and nested therein that the same infants might contribute to multiple effect sizes.
 
@@
 PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images.
-Across papers the baseline comparison varied; we used the baseline reported by the authors of each paper.
+Across papers the baseline comparison varied; since other options were not available to us, we used the baseline reported by the authors of each paper.
 Most papers (*n* = `r with(comparison_info, count[within_measure == "pre_post_naming_effect"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post_naming_effect"])` papers) subtracted the PTL score for a pre-naming baseline phase from the PTL score for a post-naming phase and report a difference score.
@@
 In the psychological sciences, there is a documented reluctance to publish null results.
-As a result, significant results tend to be over-reported and thus might be over-represented in our meta-analyses (see Ferguson & Heene, 2012).
+As a result, significant results tend to be over-reported and thus might be over-represented in our meta-analyses ([see @Ferguson2012]).
 To examine whether this is also the case in the mispronunciation sensitivity literature, which would bias the data analyzed in this meta-analysis, we conducted two tests.
@@
 
-Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app (v4.0, p-curve.com; @pcurve).
+Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app ([v4.0, http://p-curve.com; @pcurve]).
 This p-curve tests for evidential value by examining whether the p-values follow the expected distribution of a right skew in case the alternative hypothesis is true, versus a flat distribution that speaks for no effect being present in the population and all observed significant effects being spurious.
+
 Responses to correctly pronounced and mispronounced labels were predicted to show different patterns of looking behavior.
 In other words, there is an expectation that infants should look to the target when hearing a correct pronunciation, but studies vary in their report of significant looks to the target when hearing a mispronounced label (i.e.
-there might be no effect present in the population, see e.g., ); as a result, we conducted these two analyses to assess publication bias separately for both conditions.
+there might be no effect present in the population); as a result, we conducted these two analyses to assess publication bias separately for both conditions.
 
@@
 
-The models reported here are hierarchical random-effects models (infant groups nested within papers) of variance-weighted effect sizes, which we computed with the R [@R] package metafor [@metafor].
+The models reported here are multilevel random-effects models of variance-weighted effect sizes, which we computed with the R [@R] package metafor [@metafor].
 To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we introduced age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44) as a moderator to our main model.
@@
 
-Figure 2 shows the funnel plots for both correct pronunciations and mispronunciations (code adapted from Sakaluk, 2016).
+Figure 2 shows the funnel plots for both correct pronunciations and mispronunciations ([code adapted from @Sakaluk2016]).
 Funnel plot asymmetry was significant for both correct pronunciations (Kendall's $\tau$ = `r r2(rmac$tau)`, *p* `r psig(rmac$pval)`) and mispronunciations (Kendall's $\tau$ = `r r2(rmam$tau)`, *p* `r psig(rmam$pval)`).
@@
 
-The stronger publication bias for correct pronunciation might reflect the status of this condiction as a control.
+The stronger publication bias for correct pronunciation might reflect the status of this condition as a control.
 If infants were not looking to the target picture after hearing the correct label, the overall experiment design is called into questions.
-However, due to the small effect and sample sizes (which we will discuss in the following sections in more detail) one would expect the regular occurrence of null results even though as a population infants would reliably show the expected object identification effect.
-
-We should also point out that funnel plot asymmetry can be caused by multiple factors beside publication bias, such as heterogeneity in the data.
+However, even in a well-powered study one would expect the regular occurrence of null results even though as a population infants would reliably show the expected object identification effect.
+
+We should also point out that funnel plot asymmetry can be caused by multiple factors besides publication bias, such as heterogeneity in the data.
 There are various possible sources of heterogeneity, which our subsequent moderator analyses will begin to address.
@@
 The variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was significantly different from zero `r CI_p(sum_eff)`.
-This is a large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research).
+This is a small to medium effect size ([according to the criteria set by @Mills-Smith2015]).
 That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants tended to fixate on the corresponding object.
@@
 In this case, the variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was also significantly different from zero `r CI_p(sum_eff)`.
-This is considered a small effect size (Cohen, 1988), but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object.
+This is considered a small effect size [@Mills-Smith2015], but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object.
 In other words, infants are able to resolve mispronunciations, a key skill in language processing We again note the publication bias (which was smaller in this condition), and the possibility that the effect size Hedges' *g* may be overestimated.
-But, as the p-curve indicated evidential value, we are confident in the overall patterns, namely that infants fixate the target even after hearing a mispronounced label.
-
-### Mispronunciation Sensitivity Meta-analytic Effect
+But, as the p-curve indicated evidential value, we are confident in the overall pattern, namely that infants fixate the target even after hearing a mispronounced label.
+
+### Mispronunciation Sensitivity Meta-Analytic Effect
 
@@
 To this end, we combined the two datasets.
-The moderator test was significant, `r mod_test(rma_MPeffect)`.
+When condition was included (correct, mispronounced), the moderator test was significant, `r mod_test(rma_MPeffect)`.
 The estimate for mispronunciation sensitivity was `r g_SE(sum_eff)`, and infants' looking times across conditions were significantly different `r CI_p(sum_eff)`.
@@
 In other words, we observe a significant difference between the two conditions and can now quantify the modulation of fixation behavior in terms of standardized effect sizes and their variance.
-This first result has both theoretical and practical implications, as we can now reason about the amount of perturbance caused by mispronunciations and can plan future studies to further investigate this effect with suitable power.
+This first result has both theoretical and practical implications, as we can now reason about the amount of perturbation caused by mispronunciations and can plan future studies to further investigate this effect with suitable power.
 
@@
 Age did not significantly modulate object identification in response to correctly pronounced (`r mod_test(rma_correct_age)`) or mispronounced words (`r mod_test(rma_MP_age)`).
-The lack of a significant modulation together with the small estimates (correct: $\beta$ `r full_estimate(Csum_eff)`; mispronunciation: $\beta$ `r full_estimate(Msum_eff)`) indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label.
+The lack of a significant modulation together with the small estimates for age (correct: $\beta$ `r full_estimate(Csum_eff)`; mispronunciation: $\beta$ `r full_estimate(Msum_eff)`) indicates that there might be no relationship between age and target looks in response to a correctly pronounced or mispronounced label.
+We note that the estimates in both cases are positive, however, which is in line with the general assumption that infants’ language processing overall improves as they mature [@Fernald1998].
 We plot both object recognition and mispronunciation sensitivity as a function of age in Figure 3.
@@
 The interaction between age and mispronunciation sensitivity, however, was not significant ($\beta$ `r full_estimate(sum_eff)`); the moderator test was mainly driven by the difference between conditions.
-The small estimate, as well as inspection of Figure 2 suggests that as infants age, their mispronunciation sensitivity neither increases or decreases.
+The small estimate, as well as inspection of Figure 2, suggests that as infants age, their mispronunciation sensitivity neither increases or decreases.
 
@@
 Children comprehend more words than they can produce, leading to different estimates for comprehension and production.
-Production data is easier to estimate for parents in the typical questionnaire-based assessment and may therefore be more reliable (Tomasello & Mervis, 1994).
+Production data is easier to estimate for parents in the typical questionnaire-based assessment and may therefore be more reliable [@Tomasello1994].
 As a result, we planned to analyze these two types of vocabulary measurement separately.
 However, because only `r with(vi1, papers[has_vocab == "production"])` papers reported correlations with productive vocabulary scores, only limited conclusions can be drawn.
-In our vocabulary analysis, we therefore focus exclusively on the relationship between comprehension and mispronunciation sensitivity.
-
-[Katie: Tomasello reference - https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1540-5834.1994.tb00186.x]
+We also note that because individual effect sizes in our analysis were related to object recognition and not mispronunciation sensitivity, we were only able to calculate the relationship between vocabulary scores and the former.
+In our vocabulary analysis, we therefore focus exclusively on the relationship between comprehension and object recognition for correct pronunciations and mispronunciations.
+
+[Katie: Written as if moderators can not be added to metacor()]
 
@@
 Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for `r pos_rel` of `r tot_rel` experimental conditions, with correlation values ranging from `r min_cor` to `r max_cor`.
-The mean effect size Pearson's *r* of `r r2(CC$TE.fixed)` was small but did differ significantly from zero (CI [`r r2(CC$lower.fixed)`; `r r2(CC$upper.fixed)`] *p* `r psig(CC$pval.fixed)`).
+The weighted mean effect size Pearson's *r* of `r r2(CC$TE.fixed)` was small but did differ significantly from zero (CI [`r r2(CC$lower.fixed)`; `r r2(CC$upper.fixed)`] *p* `r psig(CC$pval.fixed)`).
 As a result, we can draw a tentative conclusion that there is a positive relationship between comprehension scores and object recognition in response to correct pronunciations.
@@
 We next considered the relationship between vocabulary and object recognition for mispronunciations.
-Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for `r pos_rel` of `r tot_rel` experimental conditions, with correlation values ranging from `r min_cor` to `r max_cor`.
-The mean effect size Pearson's *r* of `r r2(MC$TE.fixed)` was small and did not differ significantly from zero (CI [`r r2(MC$lower.fixed)`; `r r2(MC$upper.fixed)`] *p* `r psig(MC$pval.fixed)`).
-The small correlation suggests a lack of relationship between vocabulary and object recognition for mispronunciations.
+Higher comprehension scores were associated with greater object recognition in response to mispronunciations for `r pos_rel` of `r tot_rel` experimental conditions, with correlation values ranging from `r min_cor` to `r max_cor`.
+The weighted mean effect size Pearson's *r* of `r r2(MC$TE.fixed)` was small and did not differ significantly from zero (CI [`r r2(MC$lower.fixed)`; `r r2(MC$upper.fixed)`] *p* `r psig(MC$pval.fixed)`).
+The small correlation suggests either a very small positive or no relationship between vocabulary and object recognition for mispronunciations.
 We again emphasize that we cannot draw a firm conclusion due to the small number of studies we were able to include here.
@@
 The lack of evidence for a relationship between mispronunciation sensitivity and vocabulary size in some early studies may have contributed to increasingly fewer researchers including vocabulary measurements in their mispronunciation sensitivity experimental design.
-This may explain our underpowered analysis of the relationship between mispronunciation sensitivity and vocabulary size.
+This may explain our underpowered analysis of the relationship between object recognition for correct pronunciations and mispronunciations and vocabulary size.
 
@@
 
-The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age.
-The results seem clear: Although infants consider a mispronunciation to be a better match to the target image than to a distractor image, there was a consistent effect of mispronunciation sensitivity.
+The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age and increased vocabulary size.
+The results seem clear: Although infants consider a mispronunciation to be a better match to the target image than to a distractor image, there was a constant and stable effect of mispronunciation sensitivity.
 This did not change with development nor with vocabulary size.
-Of the three predictions about the development of infants' sensitivity to mispronunciations discussed in the Introduction, the present results lend some support for the argument that mispronunciation sensitivity stays consistent as infants develop.
-This runs counter to existing theories of phono-lexical development, which predict either an increase (PRIMR ref) or decrease (Assim Model ref) in mispronunciation sensitivity.
-Furthermore, although we found a relationship between vocabulary comprehension and target looking for correct pronunciations, we found no relationship between vocabulary and target looking for mispronunciations.
-This also runs counter to the predictions for the PRIMR (PRIMR ref) and Assimilation (Assim ref) models, but may be due to our analyses being underpowered.
+Of the three predictions about the development of infants' sensitivity to mispronunciations discussed in the Introduction, the present results lend some support for the proposal that mispronunciation sensitivity stays consistent as infants develop.
+This runs counter to existing theories of phono-lexical development, which predict either an increase [@Curtin2007; @Curtin2011; @Werker2005] or decrease [@Best1994; @Best1995] in mispronunciation sensitivity.
+Furthermore, although we found a relationship between vocabulary size (comprehension) and target looking for correct pronunciations, we found no relationship between vocabulary and target looking for mispronunciations.
+This also runs counter to the predictions for the PRIMR [@Curtin2007; @Curtin2011; @Werker2005] and Assimilation [@Best1994; @Best1995] models, but may be due to our analyses being underpowered.
 In sum, it seems that current theories of infants' phono-lexical development cannot fully capture our results, but that more investigation is needed to draw a firm conclusion.
@@
 A strong candidate that emerged during the construction of the present dataset and careful reading of the original papers was the analysis approach.
-We observed, as mentioned in the Methods section, large variance in the dependent variable reported, and additionally noted variance in the size of the chosen post-naming analysis window.
+We observed, as mentioned in the Methods section, large variation in the dependent variable reported, and additionally noted that the size of the chosen post-naming analysis window varied substantially across papers.
 Researchers might adapt their analysis strategy to infants' age or they might be influenced by having observed the data.
-For example, consider the possibility that there is a true change in mispronunciation sensitivity over development.
-In this scenario, younger infants should show no sensitivity to mispronunciations while older infants would show large sensitivity to mispronunciations.
-This lack of mispronunciation sensitivity in younger infants may be more difficult to publish (Ferguson & Heene, 2012).
+For example, consider the possibility that there is a true increase in mispronunciation sensitivity over development.
+In this scenario, younger infants should show no or only little sensitivity to mispronunciations while older infants would show a large sensitivity to mispronunciations.
+This lack of or small mispronunciation sensitivity in younger infants is likely to lead to non-significant results, which would be more difficult to publish [@Ferguson2012].
 In order to have publishable results, adjustments to the analysis approach could be made until a significant, but spurious, effect of mispronunciation sensitivity is found.
-This would lead to an increase in significant results and alter to observed developmental trajectory of mispronunciation while also (partially) explaining the publication bias we observe (Simmons, Nelson, & Simonsohn, 2011).
+This would lead to an increase in significant results and alter to observed developmental trajectory of mispronunciation sensitivity.
+Such a scenario is in line with the publication bias we observe [@Simmons2011].
 We examine whether variation in the approach to data analysis may be have an influence on findings of mispronunciation sensitivity.
-
-[Katie: I've changed the above paragraph, particularly regarding why we should find an increase in significant results, as per Caroline's suggestion.]
 
@@
 
-We identified two sets of variables which had the potential to vary across papers to assess the influence of data analysis choices on resulting effect size: timing (post-naming analysis window; offset time) and which dependent variable(s) were reported.
-In the following, we discuss the possible theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these analysis choices may have have on measurements of mispronunciation sensitivity development.
+We identified two sets of variables which varied across papers to assess the influence of data analysis choices on resulting effect size: timing (post-naming analysis window; offset time) and which dependent variable(s) were reported.
+In the following, we discuss the possible theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these analysis choices may have on measurements of mispronunciation sensitivity development.
 We focus specifically on the size of the mispronunciation sensitivity effect, considering the whole dataset and including condition (correct pronunciation, mispronunciation) as moderator.
@@
 Across papers, the length of the post-naming time window varied from `r with(post_length_info, min(post_nam_actual))*1000` to `r with(post_length_info, max(post_nam_actual))*1000` ms, with a median value of `r with(dat, median(post_nam_actual))*1000` ms.
-We note that the most popular post-naming time window length was `r with(dat, getmode(post_nam_actual))*1000` ms, used in *n* = `r with(post_length_info, n_exp_conditions[post_nam_actual == getmode(post_length_info$n_exp_conditions)])` experimental conditions.
+The most popular post-naming time window length was `r with(dat, getmode(post_nam_actual))*1000` ms, used in `r with(post_length_info, n_exp_conditions[post_nam_actual == getmode(post_length_info$n_exp_conditions)])` experimental conditions.
 There was no apparent relation between infant age and post-naming time window length (*r* = `r trial.l$estimate`, 95% CI[`r trial.l$conf.int[1]`, `r trial.l$conf.int[2]`], *p* `r psig(trial.l$p.value)`).
@@
 Across papers, the length of the post-naming analysis window varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a median value of `r with(dat, median(post_nam_dur))*1000` ms.
-We note that the most popular post-naming analysis window length was `r with(dat, getmode(post_nam_dur))*1000` ms, used in *n* = `r with(post_name_info, n_exp_conditions[post_nam_dur == with(dat, getmode(post_nam_dur))])` experimental conditions.
+The most popular post-naming analysis window length was `r with(dat, getmode(post_nam_dur))*1000` ms, used in `r with(post_name_info, n_exp_conditions[post_nam_dur == with(dat, getmode(post_nam_dur))])` experimental conditions.
 There was an inverse relationship between infant age and post-naming analysis window length, such that younger infants' looking times were analyzed using a longer post-naming analysis window, here the relationship was significant (*r* = `r post.l$estimate`, 95% CI[`r post.l$conf.int[1]`, `r post.l$conf.int[2]`], *p* `r psig(post.l$p.value)`).
-The choice to use a shorter post-naming analysis window with age is likely related to evidence that speed of processing is slower in younger infants (Fernald et al., 1998).
+The choice to use a shorter post-naming analysis window with age is likely related to evidence that speed of processing is slower in younger infants [@Fernald1998].
 To summarize, we observe variation in time-related analysis decisions related to infants' age.
 
-[Christina: Below there is a .... Just so we don't forget it.]
-[Katie: I put it in there on purpose, I'm quoting directly from the paper, but the original sentence doesn't make full sense in this context, so I cut out the part that doesn't fit.
-This is the original sentence:
-"The lower bound of 367 ms is an `educated guess' based on studies such as those cited above, and our data (here and in other studies) showing that target and distractor fixations tend to diverge at around 400 ms."
-]
-
 Another potential source of variation in studies that analyze eye-movements is the amount of time it takes for an eye movement to be initiated in response to a visual stimulus, which we refer to as offset time.
-Previous studies examining simple stimulus response latencies first determined that infants require at least 233 ms to initiate an eye-movement in response to a stimulus (Canfield & Haith, 1991).
-In the first infant mispronunciation sensitivity study, Swingley and Aslin (2000) used an offset time of 367 ms, which was "an 'educated guess' based on studies .
+Previous studies examining simple stimulus response latencies first determined that infants require at least 233 ms to initiate an eye-movement in response to a stimulus [@Canfield1991].
+In the first infant mispronunciation sensitivity study, @Swingley2000 used an offset time of 367 ms, which was "an 'educated guess' based on studies .
 .
 .
-showing that target and distractor fixations tend to diverge at around 400 ms." (Swingley & Aslin, 2000, p.
-155).
+showing that target and distractor fixations tend to diverge at around 400 ms." ([@Swingley2000, p.
+155]).
 Upon inspecting the offset time values used in the papers in our meta-analysis, the majority used a similar offset time value (between 360 and 370 ms) for analysis (*n* = `r with(offset_bin_info, n_exp_conditions[offset_bin == "367"])`), but offset values ranged from `r with(offset_bin_info, min(offset_bin))` to `r with(offset_bin_info, max(offset_bin))` ms, and were not reported for `r with(offset_info, n_exp_conditions[is.na(offset)])` experimental conditions.
-We note that Swingley (2009) also included offset values of 1133 ms to analyze responses to coda mispronunciations.
-There was an inverse relationship between infant age and size of offset, such that younger infants were given longer offsets, although this correlation was not significant (*r* = `r offset.l$estimate`, *p* `r psig(offset.l$p.value)`).
+We note that @Swingley2009 also included offset values of 1133 ms to analyze responses to coda mispronunciations.
+There was an inverse relationship between infant age and size of offset, such that younger infants were given longer offsets, although this correlation was not significant (*r* = `r offset.l$estimate`, 95% CI[`r offset.l$conf.int[1]`, `r offset.l$conf.int[2]`], *p* `r psig(offset.l$p.value)`).
 This lack of a relationship is possibly driven by the field's consensus that an offset of about 367 ms is appropriate for analyzing word recognition with PTL measures, including studies that evaluate mispronunciation sensitivity.
 
-Although there are a priori reasons to choose the post-naming analysis window (infant age) or offset time (previous studies), these choices may occur after data collection and might therefore lead to a higher rate of false-positives (Gelman & Loken, 2013).
-Considering that these choices were systematically different across infant ages, at least for the post-naming analysis window, we next explored whether the post-naming analysis window length or the offset time influenced sensitivity to mispronunciations.
+Although there are a priori reasons to choose the post-naming analysis window (infant age) or offset time (previous studies), these choices may occur after data collection and might therefore lead to a higher rate of false-positives [@Gelman2013].
+Considering that these choices were systematically different across infant ages, at least for the post-naming analysis window, we next explored whether the post-naming analysis window length or the offset time influenced our estimate of infants’ sensitivity to mispronunciations.
 
@@
 This relationship is plotted in Figure 3a.
-The results suggest that the size of the post-naming analysis window significantly impacted mispronunciation sensitivity.
+The results suggest that the size of the post-naming analysis window significantly impacted our estimate of mispronunciation sensitivity.
 Specifically, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) was significantly greater when the post-naming analysis window was shorter.
@@
 The moderator test was significant (`r mod_test(rma_post_dur_AGE_MS)`).
-The estimate for the  three-way-interaction between condition, size of the post-naming analysis window, and age was small, but significant ($\beta$ = `r full_estimate(rma_post_dur_AGE_MS_eff)`).
+The estimate for the  three-way-interaction between condition, size of the post-naming analysis window, and age was small, but significant ($\beta$ `r full_estimate(rma_post_dur_AGE_MS_eff)`).
 As can be seen in Figure 3b, a smaller post-naming analysis window leads to a greater increase in measured mispronunciation sensitivity with development.
-For example, when experimental conditions were analyzed with a post-naming analysis window of 2000 ms or less, mispronunciation sensitivity was found to increase with infant age.
+For example, when experimental conditions were analyzed with a post-naming analysis window of 2000 ms or less, mispronunciation sensitivity seems to increase with infant age.
 If the post-naming analysis window is greater than 2000 ms, however, there is no or a negative relation of mispronunciation sensitivity and age.
@@
 We next assessed whether the time between target naming and the start of the analysis, namely offset time, had an impact on the size of the reported mispronunciation sensitivity.
-When we included both condition and offset time as moderators, the moderator test was significant (`r mod_test(rma_post_dur_MS)`), but the estimate for the interaction between offset time and condition was almost zero ($\beta$`r full_estimate(rma_offset_MS_eff)`).
+When we included both condition and offset time as moderators, the moderator test was significant (`r mod_test(rma_post_dur_MS)`), but the estimate for the interaction between offset time and condition was zero ($\beta$`r full_estimate(rma_offset_MS_eff)`).
 Although we found no relationship between offset time and infant age, we also examined whether the size of offset time modulated the measure of mispronunciation sensitivity over infant age.
-When both offset time and condition were included as moderators, the moderator test was significant (`r mod_test(rma_offset_AGE_MS)`), but the three-way-interaction between condition, offset time, and age was very small and not significant ($\beta$ = `r full_estimate(rma_offset_AGE_MS_eff)`.
+When both offset time and condition were included as moderators, the moderator test was significant (`r mod_test(rma_offset_AGE_MS)`), but the three-way-interaction between condition, offset time, and age was again zero ($\beta$ `r full_estimate(rma_offset_AGE_MS_eff)`.
 Taken together, these results suggest that offset time does not modulate measured mispronunciation sensitivity.
 There is no relationship between offset time and age, and we find no influence of offset time on the estimated size of mispronunciation sensitivity over age.
+We again point out that there is a substantial field consensus, which might mask any relationship.
 
@@
 Mispronunciation studies evaluate infants' proportion of target looks (PTL) in response to correct and mispronounced words.
-Experiments typically include a phase where no naming event has occured, whether correctly pronounced or mispronounced, which we refer to as the pre-naming phase The purpose of the pre-naming phase is to ensure that infants do not have systematic preferences for the target or distractor (greater interest in a cat compared to a cup) which may drive PTL scores in the post-naming phase.
+Experiments typically include a phase where no naming event has occurred, whether correctly pronounced or mispronounced, which we refer to as the pre-naming phase The purpose of the pre-naming phase is to ensure that infants do not have systematic preferences for the target or distractor (greater interest in a cat compared to a cup) which may drive PTL scores in the post-naming phase.
 As described in the Data Analysis sub-section of the Methods, however, there was considerable variation across papers in whether this pre-naming phase was used as a baseline measurement, or whether a different baseline measurement was used.
@@
 Post can be considered similar to one another, in that they are calculated on the same type of data and consider pre-naming preferences.
-[Christina: adding sth here].
-It should be noted, however, that the Difference Score can better counter act participant- and item-level differences, whereas Pre vs.
+It should be noted, however, that the Difference Score can better counteract participant- and item-level differences, whereas Pre vs.
 Post is a group-level measure.
@@
 
+In this meta-analysis, we set out to quantify and assess the developmental trajectory of infants’ sensitivity to mispronunciations.
 Overall, the results of the meta-analysis showed that infants reliably fixate the target object when given both correctly pronounced and mispronounced labels.
-In other words, not only did infants recognize object labels when they were correctly pronounced, they also were likely to accept mispronunciations as acceptable labels for targets.
-Mispronounced labels were considered a better match for target images than a distractor image, despite the differences in the phonological form of correctly pronounced and mispronounced words.
-Nonetheless, there was a considerable difference in target fixations in response to correctly pronounced and mispronounced labels, suggesting overall mispronunciation sensitivity in the current experimental literature.
-In short, infants show knowledge of what constitutes unacceptable variation in word forms, displaying knowledge of the role of phonemic changes throughout the ages assessed here.
-At the same time, infants, like adults, can recover from mispronunciations.
+Infants not only recognize object labels when they were correctly pronounced, but are also likely to accept mispronunciations as acceptable labels for targets, in the presence of a distractor image.
+Nonetheless, there was a considerable difference in target fixations in response to correctly pronounced and mispronounced labels, suggesting that infants show an overall mispronunciation sensitivity based on the current experimental literature.
+In other words, infants show sensitivity to what constitutes unacceptable, possibly meaning-altering variation in word forms, thereby displaying knowledge of the role of phonemic changes throughout the ages assessed here (6 to 30 months).
+At the same time, infants, like adults, can recover from mispronunciations, a key skill in language processing.
 
@@
 We observed no influence of age when it was considered as a moderator of mispronunciation sensitivity.
-Of the two mainstream theories identified in our literature review, neither the Perceptual Attunement account (Best 1994, 1995) nor PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005) account for a lack of developmental change.
-The results of our meta-analysis are supported by a handful of studies directly comparing infants over a range of ages (Swingley & Aslin, 2000; Bailey & Plunkett, 2002; Zesiger et al., 2012), which also found no developmental change in mispronunciation sensitivity.
-
-Both the Perceptual Attunement (Best 1994, 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005) accounts link a change of mispronunciation sensitivity specifically with vocabulary growth, in comparison to development in general.
-Vocabulary growth leads to an increase (PRIMIR; Curtin & Werker, 2007; Werker & Curtin, 2005) or decrease (Perceptual Attunement; Best 1994, 1995) in mispronunciation sensitivity and vocabulary is expected to grow considerably in the age range considered in the current meta-analysis (see wordbank.stanford.edu; Frank et al., 2017).
-The lack of developmental effects found in our meta-analysis may therefore be due to using age, instead of vocabulary growth, as a facilitator for change in mispronunciation sensitivity.
-Yet, an analysis of correlations between vocabulary size and object recognition effect sizes does not support this argument.
+Of the two mainstream theories identified in our literature review, neither the Perceptual Attunement account [@Best1994; @Best1995] nor PRIMIR [@Curtin2007; @Werker2005; @Curtin2011] account for a lack of developmental change.
+The results of our meta-analysis are supported by a handful of studies directly comparing infants over a range of ages [@Swingley2000; @Bailey2002; @Zesiger2012], which also found no developmental change in mispronunciation sensitivity.
+
+Both the Perceptual Attunement [@Best1994; @Best1995] and PRIMIR [@Curtin2007; @Werker2005; @Curtin2011] accounts link a change of mispronunciation sensitivity specifically with vocabulary growth, in comparison to development in general.
+Vocabulary growth is predicted to lead either to an increase ([PRIMIR; @Curtin2007; @Werker2005; @Curtin2011]) or a decrease ([Perceptual Attunement; @Best1994; @Best1995]) in mispronunciation sensitivity; vocabulary has been shown to grow considerably in the age range considered in the current meta-analysis ([see http://wordbank.stanford.edu; @Frank2017]).
+However, there are also substantial individual differences in the trajectory of vocabulary growth.
+The lack of developmental effects found in our meta-analysis may therefore be due to using age, instead of vocabulary size, as a facilitator for change in mispronunciation sensitivity.
+Yet, an analysis of the subset of studies reporting correlations between vocabulary size and object recognition effect sizes does not support this argument.
 Although an increasing vocabulary size lead to increased object recognition for correctly pronounced words, this was not the case for mispronunciations.
-Some previous experimental evidence also supports a lack of a relationship between vocabulary size and mispronunciation sensitivity (e.g.
-Mani & Plunkett, 2007; Swingley & Aslin, 2000; Tao et al., 2012; but see Mani & Plunkett, 2010).
-This would suggest that object recognition for mispronunciations is not modulated by vocabulary size, contrary to the predictions of the Perceptual Attunement (Best 1994, 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005) accounts and further supporting the overall lack of an influence of age on mispronunciation sensitivity.
+Without evidence of a relationship between vocabulary size and mispronunciation object recognition and in combination with the low-powered analysis, it is difficult to draw a conclusion regarding the role of an increasing vocabulary size in mispronunciation sensitivity.
+In any case, this lack of evidence is contrary to the predictions of the Perceptual Attunement [@Best1994; @Best1995] and PRIMIR [@Curtin2007; @Werker2005; @Curtin2011] accounts and further supports the overall lack of evidence for a developmental change.
+
+[Katie: Above has been edited to acknowledge that we can't measure mispronunciation sensitivity in the vocabulary correlations. Christina, can you read through it?]
 
@@
 The lack of age or vocabulary effects in our meta-analysis suggest that this understanding is present from an age when the earliest words are learned and is maintained throughout early lexical development.
-This implies mastery of the principles of phonological constancy and phonological distinctiveness at an age earlier than previously thought, which we recommend should be taken into account by future theoretical accounts.
+This implies mastery of the principles of phonological constancy and phonological distinctiveness at an age earlier than previously thought, which we recommend should be further explored experimentally and taken into consideration by future theoretical accounts.
 
 Although the lack of a relationship between mispronunciation sensitivity and vocabulary size may reflect a true effect, we note that this may also be the result of an underpowered analysis.
-Despite the theoretical implications, fewer than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total).
-We suggest that this may be the result of publication bias.
-There are more mispronunciation sensitivity studies published every year, but this has not translated to an increasing number of mispronunciation sensitivity studies also measuring vocabulary scores.
+Despite the theoretical implications, fewer than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total; see also Figure 4).
+There are more mispronunciation sensitivity studies published every year, perhaps due to the increased use of eye-tracker which reduce the need for offline coding, but this has not translated to an increasing number of mispronunciation sensitivity studies also measuring vocabulary scores.
+We suggest that this may be the result of publication bias favoring significant effects or an overall hesitation to invest in data collection that is not expected to yield significant outcomes.
 
@@
 During the coding of these characteristics, we noted a potential for variation in a handful of variables that relate to data analysis, specifically relating to timing (post-naming analysis window; offset time) and to the calculation of the dependent variable reported.
-We focused on these variables in particular because their choice can potentially be made after researchers have examined the data, leading to an inflated increase of significant results which may also explain the publication bias observed in the funnel plot asymmetry (Simmons, Nelson, & Simonsohn, 2011).
+We focused on these variables in particular because their choice can potentially be made after researchers have examined the data, leading to an inflated number of significant results which may also explain the publication bias observed in the funnel plot asymmetry analyses [@Simmons2011].
 To explore whether this variation contributed to the lack of developmental change observed in the overall meta-analysis, we included these variables as moderators in a set of exploratory analyses.
-We noted an interesting pattern of results, specifically that different conclusions about mispronunciation sensitivity, but more notably mispronunciation sensitivity development, could be drawn depending on the length of the post-naming analysis window as well as the type of dependent variable calculated in the experiment.
-
-[Christina] It's a good start, let's see where we go from here. I jotted down some possible conclusions
-
-Infants are expected to recognize words more quickly with age (Fernald, Swingley & Pinto, 2001; Swingley, Pinto & Fernald, 1999; Swingley & Fernald, 2002).
+We noted an interesting pattern of results, specifically that different conclusions about mispronunciation sensitivity, but more notably mispronunciation sensitivity development, could be drawn depending on the length of the post-naming analysis window as well as the type of dependent variable calculated in the experiment (see Figures 5 and 6).
+
+Infants are expected to recognize words more quickly with age [@Fernald1998].
 This evidence has often guided decisions for the post-naming time window in mispronunciation sensitivity studies, including where to begin the time window (offset time) and how long this analysis window should be (post-naming analysis window).
@@
 Yet, we found no evidence for a relationship between offset time and infant age nor that offset time modulated mispronunciation sensitivity.
-Indeed, a majority of studies used an offset time between 360 and 370 ms, which follows the best guess of Swingley and Aslin (2000) for the amount of time needed for infants to initiate eye movements in response to a spoken target word.
-
-In contrast, the length of the post-naming analysis window was related to infant age and was also found to modulate mispronunciation sensitivity.
-Younger infants may take longer to reliably identify the target image, and as a result the length of the post-naming time window analyzed may be longer in younger infants.
-This was born out in the meta-analysis: studies that tested younger infants used a longer post-naming analysis window.
-Longer post-naming analysis windows, however, resulted in a smaller effect size for mispronunciation sensitivity.
-Critically, the developmental trajectory of mispronunciation sensitivity changed depending on the length of the post-naming analysis window.
-Longer analysis windows resulted in decreasing or no change in mispronunciation sensitivity, while shorter analysis windows resulting in increasing mispronunciation sensitivity.
-Given a set of mispronunciation sensitivity data, a conclusion regarding the development of mispronunciation sensitivity would be different depending on the length of the post-naming analysis window.
-
-Unlike the timing variables, the origin of a potential relationship between the type of dependent variable calculated and mispronunciation sensitivity is much less clear.
-The majority of studies created a Difference Score, subtracting pre-naming phase PTL from that of post-naming phase PTL, while the remaining studies compared pre-naming PTL with post-naming PTL (Pre vs.
-Post) or analyzed post-naming PTL alone (Post).
-Both the Difference Score and the Pre vs.
-Post dependent variables consider pre-naming phase baseline preferences for the target compared to distractor image, but were found to differentially modulate mispronunciation sensitivity.
-There was no difference in mispronunciation sensitivity between the Post and Difference Score dependent variables, but in comparison to Post, studies that reported the Pre vs.
-Post dependent variable had lower effect sizes for mispronunciation sensitivity.
-Furthermore, studies reporting the Pre vs.
-Post dependent variable showed decreasing mispronunciation sensitivity with age, while studies reporting a Difference Score or Post dependent variable showed an increase.
-Similar to the length of the post-naming time window analyzed, given a set of mispronunciation sensitivity data, a conclusion regarding the development of mispronunciation sensitivity would be different depending on the choice of dependent variable.
+Indeed, a majority of studies used an offset time between 360 and 370 ms, which follows the "best guess" of @Swingley2000 for the amount of time needed for infants to initiate eye movements in response to a spoken target word.
+
+In contrast, both the length of the post-naming analysis window and the type of dependent variable calculated modulated mispronunciation sensitivity.
+Most critically, however, variation in these variables resulted in changes to the developmental trajectory of mispronunciation sensitivity.
+Given a set of mispronunciation sensitivity data, a conclusion regarding the development of mispronunciation sensitivity would be different depending on the length of the post-naming analysis window or the choice of dependent variable.
+
+## Recommendations to Establish Analysis Standards
 
@@
 Depending on which analysis time window (see Figure 5) or dependent variable (see Figure 6) we focus on, we find support for any of the three possible trajectories of mispronunciation sensitivity.
-On the one hand, this limits the conclusions we can draw.
+On the one hand, this limits the conclusions we can draw regarding our key research question.
 Without access to the full datasets or analysis code of the studies included in this meta-analysis, it is difficult to pinpoint the exact role played by these data analysis choices.
@@
 We take this opportunity to suggest several solutions.
-Preregistration can serve as proof of a priori decisions regarding data analysis or describing how data analysis decisions will be made once data is collected.
-The peer reviewed form of Registered Reports has already been adopted by a large number of developmental journals, and general journals that publish developmental works, showing the field's increasing acceptance of such practices.
+Preregistration can serve as proof of a priori decisions regarding data analysis, which can also contain a data-dependent description of how data analysis decisions will be made once data is collected.
+The peer reviewed form of preregistration, termed Registered Reports, has already been adopted by a large number of developmental journals, and general journals that publish developmental works, showing the field’s increasing acceptance of such practices for hypothesis-testing studies.
 Sharing data (Open Data) can allow others to re-analyze existing datasets to both examine the impact of analysis decisions and cumulatively analyze different datasets in the same way.
@@
 This allows for a more detailed assessment of infants' fixations over time and reduces the need to reduce the post-naming analysis window.
-Both Growth Curve Analysis (Mirman et al., 2008; Law & Edwards, 2015) and Permutation Clusters Analysis (Maris & Oostenveld, 2007; Von Holzen & Mani, 2012; Delle Luche et al., 2015) offer potential solutions to analyze the full time course.
+Both Growth Curve Analysis [@Mirman2008; @Law2015] and Permutation Clusters Analysis [@VonHolzen2012; @Maris2007; @DelleLuche2015] offer potential solutions to analyze the full time course.
 Furthermore, it may be useful to establish standard analysis pipelines for mispronunciation studies.
@@
 
-[Katie: I've rewritten the above paragraph as per Caroline's suggestion. I'm not very happy with the last sentence, but I don't want to leave the thought hanging.]
-
-[Katie: Below is a good paragraph, but I'm not sure where it fits. Its rather not specific for our current meta-analysis, but a general comment about the field.]
-
-When it comes to designing studies, best practices and current standards might not always overlap.
-Indeed, across a set of previous meta-analyses it was shown that particularly infant research does not adjust sample sizes according to the effect in question (Bergmann et al., 2018).
-A meta-analysis is a first step in improving experiment planning by measuring the underlying effect and its variance, which is directly related to the sample needed to achieve satisfactory power in the null hypothesis significance testing framework.
+Another aspect of study design, namely sample size planning, shows that best practices and current standards might not always overlap.
+Indeed, across a set of previous meta-analyses it was shown that particularly infant research does not adjust sample sizes according to the effect in question [@Bergmann2018].
+A meta-analysis is a first step in improving experiment planning by providing an estimate of the population effect and its variance, which is directly related to the sample needed to achieve satisfactory power in the null hypothesis significance testing framework.
 Failing to take effect sizes into account can both lead to underpowered research and to testing too many participants, both consequences are undesirable for a number of reasons that have been discussed in depth elsewhere.
 We will just briefly mention two that we consider most salient for theory building: Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature (citationcitation).
+At the same time, underpowered studies with significant outcomes are likely to overestimate the effect, leading to wrong estimations of the population effect when paired with publication bias (citation).
 Overpowered studies mean that participants were tested unnecessarily, which has ethical implications particularly when working with infants and other difficult to recruit and test populations.
 
-[Katie: I am not sure where to talk about this, or actually how to talk about this.]
-For example, the Difference Score dependent variable substracts the pre-naming phase PTL from the post-naming phase PTL.
-Some studies compute this variable on the level of condition (e.g.
-White & Morgan, 2008), but this reduces SOMETHING, WHICH IS A BAD SOMETHING.
+[From Christina's comment: Christina needs to add citations here]
+
+```{r Power_calculation, echo = FALSE, results = "hide"}
+
+# effect size for mispronunciation sensitivity
+mp_effect <- r2(coef(summary(rma_MPeffect))[2,1])
+
+si <- dat[,c("short_cite", "expt_num", "same_infant", "n_1")]
+si <- unique(si)
+
+median_sample <- median(si$n_1)
+
+# resulting power, anova
+pat <- pwr.anova.test(k = 2, n = median_sample, f = mp_effect, sig.level = 0.05, power = NULL)
+
+# 80% power, anova
+pat.est <- pwr.anova.test(k = 2, n = NULL, f = mp_effect, sig.level = 0.05, power = .8)
+
+```
+
+The estimated effect for mispronunciation sensitivity in this meta-analysis is `r mp_effect`, and the most frequently observed sample size is `r median_sample` participants.
+If we were to assume that researchers assess mispronunciation sensitivity in a simple ANOVA, the resulting power is `r r2(pat$power)`.
+Reversely, to achieve 80% power, one would need to test `r round(pat.est$n, 1)` participants.
+These calculations suggest that for the comparison of responses for correct pronunciations and mispronunciations, the studies included in this meta-analysis contain well-powered analyses.
+However, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which will require even larger sample sizes.
+We thus strongly advocate for a consideration of power and the reported effect sizes to test infants’ mispronunciation sensitivity.
+
+[From Christina's comment: I want to do the math for more complex designs in pangea, i’ll try to remember, if not, poke me https://jakewestfall.shinyapps.io/pangea/ ]
 
@@
 
-The current meta-analysis aggregated studies designed to investigate mispronunciation sensitivity, but we note that these studies varied in their approach to study mispronunciation sensitivity.
-For example, some studies investigated specific questions which required additional manipulations, such as the impact of the number of phonological features changed in the mispronunciations on mispronunciation sensitivity (e.g.
-White & Morgan, 2008; Mani & Plunkett, 2011) or sensitivity to consonant and vowel mispronunciations (Mani & Plunkett, 2007; 2010 keps and tups; Hojen et al., unpublished; Swingley, 2016).
-These studies varied in their experimental design, such as whether infants were familiar with the distractor image (e.g.
-White and Morgan (2008; see also Mani & Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) or whether the labels for the target and distractor images contained phonological overlap (Fernald, Swingley, & Pinto, 2001).
+The current meta-analysis aggregated studies designed to investigate mispronunciation sensitivity, but we note that these studies varied in their approach to study our phenomenon of interest.
+For example, some studies investigated specific questions which required additional manipulations, such as the impact of the number of phonological features changed in the mispronunciations on mispronunciation sensitivity ([e.g.
+@Mani2011; @White2008]) or sensitivity to consonant and vowel mispronunciations [@Mani2007; @Mani2010kepstups; @Hojen; @Swingley2016].
+The studies in our sample additionally varied in their experimental design, such as whether infants were familiar with the distractor image ([e.g.
+@White2008; see also @Mani2011; @Skoruppa2013; @Swingley2016)] or whether the labels for the target and distractor images contained phonological overlap [@Fernald2001a].
 Futhermore, the infants included in this meta-analysis had a variety of native languages (English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese) and language backgrounds (monolingual, bilingual, monodialectal, multidialectal).
@@
 However, our dataset coded for and included these variables.
-We hope that future research will be able to better understand the role that these variables play in infants' senstivity to mispronunciations.
+We hope that future research will be able to better understand the role that these variables play in infants' sensitivity to mispronunciations.
+
+[Katie: To respond to your comment, Christina, we did include bilinguals. I checked and there was no influence in keeping or removing them.]
 
@@
 
-This meta-analysis comprises an aggregation of almost two decades of research on mispronunciation sensitivity, finding that although infants accept both corect pronunciations and mispronunciations as labels for a target image, they are more likely to accept correct pronunciations, which indcates sensitivity to mispronunciations in familiar words.
+This meta-analysis comprises an aggregation of almost two decades of research on mispronunciation sensitivity, finding that infants accept both correct pronunciations and mispronunciations as labels for a target image.
+However, they are more likely to accept correct pronunciations, which indicates sensitivity to mispronunciations in familiar words.
 Despite the predictions of theories of infant phono-lexical development, this sensitivity was not modulated by infant age or vocabulary.
-This suggests that at a young age, infants' representations for their first words may be already phonologically well-specified.
+This suggests that from a young age on, infants’ word representations may be already phonologically well-specified.
 We recommend future theoretical frameworks take this evidence into account.
@@
 Future studies should be carefully planned with this evidence in mind.
-Ideally, future experimental design and data analysis would become standardized which may be aided by the growing trend of preregistration and open science practices.
+Ideally, future experimental design and data analysis would become standardized which will be aided by the growing trend of preregistration and open science practices.
 Our analysis highlights how meta-analyses can aid in identification of issues in a particular field and play a vital role in how the field addresses such issues.
@@
 ```{r create_r-references}
-#r_refs(file = "r-MISP_MA_BIB.bib")
+r_refs(file = "MISP_MA_BIB.bib")
 ```

### 2019-01-10 Paper_Analyses.tex
added references, organized old files

@@
 while simultaneously refining their knowledge about the sounds that make
-up these words {[}Primir, Kuhl, Best{]}. In a mature phono-lexical
-system, word recognition must balance flexibility to slight variation
-(e.g., speaker identity, accented speech) while distinguishing between
-phonetic details that differentiate words in their native language
-(e.g.~cat-hat). To build robust language knowledge, it seems ueful to
-acquire this ability early during development. Indeed, before children
-can correctly pronounce a word, they already are aware that slight
-phonological deviations might signal a change in word meaning {[}Clark
-\& Clark, 1977{]}. This mispronunciation sensitivity reflects the
-specificity with which infants represent the phonological information of
-familiar words. As infants continue to develop into expert language
-users, their language processing matures and becomes more efficient,
-including their knowledge of what consistutes a permissible versus
-word-changing phonological deviation. In this paper, we aggregate and
-analyze the almost 20 years of literature investigating mispronunciation
-sensitivity in infants in an attempt to uncover its characteristics and
-the trajectory of its development.
-
-At the turn of the millenia, infant language acquisition researchers had
-established that during their first years of life, infants are sensitive
-to changes in the phonetic detail of newly segmented words (Jusczyk \&
-Aslin, 1995) and learned minimal pairs (Stager \& Werker, 1997).
-Furthermore, when presented with familiar image pairs, children fixate
-on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg,
-\& McRoberts, 1998; Tincoff \& Jusczyk, 1999). Swingley and Aslin (2000)
-were the first to tie these lines of research together and investigate
-mispronunciation sensitivity in infant familiar word recognition:
-Children aged 18 to 23 months learning American English saw pairs of
-images (e.g.~a baby and a dog) and their eye movements to each image
-were recorded and subsequently coded offline. On \enquote{correct}
+up these words (Best, 1994, 1995; Curtin \& Werker, 2007; Kuhl, 2004;
+Werker \& Curtin, 2005). In a mature phono-lexical system, word
+recognition must balance flexibility to slight variation (e.g., speaker
+identity, accented speech) while distinguishing between phonetic details
+that differentiate words in a given language (e.g.~cat-hat). To build
+robust language knowledge, it seems ueful to acquire this ability early
+during development. Indeed, before children can correctly pronounce a
+word, they already are aware that slight phonological deviations might
+signal a change in word meaning (H. H. Clark \& Clark, 1977). This
+mispronunciation sensitivity reflects the specificity with which infants
+represent the phonological information of familiar words. As infants
+continue to develop into expert language users, their language
+processing matures and becomes more efficient, including their knowledge
+of what consistutes a permissible versus word-changing phonological
+deviation. In this paper, we aggregate and analyze the nearly 20 years
+of literature investigating mispronunciation sensitivity in infants in
+an attempt to uncover its characteristics and the trajectory of its
+development.
+
+At the turn of the millenium, infant language acquisition researchers
+had established that during their first years of life, infants are
+sensitive to changes in the phonetic detail of newly segmented words
+(Jusczyk \& Aslin, 1995) and learned minimal pairs (Stager \& Werker,
+1997). Furthermore, when presented with familiar image pairs, children
+fixate on the referent of a spoken label (Fernald, Pinto, Swingley,
+Weinberg, \& McRoberts, 1998; Tincoff \& Jusczyk, 1999). Swingley and
+Aslin (2000) were the first to tie these lines of research together and
+investigate mispronunciation sensitivity in infant familiar word
+recognition: Children aged 18 to 23 months learning American English saw
+pairs of images (e.g.~a baby and a dog) and their eye movements to each
+image were recorded and subsequently coded offline. On \enquote{correct}
 trials, children heard the correct label for one of the images (e.g.
@@
 principles that infants must discover in early phonological development
-in order to form adult-like word representations: \emph{phonological
-constancy} and \emph{phonological distinctiveness}. Phonological
-constancy is the ability to resolve phonological variation across
-different instances of a word, as long as the variation does not
-compromise the overall identity of the word. For example, different
-speakers - particularly across genders and accents - produce the same
-word with notable acoustic variation, although the word remains the
-same. In contrast, phonological distinctiveness describes the ability to
-differentiate between different words that happen to be phonologically
-similar, such as bad/bed or cat/hat. To successfully recognize words,
-speakers of a given language must therefore simultaneously use both
-phonological constancy and distinctiveness to determine where
-phonological variation is appropriate and where it changes a word's
-meaning. Both abilities have to be acquired, because language systems
-differ in which sounds signal a meaning change.
+in order to form adult-like word representations and processing
+capabilities: \emph{phonological constancy} and \emph{phonological
+distinctiveness}. Phonological constancy is the ability to resolve
+phonological variation across different instances of a word, as long as
+the variation does not compromise the overall identity of the word. For
+example, different speakers - particularly across genders and accents -
+produce the same word with notable acoustic variation, although the word
+remains the same. In contrast, phonological distinctiveness describes
+the ability to differentiate between different words that happen to be
+phonologically similar, such as bad/bed or cat/hat. To successfully
+recognize words, speakers of a given language must therefore
+simultaneously use both phonological constancy and distinctiveness to
+determine where phonological variation is appropriate and where it
+changes a word's meaning. Both abilities have to be acquired, because
+language systems differ in which sounds signal a meaning change.
 
@@
 become native speakers, which are all respectively supported by single
-studies and two predicted by theoretical accounts. By aggregating all
-publicly available evidence using meta-analysis, we can examine
-developmental trends making use of data from a much larger and diverse
-sample of infants than is possible in most single studies (see Frank et
-al., 2018; for a notable exception). Before we outline the
-meta-analytical approach and its advantages in detail, we first discuss
-the proposals this study seeks to disentangle and the data supporting
-each of the accounts.
+studies and additionally two possibilities are predicted by key
+theoretical accounts. By aggregating all publicly available evidence
+using meta-analysis, we can examine developmental trends making use of
+data from a much larger and diverse sample of infants than is possible
+in most single studies (see Frank et al., 2018; for a notable
+exception). Before we outline the meta-analytical approach and its
+advantages in detail, we first discuss the proposals this study seeks to
+disentangle and the data supporting each of the accounts.
+
+{[}Katie: Christina, do you know which citation the Frank et al., 2018
+citation is referring to above? He's published a gazilion papers in
+2018{]}
 
@@
 native phonetic patterns to a more mature understanding of the abstract
-phonological structure of words (Best 1994, 1995). This shift is
-predicted to coincide with the vocabulary spurt around 18 months, and is
-therefore related to vocabulary growth. In this case, we would expect
-the size of mispronunciation sensitivity to be larger at younger ages
-and \emph{decrease} as the child matures and learn more words, although
-children continue to detect mispronunciations. Indeed, young infants are
-more perturbed by accented speakers than older infants in their
-recognition of familiar words (Best, Tyler, Gooding, Orlando, \& Quann,
-2009; Mulak, Best, \& Tyler, 2013) or learning of new words (Schmale,
-Hollich, \& Seidl, 2011).
+phonological structure of words (Best, 1994, 1995). This shift is
+predicted to coincide with the vocabulary spurt around 18 months,
+because it is causally related to vocabulary growth. In this case, we
+would expect the size of mispronunciation sensitivity to be larger at
+younger ages and \emph{decrease} as the child matures and learn more
+words, although children continue to detect mispronunciations. Indeed,
+young infants are more perturbed by accented speakers than older infants
+in their recognition of familiar words (Best, Tyler, Gooding, Orlando,
+\& Quann, 2009; Mulak, Best, Tyler, Kitamura, \& Irwin, 2014) or
+learning of new words (Schmale, Hollich, \& Seidl, 2011).
 
@@
 words and only refine their representations as language experience
-accumulates. PRIMIR (Processing Rich Information from Multidimensional
-Interactive Representations; Curtin \& Werker, 2007; Werker \& Curtin,
-2005; Curtin, Byers-Heinlein, \& Werker, 2011) describes the development
-of phonemic categories emerging as the number of word form-meaning
-linkages increases. Vocabulary growth, therefore, promotes more detailed
-phonological representations in familiar words. Following this account,
-we predict an \emph{increase} in mispronunciation sensitivity as infants
-mature and add more words to their growing lexicon.
+accumulates. PRIMIR ((Processing Rich Information from Multidimensional
+Interactive Representations; Curtin \& Werker, 2007; Curtin,
+Byers-Heinlein, \& Werker, 2011; Werker \& Curtin, 2005)) describes the
+development of phonemic categories emerging as the number of word
+form-meaning linkages increases. Vocabulary growth, therefore, promotes
+more detailed phonological representations in familiar words. Following
+this account, we predict an \emph{increase} in mispronunciation
+sensitivity as infants mature and add more words to their growing
+lexicon.
 
@@
 Regarding the change in mispronunciation sensitivity over development,
-however, only a handful of studies have compared more than one age group
-on the same mispronunciation task (see Table X), making the current
-meta-analysis very informative. One study has found evidence for infants
-to become \emph{less} sensitive to mispronunciations as children
+however, only about half of studies have compared more than one age
+group on the same mispronunciation task (see Table 1), making the
+current meta-analysis very informative. One study has found evidence for
+infants to become \emph{less} sensitive to mispronunciations as they
 develop. Mani and Plunkett (2011) presented 18- and 24-month-olds with
-mispronunciations varying in the number of features changed (see below
-for a discussion of the role of features). 18-month-olds were sensitive
-to mispronunciations, regardless of the number of features changed.
+mispronunciations varying in the number of phonological features changed
+(e.g., changing an p into a b, a 1-feature change, versus changing a p
+into a g, a 2-feature change). 18-month-olds were sensitive to
+mispronunciations, regardless of the number of features changed.
 24-month-olds, in contrast, fixated the target image equally for both
@@
 difference in target looking for correct and mispronounced trials is
-smaller in younger infants and grows as infants develop. Mani and
-Plunkett (2007) tested 15-, 18-, and 24-month-olds learning British
-English; although all three groups were sensitive to mispronunciations,
-15-month-olds showed a less robust sensitivity. An increase in
-sensitivity to mispronunciations has also been found from 20 to 24
-months (van der Feest \& Fikkert, 2015) and 15 to 18 months (Altvater
-Mackensen et al., 2013) in Dutch infants, as well as German infants from
-22 to 25 months (Altvater-Mackensen, 2010). Furthermore, van der Feest
-and Fikkert (2015) found that sensitivity to specific kinds of
-mispronunciations develop at different ages depending on language
-infants are learning. In other words, the native language constraints
-which \emph{kinds} of mispronunciations infants are sensitive to first,
-and that as infants develop, they become sensitive to other
-mispronunciations. These studies award support to the prediction that
-mispronunciation sensitivity improves with development.
+reported to be smaller in younger infants and grows as infants develop.
+Mani and Plunkett (2007) tested 15-, 18-, and 24-month-olds learning
+British English; although all three groups were sensitive to
+mispronunciations, 15-month-olds showed a less robust sensitivity. An
+increase in sensitivity to mispronunciations has also been found from 20
+to 24 months (Feest \& Fikkert, 2015) and 15 to 18 months
+(Altvater-Mackensen, Feest, \& Fikkert, 2014) in Dutch infants, as well
+as German infants from 22 to 25 months (Altvater-Mackensen, 2010).
+Furthermore, Feest and Fikkert (2015) found that sensitivity to specific
+kinds of mispronunciations develop at different ages depending on
+language infants are learning. In other words, the native language
+constraints which \emph{kinds} of mispronunciations infants are
+sensitive to first, and that as infants develop, they become sensitive
+to other mispronunciations. These studies award support to the
+prediction that mispronunciation sensitivity improves with development.
 
@@
 sensitivity) did not. This suggests that as children develop, they are
-more likely to look at the target in the presence of a mispronounced
-label and that age is not related to mispronunciation sensitivity. A
-similar response pattern has been found for British English learning
-infants aged between 18 and 24 months (Bailey \& Plunkett, 2002) as well
-as younger French-learning infants at 12 and 17 months (Zesiger,
-Lozeron, Levy, \& Frauenfelder, 2012). These studies award support to
-the prediction that mispronunciation sensitivity does not change with
-development.
+more likely to look at the target in the presence of a correct or
+mispronounced label, but that the difference between the two does not
+change. A similar response pattern has been found for British English
+learning infants aged between 18 and 24 months (Bailey \& Plunkett,
+2002) as well as younger French-learning infants at 12 and 17 months
+(Zesiger, Lozeron, Levy, \& Frauenfelder, 2012). These studies award
+support to the prediction that mispronunciation sensitivity does not
+change with development.
 
 Why would mispronunciation sensitivity change as infants develop, and
-would it increase or decrease? The main hypothesis is related to
-vocabulary growth. Both the Perceptual Attunement (Best, 1994; 1995) and
-PRIMIR (Curtin \& Werker, 2007; Werker \& Curtin, 2005; Curtin,
-Byers-Heinlein, \& Werker, 2011) accounts situate a change in
-mispronunciation sensitivity occurring along with an increase in
-vocabulary size, particularly with the vocabulary spurt at about 18
-months. Knowing more words helps infants shift their focus to the
-relevant phonetic dimensions needed for word recognition. On the one
-hand, a smaller lexicon does not require full specification to
-differentiate between words; as more phonologically similar words are
-learned, so does the need to have fully detailed representations for
-those words (Charles-Luce \& Luce, 1995). On the other hand, a growing
-vocabulary is also related to more experience or familiarity with words,
-which may sharpen the detail of their representation (Barton, 1980).
+would it increase or decrease? The main hypotheses attribute change to
+vocabulary growth. Both the Perceptual Attunement (Best, 1994, 1995) and
+PRIMIR (Curtin \& Werker, 2007; Curtin et al., 2011; Werker \& Curtin,
+2005) accounts situate a change in mispronunciation sensitivity
+occurring along with an increase in vocabulary size, particularly with
+the vocabulary spurt at about 18 months. As infants learn more words,
+their focus shifts to the relevant phonetic dimensions needed for word
+recognition. For example, an infant who knows a handful of words with
+few phonological neighbors would not need to have fully specified
+phonological representations in order to differentiate between these
+words. As more phonologically similar words are learned, however, the
+need for fully detailed phonological representations increases
+(Charles-Luce \& Luce, 1995). Furthermore, a growing vocabulary also
+reflects increased experience or familiarity with words, which may
+sharpen the detail of their phonological representation (Barton, Miller,
+\& Macken, 1980). If vocabulary growth leads to an increase in the
+phonological specificity of infants' word representation, we should find
+a relationship between vocabulary size and mispronunciation sensitivity.
 
@@
 mispronunciation sensitivity and vocabulary size have concluded that
-there is no relationship (Swingley \& Aslin 2000; 2002; Bailey \&
-Plunkett, 2002; Zesiger, Lozeron, Levy, \& Frauenfelder, 2012; Swingley,
-2009; Ballem \& Plunkett, 2005; Mani \& Plunkett, 2007; Mani, Coleman,
-\& Plunkett, 2008). One notable exception comes from Mani and Plunkett
-(2010: keps and tups). Here, 12-month-old infants were divided into a
-low and high vocabulary group based on median vocabulary size. High
-vocabulary infants showed greater sensitivity to vowel mispronunciations
-than low vocabulary infants, although this was not the case for
-consonant mispronunciations. Taken together, although receiving
-considerable support from theories of phono-lexical processing in
-language acquisition, there is very little evidence for a role of
-vocabulary size in mispronunciation sensitivity. In our current
-meta-analysis, we include the relationship between mispronunciation
-sensitivity and vocabulary size to further disentangle the disconnect
-between theory and experimental results.
+there is no relationship (Bailey \& Plunkett, 2002; Ballem \& Plunkett,
+2005; Mani \& Plunkett, 2007; Mani, Coleman, \& Plunkett, 2008;
+Swingley, 2009; Swingley \& Aslin, 2000, 2002; Zesiger et al., 2012).
+One notable exception comes from Mani and Plunkett (2010). Here,
+12-month-old infants were divided into a low and high vocabulary group
+based on median vocabulary size. High vocabulary infants showed greater
+sensitivity to vowel mispronunciations than low vocabulary infants,
+although this was not the case for consonant mispronunciations. Taken
+together, although receiving considerable support from theories of
+phono-lexical processing in language acquisition, there is very little
+evidence for a role of vocabulary size in mispronunciation sensitivity.
+In our current meta-analysis, we include the relationship between
+mispronunciation sensitivity and vocabulary size to further disentangle
+the disconnect between theory and experimental results.
 
@@
 separate brushstroke and it is only by examining all of them together
-that we can achieve a better understanding of early language
-development. Meta-analyses can provide thus further insights by
+that we can achieve a better understanding of the big picture of early
+language development. Meta-analyses can provide unique insights by
 estimating the population effect, both of infants' responses to correct
@@
 2014). The most recent version is available via the website and the
-interactive platform MetaLab (metalab.stanford.edu; Bergmann et al.,
-2018). Since the present paper was written with embedded analysis
-scripts in R {[}@R, @RMarkdown, @papaja{]}, it is always possible to
-re-analyze an updated dataset. In addition, we followed the Preferred
-Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA)
-guidelines and make the corresponding information available as
-supplementary materials (Moher, Liberati, Tetzlaff, Altman \&
-PRISMAGroup, 2009). Figure 1 plots our PRISMA flowchart illustrating the
-paper selection procedure.
+interactive platform MetaLab ((\url{https://metalab.stanford.edu};
+Bergmann et al., 2018)). Since the present paper was written with
+embedded analysis scripts in R (R Core Team, 2018, Allaire et al.
+(2018), Aust and Barth (2018)), it is always possible to re-analyze an
+updated dataset. In addition, we followed the Preferred Reporting Items
+for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make
+the corresponding information available as supplementary materials
+(Moher, Liberati, Tetzlaff, Altman, \& Group, 2009). Figure 1 plots our
+PRISMA flowchart illustrating the paper selection procedure.
 
@@
 110 items. We then used the google scholar search engine to search for
-papers citing the original Swingley \& Aslin (2000) publication. This
+papers citing the original Swingley and Aslin (2000) publication. This
 search was conducted on 22 September, 2017 and yielded 288 results. We
@@
 were auditory speech. The final sample (n = \emph{34}) consisted of 28
-journal articles, 1 proceedings paper, 3 thesis, and 2 unpublished
+journal articles, 1 proceedings paper, 3 theses, and 2 unpublished
 reports. We will refer to these items collectively as papers. Table 1
@@
 The 34 papers we identified as relevant were then coded with as much
-consistently reported detail as possible (Tsuji, Bergmann, \& Cristia,
-2014; Bergmann et al., 2018). For each experiment (note that a paper
-typically has multiple experiments), we entered variables describing the
-publication, population, experiment design and stimuli, and results. For
-the planned analyses to evaluate the development of mispronunciation
-sensitivity, we focus on the following characteristics:
+consistently reported detail as possible (Bergmann et al., 2018; Tsuji
+et al., 2014). For each experiment (note that a paper typically has
+multiple experiments), we entered variables describing the publication,
+population, experiment design and stimuli, and results. For the planned
+analyses to evaluate the development of mispronunciation sensitivity, we
+focus on the following characteristics:
 
@@
 mispronunciation conditions and the results were reported separately in
-the paper, we also entered each condition as a separate row (e.g.,
-consonant versus vowel mispronunciations; Mani \& Plunkett, 2007). The
+the paper, we also entered each condition as a separate row ((e.g.,
+consonant versus vowel mispronunciations; Mani \& Plunkett, 2007)). The
 fact that the same infants contributed data to multiple rows (minimally
@@
 means, standardized by their variance. The most well-known effect size
-from this group is Cohen's \emph{d} {[}@cohen{]}. To correct for the
-small sample sizes common in infant research, however, we used as a
-dependent variable Hedges' \emph{g} instead of Cohen's \emph{d} (Hedges,
-1981; Morris, 2000).
+from this group is Cohen's \emph{d} (Cohen, 1988). To correct for the
+small sample sizes common in infant research, however, we used Hedges'
+\emph{g} instead of Cohen's \emph{d} (Hedges, 1981; Morris \& DeShon,
+2002).
 
@@
 deviations reported in the paper (\emph{n} = 186 records from 26 papers)
-or using reported t-values (\emph{n} = 74 records from 9 papers). Two
-papers reported raw means and standard deviations for some experimental
+or reported t-values (\emph{n} = 74 records from 9 papers). Two papers
+reported raw means and standard deviations for some experimental
 conditions and just t-values for the remaining experimental conditions
-(Swingley, 2016; Altvater-Mackensen et al., 2014). Raw means and
+(Altvater-Mackensen et al., 2014; Swingley, 2016). Raw means and
 standard deviations were extracted from figures for 4 papers. In a
-within-participation design, when two means are compared (i.e.~looking
+within-participant design, when two means are compared (i.e.~looking
 during pre- and post-naming) it is necessary to obtain correlations
 between the two measurements at the participant level to calculate
-effect sizes and effect size variance based on t-values. Upon request we
-were provided with correlation values for one paper (Altvater-Mackensen,
-2010); we were able to compute correlations using means, standard
-deviations, and t-values for \emph{n} = 5 (following Csibra, et al.
-2016, Appendix B; see also Rabagliati, Ferguson, \& Lew-Williams, 2018).
-Correlations were imputed for the remaining papers (see Black \&
-Bergmann, 2017, for the same procedure). For two papers, we could not
-derive any effect size (Ballem \& Plunkett, Renner), and for a third
-paper, we do not have sufficient information in one record to compute
-effect sizes (Skoruppa). We compute a total of 106 effect sizes for
-correct pronunciations and 150 for mispronunciations. Following standard
-meta-analytic practice, we remove outliers, i.e.~effect sizes more than
-3 standard deviations from the respective mean effect size. This leads
-to the exclusion of 2 records for correct pronunciations and 3 records
-for mispronunciations.
+effect sizes and effect size variance. Upon request we were provided
+with correlation values for one paper (Altvater-Mackensen, 2010); we
+were able to compute correlations using means, standard deviations, and
+t-values for 5 papers ((following Csibra, Hernik, Mascaro, Tatone, \&
+Lengyel, 2016; see also Rabagliati, Ferguson, \& Lew-Williams, 2018)).
+Correlations were imputed for the remaining papers ((see Black \&
+Bergmann, 2017 for the same procedure)). For two papers, we could not
+derive any effect size (Ballem \& Plunkett, 2005; Renner, 2017), and for
+a third paper, we do not have sufficient information in one record to
+compute effect sizes (Skoruppa, Mani, Plunkett, Cabrol, \& Peperkamp,
+2013). We compute a total of 106 effect sizes for correct pronunciations
+and 150 for mispronunciations. Following standard meta-analytic
+practice, we remove outliers, i.e.~effect sizes more than 3 standard
+deviations from the respective mean effect size. This leads to the
+exclusion of 2 records for correct pronunciations and 3 records for
+mispronunciations.
+
+{[}Katie: Mention of Renner here{]}
 
@@
 multiple datapoints, we analyze our results in a multilevel approach
-using the R {[}@R{]} package metafor {[}@metafor{]}. This means we model
-as random effect that effect sizes from the same paper share are based
-on more similar studies than those across papers and that nested therein
-effects can stem from the same infants.
+using the R (R Core Team, 2018) package metafor (Viechtbauer, 2010). We
+use a multilevel random effects model which estimates the mean and
+variance of effect sizes sampled from an assumed distribution of effect
+sizes. In the random effect structure we take into account the shared
+variance of effect sizes drawn from the same paper, and nested therein
+that the same infants might contribute to multiple effect sizes.
 
@@
 the target by the total percentage of looks to both the target and
-distractor images. Across papers the baseline comparison varied; we used
-the baseline reported by the authors of each paper. Most papers
-(\emph{n} = 52 records from 13 papers) subtracted the PTL score for a
-pre-naming baseline phase from the PTL score for a post-naming phase and
-report a difference score.
+distractor images. Across papers the baseline comparison varied; since
+other options were not available to us, we used the baseline reported by
+the authors of each paper. Most papers (\emph{n} = 52 records from 13
+papers) subtracted the PTL score for a pre-naming baseline phase from
+the PTL score for a post-naming phase and report a difference score.
 
@@
 over-reported and thus might be over-represented in our meta-analyses
-(see Ferguson \& Heene, 2012). To examine whether this is also the case
-in the mispronunciation sensitivity literature, which would bias the
-data analyzed in this meta-analysis, we conducted two tests. We first
-examined whether effect sizes are distributed as expected based on
+((see C. J. Ferguson \& Heene, 2012)). To examine whether this is also
+the case in the mispronunciation sensitivity literature, which would
+bias the data analyzed in this meta-analysis, we conducted two tests. We
+first examined whether effect sizes are distributed as expected based on
 sampling error using the rank correlation test of funnel plot asymmetry
-with the R {[}@R{]} package metafor {[}@metafor{]}. Effect sizes with
-low variance were expected to fall closer to the estimated mean, while
-effect sizes with high variance should show an increased,
-evenly-distributed spread around the estimated mean. Publication bias
-would lead to an uneven spread.
+with the R (R Core Team, 2018) package metafor (Viechtbauer, 2010).
+Effect sizes with low variance were expected to fall closer to the
+estimated mean, while effect sizes with high variance should show an
+increased, evenly-distributed spread around the estimated mean.
+Publication bias would lead to an uneven spread.
 
 Second, we analyze all of the significant results in the dataset using a
-p-curve from the p-curve app (v4.0, p-curve.com; @pcurve). This p-curve
-tests for evidential value by examining whether the p-values follow the
-expected distribution of a right skew in case the alternative hypothesis
-is true, versus a flat distribution that speaks for no effect being
-present in the population and all observed significant effects being
-spurious. Responses to correctly pronounced and mispronounced labels
-were predicted to show different patterns of looking behavior. In other
+p-curve from the p-curve app ((v4.0, \url{http://p-curve.com};
+Simonsohn, Nelson, \& Simmons, 2014)). This p-curve tests for evidential
+value by examining whether the p-values follow the expected distribution
+of a right skew in case the alternative hypothesis is true, versus a
+flat distribution that speaks for no effect being present in the
+population and all observed significant effects being spurious.
+
+Responses to correctly pronounced and mispronounced labels were
+predicted to show different patterns of looking behavior. In other
 words, there is an expectation that infants should look to the target
@@
 of significant looks to the target when hearing a mispronounced label
-(i.e.~there might be no effect present in the population, see e.g., );
-as a result, we conducted these two analyses to assess publication bias
-separately for both conditions.
+(i.e.~there might be no effect present in the population); as a result,
+we conducted these two analyses to assess publication bias separately
+for both conditions.
 
@@
 
-The models reported here are hierarchical random-effects models (infant
-groups nested within papers) of variance-weighted effect sizes, which we
-computed with the R {[}@R{]} package metafor {[}@metafor{]}. To
-investigate how development impacts mispronunciation sensitivity, our
-core theoretical question, we introduced age (centered; continuous and
-measured in days but transformed into months for ease of interpreting
-estimates by dividing by 30.44) as a moderator to our main model. For a
-subsequent exploratory investigations of experimental characteristics,
-we introduced each characteristic as a moderator (more detail below).
+The models reported here are multilevel random-effects models of
+variance-weighted effect sizes, which we computed with the R (R Core
+Team, 2018) package metafor (Viechtbauer, 2010). To investigate how
+development impacts mispronunciation sensitivity, our core theoretical
+question, we introduced age (centered; continuous and measured in days
+but transformed into months for ease of interpreting estimates by
+dividing by 30.44) as a moderator to our main model. For a subsequent
+exploratory investigation of experimental characteristics, we introduced
+each characteristic as a moderator (more detail below).
 
@@
 Figure 2 shows the funnel plots for both correct pronunciations and
-mispronunciations (code adapted from Sakaluk, 2016). Funnel plot
-assymmetry was significant for both correct pronunciations (Kendall's
+mispronunciations ((code adapted from Sakaluk, 2016)). Funnel plot
+asymmetry was significant for both correct pronunciations (Kendall's
 \(\tau\) = 0.53, \emph{p} \textless{} .001) and mispronunciations
 (Kendall's \(\tau\) = 0.16, \emph{p} = 0.004). These results,
-quantifying the assymmetry in the funnel plots (Figure 1), indicate bias
+quantifying the asymmetry in the funnel plots (Figure 1), indicate bias
 in the literature. This is particularly evident for correct
@@
 The stronger publication bias for correct pronunciation might reflect
-the status of this condiction as a control. If infants were not looking
+the status of this condition as a control. If infants were not looking
 to the target picture after hearing the correct label, the overall
-experiment design is called into questions. However, due to the small
-effect and sample sizes (which we will discuss in the following sections
-in more detail) one would expect the regular occurrence of null results
-even though as a population infants would reliably show the expected
-object identification effect.
+experiment design is called into questions. However, even in a
+well-powered study one would expect the regular occurrence of null
+results even though as a population infants would reliably show the
+expected object identification effect.
 
 We should also point out that funnel plot asymmetry can be caused by
-multiple factors beside publication bias, such as heterogeneity in the
+multiple factors besides publication bias, such as heterogeneity in the
 data. There are various possible sources of heterogeneity, which our
@@
 size. The black line marks zero, the dashed grey line marks the effect
-estimate, and the grey line marks funnel plot assymetry.}
+estimate, and the grey line marks funnel plot asymmetry.}
 \end{figure}
@@
 (SE = 0.12) which was significantly different from zero (CI {[}0.673,
-1.143{]}, \emph{p} \textless{} .001). This is a rather large effect size
-(according to the criteria set by Cohen, 1988; see also Bergmann, et
-al., 2018; for comparative meta-analytic effect sizes in language
-acquisition research). That the effect size is significantly above zero
+1.143{]}, \emph{p} \textless{} .001). This is a small to medium effect
+size ((according to the criteria set by Mills-Smith, Spangler, Panneton,
+\& Fritz, 2015)). That the effect size is significantly above zero
 suggests that when presented with the correctly pronounced label,
-infants fixated the corresponding object. Our analysis of funnel plot
-asymmetry, however, found evidence for publication bias, which might
-lead to an overestimated effect sizes as smaller, non-significant
-results might not be published despite the fact that they should occur
-regularly even in well-powered studies. Although the effect size Hedges'
-\emph{g} may be overestimated for object identification in response to
-correctly pronounced words, the p-curve results and a CI lower bound of
-0.67, which is substantially above zero, together suggest that this
-result is somewhat robust. In other words, we are confident that the
-true population mean lies above zero for object recognition of correctly
-pronounced words.
+infants tended to fixate on the corresponding object. Although the
+publication bias present in our analysis of funnel plot asymmetry
+suggests that the effect size Hedges' \emph{g} may be overestimated for
+object identification in response to correctly pronounced words, the
+p-curve results and a CI lower bound of 0.67, which is substantially
+above zero, together suggest that this result is somewhat robust. In
+other words, we are confident that the true population mean lies above
+zero for object recognition of correctly pronounced words.
 
@@
 \emph{p} \textless{} .001). This is considered a small effect size
-(Cohen, 1988), but significantly above zero, which suggests that even
-when presented with a mispronounced label, infants fixated the correct
-object. In other words, infants are able to resolve mispronunciations, a
-key skill in language processing We again note the publication bias
-(which was smaller in this condition), and the possibility that the
-effect size Hedges' \emph{g} may be overestimated. But, as the p-curve
-indicated evidential value, we are confident in the overall patterns,
-namely that infants fixate the target even after hearing a mispronounced
-label.
-
-\subsubsection{Mispronunciation Sensitivity Meta-analytic
+(Mills-Smith et al., 2015), but significantly above zero, which suggests
+that even when presented with a mispronounced label, infants fixated the
+correct object. In other words, infants are able to resolve
+mispronunciations, a key skill in language processing We again note the
+publication bias (which was smaller in this condition), and the
+possibility that the effect size Hedges' \emph{g} may be overestimated.
+But, as the p-curve indicated evidential value, we are confident in the
+overall pattern, namely that infants fixate the target even after
+hearing a mispronounced label.
+
+\subsubsection{Mispronunciation Sensitivity Meta-Analytic
 Effect}\label{mispronunciation-sensitivity-meta-analytic-effect}
@@
 pronunciations with mispronunciations directly. To this end, we combined
-the two datasets. The moderator test was significant, QM(1) = 215.761,
-\emph{p} \textless{} .001. The estimate for mispronunciation sensitivity
-was 0.495 (SE = 0.034), and infants' looking times across conditions
-were significantly different (CI {[}0.429, 0.561{]}, \emph{p}
-\textless{} .001). This confirms that although infants fixate the
-correct object for both correct pronunciations and mispronunciations,
-the observed fixations to target (as measured by the effect sizes) were
-significantly greater for correct pronunciations. In other words, we
-observe a significant difference between the two conditions and can now
-quantify the modulation of fixation behavior in terms of standardized
-effect sizes and their variance. This first result has both theoretical
-and practical implications, as we can now reason about the amount of
-perturbance caused by mispronunciations and can plan future studies to
+the two datasets. When condition was included (correct, mispronounced),
+the moderator test was significant, QM(1) = 215.761, \emph{p}
+\textless{} .001. The estimate for mispronunciation sensitivity was
+0.495 (SE = 0.034), and infants' looking times across conditions were
+significantly different (CI {[}0.429, 0.561{]}, \emph{p} \textless{}
+.001). This confirms that although infants fixate the correct object for
+both correct pronunciations and mispronunciations, the observed
+fixations to target (as measured by the effect sizes) were significantly
+greater for correct pronunciations. In other words, we observe a
+significant difference between the two conditions and can now quantify
+the modulation of fixation behavior in terms of standardized effect
+sizes and their variance. This first result has both theoretical and
+practical implications, as we can now reason about the amount of
+perturbation caused by mispronunciations and can plan future studies to
 further investigate this effect with suitable power.
@@
 462.51, \emph{p} \textless{} .001), as well as mispronunciation
-sensitivity, which included the moderator condition, (QE(249) =
-1,088.14, \emph{p} \textless{} .001). This indicated that the sample
-contains unexplained variance leading to significant difference across
-our studies beyond what is to be expected based on random sampling
-error. We therefore continue with our moderator analysis to investigate
-possible sources of this variance.
+sensitivity, which included the moderator condition (QE(249) = 1,088.14,
+\emph{p} \textless{} .001). This indicated that the sample contains
+unexplained variance leading to significant difference between studies
+beyond what is to be expected based on random sampling error. We
+therefore continue with our moderator analysis to investigate possible
+sources of this variance.
 
@@
 words (QM(1) = 1.715, \emph{p} = 0.19). The lack of a significant
-modulation together with the small estimates (correct: \(\beta\) =
-0.015, SE = 0.018, 95\% CI{[}-0.02, 0.049{]}, \emph{p} = 0.41;
+modulation together with the small estimates for age (correct: \(\beta\)
+= 0.015, SE = 0.018, 95\% CI{[}-0.02, 0.049{]}, \emph{p} = 0.41;
 mispronunciation: \(\beta\) = 0.015, SE = 0.011, 95\% CI{[}-0.007,
-0.037{]}, \emph{p} = 0.19) indicates that there was no relationship
+0.037{]}, \emph{p} = 0.19) indicates that there might be no relationship
 between age and target looks in response to a correctly pronounced or
-mispronounced label. We plot both object recognition and
-mispronunciation sensitivity as a function of age in Figure 3.
+mispronounced label. We note that the estimates in both cases are
+positive, however, which is in line with the general assumption that
+infants' language processing overall improves as they mature (Fernald et
+al., 1998). We plot both object recognition and mispronunciation
+sensitivity as a function of age in Figure 3.
 
@@
 driven by the difference between conditions. The small estimate, as well
-as inspection of Figure 2 suggests that as infants age, their
-mispronunciation sensitivity remains the same.
+as inspection of Figure 2, suggests that as infants age, their
+mispronunciation sensitivity neither increases or decreases.
 
@@
 pronunciations (orange) and mispronunciations (blue) by participant age.
-Panel b: Effect sizes for mispronunciation sensitivyt (correct -
+Panel b: Effect sizes for mispronunciation sensitivity (correct -
 mispronunciations) by participant age. For both panels, point size
@@
 and 39 records; production = 3 papers and 20 records). There is reason
-to believe that production data are different from comprehension data
-(the former being easier to estimate for parents in the typical
-questionnaire-based assessment; Tomasello \& Mervis, 1994), and we
-therefore planned to analyze these two types of vocabulary measurement
-separately. However, because only 3 papers reported correlations with
-productive vocabulary scores, only limited conclusions that can be
-drawn. In our vocabulary analysis, we therefore focus exclusively on the
-relationship between comprehension and mispronunciation sensitivity.
-
-{[}Katie: Tomasello reference -
-\url{https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1540-5834.1994.tb00186.x}{]}
+to believe that production data are different from comprehension data.
+Children comprehend more words than they can produce, leading to
+different estimates for comprehension and production. Production data is
+easier to estimate for parents in the typical questionnaire-based
+assessment and may therefore be more reliable (Tomasello \& Mervis,
+1994). As a result, we planned to analyze these two types of vocabulary
+measurement separately. However, because only 3 papers reported
+correlations with productive vocabulary scores, only limited conclusions
+can be drawn. We also note that because individual effect sizes in our
+analysis were related to object recognition and not mispronunciation
+sensitivity, we were only able to calculate the relationship between
+vocabulary scores and the former. In our vocabulary analysis, we
+therefore focus exclusively on the relationship between comprehension
+and object recognition for correct pronunciations and mispronunciations.
+
+{[}Katie: Written as if moderators can not be added to metacor(){]}
 
@@
 pronunciations for 9 of 10 experimental conditions, with correlation
-values ranging from -0.16 to 0.48. The mean effect size Pearson's
-\emph{r} of 0.14 was small but did differ significantly from zero (CI
-{[}0.03; 0.25{]} \emph{p} = 0.012). As a result, we can draw a tentative
-conclusion that there is a positive relationship between comprehension
-scores and object recognition in response to correct pronunciations.
+values ranging from -0.16 to 0.48. The weighted mean effect size
+Pearson's \emph{r} of 0.14 was small but did differ significantly from
+zero (CI {[}0.03; 0.25{]} \emph{p} = 0.012). As a result, we can draw a
+tentative conclusion that there is a positive relationship between
+comprehension scores and object recognition in response to correct
+pronunciations.
 
@@
 recognition for mispronunciations. Higher comprehension scores were
-associated with greater object recognition in response to correct
-pronunciations for 17 of 29 experimental conditions, with correlation
-values ranging from -0.35 to 0.57. The mean effect size Pearson's
-\emph{r} of 0.05 was small and did not differ significantly from zero
-(CI {[}-0.01; 0.12{]} \emph{p} = 0.119). The small correlation suggests
-a lack of relationship between vocabulary and object recognition for
-mispronunciations. We again emphasize that we cannot draw a firm
-conclusion due to the small number of studies we were able to include
-here.
+associated with greater object recognition in response to
+mispronunciations for 17 of 29 experimental conditions, with correlation
+values ranging from -0.35 to 0.57. The weighted mean effect size
+Pearson's \emph{r} of 0.05 was small and did not differ significantly
+from zero (CI {[}-0.01; 0.12{]} \emph{p} = 0.119). The small correlation
+suggests either a very small positive or no relationship between
+vocabulary and object recognition for mispronunciations. We again
+emphasize that we cannot draw a firm conclusion due to the small number
+of studies we were able to include here.
 
@@
 sensitivity studies included in this meta-analysis. This figure
-illustrates two things: the growing number of mispronunciation
-sensitivity studies and the waning number of studies measuring
-vocabulary. The lack of evidence for a relationship between
-mispronunciation sensitivity and vocabulary size in some early studies
-may have contributed to increasingly fewer researchers including
+illustrates two things: the increasing number of mispronunciation
+sensitivity studies and the decreasing number of mispronunciation
+studies measuring vocabulary. The lack of evidence for a relationship
+between mispronunciation sensitivity and vocabulary size in some early
+studies may have contributed to increasingly fewer researchers including
 vocabulary measurements in their mispronunciation sensitivity
 experimental design. This may explain our underpowered analysis of the
-relationship between mispronunciation sensitivity and vocabulary size.
+relationship between object recognition for correct pronunciations and
+mispronunciations and vocabulary size.
 
@@
 The main goal of this paper was to assess mispronunciation sensitivity
-and its maturation with age. The results seem clear: Although infants
-consider a mispronunciation as a better match with the target image than
-a distractor image, there was a consistent effect of mispronunciation
-sensitivity. This did not change with development nor with vocabulary
-size. Of the 3 predictions and assumptions about the development of
-infants' sensitivity to mispronunciations discussed in the Introduction,
-the present results lend some support for the argument that
-mispronunciation sensitivity stays consistent as infants develop. This
-runs counter to existing theories of phono-lexical development, which
-predict either an increase (PRIMR ref) or decrease (Assim Model ref) in
-mispronunciation sensitivity. Furthermore, although we found a
-relationship between vocabulary comprehension and target looking for
-correct pronunciations, we found no relationship between vocabulary and
-target looking for mispronunciations. This also runs counter to the
-predictions for the PRIMR (PRIMR ref) and Assimilation (Assim ref)
-models, but may be due to our analyses being underpowered. In sum, it
-seems that current theories of infants' phono-lexical development cannot
-fully capture our results, but that more investigation is needed to draw
-a firm conclusion.
+and its maturation with age and increased vocabulary size. The results
+seem clear: Although infants consider a mispronunciation to be a better
+match to the target image than to a distractor image, there was a
+constant and stable effect of mispronunciation sensitivity. This did not
+change with development nor with vocabulary size. Of the three
+predictions about the development of infants' sensitivity to
+mispronunciations discussed in the Introduction, the present results
+lend some support for the proposal that mispronunciation sensitivity
+stays consistent as infants develop. This runs counter to existing
+theories of phono-lexical development, which predict either an increase
+(Curtin \& Werker, 2007; Curtin et al., 2011; Werker \& Curtin, 2005) or
+decrease (Best, 1994, 1995) in mispronunciation sensitivity.
+Furthermore, although we found a relationship between vocabulary size
+(comprehension) and target looking for correct pronunciations, we found
+no relationship between vocabulary and target looking for
+mispronunciations. This also runs counter to the predictions for the
+PRIMR (Curtin \& Werker, 2007; Curtin et al., 2011; Werker \& Curtin,
+2005) and Assimilation (Best, 1994, 1995) models, but may be due to our
+analyses being underpowered. In sum, it seems that current theories of
+infants' phono-lexical development cannot fully capture our results, but
+that more investigation is needed to draw a firm conclusion.
 
@@
 that emerged during the construction of the present dataset and careful
-reading of the original papers is the analysis approach. We observed, as
-mentioned in the Methods section, large variance in the dependent
-variable reported, and additionally noted variance in the size of the
-time window chosen for analyses. Researchers might adapt their analysis
-strategy to age or they might be influenced by having observed the data.
-In the latter case, we expect an increase in significant results, which
-at the same time can (partially) explain the publication bias we observe
-(Simmons, Nelson, \& Simonsohn, 2011).
-
-We included details related to timing and type of dependent variable
-calculated in our coding of the dataset because they are consistently
-reported and might be useful for experiment design in the future by
-highlighting typical choices and helping establish field standards. In
-the following section, we include an exploratory analysis to investigate
-the possibility of systematic differences in the approach to analysis in
-general and across infant age. The purpose of this analysis is to better
-understand the influence of choices made in analyzing mispronunciation
-sensitivity studies as well as the influence these choices may have on
-our understanding of mispronunciation sensitivity development.
+reading of the original papers was the analysis approach. We observed,
+as mentioned in the Methods section, large variation in the dependent
+variable reported, and additionally noted that the size of the chosen
+post-naming analysis window varied substantially across papers.
+Researchers might adapt their analysis strategy to infants' age or they
+might be influenced by having observed the data. For example, consider
+the possibility that there is a true increase in mispronunciation
+sensitivity over development. In this scenario, younger infants should
+show no or only little sensitivity to mispronunciations while older
+infants would show a large sensitivity to mispronunciations. This lack
+of or small mispronunciation sensitivity in younger infants is likely to
+lead to non-significant results, which would be more difficult to
+publish (C. J. Ferguson \& Heene, 2012). In order to have publishable
+results, adjustments to the analysis approach could be made until a
+significant, but spurious, effect of mispronunciation sensitivity is
+found. This would lead to an increase in significant results and alter
+to observed developmental trajectory of mispronunciation sensitivity.
+Such a scenario is in line with the publication bias we observe
+(Simmons, Nelson, \& Simonsohn, 2011). We examine whether variation in
+the approach to data analysis may be have an influence on findings of
+mispronunciation sensitivity.
+
+We included details related to timing and type of dependent variable in
+our coding of the dataset because they are consistently reported and
+might be useful for experiment design in the future by highlighting
+typical choices and helping establish field standards. In the following
+section, we include an exploratory analysis to investigate the
+possibility of systematic differences in the approach to analysis in
+general and across infant age. The purpose of this analysis was to
+better understand the influence of choices made in analyzing
+mispronunciation sensitivity studies as well as the influence these
+choices may have on our understanding of mispronunciation sensitivity
+development.
 
@@
 
-We identified two sets of variables which had the potential to vary
-across papers to assess the influence of data analysis choices on
-resulting effect size: timing (size of time window analyzed; offset
-time) and which dependent variable(s) were reported. In the following,
-we discuss the possible theoretical motivation for these data analysis
-choices, the variation present in the current meta-analysis dataset, and
-the influence these analysis choices may have have on measurements of
-mispronunciation sensitivity development. We focus specifically on the
-size of the mispronunciation sensitivity effect, considering the whole
-dataset and including condition (correct pronunciation,
-mispronunciation) as moderator.
+We identified two sets of variables which varied across papers to assess
+the influence of data analysis choices on resulting effect size: timing
+(post-naming analysis window; offset time) and which dependent
+variable(s) were reported. In the following, we discuss the possible
+theoretical motivation for these data analysis choices, the variation
+present in the current meta-analysis dataset, and the influence these
+analysis choices may have on measurements of mispronunciation
+sensitivity development. We focus specifically on the size of the
+mispronunciation sensitivity effect, considering the whole dataset and
+including condition (correct pronunciation, mispronunciation) as
+moderator.
 
@@
 after (post-naming phase) and is determined prior to data collection. To
-examine the size of the time window analyzed in the post-naming phase,
-we must first consider overall length of time post-naming, because it
-limits the overall time window available to analyze and might thus
-predict which time window was analyzed. Across papers, actual
-post-naming phase length varied from 2000 to 9000 ms, with a median
-value of 3500 ms. We note that the most popular actual post-naming phase
-length was 4000 ms, used in \emph{n} = 74 experimental conditions. There
-was no apparent relation between infant age and overall post-naming
-phase duration (\emph{r} = 0.01, 95\% CI{[}-0.11, 0.13{]}, \emph{p} =
-0.882).
-
-Unlike the actual post-naming phase length, the size of the post-naming
-time window analyzed can be chosen after the experimental data is
-collected. Interestingly, half of the experimental conditions were
-analyzed using the same length of post-naming phase as the infant heard
-in the actual experiment (124), while the other half were analyzed using
-a shorter portion of the post-naming phase, usually excluding later
-portions (127). Across papers, the length of the post-naming phase
-analyzed varied from 1510 to 4000 ms, with a median value of 2500 ms. We
-note that the most popular actual post-naming phase length was 2000 ms,
-used in \emph{n} = 97 experimental conditions. There was an inverse
-relationship between infant age and the size of the post-naming time
-window analyzed, such that younger infants' looking times were analyzed
-using a longer post-naming time window, here the relationship was
-significant (\emph{r} = -0.23, 95\% CI{[}-0.35, -0.11{]}, \emph{p}
-\textless{} .001). The choice to analyze a shorter post-naming time
-window is likely related to evidence that speed of processing is slower
-in younger infants (Fernald et al., 1998). To summarize, we observe
-variation in time-related aspects related to infants' age.
-
-{[}Christina: Below there is a \ldots{}. Just so we don't forget
-it.{]}{[}Katie: I put it in there on purpose, I'm quoting directly from
-the paper, but the original sentence doesn't make full sense in this
-context, so I cut out the part that doesn't fit. This is the original
-sentence: \enquote{The lower bound of 367 ms is an `educated guess'
-based on studies such as those cited above, and our data (here and in
-other studies) showing that target and distractor fixations tend to
-diverge at around 400 ms.}{]}
+examine the size of the time window analyzed in the post-naming phase
+(post-naming analysis window), we must first consider overall length of
+time in post-naming (post-naming time window), because it limits the
+overall time window available to analyze and might thus predict the
+post-naming analysis window. Across papers, the length of the
+post-naming time window varied from 2000 to 9000 ms, with a median value
+of 3500 ms. The most popular post-naming time window length was 4000 ms,
+used in 74 experimental conditions. There was no apparent relation
+between infant age and post-naming time window length (\emph{r} = 0.01,
+95\% CI{[}-0.11, 0.13{]}, \emph{p} = 0.882).
+
+Unlike the post-naming time window, the post-naming analysis window can
+be chosen after the experimental data is collected. Interestingly, half
+of the experimental conditions were analyzed using the whole post-naming
+time window of the trial presented to the infant (\emph{n} = 124), while
+the other half were analyzed using a shorter portion of the post-naming
+time window, usually excluding later portions (\emph{n} = 127). Across
+papers, the length of the post-naming analysis window varied from 1510
+to 4000 ms, with a median value of 2500 ms. The most popular post-naming
+analysis window length was 2000 ms, used in 97 experimental conditions.
+There was an inverse relationship between infant age and post-naming
+analysis window length, such that younger infants' looking times were
+analyzed using a longer post-naming analysis window, here the
+relationship was significant (\emph{r} = -0.23, 95\% CI{[}-0.35,
+-0.11{]}, \emph{p} \textless{} .001). The choice to use a shorter
+post-naming analysis window with age is likely related to evidence that
+speed of processing is slower in younger infants (Fernald et al., 1998).
+To summarize, we observe variation in time-related analysis decisions
+related to infants' age.
 
@@
 \enquote{educated guess} based on studies . . . showing that target and
-distractor fixations tend to diverge at around 400 ms.} (Swingley \&
-Aslin, 2000, p.~155). Upon inspecting the offset time values used in the
-papers in our meta-analysis, the majority used a similar offset time
+distractor fixations tend to diverge at around 400 ms.} ((Swingley \&
+Aslin, 2000, p. 155)). Upon inspecting the offset time values used in
+the papers in our meta-analysis, the majority used a similar offset time
 value (between 360 and 370 ms) for analysis (\emph{n} = 151), but offset
@@
 such that younger infants were given longer offsets, although this
-correlation was not significant (\emph{r} = -0.10, \emph{p} = 0.13).
-This lack of a relationship is possibly driven by the field's consensus
-that an offset of about 367 ms is appropriate for analyzing word
-recognition with PTL measures, including studies that evaluate
-mispronunciation sensitivity.
-
-Although there are a priori reasons to choose the post-naming time
+correlation was not significant (\emph{r} = -0.10, 95\% CI{[}-0.23,
+0.03{]}, \emph{p} = 0.13). This lack of a relationship is possibly
+driven by the field's consensus that an offset of about 367 ms is
+appropriate for analyzing word recognition with PTL measures, including
+studies that evaluate mispronunciation sensitivity.
+
+Although there are a priori reasons to choose the post-naming analysis
 window (infant age) or offset time (previous studies), these choices may
@@
 were systematically different across infant ages, at least for the
-post-naming time window analyzed, we next explored whether the size of
-time window analyzed or the offset time influenced sensitivity to
-mispronunciations.
-
-\paragraph{Size of post-naming time window
-analyzed}\label{size-of-post-naming-time-window-analyzed}
-
-We first assessed whether size of the post-naming time window analyzed
-had an impact on the overall size of the reported mispronunciation
-sensitivity. We considered data from both conditions in a joint analysis
-and included condition (correct pronunciation, mispronunciation) as an
-additional moderator. The moderator test was significant (QM(3) =
-236.958, \emph{p} \textless{} .001). The estimate for the interaction
-between post-naming phase size and condition was small but significant
-(\(\beta\) = -0.262, SE = 0.059, 95\% CI{[}-0.377, -0.148{]}, \emph{p}
-\textless{} .001). This relationship is plotted in Figure 3a. The
-results suggest that the size of the post-naming phase analyzed
-significantly impacted mispronunciation sensitivity. Specifically, the
+post-naming analysis window, we next explored whether the post-naming
+analysis window length or the offset time influenced our estimate of
+infants' sensitivity to mispronunciations.
+
+\paragraph{Post-naming analysis window
+length}\label{post-naming-analysis-window-length}
+
+We first assessed whether size of the post-naming analysis window had an
+impact on the overall size of the reported mispronunciation sensitivity.
+We considered data from both conditions in a joint analysis and included
+condition (correct pronunciation, mispronunciation) as an additional
+moderator. The moderator test was significant (QM(3) = 236.958, \emph{p}
+\textless{} .001). The estimate for the interaction between post-naming
+analysis window and condition was small but significant (\(\beta\) =
+-0.262, SE = 0.059, 95\% CI{[}-0.377, -0.148{]}, \emph{p} \textless{}
+.001). This relationship is plotted in Figure 3a. The results suggest
+that the size of the post-naming analysis window significantly impacted
+our estimate of mispronunciation sensitivity. Specifically, the
 difference between target fixations for correctly pronounced and
 mispronounced items (mispronunciation sensitivity) was significantly
-greater when the post-naming phase was shorter.
+greater when the post-naming analysis window was shorter.
 
 Considering that we found a significant relationship between the length
-of the post-naming time window analyzed and infant age, such that
-younger ages had a longer window of analysis, we next examined whether
-the size of post-naming time window analyzed modulated the estimated
-size of mispronunciation sensitivity as infant age changed. We therefore
+of the post-naming analysis window and infant age, such that younger
+ages had a longer window of analysis, we next examined whether the size
+of the post-naming analysis window modulated the estimated size of
+mispronunciation sensitivity as infant age changed. We therefore
 included age as additional moderator of the previous analysis. The
@@
 .001). The estimate for the three-way-interaction between condition,
-size of post-naming phase, and age was small, but significant (\(\beta\)
-= = -0.04, SE = 0.014, 95\% CI{[}-0.068, -0.012{]}, \emph{p} = 0.006).
-As can be seen in Figure 3b, smaller post-naming time window size leads
-to greater increases in measured mispronunciation sensitivity with
-development. For example, when experimental conditions were analyzed
-with a post-naming time window of 2000 ms or less, mispronunciation
-sensitivity is found to increase with infant age. If the post-naming
-time window analyzed is greater than 2000 ms, however, there is no or a
-negative relation of mispronunciation sensitivity and age. In other
-words, all three possible developmental hypotheses might be supported
-depending on analysis choices made regarding the size of the post-naming
-time window to analyze. This is especially important, considering that
-our key question is how mispronunciation sensitivity changes with
+size of the post-naming analysis window, and age was small, but
+significant (\(\beta\) = -0.04, SE = 0.014, 95\% CI{[}-0.068, -0.012{]},
+\emph{p} = 0.006). As can be seen in Figure 3b, a smaller post-naming
+analysis window leads to a greater increase in measured mispronunciation
+sensitivity with development. For example, when experimental conditions
+were analyzed with a post-naming analysis window of 2000 ms or less,
+mispronunciation sensitivity seems to increase with infant age. If the
+post-naming analysis window is greater than 2000 ms, however, there is
+no or a negative relation of mispronunciation sensitivity and age. In
+other words, all three possible developmental hypotheses might be
+supported depending on analysis choices made regarding the size of the
+post-naming analysis window. This is especially important, considering
+that our key question is how mispronunciation sensitivity changes with
 development. These results suggest that conclusions about the
 relationship between infant age and mispronunciation sensitivity may be
-mediated by the size of the post-naming time window analyzed.
+mediated by the size of the post-naming analysis window.
 
@@
 \caption{(\#fig:Plot\_post\_name\_cond\_age)Effect sizes for the
-different lengths of post-naming phase time windows analyzed: 2000 ms or
-less (orange), 2001 to 3000 ms (blue), and 3001 ms or greater (green).
-Although length of post-naming phase time window analyzed was included
-as a continuous variable in the meta-analytic model, it is divided into
+different lengths of the post-naming analysis window: 2000 ms or less
+(orange), 2001 to 3000 ms (blue), and 3001 ms or greater (green).
+Although length of the post-naming analysis window was included as a
+continuous variable in the meta-analytic model, it is divided into
 categories for ease of viewing. Panel a plots mispronunciation
@@
 
-We next assessed whether the time between the target was named and the
-start of the analysis, namely offset time, had an impact on the size of
-the reported mispronunciation sensitivity. When we included both
-condition and offset time as moderators, the moderator test was
-significant (QM(3) = 236.958, \emph{p} \textless{} .001), but the
-estimate for the interaction between offset time and condition was
-almost zero (\(\beta\) = 0, SE = 0, 95\% CI{[}-0.001, 0{]}, \emph{p} =
-0.505). Although we found no relationship between offset time and infant
-age, we also examined whether the size of offset time modulated the the
-measure of mispronunciation sensitivity over infant age. When both
-offset time and condition were included as moderators, the moderator
-test was significant (QM(7) = 200.867, \emph{p} \textless{} .001), but
-the three-way-interaction between condition, offset time, and age was
-very small and not significant (\(\beta\) = = 0, SE = 0, 95\% CI{[}0,
-0{]}, \emph{p} = 0.605. Taken together, these results suggest that
-offset time does not modulate measured mispronunciation sensitivity.
-There is no relationship between offset time and age, and we find no
-influence of offset time on the estimated size of mispronunciation
-sensitivity over age.
+We next assessed whether the time between target naming and the start of
+the analysis, namely offset time, had an impact on the size of the
+reported mispronunciation sensitivity. When we included both condition
+and offset time as moderators, the moderator test was significant (QM(3)
+= 236.958, \emph{p} \textless{} .001), but the estimate for the
+interaction between offset time and condition was zero (\(\beta\) = 0,
+SE = 0, 95\% CI{[}-0.001, 0{]}, \emph{p} = 0.505). Although we found no
+relationship between offset time and infant age, we also examined
+whether the size of offset time modulated the measure of
+mispronunciation sensitivity over infant age. When both offset time and
+condition were included as moderators, the moderator test was
+significant (QM(7) = 200.867, \emph{p} \textless{} .001), but the
+three-way-interaction between condition, offset time, and age was again
+zero (\(\beta\) = 0, SE = 0, 95\% CI{[}0, 0{]}, \emph{p} = 0.605. Taken
+together, these results suggest that offset time does not modulate
+measured mispronunciation sensitivity. There is no relationship between
+offset time and age, and we find no influence of offset time on the
+estimated size of mispronunciation sensitivity over age. We again point
+out that there is a substantial field consensus, which might mask any
+relationship.
 
@@
 (PTL) in response to correct and mispronounced words. Experiments
-typically include a phase where no naming event has occured, whether
+typically include a phase where no naming event has occurred, whether
 correctly pronounced or mispronounced, which we refer to as the
@@
 another, in that they are calculated on the same type of data and
-consider pre-naming preferences. {[}Christina: adding sth here{]}. It
-should be noted, however, that the Difference Score can better counter
-act participant- and item-level differences, whereas Pre vs.~Post is a
-group-level measure. The Post dependent variable, in contrast, does not
-consider pre-naming baseline preferences. To our knowledge, there is no
-theory or evidence that explicitly drives choice of dependent variable
-in analysis of mispronunciation sensitivity, which may explain the wide
-variation in dependent variable reported in the papers included in this
+consider pre-naming preferences. It should be noted, however, that the
+Difference Score can better counteract participant- and item-level
+differences, whereas Pre vs.~Post is a group-level measure. The Post
+dependent variable, in contrast, does not consider pre-naming baseline
+preferences. To our knowledge, there is no theory or evidence that
+explicitly drives choice of dependent variable in analysis of
+mispronunciation sensitivity, which may explain the wide variation in
+dependent variable reported in the papers included in this
 meta-analysis. We next explored whether the type of dependent variable
@@
 We next examined whether the type of dependent variable calculated
-modulated the the estimated change in mispronunciation sensitivity over
+modulated the estimated change in mispronunciation sensitivity over
 infant age. When age was included as an additional moderator, the
@@
 
-Similar to size of post-naming time window analyzed, all three possible
-developmental hypotheses might be supported depending on the dependent
-variable reported. In other words, choice of dependent variable may
-influence the conclusion drawn regarding how mispronunciation
-sensitivity may change with infant age.
+Similar to the length of the post-naming analysis window, all three
+possible developmental hypotheses might be supported depending on the
+dependent variable reported. In other words, choice of dependent
+variable may influence the conclusion drawn regarding how
+mispronunciation sensitivity may change with infant age.
 
@@
 
+In this meta-analysis, we set out to quantify and assess the
+developmental trajectory of infants' sensitivity to mispronunciations.
 Overall, the results of the meta-analysis showed that infants reliably
 fixate the target object when given both correctly pronounced and
-mispronounced labels. In other words, not only did infants recognize
-object labels when they were correctly pronounced, they also were likely
-to accept mispronunciations as acceptable labels for targets.
-Mispronounced labels were considered a better match for target images
-than a distractor image, despite the differences in the phonological
-form of correctly pronounced and mispronounced words. Nonetheless, there
-was a considerable difference in target fixations in response to
-correctly pronounced and mispronounced labels, suggesting overall
-mispronunciation sensitivity in the current experimental literature. In
-short, infants show knowledge of what constitutes unacceptable variation
-in word forms, displaying knowledge of the role of phonemic changes
-throughout the ages assessed here. At the same time, infants, like
-adults, can recover from mispronunciations.
+mispronounced labels. Infants not only recognize object labels when they
+were correctly pronounced, but are also likely to accept
+mispronunciations as acceptable labels for targets, in the presence of a
+distractor image. Nonetheless, there was a considerable difference in
+target fixations in response to correctly pronounced and mispronounced
+labels, suggesting that infants show an overall mispronunciation
+sensitivity based on the current experimental literature. In other
+words, infants show sensitivity to what constitutes unacceptable,
+possibly meaning-altering variation in word forms, thereby displaying
+knowledge of the role of phonemic changes throughout the ages assessed
+here (6 to 30 months). At the same time, infants, like adults, can
+recover from mispronunciations, a key skill in language processing.
 
@@
 theories identified in our literature review, neither the Perceptual
-Attunement account (Best 1994, 1995) nor PRIMIR (Curtin \& Werker, 2007;
-Werker \& Curtin, 2005) account for a lack of developmental change. The
-results of our meta-analysis are supported by a handful of studies
-directly comparing infants over a range of ages (Swingley \& Aslin,
-2000; Bailey \& Plunkett, 2002; Zesiger et al., 2012), which also found
-no developmental change in mispronunciation sensitivity.
-
-Both the Perceptual Attunement (Best 1994, 1995) and PRIMIR (Curtin \&
-Werker, 2007; Werker \& Curtin, 2005) accounts link a change of
-mispronunciation sensitivity specifically with vocabulary growth, in
-comparison to development in general. Vocabulary growth leads to an
-increase (PRIMIR; Curtin \& Werker, 2007; Werker \& Curtin, 2005) or
-decrease (Perceptual Attunement; Best 1994, 1995) in mispronunciation
-sensitivity and vocabulary is expected to grow considerably in the age
-range considered in the current meta-analysis (see
-wordbank.stanford.edu; Frank et al., 2017). The lack of developmental
-effects found in our meta-analysis may therefore be due to using age,
-instead of vocabulary growth, as a facilitator for change in
-mispronunciation sensitivity. Yet, an analysis of correlations between
-vocabulary size and object recognition effect sizes does not support
-this argument. Although an increasing vocabulary size lead to increased
-object recognition for correctly pronounced words, this was not the case
-for mispronunciations. Some previous experimental evidence also supports
-a lack of a relationship between vocabulary size and mispronunciation
-sensitivity (e.g.~Mani \& Plunkett, 2007; Swingley \& Aslin, 2000; Tao
-et al., 2012; but see Mani \& Plunkett, 2010). This would suggest that
-object recognition for mispronunciations is not modulated by vocabulary
-size, contrary to the predictions of the Perceptual Attunement (Best
-1994, 1995) and PRIMIR (Curtin \& Werker, 2007; Werker \& Curtin, 2005)
-accounts and further supporting the overall lack of an influence of age
-on mispronunciation sensitivity.
+Attunement account (Best, 1994, 1995) nor PRIMIR (Curtin \& Werker,
+2007; Curtin et al., 2011; Werker \& Curtin, 2005) account for a lack of
+developmental change. The results of our meta-analysis are supported by
+a handful of studies directly comparing infants over a range of ages
+(Bailey \& Plunkett, 2002; Swingley \& Aslin, 2000; Zesiger et al.,
+2012), which also found no developmental change in mispronunciation
+sensitivity.
+
+Both the Perceptual Attunement (Best, 1994, 1995) and PRIMIR (Curtin \&
+Werker, 2007; Curtin et al., 2011; Werker \& Curtin, 2005) accounts link
+a change of mispronunciation sensitivity specifically with vocabulary
+growth, in comparison to development in general. Vocabulary growth is
+predicted to lead either to an increase ((PRIMIR; Curtin \& Werker,
+2007; Curtin et al., 2011; Werker \& Curtin, 2005)) or a decrease
+((Perceptual Attunement; Best, 1994, 1995)) in mispronunciation
+sensitivity; vocabulary has been shown to grow considerably in the age
+range considered in the current meta-analysis ((see
+\url{http://wordbank.stanford.edu}; Frank, Braginsky, Yurovsky, \&
+Marchman, 2017)). However, there are also substantial individual
+differences in the trajectory of vocabulary growth. The lack of
+developmental effects found in our meta-analysis may therefore be due to
+using age, instead of vocabulary size, as a facilitator for change in
+mispronunciation sensitivity. Yet, an analysis of the subset of studies
+reporting correlations between vocabulary size and object recognition
+effect sizes does not support this argument. Although an increasing
+vocabulary size lead to increased object recognition for correctly
+pronounced words, this was not the case for mispronunciations. Without
+evidence of a relationship between vocabulary size and mispronunciation
+object recognition and in combination with the low-powered analysis, it
+is difficult to draw a conclusion regarding the role of an increasing
+vocabulary size in mispronunciation sensitivity. In any case, this lack
+of evidence is contrary to the predictions of the Perceptual Attunement
+(Best, 1994, 1995) and PRIMIR (Curtin \& Werker, 2007; Curtin et al.,
+2011; Werker \& Curtin, 2005) accounts and further supports the overall
+lack of evidence for a developmental change.
+
+{[}Katie: Above has been edited to acknowledge that we can't measure
+mispronunciation sensitivity in the vocabulary correlations. Christina,
+can you read through it?{]}
 
@@
 while simultaneously holding correctly pronounced and mispronounced
-labels as separate (mispronunciation sensitivity) may indcate an
+labels as separate (mispronunciation sensitivity) may indicate an
 abstract understanding of words' phonological structure. It appears that
-young infants may understand that the mispronunciation and correct
-pronunciation's phonological form do not match (phonological
+young infants may understand that the phonological form of
+mispronunciations and correct pronunciations do not match (phonological
 distinctiveness), but that the mispronunciation is a better label for
@@
 phonological distinctiveness at an age earlier than previously thought,
-which we recommend should be taken into account by future theoretical
-accounts.
-
-Although the lack of an relationship between mispronunciation
-sensitivity and vocabulary size may reflect a true effect, we note that
-this may also be the result of an underpowered analysis. Despite the
-theoretical implications, less than half of the papers included in this
+which we recommend should be further explored experimentally and taken
+into consideration by future theoretical accounts.
+
+Although the lack of a relationship between mispronunciation sensitivity
+and vocabulary size may reflect a true effect, we note that this may
+also be the result of an underpowered analysis. Despite the theoretical
+implications, fewer than half of the papers included in this
 meta-analysis measured vocabulary (\emph{n} = 13; out of 32 papers
-total). We suggest that this may be the result of publication bias,
-specifically a desire to not publish null results. Although the number
-of mispronunciation sensitivity studies per year has seen an increase,
-this has not translated to an increasing number of mispronunciation
-sensitivity studies also measuring vocabulary scores.
-
-{[}Katie{]} The above paragraph is a bit clunky and I don't like it. Any
-suggestions for improvement?
+total; see also Figure 4). There are more mispronunciation sensitivity
+studies published every year, perhaps due to the increased use of
+eye-tracker which reduce the need for offline coding, but this has not
+translated to an increasing number of mispronunciation sensitivity
+studies also measuring vocabulary scores. We suggest that this may be
+the result of publication bias favoring significant effects or an
+overall hesitation to invest in data collection that is not expected to
+yield significant outcomes.
 
@@
 handful of variables that relate to data analysis, specifically relating
-to timing (size of time window analyzed; offset time) and which
-dependent variable(s) were reported. We focused on these variables in
-particular because their choice can potentially be made after
-researchers have examined the data, leading to an inflated increase of
-significant results which may also explain the publication bias observed
-in the funnel plot assymmetry (Simmons, Nelson, \& Simonsohn, 2011). To
-explore whether this variation contributed to the lack of developmental
-change observed in the overall meta-analysis, we included these
-variables as moderators in a set of exploratory analyses. We noted an
-interesting pattern of results, specifically that different conclusions
-about mispronunciation sensitivity, but more notably mispronunciation
-sensitivity development, could be drawn depending on the length of the
-post-naming time window analyzed as well as the type of dependent
-variable calculated in the experiment.
-
-{[}Christina{]} It's a good start, let's see where we go from here. I
-jotted down some possible conclusions
-
-Infants are expected to recognize words more quickly with age (Fernald,
-Swingley \& Pinto, 2001; Swingley, Pinto \& Fernald, 1999; Swingley \&
-Fernald, 2002). This evidence has often guided decisions for the
-post-naming time window to be analyzed in mispronunciation sensitivity
-studies, including where to begin the time window (offset time) and how
-long this window should be (post-naming time window analyzed).
-Specifically, increasing age should lead to quicker reaction times, and
-therefore lower offset times. Yet, we found no evidence for a
-relationship between offset time and infant age nor that offset time
-modulated mispronunciation sensitivity. Indeed, a large majority used an
-offset time between 360 and 370 ms, which follows the best guess of
-Swingley and Aslin (2000) for the amount of time needed for infants to
-initiate eye movements in response to a spoken target word.
-
-In contrast, the length of the post-naming window analyzed was related
-to infant age and also found to modulate mispronunciation sensitivity.
-Younger infants may take longer to reliably identify the target image,
-and as a result the length of the post-naming time window analyzed may
-be longer in younger infants. This was born out in the meta-analysis:
-studies that tested younger infants used a longer post-naming time
-window. Longer post-naming time windows, however, resulted in a smaller
-effect size for mispronunciation sensitivity. Critically, the
-developmental trajectory of mispronunciation sensitivity changed
-depending on the length of the post-naming time window analyzed. Longer
-time windows resulted in decreasing or no change in mispronunciation
-sensitivity, while shorter time windows resulting in increasing
-mispronunciation sensitivity. Given a set of mispronunciation
-sensitivity data, a conclusion regarding the development of
-mispronunciation sensitivity would be different depending on the length
-of the post-naming time window analyzed.
-
-Unlike the timing variables, the origin of a potential relationship
-between the type of dependent variable calculated and mispronunciation
-sensitivity is much less clear. The majority of studies created a
-Difference Score, subtracting pre-naming phase PTL from that of
-post-naming phase PTL, while the remaining studies compared pre-naming
-PTL with post-naming PTL (Pre vs.~Post) or analyzed post-naming PTL
-alone (Post). Both the Difference Score and the Pre vs.~Post dependent
-variables consider pre-naming phase baseline preferences for the target
-compared to distractor image, but were found to differentially modulate
-mispronunciation sensitivity. There was no difference in
-mispronunciation sensitivity between the Post and Difference Score
-dependent variables, but in comparison to Post, studies that reported
-the Pre vs.~Post dependent variable had lower effect sizes for
-mispronunciation sensitivity. Furthermore, studies reporting the Pre
-vs.~Post dependent variable showed decreasing mispronunciation
-sensitivity with age, while studies reporting a Difference Score or Post
-dependent variable showed an increase. Similar to the length of the
-post-naming time window analyzed, given a set of mispronunciation
-sensitivity data, a conclusion regarding the development of
-mispronunciation sensitivity would be different depending on the choice
-of dependent variable.
-
-A lack of a field standards can have dire consequences, as our analyses
-show. Depending on which analysis time window (see Figure 5) or
+to timing (post-naming analysis window; offset time) and to the
+calculation of the dependent variable reported. We focused on these
+variables in particular because their choice can potentially be made
+after researchers have examined the data, leading to an inflated number
+of significant results which may also explain the publication bias
+observed in the funnel plot asymmetry analyses (Simmons et al., 2011).
+To explore whether this variation contributed to the lack of
+developmental change observed in the overall meta-analysis, we included
+these variables as moderators in a set of exploratory analyses. We noted
+an interesting pattern of results, specifically that different
+conclusions about mispronunciation sensitivity, but more notably
+mispronunciation sensitivity development, could be drawn depending on
+the length of the post-naming analysis window as well as the type of
+dependent variable calculated in the experiment (see Figures 5 and 6).
+
+Infants are expected to recognize words more quickly with age (Fernald
+et al., 1998). This evidence has often guided decisions for the
+post-naming time window in mispronunciation sensitivity studies,
+including where to begin the time window (offset time) and how long this
+analysis window should be (post-naming analysis window). Specifically,
+increasing age should lead to quicker reaction times, and therefore
+lower offset times. Yet, we found no evidence for a relationship between
+offset time and infant age nor that offset time modulated
+mispronunciation sensitivity. Indeed, a majority of studies used an
+offset time between 360 and 370 ms, which follows the \enquote{best
+guess} of Swingley and Aslin (2000) for the amount of time needed for
+infants to initiate eye movements in response to a spoken target word.
+
+In contrast, both the length of the post-naming analysis window and the
+type of dependent variable calculated modulated mispronunciation
+sensitivity. Most critically, however, variation in these variables
+resulted in changes to the developmental trajectory of mispronunciation
+sensitivity. Given a set of mispronunciation sensitivity data, a
+conclusion regarding the development of mispronunciation sensitivity
+would be different depending on the length of the post-naming analysis
+window or the choice of dependent variable.
+
+\subsection{Recommendations to Establish Analysis
+Standards}\label{recommendations-to-establish-analysis-standards}
+
+A lack of a field standard can have serious consequences, as our
+analyses show. Depending on which analysis time window (see Figure 5) or
 dependent variable (see Figure 6) we focus on, we find support for any
 of the three possible trajectories of mispronunciation sensitivity. On
-the one hand, this limits the conclusions we can draw. Without access to
-the full datasets or analysis code of the studies included in this
-meta-analysis, it is difficult to pinpoint the exact role played by
-these data analysis choices. On the other hand, this finding emphasizes
-that current practices of free, potentially ad hoc choices regarding
-data analyses are not sustainable if the field wants to move towards
-quantitative evidence for theories of language development.
-
-We take this opportunity to suggest several remedies. Preregistration
-can serve as proof of a priori decisions regarding data analysis or
-describing how data analysis decisions will be made once data is
-collected. The peer reviewed form of Registered Reports has already been
-adopted by a large number of developmental journals, and general
-journals that publish developmental works, showing the field's
-increasing acceptance of such practices. Open data can allow others to
-re-analyze existing datasets to both examine the impact of analysis
-decisions and cumulatively analyze different datasets in the same way.
-Furthermore, experimenters can analyze the time course as a whole,
-instead of aggregating the proportion of target looking behavior over
-the entire trial. This allows for a more detailed assessment of infants'
-fixations over time and reduces the need to reduce the time window of
-the post-naming phase for analysis. Both Growth Curve Analysis (Mirman
-et al., 2008; Law \& Edwards, 2015) and Permutation Clusters Analysis
-(Maris \& Oostenveld, 2007; Von Holzen \& Mani, 2012; Delle Luche et
-al., 2015) offer potential solutions to analyze the full time course. In
-general, however, it may be useful to establish standard analysis
-pipelines for mispronunciation studies. This would allow for a more
-uniform analysis of this phenomenon, as well as aid experimenters in
-future research planning.
-
-{[}Christina: Are we submitting to a place with registered reports? We
-should!{]}{[}Katie: We had been aiming for Cognition, but it doesn't
-have registered reports. But, Dev Sci does, although we're about 3,000
-words above their word limit (Cognition doesn't have a word limit).{]}
-
-{[}Katie: this is a good paragraph, but I'm not sure where it fits. Its
-rather not specific for our current meta-analysis, but a general comment
-about the field.{]}
-
-When it comes to designing studies, best practices and current standards
-might not always overlap. Indeed, across a set of previous meta-analyses
-it was shown that particularly infant research does not adjust sample
-sizes according to the effect in question (Bergmann et al., 2018). A
-meta-analysis is a first step in improving experiment planning by
-measuring the underlying effect and its variance, which is directly
-related to the sample needed to achieve satisfactory power in the null
-hypothesis significance testing framework. Failing to take effect sizes
-into account can both yield to underpowered research and to testing too
-many participants, both consequences are undesirable for a number of
-reasons that have been discussed in depth elsewhere. We will just
-briefly mention two that we consider most salient for theory building:
-Underpowered studies will lead to false negatives more frequently than
-expected, which in turn results in an unpublished body of literature
-(citationcitation). Overpowered studies mean that participants were
-tested unnecessarily, which has substantial ethical consequences
-particularly when working with infants and other difficult to recruit
-and test populations.
-
-{[}Katie: I am not sure where to talk about this, or actually how to
-talk about this.{]} For example, the Difference Score dependent variable
-substracts the pre-naming phase PTL from the post-naming phase PTL. Some
-studies compute this variable on the level of condition (e.g.~White \&
-Morgan, 2008), but this reduces SOMETHING, WHICH IS A BAD SOMETHING.
+the one hand, this limits the conclusions we can draw regarding our key
+research question. Without access to the full datasets or analysis code
+of the studies included in this meta-analysis, it is difficult to
+pinpoint the exact role played by these data analysis choices. On the
+other hand, this finding emphasizes that current practices of free,
+potentially ad hoc choices regarding data analyses are not sustainable
+if the field wants to move towards quantitative evidence for theories of
+language development.
+
+We take this opportunity to suggest several solutions. Preregistration
+can serve as proof of a priori decisions regarding data analysis, which
+can also contain a data-dependent description of how data analysis
+decisions will be made once data is collected. The peer reviewed form of
+preregistration, termed Registered Reports, has already been adopted by
+a large number of developmental journals, and general journals that
+publish developmental works, showing the field's increasing acceptance
+of such practices for hypothesis-testing studies. Sharing data (Open
+Data) can allow others to re-analyze existing datasets to both examine
+the impact of analysis decisions and cumulatively analyze different
+datasets in the same way. Experimenters can also opt to analyze the time
+course as a whole, instead of aggregating the proportion of target
+looking behavior over the entire trial. This allows for a more detailed
+assessment of infants' fixations over time and reduces the need to
+reduce the post-naming analysis window. Both Growth Curve Analysis (Law
+II \& Edwards, 2015; Mirman, Dixon, \& Magnuson, 2008) and Permutation
+Clusters Analysis (Delle Luche, Durrant, Poltrock, \& Floccia, 2015;
+Maris \& Oostenveld, 2007; Von Holzen \& Mani, 2012) offer potential
+solutions to analyze the full time course. Furthermore, it may be useful
+to establish standard analysis pipelines for mispronunciation studies.
+This would allow for a more uniform analysis of this phenomenon, as well
+as aid experimenters in future research planning. In general, however, a
+better understanding of how different levels of linguistic knowledge may
+drive looking behavior is needed. We hope this understanding can be
+achieved by applying the above suggestions.
+
+Another aspect of study design, namely sample size planning, shows that
+best practices and current standards might not always overlap. Indeed,
+across a set of previous meta-analyses it was shown that particularly
+infant research does not adjust sample sizes according to the effect in
+question (Bergmann et al., 2018). A meta-analysis is a first step in
+improving experiment planning by providing an estimate of the population
+effect and its variance, which is directly related to the sample needed
+to achieve satisfactory power in the null hypothesis significance
+testing framework. Failing to take effect sizes into account can both
+lead to underpowered research and to testing too many participants, both
+consequences are undesirable for a number of reasons that have been
+discussed in depth elsewhere. We will just briefly mention two that we
+consider most salient for theory building: Underpowered studies will
+lead to false negatives more frequently than expected, which in turn
+results in an unpublished body of literature (citationcitation). At the
+same time, underpowered studies with significant outcomes are likely to
+overestimate the effect, leading to wrong estimations of the population
+effect when paired with publication bias (citation). Overpowered studies
+mean that participants were tested unnecessarily, which has ethical
+implications particularly when working with infants and other difficult
+to recruit and test populations.
+
+{[}From Christina's comment: Christina needs to add citations here{]}
+
+The estimated effect for mispronunciation sensitivity in this
+meta-analysis is 0.50, and the most frequently observed sample size is
+24 participants. If we were to assume that researchers assess
+mispronunciation sensitivity in a simple ANOVA, the resulting power is
+0.92. Reversely, to achieve 80\% power, one would need to test 17
+participants. These calculations suggest that for the comparison of
+responses for correct pronunciations and mispronunciations, the studies
+included in this meta-analysis contain well-powered analyses. However,
+many studies in this meta-analysis included further factors to be
+tested, leading to two-way interactions (age versus mispronunciation
+sensitivity is a common example), which will require even larger sample
+sizes. We thus strongly advocate for a consideration of power and the
+reported effect sizes to test infants' mispronunciation sensitivity.
+
+{[}From Christina's comment: I want to do the math for more complex
+designs in pangea, i'll try to remember, if not, poke me
+\url{https://jakewestfall.shinyapps.io/pangea/} {]}
 
@@
 mispronunciation sensitivity, but we note that these studies varied in
-their approach to study mispronunciation sensitivity. For example, some
+their approach to study our phenomenon of interest. For example, some
 studies investigated specific questions which required additional
 manipulations, such as the impact of the number of phonological features
-changed in the mispronunciations on mispronunciation sensitivity
-(e.g.~White \& Morgan, 2008; Mani \& Plunkett, 2011) or sensitivity to
-consonant and vowel mispronunciations (Mani \& Plunkett, 2007; 2010 keps
-and tups; Hojen et al., unpublished; Swingley, 2016). These studies
-varied in their experimental design, such as whether infants were
-familiar with the distractor image (e.g.~White and Morgan (2008; see
-also Mani \& Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) or
-whether the labels for the target and distractor images contained
-phonological overlap (Fernald, Swingley, \& Pinto, 2001). Futhermore,
-the infants included in this meta-analysis had a variety of native
-languages (English, Spanish, French, Dutch, German, Catalan, Danish, and
-Mandarin Chinese) and language backgrounds (monolingual, bilingual,
-monodialectal, multidialectal). Taken together, these variables have the
-potential to modulate infant mispronunciation sensitivity, but an
-investigation of these variables is out of the scope of the current
-meta-analysis. However, our dataset coded for and included these
-variables. We hope that future research will be able to better
-understand the role that these variables play in infants' senstivity to
-mispronunciations.
-
-Furthermore, the investigation of mispronunciation sensitivity does not
-singularly capture infant phono-lexical development. For example,
-studies investigating word form recognition, typically using the
-Headturn Preference Procedure (Mandel et al., 1995), allow for an
-investigation of the specificity of infants' word form representations
-without requiring word-object associations, which is required in the
-Intermodal Preferential Looking Paradigm (Golinkoff et al., 1987; 2013).
-As a result, this approach can be used with infants of a much younger
-age than typically examined. These studies compare infants' preference
-to listen to word lists that a correct compared to word lists that
-contain a mispronunciation (e.g.~Bouchon et al., 2014; Swingley, 2005;
-Halle \& de Boysson-Bardies, 1996; Vihman et al., 2004; Vihman \&
-Majorano 2016; 2017; Poltrock \& Nazzi, 2015; Delle Luche et al., 2016).
-In contrast, studies investigating recognition of accented words use
-stimuli that are naturally occuring as opposed to artificially
-manipulated, to achieve an altered phonological form (e.g.~van Heughten
-et al., 2018; 2015; Buckler et al., 2017; van Heughten \& Johnson, 2014;
-2016; Best et al., 2009; Mulak et al., 2013; Schmale et al., 2010; 2012;
-Schmale \& Seidel, 2009; Floccia et al., 2012; Durrant et al., 2014;
-White \& Aslin, 2011). This allows for an evaluation of phono-lexical
-development in response to a type of language that infants may encounter
-in everyday life. These investigations offer complementary approaches to
-infant phono-lexical development.
+changed in the mispronunciations on mispronunciation sensitivity ((e.g.
+Mani \& Plunkett, 2011; White \& Morgan, 2008)) or sensitivity to
+consonant and vowel mispronunciations (Højen et al., n.d.; Mani \&
+Plunkett, 2007, 2010; Swingley, 2016). The studies in our sample
+additionally varied in their experimental design, such as whether
+infants were familiar with the distractor image ((see also Mani \&
+Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016); e.g. White \&
+Morgan, 2008) or whether the labels for the target and distractor images
+contained phonological overlap (Fernald, Swingley, \& Pinto, 2001).
+Futhermore, the infants included in this meta-analysis had a variety of
+native languages (English, Spanish, French, Dutch, German, Catalan,
+Danish, and Mandarin Chinese) and language backgrounds (monolingual,
+bilingual, monodialectal, multidialectal). Taken together, these
+variables have the potential to modulate infant mispronunciation
+sensitivity, but an investigation of these variables is out of the scope
+of the current meta-analysis. However, our dataset coded for and
+included these variables. We hope that future research will be able to
+better understand the role that these variables play in infants'
+sensitivity to mispronunciations.
+
+{[}Katie: To respond to your comment, Christina, we did include
+bilinguals. I checked and there was no influence in keeping or removing
+them.{]}
 
@@
 This meta-analysis comprises an aggregation of almost two decades of
-research on mispronunciation sensitivity, finding that although infants
-accept both corect pronunciations and mispronunciations as labels for a
-target image, they are more likely to accept correct pronunciations,
-which indcates sensitivity to mispronunciations in familiar words.
+research on mispronunciation sensitivity, finding that infants accept
+both correct pronunciations and mispronunciations as labels for a target
+image. However, they are more likely to accept correct pronunciations,
+which indicates sensitivity to mispronunciations in familiar words.
 Despite the predictions of theories of infant phono-lexical development,
 this sensitivity was not modulated by infant age or vocabulary. This
-suggests that at a young age, infants' representations for their first
-words may be already phonologically well-specified. We recommend future
-theoretical frameworks take this evidence into account.
+suggests that from a young age on, infants' word representations may be
+already phonologically well-specified. We recommend future theoretical
+frameworks take this evidence into account.
 
@@
 this evidence in mind. Ideally, future experimental design and data
-analysis would become standardized which may be aided by the growing
+analysis would become standardized which will be aided by the growing
 trend of preregistration and open science practices. Our analysis
@@
 \hypertarget{refs}{}
+\hypertarget{ref-RMarkdown}{}
+Allaire, J., Xie, Y., McPherson, J., Luraschi, J., Ushey, K., Atkins,
+A., \ldots{} Chang, W. (2018). rmarkdown: Dynamic Documents for R.
+Retrieved from \url{https://cran.r-project.org/package=rmarkdown}
+
+\hypertarget{ref-Altvater2010}{}
+Altvater-Mackensen, N. (2010). \emph{Do manners matter? Asymmetries in
+the acquisition of manner of articulation features.} (PhD thesis).
+Radboud University Nijmegen.
+
+\hypertarget{ref-Altvater2014}{}
+Altvater-Mackensen, N., Feest, S. V. H. van der, \& Fikkert, P. (2014).
+Asymmetries in early word recognition: The case of stops and fricatives.
+\emph{Language Learning and Development}, \emph{10}(2), 149--178.
+doi:\href{https://doi.org/10.1080/15475441.2013.808954}{10.1080/15475441.2013.808954}
+
+\hypertarget{ref-papaja}{}
+Aust, F., \& Barth, M. (2018). papaja: Prepare reproducible APA journal
+articles with R Markdown. Retrieved from
+\url{https://github.com/crsh/papaja}
+
+\hypertarget{ref-Bailey2002}{}
+Bailey, T. M., \& Plunkett, K. (2002). Phonological specificity in early
+words. \emph{Cognitive Development}, \emph{17}(2), 1265--1282.
+doi:\href{https://doi.org/10.1016/S0885-2014(02)00116-8}{10.1016/S0885-2014(02)00116-8}
+
+\hypertarget{ref-Ballem2005}{}
+Ballem, K. D., \& Plunkett, K. (2005). Phonological specificity in
+children at 1;2. \emph{Journal of Child Language}, \emph{32}(1),
+159--173.
+doi:\href{https://doi.org/10.1017/S0305000904006567}{10.1017/S0305000904006567}
+
+\hypertarget{ref-Barton1980}{}
+Barton, D., Miller, R., \& Macken, M. (1980). Do children treat clusters
+as one unit or two? In \emph{Papers and reports on child language
+development} (pp. 93--137).
+
+\hypertarget{ref-Bergelson2017}{}
+Bergelson, E., \& Swingley, D. (2017). Young infants ' word
+comprehension given an unfamiliar talker or altered pronunciations.
+\emph{Child Development}.
+doi:\href{https://doi.org/10.1111/cdev.12888}{10.1111/cdev.12888}
+
+\hypertarget{ref-Bergmann2018}{}
+Bergmann, C., Tsuji, S., Piccinini, P. E., Lewis, M. L., Braginsky, M.,
+Frank, M. C., \& Cristia, A. (2018). Promoting replicability in
+developmental research through meta-analyses: Insights from language
+acquisition research. \emph{Child Development}.
+doi:\href{https://doi.org/10.17605/OSF.IO/3UBNC}{10.17605/OSF.IO/3UBNC}
+
+\hypertarget{ref-Best1994}{}
+Best, C. T. (1994). \emph{The emergence of native-language phonological
+influences in infants: A perceptual assimilation model} (Vol. 107/108,
+pp. 1--30).
+
+\hypertarget{ref-Best1995}{}
+Best, C. T. (1995). A direct realist view of cross-language speech
+perception.
+
+\hypertarget{ref-Best2009}{}
+Best, C. T., Tyler, M. D., Gooding, T. N., Orlando, C. B., \& Quann, C.
+A. (2009). Development of phonological constancy: Toddlers' perception
+of native- and Jamaican-accented words. \emph{Psychological Science},
+\emph{20}(5).
+doi:\href{https://doi.org/10.1111/j.1467-9280.2009.02327.x.}{10.1111/j.1467-9280.2009.02327.x.}
+
+\hypertarget{ref-Black2017}{}
+Black, A., \& Bergmann, C. (2017). Quantifying infants' statistical word
+segmentation: A meta-analysis. In G. Gunzelmann, A. Howes, T. Tenbrink,
+\& E. Davelaar (Eds.), \emph{Proceedings of the 39th annual conference
+of the cognitive science society} (pp. 124--129). Austin, TX: Cognitive
+Science Society, Inc. Retrieved from
+\url{https://pdfs.semanticscholar.org/0807/41051b6e2b74d2a1fc2e568c3dd11224984b.pdf}
+
+\hypertarget{ref-Canfield1991}{}
+Canfield, R. L., \& Haith, M. M. (1991). Young infants' visual
+expectations for symmetric and asymmetric stimulus sequences.
+\emph{Developmental Psychology}, \emph{27}(2), 198--208.
+doi:\href{https://doi.org/10.1037/0012-1649.27.2.198}{10.1037/0012-1649.27.2.198}
+
+\hypertarget{ref-CharlesLuce1995}{}
+Charles-Luce, J., \& Luce, P. A. (1995). An examination of similarity
+neighbourhoods in young children's receptive vocabularies. \emph{Journal
+of Child Language}, \emph{22}(3), 727--735.
+doi:\href{https://doi.org/10.1017/S0305000900010023}{10.1017/S0305000900010023}
+
+\hypertarget{ref-clark1977}{}
+Clark, H. H., \& Clark, E. V. (1977). \emph{Psychology and Language: An
+introduction to psycholinguistics.} New York: Harcourt Brace Jovanovich.
+
+\hypertarget{ref-cohen}{}
+Cohen, J. (1988). \emph{Statistical Power Analysis for the Behavioural
+Sciences} (2nd ed.). New York: Lawrence Earlbaum Associates.
+
+\hypertarget{ref-Csibra2016}{}
+Csibra, G., Hernik, M., Mascaro, O., Tatone, D., \& Lengyel, M. (2016).
+Statistical treatment of looking-time data. \emph{Developmental
+Psychology}, \emph{52}(4), 521--36.
+doi:\href{https://doi.org/10.1037/dev0000083}{10.1037/dev0000083}
+
+\hypertarget{ref-Curtin2007}{}
+Curtin, S., \& Werker, J. F. (2007). The perceptual foundations of
+phonological development. In M. G. Gaskell (Ed.), \emph{The oxford
+handbook of psycholinguistics} (pp. 579--599). New York: Oxford
+University Press.
+doi:\href{https://doi.org/10.1093/oxfordhb/9780198568971.013.0035}{10.1093/oxfordhb/9780198568971.013.0035}
+
+\hypertarget{ref-Curtin2011}{}
+Curtin, S., Byers-Heinlein, K., \& Werker, J. F. (2011). Bilingual
+beginnings as a lens for theory development: PRIMIR in focus.
+\emph{Journal of Phonetics}, \emph{39}(4), 492--504.
+doi:\href{https://doi.org/10.1016/j.wocn.2010.12.002}{10.1016/j.wocn.2010.12.002}
+
+\hypertarget{ref-DelleLuche2015}{}
+Delle Luche, C., Durrant, S., Poltrock, S., \& Floccia, C. (2015). A
+methodological investigation of the Intermodal Preferential Looking
+paradigm: Methods of analyses, picture selection and data rejection
+criteria. \emph{Infant Behavior and Development}, \emph{40}, 151--172.
+doi:\href{https://doi.org/10.1016/j.infbeh.2015.05.005}{10.1016/j.infbeh.2015.05.005}
+
+\hypertarget{ref-vanderFeest2015}{}
+Feest, S. V. H. van der, \& Fikkert, P. (2015). Building phonological
+lexical representations. \emph{Phonology}, \emph{32}(02), 207--239.
+doi:\href{https://doi.org/10.1017/S0952675715000135}{10.1017/S0952675715000135}
+
+\hypertarget{ref-Ferguson2012}{}
+Ferguson, C. J., \& Heene, M. (2012). A vast graveyard of undead
+theories: Publication bias and psychological science's aversion to the
+null. \emph{Perspectives on Psychological Science}, \emph{7}(6),
+555--561.
+doi:\href{https://doi.org/10.1177/1745691612459059}{10.1177/1745691612459059}
+
+\hypertarget{ref-Fernald1998}{}
+Fernald, A., Pinto, J. P., Swingley, D., Weinberg, A., \& McRoberts, G.
+W. (1998). Rapid gains in speed of verbal processing by infants in the
+2nd year. \emph{Psychological Science}, \emph{9}(3), 228--231.
+doi:\href{https://doi.org/10.1111/1467-9280.00044}{10.1111/1467-9280.00044}
+
+\hypertarget{ref-Fernald2001a}{}
+Fernald, A., Swingley, D., \& Pinto, J. P. (2001). When half a word is
+enough: infants can recognize spoken words using partial phonetic
+information. \emph{Child Development}, \emph{72}(4), 1003--15.
+doi:\href{https://doi.org/10.1111/1467-8624.00331}{10.1111/1467-8624.00331}
+
+\hypertarget{ref-Frank2017}{}
+Frank, M. C., Braginsky, M., Yurovsky, D., \& Marchman, V. A. (2017).
+Wordbank: An open repository for developmental vocabulary data.
+\emph{Journal of Child Language}, \emph{44}(3), 677--694.
+doi:\href{https://doi.org/10.1017/S0305000916000209}{10.1017/S0305000916000209}
+
+\hypertarget{ref-Gelman2013}{}
+Gelman, A., \& Loken, E. (2013). \emph{The garden of forking paths: Why
+multiple comparisons can be a problem, even when there is no ``fishing
+expedition'' or ``p-hacking'' and the research hypothesis was posited
+ahead of time.} Department of Statistics, Columbia University.
+doi:\href{https://doi.org/10.1037/a0037714}{10.1037/a0037714}
+
+\hypertarget{ref-Hedges1981}{}
+Hedges, L. V. (1981). Distribution theory for glass's estimator of
+effect size and related estimators. \emph{Journal of Educational and
+Behavioral Statistics}, \emph{6}(2), 107--128.
+doi:\href{https://doi.org/10.3102/10769986006002107}{10.3102/10769986006002107}
+
+\hypertarget{ref-Hojen}{}
+Højen, A., Madsen, T. O., Vach, W., Basbøll, H., Caporali, S., \& Blese,
+D. (n.d.). \emph{Contributions of vocalic and consonantal information
+when Danish 20-month-olds recognize familiar words}.
+
+\hypertarget{ref-Jusczyk1995}{}
+Jusczyk, P. W., \& Aslin, R. N. (1995). Infants' detection of the sound
+patterns of words in fluent speech.
+doi:\href{https://doi.org/10.1006/cogp.1995.1010}{10.1006/cogp.1995.1010}
+
+\hypertarget{ref-Kuhl2004}{}
+Kuhl, P. K. (2004). Early language acquisition: Cracking the speech
+code. \emph{Nature Reviews. Neuroscience}, \emph{5}(11), 831--43.
+doi:\href{https://doi.org/10.1038/nrn1533}{10.1038/nrn1533}
+
+\hypertarget{ref-Law2015}{}
+Law II, F., \& Edwards, J. R. (2015). Effects of Vocabulary Size on
+Online Lexical Processing by Preschoolers. \emph{Language Learning and
+Development}, \emph{11}(4), 331--355.
+doi:\href{https://doi.org/10.1080/15475441.2014.961066}{10.1080/15475441.2014.961066}
+
+\hypertarget{ref-Mani2007}{}
+Mani, N., \& Plunkett, K. (2007). Phonological specificity of vowels and
+consonants in early lexical representations. \emph{Journal of Memory and
+Language}, \emph{57}(2), 252--272.
+doi:\href{https://doi.org/10.1016/j.jml.2007.03.005}{10.1016/j.jml.2007.03.005}
+
+\hypertarget{ref-Mani2010kepstups}{}
+Mani, N., \& Plunkett, K. (2010). Twelve-month-olds know their cups from
+their keps and tups. \emph{Infancy}, \emph{15}(5), 445--470.
+doi:\href{https://doi.org/10.1111/j.1532-7078.2009.00027.x}{10.1111/j.1532-7078.2009.00027.x}
+
+\hypertarget{ref-Mani2011}{}
+Mani, N., \& Plunkett, K. (2011). Does size matter? Subsegmental cues to
+vowel mispronunciation detection. \emph{Journal of Child Language},
+\emph{38}(03), 606--627.
+doi:\href{https://doi.org/10.1017/S0305000910000243}{10.1017/S0305000910000243}
+
+\hypertarget{ref-Mani2008}{}
+Mani, N., Coleman, J., \& Plunkett, K. (2008). Phonological specificity
+of vowel contrasts at 18-months. \emph{Language and Speech}, \emph{51},
+3--21.
+doi:\href{https://doi.org/10.1177/00238309080510010201}{10.1177/00238309080510010201}
+
+\hypertarget{ref-Maris2007}{}
+Maris, E., \& Oostenveld, R. (2007). Nonparametric statistical testing
+of EEG- and MEG-data. \emph{Journal of Neuroscience Methods},
+\emph{164}(1), 177--190.
+doi:\href{https://doi.org/10.1016/j.jneumeth.2007.03.024}{10.1016/j.jneumeth.2007.03.024}
+
+\hypertarget{ref-Mills-Smith2015}{}
+Mills-Smith, L., Spangler, D. P., Panneton, R., \& Fritz, M. S. (2015).
+A Missed Opportunity for Clarity: Problems in the Reporting of Effect
+Size Estimates in Infant Developmental Science. \emph{Infancy},
+\emph{20}(4), 416--432.
+doi:\href{https://doi.org/10.1111/infa.12078}{10.1111/infa.12078}
+
+\hypertarget{ref-Mirman2008}{}
+Mirman, D., Dixon, J. A., \& Magnuson, J. S. (2008). Statistical and
+computational models of the visual world paradigm: Growth curves and
+individual differences. \emph{Journal of Memory \& Language},
+\emph{59}(4), 475--494.
+doi:\href{https://doi.org/10.1016/j.jml.2007.11.006}{10.1016/j.jml.2007.11.006}
+
+\hypertarget{ref-Moher2009}{}
+Moher, D., Liberati, A., Tetzlaff, J., Altman, D. G., \& Group, T. P.
+(2009). Preferred Reporting Items for Systematic Reviews and
+Meta-Analyses: The PRISMA Statement. \emph{PLoS Medicine}, \emph{6}(7),
+e1000097.
+doi:\href{https://doi.org/10.1371/journal.pmed.1000097}{10.1371/journal.pmed.1000097}
+
+\hypertarget{ref-morris2002combining}{}
+Morris, S. B., \& DeShon, R. P. (2002). Combining effect size estimates
+in meta-analysis with repeated measures and independent-groups designs.
+\emph{Psychological Methods}, \emph{7}(1), 105--125.
+doi:\href{https://doi.org/10.1037/1082-989X.7.1.105}{10.1037/1082-989X.7.1.105}
+
+\hypertarget{ref-Mulak2014}{}
+Mulak, K. E., Best, C. T., Tyler, M. D., Kitamura, C., \& Irwin, J. R.
+(2014). Development of phonological constancy: 19-month-olds, but not
+15-month-olds, identify words in a non-native regional accent.
+\emph{Child Development}, \emph{84}(6), 2064--2074.
+doi:\href{https://doi.org/10.1111/cdev.12087}{10.1111/cdev.12087}
+
+\hypertarget{ref-R}{}
+R Core Team. (2018). \emph{R: A Language and Environment for Statistical
+Computing}. Vienna, Austria: R Foundation for Statistical Computing.
+Retrieved from \url{https://www.r-project.org/}
+
+\hypertarget{ref-Rabagliati2018}{}
+Rabagliati, H., Ferguson, B., \& Lew-Williams, C. (2018). The profile of
+abstract rule learning in infancy: Meta-analytic and experimental
+evidence. \emph{Developmental Science}, (October 2017), 1--18.
+doi:\href{https://doi.org/10.1111/desc.12704}{10.1111/desc.12704}
+
+\hypertarget{ref-Renner2017}{}
+Renner, L. F. (2017). \emph{The magic of matching -- speech production
+and perception in language acquisition} (thesis). Stockholm University.
+
+\hypertarget{ref-Sakaluk2016}{}
+Sakaluk, J. (2016). Make it pretty: Forest and funnel plots for
+meta-analysis using ggplot2. {[}Blog post{]}. Retrieved from
+\url{https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/}
+
+\hypertarget{ref-Schmale2011}{}
+Schmale, R., Hollich, G., \& Seidl, A. (2011). Contending with foreign
+accent in early word learning. \emph{Journal of Child Language},
+\emph{38}(5), 1096--108.
+doi:\href{https://doi.org/10.1017/S0305000910000619}{10.1017/S0305000910000619}
+
+\hypertarget{ref-Simmons2011}{}
+Simmons, J. P., Nelson, L. D., \& Simonsohn, U. (2011). False-positive
+psychology: Undisclosed flexibility in data collection and analysis
+allows presenting anything as significant. \emph{Psychological Science},
+\emph{22}(11), 1359--1366.
+doi:\href{https://doi.org/10.1177/0956797611417632}{10.1177/0956797611417632}
+
+\hypertarget{ref-pcurve}{}
+Simonsohn, U., Nelson, L. D., \& Simmons, J. P. (2014). P-curve: A key
+to the file-drawer. \emph{Journal of Experimental Psychology: General},
+\emph{143}(2), 534--547.
+doi:\href{https://doi.org/10.1037/a0033242}{10.1037/a0033242}
+
+\hypertarget{ref-Skoruppa2013}{}
+Skoruppa, K., Mani, N., Plunkett, K., Cabrol, D., \& Peperkamp, S.
+(2013). Early word recognition in sentence context: French and English
+24-month-olds' sensitivity to sentence-medial mispronunciations and
+assimilations. \emph{Infancy}, \emph{18}(6), 1007--1029.
+doi:\href{https://doi.org/10.1111/infa.12020}{10.1111/infa.12020}
+
+\hypertarget{ref-Stager1997}{}
+Stager, C. L., \& Werker, J. F. (1997). Infants listen for more phonetic
+detail in speech perception than in word-learning tasks. \emph{Nature},
+\emph{388}(6640), 381--382.
+doi:\href{https://doi.org/10.1038/41102}{10.1038/41102}
+
+\hypertarget{ref-Swingley2009}{}
+Swingley, D. (2009). Onsets and codas in 1.5-year-olds' word
+recognition. \emph{Journal of Memory and Language}, \emph{60}(2),
+252--269.
+doi:\href{https://doi.org/10.1016/j.jml.2008.11.003}{10.1016/j.jml.2008.11.003}
+
+\hypertarget{ref-Swingley2016}{}
+Swingley, D. (2016). Two-year-olds interpret novel phonological
+neighbors as familiar words. \emph{Developmental Psychology},
+\emph{52}(7), 1011--1023.
+doi:\href{https://doi.org/10.1037/dev0000114}{10.1037/dev0000114}
+
+\hypertarget{ref-Swingley2000}{}
+Swingley, D., \& Aslin, R. N. (2000). Spoken word recognition and
+lexical representation in very young children. \emph{Cognition},
+\emph{76}(2), 147--166.
+doi:\href{https://doi.org/10.1016/S0010-0277(00)00081-0}{10.1016/S0010-0277(00)00081-0}
+
+\hypertarget{ref-Swingley2002}{}
+Swingley, D., \& Aslin, R. N. (2002). Lexical Neighborhoods and the
+Word-Form representations of 14-Month-Olds. \emph{Psychological
+Science}, \emph{13}(5), 480--484.
+doi:\href{https://doi.org/10.1111/1467-9280.00485}{10.1111/1467-9280.00485}
+
+\hypertarget{ref-Tincoff1999}{}
+Tincoff, R., \& Jusczyk, P. W. (1999). Some beginnings of word
+comprehension in 6-month-olds. \emph{Psychological Science},
+\emph{10}(2), 172--175.
+doi:\href{https://doi.org/10.1111/1467-9280.00127}{10.1111/1467-9280.00127}
+
+\hypertarget{ref-Tomasello1994}{}
+Tomasello, M., \& Mervis, C. B. (1994). The instrument is great, but
+measuring comprehension is still a problem. In \emph{Monographs of the
+society for research in child development} (pp. 174--179).
+doi:\href{https://doi.org/10.1111/j.1540-5834.1994.tb00186.x}{10.1111/j.1540-5834.1994.tb00186.x}
+
+\hypertarget{ref-Tsuji2014}{}
+Tsuji, S., Bergmann, C., \& Cristia, A. (2014). Community-Augmented
+Meta-Analyses: Toward Cumulative Data Assessment. \emph{Psychological
+Science}, \emph{9}(6), 661--665.
+doi:\href{https://doi.org/10.1177/1745691614552498}{10.1177/1745691614552498}
+
+\hypertarget{ref-metafor}{}
+Viechtbauer, W. (2010). Conducting meta-analyses in R with the metafor
+package. \emph{Journal of Statistical Software}, \emph{36}(3), 1--48.
+doi:\href{https://doi.org/10.18637/jss.v036.i03}{10.18637/jss.v036.i03}
+
+\hypertarget{ref-VonHolzen2012}{}
+Von Holzen, K., \& Mani, N. (2012). Language nonselective lexical access
+in bilingual toddlers. \emph{Journal of Experimental Child Psychology},
+\emph{113}, 569--586.
+doi:\href{https://doi.org/10.1016/j.jecp.2011.02.002}{10.1016/j.jecp.2011.02.002}
+
+\hypertarget{ref-Werker2005}{}
+Werker, J. F., \& Curtin, S. (2005). PRIMIR: A developmental framework
+of infant speech processing. \emph{Language Learning and Development},
+\emph{1}(2), 197--234.
+doi:\href{https://doi.org/10.1207/s15473341lld0102_4}{10.1207/s15473341lld0102\_4}
+
+\hypertarget{ref-White2008}{}
+White, K. S., \& Morgan, J. L. (2008). Sub-segmental detail in early
+lexical representations. \emph{Journal of Memory and Language},
+\emph{52}(1), 114--132.
+doi:\href{https://doi.org/10.1016/j.jml.2008.03.001}{10.1016/j.jml.2008.03.001}
+
+\hypertarget{ref-Zesiger2012}{}
+Zesiger, P., Lozeron, E. D., Levy, A., \& Frauenfelder, U. H. (2012).
+Phonological specificity in 12- and 17-month-old French-speaking
+infants. \emph{Infancy}, \emph{17}(6), 591--609.
+doi:\href{https://doi.org/10.1111/j.1532-7078.2011.00111.x}{10.1111/j.1532-7078.2011.00111.x}
 

### 2019-01-11 Paper_Analyses.Rmd
added power/sample size for interaction

@@
 These calculations suggest that for the comparison of responses for correct pronunciations and mispronunciations, the studies included in this meta-analysis contain well-powered analyses.
-However, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which will require even larger sample sizes.
+However, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates requre four times the sample size to detect an effect of similar magnitue as the main effect for both ANOVA [@Fleiss1986] and mixed-effect-model [@Leon2009] analyses.
 We thus strongly advocate for a consideration of power and the reported effect sizes to test infants’ mispronunciation sensitivity.

### 2019-01-11 Paper_Analyses.tex
added power/sample size for interaction

@@
 tested, leading to two-way interactions (age versus mispronunciation
-sensitivity is a common example), which will require even larger sample
-sizes. We thus strongly advocate for a consideration of power and the
-reported effect sizes to test infants' mispronunciation sensitivity.
+sensitivity is a common example), which by some estimates requre four
+times the sample size to detect an effect of similar magnitue as the
+main effect for both ANOVA (Fleiss, 1986) and mixed-effect-model (Leon
+\& Heo, 2009) analyses. We thus strongly advocate for a consideration of
+power and the reported effect sizes to test infants' mispronunciation
+sensitivity.
 
@@
 
+\hypertarget{ref-Fleiss1986}{}
+Fleiss, J. L. (1986). \emph{The Design and Analysis of Clinical
+Experiments}. New York: Wiley; Sons.
+
 \hypertarget{ref-Frank2017}{}
@@
 
+\hypertarget{ref-Leon2009}{}
+Leon, A. C., \& Heo, M. (2009). Sample sizes required to detect
+interactions between two binary fixed-effects in a mixed-effects linear
+regression model. \emph{Computational Statistics and Data Analysis},
+\emph{53}(3), 603--608.
+doi:\href{https://doi.org/10.1016/j.csda.2008.06.010}{10.1016/j.csda.2008.06.010}
+
 \hypertarget{ref-Mani2007}{}

### 2019-01-16 Paper_Analyses.tex
submitted to Cognition

@@
 \hypersetup{unicode=true,
-            pdftitle={The development of infants' responses to mispronunciations - A Meta-Analysis},
+            pdftitle={The development of infants' responses to mispronunciations: A Meta-Analysis},
             pdfauthor={Katie Von Holzen~\& Christina Bergmann},
             pdfkeywords={language acquisition; mispronunciation sensitivity; word recognition;
-meta-analysis; lexicon},
+meta-analysis; lexicon; infancy},
             pdfborder={0 0 0},
@@
 
-  \title{The development of infants' responses to mispronunciations - A
+  \title{The development of infants' responses to mispronunciations: A
 Meta-Analysis}
@@
 \textsuperscript{1} Department of Hearing and Speech Sciences, University of Maryland, USA\\\textsuperscript{2} Laboratoire Psychologie de la Perception, Université Paris Descartes\\\textsuperscript{3} Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands\\\textsuperscript{4} LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University}
-\keywords{language acquisition; mispronunciation sensitivity; word recognition; meta-analysis; lexicon\newline\indent Word count: X}
+\keywords{language acquisition; mispronunciation sensitivity; word recognition; meta-analysis; lexicon; infancy}
 \usepackage{csquotes}
@@
 
-\authornote{
+\authornote{The authors each declare that they have no
+conflict of interest.
 
@@
 that a mature understanding of native language phonology is present in
-infants from an early age. Despite this finding, we discuss potential
-data analysis choices that may influence different conclusions about
-mispronunciation sensitivity development as well as offer
-recommendations to improve best practices in the study of
-mispronunciation sensitivity.
+infants from an early age, possibly before the vocabulary explosion.
+Despite this finding, we discuss potential data analysis choices that
+may influence different conclusions about mispronunciation sensitivity
+development as well as offer recommendations to improve best practices
+in the study of mispronunciation sensitivity.
 
@@
 that differentiate words in a given language (e.g.~cat-hat). To build
-robust language knowledge, it seems ueful to acquire this ability early
+robust language knowledge, it seems useful to acquire this ability early
 during development. Indeed, before children can correctly pronounce a
@@
 processing matures and becomes more efficient, including their knowledge
-of what consistutes a permissible versus word-changing phonological
+of what constitutes a permissible versus word-changing phonological
 deviation. In this paper, we aggregate and analyze the nearly 20 years
@@
 At the turn of the millenium, infant language acquisition researchers
-had established that during their first years of life, infants are
+had established that during their first two years of life, infants are
 sensitive to changes in the phonetic detail of newly segmented words
@@
 pairs of images (e.g.~a baby and a dog) and their eye movements to each
-image were recorded and subsequently coded offline. On \enquote{correct}
-trials, children heard the correct label for one of the images (e.g.
-\enquote{baby}). On \enquote{mispronounced} trials, children heard a
-mispronounced label of one of the images (e.g. \enquote{vaby}). The mean
-proportion of fixations to the target image (here: a baby) was
-calculated separately for both correct and mispronounced trials by
-dividing the target looking time by the sum of total looking time to
-both target and a distractor (proportion of target looking or PTL). Mean
-fixations in correct trials were significantly greater than in
-mispronounced trials, and in both conditions looks to the target were
-significantly greater than chance. We refer to this pattern of a
-difference between looks to correct and mispronounced words as
-\emph{mispronunciation sensitivity} and of looks to the target image
-above chance in each condition as \emph{object identification}. Swingley
-and Aslin (2000) concluded that already before the second birthday,
-children represent words with sufficient detail to be sensitive to
-mispronunciations.
+image were recorded. On \enquote{correct} trials, children heard the
+correct label for one of the images (e.g. \enquote{baby}). On
+\enquote{mispronounced} trials, children heard a mispronounced label of
+one of the images (e.g. \enquote{vaby}). The mean proportion of
+fixations to the target image (here: a baby) was calculated separately
+for both correct and mispronounced trials by dividing the target looking
+time by the sum of total looking time to both target and a distractor
+(proportion of target looking or PTL). Mean fixations in correct trials
+were significantly greater than in mispronounced trials, and in both
+conditions looks to the target were significantly greater than chance.
+We refer to this pattern of a difference between looks to correct and
+mispronounced words as \emph{mispronunciation sensitivity} and of looks
+to the target image above chance in each condition as \emph{object
+identification}. Swingley and Aslin (2000) concluded that already before
+the second birthday, children represent words with sufficient detail to
+be sensitive to mispronunciations.
 
@@
 In the current study, we focus on infants' developing ability to
-correctly apply the principles of phonological distinctiveness and
-constancy by using a meta-analytic approach to investigate
+correctly apply the principles of phonological constancy and
+distinctiveness by using a meta-analytic approach to investigate
 mispronunciation sensitivity. Considering that infants are sensitive to
@@
 data from a much larger and diverse sample of infants than is possible
-in most single studies (see Frank et al., 2018; for a notable
+in most single studies ({[}see Frank et al. (2017); for a notable
 exception). Before we outline the meta-analytical approach and its
@@
 disentangle and the data supporting each of the accounts.
-
-{[}Katie: Christina, do you know which citation the Frank et al., 2018
-citation is referring to above? He's published a gazilion papers in
-2018{]}
 
@@
 words and only refine their representations as language experience
-accumulates. PRIMIR ((Processing Rich Information from Multidimensional
+accumulates. PRIMIR (Processing Rich Information from Multidimensional
 Interactive Representations; Curtin \& Werker, 2007; Curtin,
-Byers-Heinlein, \& Werker, 2011; Werker \& Curtin, 2005)) describes the
+Byers-Heinlein, \& Werker, 2011; Werker \& Curtin, 2005) describes the
 development of phonemic categories emerging as the number of word
@@
 however, only about half of studies have compared more than one age
-group on the same mispronunciation task (see Table 1), making the
-current meta-analysis very informative. One study has found evidence for
-infants to become \emph{less} sensitive to mispronunciations as they
-develop. Mani and Plunkett (2011) presented 18- and 24-month-olds with
-mispronunciations varying in the number of phonological features changed
-(e.g., changing an p into a b, a 1-feature change, versus changing a p
-into a g, a 2-feature change). 18-month-olds were sensitive to
-mispronunciations, regardless of the number of features changed.
-24-month-olds, in contrast, fixated the target image equally for both
-correct and 1-feature mispronounced trials, although they were sensitive
-to larger mispronunciations. In other words, for 1-feature
-mispronunciations at least, sensitivity decreased from 18 to 24 months,
-providing support to the prediction that mispronunciation sensitivity
-may decrease with development.
+group on the same mispronunciation task (see Table 1). In those single
+studies all possible patterns of development lined out above have been
+reported, making the current meta-analysis very informative.
+
+One study has found evidence for infants to become \emph{less} sensitive
+to mispronunciations as they develop. Mani and Plunkett (2011) presented
+18- and 24-month-olds with mispronunciations varying in the number of
+phonological features changed (e.g., changing an p into a b, a 1-feature
+change, versus changing a p into a g, a 2-feature change). 18-month-olds
+were sensitive to mispronunciations, regardless of the number of
+features changed. 24-month-olds, in contrast, fixated the target image
+equally for both correct and 1-feature mispronounced trials, although
+they were sensitive to larger mispronunciations. In other words, for
+1-feature mispronunciations at least, sensitivity decreased from 18 to
+24 months, providing support to the prediction that mispronunciation
+sensitivity may decrease with development.
 
@@
 to other mispronunciations. These studies award support to the
-prediction that mispronunciation sensitivity improves with development.
+prediction that mispronunciation sensitivity increases with development.
 
@@
 more likely to look at the target in the presence of a correct or
-mispronounced label, but that the difference between the two does not
-change. A similar response pattern has been found for British English
-learning infants aged between 18 and 24 months (Bailey \& Plunkett,
-2002) as well as younger French-learning infants at 12 and 17 months
-(Zesiger, Lozeron, Levy, \& Frauenfelder, 2012). These studies award
-support to the prediction that mispronunciation sensitivity does not
-change with development.
+mispronounced label, but that the difference between looks elicited by
+the two conditions does not change. A similar response pattern has been
+found for British English learning infants aged between 18 and 24 months
+(Bailey \& Plunkett, 2002) as well as younger French-learning infants at
+12 and 17 months (Zesiger, Lozeron, Levy, \& Frauenfelder, 2012). These
+studies award support to the prediction that mispronunciation
+sensitivity does not change with development.
 
@@
 In sum, the studies we have reviewed begin to paint a picture of the
-development of mispronunciation sensitivity. Each study contributes one
-separate brushstroke and it is only by examining all of them together
-that we can achieve a better understanding of the big picture of early
-language development. Meta-analyses can provide unique insights by
-estimating the population effect, both of infants' responses to correct
-and mispronounced labels, and their mispronunciations sensitivity.
-Because we aggregate data over various age groups, this meta-analysis
-can also investigate the role of maturation by assessing the impact of
-age and vocabulary size. As a consequence, our results will be important
-in evaluating theories and drive future research. We also make hands-on
-recommendations for experiment planning, for example by providing an
-effect size estimate for a priori power analyses (Bergmann et al.,
-2018).
+development of infants' mispronunciation sensitivity. Each study
+contributes one separate brushstroke and it is only by examining all of
+them together that we can achieve a better understanding of the big
+picture of early language development. Meta-analyses can provide unique
+insights by estimating the population effect, both of infants' responses
+to correct and mispronounced labels, and of their mispronunciations
+sensitivity. Because we aggregate data over various age groups, this
+meta-analysis can also investigate the role of maturation by assessing
+the impact of age and vocabulary size. As a consequence, our results
+will be important in evaluating theories and drive future research. We
+also make hands-on recommendations for experiment planning, for example
+by providing an effect size estimate for a priori power analyses
+(Bergmann et al., 2018).
 
@@
 2014). The most recent version is available via the website and the
-interactive platform MetaLab ((\url{https://metalab.stanford.edu};
-Bergmann et al., 2018)). Since the present paper was written with
-embedded analysis scripts in R (R Core Team, 2018, Allaire et al.
-(2018), Aust and Barth (2018)), it is always possible to re-analyze an
-updated dataset. In addition, we followed the Preferred Reporting Items
-for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make
-the corresponding information available as supplementary materials
-(Moher, Liberati, Tetzlaff, Altman, \& Group, 2009). Figure 1 plots our
-PRISMA flowchart illustrating the paper selection procedure.
+interactive platform MetaLab (\url{https://metalab.stanford.edu};
+Bergmann et al., 2018). Since the present paper was written with
+embedded analysis scripts in R (R Core Team, 2018) using the papaja
+package (Aust \& Barth, 2018) in R Markdown (Allaire et al., 2018), it
+is always possible to re-analyze an updated dataset. In addition, we
+followed the Preferred Reporting Items for Systematic Reviews and
+Meta-Analyses (PRISMA) guidelines and make the corresponding information
+available as supplementary materials (Moher, Liberati, Tetzlaff, Altman,
+\& Group, 2009). Figure \ref{fig:PRISMA-image} plots our PRISMA
+flowchart illustrating the paper selection procedure.
 
@@
 \includegraphics{figures/Figure_1_PRISMA_MA_Mispronunciation.png}
-\caption{(\#fig:PRISMA\_image)A PRISMA flowchart illustrating the
+\caption{\label{fig:PRISMA-image}A PRISMA flowchart illustrating the
 selection procedure used to include studies in the current
@@
 \begin{longtable}{lllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
-\caption{\label{tab:SummaryTable}Summary of all studies.}\\
+\caption{\label{tab:SummaryTable}Summary of all studies.
+Age is calculated by truncating the mean age reported in the paper.
+The abbreviations Comp and Prod refer to comprehension and production, respectively.}\\
 \toprule
@@
 mispronunciation conditions and the results were reported separately in
-the paper, we also entered each condition as a separate row ((e.g.,
-consonant versus vowel mispronunciations; Mani \& Plunkett, 2007)). The
+the paper, we also entered each condition as a separate row (e.g.,
+consonant versus vowel mispronunciations; Mani \& Plunkett, 2007). The
 fact that the same infants contributed data to multiple rows (minimally
@@
 were able to compute correlations using means, standard deviations, and
-t-values for 5 papers ((following Csibra, Hernik, Mascaro, Tatone, \&
-Lengyel, 2016; see also Rabagliati, Ferguson, \& Lew-Williams, 2018)).
-Correlations were imputed for the remaining papers ((see Black \&
-Bergmann, 2017 for the same procedure)). For two papers, we could not
+t-values for 5 papers (following Csibra, Hernik, Mascaro, Tatone, \&
+Lengyel, 2016; see also Rabagliati, Ferguson, \& Lew-Williams, 2018).
+Correlations were imputed for the remaining papers (see Black \&
+Bergmann, 2017 for the same procedure). For two papers, we could not
 derive any effect size (Ballem \& Plunkett, 2005; Renner, 2017), and for
@@
 
-{[}Katie: Mention of Renner here{]}
-
 To take into account the fact that the same infants contributed to
@@
 (\emph{n} = 29 records from 10 papers), thus reporting two variables, or
-compared post-naming PTL with a chance level of 50\%, (\emph{n} = 23
+compared post-naming PTL with a chance level of 50\% (\emph{n} = 23
 records from 9 papers). For all these comparisons, positive values
@@
 over-reported and thus might be over-represented in our meta-analyses
-((see C. J. Ferguson \& Heene, 2012)). To examine whether this is also
-the case in the mispronunciation sensitivity literature, which would
-bias the data analyzed in this meta-analysis, we conducted two tests. We
+(see C. J. Ferguson \& Heene, 2012). To examine whether this is also the
+case in the mispronunciation sensitivity literature, which would bias
+the data analyzed in this meta-analysis, we conducted two tests. We
 first examined whether effect sizes are distributed as expected based on
@@
 Second, we analyze all of the significant results in the dataset using a
-p-curve from the p-curve app ((v4.0, \url{http://p-curve.com};
-Simonsohn, Nelson, \& Simmons, 2014)). This p-curve tests for evidential
-value by examining whether the p-values follow the expected distribution
-of a right skew in case the alternative hypothesis is true, versus a
-flat distribution that speaks for no effect being present in the
-population and all observed significant effects being spurious.
+p-curve from the p-curve app (v4.0, \url{http://p-curve.com}; Simonsohn,
+Nelson, \& Simmons, 2014). This p-curve tests for evidential value by
+examining whether the p-values follow the expected distribution of a
+right skew in case the alternative hypothesis is true, versus a flat
+distribution that speaks for no effect being present in the population
+and all observed significant effects being spurious.
 
@@
 development impacts mispronunciation sensitivity, our core theoretical
-question, we introduced age (centered; continuous and measured in days
-but transformed into months for ease of interpreting estimates by
-dividing by 30.44) as a moderator to our main model. For a subsequent
-exploratory investigation of experimental characteristics, we introduced
-each characteristic as a moderator (more detail below).
+question, we first introduced age (centered; continuous and measured in
+days but transformed into months for ease of interpreting estimates by
+dividing by 30.44) as a moderator to our main model. Second, we analyzed
+the correlation between reported vocabulary size and mispronunciation
+sensitivity using the R (R Core Team, 2018) package meta (Schwarzer,
+2007). Finally, for a subsequent exploratory investigation of
+experimental characteristics, we introduced each characteristic as a
+moderator (more detail below).
 
@@
 
-Figure 2 shows the funnel plots for both correct pronunciations and
-mispronunciations ((code adapted from Sakaluk, 2016)). Funnel plot
-asymmetry was significant for both correct pronunciations (Kendall's
-\(\tau\) = 0.53, \emph{p} \textless{} .001) and mispronunciations
-(Kendall's \(\tau\) = 0.16, \emph{p} = 0.004). These results,
-quantifying the asymmetry in the funnel plots (Figure 1), indicate bias
-in the literature. This is particularly evident for correct
-pronunciations, where larger effect sizes have greater variance (bottom
-right corner) and there are a smaller number of more precise effect
-sizes (i.e.~smaller variance) than expected (top left, outside the
-triangle).
+Figure \ref{fig:FunnelCombo} shows the funnel plots for both correct
+pronunciations and mispronunciations (code adapted from Sakaluk, 2016).
+Funnel plot asymmetry was significant for both correct pronunciations
+(Kendall's \(\tau\) = 0.53, \emph{p} \textless{} .001) and
+mispronunciations (Kendall's \(\tau\) = 0.16, \emph{p} = 0.004). These
+results, quantifying the asymmetry in the funnel plots (Figure
+\ref{fig:FunnelCombo}), indicate bias in the literature. This is
+particularly evident for correct pronunciations, where larger effect
+sizes have greater variance (bottom right corner) and the more precise
+effect sizes (i.e.~smaller variance) tend to be smaller than expected
+(top left, outside the triangle).
 
@@
 to the target picture after hearing the correct label, the overall
-experiment design is called into questions. However, even in a
+experiment design is called into question. However, even in a
 well-powered study one would expect the regular occurrence of null
@@
 
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
 \begin{figure}
@@
 \end{figure}
-
-\begin{verbatim}
-## [1] TRUE
-\end{verbatim}
-
-\begin{verbatim}
-## [1] TRUE
-\end{verbatim}
 
@@
 1.143{]}, \emph{p} \textless{} .001). This is a small to medium effect
-size ((according to the criteria set by Mills-Smith, Spangler, Panneton,
-\& Fritz, 2015)). That the effect size is significantly above zero
+size (according to the criteria set by Mills-Smith, Spangler, Panneton,
+\& Fritz, 2015). That the effect size is significantly above zero
 suggests that when presented with the correctly pronounced label,
@@
 the two datasets. When condition was included (correct, mispronounced),
-the moderator test was significant, QM(1) = 215.761, \emph{p}
-\textless{} .001. The estimate for mispronunciation sensitivity was
-0.495 (SE = 0.034), and infants' looking times across conditions were
+the moderator test was significant (QM(1) = 215.761, \emph{p}
+\textless{} .001). The estimate for mispronunciation sensitivity was
+0.495 (SE = 0.034), and infants' looking behavior across conditions was
 significantly different (CI {[}0.429, 0.561{]}, \emph{p} \textless{}
@@
 but transformed into months for ease of interpreting estimates by
-dividing by 30.44 for Figure 3).
+dividing by 30.44 for Figure \ref{fig:PlotMPEffect}).
 
@@
 al., 1998). We plot both object recognition and mispronunciation
-sensitivity as a function of age in Figure 3.
+sensitivity as a function of age in Figure \ref{fig:PlotMPEffect}.
 
@@
 driven by the difference between conditions. The small estimate, as well
-as inspection of Figure 2, suggests that as infants age, their
-mispronunciation sensitivity neither increases or decreases.
+as inspection of Figure \ref{fig:PlotMPEffect}, suggests that as infants
+age, their mispronunciation sensitivity neither increases or decreases.
 
@@
 here)}\label{insert-figure-3-about-here}
-
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
 
@@
 
-{[}Katie: Written as if moderators can not be added to metacor(){]}
-
 We first considered the relationship between vocabulary and object
@@
 
-Figure 4 plots the year of publication for all the mispronunciation
-sensitivity studies included in this meta-analysis. This figure
-illustrates two things: the increasing number of mispronunciation
-sensitivity studies and the decreasing number of mispronunciation
-studies measuring vocabulary. The lack of evidence for a relationship
-between mispronunciation sensitivity and vocabulary size in some early
-studies may have contributed to increasingly fewer researchers including
-vocabulary measurements in their mispronunciation sensitivity
-experimental design. This may explain our underpowered analysis of the
-relationship between object recognition for correct pronunciations and
-mispronunciations and vocabulary size.
+Figure \ref{fig:Vocab-describe1} plots the year of publication for all
+the mispronunciation sensitivity studies included in this meta-analysis.
+This figure illustrates two things: the increasing number of
+mispronunciation sensitivity studies and the decreasing number of
+mispronunciation studies measuring vocabulary. The lack of evidence for
+a relationship between mispronunciation sensitivity and vocabulary size
+in some early studies may have contributed to increasingly fewer
+researchers including vocabulary measurements in their mispronunciation
+sensitivity experimental design. This may explain our underpowered
+analysis of the relationship between object recognition for correct
+pronunciations and mispronunciations and vocabulary size.
 
@@
 \centering
-\includegraphics{Paper_Analyses_files/figure-latex/Vocab_describe1-1.pdf}
-\caption{(\#fig:Vocab\_describe1)Counts of studies included in the
+\includegraphics{Paper_Analyses_files/figure-latex/Vocab-describe1-1.pdf}
+\caption{\label{fig:Vocab-describe1}Counts of studies included in the
 meta-analysis as a function of publication year, representing whether
@@
 
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
 \subsubsection{Interim Discussion}\label{interim-discussion}
@@
 constant and stable effect of mispronunciation sensitivity. This did not
-change with development nor with vocabulary size. Of the three
+change with development, and we might consider age a proxy for
+vocabulary size. We observe that the data for directly reported
+vocabulary size were too sparse to draw strong conclusions. Of the three
 predictions about the development of infants' sensitivity to
@@
 found. This would lead to an increase in significant results and alter
-to observed developmental trajectory of mispronunciation sensitivity.
+the observed developmental trajectory of mispronunciation sensitivity.
 Such a scenario is in line with the publication bias we observe
 (Simmons, Nelson, \& Simonsohn, 2011). We examine whether variation in
-the approach to data analysis may be have an influence on findings of
-mispronunciation sensitivity.
+the approach to data analysis may be have an influence on our
+conclusions regarding infants' developing mispronunciation sensitivity.
 
@@
 \enquote{educated guess} based on studies . . . showing that target and
-distractor fixations tend to diverge at around 400 ms.} ((Swingley \&
-Aslin, 2000, p. 155)). Upon inspecting the offset time values used in
-the papers in our meta-analysis, the majority used a similar offset time
+distractor fixations tend to diverge at around 400 ms.} (Swingley \&
+Aslin, 2000, p. 155). Upon inspecting the offset time values used in the
+papers in our meta-analysis, the majority used a similar offset time
 value (between 360 and 370 ms) for analysis (\emph{n} = 151), but offset
@@
 -0.262, SE = 0.059, 95\% CI{[}-0.377, -0.148{]}, \emph{p} \textless{}
-.001). This relationship is plotted in Figure 3a. The results suggest
-that the size of the post-naming analysis window significantly impacted
-our estimate of mispronunciation sensitivity. Specifically, the
-difference between target fixations for correctly pronounced and
-mispronounced items (mispronunciation sensitivity) was significantly
-greater when the post-naming analysis window was shorter.
+.001). This relationship is plotted in Figure
+\ref{fig:Plot-post-name-cond-age}a. The results suggest that the size of
+the post-naming analysis window significantly impacted our estimate of
+mispronunciation sensitivity. Specifically, the difference between
+target fixations for correctly pronounced and mispronounced items
+(mispronunciation sensitivity) was significantly greater when the
+post-naming analysis window was shorter.
 
@@
 significant (\(\beta\) = -0.04, SE = 0.014, 95\% CI{[}-0.068, -0.012{]},
-\emph{p} = 0.006). As can be seen in Figure 3b, a smaller post-naming
-analysis window leads to a greater increase in measured mispronunciation
+\emph{p} = 0.006). As can be seen in Figure
+\ref{fig:Plot-post-name-cond-age}b, a smaller post-naming analysis
+window leads to a greater increase in measured mispronunciation
 sensitivity with development. For example, when experimental conditions
@@
 
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
 \begin{figure}
 \centering
-\includegraphics{Paper_Analyses_files/figure-latex/Plot_post_name_cond_age-1.pdf}
-\caption{(\#fig:Plot\_post\_name\_cond\_age)Effect sizes for the
-different lengths of the post-naming analysis window: 2000 ms or less
-(orange), 2001 to 3000 ms (blue), and 3001 ms or greater (green).
-Although length of the post-naming analysis window was included as a
-continuous variable in the meta-analytic model, it is divided into
-categories for ease of viewing. Panel a plots mispronunciation
-sensitivity aggregated over age, while panel b plots mispronunciation
-sensitivity as a function of age. The lines plot the linear regression
-and the gray shaded area indicates the standard error.}
+\includegraphics{Paper_Analyses_files/figure-latex/Plot-post-name-cond-age-1.pdf}
+\caption{\label{fig:Plot-post-name-cond-age}Effect sizes for the different
+lengths of the post-naming analysis window: 2000 ms or less (orange),
+2001 to 3000 ms (blue), and 3001 ms or greater (green). Although length
+of the post-naming analysis window was included as a continuous variable
+in the meta-analytic model, it is divided into categories for ease of
+viewing. Panel a plots mispronunciation sensitivity aggregated over age,
+while panel b plots mispronunciation sensitivity as a function of age.
+The lines plot the linear regression and the gray shaded area indicates
+the standard error.}
 \end{figure}
@@
 three-way-interaction between condition, offset time, and age was again
-zero (\(\beta\) = 0, SE = 0, 95\% CI{[}0, 0{]}, \emph{p} = 0.605. Taken
+zero (\(\beta\) = 0, SE = 0, 95\% CI{[}0, 0{]}, \emph{p} = 0.605). Taken
 together, these results suggest that offset time does not modulate
@@
 consider pre-naming preferences. It should be noted, however, that the
-Difference Score can better counteract participant- and item-level
+Difference Score may better counteract participant- and item-level
 differences, whereas Pre vs.~Post is a group-level measure. The Post
@@
 (\(\beta\) = -0.01, SE = 0.098, 95\% CI{[}-0.203, 0.183{]}, \emph{p} =
-0.916). This relationship is plotted in Figure 4a. The results suggest
-that the reported dependent variable significantly impacted the size of
-the estimated mispronunciation sensitivity effect, such that studies
+0.916). This relationship is plotted in Figure
+\ref{fig:Plot-Within-cond-age-diff-score}a. The results suggest that the
+reported dependent variable significantly impacted the size of the
+estimated mispronunciation sensitivity effect, such that studies
 reporting the Post. vs.~Pre dependent variable showed a smaller
@@
 significant (\(\beta\) = -0.036, SE = 0.027, 95\% CI{[}-0.088, 0.016{]},
-\emph{p} = 0.174). This relationship is plotted in Figure 4b. When the
-dependent variable reported was Pre vs.~Post, mispronunciation
-sensitivity was found to decrease with infant age, while in comparison,
-when the dependent variable was Post, mispronunciation sensitivity was
-found to increase with infant age. There was no difference in the
-estimated mispronunciation sensitivity change with infant age between
-the Post and Difference Score dependent variables.
+\emph{p} = 0.174). This relationship is plotted in Figure
+\ref{fig:Plot-Within-cond-age-diff-score}b. When the dependent variable
+reported was Pre vs.~Post, mispronunciation sensitivity was found to
+decrease with infant age, while in comparison, when the dependent
+variable was Post, mispronunciation sensitivity was found to increase
+with infant age. There was no difference in the estimated
+mispronunciation sensitivity change with infant age between the Post and
+Difference Score dependent variables.
 
@@
 
-\begin{verbatim}
-## pdf 
-##   2
-\end{verbatim}
-
 \begin{figure}
 \centering
-\includegraphics{Paper_Analyses_files/figure-latex/Plot_Within_cond_age_diff_score-1.pdf}
-\caption{(\#fig:Plot\_Within\_cond\_age\_diff\_score)Effect sizes for
-the different types of dependent variables calculated: Post (orange),
-Post vs.~Pre (blue), and Difference Score (green). Panel a plots
+\includegraphics{Paper_Analyses_files/figure-latex/Plot-Within-cond-age-diff-score-1.pdf}
+\caption{\label{fig:Plot-Within-cond-age-diff-score}Effect sizes for the
+different types of dependent variables calculated: Post (orange), Post
+vs.~Pre (blue), and Difference Score (green). Panel a plots
 mispronunciation sensitivity aggregated over age, while panel b plots
@@
 Overall, the results of the meta-analysis showed that infants reliably
-fixate the target object when given both correctly pronounced and
+fixate the target object when hearing both correctly pronounced and
 mispronounced labels. Infants not only recognize object labels when they
 were correctly pronounced, but are also likely to accept
-mispronunciations as acceptable labels for targets, in the presence of a
-distractor image. Nonetheless, there was a considerable difference in
-target fixations in response to correctly pronounced and mispronounced
-labels, suggesting that infants show an overall mispronunciation
-sensitivity based on the current experimental literature. In other
-words, infants show sensitivity to what constitutes unacceptable,
-possibly meaning-altering variation in word forms, thereby displaying
-knowledge of the role of phonemic changes throughout the ages assessed
-here (6 to 30 months). At the same time, infants, like adults, can
-recover from mispronunciations, a key skill in language processing.
+mispronunciations as labels for targets, in the presence of a distractor
+image. Nonetheless, there was a considerable difference in target
+fixations in response to correctly pronounced and mispronounced labels,
+suggesting that infants show an overall mispronunciation sensitivity
+based on the current experimental literature. In other words, infants
+show sensitivity to what constitutes unacceptable, possibly
+meaning-altering variation in word forms, thereby displaying knowledge
+of the role of phonemic changes throughout the ages assessed here (6 to
+30 months). At the same time, infants, like adults, can recover from
+mispronunciations, a key skill in language processing.
 
@@
 2007; Curtin et al., 2011; Werker \& Curtin, 2005) account for a lack of
-developmental change. The results of our meta-analysis are supported by
-a handful of studies directly comparing infants over a range of ages
-(Bailey \& Plunkett, 2002; Swingley \& Aslin, 2000; Zesiger et al.,
-2012), which also found no developmental change in mispronunciation
-sensitivity.
+developmental change. The results of our meta-analysis are reflecting a
+pattern previously reported by a handful of studies directly comparing
+infants over a range of ages (Bailey \& Plunkett, 2002; Swingley \&
+Aslin, 2000; Zesiger et al., 2012), which also found no developmental
+change in mispronunciation sensitivity.
 
@@
 growth, in comparison to development in general. Vocabulary growth is
-predicted to lead either to an increase ((PRIMIR; Curtin \& Werker,
-2007; Curtin et al., 2011; Werker \& Curtin, 2005)) or a decrease
-((Perceptual Attunement; Best, 1994, 1995)) in mispronunciation
-sensitivity; vocabulary has been shown to grow considerably in the age
-range considered in the current meta-analysis ((see
-\url{http://wordbank.stanford.edu}; Frank, Braginsky, Yurovsky, \&
-Marchman, 2017)). However, there are also substantial individual
-differences in the trajectory of vocabulary growth. The lack of
-developmental effects found in our meta-analysis may therefore be due to
-using age, instead of vocabulary size, as a facilitator for change in
-mispronunciation sensitivity. Yet, an analysis of the subset of studies
-reporting correlations between vocabulary size and object recognition
-effect sizes does not support this argument. Although an increasing
-vocabulary size lead to increased object recognition for correctly
-pronounced words, this was not the case for mispronunciations. Without
-evidence of a relationship between vocabulary size and mispronunciation
-object recognition and in combination with the low-powered analysis, it
-is difficult to draw a conclusion regarding the role of an increasing
-vocabulary size in mispronunciation sensitivity. In any case, this lack
-of evidence is contrary to the predictions of the Perceptual Attunement
-(Best, 1994, 1995) and PRIMIR (Curtin \& Werker, 2007; Curtin et al.,
-2011; Werker \& Curtin, 2005) accounts and further supports the overall
-lack of evidence for a developmental change.
-
-{[}Katie: Above has been edited to acknowledge that we can't measure
-mispronunciation sensitivity in the vocabulary correlations. Christina,
-can you read through it?{]}
-
-Evidence that infants accept a mispronunciation (object identification)
-while simultaneously holding correctly pronounced and mispronounced
-labels as separate (mispronunciation sensitivity) may indicate an
-abstract understanding of words' phonological structure. It appears that
-young infants may understand that the phonological form of
-mispronunciations and correct pronunciations do not match (phonological
-distinctiveness), but that the mispronunciation is a better label for
-the target compared to the distractor image (phonological constancy).
-The lack of age or vocabulary effects in our meta-analysis suggest that
-this understanding is present from an age when the earliest words are
-learned and is maintained throughout early lexical development. This
-implies mastery of the principles of phonological constancy and
-phonological distinctiveness at an age earlier than previously thought,
-which we recommend should be further explored experimentally and taken
-into consideration by future theoretical accounts.
-
-Although the lack of a relationship between mispronunciation sensitivity
-and vocabulary size may reflect a true effect, we note that this may
-also be the result of an underpowered analysis. Despite the theoretical
-implications, fewer than half of the papers included in this
-meta-analysis measured vocabulary (\emph{n} = 13; out of 32 papers
-total; see also Figure 4). There are more mispronunciation sensitivity
-studies published every year, perhaps due to the increased use of
-eye-tracker which reduce the need for offline coding, but this has not
-translated to an increasing number of mispronunciation sensitivity
-studies also measuring vocabulary scores. We suggest that this may be
-the result of publication bias favoring significant effects or an
-overall hesitation to invest in data collection that is not expected to
-yield significant outcomes.
+predicted to lead either to an increase (PRIMIR; Curtin \& Werker, 2007;
+Curtin et al., 2011; Werker \& Curtin, 2005) or a decrease (Perceptual
+Attunement; Best, 1994, 1995) in mispronunciation sensitivity;
+vocabulary has been shown to grow considerably in the age range
+considered in the current meta-analysis (see
+\url{http://wordbank.stanford.edu}; Frank et al., 2017). However, there
+are also substantial individual differences in the trajectory of
+vocabulary growth. The lack of developmental effects found in our
+meta-analysis may therefore be due to using age, instead of vocabulary
+size, as a moderator of mispronunciation sensitivity. We tried to
+address this issue by conducting an analysis of the subset of studies
+reporting correlations between infants' vocabulary size and their
+responses to correct and mispronounced labels. However, this analysis
+relied on only a few papers. We observed that an increasing vocabulary
+size lead to increased object recognition for correctly pronounced
+words; this was not the case for mispronunciations. However, it is
+difficult to draw any strong conclusions regarding the role of an
+increasing vocabulary size in mispronunciation sensitivity from this
+data.
+
+Why did we have so few samples for an analysis on vocabulary size to
+begin with? Despite the theoretical implications, fewer than half of the
+papers included in this meta-analysis measured vocabulary (\emph{n} =
+13; out of 32 papers total; see also Figure \ref{fig:Vocab-describe1}).
+There are more mispronunciation sensitivity studies published every
+year, perhaps due to the increased use of eye-trackers, which reduce the
+need for offline coding and thus make data collection much more
+efficient, but this has not translated to an increasing number of
+mispronunciation sensitivity studies also reporting vocabulary scores.
+We suggest that this may be the result of publication bias favoring
+significant effects or an overall hesitation to invest in data
+collection that is not expected to yield significant outcomes.
+
+What do our (tentative) results mean for theories of language
+development? Evidence that infants accept a mispronunciation (object
+identification) while simultaneously holding correctly pronounced and
+mispronounced labels as separate (mispronunciation sensitivity) may
+indicate an abstract understanding of words' phonological structure
+being in place early on. It appears that young infants may understand
+that the phonological form of mispronunciations and correct
+pronunciations do not match (phonological distinctiveness), but that the
+mispronunciation is a better label for the target compared to the
+distractor image (phonological constancy). The lack of age or vocabulary
+effects in our meta-analysis suggest that this understanding is present
+from an age when the earliest words are learned and is maintained
+throughout early lexical development. This implies mastery of the
+principles of phonological constancy and phonological distinctiveness at
+an age earlier than previously thought, which we recommend should be
+further explored experimentally and taken into consideration by future
+theoretical accounts.
 
@@
 the length of the post-naming analysis window as well as the type of
-dependent variable calculated in the experiment (see Figures 5 and 6).
+dependent variable calculated in the experiment (see Figures
+\ref{fig:Plot-post-name-cond-age} and
+\ref{fig:Plot-Within-cond-age-diff-score}).
 
@@
 A lack of a field standard can have serious consequences, as our
-analyses show. Depending on which analysis time window (see Figure 5) or
-dependent variable (see Figure 6) we focus on, we find support for any
-of the three possible trajectories of mispronunciation sensitivity. On
-the one hand, this limits the conclusions we can draw regarding our key
-research question. Without access to the full datasets or analysis code
-of the studies included in this meta-analysis, it is difficult to
-pinpoint the exact role played by these data analysis choices. On the
-other hand, this finding emphasizes that current practices of free,
-potentially ad hoc choices regarding data analyses are not sustainable
-if the field wants to move towards quantitative evidence for theories of
-language development.
+analyses show. Depending on which analysis time window (see Figure
+\ref{fig:Plot-post-name-cond-age}) or dependent variable (see Figure
+\ref{fig:Plot-Within-cond-age-diff-score}) we focus on, we find support
+for any of the three possible trajectories of mispronunciation
+sensitivity development. On the one hand, this limits the conclusions we
+can draw regarding our key research question. Without access to the full
+datasets or analysis code of the studies included in this meta-analysis,
+it is difficult to pinpoint the exact role played by these data analysis
+choices. On the other hand, this finding emphasizes that current
+practices of free, potentially ad hoc choices regarding data analyses
+are not sustainable if the field wants to move towards quantitative
+evidence for theories of language development.
 
@@
 can also contain a data-dependent description of how data analysis
-decisions will be made once data is collected. The peer reviewed form of
+decisions will be made once data is collected. The peer-reviewed form of
 preregistration, termed Registered Reports, has already been adopted by
@@
 lead to false negatives more frequently than expected, which in turn
-results in an unpublished body of literature (citationcitation). At the
-same time, underpowered studies with significant outcomes are likely to
-overestimate the effect, leading to wrong estimations of the population
-effect when paired with publication bias (citation). Overpowered studies
-mean that participants were tested unnecessarily, which has ethical
-implications particularly when working with infants and other difficult
-to recruit and test populations.
-
-{[}From Christina's comment: Christina needs to add citations here{]}
+results in an unpublished body of literature (Bergmann et al., 2018). At
+the same time, underpowered studies with significant outcomes are likely
+to overestimate the effect, leading to wrong estimations of the
+population effect when paired with publication bias (Jennions, Mù,
+Pierre, Curie, \& Cedex, 2002). Overpowered studies mean that
+participants were tested unnecessarily, which has ethical implications
+particularly when working with infants and other difficult to recruit
+and test populations.
 
@@
 tested, leading to two-way interactions (age versus mispronunciation
-sensitivity is a common example), which by some estimates requre four
-times the sample size to detect an effect of similar magnitue as the
+sensitivity is a common example), which by some estimates require four
+times the sample size to detect an effect of similar magnitude as the
 main effect for both ANOVA (Fleiss, 1986) and mixed-effect-model (Leon
@@
 sensitivity.
-
-{[}From Christina's comment: I want to do the math for more complex
-designs in pangea, i'll try to remember, if not, poke me
-\url{https://jakewestfall.shinyapps.io/pangea/} {]}
 
@@
 manipulations, such as the impact of the number of phonological features
-changed in the mispronunciations on mispronunciation sensitivity ((e.g.
-Mani \& Plunkett, 2011; White \& Morgan, 2008)) or sensitivity to
+changed in the mispronunciations on mispronunciation sensitivity (e.g.
+Mani \& Plunkett, 2011; White \& Morgan, 2008) or sensitivity to
 consonant and vowel mispronunciations (Højen et al., n.d.; Mani \&
@@
 additionally varied in their experimental design, such as whether
-infants were familiar with the distractor image ((see also Mani \&
-Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016); e.g. White \&
-Morgan, 2008) or whether the labels for the target and distractor images
-contained phonological overlap (Fernald, Swingley, \& Pinto, 2001).
-Futhermore, the infants included in this meta-analysis had a variety of
-native languages (English, Spanish, French, Dutch, German, Catalan,
-Danish, and Mandarin Chinese) and language backgrounds (monolingual,
-bilingual, monodialectal, multidialectal). Taken together, these
-variables have the potential to modulate infant mispronunciation
-sensitivity, but an investigation of these variables is out of the scope
-of the current meta-analysis. However, our dataset coded for and
-included these variables. We hope that future research will be able to
-better understand the role that these variables play in infants'
-sensitivity to mispronunciations.
-
-{[}Katie: To respond to your comment, Christina, we did include
-bilinguals. I checked and there was no influence in keeping or removing
-them.{]}
+infants were familiar with the distractor image (Mani \& Plunkett, 2011;
+Skoruppa et al., 2013; Swingley, 2016; White \& Morgan, 2008) or whether
+the labels for the target and distractor images contained phonological
+overlap (Fernald, Swingley, \& Pinto, 2001). Futhermore, the infants
+included in this meta-analysis had a variety of native languages
+(English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin
+Chinese) and language backgrounds (monolingual, bilingual,
+monodialectal, multidialectal). Taken together, these variables have the
+potential to modulate infant mispronunciation sensitivity, but an
+investigation of these variables is out of the scope of the current
+meta-analysis. However, our dataset includes these variables. We hope
+that future research will be able to better understand the role that
+these variables play in infants' sensitivity to mispronunciations.
 
@@
 this sensitivity was not modulated by infant age or vocabulary. This
-suggests that from a young age on, infants' word representations may be
-already phonologically well-specified. We recommend future theoretical
-frameworks take this evidence into account.
+suggests that from a young age on, before the vocabulary explosion,
+infants' word representations may be already phonologically
+well-specified. We recommend future theoretical frameworks take this
+evidence into account.
 
@@
 
+\emph{Acknowledgements}: The authors would like to thank Emelyne
+Gaudichau for valuable assistance in entering data. Author 1 was
+supported by the Agence Nationale de la Recherche (ANR-13-BSH2-0004) and
+by training grant DC-00046 from the National Institute of Deafness and
+Communicative Disorders of the National Institutes of Health. Author 2
+was supported by the European Horizon 2020 programme (Marie
+Skłodowska-Curie grant No 660911), the Agence Nationale de la Recherche
+(ANR-10-IDEX-0001-02 PSL*, ANR-10-LABX-0087 IEC) and the Fondation de
+France.
+
+\newpage
+
 \section{References}\label{references}
@@
 \hypertarget{ref-Frank2017}{}
-Frank, M. C., Braginsky, M., Yurovsky, D., \& Marchman, V. A. (2017).
-Wordbank: An open repository for developmental vocabulary data.
-\emph{Journal of Child Language}, \emph{44}(3), 677--694.
-doi:\href{https://doi.org/10.1017/S0305000916000209}{10.1017/S0305000916000209}
+Frank, M. C., Bergelson, E., Bergmann, C., Cristia, A., Floccia, C.,
+Gervain, J., \ldots{} Yurovsky, D. (2017). A collaborative approach to
+infant research: Promoting reproducibility, best practices, and
+theory-building. \emph{Infancy}, 1--15.
+doi:\href{https://doi.org/10.1111/infa.12182}{10.1111/infa.12182}
 
@@
 
+\hypertarget{ref-Jennions2002}{}
+Jennions, M. D., Mù, A. P., Pierre, Â., Curie, M., \& Cedex, F. P.
+(2002). Relationships fade with time : a meta-analysis of temporal
+trends in publication in ecology and evolution. \emph{Proceedings of the
+Royal Society of London B: Biological Sciences}, \emph{269}, 43--48.
+doi:\href{https://doi.org/10.1098/rspb.2001.1832}{10.1098/rspb.2001.1832}
+
 \hypertarget{ref-Jusczyk1995}{}
@@
 
+\hypertarget{ref-meta}{}
+Schwarzer, G. (2007). meta: An R package for meta-analysis. \emph{R
+News}, \emph{7}(3), 40--45.
+doi:\href{https://doi.org/10.1007/978-3-319-21416-0\%3E}{10.1007/978-3-319-21416-0\textgreater{}}
+
 \hypertarget{ref-Simmons2011}{}

### 2019-01-17 example_plot.R
Cleanup

@@ -1,77 +1,0 @@
-#setwd("~/Dropbox/MP_MA")
-
-library(ggplot2)
-library(wesanderson)
-library(reshape)
-library(doBy)
-
-std <- function(x) sd(x)/sqrt(length(x))
-
-correct <- rnorm(100, mean=0.730396429, sd=0.10471147)
-mispronunciation <- rnorm(100, mean=0.612614286, sd=0.093135265)
-
-cm <- data.frame(cbind(correct, mispronunciation))
-cm$sub <- seq(1, nrow(cm))
-
-dat.m2 <- melt(cm,
-               id=c(3),
-               measure=c(1:2),
-               variable="Measure", na.rm=T)
-names(dat.m2) <- c("sub", "condition", "PTL")
-
-# Color Blind palette:
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
-
-box <- ggplot(data=dat.m2, aes(x=condition, y=PTL, fill=condition)) +
-  geom_boxplot()+
-  #scale_fill_manual(values=wes_palette(name="Darjeeling"))+
-  scale_fill_manual(values=cbPalette)+
-  theme_bw()+
-  annotate("segment", x = .67, xend = .67, y = .7, yend = .5, colour="black", size=1, arrow=arrow())+
-  annotate("segment", x = 1.2, xend = 2.2, y = .96, yend = .96, colour="black", size=1)+
-  annotate("text", x = .5, y = .65, parse = TRUE, label = "recognition",angle = 90, size = 10)+
-  annotate("text", x = 1.75, y = .99, parse = TRUE, label = "misp_sensitivity", size = 10)+
-  geom_hline(yintercept = .5)+
-  coord_cartesian(ylim = c(.35, 1))+
-  theme(text = element_text(size=30),
-        legend.position = "bottom",
-        legend.title = element_blank(),
-        axis.text.x = element_blank(),
-        axis.title.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        panel.grid.major = element_blank(), 
-        panel.grid.minor = element_blank())+
-  ylab("Proportion of Target Looks")
-
-ggsave("figures/Example_boxplot.jpg", box)
-
-d.p <- summaryBy(PTL~condition, data=dat.m2, FUN=c(mean, std))
-
-
[…]

### 2019-01-18 VonHolzenBergmann_MPMetaAnalysis.Rmd
further cleanup and additional documents
separated experimental design moderator analysis to second repo:
InMisSens2
Added Survey Protocol, Literature Search, and PRISMA checklist

--- 2019-01-10 Paper_Analyses.Rmd
@@
 ---
-title             : "The development of infants' responses to mispronunciations - A Meta-Analysis"
+title             : "The development of infants' responses to mispronunciations: A Meta-Analysis"
 shorttitle        : "Mispronunciation Meta-Analysis"
@@
 
+authornote: |
+  The authors each declare that they have no conflict of interest.
+
 abstract: |
@@
 The results show that although infants are sensitive to mispronunciations, they still accept these altered forms as labels for target objects.
-Interestingly, this ability is not modulated by age or vocabulary size, challenging existing theories and suggesting that a mature understanding of native language phonology is present in infants from an early age.
+Interestingly, this ability is not modulated by age or vocabulary size, challenging existing theories and suggesting that a mature understanding of native language phonology is present in infants from an early age, possibly before the vocabulary explosion.
 Despite this finding, we discuss potential data analysis choices that may influence different conclusions about mispronunciation sensitivity development as well as offer recommendations to improve best practices in the study of mispronunciation sensitivity.
 
-keywords          : "language acquisition; mispronunciation sensitivity; word recognition; meta-analysis; lexicon"
-wordcount         : "X"
+keywords          : "language acquisition; mispronunciation sensitivity; word recognition; meta-analysis; lexicon; infancy"
 
@@
 cat-hat).
-To build robust language knowledge, it seems ueful to acquire this ability early during development.
+To build robust language knowledge, it seems useful to acquire this ability early during development.
 Indeed, before children can correctly pronounce a word, they already are aware that slight phonological deviations might signal a change in word meaning [@clark1977].
 This mispronunciation sensitivity reflects the specificity with which infants represent the phonological information of familiar words.
-As infants continue to develop into expert language users, their language processing matures and becomes more efficient, including their knowledge of what consistutes a permissible versus word-changing phonological deviation.
+As infants continue to develop into expert language users, their language processing matures and becomes more efficient, including their knowledge of what constitutes a permissible versus word-changing phonological deviation.
 In this paper, we aggregate and analyze the nearly 20 years of literature investigating mispronunciation sensitivity in infants in an attempt to uncover its characteristics and the trajectory of its development.
 
-  At the turn of the millenium, infant language acquisition researchers had established that during their first years of life, infants are sensitive to changes in the phonetic detail of newly segmented words [@Jusczyk1995] and learned minimal pairs [@Stager1997].
+  At the turn of the millenium, infant language acquisition researchers had established that during their first two years of life, infants are sensitive to changes in the phonetic detail of newly segmented words [@Jusczyk1995] and learned minimal pairs [@Stager1997].
 Furthermore, when presented with familiar image pairs, children fixate on the referent of a spoken label [@Fernald1998; @Tincoff1999].
 @Swingley2000 were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English saw pairs of images (e.g.
-a baby and a dog) and their eye movements to each image were recorded and subsequently coded offline.
+a baby and a dog) and their eye movements to each image were recorded.
 On "correct" trials, children heard the correct label for one of the images (e.g.
@@
 
-  In the current study, we focus on infants' developing ability to correctly apply the principles of phonological distinctiveness and constancy by using a meta-analytic approach to investigate mispronunciation sensitivity.
+  In the current study, we focus on infants' developing ability to correctly apply the principles of phonological constancy and distinctiveness by using a meta-analytic approach to investigate mispronunciation sensitivity.
 Considering that infants are sensitive to mispronunciations and that, in general, their processing matures with development, we examine the shape of mispronunciation sensitivity over the course of the second and third year.
 There are three distinct possibilities how mispronunciation sensitivity might change as infants become native speakers, which are all respectively supported by single studies and additionally two possibilities are predicted by key theoretical accounts.
-By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see Frank et al., 2018; for a notable exception).
+By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies ([see @Frank2017; for a notable exception).
 Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.
-
-[Katie: Christina, do you know which citation the Frank et al., 2018 citation is referring to above? He's published a gazilion papers in 2018]
 
@@
   According to a different theoretical framework, young infants may instead begin with phonologically broad representations for familiar words and only refine their representations as language experience accumulates.
-PRIMIR ([Processing Rich Information from Multidimensional Interactive Representations; @Curtin2007; @Curtin2011; @Werker2005]) describes the development of phonemic categories emerging as the number of word form-meaning linkages increases.
+PRIMIR [Processing Rich Information from Multidimensional Interactive Representations; @Curtin2007; @Curtin2011; @Werker2005] describes the development of phonemic categories emerging as the number of word form-meaning linkages increases.
 Vocabulary growth, therefore, promotes more detailed phonological representations in familiar words.
@@
   Research following the seminal study by @Swingley2000 has extended mispronunciation sensitivity to infants as young as 9 months [@Bergelson2017], indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations.
-Regarding the change in mispronunciation sensitivity over development, however, only about half of studies have compared more than one age group on the same mispronunciation task (see Table 1), making the current meta-analysis very informative.
+Regarding the change in mispronunciation sensitivity over development, however, only about half of studies have compared more than one age group on the same mispronunciation task (see Table 1).
+In those single studies all possible patterns of development lined out above have been reported, making the current meta-analysis very informative.
+
   One study has found evidence for infants to become *less* sensitive to mispronunciations as they develop.
@@
 In other words, the native language constraints which *kinds* of mispronunciations infants are sensitive to first, and that as infants develop, they become sensitive to other mispronunciations.
-These studies award support to the prediction that mispronunciation sensitivity improves with development.
+These studies award support to the prediction that mispronunciation sensitivity increases with development.
 
@@
 They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation sensitivity) did not.
-This suggests that as children develop, they are more likely to look at the target in the presence of a correct or mispronounced label, but that the difference between the two does not change.
+This suggests that as children develop, they are more likely to look at the target in the presence of a correct or mispronounced label, but that the difference between looks elicited by the two conditions does not change.
 A similar response pattern has been found for British English learning infants aged between 18 and 24 months [@Bailey2002] as well as younger French-learning infants at 12 and 17 months [@Zesiger2012].
@@
 
-In sum, the studies we have reviewed begin to paint a picture of the development of mispronunciation sensitivity.
+In sum, the studies we have reviewed begin to paint a picture of the development of infants' mispronunciation sensitivity.
 Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding of the big picture of early language development.
-Meta-analyses can provide unique insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and their mispronunciations sensitivity.
+Meta-analyses can provide unique insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and of their mispronunciations sensitivity.
 Because we aggregate data over various age groups, this meta-analysis can also investigate the role of maturation by assessing the impact of age and vocabulary size.
@@
 To this end, we provide all data and analysis scripts on the supplementary website (https://osf.io/rvbjs/) and open our meta-analysis up for updates [@Tsuji2014].
-The most recent version is available via the website and the interactive platform MetaLab ([https://metalab.stanford.edu; @Bergmann2018]).
-Since the present paper was written with embedded analysis scripts in R [@R, @RMarkdown, @papaja], it is always possible to re-analyze an updated dataset.
+The most recent version is available via the website and the interactive platform MetaLab [https://metalab.stanford.edu; @Bergmann2018].
+Since the present paper was written with embedded analysis scripts in R [@R] using the papaja package [@papaja] in R Markdown [@RMarkdown], it is always possible to re-analyze an updated dataset.
 In addition, we followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials [@Moher2009].
-Figure 1 plots our PRISMA flowchart illustrating the paper selection procedure.
+Figure \@ref(fig:PRISMA-image) plots our PRISMA flowchart illustrating the paper selection procedure.
 
@@
 
-```{r PRISMA_image, echo= FALSE, fig.cap="A PRISMA flowchart illustrating the selection procedure used to include studies in the current meta-analysis."}
+```{r PRISMA-image, echo= FALSE, fig.cap="A PRISMA flowchart illustrating the selection procedure used to include studies in the current meta-analysis."}
 
@@
 #kable(Sum_table, col.names = c("Paper", "Publication format", "Age", "Vocabulary", "N Effect Sizes"))
-apa_table(Sum_table, col.names = c("Paper", "Publication format", "Age", "Vocabulary", "N Effect Sizes"), caption = "Summary of all studies.", landscape = TRUE)
+apa_table(Sum_table, col.names = c("Paper", "Publication format", "Age", "Vocabulary", "N Effect Sizes"), caption = "Summary of all studies.
+Age is calculated by truncating the mean age reported in the paper.
+The abbreviations Comp and Prod refer to comprehension and production, respectively.", landscape = TRUE)
 
@@
 We separated conditions according to whether or not the target word was mispronounced to be able to investigate infants' looking to the target picture as well as their mispronunciation sensitivity, which is the difference between looks to the target in correct and mispronounced trials.
-When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  ([e.g., consonant versus vowel mispronunciations; @Mani2007]).
+When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  [e.g., consonant versus vowel mispronunciations; @Mani2007].
 The fact that the same infants contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section).
@@
 looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance.
-Upon request we were provided with correlation values for one paper [@Altvater2010]; we were able to compute correlations using means, standard deviations, and t-values for `r with(corr_info, n_unique[imputed_corr == "no"])` papers ([following @Csibra2016; see also @Rabagliati2018]).
-Correlations were imputed for the remaining papers ([see @Black2017 for the same procedure]).
+Upon request we were provided with correlation values for one paper [@Altvater2010]; we were able to compute correlations using means, standard deviations, and t-values for `r with(corr_info, n_unique[imputed_corr == "no"])` papers [following @Csibra2016; see also @Rabagliati2018].
+Correlations were imputed for the remaining papers [see @Black2017 for the same procedure].
 For two papers, we could not derive any effect size [@Ballem2005; @Renner2017], and for a third paper, we do not have sufficient information in one record to compute effect sizes [@Skoruppa2013].
@@
 
-[Katie: Mention of Renner here]
-
 To take into account the fact that the same infants contributed to multiple datapoints, we analyze our results in a multilevel approach using the R [@R] package metafor [@metafor].
@@
 
-Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(comparison_info, count[within_measure == "pre_post"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post"])` papers), thus reporting two variables, or compared post-naming PTL with a chance level of 50%, (*n* = `r with(comparison_info, count[within_measure == "post"])` records from `r with(comparison_info, n_unique[within_measure == "post"])` papers).
+Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(comparison_info, count[within_measure == "pre_post"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post"])` papers), thus reporting two variables, or compared post-naming PTL with a chance level of 50% (*n* = `r with(comparison_info, count[within_measure == "post"])` records from `r with(comparison_info, n_unique[within_measure == "post"])` papers).
 For all these comparisons, positive values (either as reported or after subtraction of chance level or a pre-naming baseline PTL) indicate target looks towards the target object after hearing the label, i.e.
@@
 In the psychological sciences, there is a documented reluctance to publish null results.
-As a result, significant results tend to be over-reported and thus might be over-represented in our meta-analyses ([see @Ferguson2012]).
+As a result, significant results tend to be over-reported and thus might be over-represented in our meta-analyses [see @Ferguson2012].
 To examine whether this is also the case in the mispronunciation sensitivity literature, which would bias the data analyzed in this meta-analysis, we conducted two tests.
@@
 
-Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app ([v4.0, http://p-curve.com; @pcurve]).
+Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app [v4.0, http://p-curve.com; @pcurve].
 This p-curve tests for evidential value by examining whether the p-values follow the expected distribution of a right skew in case the alternative hypothesis is true, versus a flat distribution that speaks for no effect being present in the population and all observed significant effects being spurious.
@@
 The models reported here are multilevel random-effects models of variance-weighted effect sizes, which we computed with the R [@R] package metafor [@metafor].
-To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we introduced age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44) as a moderator to our main model.
-For a subsequent exploratory investigation of experimental characteristics, we introduced each characteristic as a moderator (more detail below).
+To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we first introduced age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44) as a moderator to our main model.
+Second, we analyzed the correlation between reported vocabulary size and mispronunciation sensitivity using the R [@R] package meta [@meta].
+Finally, for a subsequent exploratory investigation of experimental characteristics, we introduced each characteristic as a moderator (more detail below).
 
@@
 
-Figure 2 shows the funnel plots for both correct pronunciations and mispronunciations ([code adapted from @Sakaluk2016]).
+Figure \@ref(fig:FunnelCombo) shows the funnel plots for both correct pronunciations and mispronunciations [code adapted from @Sakaluk2016].
 Funnel plot asymmetry was significant for both correct pronunciations (Kendall's $\tau$ = `r r2(rmac$tau)`, *p* `r psig(rmac$pval)`) and mispronunciations (Kendall's $\tau$ = `r r2(rmam$tau)`, *p* `r psig(rmam$pval)`).
-These results, quantifying the asymmetry in the funnel plots (Figure 1), indicate bias in the literature.
-This is particularly evident for correct pronunciations, where larger effect sizes have greater variance (bottom right corner) and there are a smaller number of more precise effect sizes (i.e.
-smaller variance) than expected (top left, outside the triangle).
+These results, quantifying the asymmetry in the funnel plots (Figure \@ref(fig:FunnelCombo)), indicate bias in the literature.
+This is particularly evident for correct pronunciations, where larger effect sizes have greater variance (bottom right corner) and the more precise effect sizes (i.e.
+smaller variance) tend to be smaller than expected (top left, outside the triangle).
 
 The stronger publication bias for correct pronunciation might reflect the status of this condition as a control.
-If infants were not looking to the target picture after hearing the correct label, the overall experiment design is called into questions.
+If infants were not looking to the target picture after hearing the correct label, the overall experiment design is called into question.
 However, even in a well-powered study one would expect the regular occurrence of null results even though as a population infants would reliably show the expected object identification effect.
@@
     axis.line=element_line(),
-    text=element_text(family='Times', size=22),
+    text=element_text(family='Times', size=18),
     legend.position='none')
@@
   #Add your data-points to the scatterplot
-  geom_point(size = 2.5, colour="black") +
+  geom_point(size = 2, colour="black", alpha = .5) +
   #
@@
     #Add your data-points to the scatterplot
-    geom_point(size = 2.5, colour="black") +
+  geom_point(size = 2, colour="black", alpha = .5) +
     #
@@
 ```{r FunnelCombo, echo = FALSE, fig.cap="Funnel plots for object identification, plotting the standard error of the effect size in relation to the effect size.
-The black line marks zero, the dashed grey line marks the effect estimate, and the grey line marks funnel plot asymmetry."}
+The black line marks zero, the dashed grey line marks the effect estimate, and the grey line marks funnel plot asymmetry.", results="hide"}
 
@@
 
-```{r PcurveExport}
+```{r PcurveExport, results = "hide"}
 
@@
 The variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was significantly different from zero `r CI_p(sum_eff)`.
-This is a small to medium effect size ([according to the criteria set by @Mills-Smith2015]).
+This is a small to medium effect size [according to the criteria set by @Mills-Smith2015].
 That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants tended to fixate on the corresponding object.
@@
 To this end, we combined the two datasets.
-When condition was included (correct, mispronounced), the moderator test was significant, `r mod_test(rma_MPeffect)`.
-The estimate for mispronunciation sensitivity was `r g_SE(sum_eff)`, and infants' looking times across conditions were significantly different `r CI_p(sum_eff)`.
+When condition was included (correct, mispronounced), the moderator test was significant (`r mod_test(rma_MPeffect)`).
+The estimate for mispronunciation sensitivity was `r g_SE(sum_eff)`, and infants' looking behavior across conditions was significantly different `r CI_p(sum_eff)`.
 This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations.
@@
 
-To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44 for Figure 3).
+To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44 for Figure \@ref(fig:PlotMPEffect)).
 
@@
 We note that the estimates in both cases are positive, however, which is in line with the general assumption that infants’ language processing overall improves as they mature [@Fernald1998].
-We plot both object recognition and mispronunciation sensitivity as a function of age in Figure 3.
+We plot both object recognition and mispronunciation sensitivity as a function of age in Figure \@ref(fig:PlotMPEffect).
 
@@
 The interaction between age and mispronunciation sensitivity, however, was not significant ($\beta$ `r full_estimate(sum_eff)`); the moderator test was mainly driven by the difference between conditions.
-The small estimate, as well as inspection of Figure 2, suggests that as infants age, their mispronunciation sensitivity neither increases or decreases.
+The small estimate, as well as inspection of Figure \@ref(fig:PlotMPEffect), suggests that as infants age, their mispronunciation sensitivity neither increases or decreases.
 
@@
 Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) by participant age.
-For both panels, point size depicts inverse variance and the dashed line indicates zero (chance)."}
+For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
 
@@
 
-[Katie: Written as if moderators can not be added to metacor()]
-
 ```{r ComprehensionMeta_correct}
@@
 
-Figure 4 plots the year of publication for all the mispronunciation sensitivity studies included in this meta-analysis.
+Figure \@ref(fig:Vocab-describe1) plots the year of publication for all the mispronunciation sensitivity studies included in this meta-analysis.
 This figure illustrates two things: the increasing number of mispronunciation sensitivity studies and the decreasing number of mispronunciation studies measuring vocabulary.
@@
 
-```{r Vocab_describe1, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (orange), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (green)."}
+```{r Vocab-describe1, echo = FALSE, fig.width=10,fig.height=8, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (orange), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (green).", results="hide"}
 #how did vocabulary collection change over time?
@@
 
-vocab_year
+#vocab_year
 
@@
   dev.off()
+
+grid.draw(vocab_year)
 
@@
 The results seem clear: Although infants consider a mispronunciation to be a better match to the target image than to a distractor image, there was a constant and stable effect of mispronunciation sensitivity.
-This did not change with development nor with vocabulary size.
+This did not change with development, and we might consider age a proxy for vocabulary size.
+We observe that the data for directly reported vocabulary size were too sparse to draw strong conclusions.
 Of the three predictions about the development of infants' sensitivity to mispronunciations discussed in the Introduction, the present results lend some support for the proposal that mispronunciation sensitivity stays consistent as infants develop.
@@
 In order to have publishable results, adjustments to the analysis approach could be made until a significant, but spurious, effect of mispronunciation sensitivity is found.
-This would lead to an increase in significant results and alter to observed developmental trajectory of mispronunciation sensitivity.
+This would lead to an increase in significant results and alter the observed developmental trajectory of mispronunciation sensitivity.
 Such a scenario is in line with the publication bias we observe [@Simmons2011].
-We examine whether variation in the approach to data analysis may be have an influence on findings of mispronunciation sensitivity.
+We examine whether variation in the approach to data analysis may be have an influence on our conclusions regarding infants’ developing mispronunciation sensitivity.
 
@@
 .
-showing that target and distractor fixations tend to diverge at around 400 ms." ([@Swingley2000, p.
-155]).
+showing that target and distractor fixations tend to diverge at around 400 ms." [@Swingley2000, p.
+155].
 Upon inspecting the offset time values used in the papers in our meta-analysis, the majority used a similar offset time value (between 360 and 370 ms) for analysis (*n* = `r with(offset_bin_info, n_exp_conditions[offset_bin == "367"])`), but offset values ranged from `r with(offset_bin_info, min(offset_bin))` to `r with(offset_bin_info, max(offset_bin))` ms, and were not reported for `r with(offset_info, n_exp_conditions[is.na(offset)])` experimental conditions.
@@
 The estimate for the interaction between post-naming analysis window and condition was small but significant ($\beta$`r full_estimate(rma_post_dur_MS_eff)`).
-This relationship is plotted in Figure 3a.
+This relationship is plotted in Figure \@ref(fig:Plot-post-name-cond-age)a.
 The results suggest that the size of the post-naming analysis window significantly impacted our estimate of mispronunciation sensitivity.
@@
 The estimate for the  three-way-interaction between condition, size of the post-naming analysis window, and age was small, but significant ($\beta$ `r full_estimate(rma_post_dur_AGE_MS_eff)`).
-As can be seen in Figure 3b, a smaller post-naming analysis window leads to a greater increase in measured mispronunciation sensitivity with development.
+As can be seen in Figure \@ref(fig:Plot-post-name-cond-age)b, a smaller post-naming analysis window leads to a greater increase in measured mispronunciation sensitivity with development.
 For example, when experimental conditions were analyzed with a post-naming analysis window of 2000 ms or less, mispronunciation sensitivity seems to increase with infant age.
@@
 
-```{r Plot_post_name_cond_age, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different lengths of the post-naming analysis window: 2000 ms or less (orange), 2001 to 3000 ms (blue), and 3001 ms or greater (green).
+```{r Plot-post-name-cond-age, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different lengths of the post-naming analysis window: 2000 ms or less (orange), 2001 to 3000 ms (blue), and 3001 ms or greater (green).
 Although length of the post-naming analysis window was included as a continuous variable in the meta-analytic model, it is divided into categories for ease of viewing.
 Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity as a function of age.
-The lines plot the linear regression and the gray shaded area indicates the standard error."}
+The lines plot the linear regression and the gray shaded area indicates the standard error.", results="hide"}
 
@@
 Although we found no relationship between offset time and infant age, we also examined whether the size of offset time modulated the measure of mispronunciation sensitivity over infant age.
-When both offset time and condition were included as moderators, the moderator test was significant (`r mod_test(rma_offset_AGE_MS)`), but the three-way-interaction between condition, offset time, and age was again zero ($\beta$ `r full_estimate(rma_offset_AGE_MS_eff)`.
+When both offset time and condition were included as moderators, the moderator test was significant (`r mod_test(rma_offset_AGE_MS)`), but the three-way-interaction between condition, offset time, and age was again zero ($\beta$ `r full_estimate(rma_offset_AGE_MS_eff)`).
 Taken together, these results suggest that offset time does not modulate measured mispronunciation sensitivity.
@@
 Post can be considered similar to one another, in that they are calculated on the same type of data and consider pre-naming preferences.
-It should be noted, however, that the Difference Score can better counteract participant- and item-level differences, whereas Pre vs.
+It should be noted, however, that the Difference Score may better counteract participant- and item-level differences, whereas Pre vs.
 Post is a group-level measure.
@@
 
-##########
+#
 
@@
 Post and condition was significantly smaller than that of the Post dependent variable ($\beta$`r full_estimate(rma_within_MS_effprepost)`), but the difference between the Difference Score and Post in the interaction with condition was small and not significant ($\beta$`r full_estimate(rma_within_MS_effdiff)`).
-This relationship is plotted in Figure 4a.
+This relationship is plotted in Figure \@ref(fig:Plot-Within-cond-age-diff-score)a.
 The results suggest that the reported dependent variable significantly impacted the size of the estimated mispronunciation sensitivity effect, such that studies reporting the Post.
@@
 Post, condition, and age was significantly smaller than that of the Post dependent variable ($\beta$`r full_estimate(rma_within_AGE_MS_effprepost)`), but the difference between the Difference Score and Post in the interaction with condition and age was small and not significant ($\beta$`r full_estimate(rma_within_AGE_MS_effdiff)`).
-This relationship is plotted in Figure 4b.
+This relationship is plotted in Figure \@ref(fig:Plot-Within-cond-age-diff-score)b.
 When the dependent variable reported was Pre vs.
@@
 
-```{r Plot_Within_cond_age_diff_score, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (orange), Post vs.
+```{r Plot-Within-cond-age-diff-score, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (orange), Post vs.
 Pre (blue), and Difference Score (green).
 Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity as a function of age.
-The lines plot the linear regression and the gray shaded area indicates the standard error."}
+The lines plot the linear regression and the gray shaded area indicates the standard error.", results="hide"}
 
@@
 In this meta-analysis, we set out to quantify and assess the developmental trajectory of infants’ sensitivity to mispronunciations.
-Overall, the results of the meta-analysis showed that infants reliably fixate the target object when given both correctly pronounced and mispronounced labels.
-Infants not only recognize object labels when they were correctly pronounced, but are also likely to accept mispronunciations as acceptable labels for targets, in the presence of a distractor image.
+Overall, the results of the meta-analysis showed that infants reliably fixate the target object when hearing both correctly pronounced and mispronounced labels.
+Infants not only recognize object labels when they were correctly pronounced, but are also likely to accept mispronunciations as labels for targets, in the presence of a distractor image.
 Nonetheless, there was a considerable difference in target fixations in response to correctly pronounced and mispronounced labels, suggesting that infants show an overall mispronunciation sensitivity based on the current experimental literature.
@@
 Of the two mainstream theories identified in our literature review, neither the Perceptual Attunement account [@Best1994; @Best1995] nor PRIMIR [@Curtin2007; @Werker2005; @Curtin2011] account for a lack of developmental change.
-The results of our meta-analysis are supported by a handful of studies directly comparing infants over a range of ages [@Swingley2000; @Bailey2002; @Zesiger2012], which also found no developmental change in mispronunciation sensitivity.
+The results of our meta-analysis are reflecting a pattern previously reported by a handful of studies directly comparing infants over a range of ages [@Swingley2000; @Bailey2002; @Zesiger2012], which also found no developmental change in mispronunciation sensitivity.
 
 Both the Perceptual Attunement [@Best1994; @Best1995] and PRIMIR [@Curtin2007; @Werker2005; @Curtin2011] accounts link a change of mispronunciation sensitivity specifically with vocabulary growth, in comparison to development in general.
-Vocabulary growth is predicted to lead either to an increase ([PRIMIR; @Curtin2007; @Werker2005; @Curtin2011]) or a decrease ([Perceptual Attunement; @Best1994; @Best1995]) in mispronunciation sensitivity; vocabulary has been shown to grow considerably in the age range considered in the current meta-analysis ([see http://wordbank.stanford.edu; @Frank2017]).
+Vocabulary growth is predicted to lead either to an increase [PRIMIR; @Curtin2007; @Werker2005; @Curtin2011] or a decrease [Perceptual Attunement; @Best1994; @Best1995] in mispronunciation sensitivity; vocabulary has been shown to grow considerably in the age range considered in the current meta-analysis [see http://wordbank.stanford.edu; @Frank2017].
 However, there are also substantial individual differences in the trajectory of vocabulary growth.
-The lack of developmental effects found in our meta-analysis may therefore be due to using age, instead of vocabulary size, as a facilitator for change in mispronunciation sensitivity.
-Yet, an analysis of the subset of studies reporting correlations between vocabulary size and object recognition effect sizes does not support this argument.
-Although an increasing vocabulary size lead to increased object recognition for correctly pronounced words, this was not the case for mispronunciations.
-Without evidence of a relationship between vocabulary size and mispronunciation object recognition and in combination with the low-powered analysis, it is difficult to draw a conclusion regarding the role of an increasing vocabulary size in mispronunciation sensitivity.
-In any case, this lack of evidence is contrary to the predictions of the Perceptual Attunement [@Best1994; @Best1995] and PRIMIR [@Curtin2007; @Werker2005; @Curtin2011] accounts and further supports the overall lack of evidence for a developmental change.
-
-[Katie: Above has been edited to acknowledge that we can't measure mispronunciation sensitivity in the vocabulary correlations. Christina, can you read through it?]
-
-Evidence that infants accept a mispronunciation (object identification) while simultaneously holding correctly pronounced and mispronounced labels as separate (mispronunciation sensitivity) may indicate an abstract understanding of words' phonological structure.
+The lack of developmental effects found in our meta-analysis may therefore be due to using age, instead of vocabulary size, as a moderator of mispronunciation sensitivity.
+We tried to address this issue by conducting an analysis of the subset of studies reporting correlations between infants’ vocabulary size and their responses to correct and mispronounced labels.
+However, this analysis relied on only a few papers.
+We observed that an increasing vocabulary size lead to increased object recognition for correctly pronounced words; this was not the case for mispronunciations.
+However, it is difficult to draw any strong conclusions regarding the role of an increasing vocabulary size in mispronunciation sensitivity from this data.
+
+Why did we have so few samples for an analysis on vocabulary size to begin with?
+Despite the theoretical implications, fewer than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total; see also Figure \@ref(fig:Vocab-describe1)).
+There are more mispronunciation sensitivity studies published every year, perhaps due to the increased use of eye-trackers, which reduce the need for offline coding and thus make data collection much more efficient, but this has not translated to an increasing number of mispronunciation sensitivity studies also reporting vocabulary scores.
+We suggest that this may be the result of publication bias favoring significant effects or an overall hesitation to invest in data collection that is not expected to yield significant outcomes.
+
+What do our (tentative) results mean for theories of language development?
+Evidence that infants accept a mispronunciation (object identification) while simultaneously holding correctly pronounced and mispronounced labels as separate (mispronunciation sensitivity) may indicate an abstract understanding of words' phonological structure being in place early on.
 It appears that young infants may understand that the phonological form of mispronunciations and correct pronunciations do not match (phonological distinctiveness), but that the mispronunciation is a better label for the target compared to the distractor image (phonological constancy).
@@
 This implies mastery of the principles of phonological constancy and phonological distinctiveness at an age earlier than previously thought, which we recommend should be further explored experimentally and taken into consideration by future theoretical accounts.
-
-Although the lack of a relationship between mispronunciation sensitivity and vocabulary size may reflect a true effect, we note that this may also be the result of an underpowered analysis.
-Despite the theoretical implications, fewer than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total; see also Figure 4).
-There are more mispronunciation sensitivity studies published every year, perhaps due to the increased use of eye-tracker which reduce the need for offline coding, but this has not translated to an increasing number of mispronunciation sensitivity studies also measuring vocabulary scores.
-We suggest that this may be the result of publication bias favoring significant effects or an overall hesitation to invest in data collection that is not expected to yield significant outcomes.
 
@@
 To explore whether this variation contributed to the lack of developmental change observed in the overall meta-analysis, we included these variables as moderators in a set of exploratory analyses.
-We noted an interesting pattern of results, specifically that different conclusions about mispronunciation sensitivity, but more notably mispronunciation sensitivity development, could be drawn depending on the length of the post-naming analysis window as well as the type of dependent variable calculated in the experiment (see Figures 5 and 6).
+We noted an interesting pattern of results, specifically that different conclusions about mispronunciation sensitivity, but more notably mispronunciation sensitivity development, could be drawn depending on the length of the post-naming analysis window as well as the type of dependent variable calculated in the experiment (see Figures \@ref(fig:Plot-post-name-cond-age) and \@ref(fig:Plot-Within-cond-age-diff-score)).
 
@@
 A lack of a field standard can have serious consequences, as our analyses show.
-Depending on which analysis time window (see Figure 5) or dependent variable (see Figure 6) we focus on, we find support for any of the three possible trajectories of mispronunciation sensitivity.
+Depending on which analysis time window (see Figure \@ref(fig:Plot-post-name-cond-age)) or dependent variable (see Figure \@ref(fig:Plot-Within-cond-age-diff-score)) we focus on, we find support for any of the three possible trajectories of mispronunciation sensitivity development.
 On the one hand, this limits the conclusions we can draw regarding our key research question.
@@
 Preregistration can serve as proof of a priori decisions regarding data analysis, which can also contain a data-dependent description of how data analysis decisions will be made once data is collected.
-The peer reviewed form of preregistration, termed Registered Reports, has already been adopted by a large number of developmental journals, and general journals that publish developmental works, showing the field’s increasing acceptance of such practices for hypothesis-testing studies.
+The peer-reviewed form of preregistration, termed Registered Reports, has already been adopted by a large number of developmental journals, and general journals that publish developmental works, showing the field’s increasing acceptance of such practices for hypothesis-testing studies.
 Sharing data (Open Data) can allow others to re-analyze existing datasets to both examine the impact of analysis decisions and cumulatively analyze different datasets in the same way.
@@
 Failing to take effect sizes into account can both lead to underpowered research and to testing too many participants, both consequences are undesirable for a number of reasons that have been discussed in depth elsewhere.
-We will just briefly mention two that we consider most salient for theory building: Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature (citationcitation).
-At the same time, underpowered studies with significant outcomes are likely to overestimate the effect, leading to wrong estimations of the population effect when paired with publication bias (citation).
+We will just briefly mention two that we consider most salient for theory building: Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature [@Bergmann2018].
+At the same time, underpowered studies with significant outcomes are likely to overestimate the effect, leading to wrong estimations of the population effect when paired with publication bias [@Jennions2002].
 Overpowered studies mean that participants were tested unnecessarily, which has ethical implications particularly when working with infants and other difficult to recruit and test populations.
-
-[From Christina's comment: Christina needs to add citations here]
 
@@
 pat <- pwr.anova.test(k = 2, n = median_sample, f = mp_effect, sig.level = 0.05, power = NULL)
+ptt <- pwr.t.test(n = median_sample, d = mp_effect, sig.level = 0.05, power = NULL)
 
@@
 pat.est <- pwr.anova.test(k = 2, n = NULL, f = mp_effect, sig.level = 0.05, power = .8)
+ptt.est <- pwr.t.test(n = NULL, d = mp_effect, sig.level = 0.05, power = .8)
 
@@
 These calculations suggest that for the comparison of responses for correct pronunciations and mispronunciations, the studies included in this meta-analysis contain well-powered analyses.
-However, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which will require even larger sample sizes.
+However, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates require four times the sample size to detect an effect of similar magnitude as the main effect for both ANOVA [@Fleiss1986] and mixed-effect-model [@Leon2009] analyses.
 We thus strongly advocate for a consideration of power and the reported effect sizes to test infants’ mispronunciation sensitivity.
 
-[From Christina's comment: I want to do the math for more complex designs in pangea, i’ll try to remember, if not, poke me https://jakewestfall.shinyapps.io/pangea/ ]
-
 ## Limitations
@@
 The current meta-analysis aggregated studies designed to investigate mispronunciation sensitivity, but we note that these studies varied in their approach to study our phenomenon of interest.
-For example, some studies investigated specific questions which required additional manipulations, such as the impact of the number of phonological features changed in the mispronunciations on mispronunciation sensitivity ([e.g.
-@Mani2011; @White2008]) or sensitivity to consonant and vowel mispronunciations [@Mani2007; @Mani2010kepstups; @Hojen; @Swingley2016].
-The studies in our sample additionally varied in their experimental design, such as whether infants were familiar with the distractor image ([e.g.
-@White2008; see also @Mani2011; @Skoruppa2013; @Swingley2016)] or whether the labels for the target and distractor images contained phonological overlap [@Fernald2001a].
+For example, some studies investigated specific questions which required additional manipulations, such as the impact of the number of phonological features changed in the mispronunciations on mispronunciation sensitivity [e.g.
+@Mani2011; @White2008] or sensitivity to consonant and vowel mispronunciations [@Mani2007; @Mani2010kepstups; @Hojen; @Swingley2016].
+The studies in our sample additionally varied in their experimental design, such as whether infants were familiar with the distractor image [@White2008; @Mani2011; @Skoruppa2013; @Swingley2016] or whether the labels for the target and distractor images contained phonological overlap [@Fernald2001a].
 Futhermore, the infants included in this meta-analysis had a variety of native languages (English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese) and language backgrounds (monolingual, bilingual, monodialectal, multidialectal).
 Taken together, these variables have the potential to modulate infant mispronunciation sensitivity, but an investigation of these variables is out of the scope of the current meta-analysis.
-However, our dataset coded for and included these variables.
+However, our dataset includes these variables.
 We hope that future research will be able to better understand the role that these variables play in infants' sensitivity to mispronunciations.
-
-[Katie: To respond to your comment, Christina, we did include bilinguals. I checked and there was no influence in keeping or removing them.]
 
@@
 Despite the predictions of theories of infant phono-lexical development, this sensitivity was not modulated by infant age or vocabulary.
-This suggests that from a young age on, infants’ word representations may be already phonologically well-specified.
+This suggests that from a young age on, before the vocabulary explosion, infants’ word representations may be already phonologically well-specified.
 We recommend future theoretical frameworks take this evidence into account.
@@
 
+*Acknowledgements*: The authors would like to thank Emelyne Gaudichau for valuable assistance in entering data.
+Author 1 was supported by the Agence Nationale de la Recherche (ANR-13-BSH2-0004) and by training grant DC-00046 from the National Institute of Deafness and Communicative Disorders of the National Institutes of Health.
+Author 2 was supported by the European Horizon 2020 programme (Marie Skłodowska-Curie grant No 660911), the Agence Nationale de la Recherche (ANR-10-IDEX-0001-02 PSL*, ANR-10-LABX-0087 IEC) and the Fondation de France.
+
+\newpage
+
 # References

### 2019-05-06 VonHolzenBergmann_MPMetaAnalysis.Rmd
begin Monster paper transformation

@@
 
-descriptive_dat <- db_ET
-
 db_ET <- db_ET %>%
@@
 dat <- bind_rows(db_ET_correct, db_ET_MP)
+
+descriptive_dat <- dat
 
@@
 # Introduction
-
-Acquiring a first language means that young learners are solving a host of tasks in a short amount of time.
-As infants develop into toddlers during their second and third years they learn new words in earnest while simultaneously refining their knowledge about the sounds that make up these words [@Kuhl2004; @Curtin2007; @Werker2005; @Best1994; @Best1995].
-In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonetic details that differentiate words in a given language (e.g.
-cat-hat).
-To build robust language knowledge, it seems useful to acquire this ability early during development.
-Indeed, before children can correctly pronounce a word, they already are aware that slight phonological deviations might signal a change in word meaning [@clark1977].
-This mispronunciation sensitivity reflects the specificity with which infants represent the phonological information of familiar words.
-As infants continue to develop into expert language users, their language processing matures and becomes more efficient, including their knowledge of what constitutes a permissible versus word-changing phonological deviation.
-In this paper, we aggregate and analyze the nearly 20 years of literature investigating mispronunciation sensitivity in infants in an attempt to uncover its characteristics and the trajectory of its development.
 
@@
 
-  The study of @Swingley2000 as well as subsequent studies examining mispronunciation sensitivity address two complementary principles that infants must discover in early phonological development in order to form adult-like word representations and processing capabilities: *phonological constancy* and *phonological distinctiveness*.
-Phonological constancy is the ability to resolve phonological variation across different instances of a word, as long as the variation does not compromise the overall identity of the word.
-For example, different speakers - particularly across genders and accents - produce the same word with notable acoustic variation, although the word remains the same.
-In contrast, phonological distinctiveness describes the ability to differentiate between different words that happen to be phonologically similar, such as bad/bed or cat/hat.
-To successfully recognize words, speakers of a given language must therefore simultaneously use both phonological constancy and distinctiveness to determine where phonological variation is appropriate and where it changes a word's meaning.
-Both abilities have to be acquired, because language systems differ in which sounds signal a meaning change.
-
-  In the current study, we focus on infants' developing ability to correctly apply the principles of phonological constancy and distinctiveness by using a meta-analytic approach to investigate mispronunciation sensitivity.
-Considering that infants are sensitive to mispronunciations and that, in general, their processing matures with development, we examine the shape of mispronunciation sensitivity over the course of the second and third year.
-There are three distinct possibilities how mispronunciation sensitivity might change as infants become native speakers, which are all respectively supported by single studies and additionally two possibilities are predicted by key theoretical accounts.
-By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies ([see @Frank2017; for a notable exception).
+  In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts  that differentiate words in a given language (e.g.
+cat-hat).
+The study of @Swingley2000 as well as subsequent studies examining mispronunciation sensitivity probe this latter distinction.
+Phonological contrasts relevant for the infant language-learner are determined by their native language.
+For an infant learning Catalan, the vowel contrast /e/-/E/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish.
+These contrasts are therefore not inate, but must be learned.
+In this meta-analysis, we focus on infants' developing ability to correctly apply the phonological distinctions for their native language during word recognition.
+By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; for a notable exception).
 Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.
 
-  Young infants may begin cautiously in their approach to word recognition, rejecting any phonological variation in familiar words and only later learning to accept appropriate variability.
-According to the Perceptual Attunement account, this describes a shift away from specific native phonetic patterns to a more mature understanding of the abstract phonological structure of words [@Best1994; @Best1995].
-This shift is predicted to coincide with the vocabulary spurt around 18 months, because it is causally related to vocabulary growth.
-In this case, we would expect the size of mispronunciation sensitivity to be larger at younger ages and *decrease* as the child matures and learn more words, although children continue to detect mispronunciations.
-Indeed, young infants are more perturbed by accented speakers than older infants in their recognition of familiar words [@Best2009; @Mulak2014] or learning of new words [@Schmale2011].
-
-  According to a different theoretical framework, young infants may instead begin with phonologically broad representations for familiar words and only refine their representations as language experience accumulates.
-PRIMIR [Processing Rich Information from Multidimensional Interactive Representations; @Curtin2007; @Curtin2011; @Werker2005] describes the development of phonemic categories emerging as the number of word form-meaning linkages increases.
-Vocabulary growth, therefore, promotes more detailed phonological representations in familiar words.
-Following this account, we predict an *increase* in mispronunciation sensitivity as infants mature and add more words to their growing lexicon.
-
-  Finally, sensitivity to mispronunciation may not be modulated by development at all.
-Infants' overall language processing becomes more efficient, but their sensitivity to mispronunciations may not change.
-Across infancy and toddlerhood, mispronunciations would thus be detected and lead to less looks at a target than correct pronunciations, but the size of this effect would not change, nor be related to vocabulary size.
-This pattern is not predicted by any mainstream theory of language acquisition, but for completeness we mention it here.
-
-  Research following the seminal study by @Swingley2000 has extended mispronunciation sensitivity to infants as young as 9 months [@Bergelson2017], indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations.
+  Research following the seminal study by @Swingley2000 has extended mispronunciation sensitivity to infants as young as 8 to 10 months [@Bergelson2017], indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations.
 Regarding the change in mispronunciation sensitivity over development, however, only about half of studies have compared more than one age group on the same mispronunciation task (see Table 1).
-In those single studies all possible patterns of development lined out above have been reported, making the current meta-analysis very informative.
-
-  One study has found evidence for infants to become *less* sensitive to mispronunciations as they develop.
-@Mani2011 presented 18- and 24-month-olds with mispronunciations varying in the number of phonological features changed (e.g., changing an p into a b, a 1-feature change, versus changing a p into a g, a 2-feature change).
-18-month-olds were sensitive to mispronunciations, regardless of the number of features changed.
-24-month-olds, in contrast, fixated the target image equally for both correct and 1-feature mispronounced trials, although they were sensitive to larger mispronunciations.
-In other words, for 1-feature mispronunciations at least, sensitivity decreased from 18 to 24 months, providing support to the prediction that mispronunciation sensitivity may decrease with development.
-
-  In contrast, other studies have found evidence for *greater* mispronunciation sensitivity as children develop.
+Across single studies all possible patterns of development lined out above have been reported, making the current meta-analysis very informative.
+
+Several studies have found evidence for *greater* mispronunciation sensitivity as children develop.
 More precisely, the difference in target looking for correct and mispronounced trials is reported to be smaller in younger infants and grows as infants develop.
@@
 In other words, the native language constraints which *kinds* of mispronunciations infants are sensitive to first, and that as infants develop, they become sensitive to other mispronunciations.
-These studies award support to the prediction that mispronunciation sensitivity increases with development.
-
-Finally, some studies have found no difference in mispronunciation sensitivity at different ages.
-@Swingley2000 tested infants over a wide age range of 5 months (18 to 23 months).
+
+Other studies have found no difference in mispronunciation sensitivity at different ages.
+For example, @Swingley2000 tested infants over a wide age range of 5 months (18 to 23 months).
 They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation sensitivity) did not.
@@
 A similar response pattern has been found for British English learning infants aged between 18 and 24 months [@Bailey2002] as well as younger French-learning infants at 12 and 17 months [@Zesiger2012].
-These studies award support to the prediction that mispronunciation sensitivity does not change with development.
-
-  Why would mispronunciation sensitivity change as infants develop, and would it increase or decrease?
-The main hypotheses attribute change to vocabulary growth.
-Both the Perceptual Attunement [@Best1994; @Best1995] and PRIMIR [@Curtin2007; @Werker2005; @Curtin2011] accounts situate a change in mispronunciation sensitivity occurring along with an increase in vocabulary size, particularly with the vocabulary spurt at about 18 months.
+
+  One study has found evidence for infants to become *less* sensitive to mispronunciations as they develop.
+@Mani2011 presented 18- and 24-month-olds with mispronunciations varying in the number of phonological features changed (e.g., changing an p into a b, a 1-feature change, versus changing a p into a g, a 2-feature change).
+18-month-olds were sensitive to mispronunciations, regardless of the number of features changed.
+24-month-olds, in contrast, fixated the target image equally for both correct and 1-feature mispronounced trials, although they were sensitive to larger mispronunciations.
+In other words, for 1-feature mispronunciations at least, sensitivity decreased from 18 to 24 months.
+
+  Why would mispronunciation sensitivity change as infants develop?
+Typically, a change in mispronunciation sensitivity is thought to occur along with an increase in vocabulary size, particularly with the vocabulary spurt at about 18 months.
 As infants learn more words, their focus shifts to the relevant phonetic dimensions needed for word recognition.
@@
 High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations.
-Taken together, although receiving considerable support from theories of phono-lexical processing in language acquisition, there is very little evidence for a role of vocabulary size in mispronunciation sensitivity.
-In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to further disentangle the disconnect between theory and experimental results.
+Taken together, there is very little evidence for a role of vocabulary size in mispronunciation sensitivity.
+In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to better understand the variation in experimental results.
+
+  Although all mispronunciation sensitivity studies are generally interested in the the phonological detail with which infants represent familiar words, many studies pose more nuanced questions.
+These questions concern issues at the intersection of phonological development and lexical processing and often result in manipulations of the stimuli and experimental procedure.
+Next to the core investigation of the shape of development of infants' mispronunciation sensitivity, we take the opportunity of a systematic aggregation of data to address these questions and the influence of these manipulations on infants' ability to detect mispronunciations and how this may change with development.
+
+  In designing their mispronunciation stimuli, Swingley and Aslin (2000) chose consonant mispronunciations that were likely to confuse adults (Miller & Nicely, 1955).
+Subsequent research has settled on systematically modulating phonemic features to achieve mispronunciations of familiar words.
+By utilizing mispronunciations consisting of phonemic changes, these experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level (i.e.
+1-feature, 2-features, 3-features, etc.).
+The importance of controlling for the degree of phonological mismatch, as measured by number of features changed, is further highlighted by studies that find graded sensitivity to both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes.
+The greater the number of features changed, or *mispronunciation size*, the easier it may be to detect a mispronunciation, whereas more similar mispronunciations may be more difficult to detect.
+
+  Although most research examining sensitivity to mispronunciations follows a similar design, there are some notable differences.
+For example, Swingley and Aslin (2000) presented infants with pairs of familiar images, one serving as the labeled target and one as the unlabeled distractor.
+In contrast, White and Morgan (2008; see also Mani & Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects.
+By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied (Halberda, 2003; Markman, Wasow, & Hansen, 2003).
+Infants ages 24 and 30 months associate a novel label with an unfamiliar object, although only 30-month-olds retained this label-object pairing (Bion, Borovsky, and Fernald, 2013).
+In contrast, 18-month-olds did not learn to associate a novel label with an unfamiliar object, providing evidence that this ability is developing from 18 to 30 months.
+We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar.
+Although mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared, the baseline preference for familiar compared to novel stimuli is also thought to change as infants develop (Hunter & Ames, 1988).
+Furthermore, young children have been found to look longer at objects for which they know the name, compared to objects of an unknown name (Schafer & Plukett, 1998).
+In other words, in absentia of a label, infants may be more or less likely to fixate on an unfamiliar object.
+To account for inherent preferences to the target or distractor image, mispronunciation experiments typically compare the increase in fixations to the target image from a silent baseline to post-labeling or present the same yoked pairs of target and distractor images in in both a correct and mispronounced labelling context.
+Considering this evidence, we may expect that in older, but not younger, children, the presence of an unfamiliar distractor may lead to greater mispronunciation sensitivity than in the presence of a familiar distractor.
+
+  Furthermore, when presenting infants with a familiar distractor image, some studies control the *phonological overlap between target and distractor labels*.
+For example, when examining sensitivity to a mispronunciation of the target word "dog", the vowel mispronunciation "dag" would be paired with a distractor image that shares onset overlap, such as "duck".
+This ensures that infants can not use the onset of the word to differentiate between the target and distractor images (Fernald, Swingley, & Pinto, 2001).
+Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.
+The influence of distractor overlap also depends on the *position of mispronunciation* in the word, which can be at word onset, medial, or final positions.
+Models of spoken word processing place more or less importance on the position of a phoneme in a word.
+The COHORT model (Marslen-Wilson & Zwitserlood, 1989) describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.
+In contrast, the TRACE model (McClelland & Elman, 1986) describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.
+
+  TRACE has also been used to model infants' sensitivity to mispronunciation position (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth.
+In early language acquisition, infants typically know more consonant compared to vowel onset words.
+When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations.
+The prevalence of consonant onset words may contribute to the finding that consonants carry more weight in lexical processing (C-bias; see Nazzi, Poltrock, & Von Holzen, 2016 for a recent review).
+In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations.
+Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels.
+English-learning 12-, 15-, 18-, and 24-month-olds (Mani & Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds (Hojen et al., unpublished) demonstrate similar sensitivity to consonant and vowel mispronunciations.
+One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations (Swingley, 2016).
+The English-learning infants tested by Swingley were older than previous studies (mean age 28 months).
+In word learning, the C-bias has been found to develop later in English learning infants (Floccia, Nazzi, Delle Luche, Poltrock, & Goslin, 2014; Nazzi, Floccia, Moquet, & Butler, 2009).
+In the current meta-analysis, we attempt to synthesize studies examining sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence (Floccia et al., 2014; Keidel et al., 2007; Nazzi et al., 2016).
+We further examine the impact of language family on mispronunciation sensitivity to consonants and vowels, as C-bias emergence has been found to have a different developmental trajectory for Romance (French, Italian) compared to Germanic (British English, Danish) languages (Nazzi et al., 2016).
+
+  Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (see Table 1).
+Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare.
+Although we do not explicitly compare overall mispronunciation sensitivity by language (although see previous paragraph for rationale to test by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.
 
@@
 Because we aggregate data over various age groups, this meta-analysis can also investigate the role of maturation by assessing the impact of age and vocabulary size.
-As a consequence, our results will be important in evaluating theories and drive future research.
 We also make hands-on recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses [@Bergmann2018].
@@
 dat_st <- descriptive_dat
+
+dat_st$type_feature <- as.character(dat_st$type_feature)
+dat_st$mispron_location <- as.character(dat_st$mispron_location)
+dat_st$distractor_overlap <- as.character(dat_st$distractor_overlap)
+
+dat_st$object_pair <- ifelse(dat_st$object_pair == "familiar_familiar", "fam", "unfam")
+
+dat_st$distractor_overlap <- ifelse(dat_st$distractor_overlap == "no", "none", dat_st$distractor_overlap)
 
@@
                                        ifelse(!all(is.na(r_comprehension)) & all(is.na(r_production)), "Comp", "Prod"))),
+        distractor = paste(unique(object_pair), collapse =', '),
+        dist_overlap = paste(unique(distractor_overlap), collapse =', '),
+        number_features = paste(unique(n_feature), collapse=', '),
+        misp_posit = paste(unique(mispron_location), collapse =', '),
+        misp_type = paste(unique(type_feature), collapse =', '),
         Effect_sizes_n = n())
 
+# can't chain these together, since it only checks each line once
+
+Sum_table$misp_posit <- ifelse(Sum_table$misp_posit == "NA", "unspec", Sum_table$misp_posit)
+Sum_table$misp_posit <- ifelse(grepl("onset", Sum_table$misp_posit), gsub("onset", "O", Sum_table$misp_posit), Sum_table$misp_posit)
+Sum_table$misp_posit <- ifelse(grepl("medial", Sum_table$misp_posit), gsub("medial", "M", Sum_table$misp_posit), Sum_table$misp_posit)
+Sum_table$misp_posit <- ifelse(grepl("coda", Sum_table$misp_posit), gsub("coda", "C", Sum_table$misp_posit), Sum_table$misp_posit)
+
+Sum_table$dist_overlap <- ifelse(grepl("onset", Sum_table$dist_overlap), gsub("onset", "O", Sum_table$dist_overlap), Sum_table$dist_overlap)
+Sum_table$dist_overlap <- ifelse(grepl("medial", Sum_table$dist_overlap), gsub("medial", "M", Sum_table$dist_overlap), Sum_table$dist_overlap)
+Sum_table$dist_overlap <- ifelse(grepl("coda", Sum_table$dist_overlap), gsub("coda", "C", Sum_table$dist_overlap), Sum_table$dist_overlap)
+
+Sum_table$number_features <- ifelse(grepl("0, ",Sum_table$number_features), gsub("0, ", "", Sum_table$number_features), 
+                                           ifelse(grepl(", 0",Sum_table$number_features), gsub(", 0", "", Sum_table$number_features), Sum_table$number_features))
+Sum_table$number_features <- ifelse(Sum_table$number_features == "NA", "unspec", Sum_table$number_features)
+
+Sum_table$number_features <- ifelse(grepl("1_2_3,", Sum_table$number_features), gsub("1_2_3", "1-3", Sum_table$number_features), Sum_table$number_features)
+Sum_table$number_features <- ifelse(grepl("1_2,", Sum_table$number_features), gsub("1_2", "1-2", Sum_table$number_features), Sum_table$number_features)
+Sum_table$number_features <- ifelse(grepl("2_3", Sum_table$number_features), gsub("2_3", "2-3", Sum_table$number_features), Sum_table$number_features)
+
+Sum_table$misp_type <- ifelse(grepl("consonant_and_vowel", Sum_table$misp_type), gsub("consonant_and_vowel", "C/V", Sum_table$misp_type),
+                              ifelse(grepl("consonant_vowel_tone", Sum_table$misp_type), gsub("consonant_vowel_tone", "C/V/T", Sum_table$misp_type) , Sum_table$misp_type))
+
+Sum_table$misp_type <- ifelse(grepl("consonant", Sum_table$misp_type), gsub("consonant", "C", Sum_table$misp_type), Sum_table$misp_type)
+
+Sum_table$misp_type <- ifelse(grepl("vowel", Sum_table$misp_type), gsub("vowel", "V", Sum_table$misp_type), Sum_table$misp_type)
+
+Sum_table$misp_type <- ifelse(grepl("tone", Sum_table$misp_type), gsub("tone", "T", Sum_table$misp_type), Sum_table$misp_type)
+
 #kable(Sum_table, col.names = c("Paper", "Publication format", "Age", "Vocabulary", "N Effect Sizes"))
-apa_table(Sum_table, col.names = c("Paper", "Publication format", "Age", "Vocabulary", "N Effect Sizes"), caption = "Summary of all studies.
-Age is calculated by truncating the mean age reported in the paper.
-The abbreviations Comp and Prod refer to comprehension and production, respectively.", landscape = TRUE)
+
+apa_table(Sum_table, col.names = c("Paper", "Format", "Age", "Vocabulary", "Familiarity", "Target Overlap", "Size", "Position", "Type", "N Effect Sizes"), caption = "Summary of all studies.
+Age: truncation of mean age reported in the paper.
+Vocabulary: Comp = comprehension, Prod = production.
+Distractor Familiarity: Fam = Familiar Distractor, Unfam = Unfamiliar Distractor.
+Distractor Target Overlap: position of overlap between target and distractor; O = onset, M = medial, C = coda.
+Mispronunciation Size: number of features changed; commas indicate when sizes were compared separately (e.g.
+1, 2, 3), dashes indicate the range of sizes were aggregated (e.g.
+1-3).
+Mispronunciation Position: O = onset, M = medial, C = coda.
+Mispronunciation Type: C = consonant, V = vowel, T = tone.
+For both Mispronunciation Position and Type, a slash separator indicates that is was tested but a distinction was not made in the stimuli.
+For all categories, unspec.
+indicates that the value was unspecified in the paper", landscape = TRUE, font_size = "scriptsize", col_spanners = list(`Distractor` = c(5, 6), `Mispronunciation` = c(7, 9)))
 
@@
 For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results.
-For the planned analyses to evaluate the development of mispronunciation sensitivity, we focus on the following characteristics:
+For the planned analyses to evaluate the development of mispronunciation sensitivity and modulating factors, we focus on the following characteristics:
 
@@
 3 Vocabulary size, measured by a standardized questionnaire or list;    
+4 Size of mispronunciation, measured in features changed;  
+5 Distractor familiarity: familiar or unfamiliar;  
+6 Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;  
+7 Position of mispronunciation: onset, medial, offset, or mixed;  
+8 Type of mispronunciation: consonant, vowel, or both.
 
@@
 
+```{r MPEffect_forest, echo = FALSE, results="hide"}
+
+##Borrowing some code to make this a ggplot: 
+#https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-met#a-analysis/
+#Rename a bunch of things for ease
+
+mean_correct <- with(dat, mean(g_calc[is_correct == 1]))
+mean_misp <- with(dat, mean(g_calc[is_correct == 0]))
+
+new.dat <- dat
+#new.dat <- subset(new.dat, x_type == "percent_post")
+
+# new.dat <- subset(new.dat, short_cite == "Højen et al. (n.d.)" | short_cite == "Swingley & Aslin (2000)" | short_cite == "Swingley (2003)")
+
+new.dat <-
+  new.dat %>% 
+  rename(cite = short_cite,
+         yi = g_calc,
+         vi = g_var_calc)
+#Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order
+new.dat <-
+  new.dat %>% 
+  select(cite, expt_num, expt_condition, same_infant, is_correct, mean_age_1, yi, vi, within_measure) %>% 
+  mutate(study_ref = paste(cite, expt_num, expt_condition, same_infant, is_correct, sep=',')) %>% 
+  arrange(desc(yi))
+
+new.dat$condition <- ifelse(new.dat$is_correct == 1, "correct", "mispronunciation")
+
+#Get standard errors from variances
+new.dat$se = sqrt(new.dat$vi)
+#Calculate 95% CI values
+new.dat$lowerci = (-1.96*new.dat$se)+new.dat$yi
+new.dat$upperci = (1.96*new.dat$se)+new.dat$yi
+#Themes and plot
+apatheme2=theme_bw()+
+  theme(panel.grid.major=element_blank(),
+        panel.grid.minor=element_blank(),
+        panel.border=element_blank(),
+        axis.line=element_line(),
+        text=element_text(family='Times'),
+        legend.position='none')
+p=
+  ggplot(new.dat, aes(y=reorder(study_ref, -yi), x=yi, xmin=lowerci, xmax=upperci))+
+  #Add data points and color them black
+  geom_point(color = 'black')+
+  #Add 'special' points for the summary estimates, by making them diamond shaped
+#  geom_point(data=subset(dat, tester=='Summary'), color='black', shape=18, size=4)+
+  #add the CI error bars
+  geom_errorbarh(height=.1)+
+  #Specify the limits of the x-axis and relabel it to something more meaningful
+  #scale_x_continuous(limits=c(-1.5,1.5), name='Standardized Mean Difference (g)')+
+  #Give y-axis a meaningful label
+  ylab('Reference')+
+  #Add a vertical dashed line indicating an effect size of zero, for reference
+  geom_vline(xintercept=0, color='grey', linetype='dashed')+
+  #Add a vertical line to show mean effect
+  geom_vline(xintercept=mean_correct, color='orange', linetype='dashed')+
+    geom_vline(xintercept=mean_misp, color='blue', linetype='dashed')+
+  #Create sub-plots (i.e., facets) based on levels of setting
+  #And allow them to have their own unique axes (so authors don't redundantly repeat)
+  facet_grid(condition~., scales= 'free', space='free')+
+  #Apply my APA theme
+  apatheme2
+#p
+
+```
+
 The above two analyses considered the data from mispronounced and correctly pronounced words separately.
@@
 
-#### Offset time after target naming
-
-```{r time_offset}
+#### Onset time after target naming
+
+```{r time_onset}
 
@@
 Mispronunciation studies evaluate infants' proportion of target looks (PTL) in response to correct and mispronounced words.
-Experiments typically include a phase where no naming event has occurred, whether correctly pronounced or mispronounced, which we refer to as the pre-naming phase The purpose of the pre-naming phase is to ensure that infants do not have systematic preferences for the target or distractor (greater interest in a cat compared to a cup) which may drive PTL scores in the post-naming phase.
+Experiments typically include a phase where a naming event has not yet occurred, which we refer to as the pre-naming phase.
+This is followed by a naming event, whether correctly pronounced or mispronounced, and the subsequent phase we refer to as the post-naming phase.
+The purpose of the pre-naming phase is to ensure that infants do not have systematic preferences for the target or distractor (greater interest in a cat compared to a cup) which may drive PTL scores in the post-naming phase.
 As described in the Data Analysis sub-section of the Methods, however, there was considerable variation across papers in whether this pre-naming phase was used as a baseline measurement, or whether a different baseline measurement was used.
 This resulted in different measured outcomes or dependent variables.
-Over half of the experimental conditions (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post_naming_effect"])`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase.
-This results in one value, which is then compared with a chance value of 0.
+Over half of the experimental conditions (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post_naming_effect"])`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase, resulting in a Difference Score.
+The Difference Score is one value, which is then compared with a chance value of 0.
 When positive, this indicates that infants increased their looks to the target after hearing the naming label (correct or mispronounced) relative to the pre-naming baseline PTL.
-We will refer to this dependent variable as the Difference Score.
-Another dependent variable, which was used in `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` experimental conditions, directly compared the post- and pre-naming PTL scores with one another.
+In contrast, Pre vs.
+Post (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` experimental conditions), directly compare the post- and pre-naming PTL scores with one another using a statistical test (e.g.
+t-test, ANOVA).
 This requires two values, one for the pre-naming phase and one for the post-naming phase.
 A greater post compared to pre-naming phase PTL indicates that infants increased their target looks after hearing the naming label.
-We will refer to this dependent variable as Pre vs.
-Post.
-Finally, the remaining `r with(dv_info, n_exp_conditions[within_measure == "post"])` experimental conditions compared the post-naming PTL score with a chance value of 50%.
-Here, the infants' pre-naming phase baseline preferences are not considered and instead target fixations are evaluated based on the likelihood to fixate one of two pictures.
-We will refer to this dependent variable as Post.
+The remaining experimental conditions used a Post dependent variable (*n* = `r with(dv_info, n_exp_conditions[within_measure == "post"])` experimental conditions), which compares the post-naming PTL score with a chance value of 50%.
+Here, the infants' pre-naming phase baseline preferences are not considered and instead target fixations are evaluated based on the likelihood to fixate one of two pictures (50%).
+As most papers do not specify whether these calculations are made before or after aggregating across trials, we make no assumptions about when this step is taken.
 
@@
 
+```{r Young_age, echo = FALSE, results = "hide"}
+
+youngsters <- dat %>%
+  filter(mean_age_1 < (30.44*13)) %>%
+  group_by(short_cite, same_infant) %>%
+  summarise(n_records = n(),
+            age_days = mean(mean_age_1),
+            age_months = mean(mean_age_months),
+            g = mean(g_calc))
+
+# Bergelson & Swingley: no MP sensitivity at 6-7, MP sensitivity at 8-10 and 11-14
+# Mani & Plunkett: MP sensitivity at 12 months
+# Tao & Qinmei: MP sensitivity at 12 months
+# Zesiger: MP sensitivity at 12 months
+
+age_onset <- dat %>%
+  #filter(mean_age_1 < (30.44*13)) %>%
+  group_by(short_cite, same_infant) %>%
+  summarise(age_months = mean(mean_age_months),
+            g = mean(g_calc),
+            onset = mean(offset),
+            post = mean(post_nam_dur))
+
+dv <- dat %>%
+  #filter(mean_age_1 < (30.44*13)) %>%
+  group_by(short_cite, same_infant) %>%
+  summarise(age_months = mean(mean_age_months),
+            g = mean(g_calc),
+            dv = unique(within_measure))
+
+```
+
 What do our (tentative) results mean for theories of language development?
@@
 While creating the dataset on which this meta-analysis was based, we included as many details as possible to describe each study.
-During the coding of these characteristics, we noted a potential for variation in a handful of variables that relate to data analysis, specifically relating to timing (post-naming analysis window; offset time) and to the calculation of the dependent variable reported.
+During the coding of these characteristics, we noted a potential for variation in a handful of variables that relate to data analysis, specifically relating to timing (post-naming analysis window; onset time) and to the calculation of the dependent variable reported.
 We focused on these variables in particular because their choice can potentially be made after researchers have examined the data, leading to an inflated number of significant results which may also explain the publication bias observed in the funnel plot asymmetry analyses [@Simmons2011].
@@
 
-Infants are expected to recognize words more quickly with age [@Fernald1998].
-This evidence has often guided decisions for the post-naming time window in mispronunciation sensitivity studies, including where to begin the time window (offset time) and how long this analysis window should be (post-naming analysis window).
-Specifically, increasing age should lead to quicker reaction times, and therefore lower offset times.
-Yet, we found no evidence for a relationship between offset time and infant age nor that offset time modulated mispronunciation sensitivity.
+Infants recognize words more quickly with age [@Fernald1998], which has the potential to influence decisions for the analysis of the post-naming time window in mispronunciation sensitivity studies, including where to begin the time window (onset time) and how long this analysis window should be (post-naming analysis window).
+For example, as age increases, reaction time should increase and experimenters may adjust and lower offset times in their analysis as well as shorten the length of the analysis window.
+Yet, we find no relationship between age and offset times, nor that offset time modulated mispronunciation sensitivity.
 Indeed, a majority of studies used an offset time between 360 and 370 ms, which follows the "best guess" of @Swingley2000 for the amount of time needed for infants to initiate eye movements in response to a spoken target word.
-
-In contrast, both the length of the post-naming analysis window and the type of dependent variable calculated modulated mispronunciation sensitivity.
-Most critically, however, variation in these variables resulted in changes to the developmental trajectory of mispronunciation sensitivity.
-Given a set of mispronunciation sensitivity data, a conclusion regarding the development of mispronunciation sensitivity would be different depending on the length of the post-naming analysis window or the choice of dependent variable.
+Without knowledge of the base reaction time in a given population of infants, use of this best guess offset time reduces the number of free parameters.
+In contrast, we found a negative correlation between infant age and the length of the post-naming analysis window, and that the length of the analysis window moderated mispronunciation sensitivity, such increasing the length of the analysis windows decreases the size of mispronunciation sensitivity.
+Given a set of mispronunciation sensitivity data, a conclusion regarding the development of mispronunciation sensitivity would be different depending on the length of the post-naming analysis window.
+Although we have no direct evidence, an analysis window can be potentially set after collecting data.
+At worst, this adjustment could be the result of a desire to confirm a hypothesis, increasing the rate of false-positives [@Gelman2013]: a "significant effect" of mispronunciation sensitivity is found with an analysis window of 2000 but not 3000 ms, therefore 2000 ms is chosen.
+At best, this variation introduces noise into the study of mispronunciation sensitivity, bluring the true developmental trajectory of mispronunciation sensitivity.
+In the next section, we highlight some suggestions for how the field can remedy this issue.
+
+Surpisingly, we found that the type of dependent variable calculated moderated mispronunciation sensitivity and conclusions about its developmental trajectory.
+Unlike the exploratory analyses related to timing (onset and post-naming analysis window), there is not a clear reason for one dependent variable to be chosen over another; the prevelence of each dependent variable appears distributed across ages and some authors always calculate the same dependent variable while others use them interchangeably in different publications.
+One clear difference is that both the Difference Score and Pre vs.
+Post dependent variables take into account each infants' actual preference in the pre-naming baseline phase, while the Post dependent variable does not.
+Without access to the raw data, it is difficult to conclusively determine why different dependent variable calculations influence mispronunciation sensitivity.
+In the next section, we advocate for the adoption of Open Data practices as one way to address this issue.
 
@@
 
-We take this opportunity to suggest several solutions.
+We take this opportunity to suggest several recommendations to address the issue of potential posthoc analysis decisions.
 Preregistration can serve as proof of a priori decisions regarding data analysis, which can also contain a data-dependent description of how data analysis decisions will be made once data is collected.
@@
 Sharing data (Open Data) can allow others to re-analyze existing datasets to both examine the impact of analysis decisions and cumulatively analyze different datasets in the same way.
-Experimenters can also opt to analyze the time course as a whole, instead of aggregating the proportion of target looking behavior over the entire trial.
+Considering the issue of analysis time window, experimenters can opt to analyze the time course as a whole, instead of aggregating the proportion of target looking behavior over the entire trial.
 This allows for a more detailed assessment of infants' fixations over time and reduces the need to reduce the post-naming analysis window.
@@
 ptt <- pwr.t.test(n = median_sample, d = mp_effect, sig.level = 0.05, power = NULL)
+
+ptt.correct <- pwr.t.test(n = median_sample, d = .9, sig.level = 0.05, power = NULL)
+ptt.misp <- pwr.t.test(n = median_sample, d = .25, sig.level = 0.05, power = NULL)
 

### 2019-05-06 VonHolzenBergmann_MPMetaAnalysis.tex
begin Monster paper transformation

--- 2019-01-16 Paper_Analyses.tex
@@
 
-Acquiring a first language means that young learners are solving a host
-of tasks in a short amount of time. As infants develop into toddlers
-during their second and third years they learn new words in earnest
-while simultaneously refining their knowledge about the sounds that make
-up these words (Best, 1994, 1995; Curtin \& Werker, 2007; Kuhl, 2004;
-Werker \& Curtin, 2005). In a mature phono-lexical system, word
-recognition must balance flexibility to slight variation (e.g., speaker
-identity, accented speech) while distinguishing between phonetic details
-that differentiate words in a given language (e.g.~cat-hat). To build
-robust language knowledge, it seems useful to acquire this ability early
-during development. Indeed, before children can correctly pronounce a
-word, they already are aware that slight phonological deviations might
-signal a change in word meaning (H. H. Clark \& Clark, 1977). This
-mispronunciation sensitivity reflects the specificity with which infants
-represent the phonological information of familiar words. As infants
-continue to develop into expert language users, their language
-processing matures and becomes more efficient, including their knowledge
-of what constitutes a permissible versus word-changing phonological
-deviation. In this paper, we aggregate and analyze the nearly 20 years
-of literature investigating mispronunciation sensitivity in infants in
-an attempt to uncover its characteristics and the trajectory of its
-development.
-
 At the turn of the millenium, infant language acquisition researchers
@@
 
-The study of Swingley and Aslin (2000) as well as subsequent studies
-examining mispronunciation sensitivity address two complementary
-principles that infants must discover in early phonological development
-in order to form adult-like word representations and processing
-capabilities: \emph{phonological constancy} and \emph{phonological
-distinctiveness}. Phonological constancy is the ability to resolve
-phonological variation across different instances of a word, as long as
-the variation does not compromise the overall identity of the word. For
-example, different speakers - particularly across genders and accents -
-produce the same word with notable acoustic variation, although the word
-remains the same. In contrast, phonological distinctiveness describes
-the ability to differentiate between different words that happen to be
-phonologically similar, such as bad/bed or cat/hat. To successfully
-recognize words, speakers of a given language must therefore
-simultaneously use both phonological constancy and distinctiveness to
-determine where phonological variation is appropriate and where it
-changes a word's meaning. Both abilities have to be acquired, because
-language systems differ in which sounds signal a meaning change.
-
-In the current study, we focus on infants' developing ability to
-correctly apply the principles of phonological constancy and
-distinctiveness by using a meta-analytic approach to investigate
-mispronunciation sensitivity. Considering that infants are sensitive to
-mispronunciations and that, in general, their processing matures with
-development, we examine the shape of mispronunciation sensitivity over
-the course of the second and third year. There are three distinct
-possibilities how mispronunciation sensitivity might change as infants
-become native speakers, which are all respectively supported by single
-studies and additionally two possibilities are predicted by key
-theoretical accounts. By aggregating all publicly available evidence
-using meta-analysis, we can examine developmental trends making use of
-data from a much larger and diverse sample of infants than is possible
-in most single studies ({[}see Frank et al. (2017); for a notable
-exception). Before we outline the meta-analytical approach and its
-advantages in detail, we first discuss the proposals this study seeks to
-disentangle and the data supporting each of the accounts.
-
-Young infants may begin cautiously in their approach to word
-recognition, rejecting any phonological variation in familiar words and
-only later learning to accept appropriate variability. According to the
-Perceptual Attunement account, this describes a shift away from specific
-native phonetic patterns to a more mature understanding of the abstract
-phonological structure of words (Best, 1994, 1995). This shift is
-predicted to coincide with the vocabulary spurt around 18 months,
-because it is causally related to vocabulary growth. In this case, we
-would expect the size of mispronunciation sensitivity to be larger at
-younger ages and \emph{decrease} as the child matures and learn more
-words, although children continue to detect mispronunciations. Indeed,
-young infants are more perturbed by accented speakers than older infants
-in their recognition of familiar words (Best, Tyler, Gooding, Orlando,
-\& Quann, 2009; Mulak, Best, Tyler, Kitamura, \& Irwin, 2014) or
-learning of new words (Schmale, Hollich, \& Seidl, 2011).
-
-According to a different theoretical framework, young infants may
-instead begin with phonologically broad representations for familiar
-words and only refine their representations as language experience
-accumulates. PRIMIR (Processing Rich Information from Multidimensional
-Interactive Representations; Curtin \& Werker, 2007; Curtin,
-Byers-Heinlein, \& Werker, 2011; Werker \& Curtin, 2005) describes the
-development of phonemic categories emerging as the number of word
-form-meaning linkages increases. Vocabulary growth, therefore, promotes
-more detailed phonological representations in familiar words. Following
-this account, we predict an \emph{increase} in mispronunciation
-sensitivity as infants mature and add more words to their growing
-lexicon.
-
-Finally, sensitivity to mispronunciation may not be modulated by
-development at all. Infants' overall language processing becomes more
-efficient, but their sensitivity to mispronunciations may not change.
-Across infancy and toddlerhood, mispronunciations would thus be detected
-and lead to less looks at a target than correct pronunciations, but the
-size of this effect would not change, nor be related to vocabulary size.
-This pattern is not predicted by any mainstream theory of language
-acquisition, but for completeness we mention it here.
+In a mature phono-lexical system, word recognition must balance
+flexibility to slight variation (e.g., speaker identity, accented
+speech) while distinguishing between phonological contrasts that
+differentiate words in a given language (e.g.~cat-hat). The study of
+Swingley and Aslin (2000) as well as subsequent studies examining
+mispronunciation sensitivity probe this latter distinction. Phonological
+contrasts relevant for the infant language-learner are determined by
+their native language. For an infant learning Catalan, the vowel
+contrast /e/-/E/ signifies a change in meaning, whereas this is not the
+case for an infant learning Spanish. These contrasts are therefore not
+inate, but must be learned. In this meta-analysis, we focus on infants'
+developing ability to correctly apply the phonological distinctions for
+their native language during word recognition. By aggregating all
+publicly available evidence using meta-analysis, we can examine
+developmental trends making use of data from a much larger and diverse
+sample of infants than is possible in most single studies (see Frank et
+al. (2017); for a notable exception). Before we outline the
+meta-analytical approach and its advantages in detail, we first discuss
+the proposals this study seeks to disentangle and the data supporting
+each of the accounts.
 
 Research following the seminal study by Swingley and Aslin (2000) has
-extended mispronunciation sensitivity to infants as young as 9 months
-(Bergelson \& Swingley, 2017), indicating that from early stages of the
-developing lexicon onwards, infants can and do detect mispronunciations.
-Regarding the change in mispronunciation sensitivity over development,
-however, only about half of studies have compared more than one age
-group on the same mispronunciation task (see Table 1). In those single
-studies all possible patterns of development lined out above have been
-reported, making the current meta-analysis very informative.
+extended mispronunciation sensitivity to infants as young as 8 to 10
+months (Bergelson \& Swingley, 2017), indicating that from early stages
+of the developing lexicon onwards, infants can and do detect
+mispronunciations. Regarding the change in mispronunciation sensitivity
+over development, however, only about half of studies have compared more
+than one age group on the same mispronunciation task (see Table 1).
+Across single studies all possible patterns of development lined out
+above have been reported, making the current meta-analysis very
+informative.
+
+Several studies have found evidence for \emph{greater} mispronunciation
+sensitivity as children develop. More precisely, the difference in
+target looking for correct and mispronounced trials is reported to be
+smaller in younger infants and grows as infants develop. Mani and
+Plunkett (2007) tested 15-, 18-, and 24-month-olds learning British
+English; although all three groups were sensitive to mispronunciations,
+15-month-olds showed a less robust sensitivity. An increase in
+sensitivity to mispronunciations has also been found from 20 to 24
+months (Feest \& Fikkert, 2015) and 15 to 18 months (Altvater-Mackensen,
+Feest, \& Fikkert, 2014) in Dutch infants, as well as German infants
+from 22 to 25 months (Altvater-Mackensen, 2010). Furthermore, Feest and
+Fikkert (2015) found that sensitivity to specific kinds of
+mispronunciations develop at different ages depending on language
+infants are learning. In other words, the native language constraints
+which \emph{kinds} of mispronunciations infants are sensitive to first,
+and that as infants develop, they become sensitive to other
+mispronunciations.
+
+Other studies have found no difference in mispronunciation sensitivity
+at different ages. For example, Swingley and Aslin (2000) tested infants
+over a wide age range of 5 months (18 to 23 months). They found that age
+correlated with target fixations for both correct and mispronounced
+labels, whereas the difference between the two (mispronunciation
+sensitivity) did not. This suggests that as children develop, they are
+more likely to look at the target in the presence of a correct or
+mispronounced label, but that the difference between looks elicited by
+the two conditions does not change. A similar response pattern has been
+found for British English learning infants aged between 18 and 24 months
+(Bailey \& Plunkett, 2002) as well as younger French-learning infants at
+12 and 17 months (Zesiger, Lozeron, Levy, \& Frauenfelder, 2012).
 
@@
 1-feature mispronunciations at least, sensitivity decreased from 18 to
-24 months, providing support to the prediction that mispronunciation
-sensitivity may decrease with development.
-
-In contrast, other studies have found evidence for \emph{greater}
-mispronunciation sensitivity as children develop. More precisely, the
-difference in target looking for correct and mispronounced trials is
-reported to be smaller in younger infants and grows as infants develop.
-Mani and Plunkett (2007) tested 15-, 18-, and 24-month-olds learning
-British English; although all three groups were sensitive to
-mispronunciations, 15-month-olds showed a less robust sensitivity. An
-increase in sensitivity to mispronunciations has also been found from 20
-to 24 months (Feest \& Fikkert, 2015) and 15 to 18 months
-(Altvater-Mackensen, Feest, \& Fikkert, 2014) in Dutch infants, as well
-as German infants from 22 to 25 months (Altvater-Mackensen, 2010).
-Furthermore, Feest and Fikkert (2015) found that sensitivity to specific
-kinds of mispronunciations develop at different ages depending on
-language infants are learning. In other words, the native language
-constraints which \emph{kinds} of mispronunciations infants are
-sensitive to first, and that as infants develop, they become sensitive
-to other mispronunciations. These studies award support to the
-prediction that mispronunciation sensitivity increases with development.
-
-Finally, some studies have found no difference in mispronunciation
-sensitivity at different ages. Swingley and Aslin (2000) tested infants
-over a wide age range of 5 months (18 to 23 months). They found that age
-correlated with target fixations for both correct and mispronounced
-labels, whereas the difference between the two (mispronunciation
-sensitivity) did not. This suggests that as children develop, they are
-more likely to look at the target in the presence of a correct or
-mispronounced label, but that the difference between looks elicited by
-the two conditions does not change. A similar response pattern has been
-found for British English learning infants aged between 18 and 24 months
-(Bailey \& Plunkett, 2002) as well as younger French-learning infants at
-12 and 17 months (Zesiger, Lozeron, Levy, \& Frauenfelder, 2012). These
-studies award support to the prediction that mispronunciation
-sensitivity does not change with development.
-
-Why would mispronunciation sensitivity change as infants develop, and
-would it increase or decrease? The main hypotheses attribute change to
-vocabulary growth. Both the Perceptual Attunement (Best, 1994, 1995) and
-PRIMIR (Curtin \& Werker, 2007; Curtin et al., 2011; Werker \& Curtin,
-2005) accounts situate a change in mispronunciation sensitivity
-occurring along with an increase in vocabulary size, particularly with
-the vocabulary spurt at about 18 months. As infants learn more words,
-their focus shifts to the relevant phonetic dimensions needed for word
+24 months.
+
+Why would mispronunciation sensitivity change as infants develop?
+Typically, a change in mispronunciation sensitivity is thought to occur
+along with an increase in vocabulary size, particularly with the
+vocabulary spurt at about 18 months. As infants learn more words, their
+focus shifts to the relevant phonetic dimensions needed for word
 recognition. For example, an infant who knows a handful of words with
@@
 although this was not the case for consonant mispronunciations. Taken
-together, although receiving considerable support from theories of
-phono-lexical processing in language acquisition, there is very little
-evidence for a role of vocabulary size in mispronunciation sensitivity.
-In our current meta-analysis, we include the relationship between
-mispronunciation sensitivity and vocabulary size to further disentangle
-the disconnect between theory and experimental results.
+together, there is very little evidence for a role of vocabulary size in
+mispronunciation sensitivity. In our current meta-analysis, we include
+the relationship between mispronunciation sensitivity and vocabulary
+size to better understand the variation in experimental results.
+
+Although all mispronunciation sensitivity studies are generally
+interested in the the phonological detail with which infants represent
+familiar words, many studies pose more nuanced questions. These
+questions concern issues at the intersection of phonological development
+and lexical processing and often result in manipulations of the stimuli
+and experimental procedure. Next to the core investigation of the shape
+of development of infants' mispronunciation sensitivity, we take the
+opportunity of a systematic aggregation of data to address these
+questions and the influence of these manipulations on infants' ability
+to detect mispronunciations and how this may change with development.
+
+In designing their mispronunciation stimuli, Swingley and Aslin (2000)
+chose consonant mispronunciations that were likely to confuse adults
+(Miller \& Nicely, 1955). Subsequent research has settled on
+systematically modulating phonemic features to achieve mispronunciations
+of familiar words. By utilizing mispronunciations consisting of phonemic
+changes, these experiments examine infants' sensitivity to factors that
+change the identity of a word on a measurable level (i.e.~1-feature,
+2-features, 3-features, etc.). The importance of controlling for the
+degree of phonological mismatch, as measured by number of features
+changed, is further highlighted by studies that find graded sensitivity
+to both consonant (White \& Morgan, 2008) and vowel (Mani \& Plunkett,
+2011) feature changes. The greater the number of features changed, or
+\emph{mispronunciation size}, the easier it may be to detect a
+mispronunciation, whereas more similar mispronunciations may be more
+difficult to detect.
+
+Although most research examining sensitivity to mispronunciations
+follows a similar design, there are some notable differences. For
+example, Swingley and Aslin (2000) presented infants with pairs of
+familiar images, one serving as the labeled target and one as the
+unlabeled distractor. In contrast, White and Morgan (2008; see also Mani
+\& Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented
+infants with pairs of familiar (labeled target) and unfamiliar
+(unlabeled distractor) objects. By using an unfamiliar object as a
+distractor, the infant is presented with a viable option onto which the
+mispronounced label can be applied (Halberda, 2003; Markman, Wasow, \&
+Hansen, 2003). Infants ages 24 and 30 months associate a novel label
+with an unfamiliar object, although only 30-month-olds retained this
+label-object pairing (Bion, Borovsky, and Fernald, 2013). In contrast,
+18-month-olds did not learn to associate a novel label with an
+unfamiliar object, providing evidence that this ability is developing
+from 18 to 30 months. We may find that if mispronunciation sensitivity
+changes as children develop, that this change is modulated by
+\emph{distractor familiarity}: whether the distractor used is familiar
+or unfamiliar. Although mispronunciation sensitivity in the presence of
+a familiar compared to unfamiliar distractor has not been directly
+compared, the baseline preference for familiar compared to novel stimuli
+is also thought to change as infants develop (Hunter \& Ames, 1988).
+Furthermore, young children have been found to look longer at objects
+for which they know the name, compared to objects of an unknown name
+(Schafer \& Plukett, 1998). In other words, in absentia of a label,
+infants may be more or less likely to fixate on an unfamiliar object. To
+account for inherent preferences to the target or distractor image,
+mispronunciation experiments typically compare the increase in fixations
+to the target image from a silent baseline to post-labeling or present
+the same yoked pairs of target and distractor images in in both a
+correct and mispronounced labelling context. Considering this evidence,
+we may expect that in older, but not younger, children, the presence of
+an unfamiliar distractor may lead to greater mispronunciation
+sensitivity than in the presence of a familiar distractor.
+
+Furthermore, when presenting infants with a familiar distractor image,
+some studies control the \emph{phonological overlap between target and
+distractor labels}. For example, when examining sensitivity to a
+mispronunciation of the target word \enquote{dog}, the vowel
+mispronunciation \enquote{dag} would be paired with a distractor image
+that shares onset overlap, such as \enquote{duck}. This ensures that
+infants can not use the onset of the word to differentiate between the
+target and distractor images (Fernald, Swingley, \& Pinto, 2001).
+Instead, infants must pay attention to the mispronounced phoneme in
+order to successfully detect the change. The influence of distractor
+overlap also depends on the \emph{position of mispronunciation} in the
+word, which can be at word onset, medial, or final positions. Models of
+spoken word processing place more or less importance on the position of
+a phoneme in a word. The COHORT model (Marslen-Wilson \& Zwitserlood,
+1989) describes lexical access in one direction, with the importance of
+each phoneme decreasing as its position comes later in the word. In
+contrast, the TRACE model (McClelland \& Elman, 1986) describes lexical
+access as constantly updating and reevaluating the incoming speech input
+in the search for the correct lexical entry, and therefore can recover
+from word onset and to a lesser extent medial mispronunciations.
+
+TRACE has also been used to model infants' sensitivity to
+mispronunciation position (Mayor \& Plunkett, 2014), finding that as
+lexicon size increases, so does sensitivity to onset mispronunciations,
+whereas medial mispronunciations do not experience similar growth. In
+early language acquisition, infants typically know more consonant
+compared to vowel onset words. When tested on their recognition of
+familiar words, therefore, younger infants would show greater
+sensitivity to onset mispronunciations, which are frequently consonant
+mispronunciations. The prevalence of consonant onset words may
+contribute to the finding that consonants carry more weight in lexical
+processing (C-bias; see Nazzi, Poltrock, \& Von Holzen, 2016 for a
+recent review). In mispronunciation sensitivity, this would translate to
+consonant mispronunciations impairing word recognition to a greater
+degree than vowel mispronunciations. Yet, the handful of studies
+directly comparing sensitivity to consonant and vowel mispronunciations
+mostly find symmetry as opposed to an asymmetry between consonants and
+vowels. English-learning 12-, 15-, 18-, and 24-month-olds (Mani \&
+Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds
+(Hojen et al., unpublished) demonstrate similar sensitivity to consonant
+and vowel mispronunciations. One study did find weak evidence for
+greater sensitivity to consonant compared to vowel mispronunciations
+(Swingley, 2016). The English-learning infants tested by Swingley were
+older than previous studies (mean age 28 months). In word learning, the
+C-bias has been found to develop later in English learning infants
+(Floccia, Nazzi, Delle Luche, Poltrock, \& Goslin, 2014; Nazzi, Floccia,
+Moquet, \& Butler, 2009). In the current meta-analysis, we attempt to
+synthesize studies examining sensitivity to the \emph{type of
+mispronunciation}, whether consonant or vowel, across different ages to
+determine whether infants generally exhibit more sensitivity to
+consonant compared to vowel mispronunciations in familiar word
+recognition as predicted by a learned account of C-bias emergence
+(Floccia et al., 2014; Keidel et al., 2007; Nazzi et al., 2016). We
+further examine the impact of language family on mispronunciation
+sensitivity to consonants and vowels, as C-bias emergence has been found
+to have a different developmental trajectory for Romance (French,
+Italian) compared to Germanic (British English, Danish) languages (Nazzi
+et al., 2016).
+
+Finally, mispronunciation sensitivity in infants has been examined in
+many different languages, such as English, Spanish, French, Dutch,
+German, Catalan, Danish, and Mandarin Chinese (see Table 1). Infants
+learning different languages have different ages of acquisition for
+words in their early lexicon, leaving direct comparisons between
+languages within the same study difficult and as a result rare. Although
+we do not explicitly compare overall mispronunciation sensitivity by
+language (although see previous paragraph for rationale to test by
+language family), we assess evidence of mispronunciation sensitivity
+from many different languages using a meta-analytic approach.
 
@@
 meta-analysis can also investigate the role of maturation by assessing
-the impact of age and vocabulary size. As a consequence, our results
-will be important in evaluating theories and drive future research. We
-also make hands-on recommendations for experiment planning, for example
-by providing an effect size estimate for a priori power analyses
-(Bergmann et al., 2018).
+the impact of age and vocabulary size. We also make hands-on
+recommendations for experiment planning, for example by providing an
+effect size estimate for a priori power analyses (Bergmann et al.,
+2018).
 
@@
 
-\begin{longtable}{lllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\scriptsize{
+\begin{longtable}{llllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
 \caption{\label{tab:SummaryTable}Summary of all studies.
-Age is calculated by truncating the mean age reported in the paper.
-The abbreviations Comp and Prod refer to comprehension and production, respectively.}\\
+Age: truncation of mean age reported in the paper.
+Vocabulary: Comp = comprehension, Prod = production.
+Distractor Familiarity: Fam = Familiar Distractor, Unfam = Unfamiliar Distractor.
+Distractor Target Overlap: position of overlap between target and distractor; O = onset, M = medial, C = coda.
+Mispronunciation Size: number of features changed; commas indicate when sizes were compared separately (e.g.
+1, 2, 3), dashes indicate the range of sizes were aggregated (e.g.
+1-3).
+Mispronunciation Position: O = onset, M = medial, C = coda.
+Mispronunciation Type: C = consonant, V = vowel, T = tone.
+For both Mispronunciation Position and Type, a slash separator indicates that is was tested but a distinction was not made in the stimuli.
+For all categories, unspec.
+indicates that the value was unspecified in the paper}\\
 \toprule
-Paper & Publication format & Age & Vocabulary & N Effect Sizes\\
+ &  &  &  & \multicolumn{1}{c}{Distractor} & & \multicolumn{3}{c}{Mispronunciation}  &\\
+\cmidrule(r){5-5} \cmidrule(r){7-9}
+Paper & Format & Age & Vocabulary & Familiarity & Target Overlap & Size & Position & Type & N Effect Sizes\\
 \midrule
-Altvater-Mackensen (2010) & dissertation & 22, 25 & None & 13\\
-Altvater-Mackensen et al. (2014) & paper & 18, 25 & None & 16\\
-Bailey \& Plunkett (2002) & paper & 18, 24 & Comp & 12\\
-Ballem \& Plunkett (2005) & paper & 14 & None & 4\\
-Bergelson \& Swingley (2017) & paper & 6, 7, 9, 12 & None & 9\\
-Bernier \& White (2017) & proceedings & 21 & None & 4\\
-Delle Luche et al. (2015) & paper & 20, 19 & None & 4\\
-Durrant et al. (2014) & paper & 19, 20 & None & 4\\
-Höhle et al. (2006) & paper & 18 & None & 4\\
-Højen et al. (n.d.) & gray paper & 19, 20 & Comp/Prod & 6\\
-Mani \& Plunkett (2007) & paper & 15, 18, 24, 14, 20 & Comp/Prod & 14\\
-Mani \& Plunkett (2010) & paper & 12 & Comp & 8\\
-Mani \& Plunkett (2011) & paper & 23, 17 & None & 15\\
-Mani, Coleman, \& Plunkett (2008) & paper & 18 & Comp/Prod & 4\\
-Ramon-Casas \& Bosch (2010) & paper & 24, 25 & None & 4\\
-Ramon-Casas et al. (2009) & paper & 21, 20, 43, 44 & Prod & 14\\
-Ren \& Morgan (in press) & gray paper & 19 & None & 8\\
-Renner (2017) & dissertation & 17, 24 & None & 6\\
-Skoruppa et al. (2013) & paper & 23 & None & 5\\
-Swingley (2003) & paper & 19 & Comp/Prod & 6\\
-Swingley (2009) & paper & 17 & Comp/Prod & 4\\
-Swingley (2016) & paper & 27, 28 & Prod & 9\\
-Swingley \& Aslin (2000) & paper & 20 & Comp & 2\\
-Swingley \& Aslin (2002) & paper & 15 & Comp/Prod & 4\\
-Tamasi (2016) & dissertation & 30 & None & 4\\
-Tao \& Qinmei (2013) & paper & 12 & None & 4\\
-Tao et al. (2012) & paper & 16 & Comp & 6\\
-van der Feest \& Fikkert, (2015) & paper & 24, 20 & None & 16\\
-van der Feest \& Johnson (2016) & paper & 24 & None & 24\\
-Wewalaarachchi et al. (2017) & paper & 24 & None & 8\\
-White \& Aslin (2011) & paper & 18 & None & 4\\
-White \& Morgan (2008) & paper & 18, 19 & None & 12\\
-Zesiger \& Jöhr (2011) & paper & 14 & None & 8\\
-Zesiger et al. (2012) & paper & 12, 19 & Comp/Prod & 6\\
+Altvater-Mackensen (2010) & dissertation & 22, 25 & None & fam, unfam & O, novel & 1 & O, O/M & C & 13\\
+Altvater-Mackensen et al. (2014) & paper & 18, 25 & None & fam & O & 1 & O & C & 16\\
+Bailey \& Plunkett (2002) & paper & 18, 24 & Comp & fam & none & 1, 2 & O & C & 12\\
+Bergelson \& Swingley (2017) & paper & 7, 9, 12, 6 & None & fam & none & unspec & O/M & V & 9\\
+Bernier \& White (2017) & proceedings & 21 & None & unfam & novel & 1, 2, 3 & O & C & 4\\
+Delle Luche et al. (2015) & paper & 20, 19 & None & fam & O & 1 & O & C/V & 4\\
+Durrant et al. (2014) & paper & 19, 20 & None & fam & O & 1 & O & C/V & 4\\
+Höhle et al. (2006) & paper & 18 & None & fam & none & 1 & O & C & 4\\
+Højen et al. (n.d.) & gray paper & 19, 20 & Comp/Prod & fam & C, O & 2-3 & O/M, C/M & C/V, V, C & 6\\
+Mani \& Plunkett (2007) & paper & 15, 18, 24, 14, 20 & Comp/Prod & fam & O & 1-2, 1 & O & V, C/V, C & 14\\
+Mani \& Plunkett (2010) & paper & 12 & Comp & fam & O & 1 & M, O & V, C & 8\\
+Mani \& Plunkett (2011) & paper & 23, 17 & None & unfam & novel & 1-3, 1, 2, 3 & M & V & 15\\
+Mani, Coleman, \& Plunkett (2008) & paper & 18 & Comp/Prod & fam & O & 1 & M & V & 4\\
+Ramon-Casas \& Bosch (2010) & paper & 24, 25 & None & fam & none & unspec & M & V & 4\\
+Ramon-Casas et al. (2009) & paper & 21, 20 & Prod & fam & none & unspec & M & V & 10\\
+Ren \& Morgan (in press) & gray paper & 19 & None & unfam & none & 1 & O, C & C & 8\\
+Skoruppa et al. (2013) & paper & 23 & None & unfam & O/M & 1 & C & C & 4\\
+Swingley (2003) & paper & 19 & Comp/Prod & fam & O & 1 & O, M & C & 6\\
+Swingley (2009) & paper & 17 & Comp/Prod & fam & none & 1 & O, C & C & 4\\
+Swingley (2016) & paper & 27, 28 & Prod & unfam & novel & 1 & O/M & C/V, C, V & 9\\
+Swingley \& Aslin (2000) & paper & 20 & Comp & fam & none & 1 & O & C/V & 2\\
+Swingley \& Aslin (2002) & paper & 15 & Comp/Prod & fam & none & 1, 2 & O/M & C/V & 4\\
+Tamasi (2016) & dissertation & 30 & None & unfam & novel & 1, 2, 3 & O & C & 4\\
+Tao \& Qinmei (2013) & paper & 12 & None & fam & none & unspec & unspec & T & 4\\
+Tao et al. (2012) & paper & 16 & Comp & fam & none & unspec & unspec & T & 6\\
+van der Feest \& Fikkert, (2015) & paper & 24, 20 & None & fam & O & 1 & O & C & 16\\
+van der Feest \& Johnson (2016) & paper & 24 & None & fam & O & 1 & O & C & 20\\
+Wewalaarachchi et al. (2017) & paper & 24 & None & unfam & novel & 1 & O/M/C & C/V/T, V, C, T & 8\\
+White \& Aslin (2011) & paper & 18 & None & unfam & novel & 1 & M & V & 4\\
+White \& Morgan (2008) & paper & 18, 19 & None & unfam & novel & 1, 2, 3 & O & C & 12\\
+Zesiger \& Jöhr (2011) & paper & 14 & None & fam & none & 1 & O, M & C, V & 7\\
+Zesiger et al. (2012) & paper & 12, 19 & Comp/Prod & fam & none & 1, 2 & O & C & 6\\
 \bottomrule
 \end{longtable}
+}
 \end{lltable}
@@
 image versus a distractor in a eye movement experiment; (5) the stimuli
-were auditory speech. The final sample (n = \emph{34}) consisted of 28
-journal articles, 1 proceedings paper, 3 theses, and 2 unpublished
+were auditory speech. The final sample (n = \emph{32}) consisted of 27
+journal articles, 1 proceedings paper, 2 theses, and 2 unpublished
 reports. We will refer to these items collectively as papers. Table 1
@@
 
-The 34 papers we identified as relevant were then coded with as much
+The 32 papers we identified as relevant were then coded with as much
 consistently reported detail as possible (Bergmann et al., 2018; Tsuji
@@
 population, experiment design and stimuli, and results. For the planned
-analyses to evaluate the development of mispronunciation sensitivity, we
-focus on the following characteristics:
+analyses to evaluate the development of mispronunciation sensitivity and
+modulating factors, we focus on the following characteristics:
 
@@
 2 Mean age reported per group of infants, in days;\\
-3 Vocabulary size, measured by a standardized questionnaire or list;
+3 Vocabulary size, measured by a standardized questionnaire or list;\\
+4 Size of mispronunciation, measured in features changed;\\
+5 Distractor familiarity: familiar or unfamiliar;\\
+6 Phonological overlap between target and distractor: onset,
+onset/medial, rhyme, none, novel word;\\
+7 Position of mispronunciation: onset, medial, offset, or mixed;\\
+8 Type of mispronunciation: consonant, vowel, or both.
 
@@
 analyses (see next section). We will call each row a record; in total
-there were 271 records in our data.
+there were 251 records in our data.
 
@@
 We calculated Hedges' \emph{g} using the raw means and standard
-deviations reported in the paper (\emph{n} = 186 records from 26 papers)
+deviations reported in the paper (\emph{n} = 177 records from 25 papers)
 or reported t-values (\emph{n} = 74 records from 9 papers). Two papers
@@
 (Altvater-Mackensen et al., 2014; Swingley, 2016). Raw means and
-standard deviations were extracted from figures for 4 papers. In a
+standard deviations were extracted from figures for 3 papers. In a
 within-participant design, when two means are compared (i.e.~looking
@@
 \centering
-\includegraphics{Paper_Analyses_files/figure-latex/FunnelCombo-1.pdf}
+\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/FunnelCombo-1.pdf}
 \caption{\label{fig:FunnelCombo}Funnel plots for object identification,
@@
 \centering
-\includegraphics{Paper_Analyses_files/figure-latex/PlotMPEffect-1.pdf}
+\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotMPEffect-1.pdf}
 \caption{\label{fig:PlotMPEffect}Panel a: Effect sizes for correct
@@
 \centering
-\includegraphics{Paper_Analyses_files/figure-latex/Vocab-describe1-1.pdf}
+\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/Vocab-describe1-1.pdf}
 \caption{\label{fig:Vocab-describe1}Counts of studies included in the
@@
 theories of phono-lexical development, which predict either an increase
-(Curtin \& Werker, 2007; Curtin et al., 2011; Werker \& Curtin, 2005) or
-decrease (Best, 1994, 1995) in mispronunciation sensitivity.
-Furthermore, although we found a relationship between vocabulary size
-(comprehension) and target looking for correct pronunciations, we found
-no relationship between vocabulary and target looking for
-mispronunciations. This also runs counter to the predictions for the
-PRIMR (Curtin \& Werker, 2007; Curtin et al., 2011; Werker \& Curtin,
-2005) and Assimilation (Best, 1994, 1995) models, but may be due to our
-analyses being underpowered. In sum, it seems that current theories of
-infants' phono-lexical development cannot fully capture our results, but
-that more investigation is needed to draw a firm conclusion.
+(Curtin \& Werker, 2007; Curtin, Byers-Heinlein, \& Werker, 2011; Werker
+\& Curtin, 2005) or decrease (Best, 1994, 1995) in mispronunciation
+sensitivity. Furthermore, although we found a relationship between
+vocabulary size (comprehension) and target looking for correct
+pronunciations, we found no relationship between vocabulary and target
+looking for mispronunciations. This also runs counter to the predictions
+for the PRIMR (Curtin \& Werker, 2007; Curtin et al., 2011; Werker \&
+Curtin, 2005) and Assimilation (Best, 1994, 1995) models, but may be due
+to our analyses being underpowered. In sum, it seems that current
+theories of infants' phono-lexical development cannot fully capture our
+results, but that more investigation is needed to draw a firm
+conclusion.
 
@@
 \centering
-\includegraphics{Paper_Analyses_files/figure-latex/Plot-post-name-cond-age-1.pdf}
+\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/Plot-post-name-cond-age-1.pdf}
 \caption{\label{fig:Plot-post-name-cond-age}Effect sizes for the different
@@
 
-\paragraph{Offset time after target
-naming}\label{offset-time-after-target-naming}
+\paragraph{Onset time after target
+naming}\label{onset-time-after-target-naming}
 
@@
 (PTL) in response to correct and mispronounced words. Experiments
-typically include a phase where no naming event has occurred, whether
-correctly pronounced or mispronounced, which we refer to as the
-pre-naming phase The purpose of the pre-naming phase is to ensure that
-infants do not have systematic preferences for the target or distractor
-(greater interest in a cat compared to a cup) which may drive PTL scores
-in the post-naming phase. As described in the Data Analysis sub-section
-of the Methods, however, there was considerable variation across papers
-in whether this pre-naming phase was used as a baseline measurement, or
-whether a different baseline measurement was used. This resulted in
-different measured outcomes or dependent variables. Over half of the
-experimental conditions (\emph{n} = 129) subtracted the PTL score for a
-pre-naming phase from the PTL score for a post-naming phase. This
-results in one value, which is then compared with a chance value of 0.
-When positive, this indicates that infants increased their looks to the
-target after hearing the naming label (correct or mispronounced)
-relative to the pre-naming baseline PTL. We will refer to this dependent
-variable as the Difference Score. Another dependent variable, which was
-used in 69 experimental conditions, directly compared the post- and
-pre-naming PTL scores with one another. This requires two values, one
-for the pre-naming phase and one for the post-naming phase. A greater
-post compared to pre-naming phase PTL indicates that infants increased
-their target looks after hearing the naming label. We will refer to this
-dependent variable as Pre vs.~Post. Finally, the remaining 53
-experimental conditions compared the post-naming PTL score with a chance
-value of 50\%. Here, the infants' pre-naming phase baseline preferences
-are not considered and instead target fixations are evaluated based on
-the likelihood to fixate one of two pictures. We will refer to this
-dependent variable as Post.
+typically include a phase where a naming event has not yet occurred,
+which we refer to as the pre-naming phase. This is followed by a naming
+event, whether correctly pronounced or mispronounced, and the subsequent
+phase we refer to as the post-naming phase. The purpose of the
+pre-naming phase is to ensure that infants do not have systematic
+preferences for the target or distractor (greater interest in a cat
+compared to a cup) which may drive PTL scores in the post-naming phase.
+As described in the Data Analysis sub-section of the Methods, however,
+there was considerable variation across papers in whether this
+pre-naming phase was used as a baseline measurement, or whether a
+different baseline measurement was used. This resulted in different
+measured outcomes or dependent variables. Over half of the experimental
+conditions (\emph{n} = 129) subtracted the PTL score for a pre-naming
+phase from the PTL score for a post-naming phase, resulting in a
+Difference Score. The Difference Score is one value, which is then
+compared with a chance value of 0. When positive, this indicates that
+infants increased their looks to the target after hearing the naming
+label (correct or mispronounced) relative to the pre-naming baseline
+PTL. In contrast, Pre vs.~Post (\emph{n} = 69 experimental conditions),
+directly compare the post- and pre-naming PTL scores with one another
+using a statistical test (e.g.~t-test, ANOVA). This requires two values,
+one for the pre-naming phase and one for the post-naming phase. A
+greater post compared to pre-naming phase PTL indicates that infants
+increased their target looks after hearing the naming label. The
+remaining experimental conditions used a Post dependent variable
+(\emph{n} = 53 experimental conditions), which compares the post-naming
+PTL score with a chance value of 50\%. Here, the infants' pre-naming
+phase baseline preferences are not considered and instead target
+fixations are evaluated based on the likelihood to fixate one of two
+pictures (50\%). As most papers do not specify whether these
+calculations are made before or after aggregating across trials, we make
+no assumptions about when this step is taken.
 
@@
 \centering
-\includegraphics{Paper_Analyses_files/figure-latex/Plot-Within-cond-age-diff-score-1.pdf}
+\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/Plot-Within-cond-age-diff-score-1.pdf}
 \caption{\label{fig:Plot-Within-cond-age-diff-score}Effect sizes for the
@@
 handful of variables that relate to data analysis, specifically relating
-to timing (post-naming analysis window; offset time) and to the
+to timing (post-naming analysis window; onset time) and to the
 calculation of the dependent variable reported. We focused on these
@@
 
-Infants are expected to recognize words more quickly with age (Fernald
-et al., 1998). This evidence has often guided decisions for the
+Infants recognize words more quickly with age (Fernald et al., 1998),
+which has the potential to influence decisions for the analysis of the
 post-naming time window in mispronunciation sensitivity studies,
-including where to begin the time window (offset time) and how long this
-analysis window should be (post-naming analysis window). Specifically,
-increasing age should lead to quicker reaction times, and therefore
-lower offset times. Yet, we found no evidence for a relationship between
-offset time and infant age nor that offset time modulated
-mispronunciation sensitivity. Indeed, a majority of studies used an
-offset time between 360 and 370 ms, which follows the \enquote{best
-guess} of Swingley and Aslin (2000) for the amount of time needed for
-infants to initiate eye movements in response to a spoken target word.
-
-In contrast, both the length of the post-naming analysis window and the
-type of dependent variable calculated modulated mispronunciation
-sensitivity. Most critically, however, variation in these variables
-resulted in changes to the developmental trajectory of mispronunciation
-sensitivity. Given a set of mispronunciation sensitivity data, a
-conclusion regarding the development of mispronunciation sensitivity
-would be different depending on the length of the post-naming analysis
-window or the choice of dependent variable.
+including where to begin the time window (onset time) and how long this
+analysis window should be (post-naming analysis window). For example, as
+age increases, reaction time should increase and experimenters may
+adjust and lower offset times in their analysis as well as shorten the
+length of the analysis window. Yet, we find no relationship between age
+and offset times, nor that offset time modulated mispronunciation
+sensitivity. Indeed, a majority of studies used an offset time between
+360 and 370 ms, which follows the \enquote{best guess} of Swingley and
+Aslin (2000) for the amount of time needed for infants to initiate eye
+movements in response to a spoken target word. Without knowledge of the
+base reaction time in a given population of infants, use of this best
+guess offset time reduces the number of free parameters. In contrast, we
+found a negative correlation between infant age and the length of the
+post-naming analysis window, and that the length of the analysis window
+moderated mispronunciation sensitivity, such increasing the length of
+the analysis windows decreases the size of mispronunciation sensitivity.
+Given a set of mispronunciation sensitivity data, a conclusion regarding
+the development of mispronunciation sensitivity would be different
+depending on the length of the post-naming analysis window. Although we
+have no direct evidence, an analysis window can be potentially set after
+collecting data. At worst, this adjustment could be the result of a
+desire to confirm a hypothesis, increasing the rate of false-positives
+(Gelman \& Loken, 2013): a \enquote{significant effect} of
+mispronunciation sensitivity is found with an analysis window of 2000
+but not 3000 ms, therefore 2000 ms is chosen. At best, this variation
+introduces noise into the study of mispronunciation sensitivity, bluring
+the true developmental trajectory of mispronunciation sensitivity. In
+the next section, we highlight some suggestions for how the field can
+remedy this issue.
+
+Surpisingly, we found that the type of dependent variable calculated
+moderated mispronunciation sensitivity and conclusions about its
+developmental trajectory. Unlike the exploratory analyses related to
+timing (onset and post-naming analysis window), there is not a clear
+reason for one dependent variable to be chosen over another; the
+prevelence of each dependent variable appears distributed across ages
+and some authors always calculate the same dependent variable while
+others use them interchangeably in different publications. One clear
+difference is that both the Difference Score and Pre vs.~Post dependent
+variables take into account each infants' actual preference in the
+pre-naming baseline phase, while the Post dependent variable does not.
+Without access to the raw data, it is difficult to conclusively
+determine why different dependent variable calculations influence
+mispronunciation sensitivity. In the next section, we advocate for the
+adoption of Open Data practices as one way to address this issue.
 
@@
 
-We take this opportunity to suggest several solutions. Preregistration
-can serve as proof of a priori decisions regarding data analysis, which
-can also contain a data-dependent description of how data analysis
-decisions will be made once data is collected. The peer-reviewed form of
+We take this opportunity to suggest several recommendations to address
+the issue of potential posthoc analysis decisions. Preregistration can
+serve as proof of a priori decisions regarding data analysis, which can
+also contain a data-dependent description of how data analysis decisions
+will be made once data is collected. The peer-reviewed form of
 preregistration, termed Registered Reports, has already been adopted by
@@
 the impact of analysis decisions and cumulatively analyze different
-datasets in the same way. Experimenters can also opt to analyze the time
-course as a whole, instead of aggregating the proportion of target
-looking behavior over the entire trial. This allows for a more detailed
-assessment of infants' fixations over time and reduces the need to
-reduce the post-naming analysis window. Both Growth Curve Analysis (Law
-II \& Edwards, 2015; Mirman, Dixon, \& Magnuson, 2008) and Permutation
-Clusters Analysis (Delle Luche, Durrant, Poltrock, \& Floccia, 2015;
-Maris \& Oostenveld, 2007; Von Holzen \& Mani, 2012) offer potential
-solutions to analyze the full time course. Furthermore, it may be useful
-to establish standard analysis pipelines for mispronunciation studies.
-This would allow for a more uniform analysis of this phenomenon, as well
-as aid experimenters in future research planning. In general, however, a
-better understanding of how different levels of linguistic knowledge may
-drive looking behavior is needed. We hope this understanding can be
-achieved by applying the above suggestions.
+datasets in the same way. Considering the issue of analysis time window,
+experimenters can opt to analyze the time course as a whole, instead of
+aggregating the proportion of target looking behavior over the entire
+trial. This allows for a more detailed assessment of infants' fixations
+over time and reduces the need to reduce the post-naming analysis
+window. Both Growth Curve Analysis (Law II \& Edwards, 2015; Mirman,
+Dixon, \& Magnuson, 2008) and Permutation Clusters Analysis (Delle
+Luche, Durrant, Poltrock, \& Floccia, 2015; Maris \& Oostenveld, 2007;
+Von Holzen \& Mani, 2012) offer potential solutions to analyze the full
+time course. Furthermore, it may be useful to establish standard
+analysis pipelines for mispronunciation studies. This would allow for a
+more uniform analysis of this phenomenon, as well as aid experimenters
+in future research planning. In general, however, a better understanding
+of how different levels of linguistic knowledge may drive looking
+behavior is needed. We hope this understanding can be achieved by
+applying the above suggestions.
 
@@
 
-\hypertarget{ref-Best2009}{}
-Best, C. T., Tyler, M. D., Gooding, T. N., Orlando, C. B., \& Quann, C.
-A. (2009). Development of phonological constancy: Toddlers' perception
-of native- and Jamaican-accented words. \emph{Psychological Science},
-\emph{20}(5).
-doi:\href{https://doi.org/10.1111/j.1467-9280.2009.02327.x.}{10.1111/j.1467-9280.2009.02327.x.}
-
 \hypertarget{ref-Black2017}{}
@@
 
-\hypertarget{ref-clark1977}{}
-Clark, H. H., \& Clark, E. V. (1977). \emph{Psychology and Language: An
-introduction to psycholinguistics.} New York: Harcourt Brace Jovanovich.
-
 \hypertarget{ref-cohen}{}
@@
 
-\hypertarget{ref-Kuhl2004}{}
-Kuhl, P. K. (2004). Early language acquisition: Cracking the speech
-code. \emph{Nature Reviews. Neuroscience}, \emph{5}(11), 831--43.
-doi:\href{https://doi.org/10.1038/nrn1533}{10.1038/nrn1533}
-
 \hypertarget{ref-Law2015}{}
@@
 
-\hypertarget{ref-Mulak2014}{}
-Mulak, K. E., Best, C. T., Tyler, M. D., Kitamura, C., \& Irwin, J. R.
-(2014). Development of phonological constancy: 19-month-olds, but not
-15-month-olds, identify words in a non-native regional accent.
-\emph{Child Development}, \emph{84}(6), 2064--2074.
-doi:\href{https://doi.org/10.1111/cdev.12087}{10.1111/cdev.12087}
-
 \hypertarget{ref-R}{}
@@
 \url{https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/}
-
-\hypertarget{ref-Schmale2011}{}
-Schmale, R., Hollich, G., \& Seidl, A. (2011). Contending with foreign
-accent in early word learning. \emph{Journal of Child Language},
-\emph{38}(5), 1096--108.
-doi:\href{https://doi.org/10.1017/S0305000910000619}{10.1017/S0305000910000619}
 

### 2019-05-06 scripts/Swingley_Aslin_example.R

@@ -1,0 +1,113 @@
+#### Example Plot ####
+
+# This script creates boxplots for the original data from Swingley & Aslin, 2000
+# Original Author: Katie Von Holzen
+# katie.m.vonholzen'at'gmail.com
+# last modified: March 19, 2019
+#   by Katie Von Holzen
+#### Load libraries ####
+
+#setwd("~/Dropbox/MP_MA")
+
+library(ggplot2)
+library(wesanderson)
+library(reshape)
+library(doBy)
+
+std <- function(x) sd(x)/sqrt(length(x))
+
+# Color Blind palette:
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
+
+correct <- rnorm(100, mean=0.730396429, sd=0.10471147)
+misp <- rnorm(100, mean=0.612614286, sd=0.093135265)
+
+cm <- data.frame(cbind(correct, misp))
+cm$sub <- seq(1, nrow(cm))
+
+dat.m2 <- melt(cm,
+               id=c(3),
+               measure=c(1:2),
+               variable="Measure", na.rm=T)
+names(dat.m2) <- c("sub", "condition", "PTL")
+
+
+box1 <- ggplot(data=dat.m2, aes(x=condition, y=PTL, fill=condition)) +
+  geom_boxplot()+
+  scale_fill_manual(values=cbPalette)+
+  theme_bw()+
+  annotate("segment", x = .67, xend = .67, y = .7, yend = .5, colour="black", size=1, arrow=arrow())+
+  annotate("segment", x = 1, xend = 2, y = .96, yend = .96, colour="black", size=1)+
+  annotate("text", x = .5, y = .63, parse = TRUE, label = "recognition",angle = 90, size = 10)+
+  annotate("text", x = 1.5, y = .99, parse = TRUE, label = "misp_sensitivity", size = 10)+
+  geom_hline(yintercept = .5)+
+  coord_cartesian(ylim = c(.35, 1))+
+  #coord_flip()+
+  theme(text = element_text(size=30),
+        legend.position = "bottom",
+        legend.title = element_blank(),
+        axis.text.x = element_blank(),
+        axis.title.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank())+
+  ylab("Proportion of Target Looks")
+
+#ggsave("Example_boxplot.jpg", box1)
+
[…]

### 2019-05-24 VonHolzenBergmann_MPMetaAnalysis.Rmd
moderator analysis results completed

@@
 These questions concern issues at the intersection of phonological development and lexical processing and often result in manipulations of the stimuli and experimental procedure.
+These manipulations may impact our overall estimate of the effect size of mispronunciation sensitivity.
 Next to the core investigation of the shape of development of infants' mispronunciation sensitivity, we take the opportunity of a systematic aggregation of data to address these questions and the influence of these manipulations on infants' ability to detect mispronunciations and how this may change with development.
@@
 1-feature, 2-features, 3-features, etc.).
-The importance of controlling for the degree of phonological mismatch, as measured by number of features changed, is further highlighted by studies that find graded sensitivity to both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes.
+The importance of controlling for the degree of phonological mismatch, as measured by number of features changed, is further highlighted by studies that find graded sensitivity to both consonant (Bernier & White, 2017; Tamasi, 2016; White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes.
 The greater the number of features changed, or *mispronunciation size*, the easier it may be to detect a mispronunciation, whereas more similar mispronunciations may be more difficult to detect.
@@
 
+A detailed explanation for moderating factors 3-8 can be found in their respective sections in the Results.
 We separated conditions according to whether or not the target word was mispronounced to be able to investigate infants' looking to the target picture as well as their mispronunciation sensitivity, which is the difference between looks to the target in correct and mispronounced trials.
@@
 
-### Interim Discussion
+### Interim discussion: Development of infants' mispronunciation sensitivity
 
@@
 We observe that the data for directly reported vocabulary size were too sparse to draw strong conclusions.
-Of the three predictions about the development of infants' sensitivity to mispronunciations discussed in the Introduction, the present results lend some support for the proposal that mispronunciation sensitivity stays consistent as infants develop.
-This runs counter to existing theories of phono-lexical development, which predict either an increase [@Curtin2007; @Curtin2011; @Werker2005] or decrease [@Best1994; @Best1995] in mispronunciation sensitivity.
+In the literature, evidence for all possible developmental trajectories has been found, including mispronunciation sensitivity that increases, decreases, or does not change with age or vocabulary size.
+The present results do lend some support for the proposal that mispronunciation sensitivity stays consistent as infants develop.
 Furthermore, although we found a relationship between vocabulary size (comprehension) and target looking for correct pronunciations, we found no relationship between vocabulary and target looking for mispronunciations.
-This also runs counter to the predictions for the PRIMR [@Curtin2007; @Curtin2011; @Werker2005] and Assimilation [@Best1994; @Best1995] models, but may be due to our analyses being underpowered.
-In sum, it seems that current theories of infants' phono-lexical development cannot fully capture our results, but that more investigation is needed to draw a firm conclusion.
-
-Alternatively, an effect of maturation might have been masked by other factors we have not yet captured in our analyses.
+This may be due to too few studies including reports of vocabulary size and more investigation is needed to draw a firm conclusion.
+
+Alternatively, the lack of developmental change in mispronunciation sensitivity could be due to differences in the types of tasks given to infants of different ages.
+If infants' word recognition skills are generally thought to improve with age and vocabulary size, research questions that tap more complex processes may be more likely to be investigated in older infants.
+In the following section, we investigate the role that different moderators play in mispronunciation sensitivity.
+To investigate the possibility of systematic differences in the tasks across ages, we additionally include an exploratory analysis of whether different moderators and experimental design features were included at different ages.
+
+## Moderator Analyses
+
+In this section, we consider each moderator individually and investigate its influence on mispronunciation sensitivity.
+For most moderators (except Number of features changed), we combine the correct and mispronounced datasets and include the moderator of condition, to study mispronunciation sensitivity as opposed to object recognition.
+To better understand the impact of these moderators on developmental change, we include age as subsequent moderator as well as an exploratory analysis of the age of infants tested with each type of moderator.
+The latter analysis is included to explore whether the lack of developmental change in mispronunciation sensitivity in the overall dataset is due to more complex moderator tasks being given to older infants, which may lower the overall effect size of mispronunciation sensitivity at older ages and dampen any evidence of change.
+Finally, we analyze the relationship between infant age and the moderator condition they were tested in using Fischer's exact test, which is more appropriate for small sample sizes (Fischer, 1922).
+For each moderator, we evaluate the independence of infants' age group (divided into quartiles unless otherwise specified) and assignment to each type of condition in a particular moderator.
+
+### Size of mispronunciation
+
+```{r NFeatures_demographics, results = "hide"}
+
+dat.f <- subset(dat, n_feature != "2_3" & n_feature != "1_2" & n_feature != "1_2_3")
+
+dat.f$n_feature <- factor(dat.f$n_feature, levels = c("0", "1", "2", "3"))
+
+dat.f$n_feature <- as.numeric(as.character(dat.f$n_feature))
+
+dat.f$n_feature <- ifelse(dat.f$condition == 1, 0, df$n_feature)
+
+nfeature_info <- dat.f %>%
+  group_by(n_feature) %>%
+  summarize(n_exp_conditions =  n())
+
+```
+
+To assess whether the size of the mispornunciation tested, as measured by the number of features change, modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced using 1-, 2-, and 3-feature changes.
+We did not include data for which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent (e.g., one mispronunciation included a 2-feature change whereas another only a 1-feature change).
+This analysis was therefore based on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` experimental conditions for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations.
+Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an equal impact on mispronunciation sensitivity, following the argument of graded sensitivity (White & Aslin, 2008; Mani & Plunkett 2011), and this modertor was coded as a continuous variable.
+
+```{r NFeatures, results = "hide"}
+
+dat.f <- subset(dat, n_feature != "2_3" & n_feature != "1_2" & n_feature != "1_2_3")
+
+dat.f$n_feature <- factor(dat.f$n_feature, levels = c("0", "1", "2", "3"))
+
+dat.f$n_feature <- as.numeric(as.character(dat.f$n_feature))
+
+dat.f$n_feature <- ifelse(dat.f$condition == 1, 0, dat.f$n_feature)
+
+# overall object recognition
+rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~n_feature, data = dat.f, random = ~ same_infant_calc | short_cite)
+
+ sum_eff <- coef(summary(rma_NFeatures))[2,]
+
+ linear_feature <- sum_eff$estimate
+
+```
+
+```{r NFeatures_age, results = "hide"}
+
+dat.f <- subset(dat, n_feature != "2_3" & n_feature != "1_2" & n_feature != "1_2_3")
+
+dat.f$n_feature <- factor(dat.f$n_feature, levels = c("0", "1", "2", "3"))
+
+dat.f$n_feature <- as.numeric(as.character(dat.f$n_feature))
+
+dat.f$n_feature <- ifelse(dat.f$condition == 1, 0, df$n_feature)
+
+# age moderator
+rma_NFeatures_age <- rma.mv(g_calc, g_var_calc, mods = ~n_feature*age.C, data = dat.f, random = ~same_infant_calc | short_cite)
+
+ sum_eff_age <- coef(summary(rma_NFeatures_age))[4,]
+
+ # divide into age groups
+
+ dat.f$age_group <- ntile(dat.f$mean_age_1, 4)
+
+ nfeature_ages <- dat.f %>%
+  group_by(age_group, n_feature) %>%
+  summarize(n =  n())
+
+ #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
+
+ nfeature_ages <- nfeature_ages %>% spread(n_feature, n)
+
+ #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
+fish.test <- fisher.test(nfeature_ages)
+
+```
+
+To understand the relationship between mispronunciation size and mispronunciation sensitivity, we  evaluated the effect size Hedges' *g* with number of features changed as a moderator.
+The moderator test was significant, `r mod_test(rma_NFeatures)`.
+Hedges' *g* for number of features changed was `r g_SE(sum_eff)`, which indicated that as the number of features changed increased, the effect size Hedges' *g* significantly decreased `r CI_p(sum_eff)`.
+We plot this relationship in Figure \@ref(fig:PlotFeatEffect).
+This confirms previous findings of a graded sensitivity to the number of features changed for both consonant (Bernier & White, 2017; Tamasi, 2016; White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) mispronunciations as well as the importance of controlling for the degree of phonological mismatch in experimental design.
+
+To better understand how this moderator impacted our estimate of developmental change in mispronunciation sensitivity, we added age as a moderator.
+The moderator test was significant, `r mod_test(rma_NFeatures_age)`, but the interaction between age and number of features changed was not significant, $\beta$`r full_estimate(sum_eff_age)`.
+The small effect size for the interaction between age and number of features changed suggests that the impact of number of features changed on mispronunciation sensitivity does not change with infant age.
+This may be due to the fact that only a handful of studies have explicitly examined the effect of the number of features changed on mispronunciation sensitivity and only these studies include 3-feature changes (Bernier & White, 2017; Tamasi, 2016; White & Morgan, 2008; Mani & Plunkett, 2011).
+
+The results of Fisher's exact test were not significant, *p* `r psig(fish.test$p.value)`.
+This lack of a relationship suggests that older and younger infants are not being tested in experimental conditions that differentially manipulate the number of features changed.
+
+## (Insert Figure 5 about here)
+
+```{r PlotFeatEffect, echo = FALSE}
+
+dat.f <- subset(dat, n_feature != "2_3" & n_feature != "1_2" & n_feature != "1_2_3")
+dat.f$n_feature <- factor(dat.f$n_feature, levels = c("0", "1", "2", "3"))
+dat.f$n_feature <- as.numeric(as.character(dat.f$n_feature))
+dat.f$n_feature <- ifelse(dat.f$condition == 1, 0, df$n_feature)
+
+dat.f$feat_cat <- ifelse(dat.f$n_feature == 1, "1-feature",
+                         ifelse(dat.f$n_feature == 2, "2-feature",
+                                ifelse(dat.f$n_feature == 3, "3-feature",
+                                       ifelse(dat.f$n_feature == 0, "correct", "none"))))
+
+dat.f <- subset(dat.f, feat_cat != "none")
+
+dat.f$Features_changed <- factor(dat.f$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))
+
+p.MS <- ggplot(dat.f, aes(Features_changed, g_calc, fill = Features_changed)) + 
+  geom_violin() + 
+  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "none",
+        axis.title.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Hedges' g")
+
+p.MS
+
+ms.age <- ggplot(dat.f, aes(mean_age_1/30.44, g_calc, color = Features_changed)) + 
+    #facet_grid(.~dv_label)+
+  geom_point(aes(size = n_1),show.legend=FALSE) +
+  labs(title="b")+
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Hedges' g")
+
+# ms.age
+
+  jpeg(filename = "figures/Figure_5_Number_of_Features.jpg", 
+       width = 500, height = 300, units = "px")
+
+  p.MS
+
+  dev.off()
+
+```
+
+### Distractor familiarity
+
+```{r DistFam_demographics, results = "hide"}
+
+distr_info <- dat %>%
+  group_by(object_pair) %>%
+  summarize(n_exp_conditions =  n())
+
+```
+
+To assess whether familiarity with the distractor image modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced and were either paired with a familiar or unfamiliar distractor.
+A familiar distractor was used in `r with(distr_info, n_exp_conditions[object_pair == "familiar_familiar"])` experimental conditions and a unfamiliar distractor in `r with(distr_info, n_exp_conditions[object_pair == "familiar_novel"])` experimental conditions.
+
+```{r DistractorType, results= "asis"}
+
+rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition, data = dat, random = ~ same_infant_calc | short_cite)
+
+d_fam <- coef(summary(rma_Distractor))[2,]
+d_fam_condit <- coef(summary(rma_Distractor))[4,]
+
+```
+
+```{r DistractorType_age, results= "asis"}
+
+# age moderator
+rma_Distractor_age <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition*age.C, data = dat, random = ~ same_infant_calc | short_cite)
+
+ sum_eff_age <- coef(summary(rma_NFeatures_age))[8,]
+ sum_eff_2 <- coef(summary(rma_NFeatures_age))[5,]
+
+ # divide into age groups
+
+ dat$age_group <- ntile(dat$mean_age_1, 4)
+
+ dist_fam_ages <- dat %>%
+  group_by(age_group, object_pair) %>%
+  summarize(n =  n())
+
+ #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
+
+ dist_fam_ages <- dist_fam_ages %>% spread(object_pair, n)
+
+ #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
+fish.test <- fisher.test(dist_fam_ages)
+
+```
+
+To understand the relationship between distractor familiarity and mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with distractor familiarity and condition as moderators.
+The moderator test was significant, `r mod_test(rma_NFeatures)`, but the effect of distractor familiarity ($\beta$`r full_estimate(d_fam)`) as well as the interaction between distractor familiarity and condition ($\beta$`r full_estimate(d_fam_condit)`) were not significant.
+The results suggest that overall, infants' familiarity with the distractor object (familiar or unfamiliar) did not impact their mispronunciation sensitivity.
+
+We next examined whether age modulates object recognition or mispronunciation sensitivity when the distractor image is familiar or unfamiliar.
+Based on previous results, we expected older infants  to have greater mispronunciation sensitivity than younger infants when the distractor was unfamiliar compared to familiar.
+To evaluate this prediction, we added age as a moderator.
+The moderator test was significant `r mod_test(rma_Distractor_age)`.
+The estimate for the  three-way-interaction between condition, distractor familiarity, and age was small and not significant ($\beta$ = `r full_estimate(sum_eff_age)`.
+We note that in this model, the interaction between condition and distractor familiarity was significant ($\beta$`r full_estimate(sum_eff_2)`, but that this estimate is similar to the original, non-significant estimate specifically examining this interaction in the previous model.
+Taken together, these results suggest that regardless of age, mispronunciation sensitivity was similar whether the distractor image was familiar or unfamiliar.
+
+The results of Fisher's exact test were not significant, *p* `r psig(fish.test$p.value)`.
+This lack of a relationship suggests that older and younger infants are not being tested in experimental conditions that differentially employ distractor images that are familiar or unfamiliar.
+
+### Phonological overlap between target and distractor
+
+```{r DistractorOverlap_descrip}
+
+dist_overlap_info <- dat %>%
+  group_by(distractor_overlap) %>%
+  summarize(n_exp_conditions =  n())
+
+```
+
+To assess whether phonological overlap between the target and distractor image labels has an impact on the size of mispronunciation sensitivity, we examined the meta-analytic effect for object identification in response to mispronunciations and mispronunciation sensitivity when the target-distractor pairs either had no overlap or shared the same onset phoneme.
+We did not include data for which the overlap included both the onset and medial phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset/medial"])`), coda phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "coda"])`), or for targets paired with an unfamiliar distractor image `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "novel"])`.
+The analysis was therefore based on a subset of the overall dataset, with `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset"])` experimental conditions containing onset phoneme overlap between the target and distractor and `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "no"])` containing no overlap between target and distractor.
+
+```{r DistractorOverlap}
+
+db_ET_MPo_MS = dat %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "no")
+
+db_ET_MPo_MS$distractor_overlap <- factor(db_ET_MPo_MS$distractor_overlap, levels = c("no", "onset"))
+
+rma_DistractorOverlapMS <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MPo_MS, random = ~ same_infant_calc | short_cite)
+
+#summary(rma_DistractorOverlapMS)
+
+sum_eff2 <- coef(summary(rma_DistractorOverlapMS))[4,]
+
+```
+
+```{r DistractorOverlap_age}
+
+# mispronunciation sensitivity
+dat_MPo = dat %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "no")
+
+dat_MPo$distractor_overlap <- factor(dat_MPo$distractor_overlap, levels = c("no", "onset"))
+
+rma_DistractorOverlap_age_MS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap*condition, data = dat_MPo, random = ~ same_infant_calc | short_cite)
+
+#summary(rma_DistractorOverlap_age_MS)
+
+sum_eff_age <- coef(summary(rma_DistractorOverlap_age_MS))[8,]
+
+ # divide into age groups
+
+ dat_MPo$age_group <- ntile(dat_MPo$mean_age_1, 4)
+
+ dist_overlap_ages <- dat_MPo %>%
+  group_by(age_group, distractor_overlap) %>%
+  summarize(n =  n())
+
+ #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
+
+ dist_overlap_ages <- dist_overlap_ages %>% spread(distractor_overlap, n)
+
+ #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
+fish.test <- fisher.test(dist_overlap_ages, workspace=2e8)
+
+```
+
+To understand the relationship between phonological overlap between target and distractor and  mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with distractor overlap and condition as moderators.
+The moderator test was significant, `r mod_test(rma_DistractorOverlapMS)`.
+The estimate for the interaction between condition and distractor overlap was small, but significant ($\beta$ `r full_estimate(sum_eff2)`, suggesting that mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap.
+This relationship be seen in Figure \@ref(fig:PlotDistOverlap)a.
+
+To better understand how this moderator impacted our estimate of developmental change in mispronunciation sensitivity, we added age as a moderator.
+The moderator test was significant, `r mod_test(rma_DistractorOverlap_age_MS)` and the estimate for the three-way interaction between age, condition, and distractor overlap was significant, but relatively small ($\beta$ = `r full_estimate(sum_eff_age)`.
+As can be seen in Figure \@ref(fig:PlotDistOverlap)b, mispronunciation sensitivity increases with age for target-distractor pairs containing onset overlap, but decreases with age for target-distractor pairs containing no overlap.
+
+The results of Fisher's exact test were significant, *p* `r psig(fish.test$p.value)`.
+Older infants were more likely to be tested in experimental conditions where target and distractor images overlapped on their onset phoneme, while younger infants were more likely to be tested with target and distractor images that did not control for overlap.
+A distractor image that overlaps in the onset phoneme with the target image is considered a more challenging task to the infant, as infants must pay attention to the mispronounced phoneme and can not use the differing onsets between target and distractor images to differentiate (Fernald, Swingley, & Pinto, 2001).
+It therefore appears that older infants were given a more challenging task than younger infants.
+This may explain why infants in the onset overlap condition, a harder task, have a greater effect size estimate for mispronunciation sensitivity than those in the no overlap condition, which is a comparably easier task.
+We return to this issue in the General Discussion.
+
+## (Insert Figure 6 about here)
+
+```{r PlotDistOverlap}
+
+db_ET_MPo = dat %>%
+  filter(distractor_overlap == "onset"  | distractor_overlap == "no")
+
+db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no"))
+
+db_ET_MPo$condition_label <- ifelse(db_ET_MPo$condition==1, "Correct", "Mispronunciation")
+
+db_ET_MPo$distractor_label <- ifelse(db_ET_MPo$distractor_overlap=="onset", "Onset Overlap", "No Overlap")
+
+db_ET_MPo <- db_ET_MPo[,c("short_cite", "is_correct", "is_mp", "distractor_label", "condition_label", "g_calc", "weights_g", "mean_age_1", "n_1")]
+
+dat.c <- subset(db_ET_MPo, is_correct == 1)
+dat.m <- subset(db_ET_MPo, is_mp == 1)
+
+dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "distractor_label", "mean_age_1", "n_1"))
+
+dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
+dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
+
+ms.agg <- ggplot(dat.cm, aes(distractor_label, Misp_sensitivity, fill = distractor_label)) + 
+  #facet_grid(.~dv_label)+
+    geom_violin() + 
+  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
+  labs(title="a")+
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Misp. Sensitivity")
+
+ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = distractor_label)) + 
+    #facet_grid(.~dv_label)+
+  geom_point(aes(size = n_1),show.legend=FALSE) +
+  labs(title="b")+
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Misp. Sensitivity")
+
+lay <- rbind(c(1), c(2))
+#lay <- rbind(c(1,2))
+
+  jpeg(filename = "figures/Figure_6_Distractor_Overlap.jpg",
+       width = 500, height = 600, units = "px")
+
+ger.plot.age <- grid.arrange(ms.agg, ms.age,
+                             layout_matrix = lay)
+
+ dev.off()
+
+grid.draw(ger.plot.age)
+
+```
+
+### Position of mispronunciation
+
+```{r Location_descrip}
+
+misp_location_info <- dat %>%
+  group_by(mispron_location) %>%
+  summarize(n_exp_conditions =  n())
+
+```
+
+To assess whether the position of the mispronunciation has an impact on mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to mispronunciations on the onset, medial, and coda phonemes.
+We did not include data for which the mispronunciation varied in regard to position (*n* = `r with(misp_location_info, n_exp_conditions[mispron_location == "coda/medial" | mispron_location == "onset/medial" | mispron_location == "onset/medial/coda"])`) or was not reported (*n* = `r with(misp_location_info, n_exp_conditions[is.na(mispron_location)])`).
+The analysis was therefore based on a subset of the overall dataset, with `r with(misp_location_info, n_exp_conditions[mispron_location == "onset"])` experimental conditions comparing a mispronunciation on the onset phoneme, `r with(misp_location_info, n_exp_conditions[mispron_location == "medial"])` experimental conditions comparing a mispronunciation on the medial phoneme, and `r with(misp_location_info, n_exp_conditions[mispron_location == "coda"])` experimental conditions comparing a mispronunciation on the coda phoneme.
+We coded the onset, medial, and coda positions as continuous variables, to evaluate the importance of each subsequent position (Marslen-Wilson & Zwitserlood, 1989).
+
+```{r Location_misp}
+
+db_ET_MPl = dat %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial"| mispron_location == "coda")
+
+# linear
+db_ET_MPl$m_posit <- ifelse(db_ET_MPl$mispron_location == "onset", 1,
+                            ifelse(db_ET_MPl$mispron_location == "medial", 2, 3))
+
+db_ET_MPl$m_posit <- as.numeric(as.character(db_ET_MPl$m_posit))
+
+rma_LinearLocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~m_posit*condition, data = db_ET_MPl, random = ~same_infant_calc | short_cite)
+
+sum_eff <- coef(summary(rma_LinearLocationCondition))[4,]
+
+```
+
+```{r Misp_Posit_age}
+
+# mispronunciation sensitivity
+
+db_ET_MPl = dat %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial"| mispron_location == "coda")
+
+# linear
+db_ET_MPl$m_posit <- ifelse(db_ET_MPl$mispron_location == "onset", 1,
+                            ifelse(db_ET_MPl$mispron_location == "medial", 2, 3))
+
+db_ET_MPl$m_posit <- as.numeric(as.character(db_ET_MPl$m_posit))
+
+rma_LinearLocationCondition_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*m_posit*condition, data = db_ET_MPl, random = ~same_infant_calc | short_cite)
+
+sum_eff_age <- coef(summary(rma_LinearLocationCondition_age))[8,]
+
+ # divide into age groups
+
+ db_ET_MPl$age_group <- ntile(db_ET_MPl$mean_age_1, 3)
+
+ misp_posit_ages <- db_ET_MPl %>%
+  group_by(age_group, mispron_location) %>%
+  summarize(n =  n())
+
+ #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
+
+ misp_posit_ages <- misp_posit_ages %>% spread(mispron_location, n)
+
+ #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
+fish.test <- fisher.test(misp_posit_ages)
+
+```
+
+To understand the relationship between mispronunciation position and  mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with mispronunciation position and condition as moderators.
+The moderator test was significant, `r mod_test(rma_LocationCondition)`.
+For the interaction between condition and mispronunciation position, the estimate was small but significant ($\beta$ `r full_estimate(sum_eff)`.
+As can be seen in Figure \@ref(fig:PlotMispPosit)a, mispronunciation sensitivity decreased linearly as the position of the mispronunciation moved later in the word, with sensitivity greatest for onset mispronunciations and smallest for coda mispronunciations.
+
+To better understand how this moderator impacted our estimate of developmental change in mispronunciation sensitivity, we added age as a moderator.
+The moderator test was significant, `r mod_test(rma_Misp_Posit_age_MS)`.
+The estimate for the three-way interaction between age, condition, and mispronunciation position was not significant ($\beta$ `r full_estimate(sum_eff_age_medial)`.
+As can be seen in Figure \@ref(fig:PlotMispPosit)b, mispronunciation sensitivity but stays relatively stable for onset and medial mispronunciaitons.
+For mispronunciations on the coda position it appears that mispronunciation sensitivity increases with age, but this is likely underpowered and therefore not detectable by our meta-analysis.
+
+Due to the small sample size of coda mispronunciations, we only included 3 age groups in Fisher's exact test.
+The results were significant, *p* `r psig(fish.test$p.value)`.
+Older infants were more likely to be tested on onset mispronunciations, while younger infants were more likely to be tested on medial mispronunciations.
+An onset mispronunciation may be more disruptive to lexical access than mispronunciations in subsequent positions (Marslen-Wilson & Zwitserlood, 1989), and therefore easier to detect.
+For this reason, it is rather unsuprising that onset mispronunciations show the greatest estimate of mispronunciation sensitivity.
+However, it also means that younger infants, who were more likely to be tested on medial mispronunciations, had a comparably harder task than older infants, who were more likely to be tested on onset mispronunciations.
+We return to this issue in the General Discussion.
+
+## (Insert Figure 7 about here)
+
+```{r PlotMispPosit}
+
+db_ET_MPl = dat %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial"| mispron_location == "coda")
+
+db_ET_MPl$condition_label <- ifelse(db_ET_MPl$condition==1, "Correct", "Mispronunciation")
+
+db_ET_MPl$location_label <- ifelse(db_ET_MPl$mispron_location=="onset", "Onset",
+                                   ifelse(db_ET_MPl$mispron_location == "medial", "Medial", "Coda"))
+
+db_ET_MPl$location_label <- factor(db_ET_MPl$location_label, levels = c("Onset", "Medial", "Coda"))
+
+db_ET_MPl <- db_ET_MPl[,c("short_cite", "is_correct", "is_mp", "location_label", "condition_label", "g_calc", "weights_g", "mean_age_1", "n_1")]
+
+dat.c <- subset(db_ET_MPl, is_correct == 1)
+dat.m <- subset(db_ET_MPl, is_mp == 1)
+
+dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "location_label", "mean_age_1", "n_1"))
+
+dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
+dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
+
+ms.agg <- ggplot(dat.cm, aes(location_label, Misp_sensitivity, fill = location_label)) + 
+  #facet_grid(.~dv_label)+
+    geom_violin() + 
+  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
+  labs(title="a")+
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Misp. Sensitivity")
+
+ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = location_label)) + 
+    #facet_grid(.~dv_label)+
+  geom_point(aes(size = n_1),show.legend=FALSE) +
+  labs(title="b")+
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Misp. Sensitivity")
+
+lay <- rbind(c(1), c(2))
+#lay <- rbind(c(1,2))
+
+  jpeg(filename = "figures/Figure_7_Misp_position.jpg",
+       width = 500, height = 600, units = "px")
+
+ger.plot.age <- grid.arrange(ms.agg, ms.age,
+                             layout_matrix = lay)
+
+ dev.off()
+
+grid.draw(ger.plot.age)
+
+```
+
+### Type of mispronunciation (consonant or vowel)
+
+```{r CV_descript}
+
+CV_info <- dat %>%
+  group_by(type_feature) %>%
+  summarize(n_exp_conditions =  n())
+
+CV_location_info <- dat %>%
+  group_by(type_feature, mispron_location) %>%
+  summarize(n_exp_conditions =  n())
+
+```
+
+To assess whether the type of mispronunciation impacts sensitivity to mispronunciations, we calculated the meta-analytic effect for object identification in response to the type of mispronunciation.
+Although most theoretical discussion of mispronunciation type has focused on consonants and vowels, our dataset also included tone mispronunciations.
+In our analysis, we were interested in the difference between consonants and vowels, but also include an exploratory analysis of responses to tones, consonants, and vowels.
+Furthermore, sensitivity to consonant and vowel mispronunciations is hypothesized to differ depending on whether the infant is learning a Germanic or Romance language.
+We therefore conducted two sets of analyses, one analyzing consonants and vowels alone, a second including langauge family as a moderator, and a third comparing responses to tones with that of consonants and vowels, separately.
+For the latter analysis, tones were coded as the reference condition.
+We did not include data for which mispronunciation type varied within experiment and was not reported separately (*n* = `r with(CV_info, n_exp_conditions[type_feature == "consonant_and_vowel" | type_feature == "consonant_vowel_tone"])`).
+The analysis was therefore based on a subset of the overall dataset, with `r with(CV_info, n_exp_conditions[type_feature == "consonant"])` experimental conditions comparing a consonant mispronunciation, `r with(CV_info, n_exp_conditions[type_feature == "vowel"])` experimental conditions comparing a vowel mispronunciation, and `r with(CV_info, n_exp_conditions[type_feature == "tone"])` experimental conditions comparing a tone mispronunciation.
+Below, we first report the set of analyses comparing consonants with vowels and between language families before moving on to the set of exploratory analyses comparing tones with that of consonants and vowels.
+
+```{r MPtype_cv}
+
+# C vs. V with condition
+
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
+
+rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition, data = db_type, random = ~same_infant_calc | short_cite)
+
+sum_eff2 <- coef(summary(rma_TypeFeaturesMP_Condition))[4,]
+
+```
+
+```{r MPtype_cv_age}
+
+# with condition
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
+
+rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~same_infant_calc | short_cite)
+
+sum_eff_age <- coef(summary(rma_TypeFeaturesMP_Condition))[8,]
+
+ # divide into age groups
+
+ db_type$age_group <- ntile(db_type$mean_age_1, 4)
+
+ type_ages <- db_type %>%
+  group_by(age_group, type_feature) %>%
+  summarize(n =  n())
+
+ #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
+
+ type_ages <- type_ages %>% spread(type_feature, n)
+
+ #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
+fish.test <- fisher.test(type_ages, workspace=2e8)
+
+```
+
+To understand the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with mispronunciation type and condition as moderators.
+The moderator test was significant, `r mod_test(rma_TypeFeaturesMP_Condition)`, but the interaction between mispronunciation type and condition ($\beta$`r full_estimate(sum_eff2)`) was not significant.
+The results suggest that overall, infants' sensitivity to consonant and vowel mispronunciations was similar.
+
+We next examined whether age modulates mispronunciation sensitivity when the mispronunciation is a consonant or a vowel.
+When age was added as a moderator, the moderator test was significant, `r mod_test(rma_TypeFeaturesMP_Condition)` and the estimate for the three-way interaction between age, condition, and mispronunciation type was significant, but relatively small ($\beta$ = `r full_estimate(sum_eff_age)`.
+As can be seen in Figure \@ref(fig:PlotMispType)b, as infants age, mispronunciation sensitivity grows larger for vowel mispronunciations but stays steady for consonant mispronunciations.
+Noticeably, mispronunciation sensitivity appears greater for consonant compared to vowel mispronunciations at younger ages, but this difference diminishes as infants age.
+
+The results of Fisher's exact test were significant, *p* `r psig(fish.test$p.value)`.
+Older infants were more likely to be tested on consonant mispronunciations, while younger infants were more likely to be tested on vowel mispronunciations.
+It is not immediately clear whether the relationship between infant age and type of mispronunciation influences our estimate of how mispronunciation sensitivity changes with development.
+Whether consonant or vowel mispronunciations are more "difficult" is a matter of theoretical debate, but some evidence suggest that it may be influenced by infants' native language (Nazzi, Poltrock, & Von Holzen, 2016).
+We next examined whether this was the case.
+
+## (Insert Figure 8 about here)
+
+```{r PlotMispType}
+
+db_type = dat %>%
+  filter(type_feature == "consonant" | type_feature == "vowel")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
+
+db_type$condition_label <- ifelse(db_type$condition==1, "Correct", "Mispronunciation")
+
+db_type$type_label <- ifelse(db_type$type_feature=="consonant", "Consonant", "Vowel")
+
+db_type <- db_type[,c("short_cite", "is_correct", "is_mp", "type_label", "condition_label", "g_calc", "weights_g", "mean_age_1", "n_1")]
+
+dat.c <- subset(db_type, is_correct == 1)
+dat.m <- subset(db_type, is_mp == 1)
+
+dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "type_label", "mean_age_1", "n_1"))
+
+dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
+dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
+
+ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
+  #facet_grid(.~dv_label)+
+    geom_violin() + 
+  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
+  labs(title="a")+
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Misp. Sensitivity")
+
+ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = type_label)) + 
+    #facet_grid(.~dv_label)+
+  geom_point(aes(size = n_1),show.legend=FALSE) +
+  labs(title="b")+
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Misp. Sensitivity")
+
+lay <- rbind(c(1), c(2))
+#lay <- rbind(c(1,2))
+
+  jpeg(filename = "figures/Figure_8_CV.jpg",
+       width = 500, height = 600, units = "px")
+
+ger.plot.age <- grid.arrange(ms.agg, ms.age,
+                             layout_matrix = lay)
+
+ dev.off()
+
+grid.draw(ger.plot.age)
+
+```
+
+```{r MPtype_cv_lang_descript}
+
+family <- dat %>%
+  group_by(lang_family) %>%
+  summarize(count = n())
+
+lang_family <- dat %>%
+  group_by(native_lang, lang_family) %>%
+  summarize(count = n())
+
+cv_family <- dat %>%
+  group_by(type_feature, lang_family) %>%
+  summarize(count = n())
+
+```
+
+```{r MPtype_cv_lang}
+
+# with condition
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
+
+db_type <- subset(db_type, lang_family != "Sino-Tibetian")
+
+rma_TypeFeaturesMPC <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family, data = db_type, random = ~same_infant_calc | short_cite)
+
+sum_eff_fam <- coef(summary(rma_TypeFeaturesMPC))[7,]
+sum_eff_famcv <- coef(summary(rma_TypeFeaturesMPC))[8,]
+
+```
+
+```{r MPtype_cv_lang_age}
+# with condition
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
+
+db_type <- subset(db_type, lang_family != "Sino-Tibetian")
+
+rma_TypeFeaturesMPC_age <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family*age.C, data = db_type, random = ~same_infant_calc | short_cite)
+
+sum_eff2_lang_age <- coef(summary(rma_TypeFeaturesMPC_age))[16,]
+
+# summary(glht(rma_TypeFeaturesMPC, linfct=cbind(contrMat(rep(1,8), type="Tukey"))), test=adjusted("none"))
+# 
+# ranef(rma_TypeFeaturesMPC)
+
+# divide into age groups
+
+ db_type$age_group <- ntile(db_type$mean_age_1, 3)
+
+ db_type$lang_cv <- paste(db_type$lang_family, db_type$type_feature, sep = "_")
+
+ type_lang_ages <- db_type %>%
+  group_by(age_group, lang_cv) %>%
+  summarize(n =  n())
+
+ #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
+
+ type_lang_ages <- type_lang_ages %>% spread(lang_cv, n)
+
+ #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
+fish.test <- fisher.test(type_lang_ages, workspace=2e8)
+
+```
+
+To examine whether infants' native language impacts sensitivity to consonant and vowel mispronunciations, we classified infants into language families.
+Infants learning American English (*n* = `r with(lang_family, count[native_lang == "American English"])`), British English (*n* = `r with(lang_family, count[native_lang == "British English"])`), Danish (*n* = `r with(lang_family, count[native_lang == "Danish"])`), Dutch (*n* = `r with(lang_family, count[native_lang == "Dutch"])`), and German (*n* = `r with(lang_family, count[native_lang == "German"])`) were classified into the Germanic language family (*n* = `r with(family, count[lang_family == "Germanic"])`).
+Infants learning Catalan (*n* = `r with(lang_family, count[native_lang == "Catalan"])`), Spanish (*n* = `r with(lang_family, count[native_lang == "Spanish"])`), French (*n* = `r with(lang_family, count[native_lang == "French"])`), Catalan and Spanish simultaneously (i.e.
+bilinguals; *n* = `r with(lang_family, count[native_lang == "Catalan-Spanish"])`), and Swiss French (*n* = `r with(lang_family, count[native_lang == "Swiss French"])`) were classified into the Romance language family (*n* = `r with(family, count[lang_family == "Romance"])`).
+
+We assessed whether the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity was modulated by language family.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family as additional moderators.
+The moderator test was significant, `r mod_test(rma_TypeFeaturesMPC)`.
+The interaction between condition and language family was significant ($\beta$`r full_estimate(sum_eff_fam)`), suggesting that the estimate for mispronunciation sensitivity was greater for infants learning a Romance compared to Germanic language.
+However, when a model evaluating this specific interaction, without mispronunciation type, was calculated, the estimate was much smaller and not significant.
+This suggests that the interaction between condition and language family may be over-estimated.
+The three-way interaction between mispronunciation type, condition, language family was large and also significant , $\beta$`r full_estimate(sum_eff_famcv)`.
+As can be seen in Figure \@ref(fig:PlotCVEffect_Lang)a, mispronunciation sensitivity for consonants was similar for Germanic and Romance languages.
+Mispronunciation sensitivity for vowels, however, was greater for Germanic compared to Romance languages.
+
+Finally, we examined the relationship between language family and infant age and mispronunciation sensitivity to consonants and vowels.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family and age as additional moderators.
+The moderator test was significant, `r mod_test(rma_TypeFeaturesMPC_age)`, and the estimate for the four-way interaction between mispronunciation type, condition, language family, and age was small, but significant , $\beta$`r full_estimate(sum_eff2_lang_age)`.
+As can also be seen in Figure \@ref(fig:PlotCVEffect_Lang)b, for infants learning Germanic languages, sensitivity to consonant and vowel mispronunciations did not change with age.
+In contrast, infants learning Romance languages show a decrease in sensitivity to consonant mispronunciations, but an increase in sensitivity to vowel mispronunciations with age.
+
+We were unable to use Fisher's exact test to evaluate whether infants of different ages were more or less likely to be tested on consonant or vowel mispronunciations depending on their native language.
+This was due to the small sample size of infants learning Romance languages (*n* = `r with(family, count[lang_family == "Romance"])`).
+
+## (Insert Figure 9 about here)
+
+```{r PlotCVEffect_Lang}
+
+db_type = dat %>%
+  filter(type_feature == "consonant" | type_feature == "vowel")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
+
+db_type <- subset(db_type, lang_family != "Sino-Tibetian")
+
+db_type$condition_label <- ifelse(db_type$condition==1, "Correct", "Mispronunciation")
+
+db_type$type_label <- ifelse(db_type$type_feature=="consonant", "Consonant", "Vowel")
+
+db_type <- db_type[,c("short_cite", "is_correct", "is_mp", "type_label", "condition_label", "lang_family", "g_calc", "weights_g", "mean_age_1", "n_1")]
+
+dat.c <- subset(db_type, is_correct == 1)
+dat.m <- subset(db_type, is_mp == 1)
+
+dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "type_label", "lang_family", "mean_age_1", "n_1"))
+
+dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
+dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
+
+ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
+  facet_grid(.~lang_family)+
+    geom_violin() + 
+  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
+  labs(title="a")+
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Hedges' g")
+
+ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = type_label)) + 
+  facet_grid(.~lang_family)+
+  geom_point(aes(size = n_1),show.legend=FALSE) +
+  labs(title="b")+
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Hedges' g")
+
+lay <- rbind(c(1), c(2))
+#lay <- rbind(c(1,2))
+
+  jpeg(filename = "figures/Figure_9_LangCV.jpg",
+       width = 500, height = 600, units = "px")
+
+ger.plot.age <- grid.arrange(ms.agg, ms.age,
+                             layout_matrix = lay)
+
+ dev.off()
+
+grid.draw(ger.plot.age)
+
+```
+
+```{r MPtype_cvt}
+
+# C vs. V vs. T with condition
+
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel"| type_feature == "tone")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("tone", "consonant", "vowel"))
+
+rma_TypeFeaturesMP_ConditionT <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition, data = db_type, random = ~same_infant_calc | short_cite)
+
+sum_eff2c <- coef(summary(rma_TypeFeaturesMP_ConditionT))[5,]
+sum_eff2v <- coef(summary(rma_TypeFeaturesMP_ConditionT))[6,]
+
+```
+
+```{r MPtype_cvt_age}
+
+# with condition
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" | type_feature == "tone")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("tone", "consonant", "vowel"))
+
+rma_TypeFeaturesMP_Condition_age <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~same_infant_calc | short_cite)
+
+sum_eff_tc <- coef(summary(rma_TypeFeaturesMP_Condition))[11,]
+sum_eff2_tv <- coef(summary(rma_TypeFeaturesMP_Condition))[12,]
+
+```
+
+Although we had no predictions regarding mispronunciation sensitivity to tone mispronunciations, we included an exploratory analysis to examine whether responses to tone mispronunciations were different from that of consonants or vowels.
+When mispronunciation type (tone, consonant, vowel) and condition (correct, mispronunciation) were included as moderators, the moderator test was significant, `r mod_test(rma_TypeFeaturesMP_ConditionT)`.
+The interactions between condition and consonant mispronunciations ($\beta$ = `r full_estimate(sum_eff2c)`) as well as vowel mispronunciations ($\beta$ = `r full_estimate(sum_eff2v)`), were not significant, suggesting that there was no difference in looks to the target in response to tone mispronunciations compared with consonant or vowel mispronunciations.
+
+We further included an exploratory analysis of the relationship between infant age and the impact of tone mispronunciations in comparison to consonant and vowel mispronunciations.
+We included mispronunciation type, condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
+The moderator test was significant, `r mod_test(rma_TypeFeaturesMP_ConditionT)`, but the interactions between condition, age, and both consonant ($\beta$ = `r full_estimate(sum_eff_tc$estimate)`) and vowel ($\beta$ = `r full_estimate(sum_eff_tv$estimate)`) mispronunciations were not significant.
+Infants' sensitivity to tone mispronunciations compared to consonant or vowel mispronunciations did not differ with age.
+
+### Interim discussion: Moderator analyses
+
+Next to the main goal of this paper, which was to evaluate the development of infants' sensitivity to mispronunciations, we also investigated the more nuanced questions often posed in studies investigating infants' mispronunciation sensitivity.
+We identified five additional manipulations often present in mispronunciation sensitivity studies and investigated the how those manipulations modulated mispronunciation sensitivity and whether this changed with infant age.
+Furthermore, considering the lack of developmental change found in our main analysis, we evaluted whether these additional manipulations were disproportionatly conducted with children of different ages, to assess whether older infants recieve more difficult tasks than younger infants.
+
+To briefly summarize, mispronunciation sensitivity was modulated overall by the size of the mispronunciation tested, whether target-distractor pairs shared phonological overlap, and the position of the mispronunciation.
+Neither distractor familiarity (familiar, unfamiliar) or type of mispronunciation (consonant, vowel, tone) were found to impact mispronunciation sensitivity.
+The developmental trajectory of mispronunciation sensitivity was influenced by whether target-distractor pairs shared phonological overlap and type of mispronunciation, but mispronunciation size, mispronunciation position, and distractor familiarity were found to have no influence.
+Finally, in some cases there was evidence that older and younger infants were given experimental manipulations that may have rendered the experimental task more or less difficult.
+Specifically, older children were more likely to be given target-distractor pairs that overlapped on their onset phoneme, a situation in which it is more difficult to detect a mispronunciation.
+Yet, this was not always the case; in a different instance, younger infants were given a more difficult task, mispronunciations on the medial position.
+We return to these findings in the General Discussion.
+
+We next considered whether an effect of maturation might have been masked by other factors we have not yet captured in our analyses.
 A strong candidate that emerged during the construction of the present dataset and careful reading of the original papers was the analysis approach.
@@
 
-## (Insert Figure 5 about here)
+## (Insert Figure 10 about here)
 
@@
 
-  jpeg(filename = "figures/Figure_5_Post_name_size.jpg", 
+  jpeg(filename = "figures/Figure_10_Post_name_size.jpg", 
        width = 600, height = 600, units = "px")
@@
 
-## (Insert Figure 6 about here)
+## (Insert Figure 11 about here)
 
@@
 
-  jpeg(filename = "figures/Figure_6_Dependent_variable.jpg", 
+  jpeg(filename = "figures/Figure_11_Dependent_variable.jpg", 
        width = 500, height = 600, units = "px")
@@
 We next evaluated the developmental trajectory of infants' mispronunciation sensitivity.
-Based on previous theoretical accounts and existing experimental evidence, we envisioned three possible developmental patterns: increasing, decreasing, and unchanging sensitivity.
+Based on existing experimental evidence, we envisioned three possible developmental patterns: increasing, decreasing, and unchanging sensitivity.
 We observed no influence of age when it was considered as a moderator of mispronunciation sensitivity.
-Of the two mainstream theories identified in our literature review, neither the Perceptual Attunement account [@Best1994; @Best1995] nor PRIMIR [@Curtin2007; @Werker2005; @Curtin2011] account for a lack of developmental change.
-The results of our meta-analysis are reflecting a pattern previously reported by a handful of studies directly comparing infants over a range of ages [@Swingley2000; @Bailey2002; @Zesiger2012], which also found no developmental change in mispronunciation sensitivity.
-
-Both the Perceptual Attunement [@Best1994; @Best1995] and PRIMIR [@Curtin2007; @Werker2005; @Curtin2011] accounts link a change of mispronunciation sensitivity specifically with vocabulary growth, in comparison to development in general.
-Vocabulary growth is predicted to lead either to an increase [PRIMIR; @Curtin2007; @Werker2005; @Curtin2011] or a decrease [Perceptual Attunement; @Best1994; @Best1995] in mispronunciation sensitivity; vocabulary has been shown to grow considerably in the age range considered in the current meta-analysis [see http://wordbank.stanford.edu; @Frank2017].
-However, there are also substantial individual differences in the trajectory of vocabulary growth.
-The lack of developmental effects found in our meta-analysis may therefore be due to using age, instead of vocabulary size, as a moderator of mispronunciation sensitivity.
+The results of our meta-analysis reflect a pattern previously reported by a handful of studies directly comparing infants over a range of ages [@Swingley2000; @Bailey2002; @Zesiger2012], which also found no developmental change in mispronunciation sensitivity.
+
+Typically, vocabulary growth is thought to invoke changes in mispronunciation sensitivity.
+The need for phonologically well-specified word representations increases as children learn more words and must differentiate between them [@CharlesLuce1995].
+Yet, when we examined this relationship, we found that very few studies report analyses investigating the relationship between mispronunciation sensitivity and vocabulary size.
+An analysis of this handful of studies revealed no relationship between object recognition in response to mispronunciations, but this analysis was likely underpowered.
+More experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size is needed if this is to be evaluated.
 We tried to address this issue by conducting an analysis of the subset of studies reporting correlations between infants’ vocabulary size and their responses to correct and mispronounced labels.
@@
 Evidence that infants accept a mispronunciation (object identification) while simultaneously holding correctly pronounced and mispronounced labels as separate (mispronunciation sensitivity) may indicate an abstract understanding of words' phonological structure being in place early on.
-It appears that young infants may understand that the phonological form of mispronunciations and correct pronunciations do not match (phonological distinctiveness), but that the mispronunciation is a better label for the target compared to the distractor image (phonological constancy).
+It appears that young infants may understand that the phonological form of mispronunciations and correct pronunciations do not match, but that the mispronunciation is a better label for the target compared to the distractor image.
 The lack of age or vocabulary effects in our meta-analysis suggest that this understanding is present from an age when the earliest words are learned and is maintained throughout early lexical development.
-This implies mastery of the principles of phonological constancy and phonological distinctiveness at an age earlier than previously thought, which we recommend should be further explored experimentally and taken into consideration by future theoretical accounts.
+
+## Moderator Analyses
+
+With perhaps a few exceptions, the main focus of many of the experiments included in this meta-analysis was not to evaluate whether infants are sensitive to mispronunciations in general but rather to investigate questions related to phonological and lexical processing and development.
+We included a set of moderator analyses to better understand these issues by themselves, as well as how they may have impacted our main investigation of infants' development of mispronunciation sensitivity.
+Additionally, several of these moderators include manipulations that make mispronunciation detection more or less difficult for the infant.
+Considering this, we also evaluated whether the investigation of each of these manipulations was distributed evenly across infant ages, where an uneven distribution may have subsequently heightened or dampened our estimate of developmental change.
+
+The results of the moderator analysis reflect several experimental findings.
+Although words differ from one another on many acoustic dimensions, changes in phonemes, as measured by phonological features, signal changes in meaning.
+Several studies have found that infants show graded sensitivity to both consonant (Bernier & White, 2017; Tamasi, 2016; White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes.
+This was captured in our meta-analysis, which also showed that sensitivity to mispronunciations increased linearly with the number of phonological features changed.
+For each increase in number of phonological features changed, the effect size estimate for looks to the target decreases by `r r2(linear_feature)`.
+Yet, this graded sensitivity appears to be stable across infant ages, although our analysis was likely underpowered.
+At least one study suggests that this graded sensitivity develops with age, but this was the only study to examine more than one age (Mani & Plunkett, 2011).
+All other studies only test one age (Tamasi, White & Morgan, 2008; Bernier & White, 2017).
+With more studies investigating graded sensitivity at multiple ages in infancy, we would achieve a better estimate of whether this is a stable or developing ability.
+
+Although some theories place greater importance on onset position for word recognition and decreasing importance for phonemes in subsequent positions (COHORT), other theories suggest that lexical access can still recover (TRACE).
+Is there any experimental evidence?
+That swingly study?
+Our results show that infants are more sensitive to mispronunciations earlier in the word.
+Since few studies actually compare this, this is nice evidence to have and should hopefully spure more studied.
+Again, we find no influence of development.
+
+in general, these are the things that support what has been found in the literature or theories
+
+These things were not supported
+
+One unique aspect of this meta-analysis was that we could see how these things change with development.
+However, probably underpowered.
+Yet, these were the differences we found and this is what they mean
+
+Interestingly, there were several manipulations that varied the age on which they were tested.
+These are those things.
+We think it may have impacted our overall estimate of developmental change in this way.
+
+** Position of mispronunciation **
+
+  + effect size estimate later position in words significantly decreases
+  + no effect of age
+  + Due to the small sample size of coda mispronunciations, we only included 3 age groups in Fisher's exact test.
+The results were significant, *p* `r psig(fish.test$p.value)`.
+Older infants were more likely to be tested on onset mispronunciations, while younger infants were more likely to be tested on medial mispronunciations.
+An onset mispronunciation may be more disruptive to lexical access than mispronunciations in subsequent positions (Marslen-Wilson & Zwitserlood, 1989), and therefore easier to detect.
+For this reason, it is rather unsuprising that onset mispronunciations show the greatest estimate of mispronunciation sensitivity.
+However, it also means that younger infants, who were more likely to be tested on medial mispronunciations, had a comparably harder task than older infants, who were more likely to be tested on onset mispronunciations.
+We return to this issue in the General Discussion.
+
+ The influence of distractor overlap also depends on the *position of mispronunciation* in the word, which can be at word onset, medial, or final positions.
+Models of spoken word processing place more or less importance on the position of a phoneme in a word.
+The COHORT model (Marslen-Wilson & Zwitserlood, 1989) describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.
+In contrast, the TRACE model (McClelland & Elman, 1986) describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.
+
+  TRACE has also been used to model infants' sensitivity to mispronunciation position (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth.
+In early language acquisition, infants typically know more consonant compared to vowel onset words.
+When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations.
+
+** Phonological overlap between target and distractor **
+
+  + mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap
+  + this is rather the opposite of what one would expect, right?
+  + [Katie: Yeah! Its really strange, so the time course analysis suggestion of yours is a very good one!]
+  + Maybe it would be useful to have time course analyses to address this issue further
+  + mispronunciation sensitivity increases with age for target-distractor pairs containing onset overlap, but decreases with age for target-distractor pairs containing no overlap
+  + The results of Fisher's exact test were significant, *p* `r psig(fish.test$p.value)`.
+Older infants were more likely to be tested in experimental conditions where target and distractor images overlapped on their onset phoneme, while younger infants were more likely to be tested with target and distractor images that did not control for overlap.
+A distractor image that overlaps in the onset phoneme with the target image is considered a more challenging task to the infant, as infants must pay attention to the mispronounced phoneme and can not use the differing onsets between target and distractor images to differentiate (Fernald, Swingley, & Pinto, 2001).
+It therefore appears that older infants were given a more challenging task than younger infants.
+This may explain why infants in the onset overlap condition, a harder task, have a greater effect size estimate for mispronunciation sensitivity than those in the no overlap condition, which is a comparably easier task.
+We return to this issue in the General Discussion.
+
+  Furthermore, when presenting infants with a familiar distractor image, some studies control the *phonological overlap between target and distractor labels*.
+For example, when examining sensitivity to a mispronunciation of the target word "dog", the vowel mispronunciation "dag" would be paired with a distractor image that shares onset overlap, such as "duck".
+This ensures that infants can not use the onset of the word to differentiate between the target and distractor images (Fernald, Swingley, & Pinto, 2001).
+Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.
+
+** Type of mispronunciation **
+
+  + Overall, no difference between consonants and vowels 
+  + Consonant mispronunciation sensitivity stays the same with age
+  + Vowel mispronunciation sensitivity increases with age
+  + mispronunciation sensitivity for consonants similar for Germanic and Romance languages
+  + Mispronunciation sensitivity for vowels greater for Germanic compared to Romance languages
+  + For Germanic infants, sensitivity to consonant and vowel mispronunciations did not change with age. 
+  + For Romance infants, sensitivity to mispronunciations decreases for consonants and increases for vowels with age
+  + exploratory analyses with tone mispronunciations suggest no great difference in sensitivity when compared to consonant and vowel mispronunciations
+
+  TRACE has also been used to model infants' sensitivity to mispronunciation position (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth.
+In early language acquisition, infants typically know more consonant compared to vowel onset words.
+When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations.
+The prevalence of consonant onset words may contribute to the finding that consonants carry more weight in lexical processing (C-bias; see Nazzi, Poltrock, & Von Holzen, 2016 for a recent review).
+In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations.
+Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels.
+English-learning 12-, 15-, 18-, and 24-month-olds (Mani & Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds (Hojen et al., unpublished) demonstrate similar sensitivity to consonant and vowel mispronunciations.
+One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations (Swingley, 2016).
+The English-learning infants tested by Swingley were older than previous studies (mean age 28 months).
+In word learning, the C-bias has been found to develop later in English learning infants (Floccia, Nazzi, Delle Luche, Poltrock, & Goslin, 2014; Nazzi, Floccia, Moquet, & Butler, 2009).
+In the current meta-analysis, we attempt to synthesize studies examining sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence (Floccia et al., 2014; Keidel et al., 2007; Nazzi et al., 2016).
+We further examine the impact of language family on mispronunciation sensitivity to consonants and vowels, as C-bias emergence has been found to have a different developmental trajectory for Romance (French, Italian) compared to Germanic (British English, Danish) languages (Nazzi et al., 2016).
+
+  Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (see Table 1).
+Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare.
+Although we do not explicitly compare overall mispronunciation sensitivity by language (although see previous paragraph for rationale to test by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.
+
+** Distractor Familiarity **
+
+  + No difference between familiar and unfamiliar distractors
+  + Again, ages not matched very well for the two groups here.
+
+  Although most research examining sensitivity to mispronunciations follows a similar design, there are some notable differences.
+For example, Swingley and Aslin (2000) presented infants with pairs of familiar images, one serving as the labeled target and one as the unlabeled distractor.
+In contrast, White and Morgan (2008; see also Mani & Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects.
+By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied (Halberda, 2003; Markman, Wasow, & Hansen, 2003).
+Infants ages 24 and 30 months associate a novel label with an unfamiliar object, although only 30-month-olds retained this label-object pairing (Bion, Borovsky, and Fernald, 2013).
+In contrast, 18-month-olds did not learn to associate a novel label with an unfamiliar object, providing evidence that this ability is developing from 18 to 30 months.
+We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar.
+Although mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared, the baseline preference for familiar compared to novel stimuli is also thought to change as infants develop (Hunter & Ames, 1988).
+Furthermore, young children have been found to look longer at objects for which they know the name, compared to objects of an unknown name (Schafer & Plukett, 1998).
+In other words, in absentia of a label, infants may be more or less likely to fixate on an unfamiliar object.
+To account for inherent preferences to the target or distractor image, mispronunciation experiments typically compare the increase in fixations to the target image from a silent baseline to post-labeling or present the same yoked pairs of target and distractor images in in both a correct and mispronounced labelling context.
+Considering this evidence, we may expect that in older, but not younger, children, the presence of an unfamiliar distractor may lead to greater mispronunciation sensitivity than in the presence of a familiar distractor.
 

### 2019-05-24 VonHolzenBergmann_MPMetaAnalysis.tex
moderator analysis results completed

@@
 and lexical processing and often result in manipulations of the stimuli
-and experimental procedure. Next to the core investigation of the shape
-of development of infants' mispronunciation sensitivity, we take the
-opportunity of a systematic aggregation of data to address these
-questions and the influence of these manipulations on infants' ability
-to detect mispronunciations and how this may change with development.
+and experimental procedure. These manipulations may impact our overall
+estimate of the effect size of mispronunciation sensitivity. Next to the
+core investigation of the shape of development of infants'
+mispronunciation sensitivity, we take the opportunity of a systematic
+aggregation of data to address these questions and the influence of
+these manipulations on infants' ability to detect mispronunciations and
+how this may change with development.
 
@@
 \toprule
- &  &  &  & \multicolumn{1}{c}{Distractor} & & \multicolumn{3}{c}{Mispronunciation}  &\\
-\cmidrule(r){5-5} \cmidrule(r){7-9}
+ &  &  &  & \multicolumn{2}{c}{Distractor} & \multicolumn{3}{c}{Mispronunciation}  &\\
+\cmidrule(r){5-6} \cmidrule(r){7-9}
 Paper & Format & Age & Vocabulary & Familiarity & Target Overlap & Size & Position & Type & N Effect Sizes\\
@@
 
-We separated conditions according to whether or not the target word was
-mispronounced to be able to investigate infants' looking to the target
-picture as well as their mispronunciation sensitivity, which is the
-difference between looks to the target in correct and mispronounced
-trials. When the same infants were further exposed to multiple
-mispronunciation conditions and the results were reported separately in
-the paper, we also entered each condition as a separate row (e.g.,
-consonant versus vowel mispronunciations; Mani \& Plunkett, 2007). The
-fact that the same infants contributed data to multiple rows (minimally
-those containing information on correct and mispronounced trials) leads
-to shared variance across effect sizes, which we account for in our
-analyses (see next section). We will call each row a record; in total
-there were 251 records in our data.
+A detailed explanation for moderating factors 3-8 can be found in their
+respective sections in the Results. We separated conditions according to
+whether or not the target word was mispronounced to be able to
+investigate infants' looking to the target picture as well as their
+mispronunciation sensitivity, which is the difference between looks to
+the target in correct and mispronounced trials. When the same infants
+were further exposed to multiple mispronunciation conditions and the
+results were reported separately in the paper, we also entered each
+condition as a separate row (e.g., consonant versus vowel
+mispronunciations; Mani \& Plunkett, 2007). The fact that the same
+infants contributed data to multiple rows (minimally those containing
+information on correct and mispronounced trials) leads to shared
+variance across effect sizes, which we account for in our analyses (see
+next section). We will call each row a record; in total there were 251
+records in our data.
 
@@
 
-\subsubsection{Interim Discussion}\label{interim-discussion}
+\subsubsection{Interim Discussion:
+Meta-Analysis}\label{interim-discussion-meta-analysis}
 
@@
 vocabulary size. We observe that the data for directly reported
-vocabulary size were too sparse to draw strong conclusions. Of the three
-predictions about the development of infants' sensitivity to
-mispronunciations discussed in the Introduction, the present results
-lend some support for the proposal that mispronunciation sensitivity
-stays consistent as infants develop. This runs counter to existing
-theories of phono-lexical development, which predict either an increase
-(Curtin \& Werker, 2007; Curtin, Byers-Heinlein, \& Werker, 2011; Werker
-\& Curtin, 2005) or decrease (Best, 1994, 1995) in mispronunciation
-sensitivity. Furthermore, although we found a relationship between
-vocabulary size (comprehension) and target looking for correct
-pronunciations, we found no relationship between vocabulary and target
-looking for mispronunciations. This also runs counter to the predictions
-for the PRIMR (Curtin \& Werker, 2007; Curtin et al., 2011; Werker \&
-Curtin, 2005) and Assimilation (Best, 1994, 1995) models, but may be due
-to our analyses being underpowered. In sum, it seems that current
-theories of infants' phono-lexical development cannot fully capture our
-results, but that more investigation is needed to draw a firm
-conclusion.
+vocabulary size were too sparse to draw strong conclusions. In the
+literature, evidence for all possible developmental trajectories has
+been found, including mispronunciation sensitivity that increases,
+decreases, or does not change with age or vocabulary size. The present
+results do lend some support for the proposal that mispronunciation
+sensitivity stays consistent as infants develop. Furthermore, although
+we found a relationship between vocabulary size (comprehension) and
+target looking for correct pronunciations, we found no relationship
+between vocabulary and target looking for mispronunciations. This may be
+due to too few studies including reports of vocabulary size and more
+investigation is needed to draw a firm conclusion.
+
+Alternatively, the lack of developmental change in mispronunciation
+sensitivity could be due to differences in the types of tasks given to
+infants of different ages. If infants' word recognition skills are
+generally thought to improve with age and vocabulary size, research
+questions that tap more complex processes may be more likely to be
+investigated in older infants. In the following section, we investigate
+the role that different moderators play in mispronunciation sensitivity.
+To investigate the possibility of systematic differences in the tasks
+across ages, we additionally include an exploratory analysis of whether
+different moderators and experimental design features were included at
+different ages.
+
+\subsection{Moderator Analyses}\label{moderator-analyses}
+
+In this section, we consider each moderator individually and investigate
+its influence on mispronunciation sensitivity. For most moderators
+(except Number of features changed), we combine the correct and
+mispronounced datasets and include the moderator of condition, to study
+mispronunciation sensitivity as opposed to object recognition. To better
+understand the impact of these moderators on developmental change, we
+include age as subsequent moderator as well as an exploratory analysis
+of the age of infants tested with each type of moderator. The latter
+analysis is included to explore whether the lack of developmental change
+in mispronunciation sensitivity in the overall dataset is due to more
+complex moderator tasks being given to older infants, which may lower
+the overall effect size of mispronunciation sensitivity at older ages
+and dampen any evidence of change.
+
+\subsubsection{Number of features
+changed}\label{number-of-features-changed}
+
+To assess whether the number of features changed modulates
+mispronunciation sensitivity, we calculated the meta-analytic effect for
+object identification in response to words that were pronounced
+correctly and mispronounced using 1-, 2-, and 3-feature changes. We did
+not include data for which the number of features changed in a
+mispronunciation was not specified or the number of features changed was
+not consistent (e.g., one mispronunciation included a 2-feature change
+whereas another only a 1-feature change). This analysis was therefore
+based on a subset of the overall dataset, with 81 experimental
+conditions for correct pronunciations, 108 for 1-feature
+mispronunciations, 16 for 2-feature mispronunciations, and 6 for
+3-feature mispronunciations. Each feature change (from 0 to 3; 0
+representing correct pronunciations) was considered to have an equal
+impact on mispronunciation sensitivity, following the argument of graded
+sensitivity (White \& Aslin, 2008; Mani \& Plunkett 2011), and this
+modertor was coded as a continuous variable.
+
+To understand the relationship between number of features changed and
+mispronunciation sensitivity, we evaluated the effect size Hedges'
+\emph{g} with number of features changed as a moderator. The moderator
+test was significant, QM(1) = 137.214, \emph{p} \textless{} .001.
+Hedges' \emph{g} for number of features changed was -0.306 (SE = 0.026),
+which indicated that as the number of features changed increased, the
+effect size Hedges' \emph{g} significantly decreased (CI {[}-0.357,
+-0.255{]}, \emph{p} \textless{} .001). We plot this relationship in
+Figure \ref{fig:PlotFeatEffect}. This confirms previous findings of a
+graded sensitivity to the number of features changed for both consonant
+(White \& Morgan, 2008) and vowel (Mani \& Plunkett, 2011)
+mispronunciations as well as the importance of controlling for the
+degree of phonological mismatch in experimental design.
+
+\subsection{(Insert Figure \ref{fig:PlotFeatEffect} about
+here)}\label{insert-figure-reffigplotfeateffect-about-here}
+
+\begin{figure}
+\centering
+\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotFeatEffect-1.pdf}
+\caption{}
+\end{figure}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
 
@@
 Attunement account (Best, 1994, 1995) nor PRIMIR (Curtin \& Werker,
-2007; Curtin et al., 2011; Werker \& Curtin, 2005) account for a lack of
-developmental change. The results of our meta-analysis are reflecting a
-pattern previously reported by a handful of studies directly comparing
-infants over a range of ages (Bailey \& Plunkett, 2002; Swingley \&
-Aslin, 2000; Zesiger et al., 2012), which also found no developmental
-change in mispronunciation sensitivity.
+2007; Curtin, Byers-Heinlein, \& Werker, 2011; Werker \& Curtin, 2005)
+account for a lack of developmental change. The results of our
+meta-analysis are reflecting a pattern previously reported by a handful
+of studies directly comparing infants over a range of ages (Bailey \&
+Plunkett, 2002; Swingley \& Aslin, 2000; Zesiger et al., 2012), which
+also found no developmental change in mispronunciation sensitivity.
 

### 2019-05-24 VonHolzenBergmann_MPMetaAnalysis.Rmd
begin updated random effects structure change

@@
 
+db_ET_correct$short_cite.same_infant_calc <- paste0(db_ET_correct$short_cite, ".", db_ET_correct$same_infant_calc)
+db_ET_MP$short_cite.same_infant_calc <- paste0(db_ET_MP$short_cite, ".", db_ET_MP$same_infant_calc)
+
+db_ET_correct$unique_row <- factor(seq(from = 1, to = nrow(db_ET_correct), by = 1))
+db_ET_MP$unique_row <- factor(seq(from = 1, to = nrow(db_ET_MP), by = 1))
+
 dat <- bind_rows(db_ET_correct, db_ET_MP)
+
+dat$unique_row <- factor(seq(from = 1, to = nrow(dat), by = 1))
+
+#dat$short_cite.same_infant_calc <- paste0(dat$short_cite, ".", dat$same_infant_calc)
+#random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc)
 
@@
 
-rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ same_infant_calc | short_cite)
+# rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ same_infant_calc | short_cite)
+
+# new random effects structure
+rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
 
@@
 
-rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ same_infant_calc | short_cite)
+#rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ same_infant_calc | short_cite)
+
+#
+rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
 
@@
 
-rma_MPeffect <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = ~ same_infant_calc | short_cite)
+rma_MPeffect <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
 

### 2019-06-03 VonHolzenBergmann_MPMetaAnalysis.Rmd
first draft of monster paper, updated random effects structure

@@
 We removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech.
-The final sample (n = *`r length(unique(descriptive_dat$short_cite))`*) consisted of `r with(descriptive_dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "dissertation"]))` theses, and `r with(descriptive_dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports.
+The final sample (*n* = `r length(unique(descriptive_dat$short_cite))`) consisted of `r with(descriptive_dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "dissertation"]))` theses, and `r with(descriptive_dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports.
 We will refer to these items collectively as papers.
@@
 #kable(pub_info, col.names = c("Publication Type", "# Items", "# Effect Sizes"))
+
+bil_info <- dat %>%
+  group_by(group_name_1, short_cite) %>%
+  summarize(count = n())
+
+bil_infants <- with(bil_info, count[group_name_1 == "bilingual"])
 
@@
 
-A detailed explanation for moderating factors 3-8 can be found in their respective sections in the Results.
+A detailed explanation for moderating factors 3-8 can be found in their respective sections in the Results [^1].
 We separated conditions according to whether or not the target word was mispronounced to be able to investigate infants' looking to the target picture as well as their mispronunciation sensitivity, which is the difference between looks to the target in correct and mispronounced trials.
@@
 We will call each row a record; in total there were `r nrow(descriptive_dat)` records in our data.
+
+[^1]: Two papers tested bilingual infants (Ramon-Casas & Bosch, 2010; Ramon-Casas et al., 2011), yielding `r bil_infants` experimental conditions.
+Due to this small number, we do not investigate the role of multilingualism, but do note that removing these papers from the meta-analysis did not alter the pattern of results.
 
@@
 
-rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ same_infant_calc | short_cite)
+rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
 # Publication bias can become visible in funnel plot asymmetry. 
@@
 
-rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ same_infant_calc | short_cite)
+rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
 
@@
 
-# rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ same_infant_calc | short_cite)
+# rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
 
@@
 
-#rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ same_infant_calc | short_cite)
+#rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
 
@@
 
-#rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ same_infant_calc | short_cite)
+#rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
 
@@
 
-rma_correct_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = ~ same_infant_calc | short_cite)
+rma_correct_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
 
@@
 
-rma_MP_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = ~ same_infant_calc | short_cite)
+rma_MP_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
 
@@
 
-rma_MPeffect_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = ~ same_infant_calc | short_cite)
+rma_MPeffect_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
 
@@
 
-dat.f$n_feature <- ifelse(dat.f$condition == 1, 0, df$n_feature)
+dat.f$n_feature <- ifelse(dat.f$condition == 1, 0, dat.f$n_feature)
 
@@
 # overall object recognition
-rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~n_feature, data = dat.f, random = ~ same_infant_calc | short_cite)
+rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~n_feature, data = dat.f, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
 
@@
 dat.f$n_feature <- as.numeric(as.character(dat.f$n_feature))
-dat.f$n_feature <- ifelse(dat.f$condition == 1, 0, df$n_feature)
+dat.f$n_feature <- ifelse(dat.f$condition == 1, 0, dat.f$n_feature)
 
@@
 
-rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition, data = dat, random = ~ same_infant_calc | short_cite)
+rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
 
@@
 # age moderator
-rma_Distractor_age <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition*age.C, data = dat, random = ~ same_infant_calc | short_cite)
+rma_Distractor_age <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition*age.C, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
 
@@
 
+# db_ET_MPo_MS = db_ET_MPo_MS %>%
+#   filter(mispron_location != "onset")
+
 db_ET_MPo_MS$distractor_overlap <- factor(db_ET_MPo_MS$distractor_overlap, levels = c("no", "onset"))
 
-rma_DistractorOverlapMS <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MPo_MS, random = ~ same_infant_calc | short_cite)
+rma_DistractorOverlapMS <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MPo_MS, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
 
@@
 
+# db_ET_MPo_MS = db_ET_MPo_MS %>%
+#   filter(mispron_location != "onset")
+#
+
 dat_MPo$distractor_overlap <- factor(dat_MPo$distractor_overlap, levels = c("no", "onset"))
 
-rma_DistractorOverlap_age_MS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap*condition, data = dat_MPo, random = ~ same_infant_calc | short_cite)
+rma_DistractorOverlap_age_MS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap*condition, data = dat_MPo, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
 
@@
   filter(distractor_overlap == "onset"  | distractor_overlap == "no")
+
+# db_ET_MPo_MS = db_ET_MPo_MS %>%
+#   filter(mispron_location != "onset")
 
@@
 
+ linear_position <- sum_eff$estimate
+
 ```
@@
 To understand the relationship between mispronunciation position and  mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with mispronunciation position and condition as moderators.
-The moderator test was significant, `r mod_test(rma_LocationCondition)`.
+The moderator test was significant, `r mod_test(rma_LinearLocationCondition)`.
 For the interaction between condition and mispronunciation position, the estimate was small but significant ($\beta$ `r full_estimate(sum_eff)`.
@@
 To better understand how this moderator impacted our estimate of developmental change in mispronunciation sensitivity, we added age as a moderator.
-The moderator test was significant, `r mod_test(rma_Misp_Posit_age_MS)`.
-The estimate for the three-way interaction between age, condition, and mispronunciation position was not significant ($\beta$ `r full_estimate(sum_eff_age_medial)`.
+The moderator test was significant, `r mod_test(rma_LinearLocationCondition_age)`.
+The estimate for the three-way interaction between age, condition, and mispronunciation position was not significant ($\beta$ `r full_estimate(sum_eff_age)`.
 As can be seen in Figure \@ref(fig:PlotMispPosit)b, mispronunciation sensitivity but stays relatively stable for onset and medial mispronunciaitons.
@@
 However, it also means that younger infants, who were more likely to be tested on medial mispronunciations, had a comparably harder task than older infants, who were more likely to be tested on onset mispronunciations.
-We return to this issue in the General Discussion.
+It is unlikely that this influenced our developmental trajectory estimate, as the consequence would have been mispronunciation sensitivity that increases with age.
 
@@
 
-sum_eff_tc <- coef(summary(rma_TypeFeaturesMP_Condition))[11,]
-sum_eff2_tv <- coef(summary(rma_TypeFeaturesMP_Condition))[12,]
+sum_eff_tc <- coef(summary(rma_TypeFeaturesMP_Condition_age))[11,]
+sum_eff2_tv <- coef(summary(rma_TypeFeaturesMP_Condition_age))[12,]
 
@@
 We included mispronunciation type, condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, `r mod_test(rma_TypeFeaturesMP_ConditionT)`, but the interactions between condition, age, and both consonant ($\beta$ = `r full_estimate(sum_eff_tc$estimate)`) and vowel ($\beta$ = `r full_estimate(sum_eff_tv$estimate)`) mispronunciations were not significant.
+The moderator test was significant, `r mod_test(rma_TypeFeaturesMP_ConditionT)`, but the interactions between condition, age, and both consonant ($\beta$ = `r full_estimate(sum_eff_tc)`) and vowel ($\beta$ = `r full_estimate(sum_eff2_tv)`) mispronunciations were not significant.
 Infants' sensitivity to tone mispronunciations compared to consonant or vowel mispronunciations did not differ with age.
@@
 
-#### Onset time after target naming
+#### Offset time after target naming
 
@@
 
-The results of the moderator analysis reflect several experimental findings.
+The results of the moderator analysis reflect several findings that have been found in the literature.
 Although words differ from one another on many acoustic dimensions, changes in phonemes, as measured by phonological features, signal changes in meaning.
@@
 
-Although some theories place greater importance on onset position for word recognition and decreasing importance for phonemes in subsequent positions (COHORT), other theories suggest that lexical access can still recover (TRACE).
-Is there any experimental evidence?
-That swingly study?
-Our results show that infants are more sensitive to mispronunciations earlier in the word.
-Since few studies actually compare this, this is nice evidence to have and should hopefully spure more studied.
-Again, we find no influence of development.
-
-in general, these are the things that support what has been found in the literature or theories
-
-These things were not supported
-
-One unique aspect of this meta-analysis was that we could see how these things change with development.
-However, probably underpowered.
-Yet, these were the differences we found and this is what they mean
-
-Interestingly, there were several manipulations that varied the age on which they were tested.
-These are those things.
-We think it may have impacted our overall estimate of developmental change in this way.
-
-** Position of mispronunciation **
-
-  + effect size estimate later position in words significantly decreases
-  + no effect of age
-  + Due to the small sample size of coda mispronunciations, we only included 3 age groups in Fisher's exact test.
-The results were significant, *p* `r psig(fish.test$p.value)`.
-Older infants were more likely to be tested on onset mispronunciations, while younger infants were more likely to be tested on medial mispronunciations.
-An onset mispronunciation may be more disruptive to lexical access than mispronunciations in subsequent positions (Marslen-Wilson & Zwitserlood, 1989), and therefore easier to detect.
-For this reason, it is rather unsuprising that onset mispronunciations show the greatest estimate of mispronunciation sensitivity.
-However, it also means that younger infants, who were more likely to be tested on medial mispronunciations, had a comparably harder task than older infants, who were more likely to be tested on onset mispronunciations.
-We return to this issue in the General Discussion.
-
- The influence of distractor overlap also depends on the *position of mispronunciation* in the word, which can be at word onset, medial, or final positions.
-Models of spoken word processing place more or less importance on the position of a phoneme in a word.
-The COHORT model (Marslen-Wilson & Zwitserlood, 1989) describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.
-In contrast, the TRACE model (McClelland & Elman, 1986) describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.
-
-  TRACE has also been used to model infants' sensitivity to mispronunciation position (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth.
-In early language acquisition, infants typically know more consonant compared to vowel onset words.
-When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations.
-
-** Phonological overlap between target and distractor **
-
-  + mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap
-  + this is rather the opposite of what one would expect, right?
-  + [Katie: Yeah! Its really strange, so the time course analysis suggestion of yours is a very good one!]
-  + Maybe it would be useful to have time course analyses to address this issue further
-  + mispronunciation sensitivity increases with age for target-distractor pairs containing onset overlap, but decreases with age for target-distractor pairs containing no overlap
-  + The results of Fisher's exact test were significant, *p* `r psig(fish.test$p.value)`.
-Older infants were more likely to be tested in experimental conditions where target and distractor images overlapped on their onset phoneme, while younger infants were more likely to be tested with target and distractor images that did not control for overlap.
-A distractor image that overlaps in the onset phoneme with the target image is considered a more challenging task to the infant, as infants must pay attention to the mispronounced phoneme and can not use the differing onsets between target and distractor images to differentiate (Fernald, Swingley, & Pinto, 2001).
-It therefore appears that older infants were given a more challenging task than younger infants.
-This may explain why infants in the onset overlap condition, a harder task, have a greater effect size estimate for mispronunciation sensitivity than those in the no overlap condition, which is a comparably easier task.
-We return to this issue in the General Discussion.
-
-  Furthermore, when presenting infants with a familiar distractor image, some studies control the *phonological overlap between target and distractor labels*.
-For example, when examining sensitivity to a mispronunciation of the target word "dog", the vowel mispronunciation "dag" would be paired with a distractor image that shares onset overlap, such as "duck".
-This ensures that infants can not use the onset of the word to differentiate between the target and distractor images (Fernald, Swingley, & Pinto, 2001).
-Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.
-
-** Type of mispronunciation **
-
-  + Overall, no difference between consonants and vowels 
-  + Consonant mispronunciation sensitivity stays the same with age
-  + Vowel mispronunciation sensitivity increases with age
-  + mispronunciation sensitivity for consonants similar for Germanic and Romance languages
-  + Mispronunciation sensitivity for vowels greater for Germanic compared to Romance languages
-  + For Germanic infants, sensitivity to consonant and vowel mispronunciations did not change with age. 
-  + For Romance infants, sensitivity to mispronunciations decreases for consonants and increases for vowels with age
-  + exploratory analyses with tone mispronunciations suggest no great difference in sensitivity when compared to consonant and vowel mispronunciations
-
-  TRACE has also been used to model infants' sensitivity to mispronunciation position (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth.
-In early language acquisition, infants typically know more consonant compared to vowel onset words.
-When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations.
-The prevalence of consonant onset words may contribute to the finding that consonants carry more weight in lexical processing (C-bias; see Nazzi, Poltrock, & Von Holzen, 2016 for a recent review).
-In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations.
-Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels.
-English-learning 12-, 15-, 18-, and 24-month-olds (Mani & Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds (Hojen et al., unpublished) demonstrate similar sensitivity to consonant and vowel mispronunciations.
-One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations (Swingley, 2016).
-The English-learning infants tested by Swingley were older than previous studies (mean age 28 months).
-In word learning, the C-bias has been found to develop later in English learning infants (Floccia, Nazzi, Delle Luche, Poltrock, & Goslin, 2014; Nazzi, Floccia, Moquet, & Butler, 2009).
-In the current meta-analysis, we attempt to synthesize studies examining sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence (Floccia et al., 2014; Keidel et al., 2007; Nazzi et al., 2016).
-We further examine the impact of language family on mispronunciation sensitivity to consonants and vowels, as C-bias emergence has been found to have a different developmental trajectory for Romance (French, Italian) compared to Germanic (British English, Danish) languages (Nazzi et al., 2016).
-
-  Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (see Table 1).
-Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare.
-Although we do not explicitly compare overall mispronunciation sensitivity by language (although see previous paragraph for rationale to test by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.
-
-** Distractor Familiarity **
-
-  + No difference between familiar and unfamiliar distractors
-  + Again, ages not matched very well for the two groups here.
-
-  Although most research examining sensitivity to mispronunciations follows a similar design, there are some notable differences.
-For example, Swingley and Aslin (2000) presented infants with pairs of familiar images, one serving as the labeled target and one as the unlabeled distractor.
-In contrast, White and Morgan (2008; see also Mani & Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects.
-By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied (Halberda, 2003; Markman, Wasow, & Hansen, 2003).
-Infants ages 24 and 30 months associate a novel label with an unfamiliar object, although only 30-month-olds retained this label-object pairing (Bion, Borovsky, and Fernald, 2013).
-In contrast, 18-month-olds did not learn to associate a novel label with an unfamiliar object, providing evidence that this ability is developing from 18 to 30 months.
-We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar.
-Although mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared, the baseline preference for familiar compared to novel stimuli is also thought to change as infants develop (Hunter & Ames, 1988).
-Furthermore, young children have been found to look longer at objects for which they know the name, compared to objects of an unknown name (Schafer & Plukett, 1998).
-In other words, in absentia of a label, infants may be more or less likely to fixate on an unfamiliar object.
-To account for inherent preferences to the target or distractor image, mispronunciation experiments typically compare the increase in fixations to the target image from a silent baseline to post-labeling or present the same yoked pairs of target and distractor images in in both a correct and mispronounced labelling context.
-Considering this evidence, we may expect that in older, but not younger, children, the presence of an unfamiliar distractor may lead to greater mispronunciation sensitivity than in the presence of a familiar distractor.
+Although some theories place greater importance on onset position for word recognition and decreasing importance for phonemes in subsequent positions (i.e.
+COHORT; Marslen-Wilson & Zwitserlood, 1989), other theories suggest that lexical access can still recover from onset and medial mispronunciations (i.e.
+TRACE; McClelland & Elman, 1986).
+Although many studies have examined mispronunciations on multiple positions, only a handful have directly compared sensitivity between different positions.
+These studies find that position of the mispronunciation does not modulate sensitivity (Swingley, 2009; Zesiger & Jöhr, 2011).
+This stands in contrast to the findings of our meta-analysis, which showed that for each subsequent position in the word that is changed, from onset to medial and medial to coda, the effect size estimate for looks to the target decreases by `r r2(linear_position)`; infants are more sensitive to changes in the sounds of familiar words when they occur in an earlier position as opposed to a late position.
+
+One potential explanation for the discrepancy between the results of individual studies and that of the current meta-analysis is the difference in how analysis timing is considered depending on the position of the mispronunciation.
+For example, Swingley (2009) adjusted the offset time from 367 ms for onset mispronunciations to 1133 for coda mispronunciations, to ensure that infants have a similar amount of time to respond to the mispronunciation, regardless of position.
+In contrast, if an experiment compares different kinds of medial mispronunciations, as in Mani & Plunkett (2011), it is not necessary to adjust offset time because the mispronunciations have a similar onset time.
+The length of the post-naming analysis window does impact mispronunciation sensitivity, as we discuss below, and by comparing effect sizes for different mispronuciation positions where position timing was not considered, we may have put mispronunciations that occur later in the word (i.e.
+medial and coda mispronunciations) at a disadvantage relative to onset mispronunciations.
+These issues can be addressed with the addition of more experiments that directly compare sensitivity to mispronunciations of different positions, as well as the use of analyses that account for differences in timing of sensitivity.
+
+For several moderators, we found no evidence of modulation of mispronunciation sensitivity.
+For example, sensitivity to mispronunciations was similar for experimental conditions that included either a familiar or an unfamiliar distrator image.
+Studies that include an unfamiliar, as opposed to familiar distractor image, often argue that the unfamiliar image provides a better referent candidate for mispronunciation than a familiar distractor image, where the name is already known.
+No studies have directly compared mispronunciation sensitivity for familiar and unfamiliar distractors, but these results suggest that this manipulation alone makes little difference in the design of the experiment.
+It remains possible that distractor familiarity interacts with other types of manipulations, such as number of phonological features changed, heightening the ability of the experimenter to detect more sublte differences in mispronunciation sensitivity (i.e.
+White & Morgan, 2008), but our meta-analysis is underpowered to detect these effects.
+
+Despite the proposal that infants should be more sensitive to consonant compared to vowel mispronunciations (Nazzi, Poltrock, & Von Holzen, 2016), we found no difference in sensitivity to consonant and vowel mispronunciations.
+But, a more nuanced picture was revealed regarding differences between consonant and vowel mispronunciations when further moderators were introduced.
+Sensitivity to consonant mispronunciations did not change with age and were similar for infants learning Germanic and Romance languages.
+In contrast, sensitivity to vowel mispronunciations increased with age and was greater for infants learning Germanic languages, although sensitivity to vowel mispronunciations did increase with age for infants learning Romance languages.
+Sensitivity to vowel mispronunciations is modulated both by development and by native language, whereas sensitivity to consonant mispronunciations is fairly similar across age and native language.
+This pattern of results support previous experimental evidence that sensitivity to consonants and vowels have a different developmental trajectory and that this difference also depends on whether the infant is learning a Romance (French, Italian) or Germanic (British English, Danish) native language (Nazzi et al., 2016).
+Additionally, our exploratory analysis of tone mispronunciations revealed no difference in sensitivity in comparison to vowel and consonant mispronunciations, but our ability to detect differences may have been underpowered, as only `r with(CV_info, n_exp_conditions[type_feature == "tone"])` experimental conditions included tone mispronunciations.
+We hope that the recent increase in mispronunciation studies investigating infants learning a tone language (e.g.
+Mandarin Chinese) will soon solve this power issue.
+
+Our meta-analysis revealed the rather surprising result that onset overlap between labels for the target and distractor images lead to greater mispronunciation sensitivity in comparison to target-distractor pairs that shared no phonological overlap.
+It should be arguably more, not less, difficult to detect a mispronunciation (dag) when the target and distractor overlap in their onset phoneme (dog-duck), because the infant can not use differences in the onset sound between the target and distractor to identify the intended referent.
+Perhaps including overlap between the target and distractor lead infants to pay more attention to mispronunciations, leading to an increased effect of mispronunciation sensitivity.
+When we examined the distribution of this manipulation across infant age, however, we found an alternate explanation for this pattern of results.
+Older children were more likely to recieve the arguably more difficult manipulation where target-distractor pairs overlapped in their onset phoneme.
+If older children have greater mispronunciation sensitivity in general, then this may have lead to greater mispronunciation sensitivity for overlapping target-distractor pairs, instead of the manipulation itself.
+
+But, our main developmental analysis found a lack of developmental change in mispronunciation sensitivity, suggesting that older children do not have greater mispronunciation sensitivity than younger children.
+If older children are given a more difficult task than younger children, however, this may dampen any developmental effects.
+It appears that this may be the case for overlap between target-distractor pairs.
+Older children were given a more difficult task (target-distractor pairs with onset overlap), which may have lowered the size of their mispronunciation sensitivity effect.
+Younger children were given an easier task (target-distractor pairs with no overlap), which may have relatively increased the size of their mispronunciation sensitivity effect.
+As a result, any developmental differences would be erased, hidden by task differences in the experiments that older and younger infants participated in.
+Further support comes from evidence that sensitivity to mispronunciations when the target-distractor pair overlapped on the onset phoneme increased with age.
+This pattern of results suggest that when infants are given an equally difficult task, developmental effects may be revealed.
+This explanation can be confirmed by testing more young infants on overlapping target-distractor pairs.
 
@@
 
-## Limitations
-
-The current meta-analysis aggregated studies designed to investigate mispronunciation sensitivity, but we note that these studies varied in their approach to study our phenomenon of interest.
-For example, some studies investigated specific questions which required additional manipulations, such as the impact of the number of phonological features changed in the mispronunciations on mispronunciation sensitivity [e.g.
-@Mani2011; @White2008] or sensitivity to consonant and vowel mispronunciations [@Mani2007; @Mani2010kepstups; @Hojen; @Swingley2016].
-The studies in our sample additionally varied in their experimental design, such as whether infants were familiar with the distractor image [@White2008; @Mani2011; @Skoruppa2013; @Swingley2016] or whether the labels for the target and distractor images contained phonological overlap [@Fernald2001a].
-Futhermore, the infants included in this meta-analysis had a variety of native languages (English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese) and language backgrounds (monolingual, bilingual, monodialectal, multidialectal).
-Taken together, these variables have the potential to modulate infant mispronunciation sensitivity, but an investigation of these variables is out of the scope of the current meta-analysis.
-However, our dataset includes these variables.
-We hope that future research will be able to better understand the role that these variables play in infants' sensitivity to mispronunciations.
-
 ## Conclusion
@@
 
+One unique aspect of this meta-analysis was our examination of
+
+One unique aspect of this meta-analysis was that we could see how these things change with development.
+However, probably underpowered.
+Yet, these were the differences we found and this is what they mean
+
+Interestingly, there were several manipulations that varied the age on which they were tested.
+These are those things.
+We think it may have impacted our overall estimate of developmental change in this way.
+
 Despite this overall finding, however, we note evidence that data analysis choices can modulate conclusions about mispronunciation sensitivity development.

### 2019-06-03 VonHolzenBergmann_MPMetaAnalysis.tex
first draft of monster paper, updated random effects structure

@@
 changed, is further highlighted by studies that find graded sensitivity
-to both consonant (White \& Morgan, 2008) and vowel (Mani \& Plunkett,
-2011) feature changes. The greater the number of features changed, or
-\emph{mispronunciation size}, the easier it may be to detect a
-mispronunciation, whereas more similar mispronunciations may be more
-difficult to detect.
+to both consonant (Bernier \& White, 2017; Tamasi, 2016; White \&
+Morgan, 2008) and vowel (Mani \& Plunkett, 2011) feature changes. The
+greater the number of features changed, or \emph{mispronunciation size},
+the easier it may be to detect a mispronunciation, whereas more similar
+mispronunciations may be more difficult to detect.
 
@@
 image versus a distractor in a eye movement experiment; (5) the stimuli
-were auditory speech. The final sample (n = \emph{32}) consisted of 27
+were auditory speech. The final sample (\emph{n} = 32) consisted of 27
 journal articles, 1 proceedings paper, 2 theses, and 2 unpublished
@@
 A detailed explanation for moderating factors 3-8 can be found in their
-respective sections in the Results. We separated conditions according to
-whether or not the target word was mispronounced to be able to
-investigate infants' looking to the target picture as well as their
-mispronunciation sensitivity, which is the difference between looks to
-the target in correct and mispronounced trials. When the same infants
-were further exposed to multiple mispronunciation conditions and the
-results were reported separately in the paper, we also entered each
-condition as a separate row (e.g., consonant versus vowel
-mispronunciations; Mani \& Plunkett, 2007). The fact that the same
-infants contributed data to multiple rows (minimally those containing
-information on correct and mispronounced trials) leads to shared
-variance across effect sizes, which we account for in our analyses (see
-next section). We will call each row a record; in total there were 251
-records in our data.
+respective sections in the Results.\footnote{Two papers tested bilingual
+  infants (Ramon-Casas \& Bosch, 2010; Ramon-Casas et al., 2011),
+  yielding 2 and 4 experimental conditions. Due to this small number, we
+  do not investigate the role of multilingualism, but do note that
+  removing these papers from the meta-analysis did not alter the pattern
+  of results.} We separated conditions according to whether or not the
+target word was mispronounced to be able to investigate infants' looking
+to the target picture as well as their mispronunciation sensitivity,
+which is the difference between looks to the target in correct and
+mispronounced trials. When the same infants were further exposed to
+multiple mispronunciation conditions and the results were reported
+separately in the paper, we also entered each condition as a separate
+row (e.g., consonant versus vowel mispronunciations; Mani \& Plunkett,
+2007). The fact that the same infants contributed data to multiple rows
+(minimally those containing information on correct and mispronounced
+trials) leads to shared variance across effect sizes, which we account
+for in our analyses (see next section). We will call each row a record;
+in total there were 251 records in our data.
 
@@
 identify objects when hearing correctly pronounced labels. The
-variance-weighted meta-analytic effect size Hedges' \emph{g} was 0.908
-(SE = 0.12) which was significantly different from zero (CI {[}0.673,
-1.143{]}, \emph{p} \textless{} .001). This is a small to medium effect
+variance-weighted meta-analytic effect size Hedges' \emph{g} was 0.916
+(SE = 0.122) which was significantly different from zero (CI {[}0.676,
+1.156{]}, \emph{p} \textless{} .001). This is a small to medium effect
 size (according to the criteria set by Mills-Smith, Spangler, Panneton,
@@
 object identification in response to correctly pronounced words, the
-p-curve results and a CI lower bound of 0.67, which is substantially
+p-curve results and a CI lower bound of 0.68, which is substantially
 above zero, together suggest that this result is somewhat robust. In
@@
 response to mispronounced words. In this case, the variance-weighted
-meta-analytic effect size Hedges' \emph{g} was 0.25 (SE = 0.06) which
-was also significantly different from zero (CI {[}0.133, 0.367{]},
+meta-analytic effect size Hedges' \emph{g} was 0.249 (SE = 0.06) which
+was also significantly different from zero (CI {[}0.132, 0.366{]},
 \emph{p} \textless{} .001). This is considered a small effect size
@@
 the two datasets. When condition was included (correct, mispronounced),
-the moderator test was significant (QM(1) = 215.761, \emph{p}
+the moderator test was significant (QM(1) = 103.408, \emph{p}
 \textless{} .001). The estimate for mispronunciation sensitivity was
-0.495 (SE = 0.034), and infants' looking behavior across conditions was
-significantly different (CI {[}0.429, 0.561{]}, \emph{p} \textless{}
+0.608 (SE = 0.06), and infants' looking behavior across conditions was
+significantly different (CI {[}0.49, 0.725{]}, \emph{p} \textless{}
 .001). This confirms that although infants fixate the correct object for
@@
 not significantly modulate object identification in response to
-correctly pronounced (QM(1) = 0.678, \emph{p} = 0.41) or mispronounced
-words (QM(1) = 1.715, \emph{p} = 0.19). The lack of a significant
+correctly pronounced (QM(1) = 0.558, \emph{p} = 0.455) or mispronounced
+words (QM(1) = 1.64, \emph{p} = 0.2). The lack of a significant
 modulation together with the small estimates for age (correct: \(\beta\)
-= 0.015, SE = 0.018, 95\% CI{[}-0.02, 0.049{]}, \emph{p} = 0.41;
-mispronunciation: \(\beta\) = 0.015, SE = 0.011, 95\% CI{[}-0.007,
-0.037{]}, \emph{p} = 0.19) indicates that there might be no relationship
+= 0.014, SE = 0.019, 95\% CI{[}-0.022, 0.05{]}, \emph{p} = 0.455;
+mispronunciation: \(\beta\) = 0.015, SE = 0.011, 95\% CI{[}-0.008,
+0.037{]}, \emph{p} = 0.2) indicates that there might be no relationship
 between age and target looks in response to a correctly pronounced or
@@
 sensitivity (correct vs.~mispronounced words) in our whole dataset. The
-moderator test was significant (QM(3) = 218.621, \emph{p} \textless{}
+moderator test was significant (QM(3) = 106.158, \emph{p} \textless{}
 .001). The interaction between age and mispronunciation sensitivity,
-however, was not significant (\(\beta\) = 0.003, SE = 0.008, 95\%
-CI{[}-0.012, 0.018{]}, \emph{p} = 0.731); the moderator test was mainly
+however, was not significant (\(\beta\) = 0.012, SE = 0.013, 95\%
+CI{[}-0.014, 0.039{]}, \emph{p} = 0.349); the moderator test was mainly
 driven by the difference between conditions. The small estimate, as well
@@
 
-\subsubsection{Interim Discussion:
-Meta-Analysis}\label{interim-discussion-meta-analysis}
+\subsubsection{Interim discussion: Development of infants'
+mispronunciation
+sensitivity}\label{interim-discussion-development-of-infants-mispronunciation-sensitivity}
 
@@
 the overall effect size of mispronunciation sensitivity at older ages
-and dampen any evidence of change.
-
-\subsubsection{Number of features
-changed}\label{number-of-features-changed}
-
-To assess whether the number of features changed modulates
-mispronunciation sensitivity, we calculated the meta-analytic effect for
-object identification in response to words that were pronounced
-correctly and mispronounced using 1-, 2-, and 3-feature changes. We did
-not include data for which the number of features changed in a
-mispronunciation was not specified or the number of features changed was
-not consistent (e.g., one mispronunciation included a 2-feature change
-whereas another only a 1-feature change). This analysis was therefore
-based on a subset of the overall dataset, with 81 experimental
-conditions for correct pronunciations, 108 for 1-feature
-mispronunciations, 16 for 2-feature mispronunciations, and 6 for
-3-feature mispronunciations. Each feature change (from 0 to 3; 0
-representing correct pronunciations) was considered to have an equal
-impact on mispronunciation sensitivity, following the argument of graded
-sensitivity (White \& Aslin, 2008; Mani \& Plunkett 2011), and this
-modertor was coded as a continuous variable.
-
-To understand the relationship between number of features changed and
+and dampen any evidence of change. Finally, we analyze the relationship
+between infant age and the moderator condition they were tested in using
+Fischer's exact test, which is more appropriate for small sample sizes
+(Fischer, 1922). For each moderator, we evaluate the independence of
+infants' age group (divided into quartiles unless otherwise specified)
+and assignment to each type of condition in a particular moderator.
+
+\subsubsection{Size of mispronunciation}\label{size-of-mispronunciation}
+
+To assess whether the size of the mispornunciation tested, as measured
+by the number of features change, modulates mispronunciation
+sensitivity, we calculated the meta-analytic effect for object
+identification in response to words that were pronounced correctly and
+mispronounced using 1-, 2-, and 3-feature changes. We did not include
+data for which the number of features changed in a mispronunciation was
+not specified or the number of features changed was not consistent
+(e.g., one mispronunciation included a 2-feature change whereas another
+only a 1-feature change). This analysis was therefore based on a subset
+of the overall dataset, with 90 experimental conditions for correct
+pronunciations, 99 for 1-feature mispronunciations, 16 for 2-feature
+mispronunciations, and 6 for 3-feature mispronunciations. Each feature
+change (from 0 to 3; 0 representing correct pronunciations) was
+considered to have an equal impact on mispronunciation sensitivity,
+following the argument of graded sensitivity (White \& Aslin, 2008; Mani
+\& Plunkett 2011), and this modertor was coded as a continuous variable.
+
+To understand the relationship between mispronunciation size and
 mispronunciation sensitivity, we evaluated the effect size Hedges'
 \emph{g} with number of features changed as a moderator. The moderator
-test was significant, QM(1) = 137.214, \emph{p} \textless{} .001.
-Hedges' \emph{g} for number of features changed was -0.306 (SE = 0.026),
-which indicated that as the number of features changed increased, the
-effect size Hedges' \emph{g} significantly decreased (CI {[}-0.357,
--0.255{]}, \emph{p} \textless{} .001). We plot this relationship in
-Figure \ref{fig:PlotFeatEffect}. This confirms previous findings of a
-graded sensitivity to the number of features changed for both consonant
-(White \& Morgan, 2008) and vowel (Mani \& Plunkett, 2011)
-mispronunciations as well as the importance of controlling for the
-degree of phonological mismatch in experimental design.
-
-\subsection{(Insert Figure \ref{fig:PlotFeatEffect} about
-here)}\label{insert-figure-reffigplotfeateffect-about-here}
+test was significant, QM(1) = 61.081, \emph{p} \textless{} .001. Hedges'
+\emph{g} for number of features changed was -0.406 (SE = 0.052), which
+indicated that as the number of features changed increased, the effect
+size Hedges' \emph{g} significantly decreased (CI {[}-0.507, -0.304{]},
+\emph{p} \textless{} .001). We plot this relationship in Figure
+\ref{fig:PlotFeatEffect}. This confirms previous findings of a graded
+sensitivity to the number of features changed for both consonant
+(Bernier \& White, 2017; Tamasi, 2016; White \& Morgan, 2008) and vowel
+(Mani \& Plunkett, 2011) mispronunciations as well as the importance of
+controlling for the degree of phonological mismatch in experimental
+design.
+
+To better understand how this moderator impacted our estimate of
+developmental change in mispronunciation sensitivity, we added age as a
+moderator. The moderator test was significant, QM(3) = 143.617, \emph{p}
+\textless{} .001, but the interaction between age and number of features
+changed was not significant, \(\beta\) = 0.009, SE = 0.006, 95\%
+CI{[}-0.002, 0.02{]}, \emph{p} = 0.099. The small effect size for the
+interaction between age and number of features changed suggests that the
+impact of number of features changed on mispronunciation sensitivity
+does not change with infant age. This may be due to the fact that only a
+handful of studies have explicitly examined the effect of the number of
+features changed on mispronunciation sensitivity and only these studies
+include 3-feature changes (Bernier \& White, 2017; Tamasi, 2016; White
+\& Morgan, 2008; Mani \& Plunkett, 2011).
+
+The results of Fisher's exact test were not significant, \emph{p} =
+0.703. This lack of a relationship suggests that older and younger
+infants are not being tested in experimental conditions that
+differentially manipulate the number of features changed.
+
+\subsection{(Insert Figure 5 about
+here)}\label{insert-figure-5-about-here}
 
@@
 
-Alternatively, an effect of maturation might have been masked by other
-factors we have not yet captured in our analyses. A strong candidate
-that emerged during the construction of the present dataset and careful
-reading of the original papers was the analysis approach. We observed,
-as mentioned in the Methods section, large variation in the dependent
-variable reported, and additionally noted that the size of the chosen
-post-naming analysis window varied substantially across papers.
-Researchers might adapt their analysis strategy to infants' age or they
-might be influenced by having observed the data. For example, consider
-the possibility that there is a true increase in mispronunciation
-sensitivity over development. In this scenario, younger infants should
-show no or only little sensitivity to mispronunciations while older
-infants would show a large sensitivity to mispronunciations. This lack
-of or small mispronunciation sensitivity in younger infants is likely to
-lead to non-significant results, which would be more difficult to
-publish (C. J. Ferguson \& Heene, 2012). In order to have publishable
-results, adjustments to the analysis approach could be made until a
-significant, but spurious, effect of mispronunciation sensitivity is
-found. This would lead to an increase in significant results and alter
-the observed developmental trajectory of mispronunciation sensitivity.
-Such a scenario is in line with the publication bias we observe
-(Simmons, Nelson, \& Simonsohn, 2011). We examine whether variation in
-the approach to data analysis may be have an influence on our
-conclusions regarding infants' developing mispronunciation sensitivity.
+\subsubsection{Distractor familiarity}\label{distractor-familiarity}
+
+To assess whether familiarity with the distractor image modulates
+mispronunciation sensitivity, we calculated the meta-analytic effect for
+object identification in response to words that were pronounced
+correctly and mispronounced and were either paired with a familiar or
+unfamiliar distractor. A familiar distractor was used in 179
+experimental conditions and a unfamiliar distractor in 72 experimental
+conditions.
+
+To understand the relationship between distractor familiarity and
+mispronunciation sensitivity, we evaluated the effect size Hedges'
+\emph{g} with distractor familiarity and condition as moderators. The
+moderator test was significant, QM(1) = 61.081, \emph{p} \textless{}
+.001, but the effect of distractor familiarity (\(\beta\) = -0.12, SE =
+0.144, 95\% CI{[}-0.403, 0.162{]}, \emph{p} = 0.403) as well as the
+interaction between distractor familiarity and condition (\(\beta\) =
+0.067, SE = 0.137, 95\% CI{[}-0.203, 0.336{]}, \emph{p} = 0.628) were
+not significant. The results suggest that overall, infants' familiarity
+with the distractor object (familiar or unfamiliar) did not impact their
+mispronunciation sensitivity.
+
+We next examined whether age modulates object recognition or
+mispronunciation sensitivity when the distractor image is familiar or
+unfamiliar. Based on previous results, we expected older infants to have
+greater mispronunciation sensitivity than younger infants when the
+distractor was unfamiliar compared to familiar. To evaluate this
+prediction, we added age as a moderator. The moderator test was
+significant QM(7) = 107.683, \emph{p} \textless{} .001. The estimate for
+the three-way-interaction between condition, distractor familiarity, and
+age was small and not significant (\(\beta\) = = NA, SE = NA, 95\%
+CI{[}NA, NA{]}, \emph{p} NA. We note that in this model, the interaction
+between condition and distractor familiarity was significant (\(\beta\)
+= NA, SE = NA, 95\% CI{[}NA, NA{]}, \emph{p} NA, but that this estimate
+is similar to the original, non-significant estimate specifically
+examining this interaction in the previous model. Taken together, these
+results suggest that regardless of age, mispronunciation sensitivity was
+similar whether the distractor image was familiar or unfamiliar.
+
+The results of Fisher's exact test were not significant, \emph{p} =
+0.072. This lack of a relationship suggests that older and younger
+infants are not being tested in experimental conditions that
+differentially employ distractor images that are familiar or unfamiliar.
+
+\subsubsection{Phonological overlap between target and
+distractor}\label{phonological-overlap-between-target-and-distractor}
+
+To assess whether phonological overlap between the target and distractor
+image labels has an impact on the size of mispronunciation sensitivity,
+we examined the meta-analytic effect for object identification in
+response to mispronunciations and mispronunciation sensitivity when the
+target-distractor pairs either had no overlap or shared the same onset
+phoneme. We did not include data for which the overlap included both the
+onset and medial phonemes (\emph{n} = 4), coda phonemes (\emph{n} = 3),
+or for targets paired with an unfamiliar distractor image 60. The
+analysis was therefore based on a subset of the overall dataset, with
+104 experimental conditions containing onset phoneme overlap between the
+target and distractor and 80 containing no overlap between target and
+distractor.
+
+To understand the relationship between phonological overlap between
+target and distractor and mispronunciation sensitivity, we evaluated the
+effect size Hedges' \emph{g} with distractor overlap and condition as
+moderators. The moderator test was significant, QM(3) = 59.216, \emph{p}
+\textless{} .001. The estimate for the interaction between condition and
+distractor overlap was small, but significant (\(\beta\) = 0.275, SE =
+0.157, 95\% CI{[}-0.033, 0.584{]}, \emph{p} = 0.08, suggesting that
+mispronunciation sensitivity was greater when target-distractor pairs
+shared the same onset phoneme compared to when they shared no
+phonological overlap. This relationship be seen in Figure
+\ref{fig:PlotDistOverlap}a.
+
+To better understand how this moderator impacted our estimate of
+developmental change in mispronunciation sensitivity, we added age as a
+moderator. The moderator test was significant, QM(7) = 67.82, \emph{p}
+\textless{} .001 and the estimate for the three-way interaction between
+age, condition, and distractor overlap was significant, but relatively
+small (\(\beta\) = = 0.091, SE = 0.038, 95\% CI{[}0.017, 0.166{]},
+\emph{p} = 0.016. As can be seen in Figure \ref{fig:PlotDistOverlap}b,
+mispronunciation sensitivity increases with age for target-distractor
+pairs containing onset overlap, but decreases with age for
+target-distractor pairs containing no overlap.
+
+The results of Fisher's exact test were significant, \emph{p}
+\textless{} .001. Older infants were more likely to be tested in
+experimental conditions where target and distractor images overlapped on
+their onset phoneme, while younger infants were more likely to be tested
+with target and distractor images that did not control for overlap. A
+distractor image that overlaps in the onset phoneme with the target
+image is considered a more challenging task to the infant, as infants
+must pay attention to the mispronounced phoneme and can not use the
+differing onsets between target and distractor images to differentiate
+(Fernald, Swingley, \& Pinto, 2001). It therefore appears that older
+infants were given a more challenging task than younger infants. This
+may explain why infants in the onset overlap condition, a harder task,
+have a greater effect size estimate for mispronunciation sensitivity
+than those in the no overlap condition, which is a comparably easier
+task. We return to this issue in the General Discussion.
+
+\subsection{(Insert Figure 6 about
+here)}\label{insert-figure-6-about-here}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
+
+\begin{figure}
+\centering
+\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotDistOverlap-1.pdf}
+\caption{}
+\end{figure}
+
+\subsubsection{Position of
+mispronunciation}\label{position-of-mispronunciation}
+
+To assess whether the position of the mispronunciation has an impact on
+mispronunciation sensitivity, we calculated the meta-analytic effect for
+object identification in response to mispronunciations on the onset,
+medial, and coda phonemes. We did not include data for which the
+mispronunciation varied in regard to position (\emph{n} = 3, 29, 8, and
+NA) or was not reported (\emph{n} = 10). The analysis was therefore
+based on a subset of the overall dataset, with 143 and NA experimental
+conditions comparing a mispronunciation on the onset phoneme, 48 and NA
+experimental conditions comparing a mispronunciation on the medial
+phoneme, and 10 and NA experimental conditions comparing a
+mispronunciation on the coda phoneme. We coded the onset, medial, and
+coda positions as continuous variables, to evaluate the importance of
+each subsequent position (Marslen-Wilson \& Zwitserlood, 1989).
+
+To understand the relationship between mispronunciation position and
+mispronunciation sensitivity, we evaluated the effect size Hedges'
+\emph{g} with mispronunciation position and condition as moderators. The
+moderator test was significant, QM(3) = 172.345, \emph{p} \textless{}
+.001. For the interaction between condition and mispronunciation
+position, the estimate was small but significant (\(\beta\) = -0.126, SE
+= 0.064, 95\% CI{[}-0.252, 0{]}, \emph{p} = 0.049. As can be seen in
+Figure \ref{fig:PlotMispPosit}a, mispronunciation sensitivity decreased
+linearly as the position of the mispronunciation moved later in the
+word, with sensitivity greatest for onset mispronunciations and smallest
+for coda mispronunciations.
+
+To better understand how this moderator impacted our estimate of
+developmental change in mispronunciation sensitivity, we added age as a
+moderator. The moderator test was significant, QM(7) = 175.856, \emph{p}
+\textless{} .001. The estimate for the three-way interaction between
+age, condition, and mispronunciation position was not significant
+(\(\beta\) = 0.022, SE = 0.018, 95\% CI{[}-0.013, 0.057{]}, \emph{p} =
+0.223. As can be seen in Figure \ref{fig:PlotMispPosit}b,
+mispronunciation sensitivity but stays relatively stable for onset and
+medial mispronunciaitons. For mispronunciations on the coda position it
+appears that mispronunciation sensitivity increases with age, but this
+is likely underpowered and therefore not detectable by our
+meta-analysis.
+
+Due to the small sample size of coda mispronunciations, we only included
+3 age groups in Fisher's exact test. The results were significant,
+\emph{p} = 0.02. Older infants were more likely to be tested on onset
+mispronunciations, while younger infants were more likely to be tested
+on medial mispronunciations. An onset mispronunciation may be more
+disruptive to lexical access than mispronunciations in subsequent
+positions (Marslen-Wilson \& Zwitserlood, 1989), and therefore easier to
+detect. For this reason, it is rather unsuprising that onset
+mispronunciations show the greatest estimate of mispronunciation
+sensitivity. However, it also means that younger infants, who were more
+likely to be tested on medial mispronunciations, had a comparably harder
+task than older infants, who were more likely to be tested on onset
+mispronunciations. It is unlikely that this influenced our developmental
+trajectory estimate, as the consequence would have been mispronunciation
+sensitivity that increases with age.
+
+\subsection{(Insert Figure 7 about
+here)}\label{insert-figure-7-about-here}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
+
+\begin{figure}
+\centering
+\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotMispPosit-1.pdf}
+\caption{}
+\end{figure}
+
+\subsubsection{Type of mispronunciation (consonant or
+vowel)}\label{type-of-mispronunciation-consonant-or-vowel}
+
+To assess whether the type of mispronunciation impacts sensitivity to
+mispronunciations, we calculated the meta-analytic effect for object
+identification in response to the type of mispronunciation. Although
+most theoretical discussion of mispronunciation type has focused on
+consonants and vowels, our dataset also included tone mispronunciations.
+In our analysis, we were interested in the difference between consonants
+and vowels, but also include an exploratory analysis of responses to
+tones, consonants, and vowels. Furthermore, sensitivity to consonant and
+vowel mispronunciations is hypothesized to differ depending on whether
+the infant is learning a Germanic or Romance language. We therefore
+conducted two sets of analyses, one analyzing consonants and vowels
+alone, a second including langauge family as a moderator, and a third
+comparing responses to tones with that of consonants and vowels,
+separately. For the latter analysis, tones were coded as the reference
+condition. We did not include data for which mispronunciation type
+varied within experiment and was not reported separately (\emph{n} = 21
+and 2). The analysis was therefore based on a subset of the overall
+dataset, with 145 experimental conditions comparing a consonant
+mispronunciation, 71 experimental conditions comparing a vowel
+mispronunciation, and 12 experimental conditions comparing a tone
+mispronunciation. Below, we first report the set of analyses comparing
+consonants with vowels and between language families before moving on to
+the set of exploratory analyses comparing tones with that of consonants
+and vowels.
+
+To understand the relationship between mispronunciation type (consonant
+or vowel) and mispronunciation sensitivity, we evaluated the effect size
+Hedges' \emph{g} with mispronunciation type and condition as moderators.
+The moderator test was significant, QM(7) = 153.795, \emph{p}
+\textless{} .001, but the interaction between mispronunciation type and
+condition (\(\beta\) = 0.056, SE = 0.079, 95\% CI{[}-0.099, 0.211{]},
+\emph{p} = 0.479) was not significant. The results suggest that overall,
+infants' sensitivity to consonant and vowel mispronunciations was
+similar.
+
+We next examined whether age modulates mispronunciation sensitivity when
+the mispronunciation is a consonant or a vowel. When age was added as a
+moderator, the moderator test was significant, QM(7) = 153.795, \emph{p}
+\textless{} .001 and the estimate for the three-way interaction between
+age, condition, and mispronunciation type was significant, but
+relatively small (\(\beta\) = = 0.044, SE = 0.018, 95\% CI{[}0.008,
+0.08{]}, \emph{p} = 0.016. As can be seen in Figure
+\ref{fig:PlotMispType}b, as infants age, mispronunciation sensitivity
+grows larger for vowel mispronunciations but stays steady for consonant
+mispronunciations. Noticeably, mispronunciation sensitivity appears
+greater for consonant compared to vowel mispronunciations at younger
+ages, but this difference diminishes as infants age.
+
+The results of Fisher's exact test were significant, \emph{p}
+\textless{} .001. Older infants were more likely to be tested on
+consonant mispronunciations, while younger infants were more likely to
+be tested on vowel mispronunciations. It is not immediately clear
+whether the relationship between infant age and type of mispronunciation
+influences our estimate of how mispronunciation sensitivity changes with
+development. Whether consonant or vowel mispronunciations are more
+\enquote{difficult} is a matter of theoretical debate, but some evidence
+suggest that it may be influenced by infants' native language (Nazzi,
+Poltrock, \& Von Holzen, 2016). We next examined whether this was the
+case.
+
+\subsection{(Insert Figure 8 about
+here)}\label{insert-figure-8-about-here}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
+
+\begin{figure}
+\centering
+\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotMispType-1.pdf}
+\caption{}
+\end{figure}
+
+To examine whether infants' native language impacts sensitivity to
+consonant and vowel mispronunciations, we classified infants into
+language families. Infants learning American English (\emph{n} = 56),
+British English (\emph{n} = 66), Danish (\emph{n} = 6), Dutch (\emph{n}
+= 58), and German (\emph{n} = 21) were classified into the Germanic
+language family (\emph{n} = 207). Infants learning Catalan (\emph{n} =
+4), Spanish (\emph{n} = 4), French (\emph{n} = 8), Catalan and Spanish
+simultaneously (i.e.~bilinguals; \emph{n} = 6), and Swiss French
+(\emph{n} = 6) were classified into the Romance language family
+(\emph{n} = 28).
+
+We assessed whether the relationship between mispronunciation type
+(consonant or vowel) and mispronunciation sensitivity was modulated by
+language family. We merged the two datasets and included condition
+(correct pronunciation, mispronunciation) as well as language family as
+additional moderators. The moderator test was significant, QM(7) =
+158.889, \emph{p} \textless{} .001. The interaction between condition
+and language family was significant (\(\beta\) = 0.727, SE = 0.231, 95\%
+CI{[}0.274, 1.181{]}, \emph{p} = 0.002), suggesting that the estimate
+for mispronunciation sensitivity was greater for infants learning a
+Romance compared to Germanic language. However, when a model evaluating
+this specific interaction, without mispronunciation type, was
+calculated, the estimate was much smaller and not significant. This
+suggests that the interaction between condition and language family may
+be over-estimated. The three-way interaction between mispronunciation
+type, condition, language family was large and also significant ,
+\(\beta\) = -0.872, SE = 0.28, 95\% CI{[}-1.421, -0.323{]}, \emph{p} =
+0.002. As can be seen in Figure @ref(fig:PlotCVEffect\_Lang)a,
+mispronunciation sensitivity for consonants was similar for Germanic and
+Romance languages. Mispronunciation sensitivity for vowels, however, was
+greater for Germanic compared to Romance languages.
+
+Finally, we examined the relationship between language family and infant
+age and mispronunciation sensitivity to consonants and vowels. We merged
+the two datasets and included condition (correct pronunciation,
+mispronunciation) as well as language family and age as additional
+moderators. The moderator test was significant, QM(15) = 185.148,
+\emph{p} \textless{} .001, and the estimate for the four-way interaction
+between mispronunciation type, condition, language family, and age was
+small, but significant , \(\beta\) = 0.331, SE = 0.078, 95\% CI{[}0.178,
+0.484{]}, \emph{p} \textless{} .001. As can also be seen in Figure
+@ref(fig:PlotCVEffect\_Lang)b, for infants learning Germanic languages,
+sensitivity to consonant and vowel mispronunciations did not change with
+age. In contrast, infants learning Romance languages show a decrease in
+sensitivity to consonant mispronunciations, but an increase in
+sensitivity to vowel mispronunciations with age.
+
+We were unable to use Fisher's exact test to evaluate whether infants of
+different ages were more or less likely to be tested on consonant or
+vowel mispronunciations depending on their native language. This was due
+to the small sample size of infants learning Romance languages (\emph{n}
+= 28).
+
+\subsection{(Insert Figure 9 about
+here)}\label{insert-figure-9-about-here}
+
+\begin{verbatim}
+## pdf 
+##   2
+\end{verbatim}
+
+\begin{figure}
+\centering
+\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotCVEffect_Lang-1.pdf}
+\caption{}
+\end{figure}
+
+Although we had no predictions regarding mispronunciation sensitivity to
+tone mispronunciations, we included an exploratory analysis to examine
+whether responses to tone mispronunciations were different from that of
+consonants or vowels. When mispronunciation type (tone, consonant,
+vowel) and condition (correct, mispronunciation) were included as
+moderators, the moderator test was significant, QM(5) = 154.876,
+\emph{p} \textless{} .001. The interactions between condition and
+consonant mispronunciations (\(\beta\) = = -0.189, SE = 0.206, 95\%
+CI{[}-0.591, 0.214{]}, \emph{p} = 0.359) as well as vowel
+mispronunciations (\(\beta\) = = -0.133, SE = 0.211, 95\% CI{[}-0.545,
+0.28{]}, \emph{p} = 0.528), were not significant, suggesting that there
+was no difference in looks to the target in response to tone
+mispronunciations compared with consonant or vowel mispronunciations.
+
+We further included an exploratory analysis of the relationship between
+infant age and the impact of tone mispronunciations in comparison to
+consonant and vowel mispronunciations. We included mispronunciation
+type, condition (correct pronunciation, mispronunciation) as well as age
+as additional moderators. The moderator test was significant, QM(5) =
+154.876, \emph{p} \textless{} .001, but the interactions between
+condition, age, and both consonant (\(\beta\) = = 0.017, SE = 0.105,
+95\% CI{[}-0.188, 0.222{]}, \emph{p} = 0.871) and vowel (\(\beta\) = =
+0.061, SE = 0.105, 95\% CI{[}-0.144, 0.267{]}, \emph{p} = 0.56)
+mispronunciations were not significant. Infants' sensitivity to tone
+mispronunciations compared to consonant or vowel mispronunciations did
+not differ with age.
+
+\subsubsection{Interim discussion: Moderator
+analyses}\label{interim-discussion-moderator-analyses}
+
+Next to the main goal of this paper, which was to evaluate the
+development of infants' sensitivity to mispronunciations, we also
+investigated the more nuanced questions often posed in studies
+investigating infants' mispronunciation sensitivity. We identified five
+additional manipulations often present in mispronunciation sensitivity
+studies and investigated the how those manipulations modulated
+mispronunciation sensitivity and whether this changed with infant age.
+Furthermore, considering the lack of developmental change found in our
+main analysis, we evaluted whether these additional manipulations were
+disproportionatly conducted with children of different ages, to assess
+whether older infants recieve more difficult tasks than younger infants.
+
+To briefly summarize, mispronunciation sensitivity was modulated overall
+by the size of the mispronunciation tested, whether target-distractor
+pairs shared phonological overlap, and the position of the
+mispronunciation. Neither distractor familiarity (familiar, unfamiliar)
+or type of mispronunciation (consonant, vowel, tone) were found to
+impact mispronunciation sensitivity. The developmental trajectory of
+mispronunciation sensitivity was influenced by whether target-distractor
+pairs shared phonological overlap and type of mispronunciation, but
+mispronunciation size, mispronunciation position, and distractor
+familiarity were found to have no influence. Finally, in some cases
+there was evidence that older and younger infants were given
+experimental manipulations that may have rendered the experimental task
+more or less difficult. Specifically, older children were more likely to
+be given target-distractor pairs that overlapped on their onset phoneme,
+a situation in which it is more difficult to detect a mispronunciation.
+Yet, this was not always the case; in a different instance, younger
+infants were given a more difficult task, mispronunciations on the
+medial position. We return to these findings in the General Discussion.
+
+We next considered whether an effect of maturation might have been
+masked by other factors we have not yet captured in our analyses. A
+strong candidate that emerged during the construction of the present
+dataset and careful reading of the original papers was the analysis
+approach. We observed, as mentioned in the Methods section, large
+variation in the dependent variable reported, and additionally noted
+that the size of the chosen post-naming analysis window varied
+substantially across papers. Researchers might adapt their analysis
+strategy to infants' age or they might be influenced by having observed
+the data. For example, consider the possibility that there is a true
+increase in mispronunciation sensitivity over development. In this
+scenario, younger infants should show no or only little sensitivity to
+mispronunciations while older infants would show a large sensitivity to
+mispronunciations. This lack of or small mispronunciation sensitivity in
+younger infants is likely to lead to non-significant results, which
+would be more difficult to publish (C. J. Ferguson \& Heene, 2012). In
+order to have publishable results, adjustments to the analysis approach
+could be made until a significant, but spurious, effect of
+mispronunciation sensitivity is found. This would lead to an increase in
+significant results and alter the observed developmental trajectory of
+mispronunciation sensitivity. Such a scenario is in line with the
+publication bias we observe (Simmons, Nelson, \& Simonsohn, 2011). We
+examine whether variation in the approach to data analysis may be have
+an influence on our conclusions regarding infants' developing
+mispronunciation sensitivity.
 
@@
 
-\subsection{(Insert Figure 5 about
-here)}\label{insert-figure-5-about-here}
+\subsection{(Insert Figure 10 about
+here)}\label{insert-figure-10-about-here}
 
@@
 
-\paragraph{Onset time after target
-naming}\label{onset-time-after-target-naming}
+\paragraph{Offset time after target
+naming}\label{offset-time-after-target-naming}
 
@@
 
-\subsection{(Insert Figure 6 about
-here)}\label{insert-figure-6-about-here}
+\subsection{(Insert Figure 11 about
+here)}\label{insert-figure-11-about-here}
 
@@
 We next evaluated the developmental trajectory of infants'
-mispronunciation sensitivity. Based on previous theoretical accounts and
-existing experimental evidence, we envisioned three possible
-developmental patterns: increasing, decreasing, and unchanging
-sensitivity. We observed no influence of age when it was considered as a
-moderator of mispronunciation sensitivity. Of the two mainstream
-theories identified in our literature review, neither the Perceptual
-Attunement account (Best, 1994, 1995) nor PRIMIR (Curtin \& Werker,
-2007; Curtin, Byers-Heinlein, \& Werker, 2011; Werker \& Curtin, 2005)
-account for a lack of developmental change. The results of our
-meta-analysis are reflecting a pattern previously reported by a handful
-of studies directly comparing infants over a range of ages (Bailey \&
-Plunkett, 2002; Swingley \& Aslin, 2000; Zesiger et al., 2012), which
-also found no developmental change in mispronunciation sensitivity.
-
-Both the Perceptual Attunement (Best, 1994, 1995) and PRIMIR (Curtin \&
-Werker, 2007; Curtin et al., 2011; Werker \& Curtin, 2005) accounts link
-a change of mispronunciation sensitivity specifically with vocabulary
-growth, in comparison to development in general. Vocabulary growth is
-predicted to lead either to an increase (PRIMIR; Curtin \& Werker, 2007;
-Curtin et al., 2011; Werker \& Curtin, 2005) or a decrease (Perceptual
-Attunement; Best, 1994, 1995) in mispronunciation sensitivity;
-vocabulary has been shown to grow considerably in the age range
-considered in the current meta-analysis (see
-\url{http://wordbank.stanford.edu}; Frank et al., 2017). However, there
-are also substantial individual differences in the trajectory of
-vocabulary growth. The lack of developmental effects found in our
-meta-analysis may therefore be due to using age, instead of vocabulary
-size, as a moderator of mispronunciation sensitivity. We tried to
-address this issue by conducting an analysis of the subset of studies
-reporting correlations between infants' vocabulary size and their
-responses to correct and mispronounced labels. However, this analysis
-relied on only a few papers. We observed that an increasing vocabulary
-size lead to increased object recognition for correctly pronounced
-words; this was not the case for mispronunciations. However, it is
-difficult to draw any strong conclusions regarding the role of an
-increasing vocabulary size in mispronunciation sensitivity from this
-data.
+mispronunciation sensitivity. Based on existing experimental evidence,
+we envisioned three possible developmental patterns: increasing,
+decreasing, and unchanging sensitivity. We observed no influence of age
+when it was considered as a moderator of mispronunciation sensitivity.
+The results of our meta-analysis reflect a pattern previously reported
+by a handful of studies directly comparing infants over a range of ages
+(Bailey \& Plunkett, 2002; Swingley \& Aslin, 2000; Zesiger et al.,
+2012), which also found no developmental change in mispronunciation
+sensitivity.
+
+Typically, vocabulary growth is thought to invoke changes in
+mispronunciation sensitivity. The need for phonologically well-specified
+word representations increases as children learn more words and must
+differentiate between them (Charles-Luce \& Luce, 1995). Yet, when we
+examined this relationship, we found that very few studies report
+analyses investigating the relationship between mispronunciation
+sensitivity and vocabulary size. An analysis of this handful of studies
+revealed no relationship between object recognition in response to
+mispronunciations, but this analysis was likely underpowered. More
+experimental work investigating and reporting the relationship between
+mispronunciation sensitivity and vocabulary size is needed if this is to
+be evaluated. We tried to address this issue by conducting an analysis
+of the subset of studies reporting correlations between infants'
+vocabulary size and their responses to correct and mispronounced labels.
+However, this analysis relied on only a few papers. We observed that an
+increasing vocabulary size lead to increased object recognition for
+correctly pronounced words; this was not the case for mispronunciations.
+However, it is difficult to draw any strong conclusions regarding the
+role of an increasing vocabulary size in mispronunciation sensitivity
+from this data.
 
@@
 that the phonological form of mispronunciations and correct
-pronunciations do not match (phonological distinctiveness), but that the
-mispronunciation is a better label for the target compared to the
-distractor image (phonological constancy). The lack of age or vocabulary
-effects in our meta-analysis suggest that this understanding is present
-from an age when the earliest words are learned and is maintained
-throughout early lexical development. This implies mastery of the
-principles of phonological constancy and phonological distinctiveness at
-an age earlier than previously thought, which we recommend should be
-further explored experimentally and taken into consideration by future
-theoretical accounts.
+pronunciations do not match, but that the mispronunciation is a better
+label for the target compared to the distractor image. The lack of age
+or vocabulary effects in our meta-analysis suggest that this
+understanding is present from an age when the earliest words are learned
+and is maintained throughout early lexical development.
+
+\subsection{Moderator Analyses}\label{moderator-analyses-1}
+
+With perhaps a few exceptions, the main focus of many of the experiments
+included in this meta-analysis was not to evaluate whether infants are
+sensitive to mispronunciations in general but rather to investigate
+questions related to phonological and lexical processing and
+development. We included a set of moderator analyses to better
+understand these issues by themselves, as well as how they may have
+impacted our main investigation of infants' development of
+mispronunciation sensitivity. Additionally, several of these moderators
+include manipulations that make mispronunciation detection more or less
+difficult for the infant. Considering this, we also evaluated whether
+the investigation of each of these manipulations was distributed evenly
+across infant ages, where an uneven distribution may have subsequently
+heightened or dampened our estimate of developmental change.
+
+The results of the moderator analysis reflect several findings that have
+been found in the literature. Although words differ from one another on
+many acoustic dimensions, changes in phonemes, as measured by
+phonological features, signal changes in meaning. Several studies have
+found that infants show graded sensitivity to both consonant (Bernier \&
+White, 2017; Tamasi, 2016; White \& Morgan, 2008) and vowel (Mani \&
+Plunkett, 2011) feature changes. This was captured in our meta-analysis,
+which also showed that sensitivity to mispronunciations increased
+linearly with the number of phonological features changed. For each
+increase in number of phonological features changed, the effect size
+estimate for looks to the target decreases by -0.41. Yet, this graded
+sensitivity appears to be stable across infant ages, although our
+analysis was likely underpowered. At least one study suggests that this
+graded sensitivity develops with age, but this was the only study to
+examine more than one age (Mani \& Plunkett, 2011). All other studies
+only test one age (Tamasi, White \& Morgan, 2008; Bernier \& White,
+2017). With more studies investigating graded sensitivity at multiple
+ages in infancy, we would achieve a better estimate of whether this is a
+stable or developing ability.
+
+Although some theories place greater importance on onset position for
+word recognition and decreasing importance for phonemes in subsequent
+positions (i.e.~COHORT; Marslen-Wilson \& Zwitserlood, 1989), other
+theories suggest that lexical access can still recover from onset and
+medial mispronunciations (i.e.~TRACE; McClelland \& Elman, 1986).
+Although many studies have examined mispronunciations on multiple
+positions, only a handful have directly compared sensitivity between
+different positions. These studies find that position of the
+mispronunciation does not modulate sensitivity (Swingley, 2009; Zesiger
+\& Jöhr, 2011). This stands in contrast to the findings of our
+meta-analysis, which showed that for each subsequent position in the
+word that is changed, from onset to medial and medial to coda, the
+effect size estimate for looks to the target decreases by -0.13; infants
+are more sensitive to changes in the sounds of familiar words when they
+occur in an earlier position as opposed to a late position.
+
+One potential explanation for the discrepancy between the results of
+individual studies and that of the current meta-analysis is the
+difference in how analysis timing is considered depending on the
+position of the mispronunciation. For example, Swingley (2009) adjusted
+the offset time from 367 ms for onset mispronunciations to 1133 for coda
+mispronunciations, to ensure that infants have a similar amount of time
+to respond to the mispronunciation, regardless of position. In contrast,
+if an experiment compares different kinds of medial mispronunciations,
+as in Mani \& Plunkett (2011), it is not necessary to adjust offset time
+because the mispronunciations have a similar onset time. The length of
+the post-naming analysis window does impact mispronunciation
+sensitivity, as we discuss below, and by comparing effect sizes for
+different mispronuciation positions where position timing was not
+considered, we may have put mispronunciations that occur later in the
+word (i.e.~medial and coda mispronunciations) at a disadvantage relative
+to onset mispronunciations. These issues can be addressed with the
+addition of more experiments that directly compare sensitivity to
+mispronunciations of different positions, as well as the use of analyses
+that account for differences in timing of sensitivity.
+
+For several moderators, we found no evidence of modulation of
+mispronunciation sensitivity. For example, sensitivity to
+mispronunciations was similar for experimental conditions that included
+either a familiar or an unfamiliar distrator image. Studies that include
+an unfamiliar, as opposed to familiar distractor image, often argue that
+the unfamiliar image provides a better referent candidate for
+mispronunciation than a familiar distractor image, where the name is
+already known. No studies have directly compared mispronunciation
+sensitivity for familiar and unfamiliar distractors, but these results
+suggest that this manipulation alone makes little difference in the
+design of the experiment. It remains possible that distractor
+familiarity interacts with other types of manipulations, such as number
+of phonological features changed, heightening the ability of the
+experimenter to detect more sublte differences in mispronunciation
+sensitivity (i.e.~White \& Morgan, 2008), but our meta-analysis is
+underpowered to detect these effects.
+
+Despite the proposal that infants should be more sensitive to consonant
+compared to vowel mispronunciations (Nazzi, Poltrock, \& Von Holzen,
+2016), we found no difference in sensitivity to consonant and vowel
+mispronunciations. But, a more nuanced picture was revealed regarding
+differences between consonant and vowel mispronunciations when further
+moderators were introduced. Sensitivity to consonant mispronunciations
+did not change with age and were similar for infants learning Germanic
+and Romance languages. In contrast, sensitivity to vowel
+mispronunciations increased with age and was greater for infants
+learning Germanic languages, although sensitivity to vowel
+mispronunciations did increase with age for infants learning Romance
+languages. Sensitivity to vowel mispronunciations is modulated both by
+development and by native language, whereas sensitivity to consonant
+mispronunciations is fairly similar across age and native language. This
+pattern of results support previous experimental evidence that
+sensitivity to consonants and vowels have a different developmental
+trajectory and that this difference also depends on whether the infant
+is learning a Romance (French, Italian) or Germanic (British English,
+Danish) native language (Nazzi et al., 2016). Additionally, our
+exploratory analysis of tone mispronunciations revealed no difference in
+sensitivity in comparison to vowel and consonant mispronunciations, but
+our ability to detect differences may have been underpowered, as only 12
+experimental conditions included tone mispronunciations. We hope that
+the recent increase in mispronunciation studies investigating infants
+learning a tone language (e.g.~Mandarin Chinese) will soon solve this
+power issue.
+
+Our meta-analysis revealed the rather surprising result that onset
+overlap between labels for the target and distractor images lead to
+greater mispronunciation sensitivity in comparison to target-distractor
+pairs that shared no phonological overlap. It should be arguably more,
+not less, difficult to detect a mispronunciation (dag) when the target
+and distractor overlap in their onset phoneme (dog-duck), because the
+infant can not use differences in the onset sound between the target and
+distractor to identify the intended referent. Perhaps including overlap
+between the target and distractor lead infants to pay more attention to
+mispronunciations, leading to an increased effect of mispronunciation
+sensitivity. When we examined the distribution of this manipulation
+across infant age, however, we found an alternate explanation for this
+pattern of results. Older children were more likely to recieve the
+arguably more difficult manipulation where target-distractor pairs
+overlapped in their onset phoneme. If older children have greater
+mispronunciation sensitivity in general, then this may have lead to
+greater mispronunciation sensitivity for overlapping target-distractor
+pairs, instead of the manipulation itself.
+
+But, our main developmental analysis found a lack of developmental
+change in mispronunciation sensitivity, suggesting that older children
+do not have greater mispronunciation sensitivity than younger children.
+If older children are given a more difficult task than younger children,
+however, this may dampen any developmental effects. It appears that this
+may be the case for overlap between target-distractor pairs. Older
+children were given a more difficult task (target-distractor pairs with
+onset overlap), which may have lowered the size of their
+mispronunciation sensitivity effect. Younger children were given an
+easier task (target-distractor pairs with no overlap), which may have
+relatively increased the size of their mispronunciation sensitivity
+effect. As a result, any developmental differences would be erased,
+hidden by task differences in the experiments that older and younger
+infants participated in. Further support comes from evidence that
+sensitivity to mispronunciations when the target-distractor pair
+overlapped on the onset phoneme increased with age. This pattern of
+results suggest that when infants are given an equally difficult task,
+developmental effects may be revealed. This explanation can be confirmed
+by testing more young infants on overlapping target-distractor pairs.
 
@@
 The estimated effect for mispronunciation sensitivity in this
-meta-analysis is 0.50, and the most frequently observed sample size is
+meta-analysis is 0.61, and the most frequently observed sample size is
 24 participants. If we were to assume that researchers assess
 mispronunciation sensitivity in a simple ANOVA, the resulting power is
-0.92. Reversely, to achieve 80\% power, one would need to test 17
+0.98. Reversely, to achieve 80\% power, one would need to test 11.70
 participants. These calculations suggest that for the comparison of
@@
 
-\subsection{Limitations}\label{limitations}
-
-The current meta-analysis aggregated studies designed to investigate
-mispronunciation sensitivity, but we note that these studies varied in
-their approach to study our phenomenon of interest. For example, some
-studies investigated specific questions which required additional
-manipulations, such as the impact of the number of phonological features
-changed in the mispronunciations on mispronunciation sensitivity (e.g.
-Mani \& Plunkett, 2011; White \& Morgan, 2008) or sensitivity to
-consonant and vowel mispronunciations (Højen et al., n.d.; Mani \&
-Plunkett, 2007, 2010; Swingley, 2016). The studies in our sample
-additionally varied in their experimental design, such as whether
-infants were familiar with the distractor image (Mani \& Plunkett, 2011;
-Skoruppa et al., 2013; Swingley, 2016; White \& Morgan, 2008) or whether
-the labels for the target and distractor images contained phonological
-overlap (Fernald, Swingley, \& Pinto, 2001). Futhermore, the infants
-included in this meta-analysis had a variety of native languages
-(English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin
-Chinese) and language backgrounds (monolingual, bilingual,
-monodialectal, multidialectal). Taken together, these variables have the
-potential to modulate infant mispronunciation sensitivity, but an
-investigation of these variables is out of the scope of the current
-meta-analysis. However, our dataset includes these variables. We hope
-that future research will be able to better understand the role that
-these variables play in infants' sensitivity to mispronunciations.
-
 \subsection{Conclusion}\label{conclusion}
@@
 
+One unique aspect of this meta-analysis was our examination of
+
+One unique aspect of this meta-analysis was that we could see how these
+things change with development. However, probably underpowered. Yet,
+these were the differences we found and this is what they mean
+
+Interestingly, there were several manipulations that varied the age on
+which they were tested. These are those things. We think it may have
+impacted our overall estimate of developmental change in this way.
+
 Despite this overall finding, however, we note evidence that data
@@
 
-\hypertarget{ref-Best1994}{}
-Best, C. T. (1994). \emph{The emergence of native-language phonological
-influences in infants: A perceptual assimilation model} (Vol. 107/108,
-pp. 1--30).
-
-\hypertarget{ref-Best1995}{}
-Best, C. T. (1995). A direct realist view of cross-language speech
-perception.
-
 \hypertarget{ref-Black2017}{}
@@
 
-\hypertarget{ref-Curtin2007}{}
-Curtin, S., \& Werker, J. F. (2007). The perceptual foundations of
-phonological development. In M. G. Gaskell (Ed.), \emph{The oxford
-handbook of psycholinguistics} (pp. 579--599). New York: Oxford
-University Press.
-doi:\href{https://doi.org/10.1093/oxfordhb/9780198568971.013.0035}{10.1093/oxfordhb/9780198568971.013.0035}
-
-\hypertarget{ref-Curtin2011}{}
-Curtin, S., Byers-Heinlein, K., \& Werker, J. F. (2011). Bilingual
-beginnings as a lens for theory development: PRIMIR in focus.
-\emph{Journal of Phonetics}, \emph{39}(4), 492--504.
-doi:\href{https://doi.org/10.1016/j.wocn.2010.12.002}{10.1016/j.wocn.2010.12.002}
-
 \hypertarget{ref-DelleLuche2015}{}
@@
 
-\hypertarget{ref-Fernald2001a}{}
-Fernald, A., Swingley, D., \& Pinto, J. P. (2001). When half a word is
-enough: infants can recognize spoken words using partial phonetic
-information. \emph{Child Development}, \emph{72}(4), 1003--15.
-doi:\href{https://doi.org/10.1111/1467-8624.00331}{10.1111/1467-8624.00331}
-
 \hypertarget{ref-Fleiss1986}{}
@@
 
-\hypertarget{ref-Hojen}{}
-Højen, A., Madsen, T. O., Vach, W., Basbøll, H., Caporali, S., \& Blese,
-D. (n.d.). \emph{Contributions of vocalic and consonantal information
-when Danish 20-month-olds recognize familiar words}.
-
 \hypertarget{ref-Jennions2002}{}
@@
 
-\hypertarget{ref-Werker2005}{}
-Werker, J. F., \& Curtin, S. (2005). PRIMIR: A developmental framework
-of infant speech processing. \emph{Language Learning and Development},
-\emph{1}(2), 197--234.
-doi:\href{https://doi.org/10.1207/s15473341lld0102_4}{10.1207/s15473341lld0102\_4}
-
-\hypertarget{ref-White2008}{}
-White, K. S., \& Morgan, J. L. (2008). Sub-segmental detail in early
-lexical representations. \emph{Journal of Memory and Language},
-\emph{52}(1), 114--132.
-doi:\href{https://doi.org/10.1016/j.jml.2008.03.001}{10.1016/j.jml.2008.03.001}
-
 \hypertarget{ref-Zesiger2012}{}

### 2019-11-24 VonHolzenBergmann_MPMetaAnalysis.Rmd
Monster Paper update
incorporated Christina's comments from the summer, finished Discussion, updated references

@@
   - name          : "Katie Von Holzen"
-    affiliation   : "1,2"
+    affiliation   : "1,2,3"
     corresponding : yes    # Define only one corresponding author
-    address       : "0221A LeFrak Hall, University of Maryland, College Park, MD 20742"
+    address       : "Emil-Figge-Straße 50, 44221 Dortmund, Germany"
     email         : "katie.m.vonholzen@gmail.com"
   - name          : "Christina Bergmann"
-    affiliation   : "3,4"
+    affiliation   : "4,5"
 
@@
   - id            : "1"
+    institution   : "Lehrstuhl Linguistik des Deutschen, Schwerpunkt Deutsch als Fremdsprache/Deutsch als Zweitsprache, Technische Universität Dortmund"
+  - id            : "2"
     institution   : "Department of Hearing and Speech Sciences, University of Maryland, USA"
-  - id            : "2"
+  - id            : "3"
     institution   : "Laboratoire Psychologie de la Perception, Université Paris Descartes"
-  - id            : "3"
+  - id            : "4"
     institution   : "Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands"
-  - id            : "4"
+  - id            : "5"
     institution   : "LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University"
@@
   As they develop into mature speakers of their native language, infants must not only learn words but also the sounds that make up those words.
-To do so, they must strike a balance between accepting some variation (e.g.
+To do so, they must strike a balance between accepting the speaker's variation (e.g.
 mood, voice, accent), but appropriately rejecting variation when it changes a word's meaning (e.g.
@@
 The results show that although infants are sensitive to mispronunciations, they still accept these altered forms as labels for target objects.
-Interestingly, this ability is not modulated by age or vocabulary size, challenging existing theories and suggesting that a mature understanding of native language phonology is present in infants from an early age, possibly before the vocabulary explosion.
-Despite this finding, we discuss potential data analysis choices that may influence different conclusions about mispronunciation sensitivity development as well as offer recommendations to improve best practices in the study of mispronunciation sensitivity.
+Interestingly, this ability is not modulated by age or vocabulary size, challenging existing theories and suggesting that a mature understanding of native language phonology is present in infants from an early age, possibly before the vocabulary explosion.Further examining our findings, we shed light on the impact of data analysis choices that may lead to different conclusions regarding the development of infants' mispronunciation sensitivity.
+Our paper concludes with recommendations for improved practice in testing infants' word and sentence processing on-line.
 
@@
 Furthermore, when presented with familiar image pairs, children fixate on the referent of a spoken label [@Fernald1998; @Tincoff1999].
-@Swingley2000 were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English saw pairs of images (e.g.
+@Swingley2000 were the first to tie these lines of research together and investigate how infants interpret phonological variation in familiar word recognition: Children aged 18 to 23 months learning American English saw pairs of images (e.g.
 a baby and a dog) and their eye movements to each image were recorded.
@@
 "vaby").
-The mean proportion of fixations to the target image (here: a baby) was calculated separately for both correct and mispronounced trials by dividing the target looking time by the sum of total looking time to both target and a distractor (proportion of target looking or PTL).
-Mean fixations in correct trials were significantly greater than in mispronounced trials, and in both conditions looks to the target were significantly greater than chance.
-We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance in each condition as *object identification*.
-@Swingley2000 concluded that already before the second birthday, children represent words with sufficient detail to be sensitive to mispronunciations.
+Although infants looked at the correct, target image in response to both types of trials, correct trials elicited a greater proportion of looks to the correct, target image than mispronounced trials.
+@Swingley2000 concluded that already before the second birthday, children's representations for familiar words are phonologically well specified.
 
@@
 cat-hat).
-The study of @Swingley2000 as well as subsequent studies examining mispronunciation sensitivity probe this latter distinction.
+The study of @Swingley2000 as well as subsequent studies examining infants' application of phonological categories during word recognition through the mispronunciation sensitivity paradigm probe this latter distinction.
 Phonological contrasts relevant for the infant language-learner are determined by their native language.
 For an infant learning Catalan, the vowel contrast /e/-/E/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish.
-These contrasts are therefore not inate, but must be learned.
+These contrasts are therefore not innate, but must be learned.
 In this meta-analysis, we focus on infants' developing ability to correctly apply the phonological distinctions for their native language during word recognition.
-By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; for a notable exception).
+By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; @MB1; for a notable exception).
 Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.
@@
 Regarding the change in mispronunciation sensitivity over development, however, only about half of studies have compared more than one age group on the same mispronunciation task (see Table 1).
-Across single studies all possible patterns of development lined out above have been reported, making the current meta-analysis very informative.
+Those studies find all possible patterns of development (see below), rendering conclusions regarding developmental change in mispronunciation sensitivity difficult.
 
@@
 An increase in sensitivity to mispronunciations has also been found from 20 to 24 months [@vanderFeest2015] and 15 to 18 months [@Altvater2014] in Dutch infants, as well as German infants from 22 to 25 months [@Altvater2010].
-Furthermore, @vanderFeest2015 found that sensitivity to specific kinds of mispronunciations develop at different ages depending on language infants are learning.
-In other words, the native language constraints which *kinds* of mispronunciations infants are sensitive to first, and that as infants develop, they become sensitive to other mispronunciations.
 
@@
 
-  Why would mispronunciation sensitivity change as infants develop?
-Typically, a change in mispronunciation sensitivity is thought to occur along with an increase in vocabulary size, particularly with the vocabulary spurt at about 18 months.
-As infants learn more words, their focus shifts to the relevant phonetic dimensions needed for word recognition.
+  Given the diverse evidence for developmental change, or lack thereof, the question arises as to what could be driving these differences.
+As infants develop, the rate at which they learn words increases and their focus shifts to the relevant phonetic dimensions needed for word recognition.
 For example, an infant who knows a handful of words with few phonological neighbors would not need to have fully specified phonological representations in order to differentiate between these words.
@@
 One notable exception comes from @Mani2010kepstups.
-Here, 12-month-old infants were divided into a low and high vocabulary group based on median vocabulary size.
+Here, 12-month-old infants were divided into low and high vocabulary groups.
 High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations.
@@
 
-  Although all mispronunciation sensitivity studies are generally interested in the the phonological detail with which infants represent familiar words, many studies pose more nuanced questions.
-These questions concern issues at the intersection of phonological development and lexical processing and often result in manipulations of the stimuli and experimental procedure.
-These manipulations may impact our overall estimate of the effect size of mispronunciation sensitivity.
-Next to the core investigation of the shape of development of infants' mispronunciation sensitivity, we take the opportunity of a systematic aggregation of data to address these questions and the influence of these manipulations on infants' ability to detect mispronunciations and how this may change with development.
-
-  In designing their mispronunciation stimuli, Swingley and Aslin (2000) chose consonant mispronunciations that were likely to confuse adults (Miller & Nicely, 1955).
-Subsequent research has settled on systematically modulating phonemic features to achieve mispronunciations of familiar words.
-By utilizing mispronunciations consisting of phonemic changes, these experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level (i.e.
-1-feature, 2-features, 3-features, etc.).
-The importance of controlling for the degree of phonological mismatch, as measured by number of features changed, is further highlighted by studies that find graded sensitivity to both consonant (Bernier & White, 2017; Tamasi, 2016; White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes.
-The greater the number of features changed, or *mispronunciation size*, the easier it may be to detect a mispronunciation, whereas more similar mispronunciations may be more difficult to detect.
-
-  Although most research examining sensitivity to mispronunciations follows a similar design, there are some notable differences.
-For example, Swingley and Aslin (2000) presented infants with pairs of familiar images, one serving as the labeled target and one as the unlabeled distractor.
-In contrast, White and Morgan (2008; see also Mani & Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects.
-By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied (Halberda, 2003; Markman, Wasow, & Hansen, 2003).
-Infants ages 24 and 30 months associate a novel label with an unfamiliar object, although only 30-month-olds retained this label-object pairing (Bion, Borovsky, and Fernald, 2013).
-In contrast, 18-month-olds did not learn to associate a novel label with an unfamiliar object, providing evidence that this ability is developing from 18 to 30 months.
-We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar.
-Although mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared, the baseline preference for familiar compared to novel stimuli is also thought to change as infants develop (Hunter & Ames, 1988).
-Furthermore, young children have been found to look longer at objects for which they know the name, compared to objects of an unknown name (Schafer & Plukett, 1998).
-In other words, in absentia of a label, infants may be more or less likely to fixate on an unfamiliar object.
-To account for inherent preferences to the target or distractor image, mispronunciation experiments typically compare the increase in fixations to the target image from a silent baseline to post-labeling or present the same yoked pairs of target and distractor images in in both a correct and mispronounced labelling context.
-Considering this evidence, we may expect that in older, but not younger, children, the presence of an unfamiliar distractor may lead to greater mispronunciation sensitivity than in the presence of a familiar distractor.
-
-  Furthermore, when presenting infants with a familiar distractor image, some studies control the *phonological overlap between target and distractor labels*.
+  An alternative explanation is the level of task difficulty infants are presented with in mispronunciation sensitivity experiments.
+Although all mispronunciation sensitivity studies are generally interested in the the phonological detail with which infants represent familiar words, many studies pose more nuanced questions, such as examining the impact of number of phonological features changed or the position of the mispronunciation.
+Some studies may differ in their experimental design, presenting a distractor image that overlaps with the target image in the onset phoneme or a completely novel, unfamiliar distractor image.
+These experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete.
+The PRIMIR Framework [Processing Rich Information from Multidimensional Interactive Representations; @Curtin2011; @Curtin2007; @Werker2005) describes how infants acquire and organize the incoming speech signal into phonetic and indexical detail.
+The ability to access and use this detail, however, is governed by the task or developmental demands (discrimination vs.
+word learning) probed in a particular experiment.
+In a particularly demanding task, such as when the target and distractor image share the same onset phoneme, infants' ability to access the phonological detail of familiar words may be restricted.
+
+  These manipulations may impact task demands, but they are also theoretically interesting, focus on issues at the intersection of phonological development and lexical processing.
+For specific questions where we can aggregate multiple studies, we take the opportunity to shine a meta-analytic light on what modulates infants' ability to detect mispronunciations in follow-up exploatory analyses.
+We outline below first which nuanced questions have been frequently asked to provide a more in-depth overview of the current literature.
+
+  The first set of questions concern how infants' sensitivity is modulated by different kinds of mispronunciations.
+Some experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level (i.e.
+1-feature, 2-features, 3-features, etc.), finding graded sensitivity to both consonant [@White2008; @Bernier2017; @Tamasi2016] and vowel [@Mani2011] feature changes.
+This also has consequences for task demands, as the greater the number of features changed, or *mispronunciation size*, the easier it may be to detect a mispronunciation, whereas more similar mispronunciations may be more difficult to detect.
+
+  Models of spoken word processing place more or less importance on the position of a phoneme in a word.
+The COHORT model [@Marslen-Wilson1989] describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.
+In contrast, the TRACE model [@McClelland1986] describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.
+The *position of mispronunciation* in the word may therefore differentially interrupt the infant's word recognition process, with onset mispronunciations resulting in a more demanding task than medial or coda mispronunciations.
+
+  In order to study the influence of mispronunciation position, many studies control the *phonological overlap between target and distractor labels*.
 For example, when examining sensitivity to a mispronunciation of the target word "dog", the vowel mispronunciation "dag" would be paired with a distractor image that shares onset overlap, such as "duck".
-This ensures that infants can not use the onset of the word to differentiate between the target and distractor images (Fernald, Swingley, & Pinto, 2001).
+This ensures that infants can not use the onset of the word to differentiate between the target and distractor images [@Fernald2001a].
 Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.
-The influence of distractor overlap also depends on the *position of mispronunciation* in the word, which can be at word onset, medial, or final positions.
-Models of spoken word processing place more or less importance on the position of a phoneme in a word.
-The COHORT model (Marslen-Wilson & Zwitserlood, 1989) describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.
-In contrast, the TRACE model (McClelland & Elman, 1986) describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.
-
-  TRACE has also been used to model infants' sensitivity to mispronunciation position (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth.
-In early language acquisition, infants typically know more consonant compared to vowel onset words.
-When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations.
-The prevalence of consonant onset words may contribute to the finding that consonants carry more weight in lexical processing (C-bias; see Nazzi, Poltrock, & Von Holzen, 2016 for a recent review).
+
+  Consonantal changes may be more disruptive to lexical processing than vowel changes [@Nazzi2018], which has been extended to infancy [@Nazzi2016].
 In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations.
 Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels.
-English-learning 12-, 15-, 18-, and 24-month-olds (Mani & Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds (Hojen et al., unpublished) demonstrate similar sensitivity to consonant and vowel mispronunciations.
-One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations (Swingley, 2016).
+English-learning 12-, 15-, 18-, and 24-month-olds [@Mani2007; @Mani2010kepstups] and Danish-learning 20-month-olds [@Hojen] demonstrate similar sensitivity to consonant and vowel mispronunciations.
+One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations [@Swingley2016].
 The English-learning infants tested by Swingley were older than previous studies (mean age 28 months).
-In word learning, the C-bias has been found to develop later in English learning infants (Floccia, Nazzi, Delle Luche, Poltrock, & Goslin, 2014; Nazzi, Floccia, Moquet, & Butler, 2009).
-In the current meta-analysis, we attempt to synthesize studies examining sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence (Floccia et al., 2014; Keidel et al., 2007; Nazzi et al., 2016).
-We further examine the impact of language family on mispronunciation sensitivity to consonants and vowels, as C-bias emergence has been found to have a different developmental trajectory for Romance (French, Italian) compared to Germanic (British English, Danish) languages (Nazzi et al., 2016).
+In word learning, the C-bias has been found to develop later in English- than French-learning infants [@Floccia2014; @Nazzi2009a].
+In the current meta-analysis, we attempt to synthesize studies examining sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence [@Floccia2014; @Nazzi2016; @Keidel2007].
+We further examine the impact of language family on mispronunciation sensitivity to consonants and vowels, as C-bias emergence has been found to have a different developmental trajectory for Romance (French, Italian) compared to Germanic (British English, Danish) languages [@Nazzi2016].
+
+  A second question is whether the non-linguistic context modulates infants' responses to mispronunciations: Most research on the topic presents infants with two known words, thus ruling out the unlabeled competitor, or distractor, as possible target.
+In contrast, other studies present infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects [@White2008; @Mani2011; @Skoruppa2013; @Swingley2016].
+By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied [@Halberda2003; @Markman2003].
+In a learning context, 24- and 30-month-olds associate a novel label with an unfamiliar object, but 18-month-olds do not, providing evidence that this ability, known as mutual exclusivity, is developing from 18 to 30 months [@Bion2013].
+We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar.
+This is a particularly fruitful question to investigate within the context of a meta-analysis, as mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared.
 
@@
 Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare.
+Indeed, the majority of studies focus on infants learning English as a native language and a sufficient sample of other languages is therefore lacking.
 Although we do not explicitly compare overall mispronunciation sensitivity by language (although see previous paragraph for rationale to test by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.
 
-In sum, the studies we have reviewed begin to paint a picture of the development of infants' mispronunciation sensitivity.
-Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding of the big picture of early language development.
+In sum, the studies we have reviewed begin to paint a picture of the development of infants' use of phonological detail in familiar word recognition.
+Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding of the big picture of early phono-lexical development.
 Meta-analyses can provide unique insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and of their mispronunciations sensitivity.
 Because we aggregate data over various age groups, this meta-analysis can also investigate the role of maturation by assessing the impact of age and vocabulary size.
-We also make hands-on recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses [@Bergmann2018].
+We also explore the influence of different linguistic (mispronunciation size and position, target-distractor overlap, and type of mispronunciation) and non-linguistic (distractor familiarity) demands on the study of mispronunciation sensitivity.
+Finally, we explore potential data analysis choices that may influence different conclusions about mispronunciation sensitivity development as well as offer recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses [@Bergmann2018].
 
@@
 4 Size of mispronunciation, measured in features changed;  
-5 Distractor familiarity: familiar or unfamiliar;  
-6 Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;  
-7 Position of mispronunciation: onset, medial, offset, or mixed;  
-8 Type of mispronunciation: consonant, vowel, or both.
+5 Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;  
+6 Position of mispronunciation: onset, medial, offset, or mixed;  
+7 Type of mispronunciation: consonant, vowel, or both.
+8 Distractor familiarity: familiar or unfamiliar;
 
@@
 
-[^1]: Two papers tested bilingual infants (Ramon-Casas & Bosch, 2010; Ramon-Casas et al., 2011), yielding `r bil_infants` experimental conditions.
+[^1]: Two papers tested bilingual infants [@Ramon-Casas2009; @Ramon-Casas2010], yielding `r bil_infants` experimental conditions.
 Due to this small number, we do not investigate the role of multilingualism, but do note that removing these papers from the meta-analysis did not alter the pattern of results.
@@
 Second, we analyzed the correlation between reported vocabulary size and mispronunciation sensitivity using the R [@R] package meta [@meta].
-Finally, for a subsequent exploratory investigation of experimental characteristics, we introduced each characteristic as a moderator (more detail below).
+For a subsequent exploratory investigation of experimental characteristics, we introduced each as a moderator: size of mispronunciation, position of mispronunciation, phonological overlap between target and distractor labels, type of mispronunciation, and distractor familiarity (more detail below).
 
@@
 
-Figure \@ref(fig:Vocab-describe1) plots the year of publication for all the mispronunciation sensitivity studies included in this meta-analysis.
+Figure \@ref(fig:Vocabdescribe1) plots the year of publication for all the mispronunciation sensitivity studies included in this meta-analysis.
 This figure illustrates two things: the increasing number of mispronunciation sensitivity studies and the decreasing number of mispronunciation studies measuring vocabulary.
@@
 
-```{r Vocab-describe1, echo = FALSE, fig.width=10,fig.height=8, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (orange), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (green).", results="hide"}
+```{r Vocabdescribe1, echo = FALSE, fig.width=10,fig.height=8, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (orange), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (green).", results="hide"}
 #how did vocabulary collection change over time?
@@
 The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age and increased vocabulary size.
-The results seem clear: Although infants consider a mispronunciation to be a better match to the target image than to a distractor image, there was a constant and stable effect of mispronunciation sensitivity.
-This did not change with development, and we might consider age a proxy for vocabulary size.
-We observe that the data for directly reported vocabulary size were too sparse to draw strong conclusions.
+The results seem clear: Although infants consider a mispronunciation to be a better match to the target image than to a distractor image, there was a constant and stable effect of mispronunciation sensitivity across all ages.
 In the literature, evidence for all possible developmental trajectories has been found, including mispronunciation sensitivity that increases, decreases, or does not change with age or vocabulary size.
-The present results do lend some support for the proposal that mispronunciation sensitivity stays consistent as infants develop.
+The present results do lend some support for the proposal that mispronunciation sensitivity stays constant as infants develop.
 Furthermore, although we found a relationship between vocabulary size (comprehension) and target looking for correct pronunciations, we found no relationship between vocabulary and target looking for mispronunciations.
@@
 
-Alternatively, the lack of developmental change in mispronunciation sensitivity could be due to differences in the types of tasks given to infants of different ages.
+The studies examined in this meta-analysis examined mispronunciation sensitivity, but many also included more specific questions aimed at uncovering more detailed phonological processes at play during word recognition.
+Not only are these questions theoretically interesting, they also have the potential to change the difficulty of a msipronunciation sensitivity experiment.
+It is possible that the lack of developmental change in mispronunciation sensitivity found by our meta-analysis does not capture a true lack of change, but is instead influenced by differences in the types of tasks given to infants of different ages.
 If infants' word recognition skills are generally thought to improve with age and vocabulary size, research questions that tap more complex processes may be more likely to be investigated in older infants.
@@
 In this section, we consider each moderator individually and investigate its influence on mispronunciation sensitivity.
-For most moderators (except Number of features changed), we combine the correct and mispronounced datasets and include the moderator of condition, to study mispronunciation sensitivity as opposed to object recognition.
+For most moderators (except mispronunciation size), we combine the correct and mispronounced datasets and include the moderator of condition, to study mispronunciation sensitivity as opposed to object recognition.
 To better understand the impact of these moderators on developmental change, we include age as subsequent moderator as well as an exploratory analysis of the age of infants tested with each type of moderator.
 The latter analysis is included to explore whether the lack of developmental change in mispronunciation sensitivity in the overall dataset is due to more complex moderator tasks being given to older infants, which may lower the overall effect size of mispronunciation sensitivity at older ages and dampen any evidence of change.
-Finally, we analyze the relationship between infant age and the moderator condition they were tested in using Fischer's exact test, which is more appropriate for small sample sizes (Fischer, 1922).
+Finally, we analyze the relationship between infant age and the moderator condition they were tested in using Fisher's exact test, which is more appropriate for small sample sizes [@Fisher1922].
 For each moderator, we evaluate the independence of infants' age group (divided into quartiles unless otherwise specified) and assignment to each type of condition in a particular moderator.
@@
 
-To assess whether the size of the mispornunciation tested, as measured by the number of features change, modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced using 1-, 2-, and 3-feature changes.
+To assess whether the size of the mispornunciation tested, as measured by the number of features changed, modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced using 1-, 2-, and 3-feature changes.
 We did not include data for which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent (e.g., one mispronunciation included a 2-feature change whereas another only a 1-feature change).
 This analysis was therefore based on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` experimental conditions for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations.
-Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an equal impact on mispronunciation sensitivity, following the argument of graded sensitivity (White & Aslin, 2008; Mani & Plunkett 2011), and this modertor was coded as a continuous variable.
+Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an equal impact on mispronunciation sensitivity, following the argument of graded sensitivity [@White2008; @Mani2011], and this modertor was coded as a continuous variable.
 
@@
 
-To understand the relationship between mispronunciation size and mispronunciation sensitivity, we  evaluated the effect size Hedges' *g* with number of features changed as a moderator.
-The moderator test was significant, `r mod_test(rma_NFeatures)`.
-Hedges' *g* for number of features changed was `r g_SE(sum_eff)`, which indicated that as the number of features changed increased, the effect size Hedges' *g* significantly decreased `r CI_p(sum_eff)`.
-We plot this relationship in Figure \@ref(fig:PlotFeatEffect).
-This confirms previous findings of a graded sensitivity to the number of features changed for both consonant (Bernier & White, 2017; Tamasi, 2016; White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) mispronunciations as well as the importance of controlling for the degree of phonological mismatch in experimental design.
-
-To better understand how this moderator impacted our estimate of developmental change in mispronunciation sensitivity, we added age as a moderator.
-The moderator test was significant, `r mod_test(rma_NFeatures_age)`, but the interaction between age and number of features changed was not significant, $\beta$`r full_estimate(sum_eff_age)`.
-The small effect size for the interaction between age and number of features changed suggests that the impact of number of features changed on mispronunciation sensitivity does not change with infant age.
-This may be due to the fact that only a handful of studies have explicitly examined the effect of the number of features changed on mispronunciation sensitivity and only these studies include 3-feature changes (Bernier & White, 2017; Tamasi, 2016; White & Morgan, 2008; Mani & Plunkett, 2011).
-
-The results of Fisher's exact test were not significant, *p* `r psig(fish.test$p.value)`.
-This lack of a relationship suggests that older and younger infants are not being tested in experimental conditions that differentially manipulate the number of features changed.
-
-## (Insert Figure 5 about here)
-
-```{r PlotFeatEffect, echo = FALSE}
+```{r PlotFeatEffect, echo = FALSE, fig.width=10,fig.height=6, fig.cap="Effect sizes for correct pronunciations, 1-, 2-, and 3-feature mispronunciations.", results="hide"}
 
@@
 
-### Distractor familiarity
-
-```{r DistFam_demographics, results = "hide"}
-
-distr_info <- dat %>%
-  group_by(object_pair) %>%
+To understand the relationship between mispronunciation size and mispronunciation sensitivity, we  evaluated the effect size Hedges' *g* with number of features changed as a moderator.
+The moderator test was significant, `r mod_test(rma_NFeatures)`.
+Hedges' *g* for number of features changed was `r g_SE(sum_eff)`, which indicated that as the number of features changed increased, the effect size Hedges' *g* significantly decreased `r CI_p(sum_eff)`.
+We plot this relationship in Figure \@ref(fig:PlotFeatEffect).
+This confirms previous findings of a graded sensitivity to the number of features changed for both consonant [@Bernier2017; @Tamasi2016; @White2008] and vowel [@Mani2011] mispronunciations as well as the importance of controlling for the degree of phonological mismatch in experimental design.
+In other words, the infants' ability to detect a mispronunciation depends on the size of the mispronunciation.
+
+To better understand how this moderator impacted our estimate of developmental change in mispronunciation sensitivity, we added age as a moderator.
+The moderator test was significant, `r mod_test(rma_NFeatures_age)`, but the interaction between age and number of features changed was not significant, $\beta$`r full_estimate(sum_eff_age)`.
+The small effect size for the interaction between age and number of features changed suggests that the impact of number of features changed on mispronunciation sensitivity does not substantially change with infant age.
+Alternatively, we might not have enough power to detect a small but consistent effect because only a handful of studies have explicitly examined the effect of the number of features changed on mispronunciation sensitivity and only these studies include 3-feature changes [@Bernier2017; @Tamasi2016; @White2008; @Mani2011].
+
+Finally, we examined whether infants are disproportionately tested in conditions with smaller or larger mispronunciation sizes based on their age.
+The results of Fisher's exact test were not significant, *p* `r psig(fish.test$p.value)`.
+This lack of a relationship suggests that older and younger infants are not being tested in experimental conditions that differentially manipulate the number of features changed.
+
+## (Insert Figure 5 about here)
+
+### Position of mispronunciation
+
+```{r Location_descrip}
+
+misp_location_info <- dat %>%
+  group_by(mispron_location) %>%
   summarize(n_exp_conditions =  n())
 
-```
-
-To assess whether familiarity with the distractor image modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced and were either paired with a familiar or unfamiliar distractor.
-A familiar distractor was used in `r with(distr_info, n_exp_conditions[object_pair == "familiar_familiar"])` experimental conditions and a unfamiliar distractor in `r with(distr_info, n_exp_conditions[object_pair == "familiar_novel"])` experimental conditions.
-
-```{r DistractorType, results= "asis"}
-
-rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
-
-d_fam <- coef(summary(rma_Distractor))[2,]
-d_fam_condit <- coef(summary(rma_Distractor))[4,]
-
-```
-
-```{r DistractorType_age, results= "asis"}
-
-# age moderator
-rma_Distractor_age <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition*age.C, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
-
- sum_eff_age <- coef(summary(rma_NFeatures_age))[8,]
- sum_eff_2 <- coef(summary(rma_NFeatures_age))[5,]
+misp_location_info$vary_loc <- ifelse(misp_location_info$mispron_location == "coda/medial", misp_location_info$n_exp_conditions,
+                                      ifelse(misp_location_info$mispron_location == "onset/medial", misp_location_info$n_exp_conditions,
+                                             ifelse(misp_location_info$mispron_location == "onset/medial/coda", misp_location_info$n_exp_conditions,0)))
+
+vary_loc <- sum(misp_location_info$vary_loc, na.rm = T)
+
+mli <- misp_location_info %>%
+  filter(!is.na(mispron_location))
+
+```
+
+To assess whether the position of the mispronunciation has an impact on mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to mispronunciations on the onset, medial, and coda phonemes.
+We did not include data for which the mispronunciation varied in regard to position (*n* = `r vary_loc`) or was not reported (*n* = `r with(misp_location_info, n_exp_conditions[is.na(mispron_location)])`).
+The analysis was therefore based on a subset of the overall dataset, with `r with(mli, n_exp_conditions[mispron_location == "onset"])` experimental conditions comparing a mispronunciation on the onset phoneme, `r with(mli, n_exp_conditions[mispron_location == "medial"])` experimental conditions comparing a mispronunciation on the medial phoneme, and `r with(mli, n_exp_conditions[mispron_location == "coda"])` experimental conditions comparing a mispronunciation on the coda phoneme.
+We coded the onset, medial, and coda positions as continuous variables, to evaluate the importance of each subsequent position [@Marslen-Wilson1989].
+
+```{r Location_misp}
+
+db_ET_MPl = dat %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial"| mispron_location == "coda")
+
+# linear
+db_ET_MPl$m_posit <- ifelse(db_ET_MPl$mispron_location == "onset", 1,
+                            ifelse(db_ET_MPl$mispron_location == "medial", 2, 3))
+
+db_ET_MPl$m_posit <- as.numeric(as.character(db_ET_MPl$m_posit))
+
+rma_LinearLocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~m_posit*condition, data = db_ET_MPl, random = ~same_infant_calc | short_cite)
+
+sum_eff <- coef(summary(rma_LinearLocationCondition))[4,]
+
+ linear_position <- sum_eff$estimate
+
+```
+
+```{r Misp_Posit_age}
+
+# mispronunciation sensitivity
+
+db_ET_MPl = dat %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial"| mispron_location == "coda")
+
+# linear
+db_ET_MPl$m_posit <- ifelse(db_ET_MPl$mispron_location == "onset", 1,
+                            ifelse(db_ET_MPl$mispron_location == "medial", 2, 3))
+
+db_ET_MPl$m_posit <- as.numeric(as.character(db_ET_MPl$m_posit))
+
+rma_LinearLocationCondition_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*m_posit*condition, data = db_ET_MPl, random = ~same_infant_calc | short_cite)
+
+sum_eff_age <- coef(summary(rma_LinearLocationCondition_age))[8,]
 
@@
 
- dat$age_group <- ntile(dat$mean_age_1, 4)
-
- dist_fam_ages <- dat %>%
-  group_by(age_group, object_pair) %>%
+ db_ET_MPl$age_group <- ntile(db_ET_MPl$mean_age_1, 3)
+
+ misp_posit_ages <- db_ET_MPl %>%
+  group_by(age_group, mispron_location) %>%
   summarize(n =  n())
@@
 
- dist_fam_ages <- dist_fam_ages %>% spread(object_pair, n)
+ misp_posit_ages <- misp_posit_ages %>% spread(mispron_location, n)
 
  #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
-fish.test <- fisher.test(dist_fam_ages)
-
-```
-
-To understand the relationship between distractor familiarity and mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with distractor familiarity and condition as moderators.
-The moderator test was significant, `r mod_test(rma_NFeatures)`, but the effect of distractor familiarity ($\beta$`r full_estimate(d_fam)`) as well as the interaction between distractor familiarity and condition ($\beta$`r full_estimate(d_fam_condit)`) were not significant.
-The results suggest that overall, infants' familiarity with the distractor object (familiar or unfamiliar) did not impact their mispronunciation sensitivity.
-
-We next examined whether age modulates object recognition or mispronunciation sensitivity when the distractor image is familiar or unfamiliar.
-Based on previous results, we expected older infants  to have greater mispronunciation sensitivity than younger infants when the distractor was unfamiliar compared to familiar.
-To evaluate this prediction, we added age as a moderator.
-The moderator test was significant `r mod_test(rma_Distractor_age)`.
-The estimate for the  three-way-interaction between condition, distractor familiarity, and age was small and not significant ($\beta$ = `r full_estimate(sum_eff_age)`.
-We note that in this model, the interaction between condition and distractor familiarity was significant ($\beta$`r full_estimate(sum_eff_2)`, but that this estimate is similar to the original, non-significant estimate specifically examining this interaction in the previous model.
-Taken together, these results suggest that regardless of age, mispronunciation sensitivity was similar whether the distractor image was familiar or unfamiliar.
-
-The results of Fisher's exact test were not significant, *p* `r psig(fish.test$p.value)`.
-This lack of a relationship suggests that older and younger infants are not being tested in experimental conditions that differentially employ distractor images that are familiar or unfamiliar.
+fish.test <- fisher.test(misp_posit_ages)
+
+```
+
+```{r PlotMispPosit, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions.
+Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions by age.
+For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
+
+db_ET_MPl = dat %>%
+  filter(mispron_location == "onset"  | mispron_location == "medial"| mispron_location == "coda")
+
+db_ET_MPl$condition_label <- ifelse(db_ET_MPl$condition==1, "Correct", "Mispronunciation")
+
+db_ET_MPl$location_label <- ifelse(db_ET_MPl$mispron_location=="onset", "Onset",
+                                   ifelse(db_ET_MPl$mispron_location == "medial", "Medial", "Coda"))
+
+db_ET_MPl$location_label <- factor(db_ET_MPl$location_label, levels = c("Onset", "Medial", "Coda"))
+
+db_ET_MPl <- db_ET_MPl[,c("short_cite", "is_correct", "is_mp", "location_label", "condition_label", "g_calc", "weights_g", "mean_age_1", "n_1")]
+
+dat.c <- subset(db_ET_MPl, is_correct == 1)
+dat.m <- subset(db_ET_MPl, is_mp == 1)
+
+dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "location_label", "mean_age_1", "n_1"))
+
+dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
+dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
+
+ms.agg <- ggplot(dat.cm, aes(location_label, Misp_sensitivity, fill = location_label)) + 
+  #facet_grid(.~dv_label)+
+    geom_violin() + 
+  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
+  labs(title="a")+
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Misp. Sensitivity")
+
+ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = location_label)) + 
+    #facet_grid(.~dv_label)+
+  geom_point(aes(size = n_1),show.legend=FALSE) +
+  labs(title="b")+
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Misp. Sensitivity")
+
+lay <- rbind(c(1), c(2))
+#lay <- rbind(c(1,2))
+
+  jpeg(filename = "figures/Figure_7_Misp_position.jpg",
+       width = 500, height = 600, units = "px")
+
+ger.plot.age <- grid.arrange(ms.agg, ms.age,
+                             layout_matrix = lay)
+
+ dev.off()
+
+grid.draw(ger.plot.age)
+
+```
+
+To understand the relationship between mispronunciation position and  mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with mispronunciation position and condition as moderators.
+The moderator test was significant, `r mod_test(rma_LinearLocationCondition)`.
+For the interaction between condition and mispronunciation position, the estimate was small but significant ($\beta$ `r full_estimate(sum_eff)`.
+As can be seen in Figure \@ref(fig:PlotMispPosit)a, mispronunciation sensitivity decreased linearly as the position of the mispronunciation moved later in the word, with sensitivity greatest for onset mispronunciations and smallest for coda mispronunciations.
+
+To better understand how this moderator impacted our estimate of developmental change in mispronunciation sensitivity, we added age as a moderator.
+The moderator test was significant, `r mod_test(rma_LinearLocationCondition_age)`.
+The estimate for the three-way interaction between age, condition, and mispronunciation position was not significant ($\beta$ `r full_estimate(sum_eff_age)`.
+As can be seen in Figure \@ref(fig:PlotMispPosit)b, mispronunciation sensitivity but stays relatively stable for onset and medial mispronunciaitons.
+For mispronunciations on the coda position it appears that mispronunciation sensitivity increases with age, but this is likely underpowered and therefore not detectable by our meta-analysis.
+
+Finally, we examined whether infants are disproportionately tested in conditions different mispronunciation positions based on their age.
+Due to the small sample size of coda mispronunciations, we only included 3 age groups in Fisher's exact test.
+The results were significant, *p* `r psig(fish.test$p.value)`.
+Older infants were more likely to be tested on onset mispronunciations, while younger infants were more likely to be tested on medial mispronunciations.
+An onset mispronunciation may be more disruptive to lexical access than mispronunciations in subsequent positions [@Marslen-Wilson1989], and therefore easier to detect.
+For this reason, it is rather unsuprising that onset mispronunciations show the greatest estimate of mispronunciation sensitivity.
+However, it also means that younger infants, who were more likely to be tested on medial mispronunciations, had a comparably harder task than older infants, who were more likely to be tested on onset mispronunciations.
+It is unlikely that this influenced our developmental trajectory estimate, as the consequence would have been mispronunciation sensitivity that increases with age.
+
+## (Insert Figure 7 about here)
 
@@
 
-To understand the relationship between phonological overlap between target and distractor and  mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with distractor overlap and condition as moderators.
-The moderator test was significant, `r mod_test(rma_DistractorOverlapMS)`.
-The estimate for the interaction between condition and distractor overlap was small, but significant ($\beta$ `r full_estimate(sum_eff2)`, suggesting that mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap.
-This relationship be seen in Figure \@ref(fig:PlotDistOverlap)a.
-
-To better understand how this moderator impacted our estimate of developmental change in mispronunciation sensitivity, we added age as a moderator.
-The moderator test was significant, `r mod_test(rma_DistractorOverlap_age_MS)` and the estimate for the three-way interaction between age, condition, and distractor overlap was significant, but relatively small ($\beta$ = `r full_estimate(sum_eff_age)`.
-As can be seen in Figure \@ref(fig:PlotDistOverlap)b, mispronunciation sensitivity increases with age for target-distractor pairs containing onset overlap, but decreases with age for target-distractor pairs containing no overlap.
-
-The results of Fisher's exact test were significant, *p* `r psig(fish.test$p.value)`.
-Older infants were more likely to be tested in experimental conditions where target and distractor images overlapped on their onset phoneme, while younger infants were more likely to be tested with target and distractor images that did not control for overlap.
-A distractor image that overlaps in the onset phoneme with the target image is considered a more challenging task to the infant, as infants must pay attention to the mispronounced phoneme and can not use the differing onsets between target and distractor images to differentiate (Fernald, Swingley, & Pinto, 2001).
-It therefore appears that older infants were given a more challenging task than younger infants.
-This may explain why infants in the onset overlap condition, a harder task, have a greater effect size estimate for mispronunciation sensitivity than those in the no overlap condition, which is a comparably easier task.
-We return to this issue in the General Discussion.
-
-## (Insert Figure 6 about here)
-
-```{r PlotDistOverlap}
+```{r PlotDistOverlap, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for target-distractor pairs with onset overlap or no overlap.
+Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for target-distractor pairs with onset overlap or no overlap by age.
+For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
 
@@
 
-### Position of mispronunciation
-
-```{r Location_descrip}
-
-misp_location_info <- dat %>%
-  group_by(mispron_location) %>%
-  summarize(n_exp_conditions =  n())
-
-```
-
-To assess whether the position of the mispronunciation has an impact on mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to mispronunciations on the onset, medial, and coda phonemes.
-We did not include data for which the mispronunciation varied in regard to position (*n* = `r with(misp_location_info, n_exp_conditions[mispron_location == "coda/medial" | mispron_location == "onset/medial" | mispron_location == "onset/medial/coda"])`) or was not reported (*n* = `r with(misp_location_info, n_exp_conditions[is.na(mispron_location)])`).
-The analysis was therefore based on a subset of the overall dataset, with `r with(misp_location_info, n_exp_conditions[mispron_location == "onset"])` experimental conditions comparing a mispronunciation on the onset phoneme, `r with(misp_location_info, n_exp_conditions[mispron_location == "medial"])` experimental conditions comparing a mispronunciation on the medial phoneme, and `r with(misp_location_info, n_exp_conditions[mispron_location == "coda"])` experimental conditions comparing a mispronunciation on the coda phoneme.
-We coded the onset, medial, and coda positions as continuous variables, to evaluate the importance of each subsequent position (Marslen-Wilson & Zwitserlood, 1989).
-
-```{r Location_misp}
-
-db_ET_MPl = dat %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial"| mispron_location == "coda")
-
-# linear
-db_ET_MPl$m_posit <- ifelse(db_ET_MPl$mispron_location == "onset", 1,
-                            ifelse(db_ET_MPl$mispron_location == "medial", 2, 3))
-
-db_ET_MPl$m_posit <- as.numeric(as.character(db_ET_MPl$m_posit))
-
-rma_LinearLocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~m_posit*condition, data = db_ET_MPl, random = ~same_infant_calc | short_cite)
-
-sum_eff <- coef(summary(rma_LinearLocationCondition))[4,]
-
- linear_position <- sum_eff$estimate
-
-```
-
-```{r Misp_Posit_age}
-
-# mispronunciation sensitivity
-
-db_ET_MPl = dat %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial"| mispron_location == "coda")
-
-# linear
-db_ET_MPl$m_posit <- ifelse(db_ET_MPl$mispron_location == "onset", 1,
-                            ifelse(db_ET_MPl$mispron_location == "medial", 2, 3))
-
-db_ET_MPl$m_posit <- as.numeric(as.character(db_ET_MPl$m_posit))
-
-rma_LinearLocationCondition_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*m_posit*condition, data = db_ET_MPl, random = ~same_infant_calc | short_cite)
-
-sum_eff_age <- coef(summary(rma_LinearLocationCondition_age))[8,]
-
- # divide into age groups
-
- db_ET_MPl$age_group <- ntile(db_ET_MPl$mean_age_1, 3)
-
- misp_posit_ages <- db_ET_MPl %>%
-  group_by(age_group, mispron_location) %>%
-  summarize(n =  n())
-
- #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
-
- misp_posit_ages <- misp_posit_ages %>% spread(mispron_location, n)
-
- #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
-fish.test <- fisher.test(misp_posit_ages)
-
-```
-
-To understand the relationship between mispronunciation position and  mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with mispronunciation position and condition as moderators.
-The moderator test was significant, `r mod_test(rma_LinearLocationCondition)`.
-For the interaction between condition and mispronunciation position, the estimate was small but significant ($\beta$ `r full_estimate(sum_eff)`.
-As can be seen in Figure \@ref(fig:PlotMispPosit)a, mispronunciation sensitivity decreased linearly as the position of the mispronunciation moved later in the word, with sensitivity greatest for onset mispronunciations and smallest for coda mispronunciations.
+To understand the relationship between phonological overlap between target and distractor and  mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with distractor overlap and condition as moderators.
+The moderator test was significant, `r mod_test(rma_DistractorOverlapMS)`.
+The estimate for the interaction between condition and distractor overlap was small, but significant ($\beta$ `r full_estimate(sum_eff2)`, suggesting that mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap.
+This relationship be seen in Figure \@ref(fig:PlotDistOverlap)a.
 
 To better understand how this moderator impacted our estimate of developmental change in mispronunciation sensitivity, we added age as a moderator.
-The moderator test was significant, `r mod_test(rma_LinearLocationCondition_age)`.
-The estimate for the three-way interaction between age, condition, and mispronunciation position was not significant ($\beta$ `r full_estimate(sum_eff_age)`.
-As can be seen in Figure \@ref(fig:PlotMispPosit)b, mispronunciation sensitivity but stays relatively stable for onset and medial mispronunciaitons.
-For mispronunciations on the coda position it appears that mispronunciation sensitivity increases with age, but this is likely underpowered and therefore not detectable by our meta-analysis.
-
-Due to the small sample size of coda mispronunciations, we only included 3 age groups in Fisher's exact test.
-The results were significant, *p* `r psig(fish.test$p.value)`.
-Older infants were more likely to be tested on onset mispronunciations, while younger infants were more likely to be tested on medial mispronunciations.
-An onset mispronunciation may be more disruptive to lexical access than mispronunciations in subsequent positions (Marslen-Wilson & Zwitserlood, 1989), and therefore easier to detect.
-For this reason, it is rather unsuprising that onset mispronunciations show the greatest estimate of mispronunciation sensitivity.
-However, it also means that younger infants, who were more likely to be tested on medial mispronunciations, had a comparably harder task than older infants, who were more likely to be tested on onset mispronunciations.
-It is unlikely that this influenced our developmental trajectory estimate, as the consequence would have been mispronunciation sensitivity that increases with age.
+The moderator test was significant, `r mod_test(rma_DistractorOverlap_age_MS)` and the estimate for the three-way interaction between age, condition, and distractor overlap was significant, but relatively small ($\beta$ = `r full_estimate(sum_eff_age)`.
+As can be seen in Figure \@ref(fig:PlotDistOverlap)b, mispronunciation sensitivity increases with age for target-distractor pairs containing onset overlap, but decreases with age for target-distractor pairs containing no overlap.
+
+Finally, we examined whether infants are disproportionately tested in experiments with or without phonological overlap between the target and distractor labels based on their age.
+The results of Fisher's exact test were significant, *p* `r psig(fish.test$p.value)`.
+Older infants were more likely to be tested in experimental conditions where target and distractor images overlapped on their onset phoneme, while younger infants were more likely to be tested with target and distractor images that did not control for overlap.
+A distractor image that overlaps in the onset phoneme with the target image is considered a more challenging task to the infant, as infants must pay attention to the mispronounced phoneme and can not use the differing onsets between target and distractor images to differentiate [@Fernald2001a].
+It therefore appears that older infants were given a more challenging task than younger infants.
+This may explain why infants in the onset overlap condition, a harder task, have a greater effect size estimate for mispronunciation sensitivity than those in the no overlap condition, which is a comparably easier task.
+We return to this issue in the General Discussion.
 
 ## (Insert Figure 7 about here)
-
-```{r PlotMispPosit}
-
-db_ET_MPl = dat %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial"| mispron_location == "coda")
-
-db_ET_MPl$condition_label <- ifelse(db_ET_MPl$condition==1, "Correct", "Mispronunciation")
-
-db_ET_MPl$location_label <- ifelse(db_ET_MPl$mispron_location=="onset", "Onset",
-                                   ifelse(db_ET_MPl$mispron_location == "medial", "Medial", "Coda"))
-
-db_ET_MPl$location_label <- factor(db_ET_MPl$location_label, levels = c("Onset", "Medial", "Coda"))
-
-db_ET_MPl <- db_ET_MPl[,c("short_cite", "is_correct", "is_mp", "location_label", "condition_label", "g_calc", "weights_g", "mean_age_1", "n_1")]
-
-dat.c <- subset(db_ET_MPl, is_correct == 1)
-dat.m <- subset(db_ET_MPl, is_mp == 1)
-
-dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "location_label", "mean_age_1", "n_1"))
-
-dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
-dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
-
-ms.agg <- ggplot(dat.cm, aes(location_label, Misp_sensitivity, fill = location_label)) + 
-  #facet_grid(.~dv_label)+
-    geom_violin() + 
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
-  labs(title="a")+
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Misp. Sensitivity")
-
-ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = location_label)) + 
-    #facet_grid(.~dv_label)+
-  geom_point(aes(size = n_1),show.legend=FALSE) +
-  labs(title="b")+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Misp. Sensitivity")
-
-lay <- rbind(c(1), c(2))
-#lay <- rbind(c(1,2))
-
-  jpeg(filename = "figures/Figure_7_Misp_position.jpg",
-       width = 500, height = 600, units = "px")
-
-ger.plot.age <- grid.arrange(ms.agg, ms.age,
-                             layout_matrix = lay)
-
- dev.off()
-
-grid.draw(ger.plot.age)
-
-```
 
@@
 
-To understand the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with mispronunciation type and condition as moderators.
-The moderator test was significant, `r mod_test(rma_TypeFeaturesMP_Condition)`, but the interaction between mispronunciation type and condition ($\beta$`r full_estimate(sum_eff2)`) was not significant.
-The results suggest that overall, infants' sensitivity to consonant and vowel mispronunciations was similar.
-
-We next examined whether age modulates mispronunciation sensitivity when the mispronunciation is a consonant or a vowel.
-When age was added as a moderator, the moderator test was significant, `r mod_test(rma_TypeFeaturesMP_Condition)` and the estimate for the three-way interaction between age, condition, and mispronunciation type was significant, but relatively small ($\beta$ = `r full_estimate(sum_eff_age)`.
-As can be seen in Figure \@ref(fig:PlotMispType)b, as infants age, mispronunciation sensitivity grows larger for vowel mispronunciations but stays steady for consonant mispronunciations.
-Noticeably, mispronunciation sensitivity appears greater for consonant compared to vowel mispronunciations at younger ages, but this difference diminishes as infants age.
-
-The results of Fisher's exact test were significant, *p* `r psig(fish.test$p.value)`.
-Older infants were more likely to be tested on consonant mispronunciations, while younger infants were more likely to be tested on vowel mispronunciations.
-It is not immediately clear whether the relationship between infant age and type of mispronunciation influences our estimate of how mispronunciation sensitivity changes with development.
-Whether consonant or vowel mispronunciations are more "difficult" is a matter of theoretical debate, but some evidence suggest that it may be influenced by infants' native language (Nazzi, Poltrock, & Von Holzen, 2016).
-We next examined whether this was the case.
-
-## (Insert Figure 8 about here)
-
-```{r PlotMispType}
+```{r PlotMispType, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations.
+Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations by age.
+For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
 
@@
 
+To understand the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with mispronunciation type and condition as moderators.
+The moderator test was significant, `r mod_test(rma_TypeFeaturesMP_Condition)`, but the interaction between mispronunciation type and condition ($\beta$`r full_estimate(sum_eff2)`) was not significant.
+The results suggest that overall, infants' sensitivity to consonant and vowel mispronunciations was similar.
+
+We next examined whether age modulates mispronunciation sensitivity when the mispronunciation is a consonant or a vowel.
+When age was added as a moderator, the moderator test was significant, `r mod_test(rma_TypeFeaturesMP_Condition)` and the estimate for the three-way interaction between age, condition, and mispronunciation type was significant, but relatively small ($\beta$ = `r full_estimate(sum_eff_age)`.
+As can be seen in Figure \@ref(fig:PlotMispType)b, as infants age, mispronunciation sensitivity grows larger for vowel mispronunciations but stays steady for consonant mispronunciations.
+Noticeably, mispronunciation sensitivity appears greater for consonant compared to vowel mispronunciations at younger ages, but this difference diminishes as infants age.
+
+Finally, we examined whether infants are disproportionately tested in experiments with a consonant or vowel mispronunciation based on their age.
+The results of Fisher's exact test were significant, *p* `r psig(fish.test$p.value)`.
+Older infants were more likely to be tested on consonant mispronunciations, while younger infants were more likely to be tested on vowel mispronunciations.
+It is not immediately clear whether the relationship between infant age and type of mispronunciation influences our estimate of how mispronunciation sensitivity changes with development.
+Whether consonant or vowel mispronunciations are more "difficult" is a matter of theoretical debate, but some evidence suggest that it may be influenced by infants' native language [@Nazzi2016].
+We next examined whether this was the case.
+
+## (Insert Figure 8 about here)
+
 ```{r MPtype_cv_lang_descript}
@@
 
-To examine whether infants' native language impacts sensitivity to consonant and vowel mispronunciations, we classified infants into language families.
-Infants learning American English (*n* = `r with(lang_family, count[native_lang == "American English"])`), British English (*n* = `r with(lang_family, count[native_lang == "British English"])`), Danish (*n* = `r with(lang_family, count[native_lang == "Danish"])`), Dutch (*n* = `r with(lang_family, count[native_lang == "Dutch"])`), and German (*n* = `r with(lang_family, count[native_lang == "German"])`) were classified into the Germanic language family (*n* = `r with(family, count[lang_family == "Germanic"])`).
-Infants learning Catalan (*n* = `r with(lang_family, count[native_lang == "Catalan"])`), Spanish (*n* = `r with(lang_family, count[native_lang == "Spanish"])`), French (*n* = `r with(lang_family, count[native_lang == "French"])`), Catalan and Spanish simultaneously (i.e.
-bilinguals; *n* = `r with(lang_family, count[native_lang == "Catalan-Spanish"])`), and Swiss French (*n* = `r with(lang_family, count[native_lang == "Swiss French"])`) were classified into the Romance language family (*n* = `r with(family, count[lang_family == "Romance"])`).
-
-We assessed whether the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity was modulated by language family.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family as additional moderators.
-The moderator test was significant, `r mod_test(rma_TypeFeaturesMPC)`.
-The interaction between condition and language family was significant ($\beta$`r full_estimate(sum_eff_fam)`), suggesting that the estimate for mispronunciation sensitivity was greater for infants learning a Romance compared to Germanic language.
-However, when a model evaluating this specific interaction, without mispronunciation type, was calculated, the estimate was much smaller and not significant.
-This suggests that the interaction between condition and language family may be over-estimated.
-The three-way interaction between mispronunciation type, condition, language family was large and also significant , $\beta$`r full_estimate(sum_eff_famcv)`.
-As can be seen in Figure \@ref(fig:PlotCVEffect_Lang)a, mispronunciation sensitivity for consonants was similar for Germanic and Romance languages.
-Mispronunciation sensitivity for vowels, however, was greater for Germanic compared to Romance languages.
-
-Finally, we examined the relationship between language family and infant age and mispronunciation sensitivity to consonants and vowels.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family and age as additional moderators.
-The moderator test was significant, `r mod_test(rma_TypeFeaturesMPC_age)`, and the estimate for the four-way interaction between mispronunciation type, condition, language family, and age was small, but significant , $\beta$`r full_estimate(sum_eff2_lang_age)`.
-As can also be seen in Figure \@ref(fig:PlotCVEffect_Lang)b, for infants learning Germanic languages, sensitivity to consonant and vowel mispronunciations did not change with age.
-In contrast, infants learning Romance languages show a decrease in sensitivity to consonant mispronunciations, but an increase in sensitivity to vowel mispronunciations with age.
-
-We were unable to use Fisher's exact test to evaluate whether infants of different ages were more or less likely to be tested on consonant or vowel mispronunciations depending on their native language.
-This was due to the small sample size of infants learning Romance languages (*n* = `r with(family, count[lang_family == "Romance"])`).
-
-## (Insert Figure 9 about here)
-
-```{r PlotCVEffect_Lang}
+```{r PlotCVEffect_Lang, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language.
+Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language by age.
+For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
 
@@
   jpeg(filename = "figures/Figure_9_LangCV.jpg",
-       width = 500, height = 600, units = "px")
+       width = 500, height = 900, units = "px")
 
@@
 ```
+
+To examine whether infants' native language impacts sensitivity to consonant and vowel mispronunciations, we classified infants into language families.
+Infants learning American English (*n* = `r with(lang_family, count[native_lang == "American English"])`), British English (*n* = `r with(lang_family, count[native_lang == "British English"])`), Danish (*n* = `r with(lang_family, count[native_lang == "Danish"])`), Dutch (*n* = `r with(lang_family, count[native_lang == "Dutch"])`), and German (*n* = `r with(lang_family, count[native_lang == "German"])`) were classified into the Germanic language family (*n* = `r with(family, count[lang_family == "Germanic"])`).
+Infants learning Catalan (*n* = `r with(lang_family, count[native_lang == "Catalan"])`), Spanish (*n* = `r with(lang_family, count[native_lang == "Spanish"])`), French (*n* = `r with(lang_family, count[native_lang == "French"])`), Catalan and Spanish simultaneously (i.e.
+bilinguals; *n* = `r with(lang_family, count[native_lang == "Catalan-Spanish"])`), and Swiss French (*n* = `r with(lang_family, count[native_lang == "Swiss French"])`) were classified into the Romance language family (*n* = `r with(family, count[lang_family == "Romance"])`).
+
+We assessed whether the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity was modulated by language family.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family as additional moderators.
+The moderator test was significant, `r mod_test(rma_TypeFeaturesMPC)`.
+The interaction between condition and language family was significant ($\beta$`r full_estimate(sum_eff_fam)`), suggesting that the estimate for mispronunciation sensitivity was greater for infants learning a Romance compared to Germanic language.
+However, when a model evaluating this specific interaction, without mispronunciation type, was calculated, the estimate was much smaller and not significant.
+This suggests that the interaction between condition and language family may be over-estimated.
+The three-way interaction between mispronunciation type, condition, language family was large and also significant , $\beta$`r full_estimate(sum_eff_famcv)`.
+As can be seen in Figure \@ref(fig:PlotCVEffect_Lang)a, mispronunciation sensitivity for consonants was similar for Germanic and Romance languages.
+Mispronunciation sensitivity for vowels, however, was greater for Germanic compared to Romance languages.
+
+Finally, we examined the relationship between language family and infant age and mispronunciation sensitivity to consonants and vowels.
+We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family and age as additional moderators.
+The moderator test was significant, `r mod_test(rma_TypeFeaturesMPC_age)`, and the estimate for the four-way interaction between mispronunciation type, condition, language family, and age was small, but significant , $\beta$`r full_estimate(sum_eff2_lang_age)`.
+As can also be seen in Figure \@ref(fig:PlotCVEffect_Lang)b, for infants learning Germanic languages, sensitivity to consonant and vowel mispronunciations did not change with age.
+In contrast, infants learning Romance languages show a decrease in sensitivity to consonant mispronunciations, but an increase in sensitivity to vowel mispronunciations with age.
+
+We were unable to use Fisher's exact test to evaluate whether infants of different ages were more or less likely to be tested on consonant or vowel mispronunciations depending on their native language.
+This was due to the small sample size of infants learning Romance languages (*n* = `r with(family, count[lang_family == "Romance"])`).
+
+## (Insert Figure 9 about here)
 
@@
 Infants' sensitivity to tone mispronunciations compared to consonant or vowel mispronunciations did not differ with age.
+
+### Distractor familiarity
+
+```{r DistFam_demographics, results = "hide"}
+
+distr_info <- dat %>%
+  group_by(object_pair) %>%
+  summarize(n_exp_conditions =  n())
+
+```
+
+To assess whether familiarity with the distractor image modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced and were either paired with a familiar or unfamiliar distractor.
+A familiar distractor was used in `r with(distr_info, n_exp_conditions[object_pair == "familiar_familiar"])` experimental conditions and a unfamiliar distractor in `r with(distr_info, n_exp_conditions[object_pair == "familiar_novel"])` experimental conditions.
+
+```{r DistractorType, results= "asis"}
+
+rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
+
+d_fam <- coef(summary(rma_Distractor))[2,]
+d_fam_condit <- coef(summary(rma_Distractor))[4,]
+
+```
+
+```{r DistractorType_age, results= "asis"}
+
+# age moderator
+rma_Distractor_age <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition*age.C, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
+
+ sum_eff_age <- coef(summary(rma_Distractor_age))[8,]
+ sum_eff_2 <- coef(summary(rma_Distractor_age))[5,]
+
+ # divide into age groups
+
+ dat$age_group <- ntile(dat$mean_age_1, 4)
+
+ dist_fam_ages <- dat %>%
+  group_by(age_group, object_pair) %>%
+  summarize(n =  n())
+
+ #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
+
+ dist_fam_ages <- dist_fam_ages %>% spread(object_pair, n)
+
+ #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
+fish.test <- fisher.test(dist_fam_ages)
+
+```
+
+To understand the relationship between distractor familiarity and mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with distractor familiarity and condition as moderators.
+The moderator test was significant, `r mod_test(rma_NFeatures)`, but the effect of distractor familiarity ($\beta$`r full_estimate(d_fam)`) as well as the interaction between distractor familiarity and condition ($\beta$`r full_estimate(d_fam_condit)`) were not significant.
+The results suggest that overall, infants' familiarity with the distractor object (familiar or unfamiliar) did not impact their mispronunciation sensitivity.
+
+We next examined whether age modulates object recognition or mispronunciation sensitivity when the distractor image is familiar or unfamiliar.
+Based on previous results, we expected older infants  to have greater mispronunciation sensitivity than younger infants when the distractor was unfamiliar compared to familiar.
+To evaluate this prediction, we added age as a moderator.
+The moderator test was significant `r mod_test(rma_Distractor_age)`.
+The estimate for the  three-way-interaction between condition, distractor familiarity, and age was small and not significant ($\beta$ = `r full_estimate(sum_eff_age)`.
+These results suggest that regardless of age, mispronunciation sensitivity was similar whether the distractor image was familiar or unfamiliar.
+
+Finally, we examined whether infants are disproportionately tested in experiments with familiar or unfamiliar distractors based on their age.
+The results of Fisher's exact test were not significant, *p* `r psig(fish.test$p.value)`.
+This lack of a relationship suggests that older and younger infants are not being tested in experimental conditions that differentially employ distractor images that are familiar or unfamiliar.
 
@@
 ```
-
-We first assessed whether size of the post-naming analysis window had an impact on the overall size of the reported mispronunciation sensitivity.
-We considered data from both conditions in a joint analysis and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant (`r mod_test(rma_post_dur_MS)`).
-The estimate for the interaction between post-naming analysis window and condition was small but significant ($\beta$`r full_estimate(rma_post_dur_MS_eff)`).
-This relationship is plotted in Figure \@ref(fig:Plot-post-name-cond-age)a.
-The results suggest that the size of the post-naming analysis window significantly impacted our estimate of mispronunciation sensitivity.
-Specifically, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) was significantly greater when the post-naming analysis window was shorter.
-
-Considering that we found a significant relationship between the length of the post-naming analysis window and infant age, such that younger ages had a longer window of analysis, we next examined whether the size of the post-naming analysis window modulated the estimated size of mispronunciation sensitivity as infant age changed.
-We therefore included age as additional moderator of the previous analysis.
-The moderator test was significant (`r mod_test(rma_post_dur_AGE_MS)`).
-The estimate for the  three-way-interaction between condition, size of the post-naming analysis window, and age was small, but significant ($\beta$ `r full_estimate(rma_post_dur_AGE_MS_eff)`).
-As can be seen in Figure \@ref(fig:Plot-post-name-cond-age)b, a smaller post-naming analysis window leads to a greater increase in measured mispronunciation sensitivity with development.
-For example, when experimental conditions were analyzed with a post-naming analysis window of 2000 ms or less, mispronunciation sensitivity seems to increase with infant age.
-If the post-naming analysis window is greater than 2000 ms, however, there is no or a negative relation of mispronunciation sensitivity and age.
-In other words, all three possible developmental hypotheses might be supported depending on analysis choices made regarding the size of the post-naming analysis window.
-This is especially important, considering that our key question is how mispronunciation sensitivity changes with development.
-These results suggest that conclusions about the relationship between infant age and mispronunciation sensitivity may be mediated by the size of the post-naming analysis window.
-
-## (Insert Figure 10 about here)
 
@@
 
+We first assessed whether size of the post-naming analysis window had an impact on the overall size of the reported mispronunciation sensitivity.
+We considered data from both conditions in a joint analysis and included condition (correct pronunciation, mispronunciation) as an additional moderator.
+The moderator test was significant (`r mod_test(rma_post_dur_MS)`).
+The estimate for the interaction between post-naming analysis window and condition was small but significant ($\beta$`r full_estimate(rma_post_dur_MS_eff)`).
+This relationship is plotted in Figure \@ref(fig:Plot-post-name-cond-age)a.
+The results suggest that the size of the post-naming analysis window significantly impacted our estimate of mispronunciation sensitivity.
+Specifically, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) was significantly greater when the post-naming analysis window was shorter.
+
+Considering that we found a significant relationship between the length of the post-naming analysis window and infant age, such that younger ages had a longer window of analysis, we next examined whether the size of the post-naming analysis window modulated the estimated size of mispronunciation sensitivity as infant age changed.
+We therefore included age as additional moderator of the previous analysis.
+The moderator test was significant (`r mod_test(rma_post_dur_AGE_MS)`).
+The estimate for the  three-way-interaction between condition, size of the post-naming analysis window, and age was small, but significant ($\beta$ `r full_estimate(rma_post_dur_AGE_MS_eff)`).
+As can be seen in Figure \@ref(fig:Plot-post-name-cond-age)b, a smaller post-naming analysis window leads to a greater increase in measured mispronunciation sensitivity with development.
+For example, when experimental conditions were analyzed with a post-naming analysis window of 2000 ms or less, mispronunciation sensitivity seems to increase with infant age.
+If the post-naming analysis window is greater than 2000 ms, however, there is no or a negative relation of mispronunciation sensitivity and age.
+In other words, all three possible developmental hypotheses might be supported depending on analysis choices made regarding the size of the post-naming analysis window.
+This is especially important, considering that our key question is how mispronunciation sensitivity changes with development.
+These results suggest that conclusions about the relationship between infant age and mispronunciation sensitivity may be mediated by the size of the post-naming analysis window.
+
+## (Insert Figure 10 about here)
+
 #### Offset time after target naming
@@
 Why did we have so few samples for an analysis on vocabulary size to begin with?
-Despite the theoretical implications, fewer than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total; see also Figure \@ref(fig:Vocab-describe1)).
+Despite the theoretical implications, fewer than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total; see also Figure \@ref(fig:Vocabdescribe1)).
 There are more mispronunciation sensitivity studies published every year, perhaps due to the increased use of eye-trackers, which reduce the need for offline coding and thus make data collection much more efficient, but this has not translated to an increasing number of mispronunciation sensitivity studies also reporting vocabulary scores.
@@
 Additionally, several of these moderators include manipulations that make mispronunciation detection more or less difficult for the infant.
+As a result, the size of the mispronunciation sensitivity effect may be influenced by the task demands placed on the infant, potentially masking developmental effects.
 Considering this, we also evaluated whether the investigation of each of these manipulations was distributed evenly across infant ages, where an uneven distribution may have subsequently heightened or dampened our estimate of developmental change.
@@
 Although words differ from one another on many acoustic dimensions, changes in phonemes, as measured by phonological features, signal changes in meaning.
-Several studies have found that infants show graded sensitivity to both consonant (Bernier & White, 2017; Tamasi, 2016; White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes.
+Several studies have found that infants show graded sensitivity to both consonant [@Bernier2017; @Tamasi2016; @White2008] and vowel [@Mani2011] feature changes.
 This was captured in our meta-analysis, which also showed that sensitivity to mispronunciations increased linearly with the number of phonological features changed.
@@
 Yet, this graded sensitivity appears to be stable across infant ages, although our analysis was likely underpowered.
-At least one study suggests that this graded sensitivity develops with age, but this was the only study to examine more than one age (Mani & Plunkett, 2011).
-All other studies only test one age (Tamasi, White & Morgan, 2008; Bernier & White, 2017).
+At least one study suggests that this graded sensitivity develops with age, but this was the only study to examine more than one age [@Mani2011].
+All other studies only test one age [@Bernier2017; @Tamasi2016; @White2008].
 With more studies investigating graded sensitivity at multiple ages in infancy, we would achieve a better estimate of whether this is a stable or developing ability.
 
-Although some theories place greater importance on onset position for word recognition and decreasing importance for phonemes in subsequent positions (i.e.
-COHORT; Marslen-Wilson & Zwitserlood, 1989), other theories suggest that lexical access can still recover from onset and medial mispronunciations (i.e.
-TRACE; McClelland & Elman, 1986).
+Although some theories place greater importance on onset position for word recognition and decreasing importance for phonemes in subsequent positions [i.e.
+COHORT; @Marslen-Wilson1989], other theories suggest that lexical access can still recover from onset and medial mispronunciations [i.e.
+TRACE; @McClelland1986].
 Although many studies have examined mispronunciations on multiple positions, only a handful have directly compared sensitivity between different positions.
-These studies find that position of the mispronunciation does not modulate sensitivity (Swingley, 2009; Zesiger & Jöhr, 2011).
+These studies find that position of the mispronunciation does not modulate sensitivity [@Swingley2009; @Zesiger2012].
 This stands in contrast to the findings of our meta-analysis, which showed that for each subsequent position in the word that is changed, from onset to medial and medial to coda, the effect size estimate for looks to the target decreases by `r r2(linear_position)`; infants are more sensitive to changes in the sounds of familiar words when they occur in an earlier position as opposed to a late position.
@@
 One potential explanation for the discrepancy between the results of individual studies and that of the current meta-analysis is the difference in how analysis timing is considered depending on the position of the mispronunciation.
-For example, Swingley (2009) adjusted the offset time from 367 ms for onset mispronunciations to 1133 for coda mispronunciations, to ensure that infants have a similar amount of time to respond to the mispronunciation, regardless of position.
-In contrast, if an experiment compares different kinds of medial mispronunciations, as in Mani & Plunkett (2011), it is not necessary to adjust offset time because the mispronunciations have a similar onset time.
-The length of the post-naming analysis window does impact mispronunciation sensitivity, as we discuss below, and by comparing effect sizes for different mispronuciation positions where position timing was not considered, we may have put mispronunciations that occur later in the word (i.e.
-medial and coda mispronunciations) at a disadvantage relative to onset mispronunciations.
+For example, @Swingley2009 adjusted the offset time from 367 ms for onset mispronunciations to 1133 for coda mispronunciations, to ensure that infants have a similar amount of time to respond to the mispronunciation, regardless of position.
+In contrast, if an experiment compares different kinds of medial mispronunciations, as in @Mani2011, it is not necessary to adjust offset time because the mispronunciations have a similar onset time.
+The length of the post-naming analysis window does impact mispronunciation sensitivity, as we discuss below, and by comparing effect sizes for different mispronuciation positions where position timing was not considered, mispronunciations that occur later in the word (i.e.
+medial and coda mispronunciations) may be at a disadvantage relative to onset mispronunciations.
 These issues can be addressed with the addition of more experiments that directly compare sensitivity to mispronunciations of different positions, as well as the use of analyses that account for differences in timing of sensitivity.
@@
 No studies have directly compared mispronunciation sensitivity for familiar and unfamiliar distractors, but these results suggest that this manipulation alone makes little difference in the design of the experiment.
-It remains possible that distractor familiarity interacts with other types of manipulations, such as number of phonological features changed, heightening the ability of the experimenter to detect more sublte differences in mispronunciation sensitivity (i.e.
-White & Morgan, 2008), but our meta-analysis is underpowered to detect these effects.
-
-Despite the proposal that infants should be more sensitive to consonant compared to vowel mispronunciations (Nazzi, Poltrock, & Von Holzen, 2016), we found no difference in sensitivity to consonant and vowel mispronunciations.
+It remains possible that distractor familiarity interacts with other types of manipulations, such as number of phonological features changed, heightening the ability of the experimenter to detect more sublte differences in mispronunciation sensitivity [e.g.
+@White2008], but our meta-analysis is underpowered to detect these effects.
+
+Despite the proposal that infants should be more sensitive to consonant compared to vowel mispronunciations [@Nazzi2016], we found no difference in sensitivity to consonant and vowel mispronunciations.
 But, a more nuanced picture was revealed regarding differences between consonant and vowel mispronunciations when further moderators were introduced.
@@
 Sensitivity to vowel mispronunciations is modulated both by development and by native language, whereas sensitivity to consonant mispronunciations is fairly similar across age and native language.
-This pattern of results support previous experimental evidence that sensitivity to consonants and vowels have a different developmental trajectory and that this difference also depends on whether the infant is learning a Romance (French, Italian) or Germanic (British English, Danish) native language (Nazzi et al., 2016).
+This pattern of results support previous experimental evidence that sensitivity to consonants and vowels have a different developmental trajectory and that this difference also depends on whether the infant is learning a Romance (French, Italian) or Germanic (British English, Danish) native language [@Nazzi2016].
 Additionally, our exploratory analysis of tone mispronunciations revealed no difference in sensitivity in comparison to vowel and consonant mispronunciations, but our ability to detect differences may have been underpowered, as only `r with(CV_info, n_exp_conditions[type_feature == "tone"])` experimental conditions included tone mispronunciations.
@@
 As a result, any developmental differences would be erased, hidden by task differences in the experiments that older and younger infants participated in.
+This argument is supported by the PRIMIR Framework (@Curtin2011; @Curtin2007; @Werker2005) , which argues that infants' ability to access the phonetic detail of familiar words is governed by the difficulty of their current task.
 Further support comes from evidence that sensitivity to mispronunciations when the target-distractor pair overlapped on the onset phoneme increased with age.
@@
 Indeed, a majority of studies used an offset time between 360 and 370 ms, which follows the "best guess" of @Swingley2000 for the amount of time needed for infants to initiate eye movements in response to a spoken target word.
-Without knowledge of the base reaction time in a given population of infants, use of this best guess offset time reduces the number of free parameters.
+Without knowledge of the base reaction time in a given population of infants, use of this best guess offset time reduces the number of free parameters used by researchers.
 In contrast, we found a negative correlation between infant age and the length of the post-naming analysis window, and that the length of the analysis window moderated mispronunciation sensitivity, such increasing the length of the analysis windows decreases the size of mispronunciation sensitivity.
@@
 Sharing data (Open Data) can allow others to re-analyze existing datasets to both examine the impact of analysis decisions and cumulatively analyze different datasets in the same way.
-Considering the issue of analysis time window, experimenters can opt to analyze the time course as a whole, instead of aggregating the proportion of target looking behavior over the entire trial.
+Considering the specific issue of analysis time window, experimenters can opt to analyze the time course as a whole, instead of aggregating the proportion of target looking behavior over the entire trial.
 This allows for a more detailed assessment of infants' fixations over time and reduces the need to reduce the post-naming analysis window.
@@
 A meta-analysis is a first step in improving experiment planning by providing an estimate of the population effect and its variance, which is directly related to the sample needed to achieve satisfactory power in the null hypothesis significance testing framework.
-Failing to take effect sizes into account can both lead to underpowered research and to testing too many participants, both consequences are undesirable for a number of reasons that have been discussed in depth elsewhere.
+Failing to take effect sizes into account can lead to either underpowered research or testing too many participants, both consequences are undesirable for a number of reasons that have been discussed in depth elsewhere.
 We will just briefly mention two that we consider most salient for theory building: Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature [@Bergmann2018].
@@
 However, they are more likely to accept correct pronunciations, which indicates sensitivity to mispronunciations in familiar words.
-Despite the predictions of theories of infant phono-lexical development, this sensitivity was not modulated by infant age or vocabulary.
-This suggests that from a young age on, before the vocabulary explosion, infants’ word representations may be already phonologically well-specified.
+This sensitivity was not modulated by infant age or vocabulary, suggesting that from a young age on, before the vocabulary explosion, infants’ word representations may be already phonologically well-specified.
 We recommend future theoretical frameworks take this evidence into account.
-
-One unique aspect of this meta-analysis was our examination of
-
-One unique aspect of this meta-analysis was that we could see how these things change with development.
-However, probably underpowered.
-Yet, these were the differences we found and this is what they mean
-
-Interestingly, there were several manipulations that varied the age on which they were tested.
-These are those things.
-We think it may have impacted our overall estimate of developmental change in this way.
+Our meta-analysis was also able to confirm different findings in the literature, including the role of mispronunciation size, mispronunciation position, and the role of the native langauge in sensitivity to mispronunciation type (consonant vs.
+vowel).
+Furthermore, evidence of an interaction between task demands (phonological overlap between target-distractor pairs) and infant age may partially explain the lack of developmental change in mispronunciation sensitivity.
 

### 2020-01-24 MPMetaAnalysis_exploratory.Rmd
24.1.2020 editing and cutting down words

--- 2019-05-24 VonHolzenBergmann_MPMetaAnalysis.Rmd
@@
 library(tidyverse)
+library(gtools)
 
@@
 
-# Introduction
-
-  At the turn of the millenium, infant language acquisition researchers had established that during their first two years of life, infants are sensitive to changes in the phonetic detail of newly segmented words [@Jusczyk1995] and learned minimal pairs [@Stager1997].
-Furthermore, when presented with familiar image pairs, children fixate on the referent of a spoken label [@Fernald1998; @Tincoff1999].
-@Swingley2000 were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English saw pairs of images (e.g.
-a baby and a dog) and their eye movements to each image were recorded.
-On "correct" trials, children heard the correct label for one of the images (e.g.
-"baby").
-On "mispronounced" trials, children heard a mispronounced label of one of the images (e.g.
-"vaby").
-The mean proportion of fixations to the target image (here: a baby) was calculated separately for both correct and mispronounced trials by dividing the target looking time by the sum of total looking time to both target and a distractor (proportion of target looking or PTL).
-Mean fixations in correct trials were significantly greater than in mispronounced trials, and in both conditions looks to the target were significantly greater than chance.
-We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance in each condition as *object identification*.
-@Swingley2000 concluded that already before the second birthday, children represent words with sufficient detail to be sensitive to mispronunciations.
-
-  In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts  that differentiate words in a given language (e.g.
-cat-hat).
-The study of @Swingley2000 as well as subsequent studies examining mispronunciation sensitivity probe this latter distinction.
-Phonological contrasts relevant for the infant language-learner are determined by their native language.
-For an infant learning Catalan, the vowel contrast /e/-/E/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish.
-These contrasts are therefore not inate, but must be learned.
-In this meta-analysis, we focus on infants' developing ability to correctly apply the phonological distinctions for their native language during word recognition.
-By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; for a notable exception).
-Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.
-
-  Research following the seminal study by @Swingley2000 has extended mispronunciation sensitivity to infants as young as 8 to 10 months [@Bergelson2017], indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations.
-Regarding the change in mispronunciation sensitivity over development, however, only about half of studies have compared more than one age group on the same mispronunciation task (see Table 1).
-Across single studies all possible patterns of development lined out above have been reported, making the current meta-analysis very informative.
-
-Several studies have found evidence for *greater* mispronunciation sensitivity as children develop.
-More precisely, the difference in target looking for correct and mispronounced trials is reported to be smaller in younger infants and grows as infants develop.
-@Mani2007 tested 15-, 18-, and 24-month-olds learning British English; although all three groups were sensitive to mispronunciations, 15-month-olds showed a less robust sensitivity.
-An increase in sensitivity to mispronunciations has also been found from 20 to 24 months [@vanderFeest2015] and 15 to 18 months [@Altvater2014] in Dutch infants, as well as German infants from 22 to 25 months [@Altvater2010].
-Furthermore, @vanderFeest2015 found that sensitivity to specific kinds of mispronunciations develop at different ages depending on language infants are learning.
-In other words, the native language constraints which *kinds* of mispronunciations infants are sensitive to first, and that as infants develop, they become sensitive to other mispronunciations.
-
-Other studies have found no difference in mispronunciation sensitivity at different ages.
-For example, @Swingley2000 tested infants over a wide age range of 5 months (18 to 23 months).
-They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation sensitivity) did not.
-This suggests that as children develop, they are more likely to look at the target in the presence of a correct or mispronounced label, but that the difference between looks elicited by the two conditions does not change.
-A similar response pattern has been found for British English learning infants aged between 18 and 24 months [@Bailey2002] as well as younger French-learning infants at 12 and 17 months [@Zesiger2012].
-
-  One study has found evidence for infants to become *less* sensitive to mispronunciations as they develop.
-@Mani2011 presented 18- and 24-month-olds with mispronunciations varying in the number of phonological features changed (e.g., changing an p into a b, a 1-feature change, versus changing a p into a g, a 2-feature change).
-18-month-olds were sensitive to mispronunciations, regardless of the number of features changed.
-24-month-olds, in contrast, fixated the target image equally for both correct and 1-feature mispronounced trials, although they were sensitive to larger mispronunciations.
-In other words, for 1-feature mispronunciations at least, sensitivity decreased from 18 to 24 months.
-
-  Why would mispronunciation sensitivity change as infants develop?
-Typically, a change in mispronunciation sensitivity is thought to occur along with an increase in vocabulary size, particularly with the vocabulary spurt at about 18 months.
-As infants learn more words, their focus shifts to the relevant phonetic dimensions needed for word recognition.
-For example, an infant who knows a handful of words with few phonological neighbors would not need to have fully specified phonological representations in order to differentiate between these words.
-As more phonologically similar words are learned, however, the need for fully detailed phonological representations increases [@CharlesLuce1995].
-Furthermore, a growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the detail of their phonological representation [@Barton1980].
-If vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship between vocabulary size and mispronunciation sensitivity.
-
-  Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship [@Swingley2000; @Swingley2002; @Swingley2009; @Zesiger2012; @Mani2008; @Bailey2002; @Mani2007; @Ballem2005].
-One notable exception comes from @Mani2010kepstups.
-Here, 12-month-old infants were divided into a low and high vocabulary group based on median vocabulary size.
-High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations.
-Taken together, there is very little evidence for a role of vocabulary size in mispronunciation sensitivity.
-In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to better understand the variation in experimental results.
-
-  Although all mispronunciation sensitivity studies are generally interested in the the phonological detail with which infants represent familiar words, many studies pose more nuanced questions.
-These questions concern issues at the intersection of phonological development and lexical processing and often result in manipulations of the stimuli and experimental procedure.
-These manipulations may impact our overall estimate of the effect size of mispronunciation sensitivity.
-Next to the core investigation of the shape of development of infants' mispronunciation sensitivity, we take the opportunity of a systematic aggregation of data to address these questions and the influence of these manipulations on infants' ability to detect mispronunciations and how this may change with development.
-
-  In designing their mispronunciation stimuli, Swingley and Aslin (2000) chose consonant mispronunciations that were likely to confuse adults (Miller & Nicely, 1955).
-Subsequent research has settled on systematically modulating phonemic features to achieve mispronunciations of familiar words.
-By utilizing mispronunciations consisting of phonemic changes, these experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level (i.e.
-1-feature, 2-features, 3-features, etc.).
-The importance of controlling for the degree of phonological mismatch, as measured by number of features changed, is further highlighted by studies that find graded sensitivity to both consonant (Bernier & White, 2017; Tamasi, 2016; White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes.
-The greater the number of features changed, or *mispronunciation size*, the easier it may be to detect a mispronunciation, whereas more similar mispronunciations may be more difficult to detect.
-
-  Although most research examining sensitivity to mispronunciations follows a similar design, there are some notable differences.
-For example, Swingley and Aslin (2000) presented infants with pairs of familiar images, one serving as the labeled target and one as the unlabeled distractor.
-In contrast, White and Morgan (2008; see also Mani & Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects.
-By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied (Halberda, 2003; Markman, Wasow, & Hansen, 2003).
-Infants ages 24 and 30 months associate a novel label with an unfamiliar object, although only 30-month-olds retained this label-object pairing (Bion, Borovsky, and Fernald, 2013).
-In contrast, 18-month-olds did not learn to associate a novel label with an unfamiliar object, providing evidence that this ability is developing from 18 to 30 months.
-We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar.
-Although mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared, the baseline preference for familiar compared to novel stimuli is also thought to change as infants develop (Hunter & Ames, 1988).
-Furthermore, young children have been found to look longer at objects for which they know the name, compared to objects of an unknown name (Schafer & Plukett, 1998).
-In other words, in absentia of a label, infants may be more or less likely to fixate on an unfamiliar object.
-To account for inherent preferences to the target or distractor image, mispronunciation experiments typically compare the increase in fixations to the target image from a silent baseline to post-labeling or present the same yoked pairs of target and distractor images in in both a correct and mispronounced labelling context.
-Considering this evidence, we may expect that in older, but not younger, children, the presence of an unfamiliar distractor may lead to greater mispronunciation sensitivity than in the presence of a familiar distractor.
-
-  Furthermore, when presenting infants with a familiar distractor image, some studies control the *phonological overlap between target and distractor labels*.
-For example, when examining sensitivity to a mispronunciation of the target word "dog", the vowel mispronunciation "dag" would be paired with a distractor image that shares onset overlap, such as "duck".
-This ensures that infants can not use the onset of the word to differentiate between the target and distractor images (Fernald, Swingley, & Pinto, 2001).
-Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.
-The influence of distractor overlap also depends on the *position of mispronunciation* in the word, which can be at word onset, medial, or final positions.
-Models of spoken word processing place more or less importance on the position of a phoneme in a word.
-The COHORT model (Marslen-Wilson & Zwitserlood, 1989) describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.
-In contrast, the TRACE model (McClelland & Elman, 1986) describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.
-
-  TRACE has also been used to model infants' sensitivity to mispronunciation position (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth.
-In early language acquisition, infants typically know more consonant compared to vowel onset words.
-When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations.
-The prevalence of consonant onset words may contribute to the finding that consonants carry more weight in lexical processing (C-bias; see Nazzi, Poltrock, & Von Holzen, 2016 for a recent review).
-In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations.
-Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels.
-English-learning 12-, 15-, 18-, and 24-month-olds (Mani & Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds (Hojen et al., unpublished) demonstrate similar sensitivity to consonant and vowel mispronunciations.
-One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations (Swingley, 2016).
-The English-learning infants tested by Swingley were older than previous studies (mean age 28 months).
-In word learning, the C-bias has been found to develop later in English learning infants (Floccia, Nazzi, Delle Luche, Poltrock, & Goslin, 2014; Nazzi, Floccia, Moquet, & Butler, 2009).
-In the current meta-analysis, we attempt to synthesize studies examining sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence (Floccia et al., 2014; Keidel et al., 2007; Nazzi et al., 2016).
-We further examine the impact of language family on mispronunciation sensitivity to consonants and vowels, as C-bias emergence has been found to have a different developmental trajectory for Romance (French, Italian) compared to Germanic (British English, Danish) languages (Nazzi et al., 2016).
-
-  Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (see Table 1).
-Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare.
-Although we do not explicitly compare overall mispronunciation sensitivity by language (although see previous paragraph for rationale to test by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.
-
-In sum, the studies we have reviewed begin to paint a picture of the development of infants' mispronunciation sensitivity.
-Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding of the big picture of early language development.
-Meta-analyses can provide unique insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and of their mispronunciations sensitivity.
-Because we aggregate data over various age groups, this meta-analysis can also investigate the role of maturation by assessing the impact of age and vocabulary size.
-We also make hands-on recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses [@Bergmann2018].
-
-# Methods
-
-The present meta-analysis was conducted with maximal transparency and reproducibility in mind.
-To this end, we provide all data and analysis scripts on the supplementary website (https://osf.io/rvbjs/) and open our meta-analysis up for updates [@Tsuji2014].
-The most recent version is available via the website and the interactive platform MetaLab [https://metalab.stanford.edu; @Bergmann2018].
-Since the present paper was written with embedded analysis scripts in R [@R] using the papaja package [@papaja] in R Markdown [@RMarkdown], it is always possible to re-analyze an updated dataset.
-In addition, we followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials [@Moher2009].
-Figure \@ref(fig:PRISMA-image) plots our PRISMA flowchart illustrating the paper selection procedure.
-
-## (Insert Figure 1 about here)
-
-```{r PRISMA-image, echo= FALSE, fig.cap="A PRISMA flowchart illustrating the selection procedure used to include studies in the current meta-analysis."}
-
-knitr::include_graphics("figures/Figure_1_PRISMA_MA_Mispronunciation.png")
-
-# ! [Figure X. PRISMA Flowchart.] (Users/KatesOld/Documents/R_Git/figures/PRISMA_MA_Mispronunciation.png)
-
-```
-
-## Study Selection
-
-```{r SummaryTable, results = "asis"}
-
-dat_st <- descriptive_dat
-
-dat_st$type_feature <- as.character(dat_st$type_feature)
-dat_st$mispron_location <- as.character(dat_st$mispron_location)
-dat_st$distractor_overlap <- as.character(dat_st$distractor_overlap)
-
-dat_st$object_pair <- ifelse(dat_st$object_pair == "familiar_familiar", "fam", "unfam")
-
-dat_st$distractor_overlap <- ifelse(dat_st$distractor_overlap == "no", "none", dat_st$distractor_overlap)
-
-Sum_table <- dat_st %>%
-      group_by(short_cite) %>% 
-      summarise(Publication = unique(publication_status),
-        Ages_Tested_months = paste(unique(trunc(mean_age_1/30.44)), collapse=', '),
-                Vocabulary = ifelse(all(is.na(r_comprehension)) & all(is.na(r_production)), "None",
-                                ifelse(!all(is.na(r_comprehension)) & !all(is.na(r_production)), "Comp/Prod",
-                                       ifelse(!all(is.na(r_comprehension)) & all(is.na(r_production)), "Comp", "Prod"))),
-        distractor = paste(unique(object_pair), collapse =', '),
-        dist_overlap = paste(unique(distractor_overlap), collapse =', '),
-        number_features = paste(unique(n_feature), collapse=', '),
-        misp_posit = paste(unique(mispron_location), collapse =', '),
-        misp_type = paste(unique(type_feature), collapse =', '),
-        Effect_sizes_n = n())
-
-# can't chain these together, since it only checks each line once
-
-Sum_table$misp_posit <- ifelse(Sum_table$misp_posit == "NA", "unspec", Sum_table$misp_posit)
-Sum_table$misp_posit <- ifelse(grepl("onset", Sum_table$misp_posit), gsub("onset", "O", Sum_table$misp_posit), Sum_table$misp_posit)
-Sum_table$misp_posit <- ifelse(grepl("medial", Sum_table$misp_posit), gsub("medial", "M", Sum_table$misp_posit), Sum_table$misp_posit)
-Sum_table$misp_posit <- ifelse(grepl("coda", Sum_table$misp_posit), gsub("coda", "C", Sum_table$misp_posit), Sum_table$misp_posit)
-
-Sum_table$dist_overlap <- ifelse(grepl("onset", Sum_table$dist_overlap), gsub("onset", "O", Sum_table$dist_overlap), Sum_table$dist_overlap)
-Sum_table$dist_overlap <- ifelse(grepl("medial", Sum_table$dist_overlap), gsub("medial", "M", Sum_table$dist_overlap), Sum_table$dist_overlap)
-Sum_table$dist_overlap <- ifelse(grepl("coda", Sum_table$dist_overlap), gsub("coda", "C", Sum_table$dist_overlap), Sum_table$dist_overlap)
-
-Sum_table$number_features <- ifelse(grepl("0, ",Sum_table$number_features), gsub("0, ", "", Sum_table$number_features), 
-                                           ifelse(grepl(", 0",Sum_table$number_features), gsub(", 0", "", Sum_table$number_features), Sum_table$number_features))
-Sum_table$number_features <- ifelse(Sum_table$number_features == "NA", "unspec", Sum_table$number_features)
-
-Sum_table$number_features <- ifelse(grepl("1_2_3,", Sum_table$number_features), gsub("1_2_3", "1-3", Sum_table$number_features), Sum_table$number_features)
-Sum_table$number_features <- ifelse(grepl("1_2,", Sum_table$number_features), gsub("1_2", "1-2", Sum_table$number_features), Sum_table$number_features)
-Sum_table$number_features <- ifelse(grepl("2_3", Sum_table$number_features), gsub("2_3", "2-3", Sum_table$number_features), Sum_table$number_features)
-
-Sum_table$misp_type <- ifelse(grepl("consonant_and_vowel", Sum_table$misp_type), gsub("consonant_and_vowel", "C/V", Sum_table$misp_type),
-                              ifelse(grepl("consonant_vowel_tone", Sum_table$misp_type), gsub("consonant_vowel_tone", "C/V/T", Sum_table$misp_type) , Sum_table$misp_type))
-
-Sum_table$misp_type <- ifelse(grepl("consonant", Sum_table$misp_type), gsub("consonant", "C", Sum_table$misp_type), Sum_table$misp_type)
-
-Sum_table$misp_type <- ifelse(grepl("vowel", Sum_table$misp_type), gsub("vowel", "V", Sum_table$misp_type), Sum_table$misp_type)
-
-Sum_table$misp_type <- ifelse(grepl("tone", Sum_table$misp_type), gsub("tone", "T", Sum_table$misp_type), Sum_table$misp_type)
-
-#kable(Sum_table, col.names = c("Paper", "Publication format", "Age", "Vocabulary", "N Effect Sizes"))
-
-apa_table(Sum_table, col.names = c("Paper", "Format", "Age", "Vocabulary", "Familiarity", "Target Overlap", "Size", "Position", "Type", "N Effect Sizes"), caption = "Summary of all studies.
-Age: truncation of mean age reported in the paper.
-Vocabulary: Comp = comprehension, Prod = production.
-Distractor Familiarity: Fam = Familiar Distractor, Unfam = Unfamiliar Distractor.
-Distractor Target Overlap: position of overlap between target and distractor; O = onset, M = medial, C = coda.
-Mispronunciation Size: number of features changed; commas indicate when sizes were compared separately (e.g.
-1, 2, 3), dashes indicate the range of sizes were aggregated (e.g.
-1-3).
-Mispronunciation Position: O = onset, M = medial, C = coda.
-Mispronunciation Type: C = consonant, V = vowel, T = tone.
-For both Mispronunciation Position and Type, a slash separator indicates that is was tested but a distinction was not made in the stimuli.
-For all categories, unspec.
-indicates that the value was unspecified in the paper", landscape = TRUE, font_size = "scriptsize", col_spanners = list(`Distractor` = c(5, 6), `Mispronunciation` = c(7, 9)))
-
-```
-
-We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list.
-This process yielded 110 items.
-We then used the google scholar search engine to search for papers citing the original @Swingley2000 publication.
-This search was conducted on 22 September, 2017 and yielded 288 results.
-We removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech.
-The final sample (n = *`r length(unique(descriptive_dat$short_cite))`*) consisted of `r with(descriptive_dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "dissertation"]))` theses, and `r with(descriptive_dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports.
-We will refer to these items collectively as papers.
-Table 1 provides an overview of all papers included in the present meta-analysis.
-
-## (Insert Table 1 about here)
-
-```{r DescriptivesPubtype}
-
-pub_info <- dat %>%
-  group_by(publication_status) %>%
-  summarize(n_unique = n_distinct(short_cite), count = n())
-
-#kable(pub_info, col.names = c("Publication Type", "# Items", "# Effect Sizes"))
-
-```
-
-## Data Entry
-
-The `r length(unique(descriptive_dat$short_cite))` papers we identified as relevant were then coded with as much consistently reported detail as possible [@Tsuji2014; @Bergmann2018].
-For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results.
-For the planned analyses to evaluate the development of mispronunciation sensitivity and modulating factors, we focus on the following characteristics:
-
-1 Condition: Were words mispronounced or not;  
-2 Mean age reported per group of infants, in days;  
-3 Vocabulary size, measured by a standardized questionnaire or list;    
-4 Size of mispronunciation, measured in features changed;  
-5 Distractor familiarity: familiar or unfamiliar;  
-6 Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;  
-7 Position of mispronunciation: onset, medial, offset, or mixed;  
-8 Type of mispronunciation: consonant, vowel, or both.
-
-A detailed explanation for moderating factors 3-8 can be found in their respective sections in the Results.
-We separated conditions according to whether or not the target word was mispronounced to be able to investigate infants' looking to the target picture as well as their mispronunciation sensitivity, which is the difference between looks to the target in correct and mispronounced trials.
-When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  [e.g., consonant versus vowel mispronunciations; @Mani2007].
-The fact that the same infants contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section).
-We will call each row a record; in total there were `r nrow(descriptive_dat)` records in our data.
-
-## Data analysis
-
-```{r DescriptivesComparison, echo = FALSE}
-db_ET_correct$within_measure_descriptive <- ifelse(db_ET_correct$within_measure == "post",
- "post-naming phase compared with chance (=50%)",
-ifelse(db_ET_correct$within_measure == "pre_post", "post-naming compared to pre-naming phase", "post-pre difference score compared with chance (=0)"))
-
-comparison_info <- db_ET_correct %>%
-  group_by(within_measure) %>%
-  summarize(n_unique = n_distinct(short_cite), count = n())
-
-#kable(comparison_info, col.names = c("Type of comparison", "# Papers", "# Effect Size"))
-#table(db_ET_MP$es_method)
-```
-
-```{r DescriptivesES}
-#how did we calculate effect sizes?
-
-es_info <- descriptive_dat %>%
-  filter(!is.na(d_calc)) %>%
-  group_by(es_method) %>%
-  summarize(n_unique = n_distinct(short_cite), count = n())
-
-corr_info <- descriptive_dat %>%
-  filter(!is.na(d_calc)) %>%
-  group_by(imputed_corr) %>%
-  summarize(n_unique = n_distinct(short_cite), count = n())
-
-```
-
-Effect sizes are reported for infants' looks to target pictures after hearing a correctly pronounced or a mispronounced label (object identification) as well as the difference between effect sizes for correct and mispronounced trials (i.e.
-mispronunciation sensitivity).
-The effect size reported in the present paper is based on comparison of means, standardized by their variance.
-The most well-known effect size from this group is Cohen's *d* [@cohen].
-To correct for the small sample sizes common in infant research, however, we used Hedges' *g* instead of Cohen's *d* [@Hedges1981; @morris2002combining].
-
-We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, sum(count[es_method == "group_means_one" | es_method == "group_means_two"]))` records from `r with(es_info, sum(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))` papers) or reported t-values (*n* = `r with(es_info, sum(count[es_method == "t_one" | es_method == "t_two"]))` records from `r with(es_info, sum(n_unique[es_method == "t_one" | es_method == "t_two"]))` papers).
-Two papers reported raw means and standard deviations for some experimental conditions and just t-values for the remaining experimental conditions [@Swingley2016; @Altvater2014].
-Raw means and standard deviations were extracted from figures for `r with(descriptive_dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers.
-In a within-participant design, when two means are compared (i.e.
-looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance.
-Upon request we were provided with correlation values for one paper [@Altvater2010]; we were able to compute correlations using means, standard deviations, and t-values for `r with(corr_info, n_unique[imputed_corr == "no"])` papers [following @Csibra2016; see also @Rabagliati2018].
-Correlations were imputed for the remaining papers [see @Black2017 for the same procedure].
-For two papers, we could not derive any effect size [@Ballem2005; @Renner2017], and for a third paper, we do not have sufficient information in one record to compute effect sizes [@Skoruppa2013].
-We compute a total of `r sum(dat$is_mp == 0)+n_outlier_correct` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)+n_outlier_MP` for mispronunciations.
-Following standard meta-analytic practice, we remove outliers, i.e.
-effect sizes more than 3 standard deviations from the respective mean effect size.
-This leads to the exclusion of `r n_outlier_correct` records for correct pronunciations and `r n_outlier_MP` records for mispronunciations.
-
-To take into account the fact that the same infants contributed to multiple datapoints, we analyze our results in a multilevel approach using the R [@R] package metafor [@metafor].
-We use a multilevel random effects model which estimates the mean and variance of effect sizes sampled from an assumed distribution of effect sizes.
-In the random effect structure we take into account the shared variance of effect sizes drawn from the same paper, and nested therein that the same infants might contribute to multiple effect sizes.
-
-Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement.
-PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images.
-Across papers the baseline comparison varied; since other options were not available to us, we used the baseline reported by the authors of each paper.
-Most papers (*n* = `r with(comparison_info, count[within_measure == "pre_post_naming_effect"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post_naming_effect"])` papers) subtracted the PTL score for a pre-naming baseline phase from the PTL score for a post-naming phase and report a difference score.
-
-Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(comparison_info, count[within_measure == "pre_post"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post"])` papers), thus reporting two variables, or compared post-naming PTL with a chance level of 50% (*n* = `r with(comparison_info, count[within_measure == "post"])` records from `r with(comparison_info, n_unique[within_measure == "post"])` papers).
-For all these comparisons, positive values (either as reported or after subtraction of chance level or a pre-naming baseline PTL) indicate target looks towards the target object after hearing the label, i.e.
-a recognition effect.
-Standardized effect sizes based on mean differences, as calculated here, preserve the sign.
-Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more looks to the target.
-
-## Publication Bias
-
-In the psychological sciences, there is a documented reluctance to publish null results.
-As a result, significant results tend to be over-reported and thus might be over-represented in our meta-analyses [see @Ferguson2012].
-To examine whether this is also the case in the mispronunciation sensitivity literature, which would bias the data analyzed in this meta-analysis, we conducted two tests.
-We first examined whether effect sizes are distributed as expected based on sampling error using the rank correlation test of funnel plot asymmetry with the R [@R] package metafor [@metafor].
-Effect sizes with low variance were expected to fall closer to the estimated mean, while effect sizes with high variance should show an increased, evenly-distributed spread around the estimated mean.
-Publication bias would lead to an uneven spread.
-
-Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app [v4.0, http://p-curve.com; @pcurve].
-This p-curve tests for evidential value by examining whether the p-values follow the expected distribution of a right skew in case the alternative hypothesis is true, versus a flat distribution that speaks for no effect being present in the population and all observed significant effects being spurious.
-
-Responses to correctly pronounced and mispronounced labels were predicted to show different patterns of looking behavior.
-In other words, there is an expectation that infants should look to the target when hearing a correct pronunciation, but studies vary in their report of significant looks to the target when hearing a mispronounced label (i.e.
-there might be no effect present in the population); as a result, we conducted these two analyses to assess publication bias separately for both conditions.
-
-## Meta-analysis
-
-The models reported here are multilevel random-effects models of variance-weighted effect sizes, which we computed with the R [@R] package metafor [@metafor].
-To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we first introduced age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44) as a moderator to our main model.
-Second, we analyzed the correlation between reported vocabulary size and mispronunciation sensitivity using the R [@R] package meta [@meta].
-Finally, for a subsequent exploratory investigation of experimental characteristics, we introduced each characteristic as a moderator (more detail below).
-
-# Results
-
-## Publication Bias
-
-```{r FunnelPlotAsymm_correct}
-
-rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ same_infant_calc | short_cite)
-# Publication bias can become visible in funnel plot asymmetry. 
-# Metafor comes with several options to check this, I chose ranktest and regtest
-# correct object identification
-rmac <- ranktest(rma_correct)
-#rmac
-
-```
-
-```{r FunnelPlotAsymm_misp}
-
-rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ same_infant_calc | short_cite)
-
-# mispronounced object identification
-rmam <- ranktest(rma_MP)
-#rmam
-```
-
-Figure \@ref(fig:FunnelCombo) shows the funnel plots for both correct pronunciations and mispronunciations [code adapted from @Sakaluk2016].
-Funnel plot asymmetry was significant for both correct pronunciations (Kendall's $\tau$ = `r r2(rmac$tau)`, *p* `r psig(rmac$pval)`) and mispronunciations (Kendall's $\tau$ = `r r2(rmam$tau)`, *p* `r psig(rmam$pval)`).
-These results, quantifying the asymmetry in the funnel plots (Figure \@ref(fig:FunnelCombo)), indicate bias in the literature.
-This is particularly evident for correct pronunciations, where larger effect sizes have greater variance (bottom right corner) and the more precise effect sizes (i.e.
-smaller variance) tend to be smaller than expected (top left, outside the triangle).
-
-The stronger publication bias for correct pronunciation might reflect the status of this condition as a control.
-If infants were not looking to the target picture after hearing the correct label, the overall experiment design is called into question.
-However, even in a well-powered study one would expect the regular occurrence of null results even though as a population infants would reliably show the expected object identification effect.
-
-We should also point out that funnel plot asymmetry can be caused by multiple factors besides publication bias, such as heterogeneity in the data.
-There are various possible sources of heterogeneity, which our subsequent moderator analyses will begin to address.
-Nonetheless, we will remain cautious in our interpretation of our findings and hope that an open dataset which can be expanded by the community will attract previously unpublished null results so we can better understand infants' developing mispronunciation sensitivity.
-
-```{r FunnelPrep}
-### Plots adapted from Sakaluk, 2016, see also Black & Bergmann, 2017
-### https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/
-
-#Themes and plot
-funnel_theme=theme_bw()+
-  theme(#panel.grid.major=element_blank(),
-    #panel.grid.minor=element_blank(),
-    #panel.border=element_blank(),
-    axis.line=element_line(),
-    text=element_text(family='Times', size=18),
-    legend.position='none')
-
-```
-
-```{r FunnelCorrect}
-
-#Rename a bunch of things for ease
-dat_co = db_ET_correct %>% 
-  rename(cite = short_cite,
-         yi = g_calc,
-         vi = g_var_calc) %>%
-  mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
-  dplyr::select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>%
-  arrange(desc(yi))
-
-#Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order
-
-#Get standard errors from variances
-dat_co$se = sqrt(dat_co$vi)
-
-#Calculate 95% CI values
-dat_co$lowerci = (-1.96*dat_co$se)+dat_co$yi
-dat_co$upperci = (1.96*dat_co$se)+dat_co$yi
-
-#Store the meta-analytic estimate and its standard error from whatever model you run
-#summary(rma_correct)
-estimate_co = coef(summary(rma_correct))$estimate
-se_co = coef(summary(rma_correct))$se
-
-#Store a vector of values that spans the range from 0
-#to the max value of impression (standard error) in your dataset.
-#Make the increment (the final value) small enough (I choose 0.001)
-#to ensure your whole range of data is captured
-se.seq_co=seq(0, max(dat_co$se), 0.001)
-
-#Now, compute vectors of the lower-limit and upper limit values for
-#the 95% CI region, using the range of SE that you generated in the previous step, 
-#and the stored value of your meta-analytic estimate.
-ll95_co = estimate_co-(1.96*se.seq_co)
-ul95_co = estimate_co+(1.96*se.seq_co)
-
-#You can do this for a 99% CI region too
-ll99_co = estimate_co-(3.29*se.seq_co)
-ul99_co = estimate_co+(3.29*se.seq_co)
-
-#And finally, do the same thing except now calculating the confidence interval
-#for your meta-analytic estimate based on the stored value of its standard error
-meanll95_co = estimate_co-(1.96*se_co)
-meanul95_co = estimate_co+(1.96*se_co)
-
-#Now, smash all of those calculated values into one data frame (called 'dfCI').
-#You might get a warning about '...row names were found from a short variable...'
-#You can ignore it.
-dfCI_co = data.frame(ll95_co, ul95_co, ll99_co,
-                  ul99_co, se.seq_co, estimate_co, meanll95_co, meanul95_co)
-
-#Now we can actually make the funnel plot.
-#Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
-fp_co = ggplot(aes(x = se, y = yi), data = dat_co) +
-  #Regression line for the FP asymmetry
-  geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_co) +
-  #Add your data-points to the scatterplot
-  geom_point(size = 2, colour="black", alpha = .5) +
-  #
-  #Give the x- and y- axes informative labels
-  xlab('Standard Error') + ylab('Hedges\' g')+
-  # give it a title
-    ggtitle("Correct") +
-    # make sure both plots have same scale
-    # still ylim because we haven't flipped yet
-    #coord_cartesian(ylim = c(0.5, 0))+
-  #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
-  #to the lower and upper limits of your 95% CI region
-  #And dashed lines corresponding to your 99% CI region
-  #Add lines corresponding to 0 and estimate
-  geom_line(aes(x = se.seq_co, y = 0), linetype = 'solid', data = dfCI_co) +
-  geom_line(aes(x = se.seq_co, y = estimate_co), linetype = 'dashed', data = dfCI_co) +
-  geom_line(aes(x = se.seq_co, y = ll95_co), linetype = 'dotted', data = dfCI_co) +
-  geom_line(aes(x = se.seq_co, y = ul95_co), linetype = 'dotted', data = dfCI_co) +
-  #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
-  #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
-  #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
-  #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
-  #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
-  #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
-  #at the top of the figure once we swap the x- and y-axes...
-  scale_x_reverse()+
-  #Specify the range and interval for the tick-marks of the y-axis (Zr);
-  #Choose values that work for you based on your data
-  #scale_y_continuous(breaks=seq(-.45,0.8,0.25))+
-  #And now we flip the axes so that SE is on y- and Zr is on x-
-  coord_flip()+
-  #Finally, apply my APA-format theme (see code at end of post).
-  #You could, alternatively, specify theme_bw() instead.
-  funnel_theme
-
-#Call the pretty funnel plot
-#fp_co
-#ggsave("figures/FunnelPlot_correct.pdf")
-
-```
-
-```{r FunnelMisp}
-
-  #Rename a bunch of things for ease
-dat_mp = db_ET_MP %>%
-    rename(cite = short_cite,
-           yi = g_calc,
-           vi = g_var_calc) %>%
-    dplyr::select(cite, expt_num, same_infant, mean_age_1, yi, vi) %>% 
-    mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
-    arrange(desc(yi))
-
-  #Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order
-
-  #Get standard errors from variances
-  dat_mp$se = sqrt(dat_mp$vi)
-
-  #Calculate 95% CI values
-  dat_mp$lowerci = (-1.96*dat_mp$se)+dat_mp$yi
-  dat_mp$upperci = (1.96*dat_mp$se)+dat_mp$yi
-
-  #Store the meta-analytic estimate and its standard error from whatever model you run (substitute your own values)
-  #summary(rma_MP)
-  estimate_mp = coef(summary(rma_MP))$estimate
-  se_mp = coef(summary(rma_MP))$se
-
-  #Store a vector of values that spans the range from 0
-  #to the max value of impression (standard error) in your dataset.
-  #Make the increment (the final value) small enough (I choose 0.001)
-  #to ensure your whole range of data is captured
-  se.seq_mp=seq(0, max(dat_mp$se), 0.001)
-
-  #Now, compute vectors of the lower-limit and upper limit values for
-  #the 95% CI region, using the range of SE that you generated in the previous step, 
-  #and the stored value of your meta-analytic estimate.
-  ll95_mp = estimate_mp-(1.96*se.seq_mp)
-  ul95_mp = estimate_mp+(1.96*se.seq_mp)
-
-  #You can do this for a 99% CI region too
-  ll99_mp = estimate_mp-(3.29*se.seq_mp)
-  ul99_mp = estimate_mp+(3.29*se.seq_mp)
-
-  #And finally, do the same thing except now calculating the confidence interval
-  #for your meta-analytic estimate based on the stored value of its standard error
-  meanll95_mp = estimate_mp-(1.96*se_mp)
-  meanul95_mp = estimate_mp+(1.96*se_mp)
-
-  #Now, smash all of those calculated values into one data frame (called 'dfCI').
-  #You might get a warning about '...row names were found from a short variable...'
-  #You can ignore it.
-  dfCI_mp = data.frame(ll95_mp, ul95_mp, ll99_mp,
-                       ul99_mp, se.seq_mp, estimate_mp, meanll95_mp, meanul95_mp)
-
-  #Now we can actually make the funnel plot.
-  #Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
-  fp_mp = ggplot(aes(x = se, y = yi), data = dat_mp) +
-    #Regression line for the FP asymmetry
-    geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_mp) +
-    #Add your data-points to the scatterplot
-  geom_point(size = 2, colour="black", alpha = .5) +
-    #
-  #Give the x- and y- axes informative labels
-  xlab('Standard Error') + 
-    # remove y label because it will be combined with the other funnel plot
-    ylab('Hedges\' g')+
-    # give it a title
-    ggtitle("Mispronunciation") +
-    # make sure both plots have same scale
-    # still xlim because we haven't flipped yet
-    #coord_cartesian(xlim = c(0.5, 1))+
-    #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
-    #to the lower and upper limits of your 95% CI region
-    #And dashed lines corresponding to your 99% CI region
-    #Add lines corresponding to 0 and estimate
-    geom_line(aes(x = se.seq_mp, y = 0), linetype = 'solid', data = dfCI_mp) +
-    geom_line(aes(x = se.seq_mp, y = estimate_mp), linetype = 'dashed', data = dfCI_mp) +
-    geom_line(aes(x = se.seq_mp, y = ll95_mp), linetype = 'dotted', data = dfCI_mp) +
-    geom_line(aes(x = se.seq_mp, y = ul95_mp), linetype = 'dotted', data = dfCI_mp) +
-    #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
-    #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
-    #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
-    #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
-    #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
-    #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
-    #at the top of the figure once we swap the x- and y-axes...
-    scale_x_reverse()+
-    #Specify the range and interval for the tick-marks of the y-axis (Zr);
-    #Choose values that work for you based on your data
-    #scale_y_mpntinuous(breaks=seq(-.45,0.8,0.25))+
-    #And now we flip the axes so that SE is on y- and Zr is on x-
-    coord_flip()+
-    #Finally, apply my APA-format theme (see previous).
-    #You could, alternatively, specify theme_bw() instead.
-    funnel_theme +
-    theme(axis.title.y = element_blank())
-
-  #Call the pretty funnel plot
-  #fp_mp
-#  ggsave("figures/FunnelPlot_misp.pdf")
-
-```
-
-## (Insert Figure 2 about here)
-
-```{r FunnelCombo, echo = FALSE, fig.cap="Funnel plots for object identification, plotting the standard error of the effect size in relation to the effect size.
-The black line marks zero, the dashed grey line marks the effect estimate, and the grey line marks funnel plot asymmetry.", results="hide"}
-
-  jpeg(filename = "figures/Figure_2_Funnel_Plots_Object_Identification.jpg", 
-       width = 600, height = 400, units = "px")
-
-  p <-   grid.arrange(fp_co, fp_mp, nrow = 1)
-                      #top = textGrob("Object Identification", gp=gpar(fontsize=25)))
-                      #top = "Figure 1. Funnel Plots")
-  dev.off()
-
-    grid.draw(p)
-
-```
-
-```{r PcurveExport, results = "hide"}
-
-textfile_co = "p_curve_app/p_curve_co.txt"
-
-# make sure the file is made new with our loop
-if (file.exists(textfile_co)) {file.remove(textfile_co)}
-
-for(line in 1:length(db_ET_correct$n_1)){
-  if(!is.na(db_ET_correct[line,]$t)){
-    newline = paste("t(", db_ET_correct[line,]$n_1-1, ")=",db_ET_correct[line,]$t, sep = "")
-    write(newline, file = textfile_co, append = TRUE)
-    #cat("\n")
-    #write(newline, file = textfile, append = TRUE)    
-  }
-}
-
-textfile_mp = "p_curve_app/p_curve_mp.txt"
-
-# make sure the file is made new with our loop
-if (file.exists(textfile_mp)) {file.remove(textfile_mp)}
-
-for(line in 1:length(db_ET_MP$n_1)){
-  if(!is.na(db_ET_MP[line,]$t)){
-    newline = paste("t(", db_ET_MP[line,]$n_1-1, ")=",db_ET_MP[line,]$t, sep = "")
-    write(newline, file = textfile_mp, append = TRUE)
-    #cat("\n")
-    #write(newline, file = textfile, append = TRUE)    
-  }
-}
-
-```
-
-```{r ReadIn_pcurve_app,  echo = FALSE, error = FALSE}
-
-#Get the effect size data
-source("scripts/p_curve_app_code.R")
-
-# this gives the number of significant results
-# the Z value
-# and the significance
-pcd_correct <- pcurve_app("p_curve_co.txt", "p_curve_app")
-```
-
-```{r ReadIn_pcurve_app_2,  echo = FALSE, error = FALSE}
-pcd_misp <- pcurve_app("p_curve_mp.txt", "p_curve_app")
-
-```
-
-We next examined the p-curves for significant values from the correctly pronounced and mispronounced conditions.
-The p-curve based on `r pcd_correct$ksig` statistically significant values for correct pronunciations indicates that the data contain evidential value (Z = `r r2(pcd_correct$Zppr)`, *p* `r psig(pcd_correct$p.Zppr)`) and we find no evidence of a large proportion of p-values just below the typical alpha threshold of .05 that researchers consistently apply in this line of research.
-The p-curve based on `r pcd_misp$ksig` statistically significant values for mispronunciations indicates that the data contain evidential value (Z = `r r2(pcd_misp$Zppr)`, *p* `r psig(pcd_misp$p.Zppr)`) and there is again no evidence of a large proportion of p-values just below the typical alpha threshold of .05.
-
-Taken together, the results suggest a tendency in the literature towards publication bias.
-As a result, our meta-analysis may systematically overestimate effect sizes and we therefore interpret all estimates with caution.
-Yet, the p-curve analysis suggests that the literature contains evidential value, reflecting a "real" effect.
-We therefore continue our meta-analysis.
-
-## Meta-analysis
-
-### Object Identification for Correct and Mispronounced Words
-
-```{r MAcorrect}
-
-# rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ same_infant_calc | short_cite)
-
-# new random effects structure
-rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
-
-#summary(rma_correct)
-#kable(round(coef(summary(rma_correct)), 2))
-
-sum_eff <- coef(summary(rma_correct))[1,]
-
-```
-
-We first calculated the meta-analytic effect for infants' ability to identify objects when hearing correctly pronounced labels.
-The variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was significantly different from zero `r CI_p(sum_eff)`.
-This is a small to medium effect size [according to the criteria set by @Mills-Smith2015].
-That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants tended to fixate on the corresponding object.
-Although the publication bias present in our analysis of funnel plot asymmetry suggests that the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)`, which is substantially above zero, together suggest that this result is somewhat robust.
-In other words, we are confident that the true population mean lies above zero for object recognition of correctly pronounced words.
-
-```{r MAMP}
-
-#rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ same_infant_calc | short_cite)
-
-#
-rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
-
-#summary(rma_MP)
-
-sum_eff <- coef(summary(rma_MP))[1,]
-
-```
-
-We then calculated the meta-analytic effect for object identification in response to mispronounced words.
-In this case, the variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was also significantly different from zero `r CI_p(sum_eff)`.
-This is considered a small effect size [@Mills-Smith2015], but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object.
-In other words, infants are able to resolve mispronunciations, a key skill in language processing We again note the publication bias (which was smaller in this condition), and the possibility that the effect size Hedges' *g* may be overestimated.
-But, as the p-curve indicated evidential value, we are confident in the overall pattern, namely that infants fixate the target even after hearing a mispronounced label.
-
-### Mispronunciation Sensitivity Meta-Analytic Effect
-
-```{r MPEffect}
-
-rma_MPeffect <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
-
-#summary(rma_MPeffect)
-
-#rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ same_infant_calc | short_cite)
-
-#summary(rma_MPeffect_1)
-
-sum_eff <- coef(summary(rma_MPeffect))[2,]
-
-```
-
-```{r MPEffect_forest, echo = FALSE, results="hide"}
-
-##Borrowing some code to make this a ggplot: 
-#https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-met#a-analysis/
-#Rename a bunch of things for ease
-
-mean_correct <- with(dat, mean(g_calc[is_correct == 1]))
-mean_misp <- with(dat, mean(g_calc[is_correct == 0]))
-
-new.dat <- dat
-#new.dat <- subset(new.dat, x_type == "percent_post")
-
-# new.dat <- subset(new.dat, short_cite == "Højen et al. (n.d.)" | short_cite == "Swingley & Aslin (2000)" | short_cite == "Swingley (2003)")
-
-new.dat <-
-  new.dat %>% 
-  rename(cite = short_cite,
-         yi = g_calc,
-         vi = g_var_calc)
-#Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order
-new.dat <-
-  new.dat %>% 
-  select(cite, expt_num, expt_condition, same_infant, is_correct, mean_age_1, yi, vi, within_measure) %>% 
-  mutate(study_ref = paste(cite, expt_num, expt_condition, same_infant, is_correct, sep=',')) %>% 
-  arrange(desc(yi))
-
-new.dat$condition <- ifelse(new.dat$is_correct == 1, "correct", "mispronunciation")
-
-#Get standard errors from variances
-new.dat$se = sqrt(new.dat$vi)
-#Calculate 95% CI values
-new.dat$lowerci = (-1.96*new.dat$se)+new.dat$yi
-new.dat$upperci = (1.96*new.dat$se)+new.dat$yi
-#Themes and plot
-apatheme2=theme_bw()+
-  theme(panel.grid.major=element_blank(),
-        panel.grid.minor=element_blank(),
-        panel.border=element_blank(),
-        axis.line=element_line(),
-        text=element_text(family='Times'),
-        legend.position='none')
-p=
-  ggplot(new.dat, aes(y=reorder(study_ref, -yi), x=yi, xmin=lowerci, xmax=upperci))+
-  #Add data points and color them black
-  geom_point(color = 'black')+
-  #Add 'special' points for the summary estimates, by making them diamond shaped
-#  geom_point(data=subset(dat, tester=='Summary'), color='black', shape=18, size=4)+
-  #add the CI error bars
-  geom_errorbarh(height=.1)+
-  #Specify the limits of the x-axis and relabel it to something more meaningful
-  #scale_x_continuous(limits=c(-1.5,1.5), name='Standardized Mean Difference (g)')+
-  #Give y-axis a meaningful label
-  ylab('Reference')+
-  #Add a vertical dashed line indicating an effect size of zero, for reference
-  geom_vline(xintercept=0, color='grey', linetype='dashed')+
-  #Add a vertical line to show mean effect
-  geom_vline(xintercept=mean_correct, color='orange', linetype='dashed')+
-    geom_vline(xintercept=mean_misp, color='blue', linetype='dashed')+
-  #Create sub-plots (i.e., facets) based on levels of setting
-  #And allow them to have their own unique axes (so authors don't redundantly repeat)
-  facet_grid(condition~., scales= 'free', space='free')+
-  #Apply my APA theme
-  apatheme2
-#p
-
-```
-
-The above two analyses considered the data from mispronounced and correctly pronounced words separately.
-To evaluate mispronunciation sensitivity, we compared the effect size Hedges' *g* for correct pronunciations with mispronunciations directly.
-To this end, we combined the two datasets.
-When condition was included (correct, mispronounced), the moderator test was significant (`r mod_test(rma_MPeffect)`).
-The estimate for mispronunciation sensitivity was `r g_SE(sum_eff)`, and infants' looking behavior across conditions was significantly different `r CI_p(sum_eff)`.
-This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations.
-In other words, we observe a significant difference between the two conditions and can now quantify the modulation of fixation behavior in terms of standardized effect sizes and their variance.
-This first result has both theoretical and practical implications, as we can now reason about the amount of perturbation caused by mispronunciations and can plan future studies to further investigate this effect with suitable power.
-
-Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, *p* `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, *p* `r psig(rma_MP$QEp)`), as well as mispronunciation sensitivity, which included the moderator condition (QE(249) = `r r2(rma_MPeffect$QE)`, *p* `r psig(rma_MPeffect$QEp)`).
-This indicated that the sample contains unexplained variance leading to significant difference between studies beyond what is to be expected based on random sampling error.
-We therefore continue with our moderator analysis to investigate possible sources of this variance.
-
-### Object Recognition and Mispronunciation Sensitivity Modulated by Age
-
-```{r MAcorrect_age}
-
-rma_correct_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = ~ same_infant_calc | short_cite)
-
-#summary(rma_correct_age)
-#kable(round(coef(summary(rma_correct_age)), 2))
-#aov.type <- anova(rma_correct_age)
-
-Csum_eff <- coef(summary(rma_correct_age))[2,]
-
-```
-
-```{r MAMP_age}
-
-rma_MP_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = ~ same_infant_calc | short_cite)
-
-#summary(rma_MP_age)
-#aov.type <- anova(rma_MP_age)
-
-Msum_eff <- coef(summary(rma_MP_age))[2,]
-
-```
-
-To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44 for Figure \@ref(fig:PlotMPEffect)).
-
-In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not.
-Age did not significantly modulate object identification in response to correctly pronounced (`r mod_test(rma_correct_age)`) or mispronounced words (`r mod_test(rma_MP_age)`).
-The lack of a significant modulation together with the small estimates for age (correct: $\beta$ `r full_estimate(Csum_eff)`; mispronunciation: $\beta$ `r full_estimate(Msum_eff)`) indicates that there might be no relationship between age and target looks in response to a correctly pronounced or mispronounced label.
-We note that the estimates in both cases are positive, however, which is in line with the general assumption that infants’ language processing overall improves as they mature [@Fernald1998].
-We plot both object recognition and mispronunciation sensitivity as a function of age in Figure \@ref(fig:PlotMPEffect).
-
-```{r MPEffect_age}
-
-rma_MPeffect_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = ~ same_infant_calc | short_cite)
-
-# summary(rma_MPeffect_age)  
-# 
-# aov.type <- anova(rma_MPeffect_age)
-
-sum_eff <- coef(summary(rma_MPeffect_age))[4,]
-
-```
-
-We then examined the interaction between age and mispronunciation sensitivity (correct vs.
-mispronounced words) in our whole dataset.
-The moderator test was significant (`r mod_test(rma_MPeffect_age)`).
-The interaction between age and mispronunciation sensitivity, however, was not significant ($\beta$ `r full_estimate(sum_eff)`); the moderator test was mainly driven by the difference between conditions.
-The small estimate, as well as inspection of Figure \@ref(fig:PlotMPEffect), suggests that as infants age, their mispronunciation sensitivity neither increases or decreases.
-
-## (Insert Figure 3 about here)
-
-```{r PlotMPEffect, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for correct pronunciations (orange) and mispronunciations (blue) by participant age.
-Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) by participant age.
+## Moderator Analyses
+
+### Number of mispronounced trials
+
+```{r MispTrials_Demo, results = "hide"}
+
+misptrials_info <- dat %>%
+  group_by(percent_MP) %>%
+  summarize(n_exp_conditions =  n())
+
+# majority of experimental conditions had 50% mispronunciation trials
+
+```
+
+```{r MispTrials, results= "asis"}
+
+rma_misptrials <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(percent_MP)*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
+
+#no impact of the percentage of mispronunciation trials
+
+```
+
+```{r MispTrials_age, results= "asis"}
+
+# age moderator
+rma_misptrials_age <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(percent_MP)*condition*age.C, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
+
+ sum_eff_age <- coef(summary(rma_misptrials_age))[8,]
+
+ # divide into age groups
+
+ dat$age_group <- ntile(dat$mean_age_1, 4)
+  dat$mt_group <- ntile(dat$percent_MP, 4)
+
+misp_trials_ages <- dat %>%
+  group_by(age_group, mt_group) %>%
+  summarize(n =  n())
+
+ #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
+
+ misp_trials_ages <- misp_trials_ages %>% spread(mt_group, n)
+
+ #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
+#fish.test <- fisher.test(misp_trials_ages,workspace=2e9)
+
+```
+
+```{r PlotMispTrial_age, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language.
+Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language by age.
 For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
 
-dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
-
-p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  ggtitle("a. Object Recognition")+
-  geom_point(aes(size = weights_g),show.legend=FALSE, alpha = .5) + 
-  geom_segment(aes(x = 6, y = 0, xend = 31, yend = 0), linetype="dotted", color = "black")+
-  #geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_colour_manual(values=cbPalette)+
-  xlim(6, 31) +
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Hedges' g")
-
-#p
-
-dat.cm <- dat[,c("short_cite", "is_correct", "is_mp","condition", "g_calc", "weights_g", "mean_age_1", "n_1")]
-
-dat.c <- subset(dat.cm, is_correct == 1)
-dat.m <- subset(dat.cm, is_mp == 1)
-
-dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "mean_age_1", "n_1"))
+db_misptrial <- dat
+
+db_misptrial$percent_MP <- as.numeric(db_misptrial$percent_MP)
+
+db_misptrial$condition_label <- ifelse(db_misptrial$condition==1, "Correct", "Mispronunciation")
+
+db_misptrial <- db_misptrial[,c("short_cite", "is_correct", "is_mp", "percent_MP", "condition_label", "g_calc", "weights_g", "mean_age_1", "n_1")]
+
+dat.c <- subset(db_misptrial, is_correct == 1)
+dat.m <- subset(db_misptrial, is_mp == 1)
+
+dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "percent_MP", "mean_age_1", "n_1"))
 
@@
 
-p.diff <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity)) + 
-  ggtitle("b. Mispronunciation Sensitivity")+
-  geom_point(aes(size = weight),show.legend=FALSE, alpha = .3) + 
-  geom_segment(aes(x = 6, y = 0, xend = 31, yend = 0), linetype="dotted", color = "black")+
-  #geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1), color = "black") +
-  scale_colour_manual(values=cbPalette)+
-  xlim(6, 31) +
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Hedges' g")
-
-# min(dat$mean_age_1/30.44)
-# max(dat$mean_age_1/30.44)
-
-#ggsave("figures/AgeEffect_log.jpg", p,height= 7,width= 6)
-
-lay <- rbind(c(1), c(2))
-#lay <- rbind(c(1,2))
-
-  jpeg(filename = "figures/Figure_3_AgeEffect.jpg", 
-       width = 500, height = 700, units = "px")
-
-MS_plot <- grid.arrange(p, p.diff,
-                             layout_matrix = lay)
-
-dev.off()
-
-grid.draw(MS_plot)
-
-```
-
-### Vocabulary Size: Correlation Between Mispronunciation Sensitivity and Vocabulary
-
-```{r VocabularyData, echo = FALSE}
-vocab_info <- dat %>%
-  mutate(has_vocab = ifelse(!is.na(r_comprehension), "comprehension", 
-                            ifelse(!is.na(r_production), "production", "none"))) %>%
-  group_by(has_vocab) %>%
-  summarize(count = n(),
-            papers = n_distinct(short_cite))
-
-#kable(vocab_info)
-
-vocab_info2 <- dat %>%
-  mutate(has_vocab = ifelse(!is.na(r_comprehension) | !is.na(r_production), "vocab", 
-                            "none")) %>%
-  group_by(has_vocab) %>%
-  summarize(count = n(),
-            papers = n_distinct(short_cite))
-
-vi1 <- as.data.frame(vocab_info)
-vi2 <- as.data.frame(vocab_info2)
-
-```
-
-Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` analyzed the relationship between vocabulary scores and object recognition for correct pronunciations and mispronunciations (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers and `r with(vi1, count[has_vocab == "comprehension"])` records; production = `r with(vi1, papers[has_vocab == "production"])` papers and `r with(vi1, count[has_vocab == "production"])` records).
-There is reason to believe that production data are different from comprehension data.
-Children comprehend more words than they can produce, leading to different estimates for comprehension and production.
-Production data is easier to estimate for parents in the typical questionnaire-based assessment and may therefore be more reliable [@Tomasello1994].
-As a result, we planned to analyze these two types of vocabulary measurement separately.
-However, because only `r with(vi1, papers[has_vocab == "production"])` papers reported correlations with productive vocabulary scores, only limited conclusions can be drawn.
-We also note that because individual effect sizes in our analysis were related to object recognition and not mispronunciation sensitivity, we were only able to calculate the relationship between vocabulary scores and the former.
-In our vocabulary analysis, we therefore focus exclusively on the relationship between comprehension and object recognition for correct pronunciations and mispronunciations.
-
-```{r ComprehensionMeta_correct}
-
-# coweeta.uga.edu/publications/10436.pdf, page 80 as a model for writing up these results
-
-#we're relying on the library meta function metacor
-compr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_comprehension) & r_comprehension > -1)
-
-CC <- metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
-
-# https://rdrr.io/cran/meta/man/forest.html
-#forest(CC)
-
-# number of positive correlations
-#CC$TE
-rel <- ifelse(CC$TE > 0, "pos", "neg")
-pos_rel <- sum(rel == "pos")
-neg_rel <- sum(rel == "neg")
-tot_rel <- pos_rel + neg_rel
-
-min_cor <- min(CC$TE)
-max_cor <- max(CC$TE)
-
-```
-
-```{r ProductionMeta_correct}
-#we're relying on the library meta function metacor
-#prodr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_production) & r_production < 1)
-
-#CP <- metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
-
-#Higher production scores were also associated with greater object recognition in response to correct pronunciations for 9 of 16 experimental conditions, with correlation values ranging from -0.23 to 0.44.
-The mean effect size XXX was again small and not significantly different from zero with 0.0601 (CI [-0.0331; 0.1533] *p* = .2061).
-For both comprehension and production scores, the small correlation effect sizes and large variances suggest a lack of relationship between vocabulary and object recognition for correct pronunciations.
-However, we note again that comparatively few studies report the correlation between vocabulary and infants' responses to correct pronunciations to begin with and thus we cannot draw any firm conclusions based on this small sample of studies.
-
-```
-
-We first considered the relationship between vocabulary and object recognition for correct pronunciations.
-Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for `r pos_rel` of `r tot_rel` experimental conditions, with correlation values ranging from `r min_cor` to `r max_cor`.
-The weighted mean effect size Pearson's *r* of `r r2(CC$TE.fixed)` was small but did differ significantly from zero (CI [`r r2(CC$lower.fixed)`; `r r2(CC$upper.fixed)`] *p* `r psig(CC$pval.fixed)`).
-As a result, we can draw a tentative conclusion that there is a positive relationship between comprehension scores and object recognition in response to correct pronunciations.
-
-```{r ComprehensionMeta_MP}
-#we're relying on the library meta function metacor
-compr  <- subset(db_ET_MP, !is.na(db_ET_MP$r_comprehension) & r_comprehension > -1)
-
-MC <- metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
-
-# number of positive correlations
-#CC$TE
-rel <- ifelse(MC$TE > 0, "pos", "neg")
-pos_rel <- sum(rel == "pos")
-neg_rel <- sum(rel == "neg")
-tot_rel <- pos_rel + neg_rel
-
-min_cor <- min(MC$TE)
-max_cor <- max(MC$TE)
-
-```
-
-```{r ProductionMeta_MP}
-#we're relying on the library meta function metacor
-# prodr  <- subset(db_ET_MP, !is.na(db_ET_MP$r_production) & r_production < 1)
-# 
-# MP <- metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
-
-#For production, however, lower production scores were associated with greater object recognition in response to mispronunciations for 16 of 31 experimental conditions, with correlation values ranging from -0.28 to 0.44.
-The mean effect size XXX was -0.0402, (CI [-0.1043; 0.0238] *p* = .2181).
-
-```
-
-We next considered the relationship between vocabulary and object recognition for mispronunciations.
-Higher comprehension scores were associated with greater object recognition in response to mispronunciations for `r pos_rel` of `r tot_rel` experimental conditions, with correlation values ranging from `r min_cor` to `r max_cor`.
-The weighted mean effect size Pearson's *r* of `r r2(MC$TE.fixed)` was small and did not differ significantly from zero (CI [`r r2(MC$lower.fixed)`; `r r2(MC$upper.fixed)`] *p* `r psig(MC$pval.fixed)`).
-The small correlation suggests either a very small positive or no relationship between vocabulary and object recognition for mispronunciations.
-We again emphasize that we cannot draw a firm conclusion due to the small number of studies we were able to include here.
-
-Figure \@ref(fig:Vocab-describe1) plots the year of publication for all the mispronunciation sensitivity studies included in this meta-analysis.
-This figure illustrates two things: the increasing number of mispronunciation sensitivity studies and the decreasing number of mispronunciation studies measuring vocabulary.
-The lack of evidence for a relationship between mispronunciation sensitivity and vocabulary size in some early studies may have contributed to increasingly fewer researchers including vocabulary measurements in their mispronunciation sensitivity experimental design.
-This may explain our underpowered analysis of the relationship between object recognition for correct pronunciations and mispronunciations and vocabulary size.
-
-## (Insert Figure 4 about here)
-
-```{r Vocab-describe1, echo = FALSE, fig.width=10,fig.height=8, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (orange), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (green).", results="hide"}
-#how did vocabulary collection change over time?
-
-dv <- read.csv("data/vocab_collection.csv", header = T)
-
-years.v <- as.data.frame(seq(from = 2000, to = 2018, by = 1))
-relat.v <- c("no_vocab", "no_relationship", "positive")
-
-fake.v <- merge(years.v, relat.v, all = T)
-names(fake.v) <- c("year", "relationship")
-dat.v <- merge(dv, fake.v, by = c("year", "relationship"), all.y = T)
-dat.v$vocab <- as.character(dat.v$vocab)
-dat.v$relationship <- as.character(dat.v$relationship)
-dat.v$short_cite <- as.character(dat.v$short_cite)
-
-dat.v$vocab[is.na(dat.v$vocab)] <- "none"
-dat.v$short_cite <- ifelse(dat.v$vocab == "none", "none", dat.v$short_cite)
-
-dat.v$short_cite[is.na(dat.v$short_cite)] <- "none"
-
-dat.v$tested <- ifelse(dat.v$short_cite == "none", "no", "yes")
-
-dat.v$relationship <- ifelse(dat.v$relationship == "no_vocab", "No Vocabulary",
-                                   ifelse(dat.v$relationship == "positive", "Predictive",
-                                          "No Relationship"))
-dat.v$relationship <- factor(dat.v$relationship, levels = c("No Vocabulary", "Predictive", "No Relationship"))
-
-d.v <- subset(dat.v, short_cite != "none")
-
-d.v$Year <- d.v$year
-
-vocab_year <- ggplot(d.v,aes(x=Year, fill = relationship)) + 
-  apatheme+
-  geom_histogram(alpha = 0.5, bins = 20) +
-    scale_fill_manual(values=cbPalette)+
-     theme(legend.position = "bottom",
-           legend.title = element_blank())
-
-#vocab_year
-
-  jpeg(filename = "figures/Figure_4_Vocab_findings.jpg", 
-       width = 500, height = 300, units = "px")
-
-vocab_year
-
-  dev.off()
-
-grid.draw(vocab_year)
-
-#   
-# 
-# vocab_data1 <- dat.v %>%
-#   group_by(year, relationship, tested) %>%
-#   summarize(count = n())
-# 
-# vocab_data1 <- as.data.frame(vocab_data1)
-# vocab_data1$count <- ifelse(vocab_data1$tested == "no", 0, vocab_data1$count)
-# vocab_data1$year <- as.numeric(vocab_data1$year)
-# 
-# vocab_data1$relationship <- ifelse(vocab_data1$relationship == "no_vocab", "None",
-#                                    ifelse(vocab_data1$relationship == "positive", "Predicts",
-#                                           "No Relationship"))
-# vocab_data1$relationship <- factor(vocab_data1$relationship, levels = c("Predicts", "No Relationship", "None"))
-# 
-# 
-# p <- ggplot(vocab_data1, aes(year, count, color = relationship)) + 
-#   geom_line() + 
-#   geom_point()+
-#   scale_y_continuous(breaks = c(0, 1, 2, 3, 4), limits = c(0,4))+
-#   scale_colour_manual(values=cbPalette)+
-#   apatheme +
-#   theme(legend.title = element_blank(),
-#         legend.position = "bottom")
-# p
-# 
-#   jpeg(filename = "figures/Vocab_findings.jpg", 
-#        width = 500, height = 300, units = "px")
-# 
-#   p
-#   
-#   dev.off()
-#  
-```
-
-### Interim discussion: Development of infants' mispronunciation sensitivity
-
-The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age and increased vocabulary size.
-The results seem clear: Although infants consider a mispronunciation to be a better match to the target image than to a distractor image, there was a constant and stable effect of mispronunciation sensitivity.
-This did not change with development, and we might consider age a proxy for vocabulary size.
-We observe that the data for directly reported vocabulary size were too sparse to draw strong conclusions.
-In the literature, evidence for all possible developmental trajectories has been found, including mispronunciation sensitivity that increases, decreases, or does not change with age or vocabulary size.
-The present results do lend some support for the proposal that mispronunciation sensitivity stays consistent as infants develop.
-Furthermore, although we found a relationship between vocabulary size (comprehension) and target looking for correct pronunciations, we found no relationship between vocabulary and target looking for mispronunciations.
-This may be due to too few studies including reports of vocabulary size and more investigation is needed to draw a firm conclusion.
-
-Alternatively, the lack of developmental change in mispronunciation sensitivity could be due to differences in the types of tasks given to infants of different ages.
-If infants' word recognition skills are generally thought to improve with age and vocabulary size, research questions that tap more complex processes may be more likely to be investigated in older infants.
-In the following section, we investigate the role that different moderators play in mispronunciation sensitivity.
-To investigate the possibility of systematic differences in the tasks across ages, we additionally include an exploratory analysis of whether different moderators and experimental design features were included at different ages.
-
-## Moderator Analyses
-
-In this section, we consider each moderator individually and investigate its influence on mispronunciation sensitivity.
-For most moderators (except Number of features changed), we combine the correct and mispronounced datasets and include the moderator of condition, to study mispronunciation sensitivity as opposed to object recognition.
-To better understand the impact of these moderators on developmental change, we include age as subsequent moderator as well as an exploratory analysis of the age of infants tested with each type of moderator.
-The latter analysis is included to explore whether the lack of developmental change in mispronunciation sensitivity in the overall dataset is due to more complex moderator tasks being given to older infants, which may lower the overall effect size of mispronunciation sensitivity at older ages and dampen any evidence of change.
-Finally, we analyze the relationship between infant age and the moderator condition they were tested in using Fischer's exact test, which is more appropriate for small sample sizes (Fischer, 1922).
-For each moderator, we evaluate the independence of infants' age group (divided into quartiles unless otherwise specified) and assignment to each type of condition in a particular moderator.
-
-### Size of mispronunciation
-
-```{r NFeatures_demographics, results = "hide"}
-
-dat.f <- subset(dat, n_feature != "2_3" & n_feature != "1_2" & n_feature != "1_2_3")
-
-dat.f$n_feature <- factor(dat.f$n_feature, levels = c("0", "1", "2", "3"))
-
-dat.f$n_feature <- as.numeric(as.character(dat.f$n_feature))
-
-dat.f$n_feature <- ifelse(dat.f$condition == 1, 0, df$n_feature)
-
-nfeature_info <- dat.f %>%
-  group_by(n_feature) %>%
-  summarize(n_exp_conditions =  n())
-
-```
-
-To assess whether the size of the mispornunciation tested, as measured by the number of features change, modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced using 1-, 2-, and 3-feature changes.
-We did not include data for which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent (e.g., one mispronunciation included a 2-feature change whereas another only a 1-feature change).
-This analysis was therefore based on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` experimental conditions for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations.
-Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an equal impact on mispronunciation sensitivity, following the argument of graded sensitivity (White & Aslin, 2008; Mani & Plunkett 2011), and this modertor was coded as a continuous variable.
-
-```{r NFeatures, results = "hide"}
-
-dat.f <- subset(dat, n_feature != "2_3" & n_feature != "1_2" & n_feature != "1_2_3")
-
-dat.f$n_feature <- factor(dat.f$n_feature, levels = c("0", "1", "2", "3"))
-
-dat.f$n_feature <- as.numeric(as.character(dat.f$n_feature))
-
-dat.f$n_feature <- ifelse(dat.f$condition == 1, 0, dat.f$n_feature)
-
-# overall object recognition
-rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~n_feature, data = dat.f, random = ~ same_infant_calc | short_cite)
-
- sum_eff <- coef(summary(rma_NFeatures))[2,]
-
- linear_feature <- sum_eff$estimate
-
-```
-
-```{r NFeatures_age, results = "hide"}
-
-dat.f <- subset(dat, n_feature != "2_3" & n_feature != "1_2" & n_feature != "1_2_3")
-
-dat.f$n_feature <- factor(dat.f$n_feature, levels = c("0", "1", "2", "3"))
-
-dat.f$n_feature <- as.numeric(as.character(dat.f$n_feature))
-
-dat.f$n_feature <- ifelse(dat.f$condition == 1, 0, df$n_feature)
-
-# age moderator
-rma_NFeatures_age <- rma.mv(g_calc, g_var_calc, mods = ~n_feature*age.C, data = dat.f, random = ~same_infant_calc | short_cite)
-
- sum_eff_age <- coef(summary(rma_NFeatures_age))[4,]
-
- # divide into age groups
-
- dat.f$age_group <- ntile(dat.f$mean_age_1, 4)
-
- nfeature_ages <- dat.f %>%
-  group_by(age_group, n_feature) %>%
-  summarize(n =  n())
-
- #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
-
- nfeature_ages <- nfeature_ages %>% spread(n_feature, n)
-
- #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
-fish.test <- fisher.test(nfeature_ages)
-
-```
-
-To understand the relationship between mispronunciation size and mispronunciation sensitivity, we  evaluated the effect size Hedges' *g* with number of features changed as a moderator.
-The moderator test was significant, `r mod_test(rma_NFeatures)`.
-Hedges' *g* for number of features changed was `r g_SE(sum_eff)`, which indicated that as the number of features changed increased, the effect size Hedges' *g* significantly decreased `r CI_p(sum_eff)`.
-We plot this relationship in Figure \@ref(fig:PlotFeatEffect).
-This confirms previous findings of a graded sensitivity to the number of features changed for both consonant (Bernier & White, 2017; Tamasi, 2016; White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) mispronunciations as well as the importance of controlling for the degree of phonological mismatch in experimental design.
-
-To better understand how this moderator impacted our estimate of developmental change in mispronunciation sensitivity, we added age as a moderator.
-The moderator test was significant, `r mod_test(rma_NFeatures_age)`, but the interaction between age and number of features changed was not significant, $\beta$`r full_estimate(sum_eff_age)`.
-The small effect size for the interaction between age and number of features changed suggests that the impact of number of features changed on mispronunciation sensitivity does not change with infant age.
-This may be due to the fact that only a handful of studies have explicitly examined the effect of the number of features changed on mispronunciation sensitivity and only these studies include 3-feature changes (Bernier & White, 2017; Tamasi, 2016; White & Morgan, 2008; Mani & Plunkett, 2011).
-
-The results of Fisher's exact test were not significant, *p* `r psig(fish.test$p.value)`.
-This lack of a relationship suggests that older and younger infants are not being tested in experimental conditions that differentially manipulate the number of features changed.
-
-## (Insert Figure 5 about here)
-
-```{r PlotFeatEffect, echo = FALSE}
-
-dat.f <- subset(dat, n_feature != "2_3" & n_feature != "1_2" & n_feature != "1_2_3")
-dat.f$n_feature <- factor(dat.f$n_feature, levels = c("0", "1", "2", "3"))
-dat.f$n_feature <- as.numeric(as.character(dat.f$n_feature))
-dat.f$n_feature <- ifelse(dat.f$condition == 1, 0, df$n_feature)
-
-dat.f$feat_cat <- ifelse(dat.f$n_feature == 1, "1-feature",
-                         ifelse(dat.f$n_feature == 2, "2-feature",
-                                ifelse(dat.f$n_feature == 3, "3-feature",
-                                       ifelse(dat.f$n_feature == 0, "correct", "none"))))
-
-dat.f <- subset(dat.f, feat_cat != "none")
-
-dat.f$Features_changed <- factor(dat.f$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))
-
-p.MS <- ggplot(dat.f, aes(Features_changed, g_calc, fill = Features_changed)) + 
-  geom_violin() + 
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
+ms.agg <- ggplot(dat.cm, aes(percent_MP, Misp_sensitivity, fill = percent_MP)) + 
+  #facet_grid(.~lang_family)+
+  geom_point(aes(size = weight),show.legend=FALSE, alpha = .5) + 
+    geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weight)) +
+  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
+  labs(title="a")+
   #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
+  #scale_fill_continuous(values=cbPalette)+
   apatheme +
@@
         legend.title = element_blank(),
-        legend.position = "none",
-        axis.title.x = element_blank()) + 
+        legend.position = "none") +
+        #axis.title.x = element_blank(),
+        #axis.text.x = element_blank(),
+        #axis.ticks.x = element_blank()) + 
   #xlab("Number of Features Changed") + 
@@
 
-p.MS
-
-ms.age <- ggplot(dat.f, aes(mean_age_1/30.44, g_calc, color = Features_changed)) + 
-    #facet_grid(.~dv_label)+
+  dat.cm$Prcnt_MP <- quantcut(dat.cm$percent_MP, q=3, na.rm=TRUE)
+
+ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = Prcnt_MP)) + 
   geom_point(aes(size = n_1),show.legend=FALSE) +
@@
   geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
-  scale_colour_manual(values=cbPalette)+
+  #gradient_colour_continuous(values=cbPalette)+
   apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
+  theme(legend.position = "bottom") + 
   xlab("Age in months") + 
@@
 
-# ms.age
-
-  jpeg(filename = "figures/Figure_5_Number_of_Features.jpg", 
-       width = 500, height = 300, units = "px")
-
-  p.MS
-
-  dev.off()
-
-```
-
-### Distractor familiarity
-
-```{r DistFam_demographics, results = "hide"}
-
-distr_info <- dat %>%
-  group_by(object_pair) %>%
-  summarize(n_exp_conditions =  n())
-
-```
-
-To assess whether familiarity with the distractor image modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced and were either paired with a familiar or unfamiliar distractor.
-A familiar distractor was used in `r with(distr_info, n_exp_conditions[object_pair == "familiar_familiar"])` experimental conditions and a unfamiliar distractor in `r with(distr_info, n_exp_conditions[object_pair == "familiar_novel"])` experimental conditions.
-
-```{r DistractorType, results= "asis"}
-
-rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition, data = dat, random = ~ same_infant_calc | short_cite)
-
-d_fam <- coef(summary(rma_Distractor))[2,]
-d_fam_condit <- coef(summary(rma_Distractor))[4,]
-
-```
-
-```{r DistractorType_age, results= "asis"}
-
-# age moderator
-rma_Distractor_age <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair)*condition*age.C, data = dat, random = ~ same_infant_calc | short_cite)
-
- sum_eff_age <- coef(summary(rma_NFeatures_age))[8,]
- sum_eff_2 <- coef(summary(rma_NFeatures_age))[5,]
-
- # divide into age groups
-
- dat$age_group <- ntile(dat$mean_age_1, 4)
-
- dist_fam_ages <- dat %>%
-  group_by(age_group, object_pair) %>%
-  summarize(n =  n())
-
- #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
-
- dist_fam_ages <- dist_fam_ages %>% spread(object_pair, n)
-
- #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
-fish.test <- fisher.test(dist_fam_ages)
-
-```
-
-To understand the relationship between distractor familiarity and mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with distractor familiarity and condition as moderators.
-The moderator test was significant, `r mod_test(rma_NFeatures)`, but the effect of distractor familiarity ($\beta$`r full_estimate(d_fam)`) as well as the interaction between distractor familiarity and condition ($\beta$`r full_estimate(d_fam_condit)`) were not significant.
-The results suggest that overall, infants' familiarity with the distractor object (familiar or unfamiliar) did not impact their mispronunciation sensitivity.
-
-We next examined whether age modulates object recognition or mispronunciation sensitivity when the distractor image is familiar or unfamiliar.
-Based on previous results, we expected older infants  to have greater mispronunciation sensitivity than younger infants when the distractor was unfamiliar compared to familiar.
-To evaluate this prediction, we added age as a moderator.
-The moderator test was significant `r mod_test(rma_Distractor_age)`.
-The estimate for the  three-way-interaction between condition, distractor familiarity, and age was small and not significant ($\beta$ = `r full_estimate(sum_eff_age)`.
-We note that in this model, the interaction between condition and distractor familiarity was significant ($\beta$`r full_estimate(sum_eff_2)`, but that this estimate is similar to the original, non-significant estimate specifically examining this interaction in the previous model.
-Taken together, these results suggest that regardless of age, mispronunciation sensitivity was similar whether the distractor image was familiar or unfamiliar.
-
-The results of Fisher's exact test were not significant, *p* `r psig(fish.test$p.value)`.
-This lack of a relationship suggests that older and younger infants are not being tested in experimental conditions that differentially employ distractor images that are familiar or unfamiliar.
-
-### Phonological overlap between target and distractor
-
-```{r DistractorOverlap_descrip}
-
-dist_overlap_info <- dat %>%
-  group_by(distractor_overlap) %>%
-  summarize(n_exp_conditions =  n())
-
-```
-
-To assess whether phonological overlap between the target and distractor image labels has an impact on the size of mispronunciation sensitivity, we examined the meta-analytic effect for object identification in response to mispronunciations and mispronunciation sensitivity when the target-distractor pairs either had no overlap or shared the same onset phoneme.
-We did not include data for which the overlap included both the onset and medial phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset/medial"])`), coda phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "coda"])`), or for targets paired with an unfamiliar distractor image `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "novel"])`.
-The analysis was therefore based on a subset of the overall dataset, with `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset"])` experimental conditions containing onset phoneme overlap between the target and distractor and `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "no"])` containing no overlap between target and distractor.
-
-```{r DistractorOverlap}
-
-db_ET_MPo_MS = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "no")
-
-db_ET_MPo_MS$distractor_overlap <- factor(db_ET_MPo_MS$distractor_overlap, levels = c("no", "onset"))
-
-rma_DistractorOverlapMS <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MPo_MS, random = ~ same_infant_calc | short_cite)
-
-#summary(rma_DistractorOverlapMS)
-
-sum_eff2 <- coef(summary(rma_DistractorOverlapMS))[4,]
-
-```
-
-```{r DistractorOverlap_age}
-
-# mispronunciation sensitivity
-dat_MPo = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "no")
-
-dat_MPo$distractor_overlap <- factor(dat_MPo$distractor_overlap, levels = c("no", "onset"))
-
-rma_DistractorOverlap_age_MS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap*condition, data = dat_MPo, random = ~ same_infant_calc | short_cite)
-
-#summary(rma_DistractorOverlap_age_MS)
-
-sum_eff_age <- coef(summary(rma_DistractorOverlap_age_MS))[8,]
-
- # divide into age groups
-
- dat_MPo$age_group <- ntile(dat_MPo$mean_age_1, 4)
-
- dist_overlap_ages <- dat_MPo %>%
-  group_by(age_group, distractor_overlap) %>%
-  summarize(n =  n())
-
- #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
-
- dist_overlap_ages <- dist_overlap_ages %>% spread(distractor_overlap, n)
-
- #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
-fish.test <- fisher.test(dist_overlap_ages, workspace=2e8)
-
-```
-
-To understand the relationship between phonological overlap between target and distractor and  mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with distractor overlap and condition as moderators.
-The moderator test was significant, `r mod_test(rma_DistractorOverlapMS)`.
-The estimate for the interaction between condition and distractor overlap was small, but significant ($\beta$ `r full_estimate(sum_eff2)`, suggesting that mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap.
-This relationship be seen in Figure \@ref(fig:PlotDistOverlap)a.
-
-To better understand how this moderator impacted our estimate of developmental change in mispronunciation sensitivity, we added age as a moderator.
-The moderator test was significant, `r mod_test(rma_DistractorOverlap_age_MS)` and the estimate for the three-way interaction between age, condition, and distractor overlap was significant, but relatively small ($\beta$ = `r full_estimate(sum_eff_age)`.
-As can be seen in Figure \@ref(fig:PlotDistOverlap)b, mispronunciation sensitivity increases with age for target-distractor pairs containing onset overlap, but decreases with age for target-distractor pairs containing no overlap.
-
-The results of Fisher's exact test were significant, *p* `r psig(fish.test$p.value)`.
-Older infants were more likely to be tested in experimental conditions where target and distractor images overlapped on their onset phoneme, while younger infants were more likely to be tested with target and distractor images that did not control for overlap.
-A distractor image that overlaps in the onset phoneme with the target image is considered a more challenging task to the infant, as infants must pay attention to the mispronounced phoneme and can not use the differing onsets between target and distractor images to differentiate (Fernald, Swingley, & Pinto, 2001).
-It therefore appears that older infants were given a more challenging task than younger infants.
-This may explain why infants in the onset overlap condition, a harder task, have a greater effect size estimate for mispronunciation sensitivity than those in the no overlap condition, which is a comparably easier task.
-We return to this issue in the General Discussion.
-
-## (Insert Figure 6 about here)
-
-```{r PlotDistOverlap}
-
-db_ET_MPo = dat %>%
-  filter(distractor_overlap == "onset"  | distractor_overlap == "no")
-
-db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no"))
-
-db_ET_MPo$condition_label <- ifelse(db_ET_MPo$condition==1, "Correct", "Mispronunciation")
-
-db_ET_MPo$distractor_label <- ifelse(db_ET_MPo$distractor_overlap=="onset", "Onset Overlap", "No Overlap")
-
-db_ET_MPo <- db_ET_MPo[,c("short_cite", "is_correct", "is_mp", "distractor_label", "condition_label", "g_calc", "weights_g", "mean_age_1", "n_1")]
-
-dat.c <- subset(db_ET_MPo, is_correct == 1)
-dat.m <- subset(db_ET_MPo, is_mp == 1)
-
-dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "distractor_label", "mean_age_1", "n_1"))
-
-dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
-dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
-
-ms.agg <- ggplot(dat.cm, aes(distractor_label, Misp_sensitivity, fill = distractor_label)) + 
-  #facet_grid(.~dv_label)+
-    geom_violin() + 
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
-  labs(title="a")+
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Misp. Sensitivity")
-
-ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = distractor_label)) + 
-    #facet_grid(.~dv_label)+
-  geom_point(aes(size = n_1),show.legend=FALSE) +
-  labs(title="b")+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Misp. Sensitivity")
-
 lay <- rbind(c(1), c(2))
@@
 
-  jpeg(filename = "figures/Figure_6_Distractor_Overlap.jpg",
-       width = 500, height = 600, units = "px")
+  jpeg(filename = "figures/Explore_mp_percent.jpg",
+       width = 500, height = 900, units = "px")
 
@@
 
-### Position of mispronunciation
-
-```{r Location_descrip}
-
-misp_location_info <- dat %>%
-  group_by(mispron_location) %>%
+### Same words correct and mispronounced
+
+```{r SameWords_Demo, results = "hide"}
+
+samewords_info <- dat %>%
+  group_by(word_correct_and_MP) %>%
   summarize(n_exp_conditions =  n())
@@
 
-To assess whether the position of the mispronunciation has an impact on mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to mispronunciations on the onset, medial, and coda phonemes.
-We did not include data for which the mispronunciation varied in regard to position (*n* = `r with(misp_location_info, n_exp_conditions[mispron_location == "coda/medial" | mispron_location == "onset/medial" | mispron_location == "onset/medial/coda"])`) or was not reported (*n* = `r with(misp_location_info, n_exp_conditions[is.na(mispron_location)])`).
-The analysis was therefore based on a subset of the overall dataset, with `r with(misp_location_info, n_exp_conditions[mispron_location == "onset"])` experimental conditions comparing a mispronunciation on the onset phoneme, `r with(misp_location_info, n_exp_conditions[mispron_location == "medial"])` experimental conditions comparing a mispronunciation on the medial phoneme, and `r with(misp_location_info, n_exp_conditions[mispron_location == "coda"])` experimental conditions comparing a mispronunciation on the coda phoneme.
-We coded the onset, medial, and coda positions as continuous variables, to evaluate the importance of each subsequent position (Marslen-Wilson & Zwitserlood, 1989).
-
-```{r Location_misp}
-
-db_ET_MPl = dat %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial"| mispron_location == "coda")
-
-# linear
-db_ET_MPl$m_posit <- ifelse(db_ET_MPl$mispron_location == "onset", 1,
-                            ifelse(db_ET_MPl$mispron_location == "medial", 2, 3))
-
-db_ET_MPl$m_posit <- as.numeric(as.character(db_ET_MPl$m_posit))
-
-rma_LinearLocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~m_posit*condition, data = db_ET_MPl, random = ~same_infant_calc | short_cite)
-
-sum_eff <- coef(summary(rma_LinearLocationCondition))[4,]
-
-```
-
-```{r Misp_Posit_age}
-
-# mispronunciation sensitivity
-
-db_ET_MPl = dat %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial"| mispron_location == "coda")
-
-# linear
-db_ET_MPl$m_posit <- ifelse(db_ET_MPl$mispron_location == "onset", 1,
-                            ifelse(db_ET_MPl$mispron_location == "medial", 2, 3))
-
-db_ET_MPl$m_posit <- as.numeric(as.character(db_ET_MPl$m_posit))
-
-rma_LinearLocationCondition_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*m_posit*condition, data = db_ET_MPl, random = ~same_infant_calc | short_cite)
-
-sum_eff_age <- coef(summary(rma_LinearLocationCondition_age))[8,]
-
- # divide into age groups
-
- db_ET_MPl$age_group <- ntile(db_ET_MPl$mean_age_1, 3)
-
- misp_posit_ages <- db_ET_MPl %>%
-  group_by(age_group, mispron_location) %>%
-  summarize(n =  n())
-
- #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
-
- misp_posit_ages <- misp_posit_ages %>% spread(mispron_location, n)
-
- #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
-fish.test <- fisher.test(misp_posit_ages)
-
-```
-
-To understand the relationship between mispronunciation position and  mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with mispronunciation position and condition as moderators.
-The moderator test was significant, `r mod_test(rma_LocationCondition)`.
-For the interaction between condition and mispronunciation position, the estimate was small but significant ($\beta$ `r full_estimate(sum_eff)`.
-As can be seen in Figure \@ref(fig:PlotMispPosit)a, mispronunciation sensitivity decreased linearly as the position of the mispronunciation moved later in the word, with sensitivity greatest for onset mispronunciations and smallest for coda mispronunciations.
-
-To better understand how this moderator impacted our estimate of developmental change in mispronunciation sensitivity, we added age as a moderator.
-The moderator test was significant, `r mod_test(rma_Misp_Posit_age_MS)`.
-The estimate for the three-way interaction between age, condition, and mispronunciation position was not significant ($\beta$ `r full_estimate(sum_eff_age_medial)`.
-As can be seen in Figure \@ref(fig:PlotMispPosit)b, mispronunciation sensitivity but stays relatively stable for onset and medial mispronunciaitons.
-For mispronunciations on the coda position it appears that mispronunciation sensitivity increases with age, but this is likely underpowered and therefore not detectable by our meta-analysis.
-
-Due to the small sample size of coda mispronunciations, we only included 3 age groups in Fisher's exact test.
-The results were significant, *p* `r psig(fish.test$p.value)`.
-Older infants were more likely to be tested on onset mispronunciations, while younger infants were more likely to be tested on medial mispronunciations.
-An onset mispronunciation may be more disruptive to lexical access than mispronunciations in subsequent positions (Marslen-Wilson & Zwitserlood, 1989), and therefore easier to detect.
-For this reason, it is rather unsuprising that onset mispronunciations show the greatest estimate of mispronunciation sensitivity.
-However, it also means that younger infants, who were more likely to be tested on medial mispronunciations, had a comparably harder task than older infants, who were more likely to be tested on onset mispronunciations.
-We return to this issue in the General Discussion.
-
-## (Insert Figure 7 about here)
-
-```{r PlotMispPosit}
-
-db_ET_MPl = dat %>%
-  filter(mispron_location == "onset"  | mispron_location == "medial"| mispron_location == "coda")
-
-db_ET_MPl$condition_label <- ifelse(db_ET_MPl$condition==1, "Correct", "Mispronunciation")
-
-db_ET_MPl$location_label <- ifelse(db_ET_MPl$mispron_location=="onset", "Onset",
-                                   ifelse(db_ET_MPl$mispron_location == "medial", "Medial", "Coda"))
-
-db_ET_MPl$location_label <- factor(db_ET_MPl$location_label, levels = c("Onset", "Medial", "Coda"))
-
-db_ET_MPl <- db_ET_MPl[,c("short_cite", "is_correct", "is_mp", "location_label", "condition_label", "g_calc", "weights_g", "mean_age_1", "n_1")]
-
-dat.c <- subset(db_ET_MPl, is_correct == 1)
-dat.m <- subset(db_ET_MPl, is_mp == 1)
-
-dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "location_label", "mean_age_1", "n_1"))
-
-dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
-dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
-
-ms.agg <- ggplot(dat.cm, aes(location_label, Misp_sensitivity, fill = location_label)) + 
-  #facet_grid(.~dv_label)+
-    geom_violin() + 
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
-  labs(title="a")+
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Misp. Sensitivity")
-
-ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = location_label)) + 
-    #facet_grid(.~dv_label)+
-  geom_point(aes(size = n_1),show.legend=FALSE) +
-  labs(title="b")+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Misp. Sensitivity")
-
-lay <- rbind(c(1), c(2))
-#lay <- rbind(c(1,2))
-
-  jpeg(filename = "figures/Figure_7_Misp_position.jpg",
-       width = 500, height = 600, units = "px")
-
-ger.plot.age <- grid.arrange(ms.agg, ms.age,
-                             layout_matrix = lay)
-
- dev.off()
-
-grid.draw(ger.plot.age)
-
-```
-
-### Type of mispronunciation (consonant or vowel)
-
-```{r CV_descript}
-
-CV_info <- dat %>%
-  group_by(type_feature) %>%
-  summarize(n_exp_conditions =  n())
-
-CV_location_info <- dat %>%
-  group_by(type_feature, mispron_location) %>%
-  summarize(n_exp_conditions =  n())
-
-```
-
-To assess whether the type of mispronunciation impacts sensitivity to mispronunciations, we calculated the meta-analytic effect for object identification in response to the type of mispronunciation.
-Although most theoretical discussion of mispronunciation type has focused on consonants and vowels, our dataset also included tone mispronunciations.
-In our analysis, we were interested in the difference between consonants and vowels, but also include an exploratory analysis of responses to tones, consonants, and vowels.
-Furthermore, sensitivity to consonant and vowel mispronunciations is hypothesized to differ depending on whether the infant is learning a Germanic or Romance language.
-We therefore conducted two sets of analyses, one analyzing consonants and vowels alone, a second including langauge family as a moderator, and a third comparing responses to tones with that of consonants and vowels, separately.
-For the latter analysis, tones were coded as the reference condition.
-We did not include data for which mispronunciation type varied within experiment and was not reported separately (*n* = `r with(CV_info, n_exp_conditions[type_feature == "consonant_and_vowel" | type_feature == "consonant_vowel_tone"])`).
-The analysis was therefore based on a subset of the overall dataset, with `r with(CV_info, n_exp_conditions[type_feature == "consonant"])` experimental conditions comparing a consonant mispronunciation, `r with(CV_info, n_exp_conditions[type_feature == "vowel"])` experimental conditions comparing a vowel mispronunciation, and `r with(CV_info, n_exp_conditions[type_feature == "tone"])` experimental conditions comparing a tone mispronunciation.
-Below, we first report the set of analyses comparing consonants with vowels and between language families before moving on to the set of exploratory analyses comparing tones with that of consonants and vowels.
-
-```{r MPtype_cv}
-
-# C vs. V with condition
-
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition, data = db_type, random = ~same_infant_calc | short_cite)
-
-sum_eff2 <- coef(summary(rma_TypeFeaturesMP_Condition))[4,]
-
-```
-
-```{r MPtype_cv_age}
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~same_infant_calc | short_cite)
-
-sum_eff_age <- coef(summary(rma_TypeFeaturesMP_Condition))[8,]
-
- # divide into age groups
-
- db_type$age_group <- ntile(db_type$mean_age_1, 4)
-
- type_ages <- db_type %>%
-  group_by(age_group, type_feature) %>%
-  summarize(n =  n())
-
- #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
-
- type_ages <- type_ages %>% spread(type_feature, n)
-
- #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
-fish.test <- fisher.test(type_ages, workspace=2e8)
-
-```
-
-To understand the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with mispronunciation type and condition as moderators.
-The moderator test was significant, `r mod_test(rma_TypeFeaturesMP_Condition)`, but the interaction between mispronunciation type and condition ($\beta$`r full_estimate(sum_eff2)`) was not significant.
-The results suggest that overall, infants' sensitivity to consonant and vowel mispronunciations was similar.
-
-We next examined whether age modulates mispronunciation sensitivity when the mispronunciation is a consonant or a vowel.
-When age was added as a moderator, the moderator test was significant, `r mod_test(rma_TypeFeaturesMP_Condition)` and the estimate for the three-way interaction between age, condition, and mispronunciation type was significant, but relatively small ($\beta$ = `r full_estimate(sum_eff_age)`.
-As can be seen in Figure \@ref(fig:PlotMispType)b, as infants age, mispronunciation sensitivity grows larger for vowel mispronunciations but stays steady for consonant mispronunciations.
-Noticeably, mispronunciation sensitivity appears greater for consonant compared to vowel mispronunciations at younger ages, but this difference diminishes as infants age.
-
-The results of Fisher's exact test were significant, *p* `r psig(fish.test$p.value)`.
-Older infants were more likely to be tested on consonant mispronunciations, while younger infants were more likely to be tested on vowel mispronunciations.
-It is not immediately clear whether the relationship between infant age and type of mispronunciation influences our estimate of how mispronunciation sensitivity changes with development.
-Whether consonant or vowel mispronunciations are more "difficult" is a matter of theoretical debate, but some evidence suggest that it may be influenced by infants' native language (Nazzi, Poltrock, & Von Holzen, 2016).
-We next examined whether this was the case.
-
-## (Insert Figure 8 about here)
-
-```{r PlotMispType}
-
-db_type = dat %>%
-  filter(type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-db_type$condition_label <- ifelse(db_type$condition==1, "Correct", "Mispronunciation")
-
-db_type$type_label <- ifelse(db_type$type_feature=="consonant", "Consonant", "Vowel")
-
-db_type <- db_type[,c("short_cite", "is_correct", "is_mp", "type_label", "condition_label", "g_calc", "weights_g", "mean_age_1", "n_1")]
-
-dat.c <- subset(db_type, is_correct == 1)
-dat.m <- subset(db_type, is_mp == 1)
-
-dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "type_label", "mean_age_1", "n_1"))
-
-dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
-dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
-
-ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
-  #facet_grid(.~dv_label)+
-    geom_violin() + 
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
-  labs(title="a")+
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Misp. Sensitivity")
-
-ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = type_label)) + 
-    #facet_grid(.~dv_label)+
-  geom_point(aes(size = n_1),show.legend=FALSE) +
-  labs(title="b")+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Misp. Sensitivity")
-
-lay <- rbind(c(1), c(2))
-#lay <- rbind(c(1,2))
-
-  jpeg(filename = "figures/Figure_8_CV.jpg",
-       width = 500, height = 600, units = "px")
-
-ger.plot.age <- grid.arrange(ms.agg, ms.age,
-                             layout_matrix = lay)
-
- dev.off()
-
-grid.draw(ger.plot.age)
-
-```
-
-```{r MPtype_cv_lang_descript}
-
-family <- dat %>%
-  group_by(lang_family) %>%
-  summarize(count = n())
-
-lang_family <- dat %>%
-  group_by(native_lang, lang_family) %>%
-  summarize(count = n())
-
-cv_family <- dat %>%
-  group_by(type_feature, lang_family) %>%
-  summarize(count = n())
-
-```
-
-```{r MPtype_cv_lang}
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-db_type <- subset(db_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeaturesMPC <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family, data = db_type, random = ~same_infant_calc | short_cite)
-
-sum_eff_fam <- coef(summary(rma_TypeFeaturesMPC))[7,]
-sum_eff_famcv <- coef(summary(rma_TypeFeaturesMPC))[8,]
-
-```
-
-```{r MPtype_cv_lang_age}
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-db_type <- subset(db_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeaturesMPC_age <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family*age.C, data = db_type, random = ~same_infant_calc | short_cite)
-
-sum_eff2_lang_age <- coef(summary(rma_TypeFeaturesMPC_age))[16,]
-
-# summary(glht(rma_TypeFeaturesMPC, linfct=cbind(contrMat(rep(1,8), type="Tukey"))), test=adjusted("none"))
-# 
-# ranef(rma_TypeFeaturesMPC)
-
-# divide into age groups
-
- db_type$age_group <- ntile(db_type$mean_age_1, 3)
-
- db_type$lang_cv <- paste(db_type$lang_family, db_type$type_feature, sep = "_")
-
- type_lang_ages <- db_type %>%
-  group_by(age_group, lang_cv) %>%
-  summarize(n =  n())
-
- #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
-
- type_lang_ages <- type_lang_ages %>% spread(lang_cv, n)
-
- #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
-fish.test <- fisher.test(type_lang_ages, workspace=2e8)
-
-```
-
-To examine whether infants' native language impacts sensitivity to consonant and vowel mispronunciations, we classified infants into language families.
-Infants learning American English (*n* = `r with(lang_family, count[native_lang == "American English"])`), British English (*n* = `r with(lang_family, count[native_lang == "British English"])`), Danish (*n* = `r with(lang_family, count[native_lang == "Danish"])`), Dutch (*n* = `r with(lang_family, count[native_lang == "Dutch"])`), and German (*n* = `r with(lang_family, count[native_lang == "German"])`) were classified into the Germanic language family (*n* = `r with(family, count[lang_family == "Germanic"])`).
-Infants learning Catalan (*n* = `r with(lang_family, count[native_lang == "Catalan"])`), Spanish (*n* = `r with(lang_family, count[native_lang == "Spanish"])`), French (*n* = `r with(lang_family, count[native_lang == "French"])`), Catalan and Spanish simultaneously (i.e.
-bilinguals; *n* = `r with(lang_family, count[native_lang == "Catalan-Spanish"])`), and Swiss French (*n* = `r with(lang_family, count[native_lang == "Swiss French"])`) were classified into the Romance language family (*n* = `r with(family, count[lang_family == "Romance"])`).
-
-We assessed whether the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity was modulated by language family.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family as additional moderators.
-The moderator test was significant, `r mod_test(rma_TypeFeaturesMPC)`.
-The interaction between condition and language family was significant ($\beta$`r full_estimate(sum_eff_fam)`), suggesting that the estimate for mispronunciation sensitivity was greater for infants learning a Romance compared to Germanic language.
-However, when a model evaluating this specific interaction, without mispronunciation type, was calculated, the estimate was much smaller and not significant.
-This suggests that the interaction between condition and language family may be over-estimated.
-The three-way interaction between mispronunciation type, condition, language family was large and also significant , $\beta$`r full_estimate(sum_eff_famcv)`.
-As can be seen in Figure \@ref(fig:PlotCVEffect_Lang)a, mispronunciation sensitivity for consonants was similar for Germanic and Romance languages.
-Mispronunciation sensitivity for vowels, however, was greater for Germanic compared to Romance languages.
-
-Finally, we examined the relationship between language family and infant age and mispronunciation sensitivity to consonants and vowels.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family and age as additional moderators.
-The moderator test was significant, `r mod_test(rma_TypeFeaturesMPC_age)`, and the estimate for the four-way interaction between mispronunciation type, condition, language family, and age was small, but significant , $\beta$`r full_estimate(sum_eff2_lang_age)`.
-As can also be seen in Figure \@ref(fig:PlotCVEffect_Lang)b, for infants learning Germanic languages, sensitivity to consonant and vowel mispronunciations did not change with age.
-In contrast, infants learning Romance languages show a decrease in sensitivity to consonant mispronunciations, but an increase in sensitivity to vowel mispronunciations with age.
-
-We were unable to use Fisher's exact test to evaluate whether infants of different ages were more or less likely to be tested on consonant or vowel mispronunciations depending on their native language.
-This was due to the small sample size of infants learning Romance languages (*n* = `r with(family, count[lang_family == "Romance"])`).
-
-## (Insert Figure 9 about here)
-
-```{r PlotCVEffect_Lang}
-
-db_type = dat %>%
-  filter(type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-db_type <- subset(db_type, lang_family != "Sino-Tibetian")
-
-db_type$condition_label <- ifelse(db_type$condition==1, "Correct", "Mispronunciation")
-
-db_type$type_label <- ifelse(db_type$type_feature=="consonant", "Consonant", "Vowel")
-
-db_type <- db_type[,c("short_cite", "is_correct", "is_mp", "type_label", "condition_label", "lang_family", "g_calc", "weights_g", "mean_age_1", "n_1")]
-
-dat.c <- subset(db_type, is_correct == 1)
-dat.m <- subset(db_type, is_mp == 1)
-
-dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "type_label", "lang_family", "mean_age_1", "n_1"))
-
-dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
-dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
-
-ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
-  facet_grid(.~lang_family)+
-    geom_violin() + 
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
-  labs(title="a")+
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Hedges' g")
-
-ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = type_label)) + 
-  facet_grid(.~lang_family)+
-  geom_point(aes(size = n_1),show.legend=FALSE) +
-  labs(title="b")+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Hedges' g")
-
-lay <- rbind(c(1), c(2))
-#lay <- rbind(c(1,2))
-
-  jpeg(filename = "figures/Figure_9_LangCV.jpg",
-       width = 500, height = 600, units = "px")
-
-ger.plot.age <- grid.arrange(ms.agg, ms.age,
-                             layout_matrix = lay)
-
- dev.off()
-
-grid.draw(ger.plot.age)
-
-```
-
-```{r MPtype_cvt}
-
-# C vs. V vs. T with condition
-
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel"| type_feature == "tone")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("tone", "consonant", "vowel"))
-
-rma_TypeFeaturesMP_ConditionT <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition, data = db_type, random = ~same_infant_calc | short_cite)
-
-sum_eff2c <- coef(summary(rma_TypeFeaturesMP_ConditionT))[5,]
-sum_eff2v <- coef(summary(rma_TypeFeaturesMP_ConditionT))[6,]
-
-```
-
-```{r MPtype_cvt_age}
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" | type_feature == "tone")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("tone", "consonant", "vowel"))
-
-rma_TypeFeaturesMP_Condition_age <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~same_infant_calc | short_cite)
-
-sum_eff_tc <- coef(summary(rma_TypeFeaturesMP_Condition))[11,]
-sum_eff2_tv <- coef(summary(rma_TypeFeaturesMP_Condition))[12,]
-
-```
-
-Although we had no predictions regarding mispronunciation sensitivity to tone mispronunciations, we included an exploratory analysis to examine whether responses to tone mispronunciations were different from that of consonants or vowels.
-When mispronunciation type (tone, consonant, vowel) and condition (correct, mispronunciation) were included as moderators, the moderator test was significant, `r mod_test(rma_TypeFeaturesMP_ConditionT)`.
-The interactions between condition and consonant mispronunciations ($\beta$ = `r full_estimate(sum_eff2c)`) as well as vowel mispronunciations ($\beta$ = `r full_estimate(sum_eff2v)`), were not significant, suggesting that there was no difference in looks to the target in response to tone mispronunciations compared with consonant or vowel mispronunciations.
-
-We further included an exploratory analysis of the relationship between infant age and the impact of tone mispronunciations in comparison to consonant and vowel mispronunciations.
-We included mispronunciation type, condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, `r mod_test(rma_TypeFeaturesMP_ConditionT)`, but the interactions between condition, age, and both consonant ($\beta$ = `r full_estimate(sum_eff_tc$estimate)`) and vowel ($\beta$ = `r full_estimate(sum_eff_tv$estimate)`) mispronunciations were not significant.
-Infants' sensitivity to tone mispronunciations compared to consonant or vowel mispronunciations did not differ with age.
-
-### Interim discussion: Moderator analyses
-
-Next to the main goal of this paper, which was to evaluate the development of infants' sensitivity to mispronunciations, we also investigated the more nuanced questions often posed in studies investigating infants' mispronunciation sensitivity.
-We identified five additional manipulations often present in mispronunciation sensitivity studies and investigated the how those manipulations modulated mispronunciation sensitivity and whether this changed with infant age.
-Furthermore, considering the lack of developmental change found in our main analysis, we evaluted whether these additional manipulations were disproportionatly conducted with children of different ages, to assess whether older infants recieve more difficult tasks than younger infants.
-
-To briefly summarize, mispronunciation sensitivity was modulated overall by the size of the mispronunciation tested, whether target-distractor pairs shared phonological overlap, and the position of the mispronunciation.
-Neither distractor familiarity (familiar, unfamiliar) or type of mispronunciation (consonant, vowel, tone) were found to impact mispronunciation sensitivity.
-The developmental trajectory of mispronunciation sensitivity was influenced by whether target-distractor pairs shared phonological overlap and type of mispronunciation, but mispronunciation size, mispronunciation position, and distractor familiarity were found to have no influence.
-Finally, in some cases there was evidence that older and younger infants were given experimental manipulations that may have rendered the experimental task more or less difficult.
-Specifically, older children were more likely to be given target-distractor pairs that overlapped on their onset phoneme, a situation in which it is more difficult to detect a mispronunciation.
-Yet, this was not always the case; in a different instance, younger infants were given a more difficult task, mispronunciations on the medial position.
-We return to these findings in the General Discussion.
-
-We next considered whether an effect of maturation might have been masked by other factors we have not yet captured in our analyses.
-A strong candidate that emerged during the construction of the present dataset and careful reading of the original papers was the analysis approach.
-We observed, as mentioned in the Methods section, large variation in the dependent variable reported, and additionally noted that the size of the chosen post-naming analysis window varied substantially across papers.
-Researchers might adapt their analysis strategy to infants' age or they might be influenced by having observed the data.
-For example, consider the possibility that there is a true increase in mispronunciation sensitivity over development.
-In this scenario, younger infants should show no or only little sensitivity to mispronunciations while older infants would show a large sensitivity to mispronunciations.
-This lack of or small mispronunciation sensitivity in younger infants is likely to lead to non-significant results, which would be more difficult to publish [@Ferguson2012].
-In order to have publishable results, adjustments to the analysis approach could be made until a significant, but spurious, effect of mispronunciation sensitivity is found.
-This would lead to an increase in significant results and alter the observed developmental trajectory of mispronunciation sensitivity.
-Such a scenario is in line with the publication bias we observe [@Simmons2011].
-We examine whether variation in the approach to data analysis may be have an influence on our conclusions regarding infants’ developing mispronunciation sensitivity.
-
-We included details related to timing and type of dependent variable in our coding of the dataset because they are consistently reported and might be useful for experiment design in the future by highlighting typical choices and helping establish field standards.
-In the following section, we include an exploratory analysis to investigate the possibility of systematic differences in the approach to analysis in general and across infant age.
-The purpose of this analysis was to better understand the influence of choices made in analyzing mispronunciation sensitivity studies as well as the influence these choices may have on our understanding of mispronunciation sensitivity development.
-
-## Exploratory Analyses
-
-We identified two sets of variables which varied across papers to assess the influence of data analysis choices on resulting effect size: timing (post-naming analysis window; offset time) and which dependent variable(s) were reported.
-In the following, we discuss the possible theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these analysis choices may have on measurements of mispronunciation sensitivity development.
-We focus specifically on the size of the mispronunciation sensitivity effect, considering the whole dataset and including condition (correct pronunciation, mispronunciation) as moderator.
-
-### Timing
-
-```{r time_choices_info}
-
-# can't call reshape earlier, because it will interfere with other libraries
-library(reshape)
-
-# trial length
-dat$post_nam_actual <- dat$trial_length - dat$pre_nam_dur
-
-post_length_info <- dat %>%
-  group_by(post_nam_actual) %>%
-  summarize(n_exp_conditions =  n())
-        #post_naming = paste(unique(post_nam_dur), collapse=', '))
-
-trial.l <- cor.test(dat$post_nam_actual, dat$mean_age_1)
-
-tdl <- dat[,c("short_cite", "post_nam_actual", "post_nam_dur")]
-tdl <- melt(tdl, id = "short_cite")
-
-trial_length_hist <- ggplot(dat,aes(x=value)) + 
-  apatheme+
-    geom_histogram(data=subset(tdl,variable == 'post_nam_actual'),fill = "red", alpha = 0.5) +
-    geom_histogram(data=subset(tdl,variable == 'post_nam_dur'),fill = "blue", alpha = 0.5)
-
-# post-naming
-post_name_info <- dat %>%
-  group_by(post_nam_dur) %>%
-  summarize(n_exp_conditions =  n())
-        #post_naming = paste(unique(post_nam_dur), collapse=', '))
-
-post.l <- cor.test(dat$post_nam_dur, dat$mean_age_1)
-post_nam_dur.plot <- ggplot(dat, aes(post_nam_dur, age.C)) + geom_point() +geom_smooth(method = "lm")
-
-# difference post vs. trial length
-dat$post_trial_match <- ifelse(dat$post_nam_dur == dat$post_nam_actual, "same", "different")
-dat$post_trial_prop <- dat$post_nam_dur/(dat$trial_length-dat$pre_nam_dur)
-
-post_trial_match_info <- dat %>%
-  group_by(post_trial_match) %>%
-  summarize(n_exp_conditions =  n())
-        #post_naming = paste(unique(post_nam_dur), collapse=', '))
-
-post_trial_prop_info <- dat %>%
-  group_by(post_trial_prop) %>%
-  summarize(n_exp_conditions =  n())
-        #post_naming = paste(unique(post_nam_dur), collapse=', '))
-
-post_match.l <- cor.test(dat$post_trial_prop, dat$mean_age_1)
-post_match.plot <- ggplot(subset(dat, post_trial_prop != 1), aes(post_trial_prop, age.C)) + geom_point() +geom_smooth(method = "lm")
-
-# offset
-offset_info <- dat %>%
-  group_by(offset) %>%
-  summarize(n_exp_conditions =  n())
-        #post_naming = paste(unique(post_nam_dur), collapse=', '))
-
-dob <- subset(dat, !is.na(offset) & offset < 1000)
-dob$offset_bin <- ifelse(dob$offset <371 & dob$offset > 359, 367, dob$offset)
-
-# offset
-offset_bin_info <- dob %>%
-  group_by(offset_bin) %>%
-  summarize(n_exp_conditions =  n())
-        #post_naming = paste(unique(post_nam_dur), collapse=', '))
-
-offset.l <- cor.test(dat$offset, dat$mean_age_1)
-offset.plot <- ggplot(dat, aes(offset, age.C)) + geom_point() +geom_smooth(method = "lm")
-
-detach("package:reshape", unload=TRUE)
-
-```
-
-In a typical trial in a mispronunciation sensitivity study, the target-distractor image pairs are first presented in silence, followed by auditory presentation of a carrier phrase or isolated presentation of the target word (correctly pronounced or mispronounced).
-When designing mispronunciation sensitivity studies, experimenters can choose the length of time each trial is presented.
-This includes both the length of time before the target object is named (pre-naming phase) as well as after (post-naming phase) and is determined prior to data collection.
-To examine the size of the time window analyzed in the post-naming phase (post-naming analysis window), we must first consider overall length of time in post-naming (post-naming time window), because it limits the overall time window available to analyze and might thus predict the post-naming analysis window.
-Across papers, the length of the post-naming time window varied from `r with(post_length_info, min(post_nam_actual))*1000` to `r with(post_length_info, max(post_nam_actual))*1000` ms, with a median value of `r with(dat, median(post_nam_actual))*1000` ms.
-The most popular post-naming time window length was `r with(dat, getmode(post_nam_actual))*1000` ms, used in `r with(post_length_info, n_exp_conditions[post_nam_actual == getmode(post_length_info$n_exp_conditions)])` experimental conditions.
-There was no apparent relation between infant age and post-naming time window length (*r* = `r trial.l$estimate`, 95% CI[`r trial.l$conf.int[1]`, `r trial.l$conf.int[2]`], *p* `r psig(trial.l$p.value)`).
-
-Unlike the post-naming time window, the post-naming analysis window can be chosen after the experimental data is collected.
-Interestingly, half of the experimental conditions were analyzed using the whole post-naming time window of the trial presented to the infant (*n* = `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`), while the other half were analyzed using a shorter portion of the post-naming time window, usually excluding later portions (*n* = `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`).
-Across papers, the length of the post-naming analysis window varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a median value of `r with(dat, median(post_nam_dur))*1000` ms.
-The most popular post-naming analysis window length was `r with(dat, getmode(post_nam_dur))*1000` ms, used in `r with(post_name_info, n_exp_conditions[post_nam_dur == with(dat, getmode(post_nam_dur))])` experimental conditions.
-There was an inverse relationship between infant age and post-naming analysis window length, such that younger infants' looking times were analyzed using a longer post-naming analysis window, here the relationship was significant (*r* = `r post.l$estimate`, 95% CI[`r post.l$conf.int[1]`, `r post.l$conf.int[2]`], *p* `r psig(post.l$p.value)`).
-The choice to use a shorter post-naming analysis window with age is likely related to evidence that speed of processing is slower in younger infants [@Fernald1998].
-To summarize, we observe variation in time-related analysis decisions related to infants' age.
-
-Another potential source of variation in studies that analyze eye-movements is the amount of time it takes for an eye movement to be initiated in response to a visual stimulus, which we refer to as offset time.
-Previous studies examining simple stimulus response latencies first determined that infants require at least 233 ms to initiate an eye-movement in response to a stimulus [@Canfield1991].
-In the first infant mispronunciation sensitivity study, @Swingley2000 used an offset time of 367 ms, which was "an 'educated guess' based on studies .
-.
-.
-showing that target and distractor fixations tend to diverge at around 400 ms." [@Swingley2000, p.
-155].
-Upon inspecting the offset time values used in the papers in our meta-analysis, the majority used a similar offset time value (between 360 and 370 ms) for analysis (*n* = `r with(offset_bin_info, n_exp_conditions[offset_bin == "367"])`), but offset values ranged from `r with(offset_bin_info, min(offset_bin))` to `r with(offset_bin_info, max(offset_bin))` ms, and were not reported for `r with(offset_info, n_exp_conditions[is.na(offset)])` experimental conditions.
-We note that @Swingley2009 also included offset values of 1133 ms to analyze responses to coda mispronunciations.
-There was an inverse relationship between infant age and size of offset, such that younger infants were given longer offsets, although this correlation was not significant (*r* = `r offset.l$estimate`, 95% CI[`r offset.l$conf.int[1]`, `r offset.l$conf.int[2]`], *p* `r psig(offset.l$p.value)`).
-This lack of a relationship is possibly driven by the field's consensus that an offset of about 367 ms is appropriate for analyzing word recognition with PTL measures, including studies that evaluate mispronunciation sensitivity.
-
-Although there are a priori reasons to choose the post-naming analysis window (infant age) or offset time (previous studies), these choices may occur after data collection and might therefore lead to a higher rate of false-positives [@Gelman2013].
-Considering that these choices were systematically different across infant ages, at least for the post-naming analysis window, we next explored whether the post-naming analysis window length or the offset time influenced our estimate of infants’ sensitivity to mispronunciations.
-
-#### Post-naming analysis window length
-
-```{r time_post}
-
-rma_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur), data = db_ET_MP, random = ~same_infant_calc | short_cite)
-
- rma_post_dur_eff <- coef(summary(rma_post_dur))[2,]
-
- rma_post_dur_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur)*condition, data = dat, random = ~same_infant_calc | short_cite)
-
-  rma_post_dur_MS_eff <- coef(summary(rma_post_dur_MS))[4,]
-
-  # age
-
- rma_post_dur_AGE <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur)*age.C, data = db_ET_MP, random = ~same_infant_calc | short_cite)
-
-   rma_post_dur_AGE_eff <- coef(summary(rma_post_dur_MS))[4,]
-
-  rma_post_dur_AGE_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur)*age.C*condition, data = dat, random = ~same_infant_calc | short_cite)
-
-    rma_post_dur_AGE_MS_eff <- coef(summary(rma_post_dur_AGE_MS))[8,]
-
-# First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images, including post-naming time window size as a moderator.
-The moderator test was not significant `r mod_test(rma_post_dur)` and the estimate for post-naming phase size was relatively small, $\beta$`r full_estimate(rma_post_dur_eff)`.
-
-#[Christina] Even if a test is not significant, this next sentence is always wrong because we did not test whether it's the same (i.e. we did not do an equivalence or Bayesian test!)
-#This suggests that upon hearing a mispronunciation, infants' looks to the target image did not differ as a result of the size of the post-naming time window analyzed.
-We next assessed whether post-naming phase size was related to mispronunciation sensitivity.
-
-#[Christina] To be sure, you base this again on the combined data and only plot differences for easier visualizations in figure 3?
-Ideally make that clear.
-Also, some suggestions to vary this sentence (also earlier in the paper)
-#"To investigate mispronunciation sensitivity, we considered data from both conditions in a joint analysis"
-#"Analyzing all data with condition (c, mp) as additional moderator leads to the following results"
-#etcetc
-
-# For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant `r mod_test(rma_post_dur_AGE)`, and a small estimate for the interaction between age and size of post-naming phase ($\beta$`r full_estimate(rma_post_dur_AGE_eff)`.
-This suggests that upon hearing a mispronunciation, infant measured looks to the target image were similar, regardless of infant age or size of the post-naming phase analyzed.
-We next assessed whether the relationship between size of the post-naming phase analyzed and mispronunciation sensitivity was modulated by age.
-
-```
-
-We first assessed whether size of the post-naming analysis window had an impact on the overall size of the reported mispronunciation sensitivity.
-We considered data from both conditions in a joint analysis and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant (`r mod_test(rma_post_dur_MS)`).
-The estimate for the interaction between post-naming analysis window and condition was small but significant ($\beta$`r full_estimate(rma_post_dur_MS_eff)`).
-This relationship is plotted in Figure \@ref(fig:Plot-post-name-cond-age)a.
-The results suggest that the size of the post-naming analysis window significantly impacted our estimate of mispronunciation sensitivity.
-Specifically, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) was significantly greater when the post-naming analysis window was shorter.
-
-Considering that we found a significant relationship between the length of the post-naming analysis window and infant age, such that younger ages had a longer window of analysis, we next examined whether the size of the post-naming analysis window modulated the estimated size of mispronunciation sensitivity as infant age changed.
-We therefore included age as additional moderator of the previous analysis.
-The moderator test was significant (`r mod_test(rma_post_dur_AGE_MS)`).
-The estimate for the  three-way-interaction between condition, size of the post-naming analysis window, and age was small, but significant ($\beta$ `r full_estimate(rma_post_dur_AGE_MS_eff)`).
-As can be seen in Figure \@ref(fig:Plot-post-name-cond-age)b, a smaller post-naming analysis window leads to a greater increase in measured mispronunciation sensitivity with development.
-For example, when experimental conditions were analyzed with a post-naming analysis window of 2000 ms or less, mispronunciation sensitivity seems to increase with infant age.
-If the post-naming analysis window is greater than 2000 ms, however, there is no or a negative relation of mispronunciation sensitivity and age.
-In other words, all three possible developmental hypotheses might be supported depending on analysis choices made regarding the size of the post-naming analysis window.
-This is especially important, considering that our key question is how mispronunciation sensitivity changes with development.
-These results suggest that conclusions about the relationship between infant age and mispronunciation sensitivity may be mediated by the size of the post-naming analysis window.
-
-## (Insert Figure 10 about here)
-
-```{r Plot-post-name-cond-age, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different lengths of the post-naming analysis window: 2000 ms or less (orange), 2001 to 3000 ms (blue), and 3001 ms or greater (green).
-Although length of the post-naming analysis window was included as a continuous variable in the meta-analytic model, it is divided into categories for ease of viewing.
-Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity as a function of age.
-The lines plot the linear regression and the gray shaded area indicates the standard error.", results="hide"}
-
-dat$condition_label <- ifelse(dat$condition==1, "Correct", "Mispronunciation")
-
-dat$post_size <- ifelse(dat$post_nam_dur <= 2, "2000 ms or less",
-                       ifelse(dat$post_nam_dur > 2 & dat$post_nam_dur <= 3, "2001-3000 ms", "3001 ms or greater"))
-
-dat$post_size <- factor(dat$post_size, levels = c("2000 ms or less", "2001-3000 ms", "3001 ms or greater"))
-
-dat.cm <- dat[,c("short_cite", "is_correct", "is_mp", "post_size", "condition", "g_calc", "weights_g", "mean_age_1", "n_1")]
-
-dat.c <- subset(dat.cm, is_correct == 1)
-dat.m <- subset(dat.cm, is_mp == 1)
-
-dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "post_size", "mean_age_1", "n_1"))
-
-dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
-dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
-
-p.MS <- ggplot(dat.cm, aes(post_size, Misp_sensitivity, fill = post_size)) + 
-  #facet_grid(.~post_size)+
-    geom_violin() + 
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
-  labs(title="a")+
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "none",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Misp. Sensitivity")
-
-p.AGE <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = post_size)) + 
-    #facet_grid(.~post_size)+
-  geom_point(aes(size = weight),show.legend=FALSE) +
-  labs(title="b")+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Misp. Sensitivity")
-
-lay <- rbind(c(1), c(2))
-#lay <- rbind(c(1,2))
-
-  jpeg(filename = "figures/Figure_10_Post_name_size.jpg", 
-       width = 600, height = 600, units = "px")
-
-ger.plot.age <- grid.arrange(p.MS, p.AGE,
-                             layout_matrix = lay)
-
-dev.off()
-
-grid.draw(ger.plot.age)
-
-```
-
-#### Onset time after target naming
-
-```{r time_onset}
-
-rma_offset <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset), data = db_ET_MP, random = ~same_infant_calc | short_cite)
-
-rma_offset_eff <- coef(summary(rma_offset))[2,]
-
- rma_offset_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*condition, data = dat, random = ~same_infant_calc | short_cite)
-
-  rma_offset_MS_eff <- coef(summary(rma_offset_MS))[4,]
-
-  # age
-
- rma_offset_AGE <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*age.C, data = db_ET_MP, random = ~same_infant_calc | short_cite)
-
-   rma_offset_AGE_eff <- coef(summary(rma_offset_AGE))[4,]
-
-  rma_offset_AGE_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*age.C*condition, data = dat, random = ~same_infant_calc | short_cite)
-
-    rma_offset_AGE_MS_eff <- coef(summary(rma_offset_AGE_MS))[8,]
-
-```
-
-We next assessed whether the time between target naming and the start of the analysis, namely offset time, had an impact on the size of the reported mispronunciation sensitivity.
-When we included both condition and offset time as moderators, the moderator test was significant (`r mod_test(rma_post_dur_MS)`), but the estimate for the interaction between offset time and condition was zero ($\beta$`r full_estimate(rma_offset_MS_eff)`).
-Although we found no relationship between offset time and infant age, we also examined whether the size of offset time modulated the measure of mispronunciation sensitivity over infant age.
-When both offset time and condition were included as moderators, the moderator test was significant (`r mod_test(rma_offset_AGE_MS)`), but the three-way-interaction between condition, offset time, and age was again zero ($\beta$ `r full_estimate(rma_offset_AGE_MS_eff)`).
-Taken together, these results suggest that offset time does not modulate measured mispronunciation sensitivity.
-There is no relationship between offset time and age, and we find no influence of offset time on the estimated size of mispronunciation sensitivity over age.
-We again point out that there is a substantial field consensus, which might mask any relationship.
-
-### Dependent variable-related analyses
-
-```{r dv_info}
-
-dv_info <- dat %>%
-  group_by(within_measure) %>%
-  summarize(n_exp_conditions =  n())
-
-dv.l <- summary(lm(age.C ~ within_measure, data = dat))
-
-dv.age.plot <- ggplot(dat, aes(within_measure, age.C)) +     geom_violin() + 
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)
-
-```
-
-Mispronunciation studies evaluate infants' proportion of target looks (PTL) in response to correct and mispronounced words.
-Experiments typically include a phase where a naming event has not yet occurred, which we refer to as the pre-naming phase.
-This is followed by a naming event, whether correctly pronounced or mispronounced, and the subsequent phase we refer to as the post-naming phase.
-The purpose of the pre-naming phase is to ensure that infants do not have systematic preferences for the target or distractor (greater interest in a cat compared to a cup) which may drive PTL scores in the post-naming phase.
-As described in the Data Analysis sub-section of the Methods, however, there was considerable variation across papers in whether this pre-naming phase was used as a baseline measurement, or whether a different baseline measurement was used.
-This resulted in different measured outcomes or dependent variables.
-Over half of the experimental conditions (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post_naming_effect"])`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase, resulting in a Difference Score.
-The Difference Score is one value, which is then compared with a chance value of 0.
-When positive, this indicates that infants increased their looks to the target after hearing the naming label (correct or mispronounced) relative to the pre-naming baseline PTL.
-In contrast, Pre vs.
-Post (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` experimental conditions), directly compare the post- and pre-naming PTL scores with one another using a statistical test (e.g.
-t-test, ANOVA).
-This requires two values, one for the pre-naming phase and one for the post-naming phase.
-A greater post compared to pre-naming phase PTL indicates that infants increased their target looks after hearing the naming label.
-The remaining experimental conditions used a Post dependent variable (*n* = `r with(dv_info, n_exp_conditions[within_measure == "post"])` experimental conditions), which compares the post-naming PTL score with a chance value of 50%.
-Here, the infants' pre-naming phase baseline preferences are not considered and instead target fixations are evaluated based on the likelihood to fixate one of two pictures (50%).
-As most papers do not specify whether these calculations are made before or after aggregating across trials, we make no assumptions about when this step is taken.
-
-The Difference Score and Pre vs.
-Post can be considered similar to one another, in that they are calculated on the same type of data and consider pre-naming preferences.
-It should be noted, however, that the Difference Score may better counteract participant- and item-level differences, whereas Pre vs.
-Post is a group-level measure.
-The Post dependent variable, in contrast, does not consider pre-naming baseline preferences.
-To our knowledge, there is no theory or evidence that explicitly drives choice of dependent variable in analysis of mispronunciation sensitivity, which may explain the wide variation in dependent variable reported in the papers included in this meta-analysis.
-We next explored whether the type of dependent variable calculated influenced the estimated size of sensitivity to mispronunciations.
-Considering that the dependent variable Post differs in its consideration of pre-naming baseline preferences, substituting these for a chance value, we directly compared mispronunciation sensitivity between Post as a reference condition and both Difference Score and Pre vs.
-Post dependent variables.
-
-```{r dependent_variable}
-
-dat$dv_label <- ifelse(dat$within_measure=="post", "Post",
-                       ifelse(dat$within_measure == "pre_post", "Post vs. Pre",
-                              "Difference Score"))
-
-dat$dv_label <- factor(dat$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
-
-db_ET_MP$dv_label <- ifelse(db_ET_MP$within_measure=="post", "Post",
-                       ifelse(db_ET_MP$within_measure == "pre_post", "Post vs. Pre",
-                              "Difference Score"))
-
-db_ET_MP$dv_label <- factor(db_ET_MP$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
-
-#
-
-rma_within <- rma.mv(g_calc, g_var_calc, mods = ~dv_label, data = db_ET_MP, random = ~same_infant_calc | short_cite)
-
-rma_within_effprepost <- coef(summary(rma_within))[2,]
-rma_within_effdiff <- coef(summary(rma_within))[3,]
-
- rma_within_MS <- rma.mv(g_calc, g_var_calc, mods = ~dv_label*condition, data = dat, random = ~same_infant_calc | short_cite)
-
-  rma_within_MS_effprepost <- coef(summary(rma_within_MS))[5,]
-  rma_within_MS_effdiff <- coef(summary(rma_within_MS))[6,]
-
-  # age
-
- rma_within_AGE <- rma.mv(g_calc, g_var_calc, mods = ~dv_label*age.C, data = db_ET_MP, random = ~same_infant_calc | short_cite)
-
-   rma_within_AGE_effprepost <- coef(summary(rma_within_AGE))[5,]
-   rma_within_AGE_effdiff <- coef(summary(rma_within_AGE))[6,]
-
-  rma_within_AGE_MS <- rma.mv(g_calc, g_var_calc, mods = ~dv_label*age.C*condition, data = dat, random = ~same_infant_calc | short_cite)
-
-    rma_within_AGE_MS_effprepost <- coef(summary(rma_within_AGE_MS))[11,]
-    rma_within_AGE_MS_effdiff <- coef(summary(rma_within_AGE_MS))[12,]
-
-```
-
-We first assessed whether the choice of dependent variable had an impact on the size of estimated mispronunciation sensitivity.
-When we included both condition and dependent variable as moderators, the moderator test was significant (`r mod_test(rma_within_MS)`).
-The estimate for the interaction between Pre vs.
-Post and condition was significantly smaller than that of the Post dependent variable ($\beta$`r full_estimate(rma_within_MS_effprepost)`), but the difference between the Difference Score and Post in the interaction with condition was small and not significant ($\beta$`r full_estimate(rma_within_MS_effdiff)`).
-This relationship is plotted in Figure \@ref(fig:Plot-Within-cond-age-diff-score)a.
-The results suggest that the reported dependent variable significantly impacted the size of the estimated mispronunciation sensitivity effect, such that studies reporting the Post.
-vs.
-Pre dependent variable showed a smaller mispronunciation sensitivity effect than those reporting Post, but that there was no difference between the Difference Score and Post dependent variables.
-
-We next examined whether the type of dependent variable calculated modulated the estimated change in mispronunciation sensitivity over infant age.
-When age was included as an additional moderator, the moderator test was significant (`r mod_test(rma_within_AGE_MS)`).
-The estimate for the interaction between Pre vs.
-Post, condition, and age was significantly smaller than that of the Post dependent variable ($\beta$`r full_estimate(rma_within_AGE_MS_effprepost)`), but the difference between the Difference Score and Post in the interaction with condition and age was small and not significant ($\beta$`r full_estimate(rma_within_AGE_MS_effdiff)`).
-This relationship is plotted in Figure \@ref(fig:Plot-Within-cond-age-diff-score)b.
-When the dependent variable reported was Pre vs.
-Post, mispronunciation sensitivity was found to decrease with infant age, while in comparison, when the dependent variable was Post, mispronunciation sensitivity was found to increase with infant age.
-There was no difference in the estimated mispronunciation sensitivity change with infant age between the Post and Difference Score dependent variables.
-
-Similar to the length of the post-naming analysis window, all three possible developmental hypotheses might be supported depending on the dependent variable reported.
-In other words, choice of dependent variable may influence the conclusion drawn regarding how mispronunciation sensitivity may change with infant age.
-
-## (Insert Figure 11 about here)
-
-```{r Plot-Within-cond-age-diff-score, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (orange), Post vs.
-Pre (blue), and Difference Score (green).
-Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity as a function of age.
-The lines plot the linear regression and the gray shaded area indicates the standard error.", results="hide"}
-
-dat.cm <- dat[,c("short_cite", "is_correct", "is_mp", "within_measure", "condition", "g_calc", "weights_g", "mean_age_1", "n_1")]
-
-dat.c <- subset(dat.cm, is_correct == 1)
-dat.m <- subset(dat.cm, is_mp == 1)
-
-dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "within_measure", "mean_age_1", "n_1"))
-
-dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
-
-dat.cm$condition_label <- ifelse(dat.cm$is_correct.x==1, "Correct", "Mispronunciation")
-
-dat.cm$dv_label <- ifelse(dat.cm$within_measure=="post", "Post",
-                       ifelse(dat.cm$within_measure == "pre_post", "Post vs. Pre",
-                              "Difference Score"))
-
-dat.cm$dv_label <- factor(dat.cm$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
-
-ms.agg <- ggplot(dat.cm, aes(dv_label, Misp_sensitivity, fill = dv_label)) + 
-  #facet_grid(.~dv_label)+
-    geom_violin() + 
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
-  labs(title="a")+
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Misp. Sensitivity")
-
-ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = dv_label)) + 
-    #facet_grid(.~dv_label)+
-  geom_point(aes(size = n_1),show.legend=FALSE) +
-  labs(title="b")+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Misp. Sensitivity")
-
-lay <- rbind(c(1), c(2))
-#lay <- rbind(c(1,2))
-
-  jpeg(filename = "figures/Figure_11_Dependent_variable.jpg", 
-       width = 500, height = 600, units = "px")
-
-ger.plot.age <- grid.arrange(ms.agg, ms.age,
-                             layout_matrix = lay)
-
-dev.off()
-
-grid.draw(ger.plot.age)
-
-```
-
-```{r reanalysis_misp_sens_dv_label}
-
-## Controlling for analysis choices
-
-#[Christina: Do you want to add this section?]
-#[Katie: From what I came up with, it makes no difference to the conclusions we make in the regular models.
-But, I am not sure I did it right.
-I don't really feel like they have to be included, but if you think it would be good, then we can work on it.]
-
-dat$dv_label <- ifelse(dat$within_measure=="post", "Post",
-                       ifelse(dat$within_measure == "pre_post", "Post vs. Pre",
-                              "Difference Score"))
-
-dat$dv_label <- factor(dat$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
-
-db_ET_MP$dv_label <- ifelse(db_ET_MP$within_measure=="post", "Post",
-                       ifelse(db_ET_MP$within_measure == "pre_post", "Post vs. Pre",
-                              "Difference Score"))
-
-db_ET_MP$dv_label <- factor(db_ET_MP$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
-
-db_ET_correct$dv_label <- ifelse(db_ET_correct$within_measure=="post", "Post",
-                       ifelse(db_ET_correct$within_measure == "pre_post", "Post vs. Pre",
-                              "Difference Score"))
-
-db_ET_correct$dv_label <- factor(db_ET_correct$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
-
-rma_correct_DV = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
-
-#anova(rma_correct_DV, rma_correct)
-
-rma_MP_DV = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
-
-#anova(rma_MP_DV, rma_MP)
-
-rma_MPeffect_DV <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
-
-#anova(rma_MPeffect_DV, rma_MPeffect)
-
-rma_correct_age_DV = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
-
-#anova(rma_correct_age_DV, rma_correct_age)
-
-rma_MP_age_DV = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
-
-#anova(rma_MP_age_DV, rma_MP_age)
-
-rma_MPeffect_age_DV <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))
-
-#anova(rma_MPeffect_age_DV, rma_MPeffect_age)
-
-```
-
-```{r reanalysis_misp_sens_post_dur}
-
-rma_correct_post_dur = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
-
-#anova(rma_correct_post_dur, rma_correct)
-
-rma_MP_post_dur = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
-
-#anova(rma_MP_post_dur, rma_MP)
-
-rma_MPeffect_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
-
-#anova(rma_MPeffect_post_dur, rma_MPeffect)
-
-rma_correct_age_post_dur = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
-
-#anova(rma_correct_age_post_dur, rma_correct_age)
-
-rma_MP_age_post_dur = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
-
-#anova(rma_MP_age_post_dur, rma_MP_age)
-
-rma_MPeffect_age_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))
-
-#anova(rma_MPeffect_age_post_dur, rma_MPeffect_age)
-
-```
-
-# General Discussion
-
-In this meta-analysis, we set out to quantify and assess the developmental trajectory of infants’ sensitivity to mispronunciations.
-Overall, the results of the meta-analysis showed that infants reliably fixate the target object when hearing both correctly pronounced and mispronounced labels.
-Infants not only recognize object labels when they were correctly pronounced, but are also likely to accept mispronunciations as labels for targets, in the presence of a distractor image.
-Nonetheless, there was a considerable difference in target fixations in response to correctly pronounced and mispronounced labels, suggesting that infants show an overall mispronunciation sensitivity based on the current experimental literature.
-In other words, infants show sensitivity to what constitutes unacceptable, possibly meaning-altering variation in word forms, thereby displaying knowledge of the role of phonemic changes throughout the ages assessed here (6 to 30 months).
-At the same time, infants, like adults, can recover from mispronunciations, a key skill in language processing.
-
-We next evaluated the developmental trajectory of infants' mispronunciation sensitivity.
-Based on existing experimental evidence, we envisioned three possible developmental patterns: increasing, decreasing, and unchanging sensitivity.
-We observed no influence of age when it was considered as a moderator of mispronunciation sensitivity.
-The results of our meta-analysis reflect a pattern previously reported by a handful of studies directly comparing infants over a range of ages [@Swingley2000; @Bailey2002; @Zesiger2012], which also found no developmental change in mispronunciation sensitivity.
-
-Typically, vocabulary growth is thought to invoke changes in mispronunciation sensitivity.
-The need for phonologically well-specified word representations increases as children learn more words and must differentiate between them [@CharlesLuce1995].
-Yet, when we examined this relationship, we found that very few studies report analyses investigating the relationship between mispronunciation sensitivity and vocabulary size.
-An analysis of this handful of studies revealed no relationship between object recognition in response to mispronunciations, but this analysis was likely underpowered.
-More experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size is needed if this is to be evaluated.
-We tried to address this issue by conducting an analysis of the subset of studies reporting correlations between infants’ vocabulary size and their responses to correct and mispronounced labels.
-However, this analysis relied on only a few papers.
-We observed that an increasing vocabulary size lead to increased object recognition for correctly pronounced words; this was not the case for mispronunciations.
-However, it is difficult to draw any strong conclusions regarding the role of an increasing vocabulary size in mispronunciation sensitivity from this data.
-
-Why did we have so few samples for an analysis on vocabulary size to begin with?
-Despite the theoretical implications, fewer than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total; see also Figure \@ref(fig:Vocab-describe1)).
-There are more mispronunciation sensitivity studies published every year, perhaps due to the increased use of eye-trackers, which reduce the need for offline coding and thus make data collection much more efficient, but this has not translated to an increasing number of mispronunciation sensitivity studies also reporting vocabulary scores.
-We suggest that this may be the result of publication bias favoring significant effects or an overall hesitation to invest in data collection that is not expected to yield significant outcomes.
-
-```{r Young_age, echo = FALSE, results = "hide"}
-
-youngsters <- dat %>%
-  filter(mean_age_1 < (30.44*13)) %>%
-  group_by(short_cite, same_infant) %>%
-  summarise(n_records = n(),
-            age_days = mean(mean_age_1),
-            age_months = mean(mean_age_months),
-            g = mean(g_calc))
-
-# Bergelson & Swingley: no MP sensitivity at 6-7, MP sensitivity at 8-10 and 11-14
-# Mani & Plunkett: MP sensitivity at 12 months
-# Tao & Qinmei: MP sensitivity at 12 months
-# Zesiger: MP sensitivity at 12 months
-
-age_onset <- dat %>%
-  #filter(mean_age_1 < (30.44*13)) %>%
-  group_by(short_cite, same_infant) %>%
-  summarise(age_months = mean(mean_age_months),
-            g = mean(g_calc),
-            onset = mean(offset),
-            post = mean(post_nam_dur))
-
-dv <- dat %>%
-  #filter(mean_age_1 < (30.44*13)) %>%
-  group_by(short_cite, same_infant) %>%
-  summarise(age_months = mean(mean_age_months),
-            g = mean(g_calc),
-            dv = unique(within_measure))
-
-```
-
-What do our (tentative) results mean for theories of language development?
-Evidence that infants accept a mispronunciation (object identification) while simultaneously holding correctly pronounced and mispronounced labels as separate (mispronunciation sensitivity) may indicate an abstract understanding of words' phonological structure being in place early on.
-It appears that young infants may understand that the phonological form of mispronunciations and correct pronunciations do not match, but that the mispronunciation is a better label for the target compared to the distractor image.
-The lack of age or vocabulary effects in our meta-analysis suggest that this understanding is present from an age when the earliest words are learned and is maintained throughout early lexical development.
-
-## Moderator Analyses
-
-With perhaps a few exceptions, the main focus of many of the experiments included in this meta-analysis was not to evaluate whether infants are sensitive to mispronunciations in general but rather to investigate questions related to phonological and lexical processing and development.
-We included a set of moderator analyses to better understand these issues by themselves, as well as how they may have impacted our main investigation of infants' development of mispronunciation sensitivity.
-Additionally, several of these moderators include manipulations that make mispronunciation detection more or less difficult for the infant.
-Considering this, we also evaluated whether the investigation of each of these manipulations was distributed evenly across infant ages, where an uneven distribution may have subsequently heightened or dampened our estimate of developmental change.
-
-The results of the moderator analysis reflect several experimental findings.
-Although words differ from one another on many acoustic dimensions, changes in phonemes, as measured by phonological features, signal changes in meaning.
-Several studies have found that infants show graded sensitivity to both consonant (Bernier & White, 2017; Tamasi, 2016; White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes.
-This was captured in our meta-analysis, which also showed that sensitivity to mispronunciations increased linearly with the number of phonological features changed.
-For each increase in number of phonological features changed, the effect size estimate for looks to the target decreases by `r r2(linear_feature)`.
-Yet, this graded sensitivity appears to be stable across infant ages, although our analysis was likely underpowered.
-At least one study suggests that this graded sensitivity develops with age, but this was the only study to examine more than one age (Mani & Plunkett, 2011).
-All other studies only test one age (Tamasi, White & Morgan, 2008; Bernier & White, 2017).
-With more studies investigating graded sensitivity at multiple ages in infancy, we would achieve a better estimate of whether this is a stable or developing ability.
-
-Although some theories place greater importance on onset position for word recognition and decreasing importance for phonemes in subsequent positions (COHORT), other theories suggest that lexical access can still recover (TRACE).
-Is there any experimental evidence?
-That swingly study?
-Our results show that infants are more sensitive to mispronunciations earlier in the word.
-Since few studies actually compare this, this is nice evidence to have and should hopefully spure more studied.
-Again, we find no influence of development.
-
-in general, these are the things that support what has been found in the literature or theories
-
-These things were not supported
-
-One unique aspect of this meta-analysis was that we could see how these things change with development.
-However, probably underpowered.
-Yet, these were the differences we found and this is what they mean
-
-Interestingly, there were several manipulations that varied the age on which they were tested.
-These are those things.
-We think it may have impacted our overall estimate of developmental change in this way.
-
-** Position of mispronunciation **
-
-  + effect size estimate later position in words significantly decreases
-  + no effect of age
-  + Due to the small sample size of coda mispronunciations, we only included 3 age groups in Fisher's exact test.
-The results were significant, *p* `r psig(fish.test$p.value)`.
-Older infants were more likely to be tested on onset mispronunciations, while younger infants were more likely to be tested on medial mispronunciations.
-An onset mispronunciation may be more disruptive to lexical access than mispronunciations in subsequent positions (Marslen-Wilson & Zwitserlood, 1989), and therefore easier to detect.
-For this reason, it is rather unsuprising that onset mispronunciations show the greatest estimate of mispronunciation sensitivity.
-However, it also means that younger infants, who were more likely to be tested on medial mispronunciations, had a comparably harder task than older infants, who were more likely to be tested on onset mispronunciations.
-We return to this issue in the General Discussion.
-
- The influence of distractor overlap also depends on the *position of mispronunciation* in the word, which can be at word onset, medial, or final positions.
-Models of spoken word processing place more or less importance on the position of a phoneme in a word.
-The COHORT model (Marslen-Wilson & Zwitserlood, 1989) describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.
-In contrast, the TRACE model (McClelland & Elman, 1986) describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.
-
-  TRACE has also been used to model infants' sensitivity to mispronunciation position (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth.
-In early language acquisition, infants typically know more consonant compared to vowel onset words.
-When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations.
-
-** Phonological overlap between target and distractor **
-
-  + mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap
-  + this is rather the opposite of what one would expect, right?
-  + [Katie: Yeah! Its really strange, so the time course analysis suggestion of yours is a very good one!]
-  + Maybe it would be useful to have time course analyses to address this issue further
-  + mispronunciation sensitivity increases with age for target-distractor pairs containing onset overlap, but decreases with age for target-distractor pairs containing no overlap
-  + The results of Fisher's exact test were significant, *p* `r psig(fish.test$p.value)`.
-Older infants were more likely to be tested in experimental conditions where target and distractor images overlapped on their onset phoneme, while younger infants were more likely to be tested with target and distractor images that did not control for overlap.
-A distractor image that overlaps in the onset phoneme with the target image is considered a more challenging task to the infant, as infants must pay attention to the mispronounced phoneme and can not use the differing onsets between target and distractor images to differentiate (Fernald, Swingley, & Pinto, 2001).
-It therefore appears that older infants were given a more challenging task than younger infants.
-This may explain why infants in the onset overlap condition, a harder task, have a greater effect size estimate for mispronunciation sensitivity than those in the no overlap condition, which is a comparably easier task.
-We return to this issue in the General Discussion.
-
-  Furthermore, when presenting infants with a familiar distractor image, some studies control the *phonological overlap between target and distractor labels*.
-For example, when examining sensitivity to a mispronunciation of the target word "dog", the vowel mispronunciation "dag" would be paired with a distractor image that shares onset overlap, such as "duck".
-This ensures that infants can not use the onset of the word to differentiate between the target and distractor images (Fernald, Swingley, & Pinto, 2001).
-Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.
-
-** Type of mispronunciation **
-
-  + Overall, no difference between consonants and vowels 
-  + Consonant mispronunciation sensitivity stays the same with age
-  + Vowel mispronunciation sensitivity increases with age
-  + mispronunciation sensitivity for consonants similar for Germanic and Romance languages
-  + Mispronunciation sensitivity for vowels greater for Germanic compared to Romance languages
-  + For Germanic infants, sensitivity to consonant and vowel mispronunciations did not change with age. 
-  + For Romance infants, sensitivity to mispronunciations decreases for consonants and increases for vowels with age
-  + exploratory analyses with tone mispronunciations suggest no great difference in sensitivity when compared to consonant and vowel mispronunciations
-
-  TRACE has also been used to model infants' sensitivity to mispronunciation position (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth.
-In early language acquisition, infants typically know more consonant compared to vowel onset words.
-When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations.
-The prevalence of consonant onset words may contribute to the finding that consonants carry more weight in lexical processing (C-bias; see Nazzi, Poltrock, & Von Holzen, 2016 for a recent review).
-In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations.
-Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels.
-English-learning 12-, 15-, 18-, and 24-month-olds (Mani & Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds (Hojen et al., unpublished) demonstrate similar sensitivity to consonant and vowel mispronunciations.
-One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations (Swingley, 2016).
-The English-learning infants tested by Swingley were older than previous studies (mean age 28 months).
-In word learning, the C-bias has been found to develop later in English learning infants (Floccia, Nazzi, Delle Luche, Poltrock, & Goslin, 2014; Nazzi, Floccia, Moquet, & Butler, 2009).
-In the current meta-analysis, we attempt to synthesize studies examining sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence (Floccia et al., 2014; Keidel et al., 2007; Nazzi et al., 2016).
-We further examine the impact of language family on mispronunciation sensitivity to consonants and vowels, as C-bias emergence has been found to have a different developmental trajectory for Romance (French, Italian) compared to Germanic (British English, Danish) languages (Nazzi et al., 2016).
-
-  Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (see Table 1).
-Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare.
-Although we do not explicitly compare overall mispronunciation sensitivity by language (although see previous paragraph for rationale to test by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.
-
-** Distractor Familiarity **
-
-  + No difference between familiar and unfamiliar distractors
-  + Again, ages not matched very well for the two groups here.
-
-  Although most research examining sensitivity to mispronunciations follows a similar design, there are some notable differences.
-For example, Swingley and Aslin (2000) presented infants with pairs of familiar images, one serving as the labeled target and one as the unlabeled distractor.
-In contrast, White and Morgan (2008; see also Mani & Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects.
-By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied (Halberda, 2003; Markman, Wasow, & Hansen, 2003).
-Infants ages 24 and 30 months associate a novel label with an unfamiliar object, although only 30-month-olds retained this label-object pairing (Bion, Borovsky, and Fernald, 2013).
-In contrast, 18-month-olds did not learn to associate a novel label with an unfamiliar object, providing evidence that this ability is developing from 18 to 30 months.
-We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar.
-Although mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared, the baseline preference for familiar compared to novel stimuli is also thought to change as infants develop (Hunter & Ames, 1988).
-Furthermore, young children have been found to look longer at objects for which they know the name, compared to objects of an unknown name (Schafer & Plukett, 1998).
-In other words, in absentia of a label, infants may be more or less likely to fixate on an unfamiliar object.
-To account for inherent preferences to the target or distractor image, mispronunciation experiments typically compare the increase in fixations to the target image from a silent baseline to post-labeling or present the same yoked pairs of target and distractor images in in both a correct and mispronounced labelling context.
-Considering this evidence, we may expect that in older, but not younger, children, the presence of an unfamiliar distractor may lead to greater mispronunciation sensitivity than in the presence of a familiar distractor.
-
-## Data Analysis Choices
-
-While creating the dataset on which this meta-analysis was based, we included as many details as possible to describe each study.
-During the coding of these characteristics, we noted a potential for variation in a handful of variables that relate to data analysis, specifically relating to timing (post-naming analysis window; onset time) and to the calculation of the dependent variable reported.
-We focused on these variables in particular because their choice can potentially be made after researchers have examined the data, leading to an inflated number of significant results which may also explain the publication bias observed in the funnel plot asymmetry analyses [@Simmons2011].
-To explore whether this variation contributed to the lack of developmental change observed in the overall meta-analysis, we included these variables as moderators in a set of exploratory analyses.
-We noted an interesting pattern of results, specifically that different conclusions about mispronunciation sensitivity, but more notably mispronunciation sensitivity development, could be drawn depending on the length of the post-naming analysis window as well as the type of dependent variable calculated in the experiment (see Figures \@ref(fig:Plot-post-name-cond-age) and \@ref(fig:Plot-Within-cond-age-diff-score)).
-
-Infants recognize words more quickly with age [@Fernald1998], which has the potential to influence decisions for the analysis of the post-naming time window in mispronunciation sensitivity studies, including where to begin the time window (onset time) and how long this analysis window should be (post-naming analysis window).
-For example, as age increases, reaction time should increase and experimenters may adjust and lower offset times in their analysis as well as shorten the length of the analysis window.
-Yet, we find no relationship between age and offset times, nor that offset time modulated mispronunciation sensitivity.
-Indeed, a majority of studies used an offset time between 360 and 370 ms, which follows the "best guess" of @Swingley2000 for the amount of time needed for infants to initiate eye movements in response to a spoken target word.
-Without knowledge of the base reaction time in a given population of infants, use of this best guess offset time reduces the number of free parameters.
-In contrast, we found a negative correlation between infant age and the length of the post-naming analysis window, and that the length of the analysis window moderated mispronunciation sensitivity, such increasing the length of the analysis windows decreases the size of mispronunciation sensitivity.
-Given a set of mispronunciation sensitivity data, a conclusion regarding the development of mispronunciation sensitivity would be different depending on the length of the post-naming analysis window.
-Although we have no direct evidence, an analysis window can be potentially set after collecting data.
-At worst, this adjustment could be the result of a desire to confirm a hypothesis, increasing the rate of false-positives [@Gelman2013]: a "significant effect" of mispronunciation sensitivity is found with an analysis window of 2000 but not 3000 ms, therefore 2000 ms is chosen.
-At best, this variation introduces noise into the study of mispronunciation sensitivity, bluring the true developmental trajectory of mispronunciation sensitivity.
-In the next section, we highlight some suggestions for how the field can remedy this issue.
-
-Surpisingly, we found that the type of dependent variable calculated moderated mispronunciation sensitivity and conclusions about its developmental trajectory.
-Unlike the exploratory analyses related to timing (onset and post-naming analysis window), there is not a clear reason for one dependent variable to be chosen over another; the prevelence of each dependent variable appears distributed across ages and some authors always calculate the same dependent variable while others use them interchangeably in different publications.
-One clear difference is that both the Difference Score and Pre vs.
-Post dependent variables take into account each infants' actual preference in the pre-naming baseline phase, while the Post dependent variable does not.
-Without access to the raw data, it is difficult to conclusively determine why different dependent variable calculations influence mispronunciation sensitivity.
-In the next section, we advocate for the adoption of Open Data practices as one way to address this issue.
-
-## Recommendations to Establish Analysis Standards
-
-A lack of a field standard can have serious consequences, as our analyses show.
-Depending on which analysis time window (see Figure \@ref(fig:Plot-post-name-cond-age)) or dependent variable (see Figure \@ref(fig:Plot-Within-cond-age-diff-score)) we focus on, we find support for any of the three possible trajectories of mispronunciation sensitivity development.
-On the one hand, this limits the conclusions we can draw regarding our key research question.
-Without access to the full datasets or analysis code of the studies included in this meta-analysis, it is difficult to pinpoint the exact role played by these data analysis choices.
-On the other hand, this finding emphasizes that current practices of free, potentially ad hoc choices regarding data analyses are not sustainable if the field wants to move towards quantitative evidence for theories of language development.
-
-We take this opportunity to suggest several recommendations to address the issue of potential posthoc analysis decisions.
-Preregistration can serve as proof of a priori decisions regarding data analysis, which can also contain a data-dependent description of how data analysis decisions will be made once data is collected.
-The peer-reviewed form of preregistration, termed Registered Reports, has already been adopted by a large number of developmental journals, and general journals that publish developmental works, showing the field’s increasing acceptance of such practices for hypothesis-testing studies.
-Sharing data (Open Data) can allow others to re-analyze existing datasets to both examine the impact of analysis decisions and cumulatively analyze different datasets in the same way.
-Considering the issue of analysis time window, experimenters can opt to analyze the time course as a whole, instead of aggregating the proportion of target looking behavior over the entire trial.
-This allows for a more detailed assessment of infants' fixations over time and reduces the need to reduce the post-naming analysis window.
-Both Growth Curve Analysis [@Mirman2008; @Law2015] and Permutation Clusters Analysis [@VonHolzen2012; @Maris2007; @DelleLuche2015] offer potential solutions to analyze the full time course.
-Furthermore, it may be useful to establish standard analysis pipelines for mispronunciation studies.
-This would allow for a more uniform analysis of this phenomenon, as well as aid experimenters in future research planning.
-In general, however, a better understanding of how different levels of linguistic knowledge may drive looking behavior is needed.
-We hope this understanding can be achieved by applying the above suggestions.
-
-Another aspect of study design, namely sample size planning, shows that best practices and current standards might not always overlap.
-Indeed, across a set of previous meta-analyses it was shown that particularly infant research does not adjust sample sizes according to the effect in question [@Bergmann2018].
-A meta-analysis is a first step in improving experiment planning by providing an estimate of the population effect and its variance, which is directly related to the sample needed to achieve satisfactory power in the null hypothesis significance testing framework.
-Failing to take effect sizes into account can both lead to underpowered research and to testing too many participants, both consequences are undesirable for a number of reasons that have been discussed in depth elsewhere.
-We will just briefly mention two that we consider most salient for theory building: Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature [@Bergmann2018].
-At the same time, underpowered studies with significant outcomes are likely to overestimate the effect, leading to wrong estimations of the population effect when paired with publication bias [@Jennions2002].
-Overpowered studies mean that participants were tested unnecessarily, which has ethical implications particularly when working with infants and other difficult to recruit and test populations.
-
-```{r Power_calculation, echo = FALSE, results = "hide"}
-
-# effect size for mispronunciation sensitivity
-mp_effect <- r2(coef(summary(rma_MPeffect))[2,1])
-
-si <- dat[,c("short_cite", "expt_num", "same_infant", "n_1")]
-si <- unique(si)
-
-median_sample <- median(si$n_1)
-
-# resulting power, anova
-pat <- pwr.anova.test(k = 2, n = median_sample, f = mp_effect, sig.level = 0.05, power = NULL)
-ptt <- pwr.t.test(n = median_sample, d = mp_effect, sig.level = 0.05, power = NULL)
-
-ptt.correct <- pwr.t.test(n = median_sample, d = .9, sig.level = 0.05, power = NULL)
-ptt.misp <- pwr.t.test(n = median_sample, d = .25, sig.level = 0.05, power = NULL)
-
-# 80% power, anova
-pat.est <- pwr.anova.test(k = 2, n = NULL, f = mp_effect, sig.level = 0.05, power = .8)
-ptt.est <- pwr.t.test(n = NULL, d = mp_effect, sig.level = 0.05, power = .8)
-
-```
-
-The estimated effect for mispronunciation sensitivity in this meta-analysis is `r mp_effect`, and the most frequently observed sample size is `r median_sample` participants.
-If we were to assume that researchers assess mispronunciation sensitivity in a simple ANOVA, the resulting power is `r r2(pat$power)`.
-Reversely, to achieve 80% power, one would need to test `r round(pat.est$n, 1)` participants.
-These calculations suggest that for the comparison of responses for correct pronunciations and mispronunciations, the studies included in this meta-analysis contain well-powered analyses.
-However, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates require four times the sample size to detect an effect of similar magnitude as the main effect for both ANOVA [@Fleiss1986] and mixed-effect-model [@Leon2009] analyses.
-We thus strongly advocate for a consideration of power and the reported effect sizes to test infants’ mispronunciation sensitivity.
-
-## Limitations
-
-The current meta-analysis aggregated studies designed to investigate mispronunciation sensitivity, but we note that these studies varied in their approach to study our phenomenon of interest.
-For example, some studies investigated specific questions which required additional manipulations, such as the impact of the number of phonological features changed in the mispronunciations on mispronunciation sensitivity [e.g.
-@Mani2011; @White2008] or sensitivity to consonant and vowel mispronunciations [@Mani2007; @Mani2010kepstups; @Hojen; @Swingley2016].
-The studies in our sample additionally varied in their experimental design, such as whether infants were familiar with the distractor image [@White2008; @Mani2011; @Skoruppa2013; @Swingley2016] or whether the labels for the target and distractor images contained phonological overlap [@Fernald2001a].
-Futhermore, the infants included in this meta-analysis had a variety of native languages (English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese) and language backgrounds (monolingual, bilingual, monodialectal, multidialectal).
-Taken together, these variables have the potential to modulate infant mispronunciation sensitivity, but an investigation of these variables is out of the scope of the current meta-analysis.
-However, our dataset includes these variables.
-We hope that future research will be able to better understand the role that these variables play in infants' sensitivity to mispronunciations.
-
-## Conclusion
-
-This meta-analysis comprises an aggregation of almost two decades of research on mispronunciation sensitivity, finding that infants accept both correct pronunciations and mispronunciations as labels for a target image.
-However, they are more likely to accept correct pronunciations, which indicates sensitivity to mispronunciations in familiar words.
-Despite the predictions of theories of infant phono-lexical development, this sensitivity was not modulated by infant age or vocabulary.
-This suggests that from a young age on, before the vocabulary explosion, infants’ word representations may be already phonologically well-specified.
-We recommend future theoretical frameworks take this evidence into account.
-
-Despite this overall finding, however, we note evidence that data analysis choices can modulate conclusions about mispronunciation sensitivity development.
-Future studies should be carefully planned with this evidence in mind.
-Ideally, future experimental design and data analysis would become standardized which will be aided by the growing trend of preregistration and open science practices.
-Our analysis highlights how meta-analyses can aid in identification of issues in a particular field and play a vital role in how the field addresses such issues.
+```{r SameWords, results= "asis"}
+
+rma_SameWords <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(word_correct_and_MP)*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
+
+# no effects of samewords
+
+```
+
+```{r SameWords_age, results= "asis"}
+
+# age moderator
+rma_SameWords_age <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(word_correct_and_MP)*condition*age.C, data = dat, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
+
+```
 

### 2020-01-24 VonHolzenBergmann_MPMetaAnalysis.Rmd
24.1.2020 editing and cutting down words

@@
 hat).
-We focus on studies investigating infants' ability to detect mispronunciations in familiar words, which we refer to as mispronunciation sensitivity.
-The goal of this meta-analysis was to evaluate the development of mispronunciation sensitivity in infancy, allowing for a test of competing mainstream theoretical frameworks.
+This meta-analysis focuses on studies investigating infants' ability to detect mispronunciations in familiar words, or mispronunciation sensitivity.
+Our goal was to evaluate the development of mispronunciation sensitivity in infancy as well as explore the role of experimental manipulations related to theoretical questions and analysis choices.
 The results show that although infants are sensitive to mispronunciations, they still accept these altered forms as labels for target objects.
-Interestingly, this ability is not modulated by age or vocabulary size, challenging existing theories and suggesting that a mature understanding of native language phonology is present in infants from an early age, possibly before the vocabulary explosion.Further examining our findings, we shed light on the impact of data analysis choices that may lead to different conclusions regarding the development of infants' mispronunciation sensitivity.
+Interestingly, this ability is not modulated by age or vocabulary size, suggesting that a mature understanding of native language phonology may be present in infants from an early age, possibly before the vocabulary explosion.
+The results also support several theoretical assumptions made in the literature, such as sensitivity to mispronunciation size and position of the mispronunciation modulate mispronunciation sensitivity.
+We also shed light on the impact of data analysis choices that may lead to different conclusions regarding the development of infants' mispronunciation sensitivity.
 Our paper concludes with recommendations for improved practice in testing infants' word and sentence processing on-line.
@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            :
+  papaja::apa6_docx
+
+# Use papaja::apa6_docx for Word documents
+# For PDF documents use 
+#  papaja::apa6_pdf:
+#    latex_engine: xelatex
 
@@
   - \captionsetup[figure]{font={stretch=1.5}}
+  - \usepackage{fontspec}
+  - \newfontfamily\ipa{Doulos SIL}
+  - \DeclareTextFontCommand{\ipatext}{\ipa}
 ---
@@
 
-r2 <- function(x){ round(x, 3)}
-
-psig <- function(x){
-  ifelse(x < .001, "< .001",
-         #ifelse(x < .001, "< .001",
-                #ifelse(x < .01, "< .01",
-                       ifelse(x > .001 & x < .05, paste("=", r2(x), sep = " "), paste("=", r2(x), sep = " ")))#))
-}
-
-# function for creating 1 line paired t.test results
-t.xtable <- function(x) as.data.frame(xtable(
-  t_out(toutput=x, n.equal = TRUE, welch.df.exact = TRUE, welch.n = NA,
-        d.corr = TRUE, print = TRUE)
-))
-
-g_SE <- function(x) paste0(r2(x$estimate), " (SE = ", r2(x$se), ")")
-
-CI_p <- function(x) paste0("(CI [", r2(x$ci.lb), ", ", r2(x$ci.ub), "], *p* ", psig(x$pval), ")")
-
-full_estimate <- function(x) paste0(" = ", r2(x$estimate), ", SE = ", r2(x$se), ", 95% CI[",  r2(x$ci.lb), ", ", r2(x$ci.ub),"], *p* ", psig(x$pval))
-
-# moderator test
-mod_test <- function(x) paste0("QM(", r2(x$m), ") = ", r2(x$QM), ", *p* ", psig(x$QMp))
-
-# Create the function for mode.
-getmode <- function(v) {
-   uniqv <- unique(v)
-   uniqv[which.max(tabulate(match(v, uniqv)))]
-}
-
 ```
@@
 ```{r ReadIn}
+
+#Load helpful little functions
+source("scripts/starter_functions.R")
 
@@
 
-```{r PlotAPATheme}
-# Plotting defaults
-
-#Themes and plot
-apatheme=theme_bw()+
-  theme(panel.grid.major=element_blank(),
-    panel.grid.minor=element_blank(),
-    panel.border=element_blank(),
-    axis.line=element_line(),
-    text=element_text(family='Times', size=25))
-
-# Color Blind palette:
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
-```
-
 # Introduction
 
-  At the turn of the millenium, infant language acquisition researchers had established that during their first two years of life, infants are sensitive to changes in the phonetic detail of newly segmented words [@Jusczyk1995] and learned minimal pairs [@Stager1997].
-Furthermore, when presented with familiar image pairs, children fixate on the referent of a spoken label [@Fernald1998; @Tincoff1999].
-@Swingley2000 were the first to tie these lines of research together and investigate how infants interpret phonological variation in familiar word recognition: Children aged 18 to 23 months learning American English saw pairs of images (e.g.
+  At the turn of the millenium, infant language acquisition researchers had begun to explore the phonetic information that infants attend to while segmenting words from the speech stream [@Jusczyk1995] and learning minimal pairs [@Stager1997].
+@Swingley2000 expanded this exploration to infants's existing representations, investigating how infants interpret phonological variation in familiar word recognition.
+American-English learning 18- to 23-month-olds were presented with pairs of images (e.g.
 a baby and a dog) and their eye movements to each image were recorded.
-On "correct" trials, children heard the correct label for one of the images (e.g.
-"baby").
-On "mispronounced" trials, children heard a mispronounced label of one of the images (e.g.
-"vaby").
-Although infants looked at the correct, target image in response to both types of trials, correct trials elicited a greater proportion of looks to the correct, target image than mispronounced trials.
+Infants either heard the correct label (e.g.
+"baby") or a mispronounced label (e.g.
+"vaby") for one of the images.
+Although infants looked at the correct, target image in response to both types of labels, correct labels elicited more looks to the correct, target image than mispronounced labels.
 @Swingley2000 concluded that already before the second birthday, children's representations for familiar words are phonologically well specified.
@@
 In this meta-analysis, we focus on infants' developing ability to correctly apply the phonological distinctions for their native language during word recognition.
-By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; @MB1; for a notable exception).
+By aggregating all publicly available evidence using a meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; @MB1; for a notable exception).
 Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.
 
-  Research following the seminal study by @Swingley2000 has extended mispronunciation sensitivity to infants as young as 8 to 10 months [@Bergelson2017], indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations.
-Regarding the change in mispronunciation sensitivity over development, however, only about half of studies have compared more than one age group on the same mispronunciation task (see Table 1).
-Those studies find all possible patterns of development (see below), rendering conclusions regarding developmental change in mispronunciation sensitivity difficult.
-
-Several studies have found evidence for *greater* mispronunciation sensitivity as children develop.
+  Research following the seminal study by @Swingley2000 has extended mispronunciation sensitivity to infants as young as 11 months [@Bergelson2017], indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations.
+Regarding the change in mispronunciation sensitivity over development, however, only about half of studies have compared more than one age group on the same mispronunciation task (see Table \@ref(tab:SummaryTable)) and of those, all possible patterns of development are found.
+This renders conclusions regarding developmental change in mispronunciation sensitivity difficult.
+
+Several studies  have found evidence for *greater* mispronunciation sensitivity as children develop [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010].
 More precisely, the difference in target looking for correct and mispronounced trials is reported to be smaller in younger infants and grows as infants develop.
-@Mani2007 tested 15-, 18-, and 24-month-olds learning British English; although all three groups were sensitive to mispronunciations, 15-month-olds showed a less robust sensitivity.
-An increase in sensitivity to mispronunciations has also been found from 20 to 24 months [@vanderFeest2015] and 15 to 18 months [@Altvater2014] in Dutch infants, as well as German infants from 22 to 25 months [@Altvater2010].
-
-Other studies have found no difference in mispronunciation sensitivity at different ages.
+Other studies have found *no difference* in mispronunciation sensitivity at different ages [@Swingley2000; @Bailey2002; @Zesiger2012].
 For example, @Swingley2000 tested infants over a wide age range of 5 months (18 to 23 months).
 They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation sensitivity) did not.
-This suggests that as children develop, they are more likely to look at the target in the presence of a correct or mispronounced label, but that the difference between looks elicited by the two conditions does not change.
-A similar response pattern has been found for British English learning infants aged between 18 and 24 months [@Bailey2002] as well as younger French-learning infants at 12 and 17 months [@Zesiger2012].
-
-  One study has found evidence for infants to become *less* sensitive to mispronunciations as they develop.
-@Mani2011 presented 18- and 24-month-olds with mispronunciations varying in the number of phonological features changed (e.g., changing an p into a b, a 1-feature change, versus changing a p into a g, a 2-feature change).
-18-month-olds were sensitive to mispronunciations, regardless of the number of features changed.
-24-month-olds, in contrast, fixated the target image equally for both correct and 1-feature mispronounced trials, although they were sensitive to larger mispronunciations.
-In other words, for 1-feature mispronunciations at least, sensitivity decreased from 18 to 24 months.
+At least one study has found evidence for infants to become *less* sensitive  to mispronunciations as they develop, showing a decrease in sensitivity from 18 to 24 months [@Mani2011].
 
   Given the diverse evidence for developmental change, or lack thereof, the question arises as to what could be driving these differences.
-As infants develop, the rate at which they learn words increases and their focus shifts to the relevant phonetic dimensions needed for word recognition.
-For example, an infant who knows a handful of words with few phonological neighbors would not need to have fully specified phonological representations in order to differentiate between these words.
-As more phonologically similar words are learned, however, the need for fully detailed phonological representations increases [@CharlesLuce1995].
-Furthermore, a growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the detail of their phonological representation [@Barton1980].
+The first words that infants learn are often not similar sounding [e.g.
+mama, ball, kitty; @CharlesLuce1995] and encoding representations for these words using fine phonological detail may not be necessary.
+With time, more phonologically similar words are learned, which may drive a need to the infant to represent familiar words with more fine phonological detail.
+A growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the phonological detail of their representations [@Barton1980].
 If vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship between vocabulary size and mispronunciation sensitivity.
@@
 Taken together, there is very little evidence for a role of vocabulary size in mispronunciation sensitivity.
-In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to better understand the variation in experimental results.
+In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to better understand this issue.
 
@@
 These experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete.
-The PRIMIR Framework [Processing Rich Information from Multidimensional Interactive Representations; @Curtin2011; @Curtin2007; @Werker2005) describes how infants acquire and organize the incoming speech signal into phonetic and indexical detail.
+The PRIMIR Framework [Processing Rich Information from Multidimensional Interactive Representations; @Curtin2011; @Curtin2007; @Werker2005] describes how infants acquire and organize the incoming speech signal into phonetic and indexical detail.
 The ability to access and use this detail, however, is governed by the task or developmental demands (discrimination vs.
@@
 In a particularly demanding task, such as when the target and distractor image share the same onset phoneme, infants' ability to access the phonological detail of familiar words may be restricted.
-
-  These manipulations may impact task demands, but they are also theoretically interesting, focus on issues at the intersection of phonological development and lexical processing.
+If older infants are more likely to be tested using a more demaning mispronunciation sensitivity task, this may attenuate developmental effects across studies.
+
+  These manipulations may impact task demands, but they are also theoretically interesting, focusing on issues at the intersection of phonological development and lexical processing.
 For specific questions where we can aggregate multiple studies, we take the opportunity to shine a meta-analytic light on what modulates infants' ability to detect mispronunciations in follow-up exploatory analyses.
@@
 
+  Consonantal changes may be more disruptive to lexical processing than vowel changes in both adults [@Nazzi2018] and infants [@Nazzi2016].
+In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations.
+Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels for English- [@Mani2007; @Mani2010kepstups] and Danish-learning infants [@Hojen].
+One study with English-learning infants did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations [@Swingley2016].
+Evidence from word-learning suggests that assymetry in sensitivity to consonant and vowel changes may develop at different times depending on the infants' native language [e.g.
+@Floccia2014; @Nazzi2009a].
+In the current meta-analysis, we attempt to synthesize studies examining sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence [@Floccia2014; @Nazzi2016; @Keidel2007] and whether this is impacted by the language family of the infants' native language [@Nazzi2016].
+
   Models of spoken word processing place more or less importance on the position of a phoneme in a word.
@@
 
+  A second question is whether the experimental context modulates infants' responses to mispronunciations.
 In order to study the influence of mispronunciation position, many studies control the *phonological overlap between target and distractor labels*.
-For example, when examining sensitivity to a mispronunciation of the target word "dog", the vowel mispronunciation "dag" would be paired with a distractor image that shares onset overlap, such as "duck".
+For example, when examining sensitivity to a vowel mispronunciation of the target word "dog", the image of a dog would be paired with a distractor image that shares onset overlap, such as "duck".
 This ensures that infants can not use the onset of the word to differentiate between the target and distractor images [@Fernald2001a].
 Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.
-
-  Consonantal changes may be more disruptive to lexical processing than vowel changes [@Nazzi2018], which has been extended to infancy [@Nazzi2016].
-In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations.
-Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels.
-English-learning 12-, 15-, 18-, and 24-month-olds [@Mani2007; @Mani2010kepstups] and Danish-learning 20-month-olds [@Hojen] demonstrate similar sensitivity to consonant and vowel mispronunciations.
-One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations [@Swingley2016].
-The English-learning infants tested by Swingley were older than previous studies (mean age 28 months).
-In word learning, the C-bias has been found to develop later in English- than French-learning infants [@Floccia2014; @Nazzi2009a].
-In the current meta-analysis, we attempt to synthesize studies examining sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence [@Floccia2014; @Nazzi2016; @Keidel2007].
-We further examine the impact of language family on mispronunciation sensitivity to consonants and vowels, as C-bias emergence has been found to have a different developmental trajectory for Romance (French, Italian) compared to Germanic (British English, Danish) languages [@Nazzi2016].
-
-  A second question is whether the non-linguistic context modulates infants' responses to mispronunciations: Most research on the topic presents infants with two known words, thus ruling out the unlabeled competitor, or distractor, as possible target.
+  Most studies present infants with pictures of two name-known objects, thus ruling out the unlabeled competitor, or distractor, as possible target.
 In contrast, other studies present infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects [@White2008; @Mani2011; @Skoruppa2013; @Swingley2016].
 By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied [@Halberda2003; @Markman2003].
-In a learning context, 24- and 30-month-olds associate a novel label with an unfamiliar object, but 18-month-olds do not, providing evidence that this ability, known as mutual exclusivity, is developing from 18 to 30 months [@Bion2013].
-We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar.
+This ability is developing from 18 to 30 months [@Bion2013] and we may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar.
 This is a particularly fruitful question to investigate within the context of a meta-analysis, as mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared.
 
-  Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (see Table 1).
+  Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (see Table \@ref(tab:SummaryTable)).
 Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare.
 Indeed, the majority of studies focus on infants learning English as a native language and a sufficient sample of other languages is therefore lacking.
-Although we do not explicitly compare overall mispronunciation sensitivity by language (although see previous paragraph for rationale to test by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.
+Although we do not explicitly compare overall mispronunciation sensitivity by language (although we examine consonant and vowel mispronunciation sensitivity by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.
 
@@
 Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding of the big picture of early phono-lexical development.
-Meta-analyses can provide unique insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and of their mispronunciations sensitivity.
+Meta-analyses can provide unique insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and of their mispronunciation sensitivity.
 Because we aggregate data over various age groups, this meta-analysis can also investigate the role of maturation by assessing the impact of age and vocabulary size.
-We also explore the influence of different linguistic (mispronunciation size and position, target-distractor overlap, and type of mispronunciation) and non-linguistic (distractor familiarity) demands on the study of mispronunciation sensitivity.
+We also explore the influence of different linguistic (mispronunciation size, position, and type) and experimental (overlap between target and distractor labels; distractor familiarity) demands on the study of mispronunciation sensitivity.
 Finally, we explore potential data analysis choices that may influence different conclusions about mispronunciation sensitivity development as well as offer recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses [@Bergmann2018].
@@
 
-## (Insert Figure 1 about here)
+## (Insert Figure \@ref(fig:PRISMA-image) about here)
 
@@
 We will refer to these items collectively as papers.
-Table 1 provides an overview of all papers included in the present meta-analysis.
+Table \@ref(tab:SummaryTable) provides an overview of all papers included in the present meta-analysis.
 
@@
 
-1 Condition: Were words mispronounced or not;  
-2 Mean age reported per group of infants, in days;  
-3 Vocabulary size, measured by a standardized questionnaire or list;    
-4 Size of mispronunciation, measured in features changed;  
-5 Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;  
-6 Position of mispronunciation: onset, medial, offset, or mixed;  
-7 Type of mispronunciation: consonant, vowel, or both.
-8 Distractor familiarity: familiar or unfamiliar;
+1. Condition: Were words mispronounced or not;  
+2. Mean age reported per group of infants, in days;  
+3. Vocabulary size, measured by a standardized questionnaire or list;    
+4. Position of mispronunciation: onset, medial, offset, or mixed;
+5. Size of mispronunciation, measured in features changed;
+6. Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word; 
+7. Type of mispronunciation: consonant, vowel, or both.
+8. Distractor familiarity: familiar or unfamiliar;
 
@@
 
-[^1]: Two papers tested bilingual infants [@Ramon-Casas2009; @Ramon-Casas2010], yielding `r bil_infants` experimental conditions.
+[^1]: Two papers tested bilingual infants [@Ramon-Casas2009; @Ramon-Casas2010], yielding `r bil_infants` records.
 Due to this small number, we do not investigate the role of multilingualism, but do note that removing these papers from the meta-analysis did not alter the pattern of results.
@@
 We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, sum(count[es_method == "group_means_one" | es_method == "group_means_two"]))` records from `r with(es_info, sum(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))` papers) or reported t-values (*n* = `r with(es_info, sum(count[es_method == "t_one" | es_method == "t_two"]))` records from `r with(es_info, sum(n_unique[es_method == "t_one" | es_method == "t_two"]))` papers).
-Two papers reported raw means and standard deviations for some experimental conditions and just t-values for the remaining experimental conditions [@Swingley2016; @Altvater2014].
+Two papers reported raw means and standard deviations for some records and just t-values for the remaining records [@Swingley2016; @Altvater2014].
 Raw means and standard deviations were extracted from figures for `r with(descriptive_dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers.
@@
 Second, we analyzed the correlation between reported vocabulary size and mispronunciation sensitivity using the R [@R] package meta [@meta].
-For a subsequent exploratory investigation of experimental characteristics, we introduced each as a moderator: size of mispronunciation, position of mispronunciation, phonological overlap between target and distractor labels, type of mispronunciation, and distractor familiarity (more detail below).
+For a subsequent investigation of experimental characteristics, we introduced each as a moderator: size of mispronunciation, position of mispronunciation, phonological overlap between target and distractor labels, type of mispronunciation, and distractor familiarity (more detail below).
 
@@
 
-## (Insert Figure 2 about here)
-
 ```{r FunnelCombo, echo = FALSE, fig.cap="Funnel plots for object identification, plotting the standard error of the effect size in relation to the effect size.
@@
 ```
+
+## (Insert Figure \@ref(fig:FunnelCombo) about here)
 
@@
 
-## (Insert Figure 3 about here)
+## (Insert Figure \@ref(fig:PlotMPEffect) about here)
 
@@
 Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` analyzed the relationship between vocabulary scores and object recognition for correct pronunciations and mispronunciations (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers and `r with(vi1, count[has_vocab == "comprehension"])` records; production = `r with(vi1, papers[has_vocab == "production"])` papers and `r with(vi1, count[has_vocab == "production"])` records).
-There is reason to believe that production data are different from comprehension data.
 Children comprehend more words than they can produce, leading to different estimates for comprehension and production.
@@
 We first considered the relationship between vocabulary and object recognition for correct pronunciations.
-Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for `r pos_rel` of `r tot_rel` experimental conditions, with correlation values ranging from `r min_cor` to `r max_cor`.
+Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for `r pos_rel` of `r tot_rel` records, with correlation values ranging from `r min_cor` to `r max_cor`.
 The weighted mean effect size Pearson's *r* of `r r2(CC$TE.fixed)` was small but did differ significantly from zero (CI [`r r2(CC$lower.fixed)`; `r r2(CC$upper.fixed)`] *p* `r psig(CC$pval.fixed)`).
@@
 We next considered the relationship between vocabulary and object recognition for mispronunciations.
-Higher comprehension scores were associated with greater object recognition in response to mispronunciations for `r pos_rel` of `r tot_rel` experimental conditions, with correlation values ranging from `r min_cor` to `r max_cor`.
+Higher comprehension scores were associated with greater object recognition in response to mispronunciations for `r pos_rel` of `r tot_rel` records, with correlation values ranging from `r min_cor` to `r max_cor`.
 The weighted mean effect size Pearson's *r* of `r r2(MC$TE.fixed)` was small and did not differ significantly from zero (CI [`r r2(MC$lower.fixed)`; `r r2(MC$upper.fixed)`] *p* `r psig(MC$pval.fixed)`).
 The small correlation suggests either a very small positive or no relationship between vocabulary and object recognition for mispronunciations.
-We again emphasize that we cannot draw a firm conclusion due to the small number of studies we were able to include here.
 
 Figure \@ref(fig:Vocabdescribe1) plots the year of publication for all the mispronunciation sensitivity studies included in this meta-analysis.
-This figure illustrates two things: the increasing number of mispronunciation sensitivity studies and the decreasing number of mispronunciation studies measuring vocabulary.
+This figure illustrates two things: the increasing number of mispronunciation sensitivity studies in general and the decreasing number of mispronunciation studies measuring vocabulary.
 The lack of evidence for a relationship between mispronunciation sensitivity and vocabulary size in some early studies may have contributed to increasingly fewer researchers including vocabulary measurements in their mispronunciation sensitivity experimental design.
-This may explain our underpowered analysis of the relationship between object recognition for correct pronunciations and mispronunciations and vocabulary size.
-
-## (Insert Figure 4 about here)
+This may explain our underpowered analysis of the relationship between object recognition for correct pronunciations and mispronunciations and vocabulary size, despite its theoretical interest.
+
+## (Insert Figure \@ref(fig:Vocabdescribe1 about here)
 
@@
 For most moderators (except mispronunciation size), we combine the correct and mispronounced datasets and include the moderator of condition, to study mispronunciation sensitivity as opposed to object recognition.
-To better understand the impact of these moderators on developmental change, we include age as subsequent moderator as well as an exploratory analysis of the age of infants tested with each type of moderator.
-The latter analysis is included to explore whether the lack of developmental change in mispronunciation sensitivity in the overall dataset is due to more complex moderator tasks being given to older infants, which may lower the overall effect size of mispronunciation sensitivity at older ages and dampen any evidence of change.
+To better understand the impact of these moderators on developmental change, we include age as subsequent moderator.
 Finally, we analyze the relationship between infant age and the moderator condition they were tested in using Fisher's exact test, which is more appropriate for small sample sizes [@Fisher1922].
-For each moderator, we evaluate the independence of infants' age group (divided into quartiles unless otherwise specified) and assignment to each type of condition in a particular moderator.
+This evaluates the independence of infants' age group (divided into quartiles unless otherwise specified) and assignment to each type of condition in a particular moderator.
 
@@
 We did not include data for which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent (e.g., one mispronunciation included a 2-feature change whereas another only a 1-feature change).
-This analysis was therefore based on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` experimental conditions for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations.
+This analysis was therefore based on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` records for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations.
 Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an equal impact on mispronunciation sensitivity, following the argument of graded sensitivity [@White2008; @Mani2011], and this modertor was coded as a continuous variable.
@@
 
-To better understand how this moderator impacted our estimate of developmental change in mispronunciation sensitivity, we added age as a moderator.
-The moderator test was significant, `r mod_test(rma_NFeatures_age)`, but the interaction between age and number of features changed was not significant, $\beta$`r full_estimate(sum_eff_age)`.
-The small effect size for the interaction between age and number of features changed suggests that the impact of number of features changed on mispronunciation sensitivity does not substantially change with infant age.
-Alternatively, we might not have enough power to detect a small but consistent effect because only a handful of studies have explicitly examined the effect of the number of features changed on mispronunciation sensitivity and only these studies include 3-feature changes [@Bernier2017; @Tamasi2016; @White2008; @Mani2011].
-
-Finally, we examined whether infants are disproportionately tested in conditions with smaller or larger mispronunciation sizes based on their age.
-The results of Fisher's exact test were not significant, *p* `r psig(fish.test$p.value)`.
+When age was added as a moderator to the model, the moderator test was significant, `r mod_test(rma_NFeatures_age)`, but the estimate for the interaction between age and number of features changed was small and not significant, $\beta$`r full_estimate(sum_eff_age)`.
+This suggests that the impact of number of features changed on mispronunciation sensitivity does not substantially change with infant age.
+We note, however, that only a handful of studies have explicitly examined the effect of the number of features changed on mispronunciation sensitivity and only these studies include 3-feature changes [@Bernier2017; @Tamasi2016; @White2008; @Mani2011], which may narrow our ability to draw conclusions about developmental change.
+
+Finally, results of Fisher's exact test were not significant, *p* `r psig(fish.test$p.value)`.
 This lack of a relationship suggests that older and younger infants are not being tested in experimental conditions that differentially manipulate the number of features changed.
 
-## (Insert Figure 5 about here)
+## (Insert Figure \@ref(fig:PlotFeatEffect) about here)
 
@@
 
-To assess whether the position of the mispronunciation has an impact on mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to mispronunciations on the onset, medial, and coda phonemes.
-We did not include data for which the mispronunciation varied in regard to position (*n* = `r vary_loc`) or was not reported (*n* = `r with(misp_location_info, n_exp_conditions[is.na(mispron_location)])`).
-The analysis was therefore based on a subset of the overall dataset, with `r with(mli, n_exp_conditions[mispron_location == "onset"])` experimental conditions comparing a mispronunciation on the onset phoneme, `r with(mli, n_exp_conditions[mispron_location == "medial"])` experimental conditions comparing a mispronunciation on the medial phoneme, and `r with(mli, n_exp_conditions[mispron_location == "coda"])` experimental conditions comparing a mispronunciation on the coda phoneme.
+We next calculated the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in response to mispronunciations on the onset, medial, and coda phonemes.
+We did not include data for which the mispronunciation varied within record in regard to position (*n* = `r vary_loc`) or was not reported (*n* = `r with(misp_location_info, n_exp_conditions[is.na(mispron_location)])`).
+The analysis was therefore based on a subset of records of the overall dataset, testing mispronunciations on the onset (*n* = `r with(mli, n_exp_conditions[mispron_location == "onset"])` records), medial (*n* = `r with(mli, n_exp_conditions[mispron_location == "medial"])`), and coda (*n* = `r with(mli, n_exp_conditions[mispron_location == "coda"])`) phonemes.
 We coded the onset, medial, and coda positions as continuous variables, to evaluate the importance of each subsequent position [@Marslen-Wilson1989].
@@
 
+ms.agg
+
 ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = location_label)) + 
@@
 
-lay <- rbind(c(1), c(2))
-#lay <- rbind(c(1,2))
-
-  jpeg(filename = "figures/Figure_7_Misp_position.jpg",
-       width = 500, height = 600, units = "px")
-
-ger.plot.age <- grid.arrange(ms.agg, ms.age,
-                             layout_matrix = lay)
+# lay <- rbind(c(1), c(2))
+# #lay <- rbind(c(1,2))
+# 
+#   jpeg(filename = "figures/Figure_7_Misp_position.jpg",
+#        width = 500, height = 600, units = "px")
+# 
+# ger.plot.age <- grid.arrange(ms.agg, ms.age,
+#                              layout_matrix = lay)
+# 
+#  dev.off()
+# 
+# grid.draw(ger.plot.age)
+
+  jpeg(filename = "figures/Figure_6_Misp_Position.jpg", 
+       width = 500, height = 300, units = "px")
+
+  ms.agg
 
@@
 
-grid.draw(ger.plot.age)
-
-```
-
-To understand the relationship between mispronunciation position and  mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with mispronunciation position and condition as moderators.
-The moderator test was significant, `r mod_test(rma_LinearLocationCondition)`.
+```
+
+When mispronunciation position was included as a moderator, the moderator test was significant, `r mod_test(rma_LinearLocationCondition)`.
 For the interaction between condition and mispronunciation position, the estimate was small but significant ($\beta$ `r full_estimate(sum_eff)`.
-As can be seen in Figure \@ref(fig:PlotMispPosit)a, mispronunciation sensitivity decreased linearly as the position of the mispronunciation moved later in the word, with sensitivity greatest for onset mispronunciations and smallest for coda mispronunciations.
-
-To better understand how this moderator impacted our estimate of developmental change in mispronunciation sensitivity, we added age as a moderator.
-The moderator test was significant, `r mod_test(rma_LinearLocationCondition_age)`.
-The estimate for the three-way interaction between age, condition, and mispronunciation position was not significant ($\beta$ `r full_estimate(sum_eff_age)`.
-As can be seen in Figure \@ref(fig:PlotMispPosit)b, mispronunciation sensitivity but stays relatively stable for onset and medial mispronunciaitons.
-For mispronunciations on the coda position it appears that mispronunciation sensitivity increases with age, but this is likely underpowered and therefore not detectable by our meta-analysis.
-
-Finally, we examined whether infants are disproportionately tested in conditions different mispronunciation positions based on their age.
+As can be seen in Figure \@ref(fig:PlotMispPosit), mispronunciation sensitivity decreased linearly as the position of the mispronunciation moved later in the word, with sensitivity greatest for onset mispronunciations and smallest for coda mispronunciations.
+
+When age was added as a moderator, the moderator test was significant, `r mod_test(rma_LinearLocationCondition_age)`.
+The estimate for the three-way interaction between age, condition, and mispronunciation position was small and not significant ($\beta$ `r full_estimate(sum_eff_age)`.
+
 Due to the small sample size of coda mispronunciations, we only included 3 age groups in Fisher's exact test.
@@
 
-## (Insert Figure 7 about here)
+## (Insert Figure \@ref(fig:PlotMispPosit) about here)
+
+### Type of mispronunciation (consonant or vowel)
+
+```{r CV_descript}
+
+CV_info <- dat %>%
+  group_by(type_feature) %>%
+  summarize(n_exp_conditions =  n())
+
+CV_location_info <- dat %>%
+  group_by(type_feature, mispron_location) %>%
+  summarize(n_exp_conditions =  n())
+
+```
+
+We next calculated the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in response to the type of mispronunciation, consonant or vowel.
+Furthermore, sensitivity to consonant and vowel mispronunciations is hypothesized to differ depending on whether the infant is learning a Germanic or Romance language.
+We therefore conducted two sets of analyses, one analyzing consonants and vowels alone and a second including langauge family as a moderator.
+We did not include data for which mispronunciation type varied within experiment and was not reported separately (*n* = `r with(CV_info, sum(n_exp_conditions[type_feature == "consonant_and_vowel" | type_feature == "consonant_vowel_tone"]))`).
+The analysis was therefore based on a subset of the overall dataset, comparing records with consonant (*n* = `r with(CV_info, n_exp_conditions[type_feature == "consonant"])`) and vowel (*n* = `r with(CV_info, n_exp_conditions[type_feature == "vowel"])`) mispronunciations.
+
+```{r MPtype_cv}
+
+# C vs. V with condition
+
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
+
+rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition, data = db_type, random = ~same_infant_calc | short_cite)
+
+sum_eff2 <- coef(summary(rma_TypeFeaturesMP_Condition))[4,]
+
+```
+
+```{r MPtype_cv_age}
+
+# with condition
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
+
+rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~same_infant_calc | short_cite)
+
+sum_eff_age <- coef(summary(rma_TypeFeaturesMP_Condition))[8,]
+
+ # divide into age groups
+
+ db_type$age_group <- ntile(db_type$mean_age_1, 4)
+
+ type_ages <- db_type %>%
+  group_by(age_group, type_feature) %>%
+  summarize(n =  n())
+
+ #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
+
+ type_ages <- type_ages %>% spread(type_feature, n)
+
+ #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
+fish.test <- fisher.test(type_ages, workspace=2e8)
+
+```
+
+```{r PlotMispType, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations.
+Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations by age.
+For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
+
+db_type = dat %>%
+  filter(type_feature == "consonant" | type_feature == "vowel")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
+
+db_type$condition_label <- ifelse(db_type$condition==1, "Correct", "Mispronunciation")
+
+db_type$type_label <- ifelse(db_type$type_feature=="consonant", "Consonant", "Vowel")
+
+db_type <- db_type[,c("short_cite", "is_correct", "is_mp", "type_label", "condition_label", "g_calc", "weights_g", "mean_age_1", "n_1")]
+
+dat.c <- subset(db_type, is_correct == 1)
+dat.m <- subset(db_type, is_mp == 1)
+
+dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "type_label", "mean_age_1", "n_1"))
+
+dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
+dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
+
+ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
+  #facet_grid(.~dv_label)+
+    geom_violin() + 
+  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
+  labs(title="a")+
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Misp. Sensitivity")
+
+ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = type_label)) + 
+    #facet_grid(.~dv_label)+
+  geom_point(aes(size = n_1),show.legend=FALSE) +
+  labs(title="b")+
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Misp. Sensitivity")
+
+lay <- rbind(c(1), c(2))
+#lay <- rbind(c(1,2))
+
+  jpeg(filename = "figures/Figure_8_CV.jpg",
+       width = 500, height = 600, units = "px")
+
+ger.plot.age <- grid.arrange(ms.agg, ms.age,
+                             layout_matrix = lay)
+
+ dev.off()
+
+grid.draw(ger.plot.age)
+
+```
+
+When mispronunciation type was included as a moderator, the moderator test was significant, `r mod_test(rma_TypeFeaturesMP_Condition)`, but the interaction between mispronunciation type and condition ($\beta$`r full_estimate(sum_eff2)`) was not significant.
+The results suggest that overall, infants' sensitivity to consonant and vowel mispronunciations was similar (Figure \@ref(fig:PlotMispType)a).
+
+When age was added as a moderator, the moderator test was significant, `r mod_test(rma_TypeFeaturesMP_Condition)` and the estimate for the three-way interaction between age, condition, and mispronunciation type was significant, but relatively small ($\beta$ `r full_estimate(sum_eff_age)`.
+As can be seen in Figure \@ref(fig:PlotMispType)b, as infants age, mispronunciation sensitivity grows larger for vowel mispronunciations but stays steady for consonant mispronunciations.
+Noticeably, mispronunciation sensitivity appears greater for consonant compared to vowel mispronunciations at younger ages, but this difference diminishes as infants age.
+
+The results of Fisher's exact test were significant, *p* `r psig(fish.test$p.value)`.
+Older infants were more likely to be tested on consonant mispronunciations, while younger infants were more likely to be tested on vowel mispronunciations.
+It is not immediately clear whether the relationship between infant age and type of mispronunciation influences our estimate of how mispronunciation sensitivity changes with development.
+Whether consonant or vowel mispronunciations are more "difficult" is a matter of theoretical debate, but some evidence suggest that it may be influenced by infants' native language [@Nazzi2016].
+We next examined whether this was the case.
+
+## (Insert Figure \@ref(fig:PlotMispType) about here)
+
+```{r MPtype_cv_lang_descript}
+
+family <- dat %>%
+  group_by(lang_family) %>%
+  summarize(count = n())
+
+lang_family <- dat %>%
+  group_by(native_lang, lang_family) %>%
+  summarize(count = n())
+
+cv_family <- dat %>%
+  group_by(type_feature, lang_family) %>%
+  summarize(count = n())
+
+```
+
+```{r MPtype_cv_lang}
+
+# with condition
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
+
+db_type <- subset(db_type, lang_family != "Sino-Tibetian")
+
+rma_TypeFeaturesMPC <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family, data = db_type, random = ~same_infant_calc | short_cite)
+
+sum_eff_fam <- coef(summary(rma_TypeFeaturesMPC))[7,]
+sum_eff_famcv <- coef(summary(rma_TypeFeaturesMPC))[8,]
+
+```
+
+```{r MPtype_cv_lang_age}
+# with condition
+db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
+
+db_type <- subset(db_type, lang_family != "Sino-Tibetian")
+
+rma_TypeFeaturesMPC_age <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family*age.C, data = db_type, random = ~same_infant_calc | short_cite)
+
+sum_eff2_lang_age <- coef(summary(rma_TypeFeaturesMPC_age))[16,]
+
+# summary(glht(rma_TypeFeaturesMPC, linfct=cbind(contrMat(rep(1,8), type="Tukey"))), test=adjusted("none"))
+# 
+# ranef(rma_TypeFeaturesMPC)
+
+# divide into age groups
+
+ db_type$age_group <- ntile(db_type$mean_age_1, 3)
+
+ db_type$lang_cv <- paste(db_type$lang_family, db_type$type_feature, sep = "_")
+
+ type_lang_ages <- db_type %>%
+  group_by(age_group, lang_cv) %>%
+  summarize(n =  n())
+
+ #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
+
+ type_lang_ages <- type_lang_ages %>% spread(lang_cv, n)
+
+ #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
+fish.test <- fisher.test(type_lang_ages, workspace=2e8)
+
+```
+
+```{r PlotCVEffectLang, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language.
+Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language by age.
+For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
+
+db_type = dat %>%
+  filter(type_feature == "consonant" | type_feature == "vowel")
+
+db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
+
+db_type <- subset(db_type, lang_family != "Sino-Tibetian")
+
+db_type$condition_label <- ifelse(db_type$condition==1, "Correct", "Mispronunciation")
+
+db_type$type_label <- ifelse(db_type$type_feature=="consonant", "Consonant", "Vowel")
+
+db_type <- db_type[,c("short_cite", "is_correct", "is_mp", "type_label", "condition_label", "lang_family", "g_calc", "weights_g", "mean_age_1", "n_1")]
+
+dat.c <- subset(db_type, is_correct == 1)
+dat.m <- subset(db_type, is_mp == 1)
+
+dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "type_label", "lang_family", "mean_age_1", "n_1"))
+
+dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
+dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
+
+ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
+  facet_grid(.~lang_family)+
+    geom_violin() + 
+  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
+  labs(title="a")+
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_manual(values=cbPalette)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Hedges' g")
+
+ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = type_label)) + 
+  facet_grid(.~lang_family)+
+  geom_point(aes(size = n_1),show.legend=FALSE) +
+  labs(title="b")+
+  geom_line(y= 0, linetype="dotted") + 
+  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
+  scale_colour_manual(values=cbPalette)+
+  apatheme +
+  theme(legend.title = element_blank(),
+        legend.position = "bottom") + 
+  xlab("Age in months") + 
+  ylab("Hedges' g")
+
+lay <- rbind(c(1), c(2))
+#lay <- rbind(c(1,2))
+
+  jpeg(filename = "figures/Figure_9_LangCV.jpg",
+       width = 500, height = 900, units = "px")
+
+ger.plot.age <- grid.arrange(ms.agg, ms.age,
+                             layout_matrix = lay)
+
+ dev.off()
+
+grid.draw(ger.plot.age)
+
+# The interaction between condition and language family was significant ($\beta$`r full_estimate(sum_eff_fam)`), suggesting that the estimate for mispronunciation sensitivity was greater for infants learning a Romance compared to Germanic language.
+However, when a model evaluating this specific interaction, without mispronunciation type, was calculated, the estimate was much smaller and not significant.
+This suggests that the interaction between condition and language family may be over-estimated.
+
+```
+
+We first classified infants into language families.
+Infants learning American English (*n* = `r with(lang_family, count[native_lang == "American English"])`), British English (*n* = `r with(lang_family, count[native_lang == "British English"])`), Danish (*n* = `r with(lang_family, count[native_lang == "Danish"])`), Dutch (*n* = `r with(lang_family, count[native_lang == "Dutch"])`), and German (*n* = `r with(lang_family, count[native_lang == "German"])`) were classified into the Germanic language family (*n* = `r with(family, count[lang_family == "Germanic"])`).
+Infants learning Catalan (*n* = `r with(lang_family, count[native_lang == "Catalan"])`), Spanish (*n* = `r with(lang_family, count[native_lang == "Spanish"])`), French (*n* = `r with(lang_family, count[native_lang == "French"])`), Catalan and Spanish simultaneously (i.e.
+bilinguals; *n* = `r with(lang_family, count[native_lang == "Catalan-Spanish"])`), and Swiss French (*n* = `r with(lang_family, count[native_lang == "Swiss French"])`) were classified into the Romance language family (*n* = `r with(family, count[lang_family == "Romance"])`).
+
+When language family was included as a moderator, the moderator test was significant, `r mod_test(rma_TypeFeaturesMPC)`.
+The three-way interaction between mispronunciation type, condition, language family was large and also significant , $\beta$`r full_estimate(sum_eff_famcv)`.
+As can be seen in Figure \@ref(fig:PlotCVEffectLang)a, mispronunciation sensitivity for consonants was similar for Germanic and Romance languages.
+Mispronunciation sensitivity for vowels, however, was greater for Germanic compared to Romance languages.
+
+We next added age as a moderator, resulting in a significant moderator test, `r mod_test(rma_TypeFeaturesMPC_age)`, and a small but significant estimate for the four-way interaction between mispronunciation type, condition, language family, and age $\beta$`r full_estimate(sum_eff2_lang_age)`.
+As can also be seen in Figure \@ref(fig:PlotCVEffectLang)b, for infants learning Germanic languages, sensitivity to consonant and vowel mispronunciations did not change with age.
+In contrast, infants learning Romance languages show a decrease in sensitivity to consonant mispronunciations, but an increase in sensitivity to vowel mispronunciations with age.
+
+We were unable to use Fisher's exact test to evaluate whether infants of different ages were more or less likely to be tested on consonant or vowel mispronunciations depending on their native language.
+This was due to the small sample size of infants learning Romance languages (*n* = `r with(family, count[lang_family == "Romance"])`).
+
+## (Insert Figure \@ref(fig:PlotCVEffectLang) about here)
 
@@
 
-To assess whether phonological overlap between the target and distractor image labels has an impact on the size of mispronunciation sensitivity, we examined the meta-analytic effect for object identification in response to mispronunciations and mispronunciation sensitivity when the target-distractor pairs either had no overlap or shared the same onset phoneme.
-We did not include data for which the overlap included both the onset and medial phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset/medial"])`), coda phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "coda"])`), or for targets paired with an unfamiliar distractor image `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "novel"])`.
-The analysis was therefore based on a subset of the overall dataset, with `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset"])` experimental conditions containing onset phoneme overlap between the target and distractor and `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "no"])` containing no overlap between target and distractor.
+We next examined the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in response to mispronunciations when the target-distractor pairs either had no overlap or shared the same onset phoneme.
+We did not include data for which the overlap included both the onset and medial phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset/medial"])`), coda phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "coda"])`), or for targets paired with an unfamiliar distractor image (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "novel"])`).
+The analysis was therefore based on a subset of the overall dataset, comparing `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset"])` records containing onset phoneme overlap between the target and distractor with `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "no"])` containing no overlap between target and distractor.
 
@@
 
-# db_ET_MPo_MS = db_ET_MPo_MS %>%
-#   filter(mispron_location != "onset")
+dist_overlap_info <- db_ET_MPo_MS %>%
+  group_by(distractor_overlap, mispron_location) %>%
+  summarize(n_exp_conditions =  n())
+
+ db_ET_MPo_MS = db_ET_MPo_MS %>%
+   filter(mispron_location == "onset")
 
@@
 
-To understand the relationship between phonological overlap between target and distractor and  mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with distractor overlap and condition as moderators.
-The moderator test was significant, `r mod_test(rma_DistractorOverlapMS)`.
+When target-distractor overlap was included as a moderator, the moderator test was significant, `r mod_test(rma_DistractorOverlapMS)`.
 The estimate for the interaction between condition and distractor overlap was small, but significant ($\beta$ `r full_estimate(sum_eff2)`, suggesting that mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap.
@@
 
-To better understand how this moderator impacted our estimate of developmental change in mispronunciation sensitivity, we added age as a moderator.
-The moderator test was significant, `r mod_test(rma_DistractorOverlap_age_MS)` and the estimate for the three-way interaction between age, condition, and distractor overlap was significant, but relatively small ($\beta$ = `r full_estimate(sum_eff_age)`.
+When age was added as a moderator, the moderator test was significant, `r mod_test(rma_DistractorOverlap_age_MS)` and the estimate for the three-way interaction between age, condition, and distractor overlap was significant, but relatively small ($\beta$ = `r full_estimate(sum_eff_age)`.
 As can be seen in Figure \@ref(fig:PlotDistOverlap)b, mispronunciation sensitivity increases with age for target-distractor pairs containing onset overlap, but decreases with age for target-distractor pairs containing no overlap.
 
-Finally, we examined whether infants are disproportionately tested in experiments with or without phonological overlap between the target and distractor labels based on their age.
 The results of Fisher's exact test were significant, *p* `r psig(fish.test$p.value)`.
@@
 It therefore appears that older infants were given a more challenging task than younger infants.
-This may explain why infants in the onset overlap condition, a harder task, have a greater effect size estimate for mispronunciation sensitivity than those in the no overlap condition, which is a comparably easier task.
 We return to this issue in the General Discussion.
 
-## (Insert Figure 7 about here)
-
-### Type of mispronunciation (consonant or vowel)
-
-```{r CV_descript}
-
-CV_info <- dat %>%
-  group_by(type_feature) %>%
-  summarize(n_exp_conditions =  n())
-
-CV_location_info <- dat %>%
-  group_by(type_feature, mispron_location) %>%
-  summarize(n_exp_conditions =  n())
-
-```
-
-To assess whether the type of mispronunciation impacts sensitivity to mispronunciations, we calculated the meta-analytic effect for object identification in response to the type of mispronunciation.
-Although most theoretical discussion of mispronunciation type has focused on consonants and vowels, our dataset also included tone mispronunciations.
-In our analysis, we were interested in the difference between consonants and vowels, but also include an exploratory analysis of responses to tones, consonants, and vowels.
-Furthermore, sensitivity to consonant and vowel mispronunciations is hypothesized to differ depending on whether the infant is learning a Germanic or Romance language.
-We therefore conducted two sets of analyses, one analyzing consonants and vowels alone, a second including langauge family as a moderator, and a third comparing responses to tones with that of consonants and vowels, separately.
-For the latter analysis, tones were coded as the reference condition.
-We did not include data for which mispronunciation type varied within experiment and was not reported separately (*n* = `r with(CV_info, n_exp_conditions[type_feature == "consonant_and_vowel" | type_feature == "consonant_vowel_tone"])`).
-The analysis was therefore based on a subset of the overall dataset, with `r with(CV_info, n_exp_conditions[type_feature == "consonant"])` experimental conditions comparing a consonant mispronunciation, `r with(CV_info, n_exp_conditions[type_feature == "vowel"])` experimental conditions comparing a vowel mispronunciation, and `r with(CV_info, n_exp_conditions[type_feature == "tone"])` experimental conditions comparing a tone mispronunciation.
-Below, we first report the set of analyses comparing consonants with vowels and between language families before moving on to the set of exploratory analyses comparing tones with that of consonants and vowels.
-
-```{r MPtype_cv}
-
-# C vs. V with condition
-
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition, data = db_type, random = ~same_infant_calc | short_cite)
-
-sum_eff2 <- coef(summary(rma_TypeFeaturesMP_Condition))[4,]
-
-```
-
-```{r MPtype_cv_age}
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~same_infant_calc | short_cite)
-
-sum_eff_age <- coef(summary(rma_TypeFeaturesMP_Condition))[8,]
-
- # divide into age groups
-
- db_type$age_group <- ntile(db_type$mean_age_1, 4)
-
- type_ages <- db_type %>%
-  group_by(age_group, type_feature) %>%
-  summarize(n =  n())
-
- #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
-
- type_ages <- type_ages %>% spread(type_feature, n)
-
- #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
-fish.test <- fisher.test(type_ages, workspace=2e8)
-
-```
-
-```{r PlotMispType, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations.
-Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations by age.
-For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
-
-db_type = dat %>%
-  filter(type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-db_type$condition_label <- ifelse(db_type$condition==1, "Correct", "Mispronunciation")
-
-db_type$type_label <- ifelse(db_type$type_feature=="consonant", "Consonant", "Vowel")
-
-db_type <- db_type[,c("short_cite", "is_correct", "is_mp", "type_label", "condition_label", "g_calc", "weights_g", "mean_age_1", "n_1")]
-
-dat.c <- subset(db_type, is_correct == 1)
-dat.m <- subset(db_type, is_mp == 1)
-
-dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "type_label", "mean_age_1", "n_1"))
-
-dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
-dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
-
-ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
-  #facet_grid(.~dv_label)+
-    geom_violin() + 
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
-  labs(title="a")+
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Misp. Sensitivity")
-
-ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = type_label)) + 
-    #facet_grid(.~dv_label)+
-  geom_point(aes(size = n_1),show.legend=FALSE) +
-  labs(title="b")+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Misp. Sensitivity")
-
-lay <- rbind(c(1), c(2))
-#lay <- rbind(c(1,2))
-
-  jpeg(filename = "figures/Figure_8_CV.jpg",
-       width = 500, height = 600, units = "px")
-
-ger.plot.age <- grid.arrange(ms.agg, ms.age,
-                             layout_matrix = lay)
-
- dev.off()
-
-grid.draw(ger.plot.age)
-
-```
-
-To understand the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with mispronunciation type and condition as moderators.
-The moderator test was significant, `r mod_test(rma_TypeFeaturesMP_Condition)`, but the interaction between mispronunciation type and condition ($\beta$`r full_estimate(sum_eff2)`) was not significant.
-The results suggest that overall, infants' sensitivity to consonant and vowel mispronunciations was similar.
-
-We next examined whether age modulates mispronunciation sensitivity when the mispronunciation is a consonant or a vowel.
-When age was added as a moderator, the moderator test was significant, `r mod_test(rma_TypeFeaturesMP_Condition)` and the estimate for the three-way interaction between age, condition, and mispronunciation type was significant, but relatively small ($\beta$ = `r full_estimate(sum_eff_age)`.
-As can be seen in Figure \@ref(fig:PlotMispType)b, as infants age, mispronunciation sensitivity grows larger for vowel mispronunciations but stays steady for consonant mispronunciations.
-Noticeably, mispronunciation sensitivity appears greater for consonant compared to vowel mispronunciations at younger ages, but this difference diminishes as infants age.
-
-Finally, we examined whether infants are disproportionately tested in experiments with a consonant or vowel mispronunciation based on their age.
-The results of Fisher's exact test were significant, *p* `r psig(fish.test$p.value)`.
-Older infants were more likely to be tested on consonant mispronunciations, while younger infants were more likely to be tested on vowel mispronunciations.
-It is not immediately clear whether the relationship between infant age and type of mispronunciation influences our estimate of how mispronunciation sensitivity changes with development.
-Whether consonant or vowel mispronunciations are more "difficult" is a matter of theoretical debate, but some evidence suggest that it may be influenced by infants' native language [@Nazzi2016].
-We next examined whether this was the case.
-
-## (Insert Figure 8 about here)
-
-```{r MPtype_cv_lang_descript}
-
-family <- dat %>%
-  group_by(lang_family) %>%
-  summarize(count = n())
-
-lang_family <- dat %>%
-  group_by(native_lang, lang_family) %>%
-  summarize(count = n())
-
-cv_family <- dat %>%
-  group_by(type_feature, lang_family) %>%
-  summarize(count = n())
-
-```
-
-```{r MPtype_cv_lang}
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-db_type <- subset(db_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeaturesMPC <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family, data = db_type, random = ~same_infant_calc | short_cite)
-
-sum_eff_fam <- coef(summary(rma_TypeFeaturesMPC))[7,]
-sum_eff_famcv <- coef(summary(rma_TypeFeaturesMPC))[8,]
-
-```
-
-```{r MPtype_cv_lang_age}
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-db_type <- subset(db_type, lang_family != "Sino-Tibetian")
-
-rma_TypeFeaturesMPC_age <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*lang_family*age.C, data = db_type, random = ~same_infant_calc | short_cite)
-
-sum_eff2_lang_age <- coef(summary(rma_TypeFeaturesMPC_age))[16,]
-
-# summary(glht(rma_TypeFeaturesMPC, linfct=cbind(contrMat(rep(1,8), type="Tukey"))), test=adjusted("none"))
-# 
-# ranef(rma_TypeFeaturesMPC)
-
-# divide into age groups
-
- db_type$age_group <- ntile(db_type$mean_age_1, 3)
-
- db_type$lang_cv <- paste(db_type$lang_family, db_type$type_feature, sep = "_")
-
- type_lang_ages <- db_type %>%
-  group_by(age_group, lang_cv) %>%
-  summarize(n =  n())
-
- #nfeature_ages <- subset(nfeature_ages, n_feature != 0)
-
- type_lang_ages <- type_lang_ages %>% spread(lang_cv, n)
-
- #chisq <- chisq.test(nfeature_ages, simulate.p.value = TRUE)
-fish.test <- fisher.test(type_lang_ages, workspace=2e8)
-
-```
-
-```{r PlotCVEffect_Lang, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language.
-Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language by age.
-For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
-
-db_type = dat %>%
-  filter(type_feature == "consonant" | type_feature == "vowel")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("consonant", "vowel"))
-
-db_type <- subset(db_type, lang_family != "Sino-Tibetian")
-
-db_type$condition_label <- ifelse(db_type$condition==1, "Correct", "Mispronunciation")
-
-db_type$type_label <- ifelse(db_type$type_feature=="consonant", "Consonant", "Vowel")
-
-db_type <- db_type[,c("short_cite", "is_correct", "is_mp", "type_label", "condition_label", "lang_family", "g_calc", "weights_g", "mean_age_1", "n_1")]
-
-dat.c <- subset(db_type, is_correct == 1)
-dat.m <- subset(db_type, is_mp == 1)
-
-dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "type_label", "lang_family", "mean_age_1", "n_1"))
-
-dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
-dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
-
-ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
-  facet_grid(.~lang_family)+
-    geom_violin() + 
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
-  labs(title="a")+
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Hedges' g")
-
-ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = type_label)) + 
-  facet_grid(.~lang_family)+
-  geom_point(aes(size = n_1),show.legend=FALSE) +
-  labs(title="b")+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
-  scale_colour_manual(values=cbPalette)+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Hedges' g")
-
-lay <- rbind(c(1), c(2))
-#lay <- rbind(c(1,2))
-
-  jpeg(filename = "figures/Figure_9_LangCV.jpg",
-       width = 500, height = 900, units = "px")
-
-ger.plot.age <- grid.arrange(ms.agg, ms.age,
-                             layout_matrix = lay)
-
- dev.off()
-
-grid.draw(ger.plot.age)
-
-```
-
-To examine whether infants' native language impacts sensitivity to consonant and vowel mispronunciations, we classified infants into language families.
-Infants learning American English (*n* = `r with(lang_family, count[native_lang == "American English"])`), British English (*n* = `r with(lang_family, count[native_lang == "British English"])`), Danish (*n* = `r with(lang_family, count[native_lang == "Danish"])`), Dutch (*n* = `r with(lang_family, count[native_lang == "Dutch"])`), and German (*n* = `r with(lang_family, count[native_lang == "German"])`) were classified into the Germanic language family (*n* = `r with(family, count[lang_family == "Germanic"])`).
-Infants learning Catalan (*n* = `r with(lang_family, count[native_lang == "Catalan"])`), Spanish (*n* = `r with(lang_family, count[native_lang == "Spanish"])`), French (*n* = `r with(lang_family, count[native_lang == "French"])`), Catalan and Spanish simultaneously (i.e.
-bilinguals; *n* = `r with(lang_family, count[native_lang == "Catalan-Spanish"])`), and Swiss French (*n* = `r with(lang_family, count[native_lang == "Swiss French"])`) were classified into the Romance language family (*n* = `r with(family, count[lang_family == "Romance"])`).
-
-We assessed whether the relationship between mispronunciation type (consonant or vowel) and mispronunciation sensitivity was modulated by language family.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family as additional moderators.
-The moderator test was significant, `r mod_test(rma_TypeFeaturesMPC)`.
-The interaction between condition and language family was significant ($\beta$`r full_estimate(sum_eff_fam)`), suggesting that the estimate for mispronunciation sensitivity was greater for infants learning a Romance compared to Germanic language.
-However, when a model evaluating this specific interaction, without mispronunciation type, was calculated, the estimate was much smaller and not significant.
-This suggests that the interaction between condition and language family may be over-estimated.
-The three-way interaction between mispronunciation type, condition, language family was large and also significant , $\beta$`r full_estimate(sum_eff_famcv)`.
-As can be seen in Figure \@ref(fig:PlotCVEffect_Lang)a, mispronunciation sensitivity for consonants was similar for Germanic and Romance languages.
-Mispronunciation sensitivity for vowels, however, was greater for Germanic compared to Romance languages.
-
-Finally, we examined the relationship between language family and infant age and mispronunciation sensitivity to consonants and vowels.
-We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as language family and age as additional moderators.
-The moderator test was significant, `r mod_test(rma_TypeFeaturesMPC_age)`, and the estimate for the four-way interaction between mispronunciation type, condition, language family, and age was small, but significant , $\beta$`r full_estimate(sum_eff2_lang_age)`.
-As can also be seen in Figure \@ref(fig:PlotCVEffect_Lang)b, for infants learning Germanic languages, sensitivity to consonant and vowel mispronunciations did not change with age.
-In contrast, infants learning Romance languages show a decrease in sensitivity to consonant mispronunciations, but an increase in sensitivity to vowel mispronunciations with age.
-
-We were unable to use Fisher's exact test to evaluate whether infants of different ages were more or less likely to be tested on consonant or vowel mispronunciations depending on their native language.
-This was due to the small sample size of infants learning Romance languages (*n* = `r with(family, count[lang_family == "Romance"])`).
-
-## (Insert Figure 9 about here)
-
-```{r MPtype_cvt}
-
-# C vs. V vs. T with condition
-
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel"| type_feature == "tone")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("tone", "consonant", "vowel"))
-
-rma_TypeFeaturesMP_ConditionT <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition, data = db_type, random = ~same_infant_calc | short_cite)
-
-sum_eff2c <- coef(summary(rma_TypeFeaturesMP_ConditionT))[5,]
-sum_eff2v <- coef(summary(rma_TypeFeaturesMP_ConditionT))[6,]
-
-```
-
-```{r MPtype_cvt_age}
-
-# with condition
-db_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" | type_feature == "tone")
-
-db_type$type_feature <- factor(db_type$type_feature, levels = c("tone", "consonant", "vowel"))
-
-rma_TypeFeaturesMP_Condition_age <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~same_infant_calc | short_cite)
-
-sum_eff_tc <- coef(summary(rma_TypeFeaturesMP_Condition_age))[11,]
-sum_eff2_tv <- coef(summary(rma_TypeFeaturesMP_Condition_age))[12,]
-
-```
-
-Although we had no predictions regarding mispronunciation sensitivity to tone mispronunciations, we included an exploratory analysis to examine whether responses to tone mispronunciations were different from that of consonants or vowels.
-When mispronunciation type (tone, consonant, vowel) and condition (correct, mispronunciation) were included as moderators, the moderator test was significant, `r mod_test(rma_TypeFeaturesMP_ConditionT)`.
-The interactions between condition and consonant mispronunciations ($\beta$ = `r full_estimate(sum_eff2c)`) as well as vowel mispronunciations ($\beta$ = `r full_estimate(sum_eff2v)`), were not significant, suggesting that there was no difference in looks to the target in response to tone mispronunciations compared with consonant or vowel mispronunciations.
-
-We further included an exploratory analysis of the relationship between infant age and the impact of tone mispronunciations in comparison to consonant and vowel mispronunciations.
-We included mispronunciation type, condition (correct pronunciation, mispronunciation) as well as age as additional moderators.
-The moderator test was significant, `r mod_test(rma_TypeFeaturesMP_ConditionT)`, but the interactions between condition, age, and both consonant ($\beta$ = `r full_estimate(sum_eff_tc)`) and vowel ($\beta$ = `r full_estimate(sum_eff2_tv)`) mispronunciations were not significant.
-Infants' sensitivity to tone mispronunciations compared to consonant or vowel mispronunciations did not differ with age.
+## (Insert Figure \@ref(fig:PlotDistOverlap) about here)
 
@@
 
-To assess whether familiarity with the distractor image modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced and were either paired with a familiar or unfamiliar distractor.
-A familiar distractor was used in `r with(distr_info, n_exp_conditions[object_pair == "familiar_familiar"])` experimental conditions and a unfamiliar distractor in `r with(distr_info, n_exp_conditions[object_pair == "familiar_novel"])` experimental conditions.
+We next calculated the meta-analytic effect of mispronunciaiton sensitivity (moderator: condition) in experiments were the target image was paired with a familiar or unfamiliar distractor image.
+A familiar distractor was used in `r with(distr_info, n_exp_conditions[object_pair == "familiar_familiar"])` records and a unfamiliar distractor in `r with(distr_info, n_exp_conditions[object_pair == "familiar_novel"])` records.
 
@@
 
-To understand the relationship between distractor familiarity and mispronunciation sensitivity, we evaluated the effect size Hedges' *g* with distractor familiarity and condition as moderators.
-The moderator test was significant, `r mod_test(rma_NFeatures)`, but the effect of distractor familiarity ($\beta$`r full_estimate(d_fam)`) as well as the interaction between distractor familiarity and condition ($\beta$`r full_estimate(d_fam_condit)`) were not significant.
+When distractor familiarity was included as a moderator, the moderator test was significant, `r mod_test(rma_NFeatures)`, but the effect of distractor familiarity ($\beta$`r full_estimate(d_fam)`) as well as the interaction between distractor familiarity and condition ($\beta$`r full_estimate(d_fam_condit)`) were not significant.
 The results suggest that overall, infants' familiarity with the distractor object (familiar or unfamiliar) did not impact their mispronunciation sensitivity.
 
-We next examined whether age modulates object recognition or mispronunciation sensitivity when the distractor image is familiar or unfamiliar.
-Based on previous results, we expected older infants  to have greater mispronunciation sensitivity than younger infants when the distractor was unfamiliar compared to familiar.
-To evaluate this prediction, we added age as a moderator.
-The moderator test was significant `r mod_test(rma_Distractor_age)`.
+When age was added as a moderator, the moderator test was significant `r mod_test(rma_Distractor_age)`.
 The estimate for the  three-way-interaction between condition, distractor familiarity, and age was small and not significant ($\beta$ = `r full_estimate(sum_eff_age)`.
@@
 
-Finally, we examined whether infants are disproportionately tested in experiments with familiar or unfamiliar distractors based on their age.
 The results of Fisher's exact test were not significant, *p* `r psig(fish.test$p.value)`.
-This lack of a relationship suggests that older and younger infants are not being tested in experimental conditions that differentially employ distractor images that are familiar or unfamiliar.
+This lack of a relationship suggests that older and younger infants were not tested in experimental conditions that differentially employ distractor images that are familiar or unfamiliar.
 
@@
 To briefly summarize, mispronunciation sensitivity was modulated overall by the size of the mispronunciation tested, whether target-distractor pairs shared phonological overlap, and the position of the mispronunciation.
-Neither distractor familiarity (familiar, unfamiliar) or type of mispronunciation (consonant, vowel, tone) were found to impact mispronunciation sensitivity.
-The developmental trajectory of mispronunciation sensitivity was influenced by whether target-distractor pairs shared phonological overlap and type of mispronunciation, but mispronunciation size, mispronunciation position, and distractor familiarity were found to have no influence.
+Neither distractor familiarity (familiar, unfamiliar) or type of mispronunciation (consonant, vowel) were found to impact mispronunciation sensitivity.
+The developmental trajectory of mispronunciation sensitivity was influenced by type of mispronunciation and overlap between the target and distractor labels, but mispronunciation size, mispronunciation position, and distractor familiarity were found to have no influence.
 Finally, in some cases there was evidence that older and younger infants were given experimental manipulations that may have rendered the experimental task more or less difficult.
-Specifically, older children were more likely to be given target-distractor pairs that overlapped on their onset phoneme, a situation in which it is more difficult to detect a mispronunciation.
-Yet, this was not always the case; in a different instance, younger infants were given a more difficult task, mispronunciations on the medial position.
+In one instance, younger infants were given a more difficult task, mispronunciations on the medial position, which is unlikely to contribute to the lack of developmental effects in our main analysis.
+Yet, his was not always the case; in a different instance, older children were more likely to be given target-distractor pairs that overlapped on their onset phoneme, a situation in which it is more difficult to detect a mispronunciation and may have bearing on our main developmental results.
 We return to these findings in the General Discussion.
+
+## Exploratory Analyses
 
@@
 We observed, as mentioned in the Methods section, large variation in the dependent variable reported, and additionally noted that the size of the chosen post-naming analysis window varied substantially across papers.
-Researchers might adapt their analysis strategy to infants' age or they might be influenced by having observed the data.
+Researchers' analysis strategy may be adapted to infants' age or influenced by having observed the data.
 For example, consider the possibility that there is a true increase in mispronunciation sensitivity over development.
@@
 This lack of or small mispronunciation sensitivity in younger infants is likely to lead to non-significant results, which would be more difficult to publish [@Ferguson2012].
-In order to have publishable results, adjustments to the analysis approach could be made until a significant, but spurious, effect of mispronunciation sensitivity is found.
-This would lead to an increase in significant results and alter the observed developmental trajectory of mispronunciation sensitivity.
+In order to have publishable results, adjustments to the analysis approach could be made until a significant effect of mispronunciation sensitivity is found.
+This would lead to an increase in significant results and alter the observed developmental trajectory of mispronunciation sensitivity in the current meta-analysis.
 Such a scenario is in line with the publication bias we observe [@Simmons2011].
@@
 
-We included details related to timing and type of dependent variable in our coding of the dataset because they are consistently reported and might be useful for experiment design in the future by highlighting typical choices and helping establish field standards.
-In the following section, we include an exploratory analysis to investigate the possibility of systematic differences in the approach to analysis in general and across infant age.
-The purpose of this analysis was to better understand the influence of choices made in analyzing mispronunciation sensitivity studies as well as the influence these choices may have on our understanding of mispronunciation sensitivity development.
-
-## Exploratory Analyses
-
-We identified two sets of variables which varied across papers to assess the influence of data analysis choices on resulting effect size: timing (post-naming analysis window; offset time) and which dependent variable(s) were reported.
+We analyzed analysis choices related to timing (post-naming analysis window; offset time) and type of dependent variable in our coding of the dataset because they are consistently reported and might be useful for experiment design in the future by highlighting typical choices and helping establish field standards.
 In the following, we discuss the possible theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these analysis choices may have on measurements of mispronunciation sensitivity development.
@@
 
-In a typical trial in a mispronunciation sensitivity study, the target-distractor image pairs are first presented in silence, followed by auditory presentation of a carrier phrase or isolated presentation of the target word (correctly pronounced or mispronounced).
 When designing mispronunciation sensitivity studies, experimenters can choose the length of time each trial is presented.
 This includes both the length of time before the target object is named (pre-naming phase) as well as after (post-naming phase) and is determined prior to data collection.
-To examine the size of the time window analyzed in the post-naming phase (post-naming analysis window), we must first consider overall length of time in post-naming (post-naming time window), because it limits the overall time window available to analyze and might thus predict the post-naming analysis window.
-Across papers, the length of the post-naming time window varied from `r with(post_length_info, min(post_nam_actual))*1000` to `r with(post_length_info, max(post_nam_actual))*1000` ms, with a median value of `r with(dat, median(post_nam_actual))*1000` ms.
-The most popular post-naming time window length was `r with(dat, getmode(post_nam_actual))*1000` ms, used in `r with(post_length_info, n_exp_conditions[post_nam_actual == getmode(post_length_info$n_exp_conditions)])` experimental conditions.
-There was no apparent relation between infant age and post-naming time window length (*r* = `r trial.l$estimate`, 95% CI[`r trial.l$conf.int[1]`, `r trial.l$conf.int[2]`], *p* `r psig(trial.l$p.value)`).
-
-Unlike the post-naming time window, the post-naming analysis window can be chosen after the experimental data is collected.
-Interestingly, half of the experimental conditions were analyzed using the whole post-naming time window of the trial presented to the infant (*n* = `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`), while the other half were analyzed using a shorter portion of the post-naming time window, usually excluding later portions (*n* = `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`).
+If the post-naming phase represents the amount of time the infant viewed the target-distractor image pairs after auditory presentation of the target word, then the post-naming analysis window represents how much of this phase was included in the statistical analysis.
+Unlike the post-naming phase, however, the post-naming analysis window can be chosen after the experimental data is collected.
+Evidence suggests that the speed of word recognition processing is slower in young infants [@Fernald1998], which may lead researchers to include longer post-naming phases in their experiments with younger infants.
+If this is the case, we expect a negative correlation between post-naming phase length and infant age.
+
+Across papers, the length of the post-naming phase varied from `r with(post_length_info, min(post_nam_actual))*1000` to `r with(post_length_info, max(post_nam_actual))*1000` ms, with a median value of `r with(dat, median(post_nam_actual))*1000` ms.
+The most popular post-naming phase length was `r with(dat, getmode(post_nam_actual))*1000` ms, used in `r with(post_length_info, n_exp_conditions[post_nam_actual == getmode(post_length_info$n_exp_conditions)])` records.
+Regarding the post-naming analysis window, half of the records were analyzed using the whole post-naming phase presented to the infant (*n* = `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`), while the other half were analyzed using a shorter portion of the post-naming time window, usually excluding later portions (*n* = `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`).
 Across papers, the length of the post-naming analysis window varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a median value of `r with(dat, median(post_nam_dur))*1000` ms.
-The most popular post-naming analysis window length was `r with(dat, getmode(post_nam_dur))*1000` ms, used in `r with(post_name_info, n_exp_conditions[post_nam_dur == with(dat, getmode(post_nam_dur))])` experimental conditions.
-There was an inverse relationship between infant age and post-naming analysis window length, such that younger infants' looking times were analyzed using a longer post-naming analysis window, here the relationship was significant (*r* = `r post.l$estimate`, 95% CI[`r post.l$conf.int[1]`, `r post.l$conf.int[2]`], *p* `r psig(post.l$p.value)`).
-The choice to use a shorter post-naming analysis window with age is likely related to evidence that speed of processing is slower in younger infants [@Fernald1998].
-To summarize, we observe variation in time-related analysis decisions related to infants' age.
-
-Another potential source of variation in studies that analyze eye-movements is the amount of time it takes for an eye movement to be initiated in response to a visual stimulus, which we refer to as offset time.
+The most popular post-naming analysis window length was `r with(dat, getmode(post_nam_dur))*1000` ms, used in `r with(post_name_info, n_exp_conditions[post_nam_dur == with(dat, getmode(post_nam_dur))])` records.
+
+There was no apparent relation between infant age and post-naming phase length (*r* = `r trial.l$estimate`, 95% CI[`r trial.l$conf.int[1]`, `r trial.l$conf.int[2]`], *p* `r psig(trial.l$p.value)`), but there was a significant negative relationship between infant age and post-naming analysis window length, such that younger infants' looking times were analyzed using a longer post-naming analysis window (*r* = `r post.l$estimate`, 95% CI[`r post.l$conf.int[1]`, `r post.l$conf.int[2]`], *p* `r psig(post.l$p.value)`).
+Although we observe no relationship between age and post-naming phase length, a value that is determine before data collection, we do observe a relationship with post-naming analysis window length, a value that may be determined after data collection and even driven by observation of the data itself.
+In other words, we observe variation in time-related analysis decisions related to infants' age.
+
+Another potential source of variation considers the amount of time it takes for an eye movement to be initiated in response to a visual stimulus, which we refer to as offset time (time between the onset of the target word and the offset of the post-naming analysis window).
 Previous studies examining simple stimulus response latencies first determined that infants require at least 233 ms to initiate an eye-movement in response to a stimulus [@Canfield1991].
-In the first infant mispronunciation sensitivity study, @Swingley2000 used an offset time of 367 ms, which was "an 'educated guess' based on studies .
-.
-.
+In the first infant mispronunciation sensitivity study, @Swingley2000 used an offset time of 367 ms, which was "an 'educated guess' based on studies...
 showing that target and distractor fixations tend to diverge at around 400 ms." [@Swingley2000, p.
 155].
-Upon inspecting the offset time values used in the papers in our meta-analysis, the majority used a similar offset time value (between 360 and 370 ms) for analysis (*n* = `r with(offset_bin_info, n_exp_conditions[offset_bin == "367"])`), but offset values ranged from `r with(offset_bin_info, min(offset_bin))` to `r with(offset_bin_info, max(offset_bin))` ms, and were not reported for `r with(offset_info, n_exp_conditions[is.na(offset)])` experimental conditions.
+Upon inspecting the offset time values used in the papers in our meta-analysis, the majority used a similar offset time value (between 360 and 370 ms) for analysis (*n* = `r with(offset_bin_info, n_exp_conditions[offset_bin == "367"])`), but offset values ranged from `r with(offset_bin_info, min(offset_bin))` to `r with(offset_bin_info, max(offset_bin))` ms, and were not reported for `r with(offset_info, n_exp_conditions[is.na(offset)])` records.
 We note that @Swingley2009 also included offset values of 1133 ms to analyze responses to coda mispronunciations.
 There was an inverse relationship between infant age and size of offset, such that younger infants were given longer offsets, although this correlation was not significant (*r* = `r offset.l$estimate`, 95% CI[`r offset.l$conf.int[1]`, `r offset.l$conf.int[2]`], *p* `r psig(offset.l$p.value)`).
-This lack of a relationship is possibly driven by the field's consensus that an offset of about 367 ms is appropriate for analyzing word recognition with PTL measures, including studies that evaluate mispronunciation sensitivity.
-
-Although there are a priori reasons to choose the post-naming analysis window (infant age) or offset time (previous studies), these choices may occur after data collection and might therefore lead to a higher rate of false-positives [@Gelman2013].
+This lack of a relationship is possibly driven by the field's consensus that an offset of about 367 ms is appropriate for analyzing word recognition in infants, including studies that evaluate mispronunciation sensitivity.
+
+Although there are a priori reasons, such as infant age or previous studies, to choose the post-naming analysis window or offset time, these choices may occur after data collection and might therefore lead to a higher rate of false-positives [@Gelman2013].
 Considering that these choices were systematically different across infant ages, at least for the post-naming analysis window, we next explored whether the post-naming analysis window length or the offset time influenced our estimate of infants’ sensitivity to mispronunciations.
@@
 
-```{r Plot-post-name-cond-age, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different lengths of the post-naming analysis window: 2000 ms or less (orange), 2001 to 3000 ms (blue), and 3001 ms or greater (green).
+```{r PlotPostNameCondAge, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different lengths of the post-naming analysis window: 2000 ms or less (orange), 2001 to 3000 ms (blue), and 3001 ms or greater (green).
 Although length of the post-naming analysis window was included as a continuous variable in the meta-analytic model, it is divided into categories for ease of viewing.
@@
 
-We first assessed whether size of the post-naming analysis window had an impact on the overall size of the reported mispronunciation sensitivity.
+We first assessed whether post-naming analysis window length had an impact on the overall size of the reported mispronunciation sensitivity.
 We considered data from both conditions in a joint analysis and included condition (correct pronunciation, mispronunciation) as an additional moderator.
@@
 The estimate for the interaction between post-naming analysis window and condition was small but significant ($\beta$`r full_estimate(rma_post_dur_MS_eff)`).
-This relationship is plotted in Figure \@ref(fig:Plot-post-name-cond-age)a.
-The results suggest that the size of the post-naming analysis window significantly impacted our estimate of mispronunciation sensitivity.
-Specifically, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) was significantly greater when the post-naming analysis window was shorter.
-
-Considering that we found a significant relationship between the length of the post-naming analysis window and infant age, such that younger ages had a longer window of analysis, we next examined whether the size of the post-naming analysis window modulated the estimated size of mispronunciation sensitivity as infant age changed.
-We therefore included age as additional moderator of the previous analysis.
-The moderator test was significant (`r mod_test(rma_post_dur_AGE_MS)`).
-The estimate for the  three-way-interaction between condition, size of the post-naming analysis window, and age was small, but significant ($\beta$ `r full_estimate(rma_post_dur_AGE_MS_eff)`).
-As can be seen in Figure \@ref(fig:Plot-post-name-cond-age)b, a smaller post-naming analysis window leads to a greater increase in measured mispronunciation sensitivity with development.
-For example, when experimental conditions were analyzed with a post-naming analysis window of 2000 ms or less, mispronunciation sensitivity seems to increase with infant age.
-If the post-naming analysis window is greater than 2000 ms, however, there is no or a negative relation of mispronunciation sensitivity and age.
-In other words, all three possible developmental hypotheses might be supported depending on analysis choices made regarding the size of the post-naming analysis window.
-This is especially important, considering that our key question is how mispronunciation sensitivity changes with development.
+This relationship is plotted in Figure \@ref(fig:PlotPostNameCondAge)a.
+These results show that as the length of the post-naming analysis window increased, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) decreased.
+
+Considering that we found a significant relationship between the post-naming analysis window length and infant age, such that younger ages had a longer window of analysis, we next examined whether post-naming analysis window length modulated the estimated size of mispronunciation sensitivity as infant age changed.
+When age was included as a moderator, the moderator test was significant (`r mod_test(rma_post_dur_AGE_MS)`).
+The estimate for the  three-way-interaction between condition, post-naming analysis window, and age was small, but significant ($\beta$ `r full_estimate(rma_post_dur_AGE_MS_eff)`).
+As can be seen in Figure \@ref(fig:PlotPostNameCondAge)b, when records were analyzed with a post-naming analysis window of 2000 ms or less, mispronunciation sensitivity seems to increase with infant age.
+If the post-naming analysis window is greater than 2000 ms, however, there is no or a negative relation between mispronunciation sensitivity and age.
+In other words, all three possible developmental hypotheses might be supported depending on analysis choices made regarding post-naming analysis window length.
 These results suggest that conclusions about the relationship between infant age and mispronunciation sensitivity may be mediated by the size of the post-naming analysis window.
 
-## (Insert Figure 10 about here)
+## (Insert Figure \@ref(fig:PlotPostNameCondAge) about here)
 
@@
 
-We next assessed whether the time between target naming and the start of the analysis, namely offset time, had an impact on the size of the reported mispronunciation sensitivity.
+We next assessed whether offset time had an impact on the size of the reported mispronunciation sensitivity.
 When we included both condition and offset time as moderators, the moderator test was significant (`r mod_test(rma_post_dur_MS)`), but the estimate for the interaction between offset time and condition was zero ($\beta$`r full_estimate(rma_offset_MS_eff)`).
@@
 When both offset time and condition were included as moderators, the moderator test was significant (`r mod_test(rma_offset_AGE_MS)`), but the three-way-interaction between condition, offset time, and age was again zero ($\beta$ `r full_estimate(rma_offset_AGE_MS_eff)`).
-Taken together, these results suggest that offset time does not modulate measured mispronunciation sensitivity.
-There is no relationship between offset time and age, and we find no influence of offset time on the estimated size of mispronunciation sensitivity over age.
-We again point out that there is a substantial field consensus, which might mask any relationship.
-
-### Dependent variable-related analyses
+Taken together, these results suggest that offset time does not modulate measured mispronunciation sensitivity nor its developmental trajectory.
+
+## Dependent variable
 
@@
 
-Mispronunciation studies evaluate infants' proportion of target looks (PTL) in response to correct and mispronounced words.
-Experiments typically include a phase where a naming event has not yet occurred, which we refer to as the pre-naming phase.
-This is followed by a naming event, whether correctly pronounced or mispronounced, and the subsequent phase we refer to as the post-naming phase.
-The purpose of the pre-naming phase is to ensure that infants do not have systematic preferences for the target or distractor (greater interest in a cat compared to a cup) which may drive PTL scores in the post-naming phase.
-As described in the Data Analysis sub-section of the Methods, however, there was considerable variation across papers in whether this pre-naming phase was used as a baseline measurement, or whether a different baseline measurement was used.
+Mispronunciation sensitivity experiments typically include a phase where a naming event has not yet occurred (pre-naming phase).
+This is followed by a naming event, whether correctly pronounced or mispronounced, and the subsequent phase (post-naming phase).
+The purpose of the pre-naming phase is to ensure that infants do not have systematic preferences for the target or distractor (greater interest in a cat compared to a cup) which may add variance to PTL scores in the post-naming phase.
+As described in the Methods section, however, there was considerable variation across papers in whether this pre-naming phase was used as a baseline measurement, or whether a different baseline measurement was used.
 This resulted in different measured outcomes or dependent variables.
-Over half of the experimental conditions (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post_naming_effect"])`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase, resulting in a Difference Score.
+Over half of the records (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post_naming_effect"])`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase, resulting in a Difference Score.
 The Difference Score is one value, which is then compared with a chance value of 0.
-When positive, this indicates that infants increased their looks to the target after hearing the naming label (correct or mispronounced) relative to the pre-naming baseline PTL.
 In contrast, Pre vs.
-Post (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` experimental conditions), directly compare the post- and pre-naming PTL scores with one another using a statistical test (e.g.
+Post (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` records), directly compare the post- and pre-naming PTL scores with one another using a statistical test (e.g.
 t-test, ANOVA).
 This requires two values, one for the pre-naming phase and one for the post-naming phase.
-A greater post compared to pre-naming phase PTL indicates that infants increased their target looks after hearing the naming label.
-The remaining experimental conditions used a Post dependent variable (*n* = `r with(dv_info, n_exp_conditions[within_measure == "post"])` experimental conditions), which compares the post-naming PTL score with a chance value of 50%.
+A positive Difference Score or a greater post compared to pre-naming phase PTL indicates that infants increased their target looks after hearing the naming label.
+The remaining records used a Post dependent variable (*n* = `r with(dv_info, n_exp_conditions[within_measure == "post"])` records), which compares the post-naming PTL score with a chance value of 50%.
 Here, the infants' pre-naming phase baseline preferences are not considered and instead target fixations are evaluated based on the likelihood to fixate one of two pictures (50%).
@@
 Post can be considered similar to one another, in that they are calculated on the same type of data and consider pre-naming preferences.
-It should be noted, however, that the Difference Score may better counteract participant- and item-level differences, whereas Pre vs.
-Post is a group-level measure.
 The Post dependent variable, in contrast, does not consider pre-naming baseline preferences.
-To our knowledge, there is no theory or evidence that explicitly drives choice of dependent variable in analysis of mispronunciation sensitivity, which may explain the wide variation in dependent variable reported in the papers included in this meta-analysis.
+To our knowledge, there is no theory or evidence that explicitly drives choice of dependent variable in analysis of preferential looking studies, which may explain the wide variation in dependent variable reported in the papers included in this meta-analysis.
 We next explored whether the type of dependent variable calculated influenced the estimated size of sensitivity to mispronunciations.
@@
 
-We first assessed whether the choice of dependent variable had an impact on the size of estimated mispronunciation sensitivity.
 When we included both condition and dependent variable as moderators, the moderator test was significant (`r mod_test(rma_within_MS)`).
@@
 Post and condition was significantly smaller than that of the Post dependent variable ($\beta$`r full_estimate(rma_within_MS_effprepost)`), but the difference between the Difference Score and Post in the interaction with condition was small and not significant ($\beta$`r full_estimate(rma_within_MS_effdiff)`).
-This relationship is plotted in Figure \@ref(fig:Plot-Within-cond-age-diff-score)a.
+This relationship is plotted in Figure \@ref(fig:PlotWithinCondAgeDiffScore)a.
 The results suggest that the reported dependent variable significantly impacted the size of the estimated mispronunciation sensitivity effect, such that studies reporting the Post.
@@
 
-We next examined whether the type of dependent variable calculated modulated the estimated change in mispronunciation sensitivity over infant age.
 When age was included as an additional moderator, the moderator test was significant (`r mod_test(rma_within_AGE_MS)`).
@@
 Post, condition, and age was significantly smaller than that of the Post dependent variable ($\beta$`r full_estimate(rma_within_AGE_MS_effprepost)`), but the difference between the Difference Score and Post in the interaction with condition and age was small and not significant ($\beta$`r full_estimate(rma_within_AGE_MS_effdiff)`).
-This relationship is plotted in Figure \@ref(fig:Plot-Within-cond-age-diff-score)b.
 When the dependent variable reported was Pre vs.
-Post, mispronunciation sensitivity was found to decrease with infant age, while in comparison, when the dependent variable was Post, mispronunciation sensitivity was found to increase with infant age.
-There was no difference in the estimated mispronunciation sensitivity change with infant age between the Post and Difference Score dependent variables.
-
-Similar to the length of the post-naming analysis window, all three possible developmental hypotheses might be supported depending on the dependent variable reported.
+Post, mispronunciation sensitivity was found to decrease with infant age, while in comparison, when the dependent variable was Post, mispronunciation sensitivity was found to increase with infant age (see This relationship is plotted in Figure \@ref(fig:PlotWithinCondAgeDiffScore)b.)
+
+Similar to post-naming analysis window length, all three possible developmental hypotheses might be supported depending on the dependent variable reported.
 In other words, choice of dependent variable may influence the conclusion drawn regarding how mispronunciation sensitivity may change with infant age.
-
-## (Insert Figure 11 about here)
-
-```{r Plot-Within-cond-age-diff-score, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (orange), Post vs.
+We address this issue in the General Discussion.
+
+## (Insert Figure \@ref(fig:PlotWithinCondAgeDiffScore) about here)
+
+```{r PlotWithinCondAgeDiffScore, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (orange), Post vs.
 Pre (blue), and Difference Score (green).
@@
 
-We next evaluated the developmental trajectory of infants' mispronunciation sensitivity.
-Based on existing experimental evidence, we envisioned three possible developmental patterns: increasing, decreasing, and unchanging sensitivity.
-We observed no influence of age when it was considered as a moderator of mispronunciation sensitivity.
-The results of our meta-analysis reflect a pattern previously reported by a handful of studies directly comparing infants over a range of ages [@Swingley2000; @Bailey2002; @Zesiger2012], which also found no developmental change in mispronunciation sensitivity.
+Considering the variation in findings of developmental change in mispronunciation sensitivity (see Introduction), we next evaluated the developmental trajectory of infants' mispronunciation sensitivity, envisioning three possible developmental patterns: increasing, decreasing, and unchanging sensitivity.
+Our analysis of this relationship using age as a moderator revealed a pattern of unchanging sensitivity, which has been reported by a handful of studies directly comparing infants over a small range of ages, such as 18-24 months [@Swingley2000; @Bailey2002] or 12-17 months [@Zesiger2012].
+The estimated effect size for mispronunciation sensitivity in our meta-analysis suggests that sensitivity is similar across the range of 6- to 30-month-old infants tested in the studies we include.
+Furthermore, an examination of the influence of vocabulary size revealed no relationship between object recognition in response to mispronunciations.
 
@@
 The need for phonologically well-specified word representations increases as children learn more words and must differentiate between them [@CharlesLuce1995].
-Yet, when we examined this relationship, we found that very few studies report analyses investigating the relationship between mispronunciation sensitivity and vocabulary size.
-An analysis of this handful of studies revealed no relationship between object recognition in response to mispronunciations, but this analysis was likely underpowered.
-More experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size is needed if this is to be evaluated.
-We tried to address this issue by conducting an analysis of the subset of studies reporting correlations between infants’ vocabulary size and their responses to correct and mispronounced labels.
-However, this analysis relied on only a few papers.
-We observed that an increasing vocabulary size lead to increased object recognition for correctly pronounced words; this was not the case for mispronunciations.
-However, it is difficult to draw any strong conclusions regarding the role of an increasing vocabulary size in mispronunciation sensitivity from this data.
-
-Why did we have so few samples for an analysis on vocabulary size to begin with?
 Despite the theoretical implications, fewer than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total; see also Figure \@ref(fig:Vocabdescribe1)).
@@
 We suggest that this may be the result of publication bias favoring significant effects or an overall hesitation to invest in data collection that is not expected to yield significant outcomes.
+More experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size is needed if this is to be evaluated.
 
@@
 
-What do our (tentative) results mean for theories of language development?
+What do our results mean for theories of language development?
 Evidence that infants accept a mispronunciation (object identification) while simultaneously holding correctly pronounced and mispronounced labels as separate (mispronunciation sensitivity) may indicate an abstract understanding of words' phonological structure being in place early on.
 It appears that young infants may understand that the phonological form of mispronunciations and correct pronunciations do not match, but that the mispronunciation is a better label for the target compared to the distractor image.
-The lack of age or vocabulary effects in our meta-analysis suggest that this understanding is present from an age when the earliest words are learned and is maintained throughout early lexical development.
+The lack of age or vocabulary effects in our meta-analysis suggest that this understanding is present from an early age and is maintained throughout early lexical development.
 
@@
 We included a set of moderator analyses to better understand these issues by themselves, as well as how they may have impacted our main investigation of infants' development of mispronunciation sensitivity.
-Additionally, several of these moderators include manipulations that make mispronunciation detection more or less difficult for the infant.
-As a result, the size of the mispronunciation sensitivity effect may be influenced by the task demands placed on the infant, potentially masking developmental effects.
+Several of these moderators include manipulations that make mispronunciation detection more or less difficult for the infant.
+As a result, the size of the mispronunciation sensitivity effect may be influenced by the task demands placed on the infant, especially if older infants are given more demanding tasks in comparison to younger infants, potentially masking developmental effects.
 Considering this, we also evaluated whether the investigation of each of these manipulations was distributed evenly across infant ages, where an uneven distribution may have subsequently heightened or dampened our estimate of developmental change.
@@
 Although words differ from one another on many acoustic dimensions, changes in phonemes, as measured by phonological features, signal changes in meaning.
-Several studies have found that infants show graded sensitivity to both consonant [@Bernier2017; @Tamasi2016; @White2008] and vowel [@Mani2011] feature changes.
-This was captured in our meta-analysis, which also showed that sensitivity to mispronunciations increased linearly with the number of phonological features changed.
-For each increase in number of phonological features changed, the effect size estimate for looks to the target decreases by `r r2(linear_feature)`.
+Several studies have found that infants show graded sensitivity to mispronunciations that differ in 1-, 2-, and 3-features from the correct pronunciation [@Bernier2017; @Tamasi2016; @White2008; @Mani2011].
+This was also captured in our meta-analysis, which showed that for each increase in number of phonological features changed, the effect size estimate for looks to the target decreases by `r r2(linear_feature)`.
 Yet, this graded sensitivity appears to be stable across infant ages, although our analysis was likely underpowered.
@@
 TRACE; @McClelland1986].
-Although many studies have examined mispronunciations on multiple positions, only a handful have directly compared sensitivity between different positions.
-These studies find that position of the mispronunciation does not modulate sensitivity [@Swingley2009; @Zesiger2012].
+Although many studies have examined mispronunciations on multiple positions, the handful of studies that have directly directly compared sensitivity between different positions find that position of the mispronunciation does not modulate sensitivity [@Swingley2009; @Zesiger2012].
 This stands in contrast to the findings of our meta-analysis, which showed that for each subsequent position in the word that is changed, from onset to medial and medial to coda, the effect size estimate for looks to the target decreases by `r r2(linear_position)`; infants are more sensitive to changes in the sounds of familiar words when they occur in an earlier position as opposed to a late position.
@@
 medial and coda mispronunciations) may be at a disadvantage relative to onset mispronunciations.
-These issues can be addressed with the addition of more experiments that directly compare sensitivity to mispronunciations of different positions, as well as the use of analyses that account for differences in timing of sensitivity.
+These issues can be addressed with the addition of more experiments that directly compare sensitivity to mispronunciations of different positions, as well as the use of analyses that account for timing differences.
 
@@
 No studies have directly compared mispronunciation sensitivity for familiar and unfamiliar distractors, but these results suggest that this manipulation alone makes little difference in the design of the experiment.
-It remains possible that distractor familiarity interacts with other types of manipulations, such as number of phonological features changed, heightening the ability of the experimenter to detect more sublte differences in mispronunciation sensitivity [e.g.
-@White2008], but our meta-analysis is underpowered to detect these effects.
+It remains possible that distractor familiarity interacts with other types of manipulations, such as number of phonological features changed [e.g.
+@White2008], but our meta-analysis is underpowered to detect such effects.
 
@@
 Sensitivity to consonant mispronunciations did not change with age and were similar for infants learning Germanic and Romance languages.
-In contrast, sensitivity to vowel mispronunciations increased with age and was greater for infants learning Germanic languages, although sensitivity to vowel mispronunciations did increase with age for infants learning Romance languages.
-Sensitivity to vowel mispronunciations is modulated both by development and by native language, whereas sensitivity to consonant mispronunciations is fairly similar across age and native language.
-This pattern of results support previous experimental evidence that sensitivity to consonants and vowels have a different developmental trajectory and that this difference also depends on whether the infant is learning a Romance (French, Italian) or Germanic (British English, Danish) native language [@Nazzi2016].
-Additionally, our exploratory analysis of tone mispronunciations revealed no difference in sensitivity in comparison to vowel and consonant mispronunciations, but our ability to detect differences may have been underpowered, as only `r with(CV_info, n_exp_conditions[type_feature == "tone"])` experimental conditions included tone mispronunciations.
-We hope that the recent increase in mispronunciation studies investigating infants learning a tone language (e.g.
-Mandarin Chinese) will soon solve this power issue.
+In contrast, sensitivity to vowel mispronunciations increased with age and was greater overall for infants learning Germanic languages, although sensitivity to vowel mispronunciations did increase with age for infants learning Romance languages as well.
+These results show that sensitivity to vowel mispronunciations is modulated both by development and by native language, whereas sensitivity to consonant mispronunciations is fairly similar across age and native language.This pattern of results support previous experimental evidence that sensitivity to
+consonants and vowels have a different developmental trajectory and that this difference also depends on whether the infant is learning a Romance (French, Italian) or Germanic (British English, Danish) native language [@Nazzi2016].
 
@@
 As a result, any developmental differences would be erased, hidden by task differences in the experiments that older and younger infants participated in.
-This argument is supported by the PRIMIR Framework (@Curtin2011; @Curtin2007; @Werker2005) , which argues that infants' ability to access the phonetic detail of familiar words is governed by the difficulty of their current task.
+This argument is supported by the PRIMIR Framework (@Curtin2011; @Curtin2007; @Werker2005), which argues that infants' ability to access the phonetic detail of familiar words is governed by the difficulty of their current task.
 Further support comes from evidence that sensitivity to mispronunciations when the target-distractor pair overlapped on the onset phoneme increased with age.
@@
 
-Infants recognize words more quickly with age [@Fernald1998], which has the potential to influence decisions for the analysis of the post-naming time window in mispronunciation sensitivity studies, including where to begin the time window (onset time) and how long this analysis window should be (post-naming analysis window).
-For example, as age increases, reaction time should increase and experimenters may adjust and lower offset times in their analysis as well as shorten the length of the analysis window.
+As infants' age increases, they recognize words more quickly [@Fernald1998], which may lead experimenters to adjust and lower offset times in their analysis as well as shorten the length of the analysis window.
 Yet, we find no relationship between age and offset times, nor that offset time modulated mispronunciation sensitivity.
 Indeed, a majority of studies used an offset time between 360 and 370 ms, which follows the "best guess" of @Swingley2000 for the amount of time needed for infants to initiate eye movements in response to a spoken target word.
-Without knowledge of the base reaction time in a given population of infants, use of this best guess offset time reduces the number of free parameters used by researchers.
-In contrast, we found a negative correlation between infant age and the length of the post-naming analysis window, and that the length of the analysis window moderated mispronunciation sensitivity, such increasing the length of the analysis windows decreases the size of mispronunciation sensitivity.
+Without knowledge of the base reaction time in a given population of infants, use of this best guess reduces the number of free parameters used by researchers.
+In contrast, we found a negative correlation between infant age and the length of the post-naming analysis window, and that increasing the length of the post-naming analysis window decreases the size of mispronunciation sensitivity.
 Given a set of mispronunciation sensitivity data, a conclusion regarding the development of mispronunciation sensitivity would be different depending on the length of the post-naming analysis window.
@@
 Surpisingly, we found that the type of dependent variable calculated moderated mispronunciation sensitivity and conclusions about its developmental trajectory.
-Unlike the exploratory analyses related to timing (onset and post-naming analysis window), there is not a clear reason for one dependent variable to be chosen over another; the prevelence of each dependent variable appears distributed across ages and some authors always calculate the same dependent variable while others use them interchangeably in different publications.
+Unlike the exploratory analyses related to timing, there is not a clear reason for one dependent variable to be chosen over another; the prevelence of each dependent variable appears distributed across ages and some authors always calculate the same dependent variable while others use them interchangeably in different publications.
 One clear difference is that both the Difference Score and Pre vs.
@@
 A lack of a field standard can have serious consequences, as our analyses show.
-Depending on which analysis time window (see Figure \@ref(fig:Plot-post-name-cond-age)) or dependent variable (see Figure \@ref(fig:Plot-Within-cond-age-diff-score)) we focus on, we find support for any of the three possible trajectories of mispronunciation sensitivity development.
 On the one hand, this limits the conclusions we can draw regarding our key research question.
-Without access to the full datasets or analysis code of the studies included in this meta-analysis, it is difficult to pinpoint the exact role played by these data analysis choices.
+Without access to the full datasets or analysis code of the studies included in this meta-analysis, it is difficult to pinpoint the exact role played by these experimental design and data analysis choices.
 On the other hand, this finding emphasizes that current practices of free, potentially ad hoc choices regarding data analyses are not sustainable if the field wants to move towards quantitative evidence for theories of language development.
@@
 Sharing data (Open Data) can allow others to re-analyze existing datasets to both examine the impact of analysis decisions and cumulatively analyze different datasets in the same way.
-Considering the specific issue of analysis time window, experimenters can opt to analyze the time course as a whole, instead of aggregating the proportion of target looking behavior over the entire trial.
+Considering the specific issue of analysis time window, experimenters can opt to analyze the time course as a whole, instead of aggregating the proportion of target looking behavior.
 This allows for a more detailed assessment of infants' fixations over time and reduces the need to reduce the post-naming analysis window.
@@
 
-Another aspect of study design, namely sample size planning, shows that best practices and current standards might not always overlap.
-Indeed, across a set of previous meta-analyses it was shown that particularly infant research does not adjust sample sizes according to the effect in question [@Bergmann2018].
 A meta-analysis is a first step in improving experiment planning by providing an estimate of the population effect and its variance, which is directly related to the sample needed to achieve satisfactory power in the null hypothesis significance testing framework.
-Failing to take effect sizes into account can lead to either underpowered research or testing too many participants, both consequences are undesirable for a number of reasons that have been discussed in depth elsewhere.
-We will just briefly mention two that we consider most salient for theory building: Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature [@Bergmann2018].
+Failing to take effect sizes into account can lead to either underpowered research or testing too many participants.
+Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature [@Bergmann2018].
 At the same time, underpowered studies with significant outcomes are likely to overestimate the effect, leading to wrong estimations of the population effect when paired with publication bias [@Jennions2002].
@@
 The estimated effect for mispronunciation sensitivity in this meta-analysis is `r mp_effect`, and the most frequently observed sample size is `r median_sample` participants.
-If we were to assume that researchers assess mispronunciation sensitivity in a simple ANOVA, the resulting power is `r r2(pat$power)`.
-Reversely, to achieve 80% power, one would need to test `r round(pat.est$n, 1)` participants.
-These calculations suggest that for the comparison of responses for correct pronunciations and mispronunciations, the studies included in this meta-analysis contain well-powered analyses.
-However, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates require four times the sample size to detect an effect of similar magnitude as the main effect for both ANOVA [@Fleiss1986] and mixed-effect-model [@Leon2009] analyses.
+If we were to assume that researchers assess mispronunciation sensitivity in a simple paired t-test, the resulting power is `r r2(ptt$power)`.
+Reversely, to achieve 80% power, one would need to test `r round(ptt.est$n, 1)` participants.
+These calculations suggest that for the comparison of responses for correct pronunciations and mispronunciations, the studies included in this meta-analysis are under-powered analyses.
+Furthermore, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates require four times the sample size to detect an effect of similar magnitude as the main effect for both ANOVA [@Fleiss1986] and mixed-effect-model [@Leon2009] analyses.
 We thus strongly advocate for a consideration of power and the reported effect sizes to test infants’ mispronunciation sensitivity.

### 2020-01-24 scripts/starter_functions.R

@@ -1,0 +1,46 @@
+
+r2 <- function(x){ round(x, 3)}
+
+psig <- function(x){
+  ifelse(x < .001, "< .001",
+         #ifelse(x < .001, "< .001",
+         #ifelse(x < .01, "< .01",
+         ifelse(x > .001 & x < .05, paste("=", r2(x), sep = " "), paste("=", r2(x), sep = " ")))#))
+}
+
+# function for creating 1 line paired t.test results
+t.xtable <- function(x) as.data.frame(xtable(
+  t_out(toutput=x, n.equal = TRUE, welch.df.exact = TRUE, welch.n = NA,
+        d.corr = TRUE, print = TRUE)
+))
+
+
+g_SE <- function(x) paste0(r2(x$estimate), " (SE = ", r2(x$se), ")")
+
+CI_p <- function(x) paste0("(CI [", r2(x$ci.lb), ", ", r2(x$ci.ub), "], *p* ", psig(x$pval), ")")
+
+full_estimate <- function(x) paste0(" = ", r2(x$estimate), ", SE = ", r2(x$se), ", 95% CI[",  r2(x$ci.lb), ", ", r2(x$ci.ub),"], *p* ", psig(x$pval))
+
+
+# moderator test
+mod_test <- function(x) paste0("QM(", r2(x$m), ") = ", r2(x$QM), ", *p* ", psig(x$QMp))
+
+
+# Create the function for mode.
+getmode <- function(v) {
+  uniqv <- unique(v)
+  uniqv[which.max(tabulate(match(v, uniqv)))]
+}
+
+# Plotting defaults
+
+#Themes and plot
+apatheme=theme_bw()+
+  theme(panel.grid.major=element_blank(),
+        panel.grid.minor=element_blank(),
+        panel.border=element_blank(),
+        axis.line=element_line(),
+        text=element_text(family='Times', size=25))
+
+# Color Blind palette:
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

### 2020-01-30 VonHolzenBergmann_MPMetaAnalysis.Rmd
Straightening out theoretical predictions

@@
   As they develop into mature speakers of their native language, infants must not only learn words but also the sounds that make up those words.
-To do so, they must strike a balance between accepting the speaker's variation (e.g.
-mood, voice, accent), but appropriately rejecting variation when it changes a word's meaning (e.g.
+To do so, they must strike a balance between accepting speaker dependent variation (e.g.
+mood, voice, accent), but appropriately rejecting variation when it (potentially) changes a word's meaning (e.g.
 cat vs.
@@
   - \usepackage{setspace}
+  - \usepackage{fontspec}
+  - \newfontfamily\ipa{Doulos SIL}
+  - \DeclareTextFontCommand{\ipatext}{\ipa}
   - \AtBeginEnvironment{tabular}{\singlespacing}
@@
   - \captionsetup[figure]{font={stretch=1.5}}
-  - \usepackage{fontspec}
-  - \newfontfamily\ipa{Doulos SIL}
-  - \DeclareTextFontCommand{\ipatext}{\ipa}
 ---
@@
 # https://github.com/benmarwick/wordcountaddin
+
+# able to use linguistics down by copying over some front matter from the linguistics down Untitled.Rmd template
+# https://yongfu.name/linguisticsdown/
+
+#options(encoding = "UTF-8")
 
@@
 
-  At the turn of the millenium, infant language acquisition researchers had begun to explore the phonetic information that infants attend to while segmenting words from the speech stream [@Jusczyk1995] and learning minimal pairs [@Stager1997].
+In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts  that differentiate words in a given language (e.g.
+cat-hat).
+Twenty years worth of studies have examined infants' application of phonological categories during word recognition through the mispronunciation sensitivity paradigm to probe this latter distinction.
+At the turn of the millennium, infant language acquisition researchers had begun to explore the phonetic information that infants attend to while segmenting words from the speech stream [@Jusczyk1995] and learning minimal pairs [@Stager1997].
 @Swingley2000 expanded this exploration to infants's existing representations, investigating how infants interpret phonological variation in familiar word recognition.
@@
 "vaby") for one of the images.
-Although infants looked at the correct, target image in response to both types of labels, correct labels elicited more looks to the correct, target image than mispronounced labels.
+Although infants looked at the correct target image in response to both types of labels, correct labels elicited more looks to the target image than mispronounced labels.
 @Swingley2000 concluded that already before the second birthday, children's representations for familiar words are phonologically well specified.
 
-  In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts  that differentiate words in a given language (e.g.
-cat-hat).
-The study of @Swingley2000 as well as subsequent studies examining infants' application of phonological categories during word recognition through the mispronunciation sensitivity paradigm probe this latter distinction.
-Phonological contrasts relevant for the infant language-learner are determined by their native language.
+Why should sensitivity to mispronunciations pose a challenge to the young infant?
+Critically, the native language being learned determines the relevant contrasts for the infant language-learner.
 For an infant learning Catalan, the vowel contrast /e/-/E/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish.
 These contrasts are therefore not innate, but must be learned.
-In this meta-analysis, we focus on infants' developing ability to correctly apply the phonological distinctions for their native language during word recognition.
-By aggregating all publicly available evidence using a meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; @MB1; for a notable exception).
+As we will review below, there are opposing theories and resulting predictions, supported by empirical data, as to how this knowledge is acquired.
+The time is thus ripe to aggregate all publicly available evidence using a meta-analysis to assess infants' developing ability to correclty apply the phonological distinctions for their native language during word recognition.
+In doing so, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; @MB1; for a notable exception).
 Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.
 
-  Research following the seminal study by @Swingley2000 has extended mispronunciation sensitivity to infants as young as 11 months [@Bergelson2017], indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations.
-Regarding the change in mispronunciation sensitivity over development, however, only about half of studies have compared more than one age group on the same mispronunciation task (see Table \@ref(tab:SummaryTable)) and of those, all possible patterns of development are found.
+Regarding the change in mispronunciation sensitivity over development, only roughly half of studies have compared more than one age group on the same mispronunciation task (see Table \@ref(tab:SummaryTable)) and of those, all possible patterns of development are found.
 This renders conclusions regarding developmental change in mispronunciation sensitivity difficult.
-
-Several studies  have found evidence for *greater* mispronunciation sensitivity as children develop [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010].
+Given the diverse evidence for developmental change, or lack thereof, the question arises as to what could be driving these differences.
+We thus summarize the existing empirical evidence, as well as developmental and methodological explanations for an increase, a decrease, or unchanged sensitivity to mispronunciations throughout infancy.
+
+An *increase* in mispronunciation sensitivity is predicted by a maturation in phono-lexical representations from holistic to more detailed and has been supported by several studies [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010].
 More precisely, the difference in target looking for correct and mispronounced trials is reported to be smaller in younger infants and grows as infants develop.
-Other studies have found *no difference* in mispronunciation sensitivity at different ages [@Swingley2000; @Bailey2002; @Zesiger2012].
-For example, @Swingley2000 tested infants over a wide age range of 5 months (18 to 23 months).
-They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation sensitivity) did not.
-At least one study has found evidence for infants to become *less* sensitive  to mispronunciations as they develop, showing a decrease in sensitivity from 18 to 24 months [@Mani2011].
-
-  Given the diverse evidence for developmental change, or lack thereof, the question arises as to what could be driving these differences.
 The first words that infants learn are often not similar sounding [e.g.
@@
 A growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the phonological detail of their representations [@Barton1980].
-If vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship between vocabulary size and mispronunciation sensitivity.
-
-  Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship [@Swingley2000; @Swingley2002; @Swingley2009; @Zesiger2012; @Mani2008; @Bailey2002; @Mani2007; @Ballem2005].
-One notable exception comes from @Mani2010kepstups.
+This argument is supported by the results of @Mani2010kepstups.
 Here, 12-month-old infants were divided into low and high vocabulary groups.
 High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations.
-Taken together, there is very little evidence for a role of vocabulary size in mispronunciation sensitivity.
-In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to better understand this issue.
-
-  An alternative explanation is the level of task difficulty infants are presented with in mispronunciation sensitivity experiments.
-Although all mispronunciation sensitivity studies are generally interested in the the phonological detail with which infants represent familiar words, many studies pose more nuanced questions, such as examining the impact of number of phonological features changed or the position of the mispronunciation.
+Consequently, if increasing age and/or vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship with mispronunciation sensitivity.
+
+Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship [@Swingley2000; @Swingley2002; @Swingley2009; @Zesiger2012; @Mani2008; @Bailey2002; @Mani2007; @Ballem2005].
+Furthermore, other studies testing more than one age have found *no difference* in mispronunciation sensitivity [@Swingley2000; @Bailey2002; @Zesiger2012].
+Such evidence supports an early specificity hypothesis, which suggests continuity in how infants' represent familiar words.
+According to this account, infants represent words with phonological detail already at the onset of lexical acquisition and that this persists throughout development.
+
+There are no theoretical accounts that would predict decreased *mispronunciation sensitivity*, but at least one study has found a *decrease* in sensitivity to small mispronunciations .
+@Mani2011 tested 18- and 24-month-olds' sensitivity to increasingly larger mispronunciations (1-, 2-, and 3-feature phonological changes).
+Although both groups were sensitive to mispronunciations overall, 18- but not 24-month-olds showed sensitivity to 1-feature mispronunciations.
+To account for this pattern of results, the authors suggest that when faced with large and salient mispronunciations, sensitivity to small 1-feature mispronunciations may be obscured, especially if infants show graded sensitivity to different degrees of mispronunciations (see below).
+In contrast, 18-month-olds did not show graded sensitvity, showing similar disruptions to word recognition for smaller and larger mispronunciations.
+
+To disentangle the predictions that phonological representations are progressively specified or specified early, we investigate the relationship between mispronunciation sensitivity and both age as well as vocabulary size.
+But, this may not account for all variability found in the literature.
+Although all mispronunciation sensitivity studies are generally interested in the phonological detail with which infants represent familiar words, many studies pose more nuanced questions, such as examining the impact of number of phonological features changed or the position of the mispronunciation.
 Some studies may differ in their experimental design, presenting a distractor image that overlaps with the target image in the onset phoneme or a completely novel, unfamiliar distractor image.
 These experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete.
+
 The PRIMIR Framework [Processing Rich Information from Multidimensional Interactive Representations; @Curtin2011; @Curtin2007; @Werker2005] describes how infants acquire and organize the incoming speech signal into phonetic and indexical detail.
-The ability to access and use this detail, however, is governed by the task or developmental demands (discrimination vs.
-word learning) probed in a particular experiment.
-In a particularly demanding task, such as when the target and distractor image share the same onset phoneme, infants' ability to access the phonological detail of familiar words may be restricted.
-If older infants are more likely to be tested using a more demaning mispronunciation sensitivity task, this may attenuate developmental effects across studies.
-
-  These manipulations may impact task demands, but they are also theoretically interesting, focusing on issues at the intersection of phonological development and lexical processing.
-For specific questions where we can aggregate multiple studies, we take the opportunity to shine a meta-analytic light on what modulates infants' ability to detect mispronunciations in follow-up exploatory analyses.
-We outline below first which nuanced questions have been frequently asked to provide a more in-depth overview of the current literature.
+The ability to access and use this detail, however, is governed by the task or developmental demands probed in a particular experiment.
+In a particularly demanding task, such as when the target and distractor image share the same onset (e.g.
+doggie and doll), infants' ability to access the phonological detail of familiar words may be restricted [@Swingley1999].
+If older infants are more likely to be tested using a more demanding mispronunciation sensitivity task, this may attenuate developmental effects across studies.
+Note, however, that those studies reporting change [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010] or no change [@Swingley2000; @Bailey2002; @Zesiger2012] all presented the same task across ages .
+
+The manipulations that might increase task demands, such as overlap between target and distractor, are also theoretically interesting, focusing on issues at the intersection of phonological development and lexical processing.
+For specific questions where we can aggregate multiple studies, we take the opportunity to shine a meta-analytic light on what modulates infants' ability to detect mispronunciations in follow-up exploratory analyses.
+We outline first which nuanced questions have been frequently asked to provide a more in-depth overview of the current literature.
 
 The first set of questions concern how infants' sensitivity is modulated by different kinds of mispronunciations.
-Some experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level (i.e.
+Some experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level, or *mispronunciation size* (i.e.
 1-feature, 2-features, 3-features, etc.), finding graded sensitivity to both consonant [@White2008; @Bernier2017; @Tamasi2016] and vowel [@Mani2011] feature changes.
-This also has consequences for task demands, as the greater the number of features changed, or *mispronunciation size*, the easier it may be to detect a mispronunciation, whereas more similar mispronunciations may be more difficult to detect.
-
-  Consonantal changes may be more disruptive to lexical processing than vowel changes in both adults [@Nazzi2018] and infants [@Nazzi2016].
-In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations.
+This also has consequences for understanding the developmental trajectory of mispronunciation sensitivity, as adults show similar graded sensitivity.
+
+Consonantal changes may be more disruptive to lexical processing than vowel changes in both adults [@Nazzi2018] and infants [@Nazzi2016], known as the consonant bias.
+A learned account predicts that a C-bias emerges over development [@Floccia2014; @Nazzi2016; @Keidel2007] and that this emergence is impacted by the language family of the infants' native language [@Nazzi2016].
+In mispronunciation sensitivity, this would first translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations.
 Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels for English- [@Mani2007; @Mani2010kepstups] and Danish-learning infants [@Hojen].
 One study with English-learning infants did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations [@Swingley2016].
-Evidence from word-learning suggests that assymetry in sensitivity to consonant and vowel changes may develop at different times depending on the infants' native language [e.g.
-@Floccia2014; @Nazzi2009a].
-In the current meta-analysis, we attempt to synthesize studies examining sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence [@Floccia2014; @Nazzi2016; @Keidel2007] and whether this is impacted by the language family of the infants' native language [@Nazzi2016].
+In the current meta-analysis, we examine infants' sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages and native language families to determine whether infants exhibit more sensitivity to consonant compared to vowel mispronunciations of familiar words.
 
@@
 In contrast, the TRACE model [@McClelland1986] describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.
-The *position of mispronunciation* in the word may therefore differentially interrupt the infant's word recognition process, with onset mispronunciations resulting in a more demanding task than medial or coda mispronunciations.
-
-  A second question is whether the experimental context modulates infants' responses to mispronunciations.
+The *position of mispronunciation* in the word may therefore differentially interrupt the infant's word recognition process, with onset mispronunciations leading to greater mispronunciation sensitivity than medial or coda mispronunciations.
+
+A second question is whether the context modulates infants' responses to mispronunciations.
 In order to study the influence of mispronunciation position, many studies control the *phonological overlap between target and distractor labels*.
-For example, when examining sensitivity to a vowel mispronunciation of the target word "dog", the image of a dog would be paired with a distractor image that shares onset overlap, such as "duck".
-This ensures that infants can not use the onset of the word to differentiate between the target and distractor images [@Fernald2001a].
+For example, when examining sensitivity to a vowel mispronunciation of the target word "doggie", the image of a dog would be paired with a distractor image that shares onset overlap, such as "doll".
+This ensures that infants can not use the onset of the word to differentiate between the target and distractor images [@Swingley1999].
 Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.
-  Most studies present infants with pictures of two name-known objects, thus ruling out the unlabeled competitor, or distractor, as possible target.
+Note that in this case, the mispronunciation is necessarily either word-medial or –final, thus possibly creating an interaction between mispronunciation position and phonological overlap.
+
+Most studies present infants with pictures of two known objects, thus ruling out the unlabeled competitor, or distractor, as possible target.
+It is thus not surprising that infants tend to look towards the target more, even when its label is mispronounced.
 In contrast, other studies present infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects [@White2008; @Mani2011; @Skoruppa2013; @Swingley2016].
@@
 Meta-analyses can provide unique insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and of their mispronunciation sensitivity.
-Because we aggregate data over various age groups, this meta-analysis can also investigate the role of maturation by assessing the impact of age and vocabulary size.
-We also explore the influence of different linguistic (mispronunciation size, position, and type) and experimental (overlap between target and distractor labels; distractor familiarity) demands on the study of mispronunciation sensitivity.
+Because we aggregate data over various age groups, this meta-analysis can investigate the role of maturation by assessing the impact of age and vocabulary size.
+We also explore the influence of different linguistic (mispronunciation size, position, and type) and contextual (overlap between target and distractor labels; distractor familiarity) factors on the study of mispronunciation sensitivity.
 Finally, we explore potential data analysis choices that may influence different conclusions about mispronunciation sensitivity development as well as offer recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses [@Bergmann2018].
@@
 
-[^1]: Two papers tested bilingual infants [@Ramon-Casas2009; @Ramon-Casas2010], yielding `r bil_infants` records.
+[^1]: Two papers tested bilingual infants [@Ramon-Casas2009; @Ramon-Casas2010], yielding `r bil_infants` records, respectively.
 Due to this small number, we do not investigate the role of multilingualism, but do note that removing these papers from the meta-analysis did not alter the pattern of results.
@@
 To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we first introduced age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44) as a moderator to our main model.
-Second, we analyzed the correlation between reported vocabulary size and mispronunciation sensitivity using the R [@R] package meta [@meta].
+Second, we analyzed the correlation between reported vocabulary size and mispronunciation sensitivity using the package meta [@meta].
 For a subsequent investigation of experimental characteristics, we introduced each as a moderator: size of mispronunciation, position of mispronunciation, phonological overlap between target and distractor labels, type of mispronunciation, and distractor familiarity (more detail below).
@@
 We then calculated the meta-analytic effect for object identification in response to mispronounced words.
-In this case, the variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was also significantly different from zero `r CI_p(sum_eff)`.
+In this case, the variance-weighted meta-analytic effect size was `r g_SE(sum_eff)` which was also significantly different from zero `r CI_p(sum_eff)`.
 This is considered a small effect size [@Mills-Smith2015], but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object.
-In other words, infants are able to resolve mispronunciations, a key skill in language processing We again note the publication bias (which was smaller in this condition), and the possibility that the effect size Hedges' *g* may be overestimated.
+In other words, infants are able to resolve mispronunciations, a key skill in language processing We again note the publication bias (which was smaller in this condition), and the possibility that the effect size may be overestimated.
 But, as the p-curve indicated evidential value, we are confident in the overall pattern, namely that infants fixate the target even after hearing a mispronounced label.
@@
 
-The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age and increased vocabulary size.
-The results seem clear: Although infants consider a mispronunciation to be a better match to the target image than to a distractor image, there was a constant and stable effect of mispronunciation sensitivity across all ages.
+The main goal of this paper was to assess mispronunciation sensitivity and whether it is modulated by maturation with age and increased vocabulary size.
 In the literature, evidence for all possible developmental trajectories has been found, including mispronunciation sensitivity that increases, decreases, or does not change with age or vocabulary size.
-The present results do lend some support for the proposal that mispronunciation sensitivity stays constant as infants develop.
+Regarding age, the results seem clear: Although infants consider a mispronunciation to be a better match to the target image than to a distractor image, there was a constant and stable effect of mispronunciation sensitivity across all ages.
 Furthermore, although we found a relationship between vocabulary size (comprehension) and target looking for correct pronunciations, we found no relationship between vocabulary and target looking for mispronunciations.
 This may be due to too few studies including reports of vocabulary size and more investigation is needed to draw a firm conclusion.
+These findings support the arguments set by the early specification hypothesis that infants represent words with phonological detail at the beginning of the second year of life.
 
@@
 
-To assess whether the size of the mispornunciation tested, as measured by the number of features changed, modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced using 1-, 2-, and 3-feature changes.
+To assess whether the size of the mispronunciation tested, as measured by the number of features changed, modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced using 1-, 2-, and 3-feature changes.
 We did not include data for which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent (e.g., one mispronunciation included a 2-feature change whereas another only a 1-feature change).
 This analysis was therefore based on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` records for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations.
-Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an equal impact on mispronunciation sensitivity, following the argument of graded sensitivity [@White2008; @Mani2011], and this modertor was coded as a continuous variable.
+Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an equal impact on mispronunciation sensitivity, following the argument of graded sensitivity [@White2008; @Mani2011], and this moderator was coded as a continuous variable.
 
@@
 We identified five additional manipulations often present in mispronunciation sensitivity studies and investigated the how those manipulations modulated mispronunciation sensitivity and whether this changed with infant age.
-Furthermore, considering the lack of developmental change found in our main analysis, we evaluted whether these additional manipulations were disproportionatly conducted with children of different ages, to assess whether older infants recieve more difficult tasks than younger infants.
+Furthermore, considering the lack of developmental change found in our main analysis, we evaluated whether these additional manipulations were disproportionately conducted with children of different ages, to assess whether older infants receive more difficult tasks than younger infants.
 
@@
 
-Typically, vocabulary growth is thought to invoke changes in mispronunciation sensitivity.
+In accounts predicting gradual specification of phonological representations, vocabulary growth is thought to invoke changes in mispronunciation sensitivity.
 The need for phonologically well-specified word representations increases as children learn more words and must differentiate between them [@CharlesLuce1995].
@@
 Although words differ from one another on many acoustic dimensions, changes in phonemes, as measured by phonological features, signal changes in meaning.
-Several studies have found that infants show graded sensitivity to mispronunciations that differ in 1-, 2-, and 3-features from the correct pronunciation [@Bernier2017; @Tamasi2016; @White2008; @Mani2011].
+Several studies have found that infants show graded sensitivity to mispronunciations that differ in 1-, 2-, and 3-features from the correct pronunciation [@Bernier2017; @Tamasi2016; @White2008; @Mani2011], an adult-like ability.
 This was also captured in our meta-analysis, which showed that for each increase in number of phonological features changed, the effect size estimate for looks to the target decreases by `r r2(linear_feature)`.
@@
 In contrast, sensitivity to vowel mispronunciations increased with age and was greater overall for infants learning Germanic languages, although sensitivity to vowel mispronunciations did increase with age for infants learning Romance languages as well.
-These results show that sensitivity to vowel mispronunciations is modulated both by development and by native language, whereas sensitivity to consonant mispronunciations is fairly similar across age and native language.This pattern of results support previous experimental evidence that sensitivity to
+These results show that sensitivity to vowel mispronunciations is modulated both by development and by native language, whereas sensitivity to consonant mispronunciations is fairly similar across age and native language.This pattern of results support previous experimental evidence and a learned account of the C-bias that sensitivity to
 consonants and vowels have a different developmental trajectory and that this difference also depends on whether the infant is learning a Romance (French, Italian) or Germanic (British English, Danish) native language [@Nazzi2016].
 
-Our meta-analysis revealed the rather surprising result that onset overlap between labels for the target and distractor images lead to greater mispronunciation sensitivity in comparison to target-distractor pairs that shared no phonological overlap.
-It should be arguably more, not less, difficult to detect a mispronunciation (dag) when the target and distractor overlap in their onset phoneme (dog-duck), because the infant can not use differences in the onset sound between the target and distractor to identify the intended referent.
+Our meta-analysis revealed the rather surprising result that studies which include target and distractor images that overlap in their onset elicit greater mispronunciation sensitivity than studies who do not control for this facotr.
+It should be arguably more, not less, difficult to detect a mispronunciation (dag) when the target and distractor overlap in their onset phoneme (doggie-doll), because the infant can not use differences in the onset sound between the target and distractor to identify the intended referent [@Swingley1999].
 Perhaps including overlap between the target and distractor lead infants to pay more attention to mispronunciations, leading to an increased effect of mispronunciation sensitivity.
@@
 vowel).
-Furthermore, evidence of an interaction between task demands (phonological overlap between target-distractor pairs) and infant age may partially explain the lack of developmental change in mispronunciation sensitivity.
+Furthermore, evidence of an interaction between task demands (phonological overlap between target-distractor pairs) and infant age may partially explain the lack of developmental change in our meta-analysis.
 

### 2020-02-03 VonHolzenBergmann_MPMetaAnalysis.Rmd
implementing finalization comments

@@
 cat-hat).
-Twenty years worth of studies have examined infants' application of phonological categories during word recognition through the mispronunciation sensitivity paradigm to probe this latter distinction.
+Twenty years' worth of studies have examined infants' application of phonological category knowledge during word recognition through the mispronunciation sensitivity paradigm to probe the development of this latter distinction.
+At this point, a picture on the functional use of language-specific phonetic and phonological knowledge began to emerge.
 At the turn of the millennium, infant language acquisition researchers had begun to explore the phonetic information that infants attend to while segmenting words from the speech stream [@Jusczyk1995] and learning minimal pairs [@Stager1997].
+Both studies and the lines of research they sparked showed that under the right conditions, even young infants can use their emerging native language phonological skills during word-level language processing.
+
 @Swingley2000 expanded this exploration to infants's existing representations, investigating how infants interpret phonological variation in familiar word recognition.
-American-English learning 18- to 23-month-olds were presented with pairs of images (e.g.
+American-English learning 18- to 23-month-olds were presented with pairs of images of words they were very likely to know (e.g.
 a baby and a dog) and their eye movements to each image were recorded.
@@
 
-Why should sensitivity to mispronunciations pose a challenge to the young infant?
-Critically, the native language being learned determines the relevant contrasts for the infant language-learner.
+Why should sensitivity to mispronunciations pose a challenge to the young infant and thus the findings of @Swingley2000 be found novel?
+There are two key challenges the infant learner has to contend with.
+First, the native language being learned determines the relevant contrasts for the infant language-learner.
+These contrasts are therefore not innate, but must be learned.
 For an infant learning Catalan, the vowel contrast /e/-/E/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish.
-These contrasts are therefore not innate, but must be learned.
-As we will review below, there are opposing theories and resulting predictions, supported by empirical data, as to how this knowledge is acquired.
-The time is thus ripe to aggregate all publicly available evidence using a meta-analysis to assess infants' developing ability to correclty apply the phonological distinctions for their native language during word recognition.
-In doing so, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; @MB1; for a notable exception).
+Second, across talkers, these sounds might be realized differently, and change even as the talker talks to an infant or adult [e.g.
+@Benders2013].
+As we will review below, there are opposing theories and resulting predictions, supported by empirical data, as to how this knowledge is acquired and applied to lexical representations.
+The time is thus ripe to aggregate all publicly available evidence using a meta-analysis.
+In doing so, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; @MB1; for notable exceptions).
 Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.
@@
 mama, ball, kitty; @CharlesLuce1995] and encoding representations for these words using fine phonological detail may not be necessary.
-With time, more phonologically similar words are learned, which may drive a need to the infant to represent familiar words with more fine phonological detail.
-A growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the phonological detail of their representations [@Barton1980].
+**According to PRIMIR [@Curtin2011; @Curtin2007; @Werker2005] infants's initially episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task.** A growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the phonological detail of their representations [@Barton1980].
 This argument is supported by the results of @Mani2010kepstups.
 Here, 12-month-old infants were divided into low and high vocabulary groups.
-High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations.
-Consequently, if increasing age and/or vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship with mispronunciation sensitivity.
+High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations (see below for further discussion on consonant-vowel assymmetry).
+If increasing age and/or vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship of either with mispronunciation sensitivity.
 
@@
 Furthermore, other studies testing more than one age have found *no difference* in mispronunciation sensitivity [@Swingley2000; @Bailey2002; @Zesiger2012].
-Such evidence supports an early specificity hypothesis, which suggests continuity in how infants' represent familiar words.
+Such evidence supports an early specificity hypothesis, which suggests continuity in how infants represent familiar words.
 According to this account, infants represent words with phonological detail already at the onset of lexical acquisition and that this persists throughout development.
 
-There are no theoretical accounts that would predict decreased *mispronunciation sensitivity*, but at least one study has found a *decrease* in sensitivity to small mispronunciations .
-@Mani2011 tested 18- and 24-month-olds' sensitivity to increasingly larger mispronunciations (1-, 2-, and 3-feature phonological changes).
-Although both groups were sensitive to mispronunciations overall, 18- but not 24-month-olds showed sensitivity to 1-feature mispronunciations.
+There are no theoretical accounts that would predict *decreased* mispronunciation sensitivity, but at least one study has found a decrease in sensitivity to small mispronunciations .
+@Mani2011 tested 18- and 24-month-olds' sensitivity to increasingly larger mispronunciations: 1- (bed-bud), 2- (foot-fit), and 3-feature phonological changes (doll-deal).
+Although both age groups were sensitive to mispronunciations overall, 18- but not 24-month-olds showed sensitivity to more subtle 1-feature mispronunciations.
 To account for this pattern of results, the authors suggest that when faced with large and salient mispronunciations, sensitivity to small 1-feature mispronunciations may be obscured, especially if infants show graded sensitivity to different degrees of mispronunciations (see below).
-In contrast, 18-month-olds did not show graded sensitvity, showing similar disruptions to word recognition for smaller and larger mispronunciations.
-
-To disentangle the predictions that phonological representations are progressively specified or specified early, we investigate the relationship between mispronunciation sensitivity and both age as well as vocabulary size.
+In contrast, 18-month-olds did not show graded sensitivity, showing similar disruptions to word recognition for smaller and larger mispronunciations.
+
+To disentangle the predictions that phono-lexical representations are progressively becoming more specified or are specified early, we investigate the relationship between mispronunciation sensitivity and age as well as vocabulary size.
 But, this may not account for all variability found in the literature.
-Although all mispronunciation sensitivity studies are generally interested in the phonological detail with which infants represent familiar words, many studies pose more nuanced questions, such as examining the impact of number of phonological features changed or the position of the mispronunciation.
+Although infant mispronunciation sensitivity studies are generally interested in the phonological detail with which infants represent familiar words, many studies pose more nuanced questions, such as examining the impact of number of phonological features changed or the location of the mispronunciation.
 Some studies may differ in their experimental design, presenting a distractor image that overlaps with the target image in the onset phoneme or a completely novel, unfamiliar distractor image.
 These experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete.
+We thus follow our analyses of a developmental trajectory with one of features of the task, and line out here task effects which can shed further light on early phono-lexical representations and their maturation.
 
@@
 The manipulations that might increase task demands, such as overlap between target and distractor, are also theoretically interesting, focusing on issues at the intersection of phonological development and lexical processing.
-For specific questions where we can aggregate multiple studies, we take the opportunity to shine a meta-analytic light on what modulates infants' ability to detect mispronunciations in follow-up exploratory analyses.
+For specific questions where we can aggregate multiple studies, we take the opportunity to shine a meta-analytic light on what modulates infants' ability to detect mispronunciations in follow-up analyses.
 We outline first which nuanced questions have been frequently asked to provide a more in-depth overview of the current literature.
@@
 1-feature, 2-features, 3-features, etc.), finding graded sensitivity to both consonant [@White2008; @Bernier2017; @Tamasi2016] and vowel [@Mani2011] feature changes.
-This also has consequences for understanding the developmental trajectory of mispronunciation sensitivity, as adults show similar graded sensitivity.
+This also has consequences for understanding the developmental trajectory of mispronunciation sensitivity, as adults show similar graded sensitivity [@Bailey2005]
 
 Consonantal changes may be more disruptive to lexical processing than vowel changes in both adults [@Nazzi2018] and infants [@Nazzi2016], known as the consonant bias.
-A learned account predicts that a C-bias emerges over development [@Floccia2014; @Nazzi2016; @Keidel2007] and that this emergence is impacted by the language family of the infants' native language [@Nazzi2016].
+A learned account predicts that a consonant bias emerges over development [@Floccia2014; @Nazzi2016; @Keidel2007] and that this emergence is impacted by the language family of the infants' native language [@Nazzi2016].
 In mispronunciation sensitivity, this would first translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations.
-Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels for English- [@Mani2007; @Mani2010kepstups] and Danish-learning infants [@Hojen].
+Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels for English- [@Mani2007; @Mani2010kepstups] and Danish-learning infants [@Hojen] and do not compare infants learning different native languages [for evidence from word-learning see @Floccia2014; @Nazzi2009a].
 One study with English-learning infants did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations [@Swingley2016].
-In the current meta-analysis, we examine infants' sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages and native language families to determine whether infants exhibit more sensitivity to consonant compared to vowel mispronunciations of familiar words.
-
+In the current meta-analysis, we examine infants' sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages and native language families to assess the predictions of the learned account of the consonant bias.
+
+The *position of mispronunciation* in the word may differentially interrupt the infant's word recognition process, with onset mispronunciations leading to greater mispronunciation sensitivity than medial or coda mispronunciations.
 Models of spoken word processing place more or less importance on the position of a phoneme in a word.
@@
 In contrast, the TRACE model [@McClelland1986] describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.
-The *position of mispronunciation* in the word may therefore differentially interrupt the infant's word recognition process, with onset mispronunciations leading to greater mispronunciation sensitivity than medial or coda mispronunciations.
-
-A second question is whether the context modulates infants' responses to mispronunciations.
+
+A second set of questions is whether the context modulates infants' responses to mispronunciations.
 In order to study the influence of mispronunciation position, many studies control the *phonological overlap between target and distractor labels*.
@@
 
-Most studies present infants with pictures of two known objects, thus ruling out the unlabeled competitor, or distractor, as possible target.
+We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar.
+This is a particularly fruitful question to investigate within the context of a meta-analysis, as mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared.
+Most studies present infants with pictures of two known objects, thereby ruling out the unlabeled competitor, or distractor, as possible target.
 It is thus not surprising that infants tend to look towards the target more, even when its label is mispronounced.
 In contrast, other studies present infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects [@White2008; @Mani2011; @Skoruppa2013; @Swingley2016].
-By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied [@Halberda2003; @Markman2003].
-This ability is developing from 18 to 30 months [@Bion2013] and we may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar.
-This is a particularly fruitful question to investigate within the context of a meta-analysis, as mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared.
-
-Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (see Table \@ref(tab:SummaryTable)).
-Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare.
-Indeed, the majority of studies focus on infants learning English as a native language and a sufficient sample of other languages is therefore lacking.
-Although we do not explicitly compare overall mispronunciation sensitivity by language (although we examine consonant and vowel mispronunciation sensitivity by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.
+By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied [@Halberda2003; @Markman2003], an ability that is developing from 18 to 30 months [@Bion2013].
 
@@
 Meta-analyses can provide unique insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and of their mispronunciation sensitivity.
-Because we aggregate data over various age groups, this meta-analysis can investigate the role of maturation by assessing the impact of age and vocabulary size.
-We also explore the influence of different linguistic (mispronunciation size, position, and type) and contextual (overlap between target and distractor labels; distractor familiarity) factors on the study of mispronunciation sensitivity.
+Because we aggregate data over  age groups, this meta-analysis can investigate the role of maturation by assessing the impact of age, and when possible vocabulary size.
+We also test the influence of different linguistic (mispronunciation size, position, and type) and contextual (overlap between target and distractor labels; distractor familiarity) factors on the study of mispronunciation sensitivity.
 Finally, we explore potential data analysis choices that may influence different conclusions about mispronunciation sensitivity development as well as offer recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses [@Bergmann2018].
@@
 Sum_table$dist_overlap <- ifelse(grepl("coda", Sum_table$dist_overlap), gsub("coda", "C", Sum_table$dist_overlap), Sum_table$dist_overlap)
+Sum_table$dist_overlap <- ifelse(grepl("novel", Sum_table$dist_overlap), gsub("novel", "unfam", Sum_table$dist_overlap), Sum_table$dist_overlap)
 
@@
 apa_table(Sum_table, col.names = c("Paper", "Format", "Age", "Vocabulary", "Familiarity", "Target Overlap", "Size", "Position", "Type", "N Effect Sizes"), caption = "Summary of all studies.
-Age: truncation of mean age reported in the paper.
+Age: mean age(s) reported in the paper (in months).
 Vocabulary: Comp = comprehension, Prod = production.
 Distractor Familiarity: Fam = Familiar Distractor, Unfam = Unfamiliar Distractor.
-Distractor Target Overlap: position of overlap between target and distractor; O = onset, M = medial, C = coda.
+Target Overlap: position of overlap between target and distractor; O = onset, M = medial, C = coda.
 Mispronunciation Size: number of features changed; commas indicate when sizes were compared separately (e.g.
@@
 6. Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;
-7. Type of mispronunciation: consonant, vowel, or both.
+7. Type of mispronunciation: consonant, vowel, or both;
 8. Distractor familiarity: familiar or unfamiliar;
@@
 
-To take into account the fact that the same infants contributed to multiple datapoints, we analyze our results in a multilevel approach using the R [@R] package metafor [@metafor].
+To consider the fact that the same infants contributed to multiple datapoints, we analyze our results in a multilevel approach using the R [@R] package metafor [@metafor].
 We use a multilevel random effects model which estimates the mean and variance of effect sizes sampled from an assumed distribution of effect sizes.
@@
 If infants were not looking to the target picture after hearing the correct label, the overall experiment design is called into question.
-However, even in a well-powered study one would expect the regular occurrence of null results even though as a population infants would reliably show the expected object identification effect.
+However, even in a well-powered study one would expect the regular occurrence of null results even though as a population, infants would reliably show the expected object identification effect.
 
@@
 The studies examined in this meta-analysis examined mispronunciation sensitivity, but many also included more specific questions aimed at uncovering more detailed phonological processes at play during word recognition.
-Not only are these questions theoretically interesting, they also have the potential to change the difficulty of a msipronunciation sensitivity experiment.
+Not only are these questions theoretically interesting, they also have the potential to change the difficulty of a mispronunciation sensitivity experiment.
 It is possible that the lack of developmental change in mispronunciation sensitivity found by our meta-analysis does not capture a true lack of change, but is instead influenced by differences in the types of tasks given to infants of different ages.
@@
   geom_violin() + 
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
+  geom_boxplot(width=0.1)+
+  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
   #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
@@
     geom_violin() + 
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
+    geom_boxplot(width=0.1)+
+  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
   labs(title="a")+
@@
     geom_violin() + 
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
+  geom_boxplot(width=0.1)+
+  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
   labs(title="a")+
@@
 When language family was included as a moderator, the moderator test was significant, `r mod_test(rma_TypeFeaturesMPC)`.
-The three-way interaction between mispronunciation type, condition, language family was large and also significant , $\beta$`r full_estimate(sum_eff_famcv)`.
+The three-way interaction between mispronunciation type, condition, language family was large and also significant, $\beta$`r full_estimate(sum_eff_famcv)`.
 As can be seen in Figure \@ref(fig:PlotCVEffectLang)a, mispronunciation sensitivity for consonants was similar for Germanic and Romance languages.
@@
 
-We next calculated the meta-analytic effect of mispronunciaiton sensitivity (moderator: condition) in experiments were the target image was paired with a familiar or unfamiliar distractor image.
+We next calculated the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in experiments were the target image was paired with a familiar or unfamiliar distractor image.
 A familiar distractor was used in `r with(distr_info, n_exp_conditions[object_pair == "familiar_familiar"])` records and a unfamiliar distractor in `r with(distr_info, n_exp_conditions[object_pair == "familiar_novel"])` records.
@@
 Next to the main goal of this paper, which was to evaluate the development of infants' sensitivity to mispronunciations, we also investigated the more nuanced questions often posed in studies investigating infants' mispronunciation sensitivity.
-We identified five additional manipulations often present in mispronunciation sensitivity studies and investigated the how those manipulations modulated mispronunciation sensitivity and whether this changed with infant age.
-Furthermore, considering the lack of developmental change found in our main analysis, we evaluated whether these additional manipulations were disproportionately conducted with children of different ages, to assess whether older infants receive more difficult tasks than younger infants.
+We identified two sets of additional manipulations, relating to the kind of mispronunciation and contextual factors, that are often present in mispronunciation sensitivity studies and investigated the how those manipulations modulated mispronunciation sensitivity and whether this changed with infant age.
+Furthermore, considering the lack of developmental change found in our main analysis, we evaluated whether these additional manipulations were disproportionately conducted with children of different ages, to assess whether older infants receive more difficult tasks than younger ones.
 
@@
 In one instance, younger infants were given a more difficult task, mispronunciations on the medial position, which is unlikely to contribute to the lack of developmental effects in our main analysis.
-Yet, his was not always the case; in a different instance, older children were more likely to be given target-distractor pairs that overlapped on their onset phoneme, a situation in which it is more difficult to detect a mispronunciation and may have bearing on our main developmental results.
+Yet, this was not always the case; in a different instance, older children were more likely to be given target-distractor pairs that overlapped on their onset phoneme, a situation in which it is more difficult to detect a mispronunciation and may have bearing on our main developmental results.
 We return to these findings in the General Discussion.
@@
 A strong candidate that emerged during the construction of the present dataset and careful reading of the original papers was the analysis approach.
-We observed, as mentioned in the Methods section, large variation in the dependent variable reported, and additionally noted that the size of the chosen post-naming analysis window varied substantially across papers.
+We observed, as mentioned in the Methods section, variation in the dependent variable reported, and additionally noted that the size of the chosen post-naming analysis window varied substantially across papers.
 Researchers' analysis strategy may be adapted to infants' age or influenced by having observed the data.
@@
 In this scenario, younger infants should show no or only little sensitivity to mispronunciations while older infants would show a large sensitivity to mispronunciations.
-This lack of or small mispronunciation sensitivity in younger infants is likely to lead to non-significant results, which would be more difficult to publish [@Ferguson2012].
+This lack of or small mispronunciation sensitivity in younger infants is likely to lead to non-significant results, especially given the prevalent small sample sizes, which would be more difficult to publish [@Ferguson2012].
 In order to have publishable results, adjustments to the analysis approach could be made until a significant effect of mispronunciation sensitivity is found.
@@
 Such a scenario is in line with the publication bias we observe [@Simmons2011].
+
 We examine whether variation in the approach to data analysis may be have an influence on our conclusions regarding infants’ developing mispronunciation sensitivity.
-
-We analyzed analysis choices related to timing (post-naming analysis window; offset time) and type of dependent variable in our coding of the dataset because they are consistently reported and might be useful for experiment design in the future by highlighting typical choices and helping establish field standards.
-In the following, we discuss the possible theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these analysis choices may have on measurements of mispronunciation sensitivity development.
+To do so, we analyzed analysis choices related to timing (post-naming analysis window; offset time) and type of dependent variable in our coding of the dataset because they are consistently reported.
+Further, since we observe variation in both aspects of data analysis, summarizing typical choices and their impact might be useful for experiment design in the future and might help establish field standards.
+In the following, we discuss the possible theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these analysis choices may have on reported mispronunciation sensitivity and its development.
 We focus specifically on the size of the mispronunciation sensitivity effect, considering the whole dataset and including condition (correct pronunciation, mispronunciation) as moderator.
@@
 This includes both the length of time before the target object is named (pre-naming phase) as well as after (post-naming phase) and is determined prior to data collection.
-If the post-naming phase represents the amount of time the infant viewed the target-distractor image pairs after auditory presentation of the target word, then the post-naming analysis window represents how much of this phase was included in the statistical analysis.
+The post-naming phase represents the amount of time the infant viewed the target-distractor image pairs after auditory presentation of the target word, and the post-naming analysis window represents how much of this phase was included in the statistical analysis.
 Unlike the post-naming phase, however, the post-naming analysis window can be chosen after the experimental data is collected.
@@
 The most popular post-naming phase length was `r with(dat, getmode(post_nam_actual))*1000` ms, used in `r with(post_length_info, n_exp_conditions[post_nam_actual == getmode(post_length_info$n_exp_conditions)])` records.
-Regarding the post-naming analysis window, half of the records were analyzed using the whole post-naming phase presented to the infant (*n* = `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`), while the other half were analyzed using a shorter portion of the post-naming time window, usually excluding later portions (*n* = `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`).
+Regarding the post-naming analysis window, about half of the records were analyzed using the whole post-naming phase presented to the infant (*n* = `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`), while the other half were analyzed using a shorter portion of the post-naming time window, usually excluding later portions (*n* = `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`).
 Across papers, the length of the post-naming analysis window varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a median value of `r with(dat, median(post_nam_dur))*1000` ms.
@@
 There was no apparent relation between infant age and post-naming phase length (*r* = `r trial.l$estimate`, 95% CI[`r trial.l$conf.int[1]`, `r trial.l$conf.int[2]`], *p* `r psig(trial.l$p.value)`), but there was a significant negative relationship between infant age and post-naming analysis window length, such that younger infants' looking times were analyzed using a longer post-naming analysis window (*r* = `r post.l$estimate`, 95% CI[`r post.l$conf.int[1]`, `r post.l$conf.int[2]`], *p* `r psig(post.l$p.value)`).
-Although we observe no relationship between age and post-naming phase length, a value that is determine before data collection, we do observe a relationship with post-naming analysis window length, a value that may be determined after data collection and even driven by observation of the data itself.
+Although we observe no relationship between age and post-naming phase length, a value that is determine before data collection, we do observe a relationship with post-naming analysis window length, a value that may be determined after data collection and can even be driven by observation of the data itself.
 In other words, we observe variation in time-related analysis decisions related to infants' age.
@@
 The estimate for the  three-way-interaction between condition, post-naming analysis window, and age was small, but significant ($\beta$ `r full_estimate(rma_post_dur_AGE_MS_eff)`).
-As can be seen in Figure \@ref(fig:PlotPostNameCondAge)b, when records were analyzed with a post-naming analysis window of 2000 ms or less, mispronunciation sensitivity seems to increase with infant age.
+As can be seen in Figure \@ref(fig:PlotPostNameCondAge)b, when records were analyzed with a post-naming analysis window of 2000 ms or less (a limit we imposed for visualization purposes), mispronunciation sensitivity seems to increase with infant age.
 If the post-naming analysis window is greater than 2000 ms, however, there is no or a negative relation between mispronunciation sensitivity and age.
@@
 
-Mispronunciation sensitivity experiments typically include a phase where a naming event has not yet occurred (pre-naming phase).
+Mispronunciation sensitivity experiments, as mentioned previously, typically include a phase where a naming event has not yet occurred (pre-naming phase).
 This is followed by a naming event, whether correctly pronounced or mispronounced, and the subsequent phase (post-naming phase).
@@
 Here, the infants' pre-naming phase baseline preferences are not considered and instead target fixations are evaluated based on the likelihood to fixate one of two pictures (50%).
-As most papers do not specify whether these calculations are made before or after aggregating across trials, we make no assumptions about when this step is taken.
+As most papers do not specify whether any of these calculations are made before or after aggregating across trials and/or participants, we make no assumptions about how any aggregate scores or differences were computed.
 
@@
     geom_violin() +
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
+    geom_boxplot(width=0.1)+
+  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
   labs(title="a")+
@@
 In other words, infants show sensitivity to what constitutes unacceptable, possibly meaning-altering variation in word forms, thereby displaying knowledge of the role of phonemic changes throughout the ages assessed here (6 to 30 months).
-At the same time, infants, like adults, can recover from mispronunciations, a key skill in language processing.
+At the same time, infants, like adults, can recover from mispronunciations, a key skill in language processing, as speech errors resulting in mispronunciations are very common in spoken language.
 
 Considering the variation in findings of developmental change in mispronunciation sensitivity (see Introduction), we next evaluated the developmental trajectory of infants' mispronunciation sensitivity, envisioning three possible developmental patterns: increasing, decreasing, and unchanging sensitivity.
-Our analysis of this relationship using age as a moderator revealed a pattern of unchanging sensitivity, which has been reported by a handful of studies directly comparing infants over a small range of ages, such as 18-24 months [@Swingley2000; @Bailey2002] or 12-17 months [@Zesiger2012].
+Our analysis of this relationship revealed a pattern of unchanging sensitivity, which has been reported by a handful of studies directly comparing infants over a small range of ages, such as 18-24 months [@Swingley2000; @Bailey2002] or 12-17 months [@Zesiger2012].
+
 The estimated effect size for mispronunciation sensitivity in our meta-analysis suggests that sensitivity is similar across the range of 6- to 30-month-old infants tested in the studies we include.
@@
 The need for phonologically well-specified word representations increases as children learn more words and must differentiate between them [@CharlesLuce1995].
-Despite the theoretical implications, fewer than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total; see also Figure \@ref(fig:Vocabdescribe1)).
+An examination of the influence of vocabulary size revealed no relationship between object recognition in response to mispronunciations and group-level vocabulary.
+However, only fewer than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total; see also Figure \@ref(fig:Vocabdescribe1)).
+We thus cannot draw strong conclusions about the role of vocabulary, despite their key role in theoretical models of phono-lexical development during early language acquisition.
 There are more mispronunciation sensitivity studies published every year, perhaps due to the increased use of eye-trackers, which reduce the need for offline coding and thus make data collection much more efficient, but this has not translated to an increasing number of mispronunciation sensitivity studies also reporting vocabulary scores.
 We suggest that this may be the result of publication bias favoring significant effects or an overall hesitation to invest in data collection that is not expected to yield significant outcomes.
-More experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size is needed if this is to be evaluated.
+However, it is important to note that given the small sample sizes, only large correlations are expected to become significant.
+Meta-analysis can, on the other hand, reveal smaller significant correlations.
+We thus do not know whether there is indeed no relationship between vocabulary and infants’ responses in mispronunciation studies and more experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size is needed if this link is to be evaluated.
 
@@
 
-What do our results mean for theories of language development?
+What do our results regarding mispronunciation sensitivity, and its (lack of a) relationship with age and vocabulary size, mean for theories of language development?
 Evidence that infants accept a mispronunciation (object identification) while simultaneously holding correctly pronounced and mispronounced labels as separate (mispronunciation sensitivity) may indicate an abstract understanding of words' phonological structure being in place early on.
 It appears that young infants may understand that the phonological form of mispronunciations and correct pronunciations do not match, but that the mispronunciation is a better label for the target compared to the distractor image.
-The lack of age or vocabulary effects in our meta-analysis suggest that this understanding is present from an early age and is maintained throughout early lexical development.
+The lack of age or vocabulary effects in our meta-analysis (carefully) suggest that this understanding is present from an early age and is maintained throughout early lexical development.
+If we were to take our results as robust, it becomes thus a pressing open question that theories have to answer which other factors might prompt acquiring and using language-specific phonological contrasts.
 
@@
 Several of these moderators include manipulations that make mispronunciation detection more or less difficult for the infant.
-As a result, the size of the mispronunciation sensitivity effect may be influenced by the task demands placed on the infant, especially if older infants are given more demanding tasks in comparison to younger infants, potentially masking developmental effects.
+As a result, the size of the mispronunciation sensitivity effect may be influenced by the task, especially if older infants are given more demanding tasks in comparison to younger infants, potentially masking developmental effects.
 Considering this, we also evaluated whether the investigation of each of these manipulations was distributed evenly across infant ages, where an uneven distribution may have subsequently heightened or dampened our estimate of developmental change.
 
-The results of the moderator analysis reflect several findings that have been found in the literature.
+The results of the moderator analysis reflect several findings reported in the literature.
 Although words differ from one another on many acoustic dimensions, changes in phonemes, as measured by phonological features, signal changes in meaning.
@@
 All other studies only test one age [@Bernier2017; @Tamasi2016; @White2008].
-With more studies investigating graded sensitivity at multiple ages in infancy, we would achieve a better estimate of whether this is a stable or developing ability.
+With more studies investigating graded sensitivity at multiple ages in infancy, we would achieve a better estimate of whether this is a stable or developing ability, thus also shedding more light on the progression of phono-lexical development in general that then needs to be captured in theories and models.
 
@@
 TRACE; @McClelland1986].
-Although many studies have examined mispronunciations on multiple positions, the handful of studies that have directly directly compared sensitivity between different positions find that position of the mispronunciation does not modulate sensitivity [@Swingley2009; @Zesiger2012].
+Although many studies have examined mispronunciations on multiple positions, the handful of studies that have directly compared sensitivity between different positions find that position of the mispronunciation does not modulate sensitivity [@Swingley2009; @Zesiger2012].
 This stands in contrast to the findings of our meta-analysis, which showed that for each subsequent position in the word that is changed, from onset to medial and medial to coda, the effect size estimate for looks to the target decreases by `r r2(linear_position)`; infants are more sensitive to changes in the sounds of familiar words when they occur in an earlier position as opposed to a late position.
-
-One potential explanation for the discrepancy between the results of individual studies and that of the current meta-analysis is the difference in how analysis timing is considered depending on the position of the mispronunciation.
+At face value, our results thus support theories placing more importance on earlier phonemes.
+
+One potential explanation for the discrepancy between the results of individual studies and that of the current meta-analysis is the difference in how the timing of different mispronunciation locations are considered in analysis.
 For example, @Swingley2009 adjusted the offset time from 367 ms for onset mispronunciations to 1133 for coda mispronunciations, to ensure that infants have a similar amount of time to respond to the mispronunciation, regardless of position.
 In contrast, if an experiment compares different kinds of medial mispronunciations, as in @Mani2011, it is not necessary to adjust offset time because the mispronunciations have a similar onset time.
-The length of the post-naming analysis window does impact mispronunciation sensitivity, as we discuss below, and by comparing effect sizes for different mispronuciation positions where position timing was not considered, mispronunciations that occur later in the word (i.e.
+The length of the post-naming analysis window does impact mispronunciation sensitivity, as we discuss below, and by comparing effect sizes for different mispronunciation positions where position timing was not considered, mispronunciations that occur later in the word (i.e.
 medial and coda mispronunciations) may be at a disadvantage relative to onset mispronunciations.
@@
 In contrast, sensitivity to vowel mispronunciations increased with age and was greater overall for infants learning Germanic languages, although sensitivity to vowel mispronunciations did increase with age for infants learning Romance languages as well.
-These results show that sensitivity to vowel mispronunciations is modulated both by development and by native language, whereas sensitivity to consonant mispronunciations is fairly similar across age and native language.This pattern of results support previous experimental evidence and a learned account of the C-bias that sensitivity to
-consonants and vowels have a different developmental trajectory and that this difference also depends on whether the infant is learning a Romance (French, Italian) or Germanic (British English, Danish) native language [@Nazzi2016].
-
-Our meta-analysis revealed the rather surprising result that studies which include target and distractor images that overlap in their onset elicit greater mispronunciation sensitivity than studies who do not control for this facotr.
-It should be arguably more, not less, difficult to detect a mispronunciation (dag) when the target and distractor overlap in their onset phoneme (doggie-doll), because the infant can not use differences in the onset sound between the target and distractor to identify the intended referent [@Swingley1999].
+These results show that sensitivity to vowel mispronunciations is modulated both by development and by native language, whereas sensitivity to consonant mispronunciations is fairly similar across age and native language.
+This pattern of results supports previous experimental evidence and a learned account of the so-called consonant bias that sensitivity to consonants and vowels have a different developmental trajectory and that this difference also depends on whether the infant is learning a Romance (French, Italian) or Germanic (British English, Danish) native language [@Nazzi2016].
+
+Our meta-analysis revealed that studies which include target and distractor images that overlap in their onset elicit greater mispronunciation sensitivity than studies who do not control for this factor.
+Based on reasoning in the literature, the opposite would be predicted: it should be more, not less, difficult to detect a mispronunciation (dag) when the target and distractor overlap in their onset phoneme (doggie-doll), because the infant cannot use differences in the onset sound between the target and distractor to identify the intended referent [@Swingley1999].
 Perhaps including overlap between the target and distractor lead infants to pay more attention to mispronunciations, leading to an increased effect of mispronunciation sensitivity.
 When we examined the distribution of this manipulation across infant age, however, we found an alternate explanation for this pattern of results.
-Older children were more likely to recieve the arguably more difficult manipulation where target-distractor pairs overlapped in their onset phoneme.
-If older children have greater mispronunciation sensitivity in general, then this may have lead to greater mispronunciation sensitivity for overlapping target-distractor pairs, instead of the manipulation itself.
-
-But, our main developmental analysis found a lack of developmental change in mispronunciation sensitivity, suggesting that older children do not have greater mispronunciation sensitivity than younger children.
+Older children were more likely to receive the arguably more difficult manipulation where target-distractor pairs overlapped in their onset phoneme.
+If older children have greater mispronunciation sensitivity in general, then this may have led to greater mispronunciation sensitivity for overlapping target-distractor pairs, instead of the manipulation itself.
+
+At the same time, our main developmental analysis found a lack of developmental change in mispronunciation sensitivity, suggesting that older children do not have greater mispronunciation sensitivity than younger children.
 If older children are given a more difficult task than younger children, however, this may dampen any developmental effects.
@@
 Younger children were given an easier task (target-distractor pairs with no overlap), which may have relatively increased the size of their mispronunciation sensitivity effect.
-As a result, any developmental differences would be erased, hidden by task differences in the experiments that older and younger infants participated in.
-This argument is supported by the PRIMIR Framework (@Curtin2011; @Curtin2007; @Werker2005), which argues that infants' ability to access the phonetic detail of familiar words is governed by the difficulty of their current task.
+As a result, any developmental differences would be hidden by task differences in the experiments that older and younger infants participated in.
+This argument is supported by the PRIMIR Framework [@Curtin2011; @Curtin2007; @Werker2005], which argues that infants' ability to access the phonetic detail of familiar words is governed by the difficulty of their current task.
 Further support comes from evidence that sensitivity to mispronunciations when the target-distractor pair overlapped on the onset phoneme increased with age.
-This pattern of results suggest that when infants are given an equally difficult task, developmental effects may be revealed.
+This pattern of results suggests that when infants are given an equally difficult task, developmental effects may be revealed.
 This explanation can be confirmed by testing more young infants on overlapping target-distractor pairs.
@@
 During the coding of these characteristics, we noted a potential for variation in a handful of variables that relate to data analysis, specifically relating to timing (post-naming analysis window; onset time) and to the calculation of the dependent variable reported.
-We focused on these variables in particular because their choice can potentially be made after researchers have examined the data, leading to an inflated number of significant results which may also explain the publication bias observed in the funnel plot asymmetry analyses [@Simmons2011].
-To explore whether this variation contributed to the lack of developmental change observed in the overall meta-analysis, we included these variables as moderators in a set of exploratory analyses.
-We noted an interesting pattern of results, specifically that different conclusions about mispronunciation sensitivity, but more notably mispronunciation sensitivity development, could be drawn depending on the length of the post-naming analysis window as well as the type of dependent variable calculated in the experiment (see Figures \@ref(fig:Plot-post-name-cond-age) and \@ref(fig:Plot-Within-cond-age-diff-score)).
-
-As infants' age increases, they recognize words more quickly [@Fernald1998], which may lead experimenters to adjust and lower offset times in their analysis as well as shorten the length of the analysis window.
+We focused on these variables in particular because they can be changed after researchers have examined the data, possibly leading to an inflated number of significant results which may also explain the publication bias observed in the funnel plot asymmetry analyses [@Simmons2011].
+To further explore whether this variation contributed to the lack of developmental change observed in the overall meta-analysis, we included these variables as moderators in a set of exploratory analyses.
+We noted an interesting pattern of results, specifically that different conclusions about mispronunciation sensitivity, but more notably mispronunciation sensitivity development, could be drawn depending on the length of the post-naming analysis window as well as the type of dependent variable calculated in the experiment (see Figures \@ref(fig:PlotPostNameCondAge) and \@ref(fig:PlotWithinCondAgeDiffScore)).
+
+We first examined whether variation in analysis timing impacted mispronunciation sensitivity.
+As infants mature, they recognize words more quickly [@Fernald1998], which may lead experimenters to adjust and lower offset times in their analysis as well as shorten the length of the analysis window.
 Yet, we find no relationship between age and offset times, nor that offset time modulated mispronunciation sensitivity.
@@
 At worst, this adjustment could be the result of a desire to confirm a hypothesis, increasing the rate of false-positives [@Gelman2013]: a "significant effect" of mispronunciation sensitivity is found with an analysis window of 2000 but not 3000 ms, therefore 2000 ms is chosen.
-At best, this variation introduces noise into the study of mispronunciation sensitivity, bluring the true developmental trajectory of mispronunciation sensitivity.
+At best, this variation introduces noise into the study of mispronunciation sensitivity, blurring the true developmental trajectory of mispronunciation sensitivity.
 In the next section, we highlight some suggestions for how the field can remedy this issue.
 
-Surpisingly, we found that the type of dependent variable calculated moderated mispronunciation sensitivity and conclusions about its developmental trajectory.
-Unlike the exploratory analyses related to timing, there is not a clear reason for one dependent variable to be chosen over another; the prevelence of each dependent variable appears distributed across ages and some authors always calculate the same dependent variable while others use them interchangeably in different publications.
-One clear difference is that both the Difference Score and Pre vs.
-Post dependent variables take into account each infants' actual preference in the pre-naming baseline phase, while the Post dependent variable does not.
+In further analyses on analysis parameters that can be chosen post hoc, we found that the type of dependent variable calculated moderated mispronunciation sensitivity and conclusions about its developmental trajectory.
+Unlike the exploratory analyses related to timing, there is no clear reason for one dependent variable to be chosen over another; the prevalence of each dependent variable appears distributed across ages and some authors always calculate the same dependent variable while others use them interchangeably in different publications.
+One clear difference is that both the Difference Score (reporting looks to the target image after hearing the label minus looks in silence) and Pre vs.
+Post (reporting both variables separately) dependent variables consider each infants' actual preference in the pre-naming baseline phase, while the Post dependent variable (reporting looks to target after labelling only) does not.
 Without access to the raw data, it is difficult to conclusively determine why different dependent variable calculations influence mispronunciation sensitivity.
@@
 On the one hand, this limits the conclusions we can draw regarding our key research question.
-Without access to the full datasets or analysis code of the studies included in this meta-analysis, it is difficult to pinpoint the exact role played by these experimental design and data analysis choices.
+Without access to the full datasets (and ideally analysis code) of the studies included in this meta-analysis, it is difficult to pinpoint the exact role played by these experimental design and data analysis choices.
 On the other hand, this finding emphasizes that current practices of free, potentially ad hoc choices regarding data analyses are not sustainable if the field wants to move towards quantitative evidence for theories of language development.
 
-We take this opportunity to suggest several recommendations to address the issue of potential posthoc analysis decisions.
-Preregistration can serve as proof of a priori decisions regarding data analysis, which can also contain a data-dependent description of how data analysis decisions will be made once data is collected.
-The peer-reviewed form of preregistration, termed Registered Reports, has already been adopted by a large number of developmental journals, and general journals that publish developmental works, showing the field’s increasing acceptance of such practices for hypothesis-testing studies.
-Sharing data (Open Data) can allow others to re-analyze existing datasets to both examine the impact of analysis decisions and cumulatively analyze different datasets in the same way.
+We take this opportunity to make several recommendations to address the issue of varying, potential post hoc analysis decisions.
+First, preregistration can serve as proof of a priori decisions regarding data analysis, which can also contain a data-dependent description of how data analysis decisions will be made once data is collected [see @Havron for a primer].
+The peer-reviewed form of preregistration, Registered Reports, has already been adopted by a large number of developmental journals, and general journals that publish developmental works, showing the field’s increasing acceptance of such practices for hypothesis-testing studies.
+Second, sharing data (Open Data) can allow others to re-analyze existing datasets to both examine the impact of analysis decisions and cumulatively analyze different datasets in the same way.
 Considering the specific issue of analysis time window, experimenters can opt to analyze the time course as a whole, instead of aggregating the proportion of target looking behavior.
@@
 Both Growth Curve Analysis [@Mirman2008; @Law2015] and Permutation Clusters Analysis [@VonHolzen2012; @Maris2007; @DelleLuche2015] offer potential solutions to analyze the full time course.
-Furthermore, it may be useful to establish standard analysis pipelines for mispronunciation studies.
-This would allow for a more uniform analysis of this phenomenon, as well as aid experimenters in future research planning.
+Third, it may be useful to establish standard analysis pipelines for mispronunciation studies.
+This would allow for a more uniform analysis of this phenomenon, as well as aid experimenters in future research planning [see @MB1 for a parallel effor for infant-directed speech preference studies].
 In general, however, a better understanding of how different levels of linguistic knowledge may drive looking behavior is needed.
-We hope this understanding can be achieved by applying the above suggestions.
+We hope the above suggestions take us one step closer to this important goal that clarified the link between internal abilities and behavior in a laboratory study.
 
@@
 
+ptt_power <- round(ptt$power*100, 0)
+
 ptt.correct <- pwr.t.test(n = median_sample, d = .9, sig.level = 0.05, power = NULL)
@@
 The estimated effect for mispronunciation sensitivity in this meta-analysis is `r mp_effect`, and the most frequently observed sample size is `r median_sample` participants.
-If we were to assume that researchers assess mispronunciation sensitivity in a simple paired t-test, the resulting power is `r r2(ptt$power)`.
-Reversely, to achieve 80% power, one would need to test `r round(ptt.est$n, 1)` participants.
-These calculations suggest that for the comparison of responses for correct pronunciations and mispronunciations, the studies included in this meta-analysis are under-powered analyses.
+If we were to assume that researchers assess mispronunciation sensitivity in a simple paired t-test, the resulting power is `r ptt_power`%.
+In other words, only about half the studies should report a significant result even with a true population effect.
+Reversely, to achieve 80% power, one would need to test `r round(ptt.est$n, 0)` participants.
+While this number does not seem to differ dramatically from the observed sample sizes, the impact of the smaller sample sizes on power is thus substantial and should be kept in mind when planning future studies.
 Furthermore, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates require four times the sample size to detect an effect of similar magnitude as the main effect for both ANOVA [@Fleiss1986] and mixed-effect-model [@Leon2009] analyses.
-We thus strongly advocate for a consideration of power and the reported effect sizes to test infants’ mispronunciation sensitivity.
+We thus strongly advocate for a consideration of power and the reported effect sizes to test infants’ mispronunciation sensitivity and factors influencing this ability.
 
@@
 
-This meta-analysis comprises an aggregation of almost two decades of research on mispronunciation sensitivity, finding that infants accept both correct pronunciations and mispronunciations as labels for a target image.
+This meta-analysis comprises an aggregation of two decades of research on mispronunciation sensitivity, finding that infants accept both correct pronunciations and mispronunciations as labels for a target image.
 However, they are more likely to accept correct pronunciations, which indicates sensitivity to mispronunciations in familiar words.
@@
 We recommend future theoretical frameworks take this evidence into account.
-Our meta-analysis was also able to confirm different findings in the literature, including the role of mispronunciation size, mispronunciation position, and the role of the native langauge in sensitivity to mispronunciation type (consonant vs.
+Our meta-analysis was also able to confirm different findings in the literature, including the role of mispronunciation size, mispronunciation position, and the role of the native language in sensitivity to mispronunciation type (consonant vs.
 vowel).

### 2020-02-07 Untitled/Untitled.Rmd
Dev Psych submission

---
title: "Template Title"
author: "Your Name"
date: "The Date"
output:
  bookdown::pdf_document2:
    number_sections: no
    toc: no
    latex_engine: xelatex
header-includes:    
 - \usepackage{tipa}    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

If I knit an Rmd document that includes UTF-8 characters outside the ASCII range (for instance, phonetic symbols like \textipa{[E]} or \textipa{[O]}), they never survive the transition to PDF (with output: `papaja::apa6_pdf`) or to .docx (with output: `papaja::apa6_word`).

### 2020-02-07 VonHolzenBergmann_MPMetaAnalysis.Rmd
Dev Psych submission

@@
 This meta-analysis focuses on studies investigating infants' ability to detect mispronunciations in familiar words, or mispronunciation sensitivity.
-Our goal was to evaluate the development of mispronunciation sensitivity in infancy as well as explore the role of experimental manipulations related to theoretical questions and analysis choices.
+Our goal was to evaluate the development of infants' phonological representations for familiar words as well as explore the role of experimental manipulations related to theoretical questions and analysis choices.
 The results show that although infants are sensitive to mispronunciations, they still accept these altered forms as labels for target objects.
 Interestingly, this ability is not modulated by age or vocabulary size, suggesting that a mature understanding of native language phonology may be present in infants from an early age, possibly before the vocabulary explosion.
-The results also support several theoretical assumptions made in the literature, such as sensitivity to mispronunciation size and position of the mispronunciation modulate mispronunciation sensitivity.
+These results also support several theoretical assumptions made in the literature, such as sensitivity to mispronunciation size and position of the mispronunciation.
 We also shed light on the impact of data analysis choices that may lead to different conclusions regarding the development of infants' mispronunciation sensitivity.
@@
 output            :
-  papaja::apa6_docx
+  papaja::apa6_pdf:
+    latex_engine: xelatex
 
@@
   - \usepackage{fontspec}
-  - \newfontfamily\ipa{Doulos SIL}
-  - \DeclareTextFontCommand{\ipatext}{\ipa}
+  - \usepackage{tipa}
   - \AtBeginEnvironment{tabular}{\singlespacing}
@@
 
-# Introduction
-
 In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts  that differentiate words in a given language (e.g.
@@
 Both studies and the lines of research they sparked showed that under the right conditions, even young infants can use their emerging native language phonological skills during word-level language processing.
-
 @Swingley2000 expanded this exploration to infants's existing representations, investigating how infants interpret phonological variation in familiar word recognition.
@@
 These contrasts are therefore not innate, but must be learned.
-For an infant learning Catalan, the vowel contrast /e/-/E/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish.
+For an infant learning Catalan, the vowel contrast /e/-/\textipa{E}/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish.
 Second, across talkers, these sounds might be realized differently, and change even as the talker talks to an infant or adult [e.g.
@@
 
-An *increase* in mispronunciation sensitivity is predicted by a maturation in phono-lexical representations from holistic to more detailed and has been supported by several studies [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010].
+An *increase* in mispronunciation sensitivity is predicted by a maturation from holistic to more detailed phono-lexical representations and has been supported by several studies [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010].
 More precisely, the difference in target looking for correct and mispronounced trials is reported to be smaller in younger infants and grows as infants develop.
@@
 mama, ball, kitty; @CharlesLuce1995] and encoding representations for these words using fine phonological detail may not be necessary.
-**According to PRIMIR [@Curtin2011; @Curtin2007; @Werker2005] infants's initially episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task.** A growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the phonological detail of their representations [@Barton1980].
+According to PRIMIR [@Curtin2011; @Curtin2007; @Werker2005] infants's initially episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task.
+A growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the phonological detail of their representations [@Barton1980].
 This argument is supported by the results of @Mani2010kepstups.
@@
 Although both age groups were sensitive to mispronunciations overall, 18- but not 24-month-olds showed sensitivity to more subtle 1-feature mispronunciations.
-To account for this pattern of results, the authors suggest that when faced with large and salient mispronunciations, sensitivity to small 1-feature mispronunciations may be obscured, especially if infants show graded sensitivity to different degrees of mispronunciations (see below).
+To account for this pattern of results, the authors suggest that when faced with large and salient mispronunciations, sensitivity to small 1-feature mispronunciations may be obscured, especially if infants show graded sensitivity to different degrees of mispronunciations (see below), as @Mani2011 found with 24-month-olds in their study.
 In contrast, 18-month-olds did not show graded sensitivity, showing similar disruptions to word recognition for smaller and larger mispronunciations.
@@
 But, this may not account for all variability found in the literature.
-Although infant mispronunciation sensitivity studies are generally interested in the phonological detail with which infants represent familiar words, many studies pose more nuanced questions, such as examining the impact of number of phonological features changed or the location of the mispronunciation.
+Although infant mispronunciation sensitivity studies are generally interested in the phonological detail with which infants represent familiar words, many studies pose more nuanced questions, such as examining the impact of number of phonological features changed (mispronunciation size) or the location of the mispronunciation.
 Some studies may differ in their experimental design, presenting a distractor image that overlaps with the target image in the onset phoneme or a completely novel, unfamiliar distractor image.
@@
 
-Consonantal changes may be more disruptive to lexical processing than vowel changes in both adults [@Nazzi2018] and infants [@Nazzi2016], known as the consonant bias.
-A learned account predicts that a consonant bias emerges over development [@Floccia2014; @Nazzi2016; @Keidel2007] and that this emergence is impacted by the language family of the infants' native language [@Nazzi2016].
-In mispronunciation sensitivity, this would first translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations.
-Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels for English- [@Mani2007; @Mani2010kepstups] and Danish-learning infants [@Hojen] and do not compare infants learning different native languages [for evidence from word-learning see @Floccia2014; @Nazzi2009a].
-One study with English-learning infants did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations [@Swingley2016].
-In the current meta-analysis, we examine infants' sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages and native language families to assess the predictions of the learned account of the consonant bias.
-
 The *position of mispronunciation* in the word may differentially interrupt the infant's word recognition process, with onset mispronunciations leading to greater mispronunciation sensitivity than medial or coda mispronunciations.
@@
 In contrast, the TRACE model [@McClelland1986] describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.
+
+Consonantal changes may be more disruptive to lexical processing than vowel changes in both adults [@Nazzi2018] and infants [@Nazzi2016], known as the consonant bias.
+A learned account predicts that a consonant bias emerges over development [@Floccia2014; @Nazzi2016; @Keidel2007] and that this emergence is impacted by the language family of the infants' native language [@Nazzi2016].
+In mispronunciation sensitivity, this would first translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations.
+Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels for English- [@Mani2007; @Mani2010kepstups] and Danish-learning infants [@Hojen] and do not compare infants learning different native languages [for cross-linguistic evidence from word-learning see @Nazzi2009a].
+One study with English-learning infants did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations [@Swingley2016].
+In the current meta-analysis, we examine infants' sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages and native language families to assess the predictions of the learned account of the consonant bias.
 
@@
 
-## (Insert Figure \@ref(fig:PRISMA-image) about here)
-
-```{r PRISMA-image, echo= FALSE, fig.cap="A PRISMA flowchart illustrating the selection procedure used to include studies in the current meta-analysis."}
+(Insert Figure \@ref(fig:PRISMA-image) about here)
+
+```{r PRISMA-image, echo= FALSE, out.width = "100%", fig.cap="A PRISMA flowchart illustrating the selection procedure used to include studies in the current meta-analysis."}
 
@@
 ```
-
-## Study Selection
 
@@
 
+## Study Selection
+
 We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list.
 This process yielded 110 items.
-We then used the google scholar search engine to search for papers citing the original @Swingley2000 publication.
+We then used the Google Scholar search engine to search for papers citing the original @Swingley2000 publication.
 This search was conducted on 22 September, 2017 and yielded 288 results.
@@
 
-## (Insert Table 1 about here)
+(Insert Table 1 about here)
 
@@
 3. Vocabulary size, measured by a standardized questionnaire or list;
-4. Position of mispronunciation: onset, medial, offset, or mixed;
-5. Size of mispronunciation, measured in features changed;
-6. Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;
-7. Type of mispronunciation: consonant, vowel, or both;
-8. Distractor familiarity: familiar or unfamiliar;
+4. Size of mispronunciation, measured in features changed;
+5. Position of mispronunciation: onset, medial, offset, or mixed;
+6. Type of mispronunciation: consonant, vowel, or both;
+7. Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;
+8. Distractor familiarity: familiar or unfamiliar
 
@@
 Most papers (*n* = `r with(comparison_info, count[within_measure == "pre_post_naming_effect"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post_naming_effect"])` papers) subtracted the PTL score for a pre-naming baseline phase from the PTL score for a post-naming phase and report a difference score.
-
 Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(comparison_info, count[within_measure == "pre_post"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post"])` papers), thus reporting two variables, or compared post-naming PTL with a chance level of 50% (*n* = `r with(comparison_info, count[within_measure == "post"])` records from `r with(comparison_info, n_unique[within_measure == "post"])` papers).
-For all these comparisons, positive values (either as reported or after subtraction of chance level or a pre-naming baseline PTL) indicate target looks towards the target object after hearing the label, i.e.
+For all these comparisons, positive values or values above 50% (either as reported or after subtraction of chance level or a pre-naming baseline PTL) indicate target looks towards the target object after hearing the label, i.e.
 a recognition effect.
@@
 Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more looks to the target.
+
+Finally, we assess the statistical power of studies included in our meta-analysis, as well as calculate the sample size required to achieve a 80% power considering our estimate of the population effect and its variance.
+Failing to take effect sizes into account can lead to either underpowered research or testing too many participants.
+Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature [@Bergmann2018].
+At the same time, underpowered studies with significant outcomes are likely to overestimate the effect, leading to wrong estimations of the population effect when paired with publication bias [@Jennions2002].
+Overpowered studies mean that participants were tested unnecessarily, which has ethical implications particularly when working with infants and other difficult to recruit and test populations.
 
@@
 Second, we analyzed the correlation between reported vocabulary size and mispronunciation sensitivity using the package meta [@meta].
-For a subsequent investigation of experimental characteristics, we introduced each as a moderator: size of mispronunciation, position of mispronunciation, phonological overlap between target and distractor labels, type of mispronunciation, and distractor familiarity (more detail below).
+For a subsequent investigation of experimental characteristics, we introduced each as a moderator: size of mispronunciation, position of mispronunciation, type of mispronunciation, phonological overlap between target and distractor labels, and distractor familiarity (more detail below).
 
@@
 
-## (Insert Figure \@ref(fig:FunnelCombo) about here)
+(Insert Figure \@ref(fig:FunnelCombo) about here)
 
@@
 
+```{r Power_calculation, echo = FALSE, results = "hide"}
+
+# effect size for mispronunciation sensitivity
+mp_effect <- r2(coef(summary(rma_MPeffect))[2,1])
+
+si <- dat[,c("short_cite", "expt_num", "same_infant", "n_1")]
+si <- unique(si)
+
+median_sample <- median(si$n_1)
+
+# resulting power, anova
+pat <- pwr.anova.test(k = 2, n = median_sample, f = mp_effect, sig.level = 0.05, power = NULL)
+ptt <- pwr.t.test(n = median_sample, d = mp_effect, sig.level = 0.05, power = NULL)
+
+ptt_power <- round(ptt$power*100, 0)
+
+ptt.correct <- pwr.t.test(n = median_sample, d = .9, sig.level = 0.05, power = NULL)
+ptt.misp <- pwr.t.test(n = median_sample, d = .25, sig.level = 0.05, power = NULL)
+
+# 80% power, anova
+pat.est <- pwr.anova.test(k = 2, n = NULL, f = mp_effect, sig.level = 0.05, power = .8)
+ptt.est <- pwr.t.test(n = NULL, d = mp_effect, sig.level = 0.05, power = .8)
+
+```
+
+The estimated effect for mispronunciation sensitivity in this meta-analysis is `r mp_effect`, and the most frequently observed sample size is `r median_sample` participants.
+If we were to assume that researchers assess mispronunciation sensitivity in a simple paired t-test, the resulting power is `r ptt_power`%.
+In other words, only about half the studies should report a significant result even with a true population effect.
+Reversely, to achieve 80% power, one would need to test `r round(ptt.est$n, 0)` participants.
+While this number does not seem to differ dramatically from the observed sample sizes, the impact of the smaller sample sizes on power is thus substantial and should be kept in mind when planning future studies.
+Furthermore, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates require four times the sample size to detect an effect of similar magnitude as the main effect for both ANOVA [@Fleiss1986] and mixed-effect-model [@Leon2009] analyses.
+We thus strongly advocate for a consideration of power and the reported effect sizes to test infants’ mispronunciation sensitivity and factors influencing this ability.
+
 Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, *p* `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, *p* `r psig(rma_MP$QEp)`), as well as mispronunciation sensitivity, which included the moderator condition (QE(249) = `r r2(rma_MPeffect$QE)`, *p* `r psig(rma_MPeffect$QEp)`).
 This indicated that the sample contains unexplained variance leading to significant difference between studies beyond what is to be expected based on random sampling error.
-We therefore continue with our moderator analysis to investigate possible sources of this variance.
+In our moderator analysis we investigate possible sources of this variance.
 
@@
 
-## (Insert Figure \@ref(fig:PlotMPEffect) about here)
+(Insert Figure \@ref(fig:PlotMPEffect) about here)
 
@@
 
-## (Insert Figure \@ref(fig:Vocabdescribe1 about here)
+(Insert Figure \@ref(fig:Vocabdescribe1) about here)
 
@@
 
-The main goal of this paper was to assess mispronunciation sensitivity and whether it is modulated by maturation with age and increased vocabulary size.
-In the literature, evidence for all possible developmental trajectories has been found, including mispronunciation sensitivity that increases, decreases, or does not change with age or vocabulary size.
-Regarding age, the results seem clear: Although infants consider a mispronunciation to be a better match to the target image than to a distractor image, there was a constant and stable effect of mispronunciation sensitivity across all ages.
+Although infants consider a mispronunciation to be a better match to the target image than to a distractor image, there was a constant and stable effect of mispronunciation sensitivity across all ages.
 Furthermore, although we found a relationship between vocabulary size (comprehension) and target looking for correct pronunciations, we found no relationship between vocabulary and target looking for mispronunciations.
 This may be due to too few studies including reports of vocabulary size and more investigation is needed to draw a firm conclusion.
-These findings support the arguments set by the early specification hypothesis that infants represent words with phonological detail at the beginning of the second year of life.
+These findings support the arguments set by the early specification hypothesis that infants represent words with phonological detail already at the beginning of the second year of life.
 
@@
 
-## (Insert Figure \@ref(fig:PlotFeatEffect) about here)
+(Insert Figure \@ref(fig:PlotFeatEffect) about here)
 
@@
 
-## (Insert Figure \@ref(fig:PlotMispPosit) about here)
+(Insert Figure \@ref(fig:PlotMispPosit) about here)
 
@@
 We next calculated the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in response to the type of mispronunciation, consonant or vowel.
-Furthermore, sensitivity to consonant and vowel mispronunciations is hypothesized to differ depending on whether the infant is learning a Germanic or Romance language.
-We therefore conducted two sets of analyses, one analyzing consonants and vowels alone and a second including langauge family as a moderator.
+Furthermore, sensitivity to consonant and vowel mispronunciations is hypothesized to differ depending on the language family of the infant's native language.
+We therefore conducted two sets of analyses, one analyzing consonants and vowels alone and a second including langauge family (Germanic vs.
+Romance) as a moderator.
 We did not include data for which mispronunciation type varied within experiment and was not reported separately (*n* = `r with(CV_info, sum(n_exp_conditions[type_feature == "consonant_and_vowel" | type_feature == "consonant_vowel_tone"]))`).
@@
 
-## (Insert Figure \@ref(fig:PlotMispType) about here)
+(Insert Figure \@ref(fig:PlotMispType) about here)
 
@@
 
-## (Insert Figure \@ref(fig:PlotCVEffectLang) about here)
+(Insert Figure \@ref(fig:PlotCVEffectLang) about here)
 
@@
 
-When age was added as a moderator, the moderator test was significant, `r mod_test(rma_DistractorOverlap_age_MS)` and the estimate for the three-way interaction between age, condition, and distractor overlap was significant, but relatively small ($\beta$ = `r full_estimate(sum_eff_age)`.
+When age was added as a moderator, the moderator test was significant, `r mod_test(rma_DistractorOverlap_age_MS)` and the estimate for the three-way interaction between age, condition, and distractor overlap was significant, but relatively small ($\beta$ `r full_estimate(sum_eff_age)`.
 As can be seen in Figure \@ref(fig:PlotDistOverlap)b, mispronunciation sensitivity increases with age for target-distractor pairs containing onset overlap, but decreases with age for target-distractor pairs containing no overlap.
@@
 
-## (Insert Figure \@ref(fig:PlotDistOverlap) about here)
+(Insert Figure \@ref(fig:PlotDistOverlap) about here)
 
@@
 
-Next to the main goal of this paper, which was to evaluate the development of infants' sensitivity to mispronunciations, we also investigated the more nuanced questions often posed in studies investigating infants' mispronunciation sensitivity.
-We identified two sets of additional manipulations, relating to the kind of mispronunciation and contextual factors, that are often present in mispronunciation sensitivity studies and investigated the how those manipulations modulated mispronunciation sensitivity and whether this changed with infant age.
-Furthermore, considering the lack of developmental change found in our main analysis, we evaluated whether these additional manipulations were disproportionately conducted with children of different ages, to assess whether older infants receive more difficult tasks than younger ones.
-
-To briefly summarize, mispronunciation sensitivity was modulated overall by the size of the mispronunciation tested, whether target-distractor pairs shared phonological overlap, and the position of the mispronunciation.
+Mispronunciation sensitivity was modulated overall by the size of the mispronunciation tested, whether target-distractor pairs shared phonological overlap, and the position of the mispronunciation.
 Neither distractor familiarity (familiar, unfamiliar) or type of mispronunciation (consonant, vowel) were found to impact mispronunciation sensitivity.
@@
 In the following, we discuss the possible theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these analysis choices may have on reported mispronunciation sensitivity and its development.
-We focus specifically on the size of the mispronunciation sensitivity effect, considering the whole dataset and including condition (correct pronunciation, mispronunciation) as moderator.
+We focus specifically on the size of the mispronunciation sensitivity effect, considering the whole dataset and including condition (correct pronunciation, mispronunciation) as a moderator.
 
@@
 This lack of a relationship is possibly driven by the field's consensus that an offset of about 367 ms is appropriate for analyzing word recognition in infants, including studies that evaluate mispronunciation sensitivity.
-
-Although there are a priori reasons, such as infant age or previous studies, to choose the post-naming analysis window or offset time, these choices may occur after data collection and might therefore lead to a higher rate of false-positives [@Gelman2013].
-Considering that these choices were systematically different across infant ages, at least for the post-naming analysis window, we next explored whether the post-naming analysis window length or the offset time influenced our estimate of infants’ sensitivity to mispronunciations.
 
@@
 If the post-naming analysis window is greater than 2000 ms, however, there is no or a negative relation between mispronunciation sensitivity and age.
-In other words, all three possible developmental hypotheses might be supported depending on analysis choices made regarding post-naming analysis window length.
+In other words, all three possible developmental trajectories might be supported depending on analysis choices made regarding post-naming analysis window length.
 These results suggest that conclusions about the relationship between infant age and mispronunciation sensitivity may be mediated by the size of the post-naming analysis window.
 
-## (Insert Figure \@ref(fig:PlotPostNameCondAge) about here)
+(Insert Figure \@ref(fig:PlotPostNameCondAge) about here)
 
@@
 Although we found no relationship between offset time and infant age, we also examined whether the size of offset time modulated the measure of mispronunciation sensitivity over infant age.
-When both offset time and condition were included as moderators, the moderator test was significant (`r mod_test(rma_offset_AGE_MS)`), but the three-way-interaction between condition, offset time, and age was again zero ($\beta$ `r full_estimate(rma_offset_AGE_MS_eff)`).
+When age was added as a moderator, the moderator test was significant (`r mod_test(rma_offset_AGE_MS)`), but the three-way-interaction between condition, offset time, and age was again zero ($\beta$ `r full_estimate(rma_offset_AGE_MS_eff)`).
 Taken together, these results suggest that offset time does not modulate measured mispronunciation sensitivity nor its developmental trajectory.
@@
 This requires two values, one for the pre-naming phase and one for the post-naming phase.
-A positive Difference Score or a greater post compared to pre-naming phase PTL indicates that infants increased their target looks after hearing the naming label.
+A positive Difference Score or a greater Pre- vs.
+Post-naming phase PTL indicates that infants increased their target looks after hearing the naming label.
 The remaining records used a Post dependent variable (*n* = `r with(dv_info, n_exp_conditions[within_measure == "post"])` records), which compares the post-naming PTL score with a chance value of 50%.
@@
 
-Similar to post-naming analysis window length, all three possible developmental hypotheses might be supported depending on the dependent variable reported.
+Similar to post-naming analysis window length, all three possible developmental trajectories might be supported depending on the dependent variable reported.
 In other words, choice of dependent variable may influence the conclusion drawn regarding how mispronunciation sensitivity may change with infant age.
@@
 
-## (Insert Figure \@ref(fig:PlotWithinCondAgeDiffScore) about here)
+(Insert Figure \@ref(fig:PlotWithinCondAgeDiffScore) about here)
 
@@
 
-In this meta-analysis, we set out to quantify and assess the developmental trajectory of infants’ sensitivity to mispronunciations.
+In this meta-analysis, we set out to quantify and assess the phonological specificity of infants' representations for familiar words and how this is modulated with development, as measured by infant age and vocabulary size.
 Overall, the results of the meta-analysis showed that infants reliably fixate the target object when hearing both correctly pronounced and mispronounced labels.
@@
 Considering the variation in findings of developmental change in mispronunciation sensitivity (see Introduction), we next evaluated the developmental trajectory of infants' mispronunciation sensitivity, envisioning three possible developmental patterns: increasing, decreasing, and unchanging sensitivity.
-Our analysis of this relationship revealed a pattern of unchanging sensitivity, which has been reported by a handful of studies directly comparing infants over a small range of ages, such as 18-24 months [@Swingley2000; @Bailey2002] or 12-17 months [@Zesiger2012].
-
-The estimated effect size for mispronunciation sensitivity in our meta-analysis suggests that sensitivity is similar across the range of 6- to 30-month-old infants tested in the studies we include.
-Furthermore, an examination of the influence of vocabulary size revealed no relationship between object recognition in response to mispronunciations.
+Our analysis of this relationship revealed a pattern of unchanging sensitivity over infant age, which has been reported by a handful of studies directly comparing infants over a small range of ages, such as 18-24 months [@Swingley2000; @Bailey2002] or 12-17 months [@Zesiger2012].
 
@@
 
-With perhaps a few exceptions, the main focus of many of the experiments included in this meta-analysis was not to evaluate whether infants are sensitive to mispronunciations in general but rather to investigate questions related to phonological and lexical processing and development.
+With perhaps a few exceptions, the main focus of many of the experiments included in this meta-analysis was not to evaluate whether infants are sensitive to mispronunciations in general but rather to investigate specific questions related to phonological and lexical processing and development.
 We included a set of moderator analyses to better understand these issues by themselves, as well as how they may have impacted our main investigation of infants' development of mispronunciation sensitivity.
@@
 This pattern of results supports previous experimental evidence and a learned account of the so-called consonant bias that sensitivity to consonants and vowels have a different developmental trajectory and that this difference also depends on whether the infant is learning a Romance (French, Italian) or Germanic (British English, Danish) native language [@Nazzi2016].
+TRACE simulations conducted by @Mayor2014 reveal a relationship between vocabulary size and sensitivity to vowel-medial mispronunciations, although here the authors give more weight to the role of mispronunciation position, a distinction we are unable to make in our analyses.
 
@@
 
-While creating the dataset on which this meta-analysis was based, we included as many details as possible to describe each study.
-During the coding of these characteristics, we noted a potential for variation in a handful of variables that relate to data analysis, specifically relating to timing (post-naming analysis window; onset time) and to the calculation of the dependent variable reported.
+During the coding of our meta-analysis database, we noted a potential for variation in a handful of variables that relate to data analysis, specifically relating to timing (post-naming analysis window; onset time) and to the calculation of the dependent variable reported.
 We focused on these variables in particular because they can be changed after researchers have examined the data, possibly leading to an inflated number of significant results which may also explain the publication bias observed in the funnel plot asymmetry analyses [@Simmons2011].
@@
 In contrast, we found a negative correlation between infant age and the length of the post-naming analysis window, and that increasing the length of the post-naming analysis window decreases the size of mispronunciation sensitivity.
-Given a set of mispronunciation sensitivity data, a conclusion regarding the development of mispronunciation sensitivity would be different depending on the length of the post-naming analysis window.
+TRACE also predicts that looks to the target in response to mispronunciations may be slower than that of correct pronunciations [@Mayor2014], and those studies with longer post-naming analysis windows capture this effect, thereby reducing the measured sensitivity to mispronunciations.
 Although we have no direct evidence, an analysis window can be potentially set after collecting data.
@@
 At best, this variation introduces noise into the study of mispronunciation sensitivity, blurring the true developmental trajectory of mispronunciation sensitivity.
-In the next section, we highlight some suggestions for how the field can remedy this issue.
 
@@
 Without access to the raw data, it is difficult to conclusively determine why different dependent variable calculations influence mispronunciation sensitivity.
-In the next section, we advocate for the adoption of Open Data practices as one way to address this issue.
 
@@
 Considering the specific issue of analysis time window, experimenters can opt to analyze the time course as a whole, instead of aggregating the proportion of target looking behavior.
-This allows for a more detailed assessment of infants' fixations over time and reduces the need to reduce the post-naming analysis window.
+This allows for a more detailed assessment of infants' fixations over time and removes the need to reduce the post-naming analysis window.
 Both Growth Curve Analysis [@Mirman2008; @Law2015] and Permutation Clusters Analysis [@VonHolzen2012; @Maris2007; @DelleLuche2015] offer potential solutions to analyze the full time course.
@@
 We hope the above suggestions take us one step closer to this important goal that clarified the link between internal abilities and behavior in a laboratory study.
-
-A meta-analysis is a first step in improving experiment planning by providing an estimate of the population effect and its variance, which is directly related to the sample needed to achieve satisfactory power in the null hypothesis significance testing framework.
-Failing to take effect sizes into account can lead to either underpowered research or testing too many participants.
-Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature [@Bergmann2018].
-At the same time, underpowered studies with significant outcomes are likely to overestimate the effect, leading to wrong estimations of the population effect when paired with publication bias [@Jennions2002].
-Overpowered studies mean that participants were tested unnecessarily, which has ethical implications particularly when working with infants and other difficult to recruit and test populations.
-
-```{r Power_calculation, echo = FALSE, results = "hide"}
-
-# effect size for mispronunciation sensitivity
-mp_effect <- r2(coef(summary(rma_MPeffect))[2,1])
-
-si <- dat[,c("short_cite", "expt_num", "same_infant", "n_1")]
-si <- unique(si)
-
-median_sample <- median(si$n_1)
-
-# resulting power, anova
-pat <- pwr.anova.test(k = 2, n = median_sample, f = mp_effect, sig.level = 0.05, power = NULL)
-ptt <- pwr.t.test(n = median_sample, d = mp_effect, sig.level = 0.05, power = NULL)
-
-ptt_power <- round(ptt$power*100, 0)
-
-ptt.correct <- pwr.t.test(n = median_sample, d = .9, sig.level = 0.05, power = NULL)
-ptt.misp <- pwr.t.test(n = median_sample, d = .25, sig.level = 0.05, power = NULL)
-
-# 80% power, anova
-pat.est <- pwr.anova.test(k = 2, n = NULL, f = mp_effect, sig.level = 0.05, power = .8)
-ptt.est <- pwr.t.test(n = NULL, d = mp_effect, sig.level = 0.05, power = .8)
-
-```
-
-The estimated effect for mispronunciation sensitivity in this meta-analysis is `r mp_effect`, and the most frequently observed sample size is `r median_sample` participants.
-If we were to assume that researchers assess mispronunciation sensitivity in a simple paired t-test, the resulting power is `r ptt_power`%.
-In other words, only about half the studies should report a significant result even with a true population effect.
-Reversely, to achieve 80% power, one would need to test `r round(ptt.est$n, 0)` participants.
-While this number does not seem to differ dramatically from the observed sample sizes, the impact of the smaller sample sizes on power is thus substantial and should be kept in mind when planning future studies.
-Furthermore, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates require four times the sample size to detect an effect of similar magnitude as the main effect for both ANOVA [@Fleiss1986] and mixed-effect-model [@Leon2009] analyses.
-We thus strongly advocate for a consideration of power and the reported effect sizes to test infants’ mispronunciation sensitivity and factors influencing this ability.
 

### 2020-02-10 VonHolzenBergmann_MPMetaAnalysis.Rmd
Huge page cuts to meet DevPsych requirements

@@
 documentclass     : "apa6"
-classoption       : "man"
+classoption       : "man, noextraspace"
 output            :
@@
   - \captionsetup[figure]{font={stretch=1.5}}
+  - \captionsetup[table]{font=scriptsize}
 ---
@@
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)
+
+# removing authornote for now to save space
+
+# authornote: |
+#   The authors would like to thank Emelyne Gaudichau for valuable assistance in entering data.
+Author 1 was supported by the Agence Nationale de la Recherche (ANR-13-BSH2-0004) and by training grant DC-00046 from the National Institute of Deafness and Communicative Disorders of the National Institutes of Health.
+Author 2 was supported by the European Horizon 2020 programme (Marie Skłodowska-Curie grant No 660911), the Agence Nationale de la Recherche (ANR-10-IDEX-0001-02 PSL*, ANR-10-LABX-0087 IEC) and the Fondation de France.
+The authors each declare that they have no conflict of interest.
 
@@
 library(tidyverse)
+library(kableExtra)
 
@@
 cat-hat).
-Twenty years' worth of studies have examined infants' application of phonological category knowledge during word recognition through the mispronunciation sensitivity paradigm to probe the development of this latter distinction.
-At this point, a picture on the functional use of language-specific phonetic and phonological knowledge began to emerge.
-At the turn of the millennium, infant language acquisition researchers had begun to explore the phonetic information that infants attend to while segmenting words from the speech stream [@Jusczyk1995] and learning minimal pairs [@Stager1997].
-Both studies and the lines of research they sparked showed that under the right conditions, even young infants can use their emerging native language phonological skills during word-level language processing.
-@Swingley2000 expanded this exploration to infants's existing representations, investigating how infants interpret phonological variation in familiar word recognition.
-American-English learning 18- to 23-month-olds were presented with pairs of images of words they were very likely to know (e.g.
+This meta-analysis examines on the latter, focusing how infants apply the relevant phonological categories of their native language, aggregating twenty years' worth of studies using the mispronunciation sensitivity paradigm.
+The original study of @Swingley2000 presented American-English learning 18- to 23-month-olds with pairs of images of words they were very likely to know (e.g.
 a baby and a dog) and their eye movements to each image were recorded.
@@
 @Swingley2000 concluded that already before the second birthday, children's representations for familiar words are phonologically well specified.
-
-Why should sensitivity to mispronunciations pose a challenge to the young infant and thus the findings of @Swingley2000 be found novel?
-There are two key challenges the infant learner has to contend with.
-First, the native language being learned determines the relevant contrasts for the infant language-learner.
-These contrasts are therefore not innate, but must be learned.
-For an infant learning Catalan, the vowel contrast /e/-/\textipa{E}/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish.
-Second, across talkers, these sounds might be realized differently, and change even as the talker talks to an infant or adult [e.g.
-@Benders2013].
 As we will review below, there are opposing theories and resulting predictions, supported by empirical data, as to how this knowledge is acquired and applied to lexical representations.
 The time is thus ripe to aggregate all publicly available evidence using a meta-analysis.
-In doing so, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; @MB1; for notable exceptions).
-Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.
-
-Regarding the change in mispronunciation sensitivity over development, only roughly half of studies have compared more than one age group on the same mispronunciation task (see Table \@ref(tab:SummaryTable)) and of those, all possible patterns of development are found.
-This renders conclusions regarding developmental change in mispronunciation sensitivity difficult.
-Given the diverse evidence for developmental change, or lack thereof, the question arises as to what could be driving these differences.
-We thus summarize the existing empirical evidence, as well as developmental and methodological explanations for an increase, a decrease, or unchanged sensitivity to mispronunciations throughout infancy.
-
-An *increase* in mispronunciation sensitivity is predicted by a maturation from holistic to more detailed phono-lexical representations and has been supported by several studies [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010].
-More precisely, the difference in target looking for correct and mispronounced trials is reported to be smaller in younger infants and grows as infants develop.
+In doing so, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @MB1 for a notable exception).
+
+An *increase* in mispronunciation sensitivity with age is predicted by a maturation from holistic to more detailed phono-lexical representations and has been supported by several studies [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010].
 The first words that infants learn are often not similar sounding [e.g.
 mama, ball, kitty; @CharlesLuce1995] and encoding representations for these words using fine phonological detail may not be necessary.
-According to PRIMIR [@Curtin2011; @Curtin2007; @Werker2005] infants's initially episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task.
-A growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the phonological detail of their representations [@Barton1980].
-This argument is supported by the results of @Mani2010kepstups.
-Here, 12-month-old infants were divided into low and high vocabulary groups.
-High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations (see below for further discussion on consonant-vowel assymmetry).
-If increasing age and/or vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship of either with mispronunciation sensitivity.
+According to PRIMIR [@Curtin2007; @Werker2005] infants's initially episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task.
+This argument is supported by the results of @Mani2010kepstups, who found that 12-month-old infants with a larger vocabulary showed a greater sensitivity to vowel mispronunciations than infants with a smaller vocabulary.
 
@@
 
-There are no theoretical accounts that would predict *decreased* mispronunciation sensitivity, but at least one study has found a decrease in sensitivity to small mispronunciations .
-@Mani2011 tested 18- and 24-month-olds' sensitivity to increasingly larger mispronunciations: 1- (bed-bud), 2- (foot-fit), and 3-feature phonological changes (doll-deal).
-Although both age groups were sensitive to mispronunciations overall, 18- but not 24-month-olds showed sensitivity to more subtle 1-feature mispronunciations.
-To account for this pattern of results, the authors suggest that when faced with large and salient mispronunciations, sensitivity to small 1-feature mispronunciations may be obscured, especially if infants show graded sensitivity to different degrees of mispronunciations (see below), as @Mani2011 found with 24-month-olds in their study.
-In contrast, 18-month-olds did not show graded sensitivity, showing similar disruptions to word recognition for smaller and larger mispronunciations.
+There are no theoretical accounts that would predict *decreased* mispronunciation sensitivity, but at least one study has found a decrease in sensitivity to small mispronunciations.
+Here, 18- but not 24-month-old infants showed sensitivity to more subtle mispronunciations that differed from the correct pronunciation by 1 phonological feature [@Mani2011].
+When faced with large and salient mispronunciations, sensitivity to small 1-feature mispronunciations may be obscured, especially if infants show graded sensitivity to different degrees of mispronunciations (see below), as @Mani2011 found with 24- but not 18-month-olds in their study.
 
@@
 But, this may not account for all variability found in the literature.
-Although infant mispronunciation sensitivity studies are generally interested in the phonological detail with which infants represent familiar words, many studies pose more nuanced questions, such as examining the impact of number of phonological features changed (mispronunciation size) or the location of the mispronunciation.
-Some studies may differ in their experimental design, presenting a distractor image that overlaps with the target image in the onset phoneme or a completely novel, unfamiliar distractor image.
-These experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete.
-We thus follow our analyses of a developmental trajectory with one of features of the task, and line out here task effects which can shed further light on early phono-lexical representations and their maturation.
-
-The PRIMIR Framework [Processing Rich Information from Multidimensional Interactive Representations; @Curtin2011; @Curtin2007; @Werker2005] describes how infants acquire and organize the incoming speech signal into phonetic and indexical detail.
+Many studies pose more nuanced questions, such as examining the impact of number of phonological features changed (mispronunciation size) or the location of the mispronunciation.
+Some studies may differ in their experimental design, presenting a distractor image that is either familiar or completely novel.
+We thus include an analysis of the features of the task to shed further light on early phono-lexical representations and their maturation.
+
+These research questions and experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete.
+The PRIMIR Framework [Processing Rich Information from Multidimensional Interactive Representations; @Curtin2007; @Werker2005] describes how infants acquire and organize the incoming speech signal into phonetic and indexical detail.
 The ability to access and use this detail, however, is governed by the task or developmental demands probed in a particular experiment.
@@
 If older infants are more likely to be tested using a more demanding mispronunciation sensitivity task, this may attenuate developmental effects across studies.
-Note, however, that those studies reporting change [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010] or no change [@Swingley2000; @Bailey2002; @Zesiger2012] all presented the same task across ages .
-
-The manipulations that might increase task demands, such as overlap between target and distractor, are also theoretically interesting, focusing on issues at the intersection of phonological development and lexical processing.
-For specific questions where we can aggregate multiple studies, we take the opportunity to shine a meta-analytic light on what modulates infants' ability to detect mispronunciations in follow-up analyses.
-We outline first which nuanced questions have been frequently asked to provide a more in-depth overview of the current literature.
+Note, however, that those studies reporting change [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010] or no change [@Swingley2000; @Bailey2002; @Zesiger2012] all presented the same task across ages.
 
@@
 
-The *position of mispronunciation* in the word may differentially interrupt the infant's word recognition process, with onset mispronunciations leading to greater mispronunciation sensitivity than medial or coda mispronunciations.
-Models of spoken word processing place more or less importance on the position of a phoneme in a word.
 The COHORT model [@Marslen-Wilson1989] describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.
 In contrast, the TRACE model [@McClelland1986] describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.
-
-Consonantal changes may be more disruptive to lexical processing than vowel changes in both adults [@Nazzi2018] and infants [@Nazzi2016], known as the consonant bias.
-A learned account predicts that a consonant bias emerges over development [@Floccia2014; @Nazzi2016; @Keidel2007] and that this emergence is impacted by the language family of the infants' native language [@Nazzi2016].
-In mispronunciation sensitivity, this would first translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations.
-Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels for English- [@Mani2007; @Mani2010kepstups] and Danish-learning infants [@Hojen] and do not compare infants learning different native languages [for cross-linguistic evidence from word-learning see @Nazzi2009a].
-One study with English-learning infants did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations [@Swingley2016].
+To evaluate these competing theories, studies often manipulate the *mispronunciation position*, whether onset, medial, or coda, in the word.
+
+Consonantal changes may be more disruptive to lexical processing than vowel changes, known as the consonant bias, and a learned account predicts that this bias emerges over development and is impacted by the language family of the infants' native language [for a review see @Nazzi2016].
+Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels for English- [@Mani2007; @Mani2010kepstups; but see @Swingley2016] and Danish-learning infants [@Hojen] and do not compare infants learning different native languages [for cross-linguistic evidence from word-learning see @Nazzi2009a].
 In the current meta-analysis, we examine infants' sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages and native language families to assess the predictions of the learned account of the consonant bias.
@@
 Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.
-Note that in this case, the mispronunciation is necessarily either word-medial or –final, thus possibly creating an interaction between mispronunciation position and phonological overlap.
-
-We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar.
+
+Mispronunciation sensitivity may also be modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar.
 This is a particularly fruitful question to investigate within the context of a meta-analysis, as mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared.
@@
 In contrast, other studies present infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects [@White2008; @Mani2011; @Skoruppa2013; @Swingley2016].
-By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied [@Halberda2003; @Markman2003], an ability that is developing from 18 to 30 months [@Bion2013].
+By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied [@Halberda2003; @Markman2003].
 
@@
 
-apa_table(Sum_table, col.names = c("Paper", "Format", "Age", "Vocabulary", "Familiarity", "Target Overlap", "Size", "Position", "Type", "N Effect Sizes"), caption = "Summary of all studies.
-Age: mean age(s) reported in the paper (in months).
+apa_table(Sum_table, col.names = c("Paper", "Format", "Age", "Vocabulary", "Familiarity", "Target Overlap", "Size", "Position", "Type", "N Effect Sizes"), caption = "Summary of all papers.
+Age: mean age (in months).
 Vocabulary: Comp = comprehension, Prod = production.
-Distractor Familiarity: Fam = Familiar Distractor, Unfam = Unfamiliar Distractor.
-Target Overlap: position of overlap between target and distractor; O = onset, M = medial, C = coda.
-Mispronunciation Size: number of features changed; commas indicate when sizes were compared separately (e.g.
-1, 2, 3), dashes indicate the range of sizes were aggregated (e.g.
-1-3).
+Distractor Familiarity: Fam = Familiar, Unfam = Unfamiliar  Target Overlap: O = onset, M = medial, C = coda.
+Mispronunciation Size: number of features changed; commas indicate separate comparison, dashes indicate an aggregated range.
 Mispronunciation Position: O = onset, M = medial, C = coda.
 Mispronunciation Type: C = consonant, V = vowel, T = tone.
-For both Mispronunciation Position and Type, a slash separator indicates that is was tested but a distinction was not made in the stimuli.
-For all categories, unspec.
+A slash separator indicates no distinction was made in the stimuli and unspec.
 indicates that the value was unspecified in the paper", landscape = TRUE, font_size = "scriptsize", col_spanners = list(`Distractor` = c(5, 6), `Mispronunciation` = c(7, 9)))
@@
 For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results.
-For the planned analyses to evaluate the development of mispronunciation sensitivity and modulating factors, we focus on the following characteristics:
-
-1. Condition: Were words mispronounced or not;
-2. Mean age reported per group of infants, in days; 
-3. Vocabulary size, measured by a standardized questionnaire or list;
-4. Size of mispronunciation, measured in features changed;
-5. Position of mispronunciation: onset, medial, offset, or mixed;
-6. Type of mispronunciation: consonant, vowel, or both;
-7. Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;
-8. Distractor familiarity: familiar or unfamiliar
-
+For the planned analyses to evaluate the development of mispronunciation sensitivity and modulating factors, we focus on the following characteristics: 1) Condition: Were words mispronounced or not; 2) Mean age reported per group of infants, in days; 3) Vocabulary size, measured by a standardized questionnaire or list; 4) Size of mispronunciation, measured in features changed; 5) Position of mispronunciation: onset, medial, coda; 6) Type of mispronunciation: consonant, vowel, or both; 7) Phonological overlap between target and distractor: onset, medial, coda, none; 8) Distractor familiarity: familiar or unfamiliar.
 A detailed explanation for moderating factors 3-8 can be found in their respective sections in the Results [^1].
@@
 Upon request we were provided with correlation values for one paper [@Altvater2010]; we were able to compute correlations using means, standard deviations, and t-values for `r with(corr_info, n_unique[imputed_corr == "no"])` papers [following @Csibra2016; see also @Rabagliati2018].
-Correlations were imputed for the remaining papers [see @Black2017 for the same procedure].
+Correlations were imputed for the remaining papers [@Bergmann2016].
 For two papers, we could not derive any effect size [@Ballem2005; @Renner2017], and for a third paper, we do not have sufficient information in one record to compute effect sizes [@Skoruppa2013].
@@
 
+```{r dv_info}
+
+dv_info <- dat %>%
+  group_by(within_measure) %>%
+  summarize(n_exp_conditions =  n())
+
+dv.l <- summary(lm(age.C ~ within_measure, data = dat))
+
+dv.age.plot <- ggplot(dat, aes(within_measure, age.C)) +     geom_violin() + 
+  geom_jitter(height = 0, width = 0.1, alpha = 0.5)
+
+```
+
 Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement.
@@
 Across papers the baseline comparison varied; since other options were not available to us, we used the baseline reported by the authors of each paper.
-Most papers (*n* = `r with(comparison_info, count[within_measure == "pre_post_naming_effect"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post_naming_effect"])` papers) subtracted the PTL score for a pre-naming baseline phase from the PTL score for a post-naming phase and report a difference score.
-Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(comparison_info, count[within_measure == "pre_post"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post"])` papers), thus reporting two variables, or compared post-naming PTL with a chance level of 50% (*n* = `r with(comparison_info, count[within_measure == "post"])` records from `r with(comparison_info, n_unique[within_measure == "post"])` papers).
-For all these comparisons, positive values or values above 50% (either as reported or after subtraction of chance level or a pre-naming baseline PTL) indicate target looks towards the target object after hearing the label, i.e.
-a recognition effect.
+Over half of the records (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post_naming_effect"])`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase, resulting in a Difference Score.
+The Difference Score is one value, which is then compared with a chance value of 0.
+In contrast, Pre vs.
+Post (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` records), directly compare the post- and pre-naming PTL scores with one another using a statistical test (e.g.
+t-test, ANOVA).
+This requires two values, one for the pre-naming phase and one for the post-naming phase.
+The remaining records used a Post dependent variable (*n* = `r with(dv_info, n_exp_conditions[within_measure == "post"])` records), which compares the post-naming PTL score with a chance value of 50%.
+Here, the infants' pre-naming phase baseline preferences are not considered and instead target fixations are evaluated based on the likelihood to fixate one of two pictures (50%).
 Standardized effect sizes based on mean differences, as calculated here, preserve the sign.
@@
 
-```{r FunnelCombo, echo = FALSE, fig.cap="Funnel plots for object identification, plotting the standard error of the effect size in relation to the effect size.
+```{r FunnelCombo, echo = FALSE, fig.width=7,fig.height=4, fig.cap="Funnel plots for object identification, plotting the standard error of the effect size in relation to the effect size.
 The black line marks zero, the dashed grey line marks the effect estimate, and the grey line marks funnel plot asymmetry.", results="hide"}
@@
 
+```{r MAMP}
+
+#rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
+
+#
+rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
+
+#summary(rma_MP)
+
+sum_eff_misp <- coef(summary(rma_MP))[1,]
+
+```
+
 We first calculated the meta-analytic effect for infants' ability to identify objects when hearing correctly pronounced labels.
-The variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was significantly different from zero `r CI_p(sum_eff)`.
-This is a small to medium effect size [according to the criteria set by @Mills-Smith2015].
-That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants tended to fixate on the corresponding object.
-Although the publication bias present in our analysis of funnel plot asymmetry suggests that the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)`, which is substantially above zero, together suggest that this result is somewhat robust.
-In other words, we are confident that the true population mean lies above zero for object recognition of correctly pronounced words.
-
-```{r MAMP}
-
-#rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
-
-#
-rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ unique_row |  short_cite.same_infant_calc))
-
-#summary(rma_MP)
-
-sum_eff <- coef(summary(rma_MP))[1,]
-
-```
-
+The variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)`, a large effect, which was significantly different from zero `r CI_p(sum_eff)` with a CI lower bound of `r r2(sum_eff$ci.lb)`.
 We then calculated the meta-analytic effect for object identification in response to mispronounced words.
-In this case, the variance-weighted meta-analytic effect size was `r g_SE(sum_eff)` which was also significantly different from zero `r CI_p(sum_eff)`.
-This is considered a small effect size [@Mills-Smith2015], but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object.
-In other words, infants are able to resolve mispronunciations, a key skill in language processing We again note the publication bias (which was smaller in this condition), and the possibility that the effect size may be overestimated.
-But, as the p-curve indicated evidential value, we are confident in the overall pattern, namely that infants fixate the target even after hearing a mispronounced label.
+In this case, the variance-weighted meta-analytic effect size was `r g_SE(sum_eff_misp)`, a small effect, which was also significantly different from zero `r CI_p(sum_eff_misp)`.
+When presented with a correct or mispronounced label, infants fixated the correct object.
 
@@
 The estimate for mispronunciation sensitivity was `r g_SE(sum_eff)`, and infants' looking behavior across conditions was significantly different `r CI_p(sum_eff)`.
-This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations.
-In other words, we observe a significant difference between the two conditions and can now quantify the modulation of fixation behavior in terms of standardized effect sizes and their variance.
-This first result has both theoretical and practical implications, as we can now reason about the amount of perturbation caused by mispronunciations and can plan future studies to further investigate this effect with suitable power.
+This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations, suggesting sensitivity to mispronunciations.
 
@@
 
-The estimated effect for mispronunciation sensitivity in this meta-analysis is `r mp_effect`, and the most frequently observed sample size is `r median_sample` participants.
+The estimated effect for mispronunciation sensitivity in this meta-analysis is `r mp_effect`, and the median sample size is `r median_sample` participants.
 If we were to assume that researchers assess mispronunciation sensitivity in a simple paired t-test, the resulting power is `r ptt_power`%.
@@
 Reversely, to achieve 80% power, one would need to test `r round(ptt.est$n, 0)` participants.
-While this number does not seem to differ dramatically from the observed sample sizes, the impact of the smaller sample sizes on power is thus substantial and should be kept in mind when planning future studies.
-Furthermore, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates require four times the sample size to detect an effect of similar magnitude as the main effect for both ANOVA [@Fleiss1986] and mixed-effect-model [@Leon2009] analyses.
-We thus strongly advocate for a consideration of power and the reported effect sizes to test infants’ mispronunciation sensitivity and factors influencing this ability.
 
@@
 The lack of a significant modulation together with the small estimates for age (correct: $\beta$ `r full_estimate(Csum_eff)`; mispronunciation: $\beta$ `r full_estimate(Msum_eff)`) indicates that there might be no relationship between age and target looks in response to a correctly pronounced or mispronounced label.
-We note that the estimates in both cases are positive, however, which is in line with the general assumption that infants’ language processing overall improves as they mature [@Fernald1998].
-We plot both object recognition and mispronunciation sensitivity as a function of age in Figure \@ref(fig:PlotMPEffect).
 
@@
 The moderator test was significant (`r mod_test(rma_MPeffect_age)`).
-The interaction between age and mispronunciation sensitivity, however, was not significant ($\beta$ `r full_estimate(sum_eff)`); the moderator test was mainly driven by the difference between conditions.
+The interaction between age and mispronunciation sensitivity, however, was not significant ($\beta$ `r full_estimate(sum_eff)`).
 The small estimate, as well as inspection of Figure \@ref(fig:PlotMPEffect), suggests that as infants age, their mispronunciation sensitivity neither increases or decreases.
@@
 
-```{r PlotMPEffect, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for correct pronunciations (orange) and mispronunciations (blue) by participant age.
+```{r PlotMPEffect, echo = FALSE, fig.width=7,fig.height=7, fig.cap="Panel a: Effect sizes for correct pronunciations (orange) and mispronunciations (blue) by participant age.
 Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) by participant age.
@@
 
-### Vocabulary Size: Correlation Between Mispronunciation Sensitivity and Vocabulary
+### Vocabulary Correlations
 
@@
 
+Children comprehend more words than they can produce, leading to different estimates for comprehension and production and we planned to analyze these correlations separately.
 Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` analyzed the relationship between vocabulary scores and object recognition for correct pronunciations and mispronunciations (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers and `r with(vi1, count[has_vocab == "comprehension"])` records; production = `r with(vi1, papers[has_vocab == "production"])` papers and `r with(vi1, count[has_vocab == "production"])` records).
-Children comprehend more words than they can produce, leading to different estimates for comprehension and production.
-Production data is easier to estimate for parents in the typical questionnaire-based assessment and may therefore be more reliable [@Tomasello1994].
-As a result, we planned to analyze these two types of vocabulary measurement separately.
-However, because only `r with(vi1, papers[has_vocab == "production"])` papers reported correlations with productive vocabulary scores, only limited conclusions can be drawn.
-We also note that because individual effect sizes in our analysis were related to object recognition and not mispronunciation sensitivity, we were only able to calculate the relationship between vocabulary scores and the former.
-In our vocabulary analysis, we therefore focus exclusively on the relationship between comprehension and object recognition for correct pronunciations and mispronunciations.
+Although production data may be easier to estimate for parents in the typical questionnaire-based assessment, we deemed `r with(vi1, papers[has_vocab == "production"])` papers for production correlations too few to analyze.
+We also note that individual effect sizes in our analysis were related to object recognition and not mispronunciation sensitivity, and we therefore focus exclusively on the relationship between comprehension and object recognition for correct pronunciations and mispronunciations.
 
@@
 
-```{r Vocabdescribe1, echo = FALSE, fig.width=10,fig.height=8, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (orange), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (green).", results="hide"}
+```{r Vocabdescribe1, echo = FALSE, fig.width=7,fig.height=4.5, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (orange), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (green).", results="hide"}
 #how did vocabulary collection change over time?
@@
 
+Our power analysis revealed that mispronunciation sensitivity studies typically underpowered, with `r ptt_power`% power and would need to increase their sample from an average of `r median_sample` to `r round(ptt.est$n, 0)`more infants to achieve 80% power.
+While this number does not seem to differ dramatically from the observed sample sizes, the impact of the smaller sample sizes on power is thus substantial and should be kept in mind when planning future studies.
+Furthermore, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates require four times the sample size to detect an effect of similar magnitude as the main effect for both ANOVA [@Fleiss1986] and mixed-effect-model [@Leon2009] analyses.
+We thus strongly advocate for a consideration of power and the reported effect sizes to test infants’ mispronunciation sensitivity and factors influencing this ability.
+
 The studies examined in this meta-analysis examined mispronunciation sensitivity, but many also included more specific questions aimed at uncovering more detailed phonological processes at play during word recognition.
@@
 It is possible that the lack of developmental change in mispronunciation sensitivity found by our meta-analysis does not capture a true lack of change, but is instead influenced by differences in the types of tasks given to infants of different ages.
+We examine this possibility in a set of moderator analyses
+
+## Moderator Analyses
+
 If infants' word recognition skills are generally thought to improve with age and vocabulary size, research questions that tap more complex processes may be more likely to be investigated in older infants.
-In the following section, we investigate the role that different moderators play in mispronunciation sensitivity.
-To investigate the possibility of systematic differences in the tasks across ages, we additionally include an exploratory analysis of whether different moderators and experimental design features were included at different ages.
-
-## Moderator Analyses
-
 In this section, we consider each moderator individually and investigate its influence on mispronunciation sensitivity.
@@
 To better understand the impact of these moderators on developmental change, we include age as subsequent moderator.
+Results of the moderator tests as well as the individual effects for each moderator interaction are reported in Table 2.
+All moderator tests were significant and subsequent significant interactions of critical terms are interpreted.
 Finally, we analyze the relationship between infant age and the moderator condition they were tested in using Fisher's exact test, which is more appropriate for small sample sizes [@Fisher1922].
 This evaluates the independence of infants' age group (divided into quartiles unless otherwise specified) and assignment to each type of condition in a particular moderator.
+
+(Insert Table 2 about here)
+
+```{r mod_table, results = "hide"}
+
+mod_table <- data.frame(matrix(NA, nrow=0, ncol=7))
+
+names(mod_table) <- c("moderator", "moderator test", "interaction terms", "Hedges' g", "SE", "CI", "p")
+
+```
 
@@
 
-To assess whether the size of the mispronunciation tested, as measured by the number of features changed, modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced using 1-, 2-, and 3-feature changes.
-We did not include data for which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent (e.g., one mispronunciation included a 2-feature change whereas another only a 1-feature change).
-This analysis was therefore based on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` records for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations.
-Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an equal impact on mispronunciation sensitivity, following the argument of graded sensitivity [@White2008; @Mani2011], and this moderator was coded as a continuous variable.
+To assess whether the size of the mispronunciation tested, as measured by the number of features changed, modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` records for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations.
+Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an graded impact on mispronunciation sensitivity [@White2008; @Mani2011] and this moderator was coded as a continuous variable.
+We did not include records for which the numer of features changed was not specified or consistent within a record (e.g., both 1- and 2-feature changes within one mispronunciation record).
 
@@
 
-```{r PlotFeatEffect, echo = FALSE, fig.width=10,fig.height=6, fig.cap="Effect sizes for correct pronunciations, 1-, 2-, and 3-feature mispronunciations.", results="hide"}
+```{r NFeatures_mod_table, results = "hide"}
+
+mod <- "Misp. size"
+mod.t <- mod_test(rma_NFeatures)
+inter <- ""
+E_Hg <- as.character(r2(sum_eff[1]))
+E_SE <- as.character(r2(sum_eff[2]))
+E_CI <- paste0("[", as.character(r2(sum_eff[5])), ", ", as.character(r2(sum_eff[6])), "]")
+E_p <- as.character(psig(sum_eff[4]))
+
+lin <- cbind(mod, mod.t, inter, E_Hg, E_SE, E_CI, E_p)
+
+mod.t <- mod_test(rma_NFeatures_age)
+inter <- "Age"
+E_Hg <- as.character(r2(sum_eff_age[1]))
+E_SE <- as.character(r2(sum_eff_age[2]))
+E_CI <- paste0("[", as.character(r2(sum_eff_age[5])), ", ", as.character(r2(sum_eff_age[6])), "]")
+E_p <- as.character(psig(sum_eff_age[4]))
+
+lin2 <- cbind(mod, mod.t, inter, E_Hg, E_SE, E_CI, E_p)
+
+mod_table <- rbind(mod_table, lin, lin2)
+
+```
+
+```{r PlotFeatEffect, echo = FALSE, fig.width=7,fig.height=3.5, fig.cap="Effect sizes for correct pronunciations, 1-, 2-, and 3-feature mispronunciations.", results="hide"}
 
@@
 
-To understand the relationship between mispronunciation size and mispronunciation sensitivity, we  evaluated the effect size Hedges' *g* with number of features changed as a moderator.
-The moderator test was significant, `r mod_test(rma_NFeatures)`.
-Hedges' *g* for number of features changed was `r g_SE(sum_eff)`, which indicated that as the number of features changed increased, the effect size Hedges' *g* significantly decreased `r CI_p(sum_eff)`.
+The model results revealed that as the number of features changed increased, the effect size Hedges' *g* significantly decreased (Table 2).
 We plot this relationship in Figure \@ref(fig:PlotFeatEffect).
-This confirms previous findings of a graded sensitivity to the number of features changed for both consonant [@Bernier2017; @Tamasi2016; @White2008] and vowel [@Mani2011] mispronunciations as well as the importance of controlling for the degree of phonological mismatch in experimental design.
-In other words, the infants' ability to detect a mispronunciation depends on the size of the mispronunciation.
-
-When age was added as a moderator to the model, the moderator test was significant, `r mod_test(rma_NFeatures_age)`, but the estimate for the interaction between age and number of features changed was small and not significant, $\beta$`r full_estimate(sum_eff_age)`.
-This suggests that the impact of number of features changed on mispronunciation sensitivity does not substantially change with infant age.
-We note, however, that only a handful of studies have explicitly examined the effect of the number of features changed on mispronunciation sensitivity and only these studies include 3-feature changes [@Bernier2017; @Tamasi2016; @White2008; @Mani2011], which may narrow our ability to draw conclusions about developmental change.
-
+Age did not modulate this effect.
 Finally, results of Fisher's exact test were not significant, *p* `r psig(fish.test$p.value)`.
-This lack of a relationship suggests that older and younger infants are not being tested in experimental conditions that differentially manipulate the number of features changed.
 
@@
 
-We next calculated the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in response to mispronunciations on the onset, medial, and coda phonemes.
+We next calculated the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in response to mispronunciations on the onset (*n* = `r with(mli, n_exp_conditions[mispron_location == "onset"])` records), medial medial (*n* = `r with(mli, n_exp_conditions[mispron_location == "medial"])`), and coda phonemes (*n* = `r with(mli, n_exp_conditions[mispron_location == "coda"])`).
+We coded the onset, medial, and coda positions as continuous variables, to evaluate the importance of each subsequent position [@Marslen-Wilson1989].
 We did not include data for which the mispronunciation varied within record in regard to position (*n* = `r vary_loc`) or was not reported (*n* = `r with(misp_location_info, n_exp_conditions[is.na(mispron_location)])`).
-The analysis was therefore based on a subset of records of the overall dataset, testing mispronunciations on the onset (*n* = `r with(mli, n_exp_conditions[mispron_location == "onset"])` records), medial (*n* = `r with(mli, n_exp_conditions[mispron_location == "medial"])`), and coda (*n* = `r with(mli, n_exp_conditions[mispron_location == "coda"])`) phonemes.
-We coded the onset, medial, and coda positions as continuous variables, to evaluate the importance of each subsequent position [@Marslen-Wilson1989].
 
@@
 
-```{r PlotMispPosit, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions.
+```{r Mispposit_mod_table, results = "hide"}
+
+mod <- "Misp. position"
+
+mod.t <- mod_test(rma_LinearLocationCondition)
+inter <- "Condition"
+E_Hg <- as.character(r2(sum_eff[1]))
+E_SE <- as.character(r2(sum_eff[2]))
+E_CI <- paste0("[", as.character(r2(sum_eff[5])), ", ", as.character(r2(sum_eff[6])), "]")
+E_p <- as.character(psig(sum_eff[4]))
+
+lin <- cbind(mod, mod.t, inter, E_Hg, E_SE, E_CI, E_p)
+
+mod.t <- mod_test(rma_LinearLocationCondition_age)
+inter <- "Condition * Age"
+E_Hg <- as.character(r2(sum_eff_age[1]))
+E_SE <- as.character(r2(sum_eff_age[2]))
+E_CI <- paste0("[", as.character(r2(sum_eff_age[5])), ", ", as.character(r2(sum_eff_age[6])), "]")
+E_p <- as.character(psig(sum_eff_age[4]))
+
+lin2 <- cbind(mod, mod.t, inter, E_Hg, E_SE, E_CI, E_p)
+
+mod_table <- rbind(mod_table, lin, lin2)
+
+```
+
+```{r PlotMispPosit, echo = FALSE, fig.width=7,fig.height=3.5, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions.
 Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions by age.
@@
 
-When mispronunciation position was included as a moderator, the moderator test was significant, `r mod_test(rma_LinearLocationCondition)`.
-For the interaction between condition and mispronunciation position, the estimate was small but significant ($\beta$ `r full_estimate(sum_eff)`.
-As can be seen in Figure \@ref(fig:PlotMispPosit), mispronunciation sensitivity decreased linearly as the position of the mispronunciation moved later in the word, with sensitivity greatest for onset mispronunciations and smallest for coda mispronunciations.
-
-When age was added as a moderator, the moderator test was significant, `r mod_test(rma_LinearLocationCondition_age)`.
-The estimate for the three-way interaction between age, condition, and mispronunciation position was small and not significant ($\beta$ `r full_estimate(sum_eff_age)`.
-
+The model results revealed that mispronunciation sensitivity decreased linearly as the position of the mispronunciation moved later in the word, with sensitivity greatest for onset mispronunciations and smallest for coda mispronunciations (Table 2).
+We plot this relationship in Figure \@ref(fig:PlotMispPosit).
+When age was added as a moderator, however, the interaction between age, condition, and mispronunciation position was small and not significant.
 Due to the small sample size of coda mispronunciations, we only included 3 age groups in Fisher's exact test.
@@
 Older infants were more likely to be tested on onset mispronunciations, while younger infants were more likely to be tested on medial mispronunciations.
-An onset mispronunciation may be more disruptive to lexical access than mispronunciations in subsequent positions [@Marslen-Wilson1989], and therefore easier to detect.
-For this reason, it is rather unsuprising that onset mispronunciations show the greatest estimate of mispronunciation sensitivity.
-However, it also means that younger infants, who were more likely to be tested on medial mispronunciations, had a comparably harder task than older infants, who were more likely to be tested on onset mispronunciations.
-It is unlikely that this influenced our developmental trajectory estimate, as the consequence would have been mispronunciation sensitivity that increases with age.
 
@@
 
-```
-
-We next calculated the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in response to the type of mispronunciation, consonant or vowel.
+family <- dat %>%
+  group_by(lang_family) %>%
+  summarize(count = n())
+
+lang_family <- dat %>%
+  group_by(native_lang, lang_family) %>%
+  summarize(count = n())
+
+cv_family <- dat %>%
+  group_by(type_feature, lang_family) %>%
+  summarize(count = n())
+
+```
+
+We next calculated the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in response to the type of mispronunciation, consonant (*n* = `r with(CV_info, n_exp_conditions[type_feature == "consonant"])`) or vowel (*n* = `r with(CV_info, n_exp_conditions[type_feature == "vowel"])`).
 Furthermore, sensitivity to consonant and vowel mispronunciations is hypothesized to differ depending on the language family of the infant's native language.
+Infants learning American English (*n* = `r with(lang_family, count[native_lang == "American English"])`), British English (*n* = `r with(lang_family, count[native_lang == "British English"])`), Danish (*n* = `r with(lang_family, count[native_lang == "Danish"])`), Dutch (*n* = `r with(lang_family, count[native_lang == "Dutch"])`), and German (*n* = `r with(lang_family, count[native_lang == "German"])`) were classified into the Germanic language family (*n* = `r with(family, count[lang_family == "Germanic"])`).
+Infants learning Catalan (*n* = `r with(lang_family, count[native_lang == "Catalan"])`), Spanish (*n* = `r with(lang_family, count[native_lang == "Spanish"])`), French (*n* = `r with(lang_family, count[native_lang == "French"])`), Catalan and Spanish simultaneously (i.e.
+bilinguals; *n* = `r with(lang_family, count[native_lang == "Catalan-Spanish"])`), and Swiss French (*n* = `r with(lang_family, count[native_lang == "Swiss French"])`) were classified into the Romance language family (*n* = `r with(family, count[lang_family == "Romance"])`).
 We therefore conducted two sets of analyses, one analyzing consonants and vowels alone and a second including langauge family (Germanic vs.
@@
 We did not include data for which mispronunciation type varied within experiment and was not reported separately (*n* = `r with(CV_info, sum(n_exp_conditions[type_feature == "consonant_and_vowel" | type_feature == "consonant_vowel_tone"]))`).
-The analysis was therefore based on a subset of the overall dataset, comparing records with consonant (*n* = `r with(CV_info, n_exp_conditions[type_feature == "consonant"])`) and vowel (*n* = `r with(CV_info, n_exp_conditions[type_feature == "vowel"])`) mispronunciations.
 
@@
 
-rma_TypeFeaturesMP_Condition <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~same_infant_calc | short_cite)
-
-sum_eff_age <- coef(summary(rma_TypeFeaturesMP_Condition))[8,]
+rma_TypeFeaturesMP_Condition_age <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*condition*age.C, data = db_type, random = ~same_infant_calc | short_cite)
+
+sum_eff_age <- coef(summary(rma_TypeFeaturesMP_Condition_age))[8,]
 
@@
 fish.test <- fisher.test(type_ages, workspace=2e8)
+
+```
+
+```{r MispType_mod_table, results = "hide"}
+
+mod <- "Misp. type"
+
+mod.t <- mod_test(rma_TypeFeaturesMP_Condition)
+inter <- "Condition"
+E_Hg <- as.character(r2(sum_eff2[1]))
+E_SE <- as.character(r2(sum_eff2[2]))
+E_CI <- paste0("[", as.character(r2(sum_eff2[5])), ", ", as.character(r2(sum_eff2[6])), "]")
+E_p <- as.character(psig(sum_eff2[4]))
+
+lin <- cbind(mod, mod.t, inter, E_Hg, E_SE, E_CI, E_p)
+
+mod.t <- mod_test(rma_TypeFeaturesMP_Condition_age)
+inter <- "Condition * Age"
+E_Hg <- as.character(r2(sum_eff_age[1]))
+E_SE <- as.character(r2(sum_eff_age[2]))
+E_CI <- paste0("[", as.character(r2(sum_eff_age[5])), ", ", as.character(r2(sum_eff_age[6])), "]")
+E_p <- as.character(psig(sum_eff_age[4]))
+
+lin2 <- cbind(mod, mod.t, inter, E_Hg, E_SE, E_CI, E_p)
+
+mod_table <- rbind(mod_table, lin, lin2)
 
@@
 
-When mispronunciation type was included as a moderator, the moderator test was significant, `r mod_test(rma_TypeFeaturesMP_Condition)`, but the interaction between mispronunciation type and condition ($\beta$`r full_estimate(sum_eff2)`) was not significant.
-The results suggest that overall, infants' sensitivity to consonant and vowel mispronunciations was similar (Figure \@ref(fig:PlotMispType)a).
-
-When age was added as a moderator, the moderator test was significant, `r mod_test(rma_TypeFeaturesMP_Condition)` and the estimate for the three-way interaction between age, condition, and mispronunciation type was significant, but relatively small ($\beta$ `r full_estimate(sum_eff_age)`.
-As can be seen in Figure \@ref(fig:PlotMispType)b, as infants age, mispronunciation sensitivity grows larger for vowel mispronunciations but stays steady for consonant mispronunciations.
-Noticeably, mispronunciation sensitivity appears greater for consonant compared to vowel mispronunciations at younger ages, but this difference diminishes as infants age.
-
+The model results revealed that mispronunciation sensitivity did not differ between consonant and vowel mispronunciations (Table 2).
+We plot this relationship in Figure \@ref(fig:PlotMispType)a.
+When age was added as a moderator, however, the model revealed that as infants age, mispronunciation sensitivity grows larger for vowel mispronunciations but stays steady for consonant mispronunciations (Figure \@ref(fig:PlotMispType)b).
 The results of Fisher's exact test were significant, *p* `r psig(fish.test$p.value)`.
 Older infants were more likely to be tested on consonant mispronunciations, while younger infants were more likely to be tested on vowel mispronunciations.
-It is not immediately clear whether the relationship between infant age and type of mispronunciation influences our estimate of how mispronunciation sensitivity changes with development.
 Whether consonant or vowel mispronunciations are more "difficult" is a matter of theoretical debate, but some evidence suggest that it may be influenced by infants' native language [@Nazzi2016].
@@
 (Insert Figure \@ref(fig:PlotMispType) about here)
-
-```{r MPtype_cv_lang_descript}
-
-family <- dat %>%
-  group_by(lang_family) %>%
-  summarize(count = n())
-
-lang_family <- dat %>%
-  group_by(native_lang, lang_family) %>%
-  summarize(count = n())
-
-cv_family <- dat %>%
-  group_by(type_feature, lang_family) %>%
-  summarize(count = n())
-
-```
 
@@
 fish.test <- fisher.test(type_lang_ages, workspace=2e8)
+
+```
+
+```{r MispTypeLang_mod_table, results = "hide"}
+
+mod <- "Misp. type"
+
+mod.t <- mod_test(rma_TypeFeaturesMPC)
+inter <- "Condition * Language Family"
+E_Hg <- as.character(r2(sum_eff_famcv[1]))
+E_SE <- as.character(r2(sum_eff_famcv[2]))
+E_CI <- paste0("[", as.character(r2(sum_eff_famcv[5])), ", ", as.character(r2(sum_eff_famcv[6])), "]")
+E_p <- as.character(psig(sum_eff_famcv[4]))
+
+lin <- cbind(mod, mod.t, inter, E_Hg, E_SE, E_CI, E_p)
+
+mod.t <- mod_test(rma_TypeFeaturesMPC_age)
+inter <- "Condition * Language Family * Age"
+E_Hg <- as.character(r2(sum_eff2_lang_age[1]))
+E_SE <- as.character(r2(sum_eff2_lang_age[2]))
+E_CI <- paste0("[", as.character(r2(sum_eff2_lang_age[5])), ", ", as.character(r2(sum_eff2_lang_age[6])), "]")
+E_p <- as.character(psig(sum_eff2_lang_age[4]))
+
+lin2 <- cbind(mod, mod.t, inter, E_Hg, E_SE, E_CI, E_p)
+
+mod_table <- rbind(mod_table, lin, lin2)
 
@@
 
-We first classified infants into language families.
-Infants learning American English (*n* = `r with(lang_family, count[native_lang == "American English"])`), British English (*n* = `r with(lang_family, count[native_lang == "British English"])`), Danish (*n* = `r with(lang_family, count[native_lang == "Danish"])`), Dutch (*n* = `r with(lang_family, count[native_lang == "Dutch"])`), and German (*n* = `r with(lang_family, count[native_lang == "German"])`) were classified into the Germanic language family (*n* = `r with(family, count[lang_family == "Germanic"])`).
-Infants learning Catalan (*n* = `r with(lang_family, count[native_lang == "Catalan"])`), Spanish (*n* = `r with(lang_family, count[native_lang == "Spanish"])`), French (*n* = `r with(lang_family, count[native_lang == "French"])`), Catalan and Spanish simultaneously (i.e.
-bilinguals; *n* = `r with(lang_family, count[native_lang == "Catalan-Spanish"])`), and Swiss French (*n* = `r with(lang_family, count[native_lang == "Swiss French"])`) were classified into the Romance language family (*n* = `r with(family, count[lang_family == "Romance"])`).
-
-When language family was included as a moderator, the moderator test was significant, `r mod_test(rma_TypeFeaturesMPC)`.
-The three-way interaction between mispronunciation type, condition, language family was large and also significant, $\beta$`r full_estimate(sum_eff_famcv)`.
-As can be seen in Figure \@ref(fig:PlotCVEffectLang)a, mispronunciation sensitivity for consonants was similar for Germanic and Romance languages.
-Mispronunciation sensitivity for vowels, however, was greater for Germanic compared to Romance languages.
-
-We next added age as a moderator, resulting in a significant moderator test, `r mod_test(rma_TypeFeaturesMPC_age)`, and a small but significant estimate for the four-way interaction between mispronunciation type, condition, language family, and age $\beta$`r full_estimate(sum_eff2_lang_age)`.
+The model results revealed that mispronunciation sensitivity for consonants was similar for Germanic and Romance languages.
+Mispronunciation sensitivity for vowels, however, was greater for Germanic compared to Romance languages (Table 2).
+We plot this relationship in Figure \@ref(fig:PlotCVEffectLang)a.
+Adding age as a moderator revealed a small but significant estimate for the four-way interaction between mispronunciation type, condition, language family, and age.
 As can also be seen in Figure \@ref(fig:PlotCVEffectLang)b, for infants learning Germanic languages, sensitivity to consonant and vowel mispronunciations did not change with age.
 In contrast, infants learning Romance languages show a decrease in sensitivity to consonant mispronunciations, but an increase in sensitivity to vowel mispronunciations with age.
-
-We were unable to use Fisher's exact test to evaluate whether infants of different ages were more or less likely to be tested on consonant or vowel mispronunciations depending on their native language.
-This was due to the small sample size of infants learning Romance languages (*n* = `r with(family, count[lang_family == "Romance"])`).
+Due to the small sample size of infants learning Romance languages, we were unable to use Fisher's exact test.
 
@@
 
-We next examined the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in response to mispronunciations when the target-distractor pairs either had no overlap or shared the same onset phoneme.
-We did not include data for which the overlap included both the onset and medial phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset/medial"])`), coda phonemes (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "coda"])`), or for targets paired with an unfamiliar distractor image (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "novel"])`).
-The analysis was therefore based on a subset of the overall dataset, comparing `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset"])` records containing onset phoneme overlap between the target and distractor with `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "no"])` containing no overlap between target and distractor.
+We next examined the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in response to mispronunciations when the target-distractor pairs either had no overlap (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "no"])`) or shared the same onset phoneme (*n* = `r with(dist_overlap_info, n_exp_conditions[distractor_overlap == "onset"])`).
+We did not include data for which the overlap included other phonemes (i.e.
+onset and medial, coda) or the distractor was an unfamiliar object.
 
@@
 fish.test <- fisher.test(dist_overlap_ages, workspace=2e8)
+
+```
+
+```{r D_overlap_mod_table, results = "hide"}
+
+mod <- "Distractor Overlap"
+
+mod.t <- mod_test(rma_DistractorOverlapMS)
+inter <- "Condition"
+E_Hg <- as.character(r2(sum_eff2[1]))
+E_SE <- as.character(r2(sum_eff2[2]))
+E_CI <- paste0("[", as.character(r2(sum_eff2[5])), ", ", as.character(r2(sum_eff2[6])), "]")
+E_p <- as.character(psig(sum_eff2[4]))
+
+lin <- cbind(mod, mod.t, inter, E_Hg, E_SE, E_CI, E_p)
+
+mod.t <- mod_test(rma_DistractorOverlap_age_MS)
+inter <- "Condition * Age"
+E_Hg <- as.character(r2(sum_eff_age[1]))
+E_SE <- as.character(r2(sum_eff_age[2]))
+E_CI <- paste0("[", as.character(r2(sum_eff_age[5])), ", ", as.character(r2(sum_eff_age[6])), "]")
+E_p <- as.character(psig(sum_eff_age[4]))
+
+lin2 <- cbind(mod, mod.t, inter, E_Hg, E_SE, E_CI, E_p)
+
+mod_table <- rbind(mod_table, lin, lin2)
 
@@
 
-When target-distractor overlap was included as a moderator, the moderator test was significant, `r mod_test(rma_DistractorOverlapMS)`.
-The estimate for the interaction between condition and distractor overlap was small, but significant ($\beta$ `r full_estimate(sum_eff2)`, suggesting that mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap.
-This relationship be seen in Figure \@ref(fig:PlotDistOverlap)a.
-
-When age was added as a moderator, the moderator test was significant, `r mod_test(rma_DistractorOverlap_age_MS)` and the estimate for the three-way interaction between age, condition, and distractor overlap was significant, but relatively small ($\beta$ `r full_estimate(sum_eff_age)`.
-As can be seen in Figure \@ref(fig:PlotDistOverlap)b, mispronunciation sensitivity increases with age for target-distractor pairs containing onset overlap, but decreases with age for target-distractor pairs containing no overlap.
-
+The model results revealed that mispronunciation sensitivity was greater when target-distractor pairs shared the same onset phoneme compared to when they shared no phonological overlap (Table 2).
+We plot this relationship in Figure \@ref(fig:PlotDistOverlap)a.
+Adding age as a moderator revealed a small but significant estimate for the three-way interaction between age, condition, and distractor overlap (Figure \@ref(fig:PlotCVEffectLang)b).
+Mispronunciation sensitivity increased with age for target-distractor pairs containing onset overlap, but decreased with age for target-distractor pairs containing no overlap.
 The results of Fisher's exact test were significant, *p* `r psig(fish.test$p.value)`.
-Older infants were more likely to be tested in experimental conditions where target and distractor images overlapped on their onset phoneme, while younger infants were more likely to be tested with target and distractor images that did not control for overlap.
-A distractor image that overlaps in the onset phoneme with the target image is considered a more challenging task to the infant, as infants must pay attention to the mispronounced phoneme and can not use the differing onsets between target and distractor images to differentiate [@Fernald2001a].
-It therefore appears that older infants were given a more challenging task than younger infants.
-We return to this issue in the General Discussion.
+Older infants were more likely to be tested in experimental conditions where target and distractor images overlapped on their onset phoneme, while younger infants were more likely to be tested in experimental conditions that did not control for overlap.
 
@@
 
-We next calculated the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in experiments were the target image was paired with a familiar or unfamiliar distractor image.
-A familiar distractor was used in `r with(distr_info, n_exp_conditions[object_pair == "familiar_familiar"])` records and a unfamiliar distractor in `r with(distr_info, n_exp_conditions[object_pair == "familiar_novel"])` records.
+We next calculated the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in experiments were the target image was paired with a familiar (*n* = `r with(distr_info, n_exp_conditions[object_pair == "familiar_familiar"])`) or unfamiliar (*n* = `r with(distr_info, n_exp_conditions[object_pair == "familiar_novel"])`) distractor image.
 
@@
 
-When distractor familiarity was included as a moderator, the moderator test was significant, `r mod_test(rma_NFeatures)`, but the effect of distractor familiarity ($\beta$`r full_estimate(d_fam)`) as well as the interaction between distractor familiarity and condition ($\beta$`r full_estimate(d_fam_condit)`) were not significant.
-The results suggest that overall, infants' familiarity with the distractor object (familiar or unfamiliar) did not impact their mispronunciation sensitivity.
-
-When age was added as a moderator, the moderator test was significant `r mod_test(rma_Distractor_age)`.
-The estimate for the  three-way-interaction between condition, distractor familiarity, and age was small and not significant ($\beta$ = `r full_estimate(sum_eff_age)`.
-These results suggest that regardless of age, mispronunciation sensitivity was similar whether the distractor image was familiar or unfamiliar.
-
+```{r D_fam_mod_table, results = "hide"}
+
+mod <- "Distractor Familiarity"
+
+mod.t <- mod_test(rma_Distractor)
+inter <- "Condition"
+E_Hg <- as.character(r2(d_fam_condit[1]))
+E_SE <- as.character(r2(d_fam_condit[2]))
+E_CI <- paste0("[", as.character(r2(d_fam_condit[5])), ", ", as.character(r2(d_fam_condit[6])), "]")
+E_p <- as.character(psig(d_fam_condit[4]))
+
+lin <- cbind(mod, mod.t, inter, E_Hg, E_SE, E_CI, E_p)
+
+mod.t <- mod_test(rma_Distractor_age)
+inter <- "Condition * Age"
+E_Hg <- as.character(r2(sum_eff_age[1]))
+E_SE <- as.character(r2(sum_eff_age[2]))
+E_CI <- paste0("[", as.character(r2(sum_eff_age[5])), ", ", as.character(r2(sum_eff_age[6])), "]")
+E_p <- as.character(psig(sum_eff_age[4]))
+
+lin2 <- cbind(mod, mod.t, inter, E_Hg, E_SE, E_CI, E_p)
+
+mod_table <- rbind(mod_table, lin, lin2)
+
+```
+
+```{r mod_table_finalize, results = "asis"}
+
+apa_table(mod_table, col.names = c("Moderator", "Moderator Test", "Interaction Terms", "Hedges' *g*", "SE", "95 CI", "*p*-value"), caption = "Summary of moderator tests and effect estimates.", landscape = TRUE, font_size = "scriptsize")
+
+```
+
+The model results revealed that infants' familiarity with the distractor object (familiar or unfamiliar) did not impact their mispronunciation sensitivity, nor was this relationship influenced by the age of the infant.
 The results of Fisher's exact test were not significant, *p* `r psig(fish.test$p.value)`.
-This lack of a relationship suggests that older and younger infants were not tested in experimental conditions that differentially employ distractor images that are familiar or unfamiliar.
 
@@
 This includes both the length of time before the target object is named (pre-naming phase) as well as after (post-naming phase) and is determined prior to data collection.
-The post-naming phase represents the amount of time the infant viewed the target-distractor image pairs after auditory presentation of the target word, and the post-naming analysis window represents how much of this phase was included in the statistical analysis.
-Unlike the post-naming phase, however, the post-naming analysis window can be chosen after the experimental data is collected.
 Evidence suggests that the speed of word recognition processing is slower in young infants [@Fernald1998], which may lead researchers to include longer post-naming phases in their experiments with younger infants.
 If this is the case, we expect a negative correlation between post-naming phase length and infant age.
-
-Across papers, the length of the post-naming phase varied from `r with(post_length_info, min(post_nam_actual))*1000` to `r with(post_length_info, max(post_nam_actual))*1000` ms, with a median value of `r with(dat, median(post_nam_actual))*1000` ms.
-The most popular post-naming phase length was `r with(dat, getmode(post_nam_actual))*1000` ms, used in `r with(post_length_info, n_exp_conditions[post_nam_actual == getmode(post_length_info$n_exp_conditions)])` records.
-Regarding the post-naming analysis window, about half of the records were analyzed using the whole post-naming phase presented to the infant (*n* = `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`), while the other half were analyzed using a shorter portion of the post-naming time window, usually excluding later portions (*n* = `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`).
-Across papers, the length of the post-naming analysis window varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a median value of `r with(dat, median(post_nam_dur))*1000` ms.
-The most popular post-naming analysis window length was `r with(dat, getmode(post_nam_dur))*1000` ms, used in `r with(post_name_info, n_exp_conditions[post_nam_dur == with(dat, getmode(post_nam_dur))])` records.
+The post-naming analysis window, in contrast, represents how much of this phase was included in the statistical analysis and can be chosen after the experimental data is collected and perhaps observed.
+If this is the case, we expect a negative correlation between post-naming analysis window and infant age.
+
+Across papers, there was wide variation in the length of the post-naming phase (*Median* = `r with(dat, median(post_nam_actual))*1000` ms, range = `r with(post_length_info, min(post_nam_actual))*1000` - `r with(post_length_info, max(post_nam_actual))*1000`) and the post-naming analysis window (*Median* = `r with(dat, median(post_nam_dur))*1000` ms, range = `r with(post_name_info, min(post_nam_dur))*1000` - `r with(post_name_info, max(post_nam_dur))*1000`).
+The most popular post-naming phase length was `r with(dat, getmode(post_nam_actual))*1000` ms (*n* = `r with(post_length_info, n_exp_conditions[post_nam_actual == getmode(post_length_info$n_exp_conditions)])` records) and `r with(dat, getmode(post_nam_dur))*1000` ms (*n* = `r with(post_name_info, n_exp_conditions[post_nam_dur == with(dat, getmode(post_nam_dur))])` records) was the most popular for the post-naming analysis window.
+About half of the records were analyzed using the whole post-naming phase presented to the infant (*n* = `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`), while the other half were analyzed using a shorter portion of the post-naming time window, usually excluding later portions (*n* = `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`).
 
 There was no apparent relation between infant age and post-naming phase length (*r* = `r trial.l$estimate`, 95% CI[`r trial.l$conf.int[1]`, `r trial.l$conf.int[2]`], *p* `r psig(trial.l$p.value)`), but there was a significant negative relationship between infant age and post-naming analysis window length, such that younger infants' looking times were analyzed using a longer post-naming analysis window (*r* = `r post.l$estimate`, 95% CI[`r post.l$conf.int[1]`, `r post.l$conf.int[2]`], *p* `r psig(post.l$p.value)`).
-Although we observe no relationship between age and post-naming phase length, a value that is determine before data collection, we do observe a relationship with post-naming analysis window length, a value that may be determined after data collection and can even be driven by observation of the data itself.
-In other words, we observe variation in time-related analysis decisions related to infants' age.
-
-Another potential source of variation considers the amount of time it takes for an eye movement to be initiated in response to a visual stimulus, which we refer to as offset time (time between the onset of the target word and the offset of the post-naming analysis window).
-Previous studies examining simple stimulus response latencies first determined that infants require at least 233 ms to initiate an eye-movement in response to a stimulus [@Canfield1991].
-In the first infant mispronunciation sensitivity study, @Swingley2000 used an offset time of 367 ms, which was "an 'educated guess' based on studies...
-showing that target and distractor fixations tend to diverge at around 400 ms." [@Swingley2000, p.
-155].
-Upon inspecting the offset time values used in the papers in our meta-analysis, the majority used a similar offset time value (between 360 and 370 ms) for analysis (*n* = `r with(offset_bin_info, n_exp_conditions[offset_bin == "367"])`), but offset values ranged from `r with(offset_bin_info, min(offset_bin))` to `r with(offset_bin_info, max(offset_bin))` ms, and were not reported for `r with(offset_info, n_exp_conditions[is.na(offset)])` records.
-We note that @Swingley2009 also included offset values of 1133 ms to analyze responses to coda mispronunciations.
-There was an inverse relationship between infant age and size of offset, such that younger infants were given longer offsets, although this correlation was not significant (*r* = `r offset.l$estimate`, 95% CI[`r offset.l$conf.int[1]`, `r offset.l$conf.int[2]`], *p* `r psig(offset.l$p.value)`).
-This lack of a relationship is possibly driven by the field's consensus that an offset of about 367 ms is appropriate for analyzing word recognition in infants, including studies that evaluate mispronunciation sensitivity.
-
-#### Post-naming analysis window length
+Considering the post-naming analysis window may be determined after data collection and observation, we next investigated whether this impacted measures of mispronunciation sensitivity.
 
@@
 The lines plot the linear regression and the gray shaded area indicates the standard error.", results="hide"}
-
 dat$condition_label <- ifelse(dat$condition==1, "Correct", "Mispronunciation")
-
 dat$post_size <- ifelse(dat$post_nam_dur <= 2, "2000 ms or less",
                        ifelse(dat$post_nam_dur > 2 & dat$post_nam_dur <= 3, "2001-3000 ms", "3001 ms or greater"))
-
 dat$post_size <- factor(dat$post_size, levels = c("2000 ms or less", "2001-3000 ms", "3001 ms or greater"))
-
 dat.cm <- dat[,c("short_cite", "is_correct", "is_mp", "post_size", "condition", "g_calc", "weights_g", "mean_age_1", "n_1")]
-
 dat.c <- subset(dat.cm, is_correct == 1)
 dat.m <- subset(dat.cm, is_mp == 1)
-
 dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "post_size", "mean_age_1", "n_1"))
-
 dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
 dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2
-
 p.MS <- ggplot(dat.cm, aes(post_size, Misp_sensitivity, fill = post_size)) + 
@@
   ylab("Misp. Sensitivity")
-
 p.AGE <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = post_size)) + 
@@
   ylab("Misp. Sensitivity")
-
 lay <- rbind(c(1), c(2))
 #lay <- rbind(c(1,2))
-
   jpeg(filename = "figures/Figure_10_Post_name_size.jpg", 
@@
                              layout_matrix = lay)
-
 dev.off()
-
 grid.draw(ger.plot.age)
@@
 
-We first assessed whether post-naming analysis window length had an impact on the overall size of the reported mispronunciation sensitivity.
-We considered data from both conditions in a joint analysis and included condition (correct pronunciation, mispronunciation) as an additional moderator.
-The moderator test was significant (`r mod_test(rma_post_dur_MS)`).
-The estimate for the interaction between post-naming analysis window and condition was small but significant ($\beta$`r full_estimate(rma_post_dur_MS_eff)`).
+When post-naming analysis window length and condition (correct pronunciation, mispronunciation) were included as moderators, the moderator test was significant (`r mod_test(rma_post_dur_MS)`).
+The estimate for the interaction between post-naming analysis window and condition was small but significant ($\beta$`r full_estimate(rma_post_dur_MS_eff)`), showing that as the length of the post-naming analysis window increased, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) decreased.
 This relationship is plotted in Figure \@ref(fig:PlotPostNameCondAge)a.
-These results show that as the length of the post-naming analysis window increased, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) decreased.
-
-Considering that we found a significant relationship between the post-naming analysis window length and infant age, such that younger ages had a longer window of analysis, we next examined whether post-naming analysis window length modulated the estimated size of mispronunciation sensitivity as infant age changed.
-When age was included as a moderator, the moderator test was significant (`r mod_test(rma_post_dur_AGE_MS)`).
+When age was added as a moderator, the moderator test was significant (`r mod_test(rma_post_dur_AGE_MS)`).
 The estimate for the  three-way-interaction between condition, post-naming analysis window, and age was small, but significant ($\beta$ `r full_estimate(rma_post_dur_AGE_MS_eff)`).
@@
 If the post-naming analysis window is greater than 2000 ms, however, there is no or a negative relation between mispronunciation sensitivity and age.
-In other words, all three possible developmental trajectories might be supported depending on analysis choices made regarding post-naming analysis window length.
-These results suggest that conclusions about the relationship between infant age and mispronunciation sensitivity may be mediated by the size of the post-naming analysis window.
 
@@
 
+```{r time_onset}
+
+# Upon inspecting the offset time values used in the papers in our meta-analysis, the majority used a similar offset time value (between 360 and 370 ms) for analysis (*n* = `r with(offset_bin_info, n_exp_conditions[offset_bin == "367"])`), but offset values ranged from `r with(offset_bin_info, min(offset_bin))` to `r with(offset_bin_info, max(offset_bin))` ms, and were not reported for `r with(offset_info, n_exp_conditions[is.na(offset)])` records.
+We note that @Swingley2009 also included offset values of 1133 ms to analyze responses to coda mispronunciations.
+There was an inverse relationship between infant age and size of offset, such that younger infants were given longer offsets, although this correlation was not significant (*r* = `r offset.l$estimate`, 95% CI[`r offset.l$conf.int[1]`, `r offset.l$conf.int[2]`], *p* `r psig(offset.l$p.value)`).
+This lack of a relationship is possibly driven by the field's consensus that an offset of about 367 ms is appropriate for analyzing word recognition in infants, including studies that evaluate mispronunciation sensitivity.
+
 #### Offset time after target naming
-
-```{r time_onset}
-
-rma_offset <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset), data = db_ET_MP, random = ~same_infant_calc | short_cite)
-
-rma_offset_eff <- coef(summary(rma_offset))[2,]
-
- rma_offset_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*condition, data = dat, random = ~same_infant_calc | short_cite)
-
-  rma_offset_MS_eff <- coef(summary(rma_offset_MS))[4,]
-
-  # age
-
- rma_offset_AGE <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*age.C, data = db_ET_MP, random = ~same_infant_calc | short_cite)
-
-   rma_offset_AGE_eff <- coef(summary(rma_offset_AGE))[4,]
-
-  rma_offset_AGE_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*age.C*condition, data = dat, random = ~same_infant_calc | short_cite)
-
-    rma_offset_AGE_MS_eff <- coef(summary(rma_offset_AGE_MS))[8,]
-
-```
-
-We next assessed whether offset time had an impact on the size of the reported mispronunciation sensitivity.
+# 
+# rma_offset <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset), data = db_ET_MP, random = ~same_infant_calc | short_cite)
+# 
+# rma_offset_eff <- coef(summary(rma_offset))[2,]
+# 
+# 
+#  rma_offset_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*condition, data = dat, random = ~same_infant_calc | short_cite)
+# 
+#   rma_offset_MS_eff <- coef(summary(rma_offset_MS))[4,]
+# 
+#   # age
+#  
+#  rma_offset_AGE <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*age.C, data = db_ET_MP, random = ~same_infant_calc | short_cite)
+# 
+#    rma_offset_AGE_eff <- coef(summary(rma_offset_AGE))[4,]
+# 
+#  
+#   rma_offset_AGE_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*age.C*condition, data = dat, random = ~same_infant_calc | short_cite)
+# 
+#     rma_offset_AGE_MS_eff <- coef(summary(rma_offset_AGE_MS))[8,]
+#     
+#     We next assessed whether offset time had an impact on the size of the reported mispronunciation sensitivity.
 When we included both condition and offset time as moderators, the moderator test was significant (`r mod_test(rma_post_dur_MS)`), but the estimate for the interaction between offset time and condition was zero ($\beta$`r full_estimate(rma_offset_MS_eff)`).
@@
 
+```
+
 ## Dependent variable
 
-```{r dv_info}
-
-dv_info <- dat %>%
-  group_by(within_measure) %>%
-  summarize(n_exp_conditions =  n())
-
-dv.l <- summary(lm(age.C ~ within_measure, data = dat))
-
-dv.age.plot <- ggplot(dat, aes(within_measure, age.C)) +     geom_violin() + 
-  geom_jitter(height = 0, width = 0.1, alpha = 0.5)
-
-```
-
-Mispronunciation sensitivity experiments, as mentioned previously, typically include a phase where a naming event has not yet occurred (pre-naming phase).
-This is followed by a naming event, whether correctly pronounced or mispronounced, and the subsequent phase (post-naming phase).
-The purpose of the pre-naming phase is to ensure that infants do not have systematic preferences for the target or distractor (greater interest in a cat compared to a cup) which may add variance to PTL scores in the post-naming phase.
-As described in the Methods section, however, there was considerable variation across papers in whether this pre-naming phase was used as a baseline measurement, or whether a different baseline measurement was used.
-This resulted in different measured outcomes or dependent variables.
-Over half of the records (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post_naming_effect"])`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase, resulting in a Difference Score.
-The Difference Score is one value, which is then compared with a chance value of 0.
-In contrast, Pre vs.
-Post (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` records), directly compare the post- and pre-naming PTL scores with one another using a statistical test (e.g.
-t-test, ANOVA).
-This requires two values, one for the pre-naming phase and one for the post-naming phase.
+As described in the Methods section, there was considerable variation across papers in whether the pre-naming phase was used as a baseline measurement and subtracted from the PTL score from the post-naming phase and compared with a chance value of 0 (Difference Score) or directly compared with the post-naming phase (Pre- vs.
+Post) or whether the post-naming PTL was compared with a chance value of 50% (Post).
 A positive Difference Score or a greater Pre- vs.
 Post-naming phase PTL indicates that infants increased their target looks after hearing the naming label.
-The remaining records used a Post dependent variable (*n* = `r with(dv_info, n_exp_conditions[within_measure == "post"])` records), which compares the post-naming PTL score with a chance value of 50%.
-Here, the infants' pre-naming phase baseline preferences are not considered and instead target fixations are evaluated based on the likelihood to fixate one of two pictures (50%).
+A Post PTL greater than 50% assumes recognition of the target image.
 As most papers do not specify whether any of these calculations are made before or after aggregating across trials and/or participants, we make no assumptions about how any aggregate scores or differences were computed.
 
-The Difference Score and Pre vs.
-Post can be considered similar to one another, in that they are calculated on the same type of data and consider pre-naming preferences.
-The Post dependent variable, in contrast, does not consider pre-naming baseline preferences.
-To our knowledge, there is no theory or evidence that explicitly drives choice of dependent variable in analysis of preferential looking studies, which may explain the wide variation in dependent variable reported in the papers included in this meta-analysis.
+To our knowledge, there is no theory or evidence that explicitly drives choice of dependent variable in preferential looking studies, which may explain the wide variation in dependent variable reported in the papers included in this meta-analysis.
 We next explored whether the type of dependent variable calculated influenced the estimated size of sensitivity to mispronunciations.
-Considering that the dependent variable Post differs in its consideration of pre-naming baseline preferences, substituting these for a chance value, we directly compared mispronunciation sensitivity between Post as a reference condition and both Difference Score and Pre vs.
-Post dependent variables.
+Considering that the dependent variable Post differs in its consideration of pre-naming baseline preferences, we coded this as a reference condition.
 
@@
 This relationship is plotted in Figure \@ref(fig:PlotWithinCondAgeDiffScore)a.
-The results suggest that the reported dependent variable significantly impacted the size of the estimated mispronunciation sensitivity effect, such that studies reporting the Post.
-vs.
-Pre dependent variable showed a smaller mispronunciation sensitivity effect than those reporting Post, but that there was no difference between the Difference Score and Post dependent variables.
 
@@
 
-Similar to post-naming analysis window length, all three possible developmental trajectories might be supported depending on the dependent variable reported.
-In other words, choice of dependent variable may influence the conclusion drawn regarding how mispronunciation sensitivity may change with infant age.
-We address this issue in the General Discussion.
-
 (Insert Figure \@ref(fig:PlotWithinCondAgeDiffScore) about here)
@@
 The lines plot the linear regression and the gray shaded area indicates the standard error.", results="hide"}
-
 dat.cm <- dat[,c("short_cite", "is_correct", "is_mp", "within_measure", "condition", "g_calc", "weights_g", "mean_age_1", "n_1")]
-
 dat.c <- subset(dat.cm, is_correct == 1)
 dat.m <- subset(dat.cm, is_mp == 1)
-
 dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "within_measure", "mean_age_1", "n_1"))
-
 dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
-
 dat.cm$condition_label <- ifelse(dat.cm$is_correct.x==1, "Correct", "Mispronunciation")
-
 dat.cm$dv_label <- ifelse(dat.cm$within_measure=="post", "Post",
@@
                               "Difference Score"))
-
 dat.cm$dv_label <- factor(dat.cm$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
-
 ms.agg <- ggplot(dat.cm, aes(dv_label, Misp_sensitivity, fill = dv_label)) + 
@@
   ylab("Misp. Sensitivity")
-
 ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = dv_label)) + 
@@
   ylab("Misp. Sensitivity")
-
 lay <- rbind(c(1), c(2))
 #lay <- rbind(c(1,2))
-
   jpeg(filename = "figures/Figure_11_Dependent_variable.jpg", 
@@
 ```
-
-# General Discussion
-
-In this meta-analysis, we set out to quantify and assess the phonological specificity of infants' representations for familiar words and how this is modulated with development, as measured by infant age and vocabulary size.
-Overall, the results of the meta-analysis showed that infants reliably fixate the target object when hearing both correctly pronounced and mispronounced labels.
-Infants not only recognize object labels when they were correctly pronounced, but are also likely to accept mispronunciations as labels for targets, in the presence of a distractor image.
-Nonetheless, there was a considerable difference in target fixations in response to correctly pronounced and mispronounced labels, suggesting that infants show an overall mispronunciation sensitivity based on the current experimental literature.
-In other words, infants show sensitivity to what constitutes unacceptable, possibly meaning-altering variation in word forms, thereby displaying knowledge of the role of phonemic changes throughout the ages assessed here (6 to 30 months).
-At the same time, infants, like adults, can recover from mispronunciations, a key skill in language processing, as speech errors resulting in mispronunciations are very common in spoken language.
-
-Considering the variation in findings of developmental change in mispronunciation sensitivity (see Introduction), we next evaluated the developmental trajectory of infants' mispronunciation sensitivity, envisioning three possible developmental patterns: increasing, decreasing, and unchanging sensitivity.
-Our analysis of this relationship revealed a pattern of unchanging sensitivity over infant age, which has been reported by a handful of studies directly comparing infants over a small range of ages, such as 18-24 months [@Swingley2000; @Bailey2002] or 12-17 months [@Zesiger2012].
-
-In accounts predicting gradual specification of phonological representations, vocabulary growth is thought to invoke changes in mispronunciation sensitivity.
-The need for phonologically well-specified word representations increases as children learn more words and must differentiate between them [@CharlesLuce1995].
-An examination of the influence of vocabulary size revealed no relationship between object recognition in response to mispronunciations and group-level vocabulary.
-However, only fewer than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total; see also Figure \@ref(fig:Vocabdescribe1)).
-We thus cannot draw strong conclusions about the role of vocabulary, despite their key role in theoretical models of phono-lexical development during early language acquisition.
-There are more mispronunciation sensitivity studies published every year, perhaps due to the increased use of eye-trackers, which reduce the need for offline coding and thus make data collection much more efficient, but this has not translated to an increasing number of mispronunciation sensitivity studies also reporting vocabulary scores.
-We suggest that this may be the result of publication bias favoring significant effects or an overall hesitation to invest in data collection that is not expected to yield significant outcomes.
-However, it is important to note that given the small sample sizes, only large correlations are expected to become significant.
-Meta-analysis can, on the other hand, reveal smaller significant correlations.
-We thus do not know whether there is indeed no relationship between vocabulary and infants’ responses in mispronunciation studies and more experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size is needed if this link is to be evaluated.
 
@@
 
-What do our results regarding mispronunciation sensitivity, and its (lack of a) relationship with age and vocabulary size, mean for theories of language development?
-Evidence that infants accept a mispronunciation (object identification) while simultaneously holding correctly pronounced and mispronounced labels as separate (mispronunciation sensitivity) may indicate an abstract understanding of words' phonological structure being in place early on.
-It appears that young infants may understand that the phonological form of mispronunciations and correct pronunciations do not match, but that the mispronunciation is a better label for the target compared to the distractor image.
+# General Discussion
+
+In this meta-analysis, we set out to quantify and assess the phonological specificity of infants' representations for familiar words and how this is modulated with development, as measured by infant age and vocabulary size.
+Infants not only recognize object labels when they were correctly pronounced, but are also likely to accept mispronunciations as labels for targets.
+Nonetheless, there was a considerable difference in target fixations in response to correctly pronounced and mispronounced labels, suggesting that infants show sensitivity to what constitutes unacceptable, possibly meaning-altering variation in word forms, thereby displaying knowledge of the role of phonemic changes throughout the ages assessed here (6 to 30 months).
+At the same time, infants, like adults, can recover from mispronunciations, a key skill in language processing.
+
+Considering the variation in findings of developmental change in mispronunciation sensitivity (see Introduction), we next evaluated the developmental trajectory of infants' mispronunciation sensitivity.
+Our analysis of this relationship revealed a pattern of unchanging sensitivity over infant age and vocabulary size, which has been reported by a handful of studies directly comparing infants over a small range of ages, such as 18-24 months [@Swingley2000; @Bailey2002] or 12-17 months [@Zesiger2012].
 The lack of age or vocabulary effects in our meta-analysis (carefully) suggest that this understanding is present from an early age and is maintained throughout early lexical development.
-If we were to take our results as robust, it becomes thus a pressing open question that theories have to answer which other factors might prompt acquiring and using language-specific phonological contrasts.
+We note, however, that despite an increasing publication record of mispronunciation sensitivity studies, fewer than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total; see also Figure \@ref(fig:Vocabdescribe1)).
+We suggest that this may be the result of publication bias favoring significant effects or an overall hesitation to invest in data collection that is not expected to yield significant outcomes.
+Considering the theoretical implications, more experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size is needed if this link is to be evaluated.
+Nonetheless, if we are to take our results as robust, it becomes thus a pressing open question that theories have to answer which other factors might prompt acquiring and using language-specific phonological contrasts at such an early age.
 
@@
 The results of the moderator analysis reflect several findings reported in the literature.
-Although words differ from one another on many acoustic dimensions, changes in phonemes, as measured by phonological features, signal changes in meaning.
-Several studies have found that infants show graded sensitivity to mispronunciations that differ in 1-, 2-, and 3-features from the correct pronunciation [@Bernier2017; @Tamasi2016; @White2008; @Mani2011], an adult-like ability.
-This was also captured in our meta-analysis, which showed that for each increase in number of phonological features changed, the effect size estimate for looks to the target decreases by `r r2(linear_feature)`.
-Yet, this graded sensitivity appears to be stable across infant ages, although our analysis was likely underpowered.
-At least one study suggests that this graded sensitivity develops with age, but this was the only study to examine more than one age [@Mani2011].
-All other studies only test one age [@Bernier2017; @Tamasi2016; @White2008].
+The meta-analytic effect for ispronunciation size, as measured by phonological features changed, showed graded sensitivity [@Bernier2017; @Tamasi2016; @White2008; @Mani2011], an adult-like ability.
+More studies are needed to evaluate whether this gradual sensitivity develops with age, as only one study examined more than one age [@Mani2011] and all others test the same age [@Bernier2017; @Tamasi2016; @White2008].
 With more studies investigating graded sensitivity at multiple ages in infancy, we would achieve a better estimate of whether this is a stable or developing ability, thus also shedding more light on the progression of phono-lexical development in general that then needs to be captured in theories and models.
 
-Although some theories place greater importance on onset position for word recognition and decreasing importance for phonemes in subsequent positions [i.e.
-COHORT; @Marslen-Wilson1989], other theories suggest that lexical access can still recover from onset and medial mispronunciations [i.e.
-TRACE; @McClelland1986].
-Although many studies have examined mispronunciations on multiple positions, the handful of studies that have directly compared sensitivity between different positions find that position of the mispronunciation does not modulate sensitivity [@Swingley2009; @Zesiger2012].
-This stands in contrast to the findings of our meta-analysis, which showed that for each subsequent position in the word that is changed, from onset to medial and medial to coda, the effect size estimate for looks to the target decreases by `r r2(linear_position)`; infants are more sensitive to changes in the sounds of familiar words when they occur in an earlier position as opposed to a late position.
+Our meta-analysis showed that infants are more sensitive to changes in the sounds of familiar words when they occur in an earlier position as opposed to a late position.
+This awards support to lexical access theories that place greater importance on the onset position during word recognition [i.e.
+COHORT; @Marslen-Wilson1989].
 At face value, our results thus support theories placing more importance on earlier phonemes.
-
-One potential explanation for the discrepancy between the results of individual studies and that of the current meta-analysis is the difference in how the timing of different mispronunciation locations are considered in analysis.
-For example, @Swingley2009 adjusted the offset time from 367 ms for onset mispronunciations to 1133 for coda mispronunciations, to ensure that infants have a similar amount of time to respond to the mispronunciation, regardless of position.
-In contrast, if an experiment compares different kinds of medial mispronunciations, as in @Mani2011, it is not necessary to adjust offset time because the mispronunciations have a similar onset time.
-The length of the post-naming analysis window does impact mispronunciation sensitivity, as we discuss below, and by comparing effect sizes for different mispronunciation positions where position timing was not considered, mispronunciations that occur later in the word (i.e.
-medial and coda mispronunciations) may be at a disadvantage relative to onset mispronunciations.
+But studies that have contrasted mispronunciations on different positions have found this does not modulate sensitivity [@Swingley2009; @Zesiger2012].
+One potential explanation is how the timing of different mispronunciation locations are considered in analysis.
+For example, @Swingley2009 adjusted the post-naming analysis window start from 367 ms for onset mispronunciations to 1133 for coda mispronunciations, to ensure that infants have a similar amount of time to respond to the mispronunciation, regardless of position.
+The length of the post-naming analysis window does impact mispronunciation sensitivity, as we discuss below, and mispronunciations that occur later in the word (i.e.
+medial and coda mispronunciations) may be at a disadvantage relative to onset mispronunciations if this is not taken into account.
 These issues can be addressed with the addition of more experiments that directly compare sensitivity to mispronunciations of different positions, as well as the use of analyses that account for timing differences.
@@
 For several moderators, we found no evidence of modulation of mispronunciation sensitivity.
-For example, sensitivity to mispronunciations was similar for experimental conditions that included either a familiar or an unfamiliar distrator image.
 Studies that include an unfamiliar, as opposed to familiar distractor image, often argue that the unfamiliar image provides a better referent candidate for mispronunciation than a familiar distractor image, where the name is already known.
-No studies have directly compared mispronunciation sensitivity for familiar and unfamiliar distractors, but these results suggest that this manipulation alone makes little difference in the design of the experiment.
-It remains possible that distractor familiarity interacts with other types of manipulations, such as number of phonological features changed [e.g.
-@White2008], but our meta-analysis is underpowered to detect such effects.
+Yet, no studies have directly examined this assertion and our meta-analysis found that distractor familiarity did not modulate mispronunciation sensitivity.
 
 Despite the proposal that infants should be more sensitive to consonant compared to vowel mispronunciations [@Nazzi2016], we found no difference in sensitivity to consonant and vowel mispronunciations.
-But, a more nuanced picture was revealed regarding differences between consonant and vowel mispronunciations when further moderators were introduced.
-Sensitivity to consonant mispronunciations did not change with age and were similar for infants learning Germanic and Romance languages.
-In contrast, sensitivity to vowel mispronunciations increased with age and was greater overall for infants learning Germanic languages, although sensitivity to vowel mispronunciations did increase with age for infants learning Romance languages as well.
-These results show that sensitivity to vowel mispronunciations is modulated both by development and by native language, whereas sensitivity to consonant mispronunciations is fairly similar across age and native language.
-This pattern of results supports previous experimental evidence and a learned account of the so-called consonant bias that sensitivity to consonants and vowels have a different developmental trajectory and that this difference also depends on whether the infant is learning a Romance (French, Italian) or Germanic (British English, Danish) native language [@Nazzi2016].
+But, a more nuanced picture was revealed when further moderators were introduced.
+Age and native language did not modulate sensitivity to consonant mispronunciations, but sensitivity to vowel mispronunciations increased with age and was greater overall for infants learning Germanic languages (although this increased with age for infants learning Romance languages).
+This pattern of results supports a learned account of the consonant bias, showing that sensitivity to consonants and vowels have a different developmental trajectory, which depends on whether the infant is learning a Romance (French, Italian) or Germanic (British English, Danish) native language [@Nazzi2016].
 TRACE simulations conducted by @Mayor2014 reveal a relationship between vocabulary size and sensitivity to vowel-medial mispronunciations, although here the authors give more weight to the role of mispronunciation position, a distinction we are unable to make in our analyses.
 
-Our meta-analysis revealed that studies which include target and distractor images that overlap in their onset elicit greater mispronunciation sensitivity than studies who do not control for this factor.
-Based on reasoning in the literature, the opposite would be predicted: it should be more, not less, difficult to detect a mispronunciation (dag) when the target and distractor overlap in their onset phoneme (doggie-doll), because the infant cannot use differences in the onset sound between the target and distractor to identify the intended referent [@Swingley1999].
-Perhaps including overlap between the target and distractor lead infants to pay more attention to mispronunciations, leading to an increased effect of mispronunciation sensitivity.
-When we examined the distribution of this manipulation across infant age, however, we found an alternate explanation for this pattern of results.
-Older children were more likely to receive the arguably more difficult manipulation where target-distractor pairs overlapped in their onset phoneme.
-If older children have greater mispronunciation sensitivity in general, then this may have led to greater mispronunciation sensitivity for overlapping target-distractor pairs, instead of the manipulation itself.
-
-At the same time, our main developmental analysis found a lack of developmental change in mispronunciation sensitivity, suggesting that older children do not have greater mispronunciation sensitivity than younger children.
-If older children are given a more difficult task than younger children, however, this may dampen any developmental effects.
-It appears that this may be the case for overlap between target-distractor pairs.
-Older children were given a more difficult task (target-distractor pairs with onset overlap), which may have lowered the size of their mispronunciation sensitivity effect.
-Younger children were given an easier task (target-distractor pairs with no overlap), which may have relatively increased the size of their mispronunciation sensitivity effect.
-As a result, any developmental differences would be hidden by task differences in the experiments that older and younger infants participated in.
-This argument is supported by the PRIMIR Framework [@Curtin2011; @Curtin2007; @Werker2005], which argues that infants' ability to access the phonetic detail of familiar words is governed by the difficulty of their current task.
+Contrary to predictions made from the literature, our meta-analysis revealed that studies which include target and distractor images that overlap in their onset elicit greater mispronunciation sensitivity than studies who do not control for this factor.
+Perhaps including overlap leads infants to pay more attention to mispronunciations, increasing mispronunciation sensitivity.
+Yet, older children were more likely to recieve the arguably more difficult manipulation where target-distractor pairs overlapped in their onset phoneme, added task demands which may reduce their ability to access the phonetic detail of familiar words as argued by the PRIMIR Framework [@Curtin2007; @Werker2005].
+This imbalance has the potential to dampen developmental differences, which would be hidden by task differences in the experiments that older and younger infants participated in.
 Further support comes from evidence that sensitivity to mispronunciations when the target-distractor pair overlapped on the onset phoneme increased with age.
@@
 
-During the coding of our meta-analysis database, we noted a potential for variation in a handful of variables that relate to data analysis, specifically relating to timing (post-naming analysis window; onset time) and to the calculation of the dependent variable reported.
-We focused on these variables in particular because they can be changed after researchers have examined the data, possibly leading to an inflated number of significant results which may also explain the publication bias observed in the funnel plot asymmetry analyses [@Simmons2011].
-To further explore whether this variation contributed to the lack of developmental change observed in the overall meta-analysis, we included these variables as moderators in a set of exploratory analyses.
-We noted an interesting pattern of results, specifically that different conclusions about mispronunciation sensitivity, but more notably mispronunciation sensitivity development, could be drawn depending on the length of the post-naming analysis window as well as the type of dependent variable calculated in the experiment (see Figures \@ref(fig:PlotPostNameCondAge) and \@ref(fig:PlotWithinCondAgeDiffScore)).
-
-We first examined whether variation in analysis timing impacted mispronunciation sensitivity.
+During the coding of our meta-analysis database, we noted variation in variables relating to timing and the calculation of the dependent variable reported.
 As infants mature, they recognize words more quickly [@Fernald1998], which may lead experimenters to adjust and lower offset times in their analysis as well as shorten the length of the analysis window.
-Yet, we find no relationship between age and offset times, nor that offset time modulated mispronunciation sensitivity.
-Indeed, a majority of studies used an offset time between 360 and 370 ms, which follows the "best guess" of @Swingley2000 for the amount of time needed for infants to initiate eye movements in response to a spoken target word.
-Without knowledge of the base reaction time in a given population of infants, use of this best guess reduces the number of free parameters used by researchers.
-In contrast, we found a negative correlation between infant age and the length of the post-naming analysis window, and that increasing the length of the post-naming analysis window decreases the size of mispronunciation sensitivity.
-TRACE also predicts that looks to the target in response to mispronunciations may be slower than that of correct pronunciations [@Mayor2014], and those studies with longer post-naming analysis windows capture this effect, thereby reducing the measured sensitivity to mispronunciations.
+A majority of studies used an offset time between 360 and 370 ms (*n* = `r with(offset_bin_info, n_exp_conditions[offset_bin == "367"])`), which follows the "best guess" of @Swingley2000 for the amount of time needed for infants to initiate eye movements in response to a spoken target word; in contrast, we found wide variation in the post-naming analysis window which correlated negatively with infant age and influenced the estimate of mispronunciation sensitivity.
+TRACE predicts that looks to the target in response to mispronunciations may be slower than that of correct pronunciations [@Mayor2014], and those studies with longer post-naming analysis windows capture this effect, thereby reducing the measured sensitivity to mispronunciations.
 Although we have no direct evidence, an analysis window can be potentially set after collecting data.
@@
 
-In further analyses on analysis parameters that can be chosen post hoc, we found that the type of dependent variable calculated moderated mispronunciation sensitivity and conclusions about its developmental trajectory.
+The type of depedent variable calculated also moderated mispronunciation sensitivity and conclusions about its developmental trajectory.
 Unlike the exploratory analyses related to timing, there is no clear reason for one dependent variable to be chosen over another; the prevalence of each dependent variable appears distributed across ages and some authors always calculate the same dependent variable while others use them interchangeably in different publications.
@@
 
-A lack of a field standard can have serious consequences, as our analyses show.
-On the one hand, this limits the conclusions we can draw regarding our key research question.
-Without access to the full datasets (and ideally analysis code) of the studies included in this meta-analysis, it is difficult to pinpoint the exact role played by these experimental design and data analysis choices.
-On the other hand, this finding emphasizes that current practices of free, potentially ad hoc choices regarding data analyses are not sustainable if the field wants to move towards quantitative evidence for theories of language development.
-
-We take this opportunity to make several recommendations to address the issue of varying, potential post hoc analysis decisions.
+A lack of a field standard can have serious consequences, as our analyses show, limiting our ability to draw conclusions.
+We take this opportunity to make several recommendations to address the issue of varying, potentially post hoc analysis decisions.
 First, preregistration can serve as proof of a priori decisions regarding data analysis, which can also contain a data-dependent description of how data analysis decisions will be made once data is collected [see @Havron for a primer].
@@
 This allows for a more detailed assessment of infants' fixations over time and removes the need to reduce the post-naming analysis window.
-Both Growth Curve Analysis [@Mirman2008; @Law2015] and Permutation Clusters Analysis [@VonHolzen2012; @Maris2007; @DelleLuche2015] offer potential solutions to analyze the full time course.
+Both Growth Curve Analysis [@Mirman2008] and Permutation Clusters Analysis [@VonHolzen2012; @Maris2007] offer potential solutions to analyze the full time course.
 Third, it may be useful to establish standard analysis pipelines for mispronunciation studies.
-This would allow for a more uniform analysis of this phenomenon, as well as aid experimenters in future research planning [see @MB1 for a parallel effor for infant-directed speech preference studies].
-In general, however, a better understanding of how different levels of linguistic knowledge may drive looking behavior is needed.
-We hope the above suggestions take us one step closer to this important goal that clarified the link between internal abilities and behavior in a laboratory study.
+This would allow for a more uniform analysis of this phenomenon, as well as aid experimenters in future research planning [see @MB1 for a parallel effort].
+We hope the above suggestions take us one step closer to this important goal that clarifies the link between internal abilities and behavior in a laboratory study.
 
@@
 
-This meta-analysis comprises an aggregation of two decades of research on mispronunciation sensitivity, finding that infants accept both correct pronunciations and mispronunciations as labels for a target image.
-However, they are more likely to accept correct pronunciations, which indicates sensitivity to mispronunciations in familiar words.
-This sensitivity was not modulated by infant age or vocabulary, suggesting that from a young age on, before the vocabulary explosion, infants’ word representations may be already phonologically well-specified.
+This meta-analysis comprises an aggregation of two decades of research on mispronunciation sensitivity, finding robust evidence that infants have well-specified phonological representations for familiar words.
+Furthermore, these representations may be well specified at an early age, perhaps before the vocabulary explosion.
 We recommend future theoretical frameworks take this evidence into account.
-Our meta-analysis was also able to confirm different findings in the literature, including the role of mispronunciation size, mispronunciation position, and the role of the native language in sensitivity to mispronunciation type (consonant vs.
+Our meta-analysis was also able to confirm different findings in the literature, including the role of mispronunciation size, mispronunciation position, and the role of age and native language in sensitivity to mispronunciation type (consonant vs.
 vowel).
@@
 
-Despite this overall finding, however, we note evidence that data analysis choices can modulate conclusions about mispronunciation sensitivity development.
+Despite this overall finding, we note evidence that data analysis choices can modulate conclusions about mispronunciation sensitivity development.
 Future studies should be carefully planned with this evidence in mind.
@@
 
-*Acknowledgements*: The authors would like to thank Emelyne Gaudichau for valuable assistance in entering data.
-Author 1 was supported by the Agence Nationale de la Recherche (ANR-13-BSH2-0004) and by training grant DC-00046 from the National Institute of Deafness and Communicative Disorders of the National Institutes of Health.
-Author 2 was supported by the European Horizon 2020 programme (Marie Skłodowska-Curie grant No 660911), the Agence Nationale de la Recherche (ANR-10-IDEX-0001-02 PSL*, ANR-10-LABX-0087 IEC) and the Fondation de France.
-
-\newpage
-
 # References

### 2020-02-10 scripts/starter_functions.R

@@ -44,3 +44,42 @@ apatheme=theme_bw()+
 
 # Color Blind palette:
 cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
+get_legend<-function(myggplot){
+  tmp <- ggplot_gtable(ggplot_build(myggplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)
+}
+
+grid_arrange_shared_legend <- function(..., ncol = length(list(...)), nrow = 1, position = c("bottom", "right")) {
+  
+  plots <- list(...)
+  position <- match.arg(position)
+  g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
+  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
+  lheight <- sum(legend$height)
+  lwidth <- sum(legend$width)
+  gl <- lapply(plots, function(x) x + theme(legend.position="none"))
+  gl <- c(gl, ncol = ncol, nrow = nrow)
+  
+  combined <- switch(position,
+                     "bottom" = arrangeGrob(do.call(arrangeGrob, gl),
+                                            legend,
+                                            ncol = 1,
+                                            heights = unit.c(unit(1, "npc") - lheight, lheight)),
+                     "right" = arrangeGrob(do.call(arrangeGrob, gl),
+                                           legend,
+                                           ncol = 2,
+                                           widths = unit.c(unit(1, "npc") - lwidth, lwidth)))
+  
+  grid.newpage()
+  grid.draw(combined)
+  
+  # return gtable invisibly
+  invisible(combined)
+  
+}
+
+
+

### 2020-07-01 VonHolzenBergmann_MPMetaAnalysis.Rmd
Dev Psych start of revision (1st round)

@@
 cat-hat).
-This meta-analysis examines on the latter, focusing how infants apply the relevant phonological categories of their native language, aggregating twenty years' worth of studies using the mispronunciation sensitivity paradigm.
+This meta-analysis examines the latter, focusing how infants apply the relevant phonological categories of their native language, aggregating twenty years' worth of studies using the mispronunciation sensitivity paradigm.
 The original study of @Swingley2000 presented American-English learning 18- to 23-month-olds with pairs of images of words they were very likely to know (e.g.
@@
 "vaby") for one of the images.
-Although infants looked at the correct target image in response to both types of labels, correct labels elicited more looks to the target image than mispronounced labels.
+Although infants looked at the correct target image in response to both types of labels, correct labels elicited more looking to the target image than mispronounced labels.
 @Swingley2000 concluded that already before the second birthday, children's representations for familiar words are phonologically well specified.
@@
 The time is thus ripe to aggregate all publicly available evidence using a meta-analysis.
-In doing so, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @MB1 for a notable exception).
+In doing so, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies.
 
@@
 mama, ball, kitty; @CharlesLuce1995] and encoding representations for these words using fine phonological detail may not be necessary.
-According to PRIMIR [@Curtin2007; @Werker2005] infants's initially episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task.
+According to PRIMIR [@Curtin2007; @Werker2005] infants' initially episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task.
 This argument is supported by the results of @Mani2010kepstups, who found that 12-month-old infants with a larger vocabulary showed a greater sensitivity to vowel mispronunciations than infants with a smaller vocabulary.
@@
 Here, 18- but not 24-month-old infants showed sensitivity to more subtle mispronunciations that differed from the correct pronunciation by 1 phonological feature [@Mani2011].
-When faced with large and salient mispronunciations, sensitivity to small 1-feature mispronunciations may be obscured, especially if infants show graded sensitivity to different degrees of mispronunciations (see below), as @Mani2011 found with 24- but not 18-month-olds in their study.
+@Mani2011 argue that when faced with large and salient mispronunciations, infants' sensitivity to small 1-feature mispronunciations may be obscured.
+This would especially be the case if infants show graded sensitivity to different degrees of mispronunciations (see below), as @Mani2011 found with 24- but not 18-month-olds in their study.
 
@@
 But, this may not account for all variability found in the literature.
+Indeed, different laboratories may vary in their approach to creating a mispronunciation sensitivity experiment, using different types of stimuli and methodologies.
 Many studies pose more nuanced questions, such as examining the impact of number of phonological features changed (mispronunciation size) or the location of the mispronunciation.
 Some studies may differ in their experimental design, presenting a distractor image that is either familiar or completely novel.
-We thus include an analysis of the features of the task to shed further light on early phono-lexical representations and their maturation.
+In our meta-analysis we code for features of the experiment that are often reported but vary across studies and include an analysis of these features to shed further light on early phono-lexical representations and their maturation.
 
@@
 The ability to access and use this detail, however, is governed by the task or developmental demands probed in a particular experiment.
-In a particularly demanding task, such as when the target and distractor image share the same onset (e.g.
-doggie and doll), infants' ability to access the phonological detail of familiar words may be restricted [@Swingley1999].
+For example, if infants are tested on a more subtle mispronunciation that changes only one phonological feature, they may be less likely to identify the change in comparison to a mispronunciation that changes two or three phonological features [@White2008].
 If older infants are more likely to be tested using a more demanding mispronunciation sensitivity task, this may attenuate developmental effects across studies.
@@
 The first set of questions concern how infants' sensitivity is modulated by different kinds of mispronunciations.
-Some experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level, or *mispronunciation size* (i.e.
-1-feature, 2-features, 3-features, etc.), finding graded sensitivity to both consonant [@White2008; @Bernier2017; @Tamasi2016] and vowel [@Mani2011] feature changes.
-This also has consequences for understanding the developmental trajectory of mispronunciation sensitivity, as adults show similar graded sensitivity [@Bailey2005]
-
-The COHORT model [@Marslen-Wilson1989] describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.
+Following on the above example, some experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level, or *mispronunciation size* (i.e.
+1-feature, 2-features, 3-features), finding that infants are more sensitive to larger mispronunciations (3-feature-changes) than smaller mispronunciations (1-feature changes) for both consonant [@White2008; @Bernier2017; @Tamasi2016] and vowel [@Mani2011] mispronunciations, known as graded sensitivity.
+This also has consequences for understanding the developmental trajectory of mispronunciation sensitivity, as adults show similar graded sensitivity [@Bailey2005].
+
+The position of mispronunciation in the word may differentially interrupt the infant’s word recognition process, but the degree to which position impacts word recognition is a matter of debate.
+The COHORT model [@Marslen-Wilson1989] describes lexical access in a linear direction, with the importance of each phoneme decreasing as its position comes later in the word.
 In contrast, the TRACE model [@McClelland1986] describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.
@@
 
-A second set of questions is whether the context modulates infants' responses to mispronunciations.
+A second set of questions is whether the experimental context modulates infants' responses to mispronunciations.
 In order to study the influence of mispronunciation position, many studies control the *phonological overlap between target and distractor labels*.
-For example, when examining sensitivity to a vowel mispronunciation of the target word "doggie", the image of a dog would be paired with a distractor image that shares onset overlap, such as "doll".
-This ensures that infants can not use the onset of the word to differentiate between the target and distractor images [@Swingley1999].
+For example, when examining sensitivity to a vowel mispronunciation of the target word "ball", the image of a ball would be paired with a distractor image that shares onset overlap, such as "bed".
+This ensures that infants cannot use the onset of the word to differentiate between the target and distractor images [@Mani2007].
 Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.
@@
 
-Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement.
+Mispronunciation sensitivity studies are typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement.
 PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images.
@@
 The Difference Score is one value, which is then compared with a chance value of 0.
-In contrast, Pre vs.
-Post (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` records), directly compare the post- and pre-naming PTL scores with one another using a statistical test (e.g.
+Pre vs.
+Post (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` records) accomplishes the same analysis, directly compare the post- and pre-naming PTL scores with one another using a statistical test (e.g.
 t-test, ANOVA).
@@
 Age did not significantly modulate object identification in response to correctly pronounced (`r mod_test(rma_correct_age)`) or mispronounced words (`r mod_test(rma_MP_age)`).
-The lack of a significant modulation together with the small estimates for age (correct: $\beta$ `r full_estimate(Csum_eff)`; mispronunciation: $\beta$ `r full_estimate(Msum_eff)`) indicates that there might be no relationship between age and target looks in response to a correctly pronounced or mispronounced label.
+The lack of a significant modulation together with the small estimates for age (correct: $\beta$ `r full_estimate(Csum_eff)`; mispronunciation: $\beta$ `r full_estimate(Msum_eff)`) indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label.
+However, previous experimental studies ([e.g.
+@Fernald1998]) and a recent meta-analysis [@Frank2016] have found that children's speed and accuracy in recognition of correctly pronounced words increases with age.
+Perhaps older children are more likely to be tested on less-frequent, later learned words than younger children, which could lead to a lack of a relationship between age and target looks in response to correct pronunciations in the current meta-analysis.
 
@@
 ```{r PlotMPEffect, echo = FALSE, fig.width=7,fig.height=7, fig.cap="Panel a: Effect sizes for correct pronunciations (orange) and mispronunciations (blue) by participant age.
-Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) by participant age.
+Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) by participant age.
 For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
@@
   geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_colour_manual(values=cbPalette)+
+  scale_colour_grey()+
   xlim(6, 31) +
@@
   geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1), color = "black") +
-  scale_colour_manual(values=cbPalette)+
+  scale_colour_grey()+
   xlim(6, 31) +
@@
   geom_histogram(alpha = 0.5, bins = 20) +
-    scale_fill_manual(values=cbPalette)+
+    scale_fill_grey()+
      theme(legend.position = "bottom",
@@
 #   scale_y_continuous(breaks = c(0, 1, 2, 3, 4), limits = c(0,4))+
-#   scale_colour_manual(values=cbPalette)+
+#   scale_colour_grey()+
 #   apatheme +
@@
 To better understand the impact of these moderators on developmental change, we include age as subsequent moderator.
-Results of the moderator tests as well as the individual effects for each moderator interaction are reported in Table 2.
-All moderator tests were significant and subsequent significant interactions of critical terms are interpreted.
+Results of the 5 main moderator tests (mispronunciation size, mispronunciation  position, mispronunciation type, distractor overlap, distractor familiarity) as well as the individual effects for each moderator interaction are reported in Table 2.
+The statistic that tests whether a specific moderator explains a significant proportion of variance in the data, QM, was significant for all moderators and subsequent significant interactions of critical terms are interpreted.
 Finally, we analyze the relationship between infant age and the moderator condition they were tested in using Fisher's exact test, which is more appropriate for small sample sizes [@Fisher1922].
@@
 Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an graded impact on mispronunciation sensitivity [@White2008; @Mani2011] and this moderator was coded as a continuous variable.
-We did not include records for which the numer of features changed was not specified or consistent within a record (e.g., both 1- and 2-feature changes within one mispronunciation record).
+We did not include records for which the number of features changed was not specified or consistent within a record (e.g., both 1- and 2-feature changes within one mispronunciation record).
 
@@
   #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_manual(values=cbPalette)+
+  scale_fill_grey()+
   apatheme +
@@
   geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
-  scale_colour_manual(values=cbPalette)+
+  scale_colour_grey()+
   apatheme +
@@
 
-```{r PlotMispPosit, echo = FALSE, fig.width=7,fig.height=3.5, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions.
-Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions by age.
+```{r PlotMispPosit, echo = FALSE, fig.width=7,fig.height=3.5, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions.
+Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions by age.
 For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
@@
 
-```{r PlotMispType, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations.
-Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations by age.
+```{r PlotMispType, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations.
+Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations by age.
 For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
@@
 
-```{r PlotCVEffectLang, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language.
-Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language by age.
+```{r PlotCVEffectLang, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language.
+Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language by age.
 For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
@@
 
-```{r PlotDistOverlap, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for target-distractor pairs with onset overlap or no overlap.
-Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for target-distractor pairs with onset overlap or no overlap by age.
+```{r PlotDistOverlap, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for target-distractor pairs with onset overlap or no overlap.
+Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for target-distractor pairs with onset overlap or no overlap by age.
 For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
@@
 
-apa_table(mod_table, col.names = c("Moderator", "Moderator Test", "Interaction Terms", "Hedges' *g*", "SE", "95 CI", "*p*-value"), caption = "Summary of moderator tests and effect estimates.", landscape = TRUE, font_size = "scriptsize")
+# kable(mod_table, "latex", align = 'c', booktabs = T, linesep = "", row.names = FALSE,
+#        col.names = c("Moderator", "Moderator Test", "Interaction Terms", "Hedges' *g*", "SE", "95 CI", "*p*-value"),
+#        caption = "Summary of the 5 moderator tests, including effect estimates for effects and critical interactions.")%>%
+#     kable_styling(full_width = F, font_size = 4) %>%
+#     collapse_rows(columns = 1, latex_hline = "major")
+#
+
+mod_table_print <- mod_table
+mod_table_print$mod <- c("Misp. size", "", "Misp. position", "", "Misp. type", "", "", "", "Distractor overlap", "", "Distractor familiarity", "")
+
+apa_table(mod_table_print, col.names = c("Moderator", "Moderator Test", "Interaction Terms", "Hedges' *g*", "SE", "95 CI", "*p*-value"), caption = "Summary of the 5 moderator tests, including effect estimates for effects and critical interactions.", landscape = TRUE, font_size = "scriptsize", midrules = c(2, 4, 8, 10))
 
@@
 Researchers' analysis strategy may be adapted to infants' age or influenced by having observed the data.
-For example, consider the possibility that there is a true increase in mispronunciation sensitivity over development.
-In this scenario, younger infants should show no or only little sensitivity to mispronunciations while older infants would show a large sensitivity to mispronunciations.
-This lack of or small mispronunciation sensitivity in younger infants is likely to lead to non-significant results, especially given the prevalent small sample sizes, which would be more difficult to publish [@Ferguson2012].
-In order to have publishable results, adjustments to the analysis approach could be made until a significant effect of mispronunciation sensitivity is found.
-This would lead to an increase in significant results and alter the observed developmental trajectory of mispronunciation sensitivity in the current meta-analysis.
-Such a scenario is in line with the publication bias we observe [@Simmons2011].
+For example, consider the possibility that a particular study does not find that infants looked to the target object upon hearing a correct pronunciation.
+With this pattern of behavior, interpreting an effect of mispronunciation sensitivity becomes difficult; how can infants notice a phoneme change when they do not even show recognition of the correct pronunciation?
+A lack of recognition or a small effect for correct pronunciations would be more difficult to publish [@Ferguson2012].
+In order to have publishable results, adjustments to the analysis approach could be made until a significant effect of recognition for correct pronunciations is found.
+But, these adjustments would also need to be made for the analysis of mispronunciations, which may impact the size of the mispronunciation sensitivity effect.
+Such a scenario could explain the publication bias suggested by the asymmetry for correct pronunciations in the funnel plot shown in Figure \@ref(fig:FunnelCombo) [@Simmons2011].
+This could lead to an increase in significant results and even alter the developmental trajectory of mispronunciation sensitivity.
 
@@
 Evidence suggests that the speed of word recognition processing is slower in young infants [@Fernald1998], which may lead researchers to include longer post-naming phases in their experiments with younger infants.
-If this is the case, we expect a negative correlation between post-naming phase length and infant age.
 The post-naming analysis window, in contrast, represents how much of this phase was included in the statistical analysis and can be chosen after the experimental data is collected and perhaps observed.
-If this is the case, we expect a negative correlation between post-naming analysis window and infant age.
+If infant age is influencing the length of these windows, we should expect a negative correlation.
 
@@
 Although length of the post-naming analysis window was included as a continuous variable in the meta-analytic model, it is divided into categories for ease of viewing.
-Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity as a function of age.
+Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity, within subject group and study (correct - mispronunciations), as a function of age.
 The lines plot the linear regression and the gray shaded area indicates the standard error.", results="hide"}
@@
 
-As described in the Methods section, there was considerable variation across papers in whether the pre-naming phase was used as a baseline measurement and subtracted from the PTL score from the post-naming phase and compared with a chance value of 0 (Difference Score) or directly compared with the post-naming phase (Pre- vs.
+As described in the Methods section, there was considerable variation across papers in whether the pre-naming phase was used as a baseline measurement (Difference Score or Pre- vs.
 Post) or whether the post-naming PTL was compared with a chance value of 50% (Post).
-A positive Difference Score or a greater Pre- vs.
-Post-naming phase PTL indicates that infants increased their target looks after hearing the naming label.
-A Post PTL greater than 50% assumes recognition of the target image.
-As most papers do not specify whether any of these calculations are made before or after aggregating across trials and/or participants, we make no assumptions about how any aggregate scores or differences were computed.
-
+Considering analyses of the dependent variables Difference Score or Pre- vs.
+Post produce the same result, we combined these two dependent variables into one, which we call Baseline Corrected.
 To our knowledge, there is no theory or evidence that explicitly drives choice of dependent variable in preferential looking studies, which may explain the wide variation in dependent variable reported in the papers included in this meta-analysis.
-We next explored whether the type of dependent variable calculated influenced the estimated size of sensitivity to mispronunciations.
-Considering that the dependent variable Post differs in its consideration of pre-naming baseline preferences, we coded this as a reference condition.
-
-```{r dependent_variable}
+We next explored whether the type of dependent variable calculated was related to the estimated size of sensitivity to mispronunciations.
+
+```{r dependent_variable_corrected}
+
+dat$dv_label <- ifelse(dat$within_measure=="post", "Post", "Baseline_corrected")
+
+dat$dv_label <- factor(dat$dv_label, levels = c("Post", "Baseline_corrected"))
+
+db_ET_MP$dv_label <- ifelse(db_ET_MP$within_measure=="post", "Post", "Baseline_corrected")
+
+db_ET_MP$dv_label <- factor(db_ET_MP$dv_label, levels = c("Post", "Baseline_corrected"))
+
+#
+
+rma_within <- rma.mv(g_calc, g_var_calc, mods = ~dv_label, data = db_ET_MP, random = ~same_infant_calc | short_cite)
+
+rma_within_effbaseline <- coef(summary(rma_within))[2,]
+
+ rma_within_MS <- rma.mv(g_calc, g_var_calc, mods = ~dv_label*condition, data = dat, random = ~same_infant_calc | short_cite)
+
+  rma_within_MS_effbaseline <- coef(summary(rma_within_MS))[4,]
+
+  # age
+
+ rma_within_AGE <- rma.mv(g_calc, g_var_calc, mods = ~dv_label*age.C, data = db_ET_MP, random = ~same_infant_calc | short_cite)
+
+   rma_within_AGE_effbaseline <- coef(summary(rma_within_AGE))[4,]
+
+  rma_within_AGE_MS <- rma.mv(g_calc, g_var_calc, mods = ~dv_label*age.C*condition, data = dat, random = ~same_infant_calc | short_cite)
+
+    rma_within_AGE_MS_effbaseline <- coef(summary(rma_within_AGE_MS))[8,]
+
+  #   dat_dv <- dat %>%
+  # group_by(short_cite, dv_label, condition) %>%
+  # summarize(g = mean(g_calc))
+  #   
+  #   dat_dv$comps <- ifelse(dat_dv$dv_label == "Post" & dat_dv$condition == 1, "post_correct",
+  #                          ifelse(dat_dv$dv_label == "Baseline_corrected" & dat_dv$condition == 1, "base_correct",
+  #                                 ifelse(dat_dv$dv_label == "Baseline_corrected" & dat_dv$condition == 0, "base_misp", "post_misp")))
+  #   
+  #   d.dv <- dat_dv %>%
+  # group_by(comps) %>%
+  # summarize(g = mean(g))
+
+```
+
+When we included both condition and dependent variable as moderators, the moderator test was significant (`r mod_test(rma_within_MS)`).
+The estimate for the interaction between the type of dependent variable and condition was was significant ($\beta$`r full_estimate(rma_within_MS_effbaseline)`).
+As can be seen in \@ref(fig:PlotWithinCondDV_baseline), mispronunciation sensitivity was higher when the dependent variable reported was Post compared to when it was Baseline Corrected.
+When age was included as an additional moderator, the moderator test was significant (`r mod_test(rma_within_AGE_MS)`).
+However, the estimate for the interaction between dependent variable, condition, and age was not significant ($\beta$`r full_estimate(rma_within_AGE_MS_effbaseline)`).
+
+(Insert Figure \@ref(fig:PlotWithinCondDV_baseline) about here)
+
+```{r PlotWithinCondDV_baseline, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (orange), Post vs.
+Pre (blue), and Difference Score (green).
+Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity, within subject group and study (correct - mispronunciations), as a function of age.
+The lines plot the linear regression and the gray shaded area indicates the standard error.", results="hide"}
+dat.cm <- dat[,c("short_cite", "is_correct", "is_mp", "within_measure", "condition", "g_calc", "weights_g", "mean_age_1", "n_1")]
+dat.c <- subset(dat.cm, is_correct == 1)
+dat.m <- subset(dat.cm, is_mp == 1)
+dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "within_measure", "mean_age_1", "n_1"))
+dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
+dat.cm$condition_label <- ifelse(dat.cm$is_correct.x==1, "Correct", "Mispronunciation")
+dat.cm$dv_label <- ifelse(dat.cm$within_measure=="post", "Post", "Baseline_corrected")
+dat.cm$dv_label <- factor(dat.cm$dv_label, levels = c("Post", "Baseline_corrected"))
+
+ms.agg <- ggplot(dat.cm, aes(dv_label, Misp_sensitivity, fill = dv_label)) + 
+  #facet_grid(.~dv_label)+
+    geom_violin() +
+    geom_boxplot(width=0.1)+
+  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
+  #labs(title="a")+
+  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
+  scale_fill_grey(start = 0.5)+
+  apatheme +
+  theme(text = element_text(size=25),
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) + 
+  #xlab("Number of Features Changed") + 
+  geom_hline(yintercept = 0, linetype="dotted") + 
+  ylab("Misp. Sensitivity")
+
+# ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = dv_label)) + 
+#     #facet_grid(.~dv_label)+
+#   geom_point(aes(size = n_1),show.legend=FALSE) +
+#   labs(title="b")+
+#   geom_line(y= 0, linetype="dotted") + 
+#   geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
+#   scale_colour_grey()+
+#   apatheme +
+#   theme(legend.title = element_blank(),
+#         legend.position = "bottom") + 
+#   xlab("Age in months") + 
+#   ylab("Misp. Sensitivity")
+
+lay <- rbind(c(1), c(2))
+
+#lay <- rbind(c(1,2))
+  jpeg(filename = "figures/Figure_11_Dependent_variable.jpg", 
+       width = 500, height = 350, units = "px")
+
+ms.agg
+
+dev.off()
+
+```
+
+```{r dependent_variable_old}
 
@@
 
-When we included both condition and dependent variable as moderators, the moderator test was significant (`r mod_test(rma_within_MS)`).
-The estimate for the interaction between Pre vs.
-Post and condition was significantly smaller than that of the Post dependent variable ($\beta$`r full_estimate(rma_within_MS_effprepost)`), but the difference between the Difference Score and Post in the interaction with condition was small and not significant ($\beta$`r full_estimate(rma_within_MS_effdiff)`).
-This relationship is plotted in Figure \@ref(fig:PlotWithinCondAgeDiffScore)a.
-
-When age was included as an additional moderator, the moderator test was significant (`r mod_test(rma_within_AGE_MS)`).
-The estimate for the interaction between Pre vs.
-Post, condition, and age was significantly smaller than that of the Post dependent variable ($\beta$`r full_estimate(rma_within_AGE_MS_effprepost)`), but the difference between the Difference Score and Post in the interaction with condition and age was small and not significant ($\beta$`r full_estimate(rma_within_AGE_MS_effdiff)`).
-When the dependent variable reported was Pre vs.
-Post, mispronunciation sensitivity was found to decrease with infant age, while in comparison, when the dependent variable was Post, mispronunciation sensitivity was found to increase with infant age (see This relationship is plotted in Figure \@ref(fig:PlotWithinCondAgeDiffScore)b.)
-
-(Insert Figure \@ref(fig:PlotWithinCondAgeDiffScore) about here)
-
-```{r PlotWithinCondAgeDiffScore, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (orange), Post vs.
+```{r PlotWithinCondAgeDiffScore_old, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (orange), Post vs.
 Pre (blue), and Difference Score (green).
-Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity as a function of age.
+Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity, within subject group and study (correct - mispronunciations), as a function of age.
 The lines plot the linear regression and the gray shaded area indicates the standard error.", results="hide"}
@@
 
-## Controlling for analysis choices
+## Controlling for analysis choices and re-running the main meta-analytic models
 
@@
 Our analysis of this relationship revealed a pattern of unchanging sensitivity over infant age and vocabulary size, which has been reported by a handful of studies directly comparing infants over a small range of ages, such as 18-24 months [@Swingley2000; @Bailey2002] or 12-17 months [@Zesiger2012].
-The lack of age or vocabulary effects in our meta-analysis (carefully) suggest that this understanding is present from an early age and is maintained throughout early lexical development.
+The lack of age or vocabulary effects in our meta-analysis suggest that this understanding is present from an early age and is maintained throughout early lexical development.
 We note, however, that despite an increasing publication record of mispronunciation sensitivity studies, fewer than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total; see also Figure \@ref(fig:Vocabdescribe1)).
-We suggest that this may be the result of publication bias favoring significant effects or an overall hesitation to invest in data collection that is not expected to yield significant outcomes.
-Considering the theoretical implications, more experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size is needed if this link is to be evaluated.
+This may reflect a decreasing interest in the relationship between mispronunciation sensitivity and vocabulary size and/or to invest in data collection that is not expected to yield significant outcomes.
+Considering the theoretical implications, however, more experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size is needed if this link is to be evaluated.
 Nonetheless, if we are to take our results as robust, it becomes thus a pressing open question that theories have to answer which other factors might prompt acquiring and using language-specific phonological contrasts at such an early age.
@@
 Age and native language did not modulate sensitivity to consonant mispronunciations, but sensitivity to vowel mispronunciations increased with age and was greater overall for infants learning Germanic languages (although this increased with age for infants learning Romance languages).
-This pattern of results supports a learned account of the consonant bias, showing that sensitivity to consonants and vowels have a different developmental trajectory, which depends on whether the infant is learning a Romance (French, Italian) or Germanic (British English, Danish) native language [@Nazzi2016].
+This pattern of results supports a learned account of the consonant bias, showing that sensitivity to consonants and vowels have different developmental trajectories, which depend on whether the infant is learning a Romance (French, Italian) or Germanic (British English, Danish) native language [@Nazzi2016].
 TRACE simulations conducted by @Mayor2014 reveal a relationship between vocabulary size and sensitivity to vowel-medial mispronunciations, although here the authors give more weight to the role of mispronunciation position, a distinction we are unable to make in our analyses.
@@
 Perhaps including overlap leads infants to pay more attention to mispronunciations, increasing mispronunciation sensitivity.
-Yet, older children were more likely to recieve the arguably more difficult manipulation where target-distractor pairs overlapped in their onset phoneme, added task demands which may reduce their ability to access the phonetic detail of familiar words as argued by the PRIMIR Framework [@Curtin2007; @Werker2005].
+Yet, older children were more likely to receive the arguably more difficult manipulation where target-distractor pairs overlapped in their onset phoneme, added task demands which may reduce their ability to access the phonetic detail of familiar words as argued by the PRIMIR Framework [@Curtin2007; @Werker2005].
 This imbalance has the potential to dampen developmental differences, which would be hidden by task differences in the experiments that older and younger infants participated in.
@@
 A majority of studies used an offset time between 360 and 370 ms (*n* = `r with(offset_bin_info, n_exp_conditions[offset_bin == "367"])`), which follows the "best guess" of @Swingley2000 for the amount of time needed for infants to initiate eye movements in response to a spoken target word; in contrast, we found wide variation in the post-naming analysis window which correlated negatively with infant age and influenced the estimate of mispronunciation sensitivity.
-TRACE predicts that looks to the target in response to mispronunciations may be slower than that of correct pronunciations [@Mayor2014], and those studies with longer post-naming analysis windows capture this effect, thereby reducing the measured sensitivity to mispronunciations.
+Looks to the target in response to mispronunciations may be slower than that of correct pronunciations in infants [as predicted by TRACE, @Mayor2014], and those studies with longer post-naming analysis windows capture this effect, thereby reducing the measured sensitivity to mispronunciations.
 Although we have no direct evidence, an analysis window can be potentially set after collecting data.
@@
 
-The type of depedent variable calculated also moderated mispronunciation sensitivity and conclusions about its developmental trajectory.
+The type of depedent variable calculated also moderated mispronunciation sensitivity, albeit not conclusions about its developmental trajectory.
 Unlike the exploratory analyses related to timing, there is no clear reason for one dependent variable to be chosen over another; the prevalence of each dependent variable appears distributed across ages and some authors always calculate the same dependent variable while others use them interchangeably in different publications.
@@
 
-A lack of a field standard can have serious consequences, as our analyses show, limiting our ability to draw conclusions.
+A lack of a field standards can have serious consequences, as our analyses show, limiting our ability to draw conclusions.
 We take this opportunity to make several recommendations to address the issue of varying, potentially post hoc analysis decisions.

### 2020-07-01 scripts/PrePost_Diff_example.R

@@ -1,0 +1,160 @@
+#### Example Analysis ####
+
+# This script creates paired t-test and one sample t-tests for the original data from Höhle et al., 2006
+# Original Author: Katie Von Holzen
+# katie.m.vonholzen'at'gmail.com
+# last modified: June 25, 2020
+#   by Katie Von Holzen
+#### Load libraries ####
+
+#setwd("~/Dropbox/MP_MA")
+
+library(ggplot2)
+library(wesanderson)
+library(reshape)
+library(doBy)
+library(schoRsch)
+library(dplyr)
+
+std <- function(x) sd(x)/sqrt(length(x))
+
+# Color Blind palette:
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
+set.seed(8)
+
+correct_pre <- rnorm(100, mean=47, sd=8.854377448)
+correct_post <- rnorm(100, mean=59, sd=12.01665511)
+
+misp_pre <- rnorm(100, mean=51, sd=8.854377448)
+misp_post <- rnorm(100, mean=51, sd=10.11928851)
+
+
+cm <- data.frame(cbind(correct_pre, correct_post, misp_pre, misp_post))
+cm$sub <- seq(1, nrow(cm))
+
+cm$correct_diff <- cm$correct_post - cm$correct_pre
+cm$misp_diff <- cm$misp_post - cm$misp_pre
+
+
+# t-test pre vs. post correct
+t_out(t.test(cm$correct_pre, cm$correct_post, paired =T))
+# d = -0.80
+
+# t-test pre vs. post misp
+t_out(t.test(cm$misp_pre, cm$misp_post, paired =T))
+# d = -0.07
+
+# t-test diff correct
+t_out(t.test(cm$correct_diff, mu = 0))
+# d = 0.80
+
+# t-test diff misp
+t_out(t.test(cm$misp_diff, mu = 0))
+# d = 0.07
+
+
+# misp effect for difference
+t_out(t.test(cm$misp_diff, cm$correct_diff, paired = T))
+# d = -0.58
+
+#######################################################
+# ok,now how about if the aggregation is taking place at different steps?
+
+sub <- 50
+items <- c(1,2,3,4,5)
+
+items <- rep(items, sub)
+sub <- seq(1, sub)
+
+
+d <- merge(sub, items)
+names(d) <- c("sub", "items")
[…]

### 2020-07-02 VonHolzenBergmann_MPMetaAnalysis.Rmd
wc correction factor removed

@@
 
-Our power analysis revealed that mispronunciation sensitivity studies typically underpowered, with `r ptt_power`% power and would need to increase their sample from an average of `r median_sample` to `r round(ptt.est$n, 0)`more infants to achieve 80% power.
+Our power analysis revealed that mispronunciation sensitivity studies typically underpowered, with `r ptt_power`% power and would need to increase their sample from an average of `r median_sample` to `r round(ptt.est$n, 0)` more infants to achieve 80% power.
 While this number does not seem to differ dramatically from the observed sample sizes, the impact of the smaller sample sizes on power is thus substantial and should be kept in mind when planning future studies.

### 2020-07-02 scripts/calculateES.R

@@ -55,7 +55,9 @@ for(line in 1:length(db_ET$n_1)){
     } else if (complete.cases(db_ET[line,]$t)) {
       #Dunlap et al., 1996, p.171
       wc <- sqrt(2 * (1 - db_ET[line,]$corr))
-      db_ET[line,]$d_calc <- (db_ET[line,]$t / sqrt(db_ET[line,]$n_1)) * wc
+      db_ET[line,]$d_calc <- (db_ET[line,]$t / sqrt(db_ET[line,]$n_1))
+      #based on reviewer feedback on a different MetaLab project (on which this project is based), it has been suggested we remove this correction factor (wc)
+      #db_ET[line,]$d_calc <- (db_ET[line,]$t / sqrt(db_ET[line,]$n_1)) * wc
       db_ET[line,]$es_method  <- "t_two"
     } else if (complete.cases(db_ET[line,]$x_1, db_ET[line,]$x_2, db_ET[line,]$SD_dif)) {
         within_SD <-db_ET[line,]$ SD_dif / sqrt(2 * (1 - db_ET[line,]$corr)) # Lipsey & Wilson (2001); Morris & DeShon (2002)

### 2020-07-07 VonHolzenBergmann_MPMetaAnalysis.Rmd
Small textual changes for R1

--- 2020-07-01 VonHolzenBergmann_MPMetaAnalysis.Rmd
@@
 This meta-analysis focuses on studies investigating infants' ability to detect mispronunciations in familiar words, or mispronunciation sensitivity.
-Our goal was to evaluate the development of infants' phonological representations for familiar words as well as explore the role of experimental manipulations related to theoretical questions and analysis choices.
+Our goal was to evaluate the development of infants' phonological representations for familiar words as well as explore the role of experimental manipulations related to theoretical questions and of analysis choices.
 The results show that although infants are sensitive to mispronunciations, they still accept these altered forms as labels for target objects.
 Interestingly, this ability is not modulated by age or vocabulary size, suggesting that a mature understanding of native language phonology may be present in infants from an early age, possibly before the vocabulary explosion.
-These results also support several theoretical assumptions made in the literature, such as sensitivity to mispronunciation size and position of the mispronunciation.
+These results  support several theoretical assumptions made in the literature, such as sensitivity to mispronunciation size and position of the mispronunciation.
 We also shed light on the impact of data analysis choices that may lead to different conclusions regarding the development of infants' mispronunciation sensitivity.
@@
 These research questions and experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete.
-The PRIMIR Framework [Processing Rich Information from Multidimensional Interactive Representations; @Curtin2007; @Werker2005] describes how infants acquire and organize the incoming speech signal into phonetic and indexical detail.
+The PRIMIR Framework [Processing Rich Information from Multidimensional Interactive Representations; @Curtin2007; @Werker2005] describes how infants learn to organize the incoming speech signal into phonetic and indexical detail.
 The ability to access and use this detail, however, is governed by the task or developmental demands probed in a particular experiment.
@@
 If older infants are more likely to be tested using a more demanding mispronunciation sensitivity task, this may attenuate developmental effects across studies.
-Note, however, that those studies reporting change [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010] or no change [@Swingley2000; @Bailey2002; @Zesiger2012] all presented the same task across ages.
-
-The first set of questions concern how infants' sensitivity is modulated by different kinds of mispronunciations.
+Note, however, that those studies we reviewed above reporting change [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010] or no change [@Swingley2000; @Bailey2002; @Zesiger2012] all presented the same task across ages.
+
+The first set of questions concerns how infants' sensitivity is modulated by different kinds of mispronunciations.
 Following on the above example, some experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level, or *mispronunciation size* (i.e.
@@
 The lack of a significant modulation together with the small estimates for age (correct: $\beta$ `r full_estimate(Csum_eff)`; mispronunciation: $\beta$ `r full_estimate(Msum_eff)`) indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label.
-However, previous experimental studies ([e.g.
-@Fernald1998]) and a recent meta-analysis [@Frank2016] have found that children's speed and accuracy in recognition of correctly pronounced words increases with age.
+However, previous experimental studies [e.g.
+@Fernald1998] and a recent meta-analysis [@Frank2016] have found that children's speed and accuracy in recognition of correctly pronounced words increases with age.
 Perhaps older children are more likely to be tested on less-frequent, later learned words than younger children, which could lead to a lack of a relationship between age and target looks in response to correct pronunciations in the current meta-analysis.
@@
 
-Our power analysis revealed that mispronunciation sensitivity studies typically underpowered, with `r ptt_power`% power and would need to increase their sample from an average of `r median_sample` to `r round(ptt.est$n, 0)`more infants to achieve 80% power.
+Our power analysis revealed that mispronunciation sensitivity studies typically underpowered, with `r ptt_power`% power and would need to increase their sample from an average of `r median_sample` to `r round(ptt.est$n, 0)` infants to achieve 80% power.
 While this number does not seem to differ dramatically from the observed sample sizes, the impact of the smaller sample sizes on power is thus substantial and should be kept in mind when planning future studies.
@@
 
-We next calculated the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in response to mispronunciations on the onset (*n* = `r with(mli, n_exp_conditions[mispron_location == "onset"])` records), medial medial (*n* = `r with(mli, n_exp_conditions[mispron_location == "medial"])`), and coda phonemes (*n* = `r with(mli, n_exp_conditions[mispron_location == "coda"])`).
+We next calculated the meta-analytic effect of mispronunciation sensitivity (moderator: condition) in response to mispronunciations on the onset (*n* = `r with(mli, n_exp_conditions[mispron_location == "onset"])` records), medial (*n* = `r with(mli, n_exp_conditions[mispron_location == "medial"])`), and coda phonemes (*n* = `r with(mli, n_exp_conditions[mispron_location == "coda"])`).
 We coded the onset, medial, and coda positions as continuous variables, to evaluate the importance of each subsequent position [@Marslen-Wilson1989].
@@
 Neither distractor familiarity (familiar, unfamiliar) or type of mispronunciation (consonant, vowel) were found to impact mispronunciation sensitivity.
+
 The developmental trajectory of mispronunciation sensitivity was influenced by type of mispronunciation and overlap between the target and distractor labels, but mispronunciation size, mispronunciation position, and distractor familiarity were found to have no influence.
@@
 This includes both the length of time before the target object is named (pre-naming phase) as well as after (post-naming phase) and is determined prior to data collection.
-Evidence suggests that the speed of word recognition processing is slower in young infants [@Fernald1998], which may lead researchers to include longer post-naming phases in their experiments with younger infants.
+Evidence suggests that the speed of word recognition is slower in young infants [@Fernald1998], which may lead researchers to include longer post-naming phases in their experiments with younger infants.
 The post-naming analysis window, in contrast, represents how much of this phase was included in the statistical analysis and can be chosen after the experimental data is collected and perhaps observed.
@@
 There was no apparent relation between infant age and post-naming phase length (*r* = `r trial.l$estimate`, 95% CI[`r trial.l$conf.int[1]`, `r trial.l$conf.int[2]`], *p* `r psig(trial.l$p.value)`), but there was a significant negative relationship between infant age and post-naming analysis window length, such that younger infants' looking times were analyzed using a longer post-naming analysis window (*r* = `r post.l$estimate`, 95% CI[`r post.l$conf.int[1]`, `r post.l$conf.int[2]`], *p* `r psig(post.l$p.value)`).
-Considering the post-naming analysis window may be determined after data collection and observation, we next investigated whether this impacted measures of mispronunciation sensitivity.
+We next investigated whether post-naming analysis window length impacted measures of mispronunciation sensitivity.
 
@@
 
-#
-
 rma_within <- rma.mv(g_calc, g_var_calc, mods = ~dv_label, data = db_ET_MP, random = ~same_infant_calc | short_cite)
@@
 The results of the moderator analysis reflect several findings reported in the literature.
-The meta-analytic effect for ispronunciation size, as measured by phonological features changed, showed graded sensitivity [@Bernier2017; @Tamasi2016; @White2008; @Mani2011], an adult-like ability.
-More studies are needed to evaluate whether this gradual sensitivity develops with age, as only one study examined more than one age [@Mani2011] and all others test the same age [@Bernier2017; @Tamasi2016; @White2008].
-With more studies investigating graded sensitivity at multiple ages in infancy, we would achieve a better estimate of whether this is a stable or developing ability, thus also shedding more light on the progression of phono-lexical development in general that then needs to be captured in theories and models.
+The meta-analytic effect for mispronunciation size, as measured by phonological features changed, showed graded sensitivity [@Bernier2017; @Tamasi2016; @White2008; @Mani2011], an adult-like ability.
+More studies are needed to evaluate whether this gradual sensitivity develops with age, as only one study examined more than one age [@Mani2011] and all others test the same age with a varying number of features [@Bernier2017; @Tamasi2016; @White2008].
+With more studies investigating graded sensitivity at multiple ages with all other facturs held constant, we would achieve a better estimate of whether this is a stable or developing ability, thus also shedding more light on the progression of phono-lexical development in general that then needs to be captured in theories and models.
 
@@
 
-For several moderators, we found no evidence of modulation of mispronunciation sensitivity.
+For several moderators, we found no evidence of significant modulation of mispronunciation sensitivity.
 Studies that include an unfamiliar, as opposed to familiar distractor image, often argue that the unfamiliar image provides a better referent candidate for mispronunciation than a familiar distractor image, where the name is already known.
-Yet, no studies have directly examined this assertion and our meta-analysis found that distractor familiarity did not modulate mispronunciation sensitivity.
+Yet, no studies have directly examined this assertion and our meta-analysis found that distractor familiarity did not significantly modulate mispronunciation sensitivity.
 
@@
 Yet, older children were more likely to receive the arguably more difficult manipulation where target-distractor pairs overlapped in their onset phoneme, added task demands which may reduce their ability to access the phonetic detail of familiar words as argued by the PRIMIR Framework [@Curtin2007; @Werker2005].
-This imbalance has the potential to dampen developmental differences, which would be hidden by task differences in the experiments that older and younger infants participated in.
+This imbalance in the ages tested has the potential to dampen developmental differences, due to task differences in the experiments that older and younger infants participated in.
 Further support comes from evidence that sensitivity to mispronunciations when the target-distractor pair overlapped on the onset phoneme increased with age.
 This pattern of results suggests that when infants are given an equally difficult task, developmental effects may be revealed.
-This explanation can be confirmed by testing more young infants on overlapping target-distractor pairs.
+This explanation can be confirmed by testing more infants at younger ages on overlapping target-distractor pairs in the future.
 
@@
 During the coding of our meta-analysis database, we noted variation in variables relating to timing and the calculation of the dependent variable reported.
-As infants mature, they recognize words more quickly [@Fernald1998], which may lead experimenters to adjust and lower offset times in their analysis as well as shorten the length of the analysis window.
-A majority of studies used an offset time between 360 and 370 ms (*n* = `r with(offset_bin_info, n_exp_conditions[offset_bin == "367"])`), which follows the "best guess" of @Swingley2000 for the amount of time needed for infants to initiate eye movements in response to a spoken target word; in contrast, we found wide variation in the post-naming analysis window which correlated negatively with infant age and influenced the estimate of mispronunciation sensitivity.
-Looks to the target in response to mispronunciations may be slower than that of correct pronunciations in infants [as predicted by TRACE, @Mayor2014], and those studies with longer post-naming analysis windows capture this effect, thereby reducing the measured sensitivity to mispronunciations.
-Although we have no direct evidence, an analysis window can be potentially set after collecting data.
-At worst, this adjustment could be the result of a desire to confirm a hypothesis, increasing the rate of false-positives [@Gelman2013]: a "significant effect" of mispronunciation sensitivity is found with an analysis window of 2000 but not 3000 ms, therefore 2000 ms is chosen.
-At best, this variation introduces noise into the study of mispronunciation sensitivity, blurring the true developmental trajectory of mispronunciation sensitivity.
+As infants mature, they recognize words more quickly [@Fernald1998], which may lead experimenters to shorten the length of the analysis window.
+We found wide variation in the post-naming analysis window which correlated negatively with infant age and influenced the estimate of mispronunciation sensitivity.
+Looks to the target in response to mispronunciations may be slower than in response to correct pronunciations in infants [as predicted by TRACE, @Mayor2014], and those studies with longer post-naming analysis windows allow fixations to accumulate even in the presence of mispronunciations, thereby reducing the measured sensitivity to mispronunciations.
+In fact, the exact dynamics of fixations to mispronunciations (overall flattened versus delayed) are an ongoing topic of discussion.
+Returning to the analysis window length itself, we wish to raise awareness that the observed variation might seem like it indicates a so-called Questionable Research Practice where analyses are adjusted after observing the data to obtain a significant effect, which in turn increases the rate of false-positives [@Gelman2013]: a "significant effect" of mispronunciation sensitivity is found with an analysis window of 2000 but not 3000 ms, therefore 2000 ms is chosen.
+While we have no reason to believe that this is the cause of the observed variation, consistency or justification of chosen time windows would increase the credibility of developmental eye movement research.
+In addition, and even in the absence of such practices, the variation in analysis window length introduces noise into the dataset, blurring the true developmental trajectory of mispronunciation sensitivity.
 
 The type of depedent variable calculated also moderated mispronunciation sensitivity, albeit not conclusions about its developmental trajectory.
-Unlike the exploratory analyses related to timing, there is no clear reason for one dependent variable to be chosen over another; the prevalence of each dependent variable appears distributed across ages and some authors always calculate the same dependent variable while others use them interchangeably in different publications.
+There is, to the best of our knowledge, no clear reason for one dependent variable to be chosen over another; the prevalence of each dependent variable appears distributed across ages and some authors always calculate the same dependent variable while others use them interchangeably in different publications.
 One clear difference is that both the Difference Score (reporting looks to the target image after hearing the label minus looks in silence) and Pre vs.
@@
 We recommend future theoretical frameworks take this evidence into account.
-Our meta-analysis was also able to confirm different findings in the literature, including the role of mispronunciation size, mispronunciation position, and the role of age and native language in sensitivity to mispronunciation type (consonant vs.
+Our meta-analysis was also able to confirm different findings in the literature, including the role of mispronunciation size, mispronunciation position, and infants' age and native language in sensitivity to mispronunciation type (consonant vs.
 vowel).
@@
 Ideally, future experimental design and data analysis would become standardized which will be aided by the growing trend of preregistration and open science practices.
-Our analysis highlights how meta-analyses can aid in identification of issues in a particular field and play a vital role in how the field addresses such issues.
+Our analysis highlights how meta-analyses can identify issues in a particular field and play a vital role in how the field addresses such issues.
 

### 2020-07-07 VonHolzenBergmann_MPMetaAnalysis.Rmd
revision and resubmission to Dev Psych

@@
 
-To disentangle the predictions that phono-lexical representations are progressively becoming more specified or are specified early, we investigate the relationship between mispronunciation sensitivity and age as well as vocabulary size.
+To disentangle the predictions that phono-lexical representations are progressively becoming more specified or are specified early, we investigate the relationship between mispronunciation sensitivity and age as well as vocabulary size by aggregating 20 years of mispronunciation sensitivity studies.
 But, this may not account for all variability found in the literature.
@@
 In order to study the influence of mispronunciation position, many studies control the *phonological overlap between target and distractor labels*.
-For example, when examining sensitivity to a vowel mispronunciation of the target word "ball", the image of a ball would be paired with a distractor image that shares onset overlap, such as "bed".
+For example, when examining sensitivity to a vowel mispronunciation of the target word "ball", the image of a ball would be paired with a distractor image that shares onset overlap, such as "bed", as opposed to a distractor image that does not share onset overlap, such as “truck”.
 This ensures that infants cannot use the onset of the word to differentiate between the target and distractor images [@Mani2007].
@@
 Second, we analyzed the correlation between reported vocabulary size and mispronunciation sensitivity using the package meta [@meta].
-For a subsequent investigation of experimental characteristics, we introduced each as a moderator: size of mispronunciation, position of mispronunciation, type of mispronunciation, phonological overlap between target and distractor labels, and distractor familiarity (more detail below).
+For a subsequent investigation of experimental characteristics, we introduced each separately as a moderator: size of mispronunciation, position of mispronunciation, type of mispronunciation, phonological overlap between target and distractor labels, and distractor familiarity (more detail below).
 
@@
 This figure illustrates two things: the increasing number of mispronunciation sensitivity studies in general and the decreasing number of mispronunciation studies measuring vocabulary.
-The lack of evidence for a relationship between mispronunciation sensitivity and vocabulary size in some early studies may have contributed to increasingly fewer researchers including vocabulary measurements in their mispronunciation sensitivity experimental design.
-This may explain our underpowered analysis of the relationship between object recognition for correct pronunciations and mispronunciations and vocabulary size, despite its theoretical interest.
+This decrease in mispronunciation sensitivity studies measuring and reporting vocabulary size correlations is surprising, considering its theoretical interest.
 
@@
 
-```{r PlotMispPosit, echo = FALSE, fig.width=7,fig.height=3.5, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions.
-Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions by age.
-For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
+```{r PlotMispPosit, echo = FALSE, fig.width=7,fig.height=3.5, fig.cap="Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions.
+The dashed line indicates zero (chance).", results="hide"}
 
@@
 We examine whether variation in the approach to data analysis may be have an influence on our conclusions regarding infants’ developing mispronunciation sensitivity.
-To do so, we analyzed analysis choices related to timing (post-naming analysis window; offset time) and type of dependent variable in our coding of the dataset because they are consistently reported.
+To do so, we analyzed analysis choices related to timing, specifically the post-naming analysis window, as well as type of dependent variable in our coding of the dataset because they are consistently reported.
 Further, since we observe variation in both aspects of data analysis, summarizing typical choices and their impact might be useful for experiment design in the future and might help establish field standards.
@@
 
-When we included both condition and dependent variable as moderators, the moderator test was significant (`r mod_test(rma_within_MS)`).
-The estimate for the interaction between the type of dependent variable and condition was was significant ($\beta$`r full_estimate(rma_within_MS_effbaseline)`).
-As can be seen in \@ref(fig:PlotWithinCondDV_baseline), mispronunciation sensitivity was higher when the dependent variable reported was Post compared to when it was Baseline Corrected.
-When age was included as an additional moderator, the moderator test was significant (`r mod_test(rma_within_AGE_MS)`).
-However, the estimate for the interaction between dependent variable, condition, and age was not significant ($\beta$`r full_estimate(rma_within_AGE_MS_effbaseline)`).
-
-(Insert Figure \@ref(fig:PlotWithinCondDV_baseline) about here)
-
-```{r PlotWithinCondDV_baseline, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (orange), Post vs.
+```{r PlotWithinCondDVbaseline, echo = FALSE, fig.width=7,fig.height=3.5, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (orange), Post vs.
 Pre (blue), and Difference Score (green).
@@
 The lines plot the linear regression and the gray shaded area indicates the standard error.", results="hide"}
+
 dat.cm <- dat[,c("short_cite", "is_correct", "is_mp", "within_measure", "condition", "g_calc", "weights_g", "mean_age_1", "n_1")]
@@
 
+ms.agg
+
 # ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = dv_label)) + 
@@
 
+When we included both condition and dependent variable as moderators, the moderator test was significant (`r mod_test(rma_within_MS)`).
+The estimate for the interaction between the type of dependent variable and condition was was significant ($\beta$`r full_estimate(rma_within_MS_effbaseline)`).
+As can be seen in \@ref(fig:PlotWithinCondDVbaseline), mispronunciation sensitivity was higher when the dependent variable reported was Post compared to when it was Baseline Corrected.
+When age was included as an additional moderator, the moderator test was significant (`r mod_test(rma_within_AGE_MS)`).
+However, the estimate for the interaction between dependent variable, condition, and age was not significant ($\beta$`r full_estimate(rma_within_AGE_MS_effbaseline)`).
+
+(Insert Figure \@ref(fig:PlotWithinCondDVbaseline) about here)
+
 ```{r dependent_variable_old}
@@
     rma_within_AGE_MS_effdiff <- coef(summary(rma_within_AGE_MS))[12,]
-
-```
-
-```{r PlotWithinCondAgeDiffScore_old, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (orange), Post vs.
-Pre (blue), and Difference Score (green).
-Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity, within subject group and study (correct - mispronunciations), as a function of age.
-The lines plot the linear regression and the gray shaded area indicates the standard error.", results="hide"}
-dat.cm <- dat[,c("short_cite", "is_correct", "is_mp", "within_measure", "condition", "g_calc", "weights_g", "mean_age_1", "n_1")]
-dat.c <- subset(dat.cm, is_correct == 1)
-dat.m <- subset(dat.cm, is_mp == 1)
-dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "within_measure", "mean_age_1", "n_1"))
-dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
-dat.cm$condition_label <- ifelse(dat.cm$is_correct.x==1, "Correct", "Mispronunciation")
-dat.cm$dv_label <- ifelse(dat.cm$within_measure=="post", "Post",
-                       ifelse(dat.cm$within_measure == "pre_post", "Post vs. Pre",
-                              "Difference Score"))
-dat.cm$dv_label <- factor(dat.cm$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
-ms.agg <- ggplot(dat.cm, aes(dv_label, Misp_sensitivity, fill = dv_label)) + 
-  #facet_grid(.~dv_label)+
-    geom_violin() +
-    geom_boxplot(width=0.1)+
-  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
-  labs(title="a")+
-  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_grey()+
-  apatheme +
-  theme(text = element_text(size=25),
-        legend.title = element_blank(),
-        legend.position = "bottom",
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) + 
-  #xlab("Number of Features Changed") + 
-  geom_hline(yintercept = 0, linetype="dotted") + 
-  ylab("Misp. Sensitivity")
-ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = dv_label)) + 
-    #facet_grid(.~dv_label)+
-  geom_point(aes(size = n_1),show.legend=FALSE) +
-  labs(title="b")+
-  geom_line(y= 0, linetype="dotted") + 
-  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
-  scale_colour_grey()+
-  apatheme +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
-  xlab("Age in months") + 
-  ylab("Misp. Sensitivity")
-lay <- rbind(c(1), c(2))
-#lay <- rbind(c(1,2))
-  jpeg(filename = "figures/Figure_11_Dependent_variable.jpg", 
-       width = 500, height = 600, units = "px")
-
-ger.plot.age <- grid.arrange(ms.agg, ms.age,
-                             layout_matrix = lay)
-dev.off()
-grid.draw(ger.plot.age)
 

### 2020-09-24 VonHolzenBergmann_MPMetaAnalysis.Rmd
third round of reviews response

@@
 mama, ball, kitty; @CharlesLuce1995] and encoding representations for these words using fine phonological detail may not be necessary.
-According to PRIMIR [@Curtin2007; @Werker2005] infants' initially episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task.
+According to PRIMIR [@Curtin2007; @Werker2005] infants' initial episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task.
 This argument is supported by the results of @Mani2010kepstups, who found that 12-month-old infants with a larger vocabulary showed a greater sensitivity to vowel mispronunciations than infants with a smaller vocabulary.
@@
 1-feature, 2-features, 3-features), finding that infants are more sensitive to larger mispronunciations (3-feature-changes) than smaller mispronunciations (1-feature changes) for both consonant [@White2008; @Bernier2017; @Tamasi2016] and vowel [@Mani2011] mispronunciations, known as graded sensitivity.
-This also has consequences for understanding the developmental trajectory of mispronunciation sensitivity, as adults show similar graded sensitivity [@Bailey2005].
+By aggregating studies testing infants of different ages on mispronunciations of varying size, this also has consequences for understanding whether graded sensitivity changes over development.
 
@@
 
-We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list.
+We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list (see Figure \@ref(fig:PRISMA-image) for an overview of the selection process).
 This process yielded 110 items.
@@
 This search was conducted on 22 September, 2017 and yielded 288 results.
-We removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech.
+From this combined list of 398 records we removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech.
 The final sample (*n* = `r length(unique(descriptive_dat$short_cite))`) consisted of `r with(descriptive_dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "dissertation"]))` theses, and `r with(descriptive_dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports.
@@
 
-Mispronunciation sensitivity studies are typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement.
+Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement.
 PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images.
@@
   #Add a vertical line to show mean effect
-  geom_vline(xintercept=mean_correct, color='orange', linetype='dashed')+
+  geom_vline(xintercept=mean_correct, color='yellow', linetype='dashed')+
     geom_vline(xintercept=mean_misp, color='blue', linetype='dashed')+
@@
 
-```{r PlotMPEffect, echo = FALSE, fig.width=7,fig.height=7, fig.cap="Panel a: Effect sizes for correct pronunciations (orange) and mispronunciations (blue) by participant age.
+```{r PlotMPEffect, echo = FALSE, fig.width=7,fig.height=8, fig.cap="Panel a: Effect sizes for correct pronunciations (yellow) and mispronunciations (blue) by participant age.
 Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) by participant age.
@@
 p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
-  ggtitle("a. Object Recognition")+
+  ggtitle("a.")+
   geom_point(aes(size = weights_g),show.legend=FALSE, alpha = .5) + 
@@
   geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
-  scale_colour_grey()+
+  #scale_colour_grey()+
+    scale_color_manual(values=cbPalette)+
   xlim(6, 31) +
@@
   theme(legend.title = element_blank(),
-        legend.position = "bottom") + 
+        legend.position = "bottom",
+        plot.title = element_text(size = 20)) + 
   xlab("Age in months") + 
@@
 p.diff <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity)) + 
-  ggtitle("b. Mispronunciation Sensitivity")+
+  ggtitle("b.")+
   geom_point(aes(size = weight),show.legend=FALSE, alpha = .3) + 
@@
   geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1), color = "black") +
-  scale_colour_grey()+
+  #scale_colour_grey()+
+  scale_color_manual(values=cbPalette)+
   xlim(6, 31) +
@@
 
-lay <- rbind(c(1), c(2))
+lay <- rbind(c(1),
+             c(1),
+             c(1),
+             c(2),
+             c(2))
 #lay <- rbind(c(1,2))
@@
   jpeg(filename = "figures/Figure_3_AgeEffect.jpg", 
-       width = 500, height = 700, units = "px")
+       width = 500, height = 900, units = "px")
 
@@
 
-```{r Vocabdescribe1, echo = FALSE, fig.width=7,fig.height=4.5, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (orange), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (green).", results="hide"}
+```{r Vocabdescribe1, echo = FALSE, fig.width=7,fig.height=4.5, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (yellow), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (pink).", results="hide"}
 #how did vocabulary collection change over time?
@@
   geom_histogram(alpha = 0.5, bins = 20) +
-    scale_fill_grey()+
+    #scale_fill_grey()+
+    scale_fill_manual(values=cbPalette)+
      theme(legend.position = "bottom",
@@
   #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_grey()+
+  #scale_fill_grey()+
+    scale_fill_manual(values=cbPalette)+
   apatheme +
@@
   geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
-  scale_colour_grey()+
+  #scale_colour_grey()+
+    scale_colour_manual(values=cbPalette)+
   apatheme +
@@
   #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
-  labs(title="a")+
+  #labs(title="a")+
   #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_grey()+
+  #scale_fill_grey()+
+    scale_fill_manual(values=cbPalette)+
   apatheme +
@@
   geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
-  scale_colour_grey()+
+  #scale_colour_grey()+
+    scale_color_manual(values=cbPalette)+
   apatheme +
@@
 
-  jpeg(filename = "figures/Figure_8_CV.jpg",
-       width = 500, height = 600, units = "px")
+  jpeg(filename = "figures/Figure_7_CV.jpg",
+       width = 500, height = 800, units = "px")
 
@@
 
-  jpeg(filename = "figures/Figure_9_LangCV.jpg",
+  jpeg(filename = "figures/Figure_8_LangCV.jpg",
        width = 500, height = 900, units = "px")
@@
 
-  jpeg(filename = "figures/Figure_6_Distractor_Overlap.jpg",
-       width = 500, height = 600, units = "px")
+  jpeg(filename = "figures/Figure_9_Distractor_Overlap.jpg",
+       width = 500, height = 800, units = "px")
 
@@
 
-The developmental trajectory of mispronunciation sensitivity was influenced by type of mispronunciation and overlap between the target and distractor labels, but mispronunciation size, mispronunciation position, and distractor familiarity were found to have no influence.
+When age was added as a moderator, mispronunciation sensitivity was found to vary by type of mispronunciation and overlap between the target and distractor labels over development, but age did not influence sensitivity to mispronunciation size, mispronunciation position, and distractor familiarity.
 Finally, in some cases there was evidence that older and younger infants were given experimental manipulations that may have rendered the experimental task more or less difficult.
@@
 Such a scenario could explain the publication bias suggested by the asymmetry for correct pronunciations in the funnel plot shown in Figure \@ref(fig:FunnelCombo) [@Simmons2011].
-This could lead to an increase in significant results and even alter the developmental trajectory of mispronunciation sensitivity.
+This could lead to an increase in significant results and even alter the apparent developmental trajectory of mispronunciation sensitivity measured in experiments.
 
@@
 
-```{r PlotPostNameCondAge, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different lengths of the post-naming analysis window: 2000 ms or less (orange), 2001 to 3000 ms (blue), and 3001 ms or greater (green).
+```{r PlotPostNameCondAge, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different lengths of the post-naming analysis window: 2000 ms or less (yellow), 2001 to 3000 ms (blue), and 3001 ms or greater (pink).
 Although length of the post-naming analysis window was included as a continuous variable in the meta-analytic model, it is divided into categories for ease of viewing.
@@
   jpeg(filename = "figures/Figure_10_Post_name_size.jpg", 
-       width = 600, height = 600, units = "px")
+       width = 600, height = 800, units = "px")
 
@@
 
-```{r PlotWithinCondDVbaseline, echo = FALSE, fig.width=7,fig.height=3.5, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (orange), Post vs.
-Pre (blue), and Difference Score (green).
+```{r PlotWithinCondDVbaseline, echo = FALSE, fig.width=7,fig.height=3.5, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (yellow), Post vs.
+Pre (blue), and Difference Score (pink).
 Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity, within subject group and study (correct - mispronunciations), as a function of age.
@@
   #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
-  scale_fill_grey(start = 0.5)+
+  #scale_fill_grey(start = 0.5)+
+    scale_fill_manual(values=cbPalette)+
   apatheme +
@@
 We note, however, that despite an increasing publication record of mispronunciation sensitivity studies, fewer than half of the papers included in this meta-analysis measured vocabulary (*n* = `r with(vi2, papers[has_vocab == "vocab"])`; out of `r n_distinct(dat$short_cite)` papers total; see also Figure \@ref(fig:Vocabdescribe1)).
-This may reflect a decreasing interest in the relationship between mispronunciation sensitivity and vocabulary size and/or to invest in data collection that is not expected to yield significant outcomes.
-Considering the theoretical implications, however, more experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size is needed if this link is to be evaluated.
+On the one hand, this may reflect a decreasing interest in the relationship between mispronunciation sensitivity and vocabulary size and/or to invest in data collection that is not expected to yield significant outcomes.
+On the other hand, non-significant correlations between mispronunciation sensitivity and vocabulary size may be more likely to not be reported, reducing our ability to uncover the true relationship [@Rosenthal1979; @pcurve].
+Considering the theoretical implications, however, more experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size, whether the relationship is significant or not, is needed if this link is to be evaluated.
+We encourage researchers to measure and report infants' vocabulary size in future studies.
 Nonetheless, if we are to take our results as robust, it becomes thus a pressing open question that theories have to answer which other factors might prompt acquiring and using language-specific phonological contrasts at such an early age.
@@
 More studies are needed to evaluate whether this gradual sensitivity develops with age, as only one study examined more than one age [@Mani2011] and all others test the same age with a varying number of features [@Bernier2017; @Tamasi2016; @White2008].
-With more studies investigating graded sensitivity at multiple ages with all other facturs held constant, we would achieve a better estimate of whether this is a stable or developing ability, thus also shedding more light on the progression of phono-lexical development in general that then needs to be captured in theories and models.
+With more studies investigating graded sensitivity at multiple ages with all other factors held constant, we would achieve a better estimate of whether this is a stable or developing ability, thus also shedding more light on the progression of phono-lexical development in general that then needs to be captured in theories and models.
 
@@
 Yet, no studies have directly examined this assertion and our meta-analysis found that distractor familiarity did not significantly modulate mispronunciation sensitivity.
+One possible explanation is that when the size of the mispronunciation is small (e.g.
+1-feature change), infants are unlikely to map this label onto a novel object [for evidence from infant word learning see @Dautriche2015; @Swingley2007; @Swingley2016].
 
@@
 
-Contrary to predictions made from the literature, our meta-analysis revealed that studies which include target and distractor images that overlap in their onset elicit greater mispronunciation sensitivity than studies who do not control for this factor.
+Contrary to predictions made from the literature, our meta-analysis revealed that studies which include target and distractor images that overlap in their onset elicit greater mispronunciation sensitivity than studies in which these labels do not overlap.
 Perhaps including overlap leads infants to pay more attention to mispronunciations, increasing mispronunciation sensitivity.
@@
 We found wide variation in the post-naming analysis window which correlated negatively with infant age and influenced the estimate of mispronunciation sensitivity.
-Looks to the target in response to mispronunciations may be slower than in response to correct pronunciations in infants [as predicted by TRACE, @Mayor2014], and those studies with longer post-naming analysis windows allow fixations to accumulate even in the presence of mispronunciations, thereby reducing the measured sensitivity to mispronunciations.
+Looks to the target in response to mispronunciations may be slower than in response to correct pronunciations in infants [@Swingley2000; @Mayor2014], and those studies with longer post-naming analysis windows allow fixations to accumulate even in the presence of mispronunciations, thereby reducing the measured sensitivity to mispronunciations.
 In fact, the exact dynamics of fixations to mispronunciations (overall flattened versus delayed) are an ongoing topic of discussion.
@@
 
-A lack of a field standards can have serious consequences, as our analyses show, limiting our ability to draw conclusions.
+Variation in measurement standards can have serious consequences, as our analyses show, limiting our ability to draw conclusions.
 We take this opportunity to make several recommendations to address the issue of varying, potentially post hoc analysis decisions.
@@
 This allows for a more detailed assessment of infants' fixations over time and removes the need to reduce the post-naming analysis window.
-Both Growth Curve Analysis [@Mirman2008] and Permutation Clusters Analysis [@VonHolzen2012; @Maris2007] offer potential solutions to analyze the full time course.
+Both Growth Curve Analysis [@Mirman2008] and Permutation Clusters Analysis [@VonHolzen2012; @Maris2007] offer potential solutions to analyze the full time course [although Growth Curve Analyses are not without criticism, see @Huang2020].
 Third, it may be useful to establish standard analysis pipelines for mispronunciation studies.
 This would allow for a more uniform analysis of this phenomenon, as well as aid experimenters in future research planning [see @MB1 for a parallel effort].
+As mentioned previously, one example of standardization would be for all experimenters to measure and report vocabulary size.
 We hope the above suggestions take us one step closer to this important goal that clarifies the link between internal abilities and behavior in a laboratory study.
@@
 # References
-```{r create_r-references}
-r_refs(file = "MISP_MA_BIB.bib")
-```
 
@@
 
-<div id = "refs"></div>
+<div id="refs" custom-style="Bibliography"></div>
 \endgroup

### 2020-09-24 scripts/starter_functions.R

@@ -43,7 +43,9 @@ apatheme=theme_bw()+
         text=element_text(family='Times', size=25))
 
 # Color Blind palette:
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+cbPalette <- c("#F0E442","#0072B2","#CC79A7", "#E69F00", "#999999", "#56B4E9", "#009E73", "#0072B2", "#D55E00")
+
+
 
 get_legend<-function(myggplot){
   tmp <- ggplot_gtable(ggplot_build(myggplot))

### 2020-11-10 VonHolzenBergmann_MPMetaAnalysis.Rmd
acceptance!

@@
   - name          : "Christina Bergmann"
-    affiliation   : "4,5"
+    affiliation   : "4,5, 6"
 
@@
   - id            : "1"
-    institution   : "Lehrstuhl Linguistik des Deutschen, Schwerpunkt Deutsch als Fremdsprache/Deutsch als Zweitsprache, Technische Universität Dortmund"
+    institution   : "Lehrstuhl Linguistik des Deutschen, Schwerpunkt Deutsch als Fremdsprache/Deutsch als Zweitsprache, Technische Universität Dortmund, Germany"
   - id            : "2"
@@
   - id            : "3"
-    institution   : "Laboratoire Psychologie de la Perception, Université Paris Descartes"
+    institution   : "Université Paris Descartes, Sorbonne Paris Cité, Paris, France"
   - id            : "4"
+    institution   : "CNRS (Integrative Neuroscience and Cognition Center, UMR 8002), Paris, France"   
+  - id            : "5"
     institution   : "Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands"
-  - id            : "5"
-    institution   : "LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University"
+  - id            : "6"
+    institution   : "Laboratoire de Sciences Cognitives et de Psycholinguistique, Département d’études cognitives, ENS, EHESS, CNRS, PSL University"
 
 authornote: |
+  The authors would like to thank Emelyne Gaudichau for valuable assistance in entering data.
+The data, analysis scripts, and RMarkdown file used in this study to create this manuscript are available on the Open Science Framework (Von Holzen & Bergmann, 2019; https://osf.io/rvbjs/).
+Katie Von Holzen was supported by the Agence Nationale de la Recherche (ANR-13-BSH2-0004) and by training grant DC-00046 from the National Institute of Deafness and Communicative Disorders of the National Institutes of Health.
+Christina Bergmann was supported by H2020 European Research Council Marie Skłodowska-Curie grant No 660911; the Département d'Etudes Cognitives (DEC)  ANR-17-EURE-0017, the Berkeley Initiative for Transparency in the Social Sciences, a program of the Center for Effective Global Action (CEGA), with support from the Laura and John Arnold Foundation.
 The authors each declare that they have no conflict of interest.
@@
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)
-
-# removing authornote for now to save space
-
-# authornote: |
-#   The authors would like to thank Emelyne Gaudichau for valuable assistance in entering data.
-Author 1 was supported by the Agence Nationale de la Recherche (ANR-13-BSH2-0004) and by training grant DC-00046 from the National Institute of Deafness and Communicative Disorders of the National Institutes of Health.
-Author 2 was supported by the European Horizon 2020 programme (Marie Skłodowska-Curie grant No 660911), the Agence Nationale de la Recherche (ANR-10-IDEX-0001-02 PSL*, ANR-10-LABX-0087 IEC) and the Fondation de France.
-The authors each declare that they have no conflict of interest.
 
@@
 
+---
+nocite: | 
+  @VonHolzen2019
+...
+
 ```{r ReadIn}
@@
 1-feature, 2-features, 3-features), finding that infants are more sensitive to larger mispronunciations (3-feature-changes) than smaller mispronunciations (1-feature changes) for both consonant [@White2008; @Bernier2017; @Tamasi2016] and vowel [@Mani2011] mispronunciations, known as graded sensitivity.
-By aggregating studies testing infants of different ages on mispronunciations of varying size, this also has consequences for understanding whether graded sensitivity changes over development.
+By aggregating studies testing infants of different ages on mispronunciations of varying size, this also has consequences for identifying any graded sensitivity changes over development.
 
@@
   jpeg(filename = "figures/Figure_4_Vocab_findings.jpg", 
-       width = 500, height = 300, units = "px")
+       width = 550, height = 300, units = "px")
 
@@
 Such a scenario could explain the publication bias suggested by the asymmetry for correct pronunciations in the funnel plot shown in Figure \@ref(fig:FunnelCombo) [@Simmons2011].
-This could lead to an increase in significant results and even alter the apparent developmental trajectory of mispronunciation sensitivity measured in experiments.
+This could lead to an increase in significant results and even alter the measured developmental trajectory of mispronunciation sensitivity measured in experiments.
 
@@
 On the other hand, non-significant correlations between mispronunciation sensitivity and vocabulary size may be more likely to not be reported, reducing our ability to uncover the true relationship [@Rosenthal1979; @pcurve].
-Considering the theoretical implications, however, more experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size, whether the relationship is significant or not, is needed if this link is to be evaluated.
+Considering the theoretical importance of infants' vocabulary size, however, more experimental work investigating and reporting the relationship between mispronunciation sensitivity and vocabulary size, whether the relationship is significant or not, is needed if this link is to be evaluated.
 We encourage researchers to measure and report infants' vocabulary size in future studies.
@@
 One possible explanation is that when the size of the mispronunciation is small (e.g.
-1-feature change), infants are unlikely to map this label onto a novel object [for evidence from infant word learning see @Dautriche2015; @Swingley2007; @Swingley2016].
+1-feature change), infants are unlikely to map this label onto a novel object and even seem to be biased against doing so [for evidence from infant word learning see @Dautriche2015; @Swingley2007; @Swingley2016].
 
@@
 This allows for a more detailed assessment of infants' fixations over time and removes the need to reduce the post-naming analysis window.
-Both Growth Curve Analysis [@Mirman2008] and Permutation Clusters Analysis [@VonHolzen2012; @Maris2007] offer potential solutions to analyze the full time course [although Growth Curve Analyses are not without criticism, see @Huang2020].
+Both Growth Curve Analysis [@Mirman2008] and Cluster Permutation Analysis [@VonHolzen2012; @Maris2007] offer potential solutions to analyze the full time course [although Growth Curve Analyses are not without criticism, see @Huang2020].
 Third, it may be useful to establish standard analysis pipelines for mispronunciation studies.

### 2020-12-08 VonHolzenBergmann_MPMetaAnalysis.Rmd
final proofs

@@
 From this combined list of 398 records we removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech.
-The final sample (*n* = `r length(unique(descriptive_dat$short_cite))`) consisted of `r with(descriptive_dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "dissertation"]))` theses, and `r with(descriptive_dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports.
+The final sample (*n* = `r length(unique(descriptive_dat$short_cite))`) consisted of `r with(descriptive_dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "dissertation"]))` theses, and `r with(descriptive_dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished report.
 We will refer to these items collectively as papers.
@@
   jpeg(filename = "figures/Figure_2_Funnel_Plots_Object_Identification.jpg", 
-       width = 600, height = 400, units = "px")
+       width = 1600, height = 800, units = "px", res = 300)
 
@@
 
-```{r PlotMPEffect, echo = FALSE, fig.width=7,fig.height=8, fig.cap="Panel a: Effect sizes for correct pronunciations (yellow) and mispronunciations (blue) by participant age.
+```{r PlotMPEffect, echo = FALSE, fig.width=7,fig.height=8, fig.cap="Panel a: Effect sizes for correct pronunciations (light orange, light grey) and mispronunciations (dark purple, black) by participant age.
 Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) by participant age.
@@
   jpeg(filename = "figures/Figure_3_AgeEffect.jpg", 
-       width = 500, height = 900, units = "px")
+       width = 1450, height = 1800, units = "px", res = 300)
 
@@
 
-```{r Vocabdescribe1, echo = FALSE, fig.width=7,fig.height=4.5, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (yellow), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (pink).", results="hide"}
+```{r Vocabdescribe1, echo = FALSE, fig.width=7,fig.height=4.5, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (light orange, light grey), did measure vocabulary and was reported to predict mispronunciation sensitivity (dark purple, black), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (dark orange, dark grey).", results="hide"}
 #how did vocabulary collection change over time?
@@
   jpeg(filename = "figures/Figure_4_Vocab_findings.jpg", 
-       width = 550, height = 300, units = "px")
+       width = 2200, height = 1200, units = "px", res = 300)
 
@@
   jpeg(filename = "figures/Figure_5_Number_of_Features.jpg", 
-       width = 500, height = 300, units = "px")
+       width = 1800, height = 1200, units = "px", res = 300)
 
@@
   jpeg(filename = "figures/Figure_6_Misp_Position.jpg", 
-       width = 500, height = 300, units = "px")
+       width = 1800, height = 1200, units = "px", res = 300)
 
@@
 ```{r PlotMispType, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations.
-Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations by age.
+Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant (light orange, light grey) and vowel (dark purple, black) mispronunciations by age.
 For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
@@
   jpeg(filename = "figures/Figure_7_CV.jpg",
-       width = 500, height = 800, units = "px")
+       width = 1450, height = 1800, units = "px", res = 300)
 
@@
 ```{r PlotCVEffectLang, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language.
-Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations for infants learning a Germanic (left) or a Romance (right) native language by age.
+Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant (light orange, light grey) and vowel (dark purple, black) mispronunciations for infants learning a Germanic (left) or a Romance (right) native language by age.
 For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
@@
   jpeg(filename = "figures/Figure_8_LangCV.jpg",
-       width = 500, height = 900, units = "px")
+       width = 1450, height = 2200, units = "px", res = 300)
 
@@
 ```{r PlotDistOverlap, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for target-distractor pairs with onset overlap or no overlap.
-Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for target-distractor pairs with onset overlap or no overlap by age.
+Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for target-distractor pairs with onset overlap (dark purple, black) or no overlap (light orange, light grey) by age.
 For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}
@@
   jpeg(filename = "figures/Figure_9_Distractor_Overlap.jpg",
-       width = 500, height = 800, units = "px")
+       width = 1600, height = 1800, units = "px", res = 300)
 
@@
 
-```{r PlotPostNameCondAge, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different lengths of the post-naming analysis window: 2000 ms or less (yellow), 2001 to 3000 ms (blue), and 3001 ms or greater (pink).
+```{r PlotPostNameCondAge, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different lengths of the post-naming analysis window: 2000 ms or less (light orange, light grey), 2001 to 3000 ms (dark purple, black), and 3001 ms or greater (dark orange, dark grey).
 Although length of the post-naming analysis window was included as a continuous variable in the meta-analytic model, it is divided into categories for ease of viewing.
@@
 dat$condition_label <- ifelse(dat$condition==1, "Correct", "Mispronunciation")
-dat$post_size <- ifelse(dat$post_nam_dur <= 2, "2000 ms or less",
-                       ifelse(dat$post_nam_dur > 2 & dat$post_nam_dur <= 3, "2001-3000 ms", "3001 ms or greater"))
-dat$post_size <- factor(dat$post_size, levels = c("2000 ms or less", "2001-3000 ms", "3001 ms or greater"))
+dat$post_size <- ifelse(dat$post_nam_dur <= 2, "< 2000 ms",
+                       ifelse(dat$post_nam_dur > 2 & dat$post_nam_dur <= 3, "2001-3000 ms", "> 3001 ms"))
+dat$post_size <- factor(dat$post_size, levels = c("< 2000 ms", "2001-3000 ms", "> 3001 ms"))
 dat.cm <- dat[,c("short_cite", "is_correct", "is_mp", "post_size", "condition", "g_calc", "weights_g", "mean_age_1", "n_1")]
@@
   jpeg(filename = "figures/Figure_10_Post_name_size.jpg", 
-       width = 600, height = 800, units = "px")
+       width = 2200, height = 2200, units = "px", res = 300)
 
@@
 
-```{r PlotWithinCondDVbaseline, echo = FALSE, fig.width=7,fig.height=3.5, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (yellow), Post vs.
-Pre (blue), and Difference Score (pink).
+```{r PlotWithinCondDVbaseline, echo = FALSE, fig.width=7,fig.height=3.5, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (light orange, light grey) and Baseline corrected (dark purple, black).
 Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity, within subject group and study (correct - mispronunciations), as a function of age.
@@
   jpeg(filename = "figures/Figure_11_Dependent_variable.jpg", 
-       width = 500, height = 350, units = "px")
+       width = 1800, height = 1200, units = "px", res = 300)
 
@@
 
+---
+nocite: |
+  @Ren, @Bergelson2017, @DelleLuche2015, @Durrant2014, @Hohle2006, @Swingley2003, @Tao2013, @Tao2012, @VanderFeest2016, @Wewalaarachchi2017, @White2011a, @Zesiger2011
+---
+
 \newpage

### 2020-12-08 scripts/starter_functions.R

@@ -43,8 +43,10 @@ apatheme=theme_bw()+
         text=element_text(family='Times', size=25))
 
 # Color Blind palette:
-cbPalette <- c("#F0E442","#0072B2","#CC79A7", "#E69F00", "#999999", "#56B4E9", "#009E73", "#0072B2", "#D55E00")
+# cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73",
+#                "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
 
+cbPalette <- c("#fdb863", "#5e3c99", "#e66101", "#b2abd2")
 
 
 get_legend<-function(myggplot){
